### 2023-01-10 main.tex
file copied from overleaf

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\numberwithin{equation}{section}

\usepackage[textsize=tiny]{todonotes}

% \usepackage[notref,notcite]{showkeys}
\usepackage{xspace}
\usepackage{bibentry}
\usepackage{easybmat}

\usepackage{graphicx}

\usepackage{subcaption}

\usepackage[numbers,sort&compress]{natbib}
\usepackage{hypernat}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
% MACROS
% % 
% \newcommand{\cristian}[1]{{\bf (* {\color{ForestGreen}V:{} \small #1}*)}}
% \newcommand{\jorge}[1]{{\bf (* {\color{BlueViolet}G:{} \small #1}*)}}
% \newcommand{\rouven}[1]{{ (* {\color{red}{} \small #1}*)}}

\frenchspacing

\newcommand{\changelocaltocdepth}[1]{%
  \addtocontents{toc}{\protect\setcounter{tocdepth}{#1}}%
  \setcounter{tocdepth}{#1}%
}
\newcommand{\id}{I}
\newcommand{\Xt}{\tilde{X}}

\newcommand{\len}{L}
\newcommand{\spe}{N}

\setcounter{tocdepth}{2}

\usepackage[margin=2.5cm]{geometry}

%%%%%  oscillators
\newcommand{\osc}[1]{\mathbf{#1}}
\newcommand{\oscgreek}[1]{\boldsymbol{#1}}
\newcommand{\dagg}[1]{\bar{#1}}
\newcommand{\ep}{\epsilon}
\newcommand{\ob}{\osc{b}}
\newcommand{\oc}{\osc{c}}
\newcommand{\od}{\osc{d}}
\newcommand{\oab}{\dagg{\osc{a}}}
\newcommand{\obb}{\dagg{\osc{b}}}
\newcommand{\ocb}{\dagg{\osc{c}}}
\newcommand{\odb}{\dagg{\osc{d}}}
\newcommand{\ox}{\oscgreek{\xi}}
\newcommand{\oxb}{\dagg{\oscgreek{\xi}}}
\newcommand{\och}{\oscgreek{\chi}}
\newcommand{\ochb}{\dagg{\oscgreek{\chi}}}
\newcommand{\NN}{\mathbf{N}}
\newcommand{\ccc}{\mathbf{C}}
\newcommand{\qop}{Q}
\newcommand{\sop}{Y}
\newcommand{\q}{\mathbf{\epsilon}}
\newcommand{\ID}{I}
\newcommand{\per}{P}

\newcommand{\EE}{\mathrm{E}}

\newmuskip\pFqmuskip

\newcommand*\pFq[6][8]{%
  \begingroup % only local assignments
  \pFqmuskip=#1mu\relax
  \mathchardef\normalcomma=\mathcode`,
  % make the comma math active
  \mathcode`\,=\string"8000
  % and define it to be \pFqcomma
  \begingroup\lccode`\~=`\,
  \lowercase{\endgroup\let~}\pFqcomma
  % typeset the formula
  {}_{#2}\phi_{#3}{\left[\genfrac..{0pt}{}{#4}{#5};#6\right]}%
  \endgroup
}
\newcommand{\pFqcomma}{{\normalcomma}\mskip\pFqmuskip}

\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Li}{Li}
\DeclareMathOperator{\diag}{diag}

\newcommand{\KL}{\mathcal{K}}
\newcommand{\KR}{\hat{\mathcal{K}}}
\newcommand{\oa}{\mathbf{a}}

\newcommand{\oad}{\mathbf{a}^{\dagger}}

\newcommand{\phil}{\beta_-}
\newcommand{\phir}{\beta_+}
\newcommand{\ma}{n}

\newcommand{\oaq}{\mathbf{a}_\q}

\newcommand{\oadq}{\mathbf{\bar{a}}_\q}

\newcommand{\N}{\mathbf{N}}
\newcommand{\twoj}{\nu}

\begin{document}

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
\bf Stirring process
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
% {Rouven Frassek}
 \par\endgroup
\vspace{2em}

\begingroup\sffamily 
%  
% Università degli Studi di Modena e Reggio Emilia
%University of Modena and Reggio Emilia, 
%\\Department of Physics, Informatics and Mathematics,\\
%Via G. Campi 213/b, 41125 Modena, Italy\\ 
\par\endgroup
\vspace{2em}

 Version: \today
\end{center}
%

\thispagestyle{empty}

\begin{abstract}
\noindent
....
\end{abstract}

%\vfill

\tableofcontents

% \newpage

\section{Introduction} 
In the past years duality has been developed to study stochastic processes, especially in the boundary driven case, i.e. when the system is put in contact with boundaries that generate a non-equilibrium current. The literature is huge. We can address , for instance, to \cite{giardina2009duality,carinci2013duality,frassek2020duality}. One application of duality is the attempt to characterize the non equilibrium steady state of boundary driven process via the so called absorption probabilities. Indeed, there are many cases where the dual process has absorbing boundaries. This means that the the chain is eventually empty in the long time scale. Moreover, there are cases in which the steady state of a stochastic process can be computed explicitly, thanks to the integrability property of the system (quantum inverse scattering method, matrix product ansatz). In this direction, some examples can be found in \cite{derrida1993exact,frassek2019non,frassek2020eigenstates}. In the past, the focus has been on processes where one can distinguish, in each site of a certain graph, a (or many) particles or an empty state. However, this particles are indistinguishable, in the sense that you can pile up in a site just one type of particles. Some natural questions arise: what happens if we imagine to assign different colours to the particles? Is the duality property still holding? How far can we push our analysis for the characterization of the non equilibrium steady state?\\
The way one can define a multi-type (or multi-species) interacting particle system is not unique. In the literature there are many. Two of them are the following. On one hand, the \textit{multi-layer models}, in which the process is constructed on a many layer graph where each graph correspond to a type and perform a kind of dynamic (independent jump, exclusion/inclusion walkers) and the layers communicate each other with some "switching probabilities". The state space of the Markov process is the Cartesian product of the state spaces of each layer, i.e. of the two species. For example see \cite{floreani2022switching,redig2022ergodic}. On the other hand, the \textit{single layer models}. Here, there is just one layer, where particles of each type can pile up, in a way that the exclusion dynamic concerns many species together. In other words, now the species can interact "directly", not just by switching layer. Here the state space contains all the species and it is not product anymore. Some examples of such a dynamic can be found in \cite{casini2022uphill,vanicat2017exact,zhou2021orthogonal}. \\
In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e. a dynamic in which a maximum amount of particles can be present in each site at each time. We will call this amount, the "maximal occupancy" and it will indicated with $\twoj$ where $\twoj\in\mathbb{N}$. Particle of any species can exchange their position in the graph, under this exclusion constraint. The system will be put out of equilibrium and some absorbing duality result are investigated. Moreover, we will use this duality, to study the out of equilibrium steady state. In particular, in case of $\twoj=1$ we should retrieve the model studied in \cite{vanicat2017exact}. We will then exploit this last result and the duality, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 
\paragraph{Organization of the paper}
\section{The stirring process}
We consider the stirring process with an arbitrary number of particles $N$. It is important to note that any one of them can be considered the empty (or hole) particle. Thus, in this first general setting we do not distinguish between real and empty particles. However, this distinction will be useful in the section about duality, where we will see that this empty will play a special role. The stochastic dynamics is Markovian and consist in an exchange of particles of any type between two connected site of a graph. \\
\subsection{The infinitesimal generator}
Let's consider a connected and undirected graph $G=(V,\mathcal{E})$ where $x\in V$ denotes the set of vertex and $\mathcal{E}$ denotes the set of edges $(x,y)$ with $x,y\in V$.  The process has a repulsive nature, thus the state space must contain informations about this maximal occupancy. Then we define 
\begin{equation}\label{stateSpace}
    \Omega:=\left\{n=(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; |n|=\twoj\right\}^{|V|}
\end{equation}
where $|n|=\sum_{k=1}^{N}n_{k}$ denotes the total number of particles per site and $|V|$  the total number of vertices. At each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k$, under the constraint that the total number of particle in the site is $\twoj$. \\
The dynamic consists in an exchange of particles between connected vertex. Moreover, each vertex can be connected with a reservoir that inject, remove or exchange particles. Mathematically, this can be described by an infinitesimal generator as follows
\begin{equation}\label{Generator}
    \mathcal{L}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}
\end{equation}
where the quantities $ \omega_{x,y}$ are called conductancies and $\Gamma_{x}$ local inhomogeneities. The generator $\mathcal{L}_{x,y}$ is called the \textit{edge generator}, while $\mathcal{L}_{x}$ is called the \textit{site generator}. These linear operators act on local functions $f:\Omega\to \mathbb{R}$ as follows
\begin{equation}
\mathcal{L}_{x,y}f(n)=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(n-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(n)\right]
\end{equation}
\begin{equation}
    \mathcal{L}_{x}f(n)=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(n+\delta_{k}^{x}-\delta_{l}^{x})-f(n)\right]
\end{equation}
where 
$\delta_{k}^{x}=(0,\ldots,0,1,0,\ldots,0)$ withe the one in the $k$-th position. This means that the edge generator exchanges a particle of type $k$ in the site $x$ with a particle of type $l$ in the site $y$, while the site generator inject a particle of type $k$ and remove a particle of type $l$, both in the site $x$. The following Figure \ref{fig:1}, Figure \ref{fig:2} help in understanding the dynamics. 
\begin{figure}
    \centering
    \includegraphics[scale=0.6]{Dyn_stir.eps}
    \caption{The edge dynamics}
    \label{fig:1}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[scale=0.88]{Dyn_stir_bordo.eps}
    \caption{The site dynamics}
    \label{fig:2}
\end{figure}\newline \\
\textbf{Remark}: 
    We can always assign the name "empty" to one of the species of particles in the above dynamics (let's say, without loss of generality, the species 1). This species would play the role of "compensator" in the exclusion constraint, in the sense that its occupation will always be determined once we know the others, i.e. $\forall x\in V$: 
    \begin{equation}
        n_{1}^{x}=\twoj-\sum_{k=2}^{N}n_{k}^{x}
    \end{equation}
    Moreover, if we set $N=2$ and $\twoj=2j$, we exactly retrieve the SEP(2j), where the empty occupation is indeed $2j-\eta_{x}$ where $\eta_{x}$ is the number of (color blind) particles in the site $x$. In this sense we can think about the stirring process as the natural generalization of the SEP(2j).
    \begin{flushright}
        $\square$
    \end{flushright}
The process described by \eqref{Generator} is reversible if and only if, for any $k\in\{1,\ldots,N\}$, the boundary parameters $\alpha_{k}^{x}=\alpha_{k}$ $\forall x\in V$. The reversible product measure is a Multinuomial distribution of parameter $\twoj$. That means that 
\begin{equation}\label{reversibleMeasure}
    \mu^{rev}=\bigotimes_{x\in V}\mu^{rev}_{x}\qquad \mu_{x}^{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad :\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
\end{equation}
This can be proven just by imposing the detailed balance conditions for the edge and for the site generators. Let us notice that the reversible measure is product only over the sites, but not over the species. This is due to the exclusion constraint that makes particle interact.

{\color{red}[LET'S SKIP THE PROOF? I THINK IT IS STANDARD!]}.\\
\subsection{The Lie algebraic description}

%The approach we use to find duality relations is the Lie algebraic one. The main idea is to describe the infinitesimal generator (or better, its transposed, i.e. the Hamiltonian operator) via a proper combination of the basis of a certain Lie algebra. Then, duality will be found by symmetry argument.\\

Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{a,b}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ with $\lambda_i\in \mathbb{N}$ and  $\lambda_i\geq \lambda_{i+1}$.
We are interested in the symmetric finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition:
\begin{equation}
	D= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space of the representation $\mathbb{C}^{D}$ are denoted by 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle\qquad \forall
    n=(n_{1},\ldots,n_{N})
\end{equation}
$\forall n=(n_{1},\ldots,n_{N})\in \chi$ where $\chi:=\left\{n:|n|=\twoj\right\}$ {\color{red}(let us notice that $\Omega=\chi^{|V|}$)?}. This vector can be mapped in a one-to-one correspondence with the canonical basis of $\mathbb{C}^{D}$. This basis vector satisfy the orthogonality relation
\begin{equation}\label{ortho}
    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|=| m_{1},\ldots,m_{N}\rangle^T$.

The explicit actions of the basis element of the algebra on the vectors of the space $\mathbb{C}^{D}$ are the following, for non Cartan and Cartan elements respectively: 
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle
	\end{cases}\qquad \forall a,b\in\{1,\ldots,N\}
\end{equation}  
One can check that the generators defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.

We now define the equivalent of \eqref{stateSpace} in the vector notation
 \begin{equation}
	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
	\end{equation}
where we denote 
\begin{equation}
|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)\in \Omega'
\end{equation}
such that
\begin{equation}
    \langle {\bf n}|{\bf m}\rangle =\prod_{x=1}^L\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
\end{equation}

When the state space is discrete, it is useful to write the dynamics of the process in term of an other operator, the Hamiltonian. The relation between these two operator is the following
\begin{equation}
H=\mathcal{L}^{T}
\end{equation}

Following  \cite{belitsky2015self} we define
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {\bf n}}f( {\bf n})\langle  {\bf n}|
\end{equation}

The Hamiltonian operator can be written in term of the basis element of the Lie algebra as

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{k,l=1}^{N}\left(E_{kl}\otimes E_{lk}-E_{ll}\otimes E_{kk}\right)_{x,y}
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}-E_{ll}\right)_x
\end{equation}

Moreover, by the \eqref{coproductC2} and by computing the explicit action of the diagonal part, we can write this Hamiltonian in function of the coproduct of the second Casimir
\begin{equation}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
It reads
\begin{equation}
	H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left\{\frac{1}{2}\Delta(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}\otimes\mathbbm{1}\right\}+\sum_{x\in V}\Gamma_{x}\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{k,l}-\twoj\mathbbm{1}\right)
\end{equation}
Here we introduced the standard coproduct $\Delta:E_{ab}\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}$ and used that $C_{2}=\twoj(\twoj+N)$.

\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}

\section{Duality}
Consider two Markov processes $(\eta_{t})_{t\geq 0}$ on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in \Omega$, $\forall \xi\in \widetilde{\Omega}$ and $\forall t\geq 0$ we have 
\begin{equation}
    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t}\right]
\end{equation}
Moreover, if $\eta_{t}$ and $\xi_{t}$ are the same process, we talk about \textit{self-duality} and \textit{self-duality function}. The duality property can also be characterized by a relation with the generators. Let $\mathcal{L}$ be the generator of $\eta_{t}$ and let $\mathcal{L}_{dual}$ be the generator of $\xi_{t}$, then we say that two process are in a duality relation if 
\begin{equation}
    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\mathcal{L}_{dual}D(\eta,\cdot)\right)(\xi)
\end{equation}
\subsection{Algebraic formulation}
In particular, if the process has a countable space, the duality is a matrix, and we can rewrite the above relation with the Hamiltonians has follows
\begin{equation}\label{dualityHamiltonian}
    H^{T}D=DH_{dual}
\end{equation}
By \eqref{dualityHamiltonian}, we can see the duality matrix as a similarity transformation between the original and the dual Hamiltonian. \\
We now construct our main result: \textit{the process defined in \eqref{Generator} is self dual with absorbing boundaries}. Thus, we have to construct a duality matrix $D$ and an Hamiltonian $H_{dual}$ in order to fulfill the equation \eqref{dualityHamiltonian}.
\\
The self-dual process is defined in the self-dual state space 
\begin{equation}\widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{|V|}\end{equation} with elements
\begin{equation}
	|\xi\rangle=\bigotimes_{x\in V}\left(|r_{0},\ldots,r_{N}\rangle_{x}\otimes |m_{1}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}\rangle_{x}\right)
\end{equation}
The self-dual Hamiltonian is the following
\begin{equation}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x,\varepsilon(x)}
	\end{split}
\end{equation}
where
\begin{align}
H_{x,y}&=\sum_{k,l=1}^{N}\left(E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}\right)\\
\widetilde{H}_{x,\varepsilon(x)}&=\left(\sum_{i=2}^{N}\alpha_{i}^{x}\right)\sum_{k=2}^{N}\left((a^{\dagger}_{k})_{\varepsilon(x)}E_{1k}^{x}-E_{kk}^{x}\right)
\end{align}
and where  $(a^{\dagger}_{k})_{\varepsilon(x)}$ is a bosonic creation operator acting on an extra site attached to $x$ and denoted by $\varepsilon(x)$. Let us notice that edge part of the dual Hamiltonian is exactly the one of \eqref{edgeHamiltonian} (self-duality). The site part only replace any particle of type $k\in \{2,\ldots,N\}$ with a type $1$  and put them into an extra site, attached to $x$. Dual particles of type $k$ are piled up into an this extra site, and they leave the graph forever. This means that the species $1$ plays a special role in the duality. If we think about this $1$ species as the empty, we can interpret the dual process as an absorbing dual, i.e. a process that eventually empties the graph.\\
Associated with this dual process there is the following duality matrix 
\begin{equation}\label{dualityMatrix}
	D=\prod_{x\in V}\left(\sum_{m_{2}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\alpha_{0}^{x}+\ldots+\alpha_{N}^{x}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{\varepsilon(x)}\otimes R_{x}e^{E}_{x} \right)
	=\prod_{x\in V}\left(D_{\varepsilon(x)}\otimes D_{x}\right)
\end{equation}
where we define the \textit{symmetry operator} as
\begin{equation}\label{e_def}
	E=\sum_{a=2}^{N}e_{a1}
\end{equation}
and the \textit{cheap duality matrix} as 
\begin{equation}
	R^{-1}_{x}=\sum_{n\in \chi}\frac{(2j)!}{n_{1}^{x}!\ldots n_{N}^{x}!}|n_{1},\ldots,n_{N}\rangle_{x}\langle n_{1},\ldots,n_{N}|_{x}%\quad \forall n\in \chi
\end{equation}
Moreover, the element of the matrix \eqref{dualityMatrix} are given by
\begin{equation}\label{dualityElements}
	D(n,\xi)=\langle n|D|\xi\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{(2j)!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\right)
\end{equation}
\subsubsection{Proof of the duality relation}
\textbf{The transposition property of the cheap duality}: \\
This cheap duality matrix has the following \textit{transposition property}:
\begin{equation}\label{transpositionR}
	\left(e_{ba}\right)^{T}=R e_{ab}R^{-1}\quad \forall a,b\in\{0,1,\ldots,N\}
\end{equation}
Indeed, for any configuration $\mathbf{n},\mathbf{r}\in \Omega$, by using \eqref{matrixFormulaE} we obtain
\begin{align*}
	R e_{ab}R^{-1}=&\sum_{r\in\chi}\left(\frac{r_{1}!\ldots r_{N}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots, r_{N}|\right)
	\\&
	\sum_{s\in \chi,}\left(s_{b}|s_{1},\ldots,s_{a}+1,\ldots,s_{b}-1,\ldots s_{N}\rangle \langle s_{1},\ldots,s_{N}|\right)
	\\&
	\sum_{n\in\chi}\left(\frac{(2j)!}{n_{1}!\ldots n_{N}!}|n_{1},\ldots,n_{N}\rangle \langle n_{1},\ldots, n_{N}|\right)=
	\\&
	\sum_{r,n\in \chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle \langle r_{0},\ldots, r_{N}|
	\frac{(2j)!}{n_{1}!\ldots n_{N}!}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|=\diamond
\end{align*}
By using orthogonality relation \eqref{ortho}\begin{align*}
\diamond=&\sum_{r\in \chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}\frac{(2j)!}{r_{1}!\ldots (r_{a}-1)!\ldots(r_{b}+1)!\ldots r_{N}!}(r_{b}+1)|r_{1},\ldots,r_{N}\rangle \langle r_{0},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
	\\=&\sum_{r\in\chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}\frac{(2j)!}{r_{1}!\ldots (r_{a}-1)!\ldots(r_{b}+1)!\ldots r_{N}!}(r_{b}+1)\frac{r_{a}}{r_{a}}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
	\\=&\sum_{r\in \chi}
	r_{a}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
	\\=&
	\left(e_{ba}\right)^{T}
\end{align*}
\textbf{The edge self-duality}\\
The second Casimir $C_{2}$ is a central element of $gl(N)$. Thus, every element of $gl(N)$ is a symmetry of $C_{2}$.
Let's chose the operator $E$ defined in \eqref{e_def}, then $\Delta(E)$ is a symmetry of $\Delta(C_{2})$.
In order to preserve a product structure of the duality matrix, we make the symmetry exponential:
\begin{equation}\label{Simmetry_s}
	S=e^{\Delta(E)}
\end{equation}
By considering two sites $x,y$:
\begin{equation}
	\begin{split}
		S&=e^{\Delta(E)}=e^{(\mathbbm{1}\otimes E+E\otimes \mathbbm{1})}=e^{\mathbbm{1}\otimes E}e^{E\otimes \mathbbm{1}}=\sum_{k=0}^{N}\frac{\left(\mathbbm{1}\otimes E\right)^{k}}{k!}\sum_{j=0}^{N}\frac{\left(E\otimes \mathbbm{1}\right)^{j}}{j!}
		\\&=
		\left(\mathbbm{1}\otimes \sum_{k=0}^{N}\frac{E^{k}}{k!}\right)\left(\sum_{j=0}^{N}\frac{E^{j}}{j!}\otimes \mathbbm{1}\right)=\left(\mathbbm{1}\otimes e^{E}\right)\left(e^{E}\otimes \mathbbm{1}\right)=e^{E}\otimes e^{E}
		\\&=e_{x}^{E} e^{E}_{y}
	\end{split}
\end{equation}
Since the Hamiltonian \eqref{OriginalHamiltonian}, can be written as a linear function of the coproduct of the second Casimir, we have \begin{equation}[H_{x,y},e^{\Delta (C_{2})}]=0\end{equation} and thus \begin{equation}\label{symmetryH-C}[H_{x,y},e^{E}_{x}e^{E}_{y}]=0\end{equation} then the operator \eqref{Simmetry_s} is also a symmetry for the Hamiltonian. 
Since the duality matrix \eqref{dualityMatrix} is product over the vertex of the graph it is enough to prove that $\forall x,y\in \mathcal{E}$:
\begin{align}
	H_{x,y}^{T}D=DH_{x,y}\label{bulkDuality}
\end{align}
For a fixed edge we only have $D_{x}D_{y}$. 
\begin{align*}
	H_{x,y}^{T}D&=D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}H_{x,y}R_{x}^{-1}R_{y}^{-1}R_{x}R_{y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}D_{z}
	\\&=
	D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}H_{x,y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}D_{z}
\end{align*} 
By exploiting \eqref{symmetryH-C}
\begin{align*}
	H_{x,y}^{T}D&=	D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}\otimes D_{z}H_{x,y}=
	DH_{x,y}
\end{align*}
thus (\ref{bulkDuality}) is proved.\\
\textbf{The site absorbing duality}\\
For the sake of notation we remove the superscripts "$x$" from the operators $E_{ab}$ and from the reservoirs densities $\alpha_{k}$. Exploiting again the product form of the duality matrix we can just show that, $\forall x\in V$ the following relation is true 
\begin{equation}\label{boundaryDuality}
    	H_{x}^{T}D=D\widetilde{H}_{x,\varepsilon(x)}
\end{equation}
For the sake of notation and without loss of generality we restrict to the case where $N=3$. \\
The transpose of the single site Hamiltonian reads as
\begin{equation}
	\begin{split}
	H_{x}^{T}&=\sum_{k=1}^{3}\alpha_{k}\left[E_{kl}-E_{ll}\right]^{T}\\&=
	\alpha_{1}\left[E_{12}-E_{22}\right]^{T}+\alpha_{1}\left[E_{13}-E_{33}\right]^{T}+\alpha_{2}\left[E_{21}-E_{11}\right]^{T}\\&+\alpha_{2}\left[E_{23}-E_{33}\right]^{T}+
	\alpha_{3}\left[E_{31}-E_{11}\right]^{T}+\alpha_{3}\left[E_{32}-E_{22}\right]^{T}
	\end{split}
\end{equation}
By multiplying with the single site duality matrix, i.e. $D_{x}=R_{x}e^{E}_{x}$, by using \eqref{transpositionR} and by inserting the identity operator $e^{E}_{x}e^{-E}_{x}$ we obtain 
\begin{equation}\label{transposeRBoundary}
	\begin{split}
	H^{T}_{x}R_{x}e_{x}^{E}&=R_{x}e_{x}^{E}e_{x}^{-E}\left\{\alpha_{1}\left[E_{21}-E_{22}\right]+\alpha_{1}\left[E_{31}-E_{33}\right]+\alpha_{2}\left[E_{12}-E_{11}\right]\right.\\&+\left.\alpha_{2}\left[E_{32}-E_{33}\right]+
	\alpha_{3}\left[E_{13}-E_{11}\right]+\alpha_{3}\left[E_{23}-E_{22}\right]\right\}R^{-1}_{x}R_{x}e^{E}_{x}\\=&
	R_{x}e_{x}^{E}e_{x}^{-E}\left\{\alpha_{1}\left[E_{21}-E_{22}\right]+\alpha_{1}\left[E_{31}-E_{33}\right]+\alpha_{2}\left[E_{12}-E_{11}\right]\right.\\&+\left.\alpha_{2}\left[E_{32}-E_{33}\right]+
	\alpha_{3}\left[E_{13}-E_{11}\right]+\alpha_{3}\left[E_{23}-E_{22}\right]\right\}e^{E}_{x}
	\end{split}
\end{equation}
By the Hadamard's formula:
\begin{equation}
	e^{-E}Ae^{E}=A-\left[E,A\right]+\frac{1}{2!}\left[E,\left[E,A\right]\right]-\frac{1}{3!}\left[E,\left[E,\left[E,A\right]\right]\right]+\ldots
\end{equation}
we obtain 
\begin{equation}
	\begin{split}
	H^{T}_{x}R_{x}e_{x}^{E}&=R_{x}e_{x}^{E}\left\{\alpha_{1}\left(e_{21}-e_{22}-e_{21}\right)+\alpha_{1}\left(e_{31}-e_{33}-e_{31}\right)\right. \\ &+ \left. \alpha_{2}\left(e_{12}-e_{22}+e_{11}-e_{32}-e_{21}-e_{31}-e_{11}+e_{21}+e_{31}\right)+\alpha_{2}\left(e_{32}-e_{31}-e_{33}-e_{31}\right)\right. \\&+\left.
	\alpha_{3}\left(e_{13}-e_{33}-e_{23}+e_{11}-e_{21}-e_{31}-e_{11}+e_{21}+e_{31}\right)+\alpha_{3}\left(e_{23}+e_{21}-e_{22}-e_{21}\right)\right\}
	\end{split}
\end{equation}
then, with simple computations,
\begin{equation}\label{nonStochDuality}
	\begin{split}
	H^{T}_{x}R_{x}e_{x}^{E}&=R_{x}e_{x}^{E}\left\{\alpha_{1}(-E_{22})+\alpha_{1}(-E_{32})+\alpha_{2}(E_{12}-E_{22}-E_{31})\right.\\&+\left. \alpha_{2}(E_{32}-E_{33})+\alpha_{3}(E_{13}-E_{33}-E_{23})+\alpha_{3}(E_{23}-E_{22})\right\}\\&=
	R_{x}e_{x}^{E}\left\{\left(\alpha_{2}E_{12}-(\alpha_{1}+\alpha_{2}+\alpha_{2})E_{22}\right)+\left(\alpha_{3}E_{13}-(\alpha_{1}+\alpha_{2}+\alpha_{3})E_{33}\right)\right\}
	\\&=
	R_{x}e_{x}^{E}(\alpha_{1}+\alpha_{2}+\alpha_{3})\left\{\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}-E_{22}\right)+\left(\frac{\alpha_{3}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{13}-E_{33}\right)\right\}
\end{split}
\end{equation}
We recognize $D_{x}=R_{x}e^{E}_{x}$. However, the matrix that multiplies it in the right hand side of the above equation is not a stochastic matrix. Then, we use the \textit{extra site trick}. 
Let's multiply both sides for 
\begin{equation}
\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|
\end{equation}
we have that the right-hand-side of \eqref{nonStochDuality} becomes
\begin{equation}\label{stepTrick}
\begin{split}
&(\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}-E_{22}\right)
\\+&
(\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{3}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{13}-E_{33}\right)
\end{split}
\end{equation}
Consider the creation operators defined in \eqref{creationOperators}, thus we have
\begin{equation}\label{trick}
	\langle m_{2}+1,m_{3}|a_{2}^{+}=\langle m_{2},m_{3}|\qquad	\langle m_{2}, m_{3}+1|a_{3}^{+}=\langle m_{2},m_{3}|
\end{equation}
Let's consider 
\begin{equation}
    (\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}\right)
\end{equation}
Let's replace the \eqref{trick} in the above quantity, then we have
\begin{equation}
\begin{split}
(\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2}+1,m_{3}|a_{2}^{\dagger}D_{x}\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}\right)
\end{split}
\end{equation}
By shifting the summation indexes 
\begin{equation}\label{trick1}
\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|D_{x}\left[a_{2}^{\dagger}E_{12}\right]
\end{equation}
We can rewrite similarly also the term in \eqref{stepTrick}
\begin{equation}\label{trick2}
    (\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{3}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{13}\right)
\end{equation}
Thus, by putting together \eqref{stepTrick}, \eqref{trick1} and making the same computations for \eqref{trick2} we finally obtain
\begin{equation}
\begin{split}
&\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|D_{x}\left[a_{2}^{\dagger}E_{12}-E_{22}\right]\\ +&
\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|D_{x}\left[a_{x}^{\dagger}E_{13}-E_{33}\right]
\end{split}
\end{equation}
That means 
\begin{equation}
	H^{T}_{x}D=D\widetilde{H}_{x,\varepsilon(x)}
\end{equation}
\textbf{Elements of the dual matrix}\\
We aim to prove \eqref{dualityElements}. Let's first observe that from \eqref{transpositionR}
\begin{equation}
R_{x}e_{x}^{E_{21}+\ldots+E_{N1}}=(e^{E_{12}+\ldots+E_{1N}}_{x})^{T}R_{x}
\end{equation}
let's work for a fixed site $x$
\begin{align*}
	 &\langle n|D_{x}D_{\varepsilon(x)}|\xi\rangle\\&=\langle n_{1},\ldots,n_{N}|_{x}\sum_{m_{1}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{x}
	 \otimes(e_{x}^{E_{12}+\ldots+E_{1N}})^{T}R_{x}\\&|r_{1},\ldots,r_{N}\rangle_{x} \otimes |q_{2},\ldots,q_{N}\rangle_{x}
\end{align*}
The extra-site part is trivial. Indeed by orthogonality relations \eqref{ortho}:
\begin{align*}
&\sum_{m_{2}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=1}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{\varepsilon(x)}|q_{2},\ldots,q_{N}\rangle_{\varepsilon(x)}\\&=
\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}
\end{align*}
 Let us work on the edge part:
\begin{align*}
&\langle n_{1},\ldots,n_{N}|_{x}(e_{x}^{E_{12}+\ldots+E_{1N}})^{T}R_{x}|r_{1},\ldots,r_{N}\rangle_{x}\\&= \langle  n_{1},\ldots,n_{N}|_{x}\left(\sum_{k_{2}=0}^{\infty}\frac{(E_{12}^{T})^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{(E_{1N}^{T})^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{(2j)!}|s_{1},\ldots,s_{N}\rangle_{x}\langle s_{1},\ldots,s_{N}|_{x}\right)|r_{1},\ldots,r_{N}\rangle_{x}=\diamond
\end{align*}
By using the orthogonality relations \eqref{ortho}
\begin{align*}&\diamond=
\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}+k_{2}+\ldots+k_{N},n_{2}-k_{2},\ldots,n_{N}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
\\&\cdot 
\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle_{x}=\star
\end{align*}
Again by the orthogonality relations \eqref{ortho} and by the constraints $n_{1}=2j-\sum_{k=2}^{N}n_{k}$, $r_{1}=2j-\sum_{k=2}^{N}r_{k}$ we finally write
\begin{equation}
\begin{split}
\star=&\frac{(2j-\sum_{k=1}^{N}r_{k}^{x})!r_{2}^{x}!\ldots r_{N }^{x}!}{(2j)!}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{r_{2}^{x}!\ldots r_{N}^{x}!}\frac{1}{(n_{2}^{x}-r_{1}^{x})!\ldots (n_{N}^{x}-r_{N}^{x})!}\\=&
\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{(2j)!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
\end{split}
\end{equation}
By taking the product over $x\in V$ and considering the extra site part we arrive to \eqref{dualityElements}. \newline \\
\textbf{Remark}: it is straightforward to prove that, for every fixed dual configuration $|\xi\rangle \in \widetilde{\Omega}$, the average of the duality matrix  element \eqref{dualityElements} with respect to the reversible measure \eqref{reversibleMeasure} gives 
\begin{equation}
    \mathbb{E}_{n}\left[D(n,\xi)\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\varepsilon(x)}}
\end{equation}
\begin{flushright}
    $\square$
\end{flushright}

\section{Integrability}\label{sec4}
We study the explicit steady state and the exact formulas for the correlations in the case of hard-core interaction ($\twoj=1$), i.e. when at most one particle of any is allowed in each site at any time. We simplify the geometry to a one dimensional chain $\{1,\ldots,L\}$ of length $L$ with boundaries at the ends. We assume a nearest neighbor interaction, i.e. we fix the conductances as follows
\begin{equation}
\omega_{x,y}=\begin{cases}
    1\quad \text{if}\quad |x-y|=1\\
    0\quad \text{otherwise}
\end{cases}
\end{equation}
$\forall x,y\in \{1,\ldots,L\}$.\\
The local inhomogeneities are chosen as follows: $\Gamma_{x}=0$ $\forall x\in \{2,\ldots,L-1\}$ and $\Gamma_{1}=\Gamma_{L}=1$. \\
We can think about the species $1$ as the empty state of the chain. This will be useful in the correlation formula.\\
In this section we will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra). \\
The state space of the chain is 
\begin{equation}
	\Omega=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle\;:\;n\in\mathbb{N}_0^N\;\;|n|=1\right\}^{L}
\end{equation} 
The Hamiltonian is
\begin{equation}\label{hamiltonian}
	H=B_{1}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+B_{L}
\end{equation}
where
\begin{equation}
	\begin{split}
		\mathcal{H}=P-\id
	\end{split}
\end{equation}
with 
\begin{equation}
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}
\end{equation} 
such that
\begin{equation}
	\begin{split}
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle
	\end{split}
\end{equation}
and boundary terms 
\begin{equation}
	B_{1}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\ldots&\alpha_{2}\\
		\vdots&\vdots&\vdots&\vdots\\
		\alpha_{N}&\alpha_{N}&\ldots&\alpha_{N}-1
	\end{pmatrix}
\end{equation}
\begin{equation}
	B_{L}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\ldots&\beta_{2}\\
		\vdots&\vdots&\vdots&\vdots\\
		\beta_{N}&\beta_{N}&\ldots&\beta_{N}-1
	\end{pmatrix}
\end{equation}
where the rates satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=2}^{N}\alpha_{a}=1,\qquad\sum_{a=2}^{N}\beta_{a}=1
\end{equation} 
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=2}^{N}\lambda_{a}=0\,.
\end{equation}
{\color{red} I will add a figure with the boundary driven chain}\\
The steady state can be found by the \textit{matrix product ansatz}, that was introduced for the multispecies hard-core stirring in \cite{vanicat2017exact}. The formulation is the following. We aim to compute $|\Psi\rangle$ such that 
\begin{equation}
	H|\Psi\rangle =0
\end{equation}
The matrix product ansatz tells:
\begin{equation}
	|\Psi\rangle=\frac{1}{Z^{L}}\langle W|\begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}\otimes \ldots\otimes \begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}|V\rangle
\end{equation}
with 
\begin{equation}
	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle
\end{equation}
where $X_{a}$ for $s=1,\ldots,N$ are operators on an auxiliary space $V_{0}$ while $|V\rangle\in V_{0}$ and $\langle W|\in V_{0}^{*}$ (the dual space), such that $\langle W|V\rangle=1$. \\
They fulfill
\begin{equation}\label{bulk}
	\left[X_{a},X_{b}\right]=\lambda_{a}X_{b}-\lambda_{b}X_{a}\qquad\forall a,b=1,\ldots,N
\end{equation}
and
\begin{equation}\label{leftBoundary}
	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle W|\qquad\forall a=1,\ldots,N
\end{equation}
\begin{equation}\label{rightBoundary}
	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-\lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N
\end{equation}
\newline
\textbf{Remark}: Only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
	\begin{equation}
		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle W|
	\end{equation}
	gives $0=0$. Similar computations for the right boundary.\\
 \newline
 The operators defined in \eqref{bulk},\eqref{leftBoundary},\eqref{rightBoundary} are not known explicitly. Via commutation relation is possible to compute some of the correlations. However, it would be interesting to write formulas for arbitrary correlations and the steady state, apart any choice of the form of the operators. \\
 We introduce some similarity transformations for the Hamiltonian \eqref{hamiltonian}. These allow to define two simpler Hamiltonians whose steady state can be  compute exactly. Reversing back the transformation we will obtain the original steady state. \\ 
We first use the \textit{dual similarity transformation}, defined by the symmetry operator \eqref{e_def}.
\begin{equation}
    V=\text{exp}\left(\sum_{a=2}^{N}e_{a1}\right)=e^{E}
\end{equation}
Up to the diagonal matrix $R_{x}$, this is exactly the edge duality matrix. Then, we introduce the Hamiltonian
\begin{equation}
	H_{dual}=B_{1}^{dual}+\mathcal{H}+B_{L}^{dual}
\end{equation}
where 
It is linked to the original one by: 
\begin{equation}\label{uno}
	{H}^{T}V=V{H}_{dual}\quad \Rightarrow \quad {H}=\left(V^{-1}\right)^{T}{H}_{dual}^{T}V^{T}
\end{equation}

We introduce the \textit{S similarity transformation} 
\begin{equation}\label{Esse}
    S=\exp \left(-\sum_{a=2}^N \beta_ae_{a1}\right)\exp \left(\sum_{b=2}^N e_{1b}\right)
\end{equation}
and then the Hamiltonian 
\begin{equation}\label{diagHamiltonian}
    \widetilde{H}=\widetilde{B}_{1}+\mathcal{H}+\widetilde{B}_{L}
\end{equation}
that is linked to the original one by 
\begin{equation}\label{due}
    HS=S\widetilde{H}\quad \Rightarrow \quad {H}=S\widetilde{H}S^{-1}
\end{equation}
This \eqref{diagHamiltonian} has simpler boundary: the left one is lower triangular and the right one is diagonal. The bulk part remains the same. 
Indeed, by applying the similarity transformation \eqref{Esse} to the Hamiltonian we have:
\begin{equation}
	\widetilde{B}_{1}=SB_{1}S^{-1}=\begin{pmatrix}
		0&0&\ldots&0&0\\
		\alpha_{2}-\beta_{2}&-1&\ldots&0&0\\
		\vdots&\vdots&\ddots&\vdots&\vdots\\
		\alpha_{N-1}-\beta_{N-1}&0&\vdots&-1&0\\
		\alpha_{N}-\beta_{N}&0&\vdots&0&-1
	\end{pmatrix}
\end{equation}
\begin{equation}
	\widetilde{B}_{L}=SB_{L}S^{-1}=\begin{pmatrix}
		-1&0&\ldots&0&0\\
		0&-1&\ldots&0&0\\
		\vdots&\vdots&\ddots&\vdots&\vdots\\
		0&0&\vdots&-1&0\\
		0&0&\vdots&0&0
	\end{pmatrix}=e_{NN}-\id
\end{equation}
\begin{equation}
	(S\otimes S)H_{x,x+1}(S\otimes S)^{-1}=H_{x,x+1}
\end{equation}
that also implies that \eqref{Esse} is a symmetry of the bulk part of the Hamiltonian, since  
\begin{equation}
	(S\otimes S)H_{x,x+1}=H_{x,x+1}(S\otimes S)
\end{equation}
The relation with the original Hamiltonian is found by imposing \eqref{uno}=\eqref{due}.
\begin{equation}
	\begin{split}
		\left(V^{-1}\right)^{T}H_{dual}^{T}V^{T}&=S\widetilde{H}S^{-1}\\
		VH_{dual}V^{-1}&=S^{T}\widetilde{H}^{T}\left(S^{-1}\right)^{T}\\
		H_{dual}&=V^{-1}S^{T}\widetilde{H}^{T}\left(S^{-1}\right)^{T}V\\
		H_{dual}&=T^{-1}\widetilde{H}^{T}T
	\end{split}
\end{equation}
where 
\begin{equation}
	T:=\left(S^{-1}\right)^{T}V
\end{equation}
Associated to these new Hamiltonians we can define their steady states: 
\begin{equation}
	H|\Psi\rangle=0\qquad \widetilde{H}|\widetilde{\Psi}\rangle=0\qquad H_{dual}^{T}|\Psi_{ABS}\rangle=0
\end{equation}
that are linked each others as follows
\begin{equation}\label{SteadyStates}
	|\Psi\rangle=\left(S^{-1}\right)^{\otimes L}|\widetilde{\Psi}\rangle\qquad |\Psi\rangle =\left((V^{T})^{-1}\right)^{\otimes L}|\Psi_{ABS}\rangle \qquad |\Psi_{ABS}\rangle=\left(T^{T}\right)^{\otimes L}|\widetilde{\Psi}\rangle
\end{equation}
We can exploit \eqref{SteadyStates}, to compute the steady state of the original Hamiltonian \eqref{hamiltonian}.
\subsection{Absorption probabilities}
\subsubsection*{The steady state of $\widetilde{H}$}
We will show that the steady state $|\widetilde{\Psi}\rangle$ of $\widetilde{H}$ is the following 
\begin{equation}\label{ResulsBasis}
	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}|\mathbf{s}\rangle
\end{equation}
where 
\begin{equation}
    \delta_{s_{i},1}:=\begin{cases}
        1\quad \text{if}\quad s_{i}=1\\
        0\quad \text{otherwise}
    \end{cases}
\end{equation}
and the basis vector $|s\rangle =\bigotimes_{i=1}^{L}|s_{i}\rangle$ with $s_{i}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
\newline
\\
By applying the $S$ to the vector $\left(X_{1},\ldots,X_{N}\right)$ 	we obtain new operators of the matrix product ansatz that can be written as: 
\begin{equation}\label{Xtildes2b}
	\begin{pmatrix}
		\Xt_{1}\\ 
		\Xt_{a}
	\end{pmatrix} =S\begin{pmatrix}
		X_{1}\\X_{a}
	\end{pmatrix}=\begin{pmatrix} 
		X_{1}+\ldots +X_{N}\\
		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\ 
	\end{pmatrix}=\begin{pmatrix} 
		X_{1}+\ldots +X_{N}\\
		X_{a}-\beta_{a}\Xt_{1}\\ 
	\end{pmatrix}\qquad \forall a=2,\ldots N
\end{equation}
we can also reverse the transformation by $S^{-1}$ and get: 
\begin{equation}\label{Xes}
	\begin{pmatrix}
		X_{1}\\
		X_{a} 
	\end{pmatrix} =S^{-1}\begin{pmatrix}
		\widetilde{X}_{1}\\
		\widetilde{X}_{a}
	\end{pmatrix}=\begin{pmatrix}
		\beta_1\Xt_{1}-(\Xt_{2}+\ldots+\Xt_{N})\\
		\Xt_{a}+\beta_{a}\Xt_{1}\\ 
	\end{pmatrix}\qquad\forall a\in \{2,\ldots,N\}
\end{equation}
These new $\widetilde{X}_{a}$ $\forall a\in \{1,\ldots,N\}$ satisfy new commutation relations.\\ 
Summing over \eqref{bulk} we get
\begin{equation} 
	\left[X_{a},\Xt_{1}\right]=\lambda_{a}\Xt_{1}\qquad\forall a=1,\ldots,N
\end{equation}
such that it immediately follows that
\begin{equation}\label{commutationsBulk}
	\left[\Xt_{a},\Xt_{1}\right]=\lambda_{a}\Xt_{1}\qquad \forall a\in \{2,\ldots,N\}
\end{equation}

We further get
\begin{equation}\label{commLEFT}
	\langle W|\left(\lambda_{a}\Xt_{1}-\Xt_{a}\right)=\lambda_{a}\langle W|\qquad\forall a=2,\ldots,N
\end{equation}
\begin{equation}\label{commRIGHT}
	\Xt_{a} |V\rangle= \lambda_{a}|V\rangle\qquad\forall a=2,\ldots,N
\end{equation} 
The vector $|\widetilde{\Psi}\rangle$ is written as:
\begin{equation}
	|\widetilde{\Psi}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
	|V \rangle |\mathbf{n}\rangle
\end{equation}
where the basis is 
$$
|\mathbf{n}\rangle =|n_{1}^{1},\ldots,n_{N}^{1}\rangle \otimes \ldots\otimes |n_{1}^{L},\ldots,n_{N}^{L}\rangle
$$
such that for each site $x\in \{1,\ldots,L\}$ they must fulfill the hard-core constraint $$\sum_{a=1}^{N}n_{a}^{x}=1$$
The vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
We need to compute the coefficient $\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{i}}
|V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBulk},\eqref{commLEFT} and \eqref{commRIGHT}.\\
We can rewrite \eqref{commutationsBulk} as:
\begin{equation}\label{UsefulRelation}
	\widetilde{X}_{a}\widetilde{X}_{1}=\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}
\end{equation}
We first observe that $\forall a\in \{2,\ldots,N\}$ and $\forall l,n\in \mathbb{N}$ we have, thanks to \eqref{UsefulRelation}: 
\begin{align*}
	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{l}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{l-1}
	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{l}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{l-1}
	\\&=
	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{l-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{l-1}
	\\&=\ldots\\&=
	\widetilde{X}_{1}^{l}\left(\widetilde{X}_{a}+l\lambda_{a}\right)^{n}
\end{align*}
Thus
\begin{align*}
	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{1}^{n_{1}}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+n_{1}\lambda_{a}\right)^{n_{a}}
\end{align*}
by consequence
\begin{equation}
	\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}=\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
\end{equation}
Thus we obtain
\begin{equation*}
	\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
	|V \rangle=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
\end{equation*}
by using \eqref{commRIGHT}
\begin{align*}
	W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
	|V \rangle&=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{i}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
	\\&=
	\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
	\\&=
	\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle
\end{align*}
we only need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$. For the sake of notation call $\sum_{i=1}^{L}n_{1}^{i}=n_{1}$. Take an arbitrary $a\in \{2,\ldots,N\}$
\begin{align*}
	\langle W|\widetilde{X}_{1}^{m_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\\&=
	\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle W|\widetilde{X}_{1}^{n_{1}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{1}-1)\right)|V\rangle
	\\&=
	\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\left(n_{1}+1-1\right)\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\\&=
	\left(2+n_{1}-1\right)\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\\&=
	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
\end{align*}
we have a recursion
\begin{equation}
	\begin{cases}
		\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle\\
		\langle W|\widetilde{X}_{1}^{0}|V\rangle=1
	\end{cases}
\end{equation}
\begin{align*}
	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\langle W|\widetilde{X}_{1}^{n_{1}-2}|V\rangle\\&=
	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle W|\widetilde{X}_{1}^{0}|V\rangle
	\\&=
	\frac{\Gamma(2+n_{1})}{\Gamma(2)}
\end{align*}
By using this result we have 
\begin{equation}
	\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
	|V \rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2)}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
\end{equation}
we add the normalization
\begin{align*}
	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{1}^{L}|V|\rangle=
	\frac{\Gamma(2+L)}{\Gamma(2)}
\end{align*}
All in all
\begin{equation}\label{resulEsteady}
	|\widetilde{\Psi}\rangle= \sum_{\mathbf{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{i})}{\Gamma(2+L)}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|\mathbf{n}\rangle
\end{equation}

 We now perform a change of basis. By calling $s_{i}$ the (only) species present at site $i$, we can rewrite
\begin{equation}
	|n_{1}^{i},\ldots,n_{N}^{i}\rangle=|s_{i}\rangle
\end{equation}
where $s_i=\sum_{k=1}^Nk\delta_{n_k^i,1}$. 
Then it is to see that 
\begin{equation}
	|\mathbf{s}\rangle=\bigotimes_{i=1}^{L}|s_{i}\rangle=|\mathbf{s}\rangle
\end{equation}
with $s_{i}\in\{1,\ldots,N\}$.     
\\Moreover, for a fixed site $i$, the coefficient
\begin{equation}
	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
\end{equation}
has only one factor, associated to the non empty species $a$ that is the site $i$, i.e. to the only $m_{a}^{i}\neq 0$. Furthermore, if the site $i$ has the empty, i.e. $1$, the whole coefficient equals 1. The $m_{1}^{i}$ are one if and only if the occupation of site $i$ is $1$, then it easy to see that $m_{1}^{i}=\delta_{s_{i},1}$. Then, we can write
\begin{equation}
	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}=\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}
\end{equation}
As already pointed out, $m_{1}^{i}=\delta_{s_{i},1}$, then 
\begin{equation}
	\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}
\end{equation}
Finally, making the sum over all $\mathbf{s}\in \Omega$ is equivalent to sum over all the possible values of each $s_{i}\in\{1,\ldots,N\}$ $\forall i\in\{1,\ldots,L\}$. Thus, by putting all these things together, we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}
\subsubsection*{The steady state of $H_{dual}^{T}$}
The steady state $|\Psi_{ABS}\rangle$ such that $H_{dual}^{T}|\Psi_{abs}\rangle=0$ is given by the following formula:
\begin{equation}\label{ABS}
		\begin{split}
			|\Psi_{ABS}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}\bigotimes_{r=1}^{L} |s_{r}\rangle
		\end{split}
	\end{equation} 
 By \eqref{SteadyStates}, we first need to compute $(T^{T})^{\otimes L}$. 
The matrix $T$ has the following form
\begin{equation}\label{ExplicitMatrixT}
	T=\exp\left(-\sum_{b=2}^{N}e_{b1}\right)\exp\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)\exp\left(\sum_{b=2}^{N}e_{b1}\right)=\exp\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)
\end{equation}
Thus
\begin{equation}
	T=I_{N\times N}+\begin{pmatrix}
		0&\beta_{2}&\ldots&\beta_{N}\\
		0&0&\ldots&0\\
		\vdots&\vdots&\ldots&\vdots\\
		0&0&\ldots&0
	\end{pmatrix}
\end{equation}
We introduce the following notation: $e_{a}^{b}=e_{ab}$, $e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}$ and $$\delta_{a,b}=\begin{cases}
	1\quad \text{if}\quad a=b\\
	0\quad \text{if}\quad a\neq b
\end{cases}$$ 
Then we have that 
\begin{equation}
	T^{T}=I_{N\times N}+\begin{pmatrix}
		0&0&\ldots&0\\
		\beta_{2}&0&\ldots&0\\
		\vdots&\vdots&\ldots&\vdots\\
		\beta_{N}&0&\ldots&0
	\end{pmatrix}=\sum_{s_{1}=1}^{N}e_{i}^{i}+(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
\end{equation}
For the sake of notation let us introduce also the following matrix
\begin{equation}
	Q:=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
\end{equation}
We start by computing 
\begin{equation}
	T^{T}\otimes T^{T}=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)=I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
\end{equation}
Let's compute each terms separately:
\begin{equation}
	I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}
\end{equation}
\begin{equation}
	I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}
\end{equation}
\begin{equation}
	Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}
\end{equation}
\begin{equation}
	Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}\delta_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
\end{equation}
Take a line of the matrix $T^{T}\otimes T^{T}$ identified by index $(s_{1},s_{2})$, then it can be written as
\begin{equation}
	\left(T^{T}\otimes T^{T}\right)_{(s_{1},s_{2})}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-e_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
\end{equation}
Then it is easy to generalize for an arbitrary order of tensor product. Take the configuration with $L$ sites and identify the row $\mathbf{s}=(s_{1},\ldots,s_{L})$ with $s_{i}\in \{1,\ldots,N\}$, $\forall i\in\{1,\ldots,L\}$:
\begin{equation}
	\begin{split}
		\left(T^{T}\right)^{\otimes L}_{s_{1},\ldots,s_{L}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{k_{1}=s_{1},\ldots,s_{L}\,:\,k_{1}\neq 1}e_{s_{1},\ldots,k_{1},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{k_{1}}\\&+\sum_{k_{1},k_{2}=s_{1},\ldots,s_{L}\,:\,k_{1},k_{2}\neq 1}e_{s_{1},\ldots,k_{1},\ldots,k_{2}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{k_{1}}\beta_{k_{2}}+\ldots+\left(\sum_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
	\end{split}
\end{equation}
Then, by multiplying this matrix for the vector $|\widetilde{\Psi}\rangle$ we obtain
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi_{ABS}(\mathbf{s})&=\left(T^{T}\right)^{\otimes m}_{s_{1},\ldots,s_{L}}|\widetilde{\Psi}\rangle\\&= \widetilde{\Psi}(\mathbf{s})+\sum_{k_{1}=s_{1},\ldots,s_{L}\,:\, k_{1}\neq 1}\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{k_{1}},\ldots,s_{L})\beta_{k_{1}}\\&+
		\sum_{k_{1},k_{2}=s_{1},\ldots,s_{L}\,:\, k_{1},k_{2}\neq 1}\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{k_{1}},\ldots,\overbrace{1}^{k_{2}},\ldots,s_{L})\beta_{k_{1}}\beta_{k_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\sum_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}
	\end{split}
\end{equation}
from \eqref{resulEsteady}, we have the following equation
\begin{equation}
	\widetilde{\Psi}(\mathbf{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)\right)^{1-\delta_{s_{i},1}}
\end{equation}
Then, for fixed $\mathbf{s}$ we have a contribution of a factor $\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)$ if the site is non empty, and a contribution of a factor $1$ if the site is empty. 
Let's introduce the coefficients 
\begin{equation}
	c_{i}=\begin{cases}
		1\quad \text{if}\quad s_{i}\neq 1\\
		0\quad \text{if}\quad s_{i}=1
	\end{cases}
\end{equation}
Thus we have $\widetilde{\Psi}(\mathbf{s})$ when all the $c_{i}$ are one and $\widetilde{\Psi}(1,\ldots,1)$ when all the $c_{i}$ are zero. All the configurations in between refers to different values of these $c_{i}$. \\The equation \eqref{ABS_intermediate}, can now be written in terms of $c_{i}$ as follows
\begin{equation}
	\begin{split}
		\Psi_{ABS}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right]^{c_{i}}\left(\beta_{s_{i}}\right)^{(1-c_{i})(1-\delta_{s_{i},1})}
	\end{split}
\end{equation}
The summations goes from $0$ to $\delta_{s_{i},1}$ because in \eqref{ABS_intermediate}, the configurations that has an empty occupation are cosnidered to contribute just with a $1$.
In the above formual, we make the span over all possible $c_{i}\in\{0,1\}$ when the site is non-empty, and we keep $c_{i}=0$ when the site is empty. Moreover, when $c_{i}=1$ we add a factor $\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)$, while we add a factor $\beta_{s_{i}}$ when $c_{i}=0$ and the site is non-empty.
Finally, by considering all possible occupancies of the sites we obtain \eqref{ABS}. 
\newline
\textbf{Remark}: {\color{red} Can we interpret the steady state $|\Psi_{ABS}\rangle $ as the absorption probabilities ?}
\subsection{The steady state and the exact correlations}
By using the previous result we can write explicit formulas for the steady state of the original Hamiltonian \eqref{hamiltonian} and for arbitrary order correlations. 
\newline
The steady state of the original Hamiltonian $|\Psi\rangle$, defined by $H|\Psi\rangle=0$, is characterized by the following formula
	\begin{equation}\label{ExpSteadyState}
		\begin{split}
			|\Psi\rangle &= \sum_{s_{1},\ldots,s_{L}=1}^{N}\left(\sum{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}\right. \\ &+ \left.\sum_{l=0}^{\Xi(\mathbf{s})}(-1)^{l}\delta_{j\geq 1}\sum_{k_{1},\ldots,k_{l}=s_{1},\ldots,s_{L}}\prod_{q=1}^{j}\delta_{k_{q},1}\sum_{\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}}=2}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\prod_{t=1}^{l}\delta_{c_{k_{t}},1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}\right.\\&\cdot\left.\prod_{i=1\;:\;i\neq k_{1},\ldots,k_{l}}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}\prod_{r=1}^{l}\lambda_{\tilde{s}_{k_{r}}}\left(1+L-k_{r}-\sum_{j=i}^{L}c_{j}\right)^{c_{k_{r}}}\right)\bigotimes_{i=1}^{L}|s_{i}\rangle
		\end{split}
	\end{equation}
	where
	\begin{equation}
		\Xi(\mathbf{s})=\sum_{i=1}^{L}\delta_{s_{i},1}
	\end{equation}
 \newline
 \\
 \textbf{Remark}: Let us notice that 	$\forall \mathbf{s}=(s_{1},\ldots,s_{l})$ such that $s_{i}\neq 1$ $\forall i \in\{1,\ldots,L\}$ (i.e. a configuration without any state 1, that can be interpreted as a non-empty configuration) we have that 
	\begin{equation}\label{LinkABS-corr}
		\Psi(\mathbf{s})=\Psi_{ABS}(\mathbf{s})
	\end{equation}
This can be seen, in such a situation the second addend of \eqref{ExpSteadyState} vanishes. 
 \newline
 By \eqref{SteadyStates}, we only have to compute $\left((V^{-1})^{T}\right)^{\otimes L}$.\\
For the sake of notation lets call 
\begin{equation}
	W:=(V^{-1})^{T}
\end{equation}
We have that 
\begin{equation}
	W=I_{N\times N}+\begin{pmatrix}
		0&-1&-1&\ldots&-1\\
		0&0&0&\ldots&0\\
		\vdots&\vdots&\vdots&\ddots&\vdots\\
		0&0&0&\ldots&0
	\end{pmatrix}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+\delta_{s_{1},1}\sum_{\tilde{s}_{1}=2}^{N}e_{1}^{\tilde{s}_{1}}(-1)
\end{equation}
we first take the tensor product between two of them
\begin{equation}
	\begin{split}
		W\otimes W &= \sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{s_{1}=1,\tilde{s}_{2}=2}^{N}e_{s_{1},1}^{s_{1},\tilde{s}_{2}}\\&+(-1)\delta_{s_{1},1}\sum_{\tilde{s}_{1}=2,s_{2}=1}^{N}e_{1,s_{2}}^{\tilde{s}_{1},s_{2}} +(-1)(-1)\delta_{s_{1},1}\delta_{s_{2},1}\sum_{\tilde{s}_{1},\tilde{s}_{2}=2}^{N}e_{1,1}^{\tilde{s}_{1},\tilde{s}_{2}}
	\end{split}
\end{equation}
In the above formula, there is a diagonal term that is always present, while the other addend that is non-vanishing when there is at least one empty. \\
Let's iterating the tensor product multiplication. Then, for a fixed raw, identified by $\mathbf{s}=\{s_{1},\ldots,s_{L}\}$ with $s_{i})_{i=1,\ldots,L}\in \{1,\ldots,N\}$, of the $L-$times tensor product matrix we have the following expression:
\begin{equation}
	\begin{split}
		(W)^{\otimes L}_{\mathbf{s}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{l=0}^{\Xi(\mathbf{s})}(-1)^{l}\delta_{l\geq 1}\sum_{k_{1},\ldots,k_{l}=s_{1},\ldots,s_{L}}\prod_{q=1}^{l}\delta_{k_{q},1}\sum_{\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{j}}=2}^{N}e_{s_{1},\ldots,\underbrace{1}_{k_{1}},\ldots,\underbrace{1}_{k_{l}},\ldots,s_{L}}^{s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L}}
	\end{split}
\end{equation}
where 
\begin{equation}
	\Xi(\mathbf{s})=\sum_{i=1}^{L}\delta_{s_{i},1}
\end{equation}
Now, by multiplying $(W)^{\otimes L}_{s_{1},\ldots,s_{L}}$ with $|\Psi_{ABS}\rangle $ we get
\begin{equation}
	\begin{split}
		(W)^{\otimes L}_{\mathbf{s}}|\Psi_{ABS}\rangle&=\Psi_{ABS}(\mathbf{s})\\&+\sum_{l=0}^{\Xi(\mathbf{s})}(-1)^{l}\delta_{l\geq 1}\sum_{k_{1},\ldots,k_{l}=s_{1},\ldots,s_{L}}\prod_{q=1}^{l}\delta_{k_{q},1}\sum_{\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{j}}=2}^{N}\Psi_{ABS}(s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L})
	\end{split}
\end{equation}
Now, we only need to write explicitly the term $\Psi_{ABS}(s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L})$. We use formula\eqref{ABS_intermediate} specialized to the case where we put all the $c_{k_{1}},\ldots,c_{k_{l}}=1$ and we replace the species in the coordinates $k_{1},\ldots,k_{l}$ with  $\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}}$:
\begin{equation}
	\begin{split}
		&\Psi_{ABS}(s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\prod_{t=1}^{l}\delta_{c_{k_{t}},1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}\\
		&\cdot\prod_{i=1\;:\;i\neq k_{1},\ldots,k_{l}}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}\prod_{r=1}^{l}\lambda_{\tilde{s}_{k_{r}}}\left(1+L-k_{r}-\sum_{j=i}^{L}c_{j}\right)^{c_{k_{r}}}
	\end{split}
\end{equation}
Finally, we make vary these $\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}}$  between $2$ and $N$. 
By putting things together and considering all the rows, we obtain \eqref{ExpSteadyState}.\\
We can now use the explicit expression of the steady state to find arbitrary point correlations.\\
\subsubsection*{Exact correlations}
If we think about $1$ as the empty, the correlations only involve species different from $1$. 
Thus, for the process defined by the Hamiltonian \eqref{hamiltonian}, the $m$-points correlations, between sites $\mathbf{y}=(y_{1},\ldots,y_{m})$ occupied by the species $\mathbf{s}=(s_{1},\ldots,s_{m})\in \{2,\ldots,N\}^{m}$ are characterized by the following formula:
	\begin{equation}\label{exactCorrelations}
		\langle\rho^{y_{1}}_{s_{1}},\ldots,\rho^{y_{m}}_{s_{m}}\rangle=\sum_{c_{1},\ldots,c_{m}=0}^{1}
			f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{m})
	\end{equation}
	where 
	\begin{equation}\label{powerCoeffSpecies}
		g_{k}(c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
	\end{equation}
	and 
	\begin{equation}\label{powerCoeffNOspec}
		f(c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
	\end{equation}
We aim to compute the correlations between the sites $\mathbf{y}=\left(y_{1},\ldots,y_{m}\right)$ occupied by the species $\mathbf{s}=\left(s_{1},\ldots,s_{m}\right)$, such that $s_{1},\ldots,s_{m}\in \{2,\ldots,N\}$. %We exploit the formula \eqref{ExpSteadyState}. %By duality we have that 
This means that we need to find 
\begin{equation}
	\begin{split}
		\langle\rho_{s_{1}}^{y_{1}}\ldots\rho_{s_{m}}^{y_{m}}\rangle&%=\mathbb{E}_{\mu_{stat}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\eta_{s_{k}}^{y_{k}}=1\}}\right]=\mathbb{E}_{\mu_{stat}}\left[D(\eta,\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}})\right]\\&
		=\mathbb{P}_{stat}\left(\eta_{s_{1}}^{y_{1}}=1,\ldots,\eta_{s_{m}}^{y_{m}}=1\right)
	\end{split}
\end{equation}
The probability at the stationary state that we have $m$ points occupied with $\mathbf{s}$ species, can be thought as the stationary probability of a chain of length $m$ with coordinates denoted by $y_{1},\ldots,y_{m}$ and where all the sites are occupied by $s_{1},\ldots,s_{m}$. This probability can be written as the stationary state of such a chain with the notation 
\begin{equation}
	\mathbb{P}_{\text{stat, Chain m}}\left(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m}\right)=\Psi_{m}\left(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m}\right)
\end{equation}
As already pointed out in \eqref{LinkABS-corr}, for non empty configurations we have:
\begin{equation}\label{Corr-mABS}
	\Psi_{m}(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m})=\Psi_{ABS}(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m})
\end{equation}
Thus, by applying the formula \eqref{ABS_intermediate} we have 
\begin{equation}
	\Psi_{ABS}(s_{1},\ldots,s_{m},\mathbf{y})=\sum_{c_{1},\ldots,c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(L+1-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
By using the relation \eqref{Corr-mABS} we have the equations for arbitrary correlations.
\subsubsection{One and two point correlations}
We show two examples of computation of correlations via \eqref{exactCorrelations}.\\     
\textbf{One point correlations}: choose $s_{1}=s$ and $y_{1}=x$
\begin{align*}
	\langle\rho_{s}^{x}\rangle=\sum_{c_{1}=0}^{1}(\alpha_{s}-\beta_{s})^{c_{1}}\beta_{s}^{1-c_{1}}g_{s}(c_{1})f(c_{1})
\end{align*}
we have that $f(0)=1$ and $f(1)=\frac{\Gamma(L+2-1)}{\Gamma(L+2)}=\frac{1}{L+1}$ and $g_{s}(0)=1$ and $g_{s}(1)=(L+2-x-1)$. Thus we obtain 
\begin{align*}
\langle\rho_{s}^{x}\rangle=\frac{(L+1-x)}{L+1}(\alpha_{s}-\beta_{s})+\beta_{s}
\end{align*}
that is exactly the one point correlations computed in \cite{vanicat2017exact}.\\
\textbf{Two points correlations}: %fix $s_{1}=s,\;s_{2}=s^{'}$ and $y_{1}=x,\;y_{2}=y$
\begin{equation}
	\begin{split}
	\langle\rho_{s}^{x},\rho_{s^{'}}^{y}\rangle= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{1},c_{2})
	\end{split}
\end{equation}
we have that 
\begin{align*}
	&g_{1}(0,0)=1&g_{2}(0,0)=1\\&
	g_{1}(1,0)=(L+2-y_{1}-1)&g_{2}(1,0)=1\\&
	g_{1}(0,1)=1&g_{2}(0,1)=(L+2-y_{2}-1)\\&
	g_{1}(1,1)=(L+2-y_{1}-2)&g_{2}(1,1)=(L+2-y_{2}-1)
\end{align*}
while
\begin{align*}
	f(0,0)=1\quad f(0,1)=f(1,0)=\frac{\Gamma(L+2-1)}{\Gamma(L+2)}\quad f(1,1)=\frac{\Gamma(L+2-2)}{\Gamma(L+2)}
\end{align*}
By putting things together
\begin{equation}
	\begin{split}
	\langle\rho_{s}^{x},\rho_{s^{'}}^{y}\rangle&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
	\end{split}
\end{equation}
\subsection{Absorption probabilities for general 2j}
Even though integrability does not hold anymore for $j>\frac{1}{2}$, by using the absorbing duality we can still say something about the moment of the non equilibrium steady state distribution. We write the expression for the absorption probability for the general $(2j)$ case when the setting is a one dimensional chain with two reservoirs at the ends. We assume nearest neighbor interaction, similarly to what we did at the beginning of section \ref{sec4}. \\ Let us think about the species $1$ as the empty state. 
Fix a generic initial dual configuration $\xi$ that contains $|\xi_{k}|$ particles of each non-empty species $k\in \{2,\ldots,N\}$. Since the dual chain is absorbing we have that:  
\begin{equation}
	\begin{split}
		\lim_{t\to \infty}\mathbb{E}_{\xi}\left[D(\eta,\xi(t))\right]=& \sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}\\&
		\mathbb{P}\left(\xi(\infty)=\sum_{k=2}^{N}\left(i_{k}\delta_{0}+(|\xi_{k}|-i_{k})\delta_{L+1}\right)| \xi_{0}=\xi\right)
	\end{split}
\end{equation}
we denote by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left and by $|\xi_{k}|-i_{k}$ the number of particles absorbed at right. \\
By duality we have that 
\begin{equation}
	\mathbb{E}_{\text{stationary},\eta}\left[D(\eta(t),\xi)\right]=\lim_{t\to \infty}\mathbb{E}_{\eta}\left[D(\eta(t),\xi)\right]=\lim_{t\to \infty}\mathbb{E}_{\xi}\left[D(\eta,\xi(t))\right]
\end{equation}
\textbf{One point correlations}
\begin{equation}
	D(\eta,\delta_{s}^{x})=\eta_{s}^{x}
\end{equation}
Thus
\begin{equation}
	\langle \rho_{s}^{x}\rangle_{\text{stat}}=\lim_{t\to\infty}\mathbb{E}\left[\delta_{s}^{x}(t)\right]=\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{k}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
\end{equation}
we want to determine $p^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ and by consequence $p^{x}_{s}(0)=1-p^{x}_{s}(1)$.\\
We condition on the first jump:
\begin{equation}
	p^{x}_{s}(1)=p^{x+1}_{s}(1)\;\mathbb{P}(\text{First jump on the right})+p^{x-1}_{s}(1)\;\mathbb{P}(\text{First jump on the left})
\end{equation}
Then:
\begin{itemize}
	\item If $x=1$, then the particle has probability $\frac{(\alpha_{1}+\ldots+\alpha_{N})}{1+(\alpha_{1}+\ldots+\alpha_{N})}$ of jumping to the left and $\frac{1}{1+(\alpha_{1}+\ldots+\alpha_{N})}$ of jumping to the right. Thus
	\begin{equation}
		p^{1}_{s}(1)=p^{0}_{s}(1)\frac{(\alpha_{1}+\ldots+\alpha_{N})}{1+(\alpha_{1}+\ldots+\alpha_{N})}+p^{2}_{s}(1)\frac{1}{1+(\alpha_{1}+\ldots+\alpha_{N})}
	\end{equation}
\item if $x\in \{2,\dots,L-1\}$, we have $1/2$ of probability of jumping left and right
\begin{equation}
	p_{x}^{s}(1)=\frac{1}{2}\left(p_{x+1}^{s}(1)+p_{x-1}^{s}(1)\right)
\end{equation}
	\item If $x=L$, then the particle has probability $\frac{(\beta_{1}+\ldots+\beta_{N})}{1+(\beta_{1}+\ldots+\beta_{N})}$ of jumping to the left and $\frac{1}{1+(\beta_{1}+\ldots+\beta_{N})}$ of jumping to the right. Thus
\begin{equation}
	p^{L}_{s}(1)=p^{L+1}_{s}(1)\frac{(\beta_{1}+\ldots+\beta_{N})}{1+(\beta_{1}+\ldots+\beta_{N})}+p_{L-1}^{s}(1)\frac{1}{1+(\beta_{1}+\ldots+\beta_{N})}
\end{equation}
\item Boundary conditions:
\begin{equation}
	p^{0}_{s}(1)=1\qquad p^{L+1}_{s}(1)=0
\end{equation}
\end{itemize}
Denote $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$ for the sake of notation.\\
All in all we need to solve
\begin{equation}
	\begin{cases}
		\Delta_{x}^{L}p^{x}_{s}(1)=0\\
		p^{1}_{s}(1)=\frac{A}{1+A}+p^{2}_{s}(1)\frac{1}{1+A}\\
		p^{L}_{s}(1)=p^{L-1}_{s}(1)\frac{1}{1+B}
		\end{cases}
\end{equation}
A general solution of the discerete laplace equation is
\begin{equation}
	p_{x}^{s}(1)=C_{1}x+C_{2}
\end{equation}
we match with boundary conditions:
\begin{equation}
	\begin{cases}
	C_{1}+C_{2}=\frac{A}{1+A}+\frac{2C_{1}+C_{2}}{A+1}\\
	C_{1}L+C_{2}=\frac{C_{1}(L-1)+C_{2}}{1+B}
	\end{cases}
\end{equation}
The solution
\begin{equation}
	C_{1}=\frac{(-A B)}{(A + B - A B + A B L)}\qquad C_{2}=\frac{(A (1 + B L))}{(A + B - A B + A B L)}
\end{equation}
\begin{equation}
	p_{x}^{s}(1)=\frac{A (B (L-x)+1)}{A (B (L-1)+1)+B}
\end{equation}
then 
\begin{equation}
	p^{x}_{s}(0)=1-p^{x}_{s}(1)=\frac{B (A (x-1)+1)}{A (B (L-1)+1)+B}
\end{equation}
then the average density is 
\begin{equation}
\langle\rho_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
\end{equation}
\newline \\
\textbf{Remark}: In case $A=B=1$ we have 
	\begin{equation}
\langle\rho_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
	\end{equation}
and it exactly matches with \cite{vanicat2017exact}. \\
In case $A=B=2j$ we have 
\begin{equation}
	\langle\rho_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(2jL-2jx+1)+\beta_{s}(2jx+1-2j)}{2jL-4j(j-1)}
\end{equation}
All the other correlations could be, in principle, computed with the same strategy. However, the computations become very hard as the correlation order rises, because it is not easy to find explicit solutions of the difference equations that arise from the conditioning on the first jump and the imposition of the boundary conditions. 
\subsection{Mapping to equilibrium?}
[COMPUTATIONS STILL TO DO]

\section{Conclusion}

\bibliography{ref}
\bibliographystyle{unsrt}
\end{document}

\appendix
\section{Oscillator}

\textbf{Remark}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra. Indeed, \begin{equation}\label{creationOperators}
	\begin{cases}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
	\end{cases}
\end{equation}
with commutaion relations
\begin{equation}
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
\end{equation}
The basis elements of $gl(N)$ can be written as
\begin{equation}
		e_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
\end{equation}  
\section{Representation}
The approach we use to find duality relations is the Lie algebraic one. The main idea is to describe the infinitesimal generator (or better, its transposed, i.e. the Hamiltonian operator) via a proper combination of the basis of a certain Lie algebra. Then, duality will be found by symmetry argument.\\
We chose the $gl(N)$ Lie algebra. This is compact. The abstract basis elements are denoted by $E_{a,b}$ with $a,b\in \{1,\ldots,N\}$ that obeys to the Lie bracket relations given by
\begin{equation}
\left[E_{ab},E_{cd}\right]=E_{ab}E_{cd}-E_{cd}E_{ab}=E_{ad}\delta_{bc}-E_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
We define the the following representation $(\mathcal{C}^{D},\Pi)$, where $D$ is the dimension of the representation and $\Pi:gl(N):\to \mathcal{M}_{D\times D}$ is an homeomorfism between the Lie algebra and the space $\mathcal{M}_{D\times D}$ of $D\times D$ matrices with complex coefficients. For every elements $E_{ab}$ of the abstract Lie algebra, it associates $\Pi(E_{ab})=e_{ab}$ Since this Lie algebra is compact and semi-simple, we can characterize every irreducible representation by defining its own \textit{highest weight state}. We recall that a weight is a vector $\mu=(\mu_{0},\ldots,\mu_{N})$ with $\mu_{i}\in\mathbb{N}_{0}$ such that there exist a state $|\mu\rangle$ with the property $e_{ii}|\mu\rangle=\mu_{i}|\mu\rangle$ $\forall i=0,\ldots,N$ (where $e_{ii}$ is the Cartan element). Let's consider two weights $\mu$,$\nu$, then we say that $\mu$ is positive if the first non zero component is positive. Then, we say that $\mu>\nu$ if $\mu-\nu>0$. Thus, we can define the "highest weight" of a representation the $\mu_{0}$ that is bigger then all the other weights. As already pointed out, every irreducible representation of $gl(N)$ is in a one to one correspondence with its heights weight. That means that we can characterize the representations via the highest weight. A more formal definitions: $\mu^{hws}=(\mu_{1},\ldots,\mu_{N})$ with $\mu_{i}\geq \mu_{i+1}$ is the heights weight of the representation if 
\begin{equation}
	e_{ii}|\mu^{hws}\rangle=\mu_{i}^{hws}|\mu^{hws}\rangle\qquad \text{and}\qquad e_{ij}|\mu^{hws}\rangle=0\quad \forall i<j
\end{equation}
The representation that we choose is characterized by the heighest weight state $|\mu^{hws}\rangle$ such that 
\begin{equation}
	e_{11}|\mu^{hws}\rangle=2j|\mu^{hws}\rangle\qquad \mu^{hws}=(2j,0,\ldots,0)
\end{equation}
The dimension of this representation is given by the combination of $N$ objects in $2j$ positions with repetition:
\begin{equation}
	D= \frac{(N+2j-1)!}{(2j)!(N-1)!}
\end{equation}
For example, in the case of spin $1/2$ (hard-core exclusion) with $N=2$ species we have dim$=\frac{(2+1-1)!}{1!(2-1)!}=2$ and in case of spin $1$, dim$=\frac{(3+2-1)!}{(2)!(2)!}=6$.\\
The basis element of the vector space of the representation $\mathbb{C}^{D}$ are given by 
\begin{equation}
    |n_{1},\ldots,n_{N}\rangle\qquad \forall
    n=(n_{1},\ldots,n_{N})
\end{equation}
$\forall n=(n_{1},\ldots,n_{N})\in \chi$ where $\chi:=\left\{n\;:\;\sum_{k=1}^{N}n_{k}=2j\right\}$ (let us notice that $\Omega=\xi^{|V|}$. This vector can be mapped in a one-to-one correspondence with the canonical basis of $\mathbb{C}^{D}$. By consequence, this basis vector are orthonormal, i.e. 
\begin{equation}
    \langle q_{1},\ldots,q_{N}|_{x}|t_{1},\ldots,t_{N}\rangle_{x}=\prod_{k=1}^{N}\delta_{q_{k},t_{k}}
\end{equation}

The algebra $gl(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it. It is also possible to see that this representation can be written as a direct sum of representation of $su(2)$, each with representation $2j$ and each associated with a positive root. The generator of this $su(2)$ sub-algebras can be written by:  $J^{+}=e_{ab}$, $J^{-}=e_{ba}$, $J^{0}=1/2(e_{bb}-e_{aa})$ $\forall a,b=1,\ldots,N$. \\
The explicit actions of the basis element of the algebra on the vectors of the space $\mathcal{C}^{D}$ are the following, for non Cartan and Cartan elements respectively: 
\begin{equation}
	\begin{cases}
		e_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\\
		e_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle
	\end{cases}\qquad \forall a,b\in\{1,\ldots,N\}
\end{equation}
In matrix form $\forall a,b\in \{1,\ldots,N\}$
\begin{equation}\label{matrixFormulaE}
	\begin{split}
	&e_{ab}=\sum_{n\in\chi}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|
	\end{split}
\end{equation}
\textbf{Remark}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process. The mapping with the vectors written in \eqref{stateSpace} is the following
\begin{equation}
(n_{1}^{x},\ldots,n_{N}^{x})^{T}=|n_{1},\ldots,n_{N}\rangle_{x}\qquad(n_{1}^{x},\ldots,n_{N}^{x})=\langle n_{1},\ldots,n_{N}|_{x}
\end{equation}
\begin{flushright}
    $\square$
\end{flushright}
This Lie algebra has second Casimir element given by 
\begin{equation}
    C_{2}=\sum_{a,b=1}^{N}e_{ab}e_{ba}
\end{equation}
This element is diagonal, and its action on a generic state is the following:
\begin{equation}
	C_{2}=2j(2j+N)\mathbbm{1}
\end{equation}
where $\mathbbm{1}$ is the $D\times D$ dimensional identity matrix. \\
By introducing the \textit{coproduct} operator \begin{equation}\begin{split}\Delta:(\mathbb{C}^{D},\Pi)&\to(\mathbb{C}^{D}\otimes \mathbb{C}^{D},\Pi\otimes \Pi) \\
 e_{ab}&\to e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}
\end{split}
\end{equation}
then we can compute 
\begin{equation}\label{coproductC2}
	\begin{split}
	\Delta(C_{2}&)=\sum_{a,b=0}^{N}\Delta(e_{ab})\Delta(e_{ba})
	=
	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}+e_{ab}\otimes \mathbbm{1}\right)\left(\mathbbm{1}\otimes e_{ba}+e_{ba}\otimes \mathbbm{1}\right)
	\\&=
	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}e_{ba}+e_{ba}\otimes e_{ab}+e_{ab}\otimes e_{ba}+e_{ab}e_{ba}\otimes \mathbbm{1}\right)
	\\&=
	2\left(\sum_{a,b=0}^{N}e_{ab}\otimes e_{ba}\right)+\mathbbm{1}\otimes C_{2}+C_{2}\otimes\mathbbm{1}
	\end{split}
\end{equation}
We now define the equivalent of \eqref{stateSpace} in the vector notation
 \begin{equation}
	\Omega:=\left\{|n_{1},\ldots,n_{N}\rangle \;:\;\sum_{k=1}^{N}n_{k}=2j\right\}^{\otimes|V|}
	\end{equation}
where we denote 
\begin{equation}
|n\rangle=\bigotimes_{x\in V}	\left(|n_{1},\ldots,n_{N}\rangle_{x}\right)\in \Omega
\end{equation}
The Hamiltonian operator can be written in term of the basis element of the Lie algebra as

\begin{equation}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}
H_{x,y}=\sum_{k,l=1}^{N}\left(e_{kl}\otimes e_{lk}-e_{ll}\otimes e_{kk}\right)
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}
H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(e_{k,l}-e_{ll}\right)
\end{equation}
Moreover, by the \eqref{coproductC2} and by computing the explicit action of the diagonal part, we can write this Hamiltonian in function of the coproduct of the second Casimir
\begin{equation}
	H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left\{\frac{1}{2}\Delta(C_{2})-2j(4j+N)\frac{1}{2}\mathbbm{1}\otimes\mathbbm{1}\right\}+\sum_{x\in V}\Gamma_{x}\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(e_{k,l}-2j\mathbbm{1}\right)
\end{equation}

### 2023-02-15 main.tex
ll
Try
QISM
I added the QISM

@@
 \usepackage[T1]{fontenc}
-\usepackage{microtype}
+%\usepackage{microtype}
 \usepackage[pagebackref=false]{hyperref}
@@
 
-\usepackage[textsize=tiny]{todonotes}
+%\usepackage[textsize=tiny]{todonotes}
 
@@
 \usepackage{xspace}
-\usepackage{bibentry}
-\usepackage{easybmat}
+%\usepackage{bibentry}
+%\usepackage{easybmat}
 
@@
 
-\usepackage[numbers,sort&compress]{natbib}
-\usepackage{hypernat}
+%\usepackage[numbers,sort&compress]{natbib}
+%\usepackage{hypernat}
 
@@
 \noindent
-....
+...
 \end{abstract}
@@
 \subsection{Mapping to equilibrium?}
-[COMPUTATIONS STILL TO DO]
-
+\subsubsection{Quantum inverse scattering method}
+We can apply the \textit{quantum inverse scattering method} to this process.
+We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$.
+In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
+We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
+\begin{equation}\label{Rmatrix}
+R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
+\end{equation}
+\begin{equation}\label{KmatrixHAT}
+\widehat{K}_{a}(x)=I+\frac{2x}{x+1}B_{L}
+\end{equation}
+\begin{equation}\label{Kmatrix}
+K_{a}(x)=\left((2x+3)B_{1}+(x+3)I\right)\frac{1}{(x+1)^{2}(2x+3)}
+\end{equation}
+The above matrices satisfy the following equations
+\begin{itemize}
+\item \textit{Yang-Baxter-Equation}
+\begin{equation}
+R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
+\end{equation}
+\item \textit{Boundary-Yang-Baxter-Equation}
+\begin{equation}
+R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
+\end{equation}
+\item \textit{Dual Boundary-Yang-Baxter-Equation}
+\begin{equation}
+K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
+\end{equation}
+\end{itemize}
+We define the following \textit{transfer matrix}
+\begin{equation}
+	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
+\end{equation}
+where we used the double row monodromy
+\begin{equation}
+	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
+\end{equation}
+where 
+\begin{equation}
+	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
+\end{equation}
+This trasfer matrix has the following properties
+\begin{equation}
+	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
+\end{equation}
+with $C_{1},C_{2}>0$. \\
+We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
+\begin{equation}
+	U_{0}(x)=\begin{pmatrix}
+		A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
+		C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
+		\vdots&\vdots&\ddots&\vdots\\
+		C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
+	\end{pmatrix}
+\end{equation}
+In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{Esse}, i.e.
+when the left boundary is lower triangular a end the right one is diagonal.
+We properly rescale them and we obtain
+\begin{equation}
+	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
+		1+x&0&\ldots&0\\
+		0&1-x&\ldots&0\\
+		\vdots&\vdots&\ddots&\vdots\\
+		0&0&\ldots&1-x
+	\end{pmatrix}
+\end{equation}
+\begin{equation}
+	K_{0}^{\Delta}=\left((2x+3)\widetilde{B}_{1}+(x+3)I\right)\frac{(1+x)^{2}(2x+3)}{(x+1)^{2}(2x+3)}=\begin{pmatrix}
+		3+x&0&\ldots&0\\
+		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
+		\vdots&\vdots&\ddots&\vdots\\
+		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x
+	\end{pmatrix}
+\end{equation}
+Then we obtain the correspondent transfer matrix as
+\begin{equation}
+	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
+\end{equation}
+where
+\begin{equation}
+	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
+\end{equation}
+Then we have
+\begin{equation}
+	\begin{split}
+	T^{\Delta}(x)&=tr_{0}\left(\begin{pmatrix}
+		3+x&0&\ldots&0\\
+		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
+		\vdots&\vdots&\ddots&\vdots\\
+		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x
+	\end{pmatrix}\begin{pmatrix}
+	A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
+	C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
+	\vdots&\vdots&\ddots&\vdots\\
+	C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
+\end{pmatrix}\right)\\&=
+(3+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+3)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=
+Q_{2L+2}x^{2L+2}+Q_{2L+1}x^{2L+1}+Q_{2L}x^{2L}+\ldots
+\end{split}
+\end{equation}
+We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
+\begin{equation}
+	A(x)=\sum_{k=0}^{2L+1}A^{k}x^{k}\quad D_{ii}(x)=\sum_{k=0}^{2L+1}D_{ii}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}
+\end{equation}
+The coefficients that we need are the following:
+\begin{equation}
+	A(x)=A^{2L+1}x^{2L+1}+A^{2L}x^{2L+1}+A^{2L-1}x^{2L-1}+\ldots
+\end{equation}
+where .
+\begin{equation}
+	A^{2L+1}=I^{tot}
+\end{equation}
+\begin{equation}
+	A^{2L}=I^{tot}+2e_{11}^{tot}
+\end{equation}
+\begin{equation}
+	\begin{split}
+		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=1\,:\,j\neq i}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
+	\end{split}
+\end{equation}
+While, $\forall i=2,\ldots,N$
+
+\begin{equation}
+	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
+\end{equation}
+where the coefficients
+\begin{equation}\label{a2lp}
+	D_{ii}^{2L+1}=-I^{tot}
+\end{equation}\begin{equation}\label{a2l}
+	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
+\end{equation}
+\begin{equation}\label{a2lm1}
+	\begin{split}
+		D_{ii}^{2L-1}=&2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
+	\end{split}
+\end{equation}
+
+%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
+%\begin{equation}
+%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
+%\end{equation}
+%where the coefficient is
+%\begin{equation}\label{c}
+%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
+%\end{equation}
+Moreover, $\forall j=2,\ldots,L$ and for $i=1$
+\begin{equation}
+	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
+\end{equation}
+where the coefficient is 
+\begin{equation}\label{b}
+	B_{j}^{2L-1}=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
+\end{equation}
+\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
+The interesting charges (we only look for the first non trivial one) take the following form
+
+\begin{align}
+	Q_{2L+2}&=A^{2L+1}-D_{22}^{2L+1}-D_{33}^{2L+1}\\
+	Q_{2L+1}&=2A^{2L+1}+A^{2L}-D_{22}^{2L}-D_{33}^{2L}\\
+	Q_{2L}&=3A^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}-D_{33}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+\end{align}
+The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
+It is easy to show that 
+\begin{equation}
+	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
+\end{equation}
+The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
 \section{Conclusion}

### 2023-02-15 main.tex
Fixed
;

@@
 	\begin{split}
-		D_{ii}^{2L-1}=&2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
+		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
+		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
 	\end{split}
@@
 \begin{equation}\label{b}
-	B_{j}^{2L-1}=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
+\begin{split}
+	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
+	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
+	\end{split}
 \end{equation}

### 2023-02-16 main.tex
Fixed
;;
fix
fixed
ll

@@
 \begin{equation}\label{KmatrixHAT}
-\widehat{K}_{a}(x)=I+\frac{2x}{x+1}B_{L}
+\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
 \end{equation}
 \begin{equation}\label{Kmatrix}
-K_{a}(x)=\left((2x+3)B_{1}+(x+3)I\right)\frac{1}{(x+1)^{2}(2x+3)}
+K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
 \end{equation}
@@
 \begin{equation}
-	K_{0}^{\Delta}=\left((2x+3)\widetilde{B}_{1}+(x+3)I\right)\frac{(1+x)^{2}(2x+3)}{(x+1)^{2}(2x+3)}=\begin{pmatrix}
-		3+x&0&\ldots&0\\
-		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
+	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
+		N+x&0&\ldots&0\\
+		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
 		\vdots&\vdots&\ddots&\vdots\\
-		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x
+		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
 	\end{pmatrix}
@@
 	T^{\Delta}(x)&=tr_{0}\left(\begin{pmatrix}
-		3+x&0&\ldots&0\\
-		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
+		N+x&0&\ldots&0\\
+		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
 		\vdots&\vdots&\ddots&\vdots\\
-		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x
+		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
 	\end{pmatrix}\begin{pmatrix}
@@
 \end{pmatrix}\right)\\&=
-(3+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+3)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=
+(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=
 Q_{2L+2}x^{2L+2}+Q_{2L+1}x^{2L+1}+Q_{2L}x^{2L}+\ldots
@@
 	\begin{split}
-		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=1\,:\,j\neq i}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
+		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
 	\end{split}
@@
 		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
-		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
+		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
+		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
+		&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
 	\end{split}
@@
 \begin{align}
-	Q_{2L+2}&=A^{2L+1}-D_{22}^{2L+1}-D_{33}^{2L+1}\\
-	Q_{2L+1}&=2A^{2L+1}+A^{2L}-D_{22}^{2L}-D_{33}^{2L}\\
-	Q_{2L}&=3A^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}-D_{33}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
+	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
+	Q_{2L}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
 \end{align}

### 2023-02-17 main.tex
kk

@@
 		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
-		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
-		&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
 	\end{split}

### 2023-02-17 main.tex
tot
I wrote the coefficients with e^{tot}

@@
 \end{equation}
+We observe that $\forall i,j=1,2,\ldots,N$
+\begin{equation}
+	\sum_{a,b=1}^{L}e_{i,j}^{[a]}e_{j,i}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
+\end{equation}
+then 
+\begin{equation}
+	A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}
+\end{equation}
 While, $\forall i=2,\ldots,N$
@@
 		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
-	\end{split}
-\end{equation}
-
+	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
+		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
+	\end{split}
+\end{equation}
+
+We rewrite
+\begin{equation}
+	\begin{split}
+	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
+\end{split}
+\end{equation}
+then
+\begin{equation}
+\begin{split}
+D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+	\end{split}
+\end{equation}
 %The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
@@
 \end{equation}
+then
+\begin{equation}
+\begin{split}
+	B_{j}^{2L-1}=2e_{j1}^{tot}+
+	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{k=2}^{N}e_{jk}^{[a]}e_{k1}^{[b]}
+\end{split}
+\end{equation}
 \textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\

### 2023-02-17 main.tex
boxed

@@
 \begin{equation}
-	A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}
+	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}
 \end{equation}
@@
 		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
+		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
 	\end{split}
@@
 \begin{split}
-D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
 	\end{split}
@@
 \begin{split}
-	B_{j}^{2L-1}=2e_{j1}^{tot}+
-	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{k=2}^{N}e_{jk}^{[a]}e_{k1}^{[b]}
+	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
+	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{k=2}^{N}e_{jk}^{[a]}e_{k1}^{[b]}}
 \end{split}

### 2023-02-18 main.tex
observation
Q0 Q\Delta

@@
 \end{equation}
+\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
 %The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
@@
 \end{equation}
-The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
+The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
+We introduce the following:
+\begin{equation}
+Q_{2}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
+\end{equation}
+it has the property that commute with the equilibrium Hamiltonian
+\begin{equation}
+\widetilde{H}_{0}:=\widetilde{B}_{1}^{0}+\mathcal{H}+\widetilde{B}_{L}
+\end{equation}
+where 
+\begin{equation}
+\widetilde{B}_{1}^{0}=\begin{pmatrix}
+0&0&\ldots&0\\
+0&-1&\ldots&0\\
+\vdots&\vdots&\ddots&\vdots\\
+0&0&\ldots&-1
+\end{pmatrix}
+\end{equation}
+i.e.
+\begin{equation}
+\left[Q_{2}^{0},\widetilde{H}_{0}\right]=Q_{2}^{0}\widetilde{H}_{0}-\widetilde{H}_{0}Q_{2}^{0}=0
+\end{equation}
+We also introduce 
+\begin{equation}
+Q_{2}^{\Delta}:=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+\end{equation}
+These two matrices $Q_{2}^{0}$ and $Q_{2}^{\Delta}$ are such that
+\begin{equation}
+Q_{2}=Q_{2}^{0}+Q_{2}^{\Delta}
+\end{equation}
 \section{Conclusion}

### 2023-02-21 main.tex
Eigenvectors \Delta

--- 2023-02-17 main.tex
@@
 \end{equation}
-We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
+We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
+We can also introduce 
+\begin{equation}
+	T_{0}(x)=(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
+\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
 \begin{equation}
@@
 \end{equation}
-The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
+The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
+We introduce the following:
+\begin{equation}
+Q_{2}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
+\end{equation}
+it has the property that commute with the equilibrium Hamiltonian
+\begin{equation}
+\widetilde{H}_{0}:=\widetilde{B}_{1}^{0}+\mathcal{H}+\widetilde{B}_{L}
+\end{equation}
+where 
+\begin{equation}
+\widetilde{B}_{1}^{0}=\begin{pmatrix}
+0&0&\ldots&0\\
+0&-1&\ldots&0\\
+\vdots&\vdots&\ddots&\vdots\\
+0&0&\ldots&-1
+\end{pmatrix}
+\end{equation}
+i.e.
+\begin{equation}
+\left[Q_{2}^{0},\widetilde{H}_{0}\right]=Q_{2}^{0}\widetilde{H}_{0}-\widetilde{H}_{0}Q_{2}^{0}=0
+\end{equation}
+We also introduce 
+\begin{equation}
+Q_{2}^{\Delta}:=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+\end{equation}
+These two matrices $Q_{2}^{0}$ and $Q_{2}^{\Delta}$ are such that
+\begin{equation}
+Q_{2}=Q_{2}^{0}+Q_{2}^{\Delta}
+\end{equation}
+We have that the eigenvectors and eigenvalues of the equilibrium case are given by
+\begin{equation}
+T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle =\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+\end{equation}
+where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{k=2}^{N}m_{k}$.\\
+We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries:
+\begin{equation}
+	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots\Delta_{N}^{k_{N}}G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{equation}
+where 
+\begin{equation}
+G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=(2x+N)^{N-1}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-(N-1)}B_{2}(x)\ldots B_{N}(x)
+\end{equation}
+This function has the following properties:
+\begin{equation}\label{SecondProperty}
+\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{i},\ldots,k_{N}}(x)=(2x+N)B_{i}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{i}-1,\ldots,k_{N}}(x)\quad \forall i\in \{2,\ldots,N\}
+\end{equation}
+\begin{equation}\label{FirstProperty}
+	B_{i}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{i},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle =0\quad \forall i\in \{2,\ldots,N\}
+\end{equation}
+We prove the ansatz:
+\begin{align*}
+	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots
+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
+\begin{align*}
+	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots
+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+
+	\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+
+	\Delta_{N}^{m_{N}+1}\sum_{k_{2}=0}^{m_{3}}\ldots\sum_{k_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
+\begin{align*}
+		T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots
+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+then
+\begin{align*}
+T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
+		\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&=
+	\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle
+\end{align*}
 \section{Conclusion}

### 2023-02-22 main.tex
Fixed
ll
refs
Update main.tex

@@
 \begin{equation}
-G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=(2x+N)^{N-1}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-(N-1)}B_{2}(x)\ldots B_{N}(x)
-\end{equation}
+\begin{split}
+G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&(2x+N)^{2-N+k_{2}+\ldots+k_{N}}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{N-2-k_{2}+\ldots-k_{N}}\\&B_{2}^{k_{2}}(x)\ldots B_{N}^{k_{N}}(x)
+\end{split}
+\end{equation}
+Let us notice that when all $k$'s are one, we have again the expression (2.17) of the 2 species case \cite{frassek2020eigenstates}. 
 This function has the following properties:
-\begin{equation}\label{SecondProperty}
+\begin{itemize}
+\item Property one: (this is the equivalent of equation (2.19) of \cite{frassek2020eigenstates})\begin{equation}\label{SecondProperty}
 \left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{i},\ldots,k_{N}}(x)=(2x+N)B_{i}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{i}-1,\ldots,k_{N}}(x)\quad \forall i\in \{2,\ldots,N\}
 \end{equation}
+Indeed take for example $i=2$
+\begin{align*}
+G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)&=(2x+N)(2x+N)^{2-N+k_{2}-1+k_{3}\ldots+k_{N}}\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}
+\\&
+\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{N-2-k_{2}+1-k_{3}-\ldots-k_{N}} B_{2}(x)B_{2}(x)^{k_{2}-1}B_{3}^{k_{3}}(x)\ldots B_{N}^{k_{N}}(x) 
+\\&=
+\left[\left(\Lambda_{m_{2},\ldots,m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N}}^{k_{2}-1,k_{3},\ldots,k_{N}}(x)
+\end{align*}
+\item Property two: (this is the equivalent of equation (2.20) of \cite{frassek2020eigenstates})
 \begin{equation}\label{FirstProperty}
@@
 \end{equation}
+{\color{blue}This second property can be proved by using a lower weight representation }
+\end{itemize}
 We prove the ansatz:
@@
 	\\&+\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots
+	\\&+\ldots +
 	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
@@
 	\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+
+	\\&+\ldots +
 	\Delta_{N}^{m_{N}+1}\sum_{k_{2}=0}^{m_{3}}\ldots\sum_{k_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
@@
 	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots
+	\\&+\ldots +
 	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}

### 2023-03-06 main.tex
change
l
Update main.tex
fff
ll
ReactionDiffusion

--- 2023-02-18 main.tex
@@
 \usepackage{appendix}
+\usepackage{comment}
 \numberwithin{equation}{section}
@@
 \section{The stirring process}
-We consider the stirring process with an arbitrary number of particles $N$.
+{\color{blue}We consider the stirring process with an arbitrary number of particles $N$.
 It is important to note that any one of them can be considered the empty (or hole) particle.
@@
 However, this distinction will be useful in the section about duality, where we will see that this empty will play a special role.
-The stochastic dynamics is Markovian and consist in an exchange of particles of any type between two connected site of a graph.
-\\
+The stochastic dynamics is Markovian and consist in an exchange of particles of any type between two connected site of a graph.}
 \subsection{The infinitesimal generator}
-Let's consider a connected and undirected graph $G=(V,\mathcal{E})$ where $x\in V$ denotes the set of vertex and $\mathcal{E}$ denotes the set of edges $(x,y)$ with $x,y\in V$.
-The process has a repulsive nature, thus the state space must contain informations about this maximal occupancy.
-Then we define
+We consider a connecAt each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$.
+On each vertex we allow maximal occupancy $\nu\in \mathbb{N}$.
+Then, the configuration space is
 \begin{equation}\label{stateSpace}
-    \Omega:=\left\{n=(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; |n|=\twoj\right\}^{|V|}
-\end{equation}
-where $|n|=\sum_{k=1}^{N}n_{k}$ denotes the total number of particles per site and $|V|$  the total number of vertices.
-At each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k$, under the constraint that the total number of particle in the site is $\twoj$.
-\\
-The dynamic consists in an exchange of particles between connected vertex.
-Moreover, each vertex can be connected with a reservoir that inject, remove or exchange particles.
-Mathematically, this can be described by an infinitesimal generator as follows
+    \Omega:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}^{|V|}
+\end{equation}
+
+The edge dynamics consists in an exchange of particles between connected vertices.
+Moreover, each vertex can be connected with a reservoir that exchanges particles with the external environement.
+Mathematically, this can be described by an infinitesimal generator of the form
 \begin{equation}\label{Generator}
@@
 \end{equation}
-where the quantities $ \omega_{x,y}$ are called conductancies and $\Gamma_{x}$ local inhomogeneities.
+where the quantities $ \omega_{x,y}\geq 0$ are called conductances and $\Gamma_{x}\geq 0$ local inhomogeneities.
 The generator $\mathcal{L}_{x,y}$ is called the \textit{edge generator}, while $\mathcal{L}_{x}$ is called the \textit{site generator}.
-These linear operators act on local functions $f:\Omega\to \mathbb{R}$ as follows
+These linear operators act on functions $f:\Omega\to \mathbb{R}$ as follows
 \begin{equation}
@@
 $\delta_{k}^{x}=(0,\ldots,0,1,0,\ldots,0)$ withe the one in the $k$-th position.
-This means that the edge generator exchanges a particle of type $k$ in the site $x$ with a particle of type $l$ in the site $y$, while the site generator inject a particle of type $k$ and remove a particle of type $l$, both in the site $x$.
+This means that on an edge at rate $\omega_{x,y}n_{k}^{x}n_{l}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{l}^{x}$ a particle of type $l$ is replaced with a particle of type $k$.
 The following Figure \ref{fig:1}, Figure \ref{fig:2} help in understanding the dynamics. 
@@
 \end{figure}\newline \\
-\textbf{Remark}: 
+{\color{blue}\textbf{Remark}: 
     We can always assign the name "empty" to one of the species of particles in the above dynamics (let's say, without loss of generality, the species 1).
@@
     Moreover, if we set $N=2$ and $\twoj=2j$, we exactly retrieve the SEP(2j), where the empty occupation is indeed $2j-\eta_{x}$ where $\eta_{x}$ is the number of (color blind) particles in the site $x$.
-In this sense we can think about the stirring process as the natural generalization of the SEP(2j).
+In this sense we can think about the stirring process as the natural generalization of the SEP(2j).}
     \begin{flushright}
@@
     \end{flushright}
-The process described by \eqref{Generator} is reversible if and only if, for any $k\in\{1,\ldots,N\}$, the boundary parameters $\alpha_{k}^{x}=\alpha_{k}$ $\forall x\in V$.
-The reversible product measure is a Multinuomial distribution of parameter $\twoj$.
-That means that
+The process described by the generator \eqref{Generator} is reversible if and only if, for any $k\in\{1,\ldots,N\}$, the boundary parameters $\alpha_{k}^{x}=\alpha_{k}$ $\forall x\in V$.
+The non-homogeneus reversible product measure has marginals the
 \begin{equation}\label{reversibleMeasure}
-    \mu^{rev}=\bigotimes_{x\in V}\mu^{rev}_{x}\qquad \mu_{x}^{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad :\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
+    \mu^{rev}=\bigotimes_{x\in V}\mu^{rev}_{x}\qquad \mu_{x}^{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad \text{where}\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
 \end{equation}
@@
 Let us notice that the reversible measure is product only over the sites, but not over the species.
-This is due to the exclusion constraint that makes particle interact.
-
-{\color{red}[LET'S SKIP THE PROOF? I THINK IT IS STANDARD!]}.\\
 \subsection{The Lie algebraic description}
 
-%The approach we use to find duality relations is the Lie algebraic one.
-The main idea is to describe the infinitesimal generator (or better, its transposed, i.e.
-the Hamiltonian operator) via a proper combination of the basis of a certain Lie algebra.
-Then, duality will be found by symmetry argument.\\
-
-Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{a,b}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
+Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
 \begin{equation}\label{eq:comgl}
@@
 \end{equation} 
-The dimension of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition:
-\begin{equation}
-	D= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
-\end{equation} 
-The basis elements of the vector space of the representation $\mathbb{C}^{D}$ are denoted by 
-\begin{equation}
-  |n\rangle=  |n_{1},\ldots,n_{N}\rangle\qquad \forall
-    n=(n_{1},\ldots,n_{N})
-\end{equation}
-$\forall n=(n_{1},\ldots,n_{N})\in \chi$ where $\chi:=\left\{n:|n|=\twoj\right\}$ {\color{red}(let us notice that $\Omega=\chi^{|V|}$)?}.
-This vector can be mapped in a one-to-one correspondence with the canonical basis of $\mathbb{C}^{D}$.
+The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition:
+\begin{equation}
+	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
+\end{equation} 
+The basis elements of the vector space of the representation $\mathbb{C}^{M}$ are the column vectors 
+\begin{equation}
+  |n\rangle=  |n_{1},\ldots,n_{N}\rangle
+\end{equation}
+%where $\sum_{k=1}^{N}n_{i}=\nu$. 
 This basis vector satisfy the orthogonality relation
@@
 \end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|=| m_{1},\ldots,m_{N}\rangle^T$.
-
-The explicit actions of the basis element of the algebra on the vectors of the space $\mathbb{C}^{D}$ are the following, for non Cartan and Cartan elements respectively: 
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle$ and $\delta_{m_{k},n{k}}$ is the Kronhecker delta. 
+The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
 \begin{equation}\label{actionE}
 	\begin{cases}
-		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\\[0.1cm]
-		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle
-	\end{cases}\qquad \forall a,b\in\{1,\ldots,N\}
+		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
+		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
+	\end{cases}
 \end{equation}  
 One can check that the generators defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.
-
-We now define the equivalent of \eqref{stateSpace} in the vector notation
- \begin{equation}
-	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
-	\end{equation}
-where we denote 
-\begin{equation}
-|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)\in \Omega'
-\end{equation}
-such that
+The Cartan element $E_{aa}$ conserves the number of particles of type $a$.
+\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
+\begin{equation}
+   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
+\end{equation}
+{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
+By the Lie algebra above we describe the process characterized by the generator \eqref{Generator}. We consider the state space \eqref{stateSpace} composed by
+
+%We now define the equivalent of \eqref{stateSpace} in the vector notation
+% \begin{equation}
+%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
+%	\end{equation}
+%where we denote 
+\begin{equation}
+|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
+\end{equation}
+such that, $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. Moreover, the following orthogonality relations holds:
 \begin{equation}
@@
 \end{equation}
-
-When the state space is discrete, it is useful to write the dynamics of the process in term of an other operator, the Hamiltonian. The relation between these two operator is the following
-\begin{equation}
-H=\mathcal{L}^{T}
-\end{equation}
-
-Following  \cite{belitsky2015self} we define
-\begin{equation}
-    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
-\end{equation}
-where 
-\begin{equation}
-    \langle f|=\sum_{ {\bf n}}f( {\bf n})\langle  {\bf n}|
-\end{equation}
-
-The Hamiltonian operator can be written in term of the basis element of the Lie algebra as
+We introduce the Hamiltonian operator
 
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{k,l=1}^{N}\left(E_{kl}\otimes E_{lk}-E_{ll}\otimes E_{kk}\right)_{x,y}
+H_{x,y}=\sum_{k,l=1}^{N}E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}
  \end{equation}
@@
  \begin{equation}\label{siteHamiltonian}
-H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}-E_{ll}\right)_x
-\end{equation}
-
-Moreover, by the \eqref{coproductC2} and by computing the explicit action of the diagonal part, we can write this Hamiltonian in function of the coproduct of the second Casimir
+H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)
+\end{equation}
+Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$.
+
+We can write this Hamiltonian in function of the coproduct of the second Casimir
 \begin{equation}
@@
 \begin{equation}
-	H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left\{\frac{1}{2}\Delta(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}\otimes\mathbbm{1}\right\}+\sum_{x\in V}\Gamma_{x}\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{k,l}-\twoj\mathbbm{1}\right)
-\end{equation}
-Here we introduced the standard coproduct $\Delta:E_{ab}\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}$ and used that $C_{2}=\twoj(\twoj+N)$.
-
-\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
-\begin{equation}
-   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
-\end{equation}
-{\color{red} This needs to be checked and give alternative form of Hamiltonian?}
+	H_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
+\end{equation}
+Here we introduced the standard coproduct
+\begin{equation}
+\begin{split}
+\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
+E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
+\end{split}
+\end{equation} acting on sites $x,y$ and used that $C_{2}|n\rangle=\twoj(\twoj+N)|n\rangle$.
+
+Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by the following relation:
+\begin{equation}
+H=\mathcal{L}^{T}
+\end{equation}
+The generator can also be expressed as
+
+\begin{equation}
+    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
+\end{equation}
+where 
+\begin{equation}
+    \langle f|=\sum_{ {\bf n}}f( {\bf n})\langle  {\bf n}|
+\end{equation}
+
+\begin{comment}
+We introduce the Hamiltonian operator
+
+\begin{equation}\label{OriginalHamiltonian}
+	\begin{split}
+		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
+	\end{split}
+\end{equation}
+where the edge Hamiltonian is
+\begin{equation}\label{edgeHamiltonian}
+H_{x,y}=\sum_{k,l=1}^{N}E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}
+ \end{equation}
+ and where the site Hamiltonian is
+ \begin{equation}\label{siteHamiltonian}
+H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)
+\end{equation}
+Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$.
+
+We can write this Hamiltonian in function of the coproduct of the second Casimir
+\begin{equation}
+    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
+\end{equation}
+It reads
+\begin{equation}
+	H_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
+\end{equation}
+Here we introduced the standard coproduct
+\begin{equation}
+\begin{split}
+\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
+E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
+\end{split}
+\end{equation} acting on sites $x,y$ and used that $C_{2}|n\rangle=\twoj(\twoj+N)|n\rangle$. 
+\end{comment}
 
@@
 where
-\begin{align}
+\begin{align}\label{Hedge}
 H_{x,y}&=\sum_{k,l=1}^{N}\left(E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}\right)\\
@@
 \end{flushright}
-
+{\color{blue}\subsection{Duality for the reaction diffusion process on a graph}
+[IN CASE WE DECIDE TO ADD THIS PART WE SHOULD DEFINE EVERYTHING PROPERLY... LET'S THINK ABOUT THIS]
+It is possible to prove the absorbing duality also for the family of processes introduced in \cite{casini2022uphill}. Indeed, the Hamiltonain is
+\begin{equation}\label{ReactionDiffusionHamiltonian}
+H=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}H_{x,y}^{RD}+\sum_{x\in V}\Gamma_{x}H_{x}
+\end{equation}
+The site Hamiltonian $H_{x}$ is the one defined in \eqref{siteHamiltonian}
+while the edge Hamiltonian is 
+\begin{equation}
+H_{x,y}^{RD}=H_{x,y}^{S}+H_{x,y}^{SM}+H_{x,y}^{LM}+H_{x,y}^{RM}
+\end{equation}
+with $H_{x,y}^{S}$ is exactly the one defined in \eqref{edgeHamiltonian} and 
+\begin{equation}
+H_{x,y}^{SM}=\sigma_{12}\sum_{a,b=1}^{3}\left(E_{\overline{a}b}^{x}\otimes E_{\overline{b}a}^{y}-E_{bb}^{x}\otimes E_{aa}^{y}\right)
+\end{equation}
+\begin{equation}
+H_{x,y}^{LM}=\left(\Upsilon-2\sigma_{12}-m\right)\sum_{a=1}^{3}\left(E_{\overline{a}a}^{x}\otimes \mathbbm{1}^{y}-E_{aa}\otimes\mathbbm{1}^{x}\right)
+\end{equation}
+\begin{equation}
+H_{x,y}^{RM}=m\sum_{a=1}^{3}\left(\mathbbm{1}^{x}\otimes E_{\overline{a}a}^{y}-\mathbbm{1}^{x}\otimes E_{aa}^{y}\right)
+\end{equation}
+
+The matrix $S$ defined in \eqref{Simmetry_s} is a symmetry also for $H^{RD}$. We first prove it for $H_{x,y}^{SM}$.. We will prove that 
+\begin{equation}\label{symmetrySM}
+\sum_{a,b=1}^{3}[E_{\overline{a}b}^{x}\otimes E_{\overline{b}a}^{y},S]=\sum_{a,b=1}^{3}[E_{bb}^{x}\otimes E_{aa}^{y},S]
+\end{equation}
+The left-hand-side is
+\begin{equation}
+\begin{split}
+&\left[E_{10}^{x},E_{\overline{a}b}^{x}\right]\otimes \left[E_{10}^{y},E_{\overline{b}a}^{y}\right]+\left[E_{10}^{x},E_{\overline{a}b}^{x}\right]\otimes\left[E_{20}^{y},E_{\overline{b}a}^{y}\right]+\left[E_{20}^{x},E_{\overline{a}b}^{x}\right]\otimes\left[E_{10}^{y},E_{\overline{b}a}^{y}\right]+\left[E_{20}^{x},E_{\overline{a}b}^{x}\right]\otimes\left[E_{20}^{y},E_{\overline{b}a}^{y}\right]
+\end{split}
+\end{equation}
+and the right-hand-side is
+\begin{equation}
+\begin{split}
+\left[E_{10}^{x},E_{bb}^{x}\right]\otimes \left[E_{10}^{y},E_{aa}^{y}\right]+\left[E_{10}^{x},E_{bb}^{x}\right]\otimes\left[E_{20}^{y},E_{aa}^{y}\right]+\left[E_{20}^{x},E_{bb}^{x}\right]\otimes\left[E_{10}^{y},E_{aa}^{y}\right]+\left[E_{20}^{x},E_{bb}^{x}\right]\otimes\left[E_{20}^{y},E_{aa}^{y}\right]
+\end{split}
+\end{equation}
+by using the commutators $\forall k=1,2$
+\begin{equation}
+\begin{split}
+&\left[E_{k0},E_{\overline{a}b}\right]=\left(E_{kb}\delta_{\overline{a}0}-E_{\overline{a}0}\delta_{bk}\right)\\
+&\left[E_{k0},E_{\overline{b}a}\right]=\left(E_{ka}\delta_{\overline{b}0}-E_{\overline{b}0}\delta_{ak}\right)\\
+&\left[E_{k0},E_{aa}\right]=\left(E_{ka}\delta_{a0}-E_{a0}\delta_{bk}\right)\\
+&\left[E_{k0},E_{bb}\right]=\left(E_{kb}\delta_{b0}-E_{b0}\delta_{bk}\right)
+\end{split}
+\end{equation}
+and summing over all $a,b\in\{1,2,3\}$ we obtatain \eqref{symmetrySM}. Similarly, we can prove that
+\begin{equation}\label{symmetryM}
+\sum_{a=1}^{3}\left[E_{\overline{a}a}^{x}\otimes \mathbbm{1}^{y},S\right]=\sum_{a=1}^{3}\left[E_{aa}^{x}\otimes \mathbbm{1}^{y},S\right]\qquad \sum_{a=1}^{3}\left[\mathbbm{1}^{x}\otimes E_{\overline{a}a}^{y},S\right]=\sum_{a=1}^{3}\left[\mathbbm{1}^{x}\otimes E_{aa}^{y},S\right]
+\end{equation}
+As a consequence of \eqref{symmetrySM} and \eqref{symmetryM} the Hamiltonian \eqref{ReactionDiffusionHamiltonian} is self-dual with absorbing reservoirs with self-duality matrix given by \eqref{dualityMatrix}.}
 \section{Integrability}\label{sec4}
@@
 \subsection{Mapping to equilibrium?}
+{\color{red}
+check also Appendix A in
+\cite{Alcaraz:1992zc} }
+
+\cite{Sklyanin:1988yz}
 \subsubsection{Quantum inverse scattering method}
@@
 	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
-	Q_{2L}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
 \end{align}
@@
 \begin{equation}
-Q_{2}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
+Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
+\end{equation}
+that is 
+\begin{equation}
+\begin{split}
+Q_{2L}^{0}&=N\left(I^{tot}+2e_{11}^{tot}\right)+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{j=2}^{N}e_{jj}^{tot}
+\\&
++\sum_{i=2}^{N}\left(	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\right)
+\end{split}
 \end{equation}
@@
 \end{equation}
+We have that the eigenvectors and eigenvalues of the equilibrium case are given by
+\begin{equation}
+T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle =\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+\end{equation}
+where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{k=2}^{N}m_{k}$.\\
+We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries.
+For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
+\begin{equation}
+|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{equation}
+
+We replace the above eigenvectors in 
+\begin{equation}\label{eigDELTA}
+T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
+\end{equation}
+and we obtain
+\begin{align*}
+&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\&
++\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\&=
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\end{align*}
+after a change of summation indexes we obtain
+\begin{align*}
+&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\+&
+\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\+&
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\=&
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\end{align*}
+we impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
+\begin{enumerate}
+\item $k_{2}=0$ and $k_{3}=0$
+\begin{equation}\label{cond1}
+T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle
+\end{equation}
+\item $k_{2}=m_{2}+1$ and $k_{3}\in \{0,\ldots,m_{3}\}$
+\begin{equation}\label{cond2}
+\begin{split}
+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle=0
+\end{split}
+\end{equation}
+\item $k_{2}\in\{0,\ldots,m_{2}\}$ and $k_{3}=m_{3}+1$
+\begin{equation}\label{cond3}
+\begin{split}
+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle=0
+\end{split}
+\end{equation}
+\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}\in\{1,\ldots,m_{3}\}$
+\begin{equation}\label{cond4}
+\begin{split}
+&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\=&
+\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\end{split}
+\end{equation}
+\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
+\begin{equation}\label{cond5}
+\begin{split}
+&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+=
+\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\end{split}
+\end{equation}
+\item $k_{2}\in\{1,\ldots,m_{2}\}$ and $k_{3}=0$
+\begin{equation}\label{cond6}
+\begin{split}
+&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+=
+\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\end{split}
+\end{equation}
+\end{enumerate}
+To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1},\eqref{cond2},\eqref{cond3},\eqref{cond4}, \eqref{cond5},\eqref{cond6}.
+\subsection{Bethe equations}
+Describe eigenvalues of $T_0(x)$ following.
+\cite{belliard2}
 \section{Conclusion}

### 2023-03-07 main.tex
reaction
fixedReaction
after fix

@@
 \end{align*}
-thus (\ref{bulkDuality}) is proved.\\
+thus (\ref{bulkDuality}) is proved. \\
 \textbf{The site absorbing duality}\\
@@
 \\+&
-\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \\=&
@@
 To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1},\eqref{cond2},\eqref{cond3},\eqref{cond4}, \eqref{cond5},\eqref{cond6}. 
-\subsection{Bethe equations}
-Describe eigenvalues of $T_0(x)$ following.
-\cite{belliard2}
+{\color{blue}This second property can be proved by using a lower weight representation }
+% \end{itemize}
+We prove the ansatz:
+\begin{align*}
+	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots +
+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
+\begin{align*}
+	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots
+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+
+	\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots +
+	\Delta_{N}^{m_{N}+1}\sum_{k_{2}=0}^{m_{3}}\ldots\sum_{k_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
+\begin{align*}
+		T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots +
+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+then
+\begin{align*}
+T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
+		\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	\\&+
+	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&=
+	\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle
+\end{align*}
+
+For $i\neq 1$ we have
+\begin{equation}
+\begin{split}
+ \sum_{i,j=2}^N [E_{ij}E_{ji},E_{k1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{k1}]+\sum_{i,j=2}^N  [E_{ij},E_{k1}]E_{ji}=\sum_{j=2}^N( E_{kj} E_{j1}+ E_{j1} E_{kj})
+\\&=\sum_{j=2}^N( 2E_{kj} E_{j1}+ [E_{j1}, E_{kj}])=2\sum_{j=2}^N E_{kj} E_{j1}-(N-1)E_{k1}
+ \end{split}
+\end{equation}
+
+\subsection{Bethe ansatz solution}
+Describe eigenvalues of $T_0$ following 
+\cite{Belliard2} 
 \section{Conclusion}

### 2023-03-07 main.tex

@@
 \numberwithin{equation}{section}
+\numberwithin{equation}{subsection}
 
@@
 \subsection{The infinitesimal generator}
-We consider a connecAt each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$.
+We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
+At each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$.
 On each vertex we allow maximal occupancy $\nu\in \mathbb{N}$.
@@
 \end{equation}
-The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ with $\lambda_i\in \mathbb{N}$ and  $\lambda_i\geq \lambda_{i+1}$.
-We are interested in the symmetric finite-dimensional representations with 
+{\color{red}The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.
+We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.}
+We are interested in the {\em symmetric} finite-dimensional representations with 
 \begin{equation}\label{eq:dynkin}
@@
 \end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle$ and $\delta_{m_{k},n{k}}$ is the Kronhecker delta. 
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
 The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
@@
 The Cartan element $E_{aa}$ conserves the number of particles of type $a$.
+
+\noindent
 \textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 

### 2023-03-13 main.tex
label
sec1

@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each site $x\in V$, we describe the occupation with an $N-$dimensional vector in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$.
-On each vertex we allow maximal occupancy $\nu\in \mathbb{N}$.
-Then, the configuration space is
+At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$ at site $x\in V$.
+On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$.
+Then, the configuration space of the process on the graph $G$ is
 \begin{equation}\label{stateSpace}
-    \Omega:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}^{|V|}
-\end{equation}
-
-The edge dynamics consists in an exchange of particles between connected vertices.
-Moreover, each vertex can be connected with a reservoir that exchanges particles with the external environement.
-Mathematically, this can be described by an infinitesimal generator of the form
+    \Omega:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}^{V}
+\end{equation}
+Moreover, we denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$ .\\
+The dynamics consists in an exchange of particles (at Poissonian times) between connected vertices.
+Moreover, each vertex  exchanges particles with the external environement.
+The infinitesimal generator of the process reads
 \begin{equation}\label{Generator}
@@
 These linear operators act on functions $f:\Omega\to \mathbb{R}$ as follows
-\begin{equation}
+\begin{equation}\label{edgeGenerator}
 \mathcal{L}_{x,y}f(n)=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(n-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(n)\right]
 \end{equation}
-\begin{equation}
+\begin{equation}\label{siteGenerator}
     \mathcal{L}_{x}f(n)=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(n+\delta_{k}^{x}-\delta_{l}^{x})-f(n)\right]
@@
 where 
-$\delta_{k}^{x}=(0,\ldots,0,1,0,\ldots,0)$ withe the one in the $k$-th position.
-This means that on an edge at rate $\omega_{x,y}n_{k}^{x}n_{l}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{l}^{x}$ a particle of type $l$ is replaced with a particle of type $k$.
-The following Figure \ref{fig:1}, Figure \ref{fig:2} help in understanding the dynamics. 
+\begin{equation}
+(\delta_{k}^{x})^{y}_{\ell}=\begin{cases}
+1\qquad &\text{if}\quad y=x,\;\ell=k\\
+0\qquad &\text{otherwise}
+\end{cases}
+\end{equation}
+This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{k}^{x}n_{l}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{\ell}^{x}$ a particle of type $\ell$ is replaced with a particle of type $k$.
+See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 
 \begin{figure}
@@
     \end{flushright}
-The process described by the generator \eqref{Generator} is reversible if and only if, for any $k\in\{1,\ldots,N\}$, the boundary parameters $\alpha_{k}^{x}=\alpha_{k}$ $\forall x\in V$.
-The non-homogeneus reversible product measure has marginals the
-\begin{equation}\label{reversibleMeasure}
-    \mu^{rev}=\bigotimes_{x\in V}\mu^{rev}_{x}\qquad \mu_{x}^{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad \text{where}\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
+The process described by the generator \eqref{Generator} is reversiblewith respect to the homogeneus product measure \begin{equation}\label{reversibleMeasure}
+\mu_{rev}=\bigotimes_{x\in V}\mu^{rev}_{x}
+\end{equation}
+when for any $k\in\{1,\ldots,N\}$
+\begin{equation}\label{reversibilityCondition}
+\alpha_{k}^{x}=\alpha_{k}\qquad \forall x\in V
+\end{equation}
+This measure has marginals $\mu_{rev}^{x}$ distributed as 
+\begin{equation}
+ \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad \text{where}\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
+\end{equation}
+namely
+\begin{equation}
+\mu_{rev}^{x}(n^{x})=\frac{\nu}{\prod_{k=1}^{N}n_{k}^{x}}\prod_{k=1}^{N}p_{k}^{n_{k}^{x}}
 \end{equation}
 This can be proven just by imposing the detailed balance conditions for the edge and for the site generators.
-Let us notice that the reversible measure is product only over the sites, but not over the species.
+If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own density $\alpha^{x}=(\alpha_{1}^{x},\ldots,\alpha_{N}^{x})$ and currents will arise when at least two of them are different.
 \subsection{The Lie algebraic description}
@@
 \end{equation}
-{\color{red}The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.
-We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.}
+The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.
+We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
 We are interested in the {\em symmetric} finite-dimensional representations with 
@@
 \end{equation} 
-The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition:
+The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
 \begin{equation}
@@
 \end{equation} 
-The basis elements of the vector space of the representation $\mathbb{C}^{M}$ are the column vectors 
-\begin{equation}
-  |n\rangle=  |n_{1},\ldots,n_{N}\rangle
+The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
+\begin{equation}
+  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
 \end{equation}
 %where $\sum_{k=1}^{N}n_{i}=\nu$. 
-This basis vector satisfy the orthogonality relation
+This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
 \begin{equation}\label{ortho}
@@
 \end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
 The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
@@
 \end{equation}  
-One can check that the generators defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.
-The Cartan element $E_{aa}$ conserves the number of particles of type $a$.
+One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.
 
@@
 {\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-By the Lie algebra above we describe the process characterized by the generator \eqref{Generator}. We consider the state space \eqref{stateSpace} composed by
+By the Lie algebra above we describe the process characterized by the generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements
 
@@
 \end{equation}
-such that, $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$. Moreover, the following orthogonality relations holds:
+where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$.
+The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
 \begin{equation}
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{k,l=1}^{N}E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}
+H_{x,y}=\sum_{k,l=1}^{N}\left(E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}\right)
  \end{equation}
@@
 Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
-
-We can write this Hamiltonian in function of the coproduct of the second Casimir
+Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by the following relation:
+\begin{equation}
+H=\mathcal{L}^{T}
+\end{equation}
+The generator can also be expressed as
+
+\begin{equation}
+    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
+\end{equation}
+where 
+\begin{equation}
+    \langle f|=\sum_{ {\bf n\in \Omega}}f( {\bf n})\langle  {\bf n}|
+\end{equation}
+
+We can write this Hamiltonian as a function of the coproduct of the second Casimir
 \begin{equation}
@@
 \end{equation}
-It reads
-\begin{equation}
-	H_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
-\end{equation}
-Here we introduced the standard coproduct
-\begin{equation}
-\begin{split}
-\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
-E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
-\end{split}
-\end{equation} acting on sites $x,y$ and used that $C_{2}|n\rangle=\twoj(\twoj+N)|n\rangle$.
-
-Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by the following relation:
-\begin{equation}
-H=\mathcal{L}^{T}
-\end{equation}
-The generator can also be expressed as
-
-\begin{equation}
-    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
-\end{equation}
-where 
-\begin{equation}
-    \langle f|=\sum_{ {\bf n}}f( {\bf n})\langle  {\bf n}|
+that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$. \\
+ Considering two sites $x,y\in \mathcal{E}$ the standard coproduct operator is defined as 
+\begin{equation}
+\begin{split}
+\Delta^{x,y}:gl(N)&\to gl(N)\otimes gl(N)\\
+E_{ab}&\to E_{ab}^{x}\otimes \mathbbm{1}^{y}+\mathbbm{1}^{x}\otimes E_{ab}^{y}
+\end{split}
+\end{equation}
+therefore, we have 
+\begin{equation}
+\Delta^{x,y}(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}^{x}\otimes E_{ba}^{y}+C_{2}^{x}\otimes \mathbbm{1}^{y}+\mathbbm{1}^{x}\otimes C_{2}^{y}
+\end{equation}
+
+One can check that 
+\begin{equation}\label{hamiltonianCasimir}
+	H_{x,y}=\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}
 \end{equation}

### 2023-03-13 main.tex
DualityCheck

@@
 \section{Duality}
-Consider two Markov processes $(\eta_{t})_{t\geq 0}$ on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ on a state space $\widetilde{\Omega}$.
-We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in \Omega$, $\forall \xi\in \widetilde{\Omega}$ and $\forall t\geq 0$ we have
-\begin{equation}
-    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t}\right]
-\end{equation}
-Moreover, if $\eta_{t}$ and $\xi_{t}$ are the same process, we talk about \textit{self-duality} and \textit{self-duality function}.
-The duality property can also be characterized by a relation with the generators.
-Let $\mathcal{L}$ be the generator of $\eta_{t}$ and let $\mathcal{L}_{dual}$ be the generator of $\xi_{t}$, then we say that two process are in a duality relation if
-\begin{equation}
-    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\mathcal{L}_{dual}D(\eta,\cdot)\right)(\xi)
-\end{equation}
-\subsection{Algebraic formulation}
-In particular, if the process has a countable space, the duality is a matrix, and we can rewrite the above relation with the Hamiltonians has follows
-\begin{equation}\label{dualityHamiltonian}
-    H^{T}D=DH_{dual}
-\end{equation}
-By \eqref{dualityHamiltonian}, we can see the duality matrix as a similarity transformation between the original and the dual Hamiltonian. \\
-We now construct our main result: \textit{the process defined in \eqref{Generator} is self dual with absorbing boundaries}.
-Thus, we have to construct a duality matrix $D$ and an Hamiltonian $H_{dual}$ in order to fulfill the equation \eqref{dualityHamiltonian}.
-\\
-The self-dual process is defined in the self-dual state space 
-\begin{equation}\widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{|V|}\end{equation} with elements
-\begin{equation}
-	|\xi\rangle=\bigotimes_{x\in V}\left(|r_{0},\ldots,r_{N}\rangle_{x}\otimes |m_{1}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}\rangle_{x}\right)
-\end{equation}
-The self-dual Hamiltonian is the following
-\begin{equation}
-	\begin{split}
-		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x,\varepsilon(x)}
-	\end{split}
-\end{equation}
-where
-\begin{align}\label{Hedge}
-H_{x,y}&=\sum_{k,l=1}^{N}\left(E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}\right)\\
-\widetilde{H}_{x,\varepsilon(x)}&=\left(\sum_{i=2}^{N}\alpha_{i}^{x}\right)\sum_{k=2}^{N}\left((a^{\dagger}_{k})_{\varepsilon(x)}E_{1k}^{x}-E_{kk}^{x}\right)
-\end{align}
-and where  $(a^{\dagger}_{k})_{\varepsilon(x)}$ is a bosonic creation operator acting on an extra site attached to $x$ and denoted by $\varepsilon(x)$.
-Let us notice that edge part of the dual Hamiltonian is exactly the one of \eqref{edgeHamiltonian} (self-duality).
-The site part only replace any particle of type $k\in \{2,\ldots,N\}$ with a type $1$  and put them into an extra site, attached to $x$.
-Dual particles of type $k$ are piled up into an this extra site, and they leave the graph forever.
-This means that the species $1$ plays a special role in the duality.
-If we think about this $1$ species as the empty, we can interpret the dual process as an absorbing dual, i.e.
-a process that eventually empties the graph.\\
-Associated with this dual process there is the following duality matrix 
+\subsection{Definition of duality}
+Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
+We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have
+\begin{equation}
+    \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t})\right]
+\end{equation}
+where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
+The duality definition can also be formulated as a relation between the generators.
+Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$ if
+\begin{equation}\label{dualityRelationGenerator}
+    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)
+\end{equation}
+\textbf{Remark}:
+in the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the processes are self-dual with respect to a self-duality function.
+\newline
+\newline
+\textbf{Remark}:
+when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
+Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as
+\begin{equation}
+    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})
+\end{equation}
+that can be read as
+\begin{equation}\label{dualityIntertwines}
+    \mathcal{L}D=D\widetilde{\mathcal{L}}^{T}
+\end{equation}
+where the superscript $T$ denotes the matrix transposition.
+Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining transformation between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$.
+Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads as
+\begin{equation}\label{DualityRelation}
+    H^{T}D=D\widetilde{H}
+\end{equation}
+where $\widetilde{H}=\widetilde{\mathcal{L}}^{T}$.
+\subsection{Duality for the generalized multi-species boundary driven stirring process}
+We now state our duality result.
+The process $|n\rangle$ with Hamiltonian \eqref{} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\xi\rangle$ defined on the enlarged state space
+\begin{equation}
+    \widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{V}
+\end{equation}
+with elements
+\begin{equation}
+    |\xi\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
+\end{equation}
+where $r_{x}^{k}$ denotes the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x\in V$ and $m_{k}^{\widetilde{x}}$ denotes the number of particles of species $k\in \{2,\ldots,N\}$ at an extra-site $\widetilde{x}$ connected to the site $x\in V$.\\
+The Hamiltonian of the dual process reads as
+\begin{equation}\label{DualHamiltonian}
+    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
+\end{equation}
+
+where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
+\begin{equation}\label{siteDualHamiltonian}
+    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
+\end{equation}
+By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
+$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
+The Hamiltonians \eqref{Hamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
+\begin{equation}
+    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
+\end{equation}
+We denote by $D_{x}$ the site part. This is defined as 
+\begin{equation}
+    D_{x}=R_{x}\exp{(E^{x})}
+\end{equation}
+with $E$
+\begin{equation}
+    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
+\end{equation}
+that implies 
+\begin{equation}
+    \exp{(E^{x})}=I+E^{x}
+\end{equation}
+and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
+\begin{equation}
+    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+\end{equation}
+where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
+We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as
 \begin{equation}\label{dualityMatrix}
-	D=\prod_{x\in V}\left(\sum_{m_{2}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\alpha_{0}^{x}+\ldots+\alpha_{N}^{x}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{\varepsilon(x)}\otimes R_{x}e^{E}_{x} \right)
-	=\prod_{x\in V}\left(D_{\varepsilon(x)}\otimes D_{x}\right)
-\end{equation}
-where we define the \textit{symmetry operator} as
-\begin{equation}\label{e_def}
-	E=\sum_{a=2}^{N}e_{a1}
-\end{equation}
-and the \textit{cheap duality matrix} as 
-\begin{equation}
-	R^{-1}_{x}=\sum_{n\in \chi}\frac{(2j)!}{n_{1}^{x}!\ldots n_{N}^{x}!}|n_{1},\ldots,n_{N}\rangle_{x}\langle n_{1},\ldots,n_{N}|_{x}%\quad \forall n\in \chi
-\end{equation}
-Moreover, the element of the matrix \eqref{dualityMatrix} are given by
-\begin{equation}\label{dualityElements}
-	D(n,\xi)=\langle n|D|\xi\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{(2j)!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\right)
-\end{equation}
-\subsubsection{Proof of the duality relation}
-\textbf{The transposition property of the cheap duality}: \\
-This cheap duality matrix has the following \textit{transposition property}:
-\begin{equation}\label{transpositionR}
-	\left(e_{ba}\right)^{T}=R e_{ab}R^{-1}\quad \forall a,b\in\{0,1,\ldots,N\}
-\end{equation}
-Indeed, for any configuration $\mathbf{n},\mathbf{r}\in \Omega$, by using \eqref{matrixFormulaE} we obtain
-\begin{align*}
-	R e_{ab}R^{-1}=&\sum_{r\in\chi}\left(\frac{r_{1}!\ldots r_{N}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots, r_{N}|\right)
+D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+\end{equation}
+On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph.
+On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$.
+This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites.
+Thinking about the type $1$ as the hole, similarly to what happens in the SEP(2j)\cite{GioaGiardinaGibertiFrank}, the graph is eventually emptied.
+\subsection{Proof of the duality relation}\label{subsectionDualityProof}
+To prove the duality relation between \eqref{} and \eqref{DualHamiltonian} with the duality matrix \eqref{dualityMatrix} we shall show that 
+\begin{equation}
+    H^{T}D=D\widetilde{H}
+\end{equation}
+Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
+\begin{equation}\label{edgeDualRealtion}
+    H_{x,y}^{T}D=DH_{x,y}\qquad \forall x,y\in \mathcal{E}
+\end{equation}
+and for the site Hamiltonians 
+\begin{equation}\label{siteDualRelation}
+    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
+\end{equation}
+%The key idea behind the proof of \eqref{edgeDualRealtion} is that it is possible to write the Hamiltonian \eqref{} as a function of the second Casimir of the $gl(N)$ Lie algebra.
+Finding a symmetry $S$ of this element, will imply of having a symmetry of the Hamiltonian.
+By the reversibility of the process one can make $S$ act on a proper matrix (called cheap duality) and obtain
+\paragraph{Proof of \eqref{edgeDualRealtion}}
+The proof of the edge duality relation relies on two facts: first the existence of a diagonal matrix, arising from the reversible measure, that is already a duality for the Hamiltonian (in literature called 'cheap' duality matrix, see \cite{}); second the possibility of finding a proper symmetry of the Hamiltonian.
+\\We first introduce the cheap duality matrix
+\begin{equation}\label{transpositionPropertyR}
+R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+\end{equation}
+This is diagonal with the inverse of the masses of the reversible measure \eqref{reversibleMeasure}. 
+This matrix connects the generators of the algebra $E^{x}_{ab}$ with their transposed $(E_{ab}^{x})^{T}$ by the following relation
+\begin{equation}
+(E_{ab}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
+\end{equation}
+Indeed, we have
+\begin{align*}
+RE_{ab}^{x}R^{-1}=&\sum_{r\in\chi}\left(\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|\right)
 	\\&
-	\sum_{s\in \chi,}\left(s_{b}|s_{1},\ldots,s_{a}+1,\ldots,s_{b}-1,\ldots s_{N}\rangle \langle s_{1},\ldots,s_{N}|\right)
+	\sum_{s\in \chi,}\left(s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 	\\&
-	\sum_{n\in\chi}\left(\frac{(2j)!}{n_{1}!\ldots n_{N}!}|n_{1},\ldots,n_{N}\rangle \langle n_{1},\ldots, n_{N}|\right)=
+	\sum_{n\in\chi}\left(\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|\right)
+	\\=&
+	\sum_{r,n\in \chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{0}^{x},\ldots, r_{N}^{x}|
+	\frac{\nu!}{n_{1}^{x}!\ldots n_{N}^{x}!}n_{b}^{x}
  \\&
-	\sum_{r,n\in \chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle \langle r_{0},\ldots, r_{N}|
-	\frac{(2j)!}{n_{1}!\ldots n_{N}!}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|=\diamond
-\end{align*}
-By using orthogonality relation \eqref{ortho}\begin{align*}
-\diamond=&\sum_{r\in \chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}\frac{(2j)!}{r_{1}!\ldots (r_{a}-1)!\ldots(r_{b}+1)!\ldots r_{N}!}(r_{b}+1)|r_{1},\ldots,r_{N}\rangle \langle r_{0},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
-	\\=&\sum_{r\in\chi}\frac{r_{1}!\ldots r_{N}!}{(2j)!}\frac{(2j)!}{r_{1}!\ldots (r_{a}-1)!\ldots(r_{b}+1)!\ldots r_{N}!}(r_{b}+1)\frac{r_{a}}{r_{a}}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
+ \qquad |n_{1}^{x},\ldots,n_{a}^{x}+1,\ldots,n_{b}^{x}-1,\ldots n_{N}^{x}\rangle \langle n_{1}^{x},\ldots,n_{N}^{x}|
+ \\=&
+ \sum_{r\in \chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}\frac{\nu!}{r_{1}^{x}!\ldots (r_{a}^{x}-1)!\ldots(r_{b}^{x}+1)!\ldots r_{N}^{x}!}(r_{b}^{x}+1)
+ \\&\qquad
+ |r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{0}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
+	\\=&\sum_{r\in\chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}\frac{\nu!}{r_{1}^{x}!\ldots (r_{a}^{x}-1)!\ldots(r_{b}^{x}+1)!\ldots r_{N}^{x}!}(r_{b}^{x}+1)\frac{r_{a}^{x}}{r_{a}^{x}}
+ \\& \qquad
+ |r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
 	\\=&\sum_{r\in \chi}
-	r_{a}|r_{1},\ldots,r_{N}\rangle \langle r_{1},\ldots,r_{a}-1,\ldots,r_{b}-1,\ldots,r_{N}|
+	r_{a}^{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
 	\\=&
-	\left(e_{ba}\right)^{T}
-\end{align*}
-\textbf{The edge self-duality}\\
-The second Casimir $C_{2}$ is a central element of $gl(N)$. Thus, every element of $gl(N)$ is a symmetry of $C_{2}$.
-Let's chose the operator $E$ defined in \eqref{e_def}, then $\Delta(E)$ is a symmetry of $\Delta(C_{2})$.
-In order to preserve a product structure of the duality matrix, we make the symmetry exponential:
-\begin{equation}\label{Simmetry_s}
-	S=e^{\Delta(E)}
-\end{equation}
-By considering two sites $x,y$:
-\begin{equation}
-	\begin{split}
-		S&=e^{\Delta(E)}=e^{(\mathbbm{1}\otimes E+E\otimes \mathbbm{1})}=e^{\mathbbm{1}\otimes E}e^{E\otimes \mathbbm{1}}=\sum_{k=0}^{N}\frac{\left(\mathbbm{1}\otimes E\right)^{k}}{k!}\sum_{j=0}^{N}\frac{\left(E\otimes \mathbbm{1}\right)^{j}}{j!}
+	\left(E_{ba}^{x}\right)^{T}
+\end{align*}
+where in the third to last equation we multiplied and divided for $r_{a}^{x}$. 
+The relation \eqref{transpositionPropertyR} implies that 
+\begin{equation}
+    H_{x,y}^{T}=\left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}
+\end{equation}
+We now look for a symmetry of the Hamiltonian.
+As shown in \eqref{}, it is possible to write the Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$.
+We say that a matrix $A\in gl(N)$ is symmetry of the Casimir $C_{2}$ if
+\begin{equation}
+    [A,C_{2}]=0
+\end{equation}
+By the definition of the standard coproduct operator, it is possible to show that
+\begin{equation}
+    [A,C_{2}]=0\qquad \Longrightarrow \qquad \left[\Delta(A),\Delta(C_{2})\right]=0
+\end{equation}
+ $C_{2}$ is a central element of $gl(N)$, then it commutes with every element of the algebra. 
+We chose as a symmetry 
+\begin{equation}\label{equationE}
+    E^{x}=\sum_{k=2}E_{a1}^{x}
+\end{equation}
+As a consequence of the previous considerations we can state that $E^{x}$ is a symmetry for the Hamiltonian \eqref{edgeHamiltonian}. We take the exponential of this symmetry by introducing
+\begin{equation}\label{symmetry}
+    S_{x,y}=\exp{(\Delta(E^{x}))}
+\end{equation}
+This operator can be rewritten as 
+\begin{equation}
+	\begin{split}
+		S&=e^{\Delta^{x,y}(E)}=\exp{(\mathbbm{1}^{x}\otimes E^{y}+E^{x}\otimes \mathbbm{1}^{y})}=\exp{(\mathbbm{1}^{x}\otimes E^{y})} \exp{(E^{x}\otimes \mathbbm{1}^{y})}\\&=\sum_{k=0}^{N}\frac{\left(\mathbbm{1}^{y}\otimes E^{x}\right)^{k}}{k!}\sum_{j=0}^{N}\frac{\left(E^{x}\otimes \mathbbm{1}^{y}\right)^{j}}{j!}=
+		\left(\mathbbm{1}^{x}\otimes \sum_{k=0}^{N}\frac{(E^{y})^{k}}{k!}\right)\left(\sum_{j=0}^{N}\frac{(E^{x})^{j}}{j!}\otimes \mathbbm{1}^{y}\right)\\&=\left(\mathbbm{1}^{x}\otimes \exp{({E}^{y})}\right)\left(\exp{(E^{x})}\otimes \mathbbm{1}^{y}\right)\\&=\exp{(E^{x})}\otimes \exp{(E^{y})}
+	\end{split}
+\end{equation}
+Moreover, by the exponential series of \eqref{equationE}, we have 
+\begin{equation}
+   \exp{(E^{x})}\otimes \exp{(E^{y})}= \left(\mathbbm{1}^{x}+E^{x}\right)\otimes \left(\mathbbm{1}^{y}+E^{y}\right)
+\end{equation}
+Since \eqref{equationE} is a symmetry for $C_{2}$, then we have that
+\begin{equation}\label{commutationSymm-edgeHamiltonian}
+\left[H_{x,y},S\right]=\left[H_{x,y},\exp{(E^{x})}\otimes \exp{(E^{y})}\right]=0
+\end{equation}
+By using \eqref{transpositionPropertyR} and \eqref{commutationSymm-edgeHamiltonian} we obtain
+\begin{equation}
+    \begin{split}
+        H_{x,y}^{T}D=&\left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}D
+        \\=&
+        \left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}\left(R_{x}\otimes R_{y}\right)
+        \\&
+        \left(\left(\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)\bigotimes_{z\in V\,:\,z\neq x,y}(D_{z}\otimes D_{\widetilde{z}})
+        \\=&
+        \left(R_{x}\otimes R_{y}\right)H_{x,y}\left(\left(\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)\bigotimes_{z\in V\,:\,z\neq x,y}(D_{z}\otimes D_{\widetilde{z}})
+    \\=&
+    \left(\left(R_{x}\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(R_{y}\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)H_{x,y}\bigotimes_{z\in V\,:\, z\neq x,y}\left(D_{z}\otimes D_{\widetilde{z}}\right)
+    \\=&
+    D H_{xy}
+    \end{split}
+\end{equation}
+therefore \eqref{edgeDualRealtion} is proved. 
+\paragraph{Proof of \eqref{siteDualRelation}} The proof of the site duality relations relies on the Hadamard Lemma that, $\forall E,A \in gl(N)$, reads as 
+\begin{equation}\label{HadamardFormula}
+    \exp{(-E)}A\exp{(E)}=A-\left[E,A\right]+\frac{1}{2!}\left[E,\left[E,A\right],\right]-\frac{1}{3!}\left[E,\left[E,\left[E,A\right]\right]\right]+\ldots
+\end{equation}
+ By \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
+\begin{equation}
+    \begin{split}
+H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)^{T}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}
+    \end{split}
+\end{equation}
+we multiply both sides for $R_{x}\exp{(E^{x})}$
+\begin{equation}
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
+\end{equation}
+we insert the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ in the right hand side
+\begin{equation}\label{intermediateTransposeSite}
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
+\end{equation}
+we apply the Hadamard's formula \eqref{HadamardFormula} to 
+\begin{equation}
+    \exp{(-E^{x})}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
+\end{equation}
+We compute the following quantities by the commutation relations \eqref{}:
+\begin{itemize}
+    \item for all $k\neq 1$ 
+\begin{equation}
+    \begin{split}
+        \exp{(-E^{x})}E_{k1}^{x}\exp{(E^{x})}=E_{k1}^{x},
+    \end{split}
+\end{equation}
+\begin{equation}
+    \begin{split}
+    \exp{(-E^{x})}E_{kk}^{x}\exp{(E^{x})}=E_{kk}^{x}+E_{k1}^{x}
+    \end{split}
+\end{equation}
+and
+\begin{equation}
+\begin{split}
+    \exp{(-E^{x})}E_{1k}^{x}\exp{(E^{x})}=E_{1k}^{x}+E_{11}^{x}-\sum_{a=2}^{N}\left(E_{a1}^{x}+E_{ak}^{x}\right)
+\end{split}
+\end{equation}
+Indeed we have the following commutators at the first order:
+\begin{align*}
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{kk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{k1}-E_{k1}^{x}\delta_{ak}\right)
+\end{align*}
+and 
+\begin{align*}
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{1k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{11}^{x}\delta_{ak}\right)=\sum_{a=2}^{N}E_{ak}^{x}-E_{11}^{x};
+\end{align*}
+and the following commutators at the second order:
+\begin{align*}
+&\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1}^{x},E_{ak}^{x}\right]-\sum_{b=2}^{N}\left[E_{b1}^{x},E_{11}^{x}\right]=\sum_{a,b=2}^{N}\left(E_{bk}^{x}\delta_{a1}-E_{a1}^{x}\delta_{bk}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)\\=&-2\sum_{a=2}^{N}E_{a1}^{x};
+\end{align*}
+from the third on-wards all commutators zero. 
+\item for all $k,l\neq 1$
+\begin{equation}
+        \begin{split}
+    \exp{(-E^{x})}E_{lk}^{x}\exp{(E^{x})}=E_{kl}^{x}+E_{l1}^{x}
+    \end{split}
+\end{equation}
+Indeed the first commutator gives
+\begin{align*}
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{lk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{l1}-E_{l1}^{x}\delta_{ak}\right)=-E_{l1}^{x};
+\end{align*}
+and the from the second commutator on-wards they are all zero.
+\item for the matrix $E_{11}^{x}$
+\begin{equation}
+    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{a=2}^{N}E_{a1}^{x}
+\end{equation}
+indeed the first commutator gives
+\begin{align*}
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{lk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{l1}^{x}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1}^{x};
+\end{align*}
+and the from the second commutator on-wards they are all zero.
+\end{itemize}
+Therefore we have
+\begin{equation}
+\begin{split}
+    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{l=1}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}\\&=
+     \exp{(-E^{x})}\sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
+     + \exp{(-E^{x})}\sum_{k=1}^{N}\sum_{l=2}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
      \\&=
-		\left(\mathbbm{1}\otimes \sum_{k=0}^{N}\frac{E^{k}}{k!}\right)\left(\sum_{j=0}^{N}\frac{E^{j}}{j!}\otimes \mathbbm{1}\right)=\left(\mathbbm{1}\otimes e^{E}\right)\left(e^{E}\otimes \mathbbm{1}\right)=e^{E}\otimes e^{E}
-		\\&=e_{x}^{E} e^{E}_{y}
-	\end{split}
-\end{equation}
-Since the Hamiltonian \eqref{OriginalHamiltonian}, can be written as a linear function of the coproduct of the second Casimir, we have \begin{equation}[H_{x,y},e^{\Delta (C_{2})}]=0\end{equation} and thus \begin{equation}\label{symmetryH-C}[H_{x,y},e^{E}_{x}e^{E}_{y}]=0\end{equation} then the operator \eqref{Simmetry_s} is also a symmetry for the Hamiltonian.
-Since the duality matrix \eqref{dualityMatrix} is product over the vertex of the graph it is enough to prove that $\forall x,y\in \mathcal{E}$:
-\begin{align}
-	H_{x,y}^{T}D=DH_{x,y}\label{bulkDuality}
-\end{align}
-For a fixed edge we only have $D_{x}D_{y}$. 
-\begin{align*}
-	H_{x,y}^{T}D&=D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}H_{x,y}R_{x}^{-1}R_{y}^{-1}R_{x}R_{y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}D_{z}
+     \sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{jk}^{x}+E_{l1}^{x})-E_{11}^{x}+\sum_{j=2}^{N}E_{j1}^{x}\right)+\sum_{k=1}^{N}\sum_{l=2}^{N}\left(E_{lk}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{l1}^{x}\right)
      \\&=
-	D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}H_{x,y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}D_{z}
-\end{align*} 
-By exploiting \eqref{symmetryH-C}
-\begin{align*}
-	H_{x,y}^{T}D&=	D_{\varepsilon(x)}D_{\varepsilon(y)}\otimes R_{x}R_{y}e^{E}_{x}e^{E}_{y}\prod_{z\neq x,y}D_{e(z)}\otimes D_{z}H_{x,y}=
-	DH_{x,y}
-\end{align*}
-thus (\ref{bulkDuality}) is proved. \\
-\textbf{The site absorbing duality}\\
-For the sake of notation we remove the superscripts "$x$" from the operators $E_{ab}$ and from the reservoirs densities $\alpha_{k}$.
-Exploiting again the product form of the duality matrix we can just show that, $\forall x\in V$ the following relation is true
-\begin{equation}\label{boundaryDuality}
-    	H_{x}^{T}D=D\widetilde{H}_{x,\varepsilon(x)}
-\end{equation}
-For the sake of notation and without loss of generality we restrict to the case where $N=3$. \\
-The transpose of the single site Hamiltonian reads as
-\begin{equation}
-	\begin{split}
-	H_{x}^{T}&=\sum_{k=1}^{3}\alpha_{k}\left[E_{kl}-E_{ll}\right]^{T}\\&=
-	\alpha_{1}\left[E_{12}-E_{22}\right]^{T}+\alpha_{1}\left[E_{13}-E_{33}\right]^{T}+\alpha_{2}\left[E_{21}-E_{11}\right]^{T}\\&+\alpha_{2}\left[E_{23}-E_{33}\right]^{T}+
-	\alpha_{3}\left[E_{31}-E_{11}\right]^{T}+\alpha_{3}\left[E_{32}-E_{22}\right]^{T}
-	\end{split}
-\end{equation}
-By multiplying with the single site duality matrix, i.e. $D_{x}=R_{x}e^{E}_{x}$, by using \eqref{transpositionR} and by inserting the identity operator $e^{E}_{x}e^{-E}_{x}$ we obtain 
-\begin{equation}\label{transposeRBoundary}
-	\begin{split}
-	H^{T}_{x}R_{x}e_{x}^{E}&=R_{x}e_{x}^{E}e_{x}^{-E}\left\{\alpha_{1}\left[E_{21}-E_{22}\right]+\alpha_{1}\left[E_{31}-E_{33}\right]+\alpha_{2}\left[E_{12}-E_{11}\right]\right.\\&+\left.\alpha_{2}\left[E_{32}-E_{33}\right]+
-	\alpha_{3}\left[E_{13}-E_{11}\right]+\alpha_{3}\left[E_{23}-E_{22}\right]\right\}R^{-1}_{x}R_{x}e^{E}_{x}\\=&
-	R_{x}e_{x}^{E}e_{x}^{-E}\left\{\alpha_{1}\left[E_{21}-E_{22}\right]+\alpha_{1}\left[E_{31}-E_{33}\right]+\alpha_{2}\left[E_{12}-E_{11}\right]\right.\\&+\left.\alpha_{2}\left[E_{32}-E_{33}\right]+
-	\alpha_{3}\left[E_{13}-E_{11}\right]+\alpha_{3}\left[E_{23}-E_{22}\right]\right\}e^{E}_{x}
-	\end{split}
-\end{equation}
-By the Hadamard's formula:
-\begin{equation}
-	e^{-E}Ae^{E}=A-\left[E,A\right]+\frac{1}{2!}\left[E,\left[E,A\right]\right]-\frac{1}{3!}\left[E,\left[E,\left[E,A\right]\right]\right]+\ldots
-\end{equation}
-we obtain 
-\begin{equation}
-	\begin{split}
-	H^{T}_{x}R_{x}e_{x}^{E}&=R_{x}e_{x}^{E}\left\{\alpha_{1}\left(e_{21}-e_{22}-e_{21}\right)+\alpha_{1}\left(e_{31}-e_{33}-e_{31}\right)\right.
-\\ &+ \left.
-\alpha_{2}\left(e_{12}-e_{22}+e_{11}-e_{32}-e_{21}-e_{31}-e_{11}+e_{21}+e_{31}\right)+\alpha_{2}\left(e_{32}-e_{31}-e_{33}-e_{31}\right)\right.
-\\&+\left.
-	\alpha_{3}\left(e_{13}-e_{33}-e_{23}+e_{11}-e_{21}-e_{31}-e_{11}+e_{21}+e_{31}\right)+\alpha_{3}\left(e_{23}+e_{21}-e_{22}-e_{21}\right)\right\}
-	\end{split}
-\end{equation}
-then, with simple computations,
-\begin{equation}\label{nonStochDuality}
-	\begin{split}
-	H^{T}_{x}R_{x}e_{x}^{E}&=R_{x}e_{x}^{E}\left\{\alpha_{1}(-E_{22})+\alpha_{1}(-E_{32})+\alpha_{2}(E_{12}-E_{22}-E_{31})\right.\\&+\left.
-\alpha_{2}(E_{32}-E_{33})+\alpha_{3}(E_{13}-E_{33}-E_{23})+\alpha_{3}(E_{23}-E_{22})\right\}\\&=
-	R_{x}e_{x}^{E}\left\{\left(\alpha_{2}E_{12}-(\alpha_{1}+\alpha_{2}+\alpha_{2})E_{22}\right)+\left(\alpha_{3}E_{13}-(\alpha_{1}+\alpha_{2}+\alpha_{3})E_{33}\right)\right\}
-	\\&=
-	R_{x}e_{x}^{E}(\alpha_{1}+\alpha_{2}+\alpha_{3})\left\{\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}-E_{22}\right)+\left(\frac{\alpha_{3}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{13}-E_{33}\right)\right\}
-\end{split}
-\end{equation}
-We recognize $D_{x}=R_{x}e^{E}_{x}$. However, the matrix that multiplies it in the right hand side of the above equation is not a stochastic matrix. Then, we use the \textit{extra site trick}. 
-Let's multiply both sides for 
-\begin{equation}
-\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|
-\end{equation}
-we have that the right-hand-side of \eqref{nonStochDuality} becomes
-\begin{equation}\label{stepTrick}
-\begin{split}
-&(\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}-E_{22}\right)
-\\+&
-(\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{3}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{13}-E_{33}\right)
-\end{split}
-\end{equation}
-Consider the creation operators defined in \eqref{creationOperators}, thus we have
-\begin{equation}\label{trick}
-	\langle m_{2}+1,m_{3}|a_{2}^{+}=\langle m_{2},m_{3}|\qquad	\langle m_{2}, m_{3}+1|a_{3}^{+}=\langle m_{2},m_{3}|
-\end{equation}
-Let's consider 
-\begin{equation}
-    (\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}\right)
-\end{equation}
-Let's replace the \eqref{trick} in the above quantity, then we have
-\begin{equation}
-\begin{split}
-(\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2}+1,m_{3}|a_{2}^{\dagger}D_{x}\left(\frac{\alpha_{2}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{12}\right)
-\end{split}
-\end{equation}
-By shifting the summation indexes 
-\begin{equation}\label{trick1}
-\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|D_{x}\left[a_{2}^{\dagger}E_{12}\right]
-\end{equation}
-We can rewrite similarly also the term in \eqref{stepTrick}
-\begin{equation}\label{trick2}
-    (\alpha_{1}+\alpha_{2}+\alpha_{3})\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}D_{x}\langle m_{2},m_{3}|\left(\frac{\alpha_{3}}{(\alpha_{1}+\alpha_{2}+\alpha_{3})}E_{13}\right)
-\end{equation}
-Thus, by putting together \eqref{stepTrick}, \eqref{trick1} and making the same computations for \eqref{trick2} we finally obtain
-\begin{equation}
-\begin{split}
-&\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|D_{x}\left[a_{2}^{\dagger}E_{12}-E_{22}\right]\\ +&
-\sum_{m_{2}\in\mathbb{N}_{0}}	\left(\frac{\alpha_{2}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{2}}\sum_{m_{3}\in \mathbb{N}_{0}}\left(\frac{\alpha_{3}}{\alpha_{1}+\alpha_{2}+\alpha_{3}}\right)^{m_{3}}\langle m_{2},m_{3}|D_{x}\left[a_{x}^{\dagger}E_{13}-E_{33}\right]
-\end{split}
-\end{equation}
-That means 
-\begin{equation}
-	H^{T}_{x}D=D\widetilde{H}_{x,\varepsilon(x)}
-\end{equation}
-\textbf{Elements of the dual matrix}\\
-We aim to prove \eqref{dualityElements}. Let's first observe that from \eqref{transpositionR}
-\begin{equation}
-R_{x}e_{x}^{E_{21}+\ldots+E_{N1}}=(e^{E_{12}+\ldots+E_{1N}}_{x})^{T}R_{x}
-\end{equation}
-let's work for a fixed site $x$
-\begin{align*}
-	 &\langle n|D_{x}D_{\varepsilon(x)}|\xi\rangle\\&=\langle n_{1},\ldots,n_{N}|_{x}\sum_{m_{1}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{x}
-	 \otimes(e_{x}^{E_{12}+\ldots+E_{1N}})^{T}R_{x}\\&|r_{1},\ldots,r_{N}\rangle_{x} \otimes |q_{2},\ldots,q_{N}\rangle_{x}
-\end{align*}
-The extra-site part is trivial. Indeed by orthogonality relations \eqref{ortho}:
-\begin{align*}
-&\sum_{m_{2}^{\varepsilon(x)},\ldots,m_{N}^{\varepsilon(x)}=0}^{\infty}\prod_{k=1}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{\varepsilon(x)}|q_{2},\ldots,q_{N}\rangle_{\varepsilon(x)}\\&=
-\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{m_{k}^{\varepsilon(x)}}
-\end{align*}
- Let us work on the edge part:
-\begin{align*}
-&\langle n_{1},\ldots,n_{N}|_{x}(e_{x}^{E_{12}+\ldots+E_{1N}})^{T}R_{x}|r_{1},\ldots,r_{N}\rangle_{x}\\&= \langle  n_{1},\ldots,n_{N}|_{x}\left(\sum_{k_{2}=0}^{\infty}\frac{(E_{12}^{T})^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{(E_{1N}^{T})^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{(2j)!}|s_{1},\ldots,s_{N}\rangle_{x}\langle s_{1},\ldots,s_{N}|_{x}\right)|r_{1},\ldots,r_{N}\rangle_{x}=\diamond
-\end{align*}
-By using the orthogonality relations \eqref{ortho}
-\begin{align*}&\diamond=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}+k_{2}+\ldots+k_{N},n_{2}-k_{2},\ldots,n_{N}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
-\\&\cdot 
-\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{(2j)!}|r_{1},\ldots,r_{N}\rangle_{x}=\star
-\end{align*}
-Again by the orthogonality relations \eqref{ortho} and by the constraints $n_{1}=2j-\sum_{k=2}^{N}n_{k}$, $r_{1}=2j-\sum_{k=2}^{N}r_{k}$ we finally write
-\begin{equation}
-\begin{split}
-\star=&\frac{(2j-\sum_{k=1}^{N}r_{k}^{x})!r_{2}^{x}!\ldots r_{N }^{x}!}{(2j)!}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{r_{2}^{x}!\ldots r_{N}^{x}!}\frac{1}{(n_{2}^{x}-r_{1}^{x})!\ldots (n_{N}^{x}-r_{N}^{x})!}\\=&
-\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{(2j)!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
-\end{split}
-\end{equation}
-By taking the product over $x\in V$ and considering the extra site part we arrive to \eqref{dualityElements}. \newline \\
-\textbf{Remark}: it is straightforward to prove that, for every fixed dual configuration $|\xi\rangle \in \widetilde{\Omega}$, the average of the duality matrix  element \eqref{dualityElements} with respect to the reversible measure \eqref{reversibleMeasure} gives
-\begin{equation}
-    \mathbb{E}_{n}\left[D(n,\xi)\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\varepsilon(x)}}
-\end{equation}
+     \sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}^{x}\right)
+    \end{split}
+\end{equation}
+Thus, multiplying and dividing by $\sum_{i=1}^{N}\alpha_{i}^{x}$, we rewrite \eqref{intermediateTransposeSite} as
+\begin{equation}\label{siteHadamardI}
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
+\end{equation}
+We multiply both sides of \eqref{siteHadamard} by 
+\begin{equation}
+\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+\end{equation}
+and we obtain 
+\begin{equation}\label{siteHadamardII}
+    \begin{split}
+&H_{x,y}^{T}D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+\\=&
+D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
+    \end{split}
+\end{equation}
+Recalling the action of the bosonic creation operator acting at site $\widetilde{x}$ and on the species $k\in \{2,\ldots\}$ we have that 
+\begin{equation}\label{bosonicKX}
+    \langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}}+1,\ldots,m_{N}^{\widetilde{x}}|=  \langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})^{\widetilde{x}}_{k}
+\end{equation}
+Using \eqref{bosonicKX} for a fixed $k\in \{2,\ldots,N\}$ we rewrite the term multiplied for $E_{1k}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+\begin{equation}
+    \begin{split}
+&\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}+1}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}}+1,\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}
+\\=&
+\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}
+    \end{split}
+\end{equation}
+where we performed a change of summation variable. Therefore, inserting this in \eqref{siteHadamardII} we obtain 
+\begin{equation}
+    \begin{split}
+     &H_{x,y}^{T}D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+\\=&
+D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
+    \end{split}
+\end{equation}
+Since the duality matrix \eqref{dualityMatrix} is tensor product over sites, this implies \eqref{siteDualRelation}. 
 \begin{flushright}
@@
 \end{flushright}
-{\color{blue}\subsection{Duality for the reaction diffusion process on a graph}
-[IN CASE WE DECIDE TO ADD THIS PART WE SHOULD DEFINE EVERYTHING PROPERLY... LET'S THINK ABOUT THIS]
-It is possible to prove the absorbing duality also for the family of processes introduced in \cite{casini2022uphill}. Indeed, the Hamiltonain is
-\begin{equation}\label{ReactionDiffusionHamiltonian}
-H=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}H_{x,y}^{RD}+\sum_{x\in V}\Gamma_{x}H_{x}
-\end{equation}
-The site Hamiltonian $H_{x}$ is the one defined in \eqref{siteHamiltonian}
-while the edge Hamiltonian is 
-\begin{equation}
-H_{x,y}^{RD}=H_{x,y}^{S}+H_{x,y}^{SM}+H_{x,y}^{LM}+H_{x,y}^{RM}
-\end{equation}
-with $H_{x,y}^{S}$ is exactly the one defined in \eqref{edgeHamiltonian} and 
-\begin{equation}
-H_{x,y}^{SM}=\sigma_{12}\sum_{a,b=1}^{3}\left(E_{\overline{a}b}^{x}\otimes E_{\overline{b}a}^{y}-E_{bb}^{x}\otimes E_{aa}^{y}\right)
-\end{equation}
-\begin{equation}
-H_{x,y}^{LM}=\left(\Upsilon-2\sigma_{12}-m\right)\sum_{a=1}^{3}\left(E_{\overline{a}a}^{x}\otimes \mathbbm{1}^{y}-E_{aa}\otimes\mathbbm{1}^{x}\right)
-\end{equation}
-\begin{equation}
-H_{x,y}^{RM}=m\sum_{a=1}^{3}\left(\mathbbm{1}^{x}\otimes E_{\overline{a}a}^{y}-\mathbbm{1}^{x}\otimes E_{aa}^{y}\right)
-\end{equation}
-
-The matrix $S$ defined in \eqref{Simmetry_s} is a symmetry also for $H^{RD}$. We first prove it for $H_{x,y}^{SM}$.. We will prove that 
-\begin{equation}\label{symmetrySM}
-\sum_{a,b=1}^{3}[E_{\overline{a}b}^{x}\otimes E_{\overline{b}a}^{y},S]=\sum_{a,b=1}^{3}[E_{bb}^{x}\otimes E_{aa}^{y},S]
-\end{equation}
-The left-hand-side is
-\begin{equation}
-\begin{split}
-&\left[E_{10}^{x},E_{\overline{a}b}^{x}\right]\otimes \left[E_{10}^{y},E_{\overline{b}a}^{y}\right]+\left[E_{10}^{x},E_{\overline{a}b}^{x}\right]\otimes\left[E_{20}^{y},E_{\overline{b}a}^{y}\right]+\left[E_{20}^{x},E_{\overline{a}b}^{x}\right]\otimes\left[E_{10}^{y},E_{\overline{b}a}^{y}\right]+\left[E_{20}^{x},E_{\overline{a}b}^{x}\right]\otimes\left[E_{20}^{y},E_{\overline{b}a}^{y}\right]
-\end{split}
-\end{equation}
-and the right-hand-side is
-\begin{equation}
-\begin{split}
-\left[E_{10}^{x},E_{bb}^{x}\right]\otimes \left[E_{10}^{y},E_{aa}^{y}\right]+\left[E_{10}^{x},E_{bb}^{x}\right]\otimes\left[E_{20}^{y},E_{aa}^{y}\right]+\left[E_{20}^{x},E_{bb}^{x}\right]\otimes\left[E_{10}^{y},E_{aa}^{y}\right]+\left[E_{20}^{x},E_{bb}^{x}\right]\otimes\left[E_{20}^{y},E_{aa}^{y}\right]
-\end{split}
-\end{equation}
-by using the commutators $\forall k=1,2$
-\begin{equation}
-\begin{split}
-&\left[E_{k0},E_{\overline{a}b}\right]=\left(E_{kb}\delta_{\overline{a}0}-E_{\overline{a}0}\delta_{bk}\right)\\
-&\left[E_{k0},E_{\overline{b}a}\right]=\left(E_{ka}\delta_{\overline{b}0}-E_{\overline{b}0}\delta_{ak}\right)\\
-&\left[E_{k0},E_{aa}\right]=\left(E_{ka}\delta_{a0}-E_{a0}\delta_{bk}\right)\\
-&\left[E_{k0},E_{bb}\right]=\left(E_{kb}\delta_{b0}-E_{b0}\delta_{bk}\right)
-\end{split}
-\end{equation}
-and summing over all $a,b\in\{1,2,3\}$ we obtatain \eqref{symmetrySM}. Similarly, we can prove that
-\begin{equation}\label{symmetryM}
-\sum_{a=1}^{3}\left[E_{\overline{a}a}^{x}\otimes \mathbbm{1}^{y},S\right]=\sum_{a=1}^{3}\left[E_{aa}^{x}\otimes \mathbbm{1}^{y},S\right]\qquad \sum_{a=1}^{3}\left[\mathbbm{1}^{x}\otimes E_{\overline{a}a}^{y},S\right]=\sum_{a=1}^{3}\left[\mathbbm{1}^{x}\otimes E_{aa}^{y},S\right]
-\end{equation}
-As a consequence of \eqref{symmetrySM} and \eqref{symmetryM} the Hamiltonian \eqref{ReactionDiffusionHamiltonian} is self-dual with absorbing reservoirs with self-duality matrix given by \eqref{dualityMatrix}.}
+\textbf{Remark}:
+The duality result can be state also in terms of infinitesimal generators \eqref{Generator}.
+In this case, the dual process, is denoted by $(\xi(t))_{t\geq 0}$, where for each $t\geq 0$ and for each $x\in V$ we denote
+\begin{equation}
+\xi^{x}(t)=\left(r_{1}^{x}(t),\ldots,r_{N}^{x}(t),m_{2}^{\widetilde{x}}(t),\ldots,m_{N}^{\widetilde{x}}(t)\right)
+\end{equation}
+where we denote $r_{k}^{x}$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ and with $m_{l}^{\widetilde{x}}$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\widetilde{x}$ connected to $x\in V$.
+This dual process has values in the enlarged state space
+\begin{equation}
+    \widetilde{\Omega}:=\Omega\times \mathbb{N}^{V}_{0}
+\end{equation}
+The dual generator is defined as
+\begin{equation}
+    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
+\end{equation}
+where 
+$\mathcal{L}_{x,y}$ is the one defined in \eqref{siteGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+\begin{equation}
+    \widetilde{\mathcal{L}}_{x}f(\xi)=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\xi-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widetilde{x}})-f(\xi)\right)
+\end{equation}
+The duality relation \eqref{DualityRelation} reads
+\begin{equation}\label{dualityGenerators}
+    \left(\mathcal{L}D(\cdot,\xi)\right)(n)=\left(\widetilde{\mathcal{L}}D(n,\cdot)\right)(\xi)
+\end{equation}
+where 
+\begin{equation}\label{dualityElements}
+	D(n,\xi)=\langle n|D|\xi\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{1}}\right)^{m_{k}^{\varepsilon(x)}}\right)
+\end{equation}
+are the element of the duality matrix \eqref{dualityMatrix}.
+The proof of \eqref{dualityGenerators} follows from \eqref{DualityRelation}.
+Therefore, we only need to show that the elements of \eqref{dualityMatrix} are indeed \eqref{dualityElements}.
+Fix an arbitrary site $x\in V$
+\begin{align*}
+	 &\langle n^{x}|D_{x}\otimes D_{\widetilde{x}}|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{x}
+	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widetilde{x}},\ldots,q_{N}^{\widetilde{x}}\rangle
+\end{align*}
+On one hand, on the extra-site $\widetilde{x}$ we have 
+\begin{align*}
+\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}||q_{2}^{\widetilde{x}},\ldots,q_{N}^{\widetilde{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}
+\end{align*}
+on the other hand, on the site $x$ we have 
+\begin{align*}
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&=
+\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
+\\&\cdot 
+\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1},\ldots,r_{N}\rangle_{x}\\&=\frac{(2j-\sum_{k=1}^{N}r_{k}^{x})!r_{2}^{x}!\ldots r_{N }^{x}!}{\nu!}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{r_{2}^{x}!\ldots r_{N}^{x}!}\frac{1}{(n_{2}^{x}-r_{2}^{x})!\ldots (n_{N}^{x}-r_{N}^{x})!}\\&=
+\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
+\end{align*}
+where we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{k=2}^{N}r_{k}^{x}$.
+Finally, by taking the product over $x\in V$ we prove \eqref{dualityElements}.
+\newline \\
+\textbf{Remark}: in the reverible situation, i.e.
+when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, satisfy
+\begin{equation}
+\mathbb{E}_{\mu^{rev}}\left[D(n,\xi)\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\varepsilon(x)}}
+\end{equation}
+\begin{flushright}
+    $\square$
+\end{flushright}
+\subsection{Duality for a reaction diffusion process}
+In \cite{UPHILL}, a two-species hard-core reaction diffusion process has been introduced.
+The feature of this process is that its action on the occupation variable of any species gives a difference-differential equation where both discrete Laplacians and a linear reaction term are present (multiplied for proper constants).
+In this subsection we write a generalization to $N\in \mathbb{N}$ species with arbitrary maximal occupation per site, again called $\nu\in\mathbb{N}_{0}$.
+The generator reads as follows
+\begin{equation}\label{RDGenerator}
+    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}
+\end{equation}
+where
+\begin{equation}
+    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{i=1}^{N}\mathcal{L}_{x,y}^{i}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+\end{equation}
+with $\mathcal{L}_{x,y}$ and $\mathcal{L}_{x}$ are the generators the generator \eqref{edgeGenerator} and \eqref{siteGenerator} respectively and, for any function $f:\Omega\to \mathbb{R}$
+\begin{equation}
+    \mathcal{L}_{x,u}^{i}f(n)=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(f(n-\delta_{k}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(n)\right)
+\end{equation}
+with the mapping 
+\begin{equation}
+    g_{i}(k)=\begin{cases}
+    k+i \quad &\text{if}\quad k+i\leq N\\
+    k+i-N\quad &\text{if}\quad k+i>N\\
+    0\quad &\text{if}\quad k=0
+\end{cases}
+\end{equation}
+and where
+\begin{equation}
+    \mathcal{L}_{x,y}^{m}f(n)=\sum_{l,k=0}^{N}n_{k}^{x}\left(f(n-\delta_{k}^{x}+\delta_{l}^{x})-f(n)\right)
+\end{equation}
+the action on the occupation variable $n_{\alpha}^{x}$ of particle type $\alpha\in \{2,\ldots,N\}$ at site $x\in V $
+is the following
+\begin{equation}\label{actionGraphRD}
+\begin{split}
+    \mathcal{L}_{x,y}^{rd}n_{\alpha}^{x}&=\nu \sigma_{11}(n_{\alpha}^{y}-n_{\alpha}^{x})+\nu\sigma_{12}\sum_{i=1}^{N}(n_{g_{i}(k)}^{y}-n_{\alpha}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
+\end{split}
+\end{equation}
+indeed, 
+\begin{equation}
+    \begin{split}
+\mathcal{L}_{x,y}^{i}n_{\alpha}^{x}&=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(n_{\alpha}^{x}-\delta_{k}^{x}+\delta_{g_{i}(l)^{x}}+\delta_{g_{i}(x)}^{y}-\delta_{l}^{y}-n_{\alpha}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{y}-\sum_{c=1}^{N}n_{\alpha}^{x}n_{c}^{y}
+\\&=
+\sum_{k=2}^{N}n_{k}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{c=2}^{N}n_{\alpha}^{x}n_{c}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+\\&=
+\nu(n_{q}^{y}-n_{\alpha}^{x})
+    \end{split}
+\end{equation}
+where we call $q\in \{1,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $c\in \{1,\ldots,N\}$ such that $g_{i}(c)\neq \alpha$.
+Summing over all indices $i\in\{1,\ldots,N\}$ we obtain \eqref{actionGraphRD}.\\
+Therefore, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives
+\begin{equation}\label{DifferenceEquation}
+\mathcal{L}^{rd}n_{\alpha}^{x}=\nu\sigma_{11}\Delta_{L}n_{\alpha}^{x}+\nu\sigma_{12}\sum_{l=2\,:\,l\neq k}^{N}\Delta_{L}n_{l}^{x}+\Upsilon\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
+\end{equation}
+where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e.
+$\Delta_{L}n_{k}^{x}=n_{k}^{x+1}+n_{k}^{x-1}-2n_{k}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
+In the spirit of \cite{} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
+\\
+The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
+$\alpha_{k}^{x}=\alpha$, $\forall k\in \{1,\ldots,N\}$ and $x\in V$.
+This measure is given by
+\begin{equation}
+    \Lambda^{rev}=\bigotimes_{x\in V}\Lambda_{x}^{rev}
+\end{equation}
+where the marginals are
+\begin{equation}
+    \Lambda_{x}^{rev}\sim \text{Multinomial}(\nu,p,\ldots,p)
+\end{equation}
+with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.\\
+This generator $\mathcal{L}^{rd}$ can be described by the Hamiltonian $H^{rd}$ that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
+\begin{equation}
+    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{i=1}^{N}H_{x,y}^{i}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+\end{equation}
+where $H_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
+\begin{equation}
+    H_{x,y}^{i}=\sum_{k,l=0}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)
+\end{equation}
+and 
+\begin{equation}
+    H_{x,y}^{m}=\sum_{k,l}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)
+\end{equation}
+For this model, the duality relation is
+\begin{equation}\label{DualityRelationRD}
+    (H^{rd})^{T}D=D\widetilde{H}^{rd}
+\end{equation}
+where the duality matrix $D$ is again \eqref{dualityMatrix}.
+Following subsection \ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
+This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between $H_{x,y}^{m}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
+Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
+\begin{align*}
+    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)\right]
+    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left\{\left(E_{ak}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{bk}\right)-\left(E_{ak}^{x}\delta_{k0}-E_{k0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}
+    \\=&
+    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{ak}^{x}\left(\delta_{g_{i}(l)0}-\delta_{k0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{k0}^{x}\right)\delta_{ak}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
+    \\=&\;0
+\end{align*}
+ Again, using \eqref{eq:comgl} and by a similar argument, we obtain
+\begin{equation}
+\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
+\end{equation}
+Therefore, following a proof similar to the one in subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved. 
 \section{Integrability}\label{sec4}

### 2023-03-13 main.tex
duality

@@
     \end{flushright}
-The process described by the generator \eqref{Generator} is reversiblewith respect to the homogeneus product measure \begin{equation}\label{reversibleMeasure}
-\mu_{rev}=\bigotimes_{x\in V}\mu^{rev}_{x}
+The process described by the generator \eqref{Generator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasure}
+\mu_{rev}=\bigotimes_{x\in V}\mu_{rev}^{x}
 \end{equation}
@@
 \begin{equation}
-\mu_{rev}^{x}(n^{x})=\frac{\nu}{\prod_{k=1}^{N}n_{k}^{x}}\prod_{k=1}^{N}p_{k}^{n_{k}^{x}}
+\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}p_{k}^{n_{k}^{x}}
 \end{equation}
@@
 {\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-By the Lie algebra above we describe the process characterized by the generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements
+By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements
 
@@
 Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
-Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by the following relation:
+Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
 \begin{equation}
@@
 
-We can write this Hamiltonian as a function of the coproduct of the second Casimir
+We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
 \begin{equation}
@@
 \end{equation}
-that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$. \\
+that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the basis elements).  \\
  Considering two sites $x,y\in \mathcal{E}$ the standard coproduct operator is defined as 
@@
 \subsection{Definition of duality}
-Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
+Consider two Markov processes: $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
 We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have

### 2023-03-13 main.tex
dualityupdate

@@
 We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
-\begin{equation}
+\begin{equation}\label{secondCasimir}
     C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
@@
 We now state our duality result.
-The process $|n\rangle$ with Hamiltonian \eqref{} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\xi\rangle$ defined on the enlarged state space
+The process $|\mathbf{n}\rangle$ with Hamiltonian \eqref{OriginalHamiltonian} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\bm{\xi}\rangle$ defined on the enlarged state space
 \begin{equation}
@@
 \begin{equation}
-    |\xi\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
 \end{equation}
@@
 By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
-$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
-The Hamiltonians \eqref{Hamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
+$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the occupation of the species $k\in\{2,\ldots,N\}$. \\
+The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
 \begin{equation}
@@
 \end{equation}
-with $E$
+with 
 \begin{equation}
@@
 This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites.
-Thinking about the type $1$ as the hole, similarly to what happens in the SEP(2j)\cite{GioaGiardinaGibertiFrank}, the graph is eventually emptied.
+Thinking about the type $1$ as the hole  the graph is eventually emptied, similarly to what proved in the SEP(2j)\cite{carinci2013duality}.
 \subsection{Proof of the duality relation}\label{subsectionDualityProof}
-To prove the duality relation between \eqref{} and \eqref{DualHamiltonian} with the duality matrix \eqref{dualityMatrix} we shall show that 
+To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{dualityMatrix} we shall show that 
 \begin{equation}
@@
 \end{equation}
-%The key idea behind the proof of \eqref{edgeDualRealtion} is that it is possible to write the Hamiltonian \eqref{} as a function of the second Casimir of the $gl(N)$ Lie algebra.
-Finding a symmetry $S$ of this element, will imply of having a symmetry of the Hamiltonian.
-By the reversibility of the process one can make $S$ act on a proper matrix (called cheap duality) and obtain
+We will prove these two statements seprately in the following.
+
 \paragraph{Proof of \eqref{edgeDualRealtion}}
-The proof of the edge duality relation relies on two facts: first the existence of a diagonal matrix, arising from the reversible measure, that is already a duality for the Hamiltonian (in literature called 'cheap' duality matrix, see \cite{}); second the possibility of finding a proper symmetry of the Hamiltonian.
+The proof of the edge duality relation relies on two facts: first the existence of a diagonal matrix, arising from the reversible measure, that is already a duality for the Hamiltonian (in literature called 'cheap' duality matrix, see \cite{giardina2009duality}); second the possibility of finding a proper symmetry of the Hamiltonian.
 \\We first introduce the cheap duality matrix
@@
 We now look for a symmetry of the Hamiltonian.
-As shown in \eqref{}, it is possible to write the Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$.
-We say that a matrix $A\in gl(N)$ is symmetry of the Casimir $C_{2}$ if
+As shown in \eqref{hamiltonianCasimir}, it is possible to write the Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir\eqref{secondCasimir} of $gl(N)$.
+We say that a matrix $A\in gl(N)$ is symmetry of $C_{2}$ if
 \begin{equation}
@@
 \end{equation}
- $C_{2}$ is a central element of $gl(N)$, then it commutes with every element of the algebra. 
+ $C_{2}$ is a central element of $gl(N)$, then it commutes with each element of the algebra. 
 We chose as a symmetry 
@@
  therefore \eqref{edgeDualRealtion} is proved. 
-\paragraph{Proof of \eqref{siteDualRelation}} The proof of the site duality relations relies on the Hadamard Lemma that, $\forall E,A \in gl(N)$, reads as 
+\begin{flushright}
+$\square$
+\end{flushright}
+\paragraph{Proof of \eqref{siteDualRelation}} The proof of the site duality relations relies on the Hadamard Lemma that reads, $\forall E,A \in gl(N)$, as
 \begin{equation}\label{HadamardFormula}
@@
     \begin{split}
-H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)^{T}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}
-    \end{split}
-\end{equation}
-we multiply both sides for $R_{x}\exp{(E^{x})}$
-\begin{equation}
-    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
-\end{equation}
-we insert the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ in the right hand side
+H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)^{T}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}
+    \end{split}
+\end{equation}
+First, we multiply both sides for $R_{x}\exp{(E^{x})}$
+\begin{equation}
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)R_{x}^{-1}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell =0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+\end{equation}
+then,we insert the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ in the right hand side
 \begin{equation}\label{intermediateTransposeSite}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
-\end{equation}
-we apply the Hadamard's formula \eqref{HadamardFormula} to 
-\begin{equation}
-    \exp{(-E^{x})}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
-\end{equation}
-We compute the following quantities by the commutation relations \eqref{}:
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+\end{equation}
+and finally we apply the Hadamard's formula \eqref{HadamardFormula} to 
+\begin{equation}
+    \exp{(-E^{x})}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell \ell}^{x}\right)\exp{(E^{x})}
+\end{equation}
+We compute the following quantities by the commutation relations \eqref{eq:comgl}:
 \begin{itemize}
-    \item for all $k\neq 1$ 
-\begin{equation}
-    \begin{split}
-        \exp{(-E^{x})}E_{k1}^{x}\exp{(E^{x})}=E_{k1}^{x},
-    \end{split}
-\end{equation}
-\begin{equation}
-    \begin{split}
-    \exp{(-E^{x})}E_{kk}^{x}\exp{(E^{x})}=E_{kk}^{x}+E_{k1}^{x}
+    \item for all $\ell\neq 1$ 
+\begin{equation}
+    \begin{split}
+        \exp{(-E^{x})}E_{\ell1}^{x}\exp{(E^{x})}=E_{\ell1}^{x},
+    \end{split}
+\end{equation}
+\begin{equation}
+    \begin{split}
+    \exp{(-E^{x})}E_{\ell\ell}^{x}\exp{(E^{x})}=E_{\ell\ell}^{x}+E_{\ell1}^{x}
     \end{split}
@@
 \begin{split}
-    \exp{(-E^{x})}E_{1k}^{x}\exp{(E^{x})}=E_{1k}^{x}+E_{11}^{x}-\sum_{a=2}^{N}\left(E_{a1}^{x}+E_{ak}^{x}\right)
+    \exp{(-E^{x})}E_{1\ell}^{x}\exp{(E^{x})}=E_{1\ell}^{x}+E_{11}^{x}-\sum_{a=2}^{N}\left(E_{a1}^{x}+E_{a\ell}^{x}\right)
 \end{split}
@@
 \begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{kk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{k1}-E_{k1}^{x}\delta_{ak}\right)
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}^{x}\delta_{k1}-E_{\ell1}^{x}\delta_{a\ell}\right)
 \end{align*}
@@
 \begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{1k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{11}^{x}\delta_{ak}\right)=\sum_{a=2}^{N}E_{ak}^{x}-E_{11}^{x};
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{1\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}^{x}\delta_{11}-E_{11}^{x}\delta_{a\ell}\right)=\sum_{a=2}^{N}E_{a\ell}^{x}-E_{11}^{x};
 \end{align*}
@@
 \begin{align*}
-&\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1}^{x},E_{ak}^{x}\right]-\sum_{b=2}^{N}\left[E_{b1}^{x},E_{11}^{x}\right]=\sum_{a,b=2}^{N}\left(E_{bk}^{x}\delta_{a1}-E_{a1}^{x}\delta_{bk}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)\\=&-2\sum_{a=2}^{N}E_{a1}^{x};
+&\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1}^{x},E_{a\ell}^{x}\right]-\sum_{b=2}^{N}\left[E_{b1}^{x},E_{11}^{x}\right]=\sum_{a,b=2}^{N}\left(E_{b\ell}^{x}\delta_{a1}-E_{a1}^{x}\delta_{b\ell}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)\\=&-2\sum_{a=2}^{N}E_{a1}^{x};
 \end{align*}
 from the third on-wards all commutators zero. 
-\item for all $k,l\neq 1$
-\begin{equation}
-        \begin{split}
-    \exp{(-E^{x})}E_{lk}^{x}\exp{(E^{x})}=E_{kl}^{x}+E_{l1}^{x}
+\item for all $k,\ell\neq 1$
+\begin{equation}
+        \begin{split}
+    \exp{(-E^{x})}E_{\ell k}^{x}\exp{(E^{x})}=E_{k\ell}^{x}+E_{\ell 1}^{x}
     \end{split}
@@
 \begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{lk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{l1}-E_{l1}^{x}\delta_{ak}\right)=-E_{l1}^{x};
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{\ell k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{\ell 1}-E_{\ell 1}^{x}\delta_{ak}\right)=-E_{\ell 1}^{x};
 \end{align*}
@@
 \begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{lk}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{l1}^{x}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1}^{x};
+\sum_{a=2}^{N}\left[E_{a1}^{x},E_{\ell k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{\ell 1}^{x}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1}^{x};
 \end{align*}
@@
      \\&=
-     \sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{jk}^{x}+E_{l1}^{x})-E_{11}^{x}+\sum_{j=2}^{N}E_{j1}^{x}\right)+\sum_{k=1}^{N}\sum_{l=2}^{N}\left(E_{lk}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{l1}^{x}\right)
+     \sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{ak}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{j=2}^{N}E_{j1}^{x}\right)+\sum_{k=1}^{N}\sum_{l=2}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{l1}^{x}\right)
      \\&=
-     \sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}^{x}\right)
-    \end{split}
-\end{equation}
-Thus, multiplying and dividing by $\sum_{i=1}^{N}\alpha_{i}^{x}$, we rewrite \eqref{intermediateTransposeSite} as
+\sum_{k=2}^{N}\alpha_{k}^{x}E_{1k}^{x}-\sum_{k=1}^{N}\alpha_{k}^{x}\sum_{\ell=2}^{N}E_{\ell\ell}^{x}
+=
+     \sum_{k=2}^{N}\left(\alpha_{k}^{x}E_{1k}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{kk}^{x}\right)
+\\&=
+\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+    \end{split}
+\end{equation}
+Thus, we rewrite \eqref{intermediateTransposeSite} as
 \begin{equation}\label{siteHadamardI}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
-\end{equation}
-We multiply both sides of \eqref{siteHadamard} by 
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+\end{equation}
+We multiply both sides of \eqref{siteHadamardI} by 
 \begin{equation}
@@
 \\=&
-D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\left(E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
-    \end{split}
-\end{equation}
-Recalling the action of the bosonic creation operator acting at site $\widetilde{x}$ and on the species $k\in \{2,\ldots\}$ we have that 
+D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)
+    \end{split}
+\end{equation}
+Recalling the action of the bosonic creation operator acting at site $\widetilde{x}$ and on the species $k\in \{2,\ldots,N\}$ we have that 
 \begin{equation}\label{bosonicKX}
@@
     \begin{split}
-&\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}+1}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}}+1,\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}
+&\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
+\\=&\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}+1}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}}+1,\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}
 \\=&
@@
 \end{equation}
-where we performed a change of summation variable. Therefore, inserting this in \eqref{siteHadamardII} we obtain 
+where, in the up to last equality, we performed a change of summation variable. Therefore, inserting this in \eqref{siteHadamardII} we obtain 
 \begin{equation}
@@
 \\=&
-D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}-\sum_{j=2}^{N}E_{jj}\right)
-    \end{split}
-\end{equation}
-Since the duality matrix \eqref{dualityMatrix} is tensor product over sites, this implies \eqref{siteDualRelation}. 
+D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+    \end{split}
+\end{equation}
+Since the duality matrix \eqref{dualityMatrix} is tensor product over sites, the above equality implies \eqref{siteDualRelation}. 
 \begin{flushright}
@@
 The duality result can be state also in terms of infinitesimal generators \eqref{Generator}.
-In this case, the dual process, is denoted by $(\xi(t))_{t\geq 0}$, where for each $t\geq 0$ and for each $x\in V$ we denote
+In this case, the dual process, is denoted by $(\bm{\xi}(t))_{t\geq 0}$, where for each $t\geq 0$ and for each $x\in V$ we denote
 \begin{equation}
@@
 \begin{equation}
-    \widetilde{\mathcal{L}}_{x}f(\xi)=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\xi-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widetilde{x}})-f(\xi)\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widetilde{x}})-f(\bm{\xi})\right)
 \end{equation}
@@
 \begin{equation}\label{dualityGenerators}
-    \left(\mathcal{L}D(\cdot,\xi)\right)(n)=\left(\widetilde{\mathcal{L}}D(n,\cdot)\right)(\xi)
+    \left(\mathcal{L}D(\cdot,\bm{\xi})\right)(\bm{n})=\left(\widetilde{\mathcal{L}}D(\bm{n},\cdot)\right)(\bm{\xi})
 \end{equation}
@@
 \begin{equation}\label{dualityElements}
-	D(n,\xi)=\langle n|D|\xi\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{1}}\right)^{m_{k}^{\varepsilon(x)}}\right)
+	D(\bm{n},\bm{\xi})=\langle \bm{n}|D|\bm{\xi}\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{1}}\right)^{m_{k}^{\varepsilon(x)}}\right)
 \end{equation}
@@
 \textbf{Remark}: in the reverible situation, i.e.
-when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, satisfy
-\begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(n,\xi)\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\varepsilon(x)}}
+when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, satisfies
+\begin{equation}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widetilde{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}

### 2023-03-14 main.tex
dualityUpdate

@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{k,l=1}^{N}\left(E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}\right)
+H_{x,y}=\sum_{k,\ell=1}^{N}\left(E_{k\ell}^{x}\otimes E_{\ell k}^{y}-E_{\ell\ell}^{x}\otimes E_{kk}^{y}\right)
  \end{equation}
@@
  \begin{equation}\label{siteHamiltonian}
-H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)
+H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
 \end{equation}
@@
 \end{flushright}
+
 \paragraph{Proof of \eqref{siteDualRelation}} The proof of the site duality relations relies on the Hadamard Lemma that reads, $\forall E,A \in gl(N)$, as
@@
     \begin{split}
-H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)^{T}=R_{x}\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)R_{x}^{-1}
+H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)^{T}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)R_{x}^{-1}
     \end{split}
@@
 \begin{split}
-    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{l=1}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}\\&=
-     \exp{(-E^{x})}\sum_{k=1}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
-     + \exp{(-E^{x})}\sum_{k=1}^{N}\sum_{l=2}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}-E_{ll}^{x}\right)\exp{(E^{x})}
+    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=1}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}\\&=
+     \exp{(-E^{x})}\sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
+     + \exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=2}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
      \\&=
-     \sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{ak}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{j=2}^{N}E_{j1}^{x}\right)+\sum_{k=1}^{N}\sum_{l=2}^{N}\alpha_{k}^{x}\left(E_{lk}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{l1}^{x}\right)
+     \sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{ak}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{k=1}^{N}\sum_{\ell =2}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{\ell 1}^{x}\right)
      \\&=
@@
 \textbf{Remark}:
-The duality result can be state also in terms of infinitesimal generators \eqref{Generator}.
-In this case, the dual process, is denoted by $(\bm{\xi}(t))_{t\geq 0}$, where for each $t\geq 0$ and for each $x\in V$ we denote
+The duality result can be also stated  in terms of the infinitesimal generators \eqref{Generator}. The dual process is $(\bm{\xi}(t))_{t\geq 0}$ . For each $x\in V$ we define the $x-th$ component as
 \begin{equation}
@@
  where we denote $r_{k}^{x}$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ and with $m_{l}^{\widetilde{x}}$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\widetilde{x}$ connected to $x\in V$.
-This dual process has values in the enlarged state space
+This dual process lives in the enlarged state space
 \begin{equation}
@@
 \end{equation}
-The duality relation \eqref{DualityRelation} reads
+The duality relation \eqref{DualityRelation} reads as
 \begin{equation}\label{dualityGenerators}
@@
 \begin{align*}
-	 &\langle n^{x}|D_{x}\otimes D_{\widetilde{x}}|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\varepsilon(x)}}\langle m_{2},\ldots,m_{N}|_{x}
+	 &\langle n^{x}|D_{x}\otimes D_{\widetilde{x}}|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
 	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widetilde{x}},\ldots,q_{N}^{\widetilde{x}}\rangle
@@
 \end{align*}
-on the other hand, on the site $x$ we have 
+On the other hand, on the site $x$, we have 
 \begin{align*}
@@
 \end{align*}
-where we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{k=2}^{N}r_{k}^{x}$.
-Finally, by taking the product over $x\in V$ we prove \eqref{dualityElements}.
+where we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{k=2}^{N}r_{k}^{x}$. Finally, by taking the product over $x\in V$ we prove \eqref{dualityElements}.\\
+\newline 
+\textbf{Remark}: It is important to notice that the denomiator the elements of the duality matrix \eqref{dualityElements} $(n_{k}^{x}-r_{k}^{x})!$,  implies that, at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles is lower or equal than the number of original particles.
+This means that the dynamics of the dual proces is simpler than the one of the original one.
+It is possible to perform similar computations choosing as a symmetry $E^{x}=\sum_{a=2}^{N}E_{1a}^{x}$ or $E^{x}=\sum_{a=2}^{N}E_{aa}^{x}$.
+However, these would lead to duality matrices where the number of dual particles is greater than the number of original ones loosing the simplification of the dynamics.
  \newline \\
 \textbf{Remark}: in the reverible situation, i.e.
-when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, satisfies
+when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, is
 \begin{equation}
@@
 \subsection{Duality for a reaction diffusion process}
-In \cite{UPHILL}, a two-species hard-core reaction diffusion process has been introduced.
+In \cite{casini2022uphill}, a two-species hard-core reaction diffusion process has been introduced.
 The feature of this process is that its action on the occupation variable of any species gives a difference-differential equation where both discrete Laplacians and a linear reaction term are present (multiplied for proper constants).
@@
 \begin{equation}
-    \mathcal{L}_{x,u}^{i}f(n)=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(f(n-\delta_{k}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(n)\right)
+    \mathcal{L}_{x,u}^{i}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-    \mathcal{L}_{x,y}^{m}f(n)=\sum_{l,k=0}^{N}n_{k}^{x}\left(f(n-\delta_{k}^{x}+\delta_{l}^{x})-f(n)\right)
+    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{l,k=0}^{N}n_{k}^{x}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{l}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 $\Delta_{L}n_{k}^{x}=n_{k}^{x+1}+n_{k}^{x-1}-2n_{k}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
-In the spirit of \cite{} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
+In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
 \\
@@
 Following subsection \ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
-This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between $H_{x,y}^{m}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
+This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 \end{equation}
-Therefore, following a proof similar to the one in subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved. 
+Therefore, arguing similarly to subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved. 
 \section{Integrability}\label{sec4}

### 2023-03-14 main.tex
typo
ll
jj
Eigsum

@@
 \begin{equation}
-   \bar E_{ab}=\mu\delta_{ab}-E_{N-b+1,N-a+1}
+   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
 \end{equation}
@@
  \end{equation}
+ {\color{red}confusing notation: tensor product and site index.... Remove tensor product?}
+
  and where the site Hamiltonian is
@@
 \end{equation}
-We have that the eigenvectors and eigenvalues of the equilibrium case are given by
+\subsection{Eigenvector for the diagonal-triangular chain}
+In \cite{belliard2011nested}  the eigenvectors and eigenvalues hae been computed for the $gl(N)$ spin chain with diagonal boundaries, therfore we know 
 \begin{equation}
@@
 where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{k=2}^{N}m_{k}$.\\
+For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$ and we further assume that $\Delta_{2}=\Delta_{3}=\Delta$.
+We make the following ansatz for the eigevectors of the diagonal-triangular spin chain:
+\begin{equation}\label{ansatzEigenvectorDelta}
+|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{equation}
+We replace the above eigenvectors in 
+\begin{equation}\label{eigDELTA}
+T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
+\end{equation}
+and we obtain
+\begin{align*}
+&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\\+&
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\\=&
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+We assume that $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)$, i.e.
+it only depends on the sum of $k_{2}$ and $k_{3}$.
+We make an shift of summation indexes such that
+\begin{equation}
+k_{2}+k_{3}\to k_{2}+k_{3}+1
+\end{equation}
+then we obtain
+\begin{align*}
+&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\\+&
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\\+&
+\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\\=&
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+By equalizing the powers of $\Delta$ we obtain the following condition that must be fulfilled to have that \eqref{ansatzEigenvectorDelta} are indeed the eigenvectors for the triangular-diagonal spin chain:
+\begin{enumerate}
+\item for $k_{2}=k_{3}=0$
+\begin{equation}\label{condition1}
+T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{equation}
+\item for $k_{2}+k_{3}\neq 0$
+\begin{equation}\label{condition2}
+\begin{split}
+\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{split}
+\end{equation}
+\item finally
+\begin{equation}\label{condition3}
+\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
+\end{equation}
+\end{enumerate}
+By chosing 
+\begin{equation}
+G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)=\left\{\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}^{x}\right]^{-1}\left(B_{2}(x)+B_{3}(x)\right)\right\}^{k_{2}+k_{3}}
+\end{equation}
+conditions \eqref{condition1} and \eqref{condition2} are easilly satisfied.
+To fulfill condition \eqref{condition3}% we can think about $m_{1}:=L-m_{2}-m_{3}$ as the number of empty states in the whole chain.
+We can further introducte $m:=m_{2}+m_{3}$ and then write $m_{1}=L-m$.
+Therefore we have an invertivle map between holes and particles, therefore we can think about $\left(B_{2}(x)+B_{3}(x)\right)$ as a lowering operator and
 We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries.
@@
 We replace the above eigenvectors in 
-\begin{equation}\label{eigDELTA}
+\begin{equation}
 T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle

### 2023-03-14 main.tex
G-check

@@
 For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$ and we further assume that $\Delta_{2}=\Delta_{3}=\Delta$.
-We make the following ansatz for the eigevectors of the diagonal-triangular spin chain:
+We make the following ansatz for the eigevectors of the diagonal-triangular spin chain.
+Consider the whole chain of dimension $L$.
+Then, $m=m_{2}+m_{3}$ sites have particles of a type $2$ or $3$ and the remaining $L-m$ are empty.
+For fixed $m$ there is a one to one correspondence between empty and occupeid sites.
+Therefore, our ansatz is that $\forall m\in \{0,\ldots,L\}$
 \begin{equation}\label{ansatzEigenvectorDelta}
-|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+|\Psi_{L-m}^{\Delta}\rangle=\mathbbm{1}_{\{m_{2}+m_{3}=m\}}\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{equation}
@@
 \begin{equation}\label{eigDELTA}
-T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
+T_{\Delta}(x)|\Psi_{L-m}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{L-m}^{\Delta}\rangle
 \end{equation}
@@
 \begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 \begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\+&
-\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 \begin{equation}\label{condition1}
-T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{equation}
@@
 \begin{split}
-\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{split}
@@
 \begin{equation}\label{condition3}
-\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
+\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}=0
 \end{equation}
@@
 By chosing 
-\begin{equation}
+\begin{equation}\label{G-solution}
 G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)=\left\{\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}^{x}\right]^{-1}\left(B_{2}(x)+B_{3}(x)\right)\right\}^{k_{2}+k_{3}}
@@
 conditions \eqref{condition1} and \eqref{condition2} are easilly satisfied.
-To fulfill condition \eqref{condition3}% we can think about $m_{1}:=L-m_{2}-m_{3}$ as the number of empty states in the whole chain.
-We can further introducte $m:=m_{2}+m_{3}$ and then write $m_{1}=L-m$.
-Therefore we have an invertivle map between holes and particles, therefore we can think about $\left(B_{2}(x)+B_{3}(x)\right)$ as a lowering operator and
-We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries.
+To fulfill condition \eqref{condition3} we observe that, under the condition that $m=m_{2}+m_{3}$ we have that the action of \eqref{G-solution} on $|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}$ leads to a completely occupied state (with both species $2$ and $3$).
+Therefore, applying to it the rising operator$\left(B_{2}(x)+B_{3}(x)\right)$ we obtain zero.
+
+{\color{blue}We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries.
 For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
@@
 \end{align*}
-
+}
 For $i\neq 1$ we have

### 2023-03-14 main.tex
DualityCheckCheck
Update main.tex

@@
  \begingroup\LARGE
-\bf Stirring process
+\bf Multispecies stirring process
 \par\endgroup
@@
 
-Consider the $gl(N)$ Lie algebra with with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
+Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
 \begin{equation}\label{eq:comgl}
@@
 \begin{equation}
-    \langle {\bf n}|{\bf m}\rangle =\prod_{x=1}^L\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
+    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
 \end{equation}
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{k,\ell=1}^{N}\left(E_{k\ell}^{x}\otimes E_{\ell k}^{y}-E_{\ell\ell}^{x}\otimes E_{kk}^{y}\right)
- \end{equation}
- {\color{red}confusing notation: tensor product and site index.... Remove tensor product?}
-
+H_{x,y}=\sum_{k,\ell=1}^{N}\Big(E_{k\ell}^{x} E_{\ell k}^{y}-E_{\ell\ell}^{x} E_{kk}^{y}\Big)
+ \end{equation}
   and where the site Hamiltonian is
@@
 \end{equation}
-The generator can also be expressed as
-
+The action of the generator can also be expressed as 
 \begin{equation}
@@
 \begin{equation}
-    \langle f|=\sum_{ {\bf n\in \Omega}}f( {\bf n})\langle  {\bf n}|
+    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
 \end{equation}
@@
 \end{equation}
-that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the basis elements).  \\
- Considering two sites $x,y\in \mathcal{E}$ the standard coproduct operator is defined as 
-\begin{equation}
-\begin{split}
-\Delta^{x,y}:gl(N)&\to gl(N)\otimes gl(N)\\
-E_{ab}&\to E_{ab}^{x}\otimes \mathbbm{1}^{y}+\mathbbm{1}^{x}\otimes E_{ab}^{y}
-\end{split}
-\end{equation}
-therefore, we have 
-\begin{equation}
-\Delta^{x,y}(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}^{x}\otimes E_{ba}^{y}+C_{2}^{x}\otimes \mathbbm{1}^{y}+\mathbbm{1}^{x}\otimes C_{2}^{y}
-\end{equation}
-
-One can check that 
+that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
+More precisely,  considering the standard coproduct 
+\begin{equation}
+\begin{split}
+\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
+E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
+\end{split}
+\end{equation}
+we have 
+\begin{equation}
+\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}
+\end{equation}
+Then, one can check that 
 \begin{equation}\label{hamiltonianCasimir}
-	H_{x,y}=\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}
-\end{equation}
+	H_{x,y}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
+\end{equation}
+where $\Delta^{x,y}(C_2)$ denotes a copy of $\Delta(C_2)$ acting on  
+the edge $(x,y)\in \mathcal{E}$.
 
@@
 \section{Duality}
-\subsection{Definition of duality}
-Consider two Markov processes: $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
+\subsection{Definition}
+Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
 We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have
@@
 \end{equation}
-where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
+where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect to the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
 The duality definition can also be formulated as a relation between the generators.
-Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$ if
+Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect to the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$
 \begin{equation}\label{dualityRelationGenerator}
@@
 \end{equation}
-\textbf{Remark}:
-in the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the processes are self-dual with respect to a self-duality function.
+In the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the process is self-dual.
 \newline
@@
 where the superscript $T$ denotes the matrix transposition.
-Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining transformation between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$.
-Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads as
+Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$.
+Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads
 \begin{equation}\label{DualityRelation}
@@
 \end{equation}
-where $\widetilde{H}=\widetilde{\mathcal{L}}^{T}$.
-\subsection{Duality for the generalized multi-species boundary driven stirring process}
+\subsection{Duality for the multi-species stirring process}
 We now state our duality result.
@@
 \begin{equation}
+\label{duality-function-good}
     D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
@@
 \subsection{Proof of the duality relation}\label{subsectionDualityProof}
-To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{dualityMatrix} we shall show that 
+To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{duality-function-good} we shall show that 
 \begin{equation}
@@
 \end{equation}
-We replace the above eigenvectors in 
+We fix arbitrary $m,m_{2},m_{3}\in \{0,\ldots,L\}$ such that $m=m_{2}+m_{3}$.  We replace the above eigenvectors in 
 \begin{equation}\label{eigDELTA}

### 2023-03-14 main.tex
Update main.tex
check

@@
 \begin{equation}\label{stateSpace}
-    \Omega:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}^{V}
-\end{equation}
-Moreover, we denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$ .\\
+    \Omega:=\Omega_{x}^{V}
+\end{equation}
+where
+\begin{equation}
+\Omega_{x}:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}
+\end{equation}
+Moreover, we denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$  and we denote the site occupation vector as $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$, for all $x\in V$.\\
 The dynamics consists in an exchange of particles (at Poissonian times) between connected vertices.
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(n)=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(n-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(n)\right]
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(\bm{n})\right]
 \end{equation}
 \begin{equation}\label{siteGenerator}
-    \mathcal{L}_{x}f(n)=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(n+\delta_{k}^{x}-\delta_{l}^{x})-f(n)\right]
+    \mathcal{L}_{x}f(\bm{n})=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(\bm{n}+\delta_{k}^{x}-\delta_{l}^{x})-f(\bm{n})\right]
 \end{equation}
@@
 \begin{equation}\label{edgeDualRealtion}
-    H_{x,y}^{T}D=DH_{x,y}\qquad \forall x,y\in \mathcal{E}
+    H_{x,y}^{T}D=DH_{x,y}\qquad \forall (x,y)\in \mathcal{E}
 \end{equation}
@@
 \end{equation}
-We will prove these two statements seprately in the following.
+We will prove these two statements separately in the following.
 

### 2023-03-15 main.tex
DescriptionOfHoles

@@
 \section{The stirring process}
-{\color{blue}We consider the stirring process with an arbitrary number of particles $N$.
-It is important to note that any one of them can be considered the empty (or hole) particle.
-Thus, in this first general setting we do not distinguish between real and empty particles.
-However, this distinction will be useful in the section about duality, where we will see that this empty will play a special role.
-The stochastic dynamics is Markovian and consist in an exchange of particles of any type between two connected site of a graph.}
+The process studied in this paper is the multi-species stirring process on the geometry of a graph.
+We consider the general situation where at any time and at any site a mixture of $\nu\in \mathbb{N}$, chosen among $N$ possible species (sometimes called types or colors), is present.
+Among these $N$ types of particles we will distinguish $N-1$ actual types, labelled with $k\in \{2,\ldots,N\}$ and a 'hole', labelled with $1$.
+This is an arbitrary choice, indeed one could call any of the $N$ colors the hole.
+In the description of the dynamic this choice is not important, since one could think about the dynamic as a pure exchange of types between sites, under the constraint that the maximal occupancy at each site is $\nu$.
+However, studying the duality for the boundary driven case, it will be important to chose an hole type, in order to interpret the dual dynamic as absorbing, i.e.
+to have, eventually, an empty dual process on the graph.
+Furthermore, one could think about the hole type as the only type whose occupation dependes on the occupations of all the true $N-1$ colors.
+In the two species case, this multi-species stirring process, is the SEP($\nu$) (see \cite{giardina2009duality}, \cite{carinci2013duality}).
+Indeed one of the two type is the hole (say again $1$) and its dynamics depends on the one of the true type (say 2), under the constaraint that at most $\nu$ type $2$ particles are present at a site at each time.
+Therefore, the dynamics can be describe only by species $2$.
+It is interesting to observe that, in case we stop distinguishing the colors of the true particles $\{2,\ldots,N\}$, we retrieve the SEP($\nu$), thus this multi-species stirring process seems its natural generalization.
+
 \subsection{The infinitesimal generator}
@@
 where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$.
+Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$ the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
@@
 Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
-\begin{equation}
+\begin{equation}\label{Hamiltonian-Generator}
 H=\mathcal{L}^{T}

### 2023-03-15 main.tex
DualityNew

@@
 \newcommand{\oa}{\mathbf{a}}
-
+\newcommand{\dd}{\mathcal{D}_{\hat{x}}}
 \newcommand{\oad}{\mathbf{a}^{\dagger}}
@@
 \begin{equation}\label{dualityIntertwines}
-    \mathcal{L}D=D\widetilde{\mathcal{L}}^{T}
+    \mathcal{L}D=D\widetilde{\mathcal{L}}^{\,T}
 \end{equation}
@@
 \end{equation}
-\subsection{Duality for the multi-species stirring process}
-We now state our duality result.
-The process $|\mathbf{n}\rangle$ with Hamiltonian \eqref{OriginalHamiltonian} is dual in the sense of \eqref{DualityRelation}, with respect to a process $|\bm{\xi}\rangle$ defined on the enlarged state space
-\begin{equation}
-    \widetilde{\Omega}:=\Omega\times \mathbb{N}_{0}^{V}
-\end{equation}
-with elements
-\begin{equation}
-    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}\rangle\right)
-\end{equation}
-where $r_{x}^{k}$ denotes the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x\in V$ and $m_{k}^{\widetilde{x}}$ denotes the number of particles of species $k\in \{2,\ldots,N\}$ at an extra-site $\widetilde{x}$ connected to the site $x\in V$.\\
+\subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
+The process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}, is dual to the absorbing boundary process $(\bm{\xi}(t))_{t\geq 0}$ living in the enlarged state space
+\begin{equation}\label{dualStateSpace}
+    \widetilde{\Omega}=\Omega_{x}^{V}\times \mathbb{N}_{0}^{V}
+\end{equation}
+with $\forall x\in V$ and $\forall t\geq 0$ we define
+\begin{equation}
+    \xi^{x}(t)=\left(r_{1}^{x}(t),\ldots,r_{N}^{x}(t),m_{2}^{\hat{x}}(t),\ldots,m_{N}^{\hat{x}}(t)\right)
+\end{equation}
+ where we denote $r_{k}^{x}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ at time $t\geq 0$ and where $m_{k}^{\hat{x}}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\hat{x}$ connected to $x\in V$ at time $t\geq 0$.\\
+ The dual generator is 
+ \begin{equation}\label{DualGenerator}
+    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
+\end{equation}
+where 
+$\mathcal{L}_{x,y}$ is the one defined in \eqref{siteGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+\begin{equation}\label{siteDualGenerator}
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\hat{x}})-f(\bm{\xi})\right)
+\end{equation}
+and the duality function is 
+\begin{equation}\label{dualityElements}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}\right)
+\end{equation}
+\newline
+On one hand, the edge part of the dual generator \eqref{DualGenerator} is a copy of \eqref{edgeGenerator}, therefore it performs the stirring dynamics on the graph.
+On the other hand, the site dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\hat{x}$.
+This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{k}^{x}$.
+This means that eventually the dual process empties the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites, that play the role of absorbing boundaries.
+\newline \newline
+\textbf{Remark}: in the reversible situation, i.e.
+when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, is
+\begin{equation}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\hat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\end{equation}
+
+\subsection{Proof of duality}
+To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we shall show that \eqref{dualityRelationGenerator} is fulfilled.
+Here the state space is discrete, therefore the proof consists in finding an intertwining matrix $D$ that satisfies \eqref{dualityIntertwines}.
+To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generato}) and their Lie algebraic description.
+Indeed, in this formalism the proof reduces in finding symmetries and exponential transformation of generators of the Lie algebra, that are the building blocks of the original and dual Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} respectively.
+\\
+The duality statement of subsection \ref{statementDualitySubsection} is rewritten in terms of Hamiltonian operators.
+The dual state space \eqref{dualStateSpace} is interpreted as a vector spaces with elements
+\begin{equation}
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}\rangle\right)
+\end{equation}
 The Hamiltonian of the dual process reads as
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
+    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\hat{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
 \end{equation}
 By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
-$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the occupation of the species $k\in\{2,\ldots,N\}$. \\
-The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
-\begin{equation}
-\label{duality-function-good}
-    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
-\end{equation}
-We denote by $D_{x}$ the site part. This is defined as 
-\begin{equation}
-    D_{x}=R_{x}\exp{(E^{x})}
+$(a^{\dagger})_{k}^{\hat{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\hat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
+The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual, in the sense of \eqref{DualityRelation} with respect to the duality matrix $D$ defined as 
+\begin{equation}\label{dualityMatrix}
+    D=\prod_{x\in V}d_{x}\otimes \dd
+\end{equation}
+where
+\begin{equation}
+d_{x}=R_{x}\exp{(E^{x})}
 \end{equation}
 with 
-\begin{equation}
-    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
-\end{equation}
-that implies 
-\begin{equation}
-    \exp{(E^{x})}=I+E^{x}
-\end{equation}
-and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
-\begin{equation}
-    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
-\end{equation}
-where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
-We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as
+\begin{equation}\label{EquationEx}
+E^{x}=\sum_{a=2}^{N}E_{a1}^{x}
+\end{equation}
+and
+\begin{equation}\label{Rmatrix}
+    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+\end{equation}
+and where 
 \begin{equation}\label{dualityMatrix}
-D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
-\end{equation}
-On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph.
-On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$.
-This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites.
-Thinking about the type $1$ as the hole  the graph is eventually emptied, similarly to what proved in the SEP(2j)\cite{carinci2013duality}.
-\subsection{Proof of the duality relation}\label{subsectionDualityProof}
-To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{duality-function-good} we shall show that 
-\begin{equation}
-    H^{T}D=D\widetilde{H}
-\end{equation}
-Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
+\dd=\sum_{m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}|
+\end{equation}
+The matrix $R_{x}$ is diagonal.
+Their elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}.
+In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $p_{i}=\frac{1}{N}$.
+Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has not been considered, since it does not change the duality relation.
+This $R_{x}$ is called the 'cheap' duality matrix (see \cite{giardina2009duality}).
+Since \eqref{dualityMatrix} is product over sites, \eqref{DualityRelation} is equivalent of proving that 
 \begin{equation}\label{edgeDualRealtion}
@@
 \end{equation}
-and for the site Hamiltonians 
+and 
 \begin{equation}\label{siteDualRelation}
@@
 \end{equation}
-We will prove these two statements separately in the following.
-
-\paragraph{Proof of \eqref{edgeDualRealtion}}
-The proof of the edge duality relation relies on two facts: first the existence of a diagonal matrix, arising from the reversible measure, that is already a duality for the Hamiltonian (in literature called 'cheap' duality matrix, see \cite{giardina2009duality}); second the possibility of finding a proper symmetry of the Hamiltonian.
-\\We first introduce the cheap duality matrix
+We perform the prove in three steps: first we will show that matrix \eqref{dualityMatrix} has indeed elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
+\paragraph{Proof of the elements of the duality matrix}We aim to show that 
+\begin{equation}\label{proofDualityElements}
+\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}
+\end{equation}
+with $D(\bm{n},\bm{\xi})$ defined in \eqref{dualityElements}. 
+Fix an arbitrary site $x\in V$
+\begin{align*}
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}\langle m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}|
+	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\hat{x}},\ldots,q_{N}^{\hat{x}}\rangle
+\end{align*}
+On one hand, on the extra-site $\hat{x}$ we have 
+\begin{align*}
+\sum_{m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}\langle m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}||q_{2}^{\hat{x}},\ldots,q_{N}^{\hat{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}
+\end{align*}
+where we used the orthogonality relation \eqref{ortho}. 
+On the other hand, on the site $x$, we have 
+\begin{align*}
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&=
+\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
+\\&\cdot 
+\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1},\ldots,r_{N}\rangle_{x}\\&=
+\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
+\end{align*}
+where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{k=2}^{N}r_{k}^{x}$.
+Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
+\begin{flushright}
+    $\square$
+\end{flushright}
+\paragraph{Proof of \eqref{edgeDualRealtion}}To show \eqref{edgeDualRealtion} we need two ingredients.
+First is the existence of a similarity transformation between the Hamiltonian $H_{x,y}$ defined in \eqref{edgeHamiltonian} and its transposed.
+As we will show, this similarity transformation is $R_{x}$ defined in \eqref{Rmatrix}.
+Second, the possibility of finding a symmetry for the Hamiltonian \eqref{edgeHamiltonian}, exploiting the fact that $H_{x,y}$ is (up to a constant) the coproduct of the second Casimir of $gl(N)$, as shown in \eqref{hamiltonianCasimir}.
+As we will see, this symmetry is $exp{(E^{x})}\exp{(E^{y})}$ with $E^{x}$ defined in \eqref{equationEx}.
+\\
+We show that 
 \begin{equation}\label{transpositionPropertyR}
-R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
-\end{equation}
-This is diagonal with the inverse of the masses of the reversible measure \eqref{reversibleMeasure}. 
-This matrix connects the generators of the algebra $E^{x}_{ab}$ with their transposed $(E_{ab}^{x})^{T}$ by the following relation
-\begin{equation}
 (E_{ab}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
 \end{equation}
-Indeed, we have
-\begin{align*}
-RE_{ab}^{x}R^{-1}=&\sum_{r\in\chi}\left(\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|\right)
+Indeed
+\begin{align*}
+R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\left(\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|\right)
 	\\&
-	\sum_{s\in \chi,}\left(s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+	\sum_{s^{x}\in \Omega_{x},}\left(s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 	\\&
-	\sum_{n\in\chi}\left(\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|\right)
-	\\=&
-	\sum_{r,n\in \chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{0}^{x},\ldots, r_{N}^{x}|
-	\frac{\nu!}{n_{1}^{x}!\ldots n_{N}^{x}!}n_{b}^{x}
- \\&
- \qquad |n_{1}^{x},\ldots,n_{a}^{x}+1,\ldots,n_{b}^{x}-1,\ldots n_{N}^{x}\rangle \langle n_{1}^{x},\ldots,n_{N}^{x}|
- \\=&
- \sum_{r\in \chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}\frac{\nu!}{r_{1}^{x}!\ldots (r_{a}^{x}-1)!\ldots(r_{b}^{x}+1)!\ldots r_{N}^{x}!}(r_{b}^{x}+1)
- \\&\qquad
- |r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{0}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
-	\\=&\sum_{r\in\chi}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}\frac{\nu!}{r_{1}^{x}!\ldots (r_{a}^{x}-1)!\ldots(r_{b}^{x}+1)!\ldots r_{N}^{x}!}(r_{b}^{x}+1)\frac{r_{a}^{x}}{r_{a}^{x}}
- \\& \qquad
- |r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
-	\\=&\sum_{r\in \chi}
+	\sum_{n_{x}\in\Omega_{x}}\left(\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|\right)
+ \\=&\sum_{r^{x}\in \Omega_{x}}
 	r_{a}^{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
@@
 \end{align*}
-where in the third to last equation we multiplied and divided for $r_{a}^{x}$. 
-The relation \eqref{transpositionPropertyR} implies that 
-\begin{equation}
-    H_{x,y}^{T}=\left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}
-\end{equation}
-We now look for a symmetry of the Hamiltonian.
-As shown in \eqref{hamiltonianCasimir}, it is possible to write the Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir\eqref{secondCasimir} of $gl(N)$.
-We say that a matrix $A\in gl(N)$ is symmetry of $C_{2}$ if
-\begin{equation}
-    [A,C_{2}]=0
-\end{equation}
-By the definition of the standard coproduct operator, it is possible to show that
-\begin{equation}
-    [A,C_{2}]=0\qquad \Longrightarrow \qquad \left[\Delta(A),\Delta(C_{2})\right]=0
-\end{equation}
- $C_{2}$ is a central element of $gl(N)$, then it commutes with each element of the algebra. 
-We chose as a symmetry 
+where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
+Equation \eqref{transpositionPropertyR} implies that 
+\begin{equation}\label{transpositionPropertyH}
+    H_{x,y}^{T}=\left(R_{x}R_{y}\right)H_{x,y}\left(R_{x}R_{y}\right)^{-1}
+\end{equation}
+We now search for a symmetry of $H_{x,y}$. Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
+\begin{equation}
+    [A,B]=0
+\end{equation}
+Moreover, since the coproduct is a Lie algebra homomorphism we have that 
+\begin{equation}\label{symmetryCoproduct}
+    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
+\end{equation}
+Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, we can search for a symmetry of $C_{2}$.
+$C_{2}$ is a central for $gl(N)$, i.e.
+it commutes with all the element of the the algebra.
+We consider
 \begin{equation}\label{equationE}
-    E^{x}=\sum_{k=2}E_{a1}^{x}
-\end{equation}
-As a consequence of the previous considerations we can state that $E^{x}$ is a symmetry for the Hamiltonian \eqref{edgeHamiltonian}. We take the exponential of this symmetry by introducing
-\begin{equation}\label{symmetry}
-    S_{x,y}=\exp{(\Delta(E^{x}))}
-\end{equation}
-This operator can be rewritten as 
-\begin{equation}
-	\begin{split}
-		S&=e^{\Delta^{x,y}(E)}=\exp{(\mathbbm{1}^{x}\otimes E^{y}+E^{x}\otimes \mathbbm{1}^{y})}=\exp{(\mathbbm{1}^{x}\otimes E^{y})} \exp{(E^{x}\otimes \mathbbm{1}^{y})}\\&=\sum_{k=0}^{N}\frac{\left(\mathbbm{1}^{y}\otimes E^{x}\right)^{k}}{k!}\sum_{j=0}^{N}\frac{\left(E^{x}\otimes \mathbbm{1}^{y}\right)^{j}}{j!}=
-		\left(\mathbbm{1}^{x}\otimes \sum_{k=0}^{N}\frac{(E^{y})^{k}}{k!}\right)\left(\sum_{j=0}^{N}\frac{(E^{x})^{j}}{j!}\otimes \mathbbm{1}^{y}\right)\\&=\left(\mathbbm{1}^{x}\otimes \exp{({E}^{y})}\right)\left(\exp{(E^{x})}\otimes \mathbbm{1}^{y}\right)\\&=\exp{(E^{x})}\otimes \exp{(E^{y})}
-	\end{split}
-\end{equation}
-Moreover, by the exponential series of \eqref{equationE}, we have 
-\begin{equation}
-   \exp{(E^{x})}\otimes \exp{(E^{y})}= \left(\mathbbm{1}^{x}+E^{x}\right)\otimes \left(\mathbbm{1}^{y}+E^{y}\right)
-\end{equation}
-Since \eqref{equationE} is a symmetry for $C_{2}$, then we have that
-\begin{equation}\label{commutationSymm-edgeHamiltonian}
-\left[H_{x,y},S\right]=\left[H_{x,y},\exp{(E^{x})}\otimes \exp{(E^{y})}\right]=0
-\end{equation}
-By using \eqref{transpositionPropertyR} and \eqref{commutationSymm-edgeHamiltonian} we obtain
-\begin{equation}
-    \begin{split}
-        H_{x,y}^{T}D=&\left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}D
-        \\=&
-        \left(R_{x}\otimes R_{y}\right)H_{x,y}\left(R_{x}\otimes R_{y}\right)^{-1}\left(R_{x}\otimes R_{y}\right)
-        \\&
-        \left(\left(\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)\bigotimes_{z\in V\,:\,z\neq x,y}(D_{z}\otimes D_{\widetilde{z}})
-        \\=&
-        \left(R_{x}\otimes R_{y}\right)H_{x,y}\left(\left(\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)\bigotimes_{z\in V\,:\,z\neq x,y}(D_{z}\otimes D_{\widetilde{z}})
-    \\=&
-    \left(\left(R_{x}\exp{(E^{x})}\otimes D_{\widetilde{x}}\right)\otimes \left(R_{y}\exp{(E^{y})}\otimes D_{\widetilde{y}}\right)\right)H_{x,y}\bigotimes_{z\in V\,:\, z\neq x,y}\left(D_{z}\otimes D_{\widetilde{z}}\right)
-    \\=&
-    D H_{xy}
-    \end{split}
-\end{equation}
- therefore \eqref{edgeDualRealtion} is proved. 
+    E=\sum_{a=2}^{N}E_{a2}
+\end{equation}
+To obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we take the exponential of this matrix, i.e. we introduce the symmetry
+\begin{equation}
+    S=\exp{(\Delta(E))}
+\end{equation}
+Since $[C_{2},E]=0$, we have that 
+\begin{equation}\label{commutationSC}
+    \left[S,\Delta(C_{2})\right]=0
+\end{equation}
+For fixed $(x,y)\in \mathcal{E}$ and write
+\begin{equation}
+    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
+\end{equation}
+where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{commutationSC}, we have that 
+\begin{equation}\label{symmetryH}
+    \left[S_{x,y},H_{x,y}\right]=0
+\end{equation}
+i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we have that 
+\begin{equation}
+    \begin{split}
+        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\hat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\hat{z}}\right)
+        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\hat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\hat{z}}\right)
+        \\&=
+        DH_{x,y}
+    \end{split}
+\end{equation}
+ where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
+ \newline\newline
+ \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$.
+This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
+By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.
+However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process.
  \begin{flushright}
@@
  \end{flushright}
-
-\paragraph{Proof of \eqref{siteDualRelation}} The proof of the site duality relations relies on the Hadamard Lemma that reads, $\forall E,A \in gl(N)$, as
+ \paragraph{Proof of \eqref{siteDualRelation}} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site that we connect to every site $x\in V$ of the graph $G$.
+\\
+ Considering $A,B\in gl(N)$, we can write the Hadamard formula as 
  \begin{equation}\label{HadamardFormula}
-    \exp{(-E)}A\exp{(E)}=A-\left[E,A\right]+\frac{1}{2!}\left[E,\left[E,A\right],\right]-\frac{1}{3!}\left[E,\left[E,\left[E,A\right]\right]\right]+\ldots
-\end{equation}
- By \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
+     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
+ \end{equation}
+For the following of the proof we will need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
+Therefore we compute
+\begin{enumerate}
+    \item for $A=E_{\ell 1}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
+    \begin{equation}\label{HT_El1}
+        \exp{(-E)}E_{\ell 1}\exp{(E)}=E_{\ell 1}
+    \end{equation}
+    because $E_{\ell 1}$ commutes with $E$
+    \item for $A=E_{\ell\ell}$ with $\ell \in \{2,\ldots,N\}$, we obtain 
+    \begin{equation}\label{HT_Ell}
+        \exp{(-E)}E_{\ell \ell}\exp{(E)}=E_{\ell \ell}+E_{\ell 1}
+    \end{equation}
+Indeed, using \eqref{eq:comgl} we have 
+    \begin{equation*}
+       \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
+    \end{equation*}
+    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
+    \item for $A=E_{1\ell}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
+    \begin{equation}\label{HT-E1l}
+        \exp{(-E)}E_{1 \ell}\exp{(E)}=E_{1\ell}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{j\ell}\right)
+    \end{equation}
+    Indeed, using \eqref{eq:comgl} we have 
+    \begin{equation*}
+[E,E_{1\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{11}-E_{11}\delta_{a\ell}\right)=\sum_{j=2}^{N}E_{j\ell}-E_{11};
+\end{equation*}
+and 
+\begin{equation*}
+\begin{split}
+\left[E,[E,E_{1\ell}]\right]&=\sum_{b=2}^{N}\sum_{j=2}^{N}\left[E_{b1},E_{j\ell}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
+\\&=
+\sum_{j,b=2}^{N}\left(E_{b\ell}\delta_{j1}-E_{j1}\delta_{b\ell}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
+\\=&
+-2\sum_{j=2}^{N}E_{j1};
+\end{split}
+\end{equation*}
+Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT_E1l}.
+\item for $A=E_{k\ell}$ with $k,\ell \in \{2,\ldots,N\}$ we obtain 
+\begin{equation}\label{HT-Ekl}
+    \exp{(-E)}E_{\ell k}\exp{(E)}=E_{k\ell}+E_{\ell 1}
+\end{equation}
+   Indeed, using \eqref{eq:comgl} we have 
+\begin{equation*}
+[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{\ell 1}-E_{\ell 1}^{x}\delta_{ak}\right)=-E_{\ell 1}^{x};
+\end{equation*}
+Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ekl}.
+\item for $A=E_{11}$ we obtain 
+\begin{equation}\label{HT-E11}
+    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{a=2}^{N}E_{a1}^{x}
+\end{equation}
+  Indeed, using \eqref{eq:comgl} we have
+
+\begin{align*}
+[E,E_{11}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{11}-E_{\ell 1}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1};
+\end{align*}
+  Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_E11}.
+\end{enumerate}
+Using \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
 \begin{equation}
@@
 \end{equation}
-First, we multiply both sides for $R_{x}\exp{(E^{x})}$
-\begin{equation}
-    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)R_{x}^{-1}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell =0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+First, we multiply both sides by $R_{x}\exp{(E^{x})}$
+\begin{equation}
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell =0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
 \end{equation}
@@
 \end{equation}
-and finally we apply the Hadamard's formula \eqref{HadamardFormula} to 
-\begin{equation}
-    \exp{(-E^{x})}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell \ell}^{x}\right)\exp{(E^{x})}
-\end{equation}
-We compute the following quantities by the commutation relations \eqref{eq:comgl}:
-\begin{itemize}
-    \item for all $\ell\neq 1$ 
-\begin{equation}
-    \begin{split}
-        \exp{(-E^{x})}E_{\ell1}^{x}\exp{(E^{x})}=E_{\ell1}^{x},
-    \end{split}
-\end{equation}
-\begin{equation}
-    \begin{split}
-    \exp{(-E^{x})}E_{\ell\ell}^{x}\exp{(E^{x})}=E_{\ell\ell}^{x}+E_{\ell1}^{x}
-    \end{split}
-\end{equation}
-and
-\begin{equation}
-\begin{split}
-    \exp{(-E^{x})}E_{1\ell}^{x}\exp{(E^{x})}=E_{1\ell}^{x}+E_{11}^{x}-\sum_{a=2}^{N}\left(E_{a1}^{x}+E_{a\ell}^{x}\right)
-\end{split}
-\end{equation}
-Indeed we have the following commutators at the first order:
-\begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}^{x}\delta_{k1}-E_{\ell1}^{x}\delta_{a\ell}\right)
-\end{align*}
-and 
-\begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{1\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}^{x}\delta_{11}-E_{11}^{x}\delta_{a\ell}\right)=\sum_{a=2}^{N}E_{a\ell}^{x}-E_{11}^{x};
-\end{align*}
-and the following commutators at the second order:
-\begin{align*}
-&\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1}^{x},E_{a\ell}^{x}\right]-\sum_{b=2}^{N}\left[E_{b1}^{x},E_{11}^{x}\right]=\sum_{a,b=2}^{N}\left(E_{b\ell}^{x}\delta_{a1}-E_{a1}^{x}\delta_{b\ell}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)\\=&-2\sum_{a=2}^{N}E_{a1}^{x};
-\end{align*}
-from the third on-wards all commutators zero. 
-\item for all $k,\ell\neq 1$
-\begin{equation}
-        \begin{split}
-    \exp{(-E^{x})}E_{\ell k}^{x}\exp{(E^{x})}=E_{k\ell}^{x}+E_{\ell 1}^{x}
-    \end{split}
-\end{equation}
-Indeed the first commutator gives
-\begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{\ell k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{\ell 1}-E_{\ell 1}^{x}\delta_{ak}\right)=-E_{\ell 1}^{x};
-\end{align*}
-and the from the second commutator on-wards they are all zero.
-\item for the matrix $E_{11}^{x}$
-\begin{equation}
-    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{a=2}^{N}E_{a1}^{x}
-\end{equation}
-indeed the first commutator gives
-\begin{align*}
-\sum_{a=2}^{N}\left[E_{a1}^{x},E_{\ell k}\right]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{11}-E_{\ell 1}^{x}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1}^{x};
-\end{align*}
-and the from the second commutator on-wards they are all zero.
-\end{itemize}
-Therefore we have
-\begin{equation}
-\begin{split}
-    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=1}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}\\&=
+where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$.
+Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that
+\begin{equation}
+\begin{split}
+    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=1}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+    \\=&
      \exp{(-E^{x})}\sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
      + \exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=2}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
-     \\&=
+     \\=&
      \sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{ak}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{k=1}^{N}\sum_{\ell =2}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{\ell 1}^{x}\right)
-     \\&=
+     \\=&
 \sum_{k=2}^{N}\alpha_{k}^{x}E_{1k}^{x}-\sum_{k=1}^{N}\alpha_{k}^{x}\sum_{\ell=2}^{N}E_{\ell\ell}^{x}
@@
      \sum_{k=2}^{N}\left(\alpha_{k}^{x}E_{1k}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{kk}^{x}\right)
-\\&=
+\\=&
 \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
@@
     \begin{split}
-&H_{x,y}^{T}D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+&H_{x,y}^{T}d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
 \\=&
-D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)
+d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)
     \end{split}
@@
 \end{equation}
-Using \eqref{bosonicKX} for a fixed $k\in \{2,\ldots,N\}$ we rewrite the term multiplied for $E_{1k}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+Using \eqref{bosonicKX} by a fixed $k\in \{2,\ldots,N\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{1k}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
 \begin{equation}
@@
 \end{equation}
-where, in the up to last equality, we performed a change of summation variable. Therefore, inserting this in \eqref{siteHadamardII} we obtain 
-\begin{equation}
-    \begin{split}
-     &H_{x,y}^{T}D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+where, in the up to last equality, we performed a change of summation variable. Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 
+\begin{equation}
+    \begin{split}
+     &H_{x,y}^{T}d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
 \\=&
-D_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}-E_{kk}^{x}\right)
-    \end{split}
-\end{equation}
-Since the duality matrix \eqref{dualityMatrix} is tensor product over sites, the above equality implies \eqref{siteDualRelation}. 
+d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+    \end{split}
+\end{equation}
+Since the duality matrix \eqref{dualityMatrix} is product over sites, the above equality implies \eqref{siteDualRelation}. 
 \begin{flushright}
@@
 \end{flushright}
-\textbf{Remark}:
-The duality result can be also stated  in terms of the infinitesimal generators \eqref{Generator}. The dual process is $(\bm{\xi}(t))_{t\geq 0}$ . For each $x\in V$ we define the $x-th$ component as
-\begin{equation}
-\xi^{x}(t)=\left(r_{1}^{x}(t),\ldots,r_{N}^{x}(t),m_{2}^{\widetilde{x}}(t),\ldots,m_{N}^{\widetilde{x}}(t)\right)
-\end{equation}
- where we denote $r_{k}^{x}$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ and with $m_{l}^{\widetilde{x}}$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\widetilde{x}$ connected to $x\in V$.
-This dual process lives in the enlarged state space
-\begin{equation}
-    \widetilde{\Omega}:=\Omega\times \mathbb{N}^{V}_{0}
-\end{equation}
-The dual generator is defined as
-\begin{equation}
-    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
-\end{equation}
-where 
-$\mathcal{L}_{x,y}$ is the one defined in \eqref{siteGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
-\begin{equation}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widetilde{x}})-f(\bm{\xi})\right)
-\end{equation}
-The duality relation \eqref{DualityRelation} reads as
-\begin{equation}\label{dualityGenerators}
-    \left(\mathcal{L}D(\cdot,\bm{\xi})\right)(\bm{n})=\left(\widetilde{\mathcal{L}}D(\bm{n},\cdot)\right)(\bm{\xi})
-\end{equation}
-where 
-\begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\langle \bm{n}|D|\bm{\xi}\rangle=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{1}}\right)^{m_{k}^{\varepsilon(x)}}\right)
-\end{equation}
-are the element of the duality matrix \eqref{dualityMatrix}.
-The proof of \eqref{dualityGenerators} follows from \eqref{DualityRelation}.
-Therefore, we only need to show that the elements of \eqref{dualityMatrix} are indeed \eqref{dualityElements}.
-Fix an arbitrary site $x\in V$
-\begin{align*}
-	 &\langle n^{x}|D_{x}\otimes D_{\widetilde{x}}|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
-	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widetilde{x}},\ldots,q_{N}^{\widetilde{x}}\rangle
-\end{align*}
-On one hand, on the extra-site $\widetilde{x}$ we have 
-\begin{align*}
-\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}||q_{2}^{\widetilde{x}},\ldots,q_{N}^{\widetilde{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}
-\end{align*}
-On the other hand, on the site $x$, we have 
-\begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
-\\&\cdot 
-\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1},\ldots,r_{N}\rangle_{x}\\&=\frac{(2j-\sum_{k=1}^{N}r_{k}^{x})!r_{2}^{x}!\ldots r_{N }^{x}!}{\nu!}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{r_{2}^{x}!\ldots r_{N}^{x}!}\frac{1}{(n_{2}^{x}-r_{2}^{x})!\ldots (n_{N}^{x}-r_{N}^{x})!}\\&=
-\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
-\end{align*}
-where we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{k=2}^{N}r_{k}^{x}$. Finally, by taking the product over $x\in V$ we prove \eqref{dualityElements}.\\
-\newline 
-\textbf{Remark}: It is important to notice that the denomiator the elements of the duality matrix \eqref{dualityElements} $(n_{k}^{x}-r_{k}^{x})!$,  implies that, at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles is lower or equal than the number of original particles.
-This means that the dynamics of the dual proces is simpler than the one of the original one.
-It is possible to perform similar computations choosing as a symmetry $E^{x}=\sum_{a=2}^{N}E_{1a}^{x}$ or $E^{x}=\sum_{a=2}^{N}E_{aa}^{x}$.
-However, these would lead to duality matrices where the number of dual particles is greater than the number of original ones loosing the simplification of the dynamics.
- \newline \\
-\textbf{Remark}: in the reverible situation, i.e.
-when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, is
-\begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widetilde{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
-\end{equation}
-\begin{flushright}
-    $\square$
-\end{flushright}
-\subsection{Duality for a reaction diffusion process}
-In \cite{casini2022uphill}, a two-species hard-core reaction diffusion process has been introduced.
-The feature of this process is that its action on the occupation variable of any species gives a difference-differential equation where both discrete Laplacians and a linear reaction term are present (multiplied for proper constants).
-In this subsection we write a generalization to $N\in \mathbb{N}$ species with arbitrary maximal occupation per site, again called $\nu\in\mathbb{N}_{0}$.
-The generator reads as follows
-\begin{equation}\label{RDGenerator}
-    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}
-\end{equation}
-where
-\begin{equation}
-    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{i=1}^{N}\mathcal{L}_{x,y}^{i}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
-\end{equation}
-with $\mathcal{L}_{x,y}$ and $\mathcal{L}_{x}$ are the generators the generator \eqref{edgeGenerator} and \eqref{siteGenerator} respectively and, for any function $f:\Omega\to \mathbb{R}$
-\begin{equation}
-    \mathcal{L}_{x,u}^{i}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(\bm{n})\right)
-\end{equation}
-with the mapping 
-\begin{equation}
-    g_{i}(k)=\begin{cases}
-    k+i \quad &\text{if}\quad k+i\leq N\\
-    k+i-N\quad &\text{if}\quad k+i>N\\
-    0\quad &\text{if}\quad k=0
-\end{cases}
-\end{equation}
-and where
-\begin{equation}
-    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{l,k=0}^{N}n_{k}^{x}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{l}^{x})-f(\bm{n})\right)
-\end{equation}
-the action on the occupation variable $n_{\alpha}^{x}$ of particle type $\alpha\in \{2,\ldots,N\}$ at site $x\in V $
-is the following
-\begin{equation}\label{actionGraphRD}
-\begin{split}
-    \mathcal{L}_{x,y}^{rd}n_{\alpha}^{x}&=\nu \sigma_{11}(n_{\alpha}^{y}-n_{\alpha}^{x})+\nu\sigma_{12}\sum_{i=1}^{N}(n_{g_{i}(k)}^{y}-n_{\alpha}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
-\end{split}
-\end{equation}
-indeed, 
-\begin{equation}
-    \begin{split}
-\mathcal{L}_{x,y}^{i}n_{\alpha}^{x}&=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(n_{\alpha}^{x}-\delta_{k}^{x}+\delta_{g_{i}(l)^{x}}+\delta_{g_{i}(x)}^{y}-\delta_{l}^{y}-n_{\alpha}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{y}-\sum_{c=1}^{N}n_{\alpha}^{x}n_{c}^{y}
-\\&=
-\sum_{k=2}^{N}n_{k}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{c=2}^{N}n_{\alpha}^{x}n_{c}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
-\\&=
-\nu(n_{q}^{y}-n_{\alpha}^{x})
-    \end{split}
-\end{equation}
-where we call $q\in \{1,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $c\in \{1,\ldots,N\}$ such that $g_{i}(c)\neq \alpha$.
-Summing over all indices $i\in\{1,\ldots,N\}$ we obtain \eqref{actionGraphRD}.\\
-Therefore, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives
-\begin{equation}\label{DifferenceEquation}
-\mathcal{L}^{rd}n_{\alpha}^{x}=\nu\sigma_{11}\Delta_{L}n_{\alpha}^{x}+\nu\sigma_{12}\sum_{l=2\,:\,l\neq k}^{N}\Delta_{L}n_{l}^{x}+\Upsilon\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
-\end{equation}
-where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e.
-$\Delta_{L}n_{k}^{x}=n_{k}^{x+1}+n_{k}^{x-1}-2n_{k}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
-In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
-\\
-The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
-$\alpha_{k}^{x}=\alpha$, $\forall k\in \{1,\ldots,N\}$ and $x\in V$.
-This measure is given by
-\begin{equation}
-    \Lambda^{rev}=\bigotimes_{x\in V}\Lambda_{x}^{rev}
-\end{equation}
-where the marginals are
-\begin{equation}
-    \Lambda_{x}^{rev}\sim \text{Multinomial}(\nu,p,\ldots,p)
-\end{equation}
-with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.\\
-This generator $\mathcal{L}^{rd}$ can be described by the Hamiltonian $H^{rd}$ that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
-\begin{equation}
-    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{i=1}^{N}H_{x,y}^{i}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
-\end{equation}
-where $H_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
-\begin{equation}
-    H_{x,y}^{i}=\sum_{k,l=0}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)
-\end{equation}
-and 
-\begin{equation}
-    H_{x,y}^{m}=\sum_{k,l}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)
-\end{equation}
-For this model, the duality relation is
-\begin{equation}\label{DualityRelationRD}
-    (H^{rd})^{T}D=D\widetilde{H}^{rd}
-\end{equation}
-where the duality matrix $D$ is again \eqref{dualityMatrix}.
-Following subsection \ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
-This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
-Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
-\begin{align*}
-    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)\right]
-    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left\{\left(E_{ak}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{bk}\right)-\left(E_{ak}^{x}\delta_{k0}-E_{k0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}
-    \\=&
-    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{ak}^{x}\left(\delta_{g_{i}(l)0}-\delta_{k0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{k0}^{x}\right)\delta_{ak}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
-    \\=&\;0
-\end{align*}
- Again, using \eqref{eq:comgl} and by a similar argument, we obtain
-\begin{equation}
-\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
-\end{equation}
-Therefore, arguing similarly to subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved. 
+
 \section{Integrability}\label{sec4}
@@
 \subsection{Bethe ansatz solution}
+
 Describe eigenvalues of $T_0$ following 
 \cite{Belliard2}
+
+\section{Multi-species stirring process with reaction}
+\subsection{Duality for a reaction diffusion process}
+In \cite{casini2022uphill}, a two-species hard-core reaction diffusion process has been introduced.
+The feature of this process is that its action on the occupation variable of any species gives a difference-differential equation where both discrete Laplacians and a linear reaction term are present (multiplied for proper constants).
+In this subsection we write a generalization to $N\in \mathbb{N}$ species with arbitrary maximal occupation per site, again called $\nu\in\mathbb{N}_{0}$.
+The generator reads as follows
+\begin{equation}\label{RDGenerator}
+    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}
+\end{equation}
+where
+\begin{equation}
+    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{i=1}^{N}\mathcal{L}_{x,y}^{i}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+\end{equation}
+with $\mathcal{L}_{x,y}$ and $\mathcal{L}_{x}$ are the generators the generator \eqref{edgeGenerator} and \eqref{siteGenerator} respectively and, for any function $f:\Omega\to \mathbb{R}$
+\begin{equation}
+    \mathcal{L}_{x,u}^{i}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(\bm{n})\right)
+\end{equation}
+with the mapping 
+\begin{equation}
+    g_{i}(k)=\begin{cases}
+    k+i \quad &\text{if}\quad k+i\leq N\\
+    k+i-N\quad &\text{if}\quad k+i>N\\
+    0\quad &\text{if}\quad k=0
+\end{cases}
+\end{equation}
+and where
+\begin{equation}
+    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{l,k=0}^{N}n_{k}^{x}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{l}^{x})-f(\bm{n})\right)
+\end{equation}
+the action on the occupation variable $n_{\alpha}^{x}$ of particle type $\alpha\in \{2,\ldots,N\}$ at site $x\in V $
+is the following
+\begin{equation}\label{actionGraphRD}
+\begin{split}
+    \mathcal{L}_{x,y}^{rd}n_{\alpha}^{x}&=\nu \sigma_{11}(n_{\alpha}^{y}-n_{\alpha}^{x})+\nu\sigma_{12}\sum_{i=1}^{N}(n_{g_{i}(k)}^{y}-n_{\alpha}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
+\end{split}
+\end{equation}
+indeed, 
+\begin{equation}
+    \begin{split}
+\mathcal{L}_{x,y}^{i}n_{\alpha}^{x}&=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(n_{\alpha}^{x}-\delta_{k}^{x}+\delta_{g_{i}(l)^{x}}+\delta_{g_{i}(x)}^{y}-\delta_{l}^{y}-n_{\alpha}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{y}-\sum_{c=1}^{N}n_{\alpha}^{x}n_{c}^{y}
+\\&=
+\sum_{k=2}^{N}n_{k}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{c=2}^{N}n_{\alpha}^{x}n_{c}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+\\&=
+\nu(n_{q}^{y}-n_{\alpha}^{x})
+    \end{split}
+\end{equation}
+where we call $q\in \{1,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $c\in \{1,\ldots,N\}$ such that $g_{i}(c)\neq \alpha$.
+Summing over all indices $i\in\{1,\ldots,N\}$ we obtain \eqref{actionGraphRD}.\\
+Therefore, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives
+\begin{equation}\label{DifferenceEquation}
+\mathcal{L}^{rd}n_{\alpha}^{x}=\nu\sigma_{11}\Delta_{L}n_{\alpha}^{x}+\nu\sigma_{12}\sum_{l=2\,:\,l\neq k}^{N}\Delta_{L}n_{l}^{x}+\Upsilon\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
+\end{equation}
+where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e.
+$\Delta_{L}n_{k}^{x}=n_{k}^{x+1}+n_{k}^{x-1}-2n_{k}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
+In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
+\\
+The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
+$\alpha_{k}^{x}=\alpha$, $\forall k\in \{1,\ldots,N\}$ and $x\in V$.
+This measure is given by
+\begin{equation}
+    \Lambda^{rev}=\bigotimes_{x\in V}\Lambda_{x}^{rev}
+\end{equation}
+where the marginals are
+\begin{equation}
+    \Lambda_{x}^{rev}\sim \text{Multinomial}(\nu,p,\ldots,p)
+\end{equation}
+with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.\\
+This generator $\mathcal{L}^{rd}$ can be described by the Hamiltonian $H^{rd}$ that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
+\begin{equation}
+    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{i=1}^{N}H_{x,y}^{i}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+\end{equation}
+where $H_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
+\begin{equation}
+    H_{x,y}^{i}=\sum_{k,l=0}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)
+\end{equation}
+and 
+\begin{equation}
+    H_{x,y}^{m}=\sum_{k,l}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)
+\end{equation}
+For this model, the duality relation is
+\begin{equation}\label{DualityRelationRD}
+    (H^{rd})^{T}D=D\widetilde{H}^{rd}
+\end{equation}
+where the duality matrix $D$ is again \eqref{dualityMatrix}.
+Following subsection \ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
+This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
+Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
+\begin{align*}
+    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)\right]
+    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left\{\left(E_{ak}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{bk}\right)-\left(E_{ak}^{x}\delta_{k0}-E_{k0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}
+    \\=&
+    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{ak}^{x}\left(\delta_{g_{i}(l)0}-\delta_{k0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{k0}^{x}\right)\delta_{ak}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
+    \\=&\;0
+\end{align*}
+ Again, using \eqref{eq:comgl} and by a similar argument, we obtain
+\begin{equation}
+\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
+\end{equation}
+Therefore, arguing similarly to subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.
+
 \section{Conclusion}

### 2023-03-16 main.tex
fixedDuality

@@
 \newcommand{\oa}{\mathbf{a}}
-\newcommand{\dd}{\mathcal{D}_{\hat{x}}}
+\newcommand{\dd}{\mathcal{D}_{\widehat{x}}}
 \newcommand{\oad}{\mathbf{a}^{\dagger}}
@@
 We consider the general situation where at any time and at any site a mixture of $\nu\in \mathbb{N}$, chosen among $N$ possible species (sometimes called types or colors), is present.
-Among these $N$ types of particles we will distinguish $N-1$ actual types, labelled with $k\in \{2,\ldots,N\}$ and a 'hole', labelled with $1$.
+Among these $N$ types of particles we will distinguish $N-1$ 'actual' types, labelled with $k\in \{2,\ldots,N\}$ and a 'hole', labelled with $1$.
 This is an arbitrary choice, indeed one could call any of the $N$ colors the hole.
@@
 to have, eventually, an empty dual process on the graph.
-Furthermore, one could think about the hole type as the only type whose occupation dependes on the occupations of all the true $N-1$ colors.
-In the two species case, this multi-species stirring process, is the SEP($\nu$) (see \cite{giardina2009duality}, \cite{carinci2013duality}).
+Furthermore, as the configuration of each site at each time is a mixture of $\nu$ particles, one could think about the hole as the only type whose occupation dependes on the occupations of all the true $N-1$ colors.
+In the two species case, this multi-species stirring process  is the SEP($\nu$) (see \cite{giardina2009duality}, \cite{carinci2013duality}).
 Indeed one of the two type is the hole (say again $1$) and its dynamics depends on the one of the true type (say 2), under the constaraint that at most $\nu$ type $2$ particles are present at a site at each time.
@@
 \end{equation}
-Moreover, we denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$  and we denote the site occupation vector as $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$, for all $x\in V$.\\
+We denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$ .\\
 The dynamics consists in an exchange of particles (at Poissonian times) between connected vertices.
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(\bm{n})\right]
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{k,\ell=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{k}+\delta_{\ell}^{x}+\delta_{k}^{y}-\delta_{\ell}^{y})-f(\bm{n})\right]
 \end{equation}
 \begin{equation}\label{siteGenerator}
-    \mathcal{L}_{x}f(\bm{n})=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(\bm{n}+\delta_{k}^{x}-\delta_{l}^{x})-f(\bm{n})\right]
+    \mathcal{L}_{x}f(\bm{n})=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}n_{\ell}^{x}\left[f(\bm{n}+\delta_{k}^{x}-\delta_{\ell}^{x})-f(\bm{n})\right]
 \end{equation}
@@
 \end{equation}
-This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{k}^{x}n_{l}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{\ell}^{x}$ a particle of type $\ell$ is replaced with a particle of type $k$.
+This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{k}^{x}n_{\ell}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{\ell}^{x}$ a particle of type $\ell$ is replaced with a particle of type $k$.
 See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 
@@
 \end{equation}
-This can be proven just by imposing the detailed balance conditions for the edge and for the site generators.
+This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
 If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own density $\alpha^{x}=(\alpha_{1}^{x},\ldots,\alpha_{N}^{x})$ and currents will arise when at least two of them are different.
@@
 where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$.
-Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$ the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
+Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
@@
 \begin{equation}
-    \xi^{x}(t)=\left(r_{1}^{x}(t),\ldots,r_{N}^{x}(t),m_{2}^{\hat{x}}(t),\ldots,m_{N}^{\hat{x}}(t)\right)
-\end{equation}
- where we denote $r_{k}^{x}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ at time $t\geq 0$ and where $m_{k}^{\hat{x}}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\hat{x}$ connected to $x\in V$ at time $t\geq 0$.\\
+    \xi^{x}(t)=\left(r_{1}^{x}(t),\ldots,r_{N}^{x}(t),m_{2}^{\widehat{x}}(t),\ldots,m_{N}^{\widehat{x}}(t)\right)
+\end{equation}
+ where we denote $r_{k}^{x}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ at time $t\geq 0$ and where $m_{k}^{\widehat{x}}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\widehat{x}$ connected to $x\in V$ at time $t\geq 0$.\\
  The dual generator is 
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\hat{x}})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widehat{x}})-f(\bm{\xi})\right)
 \end{equation}
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\right)
 \end{equation}
@@
 On one hand, the edge part of the dual generator \eqref{DualGenerator} is a copy of \eqref{edgeGenerator}, therefore it performs the stirring dynamics on the graph.
-On the other hand, the site dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\hat{x}$.
+On the other hand, the site dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$.
 This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{k}^{x}$.
-This means that eventually the dual process empties the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites, that play the role of absorbing boundaries.
+This means that eventually the dual process empties the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites For this reasons these $\widehat{x}$  play the role of absorbing boundaries.
 \newline \newline
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\hat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 Here the state space is discrete, therefore the proof consists in finding an intertwining matrix $D$ that satisfies \eqref{dualityIntertwines}.
-To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generato}) and their Lie algebraic description.
+To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
 Indeed, in this formalism the proof reduces in finding symmetries and exponential transformation of generators of the Lie algebra, that are the building blocks of the original and dual Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} respectively.
@@
 \begin{equation}
-    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}\rangle\right)
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle\right)
 \end{equation}
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\hat{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
+    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
 \end{equation}
 By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
-$(a^{\dagger})_{k}^{\hat{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\hat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
-The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual, in the sense of \eqref{DualityRelation} with respect to the duality matrix $D$ defined as 
+$(a^{\dagger})_{k}^{\widehat{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
+The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} with respect to the duality matrix $D$ defined as 
 \begin{equation}\label{dualityMatrix}
@@
 \begin{equation}\label{dualityMatrix}
-\dd=\sum_{m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}|
+\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \end{equation}
@@
 In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $p_{i}=\frac{1}{N}$.
-Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has not been considered, since it does not change the duality relation.
+Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation.
 This $R_{x}$ is called the 'cheap' duality matrix (see \cite{giardina2009duality}).
+\\
 Since \eqref{dualityMatrix} is product over sites, \eqref{DualityRelation} is equivalent of proving that 
@@
 \end{equation}
-We perform the prove in three steps: first we will show that matrix \eqref{dualityMatrix} has indeed elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
+We perform the proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
 \paragraph{Proof of the elements of the duality matrix}We aim to show that 
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}\langle m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}|
-	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\hat{x}},\ldots,q_{N}^{\hat{x}}\rangle
-\end{align*}
-On one hand, on the extra-site $\hat{x}$ we have 
-\begin{align*}
-\sum_{m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}\langle m_{2}^{\hat{x}},\ldots,m_{N}^{\hat{x}}||q_{2}^{\hat{x}},\ldots,q_{N}^{\hat{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\hat{x}}}
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle
+\end{align*}
+On one hand, on the extra-site $\widehat{x}$ we have 
+\begin{align*}
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}
 \end{align*}
@@
 \end{flushright}
-\paragraph{Proof of \eqref{edgeDualRealtion}}To show \eqref{edgeDualRealtion} we need two ingredients.
-First is the existence of a similarity transformation between the Hamiltonian $H_{x,y}$ defined in \eqref{edgeHamiltonian} and its transposed.
+\paragraph{Proof of \eqref{edgeDualRealtion}}To show \eqref{edgeDualRealtion} we need two 'ingredients'.
+First the existence of a similarity transformation between the Hamiltonian $H_{x,y}$ defined in \eqref{edgeHamiltonian} and its transposed.
 As we will show, this similarity transformation is $R_{x}$ defined in \eqref{Rmatrix}.
-Second, the possibility of finding a symmetry for the Hamiltonian \eqref{edgeHamiltonian}, exploiting the fact that $H_{x,y}$ is (up to a constant) the coproduct of the second Casimir of $gl(N)$, as shown in \eqref{hamiltonianCasimir}.
-As we will see, this symmetry is $exp{(E^{x})}\exp{(E^{y})}$ with $E^{x}$ defined in \eqref{equationEx}.
+Second, the possibility of finding a symmetry for the Hamiltonian \eqref{edgeHamiltonian}.
+Exploiting the fact that $H_{x,y}$ is a linear function of the coproduct of the second Casimir of $gl(N)$, (see \eqref{hamiltonianCasimir}) this symmetry is $\exp{(E^{x})}\exp{(E^{y})}$ with $E^{x}$ defined in \eqref{equationEx}.
 \\
@@
 \end{equation}
-For fixed $(x,y)\in \mathcal{E}$ and write
+For fixed $(x,y)\in \mathcal{E}$ we introduce
 \begin{equation}
@@
 \end{equation}
-i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we have that 
-\begin{equation}
-    \begin{split}
-        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\hat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\hat{z}}\right)
-        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\hat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\hat{z}}\right)
+i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we obtain that 
+\begin{equation}
+    \begin{split}
+        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
+        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
         \\&=
@@
  \end{flushright}
- \paragraph{Proof of \eqref{siteDualRelation}} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site that we connect to every site $x\in V$ of the graph $G$.
+ \paragraph{Proof of \eqref{siteDualRelation}} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$.
 \\
@@
  \end{equation}
-For the following of the proof we will need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
+For the following of the proof we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
 Therefore we compute
@@
 \end{equation*}
-Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT_E1l}.
+Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
 \item for $A=E_{k\ell}$ with $k,\ell \in \{2,\ldots,N\}$ we obtain 
@@
 \end{equation*}
-Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ekl}.
+Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-Ekl}.
 \item for $A=E_{11}$ we obtain 
 \begin{equation}\label{HT-E11}
-    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{a=2}^{N}E_{a1}^{x}
+    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{j=2}^{N}E_{j1}^{x}
 \end{equation}
@@
 \begin{align*}
-[E,E_{11}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{11}-E_{\ell 1}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1};
-\end{align*}
-  Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_E11}.
+[E,E_{11}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{11}-E_{\ell 1}\delta_{a1}\right)=\sum_{j=2}^{N}E_{j1};
+\end{align*}
+  Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-E11}.
 \end{enumerate}
@@
 \end{equation}
-We multiply both sides of \eqref{siteHadamardI} by 
-\begin{equation}
-\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+Making the tensor product on both sides of \eqref{siteHadamardI} by 
+\begin{equation}
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \end{equation}
@@
     \begin{split}
-&H_{x,y}^{T}d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \\=&
-d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)
-    \end{split}
-\end{equation}
-Recalling the action of the bosonic creation operator acting at site $\widetilde{x}$ and on the species $k\in \{2,\ldots,N\}$ we have that 
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)
+    \end{split}
+\end{equation}
+Recalling the action of the bosonic creation operator acting at site $\widehat{x}$ and on the species $k\in \{2,\ldots,N\}$ we have that 
 \begin{equation}\label{bosonicKX}
-    \langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}}+1,\ldots,m_{N}^{\widetilde{x}}|=  \langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})^{\widetilde{x}}_{k}
+    \langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|=  \langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})^{\widehat{x}}_{k}
 \end{equation}
@@
     \begin{split}
-&\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
-\\=&\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}+1}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}}+1,\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}
+&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
+\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
 \\=&
-\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{k}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|(a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}
-    \end{split}
-\end{equation}
-where, in the up to last equality, we performed a change of summation variable. Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 
-\begin{equation}
-    \begin{split}
-     &H_{x,y}^{T}d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
+    \end{split}
+\end{equation}
+where, in the last equality, we performed a change of summation variable. Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 
+\begin{equation}
+    \begin{split}
+     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \\=&
-d_{x}\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widetilde{x}}}\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)
     \end{split}

### 2023-03-16 main.tex
fixed

@@
 
-\section{Duality}
+\section{Duality}\label{sectionDuality}
 \subsection{Definition}
@@
 \end{equation}
-\subsection{Absorption probabilities for general 2j}
+\subsection{Absorption probabilities}
+{\color{blue}An application of duality is to compute the moments of the steday state of the the original process.
+Indeed, as metioned in subsection \ref{}, the dual process voids the chain.
+Therefore, the problem of computing the moments with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles.
+\\
+Calling $\mu_{stat}$ the stationary measure of the the process \eqref{Generator} starting from a configuration $\bm{n}$, we can write the following chain of equalities
+\begin{equation}
+\begin{split}
+\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+\\=&
+\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}
+\\&
+\mathbb{P}\left(\xi(\infty)=\sum_{k=2}^{N}\left(i_{k}\delta_{0}+(|\xi_{k}|-i_{k})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+\end{split}
+\end{equation}
+we denote by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left and by $|\xi_{k}|-i_{k}$ the number of particles absorbed at right. \\}
+
 Even though integrability does not hold anymore for $j>\frac{1}{2}$, by using the absorbing duality we can still say something about the moment of the non equilibrium steady state distribution.

### 2023-03-16 main.tex
Update main.tex

@@
 \begin{equation}\label{stateSpace}
-    \Omega:=\Omega_{x}^{V}
+    \Omega:=\bigtimes_{x\in V} \Omega_{x}
 \end{equation}
@@
 \subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
-The process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}, is dual to the absorbing boundary process $(\bm{\xi}(t))_{t\geq 0}$ living in the enlarged state space
+In this section we show that the process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}, is dual to a process $(\bm{\xi}(t))_{t\geq 0}$ taking values in the enlarged state space
 \begin{equation}\label{dualStateSpace}
-    \widetilde{\Omega}=\Omega_{x}^{V}\times \mathbb{N}_{0}^{V}
-\end{equation}
-with $\forall x\in V$ and $\forall t\geq 0$ we define
-\begin{equation}
-    \xi^{x}(t)=\left(r_{1}^{x}(t),\ldots,r_{N}^{x}(t),m_{2}^{\widehat{x}}(t),\ldots,m_{N}^{\widehat{x}}(t)\right)
-\end{equation}
- where we denote $r_{k}^{x}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at site $x$ at time $t\geq 0$ and where $m_{k}^{\widehat{x}}(t)$ the occupation of dual particle of type $k\in \{1,\ldots,N\}$ at extra-site $\widehat{x}$ connected to $x\in V$ at time $t\geq 0$.\\
- The dual generator is 
+    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
+\end{equation}
+To each site $x\in V$ we associate an ``extra site'', denoted $\widehat{x}$,
+where dual particles will accumulate in the course of time. 
+We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+\begin{equation}
+    \bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
+\end{equation}
+where the component $r_{k}^{x}$ is interpreted as the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{k}^{\widehat{x}}$  gives the number of dual particles of type $k\in \{2,\ldots,N\}$ at 
+the extra-site $\widehat{x}$ connected to $x\in V$.
+ The  generator of the dual process is 
  \begin{equation}\label{DualGenerator}
@@
 where 
-$\mathcal{L}_{x,y}$ is the one defined in \eqref{siteGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+$\mathcal{L}_{x,y}$ is defined in \eqref{siteGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\xi_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widehat{x}})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}r_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widehat{x}})-f(\bm{\xi})\right)
 \end{equation}
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\,\right)
 \end{equation}
@@
 On one hand, the edge part of the dual generator \eqref{DualGenerator} is a copy of \eqref{edgeGenerator}, therefore it performs the stirring dynamics on the graph.
-On the other hand, the site dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$.
+On the other hand, the dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$.
 This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{k}^{x}$.
-This means that eventually the dual process empties the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites For this reasons these $\widehat{x}$  play the role of absorbing boundaries.
+This means that eventually the dual process voids the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites.
+In other words the extra-sites play the role of absorbing boundaries.
 \newline \newline
 \textbf{Remark}: in the reversible situation, i.e.
-when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the average of the element of the duality matrix with respect to the reversible measure \eqref{reversibleMeasure}, is
+when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
 \begin{equation}
@@
 \subsection{Proof of duality}
-To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we shall show that \eqref{dualityRelationGenerator} is fulfilled.
-Here the state space is discrete, therefore the proof consists in finding an intertwining matrix $D$ that satisfies \eqref{dualityIntertwines}.
+To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{dualityIntertwines} is fulfilled.
 To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
-Indeed, in this formalism the proof reduces in finding symmetries and exponential transformation of generators of the Lie algebra, that are the building blocks of the original and dual Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} respectively.
-\\
-The duality statement of subsection \ref{statementDualitySubsection} is rewritten in terms of Hamiltonian operators.
-The dual state space \eqref{dualStateSpace} is interpreted as a vector spaces with elements
+Indeed, in this formalism the proof reduces in finding symmetries and exponential transformation of generators of the Lie algebra.\\
+The configuration space  \eqref{dualStateSpace} of the dual process is the collection of vectors
 \begin{equation}
@@
 \end{equation}
-
 where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
@@
 \end{equation}
-By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
-$(a^{\dagger})_{k}^{\widehat{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
+Here we introduced bosonic creation operator $a^{\dagger}$ acting as $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
+$(a^{\dagger})_{k}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
 The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} with respect to the duality matrix $D$ defined as 
@@
 and where 
-\begin{equation}\label{dualityMatrix}
+\begin{equation}\label{dualityMatrix2}
 \dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
@@
 The matrix $R_{x}$ is diagonal.
-Their elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}.
+Its elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}.
 In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $p_{i}=\frac{1}{N}$.
 Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation.
-This $R_{x}$ is called the 'cheap' duality matrix (see \cite{giardina2009duality}).
+This $R_{x}$ is called the ``cheap'' duality matrix (see \cite{giardina2009duality}).
 \\
-Since \eqref{dualityMatrix} is product over sites, \eqref{DualityRelation} is equivalent of proving that 
+Since \eqref{dualityMatrix} is product over sites, \eqref{DualityRelation} is equivalent to proving that 
 \begin{equation}\label{edgeDualRealtion}
@@
 We perform the proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
-\paragraph{Proof of the elements of the duality matrix}We aim to show that 
+\paragraph{Elements of the duality matrix.}We aim to show that 
 \begin{equation}\label{proofDualityElements}
@@
 \end{flushright}
-\paragraph{Proof of \eqref{edgeDualRealtion}}To show \eqref{edgeDualRealtion} we need two 'ingredients'.
+\paragraph{Proof of \eqref{edgeDualRealtion}.}To show \eqref{edgeDualRealtion} we need two 'ingredients'.
 First the existence of a similarity transformation between the Hamiltonian $H_{x,y}$ defined in \eqref{edgeHamiltonian} and its transposed.
@@
 Second, the possibility of finding a symmetry for the Hamiltonian \eqref{edgeHamiltonian}.
-Exploiting the fact that $H_{x,y}$ is a linear function of the coproduct of the second Casimir of $gl(N)$, (see \eqref{hamiltonianCasimir}) this symmetry is $\exp{(E^{x})}\exp{(E^{y})}$ with $E^{x}$ defined in \eqref{equationEx}.
+Exploiting the fact that $H_{x,y}$ is a linear function of the coproduct of the second Casimir of $gl(N)$, (see \eqref{hamiltonianCasimir}) this symmetry is $\exp{(E^{x})}\exp{(E^{y})}$ with $E^{x}$ defined in \eqref{EquationEx}.
 \\
@@
  \end{flushright}
- \paragraph{Proof of \eqref{siteDualRelation}} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$.
+ \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$.
 \\

### 2023-03-17 main.tex
E comment

@@
 This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
-By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.
+By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
+ {\color{blue} That's confusing. What is E?}
+
  However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 

### 2023-03-17 main.tex
Density
Fixed

@@
 \newcommand{\twoj}{\nu}
+\allowdisplaybreaks
 
@@
 The process described by the generator \eqref{Generator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasure}
-\mu_{rev}=\bigotimes_{x\in V}\mu_{rev}^{x}
+\mu_{rev}=\bigtimes_{x\in V}\mu_{rev}^{x}
 \end{equation}
@@
 \begin{equation}
- \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad \text{where}\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
+ \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
 \end{equation}
@@
 \begin{equation}
-\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}p_{k}^{n_{k}^{x}}
+\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}\rho_{k}^{n_{k}^{x}}
 \end{equation}
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\,\right)
+\end{equation}
+where we denote the \textit{density} of the species $k\in \{2,\ldots,N\}$ at the reservoir connected with the site $x\in V$  by 
+\begin{equation}
+\rho_{k}^{x}:=\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
 \end{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \end{equation}
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
-	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle
 \end{align*}
@@
 \begin{align*}
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}
 \end{align*}
@@
 This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
-By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
+By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
  {\color{blue} That's confusing. What is E?}
@@
 Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that
-\begin{equation}
-\begin{split}
+\begin{align*}
     &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=1}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
@@
      \sum_{k=2}^{N}\left(\alpha_{k}^{x}E_{1k}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{kk}^{x}\right)
+=
+\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
 \\=&
-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
-    \end{split}
-\end{equation}
+\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}^{x}\right)
+ \end{align*}
 Thus, we rewrite \eqref{intermediateTransposeSite} as
 \begin{equation}\label{siteHadamardI}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}^{x}\right)
 \end{equation}
@@
 \begin{equation}
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \end{equation}
@@
     \begin{split}
-&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \\=&
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}\right)
     \end{split}
@@
     \begin{split}
-&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
-\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
+&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
+\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
 \\=&
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
     \end{split}
@@
     \begin{split}
-     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \\=&
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)
     \end{split}

### 2023-03-20 main.tex
CheckFormula3.3.16
IntegrabilityFixed

@@
 \begin{equation}\label{equationE}
-    E=\sum_{a=2}^{N}E_{a2}
+    E=\sum_{a=2}^{N}E_{a1}
 \end{equation}
@@
 
-\section{Integrability}\label{sec4}
-We study the explicit steady state and the exact formulas for the correlations in the case of hard-core interaction ($\twoj=1$), i.e.
-when at most one particle of any is allowed in each site at any time.
-We simplify the geometry to a one dimensional chain $\{1,\ldots,L\}$ of length $L$ with boundaries at the ends.
-We assume a nearest neighbor interaction, i.e.
-we fix the conductances as follows
+\section{Integrability}\label{sectionIntegrabiliy}
+\subsection{The integrable chain and the matrix product ansatz}
+In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs are connected with the end site $1$ and $L$.
+These boundaries, exchanges particle with the external environment, putting the chain out of equilibrium.
+To use integrability is better to work with Hamiltonians.
+The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conducatances are
 \begin{equation}
     \omega_{x,y}=\begin{cases}
-    1\quad \text{if}\quad |x-y|=1\\
+    1 \quad \text{if}\quad |x-y|=1\\
     0\quad \text{otherwise}
@@
 \end{equation}
-$\forall x,y\in \{1,\ldots,L\}$.\\
-The local inhomogeneities are chosen as follows: $\Gamma_{x}=0$ $\forall x\in \{2,\ldots,L-1\}$ and $\Gamma_{1}=\Gamma_{L}=1$. \\
-We can think about the species $1$ as the empty state of the chain. This will be useful in the correlation formula.\\
-In this section we will denote the element of the representation of the Lie algebra by lowercase letters, i.e.
-$e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra).
-\\
+and the local inhomogeneities are
+\begin{equation}
+    \Gamma_{x}=\begin{cases}
+        1\quad \text{if} \quad x\in \{1,L\}\\
+        0\quad \text{otherwise}
+    \end{cases}
+    \end{equation}
+We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
+We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra). \\
 The state space of the chain is 
 \begin{equation}
-	\Omega=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle\;:\;n\in\mathbb{N}_0^N\;\;|n|=1\right\}^{L}
+    \Omega=\bigtimes_{x=1}^{L}\Omega_{x}
+\end{equation}
+where 
+\begin{equation}
+	\Omega_{x}=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle\;:\;n\in\mathbb{N}_0^N\;\;|n|=1\right\}
 \end{equation} 
@@
 \begin{equation}\label{hamiltonian}
-	H=B_{1}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+B_{L}
+	H=B_{1}+H_{bulk}+B_{L}
 \end{equation}
@@
 \begin{equation}
+    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
+\end{equation}
+Moreover, for a fixed site $x\in \{1,\ldots,L\}$ we have 
+\begin{equation}
 	\begin{split}
@@
 \end{equation}
-and boundary terms 
+The boundary terms are given by 
 \begin{equation}
@@
 \end{equation}
-where the rates satisfy
+where we assume that the parameters satisfy
 \begin{equation}\label{ratesConditions}
@@
 \end{equation}
-{\color{red} I will add a figure with the boundary driven chain}\\
-The steady state can be found by the \textit{matrix product ansatz}, that was introduced for the multispecies hard-core stirring in \cite{vanicat2017exact}.
-The formulation is the following.
-We aim to compute $|\Psi\rangle$ such that
+Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product anstz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat}).
+We recall the main points of this ansatz.
+\\
+ Calling $|\mathbb{P}(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
+\begin{equation}
+    \frac{d|\mathbb{P}(t)}{dt}=H|\mathbb{P}(t)\rangle
+\end{equation}
+We define the steady state of $H$ defined in \eqref{hamiltonian} a vector, denoted by $|\Psi\rangle$ that contains the probabilities of every configuration of the chain with respect to the stationary distribution, i.e.
+the probability distribution that the chain reaches when $t\to \infty$.
+We observe that, since the Markov chain with Hamiltonian \eqref{hamiltonian} is positive recurrent there exists a unique stationary distribution and, moreover, this is distribution is reached when $t\to \infty$ starting for every arbitrary initial distribution.
+ Therefore, to find the stationary state, we aim to compute $|\Psi\rangle$ such that 
 \begin{equation}
@@
 \end{equation}
-The matrix product ansatz tells:
+The MPA states the following
 \begin{equation}
@@
 \end{equation}
-with 
+with the normalization 
 \begin{equation}
@@
 \end{equation}
-where $X_{a}$ for $s=1,\ldots,N$ are operators on an auxiliary space $V_{0}$ while $|V\rangle\in V_{0}$ and $\langle W|\in V_{0}^{*}$ (the dual space), such that $\langle W|V\rangle=1$. \\
-They fulfill
+where $X_{a}$ for $a=1,\ldots,N$ are operators on an auxiliary space $V_{0}$ while $|V\rangle\in V_{0}$ and $\langle W|\in V_{0}^{*}$ ( where $V^{*}$ denotes the algebraic dual space), such that $\langle W|V\rangle=1$.
+$\langle W|$ and $|V\rangle$ are sometimes called boundary vectors.
+These operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
 \begin{equation}\label{bulk}
@@
 \end{equation}
-and
+and their action on the boundary vectors are
 \begin{equation}\label{leftBoundary}
@@
 \newline
-\textbf{Remark}: Only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
+\textbf{Remark}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
 	\begin{equation}
@@
 	\end{equation}
-	gives $0=0$. Similar computations for the right boundary.\\
- \newline
- The operators defined in \eqref{bulk},\eqref{leftBoundary},\eqref{rightBoundary} are not known explicitly.
-Via commutation relation is possible to compute some of the correlations.
-However, it would be interesting to write formulas for arbitrary correlations and the steady state, apart any choice of the form of the operators.
-\\
- We introduce some similarity transformations for the Hamiltonian \eqref{hamiltonian}.
-These allow to define two simpler Hamiltonians whose steady state can be  compute exactly.
-Reversing back the transformation we will obtain the original steady state.
-\\
-We first use the \textit{dual similarity transformation}, defined by the symmetry operator \eqref{e_def}.
-\begin{equation}
-    V=\text{exp}\left(\sum_{a=2}^{N}e_{a1}\right)=e^{E}
-\end{equation}
-Up to the diagonal matrix $R_{x}$, this is exactly the edge duality matrix. Then, we introduce the Hamiltonian
-\begin{equation}
-	H_{dual}=B_{1}^{dual}+\mathcal{H}+B_{L}^{dual}
-\end{equation}
-where 
-It is linked to the original one by: 
-\begin{equation}\label{uno}
-	{H}^{T}V=V{H}_{dual}\quad \Rightarrow \quad {H}=\left(V^{-1}\right)^{T}{H}_{dual}^{T}V^{T}
-\end{equation}
-
-We introduce the \textit{S similarity transformation} 
-\begin{equation}\label{Esse}
-    S=\exp \left(-\sum_{a=2}^N \beta_ae_{a1}\right)\exp \left(\sum_{b=2}^N e_{1b}\right)
-\end{equation}
-and then the Hamiltonian 
-\begin{equation}\label{diagHamiltonian}
-    \widetilde{H}=\widetilde{B}_{1}+\mathcal{H}+\widetilde{B}_{L}
-\end{equation}
-that is linked to the original one by 
-\begin{equation}\label{due}
-    HS=S\widetilde{H}\quad \Rightarrow \quad {H}=S\widetilde{H}S^{-1}
-\end{equation}
-This \eqref{diagHamiltonian} has simpler boundary: the left one is lower triangular and the right one is diagonal. The bulk part remains the same. 
-Indeed, by applying the similarity transformation \eqref{Esse} to the Hamiltonian we have:
-\begin{equation}
-	\widetilde{B}_{1}=SB_{1}S^{-1}=\begin{pmatrix}
+	gives $0=0$. Similar computations can be done for the right boundary.
+\subsection{The exact steady state for the multi-species stirring process on a chain}\label{subsection-exact}
+We aim to find an explicit for for the steady state $|\Psi\rangle$.
+The MPA states the form of the steady state in function of an abstract algebra of operators.
+If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}.
+Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bulk} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}.
+For the one and two point correlation and for the currents this has been done in \cite{vanicat}.
+Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bulk}, \eqref{leftBoundary} and \eqref{rightBoundary}.
+In subsection \eqref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
+This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relation simpler, and allows to find the steady state of a transformed Hamiltonian, that will be denoted by $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary.
+Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}.
+A fundamental 'ingredient' of these computation is duality, that has been proved in section \ref{sectionDuality}.
+\subsubsection{The similarity transformation}
+We aim to construct a similarity transformation that maps the Hamiltonian \eqref{hamiltonian} into an other $\mathbb{H}$ that has left boundary lower-triangular and right boundary diagonal.
+Consider the transformation
+\begin{equation}\label{transformationV}
+ V:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{a1}
+\end{equation}
+Observe that it is the the duality matrix at site $x\in \{1,\ldots,L\}$ up to the multiplication by $R_{x}$. By taking the tensor product over the chain we define
+\begin{equation}
+    \mathcal{V}=V^{\otimes L}
+\end{equation}
+ This matrix $\mathcal{V}$ is invertible and we introduce 
+\begin{equation}\label{hatHamiltonian}
+    \widehat{H}:=\widehat{B}_{1}+\mathcal{H}+\widehat{B}_{L}
+\end{equation}
+such that 
+\begin{equation}\label{similarV}
+   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}V^{T}
+\end{equation}
+Using \eqref{transformationV} we introduce the \textit{similarity transformation} 
+\begin{equation}\label{similarity}
+    S:=\sum_{a=2}^{N}\beta_{a}\sum_{b=2}^{N}e_{ab}+V=-\sum_{a=2}^{N}\beta_{a}\sum_{b=2}^{N}e_{ab}+\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}
+\end{equation}
+Taking the tensor product over the sites of the chain we further define
+\begin{equation}
+    \mathcal{S}:=S^{\otimes L}
+\end{equation}
+Therefore, we call
+\begin{equation}\label{bbHamiltonian}
+    \mathbb{H}=\mathbb{B}_{1}+H_{bulk}+\mathbb{B}_{L}
+\end{equation}
+such that 
+\begin{equation}\label{similarS}
+    H=\mathcal{S}^{-1} \mathbb{H}\mathcal{S}
+\end{equation}
+The Hamiltonian $\mathbb{H}$ has lower-triangular left boundary and diagonal right boundary, i.e.
+\begin{equation}
+    \mathbb{B}_{1}=SB_{1}S^{-1}=e_{11}-\mathbbm{1}+\sum_{a=2}^{N}\left(\alpha_{a}-\beta_{a}\right)e_{a1}=\begin{pmatrix}
 		0&0&\ldots&0&0\\
@@
 		\vdots&\vdots&\ddots&\vdots&\vdots\\
-		\alpha_{N-1}-\beta_{N-1}&0&\vdots&-1&0\\
-		\alpha_{N}-\beta_{N}&0&\vdots&0&-1
+		\alpha_{N-1}-\beta_{N-1}&0&\ldots&-1&0\\
+		\alpha_{N}-\beta_{N}&0&\ldots&0&-1
 	\end{pmatrix}
 \end{equation}
-\begin{equation}
-	\widetilde{B}_{L}=SB_{L}S^{-1}=\begin{pmatrix}
-		-1&0&\ldots&0&0\\
+and 
+\begin{equation}
+    \mathbb{B}_{L}=SB_{L}S^{-1}=e_{11}-\mathbbm{1}=\begin{pmatrix}
+		0&0&\ldots&0&0\\
 		0&-1&\ldots&0&0\\
 		\vdots&\vdots&\ddots&\vdots&\vdots\\
-		0&0&\vdots&-1&0\\
-		0&0&\vdots&0&0
-	\end{pmatrix}=e_{NN}-\id
-\end{equation}
-\begin{equation}
-	(S\otimes S)H_{x,x+1}(S\otimes S)^{-1}=H_{x,x+1}
-\end{equation}
-that also implies that \eqref{Esse} is a symmetry of the bulk part of the Hamiltonian, since  
-\begin{equation}
-	(S\otimes S)H_{x,x+1}=H_{x,x+1}(S\otimes S)
-\end{equation}
-The relation with the original Hamiltonian is found by imposing \eqref{uno}=\eqref{due}.
-\begin{equation}
-	\begin{split}
-		\left(V^{-1}\right)^{T}H_{dual}^{T}V^{T}&=S\widetilde{H}S^{-1}\\
-		VH_{dual}V^{-1}&=S^{T}\widetilde{H}^{T}\left(S^{-1}\right)^{T}\\
-		H_{dual}&=V^{-1}S^{T}\widetilde{H}^{T}\left(S^{-1}\right)^{T}V\\
-		H_{dual}&=T^{-1}\widetilde{H}^{T}T
-	\end{split}
+		0&0&\ldots&-1&0\\
+		0&0&\ldots&0&-1
+  \end{pmatrix}
+\end{equation}
+The bulk part of $\mathbb{H}$ is left unchanged by this transformation, i.e.
+\begin{equation}
+    \mathcal{H}_{x,x+1}=\left(S\otimes S\right)\mathcal{H}_{x,x+1}\left(S\otimes S\right)^{-1}
+\end{equation}
+In the following of our analysis it will be useful to have a relation between \eqref{hatHamiltonian} and \eqref{bbHamiltonian}. This relation reads as
+\begin{equation}
+    \widehat{H}=\mathcal{T}^{-1}\mathbb{H}\;\mathcal{T}
 \end{equation}
@@
 \begin{equation}
-	T:=\left(S^{-1}\right)^{T}V
-\end{equation}
-Associated to these new Hamiltonians we can define their steady states: 
-\begin{equation}
-	H|\Psi\rangle=0\qquad \widetilde{H}|\widetilde{\Psi}\rangle=0\qquad H_{dual}^{T}|\Psi_{ABS}\rangle=0
-\end{equation}
-that are linked each others as follows
-\begin{equation}\label{SteadyStates}
-	|\Psi\rangle=\left(S^{-1}\right)^{\otimes L}|\widetilde{\Psi}\rangle\qquad |\Psi\rangle =\left((V^{T})^{-1}\right)^{\otimes L}|\Psi_{ABS}\rangle \qquad |\Psi_{ABS}\rangle=\left(T^{T}\right)^{\otimes L}|\widetilde{\Psi}\rangle
-\end{equation}
-We can exploit \eqref{SteadyStates}, to compute the steady state of the original Hamiltonian \eqref{hamiltonian}.
-\subsection{Absorption probabilities}
-\subsubsection*{The steady state of $\widetilde{H}$}
-We will show that the steady state $|\widetilde{\Psi}\rangle$ of $\widetilde{H}$ is the following 
+    T=\left(S^{-1}\right)^{T}V=\exp{\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)}
+\end{equation}
+and 
+\begin{equation}
+    \mathcal{T}:=T^{\otimes L}
+\end{equation}
+Indeed, by imposing equal \eqref{similarV} and \eqref{similarS} we obtain 
+\begin{align*}
+    		\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}\mathcal{V}^{T}&=\mathcal{S}\mathbb{H}\mathcal{S}^{-1}\\
+		\mathcal{V}\widehat{H}\mathcal{V}^{-1}&=\mathcal{S}^{T}\mathbb{H}^{T}\left(\mathcal{S}^{-1}\right)^{T}\\
+		\widehat{H}&=\mathcal{V}^{-1}\mathcal{S}^{T}\mathbb{H}^{T}\left(\mathcal{S}^{-1}\right)^{T}\mathcal{V}\\
+		\widehat{H}&=\mathcal{T}^{-1}\mathbb{H}^{T}\mathcal{T}
+\end{align*}
+Associated with these new Hamiltonians $\widehat{H}$ and $\mathbb{H}$ we define the following steady states
+\begin{equation}
+	\mathbb{H}|\widetilde{\Psi}\rangle=0\qquad \widehat{H}^{T}|\widehat{\Psi}\rangle=0
+\end{equation}
+The steady states $|\Psi\rangle$, $|\widehat{\Psi}\rangle$ and $|\widetilde{\Psi}\rangle$ are linked by 
+\begin{align}
+	|\Psi\rangle=&\left(\mathcal{S}^{-1}\right)|\widetilde{\Psi}\rangle\label{SteadystateTilde}
+ \\|\Psi\rangle =&\left((\mathcal{{V}}^{T})^{-1}\right)|\widehat{\Psi}\rangle \label{SteadystateHat}
+ \\|\widehat{\Psi}\rangle=&\left(\mathcal{T}^{T}\right)|\widetilde{\Psi}\rangle\label{SteadyStateHatTilde}
+\end{align}
+In the following subsections we will first compute the steady state $|\widetilde{\Psi}\rangle$.
+Then, using the transformation $\mathcal{T}$ we will retrieve $|\widehat{\Psi}\rangle$.
+Finally, using the transformation $\mathcal{V}$ we will find $|\Psi\rangle$.
+\subsubsection{The steady state of $\mathbb{H}$}
+We state the following result. The steady state of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 
 \begin{equation}\label{ResulsBasis}
-	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}|\mathbf{s}\rangle
+	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}|\mathbf{\bm{s}}\rangle
 \end{equation}
@@
 \end{equation}
-and the basis vector $|s\rangle =\bigotimes_{i=1}^{L}|s_{i}\rangle$ with $s_{i}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
-\newline
-\\
-By applying the $S$ to the vector $\left(X_{1},\ldots,X_{N}\right)$ 	we obtain new operators of the matrix product ansatz that can be written as: 
+and the basis vector $|\bm{s}\rangle =\bigotimes_{i=1}^{L}|s_{i}\rangle$ with $s_{i}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
+\paragraph{Proof of formula \eqref{ResulsBasis}} 
+To prove \eqref{ResulsBasis} we will consider the vector composed by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we will act on it with the similarity transformation \eqref{similarity} obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators than \eqref{bulk} and simpler actions than \eqref{leftBoundary} and \eqref{rightBoundary}.
+This will allow to write explicitly the steady state \eqref{ResulsBasis}.
+For the sake of notation, we denote by 
+\begin{equation}
+    \begin{pmatrix}
+		X_{1}\\ 
+		X_{a}
+	\end{pmatrix}=\begin{pmatrix}
+	    X_{1}\\
+     \vdots\\
+     X_{N}
+	\end{pmatrix}\quad \forall a\in \{2,\ldots,N\}
+\end{equation}
+We obtain the new operators of the MPA that by transforming the original one by \eqref{similarity} 
 \begin{equation}\label{Xtildes2b}
@@
 \end{equation}
-we can also reverse the transformation by $S^{-1}$ and get: 
+We can also reverse the transformation by $S^{-1}$ and get back: 
 \begin{equation}\label{Xes}
@@
 \end{equation}
-These new $\widetilde{X}_{a}$ $\forall a\in \{1,\ldots,N\}$ satisfy new commutation relations.\\ 
-Summing over \eqref{bulk} we get
+Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have
 \begin{equation} 
@@
 \end{equation}
-such that it immediately follows that
+therefore, we obtain the commutation relations for $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$
 \begin{equation}\label{commutationsBulk}
@@
 \end{equation}
-
-We further get
+Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$ on the boundary vectors are given by 
 \begin{equation}\label{commLEFT}
@@
 The vector $|\widetilde{\Psi}\rangle$ is written as:
-\begin{equation}
+\begin{equation}\label{toDetermineTilde}
 	|\widetilde{\Psi}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
-	|V \rangle |\mathbf{n}\rangle
+	|V \rangle \,|\mathbf{n}\rangle
 \end{equation}
@@
 $$
-such that for each site $x\in \{1,\ldots,L\}$ they must fulfill the hard-core constraint $$\sum_{a=1}^{N}n_{a}^{x}=1$$
-The vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
-We need to compute the coefficient $\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{i}}
+such that for each site $x\in \{1,\ldots,L\}$ $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
+We also observe that the vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
+To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{i}}
 |V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBulk},\eqref{commLEFT} and \eqref{commRIGHT}.\\
-We can rewrite \eqref{commutationsBulk} as:
+We  rewrite \eqref{commutationsBulk} as:
 \begin{equation}\label{UsefulRelation}
@@
 \end{equation}
-We first observe that $\forall a\in \{2,\ldots,N\}$ and $\forall l,n\in \mathbb{N}$ we have, thanks to \eqref{UsefulRelation}: 
+Fixing $ a\in \{2,\ldots,N\}$ and $\forall \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
 \begin{align*}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{l}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{l-1}
-	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{l}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{l-1}
+	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
+	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{\ell-1}
 	\\&=
-	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{l-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{l-1}
+	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}
 	\\&=\ldots\\&=
-	\widetilde{X}_{1}^{l}\left(\widetilde{X}_{a}+l\lambda_{a}\right)^{n}
+	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
 \end{align*}
-Thus
+therefore 
 \begin{align*}
@@
 \end{align*}
-by consequence
+By taking the product over the sites $i$ from $1$ to L we obtain 
 \begin{equation}
@@
 \end{equation}
-Thus we obtain
+Therefore, multiplying by the boundary vectors we have 
 \begin{equation*}
@@
 \end{equation*}
-by using \eqref{commRIGHT}
+Using \eqref{commRIGHT}
 \begin{align*}
@@
 \end{align*}
-we only need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$. For the sake of notation call $\sum_{i=1}^{L}n_{1}^{i}=n_{1}$. Take an arbitrary $a\in \{2,\ldots,N\}$
+To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$.
+Calling $\sum_{i=1}^{L}n_{1}^{i}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
 \begin{align*}
-	\langle W|\widetilde{X}_{1}^{m_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
 	\\&=
@@
 \end{align*}
-we have a recursion
+This leads to the recursion relation
 \begin{equation}
@@
 \end{equation}
+that implies 
 \begin{align*}
@@
 \end{equation}
-we add the normalization
+The normalization constant is computed similarly as 
 \begin{align*}
@@
 \end{align*}
-All in all
+Therefore, we write the coefficients of the linear combination \eqref{toDetermineTilde} as 
 \begin{equation}\label{resulEsteady}
@@
 \end{equation}
-
- We now perform a change of basis. By calling $s_{i}$ the (only) species present at site $i$, we can rewrite
+Calling $s_{i}$ the species present at site $i$, we rewrite the basis vector 
 \begin{equation}
@@
 \end{equation}
-where $s_i=\sum_{k=1}^Nk\delta_{n_k^i,1}$. 
-Then it is to see that 
+where $s_i=\sum_{k=1}^N\delta_{n_k^i,1}$. Finally we take the tensor product of the vectors $|s_{i}\rangle$ and we obtain
 \begin{equation}
@@
 \end{equation}
-with $s_{i}\in\{1,\ldots,N\}$.     
-\\Moreover, for a fixed site $i$, the coefficient
-\begin{equation}
-	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
-\end{equation}
-has only one factor, associated to the non empty species $a$ that is the site $i$, i.e.
-to the only $m_{a}^{i}\neq 0$.
-Furthermore, if the site $i$ has the empty, i.e.
-$1$, the whole coefficient equals 1.
-The $m_{1}^{i}$ are one if and only if the occupation of site $i$ is $1$, then it easy to see that $m_{1}^{i}=\delta_{s_{i},1}$.
-Then, we can write
+with $s_{i}\in\{1,\ldots,N\}$. For a fixed site $i$, because of the hard-core interaction that allows at most one particle on type different from $1$ ,at site $i$ we have 
 \begin{equation}
@@
 \end{equation}
-As already pointed out, $m_{1}^{i}=\delta_{s_{i},1}$, then 
+Moreover, we have 
 \begin{equation}
@@
 \end{equation}
-Finally, making the sum over all $\mathbf{s}\in \Omega$ is equivalent to sum over all the possible values of each $s_{i}\in\{1,\ldots,N\}$ $\forall i\in\{1,\ldots,L\}$.
-Thus, by putting all these things together, we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}
-\subsubsection*{The steady state of $H_{dual}^{T}$}
-The steady state $|\Psi_{ABS}\rangle$ such that $H_{dual}^{T}|\Psi_{abs}\rangle=0$ is given by the following formula:
+Finally summing over all $\mathbf{s}\in \Omega$ (that is equivalent, $\forall i\in\{1,\ldots,L\}$, to summing over all the possible values of each $s_{i}\in\{1,\ldots,N\}$) we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}.
+\begin{flushright}
+$\square$
+\end{flushright}
+\subsubsection{The steady state of $\widehat{H}$}
+Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}.
+The result is the following
+\begin{equation}\label{ABS-vect}
+    |\widehat{\Psi}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\widehat{\Psi}(\bm{s})|\bm{s}\rangle 
+\end{equation}
+where 
 \begin{equation}\label{ABS}
 		\begin{split}
-			|\Psi_{ABS}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}\bigotimes_{r=1}^{L} |s_{r}\rangle
-		\end{split}
-	\end{equation} 
- By \eqref{SteadyStates}, we first need to compute $(T^{T})^{\otimes L}$. 
-The matrix $T$ has the following form
-\begin{equation}\label{ExplicitMatrixT}
-	T=\exp\left(-\sum_{b=2}^{N}e_{b1}\right)\exp\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)\exp\left(\sum_{b=2}^{N}e_{b1}\right)=\exp\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)
-\end{equation}
-Thus
-\begin{equation}
-	T=I_{N\times N}+\begin{pmatrix}
-		0&\beta_{2}&\ldots&\beta_{N}\\
-		0&0&\ldots&0\\
-		\vdots&\vdots&\ldots&\vdots\\
-		0&0&\ldots&0
-	\end{pmatrix}
-\end{equation}
-We introduce the following notation: $e_{a}^{b}=e_{ab}$, $e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}$ and $$\delta_{a,b}=\begin{cases}
-	1\quad \text{if}\quad a=b\\
-	0\quad \text{if}\quad a\neq b
-\end{cases}$$ 
-Then we have that 
-\begin{equation}
-	T^{T}=I_{N\times N}+\begin{pmatrix}
-		0&0&\ldots&0\\
-		\beta_{2}&0&\ldots&0\\
-		\vdots&\vdots&\ldots&\vdots\\
-		\beta_{N}&0&\ldots&0
-	\end{pmatrix}=\sum_{s_{1}=1}^{N}e_{i}^{i}+(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
-\end{equation}
-For the sake of notation let us introduce also the following matrix
-\begin{equation}
-	Q:=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
-\end{equation}
-We start by computing 
-\begin{equation}
-	T^{T}\otimes T^{T}=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)=I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
-\end{equation}
-Let's compute each terms separately:
-\begin{equation}
-	I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}
-\end{equation}
-\begin{equation}
-	I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}
-\end{equation}
-\begin{equation}
-	Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}
-\end{equation}
-\begin{equation}
-	Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}\delta_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
-\end{equation}
-Take a line of the matrix $T^{T}\otimes T^{T}$ identified by index $(s_{1},s_{2})$, then it can be written as
-\begin{equation}
-	\left(T^{T}\otimes T^{T}\right)_{(s_{1},s_{2})}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-e_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
-\end{equation}
-Then it is easy to generalize for an arbitrary order of tensor product.
-Take the configuration with $L$ sites and identify the row $\mathbf{s}=(s_{1},\ldots,s_{L})$ with $s_{i}\in \{1,\ldots,N\}$, $\forall i\in\{1,\ldots,L\}$:
-\begin{equation}
-	\begin{split}
-		\left(T^{T}\right)^{\otimes L}_{s_{1},\ldots,s_{L}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{k_{1}=s_{1},\ldots,s_{L}\,:\,k_{1}\neq 1}e_{s_{1},\ldots,k_{1},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{k_{1}}\\&+\sum_{k_{1},k_{2}=s_{1},\ldots,s_{L}\,:\,k_{1},k_{2}\neq 1}e_{s_{1},\ldots,k_{1},\ldots,k_{2}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{k_{1}}\beta_{k_{2}}+\ldots+\left(\sum_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
-	\end{split}
-\end{equation}
-Then, by multiplying this matrix for the vector $|\widetilde{\Psi}\rangle$ we obtain
-\begin{equation}\label{ABS_intermediate}
-	\begin{split}
-		\Psi_{ABS}(\mathbf{s})&=\left(T^{T}\right)^{\otimes m}_{s_{1},\ldots,s_{L}}|\widetilde{\Psi}\rangle\\&= \widetilde{\Psi}(\mathbf{s})+\sum_{k_{1}=s_{1},\ldots,s_{L}\,:\, k_{1}\neq 1}\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{k_{1}},\ldots,s_{L})\beta_{k_{1}}\\&+
-		\sum_{k_{1},k_{2}=s_{1},\ldots,s_{L}\,:\, k_{1},k_{2}\neq 1}\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{k_{1}},\ldots,\overbrace{1}^{k_{2}},\ldots,s_{L})\beta_{k_{1}}\beta_{k_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\sum_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}
-	\end{split}
-\end{equation}
-from \eqref{resulEsteady}, we have the following equation
-\begin{equation}
-	\widetilde{\Psi}(\mathbf{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)\right)^{1-\delta_{s_{i},1}}
-\end{equation}
-Then, for fixed $\mathbf{s}$ we have a contribution of a factor $\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)$ if the site is non empty, and a contribution of a factor $1$ if the site is empty.
-Let's introduce the coefficients 
-\begin{equation}
+			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+		\end{split}
+	\end{equation} 
+and where
+ \begin{equation}\label{CiEquation}
 	c_{i}=\begin{cases}
@@
 		0\quad \text{if}\quad s_{i}=1
-	\end{cases}
-\end{equation}
-Thus we have $\widetilde{\Psi}(\mathbf{s})$ when all the $c_{i}$ are one and $\widetilde{\Psi}(1,\ldots,1)$ when all the $c_{i}$ are zero.
-All the configurations in between refers to different values of these $c_{i}$.
-\\The equation \eqref{ABS_intermediate}, can now be written in terms of $c_{i}$ as follows
-\begin{equation}
-	\begin{split}
-		\Psi_{ABS}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right]^{c_{i}}\left(\beta_{s_{i}}\right)^{(1-c_{i})(1-\delta_{s_{i},1})}
-	\end{split}
-\end{equation}
-The summations goes from $0$ to $\delta_{s_{i},1}$ because in \eqref{ABS_intermediate}, the configurations that has an empty occupation are cosnidered to contribute just with a $1$.
-In the above formual, we make the span over all possible $c_{i}\in\{0,1\}$ when the site is non-empty, and we keep $c_{i}=0$ when the site is empty.
-Moreover, when $c_{i}=1$ we add a factor $\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)$, while we add a factor $\beta_{s_{i}}$ when $c_{i}=0$ and the site is non-empty.
-Finally, by considering all possible occupancies of the sites we obtain \eqref{ABS}. 
-\newline
-\textbf{Remark}: {\color{red} Can we interpret the steady state $|\Psi_{ABS}\rangle $ as the absorption probabilities ?}
-\subsection{The steady state and the exact correlations}
-By using the previous result we can write explicit formulas for the steady state of the original Hamiltonian \eqref{hamiltonian} and for arbitrary order correlations. 
-\newline
-The steady state of the original Hamiltonian $|\Psi\rangle$, defined by $H|\Psi\rangle=0$, is characterized by the following formula
-	\begin{equation}\label{ExpSteadyState}
-		\begin{split}
-			|\Psi\rangle &= \sum_{s_{1},\ldots,s_{L}=1}^{N}\left(\sum{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}\right.
-\\ &+ \left.\sum_{l=0}^{\Xi(\mathbf{s})}(-1)^{l}\delta_{j\geq 1}\sum_{k_{1},\ldots,k_{l}=s_{1},\ldots,s_{L}}\prod_{q=1}^{j}\delta_{k_{q},1}\sum_{\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}}=2}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\prod_{t=1}^{l}\delta_{c_{k_{t}},1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}\right.\\&\cdot\left.\prod_{i=1\;:\;i\neq k_{1},\ldots,k_{l}}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}\prod_{r=1}^{l}\lambda_{\tilde{s}_{k_{r}}}\left(1+L-k_{r}-\sum_{j=i}^{L}c_{j}\right)^{c_{k_{r}}}\right)\bigotimes_{i=1}^{L}|s_{i}\rangle
-		\end{split}
+	\end{cases}\qquad \forall i\in \{1,\ldots,N\}
+\end{equation}
+\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{T}^{T}$ acts on the vector $|\widetilde{\Psi}\rangle$.
+The matrix $T^{T}$ is given by
+\begin{equation}
+    T^{T}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}
+\end{equation}
+We introduce the following notation
+\begin{equation}\label{notation1}
+    e_{ab}=e_{a}^{b}=\left(\delta_{a,c}\delta_{b,d}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,\}
+\end{equation}
+and 
+\begin{equation}\label{notation2}
+    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
+    \end{equation}
+    that can be generalized for $e_{s_{1},\ldots,s_{L}}^{q_{1},\ldots,q_{L}}$ with $s_{1},\ldots,s_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that 
+    \begin{equation}
+        T^{T}=\sum_{s_{1}=1}^{N}e_{i}^{i}+Q
     \end{equation}
@@
     \begin{equation}
-		\Xi(\mathbf{s})=\sum_{i=1}^{L}\delta_{s_{i},1}
-	\end{equation}
- \newline
+	Q:=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
+\end{equation}
+We compute
+\begin{equation}
+    \begin{split}
+        	T^{T}\otimes T^{T}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
+         \\&=
+         I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
+    \end{split}
+\end{equation}
+where the addends are 
+\begin{equation*}
+\begin{split}
+	&I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}\\
+	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}\\
+	&Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}\\
+	&Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}e_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
+ \end{split}
+\end{equation*}
+The matrix $T^{T}\otimes T^{T}$ has elements $\left\{\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2},q_{1},q_{2}\in \{1,\ldots,N\}}$, where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column.
+We fix a raw of this matrix with arbitrary index $s_{1},s_{2}$
+\begin{equation}
+	\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-e_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
+\end{equation}
+Iterating this tensor product for the chain of length $L$, we write the raw with indices $\bm{s}=s_{1},\ldots,s_{L}$
+ of the matrix $\mathcal{T}^{T}$ as 
+\begin{equation}
+	\begin{split}
+		\mathcal{T}^{T}_{\bm{s}}&=\left(T^{T}\right)^{\otimes L}_{s_{1},\ldots,s_{L}}=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{N}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
+  \\&+
+  \ldots+\left(\prod_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
+	\end{split}
+\end{equation}
+The product $\mathcal{T}^{T}|\widetilde{\Psi}\rangle$ gives a vector whose component are denoted by $\widehat{\Psi}(\bm{s})$ that are given by 
+\begin{equation}\label{ABS_intermediate}
+	\begin{split}
+		\widehat{\Psi}(\mathbf{s})&=\mathcal{T}^{T}_{\bm{s}}|\widetilde{\Psi}\rangle\\&= \widetilde{\Psi}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{k_{1}}\beta_{k_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\prod_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}
+	\end{split}
+\end{equation}
+For a fixed configuration $\bm{s}=(s_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
+\begin{equation}
+  \left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right) =\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)
+\end{equation}
+we obtain 
+    \begin{equation}
+	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)\right)^{1-\delta_{s_{i},1}}
+\end{equation}
+Because of the exponent $(1-\delta_{s_{i},1})$, the element $\widetilde{\Psi}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
+Then, equation  \eqref{ABS_intermediate} reads
+\begin{equation}\label{elementsABS}
+	\begin{split}
+		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right]^{c_{i}}\left(\beta_{s_{i}}\right)^{(1-c_{i})(1-\delta_{s_{i},1})}
+	\end{split}
+\end{equation} 
+Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $b_{s_{i}}$. 
+Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS}.
+\begin{flushright}
+    $\square$
+\end{flushright}
+\subsubsection{The steady state of $H$}
+The steady state $|\Psi\rangle$ of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 
+\begin{equation}\label{steadyStateH}
+    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
+\end{equation}
+where for every $(s_{1},\ldots,s_{L})=\bm{s}$
+\begin{equation}\label{steadyStateH-coeff}
+    \begin{split}
+        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+        \\&+
+        \sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right) 
+        \sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}
+  \\ &
+  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(1-L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
+  \prod_{r=1}^{\ell}\lambda_{q_{r}}\left(1+L-q_{r}-\sum_{j=q_{r}}^{L}c_{j}\right)
+    \end{split}
+\end{equation}
+\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
+if $s_{i}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations,
+\begin{equation}\label{LinkABS-corr}
+\Psi(\bm{s})=\widehat{\Psi}(\bm{s})
+\end{equation}
+
+\paragraph{Proof of formula \eqref{steadyStateH}} To find $|\Psi\rangle$ we will use \eqref{SteadystateHat}. For the sake of notation we call
+\begin{equation}
+    F=\left(V^{-1}\right)^{T}
+\end{equation}
+and thus 
+\begin{equation}
+    \mathcal{F}=F^{\otimes L}
+\end{equation}
+By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
+\begin{equation}
+    F=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+\delta_{s_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+\end{equation}
+Taking the tensor product over two sites we obtain 
+\begin{equation}
+\begin{split}
+    F\otimes F&=\sum_{s_{1},s_{2}=1}^{N}\left(e_{s_{1},s_{2}}^{s_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{s_{1},1}^{s_{1},d_{2}}
+     \right.\\ &+\left. 
+    (-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{s_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
+    \end{split}
+\end{equation}
+therefore, fixing a raw with indices $s_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
+\begin{equation}
+\begin{split}
+    \left(F\otimes F\right)_{s_{1},s_{2}}&=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{s_{1},1}^{s_{1},d_{2}}
+    \\&+
+    (-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{s_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
+    \\&=
+    \sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{s_{i},1}^{s_{i}d_{q_{r}}}
+    +
+    (-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{s_{i},1}^{s_{i}d_{q_{r}}}
+    \end{split}
+\end{equation}
+where $e_{s_{i},d_{q_{r}}}$ denotes the matrix $e_{s_{1},s_{2}}^{s_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
 \\
- \textbf{Remark}: Let us notice that 	$\forall \mathbf{s}=(s_{1},\ldots,s_{l})$ such that $s_{i}\neq 1$ $\forall i \in\{1,\ldots,L\}$ (i.e.
-a configuration without any state 1, that can be interpreted as a non-empty configuration) we have that
-	\begin{equation}\label{LinkABS-corr}
-		\Psi(\mathbf{s})=\Psi_{ABS}(\mathbf{s})
-	\end{equation}
-This can be seen, in such a situation the second addend of \eqref{ExpSteadyState} vanishes. 
- \newline
- By \eqref{SteadyStates}, we only have to compute $\left((V^{-1})^{T}\right)^{\otimes L}$.\\
-For the sake of notation lets call 
-\begin{equation}
-	W:=(V^{-1})^{T}
-\end{equation}
-We have that 
-\begin{equation}
-	W=I_{N\times N}+\begin{pmatrix}
-		0&-1&-1&\ldots&-1\\
-		0&0&0&\ldots&0\\
-		\vdots&\vdots&\vdots&\ddots&\vdots\\
-		0&0&0&\ldots&0
-	\end{pmatrix}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+\delta_{s_{1},1}\sum_{\tilde{s}_{1}=2}^{N}e_{1}^{\tilde{s}_{1}}(-1)
-\end{equation}
-we first take the tensor product between two of them
-\begin{equation}
-	\begin{split}
-		W\otimes W &= \sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{s_{1}=1,\tilde{s}_{2}=2}^{N}e_{s_{1},1}^{s_{1},\tilde{s}_{2}}\\&+(-1)\delta_{s_{1},1}\sum_{\tilde{s}_{1}=2,s_{2}=1}^{N}e_{1,s_{2}}^{\tilde{s}_{1},s_{2}} +(-1)(-1)\delta_{s_{1},1}\delta_{s_{2},1}\sum_{\tilde{s}_{1},\tilde{s}_{2}=2}^{N}e_{1,1}^{\tilde{s}_{1},\tilde{s}_{2}}
-	\end{split}
-\end{equation}
-In the above formula, there is a diagonal term that is always present, while the other addend that is non-vanishing when there is at least one empty. \\
-Let's iterating the tensor product multiplication.
-Then, for a fixed raw, identified by $\mathbf{s}=\{s_{1},\ldots,s_{L}\}$ with $s_{i})_{i=1,\ldots,L}\in \{1,\ldots,N\}$, of the $L-$times tensor product matrix we have the following expression:
-\begin{equation}
-	\begin{split}
-		(W)^{\otimes L}_{\mathbf{s}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{l=0}^{\Xi(\mathbf{s})}(-1)^{l}\delta_{l\geq 1}\sum_{k_{1},\ldots,k_{l}=s_{1},\ldots,s_{L}}\prod_{q=1}^{l}\delta_{k_{q},1}\sum_{\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{j}}=2}^{N}e_{s_{1},\ldots,\underbrace{1}_{k_{1}},\ldots,\underbrace{1}_{k_{l}},\ldots,s_{L}}^{s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L}}
-	\end{split}
-\end{equation}
-where 
-\begin{equation}
-	\Xi(\mathbf{s})=\sum_{i=1}^{L}\delta_{s_{i},1}
-\end{equation}
-Now, by multiplying $(W)^{\otimes L}_{s_{1},\ldots,s_{L}}$ with $|\Psi_{ABS}\rangle $ we get
-\begin{equation}
-	\begin{split}
-		(W)^{\otimes L}_{\mathbf{s}}|\Psi_{ABS}\rangle&=\Psi_{ABS}(\mathbf{s})\\&+\sum_{l=0}^{\Xi(\mathbf{s})}(-1)^{l}\delta_{l\geq 1}\sum_{k_{1},\ldots,k_{l}=s_{1},\ldots,s_{L}}\prod_{q=1}^{l}\delta_{k_{q},1}\sum_{\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{j}}=2}^{N}\Psi_{ABS}(s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L})
-	\end{split}
-\end{equation}
-Now, we only need to write explicitly the term $\Psi_{ABS}(s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L})$.
-We use formula\eqref{ABS_intermediate} specialized to the case where we put all the $c_{k_{1}},\ldots,c_{k_{l}}=1$ and we replace the species in the coordinates $k_{1},\ldots,k_{l}$ with  $\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}}$:
-\begin{equation}
-	\begin{split}
-		&\Psi_{ABS}(s_{1},\ldots,\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}},\ldots,s_{L})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\prod_{t=1}^{l}\delta_{c_{k_{t}},1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}\\
-		&\cdot\prod_{i=1\;:\;i\neq k_{1},\ldots,k_{l}}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}\prod_{r=1}^{l}\lambda_{\tilde{s}_{k_{r}}}\left(1+L-k_{r}-\sum_{j=i}^{L}c_{j}\right)^{c_{k_{r}}}
-	\end{split}
-\end{equation}
-Finally, we make vary these $\tilde{s}_{k_{1}},\ldots,\tilde{s}_{k_{l}}$  between $2$ and $N$. 
-By putting things together and considering all the rows, we obtain \eqref{ExpSteadyState}.\\
-We can now use the explicit expression of the steady state to find arbitrary point correlations.\\
-\subsubsection*{Exact correlations}
-If we think about $1$ as the empty, the correlations only involve species different from $1$. 
-Thus, for the process defined by the Hamiltonian \eqref{hamiltonian}, the $m$-points correlations, between sites $\mathbf{y}=(y_{1},\ldots,y_{m})$ occupied by the species $\mathbf{s}=(s_{1},\ldots,s_{m})\in \{2,\ldots,N\}^{m}$ are characterized by the following formula:
+We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$. We write the expression of a fixed raw with indices $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$ as 
+\begin{equation}
+    \begin{split}
+        \mathcal{F}_{s_{1},\ldots,s_{L}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}
+        \\&
+        +\sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{i},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{i},\ldots,\,d_{q_{r}}\,,\ldots}
+    \end{split}
+\end{equation}
+where $e_{\ldots,s_{i},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{i},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{\ell}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{\ell}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{\ell}}$.
+\\
+Multiplying the raw with indices $s_{1},\ldots,s_{L}$ of the matrix $\mathcal{F}$ by the vector $|\widehat{\Psi}\rangle$ we obtain 
+\begin{equation}
+    \begin{split}
+        \mathcal{F}_{s_{1},\ldots,s_{L}}|\widehat{\Psi}\rangle&=\widehat{\Psi}(s_{1},\ldots,s_{L})+ 
+        \\&
+        +\sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}\widehat{\Psi}(\ldots,s_{i},\ldots,d_{q_{r}},\ldots)
+    \end{split}
+\end{equation}
+where $\widehat{\Psi}(\ldots,s_{i},\ldots,d_{q_{r}},\ldots)$ denotes the component $\widehat{\Psi}(s_{1},\ldots,s_{L})$ where the occupations  $s_{q_{1}},\ldots,s_{q_{\ell}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{\ell}}$.
+Using \eqref{elementsABS} we have
+\begin{equation}
+    \begin{split}
+  &\widehat{\Psi}(\ldots,a_{i},\ldots,d_{q_{r}},\ldots)=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\left(\prod_{r=1}^{\ell}\delta_{c_{r},1}\right)\frac{\Gamma(2+L-\sum_{k=1}^{L}}{\Gamma(2+L)}
+  \\&
+  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(1-L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
+  \prod_{r=1}^{\ell}\lambda_{q_{r}}\left(1+L-q_{r}-\sum_{j=q_{r}}^{L}c_{j}\right)
+    \end{split}
+\end{equation}
+indeed, in coordinates $q_{r}$ with $r=1,\ldots \ell$ the site is non-empty, thus $c_{q_{r}}=1$.
+Finally, considering all possible occupations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}.
+\begin{flushright}
+    $\square$
+\end{flushright}
+\subsection{Exact correlations}\label{correlation-section}
+We compute in this section a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e.
+a species with label from $2$ to $N$.
+This is motivated by interest of understanding how actual particles of the chain are correlated among each others.
+Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
+In each of these points there is a particle of species $s_{i}\in \{2,\ldots,N\}$.
+Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
 \begin{equation}\label{exactCorrelations}
-		\langle\rho^{y_{1}}_{s_{1}},\ldots,\rho^{y_{m}}_{s_{m}}\rangle=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+		\langle n^{y_{1}}_{s_{1}},\ldots,n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
 			f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{m})
@@
 	\end{equation}
-We aim to compute the correlations between the sites $\mathbf{y}=\left(y_{1},\ldots,y_{m}\right)$ occupied by the species $\mathbf{s}=\left(s_{1},\ldots,s_{m}\right)$, such that $s_{1},\ldots,s_{m}\in \{2,\ldots,N\}$.
-%We exploit the formula \eqref{ExpSteadyState}.
-%By duality we have that
-This means that we need to find 
-\begin{equation}
-	\begin{split}
-		\langle\rho_{s_{1}}^{y_{1}}\ldots\rho_{s_{m}}^{y_{m}}\rangle&%=\mathbb{E}_{\mu_{stat}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\eta_{s_{k}}^{y_{k}}=1\}}\right]=\mathbb{E}_{\mu_{stat}}\left[D(\eta,\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}})\right]\\&
-		=\mathbb{P}_{stat}\left(\eta_{s_{1}}^{y_{1}}=1,\ldots,\eta_{s_{m}}^{y_{m}}=1\right)
-	\end{split}
-\end{equation}
-The probability at the stationary state that we have $m$ points occupied with $\mathbf{s}$ species, can be thought as the stationary probability of a chain of length $m$ with coordinates denoted by $y_{1},\ldots,y_{m}$ and where all the sites are occupied by $s_{1},\ldots,s_{m}$.
-This probability can be written as the stationary state of such a chain with the notation
-\begin{equation}
-	\mathbb{P}_{\text{stat, Chain m}}\left(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m}\right)=\Psi_{m}\left(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m}\right)
-\end{equation}
-As already pointed out in \eqref{LinkABS-corr}, for non empty configurations we have:
+ \paragraph{Proof of formula \eqref{exactCorrelations}}
+ We aim to compute the correlations between the sites $\mathbf{y}=\left(y_{1},\ldots,y_{m}\right)$ occupied by the species $\mathbf{s}=\left(s_{1},\ldots,s_{m}\right)$, such that $s_{1},\ldots,s_{m}\in \{2,\ldots,N\}$ i.e.
+\begin{equation}\label{Prob-m}
+	\begin{split}
+		\langle n_{s_{1}}^{y_{1}},\ldots, n_{s_{m}}^{y_{m}}\rangle_{\text{stat}}&
+		=\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)
+	\end{split}
+\end{equation}
+where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
+This probability \eqref{Prob-m} can be seen as the component \eqref{steadyStateH-coeff} of the stationary state \eqref{steadyStateH} of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{i}\neq 1$, i.e.
+\begin{equation}
+	\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)=\Psi_{\bm{y}}\left(s_{1},\ldots,s_{m}\right)
+\end{equation}
+where the subscript $\bm{y}$ underlines the fact that we are considering a chain with length $m$. 
+As already pointed out in \eqref{LinkABS-corr}, for non-empty configurations we have:
 \begin{equation}\label{Corr-mABS}
-	\Psi_{m}(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m})=\Psi_{ABS}(s_{1},\ldots,s_{m};y_{1},\ldots,y_{m})
+	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})
 \end{equation}
@@
 \begin{equation}
-	\Psi_{ABS}(s_{1},\ldots,s_{m},\mathbf{y})=\sum_{c_{1},\ldots,c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(L+1-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-By using the relation \eqref{Corr-mABS} we have the equations for arbitrary correlations.
-\subsubsection{One and two point correlations}
-We show two examples of computation of correlations via \eqref{exactCorrelations}.\\     
-\textbf{One point correlations}: choose $s_{1}=s$ and $y_{1}=x$
-\begin{align*}
-	\langle\rho_{s}^{x}\rangle=\sum_{c_{1}=0}^{1}(\alpha_{s}-\beta_{s})^{c_{1}}\beta_{s}^{1-c_{1}}g_{s}(c_{1})f(c_{1})
-\end{align*}
-we have that $f(0)=1$ and $f(1)=\frac{\Gamma(L+2-1)}{\Gamma(L+2)}=\frac{1}{L+1}$ and $g_{s}(0)=1$ and $g_{s}(1)=(L+2-x-1)$. Thus we obtain 
-\begin{align*}
-\langle\rho_{s}^{x}\rangle=\frac{(L+1-x)}{L+1}(\alpha_{s}-\beta_{s})+\beta_{s}
-\end{align*}
-that is exactly the one point correlations computed in \cite{vanicat2017exact}.\\
-\textbf{Two points correlations}: %fix $s_{1}=s,\;s_{2}=s^{'}$ and $y_{1}=x,\;y_{2}=y$
-\begin{equation}
-	\begin{split}
-	\langle\rho_{s}^{x},\rho_{s^{'}}^{y}\rangle= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{1},c_{2})
-	\end{split}
-\end{equation}
-we have that 
-\begin{align*}
-	&g_{1}(0,0)=1&g_{2}(0,0)=1\\&
-	g_{1}(1,0)=(L+2-y_{1}-1)&g_{2}(1,0)=1\\&
-	g_{1}(0,1)=1&g_{2}(0,1)=(L+2-y_{2}-1)\\&
-	g_{1}(1,1)=(L+2-y_{1}-2)&g_{2}(1,1)=(L+2-y_{2}-1)
-\end{align*}
-while
-\begin{align*}
-	f(0,0)=1\quad f(0,1)=f(1,0)=\frac{\Gamma(L+2-1)}{\Gamma(L+2)}\quad f(1,1)=\frac{\Gamma(L+2-2)}{\Gamma(L+2)}
-\end{align*}
-By putting things together
-\begin{equation}
-	\begin{split}
-	\langle\rho_{s}^{x},\rho_{s^{'}}^{y}\rangle&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
-	\end{split}
-\end{equation}
-\subsection{Absorption probabilities}
-{\color{blue}An application of duality is to compute the moments of the steday state of the the original process.
-Indeed, as metioned in subsection \ref{}, the dual process voids the chain.
-Therefore, the problem of computing the moments with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles.
-\\
-Calling $\mu_{stat}$ the stationary measure of the the process \eqref{Generator} starting from a configuration $\bm{n}$, we can write the following chain of equalities
-\begin{equation}
+	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(L+1-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+By using the relation \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we have the equations for arbitrary correlations.
+\begin{flushright}
+    $\square$
+\end{flushright}
+\subsubsection{Explicit examples of correlations}
+We give some examples of correlations applying formula \eqref{exactCorrelations}.
+\paragraph{One point correlations}
+The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{2,\ldots,N\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
+\begin{equation}
+	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(c_{1})f(c_{1})
+\end{equation}
+Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{equation}\label{one-pts-corr}
+\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}
+\end{equation}
+\paragraph{Two points correlations}
+The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{2,\ldots,N\}$ at coordinates $y,x\in \{1,\ldots,L\}$ with $x< y$ reads
+\begin{equation}
+	\begin{split}
+	\langle n_{s_{1}}^{x},n_{s_{2}}^{y}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},c_{2})
+	\end{split}
+\end{equation}
+Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{equation}\label{two-pts-corr}
+	\begin{split}
+	\langle n_{s_{1}}^{x},n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+	\end{split}
+\end{equation}
+\paragraph{Three points correlations}
+The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{2,\ldots,N\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
+\begin{equation}
+    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}},n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{3})
+\end{equation}
+Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{equation}\label{three-pts-corr}
+    \begin{split}
+        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}},n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\prod_{k=1}^{3}\beta_{s_{k}}+\sum_{k=1}^{3}\frac{(L-y_{k})}{(L+1)}(\alpha_{s_{k}}-\beta_{s_{k}})\prod_{q=1\,:\,q\neq k}^{3}\beta_{s_{q}}
+        \\&+
+        \frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
+        \\&+
+        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
+        \\&+
+        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
+        \\&+
+        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}\prod_{k=1}^{3}(\alpha_{s_{k}}-\beta_{s_{k}})
+    \end{split}
+\end{equation}
+\textbf{Remark}: the one and two points correlations computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively are exactly the ones found in subsection 4.3 of \cite{vanicat}. 
+\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain}
+In subsection \ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
+When the maximal occupation of each site $\nu>1$, this nice property is lost.
+However, something about correlations can be said using duality.
+In this subsection we still consider the same geometry of \ref{subsection-exact}.
+As pointed out in section \ref{sectionDuality}, the dual process voids the chain.
+Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.\\
+We consider the process $(\bm{n}(t))_{t\geq 0}$ on a chain of length $L$ with the end sites connected with two reservoirs.
+This interaction with the external environment is described by the generators
+\begin{equation}
+    \mathcal{L}_{1}f(\bm{n})=\sum_{k,\ell=0}^{N}\alpha_{k}n_{\ell}^{1}\left(f(\bm{n}-\delta_{\ell}^{x}+\delta_{k}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{k,\ell=0}^{N}\beta_{k}n_{\ell}^{L}\left(f(\bm{n}-\delta_{\ell}^{x}+\delta_{k}^{x})-f(\bm{n})\right)
+\end{equation}
+The bulk generator is 
+\begin{equation}
+    \mathcal{L}_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}\quad \text{where}\quad \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{k,\ell=0}^{N}n_{k}^{x}n_{\ell}^{x+1}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{\ell}^{x}+\delta_{k}^{x+1}-\delta_{\ell}^{x+1})-f(\bm{n})\right)
+\end{equation}
+This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space $\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}$ with the same $\mathcal{L}_{\text{bulk}}$ and with absorbing boundaries, i.e.
+\begin{equation}
+\begin{split}
+        \widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=\sum_{i=1}^{N}\alpha_{i}\sum_{k=2}^{N}\xi_{k}^{1}\left(f(\bm{\xi}-\delta_{k}^{1}+\delta_{k}^{0}+\delta_{k}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{k=2}^{N}\xi_{k}^{L}\left(f(\bm{\xi}-\delta_{k}^{L}+\delta_{k}^{L+1}+\delta_{k}^{L})-f(\bm{\xi})\right)
+        \end{split}
+\end{equation}
+where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
+\begin{equation}\label{dualityFunctionChain}
+    D(\bm{n},\bm{\xi})=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}\alpha_{i}}\right)^{\xi_{k}^{0}}\prod_{x=1}^{L}\prod_{k=2}^{N}\frac{\eta_{k}^{x}!}{(n_{k}^{x}-\xi_{k}^{x})!}\prod_{k=2}^{N}\left(\frac{\beta_{k}}{\sum_{i=1}\beta_{i}}\right)^{\xi_{k}^{L+1}}
+\end{equation}
+Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
+\begin{equation}\label{ExptationSS}
 \begin{split}
@@
 \\=&
-\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}
-\\&
-\mathbb{P}\left(\xi(\infty)=\sum_{k=2}^{N}\left(i_{k}\delta_{0}+(|\xi_{k}|-i_{k})\delta_{L+1}\right)| \xi_{0}=\xi\right)
-\end{split}
-\end{equation}
-we denote by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left and by $|\xi_{k}|-i_{k}$ the number of particles absorbed at right. \\}
-
-Even though integrability does not hold anymore for $j>\frac{1}{2}$, by using the absorbing duality we can still say something about the moment of the non equilibrium steady state distribution.
-We write the expression for the absorption probability for the general $(2j)$ case when the setting is a one dimensional chain with two reservoirs at the ends.
-We assume nearest neighbor interaction, similarly to what we did at the beginning of section \ref{sec4}.
-\\ Let us think about the species $1$ as the empty state.
-Fix a generic initial dual configuration $\xi$ that contains $|\xi_{k}|$ particles of each non-empty species $k\in \{2,\ldots,N\}$. Since the dual chain is absorbing we have that:  
-\begin{equation}
-	\begin{split}
-		\lim_{t\to \infty}\mathbb{E}_{\xi}\left[D(\eta,\xi(t))\right]=& \sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}\\&
-		\mathbb{P}\left(\xi(\infty)=\sum_{k=2}^{N}\left(i_{k}\delta_{0}+(|\xi_{k}|-i_{k})\delta_{L+1}\right)| \xi_{0}=\xi\right)
-	\end{split}
-\end{equation}
-we denote by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left and by $|\xi_{k}|-i_{k}$ the number of particles absorbed at right. \\
-By duality we have that 
-\begin{equation}
-	\mathbb{E}_{\text{stationary},\eta}\left[D(\eta(t),\xi)\right]=\lim_{t\to \infty}\mathbb{E}_{\eta}\left[D(\eta(t),\xi)\right]=\lim_{t\to \infty}\mathbb{E}_{\xi}\left[D(\eta,\xi(t))\right]
-\end{equation}
-\textbf{One point correlations}
-\begin{equation}
-	D(\eta,\delta_{s}^{x})=\eta_{s}^{x}
+\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}a_{i_{1},\ldots,i_{k}}(\bm{\xi})
+\end{split}
+\end{equation}
+where 
+\begin{equation}\label{Pass}
+    a_{i_{k}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{k=2}^{N}\left(i_{k}\delta_{0}+(|\xi_{k}|-i_{k})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+\end{equation}
+where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
+Here, we denote by $|\xi_{k}|=\sum_{x=1}^{L}\xi_{k}^{x}$ and by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{k}|-i_{k}$ the number of particles of the same type absorbed at right.\\
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{s_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{i}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
+\begin{equation}
+    D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{x_{k}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species.
+This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{k}}}(\widehat{\bm{\xi}})$.
+The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the one points correlations.
+\paragraph{One point correlations for the non-integrable case}
+We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
 \end{equation}
 Thus
-\begin{equation}
-	\langle \rho_{s}^{x}\rangle_{\text{stat}}=\lim_{t\to\infty}\mathbb{E}\left[\delta_{s}^{x}(t)\right]=\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{k}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
-\end{equation}
-we want to determine $p^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ and by consequence $p^{x}_{s}(0)=1-p^{x}_{s}(1)$.\\
-We condition on the first jump:
-\begin{equation}
-	p^{x}_{s}(1)=p^{x+1}_{s}(1)\;\mathbb{P}(\text{First jump on the right})+p^{x-1}_{s}(1)\;\mathbb{P}(\text{First jump on the left})
-\end{equation}
-Then:
-\begin{itemize}
-	\item If $x=1$, then the particle has probability $\frac{(\alpha_{1}+\ldots+\alpha_{N})}{1+(\alpha_{1}+\ldots+\alpha_{N})}$ of jumping to the left and $\frac{1}{1+(\alpha_{1}+\ldots+\alpha_{N})}$ of jumping to the right.
-Thus
-	\begin{equation}
-		p^{1}_{s}(1)=p^{0}_{s}(1)\frac{(\alpha_{1}+\ldots+\alpha_{N})}{1+(\alpha_{1}+\ldots+\alpha_{N})}+p^{2}_{s}(1)\frac{1}{1+(\alpha_{1}+\ldots+\alpha_{N})}
-	\end{equation}
-\item if $x\in \{2,\dots,L-1\}$, we have $1/2$ of probability of jumping left and right
-\begin{equation}
-	p_{x}^{s}(1)=\frac{1}{2}\left(p_{x+1}^{s}(1)+p_{x-1}^{s}(1)\right)
-\end{equation}
-	\item If $x=L$, then the particle has probability $\frac{(\beta_{1}+\ldots+\beta_{N})}{1+(\beta_{1}+\ldots+\beta_{N})}$ of jumping to the left and $\frac{1}{1+(\beta_{1}+\ldots+\beta_{N})}$ of jumping to the right.
-Thus
-\begin{equation}
-	p^{L}_{s}(1)=p^{L+1}_{s}(1)\frac{(\beta_{1}+\ldots+\beta_{N})}{1+(\beta_{1}+\ldots+\beta_{N})}+p_{L-1}^{s}(1)\frac{1}{1+(\beta_{1}+\ldots+\beta_{N})}
-\end{equation}
-\item Boundary conditions:
-\begin{equation}
-	p^{0}_{s}(1)=1\qquad p^{L+1}_{s}(1)=0
-\end{equation}
-\end{itemize}
-Denote $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$ for the sake of notation.\\
-All in all we need to solve
-\begin{equation}
+\begin{equation}\label{OnePtsCORR}
+\begin{split}
+	\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{k}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{k}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+ \end{split}
+\end{equation}
+we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
+This $a_{s}^{x}(1)$ fulfils the following equations
+\begin{equation}\label{gamblers-ruin}
 	\begin{cases}
-		\Delta_{x}^{L}p^{x}_{s}(1)=0\\
-		p^{1}_{s}(1)=\frac{A}{1+A}+p^{2}_{s}(1)\frac{1}{1+A}\\
-		p^{L}_{s}(1)=p^{L-1}_{s}(1)\frac{1}{1+B}
+		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
+		a^{1}_{s}(1)=\frac{A}{1+A}+a^{2}_{s}(1)\frac{1}{1+A}\\
+		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+B}
 		\end{cases}
 \end{equation}
-A general solution of the discerete laplace equation is
-\begin{equation}
-	p_{x}^{s}(1)=C_{1}x+C_{2}
-\end{equation}
-we match with boundary conditions:
-\begin{equation}
-	\begin{cases}
-	C_{1}+C_{2}=\frac{A}{1+A}+\frac{2C_{1}+C_{2}}{A+1}\\
-	C_{1}L+C_{2}=\frac{C_{1}(L-1)+C_{2}}{1+B}
-	\end{cases}
-\end{equation}
-The solution
-\begin{equation}
-	C_{1}=\frac{(-A B)}{(A + B - A B + A B L)}\qquad C_{2}=\frac{(A (1 + B L))}{(A + B - A B + A B L)}
-\end{equation}
-\begin{equation}
-	p_{x}^{s}(1)=\frac{A (B (L-x)+1)}{A (B (L-1)+1)+B}
-\end{equation}
-then 
-\begin{equation}
-	p^{x}_{s}(0)=1-p^{x}_{s}(1)=\frac{B (A (x-1)+1)}{A (B (L-1)+1)+B}
-\end{equation}
-then the average density is 
-\begin{equation}
-\langle\rho_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
-\end{equation}
-\newline \\
+where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where, for the sake of notation, we call $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$.
+The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
+\begin{equation}
+\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
+\end{equation}
 \textbf{Remark}: In case $A=B=1$ we have 
 	\begin{equation}
-\langle\rho_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-	\end{equation}
-and it exactly matches with \cite{vanicat2017exact}. \\
-In case $A=B=2j$ we have 
-\begin{equation}
-	\langle\rho_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(2jL-2jx+1)+\beta_{s}(2jx+1-2j)}{2jL-4j(j-1)}
-\end{equation}
-All the other correlations could be, in principle, computed with the same strategy.
-However, the computations become very hard as the correlation order rises, because it is not easy to find explicit solutions of the difference equations that arise from the conditioning on the first jump and the imposition of the boundary conditions.
+\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+	\end{equation}
+that gives back \eqref{one-pts-corr}.  \\ 
 \subsection{Mapping to equilibrium?}

### 2023-03-20 main.tex
i

@@
 As pointed out in section \ref{sectionDuality}, the dual process voids the chain.
-Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.\\
+Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.
+In this context it is better to work agin with generators.
+We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry.
+\\
 We consider the process $(\bm{n}(t))_{t\geq 0}$ on a chain of length $L$ with the end sites connected with two reservoirs.

### 2023-03-21 main.tex
comments

@@
 \newcommand{\spe}{N}
+
+\newcommand{\com}[1]{{ (* {\color{red}\small #1}*)}}
 
@@
 Indeed, using \eqref{eq:comgl} we have 
-    \begin{equation*}
+    \begin{equation}
        \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
-    \end{equation*}
+    \end{equation}
     Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
@@
     \end{equation}
+  \com{Why indices have names $\ell, k, j, a, b$? Fix one set for the generators}
+
     Indeed, using \eqref{eq:comgl} we have 
-    \begin{equation*}
+    \begin{equation}
 [E,E_{1\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{11}-E_{11}\delta_{a\ell}\right)=\sum_{j=2}^{N}E_{j\ell}-E_{11};
-\end{equation*}
+\end{equation}
 and 
-\begin{equation*}
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation*}
+\end{equation}
 Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
@@
 \end{equation}
+\com{double check}
    Indeed, using \eqref{eq:comgl} we have 
-\begin{equation*}
-[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{ak}^{x}\delta_{\ell 1}-E_{\ell 1}^{x}\delta_{ak}\right)=-E_{\ell 1}^{x};
-\end{equation*}
+   {\color{red}
+\begin{equation}
+[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{\ell 1}-E_{\ell 1}\delta_{ak}\right)=-E_{\ell 1};
+\end{equation}
+}
+\begin{equation}
+[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{k1}-E_{k1}\delta_{\ell a}\right)=-E_{k1};
+\end{equation}
 Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-Ekl}.
@@
 \begin{equation}\label{HT-E11}
-    \exp{(-E^{x})}E_{11}^{x}\exp{(E^{x})}=E_{11}^{x}-\sum_{j=2}^{N}E_{j1}^{x}
+    \exp{(-E)}E_{11}\exp{(E)}=E_{11}-\sum_{j=2}^{N}E_{j1}
 \end{equation}
@@
 \begin{align*}
-[E,E_{11}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{11}-E_{\ell 1}\delta_{a1}\right)=\sum_{j=2}^{N}E_{j1};
+[E,E_{11}]=\sum_{a=2}^{N}\left(E_{a1}\delta_{11}-E_{1 1}\delta_{a1}\right)=\sum_{j=2}^{N}E_{j1};
 \end{align*}
@@
 Therefore, multiplying by the boundary vectors we have 
-\begin{equation*}
+\begin{equation}
 	\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
 	|V \rangle=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
-\end{equation*}
+\end{equation}
 Using \eqref{commRIGHT}
@@
 where the addends are 
-\begin{equation*}
+\begin{equation}
 \begin{split}
@@
  \end{split}
-\end{equation*}
+\end{equation}
 The matrix $T^{T}\otimes T^{T}$ has elements $\left\{\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2},q_{1},q_{2}\in \{1,\ldots,N\}}$, where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column.

### 2023-03-21 main.tex
fix

@@
 Moreover, we will use this duality, to study the out of equilibrium steady state.
-In particular, in case of $\twoj=1$ we should retrieve the model studied in \cite{vanicat2017exact}.
+In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}.
 We will then exploit this last result and the duality, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
@@
 Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}.
-A fundamental 'ingredient' of these computation is duality, that has been proved in section \ref{sectionDuality}.
+A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}.
+\com{clarify}
 \subsubsection{The similarity transformation}
@@
 \subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain}
-In subsection \ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
+In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
 When the maximal occupation of each site $\nu>1$, this nice property is lost.
@@
 In this subsection we still consider the same geometry of \ref{subsection-exact}.
-As pointed out in section \ref{sectionDuality}, the dual process voids the chain.
+As pointed out in section~\ref{sectionDuality}, the dual process voids the chain.
 Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.
@@
 where the duality matrix $D$ is again \eqref{dualityMatrix}.
-Following subsection \ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
+Following subsection~\ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
 This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
@@
 \end{equation}
-Therefore, arguing similarly to subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.
+Therefore, arguing similarly to subsection~\ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.
 

### 2023-03-21 main.tex
Update main.tex

@@
 \section{The stirring process}
-The process studied in this paper is the multi-species stirring process on the geometry of a graph.
-We consider the general situation where at any time and at any site a mixture of $\nu\in \mathbb{N}$, chosen among $N$ possible species (sometimes called types or colors), is present.
-Among these $N$ types of particles we will distinguish $N-1$ 'actual' types, labelled with $k\in \{2,\ldots,N\}$ and a 'hole', labelled with $1$.
-This is an arbitrary choice, indeed one could call any of the $N$ colors the hole.
-In the description of the dynamic this choice is not important, since one could think about the dynamic as a pure exchange of types between sites, under the constraint that the maximal occupancy at each site is $\nu$.
-However, studying the duality for the boundary driven case, it will be important to chose an hole type, in order to interpret the dual dynamic as absorbing, i.e.
-to have, eventually, an empty dual process on the graph.
-Furthermore, as the configuration of each site at each time is a mixture of $\nu$ particles, one could think about the hole as the only type whose occupation dependes on the occupations of all the true $N-1$ colors.
-In the two species case, this multi-species stirring process  is the SEP($\nu$) (see \cite{giardina2009duality}, \cite{carinci2013duality}).
-Indeed one of the two type is the hole (say again $1$) and its dynamics depends on the one of the true type (say 2), under the constaraint that at most $\nu$ type $2$ particles are present at a site at each time.
-Therefore, the dynamics can be describe only by species $2$.
-It is interesting to observe that, in case we stop distinguishing the colors of the true particles $\{2,\ldots,N\}$, we retrieve the SEP($\nu$), thus this multi-species stirring process seems its natural generalization.
+\subsection{Informal description}
+The process studied in this paper is the {\em multi-species stirring process}. 
+In words, the dynamics is described as follows. Each site
+of a connected graph can host up to $\nu\in \mathbb{N}$ particles.
+The particles have a {\em type} (sometimes called {\em species} or {\em color})
+which can take $N$ values.
+Then, the dynamics has two parts: on each edge of the graph, 
+any two types are swapped at rate $1$; additionally, on each site $x$, 
+a particles of a give type (if present) is replaced with a
+particle of type $k$ at rate $\alpha_k^x >0$.
+The swap dynamics taking place on the edges is of Kawasaki-type 
+with $N$ conservation laws
+(the total number of particles of each type). 
+The site-dynamics is instead of Glauber-type 
+and, in the long-time limit, so-called non-equilibrium
+steady state sets in.
+
+\vspace{.5cm}
+\noindent
+{\bf Remark:} in the following we will often consider type $1$ as a distinguished type
+(called `holes'), whose number at each site is fixed by the numbers of particles 
+of the remaining $N-1$ types (at the same site). It is interesting to observe that, in case we stop distinguishing the colors of the ``true'' particles of types $\{2,\ldots,N\}$, we retrieve the 
+boundary-driven version of the partial symmetric exclusion process \cite{ss,carinci2013duality}.
+The choice of type $1$ for the distinguished type is arbitrary and does not affect
+the results. In particular, we shall see in Section \ref{sectionDuality} about duality, that
+the dual process eventually has only particles of type $1$ on the graph.
+Interpreting type $1$ as an hole, one can then say that the dual process voids the graph.
 
 \subsection{The infinitesimal generator}
+We now give the mathematical description of the multi-species stirring process.
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
@@
     \label{fig:2}
-\end{figure}\newline \\
-{\color{blue}\textbf{Remark}: 
-    We can always assign the name "empty" to one of the species of particles in the above dynamics (let's say, without loss of generality, the species 1).
-This species would play the role of "compensator" in the exclusion constraint, in the sense that its occupation will always be determined once we know the others, i.e.
-$\forall x\in V$:
-    \begin{equation}
-        n_{1}^{x}=\twoj-\sum_{k=2}^{N}n_{k}^{x}
-    \end{equation}
-    Moreover, if we set $N=2$ and $\twoj=2j$, we exactly retrieve the SEP(2j), where the empty occupation is indeed $2j-\eta_{x}$ where $\eta_{x}$ is the number of (color blind) particles in the site $x$.
-In this sense we can think about the stirring process as the natural generalization of the SEP(2j).}
-    \begin{flushright}
-        $\square$
-    \end{flushright}
+\end{figure}
+\subsection{Reversible measures}
 The process described by the generator \eqref{Generator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasure}

### 2023-03-23 main.tex
ii
FixIntegrability
bibFix

@@
 of the remaining $N-1$ types (at the same site). It is interesting to observe that, in case we stop distinguishing the colors of the ``true'' particles of types $\{2,\ldots,N\}$, we retrieve the 
-boundary-driven version of the partial symmetric exclusion process \cite{ss,carinci2013duality}.
+boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
 The choice of type $1$ for the distinguished type is arbitrary and does not affect
@@
 \end{equation}
-\com{double check}
    Indeed, using \eqref{eq:comgl} we have 
-   {\color{red}
-\begin{equation}
-[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{\ell 1}-E_{\ell 1}\delta_{ak}\right)=-E_{\ell 1};
-\end{equation}
-}
+\begin{equation}
+[E,E_{\ell k}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{\ell 1}-E_{\ell 1}\delta_{ak}\right)=-E_{\ell 1};
+\end{equation}
 \begin{equation}
@@
 Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bulk} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}.
-For the one and two point correlation and for the currents this has been done in \cite{vanicat}.
+For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}.
 Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bulk}, \eqref{leftBoundary} and \eqref{rightBoundary}.
@@
 A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}.
+Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.
 \com{clarify}
@@
 \begin{equation}\label{similarity}
-    S:=\sum_{a=2}^{N}\beta_{a}\sum_{b=2}^{N}e_{ab}+V=-\sum_{a=2}^{N}\beta_{a}\sum_{b=2}^{N}e_{ab}+\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}
+    S:=\sum_{a=2}^{N}\beta_{a}\sum_{b=1}^{N}e_{ab}+V=-\sum_{a=2}^{N}\beta_{a}\sum_{b=1}^{N}e_{ab}+\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}
 \end{equation}
@@
 		\begin{split}
-			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
 		\end{split}
@@
 \begin{equation}
-	\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-e_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
+	\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
 \end{equation}
@@
 \begin{equation}
-  \left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right) =\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)
+  \left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right) =\left(2+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)
 \end{equation}
@@
     \begin{equation}
-	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)\right)^{1-\delta_{s_{i},1}}
+	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)\right)^{1-\delta_{s_{i},1}}
 \end{equation}
@@
 	\begin{split}
-		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}c_{j}\right)\right]^{c_{i}}\left(\beta_{s_{i}}\right)^{(1-c_{i})(1-\delta_{s_{i},1})}
-	\end{split}
-\end{equation} 
-Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $b_{s_{i}}$. 
+		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{i}}\right)^{(1-c_{i})(1-\delta_{s_{i},1})}
+	\end{split}
+\end{equation} 
+Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{i}}$. 
 Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS}.
@@
     \begin{split}
-        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
         \\&+
         \sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right) 
-        \sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}
+        \sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}
+\\&
+\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\sum_{p=1}^{\ell}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}
+  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}
  \\ &
-  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(1-L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
-  \prod_{r=1}^{\ell}\lambda_{q_{r}}\left(1+L-q_{r}-\sum_{j=q_{r}}^{L}c_{j}\right)
+ \beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
+ \prod_{t=1}^{\ell}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
     \end{split}
@@
     \begin{split}
-  &\widehat{\Psi}(\ldots,a_{i},\ldots,d_{q_{r}},\ldots)=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\left(\prod_{r=1}^{\ell}\delta_{c_{r},1}\right)\frac{\Gamma(2+L-\sum_{k=1}^{L}}{\Gamma(2+L)}
+  &\widehat{\Psi}(\ldots,a_{i},\ldots,d_{q_{r}},\ldots)=\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\sum_{p=1}^{\ell}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}
 \\&  
-  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(1-L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
-  \prod_{r=1}^{\ell}\lambda_{q_{r}}\left(1+L-q_{r}-\sum_{j=q_{r}}^{L}c_{j}\right)
-    \end{split}
-\end{equation}
-indeed, in coordinates $q_{r}$ with $r=1,\ldots \ell$ the site is non-empty, thus $c_{q_{r}}=1$.
+\prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
+\\&
+  \prod_{t=1}^{\ell}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+    \end{split}
+\end{equation}
+indeed, in coordinates $q_{r}$ with $r=1,\ldots \ell$ the species $1$ is replaced by all other possible species from $2$ to $N$.
 Finally, considering all possible occupations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}.
@@
 \begin{equation}
-	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(L+1-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
 \end{equation}

### 2023-03-24 main.tex
ii

@@
 \section{The stirring process}
-\subsection{Informal description}
+\subsection{Informal description of the process}
 The process studied in this paper is the {\em multi-species stirring process}. 
@@
 \begin{equation}
-\Omega_{x}:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}
+\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}^{x}=\twoj\right\}
 \end{equation}
@@
 \end{equation}
-This measure has marginals $\mu_{rev}^{x}$ distributed as 
+This measure has marginals $\mu_{rev}^{x}$ given by 
 \begin{equation}
@@
 To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
-Indeed, in this formalism the proof reduces in finding symmetries and exponential transformation of generators of the Lie algebra.\\
+Indeed, in this formalism the proof reduces to finding symmetries and exponential transformation of generators of the Lie algebra.\\
 The configuration space  \eqref{dualStateSpace} of the dual process is the collection of vectors
@@
 \end{equation}
-The Hamiltonian of the dual process reads as
+The Hamiltonian of the dual process reads
 \begin{equation}\label{DualHamiltonian}
@@
 $(a^{\dagger})_{k}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
-The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} with respect to the duality matrix $D$ defined as 
+We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} where the duality matrix $D$ is described as 
 \begin{equation}\label{dualityMatrix}
@@
 \\
-Since \eqref{dualityMatrix} is product over sites, \eqref{DualityRelation} is equivalent to proving that 
+Since \eqref{dualityMatrix} is product over sites, proving \eqref{DualityRelation} is equivalent to showing that 
 \begin{equation}\label{edgeDualRealtion}
@@
 \end{equation}
-We perform the proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
+We perform the duality proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
+As a preliminary result we show the following property 
+\begin{equation}\label{transpositionPropertyR}
+(E_{ab}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
+\end{equation}
+Indeed
+\begin{align*}
+R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|
+	\\&
+	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
+	\\&
+	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
+ \\=&\sum_{r^{x}\in \Omega_{x}}
+	r_{a}^{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
+	\\=&
+	\left(E_{ba}^{x}\right)^{T}
+\end{align*}
+where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
 \paragraph{Elements of the duality matrix.}We aim to show that 
@@
 with $D(\bm{n},\bm{\xi})$ defined in \eqref{dualityElements}. 
-Fix an arbitrary site $x\in V$
+Fix an arbitrary site $x\in V$, then we have that 
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
-	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|
+	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle
 \end{align*}
+where we used \eqref{transpositionPropertyR}. \\
 On one hand, on the extra-site $\widehat{x}$ we have 
 \begin{align*}
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}
+\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}
 \end{align*}
@@
 \begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\chi}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|_{x}\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
-\\&\cdot 
-\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1},\ldots,r_{N}\rangle_{x}\\&=
-\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+\\&
+\hspace{2.cm}\qquad|r_{1}^{x},\ldots,r_{N}^{x}\rangle
+\\&=
+\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
+\\&
+\hspace{2.cm}\prod_{a=2}^{N}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle
+\\&=
+\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
+\\& 
+\hspace{2.cm}\qquad\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle
+\\&=
+\frac{(\nu-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
 \end{align*}
@@
 \\
-We show that 
-\begin{equation}\label{transpositionPropertyR}
-(E_{ab}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
-\end{equation}
-Indeed
-\begin{align*}
-R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\left(\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|\right)
-	\\&
-	\sum_{s^{x}\in \Omega_{x},}\left(s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
-	\\&
-	\sum_{n_{x}\in\Omega_{x}}\left(\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|\right)
- \\=&\sum_{r^{x}\in \Omega_{x}}
-	r_{a}^{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
-	\\=&
-	\left(E_{ba}^{x}\right)^{T}
-\end{align*}
-where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
 Equation \eqref{transpositionPropertyR} implies that 
@@
 \end{equation}
-We now search for a symmetry of $H_{x,y}$. Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
-\begin{equation}
-    [A,B]=0
-\end{equation}
-Moreover, since the coproduct is a Lie algebra homomorphism we have that 
+As a consequence of \eqref{hamiltonianCasimir} we look for a symmetry of  $\Delta(C_{2})$.
+
+%We now search for a symmetry of $H_{x,y}$. % Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
+%\begin{equation}
+%    [A,B]=0
+%\end{equation}
+Since the coproduct is a Lie algebra homomorphism we have that $\forall A,B\in gl(N)$
 \begin{equation}\label{symmetryCoproduct}
@@
 \end{equation}
-Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, we can search for a symmetry of $C_{2}$.
-$C_{2}$ is a central for $gl(N)$, i.e.
-it commutes with all the element of the the algebra.
-We consider
+%Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, it is enough to identify a symmetry of $C_{2}$. But
+ $C_{2}$ is in the center of $gl(N)$, and therefore it commutes with all the element of the the algebra. Considering 
 \begin{equation}\label{equationE}
@@
 \end{equation}
-To obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we take the exponential of this matrix, i.e. we introduce the symmetry
+to obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we chose as a symmetry 
 \begin{equation}
@@
 \end{equation}
-Since $[C_{2},E]=0$, we have that 
-\begin{equation}\label{commutationSC}
-    \left[S,\Delta(C_{2})\right]=0
-\end{equation}
+%Since $[C_{2},E]=0$, we have that 
+%\begin{equation}\label{commutationSC}
+    %\left[S,\Delta(C_{2})\right]=0
+%\end{equation}
 For fixed $(x,y)\in \mathcal{E}$ we introduce
@@
 \end{equation}
-where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{commutationSC}, we have that 
+where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{symmetryCoproduct}, we have that 
 \begin{equation}\label{symmetryH}
@@
  where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
- \newline\newline
- \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$.
+ %\textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$.
 This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
 By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
- {\color{blue} That's confusing. What is E?}
-
- However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
+ %{\color{blue} That's confusing. What is E?}
+
+% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
  \begin{flushright}
@@
  \end{flushright}
- \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need two transform via Hadamard formula \eqref{HadamardFormula}, the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then introduce properly a creation operator acting on an extra-site $\widehat{x}$ that we connect to every site $x\in V$ of the graph $G$.
+ \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $\widehat{x}$.
+% that we connect to every site $x\in V$ of the graph $G$.
 \\
- Considering $A,B\in gl(N)$, we can write the Hadamard formula as 
+ Considering $A,B\in gl(N)$, the Hadamard formula reads 
  \begin{equation}\label{HadamardFormula}
@@
  \end{equation}
-For the following of the proof we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
-Therefore we compute
+In the followin we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
 \begin{enumerate}
@@
 \end{equation}
-where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$.
+%where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$.
  Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 
@@
     \begin{split}
-&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+&H_{x}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \\=&
@@
     \begin{split}
-     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
-\\=&
+H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
+     H_{x}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\\&=
 d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+\\&=
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\widetilde{H}_{x}
+\\&=
+\left(d_{x}\otimes \dd\right)\widetilde{H}_{x}
     \end{split}

### 2023-04-02 main.tex
ii

@@
 \newcommand{\osc}[1]{\mathbf{#1}}
-\newcommand{\oscgreek}[1]{\boldsymbol{#1}}
+\newcommand{\oscgreea}[1]{\boldsymbol{#1}}
 \newcommand{\dagg}[1]{\bar{#1}}
@@
  \begingroup\large \bf
-% {Rouven Frassek}
+% {Rouven Frassea}
  \par\endgroup
@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{k}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$ at site $x\in V$.
+At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{a}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$ at site $x\in V$.
 On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$.
@@
 \begin{equation}
-\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}^{x}=\twoj\right\}
-\end{equation}
-We denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$ .\\
+\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}
+\end{equation}
+We denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$ .\\
 The dynamics consists in an exchange of particles (at Poissonian times) between connected vertices.
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(\bm{n})=\sum_{k,\ell=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{k}+\delta_{\ell}^{x}+\delta_{k}^{y}-\delta_{\ell}^{y})-f(\bm{n})\right]
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{a}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-f(\bm{n})\right]
 \end{equation}
 \begin{equation}\label{siteGenerator}
-    \mathcal{L}_{x}f(\bm{n})=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}n_{\ell}^{x}\left[f(\bm{n}+\delta_{k}^{x}-\delta_{\ell}^{x})-f(\bm{n})\right]
+    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\delta_{a}^{x}-\delta_{b}^{x})-f(\bm{n})\right]
 \end{equation}
@@
 \begin{equation}
-(\delta_{k}^{x})^{y}_{\ell}=\begin{cases}
-1\qquad &\text{if}\quad y=x,\;\ell=k\\
+(\delta_{a}^{x})^{y}_{b}=\begin{cases}
+1\qquad &\text{if}\quad y=x,\;b=k\\
 0\qquad &\text{otherwise}
@@
 \end{equation}
-This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{k}^{x}n_{\ell}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{k}^{x}n_{\ell}^{x}$ a particle of type $\ell$ is replaced with a particle of type $k$.
+This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $k$.
 See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 
@@
 \begin{equation}\label{reversibilityCondition}
-\alpha_{k}^{x}=\alpha_{k}\qquad \forall x\in V
+\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V
 \end{equation}
@@
 \begin{equation}
- \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}
+ \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}
 \end{equation}
@@
 \begin{equation}
-\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}\rho_{k}^{n_{k}^{x}}
+\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}
 \end{equation}
@@
 \end{equation}
-%where $\sum_{k=1}^{N}n_{i}=\nu$. 
+%where $\sum_{a=1}^{N}n_{i}=\nu$. 
 This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
 \begin{equation}\label{ortho}
-    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{k=1}^{N}\delta_{m_{k},n_{k}}
-\end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{k},n_{k}}$ is the Kronhecker delta. 
+    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{m_{a},n_{a}}
+\end{equation}
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronhecker delta. 
 The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
@@
 \noindent
-\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
+\textbf{Remara}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
 \begin{equation}
@@
 \end{equation}
-where we require that $n_{k}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{k=1}^{N}n_{k}^{x}=\nu$.
+where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$.
 Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{k,\ell=1}^{N}\Big(E_{k\ell}^{x} E_{\ell k}^{y}-E_{\ell\ell}^{x} E_{kk}^{y}\Big)
+H_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
  \end{equation}
@@
  \begin{equation}\label{siteHamiltonian}
-H_{x}=\sum_{k,\ell=1}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)
-\end{equation}
-Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$. 
+H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
+\end{equation}
+Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$. 
 Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{k,l=1}^{N}E_{kl}^{x}\otimes E_{lk}^{y}-E_{ll}^{x}\otimes E_{kk}^{y}
+H_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
  \end{equation}
@@
  \begin{equation}\label{siteHamiltonian}
-H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(E_{kl}^{x}-E_{ll}^{x}\right)
-\end{equation}
-Here $E_{kl}^{x}$ is a copy of $E_{kl}$ defined in \eqref{actionE} acting on site $x$.
+H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(E_{al}^{x}-E_{ll}^{x}\right)
+\end{equation}
+Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$.
 
@@
 \newline
-\textbf{Remark}:
+\textbf{Remara}:
 when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
@@
 \end{equation}
-where the component $r_{k}^{x}$ is interpreted as the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{k}^{\widehat{x}}$  gives the number of dual particles of type $k\in \{2,\ldots,N\}$ at 
+where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $k\in \{2,\ldots,N\}$ at 
 the extra-site $\widehat{x}$ connected to $x\in V$.
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}r_{k}^{x}\left(f(\bm{\xi}-\delta_{k}^{x}+\delta_{1}^{x}+\delta_{k}^{\widehat{x}})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}r_{a}^{x}\left(f(\bm{\xi}-\delta_{a}^{x}+\delta_{1}^{x}+\delta_{a}^{\widehat{x}})-f(\bm{\xi})\right)
 \end{equation}
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
 \end{equation}
@@
 \begin{equation}
-\rho_{k}^{x}:=\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
+\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
 \end{equation}
@@
 On the other hand, the dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$.
-This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{k}^{x}$.
+This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{a}^{x}$.
 This means that eventually the dual process voids the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites.
@@
 \newline \newline
-\textbf{Remark}: in the reversible situation, i.e.
-when $\forall x\in V$ $\alpha_{k}^{x}=\alpha_{k}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
-\begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\textbf{Remara}: in the reversible situation, i.e.
+when $\forall x\in V$ $\alpha_{a}^{x}=\alpha_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
+\begin{equation}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\sum_{x\in V}r_{a}^{x}+\sum_{x\in V}m_{a}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
+    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{\widehat{x}}\,E_{1a}^{x}-E_{aa}^{x}\right)
 \end{equation}
 Here we introduced bosonic creation operator $a^{\dagger}$ acting as $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(a^{\dagger})_{k}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
+$(a^{\dagger})_{a}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
 We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} where the duality matrix $D$ is described as 
@@
 \begin{equation}\label{Rmatrix}
-    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
 \end{equation}
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \end{equation}
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|
 	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle
@@
 \begin{align*}
-\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{q_{k}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}
+\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}
 \end{align*}
@@
 \begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{a_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{a_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 \\&
@@
 \\&=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
+\sum_{a_{2}=0}^{n_{1}^{x}}\ldots\sum_{a_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
 \\&
@@
 \\&=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
+\sum_{a_{2}=0}^{n_{1}^{x}}\ldots\sum_{a_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
 \\& 
@@
 \\&=
-\frac{(\nu-\sum_{k=2}^{N}r_{k}^{x})}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}
+\frac{(\nu-\sum_{a=2}^{N}r_{a}^{x})}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}
 \end{align*}
-where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{k=2}^{N}r_{k}^{x}$.
+where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{a=2}^{N}r_{a}^{x}$.
 Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
@@
  where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
- %\textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$.
+ %\textbf{Remara}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$.
 This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
@@
 \begin{enumerate}
-    \item for $A=E_{\ell 1}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
+    \item for $A=E_{b 1}$ with $b\in \{2,\ldots,N\}$, we obtain 
     \begin{equation}\label{HT_El1}
-        \exp{(-E)}E_{\ell 1}\exp{(E)}=E_{\ell 1}
-    \end{equation}
-    because $E_{\ell 1}$ commutes with $E$
-    \item for $A=E_{\ell\ell}$ with $\ell \in \{2,\ldots,N\}$, we obtain 
+        \exp{(-E)}E_{b 1}\exp{(E)}=E_{b 1}
+    \end{equation}
+    because $E_{b 1}$ commutes with $E$
+    \item for $A=E_{bb}$ with $b \in \{2,\ldots,N\}$, we obtain 
     \begin{equation}\label{HT_Ell}
-        \exp{(-E)}E_{\ell \ell}\exp{(E)}=E_{\ell \ell}+E_{\ell 1}
+        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b 1}
     \end{equation}
@@
     \begin{equation}
-       \left[E, E_{\ell\ell}\right]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{\ell 1}-E_{\ell 1}\delta_{a\ell}\right)=-E_{l1}
+       \left[E, E_{bb}\right]=\sum_{a=2}^{N}\left(E_{ab}\delta_{b 1}-E_{b 1}\delta_{ab}\right)=-E_{l1}
     \end{equation}
     Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
-    \item for $A=E_{1\ell}$ with $\ell\in \{2,\ldots,N\}$, we obtain 
+    \item for $A=E_{1b}$ with $b\in \{2,\ldots,N\}$, we obtain 
     \begin{equation}\label{HT-E1l}
-        \exp{(-E)}E_{1 \ell}\exp{(E)}=E_{1\ell}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{j\ell}\right)
-    \end{equation}
-  \com{Why indices have names $\ell, k, j, a, b$? Fix one set for the generators}
+        \exp{(-E)}E_{1 b}\exp{(E)}=E_{1b}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{jb}\right)
+    \end{equation}
+  \com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}
 
@@
     \begin{equation}
-[E,E_{1\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{11}-E_{11}\delta_{a\ell}\right)=\sum_{j=2}^{N}E_{j\ell}-E_{11};
+[E,E_{1b}]=\sum_{a=2}^{N}\left(E_{ab}\delta_{11}-E_{11}\delta_{ab}\right)=\sum_{j=2}^{N}E_{jb}-E_{11};
 \end{equation}
@@
 \begin{split}
-\left[E,[E,E_{1\ell}]\right]&=\sum_{b=2}^{N}\sum_{j=2}^{N}\left[E_{b1},E_{j\ell}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
-\\&=
-\sum_{j,b=2}^{N}\left(E_{b\ell}\delta_{j1}-E_{j1}\delta_{b\ell}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
+\left[E,[E,E_{1b}]\right]&=\sum_{b=2}^{N}\sum_{j=2}^{N}\left[E_{b1},E_{jb}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
+\\&=
+\sum_{j,b=2}^{N}\left(E_{bb}\delta_{j1}-E_{j1}\delta_{bb}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
 \\=&
@@
 Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
-\item for $A=E_{k\ell}$ with $k,\ell \in \{2,\ldots,N\}$ we obtain 
+\item for $A=E_{ab}$ with $k,b \in \{2,\ldots,N\}$ we obtain 
 \begin{equation}\label{HT-Ekl}
-    \exp{(-E)}E_{\ell k}\exp{(E)}=E_{k\ell}+E_{\ell 1}
+    \exp{(-E)}E_{b a}\exp{(E)}=E_{ab}+E_{b 1}
 \end{equation}
@@
 \begin{equation}
-[E,E_{\ell k}]=\sum_{a=2}^{N}\left(E_{ak}\delta_{\ell 1}-E_{\ell 1}\delta_{ak}\right)=-E_{\ell 1};
-\end{equation}
-\begin{equation}
-[E,E_{k\ell}]=\sum_{a=2}^{N}\left(E_{a\ell}\delta_{k1}-E_{k1}\delta_{\ell a}\right)=-E_{k1};
+[E,E_{b a}]=\sum_{a=2}^{N}\left(E_{aa}\delta_{b 1}-E_{b 1}\delta_{aa}\right)=-E_{b 1};
+\end{equation}
+\begin{equation}
+[E,E_{ab}]=\sum_{a=2}^{N}\left(E_{ab}\delta_{a1}-E_{a1}\delta_{b a}\right)=-E_{a1};
 \end{equation}
@@
     \begin{split}
-H_{x}^{T}=\sum_{k,l=0}^{N}\alpha_{k}^{x}\left(E_{k\ell}^{x}-E_{\ell\ell}^{x}\right)^{T}=R_{x}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)R_{x}^{-1}
+H_{x}^{T}=\sum_{a,l=0}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}
     \end{split}
@@
 \begin{equation}
-    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{k,\ell =0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
 \end{equation}
@@
 \begin{equation}\label{intermediateTransposeSite}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{k,\ell=0}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
 \end{equation}
@@
 \begin{align*}
-    &\exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=1}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+    &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
     \\=&
-     \exp{(-E^{x})}\sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
-     + \exp{(-E^{x})}\sum_{k=1}^{N}\sum_{\ell=2}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}-E_{\ell\ell}^{x}\right)\exp{(E^{x})}
+     \exp{(-E^{x})}\sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
+     + \exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
      \\=&
-     \sum_{k=2}^{N}\alpha_{k}^{x}\left(E_{1k}+E_{11}^{x}-\sum_{a=2}^{N}(E_{ak}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{k=1}^{N}\sum_{\ell =2}^{N}\alpha_{k}^{x}\left(E_{\ell k}^{x}+E_{\ell 1}^{x}-E_{\ell\ell}^{x}-E_{\ell 1}^{x}\right)
+     \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}+E_{11}^{x}-\sum_{a=2}^{N}(E_{aa}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{a=1}^{N}\sum_{b =2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}+E_{b 1}^{x}-E_{bb}^{x}-E_{b 1}^{x}\right)
      \\=&
-\sum_{k=2}^{N}\alpha_{k}^{x}E_{1k}^{x}-\sum_{k=1}^{N}\alpha_{k}^{x}\sum_{\ell=2}^{N}E_{\ell\ell}^{x}
+\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{a=1}^{N}\alpha_{a}^{x}\sum_{b=2}^{N}E_{bb}^{x}
 =
-     \sum_{k=2}^{N}\left(\alpha_{k}^{x}E_{1k}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{kk}^{x}\right)
+     \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
 =
-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)
+\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
 \\=&
-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}^{x}\right)
+\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
  \end{align*}
@@
 \begin{equation}\label{siteHadamardI}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}^{x}\right)
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
 \end{equation}
@@
 \begin{equation}
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \end{equation}
@@
     \begin{split}
-&H_{x}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+&H_{x}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
 \\=&
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}\right)
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}\right)
     \end{split}
@@
 \begin{equation}\label{bosonicKX}
-    \langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|=  \langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})^{\widehat{x}}_{k}
-\end{equation}
-Using \eqref{bosonicKX} by a fixed $k\in \{2,\ldots,N\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{1k}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
-\begin{equation}
-    \begin{split}
-&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
-\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
+    \langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|=  \langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})^{\widehat{x}}_{a}
+\end{equation}
+Using \eqref{bosonicKX} by a fixed $k\in \{2,\ldots,N\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{1a}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+\begin{equation}
+    \begin{split}
+&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}
+\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}
 \\=&
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}
+\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}
     \end{split}
@@
 H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
-     H_{x}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
-\\&=
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)
-\\&=
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\widetilde{H}_{x}
+     H_{x}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\\&=
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=1}^{N}\left((a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}-E_{aa}^{x}\right)
+\\&=
+d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\widetilde{H}_{x}
 \\&=
@@
 \begin{equation}\label{hamiltonian}
-	H=B_{1}+H_{bulk}+B_{L}
+	H=B_{1}+H_{bula}+B_{L}
 \end{equation}
@@
 \begin{equation}
-    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
+    H_{bula}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
 \end{equation}
@@
 \end{equation}
-Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product anstz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat}).
+Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product anstz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat2017exact}).
 We recall the main points of this ansatz.
@@
 These operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
-\begin{equation}\label{bulk}
+\begin{equation}\label{bula}
 	\left[X_{a},X_{b}\right]=\lambda_{a}X_{b}-\lambda_{b}X_{a}\qquad\forall a,b=1,\ldots,N
@@
 \newline
-\textbf{Remark}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
+\textbf{Remara}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
 	\begin{equation}
@@
 If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}.
-Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bulk} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}.
+Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}.
 For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}.
-Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bulk}, \eqref{leftBoundary} and \eqref{rightBoundary}.
+Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}.
 In subsection \eqref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
@@
 \begin{equation}\label{bbHamiltonian}
-    \mathbb{H}=\mathbb{B}_{1}+H_{bulk}+\mathbb{B}_{L}
+    \mathbb{H}=\mathbb{B}_{1}+H_{bula}+\mathbb{B}_{L}
 \end{equation}
@@
 \begin{equation}\label{ResulsBasis}
-	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}|\mathbf{\bm{s}}\rangle
+	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}|\mathbf{\bm{s}}\rangle
 \end{equation}
@@
 \begin{equation}
-    \delta_{s_{i},1}:=\begin{cases}
-        1\quad \text{if}\quad s_{i}=1\\
+    \delta_{s_{x},1}:=\begin{cases}
+        1\quad \text{if}\quad s_{x}=1\\
         0\quad \text{otherwise}
@@
 \end{equation}
-and the basis vector $|\bm{s}\rangle =\bigotimes_{i=1}^{L}|s_{i}\rangle$ with $s_{i}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
+and the basis vector $|\bm{s}\rangle =\bigotimes_{i=1}^{L}|s_{x}\rangle$ with $s_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
-To prove \eqref{ResulsBasis} we will consider the vector composed by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we will act on it with the similarity transformation \eqref{similarity} obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators than \eqref{bulk} and simpler actions than \eqref{leftBoundary} and \eqref{rightBoundary}.
+To prove \eqref{ResulsBasis} we will consider the vector composed by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we will act on it with the similarity transformation \eqref{similarity} obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators than \eqref{bula} and simpler actions than \eqref{leftBoundary} and \eqref{rightBoundary}.
 This will allow to write explicitly the steady state \eqref{ResulsBasis}.
@@
 \end{equation}
-Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have
+Summing over $b\in \{1,\ldots,N\}$ in \eqref{bula} we have
 \begin{equation} 
@@
 therefore, we obtain the commutation relations for $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$
-\begin{equation}\label{commutationsBulk}
+\begin{equation}\label{commutationsBula}
 	\left[\Xt_{a},\Xt_{1}\right]=\lambda_{a}\Xt_{1}\qquad \forall a\in \{2,\ldots,N\}
@@
 \begin{equation}\label{toDetermineTilde}
-	|\widetilde{\Psi}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
+	|\widetilde{\Psi}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 	|V \rangle \,|\mathbf{n}\rangle
@@
 We also observe that the vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
-To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{i}}
-|V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBulk},\eqref{commLEFT} and \eqref{commRIGHT}.\\
-We  rewrite \eqref{commutationsBulk} as:
+To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{x}}
+|V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBula},\eqref{commLEFT} and \eqref{commRIGHT}.\\
+We  rewrite \eqref{commutationsBula} as:
 \begin{equation}\label{UsefulRelation}
@@
 \end{equation}
-Fixing $ a\in \{2,\ldots,N\}$ and $\forall \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
+Fixing $ a\in \{2,\ldots,N\}$ and $\forall b,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
 \begin{align*}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
-	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{\ell-1}
-	\\&=
-	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}
+	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{b}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{b-1}
+	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{b-1}
+	\\&=
+	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}
 	\\&=\ldots\\&=
-	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
+	\widetilde{X}_{1}^{b}\left(\widetilde{X}_{a}+b\lambda_{a}\right)^{n}
 \end{align*}
@@
 \begin{equation}
-	\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}=\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
+	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 \begin{equation}
-	\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
-	|V \rangle=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
+	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|V \rangle=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
 \end{equation}
@@
 \begin{align*}
-	W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
-	|V \rangle&=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{i}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
-	\\&=
-	\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|V\rangle
-	\\&=
-	\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle
+	W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|V \rangle&=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\\&=
+	\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\\&=
+	\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle
 \end{align*}
 To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$.
-Calling $\sum_{i=1}^{L}n_{1}^{i}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
+Calling $\sum_{i=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
 \begin{align*}
@@
 \begin{equation}
-	\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{i}}
-	|V \rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2)}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
+	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|V \rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 \begin{equation}\label{resulEsteady}
-	|\widetilde{\Psi}\rangle= \sum_{\mathbf{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{i})}{\Gamma(2+L)}\prod_{i=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}|\mathbf{n}\rangle
-\end{equation}
-Calling $s_{i}$ the species present at site $i$, we rewrite the basis vector 
-\begin{equation}
-	|n_{1}^{i},\ldots,n_{N}^{i}\rangle=|s_{i}\rangle
-\end{equation}
-where $s_i=\sum_{k=1}^N\delta_{n_k^i,1}$. Finally we take the tensor product of the vectors $|s_{i}\rangle$ and we obtain
-\begin{equation}
-	|\mathbf{s}\rangle=\bigotimes_{i=1}^{L}|s_{i}\rangle=|\mathbf{s}\rangle
-\end{equation}
-with $s_{i}\in\{1,\ldots,N\}$. For a fixed site $i$, because of the hard-core interaction that allows at most one particle on type different from $1$ ,at site $i$ we have 
-\begin{equation}
-	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}=\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}
+	|\widetilde{\Psi}\rangle= \sum_{\mathbf{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|\mathbf{n}\rangle
+\end{equation}
+Calling $s_{x}$ the species present at site $i$, we rewrite the basis vector 
+\begin{equation}
+	|n_{1}^{x},\ldots,n_{N}^{x}\rangle=|s_{x}\rangle
+\end{equation}
+where $s_i=\sum_{a=1}^N\delta_{n_k^i,1}$. Finally we take the tensor product of the vectors $|s_{x}\rangle$ and we obtain
+\begin{equation}
+	|\mathbf{s}\rangle=\bigotimes_{i=1}^{L}|s_{x}\rangle=|\mathbf{s}\rangle
+\end{equation}
+with $s_{x}\in\{1,\ldots,N\}$. For a fixed site $i$, because of the hard-core interaction that allows at most one particle on type different from $1$ ,at site $i$ we have 
+\begin{equation}
+	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}=\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}
 \end{equation}
@@
 \begin{equation}
-	\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}
-\end{equation}
-Finally summing over all $\mathbf{s}\in \Omega$ (that is equivalent, $\forall i\in\{1,\ldots,L\}$, to summing over all the possible values of each $s_{i}\in\{1,\ldots,N\}$) we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}.
+	\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}
+\end{equation}
+Finally summing over all $\mathbf{s}\in \Omega$ (that is equivalent, $\forall i\in\{1,\ldots,L\}$, to summing over all the possible values of each $s_{x}\in\{1,\ldots,N\}$) we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}.
 \begin{flushright}
@@
 		\begin{split}
-			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
 		\end{split}
@@
  \begin{equation}\label{CiEquation}
-	c_{i}=\begin{cases}
-		1\quad \text{if}\quad s_{i}\neq 1\\
-		0\quad \text{if}\quad s_{i}=1
-	\end{cases}\qquad \forall i\in \{1,\ldots,N\}
+	c_{x}=\begin{cases}
+		1\quad \text{if}\quad s_{x}\neq 1\\
+		0\quad \text{if}\quad s_{x}=1
+	\end{cases}\qquad \forall x\in \{1,\ldots,L\}
 \end{equation}
@@
     \begin{equation}
-        T^{T}=\sum_{s_{1}=1}^{N}e_{i}^{i}+Q
+        T^{T}=\sum_{s_{1}=1}^{N}e_{i}^{x}+Q
     \end{equation}
@@
   \\&+
-  \ldots+\left(\prod_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
+  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
 	\end{split}
@@
 		\widehat{\Psi}(\mathbf{s})&=\mathcal{T}^{T}_{\bm{s}}|\widetilde{\Psi}\rangle\\&= \widetilde{\Psi}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{k_{1}}\beta_{k_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\prod_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
 	\end{split}
@@
 \begin{equation}
-  \left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right) =\left(2+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)
+  \left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)
 \end{equation}
@@
     \begin{equation}
-	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)\right)^{1-\delta_{s_{i},1}}
-\end{equation}
-Because of the exponent $(1-\delta_{s_{i},1})$, the element $\widetilde{\Psi}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{i},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{i}}\left(1+L-i-\sum_{j=i}^{L}(1-\delta_{s_{i},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
+	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
+\end{equation}
+Because of the exponent $(1-\delta_{s_{x},1})$, the element $\widetilde{\Psi}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
@@
 	\begin{split}
-		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{i=1}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{i}}\right)^{(1-c_{i})(1-\delta_{s_{i},1})}
-	\end{split}
-\end{equation} 
-Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{i}}$. 
+		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
+	\end{split}
+\end{equation} 
+Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
 Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS}.
@@
     \begin{split}
-        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
         \\&+
-        \sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right) 
-        \sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}
+        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
+        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
 \\&
-\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\sum_{p=1}^{\ell}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}
-  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}
+\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
+  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}
  \\ &
- \beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
- \prod_{t=1}^{\ell}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-    \end{split}
-\end{equation}
-\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
-if $s_{i}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations,
+ \beta_{s_{x}}^{(1-c_{i})(1-\delta_{s_{x},1})}
+ \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+    \end{split}
+\end{equation}
+\textbf{Remara}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
+if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations,
 \begin{equation}\label{LinkABS-corr}
@@
     \\&=
-    \sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{s_{i},1}^{s_{i}d_{q_{r}}}
+    \sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{s_{x},1}^{s_{x}d_{q_{r}}}
     +
-    (-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{s_{i},1}^{s_{i}d_{q_{r}}}
-    \end{split}
-\end{equation}
-where $e_{s_{i},d_{q_{r}}}$ denotes the matrix $e_{s_{1},s_{2}}^{s_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
+    (-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{s_{x},1}^{s_{x}d_{q_{r}}}
+    \end{split}
+\end{equation}
+where $e_{s_{x},d_{q_{r}}}$ denotes the matrix $e_{s_{1},s_{2}}^{s_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
 \\
@@
         \\&
-        +\sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{i},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{i},\ldots,\,d_{q_{r}}\,,\ldots}
-    \end{split}
-\end{equation}
-where $e_{\ldots,s_{i},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{i},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{\ell}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{\ell}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{\ell}}$.
+        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}
+    \end{split}
+\end{equation}
+where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
 \\
@@
         \\&
-        +\sum_{\ell=1}^{L}(-1)^{\ell}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{\ell}=q_{\ell-1}+1}^{L}\left(\prod_{r=1}^{\ell}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{\ell}\sum_{d_{q_{r}}=2}^{N}\widehat{\Psi}(\ldots,s_{i},\ldots,d_{q_{r}},\ldots)
-    \end{split}
-\end{equation}
-where $\widehat{\Psi}(\ldots,s_{i},\ldots,d_{q_{r}},\ldots)$ denotes the component $\widehat{\Psi}(s_{1},\ldots,s_{L})$ where the occupations  $s_{q_{1}},\ldots,s_{q_{\ell}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{\ell}}$.
+        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}\widehat{\Psi}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)
+    \end{split}
+\end{equation}
+where $\widehat{\Psi}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\widehat{\Psi}(s_{1},\ldots,s_{L})$ where the occupations  $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
 Using \eqref{elementsABS} we have
@@
     \begin{split}
-  &\widehat{\Psi}(\ldots,a_{i},\ldots,d_{q_{r}},\ldots)=\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\sum_{p=1}^{\ell}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(2+L)}
+  &\widehat{\Psi}(\ldots,a_{i},\ldots,d_{q_{r}},\ldots)=\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
 \\&  
-\prod_{i=1\,:\, i\neq q_{1},\ldots,q_{\ell}}^{L}\left(\lambda_{s_{i}}\left(2+L-i-\sum_{j=i}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{i}}^{(1-c_{i})(1-\delta_{s_{i},1})}
+\prod_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{x}}^{(1-c_{i})(1-\delta_{s_{x},1})}
 \\&
-  \prod_{t=1}^{\ell}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-    \end{split}
-\end{equation}
-indeed, in coordinates $q_{r}$ with $r=1,\ldots \ell$ the species $1$ is replaced by all other possible species from $2$ to $N$.
+  \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+    \end{split}
+\end{equation}
+indeed, in coordinates $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
 Finally, considering all possible occupations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}.
@@
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
-In each of these points there is a particle of species $s_{i}\in \{2,\ldots,N\}$.
+In each of these points there is a particle of species $s_{x}\in \{2,\ldots,N\}$.
 Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
@@
 where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This probability \eqref{Prob-m} can be seen as the component \eqref{steadyStateH-coeff} of the stationary state \eqref{steadyStateH} of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{i}\neq 1$, i.e.
+This probability \eqref{Prob-m} can be seen as the component \eqref{steadyStateH-coeff} of the stationary state \eqref{steadyStateH} of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e.
 \begin{equation}
@@
 \begin{equation}
-	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
 \end{equation}
@@
 \end{equation}
-\textbf{Remark}: the one and two points correlations computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively are exactly the ones found in subsection 4.3 of \cite{vanicat}. 
+\textbf{Remark}: the one and two points correlations computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
 \subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain}
-In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
+In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{a})_{a=1,\ldots,N}$ and $(\beta_{a})_{a=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
 When the maximal occupation of each site $\nu>1$, this nice property is lost.
@@
 \begin{equation}
-    \mathcal{L}_{1}f(\bm{n})=\sum_{k,\ell=0}^{N}\alpha_{k}n_{\ell}^{1}\left(f(\bm{n}-\delta_{\ell}^{x}+\delta_{k}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{k,\ell=0}^{N}\beta_{k}n_{\ell}^{L}\left(f(\bm{n}-\delta_{\ell}^{x}+\delta_{k}^{x})-f(\bm{n})\right)
+    \mathcal{L}_{1}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-    \mathcal{L}_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}\quad \text{where}\quad \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{k,\ell=0}^{N}n_{k}^{x}n_{\ell}^{x+1}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{\ell}^{x}+\delta_{k}^{x+1}-\delta_{\ell}^{x+1})-f(\bm{n})\right)
-\end{equation}
-This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space $\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}$ with the same $\mathcal{L}_{\text{bulk}}$ and with absorbing boundaries, i.e.
-\begin{equation}
-\begin{split}
-        \widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=\sum_{i=1}^{N}\alpha_{i}\sum_{k=2}^{N}\xi_{k}^{1}\left(f(\bm{\xi}-\delta_{k}^{1}+\delta_{k}^{0}+\delta_{k}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{k=2}^{N}\xi_{k}^{L}\left(f(\bm{\xi}-\delta_{k}^{L}+\delta_{k}^{L+1}+\delta_{k}^{L})-f(\bm{\xi})\right)
+    \mathcal{L}_{\text{bula}}=\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}\quad \text{where}\quad \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space $\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}$ with the same $\mathcal{L}_{\text{bula}}$ and with absorbing boundaries, i.e.
+\begin{equation}
+\begin{split}
+        \widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=\sum_{i=1}^{N}\alpha_{i}\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
         \end{split}
@@
 \begin{equation}\label{dualityFunctionChain}
-    D(\bm{n},\bm{\xi})=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}\alpha_{i}}\right)^{\xi_{k}^{0}}\prod_{x=1}^{L}\prod_{k=2}^{N}\frac{\eta_{k}^{x}!}{(n_{k}^{x}-\xi_{k}^{x})!}\prod_{k=2}^{N}\left(\frac{\beta_{k}}{\sum_{i=1}\beta_{i}}\right)^{\xi_{k}^{L+1}}
-\end{equation}
+    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{\sum_{i=1}^{N}\beta_{i}}$.\\
 Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
@@
 \\=&
-\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{k}}\left(\frac{\beta_{k}}{\beta_{1}+\ldots+\beta_{N}}\right)^{|\xi_{k}|-i_{k}}a_{i_{1},\ldots,i_{k}}(\bm{\xi})
+\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{a}}(\bm{\xi})
 \end{split}
@@
 \begin{equation}\label{Pass}
-    a_{i_{k}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{k=2}^{N}\left(i_{k}\delta_{0}+(|\xi_{k}|-i_{k})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+    a_{i_{a}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
 \end{equation}
 where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{k}|=\sum_{x=1}^{L}\xi_{k}^{x}$ and by $i_{k}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{k}|-i_{k}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{s_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{i}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
-\begin{equation}
-    D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{x_{k}}}{(\nu-m+1)}
+Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{s_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
+\begin{equation}
+    D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
 \end{equation}
 Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species.
-This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{k}}}(\widehat{\bm{\xi}})$.
+This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
 The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
@@
 \begin{split}
-	\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{k}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{k}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+	\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
  \end{split}
@@
 \end{equation}
-In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{Esse}, i.e.
+In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e.
 when the left boundary is lower triangular a end the right one is diagonal.
@@
 \end{equation}
-We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
+We call these $Q_{a}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
 We can also introduce 
@@
 \begin{equation}
-	A(x)=\sum_{k=0}^{2L+1}A^{k}x^{k}\quad D_{ii}(x)=\sum_{k=0}^{2L+1}D_{ii}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}
+	A(x)=\sum_{a=0}^{2L+1}A^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}
 \end{equation}
@@
 %\begin{equation}\label{c}
-%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
+%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
 %\end{equation}
@@
 \begin{split}
-	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
-	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
+	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)\\
+	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{a=2}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)
 \end{split}
@@
 	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
-	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{k=2}^{N}e_{jk}^{[a]}e_{k1}^{[b]}}
-\end{split}
-\end{equation}
-\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
+	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{a=2}^{N}e_{ja}^{[a]}e_{a1}^{[b]}}
+\end{split}
+\end{equation}
+\textbf{Remara}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
 The interesting charges (we only look for the first non trivial one) take the following form
@@
 \end{equation}
-where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{k=2}^{N}m_{k}$.\\
+where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{a=2}^{N}m_{a}$.\\
 For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$ and we further assume that $\Delta_{2}=\Delta_{3}=\Delta$.
@@
 \begin{equation}\label{ansatzEigenvectorDelta}
-|\Psi_{L-m}^{\Delta}\rangle=\mathbbm{1}_{\{m_{2}+m_{3}=m\}}\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+|\Psi_{L-m}^{\Delta}\rangle=\mathbbm{1}_{\{m_{2}+m_{3}=m\}}\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{equation}
@@
 \begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 \begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \\+&
@@
 \\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 \begin{equation}
-|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 \end{equation}
@@
 \begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \\&
-+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\\&=
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
++\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\\&=
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \end{align*}
@@
 \begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \\+&
-\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\sum_{a_{2}=1}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{a_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
 \end{align*}
@@
 	\\&+
-	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\\&+\ldots +
-	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 	\\&+
-	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\\&+\ldots
-	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\\&+
-	\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\\&+\ldots +
-	\Delta_{N}^{m_{N}+1}\sum_{k_{2}=0}^{m_{3}}\ldots\sum_{k_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\Delta_{N}^{m_{N}+1}\sum_{a_{2}=0}^{m_{3}}\ldots\sum_{a_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 	\\&+
-	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\\&+\ldots +
-	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 \end{align*}
@@
 	\\&+
-	\sum_{k_{2}=1}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\\&=
@@
 \begin{split}
- \sum_{i,j=2}^N [E_{ij}E_{ji},E_{k1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{k1}]+\sum_{i,j=2}^N  [E_{ij},E_{k1}]E_{ji}=\sum_{j=2}^N( E_{kj} E_{j1}+ E_{j1} E_{kj})
-\\&=\sum_{j=2}^N( 2E_{kj} E_{j1}+ [E_{j1}, E_{kj}])=2\sum_{j=2}^N E_{kj} E_{j1}-(N-1)E_{k1}
+ \sum_{i,j=2}^N [E_{ij}E_{ji},E_{a1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{a1}]+\sum_{i,j=2}^N  [E_{ij},E_{a1}]E_{ji}=\sum_{j=2}^N( E_{aj} E_{j1}+ E_{j1} E_{aj})
+\\&=\sum_{j=2}^N( 2E_{aj} E_{j1}+ [E_{j1}, E_{aj}])=2\sum_{j=2}^N E_{aj} E_{j1}-(N-1)E_{a1}
  \end{split}
@@
 \begin{equation}
-    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{i=1}^{N}\mathcal{L}_{x,y}^{i}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{i=1}^{N}\mathcal{L}_{x,y}^{x}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
 \end{equation}
@@
 \begin{equation}
-    \mathcal{L}_{x,u}^{i}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(\bm{n})\right)
+    \mathcal{L}_{x,u}^{x}f(\bm{n})=\sum_{a,l=1}^{N}n_{a}^{x}n_{l}^{y}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{l,k=0}^{N}n_{k}^{x}\left(f(\bm{n}-\delta_{k}^{x}+\delta_{l}^{x})-f(\bm{n})\right)
+    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{l,k=0}^{N}n_{a}^{x}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{l}^{x})-f(\bm{n})\right)
 \end{equation}
@@
     \begin{split}
-\mathcal{L}_{x,y}^{i}n_{\alpha}^{x}&=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left(n_{\alpha}^{x}-\delta_{k}^{x}+\delta_{g_{i}(l)^{x}}+\delta_{g_{i}(x)}^{y}-\delta_{l}^{y}-n_{\alpha}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{y}-\sum_{c=1}^{N}n_{\alpha}^{x}n_{c}^{y}
-\\&=
-\sum_{k=2}^{N}n_{k}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{c=2}^{N}n_{\alpha}^{x}n_{c}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+\mathcal{L}_{x,y}^{x}n_{\alpha}^{x}&=\sum_{a,l=1}^{N}n_{a}^{x}n_{l}^{y}\left(n_{\alpha}^{x}-\delta_{a}^{x}+\delta_{g_{i}(l)^{x}}+\delta_{g_{i}(x)}^{y}-\delta_{l}^{y}-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{c=1}^{N}n_{\alpha}^{x}n_{c}^{y}
+\\&=
+\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{c=2}^{N}n_{\alpha}^{x}n_{c}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
 \\&=
@@
 \begin{equation}\label{DifferenceEquation}
-\mathcal{L}^{rd}n_{\alpha}^{x}=\nu\sigma_{11}\Delta_{L}n_{\alpha}^{x}+\nu\sigma_{12}\sum_{l=2\,:\,l\neq k}^{N}\Delta_{L}n_{l}^{x}+\Upsilon\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
+\mathcal{L}^{rd}n_{\alpha}^{x}=\nu\sigma_{11}\Delta_{L}n_{\alpha}^{x}+\nu\sigma_{12}\sum_{l=2\,:\,l\neq a}^{N}\Delta_{L}n_{l}^{x}+\Upsilon\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
 \end{equation}
 where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e.
-$\Delta_{L}n_{k}^{x}=n_{k}^{x+1}+n_{k}^{x-1}-2n_{k}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
+$\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
 In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
@@
 The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
-$\alpha_{k}^{x}=\alpha$, $\forall k\in \{1,\ldots,N\}$ and $x\in V$.
+$\alpha_{a}^{x}=\alpha$, $\forall k\in \{1,\ldots,N\}$ and $x\in V$.
 This measure is given by
@@
 \begin{equation}
-    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{i=1}^{N}H_{x,y}^{i}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{i=1}^{N}H_{x,y}^{x}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
 \end{equation}
@@
 \begin{equation}
-    H_{x,y}^{i}=\sum_{k,l=0}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)
+    H_{x,y}^{x}=\sum_{a,l=0}^{N}\left(E_{g_{i}(l)a}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{aa}^{x}\otimes E_{ll}^{y}\right)
 \end{equation}
@@
 \begin{equation}
-    H_{x,y}^{m}=\sum_{k,l}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)
+    H_{x,y}^{m}=\sum_{a,l}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
 \end{equation}
@@
 where the duality matrix $D$ is again \eqref{dualityMatrix}.
-Following subsection~\ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$.
-This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
+Following subsection~\ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{x}$ and with $H_{x,y}^{m}$.
+This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{x}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
 \begin{align*}
-    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{g_{i}(l)k}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{kk}^{x}\otimes E_{ll}^{y}\right)\right]
-    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left\{\left(E_{ak}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{bk}\right)-\left(E_{ak}^{x}\delta_{k0}-E_{k0}^{x}\delta_{ak}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}
+    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{g_{i}(l)a}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{aa}^{x}\otimes E_{ll}^{y}\right)\right]
+    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left\{\left(E_{aa}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{aa}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{ba}\right)-\left(E_{aa}^{x}\delta_{a0}-E_{a0}^{x}\delta_{aa}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}
     \\=&
-    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{ak}^{x}\left(\delta_{g_{i}(l)0}-\delta_{k0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{k0}^{x}\right)\delta_{ak}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
+    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{aa}^{x}\left(\delta_{g_{i}(l)0}-\delta_{a0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{a0}^{x}\right)\delta_{aa}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
     \\=&\;0
@@
 \begin{equation}
-\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{k,l=1}^{N}\left(E_{lk}^{x}\otimes \mathbbm{1}^{y}-E_{kk}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
+\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
 \end{equation}
@@
 
-\textbf{Remark}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra.
+\textbf{Remara}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra.
 Indeed, \begin{equation}\label{creationOperators}
@@
 \end{equation}
-$\forall n=(n_{1},\ldots,n_{N})\in \chi$ where $\chi:=\left\{n\;:\;\sum_{k=1}^{N}n_{k}=2j\right\}$ (let us notice that $\Omega=\xi^{|V|}$.
+$\forall n=(n_{1},\ldots,n_{N})\in \chi$ where $\chi:=\left\{n\;:\;\sum_{a=1}^{N}n_{a}=2j\right\}$ (let us notice that $\Omega=\xi^{|V|}$.
 This vector can be mapped in a one-to-one correspondence with the canonical basis of $\mathbb{C}^{D}$.
@@
 \begin{equation}
-    \langle q_{1},\ldots,q_{N}|_{x}|t_{1},\ldots,t_{N}\rangle_{x}=\prod_{k=1}^{N}\delta_{q_{k},t_{k}}
+    \langle q_{1},\ldots,q_{N}|_{x}|t_{1},\ldots,t_{N}\rangle_{x}=\prod_{a=1}^{N}\delta_{q_{a},t_{a}}
 \end{equation}
@@
 \end{equation}
-\textbf{Remark}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process.
+\textbf{Remara}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process.
 The mapping with the vectors written in \eqref{stateSpace} is the following
@@
  \begin{equation}
-	\Omega:=\left\{|n_{1},\ldots,n_{N}\rangle \;:\;\sum_{k=1}^{N}n_{k}=2j\right\}^{\otimes|V|}
+	\Omega:=\left\{|n_{1},\ldots,n_{N}\rangle \;:\;\sum_{a=1}^{N}n_{a}=2j\right\}^{\otimes|V|}
 	\end{equation}
@@
 \begin{equation}
-H_{x,y}=\sum_{k,l=1}^{N}\left(e_{kl}\otimes e_{lk}-e_{ll}\otimes e_{kk}\right)
+H_{x,y}=\sum_{a,l=1}^{N}\left(e_{al}\otimes e_{la}-e_{ll}\otimes e_{aa}\right)
  \end{equation}
@@
  \begin{equation}
-H_{x}=\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(e_{k,l}-e_{ll}\right)
+H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(e_{a,l}-e_{ll}\right)
 \end{equation}
@@
 \begin{equation}
-	H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left\{\frac{1}{2}\Delta(C_{2})-2j(4j+N)\frac{1}{2}\mathbbm{1}\otimes\mathbbm{1}\right\}+\sum_{x\in V}\Gamma_{x}\sum_{k,l=1}^{N}\alpha_{k}^{x}\left(e_{k,l}-2j\mathbbm{1}\right)
-\end{equation}
+	H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left\{\frac{1}{2}\Delta(C_{2})-2j(4j+N)\frac{1}{2}\mathbbm{1}\otimes\mathbbm{1}\right\}+\sum_{x\in V}\Gamma_{x}\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(e_{a,l}-2j\mathbbm{1}\right)
+\end{equation}

### 2023-04-03 main.tex
k

@@
 \noindent
-\textbf{Remara}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
+\textbf{Reamrk}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
 \begin{equation}
@@
 \newline
-\textbf{Remara}:
+\textbf{Reamrk}:
 when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
@@
 \newline \newline
-\textbf{Remara}: in the reversible situation, i.e.
+\textbf{Reamrk}: in the reversible situation, i.e.
 when $\forall x\in V$ $\alpha_{a}^{x}=\alpha_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
@@
 \begin{equation}\label{Rmatrix}
-    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
 \end{equation}
@@
  where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
- %\textbf{Remara}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$.
+ %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$.
 This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
@@
 \begin{equation}\label{hamiltonian}
-	H=B_{1}+H_{bula}+B_{L}
+	H=B_{1}+H_{bulk}+B_{L}
 \end{equation}
@@
 \begin{equation}
-    H_{bula}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
+    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
 \end{equation}
@@
 \newline
-\textbf{Remara}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
+\textbf{Reamrk}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
 	\begin{equation}
@@
 \begin{equation}\label{similarV}
-   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}V^{T}
+   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}\mathcal{V}^{T}
 \end{equation}
@@
 \begin{equation}\label{bbHamiltonian}
-    \mathbb{H}=\mathbb{B}_{1}+H_{bula}+\mathbb{B}_{L}
+    \mathbb{H}=\mathbb{B}_{1}+H_{bulk}+\mathbb{B}_{L}
 \end{equation}
@@
 \end{flushright}
-\subsubsection{The steady state of $\widehat{H}$}
+\subsubsection{The steady state of $\widehat{H}^{T}$}
 Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}.
@@
 \end{equation}
-\textbf{Remara}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
+\textbf{Reamrk}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
 if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations,
@@
 \end{equation}
-\textbf{Remara}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
+\textbf{Reamrk}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
 The interesting charges (we only look for the first non trivial one) take the following form
@@
 
-\textbf{Remara}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra.
+\textbf{Reamrk}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra.
 Indeed, \begin{equation}\label{creationOperators}
@@
 \end{equation}
-\textbf{Remara}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process.
+\textbf{Reamrk}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process.
 The mapping with the vectors written in \eqref{stateSpace} is the following

### 2023-04-03 main.tex
abs

@@
 \\&
-\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
+\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
   \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}
@@
 	\end{equation}
+\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as
+\begin{equation}
+	\langle n^{y_{1}}_{s_{1}},\ldots,n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(c_{k},\ldots,c_{m})
+\end{equation}
  \paragraph{Proof of formula \eqref{exactCorrelations}}
@@
 \textbf{Remark}: the one and two points correlations computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
-\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain}
+\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}
 In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{a})_{a=1,\ldots,N}$ and $(\beta_{a})_{a=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
@@
 \\=&
-\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{a}}(\bm{\xi})
+\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
 \end{split}
@@
 \begin{equation}\label{Pass}
-    a_{i_{a}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+    a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
 \end{equation}

### 2023-04-04 main.tex
abs
ii
Update main.tex

@@
  \begingroup\large \bf
-% {Rouven Frassea}
+% {Rouven Frassek}
  \par\endgroup
@@
 
-\subsection{The infinitesimal generator}
+\subsection{The process generator}
 We now give the mathematical description of the multi-species stirring process.
@@
 \subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
-In this section we show that the process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}, is dual to a process $(\bm{\xi}(t))_{t\geq 0}$ taking values in the enlarged state space
+In this section we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}.
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
 \begin{equation}\label{dualStateSpace}
@@
 \end{equation}
-where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $k\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $k\in \{2,\ldots,N\}$ at 
+where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
 the extra-site $\widehat{x}$ connected to $x\in V$.
- The  generator of the dual process is 
+
+The duality function is given by
+\begin{equation}\label{dualityElements}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
+\end{equation}
+where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
+\begin{equation}
+\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
+\end{equation}
+The dual process is defined by its generator, which reads
  \begin{equation}\label{DualGenerator}
@@
 where 
-$\mathcal{L}_{x,y}$ is defined in \eqref{siteGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+$\mathcal{L}_{x,y}$ is defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
 \begin{equation}\label{siteDualGenerator}
@@
 \end{equation}
-and the duality function is 
-\begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
-\end{equation}
-where we denote the \textit{density} of the species $k\in \{2,\ldots,N\}$ at the reservoir connected with the site $x\in V$  by 
-\begin{equation}
-\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
-\end{equation}
 \newline
-On one hand, the edge part of the dual generator \eqref{DualGenerator} is a copy of \eqref{edgeGenerator}, therefore it performs the stirring dynamics on the graph.
-On the other hand, the dual generator \eqref{siteDualGenerator} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widehat{x}$.
+Therefore the dual dynamics is described as follows.
+On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual generator gives rise to  the multi-species stirring dynamics on the graph.
+On the other hand, the site
+part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $a$ at the extra-site $\widehat{x}$.
 This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{a}^{x}$.
@@
 \newline \newline
-\textbf{Reamrk}: in the reversible situation, i.e.
-when $\forall x\in V$ $\alpha_{a}^{x}=\alpha_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, p_{1},\ldots,p_{N}\right)$ is
-\begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\sum_{x\in V}r_{a}^{x}+\sum_{x\in V}m_{a}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\textbf{Remark}: in the reversible situation, i.e.
+when $\forall x\in V$ $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
+\begin{equation}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}\right)^{\sum_{x\in V}r_{a}^{x}+\sum_{x\in V}m_{a}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 Indeed, in this formalism the proof reduces to finding symmetries and exponential transformation of generators of the Lie algebra.\\
-The configuration space  \eqref{dualStateSpace} of the dual process is the collection of vectors
+To each configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of the dual process we associate the vector
 \begin{equation}
@@
     \begin{equation}
-       \left[E, E_{bb}\right]=\sum_{a=2}^{N}\left(E_{ab}\delta_{b 1}-E_{b 1}\delta_{ab}\right)=-E_{l1}
+       \left[E, E_{bb}\right]=\sum_{a=2}^{N}\left(E_{ab}\delta_{b 1}-E_{b 1}\delta_{ab}\right)=-E_{b1}
     \end{equation}
@@
     \begin{equation}\label{HT-E1l}
-        \exp{(-E)}E_{1 b}\exp{(E)}=E_{1b}+E_{11}-\sum_{j=2}^{N}\left(E_{j1}+E_{jb}\right)
-    \end{equation}
-  \com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}
+        \exp{(-E)}E_{1 b}\exp{(E)}=E_{1b}+E_{11}-\sum_{a=2}^{N}\left(E_{a1}+E_{ab}\right)
+    \end{equation}
+  %\com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}
 
@@
     \begin{equation}
-[E,E_{1b}]=\sum_{a=2}^{N}\left(E_{ab}\delta_{11}-E_{11}\delta_{ab}\right)=\sum_{j=2}^{N}E_{jb}-E_{11};
+[E,E_{1b}]=\sum_{a=2}^{N}\left(E_{ab}\delta_{11}-E_{11}\delta_{ab}\right)= (\sum_{a=2}^{N}E_{ab} ) -E_{11};
 \end{equation}
@@
 \begin{split}
-\left[E,[E,E_{1b}]\right]&=\sum_{b=2}^{N}\sum_{j=2}^{N}\left[E_{b1},E_{jb}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
-\\&=
-\sum_{j,b=2}^{N}\left(E_{bb}\delta_{j1}-E_{j1}\delta_{bb}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
+\left[E,[E,E_{1b}]\right]&=\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1},E_{ab}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
+\\&=
+\sum_{a,b=2}^{N}\left(E_{bb}\delta_{a1}-E_{a1}\delta_{bb}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
 \\=&
--2\sum_{j=2}^{N}E_{j1};
+-2\sum_{a=2}^{N}E_{a1};
 \end{split}
@@
 Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
-\item for $A=E_{ab}$ with $k,b \in \{2,\ldots,N\}$ we obtain 
+\item for $A=E_{ab}$ with $a,b \in \{2,\ldots,N\}$ we obtain 
 \begin{equation}\label{HT-Ekl}
-    \exp{(-E)}E_{b a}\exp{(E)}=E_{ab}+E_{b 1}
+    \exp{(-E)}E_{a b}\exp{(E)}=E_{ab}+E_{a 1}
 \end{equation}
@@
 \begin{equation}
-[E,E_{b a}]=\sum_{a=2}^{N}\left(E_{aa}\delta_{b 1}-E_{b 1}\delta_{aa}\right)=-E_{b 1};
-\end{equation}
-\begin{equation}
-[E,E_{ab}]=\sum_{a=2}^{N}\left(E_{ab}\delta_{a1}-E_{a1}\delta_{b a}\right)=-E_{a1};
+[E,E_{ab}]=\sum_{c=2}^{N}\left(E_{cb}\delta_{a1}-E_{a1}\delta_{c b}\right)=-E_{a1};
 \end{equation}
@@
 \begin{equation}\label{HT-E11}
-    \exp{(-E)}E_{11}\exp{(E)}=E_{11}-\sum_{j=2}^{N}E_{j1}
+    \exp{(-E)}E_{11}\exp{(E)}=E_{11}-\sum_{a=2}^{N}E_{a1}
 \end{equation}
@@
 \begin{align*}
-[E,E_{11}]=\sum_{a=2}^{N}\left(E_{a1}\delta_{11}-E_{1 1}\delta_{a1}\right)=\sum_{j=2}^{N}E_{j1};
+[E,E_{11}]=\sum_{a=2}^{N}\left(E_{a1}\delta_{11}-E_{1 1}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1};
 \end{align*}
@@
     \begin{split}
-H_{x}^{T}=\sum_{a,l=0}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}
+H_{x}^{T}=\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}
     \end{split}
@@
 \subsection{The integrable chain and the matrix product ansatz}
-In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs are connected with the end site $1$ and $L$.
-These boundaries, exchanges particle with the external environment, putting the chain out of equilibrium.
-To use integrability is better to work with Hamiltonians.
-The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conducatances are
+In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
+These boundaries, exchanging particle with the external environment, put the chain out of equilibrium.
+The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
 \begin{equation}
@@
 We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
-We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra). \\
-The state space of the chain is 
-\begin{equation}
-    \Omega=\bigtimes_{x=1}^{L}\Omega_{x}
-\end{equation}
-where 
-\begin{equation}
-	\Omega_{x}=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle\;:\;n\in\mathbb{N}_0^N\;\;|n|=1\right\}
-\end{equation} 
+{\color{red} We will denote the element of the representation of the Lie algebra by lowercase letters, i.e.
+$e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra).} \\
 The Hamiltonian is
@@
 \end{equation}
-Moreover, for a fixed site $x\in \{1,\ldots,L\}$ we have 
+Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
 \begin{equation}
@@
 \begin{equation}
-	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}
-\end{equation} 
-such that
+	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
+\end{equation} 
+The action of $\mathcal{H}$ amounts to the permutation of the two sites, i.e.
 \begin{equation}
@@
 \begin{equation}\label{ratesConditions}
-	\sum_{a=2}^{N}\alpha_{a}=1,\qquad\sum_{a=2}^{N}\beta_{a}=1
+	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
 \end{equation} 
@@
 \begin{equation}\label{lambdaConditions}
-	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=2}^{N}\lambda_{a}=0\,.
-\end{equation}
-Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product anstz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat2017exact}).
-We recall the main points of this ansatz.
-\\
- Calling $|\mathbb{P}(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
-\begin{equation}
-    \frac{d|\mathbb{P}(t)}{dt}=H|\mathbb{P}(t)\rangle
-\end{equation}
-We define the steady state of $H$ defined in \eqref{hamiltonian} a vector, denoted by $|\Psi\rangle$ that contains the probabilities of every configuration of the chain with respect to the stationary distribution, i.e.
+	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
+\end{equation}
+Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product ansatz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat2017exact}). 
+ Calling $|{P}(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
+ the master equation
+\begin{equation}
+    \frac{d|{P}(t)\rangle}{dt}=H|{P}(t)\rangle
+\end{equation}
+We denote by $|\Psi\rangle$ that contains the probabilities of every configuration of the chain with respect to the stationary distribution, i.e.
 the probability distribution that the chain reaches when $t\to \infty$.
@@
 \end{equation}
-where $X_{a}$ for $a=1,\ldots,N$ are operators on an auxiliary space $V_{0}$ while $|V\rangle\in V_{0}$ and $\langle W|\in V_{0}^{*}$ ( where $V^{*}$ denotes the algebraic dual space), such that $\langle W|V\rangle=1$.
-$\langle W|$ and $|V\rangle$ are sometimes called boundary vectors.
-These operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
+where the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfill the commutators
 \begin{equation}\label{bula}
@@
 \newline
-\textbf{Reamrk}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}
+\textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them 
 	\begin{equation}
@@
 	\end{equation}
-	gives $0=0$. Similar computations can be done for the right boundary.
-\subsection{The exact steady state for the multi-species stirring process on a chain}\label{subsection-exact}
+	and using  \eqref{ratesConditions} and \eqref{lambdaConditions}.
+ Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations.
+\subsection{The explicit form of the steady state}\label{subsection-exact}
 We aim to find an explicit for for the steady state $|\Psi\rangle$.
-The MPA states the form of the steady state in function of an abstract algebra of operators.
+The MPA gives the steady state in terms of an abstract algebra of operators.
 If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}.
@@
 For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}.
-Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}.
-In subsection \eqref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
-This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relation simpler, and allows to find the steady state of a transformed Hamiltonian, that will be denoted by $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary.
+Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}.
+In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
+This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary.
 Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}.
@@
 \\&
-\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
-  \prod_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}
+\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
+  \prod_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
  \\ &
- \beta_{s_{x}}^{(1-c_{i})(1-\delta_{s_{x},1})}
+ \beta_{s_{x}}^{(1-c_{x})(1-\delta_{s_{x},1})}
  \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
@@
 \end{equation}
-\textbf{Reamrk}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
+\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
 if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations,
@@
     \begin{split}
-  &\widehat{\Psi}(\ldots,a_{i},\ldots,d_{q_{r}},\ldots)=\sum_{i=1\,:\, i\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
+  &\widehat{\Psi}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
 \\&  
-\prod_{i=1\,:\, i\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\beta_{s_{x}}^{(1-c_{i})(1-\delta_{s_{x},1})}
+\prod_{i=x\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{s_{x}}^{(1-c_{x})(1-\delta_{s_{x},1})}
 \\&
@@
 \begin{equation}\label{exactCorrelations}
-		\langle n^{y_{1}}_{s_{1}},\ldots,n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-			f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{m})
+		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+			f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(y_{k},c_{k},\ldots,c_{m})
 	\end{equation}
@@
 	\begin{equation}\label{powerCoeffSpecies}
-		g_{k}(c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
+		g_{k}(y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
 	\end{equation}
@@
 	\end{equation}
-\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as
-\begin{equation}
-	\langle n^{y_{1}}_{s_{1}},\ldots,n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(c_{k},\ldots,c_{m})
+\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as {\color{red}{add (-1)}}
+\begin{equation}
+	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
 \end{equation}
@@
 	\begin{split}
-	\langle n_{s_{1}}^{x},n_{s_{2}}^{y}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},c_{2})
+	\langle n_{s_{1}}^{x}n_{s_{2}}^{y}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},c_{2})
 	\end{split}
@@
 	\begin{split}
-	\langle n_{s_{1}}^{x},n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+	\langle n_{s_{1}}^{x} n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
 	\end{split}
@@
 \begin{equation}
-    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}},n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{3})
+    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{3})
 \end{equation}
@@
     \begin{split}
-        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}},n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\prod_{k=1}^{3}\beta_{s_{k}}+\sum_{k=1}^{3}\frac{(L-y_{k})}{(L+1)}(\alpha_{s_{k}}-\beta_{s_{k}})\prod_{q=1\,:\,q\neq k}^{3}\beta_{s_{q}}
+        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\prod_{k=1}^{3}\beta_{s_{k}}+\sum_{k=1}^{3}\frac{(L-y_{k})}{(L+1)}(\alpha_{s_{k}}-\beta_{s_{k}})\prod_{q=1\,:\,q\neq k}^{3}\beta_{s_{q}}
         \\&+

### 2023-04-05 main.tex
i

@@
 \end{flushright}
-\paragraph{Proof of \eqref{edgeDualRealtion}.}To show \eqref{edgeDualRealtion} we need two 'ingredients'.
-First the existence of a similarity transformation between the Hamiltonian $H_{x,y}$ defined in \eqref{edgeHamiltonian} and its transposed.
-As we will show, this similarity transformation is $R_{x}$ defined in \eqref{Rmatrix}.
-Second, the possibility of finding a symmetry for the Hamiltonian \eqref{edgeHamiltonian}.
-Exploiting the fact that $H_{x,y}$ is a linear function of the coproduct of the second Casimir of $gl(N)$, (see \eqref{hamiltonianCasimir}) this symmetry is $\exp{(E^{x})}\exp{(E^{y})}$ with $E^{x}$ defined in \eqref{EquationEx}.
-\\
-Equation \eqref{transpositionPropertyR} implies that 
+\paragraph{Proof of \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'.
+First the existence of a similarity transformation between the Hamiltonian $H_{x,y}$  and its transposed.
+As we will show, this similarity transformation is $R_{x}R_{y}$.
+Second, the possibility of finding a symmetry for the edge Hamiltonian.
+Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$.
+As we will see, this symmetry is $\sum_{a=2}^{N}E_{a1}$ \\
+Using \eqref{transpositionPropertyR} we obtain
+
 \begin{equation}\label{transpositionPropertyH}
@@
 \end{equation}
-As a consequence of \eqref{hamiltonianCasimir} we look for a symmetry of  $\Delta(C_{2})$.
-
-%We now search for a symmetry of $H_{x,y}$. % Given $A,B\in gl(N)$, we say that $A$ is a symmetry of $B$ if 
-%\begin{equation}
-%    [A,B]=0
-%\end{equation}
-Since the coproduct is a Lie algebra homomorphism we have that $\forall A,B\in gl(N)$
+therefore we have found the symilarity tranfsormation between $H_{x,y}$ and its transposed. \\
+As already pointed out, $H_{x,y}$ is a linear function of $\Delta(C_{2})$.
+This implies that symmetries of  $\Delta(C_{2})$ are also symmetries of  $H_{x,y}$.
+Moreover, the coproduct is a Lie algebra homomorphism, i.e.
+$\forall A,B\in gl(N)$
 \begin{equation}\label{symmetryCoproduct}
@@
 \end{equation}
-%Since $H_{x,y}$ is a linear function of the coproduct of the second Casimir, as a consequence of \eqref{symmetryCoproduct}, it is enough to identify a symmetry of $C_{2}$. But
- $C_{2}$ is in the center of $gl(N)$, and therefore it commutes with all the element of the the algebra. Considering 
+This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of $gl(N)$, and therefore it commutes with all the element of this algebra. Consider
 \begin{equation}\label{equationE}
@@
 \end{equation}
-to obtain a product structure of the elements \eqref{dualityElements} of the duality matrix, we chose as a symmetry 
+To obtain a product structure of the elements of the duality matrix, we introduce
 \begin{equation}
@@
 \end{equation}
-%Since $[C_{2},E]=0$, we have that 
-%\begin{equation}\label{commutationSC}
-    %\left[S,\Delta(C_{2})\right]=0
-%\end{equation}
-For fixed $(x,y)\in \mathcal{E}$ we introduce
+Finally, for fixed $(x,y)\in \mathcal{E}$, we define
 \begin{equation}
@@
 \end{equation}
-where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence of \eqref{symmetryCoproduct}, we have that 
+where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. This operator $S^{x,y}$ satisfies
 \begin{equation}\label{symmetryH}
@@
 \end{equation}
-i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Finally, we obtain that 
+i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write
 \begin{equation}
@@
  \end{equation}
-In the followin we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
+In the following we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
 \begin{enumerate}
@@
 \begin{split}
-\left[E,[E,E_{1b}]\right]&=\sum_{b=2}^{N}\sum_{a=2}^{N}\left[E_{b1},E_{ab}\right]-\sum_{b=2}^{N}\left[E_{b1},E_{11}\right]
-\\&=
-\sum_{a,b=2}^{N}\left(E_{bb}\delta_{a1}-E_{a1}\delta_{bb}\right)-\sum_{b=2}^{N}\left(E_{b1}\delta_{11}-E_{11}\delta_{b1}\right)
+\left[E,[E,E_{1b}]\right]&=\sum_{c=2}^{N}\sum_{a=2}^{N}\left[E_{c1},E_{ab}\right]-\sum_{c=2}^{N}\left[E_{c1},E_{11}\right]
+\\&=
+\sum_{a,c=2}^{N}\left(E_{cb}\delta_{a1}-E_{a1}\delta_{cb}\right)-\sum_{c=2}^{N}\left(E_{c1}\delta_{11}-E_{11}\delta_{c1}\right)
 \\=&

### 2023-04-05 main.tex
t

@@
 \usepackage{comment}
+\usepackage{mathtools}
 \numberwithin{equation}{section}
@@
 where
-\begin{equation}
+\begin{equation}\label{bulkElementDualityMatrix}
 d_{x}=R_{x}\exp{(E^{x})}
@@
 \end{equation}
+In this setting the extra-sites are denoted by $0$ and $L+1$, since connected with sites $1$ and $L$ of the chain respectively.
+Moreover, the matrix $R_{x}$ reduces to the identity.
+Therefore, the duality matrix reads as
+\begin{equation}
+	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{E^{x}}\otimes \mathcal{D}_{L+1}
+\end{equation}
+and the dual Hamiltonian 
+\begin{equation}
+	\widetilde{H}=H_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{L+1}
+\end{equation}
+with the operators \eqref{edgeHamiltonian} and \eqref{siteDualHamiltonian}.
+In the long-time horizon, the dual process voids the chain, and all particles are eventually absorbed at extra-site $0$ or $L+1$.
+\\
 Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product ansatz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat2017exact}). 
@@
 \begin{equation}
-    \frac{d|{P}(t)\rangle}{dt}=H|{P}(t)\rangle
-\end{equation}
-We denote by $|\Psi\rangle$ that contains the probabilities of every configuration of the chain with respect to the stationary distribution, i.e.
-the probability distribution that the chain reaches when $t\to \infty$.
-We observe that, since the Markov chain with Hamiltonian \eqref{hamiltonian} is positive recurrent there exists a unique stationary distribution and, moreover, this is distribution is reached when $t\to \infty$ starting for every arbitrary initial distribution.
- Therefore, to find the stationary state, we aim to compute $|\Psi\rangle$ such that 
+    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle
+\end{equation}
+This Markov chain is positive recurrent, therefore there exist a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial distribution. 
+We denote by $|\Psi\rangle$ the column vector that contains the probabilities of every configuration of the chain with respect to this unique stationary distribution.
+This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e.
+it solves
 \begin{equation}
@@
 where the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfill the commutators
-\begin{equation}\label{bula}
+\begin{equation}\label{bulk}
 	\left[X_{a},X_{b}\right]=\lambda_{a}X_{b}-\lambda_{b}X_{a}\qquad\forall a,b=1,\ldots,N
@@
 \subsection{The explicit form of the steady state}\label{subsection-exact}
-We aim to find an explicit for for the steady state $|\Psi\rangle$.
+As pointed already pointed out, the MPA gives an abstract form of the steady state, in terms of an algebra of operators.
+However, to write explicitly the steady state one should know a representation of this algebra.
+Another approach is to directly use the commutators and figure out correlations from them.
+This path has been followed in \cite{vanicat2017exact} to compute one and two points correlations.
+However, it is interesting to put effort in this direction and look for explicit form of arbitrary correlations.
+We will carry out this aim by the use of duality, proved in Section \ref{sectionDuality}.
+The idea is summarized in the following.
+We define a sequence of similarity transformation such that
+\begin{equation}
+	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}
+\end{equation} 
+where $S_{1}$ makes $H^{'}$ with both diagonal boundaries and $S_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one.
+Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\widetilde{\Psi}\rangle$ of $H^{''}$ will be written explicitly.
+Then, reversing the transformations we will retrieve $|\Psi\rangle$.
+The first transformation $S_{1}$ is closely related to the dual matrix.
+Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
+Therefore, $H^{'}$ is not stochastic.
+This informally explains the role of duality.
+The second transformation $S_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs.
+\\
+This idea is exposed as follows.
+We first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
+Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators.
+Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.
+
+\begin{comment}
+{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$.
 The MPA gives the steady state in terms of an abstract algebra of operators.
@@
 A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}.
-Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.
-\com{clarify}
-\subsubsection{The similarity transformation}
-We aim to construct a similarity transformation that maps the Hamiltonian \eqref{hamiltonian} into an other $\mathbb{H}$ that has left boundary lower-triangular and right boundary diagonal.
-Consider the transformation
+Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
+\end{comment}
+\subsubsection{The similarity transformation}\label{subsectionSTransf}
+We introduce the first transformation as
 \begin{equation}\label{transformationV}
- V:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{a1}
-\end{equation}
-Observe that it is the the duality matrix at site $x\in \{1,\ldots,L\}$ up to the multiplication by $R_{x}$. By taking the tensor product over the chain we define
-\begin{equation}
-    \mathcal{V}=V^{\otimes L}
-\end{equation}
- This matrix $\mathcal{V}$ is invertible and we introduce 
+ S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+\end{equation}
+Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
+By taking the tensor product over the chain we define
+\begin{equation}
+    \mathcal{S}_{1}=S_{1}^{\otimes L}
+\end{equation}
+that is related with the duality matrix by 
+\begin{equation}
+\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
+\end{equation}
+ This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
 \begin{equation}\label{hatHamiltonian}
-    \widehat{H}:=\widehat{B}_{1}+\mathcal{H}+\widehat{B}_{L}
-\end{equation}
-such that 
+   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
+\end{equation}
+that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
 \begin{equation}\label{similarV}
-   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}\mathcal{V}^{T}
-\end{equation}
+   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
+\end{equation}
+The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
+\begin{equation}
+	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
+\end{equation}
+Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
+The steady state $|\widehat{\Psi}\rangle$ of $H^{'}$ fulfils the equations
+\begin{equation}
+	H^{'}|\widehat{\Psi}\rangle=0
+\end{equation}
+therefore, it is easy to see that 
+\begin{equation}
+	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\widehat{\Psi}\rangle
+\end{equation}
+
+ We introduce the second transformation as 
+ \begin{equation}
+ 	S_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
+ \end{equation}
+
 Using \eqref{transformationV} we introduce the \textit{similarity transformation} 
@@
 Finally, using the transformation $\mathcal{V}$ we will find $|\Psi\rangle$.
-\subsubsection{The steady state of $\mathbb{H}$}
+\subsubsection{The steady state of $\mathbb{H}$}\label{subsectionSSHsec}
 We state the following result. The steady state of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 
@@
 \end{flushright}
-\subsubsection{The steady state of $\widehat{H}^{T}$}
+\subsubsection{The steady state of $\widehat{H}^{T}$}\label{subsectionSSdual}
 Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}.
@@
 \end{flushright}
-\subsubsection{The steady state of $H$}
+\subsubsection{The steady state of $H$}\label{subsectionSSH}
 The steady state $|\Psi\rangle$ of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 

### 2023-04-05 main.tex
i

@@
 \usepackage{mathtools}
+\usepackage{array}
 \numberwithin{equation}{section}
@@
 \begin{equation}
-	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}
-\end{equation} 
-where $S_{1}$ makes $H^{'}$ with both diagonal boundaries and $S_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one.
-Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\widetilde{\Psi}\rangle$ of $H^{''}$ will be written explicitly.
-Then, reversing the transformations we will retrieve $|\Psi\rangle$.
-The first transformation $S_{1}$ is closely related to the dual matrix.
+	H\;\xrightarrow{\mathcal{S}_{1}}\;H^{'}\;\xrightarrow{\mathcal{S}_{2}}\;H^{''}
+\end{equation} 
+where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one.
+Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly.
+Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$.
+The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix.
 Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
@@
 This informally explains the role of duality.
-The second transformation $S_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs.
+The second transformation $\mathcal{S}_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs.
 \\
 This idea is exposed as follows.
-We first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
+We first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$.
 Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators.
@@
 Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
-The steady state $|\widehat{\Psi}\rangle$ of $H^{'}$ fulfils the equations
-\begin{equation}
-	H^{'}|\widehat{\Psi}\rangle=0
+The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
+\begin{equation}
+	H^{'}|\Psi^{'}\rangle=0
 \end{equation}
@@
 \begin{equation}
-	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\widehat{\Psi}\rangle
+	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
 \end{equation}
@@
  \end{equation}
-
+By taking the tensor product over the chain we also define
+\begin{equation}
+	\mathcal{S}_{2}=S_{2}^{\otimes L}
+\end{equation}
+Using $\mathcal{S}$ we introduce 
+\begin{equation}
+	H^{''}=B_{1}^{''}+H_{bulk}+B_{L}^{''}
+\end{equation}
+that is similar to $H^{'}$ by $S_{2}$, i.e.
+\begin{equation}
+	H^{'}=\mathcal{S}_{2}^{-1}H^{''}\mathcal{S}_{2}
+\end{equation}
+The boundary Hamiltonians are the following 
+\begin{equation}
+	B_{1}^{''}=e_{11}-\mathbbm{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}\qquad B_{L}^{''}=e_{11}-\mathbbm{1}
+\end{equation}
+i.e. the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal. 
+The steady state of $|\Psi^{''}\rangle$ of $H^{''}$ solves 
+\begin{equation}
+	H^{''}|\Psi^{''}\rangle=0
+\end{equation}
+and it is related to $|\Psi^{'}\rangle$ by 
+\begin{equation}
+	|\Psi^{'}\rangle = \mathcal{S}_{2}^{-1}|\Psi^{''}\rangle
+\end{equation}
+It is convenient to introduce also the similarity between $H$ and $H^{''}$, such that
+\begin{equation}
+H=\mathcal{S}^{-1}H^{''}\mathcal{S}
+\end{equation}
+where 
+\begin{equation}\label{similarity}
+	S=S_{2}S_{1}=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}
+\end{equation}
+and 
+\begin{equation}
+	\mathcal{S}=S^{\otimes L}
+\end{equation}
+This transformation connect the steady states of $H$ and $H^{''}$ by 
+\begin{equation}
+	|\Psi\rangle=\mathcal{S}^{-1}|\Psi^{''}\rangle
+\end{equation}
+\begin{comment}
 Using \eqref{transformationV} we introduce the \textit{similarity transformation} 
@@
 Finally, using the transformation $\mathcal{V}$ we will find $|\Psi\rangle$.
-\subsubsection{The steady state of $\mathbb{H}$}\label{subsectionSSHsec}
-We state the following result. The steady state of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 
+\end{comment}
+\subsubsection{The steady state of $J^{''}$}\label{subsectionSSHsec}
+We state the following result. The steady state of the Hamiltonian $H^{''}$ is given by 
 \begin{equation}\label{ResulsBasis}
-	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}|\mathbf{\bm{s}}\rangle
+	|\Psi^{''} \rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}|\mathbf{\bm{s}}\rangle
 \end{equation}
@@
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
-To prove \eqref{ResulsBasis} we will consider the vector composed by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we will act on it with the similarity transformation \eqref{similarity} obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators than \eqref{bula} and simpler actions than \eqref{leftBoundary} and \eqref{rightBoundary}.
-This will allow to write explicitly the steady state \eqref{ResulsBasis}.
+To prove \eqref{ResulsBasis} we consider the vector with elements the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators.
 For the sake of notation, we denote by 
@@
 \end{equation}
-We obtain the new operators of the MPA that by transforming the original one by \eqref{similarity} 
+We obtain the new operators of the MPA that by transforming the original one by $S$
 \begin{equation}\label{Xtildes2b}
@@
 \end{equation}
-Summing over $b\in \{1,\ldots,N\}$ in \eqref{bula} we have
+Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have
 \begin{equation} 
@@
 \end{equation}
-Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$ on the boundary vectors are given by 
+Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{2,\ldots,N\}$ on the boundary vectors are given by 
 \begin{equation}\label{commLEFT}
@@
 \end{equation} 
-The vector $|\widetilde{\Psi}\rangle$ is written as:
+The vector $|\Psi^{''}\rangle$ is written as:
 \begin{equation}\label{toDetermineTilde}
-	|\widetilde{\Psi}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 	|V \rangle \,|\mathbf{n}\rangle
@@
 such that for each site $x\in \{1,\ldots,L\}$ $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
-We also observe that the vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
 To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{x}}
@@
 \end{equation}
-Fixing $ a\in \{2,\ldots,N\}$ and $\forall b,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
+Fixing $ a\in \{2,\ldots,N\}$ and for arbitrary $ \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
 \begin{align*}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{b}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{b-1}
-	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{b-1}
+	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
+	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{\ell-1}
 	\\&=
-	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}
+	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}
 	\\&=\ldots\\&=
-	\widetilde{X}_{1}^{b}\left(\widetilde{X}_{a}+b\lambda_{a}\right)^{n}
+	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
 \end{align*}
@@
 \end{align*}
-To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$.
-Calling $\sum_{i=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
+To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$.
+Calling $\sum_{x=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
 \begin{align*}
@@
 \end{flushright}
-\subsubsection{The steady state of $\widehat{H}^{T}$}\label{subsectionSSdual}
+\subsubsection{The steady state of $H^{'}$}\label{subsectionSSdual}
 Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}.
@@
 \begin{equation}\label{ABS-vect}
-    |\widehat{\Psi}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\widehat{\Psi}(\bm{s})|\bm{s}\rangle 
+    |\Psi^{'}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi^{'}(\bm{s})|\bm{s}\rangle 
 \end{equation}
@@
 		\begin{split}
-			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
 		\end{split}
@@
 \end{equation}
-\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{T}^{T}$ acts on the vector $|\widetilde{\Psi}\rangle$.
-The matrix $T^{T}$ is given by
-\begin{equation}
-    T^{T}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}
+\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+The matrix $S_{2}^{-1}$, acting on a single site, is given by
+\begin{equation}
+   S_{2}^{-1}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
@@
     \begin{equation}
-        T^{T}=\sum_{s_{1}=1}^{N}e_{i}^{x}+Q
+        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{i}^{x}+Q
     \end{equation}
@@
     \begin{split}
-        	T^{T}\otimes T^{T}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
+        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
          \\&=
@@
 \end{equation}
-The matrix $T^{T}\otimes T^{T}$ has elements $\left\{\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2},q_{1},q_{2}\in \{1,\ldots,N\}}$, where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column.
-We fix a raw of this matrix with arbitrary index $s_{1},s_{2}$
-\begin{equation}
-	\left(T^{T}\otimes T^{T}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
-\end{equation}
-Iterating this tensor product for the chain of length $L$, we write the raw with indices $\bm{s}=s_{1},\ldots,s_{L}$
- of the matrix $\mathcal{T}^{T}$ as 
-\begin{equation}
-	\begin{split}
-		\mathcal{T}^{T}_{\bm{s}}&=\left(T^{T}\right)^{\otimes L}_{s_{1},\ldots,s_{L}}=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{N}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
+The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
+\begin{equation}
+	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
+\end{equation}
+where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $s_{1},s_{2}$ reads
+\begin{equation}
+	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
+\end{equation}
+We iterate this tensor product for the chain of length $L$, and we write the raw with indices arbitrary $\bm{s}=s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$ as
+\begin{equation}
+	\begin{split}
+	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{N}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
   \\&+
@@
 \end{equation}
-The product $\mathcal{T}^{T}|\widetilde{\Psi}\rangle$ gives a vector whose component are denoted by $\widehat{\Psi}(\bm{s})$ that are given by 
+The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$ that are given by 
 \begin{equation}\label{ABS_intermediate}
 	\begin{split}
-		\widehat{\Psi}(\mathbf{s})&=\mathcal{T}^{T}_{\bm{s}}|\widetilde{\Psi}\rangle\\&= \widetilde{\Psi}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\widetilde{\Psi}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\widetilde{\Psi}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
+		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
 	\end{split}
@@
     \begin{equation}
-	\widetilde{\Psi}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
-\end{equation}
-Because of the exponent $(1-\delta_{s_{x},1})$, the element $\widetilde{\Psi}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
+\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
+\end{equation}
+Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
@@
 	\begin{split}
-		\widehat{\Psi}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
+		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
 	\end{split}

### 2023-04-05 main.tex
ii

@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{a}^{x}$ denotes the number of particles of species $k\in \{1,\ldots,N\}$ at site $x\in V$.
+At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$ at site $x\in V$.
 On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$.
@@
 \end{equation}
-when for any $k\in\{1,\ldots,N\}$
+when for any $a\in\{1,\ldots,N\}$
 \begin{equation}\label{reversibilityCondition}
@@
 Here we introduced bosonic creation operator $a^{\dagger}$ acting as $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(a^{\dagger})_{a}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $k\in\{2,\ldots,N\}$. \\
+$(a^{\dagger})_{a}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $a\in\{2,\ldots,N\}$. \\
 We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} where the duality matrix $D$ is described as 
@@
  where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
- %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$.
+ %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $a\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$.
 This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
@@
 \end{equation}
-Recalling the action of the bosonic creation operator acting at site $\widehat{x}$ and on the species $k\in \{2,\ldots,N\}$ we have that 
+Recalling the action of the bosonic creation operator acting at site $\widehat{x}$ and on the species $a\in \{2,\ldots,N\}$ we have that 
 \begin{equation}\label{bosonicKX}
@@
 \end{equation}
-Using \eqref{bosonicKX} by a fixed $k\in \{2,\ldots,N\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{1a}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+Using \eqref{bosonicKX} by a fixed $a\in \{2,\ldots,N\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{1a}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
 \begin{equation}
@@
 \begin{equation}
-	\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}
+	\frac{\Gamma(2+\sum_{x=1}^{L}n_{1}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}
 \end{equation}
@@
     \begin{equation}
-        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{i}^{x}+Q
+        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+Q
     \end{equation}
@@
 	\begin{split}
-	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{N}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
+	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
   \\&+
@@
 where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $k\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
 We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{s_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
@@
 where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e.
-$\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall k\in \{2,\ldots,N\}$.
+$\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall a\in \{2,\ldots,N\}$.
 In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
@@
 The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
-$\alpha_{a}^{x}=\alpha$, $\forall k\in \{1,\ldots,N\}$ and $x\in V$.
+$\alpha_{a}^{x}=\alpha$, $\forall a\in \{1,\ldots,N\}$ and $x\in V$.
 This measure is given by

### 2023-04-06 main.tex
i

@@
 therefore, it is easy to see that 
-\begin{equation}
+\begin{equation}\label{S1-Inverse}
 	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
@@
 and it is related to $|\Psi^{'}\rangle$ by 
-\begin{equation}
+\begin{equation}\label{S2-Inverse}
 	|\Psi^{'}\rangle = \mathcal{S}_{2}^{-1}|\Psi^{''}\rangle
@@
 \end{comment}
-\subsubsection{The steady state of $J^{''}$}\label{subsectionSSHsec}
+\subsubsection{The steady state of $H^{''}$}\label{subsectionSSHsec}
 We state the following result. The steady state of the Hamiltonian $H^{''}$ is given by 
@@
 \subsubsection{The steady state of $H^{'}$}\label{subsectionSSdual}
-Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}.
-The result is the following
+Knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
 \begin{equation}\label{ABS-vect}
@@
 		\begin{split}
-			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
 		\end{split}
@@
 \end{equation}
-\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{SteadyStateHatTilde}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
 The matrix $S_{2}^{-1}$, acting on a single site, is given by
@@
     that can be generalized for $e_{s_{1},\ldots,s_{L}}^{q_{1},\ldots,q_{L}}$ with $s_{1},\ldots,s_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that
+
+    \begin{equation}\label{InverseS2}
+    	\begin{split}
+    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    		\\&+\left.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
+    		\\&+\left.
+    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
+    		\right. \\&+ \left. 
+    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
+    	\end{split}
+    \end{equation}
+    We prove it by induction. When $L=1$ it is true, indeed
+    \begin{equation}
+    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
+    \end{equation}
+    Assuming that \eqref{InverseS2} is true for $L$, we prove that it holds for $L+1$
+\begin{align*}
+    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    	\\&+\left.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
+    	\\&+\left.
+    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
+    	\right. \\&+ \left. 
+    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
+    	\\&=
+    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right.
+    	\\&+\left.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
+    	\\&+\left.
+    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
+    	\right. \\&+ \left. 
+    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
+    	\\&=
+    	\left(S_{2}^{\otimes L+1}\right)^{-1}
+\end{align*}
+    \begin{comment}
+
     \begin{equation}
@@
 \end{equation}
-We iterate this tensor product for the chain of length $L$, and we write the raw with indices arbitrary $\bm{s}=s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$ as
+\end{comment}
+The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$. 
+To find this elements we need to fix the rows correspondent to $\bm{s}$. Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
 \begin{equation}
@@
 \end{equation}
-The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$ that are given by 
+
+Therefore, we have that 
 \begin{equation}\label{ABS_intermediate}
@@
     \begin{equation}
-\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
-\end{equation}
-Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(1+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
+\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
+\end{equation}
+Introducing
+\begin{equation}
+	c_{x}=(1-\delta_{s_{x},1}) \qquad \forall x\in \{1,\ldots L\}
+\end{equation}
+and replacing $\Psi^{'}(\bm{s})$ compute above in \eqref{ABS_intermediate} we obtain
+
+%Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
@@
 	\begin{split}
-		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
-	\end{split}
-\end{equation} 
-Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
-Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS}.
+		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
+	\end{split}
+\end{equation} 
+%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
+Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS-vect}.
 \begin{flushright}
@@
 \subsubsection{The steady state of $H$}\label{subsectionSSH}
-The steady state $|\Psi\rangle$ of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 
+The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
 \begin{equation}\label{steadyStateH}
@@
 \end{equation}
-\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e.
-if $s_{x}\neq 1$ $\forall i\in \{1,\ldots,L\}$, then the second addend vanishes and, for these particular configurations,
+\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
 \begin{equation}\label{LinkABS-corr}
-\Psi(\bm{s})=\widehat{\Psi}(\bm{s})
-\end{equation}
-
-\paragraph{Proof of formula \eqref{steadyStateH}} To find $|\Psi\rangle$ we will use \eqref{SteadystateHat}. For the sake of notation we call
+\Psi(\bm{s})=\Psi^{'}(\bm{s})
+\end{equation}
+When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
+
+\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+The matrix $S_{2}^{-1}$, acting on a single site, is given by
+\begin{equation}\label{S1-L1}
+	S_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+\end{equation}
+Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
+\begin{equation}
+	\begin{split}
+		\mathcal{S}_{1}^{-1}=\left(S_{1}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
+		\\&
+		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+	\end{split}
+\end{equation}
+where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+\\
+This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for $L$ and we prove that it holds for $L+1$. 
+\begin{align*}
+\left(S_{1}^{\otimes L}\right)^{-1}\otimes S_{1}^{-1}&=
+\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
+\\&+\left.
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+\\&\otimes
+\left\{ \sum_{s_{1}=1}^{N}e_{s_{L+1}}^{s_{L+1}}+(-1)\delta_{s_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
+\\&=
+\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+1}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}\right.
+\\&+\left.
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+\end{align*}
+\begin{comment}
+
 \begin{equation}
@@
 \\
-Multiplying the raw with indices $s_{1},\ldots,s_{L}$ of the matrix $\mathcal{F}$ by the vector $|\widehat{\Psi}\rangle$ we obtain 
-\begin{equation}
-    \begin{split}
-        \mathcal{F}_{s_{1},\ldots,s_{L}}|\widehat{\Psi}\rangle&=\widehat{\Psi}(s_{1},\ldots,s_{L})+ 
+\end{comment}
+The product $\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{s})$. 
+To find this elements we need to fix the rows correspondent to $\bm{s}$. Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
+\begin{equation}
+    \begin{split}
+        \mathcal{S}_{1}^{-1}{\bm{s}}|\Psi{'}\rangle&=\Psi{'}(s_{1},\ldots,s_{L})+ 
         \\&
-        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}\widehat{\Psi}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)
-    \end{split}
-\end{equation}
-where $\widehat{\Psi}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\widehat{\Psi}(s_{1},\ldots,s_{L})$ where the occupations  $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)
+    \end{split}
+\end{equation}
+where $\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(s_{1},\ldots,s_{L})$ where the occupations  $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
 Using \eqref{elementsABS} we have
@@
     \begin{split}
-  &\widehat{\Psi}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
+  &\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
 \\&  

### 2023-04-06 main.tex
i

@@
 	\end{equation}
-\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as {\color{red}{add (-1)}}
-\begin{equation}
-	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
-\end{equation}
+\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as 
+\begin{equation}
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+f(c_{1},\ldots,c_{m})f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(y_{q},c_{q},\ldots,c_{m})
+\end{equation}
+%\begin{equation}
+%	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
+%\end{equation}
  \paragraph{Proof of formula \eqref{exactCorrelations}}
@@
 	\begin{split}
-		\langle n_{s_{1}}^{y_{1}},\ldots, n_{s_{m}}^{y_{m}}\rangle_{\text{stat}}&
+		\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{\text{stat}}&
 		=\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)
@@
 where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This probability \eqref{Prob-m} can be seen as the component \eqref{steadyStateH-coeff} of the stationary state \eqref{steadyStateH} of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e.
+This probability \eqref{Prob-m} $\Psi(\bm{s})$ of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e. 
 \begin{equation}
@@
 \begin{equation}\label{Corr-mABS}
-	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})
-\end{equation}
-Thus, by applying the formula \eqref{ABS_intermediate} we have 
-\begin{equation}
-	\widehat{\Psi}_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-By using the relation \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we have the equations for arbitrary correlations.
+	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\Psi^{'}_{\bm{y}}(s_{1},\ldots,s_{m})
+\end{equation}
+Thus, by applying \eqref{ABS_intermediate} we have 
+\begin{equation}
+	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+Introducing $f(c_{1},\ldots,c_{m})$ and $g_{a}(y_{a},c_{a},\ldots,c_{m})$ we have the formulas for arbitrary correlations.
 \begin{flushright}
@@
 Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{equation}
+	\begin{split}
+	\langle n_{s_{1}}^{x} n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+	\end{split}
+\end{equation}
+Therefore, we obtain the second cumulant, i.e. the second truncated correlation as 
 \begin{equation}\label{two-pts-corr}
 	\begin{split}
-	\langle n_{s_{1}}^{x} n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+		\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
 	\end{split}
@@
 Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
-\begin{equation}\label{three-pts-corr}
-    \begin{split}
-        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\prod_{k=1}^{3}\beta_{s_{k}}+\sum_{k=1}^{3}\frac{(L-y_{k})}{(L+1)}(\alpha_{s_{k}}-\beta_{s_{k}})\prod_{q=1\,:\,q\neq k}^{3}\beta_{s_{q}}
-        \\&+
+\begin{align}\label{three-pts-corr}
+        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
+        \\&+\nonumber
+        \frac{(L-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
+        \\&+\nonumber
         \frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
-        \\&+
+        \\&+\nonumber
         \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
-        \\&+
+        \\&+\nonumber
         \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
-        \\&+
-        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}\prod_{k=1}^{3}(\alpha_{s_{k}}-\beta_{s_{k}})
-    \end{split}
-\end{equation}
-\textbf{Remark}: the one and two points correlations computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
+        \\&+\nonumber
+        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
+\end{align}
+\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
 \subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}

### 2023-04-06 main.tex
ii

@@
 \section{Multi-species stirring process with reaction}
-\subsection{Duality for a reaction diffusion process}
-In \cite{casini2022uphill}, a two-species hard-core reaction diffusion process has been introduced.
-The feature of this process is that its action on the occupation variable of any species gives a difference-differential equation where both discrete Laplacians and a linear reaction term are present (multiplied for proper constants).
-In this subsection we write a generalization to $N\in \mathbb{N}$ species with arbitrary maximal occupation per site, again called $\nu\in\mathbb{N}_{0}$.
-The generator reads as follows
+In \cite{casini2022uphill} it has been defined a process whose average occupation evolution equation are given by two Laplacians and a linear reaction term (mutation).
+This model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one.
+For the lattice $\mathbb{Z}$, self-duality has been showed.
+In view of what have been proved in the previous section of this work, some questions arise naturally:
+\begin{enumerate}
+	\item Is it possible to extend this last duality result to the boundary-driven case in order to have an absorbing dual process?
+	\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
+	\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
+\end{enumerate}
+The aim of this section is to give an answer to these questions. 
+\subsection{Linear reaction-diffusion process with coupled discrete Laplacians}
+Considering again a connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
 \begin{equation}\label{RDGenerator}
@@
 \begin{equation}
-    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{i=1}^{N}\mathcal{L}_{x,y}^{x}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
-\end{equation}
-with $\mathcal{L}_{x,y}$ and $\mathcal{L}_{x}$ are the generators the generator \eqref{edgeGenerator} and \eqref{siteGenerator} respectively and, for any function $f:\Omega\to \mathbb{R}$
-\begin{equation}
-    \mathcal{L}_{x,u}^{x}f(\bm{n})=\sum_{a,l=1}^{N}n_{a}^{x}n_{l}^{y}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{g_{i}(l)}^{x}+\delta_{g_{i}(k)}^{y}-\delta_{l}^{y})-f(\bm{n})\right)
+    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+\end{equation}
+with $\mathcal{L}_{x,y}$ is the generator the generator \eqref{edgeGenerator} and, for any function $f:\Omega\to \mathbb{R}$
+\begin{equation}
+    \mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-    g_{i}(k)=\begin{cases}
-    k+i \quad &\text{if}\quad k+i\leq N\\
-    k+i-N\quad &\text{if}\quad k+i>N\\
-    0\quad &\text{if}\quad k=0
-\end{cases}
+    g_{c}(k)=\begin{cases}
+    k+c \quad &\text{if}\quad k+c\leq N\\
+    k+c-N\quad &\text{if}\quad k+c>N\\
+    1\quad &\text{if}\quad k=1
+\end{cases}\qquad \forall k\in \{1,\ldots N\}
 \end{equation}
@@
 \begin{equation}
-    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{l,k=0}^{N}n_{a}^{x}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{l}^{x})-f(\bm{n})\right)
-\end{equation}
-the action on the occupation variable $n_{\alpha}^{x}$ of particle type $\alpha\in \{2,\ldots,N\}$ at site $x\in V $
+    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x})-f(\bm{n})\right)
+\end{equation}
+The site generator reads
+\begin{equation}
+	\mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+where the boundary parameters are defined as
+\begin{equation}
+	\begin{split}
+	\alpha_{a}^{x}&=\sigma_{11}\nu\rho_{a}^{x}+\sigma_{12}\nu\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-1)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
+	\end{split}
+\end{equation}
+The action on the occupation variable $n_{d}^{x}$ of particle type $d\in \{2,\ldots,N\}$ at site $x\in V $
 is the following
@@
 \begin{split}
-    \mathcal{L}_{x,y}^{rd}n_{\alpha}^{x}&=\nu \sigma_{11}(n_{\alpha}^{y}-n_{\alpha}^{x})+\nu\sigma_{12}\sum_{i=1}^{N}(n_{g_{i}(k)}^{y}-n_{\alpha}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
-\end{split}
-\end{equation}
-indeed, 
-\begin{equation}
-    \begin{split}
-\mathcal{L}_{x,y}^{x}n_{\alpha}^{x}&=\sum_{a,l=1}^{N}n_{a}^{x}n_{l}^{y}\left(n_{\alpha}^{x}-\delta_{a}^{x}+\delta_{g_{i}(l)^{x}}+\delta_{g_{i}(x)}^{y}-\delta_{l}^{y}-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{c=1}^{N}n_{\alpha}^{x}n_{c}^{y}
-\\&=
-\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{c=2}^{N}n_{\alpha}^{x}n_{c}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+    \mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{c=2\,:	,c\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
+\end{split}
+\end{equation}
+Indeed
+\begin{equation}
+    \begin{split}
+\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y}-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}
+\\&=
+\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{\alpha}^{x}n_{\ell}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
 \\&=
@@
 \end{equation}
-where we call $q\in \{1,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $c\in \{1,\ldots,N\}$ such that $g_{i}(c)\neq \alpha$.
-Summing over all indices $i\in\{1,\ldots,N\}$ we obtain \eqref{actionGraphRD}.\\
-Therefore, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives
+where we call $q\in \{2,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $\ell\in \{2,\ldots,N\}$ such that $g_{i}(\ell)\neq \alpha$.
+Summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$ we obtain \eqref{actionGraphRD}.\\
+As a consequence, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives
 \begin{equation}\label{DifferenceEquation}
-\mathcal{L}^{rd}n_{\alpha}^{x}=\nu\sigma_{11}\Delta_{L}n_{\alpha}^{x}+\nu\sigma_{12}\sum_{l=2\,:\,l\neq a}^{N}\Delta_{L}n_{l}^{x}+\Upsilon\sum_{l=1}^{N}(n_{l}^{x}-n_{\alpha}^{x})
+\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,l\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
 \end{equation}
@@
 In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
-\\
+\subsection{Reversible measure} 
 The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
@@
 \end{equation}
-with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.\\
+with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.
+\subsection{Duality}
 This generator $\mathcal{L}^{rd}$ can be described by the Hamiltonian $H^{rd}$ that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
 \begin{equation}
-    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{i=1}^{N}H_{x,y}^{x}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
 \end{equation}
@@
 \begin{equation}
-    H_{x,y}^{x}=\sum_{a,l=0}^{N}\left(E_{g_{i}(l)a}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{aa}^{x}\otimes E_{ll}^{y}\right)
+    H_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
 \end{equation}

### 2023-04-06 main.tex
i

@@
     \end{equation}
-    Assuming that \eqref{InverseS2} is true for $L$, we prove that it holds for $L+1$
+    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
 \begin{align*}
@@
 \\
-This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for $L$ and we prove that it holds for $L+1$. 
+This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
 \begin{align*}
@@
 \begin{equation}\label{RDGenerator}
-    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}
+    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \end{equation}
+\paragraph{Action on the occupation variable $n_{d}^{x}$ for the edge generator $\mathcal{L}_{x,y}^{rd}$}
 The action on the occupation variable $n_{d}^{x}$ of particle type $d\in \{2,\ldots,N\}$ at site $x\in V $
@@
 \begin{equation}
-    \begin{split}
-\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y}-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}
+	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
+\end{equation}
+while for every $c\in \{2,\ldots,N\}$ we have 
+\begin{equation}
+    \begin{split}
+\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}
 \\&=
@@
 where we call $q\in \{2,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $\ell\in \{2,\ldots,N\}$ such that $g_{i}(\ell)\neq \alpha$.
-Summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$ we obtain \eqref{actionGraphRD}.\\
+Moreover, we have
+\begin{equation}
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
+\end{equation}
+Then, summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$, we obtain \eqref{actionGraphRD}.
+\paragraph{Action on the occupation variable $n_{d}^{x}$ for the site generator $\mathcal{L}_{x}^{rd}$}
+Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
+\begin{equation}
+	\begin{split}
+	\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\delta_{b}^{x}+\delta_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
+	\\&=
+	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-1)\sigma_{12})-\alpha_{d}^{x}\right)
+	\\&=
+	\end{split}
+\end{equation}
 As a consequence, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives

### 2023-04-06 main.tex
ii

@@
 	\begin{split}
-	\alpha_{a}^{x}&=\sigma_{11}\nu\rho_{a}^{x}+\sigma_{12}\nu\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
-	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-1)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
-	\end{split}
+	\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
+	\end{split}
+\end{equation}
+and where, for every $x\in V$, we further assumed that
+\begin{equation}
+	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
 \end{equation}
@@
 \end{equation}
+
 Indeed
@@
 	\\&=
-	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-1)\sigma_{12})-\alpha_{d}^{x}\right)
-	\\&=
+	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
+	\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+	\\=&
+	\nu\sigma_{11}\rho_{d}^{x}+\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
 	\end{split}

### 2023-04-07 main.tex
RD

--- 2023-04-06 main.tex
@@
 The aim of this section is to give an answer to these questions. 
-\subsection{Linear reaction-diffusion process with coupled discrete Laplacians}
+\subsection{Linear reaction-diffusion process on a finite graph}
 Considering again a connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
@@
 where
-\begin{equation}
-    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
-\end{equation}
-with $\mathcal{L}_{x,y}$ is the generator the generator \eqref{edgeGenerator} and, for any function $f:\Omega\to \mathbb{R}$
+\begin{equation}\label{edgeGeneratorRD}
+    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+\end{equation}
+with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
 \begin{equation}
@@
 with the mapping 
+\begin{equation}
+	\begin{split}
+	g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
+	k&\to g_{c}(k)
+\end{split}
+\end{equation}
+defined $\forall c\in\{1,\ldots,N-2\}$ as 
 \begin{equation}
@@
     k+c \quad &\text{if}\quad k+c\leq N\\
-    k+c-N\quad &\text{if}\quad k+c>N\\
+    k+c-N+1\quad &\text{if}\quad k+c>N\\
     1\quad &\text{if}\quad k=1
-\end{cases}\qquad \forall k\in \{1,\ldots N\}
-\end{equation}
-and where
+\end{cases}
+\end{equation}
+Observe that $g_{c}(\cdot)$ is surjective and bijective, and thus invertible. \\
+Moreover,
 \begin{equation}
@@
 	\begin{split}
-	\alpha_{a}^{x}&=\sigma_{11}\nu\rho_{a}^{x}+\sigma_{12}\nu\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
-	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-1)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
-	\end{split}
-\end{equation}
-\paragraph{Action on the occupation variable $n_{d}^{x}$ for the edge generator $\mathcal{L}_{x,y}^{rd}$}
-The action on the occupation variable $n_{d}^{x}$ of particle type $d\in \{2,\ldots,N\}$ at site $x\in V $
-is the following 
+	\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
+	\end{split}
+\end{equation}
+and where, for every $x\in V$, we further assume that
+\begin{equation}
+	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
+\end{equation}
+\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ is exactly the one of the multi-species stirring process \eqref{siteGenerator}.
+We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
+\paragraph{Action on the occupation variable of the edge generator}
+For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
 \begin{equation}\label{actionGraphRD}
 \begin{split}
-    \mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{c=2\,:	,c\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
-\end{split}
-\end{equation}
+    \mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
+\end{split}
+\end{equation}
+
 Indeed
@@
 \end{equation}
-while for every $c\in \{2,\ldots,N\}$ we have 
-\begin{equation}
-    \begin{split}
-\mathcal{L}_{x,y}^{c}n_{a}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{\alpha}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{\alpha}^{x}n_{\ell}^{y}
-\\&=
-\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{\alpha}^{x}n_{\ell}^{y}-n_{\alpha}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
-\\&=
-\nu(n_{q}^{y}-n_{\alpha}^{x})
-    \end{split}
-\end{equation}
-where we call $q\in \{2,\ldots,N\}$ such that $g_{i}(q)=\alpha$ and $\ell\in \{2,\ldots,N\}$ such that $g_{i}(\ell)\neq \alpha$.
+while for every $c\in \{1,\ldots,N-2\}$ we have 
+\begin{equation}
+    \begin{split}
+\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
+\\&=
+\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+\\&=
+\nu(n_{q}^{y}-n_{d}^{x})
+    \end{split}
+\end{equation}
+where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, $q\neq d$ and $q\neq 1$ .
 Moreover, we have
@@
 \end{equation}
-Then, summing over all indices $c\in\{2,\ldots,N\}\,:\,c\neq d$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action on the occupation variable $n_{d}^{x}$ for the site generator $\mathcal{L}_{x}^{rd}$}
+Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
+\paragraph{Action on the occupation variable of the site generator}
 Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
-\begin{equation}
+\begin{equation}\label{actionBoudaryRD}
 	\begin{split}
@@
 	\\&=
-	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-1)\sigma_{12})-\alpha_{d}^{x}\right)
-	\\&=
-	\end{split}
-\end{equation}
-As a consequence, considering \eqref{actionGraphRD} on the geometry of a chain of finite length $L\in \mathbb{N}$, the action of the generator \eqref{RDGenerator} on the occupation variable $n_{\alpha}^{x}$ gives
+	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
+	\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+	\\=&
+	\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+	\end{split}
+\end{equation}
+\subsection{Reaction-diffusion process on a chain}
+Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$.
+This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
+Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
 \begin{equation}\label{DifferenceEquation}
-\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,l\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
-\end{equation}
-where with the symbol $\Delta_{N}$ we denote the discrete Laplacian operator on the chain, i.e.
-$\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$, $\forall x\in \{2,\ldots,L-1\}$ and $\forall a\in \{2,\ldots,N\}$.
-In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference differential equation where the discrete Laplacian of all species are coupled and linear reaction term are present.
+\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
+\end{equation}
+where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
+Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
+\begin{equation}
+\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
+\end{equation}
+On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$
+ In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
+Therefore, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
+This answers the first question of the beginning of this section.
 \subsection{Reversible measure} 
-The process defined by generator \eqref{RDGenerator} has reversible product measure when all the reservoirs have the same parameter for each site and each species, i.e.
-$\alpha_{a}^{x}=\alpha$, $\forall a\in \{1,\ldots,N\}$ and $x\in V$.
-This measure is given by
-\begin{equation}
-    \Lambda^{rev}=\bigotimes_{x\in V}\Lambda_{x}^{rev}
-\end{equation}
-where the marginals are
-\begin{equation}
-    \Lambda_{x}^{rev}\sim \text{Multinomial}(\nu,p,\ldots,p)
-\end{equation}
-with $p=\frac{1}{N}$. This can be verified by imposing the detailed balance condition.
+The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
+	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
+\end{equation}
+when for any $a\in\{1,\ldots,N\}$
+\begin{equation}\label{reversibilityConditionRD}
+	\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V
+\end{equation}
+This measure has marginals $\Lambda_{rev}^{x}$ given by 
+\begin{equation}
+	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{1}{N}
+\end{equation}
+namely
+\begin{equation}
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\left(\frac{1}{N}\right)^{\sum_{a=1}^{N}n_{a}^{x}}
+\end{equation}
+This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
+For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following.
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
+\begin{equation}
+	\begin{split}
+		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
+		\\
+		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
+		\\&
+		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
+	\end{split}
+\end{equation}
+that simplifies to 
+\begin{equation}
+	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
+\end{equation}
+that is true if and only if $p_{a}=p$ $\forall a\in \{2,\ldots,N\}$.\\
+By similar computation it is possible to show that the same result is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$. \\
+Recalling that, to have reversibility the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 
 \subsection{Duality}
-This generator $\mathcal{L}^{rd}$ can be described by the Hamiltonian $H^{rd}$ that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
-\begin{equation}
-    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+In this subsection we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
+\begin{equation}
+	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
+\end{equation}
+To each site $x\in V$ we associate an ``extra site'', denoted $\widehat{x}$,
+where dual particles will accumulate in the course of time. 
+We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+\begin{equation}
+	\bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
+\end{equation}
+where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+the extra-site $\widehat{x}$ connected to $x\in V$.
+
+The duality function is given by
+\begin{equation}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
+\end{equation}
+%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
+%\begin{equation}
+%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
+%\end{equation}
+The dual process is defined by its generator, which reads
+\begin{equation}\label{DualGenerator}
+	\widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
+\end{equation}
+where 
+$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}.
+\newline
+\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual with respect to the same duality function of $\mathcal{L}$ of the multi-species stirring process.
+Moreover, the dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
+As we will show this follows from the same $gl(N)$ algebraic structure.
+\subsubsection{Proof of duality relation for reaction-diffusion process}
+In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
+\begin{equation}
+    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
 \end{equation}
@@
 \begin{equation}
-    H_{x,y}^{m}=\sum_{a,l}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
-\end{equation}
-For this model, the duality relation is
+    H_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
+\end{equation}
+Similarly, we define the dual Hamiltonian $\widetilde{H}^{rd}$.
+For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}.
+\\ We aim to show
 \begin{equation}\label{DualityRelationRD}
@@
 \end{equation}
+Therefore, we need to prove that
+\begin{align}
+	(H_{x,y}^{rd})^{T}D&=DH_{x,y}^{rd}\label{edgeDualityRelationRD}\\
+	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
+\end{align}
 where the duality matrix $D$ is again \eqref{dualityMatrix}.
-Following subsection~\ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{x}$ and with $H_{x,y}^{m}$.
-This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{x}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$.
+As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ are the same of the stirring process, while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$.
+Therefore, we only need to show that
+\begin{align}
+	&(H_{x,y}^{c})^{T}D=DH_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
+	&(H_{x,y}^{m})^{T}D=DH_{x,y}^{m}\label{mDualityRelation}
+\end{align}
+Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ are symmetries of $\exp{E^{x}}\exp{E^{y}}$.
+The first result will follow from the commutator between $H_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
 \begin{align*}
-    &\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{g_{i}(l)a}^{x}\otimes E_{g_{i}(k)l}^{y}-E_{aa}^{x}\otimes E_{ll}^{y}\right)\right]
-    \\=&\sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left\{\left(E_{aa}^{x}\delta_{g_{i}(l)0}-E_{g_{i}(l)0}^{x}\delta_{aa}\right)\otimes \left(E_{bl}^{y}\delta_{g_{i}(k)0}-E_{g_{i}(k)0}^{y}\delta_{ba}\right)-\left(E_{aa}^{x}\delta_{a0}-E_{a0}^{x}\delta_{aa}\right)\otimes \left(E_{bl}^{y}\delta_{l0}-E_{l0}^{y}\delta_{bl}\right)\right\}
+	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]
 	\\=&
-    \sum_{a,b=2}^{N}\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{aa}^{x}\left(\delta_{g_{i}(l)0}-\delta_{a0}\right)-\left(E_{g_{i}(l)0}^{x}-E_{a0}^{x}\right)\delta_{aa}\right)\otimes \left(E_{bl}^{y}\left(\delta_{g_{i}(k)0}-\delta_{l0}\right)-\left(E_{g_{i}(k)0}^{y}-E_{l0}^{y}\right)\delta_{bl}\right)
-    \\=&\;0
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right.
+\\ \otimes&\left.
+\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
+	\\=&0
 \end{align*}
- Again, using \eqref{eq:comgl} and by a similar argument, we obtain
+where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
+ The second result will follow from the commutator between $H_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
 \begin{equation}
@@
 \end{equation}
-Therefore, arguing similarly to subsection~\ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.
+\begin{flushright}
+	$\square$
+\end{flushright}
+With this prove we answered to the second and third questions stated at the beginning of this section.
 

### 2023-04-07 main.tex
ii

@@
 \end{equation}
-Observe that $g_{c}(\cdot)$ is surjective and bijective, and thus invertible. \\
+Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
 Moreover,
@@
 Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
-\begin{equation}
+\begin{equation}\label{actionBDLine}
 \mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
 \end{equation}
-On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$
- In the spirit of \cite{casini2022uphill} we can write he the Master's equation for the evolution of the average density occupation, obtaining a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
-Therefore, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
+On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
+ \begin{equation}
+ 	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
+ \end{equation}
+ where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
+They evolve according to the Master's equation
+ \begin{equation}
+ 	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
+ \end{equation} 
+Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtaina system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
+For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
 This answers the first question of the beginning of this section.
@@
 By similar computation it is possible to show that the same result is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$. \\
-Recalling that, to have reversibility the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 
+Recalling that, to have reversibility, the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 
 \subsection{Duality}
@@
 \newline
-\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual with respect to the same duality function of $\mathcal{L}$ of the multi-species stirring process.
-Moreover, the dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
+\newline
+\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process.
+The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
 As we will show this follows from the same $gl(N)$ algebraic structure.
@@
 \end{flushright}
-With this prove we answered to the second and third questions stated at the beginning of this section.
+With this prove we answered the second and third questions stated at the beginning of this section.
 

### 2023-04-11 main.tex
organization

@@
 \end{equation}  
-One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}.
-
-\noindent
+One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
+\newline 
+\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
+\\ \\
 \textbf{Reamrk}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
@@
 therefore we have found the symilarity tranfsormation between $H_{x,y}$ and its transposed. \\
+We now look for a symmetry of $H_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
+\begin{equation}
+	H_{x,y}S_{x,y}=S_{s,y}H_{x,y}\quad \Leftrightarrow \quad [H_{x,y},S_{x,y}]=0
+\end{equation}
+Using \eqref{hamiltonianCasimir}, we observe that $H_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term.
+Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$.
+Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$
+\begin{equation}
+	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2},\Delta(A)) \right]=0
+\end{equation}
+We chose 
+\begin{equation}
+	E=\sum_{a=2}^{N}E_{a1}
+\end{equation}
+and, for a fixed $(x,y)\in \mathcal{E}$, we define
+\begin{equation}
+	S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
+\end{equation}
+where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. Therefore, this operator $S_{x,y}$ satisfies
+\begin{equation}\label{symmetryH}
+	\left[S_{x,y},H_{x,y}\right]=0
+\end{equation}
+i.e. it is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write
+
+\begin{comment}
 As already pointed out, $H_{x,y}$ is a linear function of $\Delta(C_{2})$.
@@
 i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write
+\end{comment}
 \begin{equation}
@@
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
+\section{Multi-species stirring process with reaction}
+In \cite{casini2022uphill} it has been defined a process whose average occupation evolution equation are given by two Laplacians and a linear reaction term (mutation).
+This model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one.
+For the lattice $\mathbb{Z}$, self-duality has been showed.
+In view of what have been proved in the previous section of this work, some questions arise naturally:
+\begin{enumerate}
+	\item Is it possible to extend this last duality result to the boundary-driven case in order to have an absorbing dual process?
+	\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
+	\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
+\end{enumerate}
+The aim of this section is to give an answer to these questions. 
+\subsection{The process on a finite graph}
+Considering again a connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
+\begin{equation}\label{RDGenerator}
+	\mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}
+\end{equation}
+where
+\begin{equation}\label{edgeGeneratorRD}
+	\mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+\end{equation}
+with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
+\begin{equation}
+	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-f(\bm{n})\right)
+\end{equation}
+with the mapping 
+\begin{equation}
+	\begin{split}
+		g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
+		k&\to g_{c}(k)
+	\end{split}
+\end{equation}
+defined $\forall c\in\{1,\ldots,N-2\}$ as 
+\begin{equation}
+	g_{c}(k)=\begin{cases}
+		k+c \quad &\text{if}\quad k+c\leq N\\
+		k+c-N+1\quad &\text{if}\quad k+c>N\\
+		1\quad &\text{if}\quad k=1
+	\end{cases}
+\end{equation}
+Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
+Moreover,
+\begin{equation}
+	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x})-f(\bm{n})\right)
+\end{equation}
+The site generator reads
+\begin{equation}
+	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+where the boundary parameters are defined as
+\begin{equation}
+	\begin{split}
+		\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+		\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
+	\end{split}
+\end{equation}
+and where, for every $x\in V$, we further assume that
+\begin{equation}
+	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
+\end{equation}
+\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ is exactly the one of the multi-species stirring process \eqref{siteGenerator}.
+We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
+\paragraph{Action on the occupation variable of $\mathcal{L}_{x,y}^{rd}$}
+For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
+\begin{equation}\label{actionGraphRD}
+	\begin{split}
+		\mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
+	\end{split}
+\end{equation}
+
+Indeed
+\begin{equation}
+	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
+\end{equation}
+while for every $c\in \{1,\ldots,N-2\}$ we have 
+\begin{equation}
+	\begin{split}
+		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
+		\\&=
+		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+		\\&=
+		\nu(n_{q}^{y}-n_{d}^{x})
+	\end{split}
+\end{equation}
+where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, $q\neq d$ and $q\neq 1$ .
+Moreover, we have
+\begin{equation}
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
+\end{equation}
+Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
+\paragraph{Action on the occupation variable of $\mathcal{L}_{x}^{rd}$}
+Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
+\begin{equation}\label{actionBoudaryRD}
+	\begin{split}
+		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\delta_{b}^{x}+\delta_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
+		\\&=
+		\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
+		\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\\=&
+		\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+	\end{split}
+\end{equation}
+\subsection{The process on a chain}
+Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$.
+This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
+Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
+\begin{equation}\label{DifferenceEquation}
+	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
+\end{equation}
+where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
+Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
+\begin{equation}\label{actionBDLine}
+	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
+\end{equation}
+On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
+\begin{equation}
+	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
+\end{equation}
+where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
+They evolve according to the Master's equation
+\begin{equation}
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
+\end{equation} 
+Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtaina system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
+For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
+This answers the first question of the beginning of this section.
+\subsection{Reversible measure} 
+The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
+	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
+\end{equation}
+when for any $a\in\{1,\ldots,N\}$
+\begin{equation}\label{reversibilityConditionRD}
+	\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V
+\end{equation}
+This measure has marginals $\Lambda_{rev}^{x}$ given by 
+\begin{equation}
+	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{1}{N}
+\end{equation}
+namely
+\begin{equation}
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\left(\frac{1}{N}\right)^{\sum_{a=1}^{N}n_{a}^{x}}
+\end{equation}
+This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
+For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following.
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
+\begin{equation}
+	\begin{split}
+		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
+		\\
+		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
+		\\&
+		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
+	\end{split}
+\end{equation}
+that simplifies to 
+\begin{equation}
+	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
+\end{equation}
+that is true if and only if $p_{a}=p$ $\forall a\in \{2,\ldots,N\}$.\\
+By similar computation it is possible to show that the same result is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$. \\
+Recalling that, to have reversibility, the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 
+\subsection{Duality}
+In this subsection we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
+\begin{equation}
+	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
+\end{equation}
+To each site $x\in V$ we associate an ``extra site'', denoted $\widehat{x}$,
+where dual particles will accumulate in the course of time. 
+We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+\begin{equation}
+	\bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
+\end{equation}
+where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+the extra-site $\widehat{x}$ connected to $x\in V$.
+
+The duality function is given by
+\begin{equation}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
+\end{equation}
+%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
+%\begin{equation}
+%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
+%\end{equation}
+The dual process is defined by its generator, which reads
+\begin{equation}\label{DualGenerator}
+	\widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
+\end{equation}
+where 
+$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}.
+\newline
+\newline
+\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process.
+The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
+As we will show this follows from the same $gl(N)$ algebraic structure.
+\subsubsection{Proof of duality}
+In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
+\begin{equation}
+	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+\end{equation}
+where $H_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
+\begin{equation}
+	H_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
+\end{equation}
+and 
+\begin{equation}
+	H_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
+\end{equation}
+Similarly, we define the dual Hamiltonian $\widetilde{H}^{rd}$.
+For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}.
+\\ We aim to show
+\begin{equation}\label{DualityRelationRD}
+	(H^{rd})^{T}D=D\widetilde{H}^{rd}
+\end{equation}
+Therefore, we need to prove that
+\begin{align}
+	(H_{x,y}^{rd})^{T}D&=DH_{x,y}^{rd}\label{edgeDualityRelationRD}\\
+	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
+\end{align}
+where the duality matrix $D$ is again \eqref{dualityMatrix}.
+As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ are the same of the stirring process, while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$.
+Therefore, we only need to show that
+\begin{align}
+	&(H_{x,y}^{c})^{T}D=DH_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
+	&(H_{x,y}^{m})^{T}D=DH_{x,y}^{m}\label{mDualityRelation}
+\end{align}
+Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ are symmetries of $\exp{E^{x}}\exp{E^{y}}$.
+The first result will follow from the commutator between $H_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
+Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
+\begin{align*}
+	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right.
+\\ \otimes&\left.
+\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
+	\\=&0
+\end{align*}
+where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
+The second result will follow from the commutator between $H_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
+\begin{equation}
+	\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
+\end{equation}
+\begin{flushright}
+	$\square$
+\end{flushright}
+With this prove we answered the second and third questions stated at the beginning of this section. \\
+\textbf{FROM HERE ON-WARDS STILL TO CHECK}\\
 \subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}
@@
 
-\section{Multi-species stirring process with reaction}
-In \cite{casini2022uphill} it has been defined a process whose average occupation evolution equation are given by two Laplacians and a linear reaction term (mutation).
-This model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one.
-For the lattice $\mathbb{Z}$, self-duality has been showed.
-In view of what have been proved in the previous section of this work, some questions arise naturally:
-\begin{enumerate}
-	\item Is it possible to extend this last duality result to the boundary-driven case in order to have an absorbing dual process?
-	\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
-	\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-\end{enumerate}
-The aim of this section is to give an answer to these questions. 
-\subsection{Linear reaction-diffusion process on a finite graph}
-Considering again a connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
-\begin{equation}\label{RDGenerator}
-    \mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}
-\end{equation}
-where
-\begin{equation}\label{edgeGeneratorRD}
-    \mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
-\end{equation}
-with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
-\begin{equation}
-    \mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-f(\bm{n})\right)
-\end{equation}
-with the mapping 
-\begin{equation}
-	\begin{split}
-	g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
-	k&\to g_{c}(k)
-\end{split}
-\end{equation}
-defined $\forall c\in\{1,\ldots,N-2\}$ as 
-\begin{equation}
-    g_{c}(k)=\begin{cases}
-    k+c \quad &\text{if}\quad k+c\leq N\\
-    k+c-N+1\quad &\text{if}\quad k+c>N\\
-    1\quad &\text{if}\quad k=1
-\end{cases}
-\end{equation}
-Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
-Moreover,
-\begin{equation}
-    \mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x})-f(\bm{n})\right)
-\end{equation}
-The site generator reads
-\begin{equation}
-	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
-\end{equation}
-where the boundary parameters are defined as
-\begin{equation}
-	\begin{split}
-	\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
-	\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
-	\end{split}
-\end{equation}
-and where, for every $x\in V$, we further assume that
-\begin{equation}
-	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
-\end{equation}
-\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ is exactly the one of the multi-species stirring process \eqref{siteGenerator}.
-We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
-\paragraph{Action on the occupation variable of the edge generator}
-For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
-\begin{equation}\label{actionGraphRD}
-\begin{split}
-    \mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
-\end{split}
-\end{equation}
-
-Indeed
-\begin{equation}
-	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
-\end{equation}
-while for every $c\in \{1,\ldots,N-2\}$ we have 
-\begin{equation}
-    \begin{split}
-\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
-\\&=
-\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
-\\&=
-\nu(n_{q}^{y}-n_{d}^{x})
-    \end{split}
-\end{equation}
-where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, $q\neq d$ and $q\neq 1$ .
-Moreover, we have
-\begin{equation}
-	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
-\end{equation}
-Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action on the occupation variable of the site generator}
-Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
-\begin{equation}\label{actionBoudaryRD}
-	\begin{split}
-	\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\delta_{b}^{x}+\delta_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
-	\\&=
-	\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
-	\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
-	\\=&
-	\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
-	\end{split}
-\end{equation}
-\subsection{Reaction-diffusion process on a chain}
-Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$.
-This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
-Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
-\begin{equation}\label{DifferenceEquation}
-\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
-\end{equation}
-where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
-Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
-\begin{equation}\label{actionBDLine}
-\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
-\end{equation}
-On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
- \begin{equation}
- 	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
- \end{equation}
- where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
-They evolve according to the Master's equation
- \begin{equation}
- 	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
- \end{equation} 
-Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtaina system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
-For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question of the beginning of this section.
-\subsection{Reversible measure} 
-The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
-	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
-\end{equation}
-when for any $a\in\{1,\ldots,N\}$
-\begin{equation}\label{reversibilityConditionRD}
-	\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V
-\end{equation}
-This measure has marginals $\Lambda_{rev}^{x}$ given by 
-\begin{equation}
-	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{1}{N}
-\end{equation}
-namely
-\begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\left(\frac{1}{N}\right)^{\sum_{a=1}^{N}n_{a}^{x}}
-\end{equation}
-This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
-For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
-\begin{equation}
-	\begin{split}
-		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
-		\\
-		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
-		\\&
-		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
-	\end{split}
-\end{equation}
-that simplifies to 
-\begin{equation}
-	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
-\end{equation}
-that is true if and only if $p_{a}=p$ $\forall a\in \{2,\ldots,N\}$.\\
-By similar computation it is possible to show that the same result is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$. \\
-Recalling that, to have reversibility, the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 
-\subsection{Duality}
-In this subsection we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
-\begin{equation}
-	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
-\end{equation}
-To each site $x\in V$ we associate an ``extra site'', denoted $\widehat{x}$,
-where dual particles will accumulate in the course of time. 
-We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
-\begin{equation}
-	\bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
-\end{equation}
-where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
-the extra-site $\widehat{x}$ connected to $x\in V$.
-
-The duality function is given by
-\begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
-\end{equation}
-%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
-%\begin{equation}
-%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
-%\end{equation}
-The dual process is defined by its generator, which reads
-\begin{equation}\label{DualGenerator}
-	\widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
-\end{equation}
-where 
-$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}.
-\newline
-\newline
-\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process.
-The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
-As we will show this follows from the same $gl(N)$ algebraic structure.
-\subsubsection{Proof of duality relation for reaction-diffusion process}
-In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
-\begin{equation}
-    H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
-\end{equation}
-where $H_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
-\begin{equation}
-    H_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
-\end{equation}
-and 
-\begin{equation}
-    H_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
-\end{equation}
-Similarly, we define the dual Hamiltonian $\widetilde{H}^{rd}$.
-For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}.
-\\ We aim to show
-\begin{equation}\label{DualityRelationRD}
-    (H^{rd})^{T}D=D\widetilde{H}^{rd}
-\end{equation}
-Therefore, we need to prove that
-\begin{align}
-	(H_{x,y}^{rd})^{T}D&=DH_{x,y}^{rd}\label{edgeDualityRelationRD}\\
-	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
-\end{align}
-where the duality matrix $D$ is again \eqref{dualityMatrix}.
-As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ are the same of the stirring process, while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$.
-Therefore, we only need to show that
-\begin{align}
-	&(H_{x,y}^{c})^{T}D=DH_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
-	&(H_{x,y}^{m})^{T}D=DH_{x,y}^{m}\label{mDualityRelation}
-\end{align}
-Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ are symmetries of $\exp{E^{x}}\exp{E^{y}}$.
-The first result will follow from the commutator between $H_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
-Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
-\begin{align*}
-	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]
-	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right.
-\\ \otimes&\left.
-\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
-	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
-	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
-	\\=&0
-\end{align*}
-where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
- The second result will follow from the commutator between $H_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
-\begin{equation}
-\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
-\end{equation}
-\begin{flushright}
-	$\square$
-\end{flushright}
-With this prove we answered the second and third questions stated at the beginning of this section.
-
 \section{Conclusion}
 
-\bibliography{ref}
-\bibliographystyle{unsrt}
-\end{document}
-
 \appendix
-\section{Oscillator}
-
-\textbf{Reamrk}: The basis element the we have defined above, can also be thought as proper compositions of the rising and lowering operators of th Heisenberg Lie algebra.
-Indeed, \begin{equation}\label{creationOperators}
+\section{Oscillator realization}\label{appA}
+
+ The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
+  \begin{equation}\label{creationOperators}
 	\begin{cases}
@@
 \end{equation}
-The basis elements of $gl(N)$ can be written as
-\begin{equation}
-		e_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
-\end{equation}  
+Therefore, we have that 
+\begin{equation}
+		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
+\end{equation} 
+fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} 
+\begin{comment}
 \section{Representation}
@@
 \end{equation}
+\end{comment}
+\bibliography{ref}
+\bibliographystyle{unsrt}
+
+\end{document}

### 2023-04-11 main.tex
i

@@
 In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
-These boundaries, exchanging particle with the external environment, put the chain out of equilibrium.
+These boundaries, exchanging particle with the external environment, by putting the chain out of equilibrium.
 The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
@@
 \end{equation} 
-The action of $\mathcal{H}$ amounts to the permutation of the two sites, i.e.
+The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.
 \begin{equation}
@@
 	B_{1}=\begin{pmatrix}
-		\alpha_{1}-1&\alpha_{1}&\ldots&\alpha_{1}\\
-		\alpha_{2}&\alpha_{2}-1&\ldots&\alpha_{2}\\
-		\vdots&\vdots&\vdots&\vdots\\
-		\alpha_{N}&\alpha_{N}&\ldots&\alpha_{N}-1
+		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
+		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
+		\vdots&\vdots& &\ddots& &\vdots\\
+		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
+		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
 	\end{pmatrix}
@@
 	B_{L}=\begin{pmatrix}
-		\beta_{1}-1&\beta_{1}&\ldots&\beta_{1}\\
-		\beta_{2}&\beta_{2}-1&\ldots&\beta_{2}\\
-		\vdots&\vdots&\vdots&\vdots\\
-		\beta_{N}&\beta_{N}&\ldots&\beta_{N}-1
+		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
+		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
+		\vdots&\vdots& &\ddots& &\vdots\\
+		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
+		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
 	\end{pmatrix}
@@
 \end{equation}
-In this setting the extra-sites are denoted by $0$ and $L+1$, since connected with sites $1$ and $L$ of the chain respectively.
+Under these assumption the Hamiltonian is integrable. \\
+For what concerns duality, in this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain.
 Moreover, the matrix $R_{x}$ reduces to the identity.
@@
 \begin{equation}
-	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{E^{x}}\otimes \mathcal{D}_{L+1}
+	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{(E^{x})}\otimes \mathcal{D}_{L+1}
 \end{equation}
@@
 \begin{equation}
-	\widetilde{H}=H_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{L+1}
-\end{equation}
-with the operators \eqref{edgeHamiltonian} and \eqref{siteDualHamiltonian}.
+	\widetilde{H}=\widetilde{H}_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+\widetilde{H}_{L+1}
+\end{equation}
 In the long-time horizon, the dual process voids the chain, and all particles are eventually absorbed at extra-site $0$ or $L+1$.
-\\
-Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product ansatz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat2017exact}). 
- Calling $|{P}(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
+\paragraph{Matrix Product Ansatz (MPA)} Matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we recall its main points.\\
+ Calling $|\Psi(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
  the master equation
@@
 \newline
-\textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them 
+\textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$:
 	\begin{equation}
@@
 \subsection{The explicit form of the steady state}\label{subsection-exact}
-As pointed already pointed out, the MPA gives an abstract form of the steady state, in terms of an algebra of operators.
+The MPA gives an abstract form of the steady state in terms of an algebra of operators.
 However, to write explicitly the steady state one should know a representation of this algebra.
@@
 where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one.
-Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA will become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly.
-Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$.
+Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly.
+Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$.\\
 The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix.
@@
 This informally explains the role of duality.
-The second transformation $\mathcal{S}_{2}$ allows to diagonalize the right boundary, paying the price of having the left one depending on the difference between the densities of the two reservoirs.
+The second transformation $\mathcal{S}_{2}$ diagonalize the right boundary.
+This allows to simplify a lot the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.
 \\
-This idea is exposed as follows.
-We first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$.
+The computation are organized as follows: we first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$.
 Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators.
@@
 \end{equation}
- This matrix $\mathcal{S}_{1}$ is invertible and we introduce 
+ This $\mathcal{S}_{1}$ is invertible, then we introduce 
 \begin{equation}\label{hatHamiltonian}
@@
 \end{equation}
-The boundary Hamiltonians are \eqref{siteDualHamiltonian} without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
+The boundary Hamiltonians$B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
 \begin{equation}
@@
 \end{equation}
-therefore, it is easy to see that 
+then, it is easy to see that 
 \begin{equation}\label{S1-Inverse}
@@
 \end{equation}
-
 We introduce the second transformation as 
@@
 \end{equation}
-The boundary Hamiltonians are the following 
+The boundary Hamiltonians of $H^{''}$ reads
 \begin{equation}
@@
 \end{equation}
-We obtain the new operators of the MPA that by transforming the original one by $S$
+We obtain 
 \begin{equation}\label{Xtildes2b}
@@
 \end{equation}
-We can also reverse the transformation by $S^{-1}$ and get back: 
+and, we can also reverse the transformation by $S^{-1}$ and get back: 
 \begin{equation}\label{Xes}
@@
 \end{equation} 
-The vector $|\Psi^{''}\rangle$ is written as:
+Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ is written as:
 \begin{equation}\label{toDetermineTilde}
-	|Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 	|V \rangle \,|\mathbf{n}\rangle
@@
 $$
-such that for each site $x\in \{1,\ldots,L\}$ $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
+such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
 To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{x}}
 |V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBula},\eqref{commLEFT} and \eqref{commRIGHT}.\\
-We  rewrite \eqref{commutationsBula} as:
+We have
 \begin{equation}\label{UsefulRelation}
@@
 \end{align*}
-By taking the product over the sites $i$ from $1$ to L we obtain 
+By taking the product over the sites $x$ from $1$ to $L$ we obtain 
 \begin{equation}
@@
 \end{equation}
-where $s_i=\sum_{a=1}^N\delta_{n_k^i,1}$. Finally we take the tensor product of the vectors $|s_{x}\rangle$ and we obtain
-\begin{equation}
-	|\mathbf{s}\rangle=\bigotimes_{i=1}^{L}|s_{x}\rangle=|\mathbf{s}\rangle
-\end{equation}
-with $s_{x}\in\{1,\ldots,N\}$. For a fixed site $i$, because of the hard-core interaction that allows at most one particle on type different from $1$ ,at site $i$ we have 
+where $s_{x}=\sum_{a=1}^N\delta_{n_{k}^{x},1}$. Finally we take the tensor product of the vectors $|s_{x}\rangle$ and we obtain
+\begin{equation}
+	|\mathbf{s}\rangle=\bigotimes_{x=1}^{L}|s_{x}\rangle=|\mathbf{s}\rangle
+\end{equation}
+with $s_{x}\in\{1,\ldots,N\}$. For a fixed site $x$, because of the hard-core interaction that allows at most one particle on type different from $1$, we have 
 \begin{equation}
@@
 \end{equation}
-Finally summing over all $\mathbf{s}\in \Omega$ (that is equivalent, $\forall i\in\{1,\ldots,L\}$, to summing over all the possible values of each $s_{x}\in\{1,\ldots,N\}$) we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}.
+Finally summing over all $\mathbf{s}\in \Omega$  we obtain \eqref{ResulsBasis}.
 \begin{flushright}
@@
 		\begin{split}
-			\Psi^{'}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{l}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 		\end{split}
@@
  \begin{equation}\label{CiEquation}
-	c_{x}=\begin{cases}
-		1\quad \text{if}\quad s_{x}\neq 1\\
-		0\quad \text{if}\quad s_{x}=1
-	\end{cases}\qquad \forall x\in \{1,\ldots,L\}
+	c_{y}=\begin{cases}
+		1\quad \text{if}\quad s_{y}\neq 1\\
+		0\quad \text{if}\quad s_{y}=1
+	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
 \end{equation}
@@
 \begin{equation}\label{notation1}
-    e_{ab}=e_{a}^{b}=\left(\delta_{a,c}\delta_{b,d}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,\}
+    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,\}
 \end{equation}
@@
     	\begin{split}
-    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
     		\\&+\left.
@@
 \end{comment}
-The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector whose component are denoted by $\Psi^{'}(\bm{s})$. 
-To find this elements we need to fix the rows correspondent to $\bm{s}$. Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
+The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{s})$. 
+To find these elements we need to fix the rows correspondent to $\bm{s}$ in the matrix $\mathcal{S}_{2}^{-1}$.
+Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
 \begin{equation}
@@
 \begin{equation}
-  \left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)
+  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)
 \end{equation}
@@
     \begin{equation}
-\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)\right)^{1-\delta_{s_{x},1}}
+\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)\right)^{1-\delta_{s_{y},1}}
 \end{equation}
@@
 \begin{equation}
-	c_{x}=(1-\delta_{s_{x},1}) \qquad \forall x\in \{1,\ldots L\}
+	c_{y}=(1-\delta_{s_{y},1}) \qquad \forall y\in \{1,\ldots L\}
 \end{equation}
@@
 	\begin{split}
-		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{i}}\left(\beta_{s_{x}}\right)^{(1-c_{i})(1-\delta_{s_{x},1})}
+		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{s_{y}}\right)^{(1-c_{y})(1-\delta_{s_{y},1})}
 	\end{split}
@@
     \begin{split}
-        \Psi(\bm{s})&=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(2+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
+        \Psi(\bm{s})&=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
         \\&+
@@
 \\&
-\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
-  \prod_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
+\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
  \\ &
- \beta_{s_{x}}^{(1-c_{x})(1-\delta_{s_{x},1})}
+ \beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
  \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
@@
     \begin{split}
-  &\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{L}c_{a})}{\Gamma(2+L)}
+  &\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
 \\&  
-\prod_{i=x\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{s_{x}}^{(1-c_{x})(1-\delta_{s_{x},1})}
+\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 \\&
@@
 \subsection{Exact correlations}\label{correlation-section}
-We compute in this section a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e.
+In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e.
 a species with label from $2$ to $N$.
-This is motivated by interest of understanding how actual particles of the chain are correlated among each others.
+This is motivated by interest of understanding how actual particles of the chain are correlated among each others and because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{0}^{x}=\nu-\sum_{a=2}^{N}n_{a}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
@@
 where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This probability \eqref{Prob-m} $\Psi(\bm{s})$ of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e. 
-\begin{equation}
-	\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)=\Psi_{\bm{y}}\left(s_{1},\ldots,s_{m}\right)
-\end{equation}
-where the subscript $\bm{y}$ underlines the fact that we are considering a chain with length $m$. 
-As already pointed out in \eqref{LinkABS-corr}, for non-empty configurations we have:
+This corresponds to the steady state probability of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e. 
+\begin{equation}
+	\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)=\Psi\left(s_{1},\ldots,s_{m}\right)
+\end{equation}
+where $\Psi(\bm{s})$ is the element of the vector \eqref{steadyStateH} computed for this chain $m$.
+As already remarked in \eqref{LinkABS-corr}, for non-empty configurations we have:
 \begin{equation}\label{Corr-mABS}
-	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\Psi^{'}_{\bm{y}}(s_{1},\ldots,s_{m})
+	\Psi(s_{1},\ldots,s_{m})=\Psi^{'}(s_{1},\ldots,s_{m})
 \end{equation}
@@
 \begin{equation}
-	\Psi_{\bm{y}}(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+	\Psi(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
 \end{equation}
@@
 \section{Multi-species stirring process with reaction}
-In \cite{casini2022uphill} it has been defined a process whose average occupation evolution equation are given by two Laplacians and a linear reaction term (mutation).
-This model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one.
-For the lattice $\mathbb{Z}$, self-duality has been showed.
+In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{2,3\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
+\begin{equation}\label{2SpeciesRD}
+	\partial \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)
+\end{equation} 
+for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$.
+It is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.
+\\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
+For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
 In view of what have been proved in the previous section of this work, some questions arise naturally:
 \begin{enumerate}
-	\item Is it possible to extend this last duality result to the boundary-driven case in order to have an absorbing dual process?
+		\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
 			\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
-	\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
+	\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process?
 \end{enumerate}
 The aim of this section is to give an answer to these questions.
+We first define a more general version with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with the same structure as \eqref{2SpeciesRD}.
+Second we construct the Lie algebraic description and we use it to prove absorbing duality in the general case.
 \subsection{The process on a finite graph}
@@
 where the duality matrix $D$ is again \eqref{dualityMatrix}.
-As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ are the same of the stirring process, while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$.
+As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$.
 Therefore, we only need to show that
@@
 \begin{equation}\label{dualityFunctionChain}
-    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
 \end{equation}

### 2023-04-12 main.tex
i

@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $k$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$ at site $x\in V$.
+At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$ at site $x\in V$.
 On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$.
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{a}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-f(\bm{n})\right]
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left[f(\bm{n}-\delta^{x}_{a}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-f(\bm{n})\right]
 \end{equation}
@@
 \end{equation}
-This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $k$ at site $x$ is exchanged with a particle of tipe $l$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $k$.
+This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $a$.
 See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 
@@
 \begin{equation}\label{eq:comgl}
-\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{bc}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
+\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
 \end{equation}
@@
 \end{equation} 
-The dimension $M$ of the symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
+The dimension $M$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
 \begin{equation}
@@
 \begin{equation}
-    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{i=1}^N\delta_{n^x_i,m^{x}_i}
+    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}
 \end{equation}
@@
 \end{equation}
-Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$. 
+Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$. 
 Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
@@
 \begin{equation}\label{transpositionPropertyR}
-(E_{ab}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
+(E_{ba}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
 \end{equation}
@@
 \begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{a_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{a_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 \\&
@@
 \\&=
-\sum_{a_{2}=0}^{n_{1}^{x}}\ldots\sum_{a_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
+\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
 \\&
@@
 \\&=
-\sum_{a_{2}=0}^{n_{1}^{x}}\ldots\sum_{a_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
+\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
 \\& 
@@
 As we will see, this symmetry is $\sum_{a=2}^{N}E_{a1}$ \\
-Using \eqref{transpositionPropertyR} we obtain
+We first look for the similarity between $H_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain
 
@@
 \end{equation}
-therefore we have found the symilarity tranfsormation between $H_{x,y}$ and its transposed. \\
+therefore we have found the similarity transformation between $H_{x,y}$ and its transposed. \\
 We now look for a symmetry of $H_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
@@
 Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$.
-Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$
-\begin{equation}
-	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2},\Delta(A)) \right]=0
+Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ it holds
+\begin{equation}
+	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0
 \end{equation}
@@
  \end{equation}
-In the following we need the application of the Hadamard formula with $B=E$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra. Therefore we compute 
+In the following we need the application of the Hadamard formula with $B=\sum_{a=2}^{N}E_{a1}$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
+Therefore we compute
 \begin{enumerate}
@@
     \begin{equation}\label{HT-E1l}
-        \exp{(-E)}E_{1 b}\exp{(E)}=E_{1b}+E_{11}-\sum_{a=2}^{N}\left(E_{a1}+E_{ab}\right)
+        \exp{(-E)}E_{1 a}\exp{(E)}=E_{1a}+E_{11}-\sum_{c=2}^{N}\left(E_{c1}+E_{ca}\right)
     \end{equation}
@@
     \begin{equation}
-[E,E_{1b}]=\sum_{a=2}^{N}\left(E_{ab}\delta_{11}-E_{11}\delta_{ab}\right)= (\sum_{a=2}^{N}E_{ab} ) -E_{11};
+[E,E_{1a}]=\sum_{c=2}^{N}\left(E_{ca}\delta_{11}-E_{11}\delta_{ca}\right)= (\sum_{c=2}^{N}E_{ca} ) -E_{11};
 \end{equation}
@@
 \begin{split}
-\left[E,[E,E_{1b}]\right]&=\sum_{c=2}^{N}\sum_{a=2}^{N}\left[E_{c1},E_{ab}\right]-\sum_{c=2}^{N}\left[E_{c1},E_{11}\right]
-\\&=
-\sum_{a,c=2}^{N}\left(E_{cb}\delta_{a1}-E_{a1}\delta_{cb}\right)-\sum_{c=2}^{N}\left(E_{c1}\delta_{11}-E_{11}\delta_{c1}\right)
+\left[E,[E,E_{1a}]\right]&=\sum_{d=2}^{N}\sum_{c=2}^{N}\left[E_{d1},E_{ca}\right]-\sum_{d=2}^{N}\left[E_{d1},E_{11}\right]
+\\&=
+\sum_{d,c=2}^{N}\left(E_{da}\delta_{c1}-E_{c1}\delta_{da}\right)-\sum_{d=2}^{N}\left(E_{d1}\delta_{11}-E_{11}\delta_{d1}\right)
 \\=&
--2\sum_{a=2}^{N}E_{a1};
+-2\sum_{c=2}^{N}E_{c1};
 \end{split}
@@
 Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
-\item for $A=E_{ab}$ with $a,b \in \{2,\ldots,N\}$ we obtain 
+\item for $A=E_{ba}$ with $a,b \in \{2,\ldots,N\}$ we obtain 
 \begin{equation}\label{HT-Ekl}
-    \exp{(-E)}E_{a b}\exp{(E)}=E_{ab}+E_{a 1}
+    \exp{(-E)}E_{a b}\exp{(E)}=E_{ba}+E_{b1}
 \end{equation}
@@
 \begin{equation}
-[E,E_{ab}]=\sum_{c=2}^{N}\left(E_{cb}\delta_{a1}-E_{a1}\delta_{c b}\right)=-E_{a1};
+[E,E_{ba}]=\sum_{c=2}^{N}\left(E_{ca}\delta_{b1}-E_{b1}\delta_{c a}\right)=-E_{b1};
 \end{equation}
@@
 \begin{align*}
-[E,E_{11}]=\sum_{a=2}^{N}\left(E_{a1}\delta_{11}-E_{1 1}\delta_{a1}\right)=\sum_{a=2}^{N}E_{a1};
+[E,E_{11}]=\sum_{c=2}^{N}\left(E_{c1}\delta_{11}-E_{1 1}\delta_{c1}\right)=\sum_{c=2}^{N}E_{c1};
 \end{align*}
@@
     \begin{split}
-H_{x}^{T}=\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}
+H_{x}^{T}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}
     \end{split}
@@
 \begin{equation}
-    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
 \end{equation}
@@
 \begin{equation}\label{intermediateTransposeSite}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{a,b=0}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
 \end{equation}
@@
     \\=&
-     \exp{(-E^{x})}\sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
-     + \exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
-     \\=&
-     \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}+E_{11}^{x}-\sum_{a=2}^{N}(E_{aa}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{a=1}^{N}\sum_{b =2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}+E_{b 1}^{x}-E_{bb}^{x}-E_{b 1}^{x}\right)
-     \\=&
-\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{a=1}^{N}\alpha_{a}^{x}\sum_{b=2}^{N}E_{bb}^{x}
-=
+    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}E_{c1}^{x}+E_{ca}^{x}-E_{11}^{x}+\sum_{c=2}^{N}E_{c1}^{x}\right)+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
+    \\&+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
+    \\&=\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=
     \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
-=
+    \\&=
     \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
-\\=&
+    \\&=
     \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+    % \exp{(-E^{x})}\sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
+     %+ \exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
+     %\\=&
+    % \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}+E_{11}^{x}-\sum_{a=2}^{N}(E_{aa}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{a=1}^{N}\sum_{b =2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}+E_{b 1}^{x}-E_{bb}^{x}-E_{b 1}^{x}\right)
+    % \\=&
+%\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{a=1}^{N}\alpha_{a}^{x}\sum_{b=2}^{N}E_{bb}^{x}
+%=
+  %   \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
+%=
+%\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
+%\\=&
+%\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
  \end{align*}
@@
 \begin{equation}\label{dualityFunctionChain}
-    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(ò\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
 \end{equation}

### 2023-04-12 main.tex
i
pulizia

@@
     &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
-    \\=&
-    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}E_{c1}^{x}+E_{ca}^{x}-E_{11}^{x}+\sum_{c=2}^{N}E_{c1}^{x}\right)+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
-    \\&+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
+    \\&=
+    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}(E_{c1}^{x})-\sum_{c=2}^{N}(E_{ca}^{x})-E_{11}^{x}+
+    \sum_{c=2}^{N}(E_{c1}^{x})\right)\\&+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
     \\&=\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=
@@
     \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
-    % \exp{(-E^{x})}\sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}-E_{11}^{x}\right)\exp{(E^{x})}
-     %+ \exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
-     %\\=&
-    % \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}+E_{11}^{x}-\sum_{a=2}^{N}(E_{aa}^{x}+E_{a1}^{x})-E_{11}^{x}+\sum_{a=2}^{N}E_{a1}^{x}\right)+\sum_{a=1}^{N}\sum_{b =2}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}+E_{b 1}^{x}-E_{bb}^{x}-E_{b 1}^{x}\right)
-    % \\=&
-%\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{a=1}^{N}\alpha_{a}^{x}\sum_{b=2}^{N}E_{bb}^{x}
-%=
-  %   \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
-%=
-%\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
-%\\=&
-%\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
  \end{align*}
@@
     \begin{split}
-&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}
+&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\rho_{a}^{x}E_{1a}^{x}
 \\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}
@@
 In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
-These boundaries, exchanging particle with the external environment, by putting the chain out of equilibrium.
+These boundaries, exchanging particle with the external environment, put the chain out of equilibrium.
 The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
@@
 We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
-{\color{red} We will denote the element of the representation of the Lie algebra by lowercase letters, i.e.
-$e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra).} \\
+{\color{red} We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the the fundamental representation of the algebra.} \\
 The Hamiltonian is
@@
 \end{equation}
-Under these assumption the Hamiltonian is integrable. \\
+Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact}). \\
 For what concerns duality, in this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain.
@@
  Calling $|\Psi(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
- the master equation
+ the Master equation
 \begin{equation}
@@
 where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one.
-Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simple, therefore, the steady state $|\Psi\rangle$ of $H^{''}$ will be written explicitly.
-Then, reversing the transformations we will retrieve $|\Psi^{''}\rangle$.\\
+Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
+Then, reversing the transformations we will retrieve $|\Psi\rangle$.\\
 The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix.
@@
 \begin{equation}\label{transformationV}
- S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+ S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
 \end{equation}
@@
 \end{equation}
-The boundary Hamiltonians$B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
+The boundary Hamiltonians $B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
 \begin{equation}
@@
 Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
-The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equations
+The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equation
 \begin{equation}
@@
 \end{equation}
-Using $\mathcal{S}$ we introduce 
+We introduce 
 \begin{equation}
@@
 \subsubsection{The steady state of $H^{''}$}\label{subsectionSSHsec}
-We state the following result. The steady state of the Hamiltonian $H^{''}$ is given by 
+We state the following result: the steady state of the Hamiltonian $H^{''}$ is given by 
 \begin{equation}\label{ResulsBasis}
@@
 To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{x}}
-|V \rangle$ and the normalization $Z_{L}$. We use the new commutations relations \eqref{commutationsBula},\eqref{commLEFT} and \eqref{commRIGHT}.\\
-We have
+|V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
 \begin{equation}\label{UsefulRelation}
@@
 	\\&=
-	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{b-1}
+	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell -1}
 	\\&=\ldots\\&=
@@
 \end{equation}
-Therefore, multiplying by the boundary vectors we have 
+Multiplying by the boundary vectors we have 
 \begin{equation}
@@
 \begin{align*}
-	W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 	|V \rangle&=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
@@
 \end{equation}
-Moreover, we have 
+Moreover, we write 
 \begin{equation}
@@
 		\begin{split}
-			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{l}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 		\end{split}
@@
 	\begin{split}
-		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{s_{q_{1}}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,\overbrace{1}^{s_{q_{2}}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
+		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{q_{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
 	\end{split}
@@
 \end{equation}
-and replacing $\Psi^{'}(\bm{s})$ compute above in \eqref{ABS_intermediate} we obtain
+and replacing $\Psi^{'}(\bm{s})$ computed above in \eqref{ABS_intermediate} we obtain
 
@@
 %Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
-Finally, considering all possible occupancy $\bm{s}$, we obtain \eqref{ABS-vect}.
+Finally, considering all possible configurations $\bm{s}$, we obtain \eqref{ABS-vect}.
 \begin{flushright}
@@
 \paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
-The matrix $S_{2}^{-1}$, acting on a single site, is given by
+The matrix $S_{1}^{-1}$, acting on a single site, is given by
 \begin{equation}\label{S1-L1}
@@
 \end{equation}
-indeed, in coordinates $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
-Finally, considering all possible occupations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}.
+indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
+Finally, considering all possible configurations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}.
 \begin{flushright}
@@
 a species with label from $2$ to $N$.
-This is motivated by interest of understanding how actual particles of the chain are correlated among each others and because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{0}^{x}=\nu-\sum_{a=2}^{N}n_{a}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
+This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{1}^{x}=\nu-\sum_{a=2}^{N}n_{a}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
@@
 		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-			f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(y_{k},c_{k},\ldots,c_{m})
+			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
 	\end{equation}
@@
 	\begin{equation}\label{powerCoeffSpecies}
-		g_{k}(y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
+		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
 	\end{equation}
@@
 	\begin{equation}\label{powerCoeffNOspec}
-		f(c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
+		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
 	\end{equation}
@@
 \langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(c_{1},\ldots,c_{m})f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(y_{q},c_{q},\ldots,c_{m})
+f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})
 \end{equation}
@@
 \end{equation}
-Introducing $f(c_{1},\ldots,c_{m})$ and $g_{a}(y_{a},c_{a},\ldots,c_{m})$ we have the formulas for arbitrary correlations.
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we have the formulas for arbitrary correlations.
 \begin{flushright}
@@
 \begin{equation}
-	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(c_{1})f(c_{1})
+	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})
 \end{equation}
@@
 \paragraph{Two points correlations}
-The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{2,\ldots,N\}$ at coordinates $y,x\in \{1,\ldots,L\}$ with $x< y$ reads
-\begin{equation}
-	\begin{split}
-	\langle n_{s_{1}}^{x}n_{s_{2}}^{y}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},c_{2})
+The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{2,\ldots,N\}$ at coordinates $y_{1},y_{2}\in \{1,\ldots,L\}$ with $x< y$ reads
+\begin{equation}
+	\begin{split}
+	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,c_{k},c_{2})
 	\end{split}
@@
 	\begin{split}
-	\langle n_{s_{1}}^{x} n_{s_{2}}^{y}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
 	\end{split}
@@
 \begin{equation}
-    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(c_{k},\ldots,c_{3})
+    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,c_{k},\ldots,c_{3})
 \end{equation}
@@
 \end{equation} 
-for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$.
-It is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.
-\\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
+for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$  and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.
+This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
 For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
@@
 The aim of this section is to give an answer to these questions.
-We first define a more general version with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with the same structure as \eqref{2SpeciesRD}.
-Second we construct the Lie algebraic description and we use it to prove absorbing duality in the general case.
+We first define a more general process with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with N discrete Laplacians and a reaction term.
+Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
 \subsection{The process on a finite graph}
-Considering again a connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
+Considering again a finite and connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
 \begin{equation}\label{RDGenerator}
@@
 where the boundary parameters are defined as
-\begin{equation}
+\begin{equation}\label{boundaryParamRD}
 	\begin{split}
@@
 \end{equation}
-\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ is exactly the one of the multi-species stirring process \eqref{siteGenerator}.
+\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
 We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
@@
 \end{equation}
-where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, $q\neq d$ and $q\neq 1$ .
-Moreover, we have
+where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq 1$ .
+Moreover
 \begin{equation}
@@
 where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
-They evolve according to the Master's equation
+These average occupations evolve according to the Master equation
 \begin{equation}
@@
 \end{equation} 
-Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtaina system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
+Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
 For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
@@
 \begin{equation}\label{reversibilityConditionRD}
-	\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V
+	\alpha_{a}^{x}=\alpha_{a}\quad \forall x\in V\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{2,\ldots,N\}
 \end{equation}
@@
 \begin{equation}
-	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{1}{N}
-\end{equation}
-namely
-\begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\left(\frac{1}{N}\right)^{\sum_{a=1}^{N}n_{a}^{x}}
+	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)
+\end{equation}
+where 
+\begin{equation}
+	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{2,\ldots,N\}\qquad \text{and}\qquad \rho_{1}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}
+\end{equation}
+Namely,
+\begin{equation}
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho_{1}^{n_{1}^{x}}\rho^{\sum_{a=2}^{N}n_{a}^{x}}
 \end{equation}
@@
 \end{equation}
-that is true if and only if $p_{a}=p$ $\forall a\in \{2,\ldots,N\}$.\\
-By similar computation it is possible to show that the same result is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$. \\
-Recalling that, to have reversibility, the reservoirs parameters must fulfil $\rho_{a}^{x}=\rho_{a}$ $\forall x \in V$ and $\forall a\in \{1,\ldots,N\}$, we obtain the result. 
+that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{2,\ldots,N\}$.\\
+By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,y}$.
+\\
+For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}$.
+As a consequence we have the result.
 \subsection{Duality}
@@
 The dual process is defined by its generator, which reads
-\begin{equation}\label{DualGenerator}
-	\widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
+\begin{equation}\label{DualGeneratorRD}
+	\widetilde{\mathcal{L}}^{rd}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
 \end{equation}
@@
 The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
-As we will show this follows from the same $gl(N)$ algebraic structure.
+As we will show this follows from a $gl(N)$ algebraic structure.
 \subsubsection{Proof of duality}
@@
 \end{equation}
-Similarly, we define the dual Hamiltonian $\widetilde{H}^{rd}$.
-For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}.
-\\ We aim to show
+Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$.
+For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
 \begin{equation}\label{DualityRelationRD}
@@
 \end{align}
-Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ are symmetries of $\exp{E^{x}}\exp{E^{y}}$.
+Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ have $\exp{(E^{x})}\exp{(E^{y})}$ as a symmetry.
 The first result will follow from the commutator between $H_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.

### 2023-04-12 main.tex
ii

@@
 
-\section{Integrability}\label{sectionIntegrabiliy}
+\section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
 \subsection{The integrable chain and the matrix product ansatz}
@@
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}.
+
+\section{Steady state for the non-integrable chain}
+In Section \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
+This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations.
+Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+\subsection{Steady state correlations and duality}
+We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads as
+\begin{equation}
+	\mathcal{L}=\mathcal{L}_{1}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{L}
+\end{equation} 
+where at the boundaries 
+\begin{equation}
+	\mathcal{L}_{1}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+while the bulk generator is 
+\begin{equation}
+ \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space
+ \begin{equation}	
+	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}
+\end{equation}
+The dual generator is 
+\begin{equation}
+	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{1}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{L}
+\end{equation} 
+with absorbing boundaries, i.e. 
+\begin{equation}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=\sum_{i=1}^{N}\alpha_{i}\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
+	\end{split}
+\end{equation}
+where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
+\begin{equation}\label{dualityFunctionChain}
+	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{\sum_{i=1}^{N}\beta_{i}}$.\\
+Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
+\begin{equation}\label{ExptationSS}
+	\begin{split}
+		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\\=&
+		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
+	\end{split}
+\end{equation}
+where 
+\begin{equation}\label{Pass}
+	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+\end{equation}
+where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
+Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{s_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
+\begin{equation}
+	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{2,\ldots,N\}$ situated at sites $y_{i}\in\{1,\ldots,L\}$ with $i\in \{1,\ldots,m\}$.
+This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
+The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the one points correlations.
+\paragraph{One point correlations for the non-integrable case}
+We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
+\end{equation}
+Thus
+\begin{equation}\label{OnePtsCORR}
+	\begin{split}
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+	\end{split}
+\end{equation}
+we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
+Therefore, this $a_{s}^{x}(1)$ fulfils the following equations
+\begin{equation}\label{gamblers-ruin}
+	\begin{cases}
+		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
+		a^{1}_{s}(1)=\frac{A}{1+A}+a^{2}_{s}(1)\frac{1}{1+A}\\
+		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+B}
+	\end{cases}
+\end{equation}
+where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where, for the sake of notation, we call $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$.
+The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
+\end{equation}
+\textbf{Remark}: In case $A=B=1$ we have 
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+\end{equation}
+that gives back \eqref{one-pts-corr}.
 \section{Multi-species stirring process with reaction}
@@
 \textbf{FROM HERE ON-WARDS STILL TO CHECK}\\
+\begin{comment}
 \subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}
@@
 	\end{equation}
-that gives back \eqref{one-pts-corr}.  \\ 
+that gives back \eqref{one-pts-corr}.  
+\end{comment}
 \subsection{Mapping to equilibrium?}

### 2023-04-13 main.tex
i
Update main.tex

@@
 \end{equation}
-Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$. 
+Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
+acting trivially as the identity on the other sites). 
 Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
@@
 $(a^{\dagger})_{a}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $a\in\{2,\ldots,N\}$. \\
-We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation} where the duality matrix $D$ is described as 
+We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. The duality matrix $D$ is described as 
 \begin{equation}\label{dualityMatrix}
@@
 and
-\begin{equation}\label{Rmatrix}
+\begin{equation}\label{Revmatrix}
     R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
@@
 We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
-{\color{red} We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the the fundamental representation of the algebra.} \\
+We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e.
+$(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in  the fundamental representation of the algebra.
 The Hamiltonian is
@@
 \end{equation}
-where we assume that the parameters satisfy
+where, without loss of generality,  we assume that the parameters satisfy
 \begin{equation}\label{ratesConditions}
@@
 \end{equation}
-Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact}). \\
-For what concerns duality, in this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain.
-Moreover, the matrix $R_{x}$ reduces to the identity.
-Therefore, the duality matrix reads as
+Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method). \\
+\paragraph{Duality.} 
+In this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain. Moreover, the matrix $R_{x}$ defined in \eqref{Revmatrix} 
+reduces to the identity which implies $e_{ab}^T= e_{ba}$. Therefore, the duality matrix reads
 \begin{equation}
@@
 \end{equation}
-In the long-time horizon, the dual process voids the chain, and all particles are eventually absorbed at extra-site $0$ or $L+1$.
-\paragraph{Matrix Product Ansatz (MPA)} Matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we recall its main points.\\
- Calling $|\Psi(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
+In the long-time limit, the dual process voids the chain, and all particles are eventually absorbed at the extra-sites $0$ and $L+1$.
+\paragraph{Matrix Product Ansatz (MPA).} The matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
+ Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
  the Master equation
@@
 \end{equation}
-This Markov chain is positive recurrent, therefore there exist a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial distribution. 
-We denote by $|\Psi\rangle$ the column vector that contains the probabilities of every configuration of the chain with respect to this unique stationary distribution.
-This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e.
-it solves
+This Markov chain is positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial distribution. 
+We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution. This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
 \begin{equation}
@@
 The MPA gives an abstract form of the steady state in terms of an algebra of operators.
-However, to write explicitly the steady state one should know a representation of this algebra.
-Another approach is to directly use the commutators and figure out correlations from them.
-This path has been followed in \cite{vanicat2017exact} to compute one and two points correlations.
-However, it is interesting to put effort in this direction and look for explicit form of arbitrary correlations.
-We will carry out this aim by the use of duality, proved in Section \ref{sectionDuality}.
-The idea is summarized in the following.
-We define a sequence of similarity transformation such that
+However, to write explicitly the steady state one should provide a representation of this algebra.
+Another approach is to directly use the commutators and compute the steady-state correlations using the commutation relations and the boundary actions.
+This path has been followed in \cite{vanicat2017exact} to compute one-point and two-point correlations.
+Here we follow the approach of working with the abstract commutation  relations.
+We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the actual
+computation. The idea is summarized as follows. We define a sequence of similarity transformation such that 
 \begin{equation}
@@
 \end{equation} 
-where $\mathcal{S}_{1}$ makes $H^{'}$ with both diagonal boundaries and $\mathcal{S}_{2}$ makes $H^{''}$ with left triangular boundary and right diagonal one.
-Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{rightBoundary}, \eqref{leftBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
-Then, reversing the transformations we will retrieve $|\Psi\rangle$.\\
+where $H^{'}= \mathcal{S}_{1} H \mathcal{S}_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = \mathcal{S}_{2}H' \mathcal{S}_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal.
+Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
+Then, reversing the transformations we will retrieve $|\Psi\rangle$.
+
 The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix.
@@
 Therefore, $H^{'}$ is not stochastic.
-This informally explains the role of duality.
 The second transformation $\mathcal{S}_{2}$ diagonalize the right boundary.
-This allows to simplify a lot the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.
-\\
+The composition  $\mathcal{S}_{2} \mathcal{S}_{1}$ allows to simplify the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.
+
 The computation are organized as follows: we first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$.
@@
 \end{comment}
-\subsubsection{The similarity transformation}\label{subsectionSTransf}
+\subsubsection{The similarity transformations}\label{subsectionSTransf}
 We introduce the first transformation as
@@
 \begin{equation}
-\mathcal{S}_{1}=\mathbbm{1}_{0}\otimes \prod_{x=1}^{L}d_{x}^{T}\otimes \mathbbm{1}_{L+1}
+\mathcal{S}_{1}=\prod_{x=1}^{L}d_{x}^{T}
 \end{equation}
@@
 \end{equation}
-that is similar to $H$ via $\mathcal{S}_{1}$, i.e. 
+that is related to $H$ by
 \begin{equation}\label{similarV}
@@
 \end{equation}
-The boundary Hamiltonians $B_{1}^{'}$ and $B_{L}^{'}$ are $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$ without the extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$ and $(a^{\dagger})_{a}^{L+1}$, i.e.
-\begin{equation}
-	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}E_{1a}^{1}-E_{aa}^{1}\right)\qquad B^{'}_{1}=\sum_{a=2}^{N}\left(\beta_{a}E_{1a}^{L}-E_{aa}^{L}\right)
-\end{equation}
-Therefore, we can conclude that $H^{'}$ is $\widetilde{H}^{T}$ in which the extra-site parts have been removed and replaced by identities. \\
-The steady state $|\Psi^{'}\rangle$ of $H^{'}$ fulfils the equation
-\begin{equation}
-	H^{'}|\Psi^{'}\rangle=0
-\end{equation}
-then, it is easy to see that 
+The boundary Hamiltonians $B_{1}^{'}$ and $B_{L}^{'}$ relates to the transposed of  $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian},
+they are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp.
+$(a^{\dagger})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp.
+$\beta_a$):
+\begin{equation}
+	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad B^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+\end{equation}
+Obviously
 \begin{equation}\label{S1-Inverse}
@@
 \end{equation}
+where $|\Psi^{'}\rangle$ satisfies $H^{'}|\Psi^{'}\rangle=0$.
+
 We introduce the second transformation as 
@@
 \end{equation}
-that is similar to $H^{'}$ by $S_{2}$, i.e.
+that is related to $H'$ by
 \begin{equation}
@@
 
-\section{Steady state for the non-integrable chain}
+\section{Non-integrable chain}
 In Section \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
@@
 	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
 	\end{split}
@@
 \end{comment}
-\subsection{Mapping to equilibrium?}
+\section{Mapping to equilibrium?}
 {\color{red}
@@
 \cite{Sklyanin:1988yz}
-\subsubsection{Quantum inverse scattering method}
+\subsection{Quantum inverse scattering method}
 We can apply the \textit{quantum inverse scattering method} to this process.

### 2023-04-14 main.tex
hadamard

@@
 	\begin{split}
-		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
+		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
 	\end{split}
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
+\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
  \end{equation}
@@
 \begin{equation}\label{hamiltonianCasimir}
-	H_{x,y}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
+	\mathcal{H}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
 \end{equation}
@@
 \begin{equation}\label{edgeHamiltonian}
-H_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
+\mathcal{H}_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
  \end{equation}
@@
 \begin{equation}
-	H_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
+	\mathcal{H}_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
 \end{equation}
@@
 \begin{equation}\label{DualHamiltonian}
-    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
-\end{equation}
-where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
+    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
+\end{equation}
+where $\mathcal{H}_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
 \begin{equation}\label{siteDualHamiltonian}
@@
 \begin{equation}\label{edgeDualRealtion}
-    H_{x,y}^{T}D=DH_{x,y}\qquad \forall (x,y)\in \mathcal{E}
+    \mathcal{H}_{x,y}^{T}D=D\mathcal{H}_{x,y}\qquad \forall (x,y)\in \mathcal{E}
 \end{equation}
@@
 \paragraph{Proof of \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'.
-First the existence of a similarity transformation between the Hamiltonian $H_{x,y}$  and its transposed.
+First the existence of a similarity transformation between the Hamiltonian $\mathcal{H}_{x,y}$  and its transposed.
 As we will show, this similarity transformation is $R_{x}R_{y}$.
@@
 As we will see, this symmetry is $\sum_{a=2}^{N}E_{a1}$ \\
-We first look for the similarity between $H_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain
+We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain
 
 \begin{equation}\label{transpositionPropertyH}
-    H_{x,y}^{T}=\left(R_{x}R_{y}\right)H_{x,y}\left(R_{x}R_{y}\right)^{-1}
-\end{equation}
-therefore we have found the similarity transformation between $H_{x,y}$ and its transposed. \\
-We now look for a symmetry of $H_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
-\begin{equation}
-	H_{x,y}S_{x,y}=S_{s,y}H_{x,y}\quad \Leftrightarrow \quad [H_{x,y},S_{x,y}]=0
-\end{equation}
-Using \eqref{hamiltonianCasimir}, we observe that $H_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term.
+    \mathcal{H}_{x,y}^{T}=\left(R_{x}R_{y}\right)\mathcal{H}_{x,y}\left(R_{x}R_{y}\right)^{-1}
+\end{equation}
+therefore we have found the similarity transformation between $\mathcal{H}_{x,y}$ and its transposed. \\
+We now look for a symmetry of $\mathcal{H}_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
+\begin{equation}
+	\mathcal{H}_{x,y}S_{x,y}=S_{s,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
+\end{equation}
+Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term.
 Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$.
@@
 \begin{equation}\label{symmetryH}
-	\left[S_{x,y},H_{x,y}\right]=0
-\end{equation}
-i.e. it is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write
+	\left[S_{x,y},\mathcal{H}_{x,y}\right]=0
+\end{equation}
+i.e. it is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write
 
 \begin{comment}
-As already pointed out, $H_{x,y}$ is a linear function of $\Delta(C_{2})$.
-This implies that symmetries of  $\Delta(C_{2})$ are also symmetries of  $H_{x,y}$.
+As already pointed out, $\mathcal{H}_{x,y}$ is a linear function of $\Delta(C_{2})$.
+This implies that symmetries of  $\Delta(C_{2})$ are also symmetries of  $\mathcal{H}_{x,y}$.
 Moreover, the coproduct is a Lie algebra homomorphism, i.e.
@@
 \begin{equation}\label{symmetryH}
-    \left[S_{x,y},H_{x,y}\right]=0
-\end{equation}
-i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write
+    \left[S_{x,y},\mathcal{H}_{x,y}\right]=0
+\end{equation}
+i.e. $S_{x,y}$ is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write
 \end{comment}
@@
     \begin{split}
-        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
-        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
-        \\&=
-        DH_{x,y}
+        \mathcal{H}_{x,y}^{T}D&=(R_{x}R_{y})\mathcal{H}_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
+        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)\mathcal{H}_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
+        \\&=
+        D\mathcal{H}_{x,y}
     \end{split}
@@
  \end{align*}
+in short
+\begin{equation}\label{HadTransfBoundary}
+\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+\end{equation}
 Thus, we rewrite \eqref{intermediateTransposeSite} as
@@
 \begin{equation}\label{hamiltonian}
-	H=B_{1}+H_{bulk}+B_{L}
+	H=H_{1}+H_{bulk}+H_{L}
 \end{equation}
@@
 \begin{equation}
-	B_{1}=\begin{pmatrix}
+	H_{1}=\begin{pmatrix}
 		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
@@
 \begin{equation}
-	B_{L}=\begin{pmatrix}
+	H_{L}=\begin{pmatrix}
 		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
@@
 In this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain. Moreover, the matrix $R_{x}$ defined in \eqref{Revmatrix} 
-reduces to the identity which implies $e_{ab}^T= e_{ba}$. Therefore, the duality matrix reads
+reduces to the identity which implies 
+\begin{equation}\label{transpostionPropertyFund}
+e_{ab}^T= e_{ba}
+\end{equation}
+ Therefore, the duality matrix reads
 \begin{equation}
@@
 \begin{equation}
-	\widetilde{H}=\widetilde{H}_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+\widetilde{H}_{L+1}
+	\widetilde{H}=\widetilde{H}_{1}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{L}
 \end{equation}
@@
 \end{equation}
-\newline
+Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
+\newline \newline
 \textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$:
@@
 \begin{equation}
-	H\;\xrightarrow{\mathcal{S}_{1}}\;H^{'}\;\xrightarrow{\mathcal{S}_{2}}\;H^{''}
-\end{equation} 
-where $H^{'}= \mathcal{S}_{1} H \mathcal{S}_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = \mathcal{S}_{2}H' \mathcal{S}_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal.
-Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
+	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}
+\end{equation} 
+where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal.
+Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the right eigenvector with vanishing eigenvalue $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
 Then, reversing the transformations we will retrieve $|\Psi\rangle$.
 
-The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix.
-Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
+The first transformation $S_{1}$ is closely related to the dual matrix.
+Moreover, we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
 Therefore, $H^{'}$ is not stochastic.
-The second transformation $\mathcal{S}_{2}$ diagonalize the right boundary.
-The composition  $\mathcal{S}_{2} \mathcal{S}_{1}$ allows to simplify the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.
-
-The computation are organized as follows: we first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$.
-Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators.
-Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.
+The second transformation $S_{2}$ diagonalize the right boundary.
+The composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.
+
+The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
+Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ thanks to the simpler commutators.
+Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and the steady state of $H$.
 
@@
 \subsubsection{The similarity transformations}\label{subsectionSTransf}
+Consider the matrices
+\begin{align}
+	\mathcal{S}_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}\label{S1Gen}\\
+	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}\label{S2Gen}
+\end{align}
 We introduce the first transformation as
 \begin{equation}\label{transformationV}
- S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
-\end{equation}
-Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
-By taking the tensor product over the chain we define
-\begin{equation}
-    \mathcal{S}_{1}=S_{1}^{\otimes L}
+ \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=2}^{N}e_{1a}^{x}\right)}%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+\end{equation}
+that is composed by a copy of $\mathcal{S}_{1}$ acting at site $x$ and with identities acting at all other sites of the chain. 
+Observe that $\mathcal{S}_{1}^{x}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
+By taking the product over the chain we define
+\begin{equation}
+    S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}
 \end{equation}
@@
 \begin{equation}
-\mathcal{S}_{1}=\prod_{x=1}^{L}d_{x}^{T}
-\end{equation}
- This $\mathcal{S}_{1}$ is invertible, then we introduce 
+S_{1}=\prod_{x=1}^{L}d_{x}^{T}
+\end{equation}
+ This $S_{1}$ is invertible, then we introduce 
 \begin{equation}\label{hatHamiltonian}
-   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
+   H^{'}:=H^{'}_{1}+H_{bulk}+H^{'}_{L}
 \end{equation}
@@
 \begin{equation}\label{similarV}
-   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
-\end{equation}
-The boundary Hamiltonians $B_{1}^{'}$ and $B_{L}^{'}$ relates to the transposed of  $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian},
-they are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp.
+   H^{'}=S_{1}H^{'}S_{1}^{-1}
+\end{equation}
+The bulk part of the Hamiltonian is left unchanged while the boundaries are given by 
+\begin{equation}
+	H^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+\end{equation}
+Indeed, using \eqref{HadTransfBoundary}, \eqref{ratesConditions} and \eqref{transpostionPropertyFund}, we obtain for the left boundary
+\begin{equation}
+	\begin{split}
+		H_{1}^{'}&=S_{1}H_{1}S_{1}^{-1}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}
+		\\&=
+		\left\{\exp{\left(-\sum_{c=2}^{N}e_{c1}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ba}^{1}-e_{bb}^{1}\right)\exp{\left(\sum_{c=2}^{N}e_{c1}^{1}\right)}\right\}^{T}
+		\\&=
+		\sum_{a=2}^{N}\left(\alpha_{a}e_{1a}^{1}-e_{aa}^{1}\right)^{T}
+		\\&=
+		\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)
+	\end{split}
+\end{equation}
+Similarly, for the right boundary we have 
+\begin{equation}
+H_{1}^{'}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+\end{equation}
+\textbf{Remark:} the boundary Hamiltonians $H_{1}^{'}$ and $H_{L}^{'}$ relates to the transposed of  $\widetilde{H}_{1}$ and $\widetilde{H}_{L}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
+They are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp.
 $(a^{\dagger})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp.
-$\beta_a$):
-\begin{equation}
-	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad B^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
-\end{equation}
+$\beta_a$).
+\newline\newline
 Obviously
 \begin{equation}\label{S1-Inverse}
-	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
+	|\Psi\rangle =S_{1}^{-1}|\Psi^{'}\rangle
 \end{equation}
@@
  \begin{equation}
- 	S_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
- \end{equation}
-By taking the tensor product over the chain we also define
-\begin{equation}
-	\mathcal{S}_{2}=S_{2}^{\otimes L}
-\end{equation}
-We introduce 
-\begin{equation}
-	H^{''}=B_{1}^{''}+H_{bulk}+B_{L}^{''}
+ 	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
+ \end{equation}
+that is composed by a copy of $\mathcal{S}_{2}$ acting at site $x$ and with identities acting at all other sites of the chain. 
+By taking the product over the chain we also define
+\begin{equation}
+	S_{2}=\prod_{x=1}^{L}S_{2}^{x}
+\end{equation}
+We define 
+\begin{equation}
+	H^{''}=H_{1}^{''}+H_{bulk}+H_{L}^{''}
 \end{equation}
@@
 \begin{equation}
-	H^{'}=\mathcal{S}_{2}^{-1}H^{''}\mathcal{S}_{2}
+	H^{''}=S_{2}H^{'}S_{2}^{-1}
 \end{equation}
 The boundary Hamiltonians of $H^{''}$ reads
-\begin{equation}
-	B_{1}^{''}=e_{11}-\mathbbm{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}\qquad B_{L}^{''}=e_{11}-\mathbbm{1}
-\end{equation}
-i.e. the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal. 
-The steady state of $|\Psi^{''}\rangle$ of $H^{''}$ solves 
+\begin{align}
+	H_{1}^{''}=e_{11}^{1}-\mathbbm{1}^{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}^{1}\qquad H_{L}^{''}=e_{11}^{L}-\mathbbm{1}^{L}
+\end{align}
+i.e.
+the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal.
+The expressions of $H_{1}^{''}$ and $H_{L}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=2}^{N}\beta_{c}e_{c1}$ and $A=e_{a1},$ and $A=e_{aa}$.
+We compute
+\begin{enumerate}
+	\item $A=e_{a1}$ with $a\neq 1$
+	\begin{equation}
+		\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}\right)}e_{a1}\exp{\left(\sum_{c=2}^{N}\beta_{c}e_{c1}\right)}=e_{a1}
+	\end{equation}
+\item $A=e_{aa}$ with $a\neq 1$
+\begin{equation}
+		\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{x}\right)}e_{aa}^{x}\exp{\left(\sum_{c=2}^{N}\beta_{c}e_{c1}^{x}\right)}=e_{aa}^{x}+\beta_{a}e_{a1}^{x}
+	\end{equation}
+Indeed 
+\begin{equation}
+	\sum_{c=2}^{N}[e_{c1},e_{aa}]=\sum_{c=2}^{N}\beta_{c}\left(e_{ca}\delta_{a1}-e_{a1}\delta_{ca}\right)=-\beta_{a}e_{a1}
+\end{equation}
+\end{enumerate}
+Therefore, we have for the left boundary
+\begin{equation}
+	\begin{split}
+		H_{1}^{''}&=S_{2}H_{1}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}
+		\\&=
+		\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}-\beta_{a}e_{a1}^{1}\right)
+		\\&=
+		e_{11}^{1}-\mathbbm{1}^{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}^{1}
+	\end{split}
+\end{equation}
+Similarly, for the right boundary
+\begin{equation}
+	\begin{split}
+			H_{1}^{''}&=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}
+			\\&=
+			\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}-\beta_{a}e_{a1}^{L}\right)=
+			\\&=
+			e_{11}^{L}-\mathbbm{1}^{L}
+	\end{split}
+\end{equation}
+Obviously
+\begin{equation}\label{S2-Inverse}
+	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
+\end{equation}
+and $|\Psi^{''}\rangle$ solves
 \begin{equation}
@@
 \end{equation}
-and it is related to $|\Psi^{'}\rangle$ by 
-\begin{equation}\label{S2-Inverse}
-	|\Psi^{'}\rangle = \mathcal{S}_{2}^{-1}|\Psi^{''}\rangle
-\end{equation}
-It is convenient to introduce also the similarity between $H$ and $H^{''}$, such that
+It is convenient to introduce also the transformation
+\begin{equation}\label{similarity}
+	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}\exp{\left(\sum_{a=2}^{N}e_{a1}^{x}\right)}
+\end{equation}
+This matrix $S$ connects $H$ with $H^{''}$ by 
 \begin{equation}
@@
 \end{equation}
-where 
-\begin{equation}\label{similarity}
-	S=S_{2}S_{1}=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}
-\end{equation}
-and 
-\begin{equation}
-	\mathcal{S}=S^{\otimes L}
-\end{equation}
-This transformation connect the steady states of $H$ and $H^{''}$ by 
+and, obviously
 \begin{equation}
@@
 \end{comment}
-\subsubsection{The steady state of $H^{''}$}\label{subsectionSSHsec}
+\subsubsection{Explicit formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
 We state the following result: the steady state of the Hamiltonian $H^{''}$ is given by 
@@
 \end{flushright}
-\subsubsection{The steady state of $H^{'}$}\label{subsectionSSdual}
+\subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
 Knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
@@
 \end{equation}
-\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $\mathcal{S}_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
-The matrix $S_{2}^{-1}$, acting on a single site, is given by
-\begin{equation}
-   S_{2}^{-1}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}
+\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
+Here is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
+This matrix $\mathcal{S}_{2}$ is given by
+\begin{equation}
+   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
@@
     	\begin{split}
-    		\mathcal{S}_{2}^{-1}=\left(S_{2}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
     		\\&+\left.
@@
     \begin{equation}
-    	S_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
+    	\mathcal{S}_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
     \end{equation}
@@
 \begin{align*}
-    	\left(S_{2}^{\otimes L}\right)^{-1}\otimes S_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
     	\\&+\left.
@@
     	\\&=
-    	\left(S_{2}^{\otimes L+1}\right)^{-1}
+    	\left(\mathcal{S}_{2}^{\otimes L+1}\right)^{-1}
 \end{align*}
@@
 \end{comment}
-The product $\mathcal{S}_{2}^{-1}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{s})$. 
-To find these elements we need to fix the rows correspondent to $\bm{s}$ in the matrix $\mathcal{S}_{2}^{-1}$.
+The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{s})$. 
+To find these elements we need to fix the rows correspondent to $\bm{s}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
 Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
@@
 	\begin{split}
-	(\mathcal{S}_{2}^{-1})_{\bm{s}}=\left(S_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
+\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
   \\&+
@@
 	\begin{split}
-		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{q_{1}}\\&+
+		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{q_{1}}\\&+
 		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
@@
 
-\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $\mathcal{S}_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
-The matrix $S_{1}^{-1}$, acting on a single site, is given by
+\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
+This matrix $\mathcal{S}_{1}$ is given by
 \begin{equation}\label{S1-L1}
-	S_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+	\mathcal{S}_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
 \end{equation}
@@
 	\begin{split}
-		\mathcal{S}_{1}^{-1}=\left(S_{1}^{\otimes L}\right)^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
+		\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
 		\\&
@@
 \begin{align*}
-\left(S_{1}^{\otimes L}\right)^{-1}\otimes S_{1}^{-1}&=
+\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
 \sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
@@
 \end{comment}
-The product $\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{s})$. 
+The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{s})$. 
 To find this elements we need to fix the rows correspondent to $\bm{s}$. Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
@@
     \begin{split}
-        \mathcal{S}_{1}^{-1}{\bm{s}}|\Psi{'}\rangle&=\Psi{'}(s_{1},\ldots,s_{L})+ 
+        \left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{s}}|\Psi{'}\rangle&=\Psi{'}(s_{1},\ldots,s_{L})+ 
         \\&
@@
 \end{flushright}
-\subsection{Exact correlations}\label{correlation-section}
+\subsection{Exact steady state correlations}\label{correlation-section}
 In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e.
@@
 \end{flushright}
-\subsubsection{Explicit examples of correlations}
+\subsubsection{Explicit examples of steady state correlations}
 We give some examples of correlations applying formula \eqref{exactCorrelations}.
@@
 \begin{equation}
-	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}H_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}H_{x,y}^{c}+(\Upsilon-2\sigma_{12})H_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
-\end{equation}
-where $H_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
-\begin{equation}
-	H_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
+	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}\mathcal{H}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+\end{equation}
+where $\mathcal{H}_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
+\begin{equation}
+	\mathcal{H}_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
 \end{equation}
@@
 \begin{equation}
-	H_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
+	\mathcal{H}_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
 \end{equation}
@@
 \begin{align}
-	(H_{x,y}^{rd})^{T}D&=DH_{x,y}^{rd}\label{edgeDualityRelationRD}\\
+	(\mathcal{H}_{x,y}^{rd})^{T}D&=D\mathcal{H}_{x,y}^{rd}\label{edgeDualityRelationRD}\\
 	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
@@
 where the duality matrix $D$ is again \eqref{dualityMatrix}.
-As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $H_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}H_{x,y}^{c}$ and $H_{x,y}^{m}$.
+As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $\mathcal{H}_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$.
 Therefore, we only need to show that
 \begin{align}
-	&(H_{x,y}^{c})^{T}D=DH_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
-	&(H_{x,y}^{m})^{T}D=DH_{x,y}^{m}\label{mDualityRelation}
+	&(\mathcal{H}_{x,y}^{c})^{T}D=D\mathcal{H}_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
+	&(\mathcal{H}_{x,y}^{m})^{T}D=D\mathcal{H}_{x,y}^{m}\label{mDualityRelation}
 \end{align}
-Since the matrix $R_{x}$ is the same, we shall show that $H_{x,y}^{c}$ and $H_{x,y}^{m}$ have $\exp{(E^{x})}\exp{(E^{y})}$ as a symmetry.
-The first result will follow from the commutator between $H_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
+Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$ have $\exp{(E^{x})}\exp{(E^{y})}$ as a symmetry.
+The first result will follow from the commutator between $\mathcal{H}_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
-The second result will follow from the commutator between $H_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
+The second result will follow from the commutator between $\mathcal{H}_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
 \begin{equation}
@@
 \begin{equation}
-H_{x,y}=\sum_{a,l=1}^{N}\left(e_{al}\otimes e_{la}-e_{ll}\otimes e_{aa}\right)
+\mathcal{H}_{x,y}=\sum_{a,l=1}^{N}\left(e_{al}\otimes e_{la}-e_{ll}\otimes e_{aa}\right)
  \end{equation}

### 2023-04-16 main.tex
ii
ll
z

@@
 In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}.
-We will then exploit this last result and the duality, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
+{\color{red}
+The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(n)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
+Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
+}
+We will exploit   the duality and th underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
 The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator.
@@
  Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 
-\begin{align*}
-    &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
-    \\&=
+\begin{align}
+    &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}\nonumber
+    \\&=\nonumber
     \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}(E_{c1}^{x})-\sum_{c=2}^{N}(E_{ca}^{x})-E_{11}^{x}+
-    \sum_{c=2}^{N}(E_{c1}^{x})\right)\\&+\alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
-    \\&=\sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=
+    \sum_{c=2}^{N}(E_{c1}^{x})\right)
+    \\&+\nonumber
+    \alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
+    \\&=\nonumber
+    \sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=
     \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
-    \\&=
+    \\&=\nonumber
     \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
@@
     \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
- \end{align*}
+ \end{align}
 in short
@@
 	\end{equation} 
+	\com{Double check this. Sum looks strange}
 and where
@@
 \begin{align}\label{three-pts-corr}
-        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
+        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
         \\&+\nonumber
-        \frac{(L-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
+        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
         \\&+\nonumber
@@
 \end{align}
+The third cumulant is given by 
+\begin{align*}
+	\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
+\end{align*}
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}.

### 2023-04-16 main.tex
s

@@
 }
-We will exploit   the duality and th underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
+We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
 The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator.

### 2023-04-17 main.tex
thermalization

@@
 \end{equation}
-that is composed by a copy of $\mathcal{S}_{1}$ acting at site $x$ and with identities acting at all other sites of the chain. 
+that is composed by a copy of $\mathcal{S}_{1}$ (introduced in \eqref{S1Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
 Observe that $\mathcal{S}_{1}^{x}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
@@
  \begin{equation}
- 	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
- \end{equation}
-that is composed by a copy of $\mathcal{S}_{2}$ acting at site $x$ and with identities acting at all other sites of the chain. 
+ 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
+ \end{equation}
+that is composed by a copy of $\mathcal{S}_{2}$ (introduced in \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
 By taking the product over the chain we also define
@@
 \begin{equation}
-H=\mathcal{S}^{-1}H^{''}\mathcal{S}
+H=S^{-1}H^{''}S
 \end{equation}
@@
 \begin{equation}
-	|\Psi\rangle=\mathcal{S}^{-1}|\Psi^{''}\rangle
+	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle
 \end{equation}
@@
 		\begin{split}
-			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+			\Psi^{'}(\bm{s})=\sum_{c_{1}=0}^{\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 		\end{split}
@@
     \begin{split}
-        \Psi(\bm{s})&=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+        \Psi(\bm{s})&=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
         \\&+
@@
 \begin{equation}\label{dualityFunctionChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
 \end{equation}
@@
 that gives back \eqref{one-pts-corr}.
+\subsection{Instantaneous thermalization}
+In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}).
+The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles.
+The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\bm{\epsilon}=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\bm{\epsilon}$.
+\subsubsection{The thermalization measure}
+As already mentioned, we will redistribute particles on a bond according to a probability measure that is the reversible one \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond.
+We denote
+\begin{equation}
+	\begin{split}
+	\nu_{TH}(\bm{r}|\bm{\epsilon}):&=\mathbb{P}\left(n^{x}=\bm{r}|\eta^{x}+n^{x+1}=\bm{\epsilon}\right)
+	\\&
+	=\mathbb{P}\left((n_{1}^{x},\ldots,n_{N}^{x})=
+	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)
+	\end{split}
+\end{equation}
+where
+\begin{equation}
+	\epsilon_{1}=2\nu-\sum_{a=2}^{N}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=2}^{N}r_{a}
+\end{equation}
+We construct this measure.
+Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
+\begin{equation}
+	\begin{split}
+\nu_{TH}(\bm{r}|\bm{\epsilon})&=\frac{\mathbb{P}\left(\left\{n^{x}=\bm{r}\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\bm{\epsilon}\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}=\frac{\mathbb{P}\left(n^{x}=\bm{r}\right)\,\mathbb{P}\left(n^{x+1}=\bm{\epsilon}-\bm{r}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}
+	\end{split}
+\end{equation}
+Moreover, it holds that 
+\begin{equation}
+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
+\end{equation}
+Therefore 
+\begin{equation}
+	\begin{split}
+	\nu_{TH}(\bm{r}|\bm{\epsilon})=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
+	\end{split}
+\end{equation}
+where we denote the multinomial coefficient
+\begin{equation}
+	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}
+\end{equation}
+provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
+\subsubsection{Thermalized multi-species stirring process}
+The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace} and its generator reads
+\begin{equation}\label{thermalizedGenerator}
+	\mathcal{L}^{TH}=\mathcal{L}_{1}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{L}^{TH}
+\end{equation}
+where 
+\begin{equation}\label{bulkThermalized}
+	\begin{split}
+	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}
+	\\&
+	\left\{f(n^{1},\ldots,n^{x-1},\bm{r},n^{x}+n^{x+1}-\bm{r},n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
+	\end{split}
+\end{equation}
+while
+\begin{equation}\label{boundaryThermalized}
+	\begin{split}
+		\mathcal{L}_{1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}
+		\end{split}
+	\end{equation}
+The right boundary generator is defined in a similar way. The $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
+\subsubsection{The dual thermalized process}
+The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
+\begin{equation}
+		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{1}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{L}^{TH}
+\end{equation}
+where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{1}^{TH}$ and $\widetilde{\mathcal{L}}_{L}^{TH}$ are absorbing with rate $1$, i.e. 
+\begin{equation}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{1}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
+	\end{split}
+\end{equation}
+and similarly $\widetilde{\mathcal{L}}_{L}^{TH}$. 
+The duality function is 
+\begin{equation}
+	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+The proof of the duality consists in proving 
+\begin{align}
+	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
+	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
+\end{align}
+Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
+To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function.
+For the sake of notation, we introduce
+\begin{equation}
+	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+\end{equation}
+First, we act with $\mathcal{L}_{1}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
+\begin{align}\label{ProvaBordoTH}
+	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\\&\nonumber
+	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\\&
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}
+\end{align}
+Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
+\begin{align}\label{pezzo1}
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
+	\\&\nonumber
+	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}\\=&
+	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
+\end{align}
+Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
+\begin{equation}\label{pezzo2}
+	\begin{split}
+	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
+	\end{split}
+\end{equation}
+Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
+\begin{align}
+	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\\&=
+	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+\end{align}
 \section{Multi-species stirring process with reaction}

### 2023-04-18 main.tex
figure
ii
i

@@
     \centering
-    \includegraphics[scale=0.6]{Dyn_stir.eps}
-    \caption{The edge dynamics}
+    \includegraphics[scale=0.45]{BulkStirring.eps}
+    \caption{The edge dynamics.
+Maximal occupation is $\nu=6$.
+A particle of type "square" is removed in $x$ and placed in $y$.
+A particle of type "triangle" is removed in $y$ and placed in $x$.
+This transition occurs at rate $n_{square}^{x}n_{triangle}^{y}=2\cdot 3$.}
     \label{fig:1}
@@
     \centering
-    \includegraphics[scale=0.88]{Dyn_stir_bordo.eps}
-    \caption{The site dynamics}
+    \includegraphics[scale=0.4]{BoundaryStirring.eps}
+    \caption{The site dynamics.
+Here the maxiaml occupation is $\nu=6$.
+The reservoir, represented by a square "box" containing all types of particles, remove a type "square" from site $x$ and replace it with a type "triangle".
+This transition occurs at rate $\alpha_{triangle}^{x}n_{square}^{y}$.}
     \label{fig:2}
@@
 \end{equation}
-Therefore, we obtain the second cumulant, i.e. the second truncated correlation as 
+Therefore, we obtain the second cumulant, i.e. the two-point connected correlation as 
 \begin{equation}\label{two-pts-corr}
 	\begin{split}
-		\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
+		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
 	\end{split}
@@
 \end{align}
-The third cumulant is given by 
-\begin{align*}
-	\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
-\end{align*}
+Therefore, we obtain the third cumulant, i.e. the three-point connected correlation as 
+\begin{align}
+	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
+	\\&=
+	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
+\end{align}
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}.

### 2023-04-18 main.tex
ll
i

@@
 \newcommand{\oa}{\mathbf{a}}
-\newcommand{\dd}{\mathcal{D}_{\widehat{x}}}
+\newcommand{\dd}{\mathcal{D}_{u(x)}}
 \newcommand{\oad}{\mathbf{a}^{\dagger}}
@@
 This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $a$.
+For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$.
 See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 
@@
 \end{equation}
-To each site $x\in V$ we associate an ``extra site'', denoted $\widehat{x}$,
+To each site $x\in V$ we associate an ``extra site'', denoted $u(x)$,
 where dual particles will accumulate in the course of time. 
@@
 \begin{equation}
-    \bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
-\end{equation}
-where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
-the extra-site $\widehat{x}$ connected to $x\in V$.
+    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
+\end{equation}
+where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+the extra-site $u(x)$ connected to $x\in V$.
 
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\,\right)
 \end{equation}
@@
 \begin{equation}
-\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
+\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}
 \end{equation}
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}r_{a}^{x}\left(f(\bm{\xi}-\delta_{a}^{x}+\delta_{1}^{x}+\delta_{a}^{\widehat{x}})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=2}^{N}\xi_{a}^{x}\left(f(\bm{\xi}-\delta_{a}^{x}+\delta_{1}^{x}+\delta_{a}^{u(x)})-f(\bm{\xi})\right)
 \end{equation}
@@
 On the other hand, the site
-part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $a$ at the extra-site $\widehat{x}$.
-This last transition is performed with rate $\sum_{i=1}^{N}\alpha_{i}^{x}r_{a}^{x}$.
+part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $a$ at the extra-site $u(x)$.
+This last transition is performed with rate $|\alpha^{x}|\xi_{a}^{x}$.
 This means that eventually the dual process voids the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites.
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}\right)^{\sum_{x\in V}r_{a}^{x}+\sum_{x\in V}m_{a}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}m_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 \begin{equation}
-    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|r_{1}^{x},\ldots,r_{N}^{x}\rangle\otimes |m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle\right)
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)
 \end{equation}
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{\widehat{x}}\,E_{1a}^{x}-E_{aa}^{x}\right)
+    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{u(x)}\,E_{1a}^{x}-E_{aa}^{x}\right)
 \end{equation}
 Here we introduced bosonic creation operator $a^{\dagger}$ acting as $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(a^{\dagger})_{a}^{\widehat{x}}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $\widehat{x}$ and on the species $a\in\{2,\ldots,N\}$. \\
+$(a^{\dagger})_{a}^{u(x)}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{2,\ldots,N\}$. \\
 We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. The duality matrix $D$ is described as 
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\dd=\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
 We perform the duality proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
-As a preliminary result we show the following property 
+As a preliminary result we note that 
 \begin{equation}\label{transpositionPropertyR}
@@
 \end{equation}
-Indeed
+that follows immediately from the definition of $E_{ab}$. 
+\begin{comment}
+
 \begin{align*}
-R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{r_{1}^{x}!\ldots r_{N}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots, r_{N}^{x}|
+R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
 	\\&
@@
  \\=&\sum_{r^{x}\in \Omega_{x}}
-	r_{a}^{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle \langle r_{1}^{x},\ldots,r_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,r_{N}^{x}|
+	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
 	\\=&
@@
 where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
+\end{comment}
 \paragraph{Elements of the duality matrix.}We aim to show that 
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|
-	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{2}^{u(x)},\ldots,q_{N}^{u(x)}|
+	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
 \end{align*}
 where we used \eqref{transpositionPropertyR}. \\
-On one hand, on the extra-site $\widehat{x}$ we have 
+On one hand, on the extra-site $u(x)$ we have 
 \begin{align*}
-\sum_{q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{\widehat{x}}}\langle q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}
+\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{2}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}
 \end{align*}
@@
 \begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 \\&
-\hspace{2.cm}\qquad|r_{1}^{x},\ldots,r_{N}^{x}\rangle
+\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
 \\&=
@@
 \\&
-\hspace{2.cm}\prod_{a=2}^{N}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle
+\hspace{2.cm}\prod_{a=2}^{N}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
 \\&=
@@
 \\& 
-\hspace{2.cm}\qquad\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{r_{1}^{x}!\ldots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle
-\\&=
-\frac{(\nu-\sum_{a=2}^{N}r_{a}^{x})}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}
+\hspace{2.cm}\qquad\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\\&=
+\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
 \end{align*}
-where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $r_{1}^{x}=\nu-\sum_{a=2}^{N}r_{a}^{x}$.
+where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $\xi_{1}^{x}=\nu-\sum_{a=2}^{N}\xi_{a}^{x}$.
 Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
@@
  \end{flushright}
- \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $\widehat{x}$.
+ \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
 % that we connect to every site $x\in V$ of the graph $G$.
@@
     \\&=\nonumber
-    \sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{b=2}^{N}E_{bb}^{x}=
-    \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-\sum_{i=1}^{N}\alpha_{i}^{x}E_{aa}^{x}\right)
+    \sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-|\alpha^{x}|\sum_{b=2}^{N}E_{bb}^{x}=
+    \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-|\alpha^{x}|E_{aa}^{x}\right)
     \\&=\nonumber
-    \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1a}^{x}-E_{aa}^{x}\right)
-    \\&=
-    \sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+    |\alpha^{x}|\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{|\alpha^{x}|}E_{1a}^{x}-E_{aa}^{x}\right)
+    \\&=
+    |\alpha^{x}|\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
  \end{align}
@@
 \begin{equation}\label{HadTransfBoundary}
-\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
 \end{equation}
@@
 \begin{equation}\label{siteHadamardI}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}|\alpha^{x}|\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
 \end{equation}
@@
 \begin{equation}
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
     \begin{split}
-&H_{x}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
+&H_{x}^{T}d_{x}\otimes\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \\=&
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}\right)
-    \end{split}
-\end{equation}
-Recalling the action of the bosonic creation operator acting at site $\widehat{x}$ and on the species $a\in \{2,\ldots,N\}$ we have that 
+d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}\right)
+    \end{split}
+\end{equation}
+Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{2,\ldots,N\}$ we have that 
 \begin{equation}\label{bosonicKX}
-    \langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|=  \langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})^{\widehat{x}}_{a}
+    \langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})^{u(x)}_{a}
 \end{equation}
@@
     \begin{split}
-&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\rho_{a}^{x}E_{1a}^{x}
-\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}
+&\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}E_{1a}^{x}
+\\=&\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}+1}\langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
 \\=&
-\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{a}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}
+\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
     \end{split}
@@
 H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
-     H_{x}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
-\\&=
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=1}^{N}\left((a^{\dagger})_{a}^{\widehat{x}}E_{1a}^{x}-E_{aa}^{x}\right)
-\\&=
-d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\widetilde{H}_{x}
+     H_{x}^{T}d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\\&=
+d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left((a^{\dagger})_{a}^{u(x)}E_{1a}^{x}-E_{aa}^{x}\right)
+\\&=
+d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|\widetilde{H}_{x}
 \\&=
@@
         \\&+
-        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
-        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
+        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},1}\right) 
+        \sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
 \\&
-\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
   \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
@@
 		\\&
-		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
 	\end{split}
@@
 \\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
 \\&\otimes
@@
 \\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
 \end{align*}
@@
         \\&
-        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)
+        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)
     \end{split}
@@
     \begin{split}
-  &\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+  &\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
 \\&  
@@
 a species with label from $2$ to $N$.
-This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{1}^{x}=\nu-\sum_{a=2}^{N}n_{a}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
-Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
-In each of these points there is a particle of species $s_{x}\in \{2,\ldots,N\}$.
+This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{1}^{x}=\nu-\sum_{b=2}^{N}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
+Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{x}=(y_{1},\ldots,y_{m})$, such that $x_{i}<x_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
+In each of these points there is a particle of species $a_{i}\in \{2,\ldots,N\}$.
 Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
 \begin{equation}\label{exactCorrelations}
-		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
+		\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})
 	\end{equation}
@@
 	\begin{equation}\label{powerCoeffSpecies}
-		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
+		g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
 	\end{equation}
@@
 	\end{equation}
-\textbf{Remark}: using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as 
-\begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})
+\textbf{Remark}: Using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as 
+\begin{equation}
+\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
 \end{equation}
@@
  \paragraph{Proof of formula \eqref{exactCorrelations}}
- We aim to compute the correlations between the sites $\mathbf{y}=\left(y_{1},\ldots,y_{m}\right)$ occupied by the species $\mathbf{s}=\left(s_{1},\ldots,s_{m}\right)$, such that $s_{1},\ldots,s_{m}\in \{2,\ldots,N\}$ i.e.
+ We aim to compute the correlations between the sites $\mathbf{x}=\left(x_{1},\ldots,x_{m}\right)$ occupied by the species $\mathbf{a}=\left(a_{1},\ldots,a_{m}\right)$, such that $a_{1},\ldots,a_{m}\in \{2,\ldots,N\}$ i.e.
 \begin{equation}\label{Prob-m}
 	\begin{split}
-		\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{\text{stat}}&
-		=\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)
+		\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{\text{stat}}&
+		=\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)
 	\end{split}
@@
 where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This corresponds to the steady state probability of a chain of length $m$ with each coordinates $y_{i}$ occupied by $s_{x}\neq 1$, i.e. 
-\begin{equation}
-	\mathbb{P}_{stat}\left(n_{s_{1}}^{y_{1}}=1,\ldots,n_{s_{m}}^{y_{m}}=1\right)=\Psi\left(s_{1},\ldots,s_{m}\right)
-\end{equation}
-where $\Psi(\bm{s})$ is the element of the vector \eqref{steadyStateH} computed for this chain $m$.
+This corresponds to the steady state probability of a chain of length $m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$, i.e. 
+\begin{equation}
+	\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)=\Psi\left(a_{1},\ldots,a_{m}\right)
+\end{equation}
+where $\Psi(\bm{a})$ is the element of the vector \eqref{steadyStateH} computed for this chain $m$.
 As already remarked in \eqref{LinkABS-corr}, for non-empty configurations we have:
 \begin{equation}\label{Corr-mABS}
-	\Psi(s_{1},\ldots,s_{m})=\Psi^{'}(s_{1},\ldots,s_{m})
+	\Psi(a_{1},\ldots,a_{m})=\Psi^{'}(a_{1},\ldots,a_{m})
 \end{equation}
@@
 \begin{equation}
-	\Psi(s_{1},\ldots,s_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{s_{k}}^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we have the formulas for arbitrary correlations.
+	\Psi(a_{1},\ldots,a_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ we have the formulas for arbitrary correlations.
 \begin{flushright}
@@
 \paragraph{One point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{2,\ldots,N\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
-\begin{equation}
-	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})
+The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{2,\ldots,N\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
+\begin{equation}
+	\langle n_{a_{1}}^{x_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,x_{1},c_{1})
 \end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}
+\langle n_{a_{1}}^{x_{1}}\rangle_{\text{stat}}=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}
 \end{equation}
 \paragraph{Two points correlations}
-The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{2,\ldots,N\}$ at coordinates $y_{1},y_{2}\in \{1,\ldots,L\}$ with $x< y$ reads
-\begin{equation}
-	\begin{split}
-	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,c_{k},c_{2})
+The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{2,\ldots,N\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+\begin{equation}
+	\begin{split}
+	\langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})
 	\end{split}
@@
 	\begin{split}
-	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+	\langle n_{a_{1}}^{x_{2}} n_{a_{2}}^{x_{2}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})
 	\end{split}
@@
 	\begin{split}
-		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{y_{1}}^{s_{1}}n_{y_{2}}^{s_{2}}]-\mathbb{E}[n_{y_{1}}^{s_{1}}]\mathbb{E}[n_{y_{2}}^{s_{2}}]=-\frac{y_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
+		\langle n_{a_{1}}^{x_{2}} n_{a_{2}}^{x_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}]-\mathbb{E}[n_{a_{1}}^{x_{1}}]\mathbb{E}[n_{a_{2}}^{x_{2}}]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)
 	\end{split}
@@
 \paragraph{Three points correlations}
-The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{2,\ldots,N\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
-\begin{equation}
-    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,c_{k},\ldots,c_{3})
+The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{2,\ldots,N\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
+\begin{equation}
+    \langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}n_{a_{3}}^{x_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{3})
 \end{equation}
@@
 \begin{align}\label{three-pts-corr}
-        \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
+        \langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}n_{a_{3}}^{x_{3}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
         \\&+\nonumber
-        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
+        \frac{(L+1-x_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-x_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}
         \\&+\nonumber
-        \frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
+        \frac{(L-x_{2})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}
         \\&+\nonumber
-        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
+        \frac{(L-x_{1})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}
         \\&+\nonumber
-        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
+        \frac{(L-x_{1})(L-x_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}
         \\&+\nonumber
-        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
+        \frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
 \end{align}
@@
 \begin{align}
-	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
-	\\&=
-	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
+	\langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}n_{a_{3}}^{x_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}\right]-\mathbb{E}\left[n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{x_{3}}\right]-\mathbb{E}\left[n_{a_{1}}^{x_{1}}n_{a_{3}}^{x_{3}}\right]\mathbb{E}\left[n_{a_{2}}^{x_{2}}\right]\\&-\mathbb{E}\left[n_{a_{3}}^{x_{3}}n_{a_{2}}^{x_{2}}\right]\mathbb{E}\left[n_{a_{1}}^{x_{1}}\right]+2\mathbb{E}\left[n_{a_{1}}^{x_{1}}\right]\mathbb{E}\left[n_{a_{2}}^{x_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{x_{3}}\right]
+	\\&=
+	-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
 \end{align}
@@
 \begin{equation}
-	\bm{\xi}=\left(r_{1}^{x},\ldots,r_{N}^{x},m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}\right)_{x\in V}
-\end{equation}
-where the component $r_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{a}^{\widehat{x}}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
-the extra-site $\widehat{x}$ connected to $x\in V$.
+	\bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
+\end{equation}
+where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+and the component $m_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+the extra-site $u(x)$ connected to $x\in V$.
 
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}r_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-r_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{\widehat{x}}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\,\right)
 \end{equation}
@@
 %\begin{equation}
-%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}
+%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}
 %\end{equation}

### 2023-04-19 main.tex
ii

@@
 
-\subsection{The process generator}
+\subsection{The process generator}\label{subsectionGeneratorStr}
 We now give the mathematical description of the multi-species stirring process.
@@
 \end{equation}
-We denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$ .\\
+We denote a particle configuration as $\bm{n}\in \Omega$, where $\bm{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$ .\\
 The dynamics consists in an exchange of particles (at Poissonian times) between connected vertices.
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left[f(\bm{n}-\delta^{x}_{a}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-f(\bm{n})\right]
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left[f(\bm{n}-\bm{\delta}^{x}_{a}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right]
 \end{equation}
 \begin{equation}\label{siteGenerator}
-    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\delta_{a}^{x}-\delta_{b}^{x})-f(\bm{n})\right]
+    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\bm{\delta}_{a}^{x}-\bm{\delta}_{b}^{x})-f(\bm{n})\right]
 \end{equation}
@@
 \begin{equation}
-(\delta_{a}^{x})^{y}_{b}=\begin{cases}
-1\qquad &\text{if}\quad y=x,\;b=k\\
+(\bm{\delta}_{a}^{x})^{y}_{b}=\begin{cases}
+1\qquad &\text{if}\quad y=x,\;b=a\\
 0\qquad &\text{otherwise}
@@
 \begin{equation}
- \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}
+ \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{|\alpha|}
 \end{equation}
@@
 \end{equation}
+where we denote $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. 
 This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
@@
 \begin{equation}\label{ortho}
-    \langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{m_{a},n_{a}}
-\end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronhecker delta. 
+   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}
+\end{equation}
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronhecker delta. 
 The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
@@
 \\ \\
-\textbf{Reamrk}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
+\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
 \begin{equation}
@@
 \end{equation}
-that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
+that acts diagonally as $C_{2}|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
 More precisely,  considering the standard coproduct 
@@
 \newline
-\textbf{Reamrk}:
+\textbf{Remark}:
 when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
@@
 \subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
-In this section we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
+In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}.
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the \textit{enlarged graph} $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E}})$ where 
+\begin{equation}
+	\widetilde{V}:=V\cup \left\{u(x)\,:\, x\in V\right\}\qquad \widetilde{\mathcal{E}}:=\mathcal{E}\cup \left\{(x,u(x))\,:\, x\in V\right\}
+\end{equation}
+This means that to each site $x\in V$ we associate an ``extra-site'', denoted $u(x)$. The configuration space of the dual process is the enlarged state space
 \begin{equation}\label{dualStateSpace}
-    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
-\end{equation}
-To each site $x\in V$ we associate an ``extra site'', denoted $u(x)$,
-where dual particles will accumulate in the course of time. 
-We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
-\begin{equation}
-    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
+    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})
+\end{equation}
+Dual particle will accumulate in these extra-sites in the course of time. We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+\begin{equation}
+    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
 \end{equation}
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 
 the extra-site $u(x)$ connected to $x\in V$.
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
 \end{equation}
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=2}^{N}\xi_{a}^{x}\left(f(\bm{\xi}-\delta_{a}^{x}+\delta_{1}^{x}+\delta_{a}^{u(x)})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=2}^{N}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{1}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)
 \end{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}m_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 \begin{equation}
-    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)
 \end{equation}
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\dd=\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{2}^{u(x)},\ldots,q_{N}^{u(x)}|
-	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
+	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
 \end{align*}
@@
 \begin{align*}
-\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{2}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}
+\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
 \end{align*}
@@
 \begin{equation}
-\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
     \begin{split}
-&H_{x}^{T}d_{x}\otimes\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+&H_{x}^{T}d_{x}\otimes\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \\=&
-d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}\right)
+d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}\right)
     \end{split}
@@
 \begin{equation}\label{bosonicKX}
-    \langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})^{u(x)}_{a}
+    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})^{u(x)}_{a}
 \end{equation}
@@
     \begin{split}
-&\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}E_{1a}^{x}
-\\=&\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}+1}\langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
+&\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}E_{1a}^{x}
 \\=&
-\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,m_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
+\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
+\\=&
+\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
     \end{split}
@@
 H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
-     H_{x}^{T}d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|
-\\&=
-d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left((a^{\dagger})_{a}^{u(x)}E_{1a}^{x}-E_{aa}^{x}\right)
-\\&=
-d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\langle \xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}|\widetilde{H}_{x}
+     H_{x}^{T}d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\\&=
+d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{u(x)}E_{1a}^{x}-E_{aa}^{x}\right)
+\\&=
+d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\widetilde{H}_{x}
 \\&=
@@
 	\begin{split}
-			H_{1}^{''}&=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}
+			H_{L}^{''}&=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}
 			\\&=
@@
 \end{equation}
+\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain in order to alleviate notation. Each configuration can be written as
+\begin{equation}
+	|\bm{\tau}\rangle =\begin{pmatrix}
+		\tau_{1}\\
+		\vdots\\
+		\tau_{L}
+	\end{pmatrix}
+\end{equation}
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
+This notation is equivalent to the one introduced in Subsection \ref{subsectionGeneratorStr}.
+Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$.
+Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$.
+With this notation, we have that
+\begin{equation}\label{notation}
+	|n^{x}\rangle =\tau_{x}\qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
+\end{equation}
+with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. 
 \begin{comment}
@@
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}|\mathbf{\bm{s}}\rangle
+	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{\tau_{x},1}}|\mathbf{\bm{\tau}}\rangle
 \end{equation}
@@
 \begin{equation}
-    \delta_{s_{x},1}:=\begin{cases}
-        1\quad \text{if}\quad s_{x}=1\\
+    \delta_{\tau_{x},1}:=\begin{cases}
+        1\quad \text{if}\quad \tau_{x}=1\\
         0\quad \text{otherwise}
@@
 \end{equation}
-and the basis vector $|\bm{s}\rangle =\bigotimes_{i=1}^{L}|s_{x}\rangle$ with $s_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
+%and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\mathbf{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle \,|\mathbf{n}\rangle
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|V \rangle \,|\bm{n}\rangle
 \end{equation}
@@
 $$
-|\mathbf{n}\rangle =|n_{1}^{1},\ldots,n_{N}^{1}\rangle \otimes \ldots\otimes |n_{1}^{L},\ldots,n_{N}^{L}\rangle
+|\bm{n}\rangle =|n_{1}^{1},\ldots,n_{N}^{1}\rangle \otimes \ldots\otimes |n_{1}^{L},\ldots,n_{N}^{L}\rangle
 $$
 such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
-To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{x}}
+To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}
 |V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
@@
 \begin{equation}\label{resulEsteady}
-	|\widetilde{\Psi}\rangle= \sum_{\mathbf{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|\mathbf{n}\rangle
-\end{equation}
-Calling $s_{x}$ the species present at site $i$, we rewrite the basis vector 
-\begin{equation}
-	|n_{1}^{x},\ldots,n_{N}^{x}\rangle=|s_{x}\rangle
-\end{equation}
-where $s_{x}=\sum_{a=1}^N\delta_{n_{k}^{x},1}$. Finally we take the tensor product of the vectors $|s_{x}\rangle$ and we obtain
-\begin{equation}
-	|\mathbf{s}\rangle=\bigotimes_{x=1}^{L}|s_{x}\rangle=|\mathbf{s}\rangle
-\end{equation}
-with $s_{x}\in\{1,\ldots,N\}$. For a fixed site $x$, because of the hard-core interaction that allows at most one particle on type different from $1$, we have 
-\begin{equation}
-	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}=\left[\lambda_{s_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{x},1}}
-\end{equation}
-Moreover, we write 
-\begin{equation}
-	\frac{\Gamma(2+\sum_{x=1}^{L}n_{1}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{s_{x},1}\right)}{\Gamma\left(L+2\right)}
-\end{equation}
-Finally summing over all $\mathbf{s}\in \Omega$  we obtain \eqref{ResulsBasis}.
+	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle
+\end{equation}
+Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ introduced in \eqref{notation} we have 
+\begin{equation}
+	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}=\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{\tau_{x},1}}
+\end{equation}
+and 
+\begin{equation}
+	\frac{\Gamma(2+\sum_{x=1}^{L}n_{1}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},1}\right)}{\Gamma\left(L+2\right)}
+\end{equation}
+Therefore we obtain
+\begin{equation}
+|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{\tau_{x},1}}|\mathbf{\bm{\tau}}\rangle
+\end{equation}
 \begin{flushright}
@@
 \begin{equation}\label{ABS-vect}
-    |\Psi^{'}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi^{'}(\bm{s})|\bm{s}\rangle 
+    |\Psi^{'}\rangle =\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
 \end{equation}
@@
 		\begin{split}
-			\Psi^{'}(\bm{s})=\sum_{c_{1}=0}^{\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
 		\end{split}
@@
 	c_{y}=\begin{cases}
-		1\quad \text{if}\quad s_{y}\neq 1\\
-		0\quad \text{if}\quad s_{y}=1
+		1\quad \text{if}\quad \tau_{y}\neq 1\\
+		0\quad \text{if}\quad \tau_{y}=1
 	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
@@
     \end{equation}
-    that can be generalized for $e_{s_{1},\ldots,s_{L}}^{q_{1},\ldots,q_{L}}$ with $s_{1},\ldots,s_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that
+    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that
 
@@
     	\begin{split}
-    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right.
     		\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
     		\\&+\left.
-    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
+    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
     		\right. \\&+ \left. 
-    		\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}
+    		\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
     	\end{split}
@@
     \begin{equation}
-    	\mathcal{S}_{2}^{-1}=\sum_{s_{1}=1}^{N}\left\{e_{s_{1}}^{s_{1}}+(1-\delta_{s_{1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
+    	\mathcal{S}_{2}^{-1}=\sum_{\tau_{1}=1}^{N}\left\{e_{\tau_{1}}^{\tau_{1}}+(1-\delta_{\tau_{1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
     \end{equation}
@@
 \begin{align*}
-    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}++\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\right.
+    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L-1}s_{L}}}^{1,\ldots,1,s_{L}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
     	\right. \\&+ \left. 
-    	\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\beta_{s_{x}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1} \right\}\otimes \sum_{s_{L+1}=1}^{N}\left\{e_{s_{L+1}}^{s_{L+1}}+(1-\delta_{s_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{s_{q_{1}}}e_{s_{q_{1}}}^{1}\right\}
-    	\\&=
-    	\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\right.
+    	\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
+    	\\&=
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,1,\ldots,\tau_{L+1}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L+1}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L+1}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L+1}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L+1}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{s_{1},\ldots,s_{q_{L}}s_{L+1}}^{1,\ldots,1,s_{L+1}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{q_{L}}\tau_{L+1}}^{1,\ldots,1,\tau_{L+1}}
     	\right. \\&+ \left. 
-    	\left(\prod_{x=1}^{L+1}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L+1}\beta_{s_{x}}e_{s_{1},\ldots,s_{L+1}}^{1,\ldots,1} \right\}
+    	\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L+1}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{1,\ldots,1} \right\}
     	\\&=
@@
     \begin{equation}
-        S_{2}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+Q
+        S_{2}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+Q
     \end{equation}
@@
     \begin{equation}
-	Q:=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
+	Q:=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}
 \end{equation}
@@
 \begin{split}
-	&I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}\\
-	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}\\
-	&Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}\\
-	&Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}e_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
+	&I_{N\times N}\otimes I_{N\times N}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{\tau_{1},s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}\\
+	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1,s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},1}\beta_{s_{2}}\\
+	&Q\otimes I_{N\times N}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2,s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{1,s_{2}}\beta_{\tau_{1}}\\
+	&Q\otimes Q=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1},s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{1,1}\beta_{\tau_{1}}\beta_{s_{2}}
  \end{split}
@@
 \begin{equation}
-	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}^{q_{1},q_{2}}\right\}_{s_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
-\end{equation}
-where the subscripts $s_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $s_{1},s_{2}$ reads
-\begin{equation}
-	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{s_{1},s_{2}}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
+	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}^{q_{1},q_{2}}\right\}_{\tau_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
+\end{equation}
+where the subscripts $\tau_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $\tau_{1},s_{2}$ reads
+\begin{equation}
+	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{\tau_{1},s_{2}}^{\tau_{1},1}+(1-\delta_{\tau_{1},1})\beta_{\tau_{1}}e_{\tau_{1},s_{2}}^{1,s_{2}}+(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\beta_{\tau_{1}}\beta_{s_{2}}e_{\tau_{1},s_{2}}^{1,1}
 \end{equation}
 \end{comment}
-The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{s})$. 
-To find these elements we need to fix the rows correspondent to $\bm{s}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
-Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
-\begin{equation}
-	\begin{split}
-\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{s}}&=\,e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{s_{q_{1}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{s_{1},\ldots,s_{q_{1}},\ldots,s_{q_{2}}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{s_{q_{1}}}\beta_{s_{q_{2}}}
+The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
+To find these elements we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
+Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
+\begin{equation}
+	\begin{split}
+\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}
   \\&+
-  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
+  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1}
 	\end{split}
@@
 	\begin{split}
-		\Psi^{'}(\mathbf{s})&=(\mathcal{S}_{2}^{-1})_{\bm{s}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\mathbf{s})+\sum_{q_{1}= 1}^{L}(1-\delta_{s_{q_{1}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{s_{q_{1}}},\ldots,s_{L})\beta_{q_{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{s_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(s_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,s_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{s_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{s_{x}}\right)^{1-\delta_{s_{x},1}}
-	\end{split}
-\end{equation}
-For a fixed configuration $\bm{s}=(s_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
-\begin{equation}
-  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)
+		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})\Psi^{''}(\tau_{1},\ldots,\overbrace{1}^{\tau_{q_{1}}},\ldots,\tau_{L})\beta_{q_{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(\tau_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,\tau_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}
+	\end{split}
+\end{equation}
+For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
+\begin{equation}
+  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)
 \end{equation}
@@
     \begin{equation}
-\Psi^{''}(\bm{s})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{s_{y},1})\right)\right)^{1-\delta_{s_{y},1}}
+\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)\right)^{1-\delta_{\tau_{y},1}}
 \end{equation}
@@
 \begin{equation}
-	c_{y}=(1-\delta_{s_{y},1}) \qquad \forall y\in \{1,\ldots L\}
-\end{equation}
-and replacing $\Psi^{'}(\bm{s})$ computed above in \eqref{ABS_intermediate} we obtain
-
-%Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
+	c_{y}=(1-\delta_{\tau_{y},1}) \qquad \forall y\in \{1,\ldots L\}
+\end{equation}
+and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain
+
+%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
@@
 	\begin{split}
-		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{s_{y}}\right)^{(1-c_{y})(1-\delta_{s_{y},1})}
-	\end{split}
-\end{equation} 
-%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
-Finally, considering all possible configurations $\bm{s}$, we obtain \eqref{ABS-vect}.
+		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+	\end{split}
+\end{equation} 
+%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
+Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
 \begin{flushright}
@@
 \begin{equation}\label{steadyStateH}
-    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
-\end{equation}
-where for every $(s_{1},\ldots,s_{L})=\bm{s}$
+    |\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
+\end{equation}
+where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
+\begin{equation}
+	\begin{split}
+ \Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+\\&+
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},1}\right) 
+\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
+\\&
+\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
+	\end{split}
+\end{equation}
+where we have introduced, $\forall x\in \{1,\ldots,L\}$
+\begin{equation}
+	\eta_{x}=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\neq q_{1},\ldots,q_{b}\\
+		d_{x}\qquad &\text{otherwise}
+	\end{cases}%\qquad \theta_{x}=\begin{cases}
+		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+	%	1 \qquad &\text{otherwise}
+	%\end{cases}
+\end{equation}
+{\color{blue}
 \begin{equation}\label{steadyStateH-coeff}
     \begin{split}
-        \Psi(\bm{s})&=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+        \Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
         \\&+
@@
 \\&
-\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
-  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
+\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
  \\ &
- \beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+ \beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
  \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
@@
 \end{equation}
-\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
+}
+\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $\tau_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
 \begin{equation}\label{LinkABS-corr}
-\Psi(\bm{s})=\Psi^{'}(\bm{s})
+\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
 \end{equation}
@@
 \begin{equation}\label{S1-L1}
-	\mathcal{S}_{1}^{-1}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+(-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+	\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
 \end{equation}
@@
 	\begin{split}
-		\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
+		\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
 		\\&
-		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
-	\end{split}
-\end{equation}
-where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
+	\end{split}
+\end{equation}
+where we have introduced, $\forall x\in \{1,\ldots,L\}$
+\begin{equation}
+	%\eta_{x}=\begin{cases}
+	%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+	%	d_{x}\qquad &\text{otherwise}
+	%\end{cases}\qquad
+	 \theta_{x}=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+		1 \qquad &\text{otherwise}
+\end{cases}
+\end{equation}
+  %$e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
 \\
@@
 \left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
-\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L}=1}^{N}\left\{e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}\right.
+\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
 \\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
 \\&\otimes
-\left\{ \sum_{s_{1}=1}^{N}e_{s_{L+1}}^{s_{L+1}}+(-1)\delta_{s_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
-\\&=
-\sum_{s_{1}=1}^{N}\ldots\sum_{s_{L+1}=1}^{N}\left\{e_{s_{1},\ldots,s_{L+1}}^{s_{1},\ldots,s_{L+1}}\right.
+\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
+\\&=
+	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
 \\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}\right\}
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
 \end{align*}
@@
 \begin{equation}
-    F=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}+\delta_{s_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+    F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
 \end{equation}
@@
 \begin{split}
-    F\otimes F&=\sum_{s_{1},s_{2}=1}^{N}\left(e_{s_{1},s_{2}}^{s_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{s_{1},1}^{s_{1},d_{2}}
+    F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
      \right.\\ &+\left. 
-    (-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{s_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
-    \end{split}
-\end{equation}
-therefore, fixing a raw with indices $s_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
-\begin{equation}
-\begin{split}
-    \left(F\otimes F\right)_{s_{1},s_{2}}&=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{s_{1},1}^{s_{1},d_{2}}
+    (-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
+    \end{split}
+\end{equation}
+therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
+\begin{equation}
+\begin{split}
+    \left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
     \\&+
-    (-1)\delta_{s_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{s_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
-    \\&=
-    \sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{s_{x},1}^{s_{x}d_{q_{r}}}
+    (-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
+    \\&=
+    \sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
     +
-    (-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{s_{x},1}^{s_{x}d_{q_{r}}}
-    \end{split}
-\end{equation}
-where $e_{s_{x},d_{q_{r}}}$ denotes the matrix $e_{s_{1},s_{2}}^{s_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
+    (-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+    \end{split}
+\end{equation}
+where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
 \\
-We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$. We write the expression of a fixed raw with indices $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$ as 
-\begin{equation}
-    \begin{split}
-        \mathcal{F}_{s_{1},\ldots,s_{L}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}
+We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
+We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
+\begin{equation}
+    \begin{split}
+        \mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
         \\&
-        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}
-    \end{split}
-\end{equation}
-where $e_{\ldots,s_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,s_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}$ where the subscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by "1" and the superscripts $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
+    \end{split}
+\end{equation}
+where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
 \\
 \end{comment}
-The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{s})$. 
-To find this elements we need to fix the rows correspondent to $\bm{s}$. Consider a string $\bm{s}=(s_{1},\ldots,s_{L})$ with $s_{1},\ldots,s_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
-\begin{equation}
-    \begin{split}
-        \left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{s}}|\Psi{'}\rangle&=\Psi{'}(s_{1},\ldots,s_{L})+ 
+The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
+To find this elements we need to fix the rows correspondent to $\bm{\tau}$.
+Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
+\begin{equation}
+    \begin{split}
+       \Psi(\bm{\tau}) &=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{\tau}}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
         \\&
-        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)
-    \end{split}
-\end{equation}
-where $\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(s_{1},\ldots,s_{L})$ where the occupations  $s_{q_{1}},\ldots,s_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\eta_{1},\ldots,\eta_{L})
+    \end{split}
+\end{equation}
+%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
 Using \eqref{elementsABS} we have 
@@
   \begin{split}
-  &\Psi{'}(\ldots,s_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+	\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
 	\\&
-\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
+	\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
+\end{split}
+\end{equation}
+{\color{blue}
+\begin{equation}
+    \begin{split}
+  &\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+\\&  
+\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
 \\&
@@
     \end{split}
-\end{equation}
-indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
-Finally, considering all possible configurations $\bm{s}=(s_{1},\ldots,s_{L})$ we obtain \eqref{steadyStateH}.
+\end{equation}} indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
+Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}.
 \begin{flushright}
@@
 %\begin{equation}
-%	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
+%	\langle n^{y_{1}}_{\tau_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
 %\end{equation}
@@
 where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This corresponds to the steady state probability of a chain of length $m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$, i.e. 
-\begin{equation}
-	\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)=\Psi\left(a_{1},\ldots,a_{m}\right)
-\end{equation}
-where $\Psi(\bm{a})$ is the element of the vector \eqref{steadyStateH} computed for this chain $m$.
+This corresponds to the steady state probability of a chain of length $m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$.Therefore, using again the notation \eqref{notation} and calling $\tau_{i}=a_{i}$, we have
+\begin{equation}
+	\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)=\Psi\left(\tau_{1},\ldots,\tau_{m}\right)
+\end{equation}
+where $\Psi(\bm{\tau})$ is the element of the vector \eqref{steadyStateH} computed for this chain $m$.
 As already remarked in \eqref{LinkABS-corr}, for non-empty configurations we have:
 \begin{equation}\label{Corr-mABS}
-	\Psi(a_{1},\ldots,a_{m})=\Psi^{'}(a_{1},\ldots,a_{m})
+	\Psi(\tau_{1},\ldots,\tau_{m})=\Psi^{'}(\tau_{1},\ldots,\tau_{m})
 \end{equation}
@@
 \begin{equation}
-	\Psi(a_{1},\ldots,a_{m})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ we have the formulas for arbitrary correlations.
+	\Psi(\tau_{1},\ldots,\tau_{m})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ and using $\tau_{i}=a_{i}$ $\forall i=1,\ldots,m$, we have the formulas for arbitrary correlations.
 \begin{flushright}
@@
 \begin{equation}
-	\mathcal{L}_{1}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{1}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\\bm{delta}_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
- \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
+ \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
 \end{equation}
@@
 	\begin{split}
-		\widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=\sum_{i=1}^{N}\alpha_{i}\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
+		\widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
 	\end{split}
@@
 \end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{\sum_{i=1}^{N}\beta_{i}}$.\\
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
 Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
@@
 Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{s_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
 \begin{equation}
@@
 		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
-		a^{1}_{s}(1)=\frac{A}{1+A}+a^{2}_{s}(1)\frac{1}{1+A}\\
-		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+B}
+		a^{1}_{s}(1)=\frac{|\alpha|}{1+|\alpha|}+a^{2}_{s}(1)\frac{1}{1+|\alpha|}\\
+		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+|\beta|}
 	\end{cases}
 \end{equation}
-where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where, for the sake of notation, we call $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$.
+where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where.
 The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
 \begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
-\end{equation}
-\textbf{Remark}: In case $A=B=1$ we have 
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}
+\end{equation}
+\textbf{Remark}: In case $|\alpha|=|\beta|=1$ we have 
 \begin{equation}
@@
 		\mathcal{L}_{1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
-		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
 		\end{split}
@@
 \begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
 	\\&\nonumber
@@
 	\\&
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
 \end{align}
-Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
+Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
 	\\&\nonumber
-	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}\\=&
-	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
+	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\\=&
+	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
 \end{align}
-Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
+Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
 \begin{equation}\label{pezzo2}
 	\begin{split}
-	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
+	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
 	\end{split}
@@
 \begin{align}
-	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&=
@@
 \begin{equation}
-	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-f(\bm{n})\right)
+	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \paragraph{Action on the occupation variable of $\mathcal{L}_{x,y}^{rd}$}
-For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
+For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
 \begin{equation}\label{actionGraphRD}
@@
 \begin{equation}
-	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
+	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(a)}^{y}-\delta_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
+		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
 		\\&=
@@
 \begin{equation}
-	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\delta_{a}^{x}+\delta_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\delta_{b}^{x}+\delta_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
+		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
 		\\&=
@@
 \\
-For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{\sum_{i=1}^{N}\alpha_{i}}$.
+For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$.
 As a consequence we have the result.
 \subsection{Duality}
-In this subsection we formulate duality for the multi-species stirring process $(\mathbf{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
+In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
 The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
@@
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $m_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
 the extra-site $u(x)$ connected to $x\in V$.
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{m_{a}^{u(x)}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
 \end{equation}
@@
 \begin{split}
-        \widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=\sum_{i=1}^{N}\alpha_{i}\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
+        \widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
         \end{split}
@@
 \end{equation}
-\textbf{Reamrk}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
+\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
 The interesting charges (we only look for the first non trivial one) take the following form
@@
 \end{equation}
-where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{a=2}^{N}m_{a}$.\\
+where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{a=2}^{N}\xi_{a}$.\\
 For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$ and we further assume that $\Delta_{2}=\Delta_{3}=\Delta$.

### 2023-04-19 main.tex
notation

@@
     	\begin{split}
-    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right.
+    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
     		\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     		\\&+\left.
-    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
+    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
     		\right. \\&+ \left. 
-    		\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
-    	\end{split}
-    \end{equation}
+    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
+    	\end{split}
+    \end{equation}
+where, $\forall x\in\{1,\ldots,L\}$, we have introduced
+\begin{equation}
+	\varphi_{x}(q_{1},\ldots,q_{L})=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{L}\}\\
+		1\qquad &\text{otherwise}\\
+	\end{cases}
+\end{equation}
+The dependence of $\varphi_{x}(q_{1},\ldots,q_{L})$ with respect to $q_{1},\ldots,q_{L}$ is usually understood for the sake of notation.
     We prove it by induction. When $L=1$ it is true, indeed
@@
 \begin{align*}
-    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right.
+    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=%\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right.
+    	%\\&+\left.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+    	%\\&+\left.
+    	%\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
+    	%\right. \\&+ \left. 
+    	%\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
     	\right. \\&+ \left. 
-    	\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
-    	\\&=
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,1,\ldots,\tau_{L+1}}\beta_{\tau_{q_{1}}}\right.
+    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
+    	\\&
+    	\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
+    	\\&=
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L+1}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L+1}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{q_{L}}\tau_{L+1}}^{1,\ldots,1,\tau_{L+1}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}
     	\right. \\&+ \left. 
-    	\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L+1}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{1,\ldots,1} \right\}
+    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}} \right\}
     	\\&=
@@
 	\begin{split}
-\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}
+\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
   \\&+
-  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1}
+  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
 	\end{split}
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})\Psi^{''}(\tau_{1},\ldots,\overbrace{1}^{\tau_{q_{1}}},\ldots,\tau_{L})\beta_{q_{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(\tau_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,\tau_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}
-	\end{split}
-\end{equation}
-For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
+		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{q_{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}
+	\end{split}
+\end{equation}
+For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$, using equation \eqref{ResulsBasis} and observing that 
 \begin{equation}
@@
 \begin{equation}
-	\eta_{x}=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\neq q_{1},\ldots,q_{b}\\
+	\eta_{x}(b)=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
 		d_{x}\qquad &\text{otherwise}
@@
 \end{equation}
+The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
 {\color{blue}
@@
 	%\end{cases}\qquad
-	 \theta_{x}=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+	 \theta_{x}(b)=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
 		1 \qquad &\text{otherwise}
@@
 \end{equation}
+The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
   %$e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.

### 2023-04-19 main.tex
Q0Formula

@@
 \begin{split}
-Q_{2L}^{0}&=N\left(I^{tot}+2e_{11}^{tot}\right)+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{j=2}^{N}e_{jj}^{tot}
-\\&
-+\sum_{i=2}^{N}\left(	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\right)
-\end{split}
-\end{equation}
-it has the property that commute with the equilibrium Hamiltonian
+Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+\end{split}
+\end{equation}
+it has the property that commute with the equilibrium Hamiltonian.
+In case of $N=2$ it differs with respect to the $Q_{2L}^{0}$ computed in formula (2.28) of \cite{frassek2020eigenstates} by the following matrix
+\begin{equation}
+Q_{2L}^{0,Francesco}-Q_{2L}^{0,Rouven}=	\begin{pmatrix}
+		2&0&0&0\\
+		0&-2&0&0\\
+		0&0&-2&0\\
+		0&0&0&2
+	\end{pmatrix}
+\end{equation}
 \begin{equation}

### 2023-04-23 main.tex
kk

@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$ at site $x\in V$.
+At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$.
 On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$.
@@
 \begin{equation}
-\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}
+\Omega_{x}:=\left\{n^x=(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}\,.
 \end{equation}
@@
 \end{equation}
-where the quantities $ \omega_{x,y}\geq 0$ are called conductances and $\Gamma_{x}\geq 0$ local inhomogeneities.
+where  $ \omega_{x,y}\geq 0$ are so-called conductances and $\Gamma_{x}\geq 0$ local inhomogeneities.
 The generator $\mathcal{L}_{x,y}$ is called the \textit{edge generator}, while $\mathcal{L}_{x}$ is called the \textit{site generator}.
@@
 0\qquad &\text{otherwise}
-\end{cases}
-\end{equation}
-This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $a$.
+\end{cases}\,.
+\end{equation}
+This means that on the edge $(x,y)\in \mathcal{E}$  a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$.
+Furthermore, on each site $x\in V$  a particle of type $b$ is replaced with a particle of type $a$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$.
 For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$.
-See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 
+See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dyamics. 
 \begin{figure}
@@
 \begin{equation}\label{reversibilityCondition}
-\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V
+\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V\,.
 \end{equation}
@@
 If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own density $\alpha^{x}=(\alpha_{1}^{x},\ldots,\alpha_{N}^{x})$ and currents will arise when at least two of them are different.
+
+{\color{red}add/improve explanaition of entire subsection}
 \subsection{The Lie algebraic description}
@@
 \begin{equation}\label{eq:comgl}
-\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
-\end{equation}
-The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.
-We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
+\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}\,.
+\end{equation}
+The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$, $\lambda_i\geq \lambda_{i+1}$ and $\sum_{i=1}^N \lambda_i = \nu$.
 We are interested in the {\em symmetric} finite-dimensional representations with 
 \begin{equation}\label{eq:dynkin}
-    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
-\end{equation} 
-The dimension $M$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
-\begin{equation}
-	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
-\end{equation} 
-The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
-\begin{equation}
-  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
+    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
+\end{equation} 
+The dimension $M_\twoj$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
+\begin{equation}
+	M_\twoj= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
+\end{equation} 
+The basis elements of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
+\begin{equation}
+  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
 \end{equation}
 %where $\sum_{a=1}^{N}n_{i}=\nu$. 
-This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
+The basis vectors satisfy the orthogonality relation with respect to the Euclidean scalar product 
 \begin{equation}\label{ortho}
@@
 \end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronhecker delta. 
-The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
+The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
 \begin{equation}\label{actionE}
@@
 		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
-		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
-	\end{cases}
-\end{equation}  
-One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
+		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle
+	\end{cases}\,.
+\end{equation}  
+The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
+{\color{red} Is this remark relevant for us?}
 \newline 
@@
 \end{comment}
+
+\subsection{Integrable process on a line segment}
+{\color{red}Introduce integrable model here}
 

### 2023-04-23 main.tex
ll

@@
 {\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements
-
+The process with generator \eqref{Generator} can be described in terms of $gl(n)$ Lie algebra generators.
+The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site, namely
 %We now define the equivalent of \eqref{stateSpace} in the vector notation
@@
 \end{equation}
+{\color{blue}
 where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$.
-Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
+Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.}
+{\color{red}remove?}
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
 \begin{equation}
-    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}
+    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
 \end{equation}
 We introduce the Hamiltonian operator
-
 \begin{equation}\label{OriginalHamiltonian}
@@
 \end{equation}
-where the edge Hamiltonian is
+where the edge Hamiltonian that describes the interaction between two connected sites is
 \begin{equation}\label{edgeHamiltonian}
@@
 acting trivially as the identity on the other sites). 
-Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
+Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
 \begin{equation}\label{Hamiltonian-Generator}
@@
 \end{equation}
+{\color{red} no minus sign?}
 The action of the generator can also be expressed as 
@@
 \begin{equation}
-\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}
+\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}\,.
 \end{equation}
@@
 \end{equation}
-where $\Delta^{x,y}(C_2)$ denotes a copy of $\Delta(C_2)$ acting on  
+where $\Delta^{x,y}(C_2)$ denotes a {\color{blue}copy} of $\Delta(C_2)$ acting on  
 the edge $(x,y)\in \mathcal{E}$.

### 2023-04-23 main.tex
lll

--- 2023-04-23 main.tex
@@
 \end{equation}
-The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$, $\lambda_i\geq \lambda_{i+1}$ and $\sum_{i=1}^N \lambda_i = \nu$.
+The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with  $\lambda_i\geq \lambda_{i+1}$,  $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.
 We are interested in the {\em symmetric} finite-dimensional representations with 
@@
 \end{equation} 
+The generators of the symmetric representations will be denoted by $E_{ab}$.
 The basis elements of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
@@
 \end{equation}
+{\color{blue}
 where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$.
-Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
+Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.}
+{\color{red}remove?}
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
 \begin{equation}
-    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}
-\end{equation}
+    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
+\end{equation}
+
+{\color{red}Maybe some more text below}
 We introduce the Hamiltonian operator
-
 \begin{equation}\label{OriginalHamiltonian}

### 2023-04-28 main.tex
kk
ii

@@
 \end{equation}
+{\color{red} notation}
 This means that on the edge $(x,y)\in \mathcal{E}$  a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$.
@@
 \end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vectors obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
 The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
@@
 \textbf{Remark}:
-when the state spaces of the dual processes is finite, the generators and the duality function are matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
+when the state spaces of the dual processes is finite, the generators and the duality function can be represented as with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
 Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as
@@
 Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$.
-Working with the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads
+Working in terms of the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads
 \begin{equation}\label{DualityRelation}
@@
 \end{equation}
-The dual process is defined by its generator, which reads
+The dual process is defined by its Markov generator, which reads
  \begin{equation}\label{DualGenerator}
@@
 Therefore the dual dynamics is described as follows.
-On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual generator gives rise to  the multi-species stirring dynamics on the graph.
+On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual Markov generator gives rise to  the multi-species stirring dynamics on the graph.
 On the other hand, the site
@@
 To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{dualityIntertwines} is fulfilled.
-To show this, we will use the Hamiltonians (linked with the generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
-Indeed, in this formalism the proof reduces to finding symmetries and exponential transformation of generators of the Lie algebra.\\
-To each configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of the dual process we associate the vector
+To show this, we will use the Hamiltonians (linked with the Markov generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
+Indeed, in this formalism the proof reduces to finding symmetries and group like transformation of generators of the Lie algebra.\\
+To a configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of a dual process we associate the vector
 \begin{equation}
@@
 \end{equation}
-Here we introduced bosonic creation operator $a^{\dagger}$ acting as $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
+Here we introduced bosonic creation operator $a^{\dagger}$ acting on the left-hand-side as $\langle q|a^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
 $(a^{\dagger})_{a}^{u(x)}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{2,\ldots,N\}$. \\
@@
 \end{equation}
-We perform the duality proof in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show\eqref{siteDualRelation}.
+We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show \eqref{siteDualRelation}.
 As a preliminary result we note that 
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
 	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
@@
 \begin{equation}
-	\mathcal{H}_{x,y}S_{x,y}=S_{s,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
+	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
 \end{equation}
@@
 \begin{equation}\label{hamiltonian}
-	H=H_{1}+H_{bulk}+H_{L}
+	H=H_{left}+H_{bulk}+H_{right}
 \end{equation}
@@
 \begin{equation}
-	H_{1}=\begin{pmatrix}
+	H_{left}=\begin{pmatrix}
 		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
@@
 \begin{equation}
-	H_{L}=\begin{pmatrix}
+	H_{right}=\begin{pmatrix}
 		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
@@
 \begin{equation}
-	\widetilde{H}=\widetilde{H}_{1}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{L}
+	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
 \end{equation}
@@
 \begin{equation}
-	|\Psi\rangle=\frac{1}{Z^{L}}\langle W|\begin{pmatrix}
+	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}
 		X_{1}\\
@@
 	\begin{equation}
-		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle W|
+		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle W|=0
 	\end{equation}
@@
 \begin{equation}\label{hatHamiltonian}
-   H^{'}:=H^{'}_{1}+H_{bulk}+H^{'}_{L}
+   H^{'}:=H^{'}_{left}+H_{bulk}+H^{'}_{L}
 \end{equation}
@@
 \begin{equation}
-	H^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+	H^{'}_{left}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
 \end{equation}
@@
 	\begin{split}
-		H_{1}^{'}&=S_{1}H_{1}S_{1}^{-1}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}
+		H_{left}^{'}&=S_{1}H_{left}S_{1}^{-1}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}
 		\\&=
@@
 \begin{equation}
-H_{1}^{'}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
-\end{equation}
-\textbf{Remark:} the boundary Hamiltonians $H_{1}^{'}$ and $H_{L}^{'}$ relates to the transposed of  $\widetilde{H}_{1}$ and $\widetilde{H}_{L}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
+H_{left}^{'}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+\end{equation}
+\textbf{Remark:} the boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
 They are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp.
@@
 \begin{equation}
-	H^{''}=H_{1}^{''}+H_{bulk}+H_{L}^{''}
+	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}
 \end{equation}
@@
 \begin{align}
-	H_{1}^{''}=e_{11}^{1}-\mathbbm{1}^{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}^{1}\qquad H_{L}^{''}=e_{11}^{L}-\mathbbm{1}^{L}
+	H_{left}^{''}=e_{11}^{1}-\mathbbm{1}^{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}^{1}\qquad H_{right}^{''}=e_{11}^{L}-\mathbbm{1}^{L}
 \end{align}
@@
 the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal.
-The expressions of $H_{1}^{''}$ and $H_{L}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=2}^{N}\beta_{c}e_{c1}$ and $A=e_{a1},$ and $A=e_{aa}$.
+The expressions of $H_{left}^{''}$ and $H_{right}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=2}^{N}\beta_{c}e_{c1}$ and $A=e_{a1},$ and $A=e_{aa}$.
 We compute
@@
 	\begin{split}
-		H_{1}^{''}&=S_{2}H_{1}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}
+		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}
 		\\&=
@@
 	\begin{split}
-			H_{L}^{''}&=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}
+			H_{right}^{''}&=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}
 			\\&=
@@
 \begin{equation}
-	\mathcal{L}=\mathcal{L}_{1}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{L}
+	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}
 \end{equation} 
@@
 \begin{equation}
-	\mathcal{L}_{1}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\\bm{delta}_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{delta}_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{1}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{L}
+	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
 \end{equation} 
@@
 	\begin{split}
-		\widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
+		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
 	\end{split}
@@
 	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
 	\end{split}
@@
 \begin{equation}\label{thermalizedGenerator}
-	\mathcal{L}^{TH}=\mathcal{L}_{1}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{L}^{TH}
+	\mathcal{L}^{TH}=\mathcal{L}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{right}^{TH}
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
 		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
@@
 \begin{equation}
-		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{1}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{L}^{TH}
-\end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{1}^{TH}$ and $\widetilde{\mathcal{L}}_{L}^{TH}$ are absorbing with rate $1$, i.e. 
-\begin{equation}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{1}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
-	\end{split}
-\end{equation}
-and similarly $\widetilde{\mathcal{L}}_{L}^{TH}$. 
+		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{right}^{TH}
+\end{equation}
+where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 
+\begin{equation}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{left}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
+	\end{split}
+\end{equation}
+and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$. 
 The duality function is 
@@
 \end{equation}
-First, we act with $\mathcal{L}_{1}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
+First, we act with $\mathcal{L}_{left}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
 \begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
 	\\&\nonumber
@@
 \begin{align}
-	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&=
@@
 \begin{equation}
-    \mathcal{L}_{1}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{L}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+    \mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{split}
-        \widetilde{\mathcal{L}}_{1}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
+        \widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
         \end{split}

### 2023-05-04 main.tex
SolutionG-Draft

@@
 We define 
-\begin{equation}
+\begin{equation}\label{HSecond}
 	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}
@@
 \end{equation}
+\subsection{Eigenvectors of the non equilibrium Hamiltonian}
+For simplicity we first consider the case with $N=3$.
+We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}.
+For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
+The eigenvectors are the following:
+\begin{equation}
+	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{equation}
+
+We replace the above eigenvectors in 
+\begin{equation}
+	T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
+\end{equation}
+and we obtain
+\begin{align*}
+	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\\&
+	+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\\&=
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+\end{align*}
+after a change of summation indexes we obtain
+\begin{align*}
+	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\\+&
+	\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\\+&
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\\=&
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle.
+\end{align*}
+We impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
+\begin{enumerate}
+	\item $k_{2}=0$ and $k_{3}=0$
+	\begin{equation}\label{cond1}
+		T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}
+	\end{equation}
+	\item $k_{2}=m_{2}+1$ and $k_{3}\in \{0,\ldots,m_{3}\}$
+	\begin{equation}\label{cond2}
+		\begin{split}
+			B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
+		\end{split}
+	\end{equation}
+	\item $k_{2}\in\{0,\ldots,m_{2}\}$ and $k_{3}=m_{3}+1$
+	\begin{equation}\label{cond3}
+		\begin{split}
+			B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
+		\end{split}
+	\end{equation}
+	\item $k_{2}\in \{0,\ldots,m_{2}\}$ and $k_{3}\in\{0,\ldots,m_{3}\}$
+	\begin{equation}\label{cond4}
+		\begin{split}
+			&\left(G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+			\\=&
+			\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+		\end{split}
+	\end{equation} 
+%	\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
+	%\begin{equation}\label{cond5}
+	%	\begin{split}
+	%		&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	%		=
+	%		\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	%	\end{split}
+%	\end{equation}
+%	\begin{equation}\label{cond6}
+	%	\begin{split}
+	%		&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	%		=
+	%		\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	%	\end{split}
+%	\end{equation}
+\end{enumerate}
+To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1},\eqref{cond2},\eqref{cond3},\eqref{cond4}.
+% \end{itemize}
+\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
+\begin{equation}
+	\begin{split}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}
+		\\&
+		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
+	\end{split}
+\end{equation}
+We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
+\begin{equation}
+	\begin{split}
+	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
+	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+	\end{split}
+\end{equation}
+Therefore we rewrite \eqref{cond4} as 
+\begin{equation}
+	\begin{split}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\end{split}
+\end{equation}
+The left-hand-side is 
+\begin{equation}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+\end{equation}
+while, on the right-hand-side we have
+\begin{equation}
+	\begin{split}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}+\cdots+k_{3}}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+\\&=
+\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\end{split}
+\end{equation}
+and similarly 
+\begin{equation}
+	\begin{split}
+		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+		\\&=
+		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
+	\end{split}
+\end{equation}
+Therefore,
+\begin{equation}
+	\begin{split}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+\\&+
+	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\\&=
+	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\\&=
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+	\end{split}
+\end{equation}
+We can generalize it to arbitrary number of species writing
+\begin{equation}
+	\begin{split}
+	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{N}\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\end{split}
+\end{equation}
+Denoting by
+\begin{equation}
+A_{j}=	\left\{\left((\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
+\end{equation}
+the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
+\begin{equation}
+	\begin{split}
+G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
+\\&
+\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=k_{q}\}}\right)
+\\&
+\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
+	\end{split}
+\end{equation}
+Condition \eqref{cond4} becomes
+\begin{equation}\label{cond4General}
+	G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
+\end{equation}
+Arguing as in the case $N=3$ we observe that 
+\begin{equation}
+	\begin{split}
+		A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
+	\\&
+	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=k_{q}\}}\right)
+	\\&
+	\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
+	\end{split}
+\end{equation}
+therefore \eqref{cond4General} is fulfilled. 
+\begin{comment}
+We show that, if these previous conditions are satisfied, then the $|\Psi^{\Delta}_{m_{2},m_{3}}\rangle$ are indeed eigenvalues of $H^{''}$. 
+\begin{align*}
+T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+\\&+
+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots +
+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
+\begin{align*}
+T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+\\&+
+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots
+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+
+\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots +
+\Delta_{N}^{m_{N}+1}\sum_{a_{2}=0}^{m_{3}}\ldots\sum_{a_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
+\begin{align*}
+T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+\\&+
+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots +
+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\end{align*}
+then
+\begin{align*}
+T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
+\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+\\&+
+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+\\&=
+\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle
+\end{align*} 
+\end{comment}
+\subsection{Charges}
 Then we have
@@
 \end{equation}
+\begin{comment}
 \subsection{Eigenvector for the diagonal-triangular chain}
@@
 \end{equation} 
-
+\end{comment}
 \subsection{Bethe ansatz solution}

### 2023-05-04 main.tex
G-solution II

@@
 We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}.
-For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
+We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
 The eigenvectors are the following:
@@
 \begin{align*}
-	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-	\\&
-	+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-	\\&=
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+	\\+&
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+	\\=&
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 \end{align*}
-after a change of summation indexes we obtain
+after a change of summation indices we obtain
 \begin{align*}
-	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\+&
-	\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\+&
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\=&
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle.
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}.
 \end{align*}
@@
 	\end{equation}
-	\item $k_{2}\in \{0,\ldots,m_{2}\}$ and $k_{3}\in\{0,\ldots,m_{3}\}$
+	\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}\in\{1,\ldots,m_{3}\}$ 
 	\begin{equation}\label{cond4}
 		\begin{split}
-			&\left(G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+			&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}\left(B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 			\\=&
-			\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		\end{split}
-	\end{equation} 
-%	\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
-	%\begin{equation}\label{cond5}
-	%	\begin{split}
-	%		&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
-	%		=
-	%		\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-	%	\end{split}
-%	\end{equation}
-%	\begin{equation}\label{cond6}
-	%	\begin{split}
-	%		&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
-	%		=
-	%		\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-	%	\end{split}
-%	\end{equation}
+			G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+		\end{split}
+	\end{equation} 
+\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
+\begin{equation}\label{cond5}
+	\begin{split}
+		&	\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+		=
+	G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+	\end{split}
+\end{equation}
+\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}=0$
+	\begin{equation}\label{cond6}
+		\begin{split}
+			&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+			=
+	G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+		\end{split}
+	\end{equation}
+
 \end{enumerate}
-To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1},\eqref{cond2},\eqref{cond3},\eqref{cond4}.
+To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
 % \end{itemize}
@@
 \end{equation}
+where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
 Therefore we rewrite \eqref{cond4} as 
@@
 \begin{equation}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 \end{equation}
@@
 	\begin{split}
-		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 		\\&=
@@
 	\\&=
-	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 	\\&=
@@
 \end{equation}
-We can generalize it to arbitrary number of species writing
-\begin{equation}
-	\begin{split}
-	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{N}\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.
+
+\paragraph{Genearlization to $N$ species:} we can generalize the eigenvector formula for arbitrary number of species $N>2$ by writing
+\begin{equation}
+	\begin{split}
+	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
 	\end{split}
@@
 \\&
-\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=k_{q}\}}\right)
+\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=\,k_{q}\}}\right)
 \\&
@@
 therefore \eqref{cond4General} is fulfilled.
+Again, the equivalent of conditions \eqref{cond1}, e\eqref{cond5} and \eqref{cond6} are trivially satisfied.
+The equivalents of conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{j}(x)$ are rising operators for all $j\in \{2,\ldots,N\}$.
 \begin{comment}

### 2023-05-05 main.tex
iji
better
kk
D22 pol

@@
 	\begin{split}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
 		\\&
@@
 \begin{equation}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 \end{equation}
@@
 	\begin{split}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}+\cdots+k_{3}}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&=
-\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+\\&=
+\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 	\end{split}
@@
 	\begin{split}
-		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-		\\&=
-		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
+		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+		\\&=
+		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
 	\end{split}
@@
 	\begin{split}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 \\&+
-	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-	\\&=
-	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\\&=
+	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 	\\&=
@@
 \\&
-\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=\,k_{q}\}}\right)
+\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=\,k_{q}\}}\right)
 \\&
@@
 	\\&
-	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=k_{q}\}}\right)
+	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=k_{q}\}}\right)
 	\\&
@@
 	\begin{split}
-		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
-	\end{split}
-\end{equation}
+		A^{2L-1}=3e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
+	\end{split}
+\end{equation}
+{\color{blue}ok}
+
 We observe that $\forall i,j=1,2,\ldots,N$
 \begin{equation}
-	\sum_{a,b=1}^{L}e_{i,j}^{[a]}e_{j,i}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
+	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
 \end{equation}
@@
 \end{equation}
+{\color{blue}ok}
+
 While, $\forall i=2,\ldots,N$
@@
 \end{equation}
+{\color{blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
+\begin{equation*}
+	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
+\end{equation*}
+where
+\begin{equation*}
+	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
+\end{equation*}
+This gives exactly
+\begin{equation*}
+	D_{22}^{2L-1}=\left(
+	\begin{array}{ccccccccc}
+		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
+		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
+		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
+	\end{array}
+	\right)
+\end{equation*}
+}
 \textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\

### 2023-05-05 main.tex
ll

@@
 \end{equation}
-\begin{equation}\label{a2lm1}
-	\begin{split}
-		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
-		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
-	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
-		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
-		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
-	\end{split}
-\end{equation}
+% \begin{equation}\label{a2lm1}
+% 	\begin{split}
+% 		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
+% 		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
+% 	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
+% 		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
+% 		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
+% 	\end{split}
+% \end{equation}
 
 We rewrite
-\begin{equation}
-	\begin{split}
-	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
-\end{split}
-\end{equation}
-then
-\begin{equation}
-\begin{split}
-\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
-	\end{split}
-\end{equation}
-{\color{blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
-\begin{equation*}
-	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
-\end{equation*}
-where
-\begin{equation*}
-	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
-\end{equation*}
-This gives exactly
-\begin{equation*}
-	D_{22}^{2L-1}=\left(
-	\begin{array}{ccccccccc}
-		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
-	\end{array}
-	\right)
-\end{equation*}
-}
+% \begin{equation}
+% 	\begin{split}
+% 	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
+% \end{split}
+% \end{equation}
+% then
+\begin{equation}
+\begin{split}
+\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
+	\end{split}
+\end{equation}
+{\color{blue}ok}
+
+% {\color{blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
+% \begin{equation*}
+% 	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
+% \end{equation*}
+% where
+% \begin{equation*}
+% 	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
+% \end{equation*}
+% This gives exactly
+% \begin{equation*}
+% 	D_{22}^{2L-1}=\left(
+% 	\begin{array}{ccccccccc}
+% 		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+% 		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+% 		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+% 		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
+% 		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
+% 		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
+% 		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+% 		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
+% 		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
+% 	\end{array}
+% 	\right)
+% \end{equation*}
+% }
 \textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\

### 2023-05-05 main.tex
i
ii

--- 2023-05-05 main.tex
@@
 % \end{itemize}
+\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
+TO ADD
 \subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
@@
 \end{equation}
-{\color{blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
-\begin{equation*}
-	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
-\end{equation*}
-where
-\begin{equation*}
-	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
-\end{equation*}
-This gives exactly
-\begin{equation*}
-	D_{22}^{2L-1}=\left(
-	\begin{array}{ccccccccc}
-		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
-		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
-	\end{array}
-	\right)
-\end{equation*}
-}
+{\color{blue}ok}
+%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
+%\begin{equation*}
+%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
+%\end{equation*}
+%where
+%\begin{equation*}
+%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
+%\end{equation*}
+%This gives exactly
+%\begin{equation*}
+%	D_{22}^{2L-1}=\left(
+%	\begin{array}{ccccccccc}
+%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
+%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
+%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
+%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
+%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
+%	\end{array}
+%	\right)
+%\end{equation*}
+%}
 \textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\

### 2023-05-05 main.tex
Fixed B formula

@@
 \begin{split}
-	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)\\
-	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{a=2}^{N}e_{a1}^{[a]}e_{ja}^{[b]}\right)
+	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
+	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
 \end{split}
@@
 	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
-	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{a=2}^{N}e_{ja}^{[a]}e_{a1}^{[b]}}
+	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)}
 \end{split}

### 2023-05-05 main.tex
G symmetric group

@@
 \subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
-TO ADD
-\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
+ For the sake of notation we denote by 
+\begin{equation}
+	\begin{split}
+		A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
+		A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+	\end{split}
+\end{equation}
+where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
+\begin{equation}\label{cond4A}
+	\begin{split}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\end{split}
+\end{equation}
+To write its solution we define
+\begin{equation}
+	\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
+\end{equation}
+We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
+\begin{equation}
+	\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
+\end{equation}
+We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group.
+\\
+The following expression solves \eqref{cond4A}
+\begin{equation}
+	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
+\end{equation}
+Indeed
+\begin{align}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+\\&+
+ A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&=
+ \sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&+
+ \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&=
+ \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&=
+ 	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+\end{align}
+where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
+\paragraph{Generalization to arbitrary $N$}
+For arbitrary $N\geq2$ we have 
+\begin{equation}
+	\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}
+\end{equation}
+
+Thus the explicit expression becomes
+\begin{equation}
+G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
+\end{equation}
+with the same notation as in $N=3$ case. 
+\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
 \begin{equation}

### 2023-05-09 main.tex
kk

@@
 \end{equation}
+{\color{red}Are we missing the prefactor $(N+2x)$?}
 where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
@@
 \begin{align}
-	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
-	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
+	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
+	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}2+2N}\\
 	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
@@
 it has the property that commute with the equilibrium Hamiltonian.
+
+All terms are diagonal except the last one which can  be  identified with the second Casimir of the $gl(n-1)$ subalgebra
+\begin{equation}
+\hat C_2^{N-1} \sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+\end{equation} 
+On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues given in terms of shifted weights 
+\begin{equation}
+ C_2^{N-1}=\sum\prod\frac{1}{\ell-\ell}
+\end{equation} 
+Thus the eigenvalues of the transfer matrix can be writen as 
+\begin{equation}
+ \Lambda(x)=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)\sum_{j=2}^{N}m_j+2C_{2}^{N-1}\right)x^{2L}+\ldots
+\end{equation} 
+Thus the difference is of order $2L$ and becomes
+\begin{equation}
+ \lambda(x)-T_0(x)=x^{2L}....
+\end{equation}
+
 In case of $N=2$ it differs with respect to the $Q_{2L}^{0}$ computed in formula (2.28) of \cite{frassek2020eigenstates} by the following matrix 

### 2023-05-09 main.tex
ll
prefactor
kk

@@
 	\begin{split}
-		A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-		A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+		A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
+		A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
 	\end{split}
@@
 	\begin{split}
-	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
+	A_{3}=\left\{\left((2x+N)(\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
 	\end{split}
@@
 
-All terms are diagonal except the last one which can  be  identified with the second Casimir of the $gl(n-1)$ subalgebra
+All terms are diagonal except the last one which can  be  identified with the second Casimir of the $gl(N-1)$ subalgebra
 \begin{equation}
@@
 \begin{equation}
- \Lambda(x)=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)\sum_{j=2}^{N}m_j+2C_{2}^{N-1}\right)x^{2L}+\ldots
-\end{equation} 
+\begin{split}
+ \Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
+ \\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)\sum_{j=2}^{N}m_j+2C_{2}^{N-1}\right)x^{2L}+\ldots
+ \end{split}
+\end{equation} 
+{\color{blue}Do we have $
+ \sum_{i=1}^N m_i=L$?
+}
 Thus the difference is of order $2L$ and becomes
 \begin{equation}
- \lambda(x)-T_0(x)=x^{2L}....
-\end{equation}
+ \Lambda(x)-T_0(x)=x^{2L}\left(\Lambda_{2L}-Q_{2L}^0\right)+\ldots
+\end{equation} 
+We can take the limit
+\begin{equation}
+ \lim_{x\to\infty}\frac{2x+N}{\Lambda(x)-T_0(x)}B_{i}(x)=\frac{2}{\Lambda_{2L}-Q_{2L}^0}B_i^{2L-1}
+\end{equation} 
+{\color{blue}ok?}
 

### 2023-05-09 main.tex
ll
s
ii

@@
 	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-	A_{3}=\left\{\left((2x+N)(\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+	A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
 	\end{split}
@@
 \begin{equation}
-A_{j}=	\left\{\left((\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
+A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
 \end{equation}
@@
 \begin{equation}
-	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}
-\end{equation}
-{\color{blue}ok}
+	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}=2e_{11}^{tot}\left(e_{11}^{tot}+I^{tot}\right)-L
+\end{equation}
+{\color{blue}ok?}
 
@@
 \begin{split}
-\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
-	\end{split}
-\end{equation}
-{\color{blue}ok}
+\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}=	2Ne_{ii}^{tot}+ 2e_{11}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+	\end{split}
+\end{equation}
+{\color{blue}ok?}
 %blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
@@
 \begin{split}
-Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
-\end{split}
-\end{equation}
-it has the property that commute with the equilibrium Hamiltonian.
+Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
+&=N+2e_{11}^{tot}(e_{11}^{tot}+1)-(N+2)(L-e_{11}^{tot})+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
+\end{split}
+\end{equation}
+where we used $
+ \sum_{i=1}^N m_i=L$.
+
+%  It has the property that commute with the equilibrium Hamiltonian.
 
@@
 \begin{equation}
-\hat C_2^{N-1} \sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+\hat C_2^{N-1}= \sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
 \end{equation} 
@@
 \begin{equation}
- C_2^{N-1}=\sum\prod\frac{1}{\ell-\ell}
-\end{equation} 
+ C_2^{N-1}=\sum_{j=1}^{N-1}\ell_j(\ell_j -N+2)+\frac{1}{6}(N-1)(N-2)(N-3)
+\end{equation} 
+{\color{blue}to be checked}, see e.g. [Das,Okubo].
 Thus the eigenvalues of the transfer matrix can be writen as 
@@
  \Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
- \\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)\sum_{j=2}^{N}m_j+2C_{2}^{N-1}\right)x^{2L}+\ldots
- \end{split}
-\end{equation} 
-{\color{blue}Do we have $
- \sum_{i=1}^N m_i=L$?
-}
+ \\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)(L-m_1)+2C_{2}^{N-1}\right)x^{2L}+\ldots
+ \end{split}
+\end{equation}
+
 Thus the difference is of order $2L$ and becomes
@@
 \end{equation}
+{\color{blue}Adopt notation here}
 \begin{comment}

### 2023-05-09 main.tex
ss

@@
 \end{equation}
-{\color{blue}ok?}
+{\color{blue}ok?}where we used $
+ \sum_{i=1}^Ne_{ii}^{tot}=L$.
 
@@
 Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
-&=N+2e_{11}^{tot}(e_{11}^{tot}+1)-(N+2)(L-e_{11}^{tot})+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
-\end{split}
-\end{equation}
-where we used $
- \sum_{i=1}^N m_i=L$.
+&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
+\end{split}
+\end{equation}
 

### 2023-05-26 main.tex
B
i

@@
 \subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
+
  For the sake of notation we denote by 
@@
 \end{equation}
-{\color{red}Are we missing the prefactor $(N+2x)$?}
+%{\color{red}Are we missing the prefactor $(N+2x)$?}
 where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
+
 \begin{equation}\label{cond4A}
@@
 \end{equation}
+We introduce the following indices
+\begin{equation}
+	i_{1}=\ldots=i_{k_{2}}=2\qquad i_{k_{2}+1}=\ldots =i_{k_{2}+k_{3}}=3
+\end{equation}
+Then, we introduce the permutation 
+\begin{equation}
+	\sigma(i_{j})=i_{k}\qquad \forall j,k=1,\ldots,k_{2}+k_{3}
+\end{equation}
+We write
+\begin{equation}
+	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
+\end{equation}
+where we denoted by $\text{SYM}$ the symmetric group on $\{i_{1},\ldots,i_{k_{2}+k_{3}}\}$.\\
+It solves \eqref{cond4A}, indeed
+\begin{align*}
+	&A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\\=&A_{2}\frac{k_{2}}{k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}\frac{k_{3}}{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\\=&
+	A_{2}\frac{k_{2}}{k_{2}}\frac{1}{(k_{2}-1)!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\\+&A_{3}\frac{k_{3}}{k_{3}}\frac{1}{k_{2}!(k_{3}-1)!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
+	\\=&
+	\frac{1}{k_{2}!k_{3}!}\left(\sum_{\sigma \in \text{SYM}}k_{2}A_{2}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}+ \sum_{\sigma \in \text{SYM}}k_{3}A_{3}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\right)
+	\\=&
+	\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
+	\\=&
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+\end{align*}
+where in the up to last equality we used the fact that the quantity first summation is symmetric with respect to the exchange of $A_{2}$ and thus we have $k_{2}$ equal terms.
+Similarly, for the second summation using the symmetry with respect to $A_{3}$.
+\\
+This argument can be generalized for $N>2$ species introducing
+\begin{equation}
+	G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\frac{1}{k_{2}!\cdots k_{N}!}\sum_{\sigma\in \text{SYM}}A_{i_{1}}\cdots A_{i_{k_{2}+\cdots+k_{N}}}
+\end{equation}
+where we assumed 
+\begin{equation}
+	i_{1}=\cdots=i_{k_{2}}=2,\qquad \ldots \qquad i_{k_{2}+\cdots+k_{N-1}}=\cdots=i_{k_{2}+\ldots+k_{N}}=N
+\end{equation}
+\begin{comment}
 To write its solution we define
@@
 with the same notation as in $N=3$ case. 
+\end{comment}
 \subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
@@
 \end{equation}
+\begin{equation}
+\begin{split}
+	B_{j}^{2L-1}&=
+	2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
+	&=
+	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
+\end{split}
+\end{equation}
 \textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
@@
 	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
-	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}2+2N}\\
+	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}N+2L-1}\\
 	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
@@
 \end{equation} 
-
+we also introduce 
+\begin{equation}
+	\mathcal{Q}_{2L}=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+\end{equation}
+therefore we can write 
+\begin{equation}
+	Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
+\end{equation}
 %  It has the property that commute with the equilibrium Hamiltonian.
@@
 \end{equation} 
-{\color{blue}to be checked}, see e.g. [Das,Okubo].
+{\color{blue}to be checked...} {\color{blue} It works!!}, see e.g. [Das,Okubo].
 Thus the eigenvalues of the transfer matrix can be writen as 
@@
 \end{equation} 
-{\color{blue}ok?}
-
+{\color{blue}ok}
+
+\begin{comment}
 In case of $N=2$ it differs with respect to the $Q_{2L}^{0}$ computed in formula (2.28) of \cite{frassek2020eigenstates} by the following matrix 
@@
 {\color{blue}Adopt notation here}
+\end{comment}
 \begin{comment}

### 2023-05-28 main.tex
Q0

@@
 	\begin{split}
-Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
-&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
-\end{split}
-\end{equation} 
+	Q_{2L}^{0}&=N(I^{tot}+e_{11}^{tot})+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{k=2}^{N}e_{kk}^{tot}-2N\sum_{k=2}^{N}e_{kk}^{tot}+\sum_{k=2}^{N}\left\{e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+\sum_{j=2}^{N}e_{kj}^{tot}e_{jk}^{tot}\right\}
+	\\&=
+	(N-NL-2L)I^{tot}+2(N+2)e_{11}^{tot}+2e_{11}^{tot}e_{11}^{tot}+2\sum_{j,k=2}^{N}e_{kj}^{tot}e_{jk}^{tot}
+	\end{split}
+\end{equation}
+%\begin{equation}	
+%\begin{split}
+%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
+%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
+%\end{split}
+%\end{equation} 
 we also introduce 

### 2023-06-06 main.tex
Exchange-Double-Row

@@
 \end{equation}
+This double row monodromy satisfies the following exchange relation
+\begin{equation}
+	R_{ab}(x-y)U_{a}(x)R_{ab}(x+y)U_{b}(y)=U_{b}(y)R_{ab}(x+y)U_{a}(x)R_{ab}(x-y)
+\end{equation}
 This trasfer matrix has the following properties

### 2023-07-19 main.tex
FCR
Dij charge
Cleaning up

@@
-\documentclass[11pt]{article}
+\documentclass[10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \section{Mapping to equilibrium?}
-{\color{red}
 check also Appendix A in
-\cite{Alcaraz:1992zc} }
-
-\cite{Sklyanin:1988yz}
+\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}
+
 \subsection{Quantum inverse scattering method}
@@
 In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
-We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
+We introduce the following matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
 \begin{equation}\label{Rmatrix}
@@
 \end{equation}
+\begin{comment}
+\begin{equation}
+\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
+\end{equation}
+\begin{equation}
+K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
+\end{equation}
+\end{comment}
 \begin{equation}\label{KmatrixHAT}
-\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
+	\widehat{K}_{0}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}
+		1-x&0&\ldots&0\\
+		0&1-x&\ldots&0\\
+		\vdots&\vdots&\ddots&\vdots\\
+		0&0&\ldots&1+x
+	\end{pmatrix}
 \end{equation}
 \begin{equation}\label{Kmatrix}
-K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
+	K_{0}=\left((2x+N)H^{''}_{left}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
+		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
+		0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
+		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
+		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
+		0&0&0&\ldots&0&1+x
+	\end{pmatrix}
 \end{equation}
@@
 \begin{equation}
-	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
+	T^{\Delta}(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
 \end{equation}
@@
 This double row monodromy satisfies the following exchange relation
-\begin{equation}
+\begin{equation}\label{RURU}
 	R_{ab}(x-y)U_{a}(x)R_{ab}(x+y)U_{b}(y)=U_{b}(y)R_{ab}(x+y)U_{a}(x)R_{ab}(x-y)
@@
 \begin{equation}
-	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
+	\left[T^{\Delta}(x),T^{\Delta}(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T^{\Delta}(0))=C_{1}H^{''}+C_{2}I
 \end{equation}
@@
 We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
+\begin{comment}
 \begin{equation}
 	U_{0}(x)=\begin{pmatrix}
-		A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
+		D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
 		C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
@@
 \end{equation}
-In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e.
+\end{comment}
+\begin{equation}
+	U_{0}(x)=\begin{pmatrix}
+		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
+		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
+		\vdots&\vdots&\ddots&\vdots&\vdots\\
+		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
+		B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
+	\end{pmatrix}
+\end{equation}
+The exchange relations for the elements of the above matrix can be found using \eqref{RURU}
+\begin{itemize}
+	\item for every $i\in\{1,\ldots,N-1\}$
+	\begin{equation}\label{EX1}
+		\begin{split}
+		D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
+		\end{split}	
+	\end{equation}
+\begin{equation}\label{EX2}
+	\begin{split}
+		D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
+	\end{split}
+\end{equation}
+\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
+\begin{equation}\label{EX3}
+	\begin{split}
+		D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{i,i}(y)+B_{i}(y)D_{N,N}(x)\right)
+		\\&-
+		\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)+B_{i}(x)D_{N,N}(y)\right)
+		\\&+
+		h_{1}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}\left(B_{k}(x)D_{k,i}(y)-B_{k}(y)D_{k,i}(x)\right)
+	\end{split}
+\end{equation}
+\end{itemize}
+where
+\begin{align}
+	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
+	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
+	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
+\end{align}
+\begin{comment}
+\begin{itemize}
+	\item for $j\neq N$ 
+\begin{equation}
+	\begin{split}
+	B_{j}(x)D_{jj}(y)=&\frac{(x+y)(1+x-y)}{(x-y)(1+x+y)}D_{jj}(y)B_{j}(x)-\frac{1}{(1+x+y)}\sum_{i=1\,:\,i\neq j}^{N-1}B_{i}(x)D_{i1}(y)
+	\\-&\frac{(x+y)}{(x-y)(1+x+y)}D_{jj}(x)B_{j}(y)-\frac{1}{(1+x+y)}D_{NN}(x)B_{j}(y)
+	\end{split}
+\end{equation}
+\item for $i,j\neq N$
+\begin{equation}
+	\begin{split}
+		B_{i}(x)D_{jj}(y)=D_{jj}(y)B_{j}(x)+\frac{1}{(x-y)}\left(D_{ji}(y)B_{j}(x)-D_{ji}(x)B_{j}(y)\right)
+	\end{split}
+\end{equation}
+\item for $j\neq N$
+\begin{equation}
+	\begin{split}
+		B_{j}(x)D_{NN}(y)&=\frac{(x-y)(1+x+y)}{(x+y)(1+x-y)}D_{NN}(y)B_{j}(x)+\frac{(x-y)}{(x+y)(1+x-y)}\sum_{i=1}^{N-1}B_{i}(y)D_{ij}(x)
+		\\&+
+		\frac{1}{(1+x-y)}B_{j}(y)D_{NN}(x)
+	\end{split}
+\end{equation}
+\end{itemize}
+\end{comment}
+%In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e.
 when the left boundary is lower triangular a end the right one is diagonal.
 We properly rescale them and we obtain
-\begin{equation}
-	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
-		1+x&0&\ldots&0\\
-		0&1-x&\ldots&0\\
-		\vdots&\vdots&\ddots&\vdots\\
-		0&0&\ldots&1-x
-	\end{pmatrix}
-\end{equation}
-\begin{equation}
-	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
-		N+x&0&\ldots&0\\
-		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
-		\vdots&\vdots&\ddots&\vdots\\
-		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
-	\end{pmatrix}
-\end{equation}
-Then we obtain the correspondent transfer matrix as
-\begin{equation}
-	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
-\end{equation}
-where
-\begin{equation}
-	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
-\end{equation}
+
+%Then, we obtain the correspondent transfer matrix as
+%\begin{equation}
+%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
+%\end{equation}
+%where
+%\begin{equation}
+%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
+%\end{equation}
 \subsection{Eigenvectors of the non equilibrium Hamiltonian}
@@
 	\begin{split}
-	T^{\Delta}(x)&=tr_{0}\left(\begin{pmatrix}
-		N+x&0&\ldots&0\\
-		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
-		\vdots&\vdots&\ddots&\vdots\\
-		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
-	\end{pmatrix}\begin{pmatrix}
-	A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
-	C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
-	\vdots&\vdots&\ddots&\vdots\\
-	C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
-\end{pmatrix}\right)\\&=
-(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=
-Q_{2L+2}x^{2L+2}+Q_{2L+1}x^{2L+1}+Q_{2L}x^{2L}+\ldots
-\end{split}
-\end{equation}
-We call these $Q_{a}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
+	T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
+		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
+		0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
+		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
+		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
+		0&0&0&\ldots&0&1+x
+	\end{pmatrix}\right.
+\\& \left.
+\;\;\;\begin{pmatrix}
+	D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
+	D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
+	\vdots&\vdots&\ddots&\vdots&\vdots\\
+	D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
+	B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
+\end{pmatrix}\right)
+\end{split}
+\end{equation}
+Therefore we can write the polynomial expansion
+\begin{equation}
+	\begin{split}
+		T^{\Delta}(x)=&
+		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
+		\sum_{k=0}^{2L+2}Q_{k}x^{k}
+	\end{split}
+\end{equation}
+We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
 We can also introduce 
 \begin{equation}
-	T_{0}(x)=(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
+	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
 \end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
 \begin{equation}
-	A(x)=\sum_{a=0}^{2L+1}A^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}
+	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}
 \end{equation}
@@
 \begin{equation}
-	A(x)=A^{2L+1}x^{2L+1}+A^{2L}x^{2L+1}+A^{2L-1}x^{2L-1}+\ldots
-\end{equation}
-where .
-\begin{equation}
-	A^{2L+1}=I^{tot}
-\end{equation}
-\begin{equation}
-	A^{2L}=I^{tot}+2e_{11}^{tot}
-\end{equation}
-\begin{equation}
-	\begin{split}
-		A^{2L-1}=3e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}
+	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
+\end{equation}
+where 
+\begin{equation}
+	D_{N,N}^{2L+1}=I^{tot}
+\end{equation}
+\begin{equation}
+	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
+\end{equation}
+\begin{equation}
+	\begin{split}
+		D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
 	\end{split}
@@
 
-We observe that $\forall i,j=1,2,\ldots,N$
-\begin{equation}
-	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
+We observe that $\forall i,j=1,\ldots,N-1$
+\begin{equation}
+	\sum_{a\neq b}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
 \end{equation}
@@
 \begin{equation}
-	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}=2e_{11}^{tot}\left(e_{11}^{tot}+I^{tot}\right)-L
+	D_{N,N}^{2L-1}=e_{NN}^{tot}\left(2e_{NN}^{tot}+I^{tot}\right)-\sum_{j=1}^{N}e_{jj}^{tot}%=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
+\end{equation}
+Then
+\begin{equation}
+\boxed{D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L}
 \end{equation}
@@
 
-While, $\forall i=2,\ldots,N$
+While, $\forall i=1,\ldots,N-1$
 
@@
 	\begin{split}
-		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
-		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
+		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
+		&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
 	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
 		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
-		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
+		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
 	\end{split}
@@
 	\begin{split}
-	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
+	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
 \end{split}
@@
 \begin{split}
-\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}=	2Ne_{ii}^{tot}+ 2e_{11}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
-	\end{split}
-\end{equation}
-{\color{blue}ok?}
+D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+	\end{split}
+\end{equation}
+Then 
+\begin{equation}
+\boxed{D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
+\end{equation}
+{\color{blue}ok}
 %blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
@@
 %}
-\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
+%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
 %The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
@@
 \begin{split}
-	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
-	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)}
+	B_{j}^{2L-1}=2e_{j1}^{tot}+
+	2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
 \end{split}
@@
 	2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
-	&=
-	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
-\end{split}
+%	&=
+%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
+\end{split}
+\end{equation}
+Thus
+\begin{equation}
+\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
+\end{equation}
+Finally, for every $i,j=2,\ldots,N$ such that $i\neq j$, we have that 
+\begin{equation}
+	\boxed{D_{i,j}^{2L}=-2e_{ji}^{tot}}
 \end{equation}
@@
 \begin{align}
-	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
-	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}N+2L-1}\\
-	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+	Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
+	Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
+	Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
 \end{align}
@@
 \begin{equation}
-	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
-\end{equation}
-The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
+	\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
+\end{equation}
+The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
 We introduce the following:
 \begin{equation}
-Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
+Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
 \end{equation}
@@
 	\begin{split}
-	Q_{2L}^{0}&=N(I^{tot}+e_{11}^{tot})+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{k=2}^{N}e_{kk}^{tot}-2N\sum_{k=2}^{N}e_{kk}^{tot}+\sum_{k=2}^{N}\left\{e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+\sum_{j=2}^{N}e_{kj}^{tot}e_{jk}^{tot}\right\}
-	\\&=
-	(N-NL-2L)I^{tot}+2(N+2)e_{11}^{tot}+2e_{11}^{tot}e_{11}^{tot}+2\sum_{j,k=2}^{N}e_{kj}^{tot}e_{jk}^{tot}
+	Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
+	\\&=
+	(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
 	\end{split}
@@
 \begin{equation}
-	\mathcal{Q}_{2L}=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+	\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
 \end{equation}
@@
 \begin{equation}
-\hat C_2^{N-1}= \sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+\hat C_2^{N-1}= \sum_{i,j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
 \end{equation} 
@@
 {\color{blue}ok}
+\subsubsection{Exchange relations between charges}
+Using \eqref{EX1}, \eqref{EX2} and \eqref{EX3} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
+\begin{equation}
+	Q_{0}^{2L}B_{i}^{2L-1}=B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{j=1\,:\,j\neq i}^{N-1}B_{j}^{2L-1}D_{j,i}^{2L}
+\end{equation}
+%In particular for the case $N=3$ we have
+%\begin{equation}
+%	\begin{split}
+	%	Q_{0}^{2L}B_{1}^{2L-1}&=B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{3,3}^{2L})\right)-2B_{2}^{2L-1}D_{2,1}^{2L}
+	%	\\
+	%	Q_{0}^{2L}B_{2}^{2L-1}&=B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{3,3}^{2L})\right)-2B_{1}^{2L-1}D_{1,2}^{2L}
+%	\end{split}
+%\end{equation}
+Other useful exchange relations are 
+\begin{equation}
+	\begin{split}
+		D_{N,N}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}\left(D_{N,N}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%\\
+		%D_{33}^{2L}B_{2}^{2L}&=B_{2}^{2L}\left(D_{33}^{2L}+D_{22}^{2L+1}-D_{33}^{2L+1}\right)
+	\end{split}
+\end{equation}
+and
+\begin{equation}
+	\begin{split}
+		D_{i,i}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}\left(D_{i,i}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%\\
+		%D_{22}^{2L}B_{2}^{2L}&=B_{2}^{2L}\left(D_{22}^{2L}+D_{22}^{2L+1}-D_{33}^{2L+1}\right)
+	\end{split}
+\end{equation}
+and finally
+\begin{equation}
+	\begin{split}
+		D_{i,j}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}D_{i,j}^{2L}+B_{j}^{2L-1}\left(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%	D_{21}^{2L}B_{2}^{2L-1}&=B_{2}^{2L-1}D_{21}^{2L}+B_{2}^{2L-1}\left(D_{22}^{2L+1}-D_{33}^{2L+1}\right)
+	\end{split}
+\end{equation}
+While, for $i,j\in\{1,\ldots,N-1\}$ such that $i\neq j$
+\begin{equation}
+	\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0%\qquad \left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0
+\end{equation}
+{\color{blue}Using them we also have 
+\begin{equation}
+	\begin{split}
+		&Q_{0}^{2L}B_{1}^{2L-1}Q_{0}^{2L}B_{2}^{2L-1}\\=&B_{1}^{2L-1}B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{22}^{2L}+2D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right.\\-&\left.2B_{1}^{2L-1}B_{1}^{2L-1}D_{12}^{2L}-2B_{2}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)\left(Q_{0}^{2L}-2(D_{22}^{2L}+D_{33}^{2L})\right)
+		\\&+
+		\left(-2B_{1}^{2L-1}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right)+8B_{1}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)D_{12}^{2L}
+	\end{split}
+\end{equation}}{\color{blue}Probably it is not useful}
 

### 2023-07-19 main.tex
Clean up II
In blue the parts that could not be need now

@@
 \end{align}
-\begin{comment}
-\begin{itemize}
-	\item for $j\neq N$ 
-\begin{equation}
-	\begin{split}
-	B_{j}(x)D_{jj}(y)=&\frac{(x+y)(1+x-y)}{(x-y)(1+x+y)}D_{jj}(y)B_{j}(x)-\frac{1}{(1+x+y)}\sum_{i=1\,:\,i\neq j}^{N-1}B_{i}(x)D_{i1}(y)
-	\\-&\frac{(x+y)}{(x-y)(1+x+y)}D_{jj}(x)B_{j}(y)-\frac{1}{(1+x+y)}D_{NN}(x)B_{j}(y)
-	\end{split}
-\end{equation}
-\item for $i,j\neq N$
-\begin{equation}
-	\begin{split}
-		B_{i}(x)D_{jj}(y)=D_{jj}(y)B_{j}(x)+\frac{1}{(x-y)}\left(D_{ji}(y)B_{j}(x)-D_{ji}(x)B_{j}(y)\right)
-	\end{split}
-\end{equation}
-\item for $j\neq N$
-\begin{equation}
-	\begin{split}
-		B_{j}(x)D_{NN}(y)&=\frac{(x-y)(1+x+y)}{(x+y)(1+x-y)}D_{NN}(y)B_{j}(x)+\frac{(x-y)}{(x+y)(1+x-y)}\sum_{i=1}^{N-1}B_{i}(y)D_{ij}(x)
-		\\&+
-		\frac{1}{(1+x-y)}B_{j}(y)D_{NN}(x)
-	\end{split}
-\end{equation}
-\end{itemize}
-\end{comment}
-%In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e.
-when the left boundary is lower triangular a end the right one is diagonal.
-We properly rescale them and we obtain
-
-%Then, we obtain the correspondent transfer matrix as
-%\begin{equation}
-%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
-%\end{equation}
-%where
-%\begin{equation}
-%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
-%\end{equation}
-\subsection{Eigenvectors of the non equilibrium Hamiltonian}
-For simplicity we first consider the case with $N=3$.
-We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}.
-We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
-The eigenvectors are the following:
-\begin{equation}
-	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\end{equation}
-
-We replace the above eigenvectors in 
-\begin{equation}
-	T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
-\end{equation}
-and we obtain
-\begin{align*}
-	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\\+&
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\\=&
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-after a change of summation indices we obtain
-\begin{align*}
-	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\\+&
-	\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\\+&
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\\=&
-	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}.
-\end{align*}
-We impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
-\begin{enumerate}
-	\item $k_{2}=0$ and $k_{3}=0$
-	\begin{equation}\label{cond1}
-		T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}
-	\end{equation}
-	\item $k_{2}=m_{2}+1$ and $k_{3}\in \{0,\ldots,m_{3}\}$
-	\begin{equation}\label{cond2}
-		\begin{split}
-			B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
-		\end{split}
-	\end{equation}
-	\item $k_{2}\in\{0,\ldots,m_{2}\}$ and $k_{3}=m_{3}+1$
-	\begin{equation}\label{cond3}
-		\begin{split}
-			B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
-		\end{split}
-	\end{equation}
-	\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}\in\{1,\ldots,m_{3}\}$ 
-	\begin{equation}\label{cond4}
-		\begin{split}
-			&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}\left(B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-			\\=&
-			G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		\end{split}
-	\end{equation} 
-\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
-\begin{equation}\label{cond5}
-	\begin{split}
-		&	\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		=
-	G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation}
-\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}=0$
-	\begin{equation}\label{cond6}
-		\begin{split}
-			&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-			=
-	G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		\end{split}
-	\end{equation}
-
-\end{enumerate}
-To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
-% \end{itemize}
-\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
-
- For the sake of notation we denote by 
-\begin{equation}
-	\begin{split}
-		A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-		A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
-	\end{split}
-\end{equation}
-%{\color{red}Are we missing the prefactor $(N+2x)$?}
-where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
-
-\begin{equation}\label{cond4A}
-	\begin{split}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-	\end{split}
-\end{equation}
-We introduce the following indices
-\begin{equation}
-	i_{1}=\ldots=i_{k_{2}}=2\qquad i_{k_{2}+1}=\ldots =i_{k_{2}+k_{3}}=3
-\end{equation}
-Then, we introduce the permutation 
-\begin{equation}
-	\sigma(i_{j})=i_{k}\qquad \forall j,k=1,\ldots,k_{2}+k_{3}
-\end{equation}
-We write
-\begin{equation}
-	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
-\end{equation}
-where we denoted by $\text{SYM}$ the symmetric group on $\{i_{1},\ldots,i_{k_{2}+k_{3}}\}$.\\
-It solves \eqref{cond4A}, indeed
-\begin{align*}
-	&A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-	\\=&A_{2}\frac{k_{2}}{k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}\frac{k_{3}}{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-	\\=&
-	A_{2}\frac{k_{2}}{k_{2}}\frac{1}{(k_{2}-1)!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\\+&A_{3}\frac{k_{3}}{k_{3}}\frac{1}{k_{2}!(k_{3}-1)!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
-	\\=&
-	\frac{1}{k_{2}!k_{3}!}\left(\sum_{\sigma \in \text{SYM}}k_{2}A_{2}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}+ \sum_{\sigma \in \text{SYM}}k_{3}A_{3}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\right)
-	\\=&
-	\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
-	\\=&
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
-\end{align*}
-where in the up to last equality we used the fact that the quantity first summation is symmetric with respect to the exchange of $A_{2}$ and thus we have $k_{2}$ equal terms.
-Similarly, for the second summation using the symmetry with respect to $A_{3}$.
-\\
-This argument can be generalized for $N>2$ species introducing
-\begin{equation}
-	G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\frac{1}{k_{2}!\cdots k_{N}!}\sum_{\sigma\in \text{SYM}}A_{i_{1}}\cdots A_{i_{k_{2}+\cdots+k_{N}}}
-\end{equation}
-where we assumed 
-\begin{equation}
-	i_{1}=\cdots=i_{k_{2}}=2,\qquad \ldots \qquad i_{k_{2}+\cdots+k_{N-1}}=\cdots=i_{k_{2}+\ldots+k_{N}}=N
-\end{equation}
-\begin{comment}
-To write its solution we define
-\begin{equation}
-	\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
-\end{equation}
-We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
-\begin{equation}
-	\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
-\end{equation}
-We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group.
-\\
-The following expression solves \eqref{cond4A}
-\begin{equation}
-	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
-\end{equation}
-Indeed
-\begin{align}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
-\\&+
- A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
- \\&=
- \sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
- \\&+
- \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
- \\&=
- \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
- \\&=
- 	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
-\end{align}
-where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
-\paragraph{Generalization to arbitrary $N$}
-For arbitrary $N\geq2$ we have 
-\begin{equation}
-	\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}
-\end{equation}
-
-Thus the explicit expression becomes
-\begin{equation}
-G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
-\end{equation}
-with the same notation as in $N=3$ case. 
-\end{comment}
-\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
-\begin{equation}
-	\begin{split}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
-		\\&
-		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
-	\end{split}
-\end{equation}
-We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
-\begin{equation}
-	\begin{split}
-	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-	A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
-	\end{split}
-\end{equation}
-where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
-Therefore we rewrite \eqref{cond4} as 
-\begin{equation}
-	\begin{split}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-	\end{split}
-\end{equation}
-The left-hand-side is 
-\begin{equation}
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\end{equation}
-while, on the right-hand-side we have
-\begin{equation}
-	\begin{split}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&=
-\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-	\end{split}
-\end{equation}
-and similarly 
-\begin{equation}
-	\begin{split}
-		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-		\\&=
-		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
-	\end{split}
-\end{equation}
-Therefore,
-\begin{equation}
-	\begin{split}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&+
-	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-	\\&=
-	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-	\\&=
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
-	\end{split}
-\end{equation}
-Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.
-
-\paragraph{Genearlization to $N$ species:} we can generalize the eigenvector formula for arbitrary number of species $N>2$ by writing
-\begin{equation}
-	\begin{split}
-	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation}
-Denoting by
-\begin{equation}
-A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
-\end{equation}
-the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
-\begin{equation}
-	\begin{split}
-G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
-\\&
-\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=\,k_{q}\}}\right)
-\\&
-\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
-	\end{split}
-\end{equation}
-Condition \eqref{cond4} becomes
-\begin{equation}\label{cond4General}
-	G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
-\end{equation}
-Arguing as in the case $N=3$ we observe that 
-\begin{equation}
-	\begin{split}
-		A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
-	\\&
-	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=k_{q}\}}\right)
-	\\&
-	\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
-	\end{split}
-\end{equation}
-therefore \eqref{cond4General} is fulfilled.
-Again, the equivalent of conditions \eqref{cond1}, e\eqref{cond5} and \eqref{cond6} are trivially satisfied.
-The equivalents of conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{j}(x)$ are rising operators for all $j\in \{2,\ldots,N\}$.
-\begin{comment}
-We show that, if these previous conditions are satisfied, then the $|\Psi^{\Delta}_{m_{2},m_{3}}\rangle$ are indeed eigenvalues of $H^{''}$. 
-\begin{align*}
-T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-\\&+
-\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots +
-\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
-\begin{align*}
-T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-\\&+
-\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots
-\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+
-\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots +
-\Delta_{N}^{m_{N}+1}\sum_{a_{2}=0}^{m_{3}}\ldots\sum_{a_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
-\begin{align*}
-T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-\\&+
-\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots +
-\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-then
-\begin{align*}
-T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
-\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-\\&+
-\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\\&=
-\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle
-\end{align*} 
-\end{comment}
 \subsection{Charges}
@@
 \end{equation}
+Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
 %  It has the property that commute with the equilibrium Hamiltonian.
@@
 
+\subsection{The non local transformation}
+We define the equilibrium Hamiltonian as
+\begin{equation}
+	H^{0}=H_{left}^{0}+H_{bulk}+H^{''}_{right}
+\end{equation}
+where
+\begin{equation}
+		H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
+\end{equation}
+Therefore we have that
+\begin{equation}
+	H^{''}=H^{0}+H^{B}
+\end{equation}
+where
+\begin{equation}
+	H^{B}=\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
+\end{equation}
+We look for a matrix $W$ such that 
+\begin{equation}\label{GoalWH}
+	H^{''}W=WH_{0}
+\end{equation}
+We have that 
+\begin{equation}
+	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
+\end{equation}
+thus it is enough to look for a matrix $W$ such that 
+\begin{equation}\label{GoalWQ}
+	Q^{2L}W=WQ_{2L}^{0}
+\end{equation}
+To find a matrix $W$ such that \eqref{GoalWH} is fulfilled we use the \textit{resolvent operator} defined as
+\begin{equation}
+	R(z,H):=\left(zI-H\right)^{-1}
+\end{equation}
+where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the resolvent is well defined. 
+The above equation implies that 
+\begin{equation}
+	(z-H)R(H,z)=1
+\end{equation}
+In order to be well defined we must $z$ must not be an eigenvalue of $H$ (and thus of $H_{0}$).
+We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
+Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
+We take $z=\Lambda_{\bm{m}}+\epsilon$
+\begin{equation}
+	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)=1
+\end{equation}
+We multiply both sides by $|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|$
+\begin{equation}
+	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+We sum over all possible $m$ 
+\begin{equation}
+	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+We multiply both sides by $\epsilon$ 
+\begin{equation}
+	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+We take the limit for $\epsilon\to 0$ on both sides 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+Observe that 
+\begin{equation}
+	\lim_{\epsilon\to 0}\left(\Lambda_{\bm{m}}+\epsilon-H\right)=\left(\Lambda_{\bm{m}}-H\right)<\infty
+\end{equation}
+and using the following power expansion
+\begin{equation}\label{veryUsefulSeries}
+	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
+\end{equation}
+we have that for each $\bm{m}$ 
+\begin{equation}
+	\begin{split}
+		&\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}H\right)^{n}(\Lambda_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
+		\\=&
+		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\Lambda_{\bm{m}}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-\Lambda_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
+	\end{split}
+\end{equation}
+therefore the limit of the product is the product of the limit and we obtain that 
+\begin{equation}
+	\sum_{m=0}^{L}  (\Lambda_{\bm{m}}-H)\lim_{\epsilon\to 0}\epsilon R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
+\end{equation}
+Since the limit of the sum is the sum of the limit we have   
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+thus 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+Since $H_{0}=H_{0}^{T}$ 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+By calling 
+\begin{equation}\label{W-extended}
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+we finally obtain 
+\begin{equation}
+	WH_{0}=HW
+\end{equation}
+Power expanding the transfer matrix by charges and considering the limit for $x\to\infty$ we have that 
+\begin{equation}
+	\begin{split}
+		W&= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}-\mathcal{Q}_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+		\end{split}
+\end{equation}
+and also satisfies \eqref{GoalWQ}. We now write the power expansion with respect to $B_{i}^{2L-1}$ of $W$. We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},
+\begin{equation}
+	\begin{split}
+	W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+	\\&
+	\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{split}
+\end{equation} 
+we further observe that in the limit for $\epsilon\to 0$ the quantity 
+\begin{equation}
+\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
+\end{equation}
+therefore we have that 
+\begin{equation}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation}
 \begin{comment}
-In case of $N=2$ it differs with respect to the $Q_{2L}^{0}$ computed in formula (2.28) of \cite{frassek2020eigenstates} by the following matrix 
-\begin{equation}
-Q_{2L}^{0,Francesco}-Q_{2L}^{0,Rouven}=	\begin{pmatrix}
-		2&0&0&0\\
-		0&-2&0&0\\
-		0&0&-2&0\\
-		0&0&0&2
-	\end{pmatrix}
-\end{equation}
-\begin{equation}
-\widetilde{H}_{0}:=\widetilde{B}_{1}^{0}+\mathcal{H}+\widetilde{B}_{L}
-\end{equation}
-where 
-\begin{equation}
-\widetilde{B}_{1}^{0}=\begin{pmatrix}
-0&0&\ldots&0\\
-0&-1&\ldots&0\\
-\vdots&\vdots&\ddots&\vdots\\
-0&0&\ldots&-1
-\end{pmatrix}
-\end{equation}
-i.e.
-\begin{equation}
-\left[Q_{2}^{0},\widetilde{H}_{0}\right]=Q_{2}^{0}\widetilde{H}_{0}-\widetilde{H}_{0}Q_{2}^{0}=0
-\end{equation}
-We also introduce 
-\begin{equation}
-Q_{2}^{\Delta}:=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
-\end{equation}
-These two matrices $Q_{2}^{0}$ and $Q_{2}^{\Delta}$ are such that
-\begin{equation}
-Q_{2}=Q_{2}^{0}+Q_{2}^{\Delta}
-\end{equation}
-{\color{blue}Adopt notation here}
+\begin{itemize}
+	\item for $j\neq N$ 
+\begin{equation}
+	\begin{split}
+	B_{j}(x)D_{jj}(y)=&\frac{(x+y)(1+x-y)}{(x-y)(1+x+y)}D_{jj}(y)B_{j}(x)-\frac{1}{(1+x+y)}\sum_{i=1\,:\,i\neq j}^{N-1}B_{i}(x)D_{i1}(y)
+	\\-&\frac{(x+y)}{(x-y)(1+x+y)}D_{jj}(x)B_{j}(y)-\frac{1}{(1+x+y)}D_{NN}(x)B_{j}(y)
+	\end{split}
+\end{equation}
+\item for $i,j\neq N$
+\begin{equation}
+	\begin{split}
+		B_{i}(x)D_{jj}(y)=D_{jj}(y)B_{j}(x)+\frac{1}{(x-y)}\left(D_{ji}(y)B_{j}(x)-D_{ji}(x)B_{j}(y)\right)
+	\end{split}
+\end{equation}
+\item for $j\neq N$
+\begin{equation}
+	\begin{split}
+		B_{j}(x)D_{NN}(y)&=\frac{(x-y)(1+x+y)}{(x+y)(1+x-y)}D_{NN}(y)B_{j}(x)+\frac{(x-y)}{(x+y)(1+x-y)}\sum_{i=1}^{N-1}B_{i}(y)D_{ij}(x)
+		\\&+
+		\frac{1}{(1+x-y)}B_{j}(y)D_{NN}(x)
+	\end{split}
+\end{equation}
+\end{itemize}
 \end{comment}
-\begin{comment}
-\subsection{Eigenvector for the diagonal-triangular chain}
-In \cite{belliard2011nested}  the eigenvectors and eigenvalues hae been computed for the $gl(N)$ spin chain with diagonal boundaries, therfore we know 
-\begin{equation}
-T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle =\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-\end{equation}
-where $m_{2},\ldots,m_{N}$ denote the total occupation along the chain of species $2,\ldots,N$. Let us notice that $m_{1}=L-\sum_{a=2}^{N}\xi_{a}$.\\
-For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$ and we further assume that $\Delta_{2}=\Delta_{3}=\Delta$.
-We make the following ansatz for the eigevectors of the diagonal-triangular spin chain.
-Consider the whole chain of dimension $L$.
-Then, $m=m_{2}+m_{3}$ sites have particles of a type $2$ or $3$ and the remaining $L-m$ are empty.
-For fixed $m$ there is a one to one correspondence between empty and occupeid sites.
-Therefore, our ansatz is that $\forall m\in \{0,\ldots,L\}$
-\begin{equation}\label{ansatzEigenvectorDelta}
-|\Psi_{L-m}^{\Delta}\rangle=\mathbbm{1}_{\{m_{2}+m_{3}=m\}}\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
-\end{equation}
-We fix arbitrary $m,m_{2},m_{3}\in \{0,\ldots,L\}$ such that $m=m_{2}+m_{3}$.  We replace the above eigenvectors in 
-\begin{equation}\label{eigDELTA}
-T_{\Delta}(x)|\Psi_{L-m}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{L-m}^{\Delta}\rangle
+%In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e.
+when the left boundary is lower triangular a end the right one is diagonal.
+We properly rescale them and we obtain
+
+%Then, we obtain the correspondent transfer matrix as
+%\begin{equation}
+%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
+%\end{equation}
+%where
+%\begin{equation}
+%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
+%\end{equation}
+{\color{blue}
+\subsection{Eigenvectors of the non equilibrium Hamiltonian}
+For simplicity we first consider the case with $N=3$.
+We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}.
+We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
+The eigenvectors are the following:
+\begin{equation}
+	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+\end{equation}
+
+We replace the above eigenvectors in 
+\begin{equation}
+	T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
 \end{equation}
@@
 \begin{align*}
-&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\+&
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\=&
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 \end{align*}
-We assume that $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)$, i.e.
-it only depends on the sum of $k_{2}$ and $k_{3}$.
-We make an shift of summation indexes such that
-\begin{equation}
-k_{2}+k_{3}\to k_{2}+k_{3}+1
-\end{equation}
-then we obtain
+after a change of summation indices we obtain
 \begin{align*}
-&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x) |\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\+&
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\mathbbm{1}_{\{k_{2}+k_{3}\neq 0\}}\Delta^{k_{2}+k_{3}}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\+&
-\Delta^{m_{2}+m_{3}+1}\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2}+m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 	\\=&
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta^{k_{2}+k_{3}}\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3}\epsilon}^{k_{2},k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
+	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}.
 \end{align*}
-By equalizing the powers of $\Delta$ we obtain the following condition that must be fulfilled to have that \eqref{ansatzEigenvectorDelta} are indeed the eigenvectors for the triangular-diagonal spin chain:
-\begin{enumerate}
-\item for $k_{2}=k_{3}=0$
-\begin{equation}\label{condition1}
-T_{0}(x)|\Psi_{m_{2},m_{3}}^{0}|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
-\end{equation}
-\item for $k_{2}+k_{3}\neq 0$
-\begin{equation}\label{condition2}
-\begin{split}
-\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}(x)\right]^{-1}&G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}\\&=\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}
-\end{split}
-\end{equation}
-\item finally
-\begin{equation}\label{condition3}
-\left(B_{2}(x)+B_{3}(x)\right)G_{m_{2},m_{3},\epsilon}^{m_{2},m_{3}}(x)|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}=0
-\end{equation}
-\end{enumerate}
-By chosing 
-\begin{equation}\label{G-solution}
-G_{m_{2},m_{3},\epsilon}^{k_{2}+k_{3}}(x)=\left\{\left[\left(\Lambda_{m_{2},m_{3}}(x)+\epsilon\right)I-T_{0}^{x}\right]^{-1}\left(B_{2}(x)+B_{3}(x)\right)\right\}^{k_{2}+k_{3}}
-\end{equation}
-conditions \eqref{condition1} and \eqref{condition2} are easilly satisfied.
-To fulfill condition \eqref{condition3} we observe that, under the condition that $m=m_{2}+m_{3}$ we have that the action of \eqref{G-solution} on $|\Psi_{L-m}^{0}\rangle|_{\epsilon=0}$ leads to a completely occupied state (with both species $2$ and $3$).
-Therefore, applying to it the rising operator$\left(B_{2}(x)+B_{3}(x)\right)$ we obtain zero.
-
-{\color{blue}We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries.
-For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
-\begin{equation}
-|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\end{equation}
-
-We replace the above eigenvectors in 
-\begin{equation}
-T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
-\end{equation}
-and we obtain
-\begin{align*}
-&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\\&
-+\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\\&=
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\end{align*}
-after a change of summation indexes we obtain
-\begin{align*}
-&\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\\+&
-\sum_{a_{2}=1}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\\+&
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{a_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\\=&
-\sum_{a_{2}=0}^{m_{2}}\sum_{a_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\end{align*}
-we impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
+We impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
 \begin{enumerate}
@@
 	\begin{equation}\label{cond1}
-T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle
+		T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}
 	\end{equation}
@@
 		\begin{split}
-B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle=0
+			B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
 		\end{split}
@@
 		\begin{split}
-B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle=0
+			B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
 		\end{split}
@@
 		\begin{split}
-&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+			&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}\left(B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 			\\=&
-\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
+			G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 		\end{split}
@@
 	\begin{split}
-&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+		&	\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 		=
-\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\end{split}
-\end{equation}
-\item $k_{2}\in\{1,\ldots,m_{2}\}$ and $k_{3}=0$
+	G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+	\end{split}
+\end{equation}
+\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}=0$
 	\begin{equation}\label{cond6}
 		\begin{split}
-&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
+			&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
 			=
-\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
-\end{split}
-\end{equation}
+	G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
+		\end{split}
+	\end{equation}
+
 \end{enumerate}
-To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1},\eqref{cond2},\eqref{cond3},\eqref{cond4}, \eqref{cond5},\eqref{cond6}.
-{\color{blue}This second property can be proved by using a lower weight representation }
+To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
 % \end{itemize}
-We prove the ansatz:
+\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
+
+ For the sake of notation we denote by 
+\begin{equation}
+	\begin{split}
+		A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
+		A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+	\end{split}
+\end{equation}
+%{\color{red}Are we missing the prefactor $(N+2x)$?}
+where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
+
+\begin{equation}\label{cond4A}
+	\begin{split}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\end{split}
+\end{equation}
+We introduce the following indices
+\begin{equation}
+	i_{1}=\ldots=i_{k_{2}}=2\qquad i_{k_{2}+1}=\ldots =i_{k_{2}+k_{3}}=3
+\end{equation}
+Then, we introduce the permutation 
+\begin{equation}
+	\sigma(i_{j})=i_{k}\qquad \forall j,k=1,\ldots,k_{2}+k_{3}
+\end{equation}
+We write
+\begin{equation}
+	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
+\end{equation}
+where we denoted by $\text{SYM}$ the symmetric group on $\{i_{1},\ldots,i_{k_{2}+k_{3}}\}$.\\
+It solves \eqref{cond4A}, indeed
 \begin{align*}
-	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+	&A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\\=&A_{2}\frac{k_{2}}{k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}\frac{k_{3}}{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\\=&
+	A_{2}\frac{k_{2}}{k_{2}}\frac{1}{(k_{2}-1)!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\\+&A_{3}\frac{k_{3}}{k_{3}}\frac{1}{k_{2}!(k_{3}-1)!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
+	\\=&
+	\frac{1}{k_{2}!k_{3}!}\left(\sum_{\sigma \in \text{SYM}}k_{2}A_{2}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}+ \sum_{\sigma \in \text{SYM}}k_{3}A_{3}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\right)
+	\\=&
+	\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
+	\\=&
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+\end{align*}
+where in the up to last equality we used the fact that the quantity first summation is symmetric with respect to the exchange of $A_{2}$ and thus we have $k_{2}$ equal terms.
+Similarly, for the second summation using the symmetry with respect to $A_{3}$.
+\\
+This argument can be generalized for $N>2$ species introducing
+\begin{equation}
+	G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\frac{1}{k_{2}!\cdots k_{N}!}\sum_{\sigma\in \text{SYM}}A_{i_{1}}\cdots A_{i_{k_{2}+\cdots+k_{N}}}
+\end{equation}
+where we assumed 
+\begin{equation}
+	i_{1}=\cdots=i_{k_{2}}=2,\qquad \ldots \qquad i_{k_{2}+\cdots+k_{N-1}}=\cdots=i_{k_{2}+\ldots+k_{N}}=N
+\end{equation}
+\begin{comment}
+To write its solution we define
+\begin{equation}
+	\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
+\end{equation}
+We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
+\begin{equation}
+	\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
+\end{equation}
+We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group.
+\\
+The following expression solves \eqref{cond4A}
+\begin{equation}
+	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
+\end{equation}
+Indeed
+\begin{align}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&+
-	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots +
-	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
-\begin{align*}
-	T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
+ A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&=
+ \sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
  \\&+
-	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots
-	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+ \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&=
+ \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
+ \\&=
+ 	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+\end{align}
+where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
+\paragraph{Generalization to arbitrary $N$}
+For arbitrary $N\geq2$ we have 
+\begin{equation}
+	\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}
+\end{equation}
+
+Thus the explicit expression becomes
+\begin{equation}
+G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
+\end{equation}
+with the same notation as in $N=3$ case. 
+\end{comment}
+\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
+\begin{equation}
+	\begin{split}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
+		\\&
+		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
+	\end{split}
+\end{equation}
+We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
+\begin{equation}
+	\begin{split}
+	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
+	A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
+	\end{split}
+\end{equation}
+where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
+Therefore we rewrite \eqref{cond4} as 
+\begin{equation}
+	\begin{split}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
+	\end{split}
+\end{equation}
+The left-hand-side is 
+\begin{equation}
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+\end{equation}
+while, on the right-hand-side we have
+\begin{equation}
+	\begin{split}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+\\&=
+\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\end{split}
+\end{equation}
+and similarly 
+\begin{equation}
+	\begin{split}
+		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+		\\&=
+		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
+	\end{split}
+\end{equation}
+Therefore,
+\begin{equation}
+	\begin{split}
+A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
 \\&+
-	\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots +
-	\Delta_{N}^{m_{N}+1}\sum_{a_{2}=0}^{m_{3}}\ldots\sum_{a_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
-\begin{align*}
-		T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-	\\&+
-	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots +
-	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-then
-\begin{align*}
-T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
-		\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
-	\\&+
-	\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-	\\&=
-	\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle
-\end{align*}
+	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\\&=
+	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
+	\\&=
+		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+	\end{split}
+\end{equation}
+Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.
+
+\paragraph{Genearlization to $N$ species:} we can generalize the eigenvector formula for arbitrary number of species $N>2$ by writing
+\begin{equation}
+	\begin{split}
+	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
+	\end{split}
+\end{equation}
+Denoting by
+\begin{equation}
+A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
+\end{equation}
+the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
+\begin{equation}
+	\begin{split}
+G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
+\\&
+\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=\,k_{q}\}}\right)
+\\&
+\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
+	\end{split}
+\end{equation}
+Condition \eqref{cond4} becomes
+\begin{equation}\label{cond4General}
+	G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
+\end{equation}
+Arguing as in the case $N=3$ we observe that 
+\begin{equation}
+	\begin{split}
+		A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
+	\\&
+	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=k_{q}\}}\right)
+	\\&
+	\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
+	\end{split}
+\end{equation}
+therefore \eqref{cond4General} is fulfilled.
+Again, the equivalent of conditions \eqref{cond1}, e\eqref{cond5} and \eqref{cond6} are trivially satisfied.
+The equivalents of conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{j}(x)$ are rising operators for all $j\in \{2,\ldots,N\}$.
 }
-For $i\neq 1$ we have
-\begin{equation}
-\begin{split}
- \sum_{i,j=2}^N [E_{ij}E_{ji},E_{a1}]&=\sum_{i,j=2}^N E_{ij} [E_{ji},E_{a1}]+\sum_{i,j=2}^N  [E_{ij},E_{a1}]E_{ji}=\sum_{j=2}^N( E_{aj} E_{j1}+ E_{j1} E_{aj})
-\\&=\sum_{j=2}^N( 2E_{aj} E_{j1}+ [E_{j1}, E_{aj}])=2\sum_{j=2}^N E_{aj} E_{j1}-(N-1)E_{a1}
- \end{split}
-\end{equation} 
-\end{comment}
+
 \subsection{Bethe ansatz solution}

### 2023-07-20 main.tex
cleanUpIII
add mapping empty-steady state

@@
 and $|\Psi^{''}\rangle$ solves
-\begin{equation}
+\begin{equation}\label{steadyS-SECOND-def}
 	H^{''}|\Psi^{''}\rangle=0
@@
 Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
-\\&=
-(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
+\end{split}
+\end{equation}
+\begin{equation}
+	\begin{split}
+\boxed{Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}}
 \end{split}
@@
 	\end{split}
+\end{equation}
+Considering the empty state as 
+\begin{equation}
+	|\Psi_{0}^{0}\rangle:=\begin{pmatrix}
+		0\\
+		\vdots\\
+		0\\
+		1
+	\end{pmatrix}\otimes \cdots \otimes\begin{pmatrix}
+	0\\
+	\vdots\\
+	0\\
+	1
+\end{pmatrix}
+\end{equation}
+then, we can map via $W$ the above vector to the steady state $|\Psi^{''}\rangle$ of $H^{''}$ defined in \eqref{steadyS-SECOND-def}, namely
+\begin{equation}
+	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
 \end{equation}

### 2023-07-21 main.tex
fixed

@@
 	\begin{split}
-		D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{i,i}(y)+B_{i}(y)D_{N,N}(x)\right)
-		\\&-
-		\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)+B_{i}(x)D_{N,N}(y)\right)
+		D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
 		\\&+
-		h_{1}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}\left(B_{k}(x)D_{k,i}(y)-B_{k}(y)D_{k,i}(x)\right)
-	\end{split}
-\end{equation}
+		\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
+		\\&+
+	h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
+	\\&+
+	\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
+	\end{split}
+\end{equation}
+
 \end{itemize}

### 2023-08-25 main.tex
Fix 1

@@
 \subsection{Integrable process on a line segment}
-{\color{red}Introduce integrable model here}
+In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
+These boundaries, exchanging particle with the external environment, put the chain out of equilibrium.
+The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
+\begin{equation}
+	\omega_{x,y}=\begin{cases}
+		1 \quad \text{if}\quad |x-y|=1\\
+		0\quad \text{otherwise}
+	\end{cases}
+\end{equation}
+and the local inhomogeneities are
+\begin{equation}
+	\Gamma_{x}=\begin{cases}
+		1\quad \text{if} \quad x\in \{1,L\}\\
+		0\quad \text{otherwise}
+	\end{cases}
+\end{equation}
+We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
+We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e.
+$(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in  the fundamental representation of the algebra.
+The Hamiltonian is
+\begin{equation}\label{hamiltonian}
+	H=H_{left}+H_{bulk}+H_{right}
+\end{equation}
+where
+\begin{equation}
+	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
+\end{equation}
+Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
+\begin{equation}
+	\begin{split}
+		\mathcal{H}=P-\id
+	\end{split}
+\end{equation}
+with 
+\begin{equation}
+	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
+\end{equation} 
+The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.
+\begin{equation}
+	\begin{split}
+		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle
+	\end{split}
+\end{equation}
+The boundary terms are given by 
+\begin{equation}
+	H_{left}=\begin{pmatrix}
+		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
+		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
+		\vdots&\vdots& &\ddots& &\vdots\\
+		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
+		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
+	\end{pmatrix}
+\end{equation}
+\begin{equation}
+	H_{right}=\begin{pmatrix}
+		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
+		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
+		\vdots&\vdots& &\ddots& &\vdots\\
+		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
+		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
+	\end{pmatrix}
+\end{equation}
+where, without loss of generality,  we assume that the parameters satisfy
+\begin{equation}\label{ratesConditions}
+	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
+\end{equation} 
+We define also 
+\begin{equation}\label{lambdaConditions}
+	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
+\end{equation}
+Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
 
@@
 \end{flushright}
-
-\section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
-\subsection{The integrable chain and the matrix product ansatz}
-In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
-These boundaries, exchanging particle with the external environment, put the chain out of equilibrium.
-The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
-\begin{equation}
-    \omega_{x,y}=\begin{cases}
-    1 \quad \text{if}\quad |x-y|=1\\
-    0\quad \text{otherwise}
-    \end{cases}
-\end{equation}
-and the local inhomogeneities are
-\begin{equation}
-    \Gamma_{x}=\begin{cases}
-        1\quad \text{if} \quad x\in \{1,L\}\\
-        0\quad \text{otherwise}
-    \end{cases}
-    \end{equation}
-We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
-We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e.
-$(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in  the fundamental representation of the algebra.
-The Hamiltonian is
-\begin{equation}\label{hamiltonian}
-	H=H_{left}+H_{bulk}+H_{right}
-\end{equation}
-where
-\begin{equation}
-    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
-\end{equation}
-Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
-\begin{equation}
-	\begin{split}
-		\mathcal{H}=P-\id
-	\end{split}
-\end{equation}
-with 
-\begin{equation}
-	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
-\end{equation} 
-The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.
-\begin{equation}
-	\begin{split}
-		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle
-	\end{split}
-\end{equation}
-The boundary terms are given by 
-\begin{equation}
-	H_{left}=\begin{pmatrix}
-		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
-		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
-		\vdots&\vdots& &\ddots& &\vdots\\
-		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
-		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
-	\end{pmatrix}
-\end{equation}
-\begin{equation}
-	H_{right}=\begin{pmatrix}
-		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
-		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
-		\vdots&\vdots& &\ddots& &\vdots\\
-		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
-		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
-	\end{pmatrix}
-\end{equation}
-where, without loss of generality,  we assume that the parameters satisfy
-\begin{equation}\label{ratesConditions}
-	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
-\end{equation} 
-We define also 
-\begin{equation}\label{lambdaConditions}
-	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
-\end{equation}
-Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method). \\
-\paragraph{Duality.} 
+\subsection{Duality for the integrable process on a line segment}
 In this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain. Moreover, the matrix $R_{x}$ defined in \eqref{Revmatrix} 
@@
 \end{equation}
-In the long-time limit, the dual process voids the chain, and all particles are eventually absorbed at the extra-sites $0$ and $L+1$.
-\paragraph{Matrix Product Ansatz (MPA).} The matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
+In the long-time limit, the dual process voids the chain, and all particles are eventually absorbed at the extra-sites $0$ and $L+1$.\\
+In this situation the elements of the duality matrix \eqref{dualityElements} read
+\begin{equation}\label{ElementsDualityMatrixChain}
+	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=2}^{N}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=2}^{N}\beta_{a}^{\xi_{a}^{L+1}}
+\end{equation}
+Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
+Consider a dual configuration $\hat{\xi}:=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ where $a_{k}\in\{2,\ldots,N\}$ and $x_{k}\in\{1,\ldots,L\}$ for every $k\in\{1,\ldots,m\}$.
+Considering the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\hat{\xi}$ we obtain that, for every $\bm{n}$
+\begin{equation}
+	D(\bm{n},\hat{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{a_{k}}^{x_{k}}=1\}}
+\end{equation}
+therefore, its expectation with respect to the steady state non-equilibrium distribution gives the $m$-points correlations.
+Moreover, recalling that the dual process eventually voids the chain by putting all particles in the extra-sites $0$ and $L$ we have the following chain of equalities
+\begin{equation}\label{CorrelationByABS-prob}
+	\begin{split}
+	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{stat}&=\mathbb{E}_{stat}\left[D(\bm{n},\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\hat{\xi}(t))\right]
+	\\&=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{i_{k}}\beta_{a_{k}}^{1-i_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
+\end{split}
+\end{equation}
+where
+\begin{equation}\label{absProbabilitiesIntegrable}
+	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+and they are called \textit{absorption probabilities}.
+
+\section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
+\subsection{The integrable chain and the matrix product ansatz}
+The matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
  Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
@@
 \begin{equation}
-	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}
+	|\Psi\rangle=\frac{1}{Z_{L}}\langle V^{*}|\begin{pmatrix}
 		X_{1}\\
@@
 \begin{equation}
-	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle
+	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle
 \end{equation}
@@
 \begin{equation}\label{leftBoundary}
-	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle W|\qquad\forall a=1,\ldots,N
+	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N
 \end{equation}
@@
 \end{equation}
-Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
+Without loss of generality, we further assume that $\langle V^{*}|V\rangle=1$. 
 \newline \newline
@@
 	\begin{equation}
-		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle W|=0
+		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle V^{*}|=0
 	\end{equation}
@@
 \begin{equation}\label{commLEFT}
-	\langle W|\left(\lambda_{a}\Xt_{1}-\Xt_{a}\right)=\lambda_{a}\langle W|\qquad\forall a=2,\ldots,N
+	\langle V^{*}|\left(\lambda_{a}\Xt_{1}-\Xt_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=2,\ldots,N
 \end{equation}
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 	|V \rangle \,|\bm{n}\rangle
@@
 such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
-To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}
+To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}
 |V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
@@
 \begin{equation}
-	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|V \rangle=\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
 \end{equation}
@@
 \begin{align*}
-	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle&=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
-	\\&=
-	\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
-	\\&=
-	\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle
+	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	|V \rangle&=\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\\&=
+	\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\\&=
+	\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle
 \end{align*}
-To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$.
+To determine the state we need to compute $\langle V^{*}|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$.
 Calling $\sum_{x=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
 \begin{align*}
-	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
-	\\&=
-	\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle W|\widetilde{X}_{1}^{n_{1}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{1}-1)\right)|V\rangle
-	\\&=
-	\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\left(n_{1}+1-1\right)\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
-	\\&=
-	\left(2+n_{1}-1\right)\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
-	\\&=
-	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle V^{*}|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\\&=
+	\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{1}-1)\right)|V\rangle
+	\\&=
+	\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\left(n_{1}+1-1\right)\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\\&=
+	\left(2+n_{1}-1\right)\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\\&=
+	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
 \end{align*}
@@
 	\begin{cases}
-		\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle\\
-		\langle W|\widetilde{X}_{1}^{0}|V\rangle=1
+		\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle\\
+		\langle V^{*}|\widetilde{X}_{1}^{0}|V\rangle=1
 	\end{cases}
@@
 \begin{align*}
-	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\langle W|\widetilde{X}_{1}^{n_{1}-2}|V\rangle\\&=
-	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle W|\widetilde{X}_{1}^{0}|V\rangle
+	\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-2}|V\rangle\\&=
+	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{1}^{0}|V\rangle
 	\\&=
@@
 \begin{equation}
-	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 	|V \rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}
@@
 \begin{align*}
-	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{1}^{L}|V|\rangle=
+	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{L}|V|\rangle=
 	\frac{\Gamma(2+L)}{\Gamma(2)}
@@
 \langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
-\end{equation}
+f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\end{equation}
+By exchanging the summations we rewrite it as 
+\begin{equation}
+\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{t_{1},\ldots,t_{m}=0}^{1}
+\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\end{equation}
+Therefore, comparing this formula and \eqref{absProbabilitiesIntegrable}, we can determine the absorption probabilities 
+\begin{equation}
+	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\end{equation}
+where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{a_{i}}^{x_{i}}$. 
+This means that the $m$-point correlations can also be written in terms of these absorption probabilities. 
 %\begin{equation}
@@
 %\end{equation}
+\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $a_{i}\in\{2,\ldots,N\}$ in positions $x_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$.
+We aim to compute the non-equilibrium stationary state correlation $\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}$.
+By using duality, we showed in \eqref{CorrelationByABS-prob} that
+ \begin{equation}
+ 	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
+ \end{equation} 
+Using formula \eqref{ABS} for a configuration where all $\tau_{i}$ are non-empty species, we obtain that 
+\begin{equation}
+	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ and using $\tau_{i}=a_{i}$ $\forall i=1,\ldots,m$, we have the formulas for arbitrary correlations.
+{\color{blue}
  \paragraph{Proof of formula \eqref{exactCorrelations}}
@@
     $\square$
-\end{flushright}
+\end{flushright}}
+
 \subsubsection{Explicit examples of steady state correlations}

### 2023-08-25 main.tex
Fix 2

@@
 	\end{equation} 
-	\com{Double check this. Sum looks strange}
-and where
- \begin{equation}\label{CiEquation}
-	c_{y}=\begin{cases}
-		1\quad \text{if}\quad \tau_{y}\neq 1\\
-		0\quad \text{if}\quad \tau_{y}=1
-	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
-\end{equation}
+	%\com{Double check this. Sum looks strange}
+%and where
+% \begin{equation}\label{CiEquation}
+%	c_{y}=\begin{cases}
+%		1\quad \text{if}\quad \tau_{y}\neq 1\\
+%		0\quad \text{if}\quad \tau_{y}=1
+%	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
+%\end{equation}
 \paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 \end{flushright}
-\subsubsection{The steady state of $H$}\label{subsectionSSH}
-The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
-\begin{equation}\label{steadyStateH}
-    |\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
-\end{equation}
-where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
-\begin{equation}
-	\begin{split}
- \Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
-\\&+
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},1}\right) 
-\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
-\\&
-\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
-	\end{split}
-\end{equation}
-where we have introduced, $\forall x\in \{1,\ldots,L\}$
-\begin{equation}
-	\eta_{x}(b)=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-		d_{x}\qquad &\text{otherwise}
-	\end{cases}%\qquad \theta_{x}=\begin{cases}
-		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-	%	1 \qquad &\text{otherwise}
-	%\end{cases}
-\end{equation}
-The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
-{\color{blue}
-\begin{equation}\label{steadyStateH-coeff}
-    \begin{split}
-        \Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
-        \\&+
-        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},1}\right) 
-        \sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
-\\&
-\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
-  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
- \\ &
- \beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
- \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-    \end{split}
-\end{equation}
-}
-\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $\tau_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
-\begin{equation}\label{LinkABS-corr}
-\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
-\end{equation}
-When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
-
-\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
-Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
-This matrix $\mathcal{S}_{1}$ is given by
-\begin{equation}\label{S1-L1}
-	\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
-\end{equation}
-Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
-\begin{equation}
-	\begin{split}
-		\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-		\\&
-		+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
-	\end{split}
-\end{equation}
-where we have introduced, $\forall x\in \{1,\ldots,L\}$
-\begin{equation}
-	%\eta_{x}=\begin{cases}
-	%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-	%	d_{x}\qquad &\text{otherwise}
-	%\end{cases}\qquad
-	 \theta_{x}(b)=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-		1 \qquad &\text{otherwise}
-\end{cases}
-\end{equation}
-The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
-  %$e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-\\
-This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
-\begin{align*}
-\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
-\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-\\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
-\\&\otimes
-\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
-\\&=
-	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
-\\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
-\end{align*}
-\begin{comment}
-
-\begin{equation}
-    F=\left(V^{-1}\right)^{T}
-\end{equation}
-and thus 
-\begin{equation}
-    \mathcal{F}=F^{\otimes L}
-\end{equation}
-By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
-\begin{equation}
-    F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
-\end{equation}
-Taking the tensor product over two sites we obtain 
-\begin{equation}
-\begin{split}
-    F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-     \right.\\ &+\left. 
-    (-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
-    \end{split}
-\end{equation}
-therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
-\begin{equation}
-\begin{split}
-    \left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-    \\&+
-    (-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
-    \\&=
-    \sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-    +
-    (-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-    \end{split}
-\end{equation}
-where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
-\\
-We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
-We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
-\begin{equation}
-    \begin{split}
-        \mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
-        \\&
-        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
-    \end{split}
-\end{equation}
-where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-\\
-\end{comment}
-The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
-To find this elements we need to fix the rows correspondent to $\bm{\tau}$.
-Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
-\begin{equation}
-    \begin{split}
-       \Psi(\bm{\tau}) &=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{\tau}}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
-        \\&
-        +\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\eta_{1},\ldots,\eta_{L})
-    \end{split}
-\end{equation}
-%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-Using \eqref{elementsABS} we have 
-\begin{equation}
-  \begin{split}
-	\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
-	\\&
-	\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
-\end{split}
-\end{equation}
-{\color{blue}
-\begin{equation}
-    \begin{split}
-  &\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
-\\&  
-\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
-\\&
-  \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-    \end{split}
-\end{equation}} indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
-Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}.
-\begin{flushright}
-    $\square$
-\end{flushright}
+
 \subsection{Exact steady state correlations}\label{correlation-section}
@@
 Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ and using $\tau_{i}=a_{i}$ $\forall i=1,\ldots,m$, we have the formulas for arbitrary correlations.
+\begin{comment}
 {\color{blue}
@@
 \end{flushright}}
-
+\end{comment}
 \subsubsection{Explicit examples of steady state correlations}
@@
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
-
-\section{Non-integrable chain}
-In Section \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
-This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations.
-Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
-\subsection{Steady state correlations and duality}
-We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads as
-\begin{equation}
-	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}
-\end{equation} 
-where at the boundaries 
-\begin{equation}
-	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{delta}_{a}^{x})-f(\bm{n})\right)
-\end{equation}
-while the bulk generator is 
-\begin{equation}
- \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space
- \begin{equation}	
-	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}
-\end{equation}
-The dual generator is 
-\begin{equation}
-	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
-\end{equation} 
-with absorbing boundaries, i.e. 
-\begin{equation}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
-	\end{split}
-\end{equation}
-where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
-\begin{equation}\label{dualityFunctionChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
-\begin{equation}\label{ExptationSS}
-	\begin{split}
-		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
-		\\=&
-		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
-	\end{split}
-\end{equation}
-where 
-\begin{equation}\label{Pass}
-	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
-\end{equation}
-where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
-\begin{equation}
-	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{2,\ldots,N\}$ situated at sites $y_{i}\in\{1,\ldots,L\}$ with $i\in \{1,\ldots,m\}$.
-This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
-The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the one points correlations.
-\paragraph{One point correlations for the non-integrable case}
-We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
-\end{equation}
-Thus
-\begin{equation}\label{OnePtsCORR}
-	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
-	\end{split}
-\end{equation}
-we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
-Therefore, this $a_{s}^{x}(1)$ fulfils the following equations
-\begin{equation}\label{gamblers-ruin}
-	\begin{cases}
-		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
-		a^{1}_{s}(1)=\frac{|\alpha|}{1+|\alpha|}+a^{2}_{s}(1)\frac{1}{1+|\alpha|}\\
-		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+|\beta|}
-	\end{cases}
-\end{equation}
-where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where.
-The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}
-\end{equation}
-\textbf{Remark}: In case $|\alpha|=|\beta|=1$ we have 
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-\end{equation}
-that gives back \eqref{one-pts-corr}.
-\subsection{Instantaneous thermalization}
-In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}).
-The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles.
-The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\bm{\epsilon}=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\bm{\epsilon}$.
-\subsubsection{The thermalization measure}
-As already mentioned, we will redistribute particles on a bond according to a probability measure that is the reversible one \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond.
-We denote
-\begin{equation}
-	\begin{split}
-	\nu_{TH}(\bm{r}|\bm{\epsilon}):&=\mathbb{P}\left(n^{x}=\bm{r}|\eta^{x}+n^{x+1}=\bm{\epsilon}\right)
-	\\&
-	=\mathbb{P}\left((n_{1}^{x},\ldots,n_{N}^{x})=
-	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)
-	\end{split}
-\end{equation}
-where
-\begin{equation}
-	\epsilon_{1}=2\nu-\sum_{a=2}^{N}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=2}^{N}r_{a}
-\end{equation}
-We construct this measure.
-Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
-\begin{equation}
-	\begin{split}
-\nu_{TH}(\bm{r}|\bm{\epsilon})&=\frac{\mathbb{P}\left(\left\{n^{x}=\bm{r}\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\bm{\epsilon}\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}=\frac{\mathbb{P}\left(n^{x}=\bm{r}\right)\,\mathbb{P}\left(n^{x+1}=\bm{\epsilon}-\bm{r}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}
-	\end{split}
-\end{equation}
-Moreover, it holds that 
-\begin{equation}
-\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
-\end{equation}
-Therefore 
-\begin{equation}
-	\begin{split}
-	\nu_{TH}(\bm{r}|\bm{\epsilon})=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
-	\end{split}
-\end{equation}
-where we denote the multinomial coefficient
-\begin{equation}
-	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}
-\end{equation}
-provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
-\subsubsection{Thermalized multi-species stirring process}
-The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace} and its generator reads
-\begin{equation}\label{thermalizedGenerator}
-	\mathcal{L}^{TH}=\mathcal{L}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{right}^{TH}
-\end{equation}
-where 
-\begin{equation}\label{bulkThermalized}
-	\begin{split}
-	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}
-	\\&
-	\left\{f(n^{1},\ldots,n^{x-1},\bm{r},n^{x}+n^{x+1}-\bm{r},n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
-	\end{split}
-\end{equation}
-while
-\begin{equation}\label{boundaryThermalized}
-	\begin{split}
-		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
-		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
-		\end{split}
-	\end{equation}
-The right boundary generator is defined in a similar way. The $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
-\subsubsection{The dual thermalized process}
-The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
-\begin{equation}
-		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{right}^{TH}
-\end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 
-\begin{equation}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{left}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
-	\end{split}
-\end{equation}
-and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$. 
-The duality function is 
-\begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-The proof of the duality consists in proving 
-\begin{align}
-	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
-	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
-\end{align}
-Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
-To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function.
-For the sake of notation, we introduce
-\begin{equation}
-	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
-\end{equation}
-First, we act with $\mathcal{L}_{left}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
-\begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
-	\\&\nonumber
-	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
-	\\&
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
-\end{align}
-Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
-\begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
-	\\&\nonumber
-	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\\=&
-	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
-\end{align}
-Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
-\begin{equation}\label{pezzo2}
-	\begin{split}
-	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
-	\end{split}
-\end{equation}
-Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
-\begin{align}
-	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
-	\\&=
-	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
-\end{align}
-\section{Multi-species stirring process with reaction}
-In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{2,3\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
-\begin{equation}\label{2SpeciesRD}
-	\partial \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)
-\end{equation} 
-for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$  and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.
-This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
-For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
-In view of what have been proved in the previous section of this work, some questions arise naturally:
-\begin{enumerate}
-		\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-			\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
-	\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process?
-\end{enumerate}
-The aim of this section is to give an answer to these questions.
-We first define a more general process with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with N discrete Laplacians and a reaction term.
-Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
-\subsection{The process on a finite graph}
-Considering again a finite and connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
-\begin{equation}\label{RDGenerator}
-	\mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}
-\end{equation}
-where
-\begin{equation}\label{edgeGeneratorRD}
-	\mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
-\end{equation}
-with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
-\begin{equation}
-	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right)
-\end{equation}
-with the mapping 
-\begin{equation}
-	\begin{split}
-		g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
-		k&\to g_{c}(k)
-	\end{split}
-\end{equation}
-defined $\forall c\in\{1,\ldots,N-2\}$ as 
-\begin{equation}
-	g_{c}(k)=\begin{cases}
-		k+c \quad &\text{if}\quad k+c\leq N\\
-		k+c-N+1\quad &\text{if}\quad k+c>N\\
-		1\quad &\text{if}\quad k=1
-	\end{cases}
-\end{equation}
-Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
-Moreover,
-\begin{equation}
-	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
-\end{equation}
-The site generator reads
-\begin{equation}
-	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
-\end{equation}
-where the boundary parameters are defined as
-\begin{equation}\label{boundaryParamRD}
-	\begin{split}
-		\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
-		\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
-	\end{split}
-\end{equation}
-and where, for every $x\in V$, we further assume that
-\begin{equation}
-	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
-\end{equation}
-\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
-We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
-\paragraph{Action on the occupation variable of $\mathcal{L}_{x,y}^{rd}$}
-For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
-\begin{equation}\label{actionGraphRD}
-	\begin{split}
-		\mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
-	\end{split}
-\end{equation}
-
-Indeed
-\begin{equation}
-	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
-\end{equation}
-while for every $c\in \{1,\ldots,N-2\}$ we have 
-\begin{equation}
-	\begin{split}
-		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
-		\\&=
-		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
-		\\&=
-		\nu(n_{q}^{y}-n_{d}^{x})
-	\end{split}
-\end{equation}
-where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq 1$ .
-Moreover
-\begin{equation}
-	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
-\end{equation}
-Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action on the occupation variable of $\mathcal{L}_{x}^{rd}$}
-Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
-\begin{equation}\label{actionBoudaryRD}
-	\begin{split}
-		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
-		\\&=
-		\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
-		\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
-		\\=&
-		\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
-	\end{split}
-\end{equation}
-\subsection{The process on a chain}
-Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$.
-This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
-Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
-\begin{equation}\label{DifferenceEquation}
-	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
-\end{equation}
-where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
-Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
-\begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
-\end{equation}
-On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
-\begin{equation}
-	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
-\end{equation}
-where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
-These average occupations evolve according to the Master equation
-\begin{equation}
-	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
-\end{equation} 
-Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
-For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question of the beginning of this section.
-\subsection{Reversible measure} 
-The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
-	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
-\end{equation}
-when for any $a\in\{1,\ldots,N\}$
-\begin{equation}\label{reversibilityConditionRD}
-	\alpha_{a}^{x}=\alpha_{a}\quad \forall x\in V\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{2,\ldots,N\}
-\end{equation}
-This measure has marginals $\Lambda_{rev}^{x}$ given by 
-\begin{equation}
-	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)
-\end{equation}
-where 
-\begin{equation}
-	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{2,\ldots,N\}\qquad \text{and}\qquad \rho_{1}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}
-\end{equation}
-Namely,
-\begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho_{1}^{n_{1}^{x}}\rho^{\sum_{a=2}^{N}n_{a}^{x}}
-\end{equation}
-This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
-For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
-\begin{equation}
-	\begin{split}
-		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
-		\\
-		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
-		\\&
-		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
-	\end{split}
-\end{equation}
-that simplifies to 
-\begin{equation}
-	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
-\end{equation}
-that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{2,\ldots,N\}$.\\
-By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,y}$.
-\\
-For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$.
-As a consequence we have the result.
-\subsection{Duality}
-In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
-\begin{equation}
-	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
-\end{equation}
-To each site $x\in V$ we associate an ``extra site'', denoted $u(x)$,
-where dual particles will accumulate in the course of time. 
-We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
-\begin{equation}
-	\bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
-\end{equation}
-where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
-the extra-site $u(x)$ connected to $x\in V$.
-
-The duality function is given by
-\begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
-\end{equation}
-%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
-%\begin{equation}
-%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}
-%\end{equation}
-The dual process is defined by its generator, which reads
-\begin{equation}\label{DualGeneratorRD}
-	\widetilde{\mathcal{L}}^{rd}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
-\end{equation}
-where 
-$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}.
-\newline
-\newline
-\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process.
-The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
-As we will show this follows from a $gl(N)$ algebraic structure.
-\subsubsection{Proof of duality}
-In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
-\begin{equation}
-	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}\mathcal{H}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
-\end{equation}
-where $\mathcal{H}_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
-\begin{equation}
-	\mathcal{H}_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
-\end{equation}
-and 
-\begin{equation}
-	\mathcal{H}_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
-\end{equation}
-Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$.
-For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
-\begin{equation}\label{DualityRelationRD}
-	(H^{rd})^{T}D=D\widetilde{H}^{rd}
-\end{equation}
-Therefore, we need to prove that
-\begin{align}
-	(\mathcal{H}_{x,y}^{rd})^{T}D&=D\mathcal{H}_{x,y}^{rd}\label{edgeDualityRelationRD}\\
-	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
-\end{align}
-where the duality matrix $D$ is again \eqref{dualityMatrix}.
-As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $\mathcal{H}_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$.
-Therefore, we only need to show that
-\begin{align}
-	&(\mathcal{H}_{x,y}^{c})^{T}D=D\mathcal{H}_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
-	&(\mathcal{H}_{x,y}^{m})^{T}D=D\mathcal{H}_{x,y}^{m}\label{mDualityRelation}
-\end{align}
-Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$ have $\exp{(E^{x})}\exp{(E^{y})}$ as a symmetry.
-The first result will follow from the commutator between $\mathcal{H}_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
-Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
-\begin{align*}
-	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]
-	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right.
-\\ \otimes&\left.
-\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
-	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
-	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
-	\\=&0
-\end{align*}
-where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
-The second result will follow from the commutator between $\mathcal{H}_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
-\begin{equation}
-	\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
-\end{equation}
-\begin{flushright}
-	$\square$
-\end{flushright}
-With this prove we answered the second and third questions stated at the beginning of this section. \\
-\textbf{FROM HERE ON-WARDS STILL TO CHECK}\\
-\begin{comment}
-\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}
-In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{a})_{a=1,\ldots,N}$ and $(\beta_{a})_{a=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
-When the maximal occupation of each site $\nu>1$, this nice property is lost.
-However, something about correlations can be said using duality.
-In this subsection we still consider the same geometry of \ref{subsection-exact}.
-As pointed out in section~\ref{sectionDuality}, the dual process voids the chain.
-Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.
-In this context it is better to work agin with generators.
-We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry.
-\\
-We consider the process $(\bm{n}(t))_{t\geq 0}$ on a chain of length $L$ with the end sites connected with two reservoirs.
-This interaction with the external environment is described by the generators
-\begin{equation}
-    \mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
-\end{equation}
-The bulk generator is 
-\begin{equation}
-    \mathcal{L}_{\text{bula}}=\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}\quad \text{where}\quad \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space $\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}$ with the same $\mathcal{L}_{\text{bula}}$ and with absorbing boundaries, i.e.
-\begin{equation}
-\begin{split}
-        \widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
-        \end{split}
-\end{equation}
-where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
-\begin{equation}\label{dualityFunctionChain}
-    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(ò\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
-\begin{equation}\label{ExptationSS}
-\begin{split}
-\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
-\\=&
-\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
-\end{split}
-\end{equation}
-where 
-\begin{equation}\label{Pass}
-    a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
-\end{equation}
-where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
-\begin{equation}
-    D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species.
-This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
-The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the one points correlations.
-\paragraph{One point correlations for the non-integrable case}
-We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
-\end{equation}
-Thus
-\begin{equation}\label{OnePtsCORR}
-\begin{split}
-	\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
- \end{split}
-\end{equation}
-we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
-This $a_{s}^{x}(1)$ fulfils the following equations
-\begin{equation}\label{gamblers-ruin}
-	\begin{cases}
-		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
-		a^{1}_{s}(1)=\frac{A}{1+A}+a^{2}_{s}(1)\frac{1}{1+A}\\
-		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+B}
-		\end{cases}
-\end{equation}
-where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where, for the sake of notation, we call $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$.
-The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
-\begin{equation}
-\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
-\end{equation}
-\textbf{Remark}: In case $A=B=1$ we have 
-	\begin{equation}
-\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-	\end{equation}
-that gives back \eqref{one-pts-corr}.  
-\end{comment}
-\section{Mapping to equilibrium?}
+\section{Mapping to equilibrium}
 check also Appendix A in
 \cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz} 
-
+\subsection{The non local transformation}\label{SectionNonLocalTrasformation}
+We define the equilibrium Hamiltonian as
+\begin{equation}
+	H^{0}=H_{left}^{0}+H_{bulk}+H^{''}_{right}
+\end{equation}
+where
+\begin{equation}
+	H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
+\end{equation}
+Therefore we have that
+\begin{equation}
+	H^{''}=H^{0}+H^{B}
+\end{equation}
+where
+\begin{equation}
+	H^{B}=\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
+\end{equation}
+We look for a matrix $W$ such that 
+\begin{equation}\label{GoalWH}
+	H^{''}W=WH_{0}
+\end{equation}
+This matrix is 
+\begin{equation}\label{W-extended}
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+%We have that 
+%\begin{equation}
+%	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
+%\end{equation}
+%thus it is enough to look for a matrix $W$ such that 
+%\begin{equation}\label{GoalWQ}
+%	Q^{2L}W=WQ_{2L}^{0}
+%\end{equation}
+To find a matrix $W$ such that \eqref{GoalWH} is fulfilled we use the \textit{resolvent operator} defined as
+\begin{equation}
+	R(z,H):=\left(zI-H\right)^{-1}
+\end{equation}
+where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the resolvent is well defined. 
+The above equation implies that 
+\begin{equation}
+	(z-H)R(H,z)=1
+\end{equation}
+In order to be well defined we must $z$ must not be an eigenvalue of $H$ (and thus of $H_{0}$).
+We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
+Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
+We take $z=\Lambda_{\bm{m}}+\epsilon$
+\begin{equation}
+	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)=1
+\end{equation}
+We multiply both sides by $|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|$
+\begin{equation}
+	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+We sum over all possible $m$ 
+\begin{equation}
+	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+We multiply both sides by $\epsilon$ 
+\begin{equation}
+	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+We take the limit for $\epsilon\to 0$ on both sides 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+Observe that 
+\begin{equation}
+	\lim_{\epsilon\to 0}\left(\Lambda_{\bm{m}}+\epsilon-H\right)=\left(\Lambda_{\bm{m}}-H\right)<\infty
+\end{equation}
+and using the following power expansion
+\begin{equation}\label{veryUsefulSeries}
+	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
+\end{equation}
+we have that for each $\bm{m}$ 
+\begin{equation}
+	\begin{split}
+		&\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}H\right)^{n}(\Lambda_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
+		\\=&
+		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\Lambda_{\bm{m}}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-\Lambda_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
+	\end{split}
+\end{equation}
+therefore the limit of the product is the product of the limit and we obtain that 
+\begin{equation}
+	\sum_{m=0}^{L}  (\Lambda_{\bm{m}}-H)\lim_{\epsilon\to 0}\epsilon R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
+\end{equation}
+Since the limit of the sum is the sum of the limit we have   
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+thus 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+Since $H_{0}=H_{0}^{T}$ 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+By calling 
+\begin{equation}\label{W-extended}
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+we finally obtain 
+\begin{equation}
+	WH_{0}=HW
+\end{equation}
+Formula \eqref{W-extended} comes from standard perturbation theory.
+However, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system.
+This expression, as it will be show in the following sections, allows to find explicit expression of the eigenvector by the Bethe ansatz and also allows to retrieve again the steady state of $H^{''}$ by applying $W$ to the ground state.
+To find it, we use the Quantum Inverse Scattering Method (QISM).
+We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$.
 \subsection{Quantum inverse scattering method}
@@
 In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
-We introduce the following matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
+We introduce the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
 \begin{equation}\label{Rmatrix}
@@
 \end{equation}
+and the $K$-matrices
 \begin{comment}
@@
 \end{itemize}
-We define the following \textit{transfer matrix}
+We define the \textit{transfer matrix}
 \begin{equation}
@@
 \end{equation}
-where we used the double row monodromy
+where we used the double row monodromy defined as
 \begin{equation}
@@
 			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
-			B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
+			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
 		\end{pmatrix}\right)
@@
 \begin{equation}
-	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}
-\end{equation}
-The coefficients that we need are the following:
-\begin{equation}
-	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
-\end{equation}
+	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
+\end{equation}
+In the following it will be clear that only the first three coefficients of the diagonal elements and only the first coefficient of the non diagonal element are needed. 
+\begin{itemize}
+	\item For the element $D_{N,N}(x)$: 
+%The coefficients that we need are the following:
+%\begin{equation}
+%	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
+%\end{equation}
 where 
@@
 \begin{equation}
-	\begin{split}
-		D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
-	\end{split}
-\end{equation}
+	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
+\end{equation}
+%\begin{equation}
+%	\begin{split}
+	%	D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
+%	\end{split}
+%\end{equation}
+\begin{comment}
 {\color{blue}ok}
@@
 Then
-\begin{equation}
-	\boxed{D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L}
-\end{equation}
+
 {\color{blue}ok?}where we used $
 \sum_{i=1}^Ne_{ii}^{tot}=L$. 
-
-While, $\forall i=1,\ldots,N-1$
-
-\begin{equation}
-	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
-\end{equation}
-where the coefficients
+\end{comment}
+\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$ 
+%\begin{equation}
+%	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
+%\end{equation}
+%where the coefficients
 \begin{equation}\label{a2lp}
@@
 \end{equation}
-\begin{equation}\label{a2lm1}
-	\begin{split}
-		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
-		&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
-		%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
+\begin{equation}
+	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
+\end{equation}
+%\begin{equation}\label{a2lm1}
+%	\begin{split}
+	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
+	%	&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
+	%	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
 		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
-		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
-	\end{split}
-\end{equation}
-
-We rewrite
-\begin{equation}
-	\begin{split}
-		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
-	\end{split}
-\end{equation}
-then
-\begin{equation}
-	\begin{split}
-		D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
-	\end{split}
-\end{equation}
-Then 
-\begin{equation}
-	\boxed{D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
-\end{equation}
-{\color{blue}ok}
+%		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
+%	\end{split}
+%\end{equation}
+
+%We rewrite
+%\begin{equation}
+%	\begin{split}
+	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N%-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
+%	\end{split}
+%\end{equation}
+%then
+%\begin{equation}
+%	\begin{split}
+%		D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
+%	\end{split}
+%\end{equation}
+
 %blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
@@
 %\end{equation}
-Moreover, $\forall j=2,\ldots,L$ and for $i=1$
+\item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
+\begin{equation}
+		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
+\end{equation}
+\begin{comment}
 \begin{equation}
@@
 \end{equation}
-Finally, for every $i,j=2,\ldots,N$ such that $i\neq j$, we have that 
-\begin{equation}
-\boxed{D_{i,j}^{2L}=-2e_{ji}^{tot}}
-\end{equation}
+\end{comment}
+\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
+\begin{equation}
+D_{i,j}^{2L}=-2e_{ji}^{tot}
+\end{equation}
+\end{itemize}
 \textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
@@
 that is 
-\begin{equation}
-\begin{split}
-Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
-\end{split}
-\end{equation}
-\begin{equation}
-	\begin{split}
-\boxed{Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}}
+%\begin{equation}
+%\begin{split}
+%Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
+%\end{split}
+%\end{equation}
+\begin{equation}\label{Q0Exp}
+\begin{split}
+Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
 \end{split}
@@
 %\end{equation} 
-we also introduce 
+We also introduce 
 \begin{equation}
@@
 
-All terms are diagonal except the last one which can  be  identified with the second Casimir of the $gl(N-1)$ subalgebra
+Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}.
+All terms are diagonal except the last one.
+However, this last non-diagonal term acts diagonally on the states.
+Indeed, can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
+We denote it by $\hat{C}_{2}$ and it reads
 \begin{equation}
@@
 \end{equation} 
-On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues given in terms of shifted weights 
+We denote its eigenvector by $C_{2}^{N-1}$.
+On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
 \begin{equation}
@@
 \end{equation} 
-{\color{blue}to be checked...} {\color{blue} It works!!}, see e.g. [Das,Okubo].
+ where 
+ \begin{equation}
+ 	\ell_{j}=\mu_{j}+N-j
+ \end{equation}
+with $\mu_{j}$ the representation labels of tensor product over the chain of the fundamental representation of $gl(N)$ (it can be decomposed by branching rule).  
 Thus the eigenvalues of the transfer matrix can be writen as 
@@
 \end{equation} 
-
 Thus the difference is of order $2L$ and becomes
@@
 \end{equation} 
-We can take the limit
+By taking the limit we obtain
 \begin{equation}
@@
 \end{equation} 
-{\color{blue}ok}
-\subsubsection{Exchange relations between charges}
+\paragraph{Exchange relations between charges}
 Using \eqref{EX1}, \eqref{EX2} and \eqref{EX3} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
-\begin{equation}
+\begin{equation}\label{ExQ0B-charges}
 Q_{0}^{2L}B_{i}^{2L-1}=B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{j=1\,:\,j\neq i}^{N-1}B_{j}^{2L-1}D_{j,i}^{2L}
@@
 Other useful exchange relations are 
-\begin{equation}
+\begin{equation}\label{ExDNB-charges}
 \begin{split}
@@
 and
-\begin{equation}
+\begin{equation}\label{ExDiB-charges}
 \begin{split}
@@
 and finally
-\begin{equation}
+\begin{equation}\label{ExDijB-charges}
 \begin{split}
@@
 \end{equation}}{\color{blue}Probably it is not useful}
-
-\subsection{The non local transformation}
-We define the equilibrium Hamiltonian as
-\begin{equation}
-	H^{0}=H_{left}^{0}+H_{bulk}+H^{''}_{right}
-\end{equation}
-where
-\begin{equation}
-		H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
-\end{equation}
-Therefore we have that
-\begin{equation}
-	H^{''}=H^{0}+H^{B}
-\end{equation}
-where
-\begin{equation}
-	H^{B}=\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
-\end{equation}
-We look for a matrix $W$ such that 
-\begin{equation}\label{GoalWH}
-	H^{''}W=WH_{0}
-\end{equation}
-We have that 
-\begin{equation}
-	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
-\end{equation}
-thus it is enough to look for a matrix $W$ such that 
-\begin{equation}\label{GoalWQ}
-	Q^{2L}W=WQ_{2L}^{0}
-\end{equation}
-To find a matrix $W$ such that \eqref{GoalWH} is fulfilled we use the \textit{resolvent operator} defined as
-\begin{equation}
-	R(z,H):=\left(zI-H\right)^{-1}
-\end{equation}
-where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the resolvent is well defined. 
-The above equation implies that 
-\begin{equation}
-	(z-H)R(H,z)=1
-\end{equation}
-In order to be well defined we must $z$ must not be an eigenvalue of $H$ (and thus of $H_{0}$).
-We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
-Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
-We take $z=\Lambda_{\bm{m}}+\epsilon$
-\begin{equation}
-	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)=1
-\end{equation}
-We multiply both sides by $|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|$
-\begin{equation}
-	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We sum over all possible $m$ 
-\begin{equation}
-	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We multiply both sides by $\epsilon$ 
-\begin{equation}
-	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We take the limit for $\epsilon\to 0$ on both sides 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-Observe that 
-\begin{equation}
-	\lim_{\epsilon\to 0}\left(\Lambda_{\bm{m}}+\epsilon-H\right)=\left(\Lambda_{\bm{m}}-H\right)<\infty
-\end{equation}
-and using the following power expansion
+\section{Conserved charges form of W}
+By using the QISM results found in the previous section it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system.
+This is possible because , thanks to integrability
+\begin{equation}
+	[H,T(x)]=0
+\end{equation}
+and moreover $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$ with the property that, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can look for a matrix $W$ such that 
+\begin{equation}
+	Q^{2L}W=WQ_{0}^{2L}
+\end{equation}
+Arguing as in section \ref{SectionNonLocalTrasformation}, we can show that 
+\begin{equation}\label{WInCharges}
+	\begin{split}
+	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+\end{split}
+\end{equation}
+Since $Q^{2L}$ and $H$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones.
+The advantage is that now we can do more with this more with this expression.
+Hopefully, using exchange relation between charges, we could try to handle \eqref{WInCharges} and rewrite it independently from the equilibrium eigenvectors.
+Moreover, we can use it to extract the steady state by rising the vacum state.
+\subsection{The gl(2) case}
+In this simpler situation the double row monodromy reads
+\begin{equation}
+	U_{0}=\begin{pmatrix}
+		D_{1,1}(x)&C_{1}(x)\\
+		B_{1}(x)&D_{2,2}(x)
+	\end{pmatrix}
+\end{equation}
+Therefore, using the conserved charges and formula \eqref{WInCharges} we have
+\begin{equation}\label{W}
+	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|
+\end{equation}
+Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and making it act on 
+\begin{equation}\label{LinkWG}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\
+		=&\lim_{\epsilon\to 0}\sum_{m=0}^{L}\epsilon\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+		\\=&
+		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+	\end{split}
+\end{equation}
+where in the last equality we used 
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}
+\end{equation}
+Expression \eqref{LinkWG} can be rewritten using the adaptation to $gl(2)$ of the exchange relation between charges written in \eqref{ExQ0B-charges},\eqref{ExDNB-charges} and \eqref{ExDiB-charges}.
+These relation now read
+\begin{equation}\label{exchangeQ0B}
+	Q_{0}^{2L}B_{1}^{2L-1}=B_{1}^{2L-1}\left(Q_{0}^{2L}-2\left(D_{2,2}^{2L}+D_{1,1}^{2L}\right)\right)
+\end{equation}
+
+\begin{equation}
+	D_{2,2}^{2L}B_{1}^{2L-1}=B_{1}^{2L-1}\left(D_{2,2}^{2L}-Q_{0}^{2L+2}\right)
+\end{equation}
+and 
+\begin{equation}
+	D_{1,1}^{2L}B_{1}^{2L-1}=B_{1}^{2L-1}\left(D_{1,1}^{2L}-Q_{0}^{2L+2}\right)
+\end{equation}
+Therefore we obtain 
+\begin{equation}\label{exchangeQk}
+	\begin{split}
+		(Q_{0}^{2L}B_{1}^{2L-1})^{k}&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+\mathbbm{1}_{\{j>1\}}4\sum_{i=1}^{j-1}(j-i)Q_{0}^{2L+2}\right)\\
+		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+2j(j-1)N\right)\\
+		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+2j(j-1)N\right)
+	\end{split}
+\end{equation}
+We use the following power expansion
 \begin{equation}\label{veryUsefulSeries}
@@
 \end{equation}
-we have that for each $\bm{m}$ 
-\begin{equation}
-	\begin{split}
-		&\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}H\right)^{n}(\Lambda_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
+We obtain
+\begin{equation}
+	\begin{split}
+		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}^{Q}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}^{Q}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\
+		=&
+		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)^{-1-n}(Q_{0}^{2L})^{n}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)^{-1-n}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}\right\}^{k}
 		\\=&
-		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\Lambda_{\bm{m}}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-\Lambda_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
-	\end{split}
-\end{equation}
-therefore the limit of the product is the product of the limit and we obtain that 
-\begin{equation}
-	\sum_{m=0}^{L}  (\Lambda_{\bm{m}}-H)\lim_{\epsilon\to 0}\epsilon R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
-\end{equation}
-Since the limit of the sum is the sum of the limit we have   
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-thus 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-Since $H_{0}=H_{0}^{T}$ 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-By calling 
-\begin{equation}\label{W-extended}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-we finally obtain 
-\begin{equation}
-	WH_{0}=HW
-\end{equation}
-Power expanding the transfer matrix by charges and considering the limit for $x\to\infty$ we have that 
-\begin{equation}
-	\begin{split}
-		W&= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}-\mathcal{Q}_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-		\end{split}
-\end{equation}
-and also satisfies \eqref{GoalWQ}. We now write the power expansion with respect to $B_{i}^{2L-1}$ of $W$. We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},
-\begin{equation}
-	\begin{split}
-	W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
-	\\&
-	\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{split}
-\end{equation} 
-we further observe that in the limit for $\epsilon\to 0$ the quantity 
-\begin{equation}
-\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
-\end{equation}
-therefore we have that 
-\begin{equation}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
-		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation}
-Considering the empty state as 
-\begin{equation}
-	|\Psi_{0}^{0}\rangle:=\begin{pmatrix}
-		0\\
-		\vdots\\
-		0\\
-		1
-	\end{pmatrix}\otimes \cdots \otimes\begin{pmatrix}
-	0\\
-	\vdots\\
-	0\\
-	1
-\end{pmatrix}
-\end{equation}
-then, we can map via $W$ the above vector to the steady state $|\Psi^{''}\rangle$ of $H^{''}$ defined in \eqref{steadyS-SECOND-def}, namely
-\begin{equation}
-	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
-\end{equation}
-\begin{comment}
-\begin{itemize}
-	\item for $j\neq N$ 
-\begin{equation}
-	\begin{split}
-	B_{j}(x)D_{jj}(y)=&\frac{(x+y)(1+x-y)}{(x-y)(1+x+y)}D_{jj}(y)B_{j}(x)-\frac{1}{(1+x+y)}\sum_{i=1\,:\,i\neq j}^{N-1}B_{i}(x)D_{i1}(y)
-	\\-&\frac{(x+y)}{(x-y)(1+x+y)}D_{jj}(x)B_{j}(y)-\frac{1}{(1+x+y)}D_{NN}(x)B_{j}(y)
-	\end{split}
-\end{equation}
-\item for $i,j\neq N$
-\begin{equation}
-	\begin{split}
-		B_{i}(x)D_{jj}(y)=D_{jj}(y)B_{j}(x)+\frac{1}{(x-y)}\left(D_{ji}(y)B_{j}(x)-D_{ji}(x)B_{j}(y)\right)
-	\end{split}
-\end{equation}
-\item for $j\neq N$
-\begin{equation}
-	\begin{split}
-		B_{j}(x)D_{NN}(y)&=\frac{(x-y)(1+x+y)}{(x+y)(1+x-y)}D_{NN}(y)B_{j}(x)+\frac{(x-y)}{(x+y)(1+x-y)}\sum_{i=1}^{N-1}B_{i}(y)D_{ij}(x)
-		\\&+
-		\frac{1}{(1+x-y)}B_{j}(y)D_{NN}(x)
-	\end{split}
-\end{equation}
-\end{itemize}
-\end{comment}
-%In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e.
-when the left boundary is lower triangular a end the right one is diagonal.
-We properly rescale them and we obtain
-
-%Then, we obtain the correspondent transfer matrix as
-%\begin{equation}
-%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
-%\end{equation}
-%where
-%\begin{equation}
-%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
-%\end{equation}
+		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{B_{1}^{2L-1}\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}\right\}^{k}
+	\end{split}
+\end{equation}
+where we used \eqref{exchangeQ0B}.
+We now need the exchange relations between $\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}$ and $B^{2L-1}$.
+They follow from \eqref{exchangeQk} and by observing that
+\begin{equation}
+	\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(A^{2L}+D_{1,1}^{2L})\right)\right)^{-1}=\sum_{n=0}^{\infty}(\Lambda_{m}^{Q}+\epsilon)^{-1-n}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}
+\end{equation}
+Finally we obtain 
+\begin{equation}\label{GoodBleft}
+	\begin{split}
+		W|\Psi_{m}^{0}\rangle=&\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		\\=&
+		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		\\=&
+		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+	\end{split}
+\end{equation}
+Using again \eqref{veryUsefulSeries} and re-summing we obtain 
+\begin{equation}
+	\begin{split}
+		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\lambda_{m}^{Q}+\epsilon)-\Lambda_{m}^{Q}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		\\=&
+		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\frac{1}{4^{k}}\frac{1}{k!}\prod_{j=1}^{k}\left\{e_{11}^{tot}-e_{22}^{tot}+2-j\right\}^{-1}|\Psi_{m}^{0}\rangle
+	\end{split}
+\end{equation}
+Calling $m$ the magnon number of the chain and observing that $e_{22}^{tot}|\Psi_{m}^{0}\rangle=m|\Psi_{m}^{0}\rangle$ and $e_{11}^{tot}|\Psi_{m}^{0}\rangle=(L-m)|\Psi_{m}^{0}\rangle$ we obtain 
+\begin{equation}
+	\begin{split}
+		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{L-2m+2-j\right\}^{-1}|\Psi_{m}^{0}\rangle
+	\end{split}
+\end{equation}
+Since 
+\begin{equation}
+	(L+2m+2-j)=\frac{\Gamma(L-2m+2-j+1)}{\Gamma(L-2m+2-j)}\quad \Rightarrow\quad \prod_{j=1}^{k}(L-2m+2-j)^{-1}=\frac{\Gamma(L-2m+2-k)}{\Gamma(L-2m+2)}
+\end{equation}
+indeed
+\begin{equation}
+	\prod_{j=1}^{k}(L-2m+2-j)^{-1}=\frac{\Gamma(L-2m+2-1)}{\Gamma(L-2m+2)}\frac{\Gamma(L-2m+2-2)}{\Gamma(L-2m+2-2+1)}\cdots\frac{\Gamma(L-2m+2-k+1)}{\Gamma(L-2m+2-k+2)}\frac{\Gamma(L-2m+2-k)}{\Gamma(L-2m+2-k+1)}
+\end{equation}
+Finally, using again the property of $e_{11}^{tot}$ and $e_{22}^{tot}$ and using the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain 
+\begin{equation}
+	\begin{split}
+		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}\frac{\Delta^{k}}{k!}\left(\frac{B_{1}^{2L-1}}{2}\right)^{k}\frac{\Gamma(\sigma_{0}^{tot}+2-k)}{\Gamma(\sigma_{0}^{tot}+2)}|\Psi_{m}^{0}\rangle
+	\end{split}
+\end{equation}
+This gives an explicit formula in term of the charge $B_{1}^{2L-1}$ of the matrix $W$.
+We stress the fact that these nice formula comes from the simple commutation relations between charges.
+Moreover, with such a formula it has been proved in \cite{frassek2020eigenstates} that the steady state $|\Psi^{''}\rangle$ can be found by acting on the vacum.
+\subsection{The gl(N) case}
+Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. 
 {\color{blue}
@@
 \cite{Belliard2} 
+\section{Extensions}
+\subsection{The non integrable chain}
+In Section \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
+This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations.
+Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+\subsection{Steady state correlations and duality}
+We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads as
+\begin{equation}
+	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}
+\end{equation} 
+where at the boundaries 
+\begin{equation}
+	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{delta}_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+while the bulk generator is 
+\begin{equation}
+ \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space
+ \begin{equation}	
+	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}
+\end{equation}
+The dual generator is 
+\begin{equation}
+	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
+\end{equation} 
+with absorbing boundaries, i.e. 
+\begin{equation}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
+	\end{split}
+\end{equation}
+where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
+\begin{equation}\label{dualityFunctionChain}
+	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
+Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
+\begin{equation}\label{ExptationSS}
+	\begin{split}
+		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\\=&
+		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
+	\end{split}
+\end{equation}
+where 
+\begin{equation}\label{Pass}
+	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+\end{equation}
+where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
+Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
+\begin{equation}
+	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{2,\ldots,N\}$ situated at sites $y_{i}\in\{1,\ldots,L\}$ with $i\in \{1,\ldots,m\}$.
+This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
+The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the one points correlations.
+\paragraph{One point correlations for the non-integrable case}
+We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
+\end{equation}
+Thus
+\begin{equation}\label{OnePtsCORR}
+	\begin{split}
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+	\end{split}
+\end{equation}
+we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
+Therefore, this $a_{s}^{x}(1)$ fulfils the following equations
+\begin{equation}\label{gamblers-ruin}
+	\begin{cases}
+		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
+		a^{1}_{s}(1)=\frac{|\alpha|}{1+|\alpha|}+a^{2}_{s}(1)\frac{1}{1+|\alpha|}\\
+		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+|\beta|}
+	\end{cases}
+\end{equation}
+where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where.
+The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}
+\end{equation}
+\textbf{Remark}: In case $|\alpha|=|\beta|=1$ we have 
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+\end{equation}
+that gives back \eqref{one-pts-corr}.
+\subsection{Instantaneous thermalization}
+In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}).
+The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles.
+The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\bm{\epsilon}=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\bm{\epsilon}$.
+\subsubsection{The thermalization measure}
+As already mentioned, we will redistribute particles on a bond according to a probability measure that is the reversible one \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond.
+We denote
+\begin{equation}
+	\begin{split}
+	\nu_{TH}(\bm{r}|\bm{\epsilon}):&=\mathbb{P}\left(n^{x}=\bm{r}|\eta^{x}+n^{x+1}=\bm{\epsilon}\right)
+	\\&
+	=\mathbb{P}\left((n_{1}^{x},\ldots,n_{N}^{x})=
+	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)
+	\end{split}
+\end{equation}
+where
+\begin{equation}
+	\epsilon_{1}=2\nu-\sum_{a=2}^{N}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=2}^{N}r_{a}
+\end{equation}
+We construct this measure.
+Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
+\begin{equation}
+	\begin{split}
+\nu_{TH}(\bm{r}|\bm{\epsilon})&=\frac{\mathbb{P}\left(\left\{n^{x}=\bm{r}\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\bm{\epsilon}\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}=\frac{\mathbb{P}\left(n^{x}=\bm{r}\right)\,\mathbb{P}\left(n^{x+1}=\bm{\epsilon}-\bm{r}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}
+	\end{split}
+\end{equation}
+Moreover, it holds that 
+\begin{equation}
+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
+\end{equation}
+Therefore 
+\begin{equation}
+	\begin{split}
+	\nu_{TH}(\bm{r}|\bm{\epsilon})=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
+	\end{split}
+\end{equation}
+where we denote the multinomial coefficient
+\begin{equation}
+	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}
+\end{equation}
+provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
+\subsubsection{Thermalized multi-species stirring process}
+The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace} and its generator reads
+\begin{equation}\label{thermalizedGenerator}
+	\mathcal{L}^{TH}=\mathcal{L}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{right}^{TH}
+\end{equation}
+where 
+\begin{equation}\label{bulkThermalized}
+	\begin{split}
+	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}
+	\\&
+	\left\{f(n^{1},\ldots,n^{x-1},\bm{r},n^{x}+n^{x+1}-\bm{r},n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
+	\end{split}
+\end{equation}
+while
+\begin{equation}\label{boundaryThermalized}
+	\begin{split}
+		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+		\end{split}
+	\end{equation}
+The right boundary generator is defined in a similar way. The $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
+\subsubsection{The dual thermalized process}
+The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
+\begin{equation}
+		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{right}^{TH}
+\end{equation}
+where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 
+\begin{equation}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{left}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
+	\end{split}
+\end{equation}
+and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$. 
+The duality function is 
+\begin{equation}
+	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+The proof of the duality consists in proving 
+\begin{align}
+	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
+	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
+\end{align}
+Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
+To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function.
+For the sake of notation, we introduce
+\begin{equation}
+	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+\end{equation}
+First, we act with $\mathcal{L}_{left}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
+\begin{align}\label{ProvaBordoTH}
+	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\\&\nonumber
+	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\\&
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+\end{align}
+Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
+\begin{align}\label{pezzo1}
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
+	\\&\nonumber
+	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\\=&
+	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
+\end{align}
+Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
+\begin{equation}\label{pezzo2}
+	\begin{split}
+	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
+	\end{split}
+\end{equation}
+Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
+\begin{align}
+	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\\&=
+	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+\end{align}
+\subsection{Multi-species stirring process with reaction}
+In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{2,3\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
+\begin{equation}\label{2SpeciesRD}
+	\partial \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)
+\end{equation} 
+for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$  and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.
+This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
+For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
+In view of what have been proved in the previous section of this work, some questions arise naturally:
+\begin{enumerate}
+		\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
+			\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
+	\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process?
+\end{enumerate}
+The aim of this section is to give an answer to these questions.
+We first define a more general process with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with N discrete Laplacians and a reaction term.
+Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
+\subsection{The process on a finite graph}
+Considering again a finite and connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
+\begin{equation}\label{RDGenerator}
+	\mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}
+\end{equation}
+where
+\begin{equation}\label{edgeGeneratorRD}
+	\mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
+\end{equation}
+with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
+\begin{equation}
+	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right)
+\end{equation}
+with the mapping 
+\begin{equation}
+	\begin{split}
+		g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
+		k&\to g_{c}(k)
+	\end{split}
+\end{equation}
+defined $\forall c\in\{1,\ldots,N-2\}$ as 
+\begin{equation}
+	g_{c}(k)=\begin{cases}
+		k+c \quad &\text{if}\quad k+c\leq N\\
+		k+c-N+1\quad &\text{if}\quad k+c>N\\
+		1\quad &\text{if}\quad k=1
+	\end{cases}
+\end{equation}
+Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
+Moreover,
+\begin{equation}
+	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
+\end{equation}
+The site generator reads
+\begin{equation}
+	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+where the boundary parameters are defined as
+\begin{equation}\label{boundaryParamRD}
+	\begin{split}
+		\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+		\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
+	\end{split}
+\end{equation}
+and where, for every $x\in V$, we further assume that
+\begin{equation}
+	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
+\end{equation}
+\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
+\paragraph{Action on the occupation variable of $\mathcal{L}_{x,y}^{rd}$}
+For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
+\begin{equation}\label{actionGraphRD}
+	\begin{split}
+		\mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
+	\end{split}
+\end{equation}
+
+Indeed
+\begin{equation}
+	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
+\end{equation}
+while for every $c\in \{1,\ldots,N-2\}$ we have 
+\begin{equation}
+	\begin{split}
+		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
+		\\&=
+		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
+		\\&=
+		\nu(n_{q}^{y}-n_{d}^{x})
+	\end{split}
+\end{equation}
+where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq 1$ .
+Moreover
+\begin{equation}
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
+\end{equation}
+Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
+\paragraph{Action on the occupation variable of $\mathcal{L}_{x}^{rd}$}
+Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
+\begin{equation}\label{actionBoudaryRD}
+	\begin{split}
+		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
+		\\&=
+		\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
+		\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\\=&
+		\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+	\end{split}
+\end{equation}
+\subsection{The process on a chain}
+Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$.
+This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
+Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
+\begin{equation}\label{DifferenceEquation}
+	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
+\end{equation}
+where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
+Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
+\begin{equation}\label{actionBDLine}
+	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
+\end{equation}
+On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
+\begin{equation}
+	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
+\end{equation}
+where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
+These average occupations evolve according to the Master equation
+\begin{equation}
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
+\end{equation} 
+Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
+For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
+This answers the first question of the beginning of this section.
+\subsection{Reversible measure} 
+The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
+	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
+\end{equation}
+when for any $a\in\{1,\ldots,N\}$
+\begin{equation}\label{reversibilityConditionRD}
+	\alpha_{a}^{x}=\alpha_{a}\quad \forall x\in V\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{2,\ldots,N\}
+\end{equation}
+This measure has marginals $\Lambda_{rev}^{x}$ given by 
+\begin{equation}
+	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)
+\end{equation}
+where 
+\begin{equation}
+	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{2,\ldots,N\}\qquad \text{and}\qquad \rho_{1}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}
+\end{equation}
+Namely,
+\begin{equation}
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho_{1}^{n_{1}^{x}}\rho^{\sum_{a=2}^{N}n_{a}^{x}}
+\end{equation}
+This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
+For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following.
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
+\begin{equation}
+	\begin{split}
+		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
+		\\
+		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
+		\\&
+		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
+	\end{split}
+\end{equation}
+that simplifies to 
+\begin{equation}
+	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
+\end{equation}
+that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{2,\ldots,N\}$.\\
+By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,y}$.
+\\
+For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$.
+As a consequence we have the result.
+\subsection{Duality}
+In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
+\begin{equation}
+	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
+\end{equation}
+To each site $x\in V$ we associate an ``extra site'', denoted $u(x)$,
+where dual particles will accumulate in the course of time. 
+We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+\begin{equation}
+	\bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
+\end{equation}
+where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
+the extra-site $u(x)$ connected to $x\in V$.
+
+The duality function is given by
+\begin{equation}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
+\end{equation}
+%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
+%\begin{equation}
+%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}
+%\end{equation}
+The dual process is defined by its generator, which reads
+\begin{equation}\label{DualGeneratorRD}
+	\widetilde{\mathcal{L}}^{rd}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
+\end{equation}
+where 
+$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}.
+\newline
+\newline
+\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process.
+The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
+As we will show this follows from a $gl(N)$ algebraic structure.
+\subsubsection{Proof of duality}
+In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
+\begin{equation}
+	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}\mathcal{H}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
+\end{equation}
+where $\mathcal{H}_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
+\begin{equation}
+	\mathcal{H}_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
+\end{equation}
+and 
+\begin{equation}
+	\mathcal{H}_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
+\end{equation}
+Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$.
+For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
+\begin{equation}\label{DualityRelationRD}
+	(H^{rd})^{T}D=D\widetilde{H}^{rd}
+\end{equation}
+Therefore, we need to prove that
+\begin{align}
+	(\mathcal{H}_{x,y}^{rd})^{T}D&=D\mathcal{H}_{x,y}^{rd}\label{edgeDualityRelationRD}\\
+	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
+\end{align}
+where the duality matrix $D$ is again \eqref{dualityMatrix}.
+As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $\mathcal{H}_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$.
+Therefore, we only need to show that
+\begin{align}
+	&(\mathcal{H}_{x,y}^{c})^{T}D=D\mathcal{H}_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
+	&(\mathcal{H}_{x,y}^{m})^{T}D=D\mathcal{H}_{x,y}^{m}\label{mDualityRelation}
+\end{align}
+Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$ have $\exp{(E^{x})}\exp{(E^{y})}$ as a symmetry.
+The first result will follow from the commutator between $\mathcal{H}_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
+Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
+\begin{align*}
+	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right.
+\\ \otimes&\left.
+\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
+	\\=&
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
+	\\=&0
+\end{align*}
+where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
+The second result will follow from the commutator between $\mathcal{H}_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
+\begin{equation}
+	\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
+\end{equation}
+\begin{flushright}
+	$\square$
+\end{flushright}
+With this prove we answered the second and third questions stated at the beginning of this section. \\
+\textbf{FROM HERE ON-WARDS STILL TO CHECK}\\
+\begin{comment}
+\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}
+In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{a})_{a=1,\ldots,N}$ and $(\beta_{a})_{a=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
+When the maximal occupation of each site $\nu>1$, this nice property is lost.
+However, something about correlations can be said using duality.
+In this subsection we still consider the same geometry of \ref{subsection-exact}.
+As pointed out in section~\ref{sectionDuality}, the dual process voids the chain.
+Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.
+In this context it is better to work agin with generators.
+We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry.
+\\
+We consider the process $(\bm{n}(t))_{t\geq 0}$ on a chain of length $L$ with the end sites connected with two reservoirs.
+This interaction with the external environment is described by the generators
+\begin{equation}
+    \mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+The bulk generator is 
+\begin{equation}
+    \mathcal{L}_{\text{bula}}=\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}\quad \text{where}\quad \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space $\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}$ with the same $\mathcal{L}_{\text{bula}}$ and with absorbing boundaries, i.e.
+\begin{equation}
+\begin{split}
+        \widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
+        \end{split}
+\end{equation}
+where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
+\begin{equation}\label{dualityFunctionChain}
+    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(ò\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
+Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
+\begin{equation}\label{ExptationSS}
+\begin{split}
+\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+\\=&
+\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
+\end{split}
+\end{equation}
+where 
+\begin{equation}\label{Pass}
+    a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+\end{equation}
+where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
+Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
+\begin{equation}
+    D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species.
+This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
+The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the one points correlations.
+\paragraph{One point correlations for the non-integrable case}
+We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
+\end{equation}
+Thus
+\begin{equation}\label{OnePtsCORR}
+\begin{split}
+	\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+ \end{split}
+\end{equation}
+we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
+This $a_{s}^{x}(1)$ fulfils the following equations
+\begin{equation}\label{gamblers-ruin}
+	\begin{cases}
+		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
+		a^{1}_{s}(1)=\frac{A}{1+A}+a^{2}_{s}(1)\frac{1}{1+A}\\
+		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+B}
+		\end{cases}
+\end{equation}
+where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where, for the sake of notation, we call $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$.
+The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
+\begin{equation}
+\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
+\end{equation}
+\textbf{Remark}: In case $A=B=1$ we have 
+	\begin{equation}
+\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+	\end{equation}
+that gives back \eqref{one-pts-corr}.  
+\end{comment}
 
@@
 fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} 
+\section{Exact steady state of $H$}\label{subsectionSSH}
+
+The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
+\begin{equation}\label{steadyStateH}
+	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
+\end{equation}
+where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
+\begin{equation}
+	\begin{split}
+		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+		\\&+
+		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},1}\right) 
+		\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
+		\\&
+		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
+	\end{split}
+\end{equation}
+where we have introduced, $\forall x\in \{1,\ldots,L\}$
+\begin{equation}
+	\eta_{x}(b)=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
+		d_{x}\qquad &\text{otherwise}
+	\end{cases}%\qquad \theta_{x}=\begin{cases}
+		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+		%	1 \qquad &\text{otherwise}
+		%\end{cases}
+	\end{equation}
+	The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
+	{\color{blue}
+		\begin{equation}\label{steadyStateH-coeff}
+			\begin{split}
+				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+				\\&+
+				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},1}\right) 
+				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
+				\\&
+				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
+				\\ &
+				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+			\end{split}
+		\end{equation}
+	}
+	\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $\tau_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
+	\begin{equation}\label{LinkABS-corr}
+		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
+	\end{equation}
+	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
+
+	\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
+This matrix $\mathcal{S}_{1}$ is given by
+	\begin{equation}\label{S1-L1}
+		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+	\end{equation}
+	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
+	\begin{equation}
+		\begin{split}
+			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
+			\\&
+			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
+		\end{split}
+	\end{equation}
+	where we have introduced, $\forall x\in \{1,\ldots,L\}$
+	\begin{equation}
+		%\eta_{x}=\begin{cases}
+			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+			%	d_{x}\qquad &\text{otherwise}
+			%\end{cases}\qquad
+			\theta_{x}(b)=\begin{cases}
+				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
+				1 \qquad &\text{otherwise}
+			\end{cases}
+		\end{equation}
+		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
+		%$e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+\\
+		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
+		\begin{align*}
+			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
+			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
+\\&+\left.
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
+			\\&\otimes
+			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
+			\\&=
+			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
+\\&+\left.
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
+		\end{align*}
+		\begin{comment}
+
+			\begin{equation}
+				F=\left(V^{-1}\right)^{T}
+			\end{equation}
+			and thus 
+			\begin{equation}
+				\mathcal{F}=F^{\otimes L}
+			\end{equation}
+			By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
+			\begin{equation}
+				F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+			\end{equation}
+			Taking the tensor product over two sites we obtain 
+			\begin{equation}
+				\begin{split}
+					F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
+					\right.\\ &+\left. 
+					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
+				\end{split}
+			\end{equation}
+			therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
+			\begin{equation}
+				\begin{split}
+					\left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
+					\\&+
+					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
+					\\&=
+					\sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+					+
+					(-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+				\end{split}
+			\end{equation}
+			where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
+\\
+			We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
+We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
+			\begin{equation}
+				\begin{split}
+					\mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
+					\\&
+					+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
+				\end{split}
+			\end{equation}
+			where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+\\
+		\end{comment}
+		The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
+		To find this elements we need to fix the rows correspondent to $\bm{\tau}$.
+Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
+		\begin{equation}
+			\begin{split}
+				\Psi(\bm{\tau}) &=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{\tau}}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
+				\\&
+				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\eta_{1},\ldots,\eta_{L})
+			\end{split}
+		\end{equation}
+		%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+		Using \eqref{elementsABS} we have 
+		\begin{equation}
+			\begin{split}
+				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
+				\\&
+				\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
+			\end{split}
+		\end{equation}
+		{\color{blue}
+			\begin{equation}
+				\begin{split}
+					&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+					\\&  
+					\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+					\\&
+					\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+				\end{split}
+		\end{equation}} indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
+Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}.
+		\begin{flushright}
+			$\square$
+		\end{flushright}
 \begin{comment}

### 2023-08-28 main.tex
fix 3
Fix3

@@
 \langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{t_{1},\ldots,t_{m}=0}^{1}
-\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}
 \end{equation}
@@
 We also introduce 
-\begin{equation}
-\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
-\end{equation}
-therefore we can write 
+\begin{equation}\label{Q-nonDiag}
+\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
+\end{equation}
+where $\Delta_{i}=(\alpha_{i}-\beta_{i})$. 
+Therefore we can write 
 \begin{equation}
@@
 \end{equation}}{\color{blue}Probably it is not useful}
-\section{Conserved charges form of W}
+\subsection{Conserved charges form of W}
 By using the QISM results found in the previous section it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system.
@@
 \subsection{The gl(N) case}
-Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. 
+Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. Repeating the computations we find that 
+\begin{equation}\label{W-extended}
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+Using the fact that $\left[H^{'},Q^{2L}\right]=0$ we can determine the matrix $W$ in function of the first non-trivial conserved charge $Q^{2L}$ as
+\begin{equation}
+	\begin{split}
+		W&= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}-\mathcal{Q}_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation}
+ Recalling the expression of $\mathcal{Q}^{2L}$ given in \eqref{Q-nonDiag} we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
+We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},
+\begin{equation}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
+		\\&
+		\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation} 
+Here $SYM$ is the following transformation. Introduce, the following $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$ indices, such that 
+\begin{equation}
+	\begin{split}
+		&i_{1}=\ldots=i_{k_{1}}=1\\
+	&	i_{k_{1}+1}=\ldots=i_{k_{1}+k_{2}}=2\\
+		&\vdots\\
+		&i_{k_{1}+\ldots+k_{N-2}+1}=\ldots=i_{k_{1}+\ldots+k_{N-1}}=N-1
+	\end{split}
+\end{equation}
+By denoting with 
+\begin{equation}
+	A_{i_{j}}=\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{i_{j}}^{2L-1}\right\}
+\end{equation}
+then 
+\begin{equation}
+	\begin{split}
+&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\&:=\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}
+	\end{split}
+\end{equation}
+where $Sym$ is the symmetric group. 
+We further observe that in the limit for $\epsilon\to 0$ the quantity 
+\begin{equation}
+	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
+\end{equation}
+therefore we have that 
+\begin{equation}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation}
 {\color{blue}

### 2023-08-28 main.tex
Fix 4

@@
 By taking the product over the chain we define
-\begin{equation}
+\begin{equation}\label{S1-Whole}
     S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}
@@
 By taking the product over the chain we also define
-\begin{equation}
+\begin{equation}\label{S2-Whole}
 	S_{2}=\prod_{x=1}^{L}S_{2}^{x}
@@
 \end{equation}
-Formula \eqref{W-extended} comes from standard perturbation theory.
-However, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system.
-This expression, as it will be show in the following sections, allows to find explicit expression of the eigenvector by the Bethe ansatz and also allows to retrieve again the steady state of $H^{''}$ by applying $W$ to the ground state.
-To find it, we use the Quantum Inverse Scattering Method (QISM).
+Formula \eqref{W-extended} may be evaluated by perturbation theory.
+Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz.
+This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state.
+To write formula \eqref{W-extended} using the charges of the system, we the Quantum Inverse Scattering Method (QISM).
 We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$.
@@
 \item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
-\begin{equation}
+\begin{equation}\label{B-charge}
 		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
@@
 Hopefully, using exchange relation between charges, we could try to handle \eqref{WInCharges} and rewrite it independently from the equilibrium eigenvectors.
-Moreover, we can use it to extract the steady state by rising the vacum state.
+Moreover, we can use it to extract the steady state by rising the vacuum state.
 \subsection{The gl(2) case}
@@
 \end{equation}
-Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and making it act on 
+Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and
 \begin{equation}\label{LinkWG}
@@
 \end{equation}
-We use the following power expansion
+We use the following series expansion
 \begin{equation}\label{veryUsefulSeries}
@@
 Finally, using again the property of $e_{11}^{tot}$ and $e_{22}^{tot}$ and using the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain 
-\begin{equation}
+\begin{equation}\label{Nice-W2}
 	\begin{split}
@@
 \subsection{The gl(N) case}
-Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. Repeating the computations we find that 
+Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains ($N>2$). Repeating the computations we find that 
 \begin{equation}\label{W-extended}
@@
  Recalling the expression of $\mathcal{Q}^{2L}$ given in \eqref{Q-nonDiag} we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
-We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},
+We obtain that, using also the multi-variate version of \eqref{veryUsefulSeries},
 \begin{equation}
@@
 \end{equation} 
-Here $SYM$ is the following transformation. Introduce, the following $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$ indices, such that 
+Here $SYM$ is the following transformation. We introduce, the following indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that 
 \begin{equation}
@@
 By denoting with 
-\begin{equation}
+\begin{equation}\label{definitionA}
 	A_{i_{j}}=\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{i_{j}}^{2L-1}\right\}
@@
 	\begin{split}
-&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\&:=\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}
+&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\=&
+SYM_{k_{1},\ldots,k_{N-1}}\left(A_{1},\ldots,A_{N-1}\right)\\
+=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}
 	\end{split}
@@
 \end{equation}
-{\color{blue}
-\subsection{Eigenvectors of the non equilibrium Hamiltonian}
-For simplicity we first consider the case with $N=3$.
-We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}.
-We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$.
-The eigenvectors are the following:
-\begin{equation}
-|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\end{equation}
-
-We replace the above eigenvectors in 
-\begin{equation}
-T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
-\end{equation}
-and we obtain
-\begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\end{align*}
-after a change of summation indices we obtain
-\begin{align*}
-&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\\+&
-\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\\+&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-\\=&
-\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}.
-\end{align*}
-We impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
-\begin{enumerate}
-\item $k_{2}=0$ and $k_{3}=0$
-\begin{equation}\label{cond1}
-	T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}
-\end{equation}
-\item $k_{2}=m_{2}+1$ and $k_{3}\in \{0,\ldots,m_{3}\}$
-\begin{equation}\label{cond2}
-	\begin{split}
-		B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
-	\end{split}
-\end{equation}
-\item $k_{2}\in\{0,\ldots,m_{2}\}$ and $k_{3}=m_{3}+1$
-\begin{equation}\label{cond3}
-	\begin{split}
-		B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
-	\end{split}
-\end{equation}
-\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}\in\{1,\ldots,m_{3}\}$ 
-\begin{equation}\label{cond4}
-	\begin{split}
-		&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}\left(B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		\\=&
-		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation} 
-\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
-\begin{equation}\label{cond5}
-	\begin{split}
-		&	\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		=
-		G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation}
-\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}=0$
-\begin{equation}\label{cond6}
-	\begin{split}
-		&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-		=
-		G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation}
-
-\end{enumerate}
-To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
-% \end{itemize}
-\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
-
-For the sake of notation we denote by 
-\begin{equation}
-\begin{split}
-A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
-\end{split}
-\end{equation}
-%{\color{red}Are we missing the prefactor $(N+2x)$?}
-where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
-
-\begin{equation}\label{cond4A}
-\begin{split}
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-\end{split}
-\end{equation}
-We introduce the following indices
-\begin{equation}
-i_{1}=\ldots=i_{k_{2}}=2\qquad i_{k_{2}+1}=\ldots =i_{k_{2}+k_{3}}=3
-\end{equation}
-Then, we introduce the permutation 
-\begin{equation}
-\sigma(i_{j})=i_{k}\qquad \forall j,k=1,\ldots,k_{2}+k_{3}
-\end{equation}
-We write
-\begin{equation}
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
-\end{equation}
-where we denoted by $\text{SYM}$ the symmetric group on $\{i_{1},\ldots,i_{k_{2}+k_{3}}\}$.\\
-It solves \eqref{cond4A}, indeed
-\begin{align*}
-&A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-\\=&A_{2}\frac{k_{2}}{k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}\frac{k_{3}}{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-\\=&
-A_{2}\frac{k_{2}}{k_{2}}\frac{1}{(k_{2}-1)!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\\+&A_{3}\frac{k_{3}}{k_{3}}\frac{1}{k_{2}!(k_{3}-1)!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
-\\=&
-\frac{1}{k_{2}!k_{3}!}\left(\sum_{\sigma \in \text{SYM}}k_{2}A_{2}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}+ \sum_{\sigma \in \text{SYM}}k_{3}A_{3}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\right)
-\\=&
-\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
-\\=&
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
-\end{align*}
-where in the up to last equality we used the fact that the quantity first summation is symmetric with respect to the exchange of $A_{2}$ and thus we have $k_{2}$ equal terms.
-Similarly, for the second summation using the symmetry with respect to $A_{3}$.
-\\
-This argument can be generalized for $N>2$ species introducing
-\begin{equation}
-G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\frac{1}{k_{2}!\cdots k_{N}!}\sum_{\sigma\in \text{SYM}}A_{i_{1}}\cdots A_{i_{k_{2}+\cdots+k_{N}}}
-\end{equation}
-where we assumed 
-\begin{equation}
-i_{1}=\cdots=i_{k_{2}}=2,\qquad \ldots \qquad i_{k_{2}+\cdots+k_{N-1}}=\cdots=i_{k_{2}+\ldots+k_{N}}=N
-\end{equation}
-\begin{comment}
-To write its solution we define
-\begin{equation}
-\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
-\end{equation}
-We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
-\begin{equation}
-\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
-\end{equation}
-We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group.
-\\
-The following expression solves \eqref{cond4A}
-\begin{equation}
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
-\end{equation}
-Indeed
+In this case, the commutation relations between $Q_{0}^{2L}$ and $B_{i}^{2L-1}$ are given by \eqref{ExQ0B-charges}.
+Exchanging $Q_{0}^{2L}$ with $B_{i}^{2L-1}$ generates also charges $B_{j}^{2L-1}$ with $j\neq 1$.
+Therefore, it is hard to obtain the multivariate equivalent of \eqref{Nice-W2}.
+\subsection{Non-equilibrium steady state from the W transformation}
+By using $W$ it is possible to obtain all the non-equilibrium eigenvectors by the knowledge of the equilibrium ones.
+As a consequence, also the non-equilibrium steady state can by found by using $W$.
+For the $N=2$ chain, this property has been proved in \cite{frassek2020eigenstates}.
+Also for the $gl(N)$ case, we can retrieve the non-equilibrium steady state of the Hamiltonian $H^{''}$ given in \eqref{ResulsBasis}, by acting with $W$ on the vacuum state
+\begin{equation}
+	|\Psi_{0}^{0}\rangle:=\underbrace{\begin{pmatrix}
+		0\\
+		\vdots\\
+		0\\
+		1
+	\end{pmatrix}\otimes \cdots \otimes\begin{pmatrix}
+		0\\
+		\vdots\\
+		0\\
+		1
+	\end{pmatrix}}_{L-\text{times}}
+\end{equation}
+Therefore, we have that 
+\begin{equation}
+	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
+\end{equation}
+We do not write the full proof, but only the result for the first non-trivial case, i.e. a chain of length $L=2$ with $N=3$ species. We set $3$ as the empty species.  
+\paragraph{Steady state for a $L=2$ and $N=3$ chain}
+Here we have 
+\begin{equation}
+	|\Psi_{0}^{0}\rangle=\begin{pmatrix}
+		0\\0\\1
+	\end{pmatrix}\otimes \begin{pmatrix}
+	0\\0\\1
+\end{pmatrix}=|\phi_{33}\rangle
+\end{equation}
+where we denoted by $(|\phi_{i}\rangle)_{j}=\delta_{j,i}$ the canonical basis of $\mathbb{C}^{3}$ and $|\phi_{ij}\rangle=|\phi_{i}\rangle\otimes|\phi_{j}\rangle$ the basis of the tensor product space $\mathbb{C}^{3}\otimes\mathbb{C}^{3}$.
+We have
+\begin{equation}
+	\begin{split}
+|\Psi^{''}\rangle=&	W|\Psi_{0}^{0}\rangle =\lim_{\epsilon\to 0}\sum_{k_{1}=0}^{2}\sum_{k_{2}=0}^{2}\Delta_{1}^{k_{1}}\Delta_{2}^{k_{2}}2^{k_{1}+k_{2}}SYM_{k_{1},k_{2}}\left(A_{1},A_{2}\right)|\Psi_{0}^{0}\rangle
+	\\=&\lim_{\epsilon\to 0}\left\{I+2\Delta_{1}A_{1}+2\Delta_{2}A_{2}+4\Delta_{1}^{2}A_{1}^{2}+4\Delta_{2}^{2}A_{2}^{2}+4\Delta_{1}\Delta_{2}\left(A_{1}A_{2}+A_{2}A_{1}\right)\right\}|\Psi_{0}^{0}\rangle
+	\end{split}
+\end{equation}
+where we recall $A_{i}$ defined in \eqref{definitionA}. We need to compute the action of each addend in the last equality on the state $|\Psi_{0}^{0}\rangle$.\\
+Using the charges computed in \eqref{B-charge} and \eqref{Q0Exp} we obtain that 
+\begin{equation}
+	\begin{split}
+A_{i}=	&\left(\Lambda_{0}^{Q}+\epsilon-Q_{0}\right)^{-1}B_{i}^{2L-1}\\=&\left((28+\epsilon)I^{tot}-10e_{33}^{tot}-2(e_{11}^{tot}e_{11}^{tot}+e_{22}^{tot}e_{22}^{tot}+e_{33}e_{33}^{tot})-2(e_{12}^{tot}e_{21}^{tot}+e_{21}^{tot}e_{12}^{tot})\right)^{-1}\\&\left(2e_{i3}^{tot}+2e_{i3}^{tot}e_{33}-2(e_{ii}^{[1]}e_{i3}^{[b]}+e_{i2}^{[2]}e_{23}^{[1]})\right)
+	\end{split}
+\end{equation}
+By the help of an algebraic manipulator we obtain 
 \begin{align}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
-\\&+
-A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
-\\&=
-\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
-\\&+
-\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
-\\&=
-\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
-\\&=
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
+	\lim_{\epsilon\to 0}2\Delta_{1}A_{1}|\phi_{33}\rangle&=\frac{2}{3}\Delta_{1}|\phi_{13}\rangle+\frac{1}{3}\Delta_{1}|\phi_{31}\rangle\\
+	\lim_{\epsilon\to 0}2\Delta_{2}A_{2}|\phi_{33}\rangle&=\frac{2}{3}\Delta_{2}|\phi_{23}\rangle+\frac{1}{3}\Delta_{3}|\phi_{32}\rangle\\
+\lim_{\epsilon\to 0}	4\Delta_{1}^{2}A_{1}^{2}|\phi_{33}\rangle&=\frac{1}{6}\Delta_{1}^{2}|\phi_{11}\rangle\\
+\lim_{\epsilon\to 0}	4\Delta_{1}^{2}A_{2}^{2}|\phi_{33}\rangle&=\frac{1}{6}\Delta_{2}^{2}|\phi_{22}\rangle\\
+\lim_{\epsilon\to 0}	4\Delta_{1}\Delta_{2}\left(A_{1}A_{2}+A_{2}A_{1}\right)|\phi_{33}\rangle&=\frac{1}{6}\Delta_{1}\Delta_{2}|\phi_{12}\rangle+\frac{1}{6}\Delta_{21}|\phi_{21}\rangle
 \end{align}
-where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
-\paragraph{Generalization to arbitrary $N$}
-For arbitrary $N\geq2$ we have 
-\begin{equation}
-\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}
-\end{equation}
-
-Thus the explicit expression becomes
-\begin{equation}
-G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
-\end{equation}
-with the same notation as in $N=3$ case. 
-\end{comment}
-\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
-\begin{equation}
-\begin{split}
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
-\\&
-\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
-\end{split}
-\end{equation}
-We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
-\begin{equation}
-\begin{split}
-A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
-A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
-\end{split}
-\end{equation}
-where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
-Therefore we rewrite \eqref{cond4} as 
-\begin{equation}
-\begin{split}
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
-\end{split}
-\end{equation}
-The left-hand-side is 
-\begin{equation}
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\end{equation}
-while, on the right-hand-side we have
-\begin{equation}
-\begin{split}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&=
-\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\end{split}
-\end{equation}
-and similarly 
-\begin{equation}
-\begin{split}
-A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&=
-\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
-\end{split}
-\end{equation}
-Therefore,
-\begin{equation}
-\begin{split}
-A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&+
-\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&=
-\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
-\\&=
-G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
-\end{split}
-\end{equation}
-Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.
-
-\paragraph{Genearlization to $N$ species:} we can generalize the eigenvector formula for arbitrary number of species $N>2$ by writing
-\begin{equation}
-\begin{split}
-|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
-\end{split}
-\end{equation}
-Denoting by
-\begin{equation}
-A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
-\end{equation}
-the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
-\begin{equation}
-\begin{split}
-G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
-\\&
-\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=\,k_{q}\}}\right)
-\\&
-\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
-\end{split}
-\end{equation}
-Condition \eqref{cond4} becomes
-\begin{equation}\label{cond4General}
-G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
-\end{equation}
-Arguing as in the case $N=3$ we observe that 
-\begin{equation}
-\begin{split}
-A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
-\\&
-\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=k_{q}\}}\right)
-\\&
-\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
-\end{split}
-\end{equation}
-therefore \eqref{cond4General} is fulfilled.
-Again, the equivalent of conditions \eqref{cond1}, e\eqref{cond5} and \eqref{cond6} are trivially satisfied.
-The equivalents of conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{j}(x)$ are rising operators for all $j\in \{2,\ldots,N\}$.
-}
-
+therefore, we have that
+\begin{equation}
+	\begin{split}
+	W|\Psi_{0}^{0}\rangle=&|\phi_{33}\rangle+\frac{2}{3}\Delta_{1}|\phi_{13}\rangle+\frac{1}{3}\Delta_{1}|\phi_{31}\rangle+\frac{2}{3}\Delta_{2}|\phi_{23}\rangle+\frac{1}{3}\Delta_{3}|\phi_{32}\rangle\\+&\frac{1}{6}\Delta_{1}^{2}|\phi_{11}\rangle+\frac{1}{6}\Delta_{2}^{2}|\phi_{22}\rangle+\frac{1}{6}\Delta_{1}\Delta_{2}|\phi_{12}\rangle+\frac{1}{6}\Delta_{21}|\phi_{21}\rangle
+	\\=& \left(\frac{1}{6}\Delta_{1}^{2},\;\frac{1}{6}\Delta_{1}\Delta_{2},\;\frac{2}{3}\Delta_{1},\;\frac{1}{6}\Delta_{1}\Delta_{2},\;\frac{1}{6}\Delta_{2}^{2},\;\frac{2}{3}\Delta_{2}\;\frac{1}{3}\Delta_{1},\;\frac{1}{3}\Delta_{2},\;1\right)\\=& |\Psi^{''}\rangle
+	\end{split}
+\end{equation}
+that is exactly the steady state $|\Psi^{''}\rangle$ computed in \eqref{ResulsBasis} in the case $L=2$ and $N=3$.
+To obtain the steady state $|\Psi\rangle$ of $H$ we only need to invert the transformations $S_{1}$ and $S_{2}$ defined in \eqref{S1-Whole} and \eqref{S2-Whole}.
 \subsection{Bethe ansatz solution}
@@
 \begin{equation}
-	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{delta}_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
 \end{equation}

### 2023-09-06 main.tex
Fix 5
kj
lk
W exact draft

@@
 \begin{equation}
-\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+\begin{split}
+\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
 f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\end{split}
 \end{equation}
@@
 \begin{equation}
-\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{t_{1},\ldots,t_{m}=0}^{1}
-\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}
+\begin{split}
+\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
+=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\end{split}
 \end{equation}
@@
 %\end{equation}
-\item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
+\item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
 \begin{equation}\label{B-charge}
-		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
+		B_{j}^{2L-1}=	2e_{jN}^{tot}e_{NN}^{tot}-2\sum_{a,b=1\,:\, a<b}^{L}\,\sum_{k=1}^{N}e_{kN}^{[a]} e_{jk}^{[b]}
 \end{equation}
@@
 therefore we have that 
-\begin{equation}
+\begin{equation}\label{W-charges-Bad}
 	\begin{split}
@@
 \end{equation}
+To prove this statement we introduce the following notation. We identify each state by 
+\begin{equation}
+	|\tau_{1},\ldots,\tau_{L}\rangle\qquad \text{where}\qquad \tau_{x}\in\{1,\ldots,N\}\quad \forall x\in \{1,\ldots,L\}
+\end{equation}
+therefore the vacuum state reads
+\begin{equation}
+	|\Psi_{0}^{0}\rangle=|N,\ldots,N\rangle
+\end{equation}
+We first write some relations that will be useful in the proof.
+\begin{equation}\label{BActionVoid}
+	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
+\end{equation}
+\begin{equation}
+	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
+\end{equation}
+\begin{equation}
+	D_{i,j}^{2L}|\tau_{1},\ldots,\tau_{L}\rangle=-2|\tau_{1}^{'}\ldots,\tau_{L}^{'}\rangle \qquad \text{where}\qquad \tau^{'}_{x}=\begin{cases}
+		\tau_{x}\quad &\text{if}\quad \tau_{x}\neq i\\
+		j\quad &\text{if}\quad \tau_{x}=i
+	\end{cases}
+\end{equation}
+\begin{equation}\label{GoodRelation}
+	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
+\end{equation}
+Indeed
+\begin{align}
+	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
+	\\&=
+	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
+	\\&=
+	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
+	\\&=
+	-2B_{i}|\Psi_{0}^{0}\rangle
+\end{align}
+\begin{equation}
+	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0\qquad \forall k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i
+\end{equation}
+\begin{equation}
+	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle \qquad \forall i\in \{1,\ldots,N-1\}
+\end{equation}
+Indeed,
+\begin{align}
+D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=	(2e_{ii}^{tot}-I)|\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
+\end{align}
+\begin{equation}\label{GainCommutationQ}
+	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
+\end{equation}
+Therefore, $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$. Indeed,
+\begin{align}
+	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
+		\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
+		\\&=
+		(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
+\end{align}
+since 
+\begin{equation}
+\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0\qquad e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
+\end{equation}
+Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j,k\in\{1,\ldots,N-1\}$
+\begin{equation}\label{Three-Relation}
+	Q_{0}^{2L}B_{k}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}B_{k}^{2L-1}\prod_{j=}^{3}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
+\end{equation}
+Observe that \eqref{Three-Relation} also implies that 
+\begin{equation}
+	Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle
+\end{equation}
+i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute. This simplify formula \eqref{W-charges-Bad} as
+\begin{equation}
+	\begin{split}
+	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
+\end{split}
+\end{equation}
+Therefore, we can generalize \eqref{Three-Relation} and find 
+\begin{equation}
+	\begin{split}
+		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&
+		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+	\end{split}
+\end{equation}
+where 
+\begin{equation}
+	\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
+\end{equation}
+This can be written as
+\begin{equation}
+	\begin{split}
+		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
+		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
+	\end{split}
+\end{equation}
+\begin{comment}
 We do not write the full proof, but only the result for the first non-trivial case, i.e. a chain of length $L=2$ with $N=3$ species. We set $3$ as the empty species.  
@@
 To obtain the steady state $|\Psi\rangle$ of $H$ we only need to invert the transformations $S_{1}$ and $S_{2}$ defined in \eqref{S1-Whole} and \eqref{S2-Whole}.
+\end{comment}
 \subsection{Bethe ansatz solution}

### 2023-09-07 main.tex
jkl

@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{Dij-ref}
 	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
@@
 \end{align}
-\begin{equation}
+\begin{equation}\label{DijBk-different}
 	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0\qquad \forall k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i
 \end{equation}
-\begin{equation}
+\begin{equation}\label{Dii-ref}
 	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle \qquad \forall i\in \{1,\ldots,N-1\}
@@
 \end{equation}
-Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j,k\in\{1,\ldots,N-1\}$
-\begin{equation}\label{Three-Relation}
-	Q_{0}^{2L}B_{k}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}B_{k}^{2L-1}\prod_{j=}^{3}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
-\end{equation}
-Observe that \eqref{Three-Relation} also implies that 
+Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j\in\{1,\ldots,N-1\}$
+\begin{equation}\label{Two-Relation}
+	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
+\end{equation}
+Indeed, consider \eqref{ExQ0B-charges} then we can write 
+\begin{align}
+	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right\}|\Psi_{0}^{0}\rangle
+\end{align}
+Using \eqref{Dij-ref}, and \eqref{Dii-ref} we obtain 
+\begin{align}
+	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)\right\}|\Psi_{0}^{0}\rangle
+\end{align}
+Now two different cases are possible:
+\begin{itemize}
+	\item \textit{Case 1}: $i=j$ therefore using \eqref{DijBk-different} we obtain 
+	\begin{align}
+		&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+		\\=&
+		B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+	\end{align}
+Using again 
+\end{itemize}
+Observe that \eqref{Two-Relation} also implies that 
 \begin{equation}
@@
 \end{equation}
+where 
+\begin{equation}
+	\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
+\end{equation}
 Therefore, we can generalize \eqref{Three-Relation} and find 
@@
 	\begin{split}
-		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&
-		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
-	\end{split}
-\end{equation}
-where 
-\begin{equation}
-	\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
-\end{equation}
+		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}\\&
+		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
+	\end{split}
+\end{equation}
+
 This can be written as

### 2023-09-07 main.tex
lkj

@@
 While, for $i,j\in\{1,\ldots,N-1\}$ such that $i\neq j$
-\begin{equation}
+\begin{equation}\label{Commuting-Charges}
 \left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0%\qquad \left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0
@@
 \end{align}
-\begin{equation}\label{GainCommutationQ}
+\begin{equation}\label{Diagonal-Q-void}
 	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
@@
 	\end{align}
-Using again 
+Using \eqref{ExQ0B-charges}, \eqref{ExDiB-charges} and \eqref{ExDNB-charges} we obtain 
+\begin{align}
+	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)-2\sum_{\ell=0\;\ell\neq i}B_{\ell}^{2L-1}D_{\ell,i}\right\}\nonumber\\&
+	\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+\end{align}
+By using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 
+\begin{equation}\label{D2Lp1}
+	D_{i,i}^{2L+1}-D_{N,N}^{2L+1}=-2I
+\end{equation}
+we have 
+\begin{align}
+	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber=\left(B_{i}^{2L-1}\right)^{2}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+\end{align}
+that can be rewritten as \eqref{Two-Relation}.
+\item \textit{Case 2}: $i\neq j$. Using \eqref{GoodRelation} we have
+\begin{align}
+	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+\end{align} 
+thus we have 
+\begin{align}
+ &Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})+4\right)\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+\end{align}
+Using \eqref{ExQ0B-charges}, \eqref{ExDiB-charges}, \eqref{ExDNB-charges}, \eqref{Commuting-Charges} and \eqref{D2Lp1} we obtain 
+\begin{align}
+	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\=&B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})+4-2D_{j,j}^{2L}-2(D_{N,N}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1})\right)\nonumber\\&\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
+	\\=&
+	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
+	\\=&
+	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+\end{align}
+that can be written as \eqref{Two-Relation}. 
 \end{itemize}
 Observe that \eqref{Two-Relation} also implies that 
-\begin{equation}
+\begin{equation}\label{Commutativity-Gained}
 	Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle
 \end{equation}
-i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute. This simplify formula \eqref{W-charges-Bad} as
-\begin{equation}
-	\begin{split}
-	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
-\end{split}
-\end{equation}
-where 
-\begin{equation}
-	\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
-\end{equation}
-Therefore, we can generalize \eqref{Three-Relation} and find 
-\begin{equation}
-	\begin{split}
-		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}\\&
+i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute.
+For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
+\begin{equation}\label{k-times-QB}
+	\begin{split}
+		\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle=\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
+	\end{split}
+\end{equation}
+Therefore, using \eqref{veryUsefulSeries}, we obtain
+\begin{equation}\label{k-times-LQB}
+	\begin{split}
+		&\prod_{\ell=1}^{N-1}\left((\Lambda_{0}+\epsilon-Q_{0}^{2L})^{-1}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle\\=&\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
+	\end{split}
+\end{equation}
+ %This simplify formula \eqref{W-charges-Bad} as
+%\begin{equation}
+%	\begin{split}
+%	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
+%\end{split}
+%\end{equation}
+%where 
+%\begin{equation}
+	%\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
+%\end{equation}
+Therefore, we find 
+\begin{equation}
+	\begin{split}
+		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\\&
 		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
@@
 \end{equation}
-
-This can be written as
+Using \eqref{veryUsefulSeries} and \eqref{Diagonal-Q-void} we obtain 
 \begin{equation}

### 2023-09-08 main.tex
jkl
lkjlkj

@@
 \item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
-\begin{equation}
+\begin{equation}\label{Dij-Charge}
 D_{i,j}^{2L}=-2e_{ji}^{tot}
@@
 Therefore, we have that 
-\begin{equation}
-	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
-\end{equation}
-To prove this statement we introduce the following notation. We identify each state by 
+\begin{equation}\label{SteadyState-W-Good}
+	\begin{split}
+		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
+		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
+	\end{split}
+\end{equation}
+To prove \eqref{SteadyState-W-Good} we do some steps. 
+\paragraph{Useful relations}
+We introduce the following notation:
 \begin{equation}
@@
 \end{equation}
-We first write some relations that will be useful in the proof.
+We first write some relations that will be useful in the proof:
+\begin{itemize}
+	\item For all $i\in\{1,\ldots,N-1\}$
 	\begin{equation}\label{BActionVoid}
@@
 	\end{equation}
+
+\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
+\begin{align}
+	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
+	\\=&
+	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
+	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
+\end{align}
+where we used the fact that 
+\begin{equation}
+	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
+\end{equation}
+\begin{flushright}
+	$\square$
+\end{flushright}
+\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
 \begin{equation}\label{Dij-ref}
@@
 \end{equation}
-\begin{equation}
-	D_{i,j}^{2L}|\tau_{1},\ldots,\tau_{L}\rangle=-2|\tau_{1}^{'}\ldots,\tau_{L}^{'}\rangle \qquad \text{where}\qquad \tau^{'}_{x}=\begin{cases}
-		\tau_{x}\quad &\text{if}\quad \tau_{x}\neq i\\
-		j\quad &\text{if}\quad \tau_{x}=i
-	\end{cases}
-\end{equation}
+The proof is trivial from the definition of \eqref{Dij-Charge}. 
+\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
+\begin{equation}
+	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
+\end{equation}
+The proof is trivial from \eqref{Dij-Charge}. 
+\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
 \begin{equation}\label{GoodRelation}
@@
 \end{equation}
-Indeed
+\textbf{Proof of \eqref{GoodRelation}:}
 \begin{align}
@@
 \end{align}
+\begin{flushright}
+	$\square$
+\end{flushright}
+\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
 \begin{equation}\label{DijBk-different}
-	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0\qquad \forall k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i
-\end{equation}
+	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
+\end{equation}
+The proof is trivial following the one of \eqref{GoodRelation}. 
+\item For all $ \forall i\in \{1,\ldots,N-1\}$
 \begin{equation}\label{Dii-ref}
-	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle \qquad \forall i\in \{1,\ldots,N-1\}
-\end{equation}
-Indeed,
+	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
+\end{equation}
+\textbf{Proof of \eqref{Dii-ref}:}
 \begin{align}
@@
 \end{align}
+\begin{flushright}
+	$\square$
+\end{flushright}
+\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
 \begin{equation}\label{Diagonal-Q-void}
@@
 \end{equation}
-Therefore, $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$. Indeed,
+\textbf{Proof of \eqref{Diagonal-Q-void}:}
 \begin{align}
@@
 \end{align}
-since 
-\begin{equation}
-\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0\qquad e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
-\end{equation}
-Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j\in\{1,\ldots,N-1\}$
+where we used the fact that 
+\begin{equation}
+	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
+\end{equation}
+\begin{flushright}
+	$\square$
+\end{flushright}
+\end{itemize}
+
+\paragraph{Two indices formula}
+Using \eqref{BActionVoid} and \eqref{Commutativity-Gained} we have that for all $i,j\in\{1,\ldots,N-1\}$
 \begin{equation}\label{Two-Relation}
@@
 \end{equation}
-Indeed, consider \eqref{ExQ0B-charges} then we can write 
+\textbf{Proof of \eqref{Two-Relation}:}
+consider \eqref{ExQ0B-charges} then we can write 
 \begin{align}
@@
 \begin{align}
-	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\\&
+	B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber\\=&\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
 \end{align} 
@@
 \end{itemize}
+\begin{flushright}
+	$\square$
+\end{flushright}
 Observe that \eqref{Two-Relation} also implies that 
@@
 i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute.
-For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
+\paragraph{Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
 \begin{equation}\label{k-times-QB}
@@
 \end{equation}
+\textbf{Proof of \eqref{k-times-QB}}
+\begin{flushright}
+	$\square$
+\end{flushright}
 Therefore, using \eqref{veryUsefulSeries}, we obtain
@@
 %\end{equation}
-Therefore, we find 
+\paragraph{Final formula.} Therefore, we find 
 \begin{equation}

### 2023-09-08 main.tex
fixed

@@
 \end{equation}
-\textbf{Proof of \eqref{k-times-QB}}
+\textbf{Proof of \eqref{k-times-QB}}: we can prove it inductively. For arbitrary $i\in\{1,\ldots,N-1\}$ it is true, since, using \eqref{ExQ0B-charges} and \eqref{Dij-ref} we have that 
+\begin{align}
+	Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&\left(B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,:\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+\end{align}
+We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\{1,\ldots,N-1\}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  
+\begin{align}
+&\left(Q_{0}^{2L}B_{i}^{2L-1}\right)\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle=\left(B_{i}^{2L-1}\right)^{k_{i}+1}\prod_{\ell=1\,:\;\ell\neq i}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\nonumber\\&\prod_{j=1}^{k_{1}+\ldots+k_{N-1}+1}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
+\end{align}
+it is also true. This can be shown by applying repeatedly \eqref{Two-Relation}.
 \begin{flushright}

### 2023-09-08 main.tex
fixed fixed
W-steady-proof

@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{DNN-charge}
 	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
@@
 	D_{ii}^{2L+1}=-I^{tot}
-\end{equation}\begin{equation}\label{a2l}
+\end{equation}\begin{equation}\label{Dii-charge}
 	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
@@
 Also for the $gl(N)$ case, we can retrieve the non-equilibrium steady state of the Hamiltonian $H^{''}$ given in \eqref{ResulsBasis}, by acting with $W$ on the vacuum state
-\begin{equation}
+\begin{equation}\label{Vacuum-state}
 	|\Psi_{0}^{0}\rangle:=\underbrace{\begin{pmatrix}
@@
 \end{equation}
-To prove \eqref{SteadyState-W-Good} we do some steps. 
-\paragraph{Useful relations}
+\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
+Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult and we cannot rewrite \eqref{W-charges-Bad} in such a simpler form.
+\subsubsection{Proof of \eqref{SteadyState-W-Good}}
+To prove \eqref{SteadyState-W-Good} we do four steps. 
+\paragraph{1. Useful relations}
 We introduce the following notation:
@@
 where we used the fact that 
-\begin{equation}
+\begin{equation}\label{eNN-action}
 	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
@@
 \begin{equation}\label{Dii-ref}
-	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
-\end{equation}
-\textbf{Proof of \eqref{Dii-ref}:}
-\begin{align}
-	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=	(2e_{ii}^{tot}-I)|\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
-\end{align}
-\begin{flushright}
-	$\square$
-\end{flushright}
+	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
+\end{equation}
+The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
 \item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
@@
 
-\paragraph{Two indices formula}
+\paragraph{2. Two indices formula}
 Using \eqref{BActionVoid} and \eqref{Commutativity-Gained} we have that for all $i,j\in\{1,\ldots,N-1\}$
@@
 i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute.
-\paragraph{Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
+\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
 \begin{equation}\label{k-times-QB}
@@
 \end{align}
-We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\{1,\ldots,N-1\}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  
+We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  
 \begin{align}
@@
 \end{flushright}
-Therefore, using \eqref{veryUsefulSeries}, we obtain
+As a consequence of \eqref{veryUsefulSeries} and of \eqref{Two-Relation}, it is easy to prove that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$
 \begin{equation}\label{k-times-LQB}
@@
 %\end{equation}
-\paragraph{Final formula.} Therefore, we find 
-\begin{equation}
+\paragraph{4.
+Final formula.} Using \eqref{Commutativity-Gained} and \eqref{k-times-QB} the symmetrization operator written in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads, for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$
+\begin{align}
+	&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+	|\Psi_{0}^{0}\rangle
+	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle
+	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
+\end{align}
+Therefore, the action of the matrix $W$ on $|\Psi_{0}^{0}\rangle$ is given by
+\begin{equation}\label{intermediate-W-ss}
 	\begin{split}
@@
 \end{equation}
-Using \eqref{veryUsefulSeries} and \eqref{Diagonal-Q-void} we obtain 
-\begin{equation}
-	\begin{split}
-		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
-		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
-	\end{split}
-\end{equation}
+Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have that, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 
+\begin{align}
+&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\\=&
+\sum_{t=0}^{\infty}\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-t-1}|\Psi_{0}^{0}\rangle
+\end{align}
+We observe that
+\begin{equation}
+	\lim_{\epsilon\to 0}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}\Psi_{0}^{0}=|\Psi_{0}^{0}\rangle
+\end{equation}
+therefore, re-summing the series we obtain
+\begin{align}
+	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
+	\\=&
+	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}\Psi_{0}^{0}
+	\\=&
+	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+	\\=&
+	\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+\end{align}
+Using \eqref{Dii-ref} we have 
+\begin{align}
+	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+	\\=&
+	\frac{1}{4j}\left\{L-j+2\right\}^{-1}|\Psi_{0}^{0}\rangle
+\end{align}
+Using the Euler $\Gamma$-function we have 
+\begin{align}
+\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\frac{1}{2j}\left\{L-j+2\right\}^{-1}|\Psi_{0}^{0}\rangle=\frac{1}{4^{k_{1}+\ldots+k_{N-1}}}\frac{1}{(k_{1}+\ldots+k_{N-1})!}\frac{\Gamma(L+2-(k_{1}+\ldots+k_{N-1}))}{\Gamma(L+2)}|\Psi_{0}^{0}\rangle
+\end{align}
+Finally, replacing this formula in \eqref{intermediate-W-ss} and using \eqref{eNN-action} we obtain \eqref{SteadyState-W-Good}. 
+\begin{flushright}
+	$\square$
+\end{flushright}
+%\begin{equation}
+%	\begin{split}
+%		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
+%		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
+%	\end{split}
+%\end{equation}
 \begin{comment}

### 2023-09-08 main.tex
fixed
Motivation Q0-1

@@
 	\\&=
-	-2B_{i}|\Psi_{0}^{0}\rangle
+	-2B_{j}|\Psi_{0}^{0}\rangle
 \end{align}
@@
 \end{equation}
-i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute.
+i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute when acting on $|\Psi_{0}^{0}\rangle$.\\
+We further observe that 
+\begin{align}\label{Two-Points-m1}
+	&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+	\\=&
+	B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
+\end{align}
+Indeed, as a consequence of \eqref{veryUsefulSeries}, we have 
+\begin{align}
+	&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left\{\left(\Lambda_{0}+\epsilon\right)^{-1}Q_{0}^{2L}\right\}^{n}\left(\Lambda_{0}+\epsilon\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}(Q_{0}^{2L})^{n}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+\end{align}
+We have that, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},
+\begin{align}
+&(Q_{0}^{2L})^{n}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=(Q_{0}^{2L})^{n-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}\right\}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+(Q_{0}^{2L})^{n-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{n}|\Psi_{0}^{0}\rangle
+\end{align}
+Therefore
+\begin{align}
+&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}B_{i}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{n}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)^{-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle
+\end{align}
+Using again \eqref{veryUsefulSeries} and applying the same argument we have 
+\begin{align}
+&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+B_{j}^{2L-1}\sum_{n=0}^{\infty}\left\{\left(\Lambda_{0}+\epsilon\right)^{-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)\right\}^{n}\left(\Lambda_{0}+\epsilon\right)^{-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle\nonumber
+\\=&
+B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
+\end{align}
 \paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
@@
 \end{flushright}
-As a consequence of \eqref{veryUsefulSeries} and of \eqref{Two-Relation}, it is easy to prove that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$
+As a consequence of \eqref{Two-Points-m1} we have that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$
 \begin{equation}\label{k-times-LQB}
@@
 	&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
-	|\Psi_{0}^{0}\rangle
-	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle
+	|\Psi_{0}^{0}\rangle\nonumber
+	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle\nonumber
 	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
@@
 &\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\\=&
-\sum_{t=0}^{\infty}\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-t-1}|\Psi_{0}^{0}\rangle
+\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle
 \end{align}
-We observe that
-\begin{equation}
-	\lim_{\epsilon\to 0}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}\Psi_{0}^{0}=|\Psi_{0}^{0}\rangle
-\end{equation}
-therefore, re-summing the series we obtain
+Therefore, re-summing the series we obtain
 \begin{align}
-	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
+	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\nonumber
 	\\=&
-	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}\Psi_{0}^{0}
+	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle\nonumber
 	\\=&
-	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
 	\\=&
@@
 \begin{align}
-	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
-	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
+	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
+	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
 	\\=&

### 2023-09-11 main.tex
fix
lkj

@@
 \end{equation}
-This matrix is 
+We will prove that 
 \begin{equation}\label{W-extended}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-%We have that 
-%\begin{equation}
-%	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
-%\end{equation}
-%thus it is enough to look for a matrix $W$ such that 
-%\begin{equation}\label{GoalWQ}
-%	Q^{2L}W=WQ_{2L}^{0}
-%\end{equation}
-To find a matrix $W$ such that \eqref{GoalWH} is fulfilled we use the \textit{resolvent operator} defined as
-\begin{equation}
-	R(z,H):=\left(zI-H\right)^{-1}
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+\end{equation}
+\paragraph{Construction of matrix W}
+We aim to show that \eqref{W-extended} fulfils \eqref{GoalWH}. Consider the \textit{resolvent operator}
+\begin{equation}
+	R(z,H^{''}):=\left(z-H^{''}\right)^{-1}
 \end{equation}
@@
 \begin{equation}
-	(z-H)R(H,z)=1
-\end{equation}
-In order to be well defined we must $z$ must not be an eigenvalue of $H$ (and thus of $H_{0}$).
+	(z-H^{''})R(H^{''},z)=I
+\end{equation}
+In order to be well defined $z$ must not be an eigenvalue of $H^{''}$.
 We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
 Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
-We take $z=\Lambda_{\bm{m}}+\epsilon$
-\begin{equation}
-	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)=1
+We chose $z=\Lambda_{\bm{m}}+\epsilon$
+\begin{equation}
+	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)=1
 \end{equation}
@@
 \begin{equation}
-	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We sum over all possible $m$ 
-\begin{equation}
-	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We multiply both sides by $\epsilon$ 
-\begin{equation}
-	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We take the limit for $\epsilon\to 0$ on both sides 
+	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+\end{equation}
+we sum over all possible $\bm{m}$'s 
+\begin{equation}
+	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+\end{equation}
+we multiply both sides by $\epsilon$ 
+\begin{equation}
+	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+\end{equation}
+we take the limit for $\epsilon\to 0$ on both sides 
 \begin{equation}
@@
 \end{equation}
-Observe that 
+Observe that, trivially,
 \begin{equation}
@@
 By calling 
-\begin{equation}\label{W-extended}
+\begin{equation}
 	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
@@
 Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz.
-This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state.
-To write formula \eqref{W-extended} using the charges of the system, we the Quantum Inverse Scattering Method (QISM).
-We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$.
+This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
+To write formula \eqref{W-extended} using the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM).
+We first present the simpler case of $gl(2)$, then we adapt the proof to the general $gl(N)$.
 \subsection{Quantum inverse scattering method}
-We can apply the \textit{quantum inverse scattering method} to this process.
-We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$.
+ We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$.
 In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
-We introduce the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
+We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
 \begin{equation}\label{Rmatrix}
@@
 \end{equation}
-The above matrices satisfy the following equations
+The above matrices satisfy
 \begin{itemize}
@@
 \end{itemize}
-We define the \textit{transfer matrix}
+We introduce the \textit{transfer matrix}
 \begin{equation}
@@
 \end{equation}
-where we used the double row monodromy defined as
+that satisfies
+\begin{equation}
+	\left[T^{\Delta}(x),T^{\Delta}(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T^{\Delta}(0))=C_{1}H^{''}+C_{2}I
+\end{equation}
+with $C_{1},C_{2}>0$. \\
+The double row monodromy is given by
 \begin{equation}
@@
 \end{equation}
-This double row monodromy satisfies the following exchange relation
+$U_{0}(x)$ satisfies the following exchange relation
 \begin{equation}\label{RURU}
@@
 \end{equation}
-This trasfer matrix has the following properties
-\begin{equation}
-	\left[T^{\Delta}(x),T^{\Delta}(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T^{\Delta}(0))=C_{1}H^{''}+C_{2}I
-\end{equation}
-with $C_{1},C_{2}>0$. \\
+
 We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
@@
 		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
-		B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
+		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
 	\end{pmatrix}
@@
 \subsection{Charges}
-Then we have
+The transfer matrix $T^{\Delta}(x)$ reads
 \begin{equation}
@@
 			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
-		\end{pmatrix}\right)
-	\end{split}
-\end{equation}
-Therefore we can write the polynomial expansion
-\begin{equation}
-	\begin{split}
-		T^{\Delta}(x)=&
-		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
+		\end{pmatrix}\right)\\
+	=&
+	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
+	\end{split}
+\end{equation}
+therefore, it is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
+\begin{equation}
+	\begin{split}
+		T^{\Delta}(x)=
 		\sum_{k=0}^{2L+2}Q_{k}x^{k}
@@
 \end{equation}
-We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
-We can also introduce 
+where, for all $k\in\{0,\ldots,2L+2\}$, we call these $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
 \begin{equation}
 	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
-\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
+\end{equation}
+Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
 \begin{equation}
@@
 \end{equation}
-In the following it will be clear that only the first three coefficients of the diagonal elements and only the first coefficient of the non diagonal element are needed. 
+ Only the first three coefficients of the diagonal elements and the first coefficient of the non diagonal elements do survive when $x\to \infty$, therefore we only compute them. We obtain:
 \begin{itemize}
-	\item For the element $D_{N,N}(x)$: 
-%The coefficients that we need are the following:
-%\begin{equation}
-%	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
-%\end{equation}
-where 
+	\item For $D_{N,N}(x)$:
+
 \begin{equation}
@@
 \end{equation}
-%\begin{equation}
-%	\begin{split}
-	%	D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
-%	\end{split}
-%\end{equation}
-\begin{comment}
-{\color{blue}ok}
-
-We observe that $\forall i,j=1,\ldots,N-1$
-\begin{equation}
-	\sum_{a\neq b}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
-\end{equation}
-then 
-\begin{equation}
-	D_{N,N}^{2L-1}=e_{NN}^{tot}\left(2e_{NN}^{tot}+I^{tot}\right)-\sum_{j=1}^{N}e_{jj}^{tot}%=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
-\end{equation}
-Then
-
-{\color{blue}ok?}where we used $
-\sum_{i=1}^Ne_{ii}^{tot}=L$. 
-\end{comment}
+
 \item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$
-%\begin{equation}
-%	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
-%\end{equation}
-%where the coefficients
+
 \begin{equation}\label{a2lp}
@@
 \end{equation}
-%\begin{equation}\label{a2lm1}
-%	\begin{split}
-	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=1\,:\,j\neq i}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
-	%	&=e_{11}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\
-	%	%&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
-		%&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
-%		&=e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=1}^{N-1}e_{ij}^{[a]}e_{ji}^{[b]}\\ 
-%	\end{split}
-%\end{equation}
-
-%We rewrite
-%\begin{equation}
-%	\begin{split}
-	%	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=1}^{N%-1}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
-%	\end{split}
-%\end{equation}
-%then
-%\begin{equation}
-%	\begin{split}
-%		D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}%=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}
-%	\end{split}
-%\end{equation}
-
-%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
-%\begin{equation*}
-%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
-%\end{equation*}
-%where
-%\begin{equation*}
-%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
-%\end{equation*}
-%This gives exactly
-%\begin{equation*}
-%	D_{22}^{2L-1}=\left(
-%	\begin{array}{ccccccccc}
-%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
-%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
-%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
-%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
-%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
-%	\end{array}
-%	\right)
-%\end{equation*}
-%}
-%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
-%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
-%\begin{equation}
-%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
-%\end{equation}
-%where the coefficient is
-%\begin{equation}\label{c}
-%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
-%\end{equation}
+
 \item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
@@
 \end{equation}
-\begin{comment}
-\begin{equation}
-B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
-\end{equation}
-where the coefficient is 
-\begin{equation}\label{b}
-\begin{split}
-B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
-&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
-\end{split}
-\end{equation}
-then
-\begin{equation}
-\begin{split}
-B_{j}^{2L-1}=2e_{j1}^{tot}+
-2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
-\end{split}
-\end{equation}
-\begin{equation}
-\begin{split}
-B_{j}^{2L-1}&=
-2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
-%	&=
-%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
-\end{split}
-\end{equation}
-Thus
-\begin{equation}
-\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
-\end{equation}
-\end{comment}
+
 \item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
@@
 \end{itemize}
-\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
-The interesting charges (we only look for the first non trivial one) take the following form
+\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
+Using these polynomial expansions we write the first three charges
 
@@
 The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
-It is easy to show that 
+By construction it follows that 
 \begin{equation}
@@
 \end{equation}
-that is 
-%\begin{equation}
-%\begin{split}
-%Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
-%\end{split}
-%\end{equation}
+that is, using the coefficients previously computed, 
 \begin{equation}\label{Q0Exp}
@@
 \end{equation}
-%\begin{equation}	
-%\begin{split}
-%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
-%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
-%\end{split}
-%\end{equation} 
+
 We also introduce 
@@
 Indeed, can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
-We denote it by $\hat{C}_{2}$ and it reads
+We denote it by $\hat{C}_{2}^{N-1}$ and it reads
 \begin{equation}
@@
 We denote its eigenvector by $C_{2}^{N-1}$.
-On the Bethe states (and on the irrep decomposition of the spin chain) it acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
+On the Bethe states (and on the decomposition into irreducible representation of the spin chain) it acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
 \begin{equation}
@@
 We use the following series expansion
-\begin{equation}\label{veryUsefulSeries}
+\begin{equation}
 	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
@@
 Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains ($N>2$). Repeating the computations we find that 
-\begin{equation}\label{W-extended}
+\begin{equation}
 	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
@@
 \\=&
-\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}(Q_{0}^{2L})^{n}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
+\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}(Q_{0}^{2L})^{n}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle
 \end{align}

### 2023-09-11 main.tex
yui

@@
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
-\section{Mapping to equilibrium}
+\section{Mapping to equilibrium} \label{Section-Mapping}
 check also Appendix A in
@@
 \begin{align}
-Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
-Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
+Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
+\end{align}
+\begin{align}
+Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
+\end{align}
+\begin{align}
 Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
@@
 \end{equation} 
-Thus the difference is of order $2L$ and becomes
+Thus the following difference is of order $2L$
 \begin{equation}
@@
 \end{equation} 
-By taking the limit we obtain
+In the following it will be useful to compute the quantity 
 \begin{equation}
@@
 \end{equation}
-{\color{blue}Using them we also have 
-\begin{equation}
-\begin{split}
-	&Q_{0}^{2L}B_{1}^{2L-1}Q_{0}^{2L}B_{2}^{2L-1}\\=&B_{1}^{2L-1}B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{22}^{2L}+2D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right.\\-&\left.2B_{1}^{2L-1}B_{1}^{2L-1}D_{12}^{2L}-2B_{2}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)\left(Q_{0}^{2L}-2(D_{22}^{2L}+D_{33}^{2L})\right)
-	\\&+
-	\left(-2B_{1}^{2L-1}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right)+8B_{1}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)D_{12}^{2L}
-\end{split}
-\end{equation}}{\color{blue}Probably it is not useful}
+%{\color{blue}Using them we also have 
+%\begin{equation}
+%\begin{split}
+	%&Q_{0}^{2L}B_{1}^{2L-1}Q_{0}^{2L}B_{2}^{2L-1}\\=&B_{1}^{2L-1}B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{22}^{2L}+2D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right.\\-&\left.2B_{1}^{2L-1}B_{1}^{2L-1}D_{12}^{2L}-2B_{2}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)\left(Q_{0}^{2L}-2(D_{22}^{2L}+D_{33}^{2L})\right)
+	%\\&+
+	%\left(-2B_{1}^{2L-1}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right)+8B_{1}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)D_{12}^{2L}
+%\end{split}
+%\end{equation}}{\color{blue}Probably it is not useful}
 \subsection{Conserved charges form of W}
 By using the QISM results found in the previous section it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system.
-This is possible because , thanks to integrability
-\begin{equation}
-	[H,T(x)]=0
+This is possible because, thanks to integrability
+\begin{equation}
+	[H^{''},T(x)]=0
 \end{equation}
@@
 \end{equation}
-Arguing as in section \ref{SectionNonLocalTrasformation}, we can show that 
+Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$, one can show that 
 \begin{equation}\label{WInCharges}
@@
 \end{equation}
-Since $Q^{2L}$ and $H$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones.
-The advantage is that now we can do more with this more with this expression.
-Hopefully, using exchange relation between charges, we could try to handle \eqref{WInCharges} and rewrite it independently from the equilibrium eigenvectors.
+Since $Q^{2L}$ and $H^{''}$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones.
+The advantage is that now we can do more with the above expression.
+Hopefully, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form, independently from the equilibrium eigenvectors.
 Moreover, we can use it to extract the steady state by rising the vacuum state.
+We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$.
 \subsection{The gl(2) case}
+In the case of $gl(2)$ we have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
+\begin{equation}\label{Nice-W2}
+	\begin{split}
+		|\Psi^{''}\rangle=W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}\frac{\Delta^{k}}{k!}\left(\frac{B_{1}^{2L-1}}{2}\right)^{k}\frac{\Gamma(\sigma_{0}^{tot}+2-k)}{\Gamma(\sigma_{0}^{tot}+2)}|\Psi_{m}^{0}\rangle
+	\end{split}
+\end{equation}
+where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix. \\
+Observe that, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state 
+\begin{equation}
+	|\Psi_{0}^{0}\rangle=\underbrace{\begin{pmatrix}
+		0\\1
+	\end{pmatrix}\otimes \ldots\otimes \begin{pmatrix}
+	0\\
+	1
+\end{pmatrix}}_{\text{L-times}}
+\end{equation} we retrieve the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N=2$. \\
+Equation \eqref{Nice-W2} gives an explicit formula in term of the charge $B_{1}^{2L-1}$ of the matrix $W$.
+We stress the fact that these nice formula comes from the simple commutation relations between charges.
+\eqref{Nice-W2} was found with different arguments and up to some constants also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}.
+\subsubsection{Proof of formula \eqref{Nice-W2}}
 In this simpler situation the double row monodromy reads
@@
 \end{equation}
-Therefore, using the conserved charges and formula \eqref{WInCharges} we have
+Using \eqref{Q-nonDiag} we rewrite \eqref{WInCharges} as
 \begin{equation}\label{W}
@@
 \end{equation}
-Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and
+Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ we obtain 
 \begin{equation}\label{LinkWG}
@@
 		(Q_{0}^{2L}B_{1}^{2L-1})^{k}&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+\mathbbm{1}_{\{j>1\}}4\sum_{i=1}^{j-1}(j-i)Q_{0}^{2L+2}\right)\\
-		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+2j(j-1)N\right)\\
-		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+2j(j-1)N\right)
-	\end{split}
-\end{equation}
-We use the following series expansion
+		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)N\right)\\
+		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)
+	\end{split}
+\end{equation}
+Recalling series expansion defined in \eqref{veryUsefulSeries}
 \begin{equation}
@@
 \end{equation}
-We obtain
-\begin{equation}
+we obtain 
+\begin{equation}
+	\begin{split}
+		\left\{(\Lambda_{m}+\epsilon-Q_{0}^{2L})^{-1}B_{1}^{2L-1}\right\}^{k}
+		=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(\Lambda_{m}+\epsilon-Q_{0}^{2L}+4j(1+e_{11}^{tot}-e_{22}^{tot})-4j(j-1)\right)^{-1}
+	\end{split}
+\end{equation}
+Therefore we have that 
+\begin{equation}\label{intermediate-Wgl2}
 	\begin{split}
@@
 \end{equation}
-where we used \eqref{exchangeQ0B}.
-We now need the exchange relations between $\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}$ and $B^{2L-1}$.
-They follow from \eqref{exchangeQk} and by observing that
-\begin{equation}
-	\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(A^{2L}+D_{1,1}^{2L})\right)\right)^{-1}=\sum_{n=0}^{\infty}(\Lambda_{m}^{Q}+\epsilon)^{-1-n}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}
-\end{equation}
-Finally we obtain 
+By replacing \eqref{intermediate-Wgl2} in \eqref{LinkWG}, we obtain 
 \begin{equation}\label{GoodBleft}
@@
 \end{equation}
-Using again \eqref{veryUsefulSeries} and re-summing we obtain 
+Using again \eqref{veryUsefulSeries} and re-summing the series we obtain 
 \begin{equation}
@@
 \end{equation}
-Finally, using again the property of $e_{11}^{tot}$ and $e_{22}^{tot}$ and using the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain 
-\begin{equation}\label{Nice-W2}
-	\begin{split}
-		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}\frac{\Delta^{k}}{k!}\left(\frac{B_{1}^{2L-1}}{2}\right)^{k}\frac{\Gamma(\sigma_{0}^{tot}+2-k)}{\Gamma(\sigma_{0}^{tot}+2)}|\Psi_{m}^{0}\rangle
-	\end{split}
-\end{equation}
-This gives an explicit formula in term of the charge $B_{1}^{2L-1}$ of the matrix $W$.
-We stress the fact that these nice formula comes from the simple commutation relations between charges.
-Moreover, with such a formula it has been proved in \cite{frassek2020eigenstates} that the steady state $|\Psi^{''}\rangle$ can be found by acting on the vacum.
+Finally, using the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain \eqref{Nice-W2}. 
+\begin{flushright}
+	$\square$
+\end{flushright}
 \subsection{The gl(N) case}
-Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains ($N>2$). Repeating the computations we find that 
-\begin{equation}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-Using the fact that $\left[H^{'},Q^{2L}\right]=0$ we can determine the matrix $W$ in function of the first non-trivial conserved charge $Q^{2L}$ as
-\begin{equation}
-	\begin{split}
-		W&= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}-\mathcal{Q}_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation}
- Recalling the expression of $\mathcal{Q}^{2L}$ given in \eqref{Q-nonDiag} we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
+In the general case of $N>2$ species we have that \eqref{WInCharges} reads 
+\begin{equation}\label{W-charges-Bad}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation}
+Indeed, since the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
+\begin{equation}
+	-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}
+\end{equation}
+that gives rise to a proliferation of terms that does not vanish, thus only part of the argument done in the $N=2$ case can be followed.
+However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the steady state can be written, since when acting on the vacuum the exchange relations do remain simple.
+\paragraph{Proof of formula \eqref{W-charges-Bad}}
+Following the result in the simpler $gl(2)$ case, we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
 We obtain that, using also the multi-variate version of \eqref{veryUsefulSeries},
@@
 \end{equation}
-By denoting with 
-\begin{equation}\label{definitionA}
-	A_{i_{j}}=\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{i_{j}}^{2L-1}\right\}
-\end{equation}
-then 
-\begin{equation}
-	\begin{split}
-&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\=&
-SYM_{k_{1},\ldots,k_{N-1}}\left(A_{1},\ldots,A_{N-1}\right)\\
-=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}
-	\end{split}
-\end{equation}
-where $Sym$ is the symmetric group. 
-We further observe that in the limit for $\epsilon\to 0$ the quantity 
+We define
+\begin{equation}
+	\begin{split}
+&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
+=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}
+	\end{split}
+\end{equation}
+where $Sym$ is the symmetric group. \\
+Observing that 
 \begin{equation}
@@
 \end{equation}
-therefore we have that 
-\begin{equation}\label{W-charges-Bad}
+we finally have 
+\begin{equation}
 	\begin{split}
@@
 \end{equation}
-In this case, the commutation relations between $Q_{0}^{2L}$ and $B_{i}^{2L-1}$ are given by \eqref{ExQ0B-charges}.
-Exchanging $Q_{0}^{2L}$ with $B_{i}^{2L-1}$ generates also charges $B_{j}^{2L-1}$ with $j\neq 1$.
-Therefore, it is hard to obtain the multivariate equivalent of \eqref{Nice-W2}.
-\subsection{Non-equilibrium steady state from the W transformation}
-By using $W$ it is possible to obtain all the non-equilibrium eigenvectors by the knowledge of the equilibrium ones.
-As a consequence, also the non-equilibrium steady state can by found by using $W$.
-For the $N=2$ chain, this property has been proved in \cite{frassek2020eigenstates}.
-Also for the $gl(N)$ case, we can retrieve the non-equilibrium steady state of the Hamiltonian $H^{''}$ given in \eqref{ResulsBasis}, by acting with $W$ on the vacuum state
+\begin{flushright}
+	$\square$
+\end{flushright}
+\subsection{Non-equilibrium steady state from the W transformation}\label{subsection-NONSS-W}
+Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by actin with $W$ on the vacuum state 
 \begin{equation}\label{Vacuum-state}
@@
 \end{equation} 
-Therefore, we have that 
+This steady state reads 
 \begin{equation}\label{SteadyState-W-Good}
@@
 \textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
-Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult and we cannot rewrite \eqref{W-charges-Bad} in such a simpler form.
+Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult and we cannot rewrite \eqref{W-charges-Bad} in such a simple form.
 \subsubsection{Proof of \eqref{SteadyState-W-Good}}
@@
 \cite{Belliard2} 
-\section{Extensions}
-\subsection{The non integrable chain}
-In Section \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
+\section{Extensions for the non-integrable chain}
+In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
 This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations.
 Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+Moreover, the thermalized process can be studied, by finding the thermalization measure and the dual-thermalized process.
+Finally, a reaction can be added by conserving the same duality function.
 \subsection{Steady state correlations and duality}
-We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads as
+We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads
 \begin{equation}
@@
  \begin{equation}	
-	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}
+	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N-1}
 \end{equation}
@@
 	\begin{split}
-		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
+		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
 	\end{split}
@@
 \begin{equation}\label{dualityFunctionChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
 \end{equation}
@@
 		\\=&
-		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
+		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
 	\end{split}
@@
 \begin{equation}\label{Pass}
-	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
+	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
 \end{equation}
 where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
-\begin{equation}
-	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{2,\ldots,N\}$ situated at sites $y_{i}\in\{1,\ldots,L\}$ with $i\in \{1,\ldots,m\}$.
-This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
+Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$ $\forall x\in \{1,\ldots,m-1\}$ and $s_{x}\in \{1,\ldots,N-1\}$ $\forall x=\{1,\ldots,m\}$ is given by
+\begin{equation}
+	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{a}}^{y_{x}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$.
+This expectation is computed by \eqref{ExptationSS} once the absorption probabilities is known.
 The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.

### 2023-09-11 main.tex
lkj

@@
 \section{Extensions for the non-integrable chain}
-In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
-This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations.
-Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
-Moreover, the thermalized process can be studied, by finding the thermalization measure and the dual-thermalized process.
-Finally, a reaction can be added by conserving the same duality function.
-\subsection{Steady state correlations and duality}
+The aim of this section is studying some extension to the analysis previously done when integrability property is lost. 
+In particular, Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
+This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$. For the sake of simplicity we still study the geometry of chain and we provide the following extensions: 
+\begin{enumerate}
+	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+These probability are hard to find in this partial exclusion situation, however correlation can be formally written.
+Subsection \ref{Subsection-ss-nonI}.
+	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we can define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+Subsection \ref{Subsection-Thermalized}.
+	\item \textit{Reaction-diffusion process}: a further dynamics is added.
+Particle can now change type.
+The model is constructed with the goal of having the average density evolving a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+Subsection \ref{Subsection-RD}
+\end{enumerate}
+
+\subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}
 We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads
@@
 \end{equation}
-The dual generator is 
+whit dual generator
 \begin{equation}
@@
 where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
+The dual process has absorbing boundaries, i.e.
+all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
+This implies that, the chain is eventually void and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following.
+We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+We assume that it is initially distribute with a configuration $\bm{n}$.
+For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m-1\}$.
+The following chain of equalities holds
 \begin{equation}\label{ExptationSS}
 	\begin{split}
-		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\=&
-		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
+		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
 	\end{split}
@@
 \begin{equation}\label{Pass}
-	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
-\end{equation}
-where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$ $\forall x\in \{1,\ldots,m-1\}$ and $s_{x}\in \{1,\ldots,N-1\}$ $\forall x=\{1,\ldots,m\}$ is given by
-\begin{equation}
-	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{a}}^{y_{x}}}{(\nu-m+1)}
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$.
+\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi_{0}}=\hat{\bm{\xi}}\right)
+\end{equation}
+and where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
+Here, we denote by $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\hat{\xi}_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
+\begin{equation}
+	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{a}}^{y_{x}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$.
 This expectation is computed by \eqref{ExptationSS} once the absorption probabilities is known.
-The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
+The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve.
 For example, we report here the solution for the one points correlations.
 \paragraph{One point correlations for the non-integrable case}
-We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
+We have that $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}
 \end{equation}
@@
 	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
-	\end{split}
-\end{equation}
-we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
-Therefore, this $a_{s}^{x}(1)$ fulfils the following equations
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+	\end{split}
+\end{equation}
+we want to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
+Therefore, this $\mathcal{P}(1,\delta_{s}^{y})$ fulfils the following equations
 \begin{equation}\label{gamblers-ruin}
 	\begin{cases}
-		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
-		a^{1}_{s}(1)=\frac{|\alpha|}{1+|\alpha|}+a^{2}_{s}(1)\frac{1}{1+|\alpha|}\\
-		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+|\beta|}
+		\Delta_{x}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
+		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
+	\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
 	\end{cases}
 \end{equation}
-where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where.
-The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
+where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$.
+The equations \eqref{gamblers-ruin} can be solved.
+Therefore, using \eqref{OnePtsCORR} and $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
 \begin{equation}
@@
 that gives back \eqref{one-pts-corr}.
-\subsection{Instantaneous thermalization}
+\subsection{Instantaneous thermalization}\label{Subsection-Thermalized}
 In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}).
@@
 \begin{equation}
-	\epsilon_{1}=2\nu-\sum_{a=2}^{N}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=2}^{N}r_{a}
+	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=1}^{N-1}r_{a}
 \end{equation}
@@
 	\begin{split}
-	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}
+	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
 	\\&
@@
 	\begin{split}
-		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
-		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
 		\end{split}
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-The proof of the duality consists in proving 
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+The proof of the duality consists in showing
 \begin{align}
@@
 \begin{equation}
-	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
 \end{equation}
@@
 \begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
 	\\&\nonumber
-	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
-\end{align}
-Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+\end{align}
+Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
 	\\&\nonumber
-	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\\=&
-	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
-\end{align}
-Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
+	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu-\xi_{k}^{1}+\xi_{k}^{1}-r_{a}+r_{a}}\\=&
+	\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
+\end{align}
+Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
 \begin{equation}\label{pezzo2}
 	\begin{split}
-	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
+	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
 	\end{split}
@@
 \begin{align}
-	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&=
@@
 \end{align}
-\subsection{Multi-species stirring process with reaction}
+\subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
 In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{2,3\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.

### 2023-09-12 main.tex
lkj

@@
 \end{align}
-Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
+We consider the first addend in the curly bracket of the previous equation.
+We multiplying it by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$ and by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}$ and we have
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
-	\\&\nonumber
-	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu-\xi_{k}^{1}+\xi_{k}^{1}-r_{a}+r_{a}}\\=&
-	\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
-\end{align}
-Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
+	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
+	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber
+	\\=&
+	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
+\end{align}
+where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.
+We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ 
 \begin{equation}\label{pezzo2}
@@
 \end{equation}
-Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
+where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
 \begin{align}
@@
 The aim of this section is to give an answer to these questions.
-We first define a more general process with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with N discrete Laplacians and a reaction term.
+We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term.
 Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
 \subsection{The process on a finite graph}
-Considering again a finite and connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator
+We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at left of site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at right of site $L$.
+The generator reads
 \begin{equation}\label{RDGenerator}
-	\mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}
+	\mathcal{L}^{rd}=+\mathcal{L}_{right}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{right}^{rd}
 \end{equation}
@@
 \begin{equation}\label{edgeGeneratorRD}
-	\mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
-\end{equation}
-with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
-\begin{equation}
-	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right)
+	\mathcal{L}_{x,x+1}^{rd}=\sigma_{11}\mathcal{L}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,x+1}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,x+1}^{m}
+\end{equation}
+with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
+\begin{equation}
+	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
 \end{equation}
@@
 	g_{c}(k)=\begin{cases}
-		k+c \quad &\text{if}\quad k+c\leq N\\
-		k+c-N+1\quad &\text{if}\quad k+c>N\\
-		1\quad &\text{if}\quad k=1
+		k+c \quad &\text{if}\quad k+c< N \\
+		k+c-N+1\quad &\text{if}\quad k+c\geq N,\quad k\neq N\\
+		1\quad &\text{if}\quad k=N
 	\end{cases}
@@
 \begin{equation}
-	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{left}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 	\begin{split}
-		\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
-		\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}
+		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}
 	\end{split}
@@
 \end{equation}
-\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
-We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above.
+The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s. \\ \\
+\textbf{Remark}: observe that the site generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}$, as specified above.
 \paragraph{Action on the occupation variable of $\mathcal{L}_{x,y}^{rd}$}
-For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads
+For arbitrary site $x\in \{1,\ldots,L\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
 \begin{equation}\label{actionGraphRD}
 	\begin{split}
-		\mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
-	\end{split}
-\end{equation}
-
+		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
+	\end{split}
+\end{equation}
 Indeed
 \begin{equation}
-	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)
+	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
-		\\&=
-		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
-		\\&=
-		\nu(n_{q}^{y}-n_{d}^{x})
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
+		\\&=
+		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{x+1}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{x+1}\right)
+		\\&=
+		\nu(n_{q}^{x+1}-n_{d}^{x})
 	\end{split}
@@
 Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action on the occupation variable of $\mathcal{L}_{x}^{rd}$}
-Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain
+\paragraph{Action on the occupation variable of $\mathcal{L}_{left}^{rd}$}
+Acting on $n_{d}^{1}$  with $\mathcal{L}_{left}^{rd}$ we obtain
 \begin{equation}\label{actionBoudaryRD}
 	\begin{split}
-		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
-		\\&=
-		\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
-		\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\mathcal{L}_{left}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
+		\\&=
+		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
+		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
 		\\=&
-		\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
-	\end{split}
-\end{equation}
-\subsection{The process on a chain}
-Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$.
-This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\
+		\nu\sigma_{11}\rho_{d}^{L}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{1}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+	\end{split}
+\end{equation}
 Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
@@
 This answers the first question of the beginning of this section.
-\subsection{Reversible measure} 
+
+\subsubsection{Reversible measure for the reaction-diffusion process} 
 The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
-	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}
+	\Lambda_{rev}=\bigtimes_{x=1}^{L}\Lambda_{rev}^{x}
 \end{equation}
@@
 \begin{equation}\label{reversibilityConditionRD}
-	\alpha_{a}^{x}=\alpha_{a}\quad \forall x\in V\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{2,\ldots,N\}
+	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}
 \end{equation}
@@
 \begin{equation}
-	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{2,\ldots,N\}\qquad \text{and}\qquad \rho_{1}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}
+	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}
 \end{equation}
@@
 \begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho_{1}^{n_{1}^{x}}\rho^{\sum_{a=2}^{N}n_{a}^{x}}
-\end{equation}
-This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
-For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
-\begin{equation}
-	\begin{split}
-		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{1}^{n_{1}^{x}}
+\end{equation}
+This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundary generators.
+For fixed edge $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators the computation is similar.
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$; the detailled balance reads
+\begin{equation}
+	\begin{split}
+		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}
 		\\
-		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}
+		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
 		\\&
-		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}
+		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{x+1}}
 	\end{split}
@@
 that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{2,\ldots,N\}$.\\
-By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,y}$.
+By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,x+1}$.
 \\
-For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$.
+For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$.
 As a consequence we have the result.
-\subsection{Duality}
+\subsubsection{Duality for the reaction-diffusion process}
 In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
@@
 \begin{equation}
-	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
-\end{equation}
-To each site $x\in V$ we associate an ``extra site'', denoted $u(x)$,
+	\widetilde{\Omega}=\mathbb{N}_{0}^{N-1}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N-1}
+\end{equation}
+To sites $1,L$ we associate an ``extra site'', denoted by $0$ and $L+1$ respectively,
 where dual particles will accumulate in the course of time. 
@@
 \begin{equation}
-	\bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
+	\bm{\xi}=\left(\xi_{2}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{2}^{L+1},\ldots,\xi_{N}^{L+1}\right)
 \end{equation}
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 
-the extra-site $u(x)$ connected to $x\in V$.
-
+and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
+the extra-site $0$ connected to $1$ and similarly for $xi_{a}^{L+1}$. \\
 The duality function is given by
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{u(x)}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{u(x)}}
 \end{equation}
@@
 \begin{equation}\label{DualGeneratorRD}
-	\widetilde{\mathcal{L}}^{rd}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}
+	\widetilde{\mathcal{L}}_{left}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{right}^{rd}
 \end{equation}
 where 
-$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}.
+$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator} and specialized for sites $x=1$ and $x=L$.
 \newline
@@
 \begin{equation}
-	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}\mathcal{H}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
-\end{equation}
-where $\mathcal{H}_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
-\begin{equation}
-	\mathcal{H}_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)
+	H^{rd}=H_{left}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{right}
+\end{equation}
+where $\mathcal{H}_{x,x+1}$ and $H_{left},H_{right}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
+\begin{equation}
+	\mathcal{H}_{x,x+1}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}\otimes E_{g_{c}(b)a}-E_{aa}\otimes E_{bb}\right)
 \end{equation}
@@
 \begin{equation}
-	\mathcal{H}_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
+	\mathcal{H}_{x,x+1}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}\otimes \mathbbm{1}-E_{aa}\otimes \mathbbm{1}\right)
 \end{equation}
 Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$.
-For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
+For the edge dynamics, the original and the dual Hamiltonians do coincide, while the boundary ones are again $\widetilde{H}_{left},H_{right}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
 \begin{equation}\label{DualityRelationRD}
@@
 \end{equation}
-Therefore, we need to prove that
+Therefore, we need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
 \begin{align}
-	(\mathcal{H}_{x,y}^{rd})^{T}D&=D\mathcal{H}_{x,y}^{rd}\label{edgeDualityRelationRD}\\
-	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
-\end{align}
-where the duality matrix $D$ is again \eqref{dualityMatrix}.
-As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $\mathcal{H}_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$.
+	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}\\
+	H_{left}^{T}D&=D\widetilde{H}_{left}D\label{siteDualityRelationRD}
+\end{align}
+and similarly for $H_{right}$.
+The duality matrix $D$ is again \eqref{dualityMatrix}.
+As already pointed out, $H_{left}$ and $\widetilde{H}_{left}$ have the same structure (up to a specific choice of the reservoirs parameters) therefore the duality relation for the boundaries is proved.
+However, $\mathcal{H}_{x,x+1}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$.
 Therefore, we only need to show that
 \begin{align}
-	&(\mathcal{H}_{x,y}^{c})^{T}D=D\mathcal{H}_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
-	&(\mathcal{H}_{x,y}^{m})^{T}D=D\mathcal{H}_{x,y}^{m}\label{mDualityRelation}
-\end{align}
-Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$ have $\exp{(E^{x})}\exp{(E^{y})}$ as a symmetry.
-The first result will follow from the commutator between $\mathcal{H}_{x,y}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
+	&(\mathcal{H}_{x,x+1}^{c})^{T}D=D\mathcal{H}_{x,x+1}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
+	&(\mathcal{H}_{x,x+1}^{m})^{T}D=D\mathcal{H}_{x,x+1}^{m}\label{mDualityRelation}
+\end{align}
+Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x})}$ as a symmetry.
+The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
 \begin{align*}
-	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{y}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{y} -E_{aa}^{x}\otimes E_{bb}^{y}\right)\right]
+	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{x+1}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{x+1} -E_{aa}^{x}\otimes E_{bb}^{x+1}\right)\right]
 	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{y}\delta_{a1}-E_{a1}^{y}\delta_{da})\right)\right.
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{x+1}\delta_{a1}-E_{a1}^{x+1}\delta_{da})\right)\right.
 \\ \otimes&\left.
-\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{y}\delta_{kb})-(E_{kb}^{y}\delta_{b1}-E_{b1}^{y}\delta_{kb})\right)\right\}
+\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{b1}-E_{b1}^{x+1}\delta_{kb})\right)\right\}
 	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{y}-E_{g_{c}(a)1}^{y}-E_{kb}^{y}+E_{b1}^{y}\right)\right\}
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)1}^{x+1}-E_{kb}^{y}+E_{b1}^{x+1}\right)\right\}
 	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{y}-E_{g_{c}(a)1}^{y}\right)\right\}
+	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{x+1}-E_{g_{c}(a)1}^{x+1}\right)\right\}
 	\\=&0
@@
 where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
-The second result will follow from the commutator between $\mathcal{H}_{x,y}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
-\begin{equation}
-	\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)\right]=0
+The second result will follow from the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
+\begin{equation}
+	\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{x+1}-E_{aa}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0
 \end{equation}
@@
 With this prove we answered the second and third questions stated at the beginning of this section. \\
-\textbf{FROM HERE ON-WARDS STILL TO CHECK}\\
 \begin{comment}

### 2023-09-13 main.tex
asd
jll
ffg
1 to N

@@
 \noindent
-{\bf Remark:} in the following we will often consider type $1$ as a distinguished type
+{\bf Remark:} in the following we will often consider type $N$ as a distinguished type
 (called `holes'), whose number at each site is fixed by the numbers of particles 
-of the remaining $N-1$ types (at the same site). It is interesting to observe that, in case we stop distinguishing the colors of the ``true'' particles of types $\{2,\ldots,N\}$, we retrieve the 
+of the remaining $N-1$ types (at the same site). It is interesting to observe that, in case we stop distinguishing the colors of the ``true'' particles of types $\{1,\ldots,N-1\}$, we retrieve the 
 boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
-The choice of type $1$ for the distinguished type is arbitrary and does not affect
+The choice of type $N$ for the distinguished type is arbitrary and does not affect
 the results. In particular, we shall see in Section \ref{sectionDuality} about duality, that
-the dual process eventually has only particles of type $1$ on the graph.
-Interpreting type $1$ as an hole, one can then say that the dual process voids the graph.
+the dual process eventually has only particles of type $N$ on the graph.
+Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.
 
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
 \end{equation}
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=2}^{N}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{1}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{1}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)
 \end{equation}
@@
 On the other hand, the site
-part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $a$ at the extra-site $u(x)$.
+part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{2,\ldots,N\}$ at site $x$ with a particle of type $N$ and creates a particle of the same type $a$ at the extra-site $u(x)$.
 This last transition is performed with rate $|\alpha^{x}|\xi_{a}^{x}$.
-This means that eventually the dual process voids the graph, putting all the dual particles of species $\{2,\ldots,N\}$ in the extra-sites.
+This means that eventually the dual process voids the graph, putting all the dual particles of species $\{1,\ldots,N-1\}$ in the extra-sites.
 In other words the extra-sites play the role of absorbing boundaries.
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=2}^{N}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
 \end{equation}
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{u(x)}\,E_{1a}^{x}-E_{aa}^{x}\right)
+    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)
 \end{equation}
 Here we introduced bosonic creation operator $a^{\dagger}$ acting on the left-hand-side as $\langle q|a^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(a^{\dagger})_{a}^{u(x)}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{2,\ldots,N\}$. \\
+$(a^{\dagger})_{a}^{u(x)}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
 We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. The duality matrix $D$ is described as 
@@
 \begin{equation}\label{EquationEx}
-E^{x}=\sum_{a=2}^{N}E_{a1}^{x}
+E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}
 \end{equation}
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
 \begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
 	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
@@
 \begin{align*}
-\sum_{q_{2}^{u(x)},\ldots,q_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
+\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
 \end{align*}
@@
 \begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{2}=0}^{\infty}\frac{\left\{\left(E_{12}^{x}\right)^{T}\right\}^{k_{2}}}{k_{2}!}\ldots\sum_{k_{N}=0}^{\infty}\frac{\left\{\left(E_{1N}^{x}\right)^{T}\right\}^{k_{N}}}{k_{N}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 \\&
@@
 \\&=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|
+\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
 \\&
-\hspace{2.cm}\prod_{a=2}^{N}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
-\\&=
-\sum_{k_{2}=0}^{n_{1}^{x}}\ldots\sum_{k_{N}=0}^{n_{N}^{x}}\langle n_{1}^{x}+k_{2}+\ldots+k_{N},n_{2}^{x}-k_{2},\ldots,n_{N}^{x}-k_{N}|\frac{n_{2}^{x}!\ldots n_{N}^{x}!}{(n_{2}^{x}-k_{2})!\ldots(n_{N}^{x}-k_{N})!}
+\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\\&=
+\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\ldots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\ldots(n_{N-1}^{x}-k_{N-1})!}
 \\& 
-\hspace{2.cm}\qquad\frac{1}{k_{2}!,\ldots,k_{N}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
-\\&=
-\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+\hspace{2.cm}\qquad\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\\&=
+\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
 \end{align*}
-where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $\xi_{1}^{x}=\nu-\sum_{a=2}^{N}\xi_{a}^{x}$.
+where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$.
 Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
@@
 Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$.
-As we will see, this symmetry is $\sum_{a=2}^{N}E_{a1}$ \\
+As we will see, this symmetry is $\sum_{a=1}^{N-1}E_{a1}$ \\
 We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain
@@
 \begin{equation}
-	E=\sum_{a=2}^{N}E_{a1}
+	E=\sum_{a=1}^{N-1}E_{a1}
 \end{equation}
@@
  \end{equation}
-In the following we need the application of the Hadamard formula with $B=\sum_{a=2}^{N}E_{a1}$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
+In the following we need the application of the Hadamard formula with $B=\sum_{a=1}^{N-1}E_{a1}$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
 Therefore we compute
 \begin{enumerate}
-    \item for $A=E_{b 1}$ with $b\in \{2,\ldots,N\}$, we obtain 
+    \item for $A=E_{b N}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
     \begin{equation}\label{HT_El1}
-        \exp{(-E)}E_{b 1}\exp{(E)}=E_{b 1}
+        \exp{(-E)}E_{b N}\exp{(E)}=E_{b N}
     \end{equation}
     because $E_{b 1}$ commutes with $E$
-    \item for $A=E_{bb}$ with $b \in \{2,\ldots,N\}$, we obtain 
+    \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
     \begin{equation}\label{HT_Ell}
-        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b 1}
+        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b N}
     \end{equation}
@@
     \begin{equation}
-       \left[E, E_{bb}\right]=\sum_{a=2}^{N}\left(E_{ab}\delta_{b 1}-E_{b 1}\delta_{ab}\right)=-E_{b1}
+       \left[E, E_{bb}\right]=\sum_{a=1}^{N-1}\left(E_{ab}\delta_{b N}-E_{b N}\delta_{ab}\right)=-E_{bN}
     \end{equation}
     Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
-    \item for $A=E_{1b}$ with $b\in \{2,\ldots,N\}$, we obtain 
+    \item for $A=E_{Nb}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
     \begin{equation}\label{HT-E1l}
-        \exp{(-E)}E_{1 a}\exp{(E)}=E_{1a}+E_{11}-\sum_{c=2}^{N}\left(E_{c1}+E_{ca}\right)
+        \exp{(-E)}E_{N a}\exp{(E)}=E_{Na}+E_{NN}-\sum_{c=1}^{N-1}\left(E_{cN}+E_{ca}\right)
     \end{equation}
@@
     \begin{equation}
-[E,E_{1a}]=\sum_{c=2}^{N}\left(E_{ca}\delta_{11}-E_{11}\delta_{ca}\right)= (\sum_{c=2}^{N}E_{ca} ) -E_{11};
+[E,E_{Na}]=\sum_{c=1}^{N-1}\left(E_{ca}\delta_{NN}-E_{NN}\delta_{ca}\right)= (\sum_{c=1}^{N-1}E_{ca} ) -E_{NN};
 \end{equation}
@@
 \begin{split}
-\left[E,[E,E_{1a}]\right]&=\sum_{d=2}^{N}\sum_{c=2}^{N}\left[E_{d1},E_{ca}\right]-\sum_{d=2}^{N}\left[E_{d1},E_{11}\right]
-\\&=
-\sum_{d,c=2}^{N}\left(E_{da}\delta_{c1}-E_{c1}\delta_{da}\right)-\sum_{d=2}^{N}\left(E_{d1}\delta_{11}-E_{11}\delta_{d1}\right)
+\left[E,[E,E_{Na}]\right]&=\sum_{d=1}^{N-1}\sum_{c=1}^{N-1}\left[E_{dN},E_{ca}\right]-\sum_{d=1}^{N-1}\left[E_{dN},E_{NN}\right]
+\\&=
+\sum_{d,c=1}^{N-1}\left(E_{da}\delta_{cN}-E_{cN}\delta_{da}\right)-\sum_{d=1}^{N-1}\left(E_{dN}\delta_{NN}-E_{NN}\delta_{dN}\right)
 \\=&
--2\sum_{c=2}^{N}E_{c1};
+-2\sum_{c=1}^{N-1}E_{cN};
 \end{split}
@@
 Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
-\item for $A=E_{ba}$ with $a,b \in \{2,\ldots,N\}$ we obtain 
+\item for $A=E_{ba}$ with $a,b \in \{1,\ldots,N-1\}$ we obtain 
 \begin{equation}\label{HT-Ekl}
-    \exp{(-E)}E_{a b}\exp{(E)}=E_{ba}+E_{b1}
+    \exp{(-E)}E_{a b}\exp{(E)}=E_{ba}+E_{bN}
 \end{equation}
@@
 \begin{equation}
-[E,E_{ba}]=\sum_{c=2}^{N}\left(E_{ca}\delta_{b1}-E_{b1}\delta_{c a}\right)=-E_{b1};
+[E,E_{ba}]=\sum_{c=1}^{N-1}\left(E_{ca}\delta_{b1}-E_{bN}\delta_{c a}\right)=-E_{bN};
 \end{equation}
 Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-Ekl}.
-\item for $A=E_{11}$ we obtain 
+\item for $A=E_{NN}$ we obtain 
 \begin{equation}\label{HT-E11}
-    \exp{(-E)}E_{11}\exp{(E)}=E_{11}-\sum_{a=2}^{N}E_{a1}
+    \exp{(-E)}E_{NN}\exp{(E)}=E_{NN}-\sum_{a=1}^{N-1}E_{aN}
 \end{equation}
@@
 \begin{align*}
-[E,E_{11}]=\sum_{c=2}^{N}\left(E_{c1}\delta_{11}-E_{1 1}\delta_{c1}\right)=\sum_{c=2}^{N}E_{c1};
+[E,E_{NN}]=\sum_{c=1}^{N-1}\left(E_{cN}\delta_{NN}-E_{NN}\delta_{cN}\right)=\sum_{c=1}^{N-1}E_{cN};
 \end{align*}
@@
     \\&=\nonumber
-    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{1a}^{x}+E_{11}^{x}-\sum_{c=2}^{N}(E_{c1}^{x})-\sum_{c=2}^{N}(E_{ca}^{x})-E_{11}^{x}+
-    \sum_{c=2}^{N}(E_{c1}^{x})\right)
+    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{Na}^{x}+E_{NN}^{x}-\sum_{c=1}^{N-1}(E_{cN}^{x})-\sum_{c=1}^{N-1}(E_{ca}^{x})-E_{NN}^{x}+
+    \sum_{c=2}^{N}(E_{cN}^{x})\right)
     \\&+\nonumber
-    \alpha_{1}^{x}\sum_{b=2}^{N}\left(E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)+\sum_{a=2}^{N}\sum_{b=2}^{N}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{b1}^{x}-E_{bb}^{x}-E_{b1}^{x}\right)
+    \alpha_{N}^{x}\sum_{b=1}^{N-1}\left(E_{bN}^{x}-E_{bb}^{x}-E_{bN}^{x}\right)+\sum_{a=1}^{N-1}\sum_{b=1}^{N-1}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{bN}^{x}-E_{bb}^{x}-E_{bN}^{x}\right)
     \\&=\nonumber
-    \sum_{a=2}^{N}\alpha_{a}^{x}E_{1a}^{x}-|\alpha^{x}|\sum_{b=2}^{N}E_{bb}^{x}=
-    \sum_{a=2}^{N}\left(\alpha_{a}^{x}E_{1a}^{x}-|\alpha^{x}|E_{aa}^{x}\right)
+    \sum_{a=1}^{N-1}\alpha_{a}^{x}E_{Na}^{x}-|\alpha^{x}|\sum_{b=1}^{N-1}E_{bb}^{x}=
+    \sum_{a=1}^{N-1}\left(\alpha_{a}^{x}E_{Na}^{x}-|\alpha^{x}|E_{aa}^{x}\right)
     \\&=\nonumber
-    |\alpha^{x}|\sum_{a=2}^{N}\left(\frac{\alpha_{a}^{x}}{|\alpha^{x}|}E_{1a}^{x}-E_{aa}^{x}\right)
-    \\&=
-    |\alpha^{x}|\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+    |\alpha^{x}|\sum_{a=1}^{N-1}\left(\frac{\alpha_{a}^{x}}{|\alpha^{x}|}E_{Na}^{x}-E_{aa}^{x}\right)
+    \\&=
+    |\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)
  \end{align}
@@
 \begin{equation}\label{HadTransfBoundary}
-\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)
 \end{equation}
@@
 \begin{equation}\label{siteHadamardI}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}|\alpha^{x}|\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)
 \end{equation}
@@
 \begin{equation}
-\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
     \begin{split}
-&H_{x}^{T}d_{x}\otimes\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+&H_{x}^{T}d_{x}\otimes\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \\=&
-d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}\right)
-    \end{split}
-\end{equation}
-Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{2,\ldots,N\}$ we have that 
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}\right)
+    \end{split}
+\end{equation}
+Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
 \begin{equation}\label{bosonicKX}
@@
 \end{equation}
-Using \eqref{bosonicKX} by a fixed $a\in \{2,\ldots,N\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{1a}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
-\begin{equation}
-    \begin{split}
-&\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}E_{1a}^{x}
+Using \eqref{bosonicKX} by a fixed $a\in \{1,\ldots,N-1\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+\begin{equation}
+    \begin{split}
+&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}E_{Na}^{x}
 \\=&
-\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{Na}^{x}
 \\=&
-\sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{1a}^{x}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{Na}^{x}
     \end{split}
@@
 H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
-     H_{x}^{T}d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
-\\&=
-d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=2}^{N}\left((a^{\dagger})_{a}^{u(x)}E_{1a}^{x}-E_{aa}^{x}\right)
-\\&=
-d_{x}\otimes \sum_{\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}=0}^{\infty}\prod_{a=2}^{N}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\widetilde{H}_{x}
+     H_{x}^{T}d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\\&=
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
+\\&=
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\widetilde{H}_{x}
 \\&=
@@
 \begin{equation}\label{ElementsDualityMatrixChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=2}^{N}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=2}^{N}\beta_{a}^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}
 \end{equation}
 Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
-Consider a dual configuration $\hat{\xi}:=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ where $a_{k}\in\{2,\ldots,N\}$ and $x_{k}\in\{1,\ldots,L\}$ for every $k\in\{1,\ldots,m\}$.
+Consider a dual configuration $\hat{\xi}:=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ where $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ for every $k\in\{1,\ldots,m\}$.
 Considering the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\hat{\xi}$ we obtain that, for every $\bm{n}$
@@
 \begin{align}
-	\mathcal{S}_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}\label{S1Gen}\\
-	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}\label{S2Gen}
+	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\\
+	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\label{S2Gen}
 \end{align}
@@
 \begin{equation}\label{transformationV}
- \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=2}^{N}e_{1a}^{x}\right)}%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+ \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
 \end{equation}
@@
 \begin{equation}
-	H^{'}_{left}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+	H^{'}_{left}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
 \end{equation}
@@
 	\begin{split}
-		H_{left}^{'}&=S_{1}H_{left}S_{1}^{-1}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}
-		\\&=
-		\left\{\exp{\left(-\sum_{c=2}^{N}e_{c1}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ba}^{1}-e_{bb}^{1}\right)\exp{\left(\sum_{c=2}^{N}e_{c1}^{1}\right)}\right\}^{T}
-		\\&=
-		\sum_{a=2}^{N}\left(\alpha_{a}e_{1a}^{1}-e_{aa}^{1}\right)^{T}
-		\\&=
-		\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)
+		H_{left}^{'}&=S_{1}H_{left}S_{1}^{-1}=\exp{\left(\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}
+		\\&=
+		\left\{\exp{\left(-\sum_{c=1}^{N-1}e_{cN}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ba}^{1}-e_{bb}^{1}\right)\exp{\left(\sum_{c=1}^{N-1}e_{cN}^{1}\right)}\right\}^{T}
+		\\&=
+		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{Na}^{1}-e_{aa}^{1}\right)^{T}
+		\\&=
+		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)
 	\end{split}
@@
 \begin{equation}
-H_{left}^{'}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
+H_{left}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
 \end{equation}
@@
  \begin{equation}
- 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
+ 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
  \end{equation}
@@
 \begin{align}
-	H_{left}^{''}=e_{11}^{1}-\mathbbm{1}^{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}^{1}\qquad H_{right}^{''}=e_{11}^{L}-\mathbbm{1}^{L}
+	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}^{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
 \end{align}
@@
 the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal.
-The expressions of $H_{left}^{''}$ and $H_{right}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=2}^{N}\beta_{c}e_{c1}$ and $A=e_{a1},$ and $A=e_{aa}$.
+The expressions of $H_{left}^{''}$ and $H_{right}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{c1}$ and $A=e_{aN},$ and $A=e_{aa}$.
 We compute
 \begin{enumerate}
-	\item $A=e_{a1}$ with $a\neq 1$
-	\begin{equation}
-		\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}\right)}e_{a1}\exp{\left(\sum_{c=2}^{N}\beta_{c}e_{c1}\right)}=e_{a1}
+	\item $A=e_{aN}$ with $a\neq 1$
+	\begin{equation}
+		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
 	\end{equation}
@@
 \begin{equation}
-		\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{x}\right)}e_{aa}^{x}\exp{\left(\sum_{c=2}^{N}\beta_{c}e_{c1}^{x}\right)}=e_{aa}^{x}+\beta_{a}e_{a1}^{x}
+		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{x}\right)}e_{aa}^{x}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}^{x}\right)}=e_{aa}^{x}+\beta_{a}e_{aN}^{x}
 	\end{equation}
@@
 \begin{equation}
-	\sum_{c=2}^{N}[e_{c1},e_{aa}]=\sum_{c=2}^{N}\beta_{c}\left(e_{ca}\delta_{a1}-e_{a1}\delta_{ca}\right)=-\beta_{a}e_{a1}
+	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
 \end{equation}
@@
 	\begin{split}
-		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{1}\right)}
-		\\&=
-		\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}-\beta_{a}e_{a1}^{1}\right)
-		\\&=
-		e_{11}^{1}-\mathbbm{1}^{1}+\sum_{a=2}^{N}(\alpha_{a}-\beta_{a})e_{a1}^{1}
+		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
+		\\&=
+		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
+		\\&=
+		e_{NN}^{1}-\mathbbm{1}^{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
 	\end{split}
@@
 	\begin{split}
-			H_{right}^{''}&=\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=2}^{N}\beta_{c}e_{c1}^{L}\right)}
-			\\&=
-			\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}-\beta_{a}e_{a1}^{L}\right)=
-			\\&=
-			e_{11}^{L}-\mathbbm{1}^{L}
+			H_{right}^{''}&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
+			\\&=
+			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
+			\\&=
+			e_{NN}^{L}-\mathbbm{1}^{L}
 	\end{split}
@@
 \begin{equation}\label{similarity}
-	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}\exp{\left(\sum_{a=2}^{N}e_{a1}^{x}\right)}
+	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}
 \end{equation}
@@
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{\tau_{x},1}}|\mathbf{\bm{\tau}}\rangle
+	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle
 \end{equation}
@@
     \delta_{\tau_{x},1}:=\begin{cases}
-        1\quad \text{if}\quad \tau_{x}=1\\
+        N\quad \text{if}\quad \tau_{x}=N\\
         0\quad \text{otherwise}
@@
     \begin{pmatrix}
-		X_{1}\\ 
-		X_{a}
+		X_{a}\\ 
+		X_{N}
 	\end{pmatrix}=\begin{pmatrix}
@@
      X_{N}
-	\end{pmatrix}\quad \forall a\in \{2,\ldots,N\}
+	\end{pmatrix}\quad \forall a\in \{1,\ldots,N-1\}
 \end{equation}
@@
 	\begin{pmatrix}
-		\Xt_{1}\\ 
-		\Xt_{a}
+		\Xt_{a}\\ 
+		\Xt_{N}
 	\end{pmatrix} =S\begin{pmatrix}
-		X_{1}\\X_{a}
+		X_{a}\\X_{N}
 	\end{pmatrix}=\begin{pmatrix} 
+		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\
 				X_{1}+\ldots +X_{N}\\
-		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\ 
 	\end{pmatrix}=\begin{pmatrix} 
+		X_{a}-\beta_{a}\Xt_{N}\\ 
 			X_{1}+\ldots +X_{N}\\
-		X_{a}-\beta_{a}\Xt_{1}\\ 
 	\end{pmatrix}\qquad \forall a=2,\ldots N
@@
 	\begin{pmatrix}
-		X_{1}\\
-		X_{a} 
+		X_{a}\\
+		X_{N} 
 	\end{pmatrix} =S^{-1}\begin{pmatrix}
-		\widetilde{X}_{1}\\
-		\widetilde{X}_{a}
+		\widetilde{X}_{a}\\
+		\widetilde{X}_{N}
 	\end{pmatrix}=\begin{pmatrix}
-		\beta_1\Xt_{1}-(\Xt_{2}+\ldots+\Xt_{N})\\
 		\Xt_{a}+\beta_{a}\Xt_{1}\\ 
-	\end{pmatrix}\qquad\forall a\in \{2,\ldots,N\}
+		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
+	\end{pmatrix}\qquad\forall a\in \{1,\ldots,N-1\}
 \end{equation}
@@
 \begin{equation} 
-	\left[X_{a},\Xt_{1}\right]=\lambda_{a}\Xt_{1}\qquad\forall a=1,\ldots,N
+	\left[X_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad\forall a=1,\ldots,N
 \end{equation}
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{1}\right]=\lambda_{a}\Xt_{1}\qquad \forall a\in \{2,\ldots,N\}
+	\left[\Xt_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}
 \end{equation}
@@
 \begin{equation}\label{commLEFT}
-	\langle V^{*}|\left(\lambda_{a}\Xt_{1}-\Xt_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=2,\ldots,N
+	\langle V^{*}|\left(\lambda_{a}\Xt_{N}-\Xt_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N-1
 \end{equation}
 \begin{equation}\label{commRIGHT}
-	\Xt_{a} |V\rangle= \lambda_{a}|V\rangle\qquad\forall a=2,\ldots,N
+	\Xt_{a} |V\rangle= \lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N-1
 \end{equation} 
@@
 \begin{equation}\label{UsefulRelation}
-	\widetilde{X}_{a}\widetilde{X}_{1}=\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}
-\end{equation}
-Fixing $ a\in \{2,\ldots,N\}$ and for arbitrary $ \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
+	\widetilde{X}_{a}\widetilde{X}_{N}=\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}
+\end{equation}
+Fixing $ a\in \{1,\ldots,N-1\}$ and for arbitrary $ \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
 \begin{align*}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
-	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{\ell-1}
-	\\&=
-	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell -1}
+	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
+	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
+	\\&=
+	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
 	\\&=\ldots\\&=
-	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
+	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
 \end{align*}
@@
 \begin{align*}
-	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{1}^{n_{1}}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+n_{1}\lambda_{a}\right)^{n_{a}}
+	\widetilde{X}_{N}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{1}^{n_{1}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}
 \end{align*}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}
+	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
+	|V \rangle=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
 \end{equation}
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle&=\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
-	\\&=
-	\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
-	\\&=
-	\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle
+	|V \rangle&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\\&=
+	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
+	\\&=
+	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}|V\rangle
 \end{align*}
-To determine the state we need to compute $\langle V^{*}|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$.
-Calling $\sum_{x=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
+To determine the state we need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}n_{N}^{l}}|V\rangle$.
+Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and taking an arbitrary $a\in \{1,\ldots,N-1\}$ we have
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle V^{*}|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
-	\\&=
-	\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{1}-1)\right)|V\rangle
-	\\&=
-	\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\left(n_{1}+1-1\right)\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{N}^{n_{N}-1}|V\rangle
+	\\&=
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{N}-1)\right)|V\rangle
+	\\&=
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle+\left(n_{N}+1-1\right)\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
 	\\&=
@@
 	\\&=
-	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{1}-1}|V\rangle
 \end{align*}
@@
 	\begin{cases}
-		\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle\\
-		\langle V^{*}|\widetilde{X}_{1}^{0}|V\rangle=1
+		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle\\
+		\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=1
 	\end{cases}
@@
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-2}|V\rangle\\&=
-	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{1}^{0}|V\rangle
-	\\&=
-	\frac{\Gamma(2+n_{1})}{\Gamma(2)}
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
+	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle
+	\\&=
+	\frac{\Gamma(2+n_{N})}{\Gamma(2)}
 \end{align*}
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}
+	|V \rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 \begin{align*}
-	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{L}|V|\rangle=
+	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle=
 	\frac{\Gamma(2+L)}{\Gamma(2)}
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{1}^{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle
+	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle
 \end{equation}
@@
 \begin{equation}
-	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}=\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{\tau_{x},1}}
+	\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}=\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}
 \end{equation}
@@
 \begin{equation}
-	\frac{\Gamma(2+\sum_{x=1}^{L}n_{1}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},1}\right)}{\Gamma\left(L+2\right)}
+	\frac{\Gamma(2+\sum_{x=1}^{L}n_{N}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}
 \end{equation}
@@
 \begin{equation}
-|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},1}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{\tau_{x},1}}|\mathbf{\bm{\tau}}\rangle
+|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle
 \end{equation}
@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 		\end{split}
@@
 \begin{equation}
-   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=2}^{N}\beta_{a}e_{a1}
+   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}
 \end{equation}
@@
 \begin{equation}\label{notation1}
-    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,\}
+    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
 \end{equation}
@@
     	\begin{split}
-    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
+    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
     		\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     		\\&+\left.
-    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
+    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
     		\right. \\&+ \left. 
-    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
+    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
     	\end{split}
@@
     \begin{equation}
-    	\mathcal{S}_{2}^{-1}=\sum_{\tau_{1}=1}^{N}\left\{e_{\tau_{1}}^{\tau_{1}}+(1-\delta_{\tau_{1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
+    	\mathcal{S}_{2}^{-1}=\sum_{\tau_{1}=1}^{N}\left\{e_{\tau_{1}}^{\tau_{1}}+(1-\delta_{\tau_{1},N})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
     \end{equation}
@@
     	%\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
     	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
+    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
     	\\&
-    	\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
-    	\\&=
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\right.
+    	\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},N})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
+    	\\&=
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}
     	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}} \right\}
+    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}} \right\}
     	\\&=
@@
     \begin{comment}
-
     \begin{equation}
@@
 	\begin{split}
-\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
+\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
   \\&+
-  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
+  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
 	\end{split}
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{q_{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}
+		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{q_{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
 	\end{split}
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 	\end{split}
@@
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{x}=(y_{1},\ldots,y_{m})$, such that $x_{i}<x_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
-In each of these points there is a particle of species $a_{i}\in \{2,\ldots,N\}$.
+In each of these points there is a particle of species $a_{i}\in \{1,\ldots,N-1\}$.
 Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
@@
 \paragraph{One point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{2,\ldots,N\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
+The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
 \begin{equation}
@@
 \paragraph{Two points correlations}
-The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{2,\ldots,N\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
 \begin{equation}
@@
 \paragraph{Three points correlations}
-The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{2,\ldots,N\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
+The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
 \begin{equation}
@@
 \begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{a}}^{y_{x}}}{(\nu-m+1)}
+	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{x}}^{y_{x}}}{(\nu-m+1)}
 \end{equation}
@@
 		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
-		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
 		\end{split}
@@
 Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
-\subsection{The process on a finite graph}
+\subsubsection{The process on a chain}
 We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at left of site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at right of site $L$.
@@
 We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}$, as specified above.
-\paragraph{Action on the occupation variable of $\mathcal{L}_{x,y}^{rd}$}
+\paragraph{Action on the occupation variable of $\mathcal{L}_{x,+1}^{rd}$}
 For arbitrary site $x\in \{1,\ldots,L\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
@@
 where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
-Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{2,\ldots,N\}$ 
+Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{1,\ldots,N-1\}$ 
 \begin{equation}\label{actionBDLine}
@@
 \begin{equation}
-	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
+	\rho_{d}(x,t)=\mathbb{E}_{\mu}\left[n_{d}^{x}(t)\right]
 \end{equation}
@@
 \begin{equation}
-	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
+	\frac{d \rho_{d}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{d}^{x}(t)\right]
 \end{equation} 
@@
 \begin{equation}
-	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}
+	\rho=\rho_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{N}}{\alpha_{1}+(N-1)\alpha}
 \end{equation}
@@
 \begin{equation}
-	\bm{\xi}=\left(\xi_{2}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{2}^{L+1},\ldots,\xi_{N}^{L+1}\right)
+	\bm{\xi}=\left(\xi_{2}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
 \end{equation}
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{u(x)}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{u(x)}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
 \end{equation}
@@
 Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x})}$ as a symmetry.
-The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$.
+The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
 \begin{align*}
-	&\left[\left(\sum_{d=2}^{N}E_{d1}^{x}\otimes\sum_{k=2}^{N}E_{k1}^{x+1}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{x+1} -E_{aa}^{x}\otimes E_{bb}^{x+1}\right)\right]
+	&\left[\left(\sum_{d=1}^{N-1}E_{dN}^{x}\otimes\sum_{k=1}^{N-1}E_{kN}^{x+1}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{x+1} -E_{aa}^{x}\otimes E_{bb}^{x+1}\right)\right]
 	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)1}-E_{g_{c}(b)1}^{x}\delta_{ad})-(E_{da}^{x+1}\delta_{a1}-E_{a1}^{x+1}\delta_{da})\right)\right.
+	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x+1}\delta_{aN}-E_{aN}^{x+1}\delta_{da})\right)\right.
 \\ \otimes&\left.
-\left((E_{kb}^{y}\delta_{g_{c}(a)1}-E_{g_{c}1}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{b1}-E_{b1}^{x+1}\delta_{kb})\right)\right\}
+\left((E_{kb}^{y}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
 	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)1}^{x}-E_{da}^{x}+E_{a1}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)1}^{x+1}-E_{kb}^{y}+E_{b1}^{x+1}\right)\right\}
+	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{y}+E_{bN}^{x+1}\right)\right\}
 	\\=&
-	\sum_{d,k=2}^{N}\sum_{a,b=1}^{N}\left\{\left(E_{a1}^{x}-E_{g_{c}(b)1}^{x}\right)\otimes \left(E_{b1}^{x+1}-E_{g_{c}(a)1}^{x+1}\right)\right\}
+	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{aN}^{x}-E_{g_{c}(b)N}^{x}\right)\otimes \left(E_{bN}^{x+1}-E_{g_{c}(a)N}^{x+1}\right)\right\}
 	\\=&0
@@
 where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
-The second result will follow from the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=2}^{N}(E_{d1}^{x})\otimes \sum_{k=2}^{N}E_{b,1}^{x}$. The prof is similar and gives
-\begin{equation}
-	\left[\sum_{a=2}^{N}E_{a1}^{x}\otimes \sum_{b=2}^{N}E_{b1}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{x+1}-E_{aa}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0
+The second result will follow from the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
+\begin{equation}
+	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{x+1}-E_{aa}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0
 \end{equation}
@@
 	\begin{split}
-		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 		\\&+
-		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},1}\right) 
+		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
 		\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
 		\\&
-		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
+		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
 	\end{split}
@@
 			\begin{split}
-				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 				\\&+
-				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},1}\right) 
+				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
 				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
 				\\&
-				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
 				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
 				\\ &
-				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
@@
 	\begin{equation}\label{S1-L1}
-		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},N}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
 	\end{equation}
@@
 			\\&
-			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
+			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
 		\end{split}
@@
 		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
-		%$e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-\\
 		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
@@
 \\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
 			\\&\otimes
-			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},1}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
+			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
 			\\&=
@@
 \\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
 		\end{align*}
@@
 				\\&
-				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\eta_{1},\ldots,\eta_{L})
+				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\eta_{1},\ldots,\eta_{L})
 			\end{split}
@@
 			\begin{split}
-				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\sum_{c_{1}=0}^{1-\delta_{\eta_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
+				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
 				\\&
-				\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},1})}
+				\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
 			\end{split}
@@
 				\begin{split}
-					&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},1}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+					&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
 					\\&  
-					\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},1})}
+					\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 					\\&

### 2023-09-13 main.tex
sequence of similarity

@@
 We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution. This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
-\begin{equation}
+\begin{equation}\label{definition-SteadyStateH}
 	H|\Psi\rangle =0
@@
 \begin{equation}
-	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}
+	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}
 \end{equation} 
@@
 \begin{equation}\label{similarV}
-   H^{'}=S_{1}H^{'}S_{1}^{-1}
+   H^{'}=S_{1}HS_{1}^{-1}
 \end{equation}
@@
 \subsection{Bethe ansatz solution}
-
 Describe eigenvalues of $T_0$ following 
 \cite{Belliard2} 
+\subsection{A sequence of similarity transformation}
+In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$.
+Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one as
+\begin{equation}
+	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
+\end{equation} 
+More explicitly we have 
+\begin{equation}
+	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
+\end{equation}
+as a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
+\begin{equation}
+	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
+\end{equation}
+and using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
+\begin{align}
+	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\\&
+	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
+	\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
+\end{align}
 \section{Extensions for the non-integrable chain}
@@
 \subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
-In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{2,3\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
+In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
 \begin{equation}\label{2SpeciesRD}
@@
 \end{equation} 
-for $ x\in\{1,\ldots,L\}\quad a\in\{2,3\}$  and where $\overline{a}=3$ if $a=2$ and $\overline{a}=2$ if $a=3$.
+for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$.
 This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).

### 2023-09-13 main.tex
oiu

@@
 check also Appendix A in
-\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz} 
+\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz} \\
+As observed in Subsection \ref{subsection-exact}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$ that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations.
+To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal.
+Therefore, these boundaries do not produce any current and this $H_{0}$ is called \textit{equilibrium Hamiltonian}.
+For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.
+This can be represented by the following diagram 
+\begin{equation}
+	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
+\end{equation} 
+The eigenvectors and the eigenvalues of $H_{0}$ are known and they have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
+As a consequence, this allows to find again the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e.
+a state where all the sites are empty.
+This transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM).
 \subsection{The non local transformation}\label{SectionNonLocalTrasformation}
@@
 \end{equation}
-We will prove that 
+ We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
+Therefore, we call $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
+We prove that
 \begin{equation}\label{W-extended}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \end{equation}
-In order to be well defined $z$ must not be an eigenvalue of $H^{''}$.
-We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
-Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
-We chose $z=\Lambda_{\bm{m}}+\epsilon$
-\begin{equation}
-	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)=1
+In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. We chose $z=\mathcal{E}_{\bm{m}}+\epsilon$ 
+\begin{equation}
+	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1
 \end{equation}
@@
 \begin{equation}
-	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
 \end{equation}
@@
 \begin{equation}
-	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
 \end{equation}
@@
 \begin{equation}
-	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\left(\Lambda_{\bm{m}}+\epsilon-H\right)=\left(\Lambda_{\bm{m}}-H\right)<\infty
+	\lim_{\epsilon\to 0}\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)=\left(\Lambda_{\bm{m}}-H^{''}\right)<\infty
 \end{equation}
@@
 	\begin{split}
-		&\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}H\right)^{n}(\Lambda_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
+		&\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\mathcal{E}_{\bm{m}}+\epsilon)^{-1}H^{''}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
 		\\=&
-		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\Lambda_{\bm{m}}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-\Lambda_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
+		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\mathcal{E}_{\bm{m}}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-\mathcal{E}_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
 	\end{split}
@@
 \begin{equation}
-	\sum_{m=0}^{L}  (\Lambda_{\bm{m}}-H)\lim_{\epsilon\to 0}\epsilon R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
+	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	WH_{0}=HW
+	WH_{0}=H^{''}W
 \end{equation}
@@
 \end{equation}
-Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$, one can show that 
+Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{m}$, one can show that 
 \begin{equation}\label{WInCharges}
@@
 \begin{equation}\label{W}
-	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|
+	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|
 \end{equation}
@@
 	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\
-		=&\lim_{\epsilon\to 0}\sum_{m=0}^{L}\epsilon\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\
+		=&\lim_{\epsilon\to 0}\sum_{m=0}^{L}\epsilon\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
 		\\=&
-		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
 	\end{split}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}
+	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}
 \end{equation}
@@
 	\begin{split}
-		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}^{Q}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}^{Q}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\
+		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\
 		=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)^{-1-n}(Q_{0}^{2L})^{n}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)^{-1-n}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}\right\}^{k}
+		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}+\epsilon)^{-1-n}(Q_{0}^{2L})^{n}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}+\epsilon)^{-1-n}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}\right\}^{k}
 		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{B_{1}^{2L-1}\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}\right\}^{k}
+		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{B_{1}^{2L-1}\left((\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}\right\}^{k}
 	\end{split}
@@
 	\begin{split}
-		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
 		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
@@
 \end{equation}
+where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain. \\
 Indeed, since the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
@@
 	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
 		\\&
-		\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+		\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 	\end{split}
@@
 	\begin{split}
-&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
-=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}
+&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
+=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}
 	\end{split}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
+	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
 \end{equation}
@@
 	\end{pmatrix}}_{L-\text{times}}
-\end{equation} 
+\end{equation} whose eigenvalue is $\Lambda_{0}$. 
 This steady state reads 
@@
 \begin{align}
-	&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
 	|\Psi_{0}^{0}\rangle\nonumber
@@
 \end{equation}
-as a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
+As a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
 \begin{equation}
@@
 \end{equation}
-and using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
+Moreover, using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
 \begin{align}
@@
 \end{enumerate}
-The aim of this section is to give an answer to these questions.
+The aim of this section is to answer to these questions.
 We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term.

### 2023-09-13 main.tex
asd

@@
 The advantage is that now we can do more with the above expression.
-Hopefully, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form, independently from the equilibrium eigenvectors.
-Moreover, we can use it to extract the steady state by rising the vacuum state.
+Firstly the eigenvalues $\Lambda_{\bm{m}}$ can be explicitly computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form that can be used to extract the steady state by rising the vacuum state.
 We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$.

### 2023-09-13 main.tex
abs-check
sdfg
lkj

@@
 	\end{equation}
-\textbf{Remark}: Using the Binomial Theorem we rewrite the \eqref{exactCorrelations} as 
-\begin{equation}
-\begin{split}
-\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
+\textbf{Remark}: using binomial theorem we rewrite the \eqref{exactCorrelations} as 
+\begin{equation}
+\begin{split}
+\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&
+\sum_{c_{1},\ldots,c_{m}=0}^{1}
+f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})\right)\\
+=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
 f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
@@
 \sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
-=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
 \end{split}
@@
  \end{equation} 
-Using formula \eqref{ABS} for a configuration where all $\tau_{i}$ are non-empty species, we obtain that 
-\begin{equation}
-	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ and using $\tau_{i}=a_{i}$ $\forall i=1,\ldots,m$, we have the formulas for arbitrary correlations.
+Using formula \eqref{ABS} for a configuration where all $\tau_{x_{i}}=a_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{x_{1},\ldots,x_{m}\}$, we obtain 
+\begin{equation}
+ \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{''}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.
 \begin{comment}
@@
 \end{equation}
-The above matrices satisfy
+The above matrices satisfy:
 \begin{itemize}
@@
 \end{equation}
-Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{m}$, one can show that 
+Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{\bm{m}}$, one can show that 
 \begin{equation}\label{WInCharges}
 	\begin{split}
-	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{m}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
 \end{split}
@@
 		\\=&
-		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
 	\end{split}
@@
 	\begin{split}
-		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\
+		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\
 		=&
@@
 	\begin{split}
-		W|\Psi_{m}^{0}\rangle=&\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		W|\Psi_{m}^{0}\rangle=&\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
 		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
 		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-Q_{0}^{2L}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
 	\end{split}
@@
 	\begin{split}
-		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\lambda_{m}^{Q}+\epsilon)-\Lambda_{m}^{Q}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
+		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\Lambda_{m}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
 		\\=&

### 2023-09-14 main.tex
lkj

@@
 any two types are swapped at rate $1$; additionally, on each site $x$, 
-a particles of a give type (if present) is replaced with a
+a particles of a given type (if present) is replaced with a
 particle of type $k$ at rate $\alpha_k^x >0$.
@@
 
-\subsection{Integrable process on a line segment}
+\subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
 In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
-These boundaries, exchanging particle with the external environment, put the chain out of equilibrium.
+These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium.
 The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
@@
 We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e.
-$(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in  the fundamental representation of the algebra.
+$(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
 The Hamiltonian is
@@
 Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
-\begin{equation}
+\begin{equation}\label{H-corsivo}
 	\begin{split}
@@
 \textbf{Remark}:
-when the state spaces of the dual processes is finite, the generators and the duality function can be represented as with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
+when the state spaces of the dual processes is finite, the generators and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
 Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as
@@
 \begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
-\end{equation}
-where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
+\end{equation}
+where we denote the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$  by 
 \begin{equation}
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{1}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)
 \end{equation}
@@
 On the other hand, the site
-part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{2,\ldots,N\}$ at site $x$ with a particle of type $N$ and creates a particle of the same type $a$ at the extra-site $u(x)$.
+part $\widetilde{\mathcal{L}}_{x}$ of the dual generator replaces a particle of any type $a\in\{1,\ldots,N-1\}$ at site $x$ with a particle of type $N$ and creates a particle of the same type $a$ at the extra-site $u(x)$.
 This last transition is performed with rate $|\alpha^{x}|\xi_{a}^{x}$.
@@
 \textbf{Remark}: in the reversible situation, i.e.
-when $\forall x\in V$ $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
+when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
 \begin{equation}
@@
 Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$.
-As we will see, this symmetry is $\sum_{a=1}^{N-1}E_{a1}$ \\
+As we will see, this symmetry is $\sum_{a=1}^{N-1}E_{aN}$ \\
 We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain
@@
 \begin{equation}
-	E=\sum_{a=1}^{N-1}E_{a1}
+	E=\sum_{a=1}^{N-1}E_{aN}
 \end{equation}
@@
  \end{equation}
-In the following we need the application of the Hadamard formula with $B=\sum_{a=1}^{N-1}E_{a1}$ defined in \eqref{equationE} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
+In the following we need the application of the Hadamard formula with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
 Therefore we compute
@@
     \end{equation}
-    because $E_{b 1}$ commutes with $E$
+    because $E_{b N}$ commutes with $E$
     \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
@@
 \\=&
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}\right)
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}\right)
     \end{split}
@@
 \\&=
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}||\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
 \\&=
@@
 \subsection{Duality for the integrable process on a line segment}
-In this setting the extra-sites are denoted by $0$ and $L+1$, since connected respectively with sites $1$ and $L$ of the chain. Moreover, the matrix $R_{x}$ defined in \eqref{Revmatrix} 
+Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}.
+In this setting the extra-sites are denoted by $0$ and $L+1$, connected respectively with sites $1$ and $L$ of the chain.
+Moreover, the matrix $R_{x}$ defined in \eqref{Revmatrix}
 reduces to the identity which implies 
@@
 \begin{equation}
-	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{(E^{x})}\otimes \mathcal{D}_{L+1}
+	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
 \end{equation}
@@
 	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
+\end{equation}
+where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
+\begin{equation}
+	\widetilde{H}_{left}=|\alpha|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=|\alpha|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)
 \end{equation}
@@
 \end{equation}
-Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
+Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the so called absorption probabilities.
 Consider a dual configuration $\hat{\xi}:=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ where $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ for every $k\in\{1,\ldots,m\}$.
-Considering the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\hat{\xi}$ we obtain that, for every $\bm{n}$
+Considering an arbitrary $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\hat{\xi}$ read
 \begin{equation}
@@
 \end{equation}
-therefore, its expectation with respect to the steady state non-equilibrium distribution gives the $m$-points correlations.
-Moreover, recalling that the dual process eventually voids the chain by putting all particles in the extra-sites $0$ and $L$ we have the following chain of equalities
+To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
+Therefore, we have the following equalities
 \begin{equation}\label{CorrelationByABS-prob}
@@
 	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{stat}&=\mathbb{E}_{stat}\left[D(\bm{n},\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\hat{\xi}(t))\right]
-	\\&=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{i_{k}}\beta_{a_{k}}^{1-i_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
+	\\&=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
 \end{split}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
-\end{equation}
-and they are called \textit{absorption probabilities}.
+	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{a}\delta_{0}+(1-c_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+and they are called \textit{absorption probabilities}, namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $a_{k}$ absorbed at left and $1-c_{k}$ absorbed at right.
+Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
 
 \section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
+In this section we aim to use duality and the matrix product ansatz to determine the non equilibrium steady state and its arbitrary correlation for the integrable version of the multi-species stirring process, defined in Subsection \ref{subsection-description-process-LINE}.
+As it will turn out, duality simplifies the commutation relations of the matrix product ansatz allowing to determined a closed formula for all correlations.
+As a by-product, absorption probabilities can be explicitly determined, giving a further probabilistic interpretation for the non-equilibrium steady state.
 \subsection{The integrable chain and the matrix product ansatz}
@@
 However, to write explicitly the steady state one should provide a representation of this algebra.
-Another approach is to directly use the commutators and compute the steady-state correlations using the commutation relations and the boundary actions.
+Another approach is to directly use the commutators and and the boundary actions compute the steady-state correlations.
 This path has been followed in \cite{vanicat2017exact} to compute one-point and two-point correlations.
-Here we follow the approach of working with the abstract commutation  relations.
-We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the actual
+Here we follow the same approach. We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the actual
 computation. The idea is summarized as follows. We define a sequence of similarity transformation such that 
@@
 The second transformation $S_{2}$ diagonalize the right boundary.
-The composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.
+The composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
+\\
 
@@
 Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ thanks to the simpler commutators.
-Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and the steady state of $H$.
+Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and  the arbitrary correlations and the absorption probabilities.
+The explicit expression of the steady state of $H$ is reported in appendix \ref{appB}.
 
@@
 that is composed by a copy of $\mathcal{S}_{2}$ (introduced in \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
-By taking the product over the chain we also define
+By taking the product over the chain
 \begin{equation}\label{S2-Whole}
@@
 \begin{equation}
-	|\bm{\tau}\rangle =\begin{pmatrix}
+	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
 		\tau_{1}\\
@@
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
-To prove \eqref{ResulsBasis} we consider the vector with elements the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators.
+We consider the vector with elements the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators.
 For the sake of notation, we denote by 
@@
 			X_{1}+\ldots +X_{N}\\
-	\end{pmatrix}\qquad \forall a=2,\ldots N
+	\end{pmatrix}\qquad \forall a=1,\ldots N-1
 \end{equation}
@@
 	\end{pmatrix}=\begin{pmatrix}
-		\Xt_{a}+\beta_{a}\Xt_{1}\\ 
+		\Xt_{a}+\beta_{a}\Xt_{N}\\ 
 		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
@@
 \end{equation}
-therefore, we obtain the commutation relations for $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$
+therefore, we obtain the commutation relations for $\Xt_{a}$ 
 \begin{equation}\label{commutationsBula}
@@
 \end{equation}
-Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{2,\ldots,N\}$ on the boundary vectors are given by 
+Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ on the boundary vectors are given by 
 \begin{equation}\label{commLEFT}
@@
 \begin{align*}
-	\widetilde{X}_{N}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{1}^{n_{1}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}
+	\widetilde{X}_{N}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}
 \end{align*}
@@
 	\\&=
-	\left(2+n_{1}-1\right)\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
+	\left(2+n_{N}-1\right)\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
 	\\&=
@@
 \paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
-Here is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
+Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
 This matrix $\mathcal{S}_{2}$ is given by
@@
 		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{L}\}\\
-		1\qquad &\text{otherwise}\\
+		N\qquad &\text{otherwise}\\
 	\end{cases}
@@
 In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e.
-a species with label from $2$ to $N$.
-This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{1}^{x}=\nu-\sum_{b=2}^{N}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
-Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{x}=(y_{1},\ldots,y_{m})$, such that $x_{i}<x_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
+a species with label from $1$ to $N-1$.
+This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
+Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
 In each of these points there is a particle of species $a_{i}\in \{1,\ldots,N-1\}$.
@@
 \begin{equation}\label{exactCorrelations}
-		\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})
+		\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
 	\end{equation}
@@
 	\begin{equation}\label{powerCoeffSpecies}
-		g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
+		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
 	\end{equation}
@@
 \begin{split}
-\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&
+\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=&
 \sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})\right)\\
+f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\
 =&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})
 \end{split}
@@
 \begin{split}
-\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
-=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
+=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})
 \end{split}
@@
 where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{a_{i}}^{x_{i}}$.  
-This means that the $m$-point correlations can also be written in terms of these absorption probabilities. 
-%\begin{equation}
-%	\langle n^{y_{1}}_{\tau_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})g_{k}(y_{k},c_{k},\ldots,c_{m})
-%\end{equation}
-\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $a_{i}\in\{2,\ldots,N\}$ in positions $x_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$.
-We aim to compute the non-equilibrium stationary state correlation $\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}$.
+\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $a_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$.
+We aim to compute the non-equilibrium stationary state correlation $\langle n_{a_{1}}^{y_{1}}\cdots n_{a_{m}}^{y_{m}} \rangle_{stat}$.
 By using duality, we showed in \eqref{CorrelationByABS-prob} that
  \begin{equation}
- 	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
- \end{equation} 
-Using formula \eqref{ABS} for a configuration where all $\tau_{x_{i}}=a_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{x_{1},\ldots,x_{m}\}$, we obtain 
-\begin{equation}
- \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{''}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.
+ 	\langle n_{a_{1}}^{y_{1}}\cdots n_{a_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
+ \end{equation} 
+Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=a_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 
+\begin{equation}
+ \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.
 \begin{comment}
@@
 \paragraph{One point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
-\begin{equation}
-	\langle n_{a_{1}}^{x_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,x_{1},c_{1})
+The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
+\begin{equation}
+	\langle n_{a_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,y_{1},c_{1})
 \end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-\langle n_{a_{1}}^{x_{1}}\rangle_{\text{stat}}=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}
+\langle n_{a_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}
 \end{equation}
@@
 	\begin{split}
-	\langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})
+	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})
 	\end{split}
@@
 	\begin{split}
-	\langle n_{a_{1}}^{x_{2}} n_{a_{2}}^{x_{2}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})
+	\langle n_{a_{1}}^{y_{2}} n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})
 	\end{split}
@@
 	\begin{split}
-		\langle n_{a_{1}}^{x_{2}} n_{a_{2}}^{x_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}]-\mathbb{E}[n_{a_{1}}^{x_{1}}]\mathbb{E}[n_{a_{2}}^{x_{2}}]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)
+		\langle n_{a_{1}}^{y_{2}} n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}]-\mathbb{E}[n_{a_{1}}^{y_{1}}]\mathbb{E}[n_{a_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)
 	\end{split}
@@
 \paragraph{Three points correlations}
-The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
-\begin{equation}
-    \langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}n_{a_{3}}^{x_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{3})
+The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
+\begin{equation}
+    \langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})
 \end{equation}
@@
 \begin{align}\label{three-pts-corr}
-        \langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}n_{a_{3}}^{x_{3}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
+        \langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
         \\&+\nonumber
-        \frac{(L+1-x_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-x_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}
+        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}
         \\&+\nonumber
-        \frac{(L-x_{2})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}
+        \frac{(L-x_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}
         \\&+\nonumber
-        \frac{(L-x_{1})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}
+        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}
         \\&+\nonumber
-        \frac{(L-x_{1})(L-x_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}
+        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}
         \\&+\nonumber
-        \frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
+        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
 \end{align}
@@
 \begin{align}
-	\langle n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}n_{a_{3}}^{x_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}\right]-\mathbb{E}\left[n_{a_{1}}^{x_{1}}n_{a_{2}}^{x_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{x_{3}}\right]-\mathbb{E}\left[n_{a_{1}}^{x_{1}}n_{a_{3}}^{x_{3}}\right]\mathbb{E}\left[n_{a_{2}}^{x_{2}}\right]\\&-\mathbb{E}\left[n_{a_{3}}^{x_{3}}n_{a_{2}}^{x_{2}}\right]\mathbb{E}\left[n_{a_{1}}^{x_{1}}\right]+2\mathbb{E}\left[n_{a_{1}}^{x_{1}}\right]\mathbb{E}\left[n_{a_{2}}^{x_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{x_{3}}\right]
-	\\&=
-	-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
+	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{a_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{a_{3}}^{y_{3}}n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{a_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{y_{3}}\right]
+	\\&=
+	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
 \end{align}
@@
 \section{Mapping to equilibrium} \label{Section-Mapping}
-check also Appendix A in
-\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz} \\
-As observed in Subsection \ref{subsection-exact}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$ that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations.
+{\color{blue}check also Appendix A in
+\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}} \\
+In Subsection \ref{subsection-exact}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations.
 To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal.
-Therefore, these boundaries do not produce any current and this $H_{0}$ is called \textit{equilibrium Hamiltonian}.
+These boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}.
 For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.
@@
 \end{equation} 
-The eigenvectors and the eigenvalues of $H_{0}$ are known and they have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
-As a consequence, this allows to find again the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e.
+The eigenvectors and the eigenvalues of $H_{0}$ have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
+As a consequence, we can find all the eigenvectors of $H$ from the ones of $H_{0}$.
+Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e.
 a state where all the sites are empty.
-This transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM).
+This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM).
 \subsection{The non local transformation}\label{SectionNonLocalTrasformation}
@@
 \begin{equation}
-	H^{0}=H_{left}^{0}+H_{bulk}+H^{''}_{right}
+	H^{0}=H_{left}^{0}+H_{bulk}+H^{0}_{right}
 \end{equation}
@@
 \begin{equation}
-	H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
+	H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{0}=e_{NN}^{L}-\mathbbm{1}^{L}
 \end{equation}
@@
 \end{equation}
- We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
-Therefore, we call $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
+ We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}=\sum_{x=1}^{L}n_{i}^{x}$, i.e.
+it means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
+Observe that $|\bm{m}|=\sum_{i=1}^{N}m_{i}=L$.
+We call $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
 We prove that
@@
 \end{equation}
-\paragraph{Construction of matrix W}
+\paragraph{Construction of the matrix W}
 We aim to show that \eqref{W-extended} fulfils \eqref{GoalWH}. Consider the \textit{resolvent operator}
@@
 \end{equation}
-In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. We chose $z=\mathcal{E}_{\bm{m}}+\epsilon$ 
+In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix with $\epsilon>0$ and arbitrary, then we chose $z=\mathcal{E}_{\bm{m}}+\epsilon$, 
 \begin{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz.
-This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
+This expression, as it will be shown in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
 To write formula \eqref{W-extended} using the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM).
-We first present the simpler case of $gl(2)$, then we adapt the proof to the general $gl(N)$.
-\subsection{Quantum inverse scattering method}
+This will be presented in Subsection \ref{SubsectionQISM}.
+In Subsection \ref{SubsectionGL2} we first present the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$.
+\subsection{Quantum inverse scattering method}\label{SubsectionQISM}
  We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$.
@@
 We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$.
-\subsection{The gl(2) case}
+\subsection{The gl(2) case}\label{SubsectionGL2}
 In the case of $gl(2)$ we have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
@@
 \end{flushright}
-\subsection{The gl(N) case}
+\subsection{The gl(N) case}\label{SubsectionGLN}
 In the general case of $N>2$ species we have that \eqref{WInCharges} reads 
@@
 fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} 
-\section{Exact steady state of $H$}\label{subsectionSSH}
+\section{Exact steady state of $H$}\label{appB}
 

### 2023-09-14 main.tex
ghj

@@
 \begin{equation}\label{KmatrixHAT}
-	\widehat{K}_{0}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}
+	\widehat{K}_{a}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}
 		1-x&0&\ldots&0\\
@@
 \begin{equation}\label{Kmatrix}
-	K_{0}=\left((2x+N)H^{''}_{left}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
+	K_{a}(x)=\frac{\left((2x+N)H^{''}_{left}+(x+N)I\right)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
 		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
@@
 		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
-		0&0&0&\ldots&0&1+x
+		0&0&0&\ldots&0&N+x
 	\end{pmatrix}
 \end{equation}
+where the lower index $a$ means that they are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$, for $a\in\{0,\ldots,L\}$ and where $x,y\in\mathbb{C}$ are called spectral parameters.
 The above matrices satisfy:
@@
 \begin{equation}
-	T^{\Delta}(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
+	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
 \end{equation}
@@
 \begin{equation}
-	\left[T^{\Delta}(x),T^{\Delta}(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T^{\Delta}(0))=C_{1}H^{''}+C_{2}I
+	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(x))\lvert_{x=0}=C_{1}H^{''}+C_{2}I
 \end{equation}
 with $C_{1},C_{2}>0$. \\
-The double row monodromy is given by
+The double row monodromy $U_{0}(x)$ is given by
 \begin{equation}
@@
 
-We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
+We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename its elements, each of them acting on the quantum space $V$, has follows
 \begin{comment}
@@
 \end{equation}
-The exchange relations for the elements of the above matrix can be found using \eqref{RURU}
+The exchange relations for the elements of the above matrix can be found using \eqref{RURU} and they read:
 \begin{itemize}
@@
 	\begin{split}
-		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
-			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
-			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
-			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
-			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
-			0&0&0&\ldots&0&1+x
-		\end{pmatrix}\right.
-		\\& \left.
-		\;\;\;\begin{pmatrix}
-			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
-			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
-			\vdots&\vdots&\ddots&\vdots&\vdots\\
-			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
-			B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
-		\end{pmatrix}\right)\\
-	=&
+		T^{\Delta}(x)=%tr_{0}&\left(\begin{pmatrix}
+			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
+		%	0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
+		%	\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
+		%	0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
+		%	0&0&0&\ldots&0&N+x
+	%	\end{pmatrix}\right.
+	%	\;\;\;\begin{pmatrix}
+	%		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
+	%		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
+	%		\vdots&\vdots&\ddots&\vdots&\vdots\\
+	%		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
+	%		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
+	%	\end{pmatrix}\right)\\
+	%=&
 	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
@@
 \end{equation}
-therefore, it is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
-\begin{equation}
-	\begin{split}
-		T^{\Delta}(x)=
+By construction,$T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
+\begin{equation}
+	\begin{split}
+		T(x)=
 		\sum_{k=0}^{2L+2}Q_{k}x^{k}
@@
 \end{equation}
-where, for all $k\in\{0,\ldots,2L+2\}$, we call these $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
-\begin{equation}
-	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
+where, for all $k\in\{0,\ldots,2L+2\}$, we call $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
+\begin{equation}
+	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
 \end{equation}
@@
 \end{equation}
- Only the first three coefficients of the diagonal elements and the first coefficient of the non diagonal elements do survive when $x\to \infty$, therefore we only compute them. We obtain:
+ In the following we will study the charge expansion of $T^{\Delta}(x)$ when $x\to \infty$.
+As it will be clear in the following, only the first three coefficients for the diagonal elements and only the first one for the non-diagonal elements will be needed.
+Therefore, using \eqref{RURU}, we compute:
 \begin{itemize}
@@
 All terms are diagonal except the last one.
-However, this last non-diagonal term acts diagonally on the states.
-Indeed, can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
+This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
 We denote it by $\hat{C}_{2}^{N-1}$ and it reads
@@
 We denote its eigenvector by $C_{2}^{N-1}$.
-On the Bethe states (and on the decomposition into irreducible representation of the spin chain) it acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
+Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$.
+The Bethe states belong to the configurations space, and thus we can write them as a direct sum of vectors, each belonging to an irreducible representation of $gl(N)$.
+On these irreducible vectors .
+$\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
 \begin{equation}
@@
  \end{equation}
-with $\mu_{j}$ the representation labels of tensor product over the chain of the fundamental representation of $gl(N)$ (it can be decomposed by branching rule).  
-Thus the eigenvalues of the transfer matrix can be writen as 
+with $\mu_{j}$ the representation labels of irreducible representation of $gl(N)$. This argument allows to write explicit expression for the eigenvalues of $Q_{0}^{2L}$, indeed 
 \begin{equation}
@@
 \end{equation} 
+{\color{blue}
 Thus the following difference is of order $2L$
@@
 \lim_{x\to\infty}\frac{2x+N}{\Lambda(x)-T_0(x)}B_{i}(x)=\frac{2}{\Lambda_{2L}-Q_{2L}^0}B_i^{2L-1}
-\end{equation} 
+\end{equation} }
 \paragraph{Exchange relations between charges}
@@
 \end{equation}
-While, for $i,j\in\{1,\ldots,N-1\}$ such that $i\neq j$
+While, for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j$, $k\neq i,h$
 \begin{equation}\label{Commuting-Charges}
-\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0%\qquad \left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0
+\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0\qquad \left[B_{k}^{2L-1},D_{j,i}^{2L}\right]=0%\left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0
 \end{equation}
@@
 \end{equation}
-Since $Q^{2L}$ and $H^{''}$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones.
+Since $Q^{2L}$ and $H^{''}$ commutes the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones.
 The advantage is that now we can do more with the above expression.
@@
 \subsection{The gl(2) case}\label{SubsectionGL2}
-In the case of $gl(2)$ we have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
+Here, the multi-species stirring process reduces to the Simple Symmetric Exclusion Process (SSEP).
+We have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
 \begin{equation}\label{Nice-W2}
@@
 \subsubsection{Proof of formula \eqref{Nice-W2}}
-In this simpler situation the double row monodromy reads
+The double row monodromy reads
 \begin{equation}
@@
 \end{equation}
-Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ we obtain 
+Power expanding the matrix $W$ with respect to $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for all $i\in\{1,\ldots,N-1\}$ we obtain 
 \begin{equation}\label{LinkWG}
@@
 		(Q_{0}^{2L}B_{1}^{2L-1})^{k}&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+\mathbbm{1}_{\{j>1\}}4\sum_{i=1}^{j-1}(j-i)Q_{0}^{2L+2}\right)\\
-		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)N\right)\\
+		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\\
 		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)

### 2023-09-14 main.tex
rew

@@
 \textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain in order to alleviate notation. Each configuration can be written as
-\begin{equation}
+\begin{equation}\label{Tau-Notation}
 	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
@@
 \end{equation}
-where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain. \\
-Indeed, since the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
-\begin{equation}
-	-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}
-\end{equation}
-that gives rise to a proliferation of terms that does not vanish, thus only part of the argument done in the $N=2$ case can be followed.
-However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the steady state can be written, since when acting on the vacuum the exchange relations do remain simple.
-\paragraph{Proof of formula \eqref{W-charges-Bad}}
-Following the result in the simpler $gl(2)$ case, we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
-We obtain that, using also the multi-variate version of \eqref{veryUsefulSeries},
-\begin{equation}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
-		\\&
-		\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation} 
-Here $SYM$ is the following transformation. We introduce, the following indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that 
+where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain.
+Here $SYM$ is the following transformation.
+We introduce, the indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that
 \begin{equation}
@@
 \end{equation}
-where $Sym$ is the symmetric group. \\
+where $Sym$ is the symmetric group among $N-1$ objects. \\
+In this case we do not have a closed formula as in the case of $gl(2)$. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
+\begin{equation}
+	-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}
+\end{equation}
+This extra creation operator, mixes up the species different from $N$.
+However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do remain simple.
+\paragraph{Proof of formula \eqref{W-charges-Bad}}
+Following the result in the simpler $gl(2)$ case, we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
+We obtain that, using also the multi-variate version of \eqref{veryUsefulSeries},
+\begin{equation}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
+		\\&
+		\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation} 
 Observing that 
@@
 \end{equation}
-we finally have 
-\begin{equation}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
-		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation}
+we finally obtain \eqref{W-charges-Bad}. 
+%\begin{equation}
+%	\begin{split}
+%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+%		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+%	\end{split}
+%\end{equation}
 \begin{flushright}
@@
 \subsection{Non-equilibrium steady state from the W transformation}\label{subsection-NONSS-W}
-Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by actin with $W$ on the vacuum state 
+Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state 
 \begin{equation}\label{Vacuum-state}
@@
 \end{equation} whose eigenvalue is $\Lambda_{0}$. 
-This steady state reads 
+We obtain 
 \begin{equation}\label{SteadyState-W-Good}
@@
 \textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
-Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult and we cannot rewrite \eqref{W-charges-Bad} in such a simple form.
+Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult because of the presence of creation operators that mixes up species and we cannot rewrite \eqref{W-charges-Bad} in such a simple form.
 \subsubsection{Proof of \eqref{SteadyState-W-Good}}
-To prove \eqref{SteadyState-W-Good} we do four steps. 
+We prove \eqref{SteadyState-W-Good} in four steps. 
 \paragraph{1. Useful relations}
-We introduce the following notation:
+We recall the following notation, already used in \eqref{Tau-Notation}:
 \begin{equation}
@@
 \end{equation}
-We first write some relations that will be useful in the proof:
+We first write and prove some relations that will be useful:
 \begin{itemize}
@@
 \begin{equation}
-	D_{i,j}^{2L}||N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
+	D_{i,j}^{2L}|N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
 \end{equation}
@@
 \begin{equation}\label{Dii-ref}
-	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
+	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}|\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
 \end{equation}
@@
 \begin{align}
-	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
-	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
+	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber\\&=
+	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber
 	\\&=
@@
 \begin{align}
-	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)-2\sum_{\ell=0\;\ell\neq i}B_{\ell}^{2L-1}D_{\ell,i}\right\}\nonumber\\&
+	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)\right.\nonumber\\&\left.-2B_{i}^{2L-1}\sum_{\ell=1\;\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right\}|\Psi_{0}^{0}\rangle
 	\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
@@
 \end{flushright}
-Observe that \eqref{Two-Relation} also implies that 
+Observe that \eqref{Two-Relation} also implies
 \begin{equation}\label{Commutativity-Gained}
@@
 \end{align}
-We have that, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},
+Moreover, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},
 \begin{align}
@@
 \end{equation}
-Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have that, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 
+Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 
 \begin{align}
@@
 Describe eigenvalues of $T_0$ following 
-\cite{Belliard2} 
+\cite{belliard2} 
 \subsection{A sequence of similarity transformation}
 In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$.
-Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one as
+Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one (i.e.
+$H_{0}$) as
 \begin{equation}
@@
 \end{equation}
-As a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
+As a consequence for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
 \begin{equation}
@@
 \appendix
+{\color{blue}
 \section{Oscillator realization}\label{appA}
@@
 \end{equation} 
-fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} 
+fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
 \section{Exact steady state of $H$}\label{appB}

### 2023-09-15 main.tex
sdf

@@
 \section{Extensions for the non-integrable chain}
+In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
 The aim of this section is studying some extension to the analysis previously done when integrability property is lost.
-In particular, Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.
-This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$. For the sake of simplicity we still study the geometry of chain and we provide the following extensions: 
+We fix $\nu>1$ and, for the sake of simplicity, we still study the geometry of chain.
+We provide the following extensions:
 \begin{enumerate}
@@
 Subsection \ref{Subsection-ss-nonI}.
-	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we can define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+Also for this thermalized process we prove duality.
 Subsection \ref{Subsection-Thermalized}.
@@
 \subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}
-We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs. Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types. The generator reads
+We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs.
+Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
+The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and the generator reads
 \begin{equation}
@@
 \end{equation} 
-where at the boundaries 
+The bulk is 
+\begin{equation}
+	\mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+while at the boundaries 
 \begin{equation}
@@
 \end{equation}
-while the bulk generator is 
-\begin{equation}
- \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space
+This process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
  \begin{equation}	
@@
 \end{equation} 
-with absorbing boundaries, i.e. 
+where the boundaries are absorbing, i.e. 
 \begin{equation}
@@
 all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
-This implies that, the chain is eventually void and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following.
+This implies that, the chain is eventually voided and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following.
 We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
 We assume that it is initially distribute with a configuration $\bm{n}$.
-For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m-1\}$.
+For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m\}$.
 The following chain of equalities holds
@@
 \end{equation}
-and where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\hat{\xi}_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
+ are called the \textit{absorption probabilities}, i.e.
+the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$.
+Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
 The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
@@
 \end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$.
-This expectation is computed by \eqref{ExptationSS} once the absorption probabilities is known.
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$.
+This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities is known.
 The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve.
@@
 \paragraph{One point correlations for the non-integrable case}
-We have that $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
+We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
 \begin{equation}
@@
 \end{equation}
-Thus
+The average occupation reads
 \begin{equation}\label{OnePtsCORR}
@@
 \end{equation}
-we want to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
-Therefore, this $\mathcal{P}(1,\delta_{s}^{y})$ fulfils the following equations
+To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
+This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
 \begin{equation}\label{gamblers-ruin}
@@
 where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved.
-Therefore, using \eqref{OnePtsCORR} and $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
+The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
 \begin{equation}
@@
 	\end{equation}
-The right boundary generator is defined in a similar way. The $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
+The right boundary generator is defined in a similar way, where $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
 \subsubsection{The dual thermalized process}
@@
 \end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 
+where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 
 \begin{equation}
@@
 \end{equation}
-and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$. 
-The duality function is 
+and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$, but acting on the site $L$. 
+The duality function is the same, i.e.
 \begin{equation}

### 2023-09-15 main.tex
lll

@@
 \begin{equation}\label{2SpeciesRD}
-	\partial \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)
+	\frac{d}{dt} \rho_{a}(x,t)=\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\sigma_{12}\Delta_{L}\rho_{\overline{a}}(x,t)+\Upsilon\left(\rho_{\overline{a}}(x,t)-\rho_{a}(x,t)\right)
 \end{equation} 
@@
 \begin{enumerate}
-		\item Is it possible to extend the results to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
+		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
 			\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
@@
 \end{enumerate}
-The aim of this section is to answer to these questions.
-We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term.
-Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
+Therefore, we aim to find a process whose average occupations $\rho_{a}(x,t)$ for any species $a\in\{1,\ldots,N-1\}$ evolve as a system of difference differential equation given by 
+\begin{equation}\label{NSpeciesRD}
+	\frac{d}{dt} \rho_{a}(x,t)=\nu\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\nu\sigma_{12}\sum_{b=1,b\neq a}^{N-1}\Delta_{L}\rho_{b}(x,t)+\Upsilon\sum_{b=1,b\neq a}^{N-1}\left(\rho_{b}(x,t)-\rho_{a}(x,t)\right)
+\end{equation} 
+ We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{L}$ and $\rho_{a}^{R}$ for all $a\in\{1,\ldots,N\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{L}=\nu$.
+In the following of this section we answer to these questions.
+We first define the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$.
+Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
 \subsubsection{The process on a chain}
@@
 \begin{equation}\label{edgeGeneratorRD}
-	\mathcal{L}_{x,x+1}^{rd}=\sigma_{11}\mathcal{L}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,x+1}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,x+1}^{m}
+	\mathcal{L}_{x,x+1}^{rd}=\nu \sigma_{11}\mathcal{L}_{x,x+1}+\nu \sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,x+1}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,x+1}^{m}
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
-\end{equation}
-The site generator reads
+	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N-1}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
+\end{equation}
+The left boundary generator reads
 \begin{equation}
@@
 \end{equation}
-where the boundary parameters are defined as
+where the $\alpha$'s parameters are defined in function of the given boundary condition of the difference-differential system:
 \begin{equation}\label{boundaryParamRD}
 	\begin{split}
-		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
+		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{L}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\\
 		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}
@@
 \end{equation}
-and where, for every $x\in V$, we further assume that
-\begin{equation}
-	\sum_{a=1}^{N}\rho_{a}^{x}=\nu
-\end{equation}
 The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s. \\ \\
-\textbf{Remark}: observe that the site generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
-We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}$, as specified above.
+\textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
 \paragraph{Action on the occupation variable of $\mathcal{L}_{x,+1}^{rd}$}
@@
 \begin{equation}
-	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=2}^{N}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N}(n_{b}^{x}-n_{d}^{x})
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
 \end{equation}
@@
 \end{equation}
-Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{2,\ldots,N\}$
+Using equation \eqref{actionGraphRD} we have that $\forall x\in \{1,\ldots,L-1\}$ and $\forall d\in\{1,\ldots,N-1\}$
 \begin{equation}\label{DifferenceEquation}
-	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{c=2\,:\,c\neq d}^{N}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{c=2}^{N}(n_{c}^{x}-n_{\alpha}^{x})
+	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{c}^{x}-n_{\alpha}^{x})
 \end{equation}
@@
 \begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{c=2\,:\,c\neq d}^{N}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{c=2\,:\,c\neq d}^{N}\left(n_{c}^{1}-n_{d}^{1}\right)
-\end{equation}
-On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $a$ at site $x$ as
+	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq d}^{N-1}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{c}^{1}-n_{d}^{1}\right)
+\end{equation}
+On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $d$ at site $x$ as
 \begin{equation}
@@
 \begin{equation}
-	\rho=\rho_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{N}}{\alpha_{1}+(N-1)\alpha}
+	\rho=\rho_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
 \end{equation}
@@
 \begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{1}^{n_{1}^{x}}
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{N}^{n_{N}^{x}}
 \end{equation}
@@
 For fixed edge $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators the computation is similar.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$; the detailled balance reads
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b,\in\{1,\ldots,N-1\}$; the detailled balance reads
 \begin{equation}
@@
 \end{equation}
-that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{2,\ldots,N\}$.\\
+that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{1,\ldots,N-1\}$.\\
 By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,x+1}$.
 \\
-For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$.
-As a consequence we have the result.
+For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$.
 \subsubsection{Duality for the reaction-diffusion process}
@@
 \begin{equation}
-	\bm{\xi}=\left(\xi_{2}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
+	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
 \end{equation}
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
+and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 
 the extra-site $0$ connected to $1$ and similarly for $xi_{a}^{L+1}$. \\
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
 \end{equation}
@@
 $\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator} and specialized for sites $x=1$ and $x=L$.
-\newline
-\newline
-\textbf{Remark}: the generator $\mathcal{L}^{rd}$ has a dual $\widetilde{\mathcal{L}}^{rd}$ with respect to the same duality function \eqref{dualityElements} of the multi-species stirring process.
-The dual process has absorbing boundaries while it performs the same edge dynamics of $\mathcal{L}^{rd}$.
-As we will show this follows from a $gl(N)$ algebraic structure.
+Observe that the generator $\widetilde{\mathcal{L}}^{rd}$ has the same dynamics as $\mathcal{L}^{rd}$ in the bulk, while the boundaries are absorbing. 
 \subsubsection{Proof of duality}
+The duality between the boundary generators is trivial, because they have the same form of \eqref{siteDualGenerator}, up to a specific choice of the parameters.
+Therefore we only need to prove the duality relation for the bulk generator.
 In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
@@
 \end{equation}
-Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$.
-For the edge dynamics, the original and the dual Hamiltonians do coincide, while the boundary ones are again $\widetilde{H}_{left},H_{right}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show
-\begin{equation}\label{DualityRelationRD}
-	(H^{rd})^{T}D=D\widetilde{H}^{rd}
-\end{equation}
-Therefore, we need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
+We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
 \begin{align}
-	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}\\
-	H_{left}^{T}D&=D\widetilde{H}_{left}D\label{siteDualityRelationRD}
-\end{align}
-and similarly for $H_{right}$.
-The duality matrix $D$ is again \eqref{dualityMatrix}.
-As already pointed out, $H_{left}$ and $\widetilde{H}_{left}$ have the same structure (up to a specific choice of the reservoirs parameters) therefore the duality relation for the boundaries is proved.
-However, $\mathcal{H}_{x,x+1}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$.
-Therefore, we only need to show that
+	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
+\end{align}
+That is equivalent of showing 
 \begin{align}
@@
 Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x})}$ as a symmetry.
-The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$.
+The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 \end{flushright}
-With this prove we answered the second and third questions stated at the beginning of this section. \\
 \begin{comment}
@@
 	The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
+\begin{comment}
 	{\color{blue}
@@
 	}
-	\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $\tau_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
+\end{comment}
+\newline \newline
+	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
 	\begin{equation}\label{LinkABS-corr}
@@
 	\begin{equation}\label{S1-L1}
-		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},N}\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},N}\sum_{d_{1}=1}^{N-1}e_{1}^{d_{1}}
 	\end{equation}
@@
 			\\&
-			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
+			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
 		\end{split}
@@
 \\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
 			\\&\otimes
-			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=2}^{N}e_{1}^{d_{L+1}}\right\}
+			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
 			\\&=
@@
 \\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
 		\end{align*}
@@
 				\\&
-				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{r}}=2}^{N}\Psi{'}(\eta_{1},\ldots,\eta_{L})
+				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})
 			\end{split}
@@
 		\end{equation}
+	\begin{comment}
 		{\color{blue}
@@
 				\end{split}
-		\end{equation}} indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
+		\end{equation}} 
+	\end{comment}
+indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
 Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}.

### 2023-09-17 main.tex
Exchange Upadate

@@
 	\end{equation}
-
+\item for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
+\begin{equation}\label{EX4}
+	\begin{split}
+		D_{i,j}(x)B_{i}(y)=&-(x-y)h_{1}(x,y)B_{i}(y)D_{i,j}(x)+f_{2}(x,y)\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(y)D_{k,j}(x)\\+&\frac{1}{(x-y)}\left(B_{j}(y)D_{i,i}(x)-B_{j}(x)D_{i,i}(y)\right)\\+&\frac{1}{2}h_{3}(x,y)\left((1+x-y)B_{j}(x)D_{N,N}(y)-B_{j}(y)D_{N,N}(x)\right)
+	\end{split}
+\end{equation}
+and
+\begin{equation}\label{EX5}
+	D_{i,j}(x)B_{j}(y)=\frac{(x-y)}{(x-y-1)}B_{j}D_{i,j}(x)+\frac{1}{(y+1-x)}D_{i,j}(y)B_{j}(x)
+\end{equation}
+\item  for every $i,j,k\in \{1,\ldots,N-1\}$ such that $i\neq j\neq k$
+\begin{equation}\label{EX6}
+	D_{i,j}(x)B_{k}(y)=B_{k}(y)D_{i,j}(x)+\frac{1}{(x-y)}\left(B_{k}(y)D_{j,i}(x)-B_{k}(x)D_{j,i}(y)\right)
+\end{equation}
 \end{itemize}
@@
 \paragraph{Exchange relations between charges}
-Using \eqref{EX1}, \eqref{EX2} and \eqref{EX3} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
+Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
 \begin{equation}\label{ExQ0B-charges}

### 2023-09-18 main.tex
figure

@@
 Maximal occupation is $\nu=6$.
-A particle of type "square" is removed in $x$ and placed in $y$.
-A particle of type "triangle" is removed in $y$ and placed in $x$.
-This transition occurs at rate $n_{square}^{x}n_{triangle}^{y}=2\cdot 3$.}
+A particle of type $2$ is removed in $x$ and placed in $y$.
+A particle of type $3$ is removed in $y$ and placed in $x$.
+This transition occurs at rate $n_{2}^{x}n_{3}^{y}=2\cdot 3$.}
     \label{fig:1}
@@
 Here the maxiaml occupation is $\nu=6$.
-The reservoir, represented by a square "box" containing all types of particles, remove a type "square" from site $x$ and replace it with a type "triangle".
-This transition occurs at rate $\alpha_{triangle}^{x}n_{square}^{y}$.}
+The reservoir, represented by a square "box" containing all types of particles, remove a type $2$ from site $x$ and replace it with a type $3$.
+This transition occurs at rate $\alpha_{3}^{x}n_{2}^{x}$.}
     \label{fig:2}
@@
 The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
-{\color{red} Is this remark relevant for us?}
-\newline 
-\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
+%{\color{red} Is this remark relevant for us?}
+%\newline 
+%\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
 \\ \\
@@
 Following the result in the simpler $gl(2)$ case, we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
-We obtain that, using also the multi-variate version of \eqref{veryUsefulSeries},
+Using also the multi-variate version of \eqref{veryUsefulSeries}, we obtain
 \begin{equation}
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
+		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{q}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
 	\end{split}
@@
 \appendix
+\begin{comment}
 {\color{blue}
@@
 fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
+\end{comment}
 \section{Exact steady state of $H$}\label{appB}

### 2023-09-20 main.tex
check partial

@@
 \newcommand{\id}{I}
-\newcommand{\Xt}{\tilde{X}}
+\newcommand{\Xt}{\widetilde{X}}
 
@@
 We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have
-\begin{equation}
+\begin{equation}\label{duality-expectation}
     \mathbb{E}_{\eta}\left[D(\eta_{t},\xi)\right]=\mathbb{E}_{\xi}\left[D(\eta,\xi_{t})\right]
@@
 \end{flushright}
-\subsection{Duality for the integrable process on a line segment}
+\subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}
+As already pointed out in Subsection \ref{statementDualitySubsection}, the dual process voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites and replacing them by types $N$.
+This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
+Here we consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs.
+Each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
+The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and the generator reads
+\begin{equation}
+	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}
+\end{equation} 
+The bulk is 
+\begin{equation}
+	\mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+while at the boundaries 
+\begin{equation}
+	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
+\end{equation}
+We specialize the results of Subsection \ref{statementDualitySubsection} to this chain. The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
+\begin{equation}	
+	\widetilde{\Omega}=N_{0}^{N}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
+\end{equation}
+whit dual generator
+\begin{equation}
+	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
+\end{equation} 
+where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundaries are absorbing, i.e. 
+\begin{equation}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{N}^{1}+\bm{\delta}_{a}^{0})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{N}^{L}+\bm{\delta}_{a}^{L+1})-f(\bm{\xi})\right)
+	\end{split}
+\end{equation}
+where $0$ and $L+1$ are the extra-sites. The duality function reads
+\begin{equation}\label{dualityFunctionChain}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
+The dual process has absorbing boundaries, i.e.
+all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
+This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
+We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+We assume that it has an arbitrary configuration $\bm{n}$.
+For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
+The following  equalities holds thanks to the duality relation \eqref{duality-expectation}:
+\begin{equation}\label{ExptationSS}
+	\begin{split}
+		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\\&=
+		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
+	\end{split}
+\end{equation}
+where 
+\begin{equation}\label{Pass}
+	\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+are called the \textit{absorption probabilities}, i.e.
+the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$.
+Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
+The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
+\begin{equation}
+	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{k}\in\{1,\ldots,N-1\}$ situated at sites $y_{k}\in\{1,\ldots,L\}$ with $k\in \{1,\ldots,m\}$.
+This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
+The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the simplest case of one point correlations, since the single dual particle behaves as an independent random walker.
+\paragraph{One point correlations for the $\nu\geq 1$ case}
+We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}
+\end{equation}
+The average occupation reads
+\begin{equation}\label{OnePtsCORR}
+	\begin{split}
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+	\end{split}
+\end{equation}
+To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
+This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
+\begin{equation}\label{gamblers-ruin}
+	\begin{cases}
+		\Delta_{y}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
+		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
+		\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
+	\end{cases}
+\end{equation}
+where $\Delta_{y}^{L}$ is the discrete Laplace operator on the chain of length $L$.
+The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}
+\end{equation}
+\textbf{Remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+\end{equation}
+that is the same result obtained in \cite{vanicat2017exact}. 
+\\
+\\ Already for two-point correlations the computations become more involving and hard to solve.
+In the following we specialize the chain to the integrable case $\nu=1$.
+As it will be shown, in such a situation the non-equilibrium steady state correlations can be computed with different techniques exploiting the integrability of the process (matrix product ansatz and quantum inverse scattering method) combined with duality and, as a by-product, all absorption probabilities can be explicitly found.
+\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
 Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}.
-In this setting the extra-sites are denoted by $0$ and $L+1$, connected respectively with sites $1$ and $L$ of the chain.
-Moreover, the matrix $R_{x}$ defined in \eqref{Revmatrix}
-reduces to the identity which implies 
+We recall that the geometry is again a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$, but with the hard-core exclusion rule, i.e.
+$\nu=1$.
+The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$.
+Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted.
+The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively.
+The matrix $R_{x}$ defined in \eqref{Revmatrix}
+reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
 \begin{equation}\label{transpostionPropertyFund}
@@
 \end{equation}
-Therefore, the duality matrix reads
+Therefore, duality matrix reads
 \begin{equation}
@@
 \end{equation}
-and the dual Hamiltonian 
-\begin{equation}
-	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
-\end{equation}
-where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
-\begin{equation}
-	\widetilde{H}_{left}=|\alpha|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=|\alpha|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)
-\end{equation}
-In the long-time limit, the dual process voids the chain, and all particles are eventually absorbed at the extra-sites $0$ and $L+1$.\\
-In this situation the elements of the duality matrix \eqref{dualityElements} read
+and its elements are given by
 \begin{equation}\label{ElementsDualityMatrixChain}
@@
 \end{equation}
-Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the so called absorption probabilities.
-Consider a dual configuration $\hat{\xi}:=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ where $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ for every $k\in\{1,\ldots,m\}$.
-Considering an arbitrary $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\hat{\xi}$ read
-\begin{equation}
-	D(\bm{n},\hat{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{a_{k}}^{x_{k}}=1\}}
-\end{equation}
-To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
+The dual Hamiltonian is
+\begin{equation}
+	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
+\end{equation}
+where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
+\begin{equation}\label{boundary-H-dual-chain}
+	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)
+\end{equation}
+In the long-time limit the dual process voids the chain, i.e.
+all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$.
+We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
+This simplification will be crucial in Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping}.\\
+
+Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
+Consider a dual configuration $\bm{\hat{\xi}}:=\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}}$ where $s_{k}\in\{1,\ldots,N-1\}$ and $y_{k}\in\{1,\ldots,L\}$ such that $y_{k}<y_{k+1}$ for every $k\in\{1,\ldots,m\}$.
+Fix an arbitrary initial configuration $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\bm{\hat{\xi}}$ read
+\begin{equation}
+	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{s_{k}}^{s_{k}}=1\}}
+\end{equation}
+Repeating the argument of Subsection \ref{Subsection-ss-nonI} and denoting the $m$-point correlations by $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}$ we have 
+%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
 Therefore, we have the following equalities
@@
 	\begin{split}
-	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{stat}&=\mathbb{E}_{stat}\left[D(\bm{n},\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\hat{\xi}(t))\right]
-	\\&=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
+	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
+	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
 \end{split}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{a}\delta_{0}+(1-c_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
-\end{equation}
-and they are called \textit{absorption probabilities}, namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $a_{k}$ absorbed at left and $1-c_{k}$ absorbed at right.
+	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta_{0}+(1-c_{k})\delta_{L+1}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+ namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ absorbed at right.
 Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
@@
 \section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
-In this section we aim to use duality and the matrix product ansatz to determine the non equilibrium steady state and its arbitrary correlation for the integrable version of the multi-species stirring process, defined in Subsection \ref{subsection-description-process-LINE}.
+In this section we aim to use duality and the matrix product ansatz to determine the non equilibrium steady state and its arbitrary correlation for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
 As it will turn out, duality simplifies the commutation relations of the matrix product ansatz allowing to determined a closed formula for all correlations.
@@
 \end{equation}
-This Markov chain is positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial distribution. 
+This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial distribution. 
 We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution. This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
@@
 However, to write explicitly the steady state one should provide a representation of this algebra.
-Another approach is to directly use the commutators and and the boundary actions compute the steady-state correlations.
+Another approach is to directly use the commutators and and the boundary actions compute correlations.
 This path has been followed in \cite{vanicat2017exact} to compute one-point and two-point correlations.
-Here we follow the same approach. We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the actual
+Here we follow the same approach. We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the
 computation. The idea is summarized as follows. We define a sequence of similarity transformation such that 
@@
 
-The first transformation $S_{1}$ is closely related to the dual matrix.
-Moreover, we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
+The first transformation $S_{1}$ is closely related to the dual matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
 Therefore, $H^{'}$ is not stochastic.
 The second transformation $S_{2}$ diagonalize the right boundary.
-The composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
+Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
 \\
@@
 Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ thanks to the simpler commutators.
-Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and  the arbitrary correlations and the absorption probabilities.
-The explicit expression of the steady state of $H$ is reported in appendix \ref{appB}.
+Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and  the arbitrary correlations in the non-equilibrium steady state.
+The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix \ref{appB}.
 
@@
 \end{equation}
-\textbf{Remark:} the boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
+\textbf{Remark:} the boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e.
+to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
 They are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp.
@@
 the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal.
-The expressions of $H_{left}^{''}$ and $H_{right}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{c1}$ and $A=e_{aN},$ and $A=e_{aa}$.
+The expressions of $H_{left}^{''}$ and $H_{right}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A=e_{aN},$ and $A=e_{aa}$.
 We compute
@@
 \end{equation}
-It is convenient to introduce also the transformation
+It is convenient to introduce also the whole transformation
 \begin{equation}\label{similarity}
@@
 \begin{equation}
-    \delta_{\tau_{x},1}:=\begin{cases}
+    \delta_{\tau_{x},N}:=\begin{cases}
         N\quad \text{if}\quad \tau_{x}=N\\
@@
 \end{equation} 
-Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ is written as:
+Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as:
 \begin{equation}\label{toDetermineTilde}
@@
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
-Knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
+By knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
 \begin{equation}\label{ABS-vect}
@@
 
-\subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}
-We consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs.
-Now, each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
-The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and the generator reads
-\begin{equation}
-	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}
-\end{equation} 
-The bulk is 
-\begin{equation}
-	\mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-while at the boundaries 
-\begin{equation}
-	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
-\end{equation}
-This process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
- \begin{equation}	
-	\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N-1}
-\end{equation}
-whit dual generator
-\begin{equation}
-	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
-\end{equation} 
-where the boundaries are absorbing, i.e. 
-\begin{equation}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{a}^{0}+\bm{\delta}_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{a}^{L+1}+\bm{\delta}_{a}^{L})-f(\bm{\xi})\right)
-	\end{split}
-\end{equation}
-where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
-\begin{equation}\label{dualityFunctionChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-The dual process has absorbing boundaries, i.e.
-all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
-This implies that, the chain is eventually voided and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
-We assume that it is initially distribute with a configuration $\bm{n}$.
-For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m\}$.
-The following chain of equalities holds
-\begin{equation}\label{ExptationSS}
-	\begin{split}
-		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
-		\\=&
-		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
-	\end{split}
-\end{equation}
-where 
-\begin{equation}\label{Pass}
-\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi_{0}}=\hat{\bm{\xi}}\right)
-\end{equation}
- are called the \textit{absorption probabilities}, i.e.
-the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$.
-Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
-The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
-\begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{x}}^{y_{x}}}{(\nu-m+1)}
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$.
-This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities is known.
-The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the one points correlations.
-\paragraph{One point correlations for the non-integrable case}
-We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}
-\end{equation}
-The average occupation reads
-\begin{equation}\label{OnePtsCORR}
-	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
-	\end{split}
-\end{equation}
-To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
-This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
-\begin{equation}\label{gamblers-ruin}
-	\begin{cases}
-		\Delta_{x}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
-		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
-	\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
-	\end{cases}
-\end{equation}
-where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}
-\end{equation}
-\textbf{Remark}: In case $|\alpha|=|\beta|=1$ we have 
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-\end{equation}
-that gives back \eqref{one-pts-corr}.
 \subsection{Instantaneous thermalization}\label{Subsection-Thermalized}

### 2023-09-20 main.tex
jkl

@@
     	\begin{split}
-    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
+    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\right.
     		\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     		\\&+\left.
-    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
+    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L-1},\ldots,\varphi_{L}^{L-1}}
     		\right. \\&+ \left. 
-    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
+    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}} \right\}
     	\end{split}
@@
 \begin{equation}
-	\varphi_{x}(q_{1},\ldots,q_{L})=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{L}\}\\
+	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\
 		N\qquad &\text{otherwise}\\
@@
 \end{equation}
-The dependence of $\varphi_{x}(q_{1},\ldots,q_{L})$ with respect to $q_{1},\ldots,q_{L}$ is usually understood for the sake of notation.
+where $i\in\{1,\ldots,L\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
     We prove it by induction. When $L=1$ it is true, indeed
@@
     	%\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right.
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L-1},\ldots,\varphi_{L}^{L-1}}
     	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
+    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}} \right\}
     	\\&
@@
     	\\&=
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\right.
+    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{1},\ldots,\varphi_{L+1}^{1}}\beta_{\tau_{q_{1}}}\right.
     	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{2},\ldots,\varphi_{L+1}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L},\ldots,\varphi_{L+1}^{L}}
     	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}} \right\}
+    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L+1},\ldots,\varphi_{L+1}^{L+1}} \right\}
     	\\&=
@@
 	\begin{split}
-\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
+\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
   \\&+
-  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
+  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
 	\end{split}
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{q_{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
+		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
 	\end{split}
@@
 \begin{equation}
-  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)
+  \left(1+\sum_{j=y}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)
 \end{equation}
@@
     \begin{equation}
-\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)\right)^{1-\delta_{\tau_{y},1}}
+\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)\right)^{1-\delta_{\tau_{y},N}}
 \end{equation}
@@
 \begin{equation}
-	c_{y}=(1-\delta_{\tau_{y},1}) \qquad \forall y\in \{1,\ldots L\}
+	c_{y}=(1-\delta_{\tau_{y},N}) \qquad \forall y\in \{1,\ldots L\}
 \end{equation}
@@
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
-In each of these points there is a particle of species $a_{i}\in \{1,\ldots,N-1\}$.
+In each of these points there is a particle of species $s_{i}\in \{1,\ldots,N-1\}$.
 Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
 \begin{equation}\label{exactCorrelations}
-		\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
+		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
 	\end{equation}
@@
 \begin{split}
-\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=&
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&
 \sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\
+f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\
 =&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})
+f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})
 \end{split}
@@
 \begin{split}
-\langle n^{y_{1}}_{a_{1}}\cdots n^{y_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
-=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
+=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})
 \end{split}
@@
 \end{equation}
-where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{a_{i}}^{x_{i}}$.  
-\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $a_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$.
-We aim to compute the non-equilibrium stationary state correlation $\langle n_{a_{1}}^{y_{1}}\cdots n_{a_{m}}^{y_{m}} \rangle_{stat}$.
+where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{s_{i}}^{y_{i}}$.  
+\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$.
+We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$.
 By using duality, we showed in \eqref{CorrelationByABS-prob} that
  \begin{equation}
- 	\langle n_{a_{1}}^{y_{1}}\cdots n_{a_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
- \end{equation} 
-Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=a_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 
+ 	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
+ \end{equation} 
+where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
+Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=s_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 
 \begin{equation}

### 2023-09-20 main.tex
rty

@@
 The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator.
+\\
+ For a complete review of the quantum inverse scattering method see \cite{Sklyanin:1988yz} and \cite{faddeev1996algebraic}.
+For application of the QISM to interacting particle systems we refer to \cite{frassek2020eigenstates,frassek2019non,frassek2022exact,vanicat2017exact}.
+\\
 \paragraph{Organization of the paper}
@@
 \paragraph{One point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
-\begin{equation}
-	\langle n_{a_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,y_{1},c_{1})
+The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
+\begin{equation}
+	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})
 \end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-\langle n_{a_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}
+\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}
 \end{equation}
 \paragraph{Two points correlations}
-The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
-\begin{equation}
-	\begin{split}
-	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})
+The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+\begin{equation}
+	\begin{split}
+	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})
 	\end{split}
@@
 	\begin{split}
-	\langle n_{a_{1}}^{y_{2}} n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})
+	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
 	\end{split}
@@
 	\begin{split}
-		\langle n_{a_{1}}^{y_{2}} n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}]-\mathbb{E}[n_{a_{1}}^{y_{1}}]\mathbb{E}[n_{a_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)
+		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
 	\end{split}
@@
 \paragraph{Three points correlations}
-The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
-\begin{equation}
-    \langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})
+The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
+\begin{equation}
+    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})
 \end{equation}
@@
 \begin{align}\label{three-pts-corr}
-        \langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
+        \langle n_{a_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
         \\&+\nonumber
-        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}
+        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
         \\&+\nonumber
-        \frac{(L-x_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}
+        \frac{(L-x_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
         \\&+\nonumber
-        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}
+        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
         \\&+\nonumber
-        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}
+        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
         \\&+\nonumber
-        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
+        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
 \end{align}
@@
 \begin{align}
-	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{a_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{a_{3}}^{y_{3}}n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{a_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{y_{3}}\right]
-	\\&=
-	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})
+	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
+	\\&=
+	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
 \end{align}
@@
 \cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}} \\
-In Subsection \ref{subsection-exact}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations.
+In Section \ref{sectionIntegrabiliy}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations.
 To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal.
@@
  We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}=\sum_{x=1}^{L}n_{i}^{x}$, i.e.
-it means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
+$m_{i}$ indicates the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
 Observe that $|\bm{m}|=\sum_{i=1}^{N}m_{i}=L$.
-We call $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
+We denote by $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
 We prove that
@@
 \end{equation}
-In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix with $\epsilon>0$ and arbitrary, then we chose $z=\mathcal{E}_{\bm{m}}+\epsilon$, 
+In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix an arbitrary $\epsilon>0$ and consider $z=\mathcal{E}_{\bm{m}}+\epsilon$, 
 \begin{equation}
@@
 \end{equation}
-we sum over all possible $\bm{m}$'s 
-\begin{equation}
-	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
-\end{equation}
-we multiply both sides by $\epsilon$ 
-\begin{equation}
-	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
-\end{equation}
-we take the limit for $\epsilon\to 0$ on both sides 
+by summing over all possible $\bm{m}$'s such that $|\bm{m}|=L$ and multiply by $\epsilon$ both sides
+%\begin{equation}
+%	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+%\end{equation}
+%we multiply both sides by $\epsilon$ 
+\begin{equation}
+	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.
+\end{equation}
+We take the limit for $\epsilon\to 0$ on both sides 
 \begin{equation}
@@
 \end{equation}
-Observe that, trivially,
+We first observe that
 \begin{equation}
@@
 \end{equation}
-and using the following power expansion
+Second, using the power expansion
 \begin{equation}\label{veryUsefulSeries}
@@
 \end{equation}
-we have that for each $\bm{m}$ 
+we have that, for each $\bm{m}$, 
 \begin{equation}
@@
 \end{equation}
-therefore the limit of the product is the product of the limit and we obtain that 
+Since both factor are finite, the limit of the product is the product of the limit and we obtain
 \begin{equation}
@@
 \end{equation}
-Since the limit of the sum is the sum of the limit we have   
+Since the limit of the sum is the sum of the limit   
 \begin{equation}
@@
 \end{equation}
-thus 
+Recalling that $|\Psi_{\bm{m}}^{0}\rangle$ are the eigenvectors with eigenvalue $\mathcal{E}_{\bm{m}}$ of $H_{0}$ we have 
 \begin{equation}
@@
 \end{equation}
-Formula \eqref{W-extended} may be evaluated by perturbation theory.
-Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz.
-This expression, as it will be shown in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
-To write formula \eqref{W-extended} using the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM).
-This will be presented in Subsection \ref{SubsectionQISM}.
-In Subsection \ref{SubsectionGL2} we first present the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$.
+Formula \eqref{W-extended} may be evaluated by perturbation theory (see \cite{frassek2020duality}).
+Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system.
+This expression allows a simpler treatment of the mapping and allows also to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
+To write formula \eqref{W-extended} through the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}).
+In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$.
 \subsection{Quantum inverse scattering method}\label{SubsectionQISM}
@@
 \end{equation}
-where the lower index $a$ means that they are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$, for $a\in\{0,\ldots,L\}$ and where $x,y\in\mathbb{C}$ are called spectral parameters.
+where the lower index $a\in\{0,\ldots,L\}$ means that these matrices are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$.
+Variables $x,y\in\mathbb{C}$ are called spectral parameters.
 The above matrices satisfy:
@@
 with $C_{1},C_{2}>0$. \\
-The double row monodromy $U_{0}(x)$ is given by
+The matrix $U_{0}(x)$ used to construct $T(x)$ is called double row monodromy and it is given by
 \begin{equation}
@@
 
-We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename its elements, each of them acting on the quantum space $V$, has follows
+ $U_{0}(x)$ can be written in the canonical basis of $V_{0}$ 
 \begin{comment}
@@
 \end{comment}
-\begin{equation}
+\begin{equation}\label{matrixForm-U}
 	U_{0}(x)=\begin{pmatrix}
@@
 \end{equation}
-The exchange relations for the elements of the above matrix can be found using \eqref{RURU} and they read:
+where each of the above element acts on the quantum space $V$. These element satisfy some \textit{exchange relations} that can be found by \eqref{RURU} and they are given by: 
 \begin{itemize}
@@
 \subsection{Charges}
-The transfer matrix $T^{\Delta}(x)$ reads
-\begin{equation}
-	\begin{split}
-		T^{\Delta}(x)=%tr_{0}&\left(\begin{pmatrix}
+Using the matrix form of $U_{0}(x)$ written in \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads
+\begin{equation}
+	\begin{split}
+		T(x)=%tr_{0}&\left(\begin{pmatrix}
 			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
@@
 \end{equation}
-By construction,$T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
+By construction, $T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$, i.e. 
 \begin{equation}
@@
 \end{equation}
-where, for all $k\in\{0,\ldots,2L+2\}$, we call $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
+where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
 \begin{equation}
@@
 \end{equation}
-Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
-\begin{equation}
-	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
-\end{equation}
- In the following we will study the charge expansion of $T^{\Delta}(x)$ when $x\to \infty$.
-As it will be clear in the following, only the first three coefficients for the diagonal elements and only the first one for the non-diagonal elements will be needed.
+Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ as 
+\begin{equation}
+	D_{N,N}(x)=\sum_{k=0}^{2L+1}D_{N,N}^{k}x^{k}\quad D_{i,i}(x)=\sum_{k=0}^{2L+1}D_{i,i}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}\quad D_{i,j}(x)=\sum_{k=0}^{2L}D_{i,j}^{k}x^{k}
+\end{equation}
+ In the following we will need the charge expansion of $T(x)$.
+As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed.
 Therefore, using \eqref{RURU}, we compute:
@@
 	\item For $D_{N,N}(x)$: 
-
 \begin{equation}
@@
 \end{itemize}
-\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
+\textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
 Using these polynomial expansions we write the first three charges
@@
 \end{align}
-The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
+The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
 By construction it follows that 
@@
 \end{equation}
-The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
-We introduce the following:
+while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
 \begin{equation}
@@
 \end{equation}
-where $\Delta_{i}=(\alpha_{i}-\beta_{i})$. 
-Therefore we can write 
+where, for the sake of notation we denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we can write 
 \begin{equation}
@@
 This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
-We denote it by $\hat{C}_{2}^{N-1}$ and it reads
+We denote it by $\hat{C}_{2}^{N-1}$, i.e.
 \begin{equation}
@@
 \end{equation} 
-We denote its eigenvector by $C_{2}^{N-1}$.
+We denote its eigenvalues by $C_{2}^{N-1}$.
 Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$.
-The Bethe states belong to the configurations space, and thus we can write them as a direct sum of vectors, each belonging to an irreducible representation of $gl(N)$.
-On these irreducible vectors .
-$\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
+As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$.
+On these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
 \begin{equation}
@@
 \Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
-\\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)(L-m_1)+2C_{2}^{N-1}\right)x^{2L}+\ldots
-\end{split}
-\end{equation} 
+\\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_N+1)-(N+2)(L-m_N)+2C_{2}^{N-1}\right)x^{2L}+\ldots
+\end{split}
+\end{equation} 
+where we denote by 
+\begin{equation}
+	\Lambda_{\bm{m}}:=N+2m_1(m_N+1)-(N+2)(L-m_{N})+2C_{2}^{N-1}
+\end{equation}
+the eigenvalues for arbitrary $\bm{m}$ of $Q_{0}^{2L}$. 
+\begin{comment}
 {\color{blue}
@@
 \end{equation} }
-\paragraph{Exchange relations between charges}
-Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
+\end{comment}
+\paragraph{Exchange relations between charges} Since, in general, the coefficients of the polynomial form of the elements of $U_{0}(x)$ and the charges do not commute, it is useful to find explicit exchange relations among them.
+Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain:
+\begin{itemize}
+	\item 
+for every $i,j\in\{1,\ldots,N-1\}$ 
 \begin{equation}\label{ExQ0B-charges}
@@
 \end{equation}
-While, for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j$, $k\neq i,h$
+\item  for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j\neq k\neq i,$
 \begin{equation}\label{Commuting-Charges}
@@
 \end{equation}
+\end{itemize} 
 %{\color{blue}Using them we also have 
@@
 \subsection{Conserved charges form of W}
-By using the QISM results found in the previous section it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system.
-This is possible because, thanks to integrability
+Using the QISM results found in the previous subsections it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system. Indeed, thanks to integrability
 \begin{equation}
@@
 \end{equation}
-and moreover $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$ with the property that, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can look for a matrix $W$ such that 
+Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
 \begin{equation}
@@
 \end{equation}
-Since $Q^{2L}$ and $H^{''}$ commutes the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones.
-The advantage is that now we can do more with the above expression.
-Firstly the eigenvalues $\Lambda_{\bm{m}}$ can be explicitly computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form that can be used to extract the steady state by rising the vacuum state.
-We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$.
+This expression in function of charges carries some advantages: firstly the eigenvalues $\Lambda_{\bm{m}}$ can be more easily computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a form that can be used to extract the steady state by rising the vacuum state of $H_{0}$.
+We first show this last property in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$.\\ \\
+\textbf{Remark}: in the $gl(2)$ case a closed formula can be found for all the non-equilibrium eigenvectors (not just for the steady state), since the exchange relations between charges are simpler.
+However, in the general $gl(N)$ case, only the steady state can be found via a closed and simple relation.
 \subsection{The gl(2) case}\label{SubsectionGL2}
-Here, the multi-species stirring process reduces to the Simple Symmetric Exclusion Process (SSEP).
-We have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, are written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
+Here the multi-species stirring process reduces to the Simple Symmetric Exclusion Process (SSEP).
+We have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, can be written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
 \begin{equation}\label{Nice-W2}
@@
 where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix. \\ 
-Observe that, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state 
+In particular, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state 
 \begin{equation}
@@
 \end{equation} we retrieve the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N=2$. \\
-Equation \eqref{Nice-W2} gives an explicit formula in term of the charge $B_{1}^{2L-1}$ of the matrix $W$.
-We stress the fact that these nice formula comes from the simple commutation relations between charges.
-\eqref{Nice-W2} was found with different arguments and up to some constants also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}.
+Equation \eqref{Nice-W2} gives an explicit formula in term of the matrices $B_{1}^{2L-1}$ of the matrix $W$.
+We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges.
+We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a different technique to obtain it.
 \subsubsection{Proof of formula \eqref{Nice-W2}}
@@
 \end{equation}
-Power expanding the matrix $W$ with respect to $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for all $i\in\{1,\ldots,N-1\}$ we obtain 
+Power expanding the matrix $W$ with respect to $\Delta_{1}=(\alpha_{1}-\beta_{1})$ we obtain 
 \begin{equation}\label{LinkWG}
@@
 \end{equation}
-Calling $m$ the magnon number of the chain and observing that $e_{22}^{tot}|\Psi_{m}^{0}\rangle=m|\Psi_{m}^{0}\rangle$ and $e_{11}^{tot}|\Psi_{m}^{0}\rangle=(L-m)|\Psi_{m}^{0}\rangle$ we obtain 
+Observing that $e_{22}^{tot}|\Psi_{m}^{0}\rangle=m|\Psi_{m}^{0}\rangle$ and $e_{11}^{tot}|\Psi_{m}^{0}\rangle=(L-m)|\Psi_{m}^{0}\rangle$ we obtain 
 \begin{equation}
@@
 \end{equation}
-Finally, using the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain \eqref{Nice-W2}. 
+Finally, introducing the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain \eqref{Nice-W2}. 
 \begin{flushright}
@@
 where $Sym$ is the symmetric group among $N-1$ objects. \\
-In this case we do not have a closed formula as in the case of $gl(2)$. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
+In this case we do not have a closed formula for all non-equilibrium eigenvectors as in the case of $gl(2)$. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
 \begin{equation}
@@
 \subsection{Non-equilibrium steady state from the W transformation}\label{subsection-NONSS-W}
-Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state 
+Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state of the Hamiltonian $H_{0}$, i.e.
 \begin{equation}\label{Vacuum-state}
@@
 \end{equation}
-\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
+%\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
 Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult because of the presence of creation operators that mixes up species and we cannot rewrite \eqref{W-charges-Bad} in such a simple form.
@@
 \begin{enumerate}
-	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+	%\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
 These probability are hard to find in this partial exclusion situation, however correlation can be formally written.

### 2023-09-20 main.tex
ert

@@
 \end{equation}
+where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. 
 %\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
@@
 We prove \eqref{SteadyState-W-Good} in four steps. 
-\paragraph{1. Useful relations}
+\paragraph{1. Useful relations} Here we derive some relations that are needed in the following of the proof. 
 We recall the following notation, already used in \eqref{Tau-Notation}:
@@
 \end{equation}
-We first write and prove some relations that will be useful:
+We prove the following:
 \begin{itemize}
@@
 \end{align}
-By using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 
+Using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 
 \begin{equation}\label{D2Lp1}
@@
 i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute when acting on $|\Psi_{0}^{0}\rangle$.\\
-We further observe that 
+As a further implication of \eqref{Two-Relation} we have
 \begin{align}\label{Two-Points-m1}
@@
 \end{align}
-\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
+\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, exploiting \eqref{Two-Relation} and \eqref{Commutativity-Gained} we obtain 
 \begin{equation}\label{k-times-QB}
@@
 \paragraph{4.
-Final formula.} Using \eqref{Commutativity-Gained} and \eqref{k-times-QB} the symmetrization operator written in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads, for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$
+Final formula.} For all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$, using \eqref{Commutativity-Gained} and \eqref{k-times-LQB} the symmetrization operator introduced in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads
 \begin{align}
@@
 \end{equation}
-Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in{1,\ldots,k_{1}+\ldots+k_{N-1}}$ 
+Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in\{1,\ldots,k_{1}+\ldots+k_{N-1}\}$ 
 \begin{align}
-&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\\=&
+&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\nonumber\\=&
 \sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle
@@
 \end{align}
-Using the Euler $\Gamma$-function we have 
+introducing the Euler $\Gamma$-function we have 
 \begin{align}
@@
 \end{align}
+Observe that, while $S_{1}$ and $S_{2}$ are local, $W$ is not. 
 \section{Extensions for the non-integrable chain}

### 2023-09-21 main.tex
fix

@@
 To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal.
-These boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}.
-For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.
+These diagonal boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}.
+For this reason, we say that the process is mapped onto equilibrium.
 This can be represented by the following diagram 
@@
 The eigenvectors and the eigenvalues of $H_{0}$ have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
-As a consequence, we can find all the eigenvectors of $H$ from the ones of $H_{0}$.
+As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$.
 Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e.
 a state where all the sites are empty.
-This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM).
+This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM), to be constructed.
 \subsection{The non local transformation}\label{SectionNonLocalTrasformation}
@@
 \begin{equation}
-	R(z,H^{''}):=\left(z-H^{''}\right)^{-1}
-\end{equation}
-where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the resolvent is well defined. 
+	\mathcal{R}(z,H^{''}):=\left(z-H^{''}\right)^{-1}
+\end{equation}
+where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the $\mathcal{R}(x,H^{''})$ is well defined. 
 The above equation implies that 
 \begin{equation}
-	(z-H^{''})R(H^{''},z)=I
+	(z-H^{''})\mathcal{R}(H^{''},z)=I
 \end{equation}
@@
 \begin{equation}
-	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1
+	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1
 \end{equation}
@@
 \begin{equation}
-	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
+	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
 \end{equation}
@@
 \begin{equation}
-	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.
+	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
+	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 \end{equation}
@@
 Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system.
-This expression allows a simpler treatment of the mapping and allows also to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
-To write formula \eqref{W-extended} through the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}).
-In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$.
+This expression allows a simpler treatment of the mapping and also allows to  find a closed formula for the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
+To achieve this aim, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}).
+In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$ situation.
 \subsection{Quantum inverse scattering method}\label{SubsectionQISM}
 We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$.
-In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
+In the case of the multi-species stirring process we chose $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
 We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
@@
 \begin{equation}
-	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
+	U_{0}(x)=M_{0}(x)\widehat{K}_{0}(x)\widehat{M}_{0}(x)
 \end{equation}
@@
 \end{equation}
-where each of the above element acts on the quantum space $V$. These element satisfy some \textit{exchange relations} that can be found by \eqref{RURU} and they are given by: 
+where each of the above element acts on the quantum space $V$. Using \eqref{RURU}, we find some \textit{exchange relations} that the elements of $U_{0}(x)$ must satisfy: 
 \begin{itemize}
@@
 		T(x)=
-		\sum_{k=0}^{2L+2}Q_{k}x^{k}
-	\end{split}
-\end{equation}
-where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
+		\sum_{k=0}^{2L+2}Q^{k}x^{k}
+	\end{split}
+\end{equation}
+where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q^{k}$ the \textit{conserved charges} of the system. 
+\begin{comment}
+We also introduce 
 \begin{equation}
@@
 \end{equation}
-Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ as 
+\end{comment}
+Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ 
 \begin{equation}
@@
 \end{equation}
- In the following we will need the charge expansion of $T(x)$.
+We will need the charge expansion of $T(x)$.
 As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed.
@@
 \textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
-Using these polynomial expansions we write the first three charges
+Using these polynomial expansions we write the first three conserved charges of the system
 
 \begin{align}
-Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
+Q^{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
 \end{align}
 \begin{align}
-Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
+Q^{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
 \end{align}
 \begin{align}
-Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
-\end{align}
-The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
+Q^{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
+\end{align}
+The charges $Q^{2L+2}$ and $Q^{2L+1}$ are proportional to the identity matrix, while $Q^{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
 By construction it follows that 
 \begin{equation}
-\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
+\left[Q^{2L},H^{''}\right]=Q^{2L}H^{''}-H^{''}Q^{2L}=0
 \end{equation}
@@
 \begin{equation}
-Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
+Q^{2L}_{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
 \end{equation}
@@
 \begin{split}
-Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
+Q^{2L}_{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
 \end{split}
@@
 \begin{equation}\label{Q-nonDiag}
-\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
+Q_{+}^{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
 \end{equation}
@@
 \begin{equation}
-Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
-\end{equation}
-Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
+Q^{2L}=Q^{2L}_{0}+Q_{+}^{2L}
+\end{equation}
+Observe that $Q^{2L}$ and $Q^{2L}_{0}$ are isospectral. \\
 %  It has the property that commute with the equilibrium Hamiltonian.
@@
 \end{equation} 
-We denote its eigenvalues by $C_{2}^{N-1}$.
+Moreover, we denote its eigenvalues by $C_{2}^{N-1}$.
 Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$.
@@
 \end{equation} 
-where we denote by 
+In the following, we will denote by 
 \begin{equation}
@@
 \end{equation}
-Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
+Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q_{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
 \begin{equation}
@@
 	\begin{split}
-	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
+	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-Q_{+}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
 \end{split}
@@
 We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges.
-We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a different technique to obtain it.
+We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a slightly different technique to obtain it.
 \subsubsection{Proof of formula \eqref{Nice-W2}}
@@
 \end{equation}
-where in the last equality we used 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}
+where in the last equality we used that $\forall m\in \{1,\ldots,L\}$
+\begin{equation}
+	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}\rangle=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}|\Psi_{m}\rangle
 \end{equation}
@@
 		&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
-		=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}
+		=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}
 	\end{split}
@@
 \paragraph{Proof of formula \eqref{W-charges-Bad}}
-Following the result in the simpler $gl(2)$ case, we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$.
-Using also the multi-variate version of \eqref{veryUsefulSeries}, we obtain
-\begin{equation}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
+Performing a multi-variable power expansion of formula \eqref{WInCharges} with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
+\begin{equation}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
 		\\&
-		\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+		\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 	\end{split}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
+	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
 \end{equation}
@@
 %	\begin{split}
-%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilonQ_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilonQ_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
 %		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
@@
 \paragraph{1. Useful relations} Here we derive some relations that are needed in the following of the proof. 
-We recall the following notation, already used in \eqref{Tau-Notation}:
+We recall the notation, already used in \eqref{Tau-Notation}:
 \begin{equation}
@@
 \end{equation}
-We prove the following:
+We prove that:
 \begin{itemize}
@@
 \paragraph{2. Two indices formula}
-Using \eqref{BActionVoid} and \eqref{Commutativity-Gained} we have that for all $i,j\in\{1,\ldots,N-1\}$
+For all $i,j\in\{1,\ldots,N-1\}$
 \begin{equation}\label{Two-Relation}
@@
 \begin{align}
-	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
 	|\Psi_{0}^{0}\rangle\nonumber
@@
 \end{comment}
-\subsection{Bethe ansatz solution}
-Describe eigenvalues of $T_0$ following 
-\cite{belliard2} 
+%\subsection{Bethe ansatz solution}
+%Describe eigenvalues of $T_0$ following 
+%\cite{belliard2} 
 \subsection{A sequence of similarity transformation}
-In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$.
-Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one (i.e.
-$H_{0}$) as
+In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$
 \begin{equation}
@@
 \end{equation} 
-More explicitly we have 
+ Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one $H_{0}$ as 
 \begin{equation}
@@
 \begin{align}
-	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\\&
-	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
+	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\nonumber\\&
+	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\nonumber\\&
 	\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
@@
 In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
-The aim of this section is studying some extension to the analysis previously done when integrability property is lost.
-We fix $\nu>1$ and, for the sake of simplicity, we still study the geometry of chain.
+The aim of this section is studying some extension of the analysis previously done when integrability property is lost.
+We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
 We provide the following extensions:
@@
 Particle can now change type.
-The model is constructed with the goal of having the average density evolving a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+The model is carefully constructed with the goal of having the average density evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+Duality for the boundary driven process is proved.
 Subsection \ref{Subsection-RD}
@@
 \subsubsection{The thermalization measure}
-As already mentioned, we will redistribute particles on a bond according to a probability measure that is the reversible one \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond.
-We denote
+We introduce the reversible measure \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond
 \begin{equation}
@@
 \begin{equation}
-	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=1}^{N-1}r_{a}
-\end{equation}
-We construct this measure.
+	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{N}=\nu-\sum_{a=1}^{N-1}r_{a}
+\end{equation}
  Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
@@
 	\end{equation}
-The right boundary generator is defined in a similar way, where $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
+and 
+\begin{equation}
+	\begin{split}
+		\mathcal{L}_{right}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},\bm{r})-f(\bm{n})\right\}\\&
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
+	\end{split}
+\end{equation}
+In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n_{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters.
 \subsubsection{The dual thermalized process}
@@
 \end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$, i.e. 
-\begin{equation}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{left}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
-	\end{split}
-\end{equation}
-and similarly $\widetilde{\mathcal{L}}_{right}^{TH}$, but acting on the site $L$. 
-The duality function is the same, i.e.
+where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$
+\begin{align}
+		\widetilde{\mathcal{L}}_{left}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{right}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}
+	\end{align}
+i.e. they remove all dual particles at site $1$ (and $L$) and put these particles in the extra-site $0$ (and $L+1$) with rate 1. 
+The duality function is the same as the original process, i.e.
 \begin{equation}
@@
 \end{equation}
+\paragraph{Proof of thermalized duality}
 The proof of the duality consists in showing
@@
 \end{align}
+The proof is similar for $\widetilde{\mathcal{L}}_{y}^{TH}$. 
+\begin{flushright}
+	$\square$
+\end{flushright}
 \subsection{Multi-species stirring process with reaction} \label{Subsection-RD}

### 2023-09-22 main.tex
fixed

@@
 \\
+ A new technique to compute absorption probabilities has been proposed in \cite{floreani2023non}.
 \paragraph{Organization of the paper}
@@
 where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundaries are absorbing, i.e. 
-\begin{equation}
+\begin{equation}\label{abs-dual-boundary-chain}
 	\begin{split}
@@
 \end{equation} 
- We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{L}$ and $\rho_{a}^{R}$ for all $a\in\{1,\ldots,N\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{L}=\nu$.
-In the following of this section we answer to these questions.
+ We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{0}$ and $\rho_{a}^{L+1}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$.
  We first define the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$.
-Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality in this general case.
+Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality.
 \subsubsection{The process on a chain}
@@
 \begin{equation}\label{RDGenerator}
-	\mathcal{L}^{rd}=+\mathcal{L}_{right}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{right}^{rd}
+	\mathcal{L}^{rd}=\mathcal{L}_{right}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{right}^{rd}
 \end{equation}
@@
 \end{equation}
-defined $\forall c\in\{1,\ldots,N-2\}$ as 
+defined as
 \begin{equation}
@@
 		k+c-N+1\quad &\text{if}\quad k+c\geq N,\quad k\neq N\\
-		1\quad &\text{if}\quad k=N
+		N\quad &\text{if}\quad k=N
 	\end{cases}
@@
 	\begin{split}
-		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{L}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\\
+		\alpha_{a}&=\sigma_{11}\rho_{a}^{0}+\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\rho_{b}^{0}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\\
 		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}
@@
 		\\&=
-		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{x+1}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{x+1}\right)
+		\sum_{a=1}^{N-1}n_{a}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
 		\\&=
@@
 \end{equation}
-where we call $q$ such that $g_{i}^{-1}(d)=q$. Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq 1$ .
+where we call $q$ such that $g_{i}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
+Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
 Moreover
@@
 		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
-		\\=&
-		\nu\sigma_{11}\rho_{d}^{L}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{1}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
-	\end{split}
-\end{equation}
-Using equation \eqref{actionGraphRD} we have that $\forall x\in \{1,\ldots,L-1\}$ and $\forall d\in\{1,\ldots,N-1\}$
+		\\&=
+		\nu\sigma_{11}\rho_{d}^{0}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{0}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\\&=
+		\nu \sigma_{11} (\rho_{d}^{0}-n_{d}^{1})+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}(\rho_{b}^{0}-n_{d}^{1})
+	\end{split}
+\end{equation}
+Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{1,\ldots,N-1\}$
 \begin{equation}\label{DifferenceEquation}
@@
 \begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{1}-2n_{d}^{1}+n_{2}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq d}^{N-1}\left(\rho_{c}^{1}-2n_{c}^{1}+n_{c}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{c}^{1}-n_{d}^{1}\right)
+	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{0}-2n_{d}^{1}+n_{d}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq d}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{d}^{1}\right)
 \end{equation}
@@
 \end{equation}
-where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n})_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
+where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
 These average occupations evolve according to the Master equation
@@
 For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question of the beginning of this section.
+This answers the first question we addressed to in the beginning of this section.
 
@@
 This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundary generators.
-For fixed edge $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators the computation is similar.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b,\in\{1,\ldots,N-1\}$; the detailled balance reads
-\begin{equation}
-	\begin{split}
-		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}
+For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators  $\mathcal{L}_{x,x+1}^{m}$, $\mathcal{L}_{left}^{rd}$ and $\mathcal{L}_{right}^{rd}$ the computation is similar.
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance reads
+\begin{equation}
+	\begin{split}
+		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
 		\\
@@
 		\\&
-		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{x+1}}
+		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}+1}
 	\end{split}
@@
 \begin{equation}
-	\rho_{a}\rho_{b}=\rho_{g_{c}(b)}\rho_{g_{c}(a)}
-\end{equation}
-that is true if and only if $\rho_{a}=\rho$ $\forall a\in \{1,\ldots,N-1\}$.\\
-By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,x+1}$.
-\\
+	\rho_{a}\rho_{b}=\rho_{g_{c}(a)}\rho_{g_{c}(b)}
+\end{equation}
+By the arbitrariness of $a,b,$ it is true if and only if $\rho_{a}=\rho$ $\forall a\in \{1,\ldots,N-1\}$.\\
 For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$.
@@
 \end{equation}
-To sites $1,L$ we associate an ``extra site'', denoted by $0$ and $L+1$ respectively,
+We associate an ``extra site'', denoted by $0$ and $L+1$ attached to $1$ and $L$ respectively,
 where dual particles will accumulate in the course of time. 
-We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+We denote the configurations $\bm{\xi} \in \widetilde\Omega$  as
 \begin{equation}
@@
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 
-the extra-site $0$ connected to $1$ and similarly for $xi_{a}^{L+1}$. \\
+and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
 The duality function is given by
@@
 where 
-$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator} and specialized for sites $x=1$ and $x=L$.
-Observe that the generator $\widetilde{\mathcal{L}}^{rd}$ has the same dynamics as $\mathcal{L}^{rd}$ in the bulk, while the boundaries are absorbing. 
+$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{abs-dual-boundary-chain}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
 \subsubsection{Proof of duality}
-The duality between the boundary generators is trivial, because they have the same form of \eqref{siteDualGenerator}, up to a specific choice of the parameters.
-Therefore we only need to prove the duality relation for the bulk generator.
-In the spirit of what we did in Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
+We only need to prove duality for the bulk generator, since the boundary generators are the same as in Subsection \ref{Subsection-ss-nonI}. 
+In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
 \begin{equation}
@@
 \end{align}
-That is equivalent of showing 
+It is enough of showing 
 \begin{align}
@@
 \end{align}
-Since the matrix $R_{x}$ is the same, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x})}$ as a symmetry.
-The first result will follow from the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$.
+Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x+1})}$ as a symmetry.
+
+\paragraph{Duality for $H_{x,x+1}^{c}$} We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
-The second result will follow from the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
+\paragraph{Duality for $H_{x,x+1}^{m}$} We compute the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
 \begin{equation}
@@
 \appendix
+\section*{Appendix}
 \begin{comment}

### 2023-09-25 main.tex
fds

@@
 
-{\color{red}add/improve explanaition of entire subsection}
+{\color{red}add/improve explanaition of entire subsection} {\color{blue}Is it not standard?}
 \subsection{The Lie algebraic description}
@@
 \end{equation}
-{\color{blue}
 where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$.
-Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.}
-{\color{red}remove?}
+Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
@@
 \end{equation}
-{\color{red} no minus sign?}
+{\color{red} no minus sign?} {\color{blue}I think we decided to keep it without minus sign}
 The action of the generator can also be expressed as 
@@
 $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
-The Hamiltonian is
+The Hamiltonian now reads
 \begin{equation}\label{hamiltonian}
@@
 \end{equation} 
-The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.
+The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
 \begin{equation}
@@
 \end{equation}
-where $\mathbb{E}_{\eta}$ denotes the expectation with respect the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect to the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
+where $\mathbb{E}_{\eta}$ denotes the expectation with respect to the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect to the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
 The duality definition can also be formulated as a relation between the generators.
@@
 \subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}
-As already pointed out in Subsection \ref{statementDualitySubsection}, the dual process voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites and replacing them by types $N$.
+In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
+Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types.
+Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present.
+As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
 This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
-Here we consider a chain of length $L$ where the end sites $1$ and $L$ are connected with two reservoirs.
-Each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
-The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and the generator reads
+\\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and its generator reads
 \begin{equation}
@@
 \end{equation}
-We specialize the results of Subsection \ref{statementDualitySubsection} to this chain. The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
+ The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
 \begin{equation}	
@@
 We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
-We assume that it has an arbitrary configuration $\bm{n}$.
+Consider an arbitrary initial configuration of $(\bm{n}(t))_{t\geq 0}$ denoted by $\bm{n}$.
 For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
@@
 Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{k}\in\{1,\ldots,N-1\}$ situated at sites $y_{k}\in\{1,\ldots,L\}$ with $k\in \{1,\ldots,m\}$.
-This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
-The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the simplest case of one point correlations, since the single dual particle behaves as an independent random walker.
+Using \eqref{ExptationSS}, this expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
+However, these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
 \paragraph{One point correlations for the $\nu\geq 1$ case}
@@
 Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}.
-We recall that the geometry is again a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$, but with the hard-core exclusion rule, i.e.
+We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$.
+Now we assume the hard-core exclusion rule, i.e.
 $\nu=1$.
@@
 \end{equation}
-and its elements are given by
+where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
+The elements of this duality matrix are given by
 \begin{equation}\label{ElementsDualityMatrixChain}
@@
 \end{equation}
- namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ absorbed at right.
+ namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right.
 Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
@@
 \subsection{The integrable chain and the matrix product ansatz}
-The matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
+The matrix product ansatz has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
  Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
@@
 \end{equation}
-This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial distribution. 
+This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial configuration. 
 We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution. This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
@@
 However, to write explicitly the steady state one should provide a representation of this algebra.
-Another approach is to directly use the commutators and and the boundary actions compute correlations.
-This path has been followed in \cite{vanicat2017exact} to compute one-point and two-point correlations.
+Another approach is to directly use the commutators and the boundary actions to compute correlations.
+This path has been followed in \cite{vanicat2017exact} to find one-point and two-point correlations.
 Here we follow the same approach. We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the
@@
 Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the right eigenvector with vanishing eigenvalue $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
-Then, reversing the transformations we will retrieve $|\Psi\rangle$.
+Finally, reversing the transformations we will retrieve $|\Psi\rangle$.
 
@@
 \end{align}
-We introduce the first transformation as
+We introduce
 \begin{equation}\label{transformationV}
@@
 \end{equation}
-that is composed by a copy of $\mathcal{S}_{1}$ (introduced in \eqref{S1Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
+that is composed by a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
 Observe that $\mathcal{S}_{1}^{x}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
@@
 \end{equation}
- This $S_{1}$ is invertible, then we introduce 
+ $S_{1}$ is invertible, then we introduce 
 \begin{equation}\label{hatHamiltonian}
@@
 
-We introduce the second transformation as 
+We introduce
  \begin{equation}
@@
  \end{equation}
-that is composed by a copy of $\mathcal{S}_{2}$ (introduced in \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
+that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
 By taking the product over the chain
@@
 \end{equation}
-The boundary Hamiltonians of $H^{''}$ reads
+The boundary Hamiltonians of $H^{''}$ read
 \begin{align}
@@
 \end{equation}
-\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain in order to alleviate notation. Each configuration can be written as
+\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
 \begin{equation}\label{Tau-Notation}
@@
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
-We consider the vector with elements the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators.
+We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators.
 For the sake of notation, we denote by 
@@
 \end{equation}
-We obtain 
+We have
 \begin{equation}\label{Xtildes2b}
@@
 \end{equation} 
-Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as:
+Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
 \begin{equation}\label{toDetermineTilde}
@@
 $$
-such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
+such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. \\
 To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}
@@
 \end{equation}
-Fixing $ a\in \{1,\ldots,N-1\}$ and for arbitrary $ \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
+Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying many times \eqref{UsefulRelation} we have
 \begin{align*}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
+	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 \end{align*}
-To determine the state we need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}n_{N}^{l}}|V\rangle$.
+To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}n_{N}^{l}}|V\rangle$.
 Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and taking an arbitrary $a\in \{1,\ldots,N-1\}$ we have
@@
 Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
-This matrix $\mathcal{S}_{2}$ is given by
+Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by
 \begin{equation}
@@
     	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L},\ldots,\varphi_{L+1}^{L}}
+    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L+1}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L},\ldots,\varphi_{L+1}^{L}}
     	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L+1},\ldots,\varphi_{L+1}^{L+1}} \right\}
+    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L+1}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L+1},\ldots,\varphi_{L+1}^{L+1}} \right\}
     	\\&=
@@
 The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
-To find these elements we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
+To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
 Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads

### 2023-09-25 main.tex
fixed

@@
 where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{s_{i}}^{y_{i}}$.  
-\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$.
+\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$.
 We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$.
@@
 Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.
+\begin{flushright}
+	$\square$
+\end{flushright}
 \begin{comment}
@@
 \paragraph{Two points correlations}
-The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+The two points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
 \begin{equation}
@@
 \end{equation}
-Therefore, we obtain the second cumulant, i.e. the two-point connected correlation as 
+Therefore, we compute the second cumulant, i.e. the two-point connected correlation
 \begin{equation}\label{two-pts-corr}
@@
 \paragraph{Three points correlations}
-The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
+The three points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
 \begin{equation}
@@
 \end{align}
-Therefore, we obtain the third cumulant, i.e. the three-point connected correlation as 
+Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
 \begin{align}
@@
 As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$.
-Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e.
+Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e.
 a state where all the sites are empty.
-This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM), to be constructed.
+This last transformation $W$ is non-local and to be constructed requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM).
 \subsection{The non local transformation}\label{SectionNonLocalTrasformation}
@@
 Variables $x,y\in\mathbb{C}$ are called spectral parameters.
-The above matrices satisfy:
+The matrices $R_{a,b}(x)$, $K_{a}(x)$ and $\widehat{K}_{a}(x)$ satisfy:
 \begin{itemize}
@@
 \begin{equation}
-	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
-\end{equation}
-$U_{0}(x)$ satisfies the following exchange relation
+	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}(x)=R_{0L}(x)\ldots R_{01}(x)
+\end{equation}
+$U_{0}(x)$ satisfies the following relation
 \begin{equation}\label{RURU}
@@
 \end{equation}
-
  $U_{0}(x)$ can be written in the canonical basis of $V_{0}$ 
@@
 \subsection{Charges}
-Using the matrix form of $U_{0}(x)$ written in \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads
+Using the matrix form of $U_{0}(x)$ \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads
 \begin{equation}
@@
 \end{comment}
-Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ 
+Arguing similarly, we also write the elements of $U_{0}(x)$ as polynomials in $x$ 
 \begin{equation}
@@
 We will need the charge expansion of $T(x)$.
-As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed.
+As it will be clear in the following, only the first three conserved charges of the systems.
+As a consequence, we will compute only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed.
 Therefore, using \eqref{RURU}, we compute:
@@
 \end{itemize}
-\textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
+\textbf{Remark}: when restricted to the case of $N=2$ species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
 Using these polynomial expansions we write the first three conserved charges of the system
@@
 \begin{align}
-Q^{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
+Q^{2L+1}&=ND_{N,N}^{2L+1}+D_{N,N}^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
 \end{align}
@@
 \end{equation}
-
 We also introduce 
@@
 \end{equation}
-where, for the sake of notation we denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we can write 
+where, for the sake of notation we have denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we write 
 \begin{equation}
@@
 All terms are diagonal except the last one.
-This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
+This last non-diagonal term can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
 We denote it by $\hat{C}_{2}^{N-1}$, i.e.
@@
 Moreover, we denote its eigenvalues by $C_{2}^{N-1}$.
-Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$.
+Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$ (branching rule).
 As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$.
-On these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e.
+On each of these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ as
 \begin{equation}
@@
 \end{equation} 
- where 
+ where we introduce the shifted weights
  \begin{equation}
@@
 \end{comment}
-\paragraph{Exchange relations between charges} Since, in general, the coefficients of the polynomial form of the elements of $U_{0}(x)$ and the charges do not commute, it is useful to find explicit exchange relations among them.
-Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain:
+\paragraph{Exchange relations between charges} It is useful to find explicit exchange relations among the coefficients of the polynomial form of the elements of the matrix $U_{0}(x)$ defined in \eqref{matrixForm-U}.
+Using relations \eqref{EX1}-\eqref{EX6} we obtain:
 \begin{itemize}
@@
 \end{equation}
-Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q_{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
+Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
 \begin{equation}
@@
 \end{equation}
-where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix. \\ 
+where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix and where $B_{1}^{2L-1}$ is given in \eqref{B-charge}.
 In particular, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state
@@
 \end{equation} we retrieve the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N=2$. \\
-Equation \eqref{Nice-W2} gives an explicit formula in term of the matrices $B_{1}^{2L-1}$ of the matrix $W$.
+Equation \eqref{Nice-W2} gives an explicit formula in term of the $B_{1}^{2L-1}$ of the matrix $W$.
 We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges.
@@
 \end{equation}
-Power expanding the matrix $W$ with respect to $\Delta_{1}=(\alpha_{1}-\beta_{1})$ we obtain 
+Power expanding the matrix $W$ using \eqref{veryUsefulSeries} and denoting $\Delta_{1}=(\alpha_{1}-\beta_{1})$ we obtain 
 \begin{equation}\label{LinkWG}
@@
 \begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}\rangle=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}|\Psi_{m}\rangle
+	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle=|\Psi_{m}^{0}\rangle
 \end{equation}
@@
 	\begin{split}
-		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
+		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
 		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
@@
 where $Sym$ is the symmetric group among $N-1$ objects. \\
-In this case we do not have a closed formula for all non-equilibrium eigenvectors as in the case of $gl(2)$. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
+In this case we do not have a closed formula for all non-equilibrium eigenvectors. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
 \begin{equation}
@@
 This extra creation operator, mixes up the species different from $N$.
-However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do remain simple.
+However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do simplify.
 \paragraph{Proof of formula \eqref{W-charges-Bad}}
-Performing a multi-variable power expansion of formula \eqref{WInCharges} with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
-\begin{equation}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
-		\\&
-		\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation} 
-Observing that 
+Performing a multi-variable power expansion of formula \eqref{WInCharges} using \eqref{veryUsefulSeries} and denoting $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
+\begin{equation}
+	\begin{split}
+		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
+	\end{split}
+\end{equation} 
+where we used the fact that 
 \begin{equation}
@@
 \end{equation}
-we finally obtain \eqref{W-charges-Bad}. 
+This implies \eqref{W-charges-Bad}. 
 %\begin{equation}
@@
 \subsection{Non-equilibrium steady state from the W transformation}\label{subsection-NONSS-W}
-Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state of the Hamiltonian $H_{0}$, i.e.
+Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state $|\Psi_{m}^{0}\rangle$ of the Hamiltonian $H_{0}$, defined as
 \begin{equation}\label{Vacuum-state}
@@
 	\\&=
-	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
+	-2\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
 	\\&=
@@
 \begin{equation}\label{Two-Relation}
-	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
+	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
 \end{equation}
@@
 	\\=&
-	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
+	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
 	\\=&
-	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
+	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
 \end{align}
@@
 \end{align}
-it is also true. This can be shown by applying repeatedly \eqref{Two-Relation}.
+it is also true. This can be shown by aa straight forward computation applying repeatedly \eqref{Two-Relation}.
 \begin{flushright}

### 2023-09-26 main.tex
check

@@
 This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
-\\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and its generator reads
+\\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
+ \begin{equation}\label{stateSpace-Chain}
+ 	\Omega=\bigtimes_{x=1}^{L} \Omega_{x}
+ \end{equation} and its generator reads
 \begin{equation}
@@
  The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
-\begin{equation}	
+\begin{equation}\label{stateSpaceDUAL-Chain}	
 	\widetilde{\Omega}=N_{0}^{N}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
@@
 For this reason, we say that the process is mapped onto equilibrium.
-This can be represented by the following diagram 
+This can be represented by the diagram 
 \begin{equation}
@@
 \end{equation} 
+Namely, the following equation holds true
+\begin{equation}
+	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
+\end{equation}
 The eigenvectors and the eigenvalues of $H_{0}$ have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
-As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$.
+As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$
+\begin{equation}
+	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
+\end{equation}
 Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e.
@@
 \end{equation}
-where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. 
+where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. \\
+As a consequence, the steady state of the original process $H$ reads
+\begin{align}
+	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\nonumber\\&
+	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\nonumber\\&
+	\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
+\end{align}
 %\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
@@
 To obtain the steady state $|\Psi\rangle$ of $H$ we only need to invert the transformations $S_{1}$ and $S_{2}$ defined in \eqref{S1-Whole} and \eqref{S2-Whole}.
-\end{comment}
+
 %\subsection{Bethe ansatz solution}
@@
 Observe that, while $S_{1}$ and $S_{2}$ are local, $W$ is not. 
+\end{comment}
 \section{Extensions for the non-integrable chain}
 In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
-The aim of this section is studying some extension of the analysis previously done when integrability property is lost.
+The aim of this section is studying some property of the process when integrability is lost.
 We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
@@
 Particle can now change type.
-The model is carefully constructed with the goal of having the average density evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
-Duality for the boundary driven process is proved.
+The model is carefully constructed with the goal of having the average densities evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+Duality for the boundary driven process is also proved.
 Subsection \ref{Subsection-RD}
@@
 \subsubsection{Thermalized multi-species stirring process}
-The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace} and its generator reads
+The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace-Chain} and its generator reads
 \begin{equation}\label{thermalizedGenerator}
@@
 \end{equation}
-In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n_{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters.
+In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n^{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters.
 \subsubsection{The dual thermalized process}
-The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
+The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{stateSpaceDUAL-Chain}. Its generator reads
 \begin{equation}
@@
 \begin{equation}
-	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
 \end{equation}
@@
 	\\&\nonumber
-	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&
@@
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
-	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
+	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
 	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber
 	\\=&
-	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
+	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
 \end{align}

### 2023-09-26 main.tex
check

@@
 We consider the first addend in the curly bracket of the previous equation.
-We multiplying it by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$ and by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}$ and we have
+We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$; we have
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{k}^{1}-\xi_{k}^{1}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\nonumber\\=&
 	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&

### 2023-09-26 main.tex
fixed

@@
 \end{equation} 
-for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$.
+for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$. Here $\Delta_{L}\rho(x,t)=\rho_{a}(x+1,t)+\rho_{a}(x-1,t)-2\rho_{a}(x,t)$.
 This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
@@
  We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{0}$ and $\rho_{a}^{L+1}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$.
- We first define the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$.
+ We construct the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$.
 Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality.
 \subsubsection{The process on a chain}
-We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at left of site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at right of site $L$.
-The generator reads
+We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $L$.
+The state space is $\Omega$ given in \eqref{stateSpace-Chain} and the generator reads
 \begin{equation}\label{RDGenerator}
@@
 \end{equation}
-with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
+with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce
 \begin{equation}
@@
 \end{equation}
-The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s. \\ \\
+The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s and the boundary densities are considered at site $L+1$. \\ \\
 \textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
-\paragraph{Action on the occupation variable of $\mathcal{L}_{x,+1}^{rd}$}
+\paragraph{Action of $\mathcal{L}_{x,+1}^{rd}$ on the occupation variable}
 For arbitrary site $x\in \{1,\ldots,L\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
@@
 Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action on the occupation variable of $\mathcal{L}_{left}^{rd}$}
+\paragraph{Action of $\mathcal{L}_{left}^{rd}$ on the occupation variable}
 Acting on $n_{d}^{1}$  with $\mathcal{L}_{left}^{rd}$ we obtain
@@
 \end{equation} 
-Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present.
+Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation\eqref{NSpeciesRD} where the discrete Laplacians of all species are coupled and linear reaction terms are present that we aimed for.
 For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question we addressed to in the beginning of this section.
+This answers the first question we addressed to in the beginning of this subsection.
 
@@
 In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
-\begin{equation}
-	\widetilde{\Omega}=\mathbb{N}_{0}^{N-1}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N-1}
-\end{equation}
-We associate an ``extra site'', denoted by $0$ and $L+1$ attached to $1$ and $L$ respectively,
-where dual particles will accumulate in the course of time. 
-We denote the configurations $\bm{\xi} \in \widetilde\Omega$  as
-\begin{equation}
-	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
-\end{equation}
-where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
-The duality function is given by
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ still takes values in the enlarged state space \eqref{stateSpaceDUAL-Chain}
+%\begin{equation}
+%	\widetilde{\Omega}=\mathbb{N}_{0}^{N}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N}
+%\end{equation}
+%We associate an ``extra site'', denoted by $0$ and $L+1$ attached to $1$ and $L$ respectively,
+%where dual particles will accumulate in the course of time. 
+We denote the configurations $\bm{\xi} \in \widetilde\Omega$ 
+%\begin{equation}
+%	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
+%\end{equation}
+%where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
+%and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
+The duality function is still given by
 \begin{equation}
@@
 %\end{equation}
-The dual process is defined by its generator, which reads
+The dual process is defined by the dual generator
 \begin{equation}\label{DualGeneratorRD}
@@
 $\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{abs-dual-boundary-chain}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
-\subsubsection{Proof of duality}
+\paragraph{Proof of duality}
 We only need to prove duality for the bulk generator, since the boundary generators are the same as in Subsection \ref{Subsection-ss-nonI}. 
@@
 Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x+1})}$ as a symmetry.
-
-\paragraph{Duality for $H_{x,x+1}^{c}$} We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$.
+\\
+%\paragraph{Duality for $H_{x,x+1}^{c}$}
+ We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
-\paragraph{Duality for $H_{x,x+1}^{m}$} We compute the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
+%\paragraph{Duality for $H_{x,x+1}^{m}$} 
+We compute the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
 \begin{equation}

### 2023-09-27 main.tex
clean

@@
  \begingroup\LARGE
-\bf Multispecies stirring process
+\bf Multispecies stirring process: duality and exact solution
 \par\endgroup
@@
 of the two species.
-For example see \cite{floreani2022switching,redig2022ergodic}.
+For example see \cite{floreani2022switching,redig2022ergodic,redig2023equilibrium}.
 On the other hand, the \textit{single layer models}.
@@
 {\color{red}
-The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(n)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
+The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
 Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
@@
 For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$.
-See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dyamics. 
-\begin{figure}
+See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dynamics. 
+\begin{figure}[h]
     \centering
@@
 \end{figure}
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 \section{Mapping to equilibrium} \label{Section-Mapping}
-{\color{blue}check also Appendix A in
+{\color{red}check also Appendix A in
 \cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}} \\
@@
 \end{equation}
-The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s and the boundary densities are considered at site $L+1$. \\ \\
+As a consequence, we can define the boundary values in terms of the reservoir parameters as
+\begin{equation}
+	\rho_{a}^{0}=\frac{\alpha_{a}\sigma_{11}-\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\alpha_{b}}{(\sigma_{11}-(N-2)\sigma_{12})(\sigma_{11}+(N-2)\sigma_{12})}\qquad \rho_{N}^{0}=\frac{\alpha_{N}}{(\sigma_{11}+(N-2)\sigma_{12})}
+\end{equation}
+for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$. \\
+The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$. \\ \\
 \textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
@@
 \begin{equation}
-	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)
+	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
 \end{equation}
@@
 \begin{equation}
-	\rho=\rho_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
+	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
 \end{equation}
@@
 \begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{N}^{n_{N}^{x}}
-\end{equation}
-This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundary generators.
-For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators  $\mathcal{L}_{x,x+1}^{m}$, $\mathcal{L}_{left}^{rd}$ and $\mathcal{L}_{right}^{rd}$ the computation is similar.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance reads
+	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
+\end{equation}
+This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries.
+For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
+\begin{comment}
 \begin{equation}
@@
 that simplifies to 
-\begin{equation}
-	\rho_{a}\rho_{b}=\rho_{g_{c}(a)}\rho_{g_{c}(b)}
-\end{equation}
-By the arbitrariness of $a,b,$ it is true if and only if $\rho_{a}=\rho$ $\forall a\in \{1,\ldots,N-1\}$.\\
-For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$.
+\end{comment}
+\begin{equation}
+	p_{a}p_{b}=p_{g_{c}(a)}p_{g_{c}(b)}
+\end{equation}
+By the arbitrariness of $a,b,$ it is true if and only if
+\begin{equation}\label{p-equal}
+	p_{a}=p\qquad \forall a\in \{1,\ldots,N-1\}
+\end{equation}
+while $p_{N}=1-\sum_{a=1}^{N-1}p_{a}$\\
+For the boundary generators $\mathcal{L}_{left}^{rd}$ and $\mathcal{L}_{right}^{rd}$ we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
 \subsubsection{Duality for the reaction-diffusion process}
 In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ still takes values in the enlarged state space \eqref{stateSpaceDUAL-Chain}
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ still takes values in the enlarged state space $\widetilde{\Omega}$ defined in \eqref{stateSpaceDUAL-Chain}
 %\begin{equation}
@@
 %where dual particles will accumulate in the course of time. 
-We denote the configurations $\bm{\xi} \in \widetilde\Omega$ 
+%and we denote its configurations by $\bm{\xi} \in \widetilde\Omega$.
 %\begin{equation}
@@
 %\end{equation}
-The dual process is defined by the dual generator
+The dual generator now reads
 \begin{equation}\label{DualGeneratorRD}
@@
 \end{align}
-It is enough of showing 
+but it is enough of showing 
 \begin{align}
@@
 %\paragraph{Duality for $H_{x,x+1}^{c}$}
- We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$.
+ We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x+1})$.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 	\\=&
-	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x+1}\delta_{aN}-E_{aN}^{x+1}\delta_{da})\right)\right.
+	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right.
 \\ \otimes&\left.
-\left((E_{kb}^{y}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
+\left((E_{kb}^{x+1}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
 	\\=&
-	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{y}+E_{bN}^{x+1}\right)\right\}
+	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
 	\\=&
@@
 \end{align*}
-where in the last equality we used the invertibility of the map $g_{c}(\cdot)$. \\
+where in the last equality we used the fact that map $g_{c}(\cdot)$ is surjective. \\
 %\paragraph{Duality for $H_{x,x+1}^{m}$} 
-We compute the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
+Concerning the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x+1})$, the proof is similar and gives
 \begin{equation}
@@
 
-\section{Conclusion}
+\section{Conclusion and outlook}
+Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
+Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
+Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
+Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
+Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.
 
@@
 				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-				1 \qquad &\text{otherwise}
+				N \qquad &\text{otherwise}
 			\end{cases}
@@
 	\end{comment}
-indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $1$ is replaced by all other possible species from $2$ to $N$.
+indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
 Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}.

### 2023-10-03 main.tex
biblio
Hadamard

@@
 Here the state space contains all the species and it is not product anymore.
-Some examples of such a dynamic can be found in \cite{casini2022uphill,vanicat2017exact,zhou2021orthogonal}.
+Some examples of such a dynamic can be found in \cite{casini2022uphill,vanicat2017exact,zhou2021orthogonal,casini2023density}.
 \\
@@
  \end{equation}
-In the following we need the application of the Hadamard formula with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{ab}$ of the Lie algebra.
+In the following we need the application of the Hadamard formula with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra with $c,d\in\{1,\ldots,N\}$.
 Therefore we compute
+\begin{align}
+	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-\delta_{d<N}E_{cN}
+\end{align}
+and 
+\begin{align}
+	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-\delta_{d<N}E_{cN}\right]\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-\delta_{d<N}\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left(E_{ad}\delta_{bN}-\delta_{ad}E_{bN}\right)-\delta_{d<N}\left(E_{aN}\delta_{cN}-E_{cN}\delta_{aN}\right)\right)\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-\delta_{d<N}\delta_{cN}E_{aN}\right)\nonumber\\=&
+	-\left(-\delta_{cN}\delta_{d<N}-\delta_{d<N}\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
+	\\=&
+	-2\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
+\end{align}
+From the third commutator on we always obtain zero. All in all we have that 
+ \begin{align}\label{HT-BA}
+ 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\left(\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-\delta_{d<N}E_{cN}\right)-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
+ \end{align}
+\begin{comment}
 \begin{enumerate}
@@
 \end{split}
+\end{equation}
+therefore we have that 
+\begin{equation}
+	content...
 \end{equation}
@@
 \end{enumerate}
+\end{comment}
 Using \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
@@
 \end{equation}
-First, we multiply both sides by $R_{x}\exp{(E^{x})}$
-\begin{equation}
+We multiply both sides by $R_{x}\exp{(E^{x})}$
+\begin{equation}\label{intermediateTransposeSite}
     H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
 \end{equation}
-then,we insert the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ in the right hand side
+%By inserting the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ and 
+By using \eqref{HT-BA} and the fact that the Casimir operator \eqref{secondCasimir} is central for the algebra we have 
+\begin{comment}
+then, in the right hand side
 \begin{equation}\label{intermediateTransposeSite}
@@
 \end{equation}
+\end{comment}
 %where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$.
- Using \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 
+% Using 
+ \begin{comment}
+ \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 
 \begin{align}
@@
 in short
+\end{comment}
 \begin{equation}\label{HadTransfBoundary}

### 2023-10-03 main.tex
fixed

@@
 	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-\delta_{d<N}\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
-	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left(E_{ad}\delta_{bN}-\delta_{ad}E_{bN}\right)-\delta_{d<N}\left(E_{aN}\delta_{cN}-E_{cN}\delta_{aN}\right)\right)\nonumber\\=&
 	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-\delta_{d<N}\delta_{cN}E_{aN}\right)\nonumber\\=&
@@
  \begin{align}\label{HT-BA}
- 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\left(\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-\delta_{d<N}E_{cN}\right)-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
+ 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+\delta_{d<N}E_{cN}-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
  \end{align}
@@
 %By inserting the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ and 
-By using \eqref{HT-BA} and the fact that the Casimir operator \eqref{secondCasimir} is central for the algebra we have 
+By using \eqref{HT-BA} and the fact that the first Casimir operator $C_{1}=\sum_{a,b=1}^{N}E_{ab}$ is central for the algebra we have 
 \begin{comment}

### 2023-10-03 main.tex
k

@@
 	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-\delta_{d<N}\delta_{cN}E_{aN}\right)\nonumber\\=&
-	-\left(-\delta_{cN}\delta_{d<N}-\delta_{d<N}\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
+	-\left(\delta_{cN}\delta_{d<N}+\delta_{d<N}\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
 	\\=&

### 2023-10-03 main.tex
fixed

--- 2023-10-03 main.tex
@@
 \section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
-In this section we aim to use duality and the matrix product ansatz to determine the non equilibrium steady state and its arbitrary correlation for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
-As it will turn out, duality simplifies the commutation relations of the matrix product ansatz allowing to determined a closed formula for all correlations.
-As a by-product, absorption probabilities can be explicitly determined, giving a further probabilistic interpretation for the non-equilibrium steady state.
-\subsection{The integrable chain and the matrix product ansatz}
+In this section we aim to use duality and the matrix product ansatz (MPA) to determine the moments and correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
+As it will turn out, the commutation relations of the matrix product ansatz allowing to determine a closed formula for all correlations.
+As a by-product, absorption probabilities can be explicitly found.%, giving a further probabilistic interpretation for the non-equilibrium steady state.
+\subsection{The integrable chain and the non-equilibrium steady state}
 The matrix product ansatz has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
  Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
- the Master equation
-\begin{equation}
-    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle
+ the master equation
+\begin{equation}
+    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle.
 \end{equation}
@@
 \begin{equation}\label{definition-SteadyStateH}
-	H|\Psi\rangle =0
+	H|\Psi\rangle =0.
 \end{equation}
@@
 \begin{equation}
-	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle
-\end{equation}
-where the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfill the commutators
+	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle.
+\end{equation}
+Here the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
 \begin{equation}\label{bulk}
@@
 \begin{equation}\label{leftBoundary}
-	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N
+	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N,
 \end{equation}
 \begin{equation}\label{rightBoundary}
-	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-\lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N
+	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-\lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N.
 \end{equation}
@@
 \newline \newline
-\textbf{Remark}: only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$:
-	\begin{equation}
-		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle V^{*}|=0
+\textbf{Remark}: Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
+	\begin{equation}
+		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}\lambda_{a}\langle V^{*}|=0
 	\end{equation}
@@
 \subsection{The explicit form of the steady state}\label{subsection-exact}
-The MPA gives an abstract form of the steady state in terms of an algebra of operators.
-However, to write explicitly the steady state one should provide a representation of this algebra.
-Another approach is to directly use the commutators and the boundary actions to compute correlations.
-This path has been followed in \cite{vanicat2017exact} to find one-point and two-point correlations.
-Here we follow the same approach. We will show that the duality property established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the
+The MPA gives an abstract form of the steady state in terms of an algebra of operators. This path has been followed in \cite{vanicat2017exact} to find one and two-point correlations. 
+Here we follow the same approach. We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the
 computation. The idea is summarized as follows. We define a sequence of similarity transformation such that 
@@
 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal.
-Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the right eigenvector with vanishing eigenvalue $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly.
-Finally, reversing the transformations we will retrieve $|\Psi\rangle$.
-
-The first transformation $S_{1}$ is closely related to the dual matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
+Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler.
+As a consequence, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
+Finally, reversing the transformations we can retrieve $|\Psi\rangle$.
+
+The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
 Therefore, $H^{'}$ is not stochastic.
-The second transformation $S_{2}$ diagonalize the right boundary.
+The second transformation $S_{2}$ diagonalizes the right boundary.
 Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
@@
 The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
-Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ thanks to the simpler commutators.
-Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and  the arbitrary correlations in the non-equilibrium steady state.
+Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ exploiting the simpler commutators.
+Finally, we invert the similarities and retrieve the right eigenvector of $H^{'}$ with vanishing eigenvalue and  the arbitrary correlations in the non-equilibrium steady state.
 The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix \ref{appB}.
@@
 \begin{align}
-	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\\
-	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\label{S2Gen}
+	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen},\\
+	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}.\label{S2Gen}
 \end{align}
@@
 \begin{equation}\label{transformationV}
- \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+ \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)},%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
 \end{equation}
@@
 \end{equation}
- $S_{1}$ is invertible, then we introduce 
+ The transformation $S_{1}$ is invertible. We introduce 
 \begin{equation}\label{hatHamiltonian}
-   H^{'}:=H^{'}_{left}+H_{bulk}+H^{'}_{L}
+   H^{'}:=H^{'}_{left}+H_{bulk}+H^{'}_{right}
 \end{equation}
@@
 \begin{equation}
-	H^{'}_{left}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
+	H^{'}_{left}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{right}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
 \end{equation}
@@
 		\\&=
-		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)
+		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right).
 	\end{split}
@@
 \begin{equation}
-H_{left}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
-\end{equation}
-\textbf{Remark:} the boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e.
+H_{right}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
+\end{equation}
+\textbf{Remark:} The boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e.
 to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
@@
 \newline\newline
-Obviously
+We have the following correspondence between eigenvectors with zero eigenvalues
 \begin{equation}\label{S1-Inverse}
@@
 that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
-By taking the product over the chain
+Therefore, by taking the product over the chain we obtain 
 \begin{equation}\label{S2-Whole}
-	S_{2}=\prod_{x=1}^{L}S_{2}^{x}
+	S_{2}=\prod_{x=1}^{L}S_{2}^{x}.
 \end{equation}
@@
 \begin{equation}
-	H^{''}=S_{2}H^{'}S_{2}^{-1}
+	H^{''}=S_{2}H^{'}S_{2}^{-1}.
 \end{equation}
 The boundary Hamiltonians of $H^{''}$ read
-\begin{align}
-	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}^{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
-\end{align}
-i.e.
-the left one is lower triangular and depends on the differences between boundary parameters, while the right one is diagonal.
-The expressions of $H_{left}^{''}$ and $H_{right}^{''}$ are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A=e_{aN},$ and $A=e_{aa}$.
+\begin{align}\label{tri-diag-boundaryHamiltonians}
+	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}.
+\end{align}
+The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal.
+Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
+\begin{comment}
  We compute
 \begin{enumerate}
-	\item $A=e_{aN}$ with $a\neq 1$
+	\item $A_{N}=e_{aN}$ with $a\neq 1$
 	\begin{equation}
@@
 	\end{equation}
-\item $A=e_{aa}$ with $a\neq 1$
-\begin{equation}
-		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{x}\right)}e_{aa}^{x}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}^{x}\right)}=e_{aa}^{x}+\beta_{a}e_{aN}^{x}
+\item $A_{a}=e_{aa}$ with $a\neq 1$
+\begin{equation}
+		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
 	\end{equation}
@@
 \end{enumerate}
-Therefore, we have for the left boundary
+\end{comment}
+Therefore, using \eqref{HT-BA} we obtain for the left boundary 
 \begin{equation}
@@
 		\\&=
-		e_{NN}^{1}-\mathbbm{1}^{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
-	\end{split}
-\end{equation}
-Similarly, for the right boundary
+		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}.
+	\end{split}
+\end{equation}
+Similarly, using again \eqref{HT-BA} we have for the right boundary 
 \begin{equation}
@@
 			\\&=
-			e_{NN}^{L}-\mathbbm{1}^{L}
-	\end{split}
-\end{equation}
-Obviously
+			e_{NN}^{L}-\mathbbm{1}.
+	\end{split}
+\end{equation}
+The relation between eigenvectors with vanishing eigenvalue is 
 \begin{equation}\label{S2-Inverse}
@@
 \begin{equation}\label{steadyS-SECOND-def}
-	H^{''}|\Psi^{''}\rangle=0
-\end{equation}
-It is convenient to introduce also the whole transformation
+	H^{''}|\Psi^{''}\rangle=0.
+\end{equation}
+It is convenient to introduce also the transformation
 \begin{equation}\label{similarity}
@@
 \end{equation}
-and, obviously
+and, the relation between eigenvectors with vanishing eigenvalue is
 \begin{equation}

### 2023-10-03 main.tex
dot

@@
 \newcommand{\Xt}{\widetilde{X}}
+\newcommand{\co}{\;,}
+\newcommand{\dt}{\;.}
 
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left[f(\bm{n}-\bm{\delta}^{x}_{a}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right]
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left[f(\bm{n}-\bm{\delta}^{x}_{a}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right]\co
 \end{equation}
 \begin{equation}\label{siteGenerator}
-    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\bm{\delta}_{a}^{x}-\bm{\delta}_{b}^{x})-f(\bm{n})\right]
+    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\bm{\delta}_{a}^{x}-\bm{\delta}_{b}^{x})-f(\bm{n})\right]\co
 \end{equation}
@@
 1\qquad &\text{if}\quad y=x,\;b=a\\
-0\qquad &\text{otherwise}
+0\qquad &\text{otherwise}\dt
 \end{cases}\,.
@@
 \begin{equation}
- \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{|\alpha|}
+ \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{|\alpha|}\co
 \end{equation}
@@
 \begin{equation}
-	M_\twoj= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
+	M_\twoj= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}\dt
 \end{equation} 
@@
 \begin{equation}\label{ortho}
-   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}
+   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}\co
 \end{equation}
@@
 		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
-		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle
+		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle\dt
 	\end{cases}\,.
@@
 \begin{equation}
-   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
+   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}\dt
 \end{equation}
@@
 \begin{equation}\label{Hamiltonian-Generator}
-H=\mathcal{L}^{T}
+H=\mathcal{L}^{T}\dt
 \end{equation}
@@
 	\begin{split}
-		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle
+		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle\dt
 	\end{split}
@@
 \begin{equation}\label{DualityRelation}
-    H^{T}D=D\widetilde{H}
+    H^{T}D=D\widetilde{H}\dt
 \end{equation}
@@
 \begin{equation}
-	\widetilde{V}:=V\cup \left\{u(x)\,:\, x\in V\right\}\qquad \widetilde{\mathcal{E}}:=\mathcal{E}\cup \left\{(x,u(x))\,:\, x\in V\right\}
+	\widetilde{V}:=V\cup \left\{u(x)\,:\, x\in V\right\}\qquad \widetilde{\mathcal{E}}:=\mathcal{E}\cup \left\{(x,u(x))\,:\, x\in V\right\}\dt
 \end{equation}
@@
 \begin{equation}\label{dualStateSpace}
-    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})
+    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
 \end{equation}
@@
 \begin{equation}
-\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}
+\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
 \end{equation}
@@
 \begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)\dt
 \end{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}
+\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt
 \end{equation}
@@
 \begin{equation}
-    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\dt
 \end{equation}
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)
+    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
 \end{equation}
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
 \end{equation}
@@
 \begin{equation}
-	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
+	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0\dt
 \end{equation}
@@
 \begin{equation}
-	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0
+	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0\dt
 \end{equation}
@@
  \begin{align}\label{HT-BA}
- 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+\delta_{d<N}E_{cN}-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
+ 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+\delta_{d<N}E_{cN}-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}\dt
  \end{align}
@@
     \begin{split}
-H_{x}^{T}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}
+H_{x}^{T}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}\dt
     \end{split}
@@
 \begin{equation}\label{intermediateTransposeSite}
-    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}\dt
 \end{equation}
@@
 \begin{equation}\label{HadTransfBoundary}
-\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)
+\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\dt
 \end{equation}
@@
 \begin{equation}\label{siteHadamardI}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)
+H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\dt
 \end{equation}
@@
 \\=&
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}\right)
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}\right)\dt
     \end{split}
@@
 \begin{equation}\label{bosonicKX}
-    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})^{u(x)}_{a}
+    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})^{u(x)}_{a}\dt
 \end{equation}
@@
 \\&=
-\left(d_{x}\otimes \dd\right)\widetilde{H}_{x}
+\left(d_{x}\otimes \dd\right)\widetilde{H}_{x}\dt
     \end{split}
@@
 \begin{equation}
-	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}
+	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}\dt
 \end{equation} 
@@
 \begin{equation}
-	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\dt
 \end{equation}
@@
 \begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}
+	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}\dt
 \end{equation}
@@
 \begin{equation}
-	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}
+	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt
 \end{equation}
@@
 	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt
 	\end{split}
@@
 \begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
 \end{equation}
@@
 \begin{equation}\label{transpostionPropertyFund}
-	e_{ab}^T= e_{ba}
+	e_{ab}^T= e_{ba}\dt
 \end{equation}
@@
 \begin{equation}\label{ElementsDualityMatrixChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
 \end{equation}
@@
 \begin{equation}\label{boundary-H-dual-chain}
-	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)
+	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)\dt
 \end{equation}
@@
 \begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{s_{k}}^{s_{k}}=1\}}
+	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{s_{k}}^{s_{k}}=1\}}\dt
 \end{equation}
@@
 \begin{equation}
-    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle.
+    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle\dt
 \end{equation}
@@
 \begin{equation}\label{definition-SteadyStateH}
-	H|\Psi\rangle =0.
+	H|\Psi\rangle =0\dt
 \end{equation}
@@
 \begin{equation}
-	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle.
+	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle\dt
 \end{equation}
@@
 \begin{equation}\label{leftBoundary}
-	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N,
+	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N\co
 \end{equation}
 \begin{equation}\label{rightBoundary}
-	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-\lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N.
+	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-\lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N\dt
 \end{equation}
@@
 \begin{align}
-	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen},\\
-	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}.\label{S2Gen}
+	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\co\\
+	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
 \end{align}
@@
 \begin{equation}\label{transformationV}
- \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)},%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+ \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}\co %=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
 \end{equation}
@@
 \begin{equation}\label{S1-Whole}
-    S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}
+    S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}\dt
 \end{equation}
@@
 \begin{equation}\label{similarV}
-   H^{'}=S_{1}HS_{1}^{-1}
+   H^{'}=S_{1}HS_{1}^{-1}\dt
 \end{equation}
@@
 \begin{equation}
-	H^{'}_{left}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{right}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
+	H^{'}_{left}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{right}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 		\\&=
-		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right).
+		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\dt
 	\end{split}
@@
 \begin{equation}
-H_{right}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)
+H_{right}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
  \begin{equation}
- 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
+ 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
  \end{equation}
@@
 \begin{equation}\label{S2-Whole}
-	S_{2}=\prod_{x=1}^{L}S_{2}^{x}.
+	S_{2}=\prod_{x=1}^{L}S_{2}^{x}\dt
 \end{equation}
@@
 \begin{equation}\label{HSecond}
-	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}
+	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}\co
 \end{equation}
@@
 \begin{equation}
-	H^{''}=S_{2}H^{'}S_{2}^{-1}.
+	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
 \end{equation}
@@
 \begin{align}\label{tri-diag-boundaryHamiltonians}
-	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}.
+	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
 \end{align}
@@
 		\\&=
-		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}.
+		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
 	\end{split}
@@
 			\\&=
-			e_{NN}^{L}-\mathbbm{1}.
+			e_{NN}^{L}-\mathbbm{1}\dt
 	\end{split}
@@
 \begin{equation}\label{steadyS-SECOND-def}
-	H^{''}|\Psi^{''}\rangle=0.
+	H^{''}|\Psi^{''}\rangle=0\dt
 \end{equation}
@@
 \begin{equation}\label{similarity}
-	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}
+	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
 \end{equation}
@@
 \begin{equation}
-	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle
+	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
 \end{equation}

### 2023-10-04 main.tex
fix
N2 correlations

@@
 where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{s_{i}}^{y_{i}}$. 
+\\ \\
+\textbf{Remark}: If we stop distinguishing the types of particles we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}.
+Indeed, introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
+\begin{align}
+	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
+	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
+\end{align}
+We observe that, at most $q$ factors do survive in the product over $k$.
+Moreover, for a fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
+For each of these of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
+\begin{equation}
+	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
+\end{equation}
+For any $q\in\{1,\ldots,m\}$, we can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
+\begin{equation}
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
+\end{equation}
+Moreover, observing that 
+\begin{equation}
+	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
+\end{equation}
+All in all we obtain 
+\begin{equation}
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation}
+that is exactly equation (4.26) of \cite{frassek2020eigenstates}.
+
 \paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$.
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
 \end{equation}

### 2023-10-05 main.tex
fix

@@
 We observe that, at most $q$ factors do survive in the product over $k$.
-Moreover, for a fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
-For each of these of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
+For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
+For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
 \begin{equation}
@@
 \end{equation}
-For any $q\in\{1,\ldots,m\}$, we can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
+We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
 \begin{equation}
@@
 \end{equation}
-Moreover, observing that 
-\begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
+Moreover, we observe that 
+\begin{equation}
+	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
 \end{equation}

### 2023-10-05 main.tex
blue

@@
 \end{equation}
+
+{\color{blue}
+\begin{equation}
+  \mathcal{S}_{2}^{-1} |\tau\rangle= |\tau\rangle+\delta_{N,\tau}\sum_{a=1}^{N-1}\beta_a|a\rangle
+\end{equation} 
+\begin{equation}
+  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\tau}\rangle=\left( |\tau_1\rangle+\delta_{N,\tau_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\tau_L\rangle+\delta_{N,\tau_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
+\end{equation} 
+\begin{equation}
+  \langle \bm{\mu}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\tau}\rangle=\prod_{i=1}^L\left[ \delta_{\mu_i,\tau_i}+\delta_{N,\tau_i}\beta_{\mu_i} (1-\delta_{\mu_i,N)}\right]
+\end{equation}
+
+}
+
 We introduce the following notation

### 2023-10-05 main.tex
fix

@@
 \subsubsection{Explicit formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
-We state the following result: the steady state of the Hamiltonian $H^{''}$ is given by 
+We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle
+	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
 \end{equation}
@@
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
-We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators.
-For the sake of notation, we denote by 
+We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations.
+For the sake of notation 
 \begin{equation}
@@
 \end{equation}
-We have
+We define the transformed matrix product operators
 \begin{equation}\label{Xtildes2b}
@@
 				X_{1}+\ldots +X_{N}\\
-	\end{pmatrix}=\begin{pmatrix} 
-		X_{a}-\beta_{a}\Xt_{N}\\ 
-			X_{1}+\ldots +X_{N}\\
-	\end{pmatrix}\qquad \forall a=1,\ldots N-1
+	\end{pmatrix}%=\begin{pmatrix} 
+	%	X_{a}-\beta_{a}\Xt_{N}\\ 
+		%	X_{1}+\ldots +X_{N}\\
+	%\end{pmatrix}
+	\qquad \forall a=1,\ldots N-1
 \end{equation}
@@
 \end{equation}
-Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have
+Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have
 \begin{equation} 
@@
 \end{equation}
-therefore, we obtain the commutation relations for $\Xt_{a}$ 
+with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{1}$, see \eqref{Xtildes2b}. 
+Therefore, we obtain the commutation relations for $\Xt_{a}$ 
 \begin{equation}\label{commutationsBula}
@@
 \end{equation}
-where the basis is 
+where the normalization is given by 
+\begin{align}
+		Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle\dt
+\end{align}
+The basis is 
 $$
@@
 \begin{equation}\label{UsefulRelation}
-	\widetilde{X}_{a}\widetilde{X}_{N}=\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}
-\end{equation}
-Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying many times \eqref{UsefulRelation} we have
-\begin{align*}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
-	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
-	\\&=
-	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
-	\\&=\ldots\\&=
-	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
-\end{align*}
+	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left(\lambda_{a}+\widetilde{X}_{a}\right)
+\end{equation}
+Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
+\begin{align}\label{usefulRelaton-many}
+	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=%\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
+%	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
+%	\\&=
+%	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
+%	\\&=\ldots\\&=
+	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
+\end{align}
 therefore 
 \begin{align*}
-	\widetilde{X}_{N}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}
+	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}
 \end{align*}
@@
 \end{equation}
-Multiplying by the boundary vectors we have 
-\begin{equation}
+Multiplying by the boundary vectors and by using \eqref{commRIGHT} we have 
+%\begin{equation}
+%	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+%	|V \rangle=\langle %V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
+%\end{equation}
+%Using 
+\begin{align}
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
-\end{equation}
-Using \eqref{commRIGHT}
-\begin{align*}
-	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
-	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
-	\\&=
-	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}|V\rangle
-\end{align*}
-To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}n_{N}^{l}}|V\rangle$.
-Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and taking an arbitrary $a\in \{1,\ldots,N-1\}$ we have
+	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
+	\\&=
+	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
+	\\&=
+	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle
+\end{align}
+To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle$.
+Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain
 \begin{align*}
@@
 \end{align*}
+where in the second equality we used \eqref{usefulRelaton-many}. 
 This leads to the recursion relation
-\begin{equation}
-	\begin{cases}
-		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle\\
-		\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=1
-	\end{cases}
-\end{equation}
-that implies 
+\begin{align}
+		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
+\end{align}
+with $	\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=1$. 
+Therefore, we obtain 
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
 	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle

### 2023-10-06 main.tex
fix
c
Update main.tex
e

--- 2023-10-05 main.tex
@@
  \begingroup\LARGE
-\bf Multispecies stirring process: duality and exact solution
+%\bf Multispecies stirring process: duality and exact solution
+\bf Multispecies stirring process \\
+ with open boundaries
 \par\endgroup
@@
 \paragraph{Organization of the paper}
-\section{The stirring process}
+%
+%
+%
+%
+\section{The stirring process with open boundaries}
 \subsection{Informal description of the process}
-The process studied in this paper is the {\em multi-species stirring process}. 
+The process studied in this paper is the {\em multi-species stirring process}
+with open boundaries. 
 In words, the dynamics is described as follows. Each site
@@
 a particles of a given type (if present) is replaced with a
-particle of type $k$ at rate $\alpha_k^x >0$.
+particle of type $a$ at rate $\alpha_a^x >0$.
 The swap dynamics taking place on the edges is of Kawasaki-type 
@@
 (the total number of particles of each type). 
-The site-dynamics is instead of Glauber-type 
-and, in the long-time limit, so-called non-equilibrium
+The site-dynamics is instead of Glauber-type. 
+In the long-time limit, a so-called non-equilibrium
 steady state sets in.
@@
 \noindent
-{\bf Remark:} in the following we will often consider type $N$ as a distinguished type
+{\bf Remark.} In the following we will often consider type $N$ as a distinguished type
 (called `holes'), whose number at each site is fixed by the numbers of particles 
-of the remaining $N-1$ types (at the same site). It is interesting to observe that, in case we stop distinguishing the colors of the ``true'' particles of types $\{1,\ldots,N-1\}$, we retrieve the 
+of the remaining $N-1$ types. It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
+(those of types $\{1,\ldots,N-1\}$), we retrieve the 
 boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
@@
 \begin{equation}\label{stateSpace}
-    \Omega:=\bigtimes_{x\in V} \Omega_{x}
+    \Omega:=\bigotimes_{x\in V} \Omega_{x}
 \end{equation}
@@
 \end{equation}
-We denote a particle configuration as $\bm{n}\in \Omega$, where $\bm{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$ .\\
-The dynamics consists in an exchange of particles (at Poissonian times) between connected vertices.
-Moreover, each vertex  exchanges particles with the external environement.
+We denote a particle configuration on the graph as $\bm{n}\in \Omega$, where $\bm{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$.
 The infinitesimal generator of the process reads
@@
 \end{equation}
-where  $ \omega_{x,y}\geq 0$ are so-called conductances and $\Gamma_{x}\geq 0$ local inhomogeneities.
+where  $ \omega_{x,y}\geq 0$ are so-called conductances and $\Gamma_{x}\geq 0$ are the couplings to reservoirs. 
 The generator $\mathcal{L}_{x,y}$ is called the \textit{edge generator}, while $\mathcal{L}_{x}$ is called the \textit{site generator}.
@@
 (\bm{\delta}_{a}^{x})^{y}_{b}=\begin{cases}
-1\qquad &\text{if}\quad y=x,\;b=a\\
+1\qquad &\text{if}\quad y=x,\;b=a\;,\\
 0\qquad &\text{otherwise}\dt
-\end{cases}\,.
-\end{equation}
-{\color{red} notation}
+\end{cases}
+\end{equation}
+Thus the dynamics consists in an exchange of particles between connected vertices at Poissonian times. 
 This means that on the edge $(x,y)\in \mathcal{E}$  a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$. 
-Furthermore, on each site $x\in V$  a particle of type $b$ is replaced with a particle of type $a$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$.
-For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$.
-See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dynamics. 
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.45]{BulkStirring.eps}
-    \caption{The edge dynamics.
+Moreover, each vertex  exchanges particles with the external environment (reservoirs). 
+Namely, on each site $x\in V$  a particle of type $b$ is replaced with a particle of type $a$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$. 
+%
+%For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$. 
+%See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dynamics. 
+%\begin{figure}[h]
+%    \centering
+%    \includegraphics[scale=0.45]{BulkStirring.eps}
+%    \caption{The edge dynamics.
 Maximal occupation is $\nu=6$.
@@
 This transition occurs at rate $n_{2}^{x}n_{3}^{y}=2\cdot 3$.}
-    \label{fig:1}
-\end{figure}
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.4]{BoundaryStirring.eps}
-    \caption{The site dynamics.
+%    \label{fig:1}
+%\end{figure}
+%\begin{figure}[h]
+%    \centering
+%    \includegraphics[scale=0.4]{BoundaryStirring.eps}
+%    \caption{The site dynamics.
 Here the maxiaml occupation is $\nu=6$.
@@
 This transition occurs at rate $\alpha_{3}^{x}n_{2}^{x}$.}
-    \label{fig:2}
-\end{figure}
-\subsection{Reversible measures}
-The process described by the generator \eqref{Generator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasure}
-\mu_{rev}=\bigtimes_{x\in V}\mu_{rev}^{x}
-\end{equation}
-when for any $a\in\{1,\ldots,N\}$
+%    \label{fig:2}
+%\end{figure}
+\subsection{Reversible measures (equilibrium)}
+For a particular choice of the reservoir parameters one has an $N$-parameter family of reversible measures. More precisely
+when the parameters are the same on each site, i.e.
 \begin{equation}\label{reversibilityCondition}
-\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V\,.
-\end{equation}
-This measure has marginals $\mu_{rev}^{x}$ given by 
-\begin{equation}
- \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{a}=\frac{\alpha_{a}}{|\alpha|}\co
-\end{equation}
-namely
-\begin{equation}
-\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}
-\end{equation}
-where we denote $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. 
-This can be proved just by imposing the detailed balance conditions for the edge and for the site generators.
-If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own density $\alpha^{x}=(\alpha_{1}^{x},\ldots,\alpha_{N}^{x})$ and currents will arise when at least two of them are different.
-
-{\color{red}add/improve explanaition of entire subsection} {\color{blue}Is it not standard?}
+\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V\,,
+\end{equation}
+then the process described by the generator \eqref{Generator} is reversible with respect to the 
+homogeneous product measure 
+\begin{equation}
+\label{reversibleMeasure}
+\mu_{rev}=\bigotimes_{x\in V}\mu_{rev}^{x}
+\end{equation}
+with marginals $\mu_{rev}^{x}$ given by 
+\begin{equation}
+ \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\,.
+\end{equation}
+Here
+ $$
+\rho_{a}=\frac{\alpha_{a}}{|\alpha|}\co
+$$
+is the density of specie $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 
+\begin{equation}
+\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}\,.
+\end{equation}
+This can be proved  by checking that detailed balance is satisfied. 
+If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
+ $$
+\rho_{a}^x=\frac{\alpha_{a}}{|\alpha^x|}
+$$
+and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}$. 
+Currents will arise when at least two reservoirs have different densities.
+
 \subsection{The Lie algebraic description}
@@
 where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{s_{i}}^{y_{i}}$.  
-\\ \\
-\textbf{Remark}: If we stop distinguishing the types of particles we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}.
-Indeed, introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
-\begin{align}
-	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
-	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
-\end{align}
-We observe that, at most $q$ factors do survive in the product over $k$.
-For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
-For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
-\begin{equation}
-	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
-\end{equation}
-We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
-\begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
-\end{equation}
-Moreover, we observe that 
-\begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
-\end{equation}
-All in all we obtain 
-\begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
-\end{equation}
-that is exactly equation (4.26) of \cite{frassek2020eigenstates}.
-
 \paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$.

### 2023-10-06 main.tex

--- 2023-10-05 main.tex
@@
 \begin{align}
-		Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle\dt
+		Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V\rangle\dt
 \end{align}
@@
 	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
-	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle
-	\\&=
-	\frac{\Gamma(2+n_{N})}{\Gamma(2)}
+	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=
+	\Gamma(2+n_{N})
 \end{align*}
@@
 \begin{align*}
-	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle=
-	\frac{\Gamma(2+L)}{\Gamma(2)}
+	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}\widetilde{X}_{N}^{L}|V|\rangle=
+	\Gamma(2+L)
 \end{align*}
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle
+	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle
 \end{equation}
@@
 \begin{equation}
-	\frac{\Gamma(2+\sum_{x=1}^{L}n_{N}^{x})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}
+	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}
 \end{equation}
@@
 \begin{equation}
-|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle
+|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle
 \end{equation}
@@
 \begin{equation}
-  \mathcal{S}_{2}^{-1} |\tau\rangle= |\tau\rangle+\delta_{N,\tau}\sum_{a=1}^{N-1}\beta_a|a\rangle
-\end{equation} 
-\begin{equation}
-  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\tau}\rangle=\left( |\tau_1\rangle+\delta_{N,\tau_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\tau_L\rangle+\delta_{N,\tau_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
-\end{equation} 
-\begin{equation}
-  \langle \bm{\mu}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\tau}\rangle=\prod_{i=1}^L\left[ \delta_{\mu_i,\tau_i}+\delta_{N,\tau_i}\beta_{\mu_i} (1-\delta_{\mu_i,N)}\right]
+  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\tau}\sum_{a=1}^{N-1}\beta_a|a\rangle
+\end{equation} 
+\begin{equation}
+  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
+\end{equation} 
+\begin{equation}
+  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
 \end{equation}
@@
     \begin{equation}
-\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)\right)^{1-\delta_{\tau_{y},N}}
+\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{j},N})\right)\right)^{1-\delta_{\tau_{y},N}}
 \end{equation}
@@
 \begin{equation}
-	c_{y}=(1-\delta_{\tau_{y},N}) \qquad \forall y\in \{1,\ldots L\}
+	c_{y}\in\{0,1\} \qquad \forall y\in \{1,\ldots L\}
 \end{equation}

### 2023-10-06 main.tex
proof

@@
 \begin{equation}
-   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}
-\end{equation}
-
-{\color{blue}
-\begin{equation}
-  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\tau}\sum_{a=1}^{N-1}\beta_a|a\rangle
-\end{equation} 
+   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}\co
+\end{equation}
+which action on the occupation variable of a site is 
+\begin{equation}
+  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
+\end{equation} 
+Therefore, taking the tensor product over the chain we obtain 
 \begin{equation}
@@
 \end{equation} 
-\begin{equation}
+By projecting over a vector $\langle \bm{\tau}|$ we have 
+\begin{equation}\label{goodTP-S2}
   \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
 \end{equation} 
-
-}
-
+For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, using equation \eqref{ResulsBasis} and observing that 
+\begin{equation}
+	\left(1+\sum_{j=y}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\mu_{y},N})\right)
+\end{equation}
+we obtain 
+\begin{equation}
+	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\dt
+\end{equation}
+Introducing $c_{x}$ defined as 
+\begin{equation}
+	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}
+\end{equation}
+we obtain 
+\begin{equation}\label{coefficients-psiSec}
+	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{y}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
+\end{equation}
+where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.
+\begin{comment}
 We introduce the following notation
@@
     \end{equation}
-where, $\forall x\in\{1,\ldots,L\}$, we have introduced
+\end{comment}
+We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 
 \begin{equation}
@@
 		N\qquad &\text{otherwise}\\
-	\end{cases}
-\end{equation}
-where $i\in\{1,\ldots,L\}$. The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
+	\end{cases}\dt
+\end{equation}
+ This is a new configuration where  $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ with $N$ and leaves the others sites with the same occupation.
+The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
+    \begin{comment}
     We prove it by induction. When $L=1$ it is true, indeed
@@
 \end{align*}
+\end{comment}
     \begin{comment}
@@
 \end{equation}
-\end{comment}
+
 The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
@@
 \end{equation}
-
-Therefore, we have that 
+\end{comment}
+By considering a fixed $\langle\bm{\tau}|$, by taking \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients \eqref{coefficients-psiSec} and by using \eqref{goodTP-S2} we write
 \begin{equation}\label{ABS_intermediate}
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation}
-For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$, using equation \eqref{ResulsBasis} and observing that 
-\begin{equation}
-  \left(1+\sum_{j=y}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},N})\right)
-\end{equation}
-we obtain 
-    \begin{equation}
-\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{j},N})\right)\right)^{1-\delta_{\tau_{y},N}}
-\end{equation}
-Introducing
-\begin{equation}
-	c_{y}\in\{0,1\} \qquad \forall y\in \{1,\ldots L\}
-\end{equation}
-and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation}
+
+Therefore, we have that equation \eqref{ABS_intermediate} becomes
 
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 	\end{split}

### 2023-10-06 main.tex
Update main.tex

@@
 
-\subsection{The Lie algebraic description}
+\subsection{Lie algebraic description}
+
+In this paper we will often use the fact that the Markov generator of the multispecies stirring process can be described in terms a Lie algebra of rank $N$.
+In this section we provide details about this.
 
@@
 \end{equation}
-The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with  $\lambda_i\geq \lambda_{i+1}$,  $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$.
+The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with  $\lambda_i\geq \lambda_{i+1}$,  $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu\in\mathbb{N}$.
 We are interested in the {\em symmetric} finite-dimensional representations with 
 \begin{equation}\label{eq:dynkin}
-    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
+    \lambda=(\twoj,0,\ldots,0) \;.
+    %\qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
 \end{equation} 
@@
 The generators of the symmetric representations will be denoted by $E_{ab}$.
-The basis elements of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
+A basis of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
 \begin{equation}
@@
 %where $\sum_{a=1}^{N}n_{i}=\nu$. 
+{\color{red}
 The basis vectors satisfy the orthogonality relation with respect to the Euclidean scalar product 
@@
 where  $ \langle m_{1},\ldots,m_{N}|$ is the row vectors obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
+}
 The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
@@
 	\begin{cases}
-		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
+		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\qquad\qquad a\neq b\\[0.1cm]
 		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle\dt
-	\end{cases}\,.
+	\end{cases}
 \end{equation}  
@@
 {\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-The process with generator \eqref{Generator} can be described in terms of $gl(n)$ Lie algebra generators.
-The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site, namely
+The process with generator \eqref{Generator} can be described in terms of $gl(N)$ Lie algebra generators.
+The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site.
+Namely,
+a vector $|{\bf n}\rangle \in \Omega$ can be written as
 %We now define the equivalent of \eqref{stateSpace} in the vector notation
@@
 \end{equation}
-where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have $\sum_{a=1}^{N}n_{a}^{x}=\nu$.
-Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
+%where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
+with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
+{\color{red}
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
@@
 \end{equation}
-
-{\color{red}Maybe some more text below}
+}
+
 We introduce the Hamiltonian operator
@@
 \end{equation}
-{\color{red} no minus sign?} {\color{blue}I think we decided to keep it without minus sign}
 The action of the generator can also be expressed as 
@@
 \begin{equation}
-    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
-\end{equation}
-
-We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
+    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|
+\end{equation}
+
+We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the {\color{red} quadratic} Casimir of $gl(N)$
 \begin{equation}\label{secondCasimir}
-    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
-\end{equation}
-that acts diagonally as $C_{2}|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
+    C=\sum_{a,b=1}^{N}E_{ab}E_{ba}
+\end{equation}
+that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
 More precisely,  considering the standard coproduct 
@@
 \begin{equation}
-\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}\,.
+\Delta(C)=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C\otimes \mathbbm{1}+\mathbbm{1}\otimes C\,.
 \end{equation}
@@
 \begin{equation}\label{hamiltonianCasimir}
-	\mathcal{H}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
-\end{equation}
-where $\Delta^{x,y}(C_2)$ denotes a {\color{blue}copy} of $\Delta(C_2)$ acting on  
-the edge $(x,y)\in \mathcal{E}$.
+	\mathcal{H}_{x,y}=\frac{1}{2}\Delta_{x,y}(C)-\twoj(2\twoj+N)
+\end{equation}
+where $\Delta_{x,y}(C)$ denotes a copy of $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.
 
@@
 These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium.
-The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
+The Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are
 \begin{equation}
@@
 \end{equation}
-and the local inhomogeneities are
+and the coupling to reservoirs are
 \begin{equation}
@@
 We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
-We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e.
+We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
 $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
@@
 \end{equation}
-Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
+Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the vertices of the edge $x,x+1$) of the two-site Hamiltonian
 \begin{equation}\label{H-corsivo}
@@
 \end{equation}
-Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
+Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
 

### 2023-10-09 main.tex
Update main.tex
app

@@
 	\begin{split}
-		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
+		H=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
 	\end{split}
@@
 \begin{equation}\label{ratesConditions}
-	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
+	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1\;.
 \end{equation} 
@@
 		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
-		\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
+		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
 		\\&
-		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
+		\sum_{c_{1}=0}^{1-\delta_{\eta_{1}^{b},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L}^{b},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}^{b}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}^{b}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
 	\end{split}
@@
 where we have introduced, $\forall x\in \{1,\ldots,L\}$
-\begin{equation}
-	\eta_{x}(b)=\begin{cases}
+\begin{equation}\label{eta-notation}
+	\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
 		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-		d_{x}\qquad &\text{otherwise}
+		i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
 	\end{cases}%\qquad \theta_{x}=\begin{cases}
@@
 	\end{equation}
-	The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
+	The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
 \begin{comment}
@@
 	\begin{equation}\label{S1-L1}
-		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},N}\sum_{d_{1}=1}^{N-1}e_{1}^{d_{1}}
-	\end{equation}
+		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
+	\end{equation}
+thus
+\begin{equation}
+\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)\delta_{\mu<N}|N\rangle
+\end{equation}
+By taking the tensor product over the chain we obtain 
+\begin{equation}
+	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)\delta_{\mu_{1}<N}|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)\delta_{\mu_{L}<N}|N\rangle\right)
+\end{equation}
+therefore, projecting on $\langle \bm{\tau}|$ we have
+\begin{equation}
+	\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
+\end{equation}
+\begin{comment}
 	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
@@
 \\
-		\end{comment}
 		The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
@@
 Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
-		\begin{equation}
-			\begin{split}
-				\Psi(\bm{\tau}) &=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{\tau}}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
+		\end{comment}
+	By introducing the notation \eqref{eta-notation} and by considering 
+	\begin{equation}
+		|\Psi^{'}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{'}(\bm{\mu})|\bm{\mu}\rangle
+	\end{equation} we obtain  
+		\begin{equation}
+			\begin{split}
+				\Psi(\bm{\tau}) &=\langle\bm{\tau}|\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
 				\\&
-				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})
+				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})
 			\end{split}
@@
 		\end{equation}}
+
+indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
 \end{comment}
-indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
  Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}. 

### 2023-10-09 main.tex
fix

@@
 \end{flushright}
-\subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}
+\subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
 In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
@@
 
-\section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}
+\section{Exact steady state and correlations for the integrable chain}\label{sectionIntegrabiliy}
 In this section we aim to use duality and the matrix product ansatz (MPA) to determine the moments and correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
@@
 As a by-product, absorption probabilities can be explicitly found.%, giving a further probabilistic interpretation for the non-equilibrium steady state.
-\subsection{The integrable chain and the non-equilibrium steady state}
+\subsection{Matrix product ansatz for the non-equilibrium steady state}
 The matrix product ansatz has been formulated in \cite{vanicat2017exact}, here we briefly recall it.

### 2023-10-09 main.tex
fix

@@
 %\end{equation}
-\paragraph{Proof of formula \eqref{ABS-vect}} As a consequence of \eqref{S2-Inverse}, we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
+\paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
 Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
@@
 We give some examples of correlations applying formula \eqref{exactCorrelations}.
-\paragraph{One point correlations}
+\paragraph{One-point correlations}
 The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
@@
 \end{equation}
-\paragraph{Two points correlations}
-The two points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+\paragraph{Two-point correlations}
+The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
 \begin{equation}
@@
 \paragraph{Three points correlations}
-The three points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
+The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
 \begin{equation}

### 2023-10-09 main.tex
N2

@@
 \end{equation}
+\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+Moreover, we call $\ell_{1},\ldots,\ell_{q}$ the coordinates where particles of type $1$ are present.
+Thus, the coefficient of the above formula can be written as
+\begin{align}
+&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)\right]^{1-\delta_{\tau_{x},N}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=k+1}^{q}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}
+\end{align}
+Moreover, for each $q\in \{1,\ldots,L\}$ we introduce the coordinates $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ and, by varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Therefore, we can write 
+\begin{equation}
+	|\Psi^{''}\rangle=\sum_{q=0}^{L}\lambda_{1}^{k}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
+\end{equation}
 %and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.

### 2023-10-09 main.tex
fix

--- 2023-10-09 main.tex
@@
 \end{equation}
+\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+Moreover, we call $\ell_{1},\ldots,\ell_{q}$ the coordinates where particles of type $1$ are present.
+Thus, the coefficient of the above formula can be written as
+\begin{align}
+&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},N}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=k+1}^{q}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}
+\end{align}
+Moreover, for each $q\in \{1,\ldots,L\}$ using the coordinates $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$, calling $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$ and, by varying $q$, we have a one-to-one mapping with $\bm{\tau}$.
+Therefore, we can write
+\begin{equation}
+	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
+\end{equation}
 %and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
@@
 %\end{equation}
+\textbf{Remark}: In case of $N=2$ we can argue as in the case of $|\Psi^{''}\rangle$ and we obtain 
+\begin{equation}
+	|\Psi^{'}\rangle= 
+\end{equation}
 \paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+		\Psi^{'}(\bm{\tau})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\mathbbm{1}_{\{c_{1}+\ldots+c_{L}>0\}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\\&\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
 	\end{split}

### 2023-10-09 main.tex
fixx
fix 1

@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{x=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{y}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
 		\end{split}
@@
 %\end{equation}
-\textbf{Remark}: In case of $N=2$ we can argue as in the case of $|\Psi^{''}\rangle$ and we obtain 
-\begin{equation}
-	|\Psi^{'}\rangle= 
-\end{equation}
+\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$.
+Indeed, the empty species does not produce changes in the correlations between the non-empty species.
 \paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\mathbbm{1}_{\{c_{1}+\ldots+c_{L}>0\}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\\&\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{\tau_{y}}\right)^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}
 	\end{split}
@@
 \end{flushright}
-
+\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}.
+If we stop distinguishing types of non-empty particles we have that \eqref{ABS} reads
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
+	\\&\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)\dt
+\end{align}
+where $x_{k}$ denotes the position of the particle $k$ among $q$.
+For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
+For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
+\begin{equation}
+	\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}\dt
+\end{equation}
+We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
+\begin{equation}
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-\ell_{k}-(q-k+1)\right)\dt
+\end{equation}
+Moreover, we observe that 
+\begin{equation}
+	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
+\end{equation}
+All in all we obtain 
+\begin{equation}\label{PsiI-N2}
+\Psi^{'}(\bm{\ell},q)=\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-\ell_{k}-q+k\right)}{(2+L-k)}\dt
+\end{equation}
+where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. 
 \subsection{Exact steady state correlations}\label{correlation-section}
@@
 \\ \\
-\textbf{Remark}: If we stop distinguishing the types of particles we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}.
-Indeed, introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
+\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}.
+Indeed, by adapting \eqref{PsiI-N2} we obtain
+\begin{comment} introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
 \begin{align}
@@
 \end{equation}
-All in all we obtain 
+\end{comment}
 \begin{equation}

### 2023-10-09 main.tex
fix

@@
 \textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
-Moreover, we call $\ell_{1},\ldots,\ell_{q}$ the coordinates where particles of type $1$ are present.
+Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
+By varying $q$, we have a one-to-one mapping with $\bm{\tau}$.
 Thus, the coefficient of the above formula can be written as
@@
 &\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},N}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
-=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=k+1}^{q}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}
-\end{align}
-Moreover, for each $q\in \{1,\ldots,L\}$ using the coordinates $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$, calling $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$ and, by varying $q$, we have a one-to-one mapping with $\bm{\tau}$.
+=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
+\end{align}
 Therefore, we can write 
@@
 \end{flushright}
+\begin{comment}
 \textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}.
-If we stop distinguishing types of non-empty particles we have that \eqref{ABS} reads
-\begin{align}
-	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
-	\\&\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)\dt
-\end{align}
-where $x_{k}$ denotes the position of the particle $k$ among $q$.
-For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
-For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
-\begin{equation}
-	\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}\dt
-\end{equation}
-We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
-\begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-\ell_{k}-(q-k+1)\right)\dt
+If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
+	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
+\end{align}
+ For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
+\begin{equation}
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
+\end{equation}
+where $x_{k}$ is the position of the $k$-th particle among $q$. 
+We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, thus we have that 
+\begin{equation}
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
 \end{equation}
@@
 \begin{equation}\label{PsiI-N2}
-\Psi^{'}(\bm{\ell},q)=\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-\ell_{k}-q+k\right)}{(2+L-k)}\dt
-\end{equation}
-where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. 
+\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation}
+\end{comment}
 \subsection{Exact steady state correlations}\label{correlation-section}
@@
 Indeed, by adapting \eqref{PsiI-N2} we obtain
-\begin{comment} introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
+ introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
 \begin{align}
@@
 \end{equation}
-\end{comment}
+All in all we have that
 \begin{equation}

### 2023-10-09 main.tex
fix 2

@@
 \end{equation}
-\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
 Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
@@
 \end{align}
-Therefore, we can write 
+Therefore, we write 
 \begin{equation}
@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{x=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{y}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
+			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
 		\end{split}
@@
 Indeed, the empty species does not produce changes in the correlations between the non-empty species.
+\\ \\
+\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty.
+We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites.
+We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS} as
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
+	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
+\end{align}
+For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
+\begin{equation}
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
+\end{equation}
+We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$.
+Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$.
+It follows that we have
+\begin{equation}
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
+\end{equation} 
+Observing that
+\begin{equation}
+	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
+\end{equation}
+we finally obtain 
+\begin{equation}\label{PsiI-N2}
+	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation}
+
 \paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 Indeed, by adapting \eqref{PsiI-N2} we obtain
+\begin{comment}
  introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
@@
 All in all we have that
+\end{comment}
 \begin{equation}

### 2023-10-10 main.tex
fix
ll
dd

@@
 \begin{equation}
-H_{right}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
+H_{right}^{'}=S_{1}H_{right}S_{1}^{-1}=
+% \exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=
+\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 \begin{equation}\label{S2-Whole}
-	S_{2}=\prod_{x=1}^{L}S_{2}^{x}\dt
+	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
 \end{equation}
@@
 	\begin{split}
-		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
-		\\&=
+		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}
+% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
+		=
 		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
-		\\&=
+		=
 		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
@@
 	\begin{split}
-			H_{right}^{''}&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
-			\\&=
+			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
+% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
+			=
 			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
-			\\&=
 			e_{NN}^{L}-\mathbbm{1}\dt
@@
 \begin{align}
-&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},N}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
 =\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt

### 2023-10-10 main.tex
fix

@@
 \begin{equation}
-H_{right}^{'}=S_{1}H_{right}S_{1}^{-1}=
-% \exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=
-\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
+H_{right}^{'}=\exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 \begin{equation}\label{S2-Whole}
-	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
+	S_{2}=\prod_{x=1}^{L}S_{2}^{x}\dt
 \end{equation}
@@
 	\begin{split}
-		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}
-% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
-		=
+		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
+		\\&=
 		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
-		=
+		\\&=
 		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
@@
 	\begin{split}
-			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
-% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
-			=
+			H_{right}^{''}&=S_{2}H_{right}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
+			\\&=
 			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
+			\\&=
 			e_{NN}^{L}-\mathbbm{1}\dt
@@
 \end{equation}
-\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
-\begin{equation}\label{Tau-Notation}
-	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
-		\tau_{1}\\
-		\vdots\\
-		\tau_{L}
-	\end{pmatrix}
-\end{equation}
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-This notation is equivalent to the one introduced in Subsection \ref{subsectionGeneratorStr}.
-Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$.
-Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$.
-With this notation, we have that
-\begin{equation}\label{notation}
-	|n^{x}\rangle =\tau_{x}\qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
-\end{equation}
-with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. 
+
 \begin{comment}
@@
 \subsubsection{Explicit formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
+\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
+\begin{equation}\label{Tau-Notation}
+	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
+		\tau_{1}\\
+		\vdots\\
+		\tau_{L}
+	\end{pmatrix}
+\end{equation}
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
+This notation is equivalent to the one introduced in Subsection \ref{subsectionGeneratorStr}.
+Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$.
+Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$.
+With this notation, we have that
+\begin{equation}\label{notation}
+	|n^{x}\rangle =\tau_{x}\qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
+\end{equation}
+with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\
 We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
@@
 a species with label from $1$ to $N-1$.
-This is motivated by interest of understanding how actual particles of the chain are correlated among each others and also because the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
+This is motivated by the interest of understanding how actual particles of the chain are correlated among each others and also because in the steady state the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=1-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
@@
 	\end{equation}
-\textbf{Remark}: using binomial theorem we rewrite the \eqref{exactCorrelations} as 
+\textbf{Remark}: using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
 \begin{equation}
@@
 \end{equation}
-By exchanging the summations we rewrite it as 
+By exchanging the summations we rewrite as 
 \begin{equation}

### 2023-10-10 main.tex
l
ss

--- 2023-10-10 main.tex
@@
 \textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
-Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
+Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
 By varying $q$, we have a one-to-one mapping with $\bm{\tau}$.
@@
 \\ \\
-\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}.
+\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}.
 Indeed, by adapting \eqref{PsiI-N2} we obtain
@@
 \end{equation}
-that is exactly equation (4.26) of \cite{frassek2020eigenstates}.
 
@@
 \subsubsection{Explicit examples of steady state correlations}
-We give some examples of correlations applying formula \eqref{exactCorrelations}.
+We give examples  of correlations for up to three points applying formula \eqref{exactCorrelations}.
 \paragraph{One-point correlations}
@@
 \begin{equation}
-	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})
+	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})\dt
 \end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}
+\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}\dt
 \end{equation}
@@
 	\begin{split}
-	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})
+	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})\dt
 	\end{split}
@@
 	\begin{split}
-	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})
+	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\dt
 	\end{split}
@@
 	\begin{split}
-		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)
-	\end{split}
-\end{equation}
-\paragraph{Three points correlations}
+		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)\dt
+	\end{split}
+\end{equation}
+\paragraph{Three-point correlations}
 The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
 \begin{equation}
-    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})
+    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})\dt
 \end{equation}
@@
         \\&+\nonumber
-        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
+        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
 \end{align}
@@
 	\\&=
-	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})
-\end{align}
-\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, are exactly the ones found in subsection 4.3 of \cite{vanicat2017exact}. 
+	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
+\end{align}
+\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}. 
 \section{Mapping to equilibrium} \label{Section-Mapping}

### 2023-10-10 main.tex
ll

@@
 	\begin{split}
+% <<<<<<< HEAD
+% 			H_{right}^{''}&=S_{2}H_{right}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
+% 			\\&=
+% =======
 			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
@@
 			=
+% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
 			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=

### 2023-10-10 main.tex
Update main.tex

@@
 \subsection{Definition}
-Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
+Consider two Markov processes, $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
 We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have
@@
 where $\mathbb{E}_{\eta}$ denotes the expectation with respect to the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect to the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
-The duality definition can also be formulated as a relation between the generators.
+The duality definition can also be formulated as a relation between the generators, provided some minimal technical conditions are satisfied \cite{jansen2014notion}.
 Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect to the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$
@@
 \textbf{Remark}:
-when the state spaces of the dual processes is finite, the generators and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
+when the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$.
 Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as
 \begin{equation}
-    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})
+    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')
 \end{equation}
@@
 where the superscript $T$ denotes the matrix transposition.
-Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$.
-Working in terms of the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads
+Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}^{\,T}$.
+Working in terms of the Hamiltonian operators the duality relation reads
 \begin{equation}\label{DualityRelation}
@@
 \end{equation}
-\subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
-In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}.
+\subsection{Duality for the open multi-species stirring process}\label{statementDualitySubsection}
+In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ with open boundaries, defined by the generator \eqref{Generator}.
 The dual  process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the \textit{enlarged graph} $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E}})$ where 
@@
 \end{equation}
-This means that to each site $x\in V$ we associate an ``extra-site'', denoted $u(x)$. The configuration space of the dual process is the enlarged state space
+This means that to each site $x\in V$ we associate an ``extra-site'' via a bijection $u:V\to V$.
+We denote as $u(x)$ the extra-site asspciated to $x\in V$ .
+The configuration space of the dual process is the enlarged state space
 \begin{equation}\label{dualStateSpace}
-    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
+    \widetilde{\Omega}= \bigotimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigotimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
 \end{equation}

### 2023-10-10 main.tex
Update main.tex

@@
 If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
- $$
+\begin{equation}
+\label{rhox}
 \rho_{a}^x=\frac{\alpha_{a}}{|\alpha^x|}
-$$
+\end{equation}
 and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}$. 
@@
 \end{equation}
-Dual particle will accumulate in these extra-sites in the course of time. We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+Note that on the extra-site we allow an unbounded number of particles. Thus
+dual particle will accumulate in these extra-sites in the course of time. 
+We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
 \begin{equation}
@@
 
-The duality function is given by
+We define the duality function of the open multi-species stirring process as
 \begin{equation}\label{dualityElements}
@@
 \end{equation}
-where we denote the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$  by 
-\begin{equation}
-\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
+where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
+\begin{equation}
+\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
 \end{equation}
@@
 \textbf{Remark}: in the reversible situation, i.e.
-when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
+when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
 \begin{equation}
@@
 \subsection{Proof of duality}
-To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{dualityIntertwines} is fulfilled.
-To show this, we will use the Hamiltonians (linked with the Markov generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
-Indeed, in this formalism the proof reduces to finding symmetries and group like transformation of generators of the Lie algebra.\\
+To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.
+To show this, we will use the Hamiltonians and their Lie algebraic description.
+Indeed, in this formalism the proof
+reduces to finding symmetries of the generator (for the bulk duality) and group like transformations (for the ``boundary duality'').
+
 To a configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of a dual process we associate the vector
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
-\end{equation}
-Here we introduced bosonic creation operator $a^{\dagger}$ acting on the left-hand-side as $\langle q|a^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(a^{\dagger})_{a}^{u(x)}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
-We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. The duality matrix $D$ is described as 
+    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
+\end{equation}
+Here we introduced bosonic creation operator $A^{\dagger}$ acting on the left-hand-side as $\langle q|A^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
+$(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
+We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}.
+From an algebraic point of view, the duality matrix $D$ \eqref{dualityElements} is described as
 \begin{equation}\label{dualityMatrix}
-    D=\prod_{x\in V}d_{x}\otimes \dd
-\end{equation}
-where
+    D=\prod_{x\in V}d_{x}\otimes \dd \;.
+\end{equation}
+Here
 \begin{equation}\label{bulkElementDualityMatrix}
@@
 with 
-\begin{equation}\label{EquationEx}
-E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}
-\end{equation}
-and
 \begin{equation}\label{Revmatrix}
@@
 \end{equation}
-and where 
+and
+\begin{equation}\label{EquationEx}
+E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}\,.
+\end{equation}
+Furthermore
 \begin{equation}\label{dualityMatrix2}
@@
 \end{equation}
-The matrix $R_{x}$ is diagonal.
+We observe that the matrix $R_{x}$ is diagonal.
 Its elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}.
-In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $p_{i}=\frac{1}{N}$.
+In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $\rho_{a}=\frac{1}{N}$.
 Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation.
-This $R_{x}$ is called the ``cheap'' duality matrix (see \cite{giardina2009duality}).
+This $R_{x}$ is called the ``cheap'' duality matrix and is associated to reversibility (see \cite{giardina2009duality}).
 \\
+
 Since \eqref{dualityMatrix} is product over sites, proving \eqref{DualityRelation} is equivalent to showing that 
@@
 \end{equation}
-We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show \eqref{siteDualRelation}.
+We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove the bulk duality \eqref{edgeDualRealtion}; finally we will show the boundary duality \eqref{siteDualRelation}.
 As a preliminary result we note that 
@@
 \end{comment}
-\paragraph{Elements of the duality matrix.}We aim to show that 
+\paragraph{Elements of the duality matrix.}
+Consider the matrix $D$ defined in \eqref{dualityMatrix}.
+We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
 \begin{equation}\label{proofDualityElements}
-\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}
-\end{equation}
-with $D(\bm{n},\bm{\xi})$ defined in \eqref{dualityElements}. 
+\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
+\end{equation}
 Fix an arbitrary site $x\in V$, then we have that 
@@
 \end{align*}
-where we used the orthogonality relation \eqref{ortho}. 
+where {\color{red} we used the orthogonality relation \eqref{ortho}}. 
 On the other hand, on the site $x$, we have 

### 2023-10-10 main.tex
check

@@
 As a consequence, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
-Finally, reversing the transformations we can retrieve $|\Psi\rangle$.
+Finally, reversing the transformations we retrieve $|\Psi\rangle$.
 
@@
 \begin{equation}\label{hatHamiltonian}
-   H^{'}:=H^{'}_{left}+H_{bulk}+H^{'}_{right}
+   H^{'}=H^{'}_{left}+H_{bulk}+H^{'}_{right}
 \end{equation}
@@
 \end{equation}
-The boundary Hamiltonians of $H^{''}$ read
+The boundary Hamiltonians of $H^{''}$ reads
 \begin{align}\label{tri-diag-boundaryHamiltonians}
@@
 \begin{equation}\label{notation}
-	|n^{x}\rangle =\tau_{x}\qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
-\end{equation}
-with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\
+	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
+\end{equation}
+with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\ \\
 We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
+	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
 	\\&=
@@
 To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle$.
-Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain
+Calling $\sum_{i=1}^{L}n_{N}^{i}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain
 \begin{align*}
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
+	|V \rangle=\Gamma(2+n_{N})\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 \end{equation} 
-For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, using equation \eqref{ResulsBasis} and observing that 
-\begin{equation}
-	\left(1+\sum_{j=y}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\mu_{y},N})\right)
-\end{equation}
-we obtain 
-\begin{equation}
-	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\dt
+We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 
+\begin{equation}
+	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\
+		N\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{i}\}\\
+	\end{cases}\dt
+\end{equation}
+This is a new configuration where the occupations $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ at sites $q_{1},\ldots,q_{i}$ are replaced with $N$'s, while the occupations on the other sites are left untouched.
+The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
+By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain
+\begin{equation}\label{ABS_intermediate}
+	\begin{split}
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation}
+For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis},we obtain 
+\begin{equation}
+	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\co
+\end{equation} where we have used the fact that 
+\begin{equation}
+	\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\mu_{x},N})\right)\co
 \end{equation}
@@
 \begin{equation}
-	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}
+	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}\co
 \end{equation}
@@
 \end{equation}
-where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.
+where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.\\
 \begin{comment}
@@
 \end{comment}
-We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 
-\begin{equation}
-	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\
-		N\qquad &\text{otherwise}\\
-	\end{cases}\dt
-\end{equation}
- This is a new configuration where  $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ with $N$ and leaves the others sites with the same occupation.
-The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
     \begin{comment}
@@
 \end{comment}
-By considering a fixed $\langle\bm{\tau}|$, by taking \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients \eqref{coefficients-psiSec} and by using \eqref{goodTP-S2} we write
-\begin{equation}\label{ABS_intermediate}
-	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation}
-
-Therefore, we have that equation \eqref{ABS_intermediate} becomes
-
+%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
+%Therefore, we have that equation \eqref{ABS_intermediate} becomes
 %Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
+Therefore, using equation \eqref{ABS_intermediate}, we obtain 
 \begin{equation}\label{elementsABS}

### 2023-10-11 main.tex
fix

@@
 Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
-By varying $q$, we have a one-to-one mapping with $\bm{\tau}$.
 Thus, the coefficient of the above formula can be written as
@@
 \end{align}
-Therefore, we write 
+By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore, we write 
 \begin{equation}
@@
 \begin{align*}
-	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}
+	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}\dt
 \end{align*}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
+	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\dt
 \end{equation}
@@
 	\\&=
-	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle
+	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle \dt
 \end{align}
@@
 \end{equation} 
-We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 
+We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ 
 \begin{equation}
@@
 \end{equation}
-This is a new configuration where the occupations $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ at sites $q_{1},\ldots,q_{i}$ are replaced with $N$'s, while the occupations on the other sites are left untouched.
+This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$.
 The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.

### 2023-10-11 main.tex
Remove mapping

@@
      X_{N}
-	\end{pmatrix}\quad \forall a\in \{1,\ldots,N-1\}
+	\end{pmatrix}\quad \forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
-	\end{pmatrix}\qquad\forall a\in \{1,\ldots,N-1\}
+	\end{pmatrix}\qquad\forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation} 
-	\left[X_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad\forall a=1,\ldots,N
+	\left[X_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad\forall a=1,\ldots,N\co
 \end{equation}
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}
+	\left[\Xt_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}\widetilde{X}_{N}^{L}|V|\rangle=
-	\Gamma(2+L)
+	\Gamma(2+L)\dt
 \end{align*}
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle
+	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle\dt
 \end{equation}
@@
 \begin{equation}
-	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}
+	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\dt
 \end{equation}
@@
 \begin{equation}
-|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle
+|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle\dt
 \end{equation}
@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
+			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
 		\end{split}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)\dt
 \end{equation}
@@
 \begin{equation}
-  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
+  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt
 \end{equation} 
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}
+		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
 	\end{split}
@@
 =&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})
+f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
 \end{split}
@@
 \sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
-=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})
+=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
 \end{split}
@@
 \begin{equation}
- \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+ \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
 \end{equation}
@@
 \textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
-\section{Mapping to equilibrium} \label{Section-Mapping}
-{\color{red}check also Appendix A in
-\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz}} \\
-In Section \ref{sectionIntegrabiliy}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations.
-To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal.
-These diagonal boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}.
-For this reason, we say that the process is mapped onto equilibrium.
-This can be represented by the diagram 
-\begin{equation}
-	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
-\end{equation} 
-Namely, the following equation holds true
-\begin{equation}
-	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
-\end{equation}
-The eigenvectors and the eigenvalues of $H_{0}$ have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
-As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$
-\begin{equation}
-	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
-\end{equation}
-Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e.
-a state where all the sites are empty.
-This last transformation $W$ is non-local and to be constructed requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM).
-\subsection{The non local transformation}\label{SectionNonLocalTrasformation}
-We define the equilibrium Hamiltonian as
-\begin{equation}
-	H^{0}=H_{left}^{0}+H_{bulk}+H^{0}_{right}
-\end{equation}
-where
-\begin{equation}
-	H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{0}=e_{NN}^{L}-\mathbbm{1}^{L}
-\end{equation}
-Therefore we have that
-\begin{equation}
-	H^{''}=H^{0}+H^{B}
-\end{equation}
-where
-\begin{equation}
-	H^{B}=\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
-\end{equation}
-We look for a matrix $W$ such that 
-\begin{equation}\label{GoalWH}
-	H^{''}W=WH_{0}
-\end{equation}
- We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}=\sum_{x=1}^{L}n_{i}^{x}$, i.e.
-$m_{i}$ indicates the total occupation over the chain of each species $i\in\{1,\ldots,N\}$.
-Observe that $|\bm{m}|=\sum_{i=1}^{N}m_{i}=L$.
-We denote by $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$.
-We prove that
-\begin{equation}\label{W-extended}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-\paragraph{Construction of the matrix W}
-We aim to show that \eqref{W-extended} fulfils \eqref{GoalWH}. Consider the \textit{resolvent operator}
-\begin{equation}
-	\mathcal{R}(z,H^{''}):=\left(z-H^{''}\right)^{-1}
-\end{equation}
-where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the $\mathcal{R}(x,H^{''})$ is well defined. 
-The above equation implies that 
-\begin{equation}
-	(z-H^{''})\mathcal{R}(H^{''},z)=I
-\end{equation}
-In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix an arbitrary $\epsilon>0$ and consider $z=\mathcal{E}_{\bm{m}}+\epsilon$, 
-\begin{equation}
-	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1
-\end{equation}
-We multiply both sides by $|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|$
-\begin{equation}
-	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
-\end{equation}
-by summing over all possible $\bm{m}$'s such that $|\bm{m}|=L$ and multiply by $\epsilon$ both sides
-%\begin{equation}
-%	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
-%\end{equation}
-%we multiply both sides by $\epsilon$ 
-\begin{equation}
-	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.
-\end{equation}
-We take the limit for $\epsilon\to 0$ on both sides 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-We first observe that
-\begin{equation}
-	\lim_{\epsilon\to 0}\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)=\left(\Lambda_{\bm{m}}-H^{''}\right)<\infty
-\end{equation}
-Second, using the power expansion
-\begin{equation}\label{veryUsefulSeries}
-	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
-\end{equation}
-we have that, for each $\bm{m}$, 
-\begin{equation}
-	\begin{split}
-		&\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\mathcal{E}_{\bm{m}}+\epsilon)^{-1}H^{''}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
-		\\=&
-		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\mathcal{E}_{\bm{m}}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-\mathcal{E}_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
-	\end{split}
-\end{equation}
-Since both factor are finite, the limit of the product is the product of the limit and we obtain
-\begin{equation}
-	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
-\end{equation}
-Since the limit of the sum is the sum of the limit   
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-Recalling that $|\Psi_{\bm{m}}^{0}\rangle$ are the eigenvectors with eigenvalue $\mathcal{E}_{\bm{m}}$ of $H_{0}$ we have 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-Since $H_{0}=H_{0}^{T}$ 
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-By calling 
-\begin{equation}
-	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-\end{equation}
-we finally obtain 
-\begin{equation}
-	WH_{0}=H^{''}W
-\end{equation}
-Formula \eqref{W-extended} may be evaluated by perturbation theory (see \cite{frassek2020duality}).
-Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system.
-This expression allows a simpler treatment of the mapping and also allows to  find a closed formula for the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$.
-To achieve this aim, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}).
-In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$ situation.
-\subsection{Quantum inverse scattering method}\label{SubsectionQISM}
-We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$.
-In the case of the multi-species stirring process we chose $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$.
-We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$
-\begin{equation}\label{Rmatrix}
-	R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
-\end{equation}
-and the $K$-matrices
-\begin{comment}
-	\begin{equation}
-		\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
-	\end{equation}
-	\begin{equation}
-		K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
-	\end{equation}
-\end{comment}
-\begin{equation}\label{KmatrixHAT}
-	\widehat{K}_{a}(x)=(1+x)\left(I+\frac{2x}{x+1}H^{''}_{right}\right)=\begin{pmatrix}
-		1-x&0&\ldots&0\\
-		0&1-x&\ldots&0\\
-		\vdots&\vdots&\ddots&\vdots\\
-		0&0&\ldots&1+x
-	\end{pmatrix}
-\end{equation}
-\begin{equation}\label{Kmatrix}
-	K_{a}(x)=\frac{\left((2x+N)H^{''}_{left}+(x+N)I\right)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
-		-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
-		0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
-		\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
-		0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
-		0&0&0&\ldots&0&N+x
-	\end{pmatrix}
-\end{equation}
-where the lower index $a\in\{0,\ldots,L\}$ means that these matrices are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$.
-Variables $x,y\in\mathbb{C}$ are called spectral parameters.
-The matrices $R_{a,b}(x)$, $K_{a}(x)$ and $\widehat{K}_{a}(x)$ satisfy:
-\begin{itemize}
-	\item \textit{Yang-Baxter-Equation}
-	\begin{equation}
-		R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
-	\end{equation}
-	\item \textit{Boundary-Yang-Baxter-Equation}
-	\begin{equation}
-		R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
-	\end{equation}
-	\item \textit{Dual Boundary-Yang-Baxter-Equation}
-	\begin{equation}
-		K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
-	\end{equation}
-\end{itemize}
-We introduce the \textit{transfer matrix}
-\begin{equation}
-	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
-\end{equation}
-that satisfies
-\begin{equation}
-	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(x))\lvert_{x=0}=C_{1}H^{''}+C_{2}I
-\end{equation}
-with $C_{1},C_{2}>0$. \\
-The matrix $U_{0}(x)$ used to construct $T(x)$ is called double row monodromy and it is given by
-\begin{equation}
-	U_{0}(x)=M_{0}(x)\widehat{K}_{0}(x)\widehat{M}_{0}(x)
-\end{equation}
-where 
-\begin{equation}
-	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}(x)=R_{0L}(x)\ldots R_{01}(x)
-\end{equation}
-$U_{0}(x)$ satisfies the following relation
-\begin{equation}\label{RURU}
-	R_{ab}(x-y)U_{a}(x)R_{ab}(x+y)U_{b}(y)=U_{b}(y)R_{ab}(x+y)U_{a}(x)R_{ab}(x-y)
-\end{equation}
- $U_{0}(x)$ can be written in the canonical basis of $V_{0}$ 
-\begin{comment}
-	\begin{equation}
-		U_{0}(x)=\begin{pmatrix}
-			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
-			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
-			\vdots&\vdots&\ddots&\vdots\\
-			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
-		\end{pmatrix}
-	\end{equation}
-\end{comment}
-\begin{equation}\label{matrixForm-U}
-	U_{0}(x)=\begin{pmatrix}
-		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
-		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
-		\vdots&\vdots&\ddots&\vdots&\vdots\\
-		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
-		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
-	\end{pmatrix}
-\end{equation}
-where each of the above element acts on the quantum space $V$. Using \eqref{RURU}, we find some \textit{exchange relations} that the elements of $U_{0}(x)$ must satisfy: 
-\begin{itemize}
-	\item for every $i\in\{1,\ldots,N-1\}$
-	\begin{equation}\label{EX1}
-		\begin{split}
-			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
-		\end{split}	
-	\end{equation}
-	\begin{equation}\label{EX2}
-		\begin{split}
-			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
-		\end{split}
-	\end{equation}
-	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
-	\begin{equation}\label{EX3}
-		\begin{split}
-			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
-			\\&+
-			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
-			\\&+
-			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
-			\\&+
-			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
-		\end{split}
-	\end{equation}
-\item for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
-\begin{equation}\label{EX4}
-	\begin{split}
-		D_{i,j}(x)B_{i}(y)=&-(x-y)h_{1}(x,y)B_{i}(y)D_{i,j}(x)+f_{2}(x,y)\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(y)D_{k,j}(x)\\+&\frac{1}{(x-y)}\left(B_{j}(y)D_{i,i}(x)-B_{j}(x)D_{i,i}(y)\right)\\+&\frac{1}{2}h_{3}(x,y)\left((1+x-y)B_{j}(x)D_{N,N}(y)-B_{j}(y)D_{N,N}(x)\right)
-	\end{split}
-\end{equation}
-and
-\begin{equation}\label{EX5}
-	D_{i,j}(x)B_{j}(y)=\frac{(x-y)}{(x-y-1)}B_{j}D_{i,j}(x)+\frac{1}{(y+1-x)}D_{i,j}(y)B_{j}(x)
-\end{equation}
-\item  for every $i,j,k\in \{1,\ldots,N-1\}$ such that $i\neq j\neq k$
-\begin{equation}\label{EX6}
-	D_{i,j}(x)B_{k}(y)=B_{k}(y)D_{i,j}(x)+\frac{1}{(x-y)}\left(B_{k}(y)D_{j,i}(x)-B_{k}(x)D_{j,i}(y)\right)
-\end{equation}
-\end{itemize}
-where
-\begin{align}
-	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
-	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
-	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
-\end{align}
-\subsection{Charges}
-Using the matrix form of $U_{0}(x)$ \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads
-\begin{equation}
-	\begin{split}
-		T(x)=%tr_{0}&\left(\begin{pmatrix}
-			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
-		%	0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
-		%	\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
-		%	0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
-		%	0&0&0&\ldots&0&N+x
-	%	\end{pmatrix}\right.
-	%	\;\;\;\begin{pmatrix}
-	%		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
-	%		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
-	%		\vdots&\vdots&\ddots&\vdots&\vdots\\
-	%		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
-	%		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
-	%	\end{pmatrix}\right)\\
-	%=&
-	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
-	\end{split}
-\end{equation}
-By construction, $T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$, i.e. 
-\begin{equation}
-	\begin{split}
-		T(x)=
-		\sum_{k=0}^{2L+2}Q^{k}x^{k}
-	\end{split}
-\end{equation}
-where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q^{k}$ the \textit{conserved charges} of the system. 
-\begin{comment}
-We also introduce 
-\begin{equation}
-	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
-\end{equation}
-\end{comment}
-Arguing similarly, we also write the elements of $U_{0}(x)$ as polynomials in $x$ 
-\begin{equation}
-	D_{N,N}(x)=\sum_{k=0}^{2L+1}D_{N,N}^{k}x^{k}\quad D_{i,i}(x)=\sum_{k=0}^{2L+1}D_{i,i}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}\quad D_{i,j}(x)=\sum_{k=0}^{2L}D_{i,j}^{k}x^{k}
-\end{equation}
-We will need the charge expansion of $T(x)$.
-As it will be clear in the following, only the first three conserved charges of the systems.
-As a consequence, we will compute only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed.
-Therefore, using \eqref{RURU}, we compute:
-\begin{itemize}
-	\item For $D_{N,N}(x)$: 
-\begin{equation}
-	D_{N,N}^{2L+1}=I^{tot}
-\end{equation}
-\begin{equation}\label{DNN-charge}
-	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
-\end{equation}
-\begin{equation}
-	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
-\end{equation}
-
-\item For $D_{i,i}(x)$ with arbitrary $ i\in\{1,\ldots,N-1\}$
-
-\begin{equation}\label{a2lp}
-	D_{ii}^{2L+1}=-I^{tot}
-\end{equation}\begin{equation}\label{Dii-charge}
-	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
-\end{equation}
-\begin{equation}
-	D_{ii}^{2L-1}=2Ne_{ii}^{tot}+ 2e_{NN}^{tot}-L -2\sum_{j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
-\end{equation}
-
-\item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
-\begin{equation}\label{B-charge}
-		B_{j}^{2L-1}=	2e_{jN}^{tot}e_{NN}^{tot}-2\sum_{a,b=1\,:\, a<b}^{L}\,\sum_{k=1}^{N}e_{kN}^{[a]} e_{jk}^{[b]}
-\end{equation}
-
-\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
-\begin{equation}\label{Dij-Charge}
-D_{i,j}^{2L}=-2e_{ji}^{tot}
-\end{equation}
-\end{itemize}
-\textbf{Remark}: when restricted to the case of $N=2$ species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
-Using these polynomial expansions we write the first three conserved charges of the system
-
-\begin{align}
-Q^{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
-\end{align}
-\begin{align}
-Q^{2L+1}&=ND_{N,N}^{2L+1}+D_{N,N}^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
-\end{align}
-\begin{align}
-Q^{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
-\end{align}
-The charges $Q^{2L+2}$ and $Q^{2L+1}$ are proportional to the identity matrix, while $Q^{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
-By construction it follows that 
-\begin{equation}
-\left[Q^{2L},H^{''}\right]=Q^{2L}H^{''}-H^{''}Q^{2L}=0
-\end{equation}
-while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
-\begin{equation}
-Q^{2L}_{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
-\end{equation}
-that is, using the coefficients previously computed, 
-\begin{equation}\label{Q0Exp}
-\begin{split}
-Q^{2L}_{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
-\end{split}
-\end{equation}
-We also introduce 
-\begin{equation}\label{Q-nonDiag}
-Q_{+}^{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
-\end{equation}
-where, for the sake of notation we have denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we write 
-\begin{equation}
-Q^{2L}=Q^{2L}_{0}+Q_{+}^{2L}
-\end{equation}
-Observe that $Q^{2L}$ and $Q^{2L}_{0}$ are isospectral. \\
-%  It has the property that commute with the equilibrium Hamiltonian.
-
-Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}.
-All terms are diagonal except the last one.
-This last non-diagonal term can be identified with the second Casimir of the $gl(N-1)$ subalgebra.
-We denote it by $\hat{C}_{2}^{N-1}$, i.e.
-\begin{equation}
-\hat C_2^{N-1}= \sum_{i,j=1}^{N-1}e_{ij}^{tot}e_{ji}^{tot}
-\end{equation} 
-Moreover, we denote its eigenvalues by $C_{2}^{N-1}$.
-Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$ (branching rule).
-As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$.
-On each of these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ as
-\begin{equation}
-C_2^{N-1}=\sum_{j=1}^{N-1}\ell_j(\ell_j -N+2)+\frac{1}{6}(N-1)(N-2)(N-3)
-\end{equation} 
- where we introduce the shifted weights
- \begin{equation}
- 	\ell_{j}=\mu_{j}+N-j
- \end{equation}
-with $\mu_{j}$ the representation labels of irreducible representation of $gl(N)$. This argument allows to write explicit expression for the eigenvalues of $Q_{0}^{2L}$, indeed 
-\begin{equation}
-\begin{split}
-\Lambda(x)&= \Lambda_{2L+2} x^{2L+2}+ \Lambda_{2L+1} x^{2L+1}+ \Lambda_{2L}x^{2L}+\ldots
-\\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_N+1)-(N+2)(L-m_N)+2C_{2}^{N-1}\right)x^{2L}+\ldots
-\end{split}
-\end{equation} 
-In the following, we will denote by 
-\begin{equation}
-	\Lambda_{\bm{m}}:=N+2m_1(m_N+1)-(N+2)(L-m_{N})+2C_{2}^{N-1}
-\end{equation}
-the eigenvalues for arbitrary $\bm{m}$ of $Q_{0}^{2L}$. 
-\begin{comment}
-{\color{blue}
-Thus the following difference is of order $2L$
-\begin{equation}
-\Lambda(x)-T_0(x)=x^{2L}\left(\Lambda_{2L}-Q_{2L}^0\right)+\ldots
-\end{equation} 
-In the following it will be useful to compute the quantity 
-\begin{equation}
-\lim_{x\to\infty}\frac{2x+N}{\Lambda(x)-T_0(x)}B_{i}(x)=\frac{2}{\Lambda_{2L}-Q_{2L}^0}B_i^{2L-1}
-\end{equation} }
-\end{comment}
-\paragraph{Exchange relations between charges} It is useful to find explicit exchange relations among the coefficients of the polynomial form of the elements of the matrix $U_{0}(x)$ defined in \eqref{matrixForm-U}.
-Using relations \eqref{EX1}-\eqref{EX6} we obtain:
-\begin{itemize}
-	\item 
-for every $i,j\in\{1,\ldots,N-1\}$ 
-\begin{equation}\label{ExQ0B-charges}
-Q_{0}^{2L}B_{i}^{2L-1}=B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{j=1\,:\,j\neq i}^{N-1}B_{j}^{2L-1}D_{j,i}^{2L}
-\end{equation}
-%In particular for the case $N=3$ we have
-%\begin{equation}
-%	\begin{split}
-%	Q_{0}^{2L}B_{1}^{2L-1}&=B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{3,3}^{2L})\right)-2B_{2}^{2L-1}D_{2,1}^{2L}
-%	\\
-%	Q_{0}^{2L}B_{2}^{2L-1}&=B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{3,3}^{2L})\right)-2B_{1}^{2L-1}D_{1,2}^{2L}
-%	\end{split}
-%\end{equation}
-Other useful exchange relations are 
-\begin{equation}\label{ExDNB-charges}
-\begin{split}
-D_{N,N}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}\left(D_{N,N}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%\\
-%D_{33}^{2L}B_{2}^{2L}&=B_{2}^{2L}\left(D_{33}^{2L}+D_{22}^{2L+1}-D_{33}^{2L+1}\right)
-\end{split}
-\end{equation}
-and
-\begin{equation}\label{ExDiB-charges}
-\begin{split}
-D_{i,i}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}\left(D_{i,i}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%\\
-%D_{22}^{2L}B_{2}^{2L}&=B_{2}^{2L}\left(D_{22}^{2L}+D_{22}^{2L+1}-D_{33}^{2L+1}\right)
-\end{split}
-\end{equation}
-and finally
-\begin{equation}\label{ExDijB-charges}
-\begin{split}
-D_{i,j}^{2L}B_{i}^{2L-1}&=B_{i}^{2L-1}D_{i,j}^{2L}+B_{j}^{2L-1}\left(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}\right)%	D_{21}^{2L}B_{2}^{2L-1}&=B_{2}^{2L-1}D_{21}^{2L}+B_{2}^{2L-1}\left(D_{22}^{2L+1}-D_{33}^{2L+1}\right)
-\end{split}
-\end{equation}
-\item  for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j\neq k\neq i,$
-\begin{equation}\label{Commuting-Charges}
-\left[D_{j,j}^{2L},B_{i}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},B_{j}^{2L-1}\right]=0\qquad \left[B_{i}^{2L-1},D_{j,i}^{2L}\right]=0\qquad \left[B_{k}^{2L-1},D_{j,i}^{2L}\right]=0%\left[D_{12}^{2L},B_{2}^{2L-1}\right]=0\qquad \left[D_{11}^{2L},B_{2}^{2L-1}\right]=0
-\end{equation}
-\end{itemize} 
-%{\color{blue}Using them we also have 
-%\begin{equation}
-%\begin{split}
-	%&Q_{0}^{2L}B_{1}^{2L-1}Q_{0}^{2L}B_{2}^{2L-1}\\=&B_{1}^{2L-1}B_{2}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{22}^{2L}+2D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right.\\-&\left.2B_{1}^{2L-1}B_{1}^{2L-1}D_{12}^{2L}-2B_{2}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)\left(Q_{0}^{2L}-2(D_{22}^{2L}+D_{33}^{2L})\right)
-	%\\&+
-	%\left(-2B_{1}^{2L-1}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{11}^{2L}+D_{33}^{2L})+4(D_{33}^{2L+1}-D_{11}^{2L+1})\right)+8B_{1}^{2L-1}B_{2}^{2L-1}D_{21}^{2L}\right)D_{12}^{2L}
-%\end{split}
-%\end{equation}}{\color{blue}Probably it is not useful}
-\subsection{Conserved charges form of W}
-Using the QISM results found in the previous subsections it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system. Indeed, thanks to integrability
-\begin{equation}
-	[H^{''},T(x)]=0
-\end{equation}
-Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
-\begin{equation}
-	Q^{2L}W=WQ_{0}^{2L}
-\end{equation}
-Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{\bm{m}}$, one can show that 
-\begin{equation}\label{WInCharges}
-	\begin{split}
-	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-Q_{+}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
-\end{split}
-\end{equation}
-This expression in function of charges carries some advantages: firstly the eigenvalues $\Lambda_{\bm{m}}$ can be more easily computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a form that can be used to extract the steady state by rising the vacuum state of $H_{0}$.
-We first show this last property in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$.\\ \\
-\textbf{Remark}: in the $gl(2)$ case a closed formula can be found for all the non-equilibrium eigenvectors (not just for the steady state), since the exchange relations between charges are simpler.
-However, in the general $gl(N)$ case, only the steady state can be found via a closed and simple relation.
-\subsection{The gl(2) case}\label{SubsectionGL2}
-Here the multi-species stirring process reduces to the Simple Symmetric Exclusion Process (SSEP).
-We have that for every magnon number $m\in\{0,\ldots,L\}$ non-equilibrium eigenvectors $|\Psi_{m}\rangle$ of $H^{''}$, can be written in terms of the eigenvectors $|\Psi_{m}^{0}\rangle$ of the equilibrium Hamiltonian $H_{0}$ by the following formula
-\begin{equation}\label{Nice-W2}
-	\begin{split}
-		|\Psi^{''}\rangle=W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}\frac{\Delta^{k}}{k!}\left(\frac{B_{1}^{2L-1}}{2}\right)^{k}\frac{\Gamma(\sigma_{0}^{tot}+2-k)}{\Gamma(\sigma_{0}^{tot}+2)}|\Psi_{m}^{0}\rangle
-	\end{split}
-\end{equation}
-where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix and where $B_{1}^{2L-1}$ is given in \eqref{B-charge}.
-In particular, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state
-\begin{equation}
-	|\Psi_{0}^{0}\rangle=\underbrace{\begin{pmatrix}
-		0\\1
-	\end{pmatrix}\otimes \ldots\otimes \begin{pmatrix}
-	0\\
-	1
-\end{pmatrix}}_{\text{L-times}}
-\end{equation} we retrieve the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N=2$. \\
-Equation \eqref{Nice-W2} gives an explicit formula in term of the $B_{1}^{2L-1}$ of the matrix $W$.
-We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges.
-We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a slightly different technique to obtain it.
-\subsubsection{Proof of formula \eqref{Nice-W2}}
-The double row monodromy reads
-\begin{equation}
-	U_{0}=\begin{pmatrix}
-		D_{1,1}(x)&C_{1}(x)\\
-		B_{1}(x)&D_{2,2}(x)
-	\end{pmatrix}
-\end{equation}
-Using \eqref{Q-nonDiag} we rewrite \eqref{WInCharges} as
-\begin{equation}\label{W}
-	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|
-\end{equation}
-Power expanding the matrix $W$ using \eqref{veryUsefulSeries} and denoting $\Delta_{1}=(\alpha_{1}-\beta_{1})$ we obtain 
-\begin{equation}\label{LinkWG}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\
-		=&\lim_{\epsilon\to 0}\sum_{m=0}^{L}\epsilon\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
-		\\=&
-		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
-	\end{split}
-\end{equation}
-where in the last equality we used that $\forall m\in \{1,\ldots,L\}$
-\begin{equation}
-	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle=|\Psi_{m}^{0}\rangle
-\end{equation}
-Expression \eqref{LinkWG} can be rewritten using the adaptation to $gl(2)$ of the exchange relation between charges written in \eqref{ExQ0B-charges},\eqref{ExDNB-charges} and \eqref{ExDiB-charges}.
-These relation now read
-\begin{equation}\label{exchangeQ0B}
-	Q_{0}^{2L}B_{1}^{2L-1}=B_{1}^{2L-1}\left(Q_{0}^{2L}-2\left(D_{2,2}^{2L}+D_{1,1}^{2L}\right)\right)
-\end{equation}
-
-\begin{equation}
-	D_{2,2}^{2L}B_{1}^{2L-1}=B_{1}^{2L-1}\left(D_{2,2}^{2L}-Q_{0}^{2L+2}\right)
-\end{equation}
-and 
-\begin{equation}
-	D_{1,1}^{2L}B_{1}^{2L-1}=B_{1}^{2L-1}\left(D_{1,1}^{2L}-Q_{0}^{2L+2}\right)
-\end{equation}
-Therefore we obtain 
-\begin{equation}\label{exchangeQk}
-	\begin{split}
-		(Q_{0}^{2L}B_{1}^{2L-1})^{k}&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+\mathbbm{1}_{\{j>1\}}4\sum_{i=1}^{j-1}(j-i)Q_{0}^{2L+2}\right)\\
-		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\\
-		&=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)
-	\end{split}
-\end{equation}
-Recalling series expansion defined in \eqref{veryUsefulSeries}
-\begin{equation}
-	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
-\end{equation}
-we obtain 
-\begin{equation}
-	\begin{split}
-		\left\{(\Lambda_{m}+\epsilon-Q_{0}^{2L})^{-1}B_{1}^{2L-1}\right\}^{k}
-		=(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left(\Lambda_{m}+\epsilon-Q_{0}^{2L}+4j(1+e_{11}^{tot}-e_{22}^{tot})-4j(j-1)\right)^{-1}
-	\end{split}
-\end{equation}
-Therefore we have that 
-\begin{equation}\label{intermediate-Wgl2}
-	\begin{split}
-		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\
-		=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}+\epsilon)^{-1-n}(Q_{0}^{2L})^{n}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}+\epsilon)^{-1-n}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}\right\}^{k}
-		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{B_{1}^{2L-1}\left((\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}\right\}^{k}
-	\end{split}
-\end{equation}
-By replacing \eqref{intermediate-Wgl2} in \eqref{LinkWG}, we obtain 
-\begin{equation}\label{GoodBleft}
-	\begin{split}
-		W|\Psi_{m}^{0}\rangle=&\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-2j(D_{2,2}^{2L}+D_{1,1}^{2L})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
-		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-4j(1+e_{11}^{tot}-e_{22}^{tot})+4j(j-1)\right)\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
-		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-Q_{0}^{2L}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation}
-Using again \eqref{veryUsefulSeries} and re-summing the series we obtain 
-\begin{equation}
-	\begin{split}
-		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{(\Lambda_{m}+\epsilon)-\Lambda_{m}+4j(e_{11}^{tot}-e_{22}^{tot})-4j^{2}+8j\right\}^{-1}|\Psi_{m}^{0}\rangle|_{\epsilon=0}
-		\\=&
-		\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\frac{1}{4^{k}}\frac{1}{k!}\prod_{j=1}^{k}\left\{e_{11}^{tot}-e_{22}^{tot}+2-j\right\}^{-1}|\Psi_{m}^{0}\rangle
-	\end{split}
-\end{equation}
-Observing that $e_{22}^{tot}|\Psi_{m}^{0}\rangle=m|\Psi_{m}^{0}\rangle$ and $e_{11}^{tot}|\Psi_{m}^{0}\rangle=(L-m)|\Psi_{m}^{0}\rangle$ we obtain 
-\begin{equation}
-	\begin{split}
-		W|\Psi_{m}^{0}\rangle=&	\sum_{k=0}^{L}2^{k}\Delta^{k}(B_{1}^{2L-1})^{k}\prod_{j=1}^{k}\left\{L-2m+2-j\right\}^{-1}|\Psi_{m}^{0}\rangle
-	\end{split}
-\end{equation}
-Since 
-\begin{equation}
-	(L+2m+2-j)=\frac{\Gamma(L-2m+2-j+1)}{\Gamma(L-2m+2-j)}\quad \Rightarrow\quad \prod_{j=1}^{k}(L-2m+2-j)^{-1}=\frac{\Gamma(L-2m+2-k)}{\Gamma(L-2m+2)}
-\end{equation}
-indeed
-\begin{equation}
-	\prod_{j=1}^{k}(L-2m+2-j)^{-1}=\frac{\Gamma(L-2m+2-1)}{\Gamma(L-2m+2)}\frac{\Gamma(L-2m+2-2)}{\Gamma(L-2m+2-2+1)}\cdots\frac{\Gamma(L-2m+2-k+1)}{\Gamma(L-2m+2-k+2)}\frac{\Gamma(L-2m+2-k)}{\Gamma(L-2m+2-k+1)}
-\end{equation}
-Finally, introducing the Pauli matrix $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$, we obtain \eqref{Nice-W2}. 
-\begin{flushright}
-	$\square$
-\end{flushright}
-\subsection{The gl(N) case}\label{SubsectionGLN}
-In the general case of $N>2$ species we have that \eqref{WInCharges} reads 
-\begin{equation}\label{W-charges-Bad}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
-		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation}
-where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain.
-Here $SYM$ is the following transformation.
-We introduce, the indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that
-\begin{equation}
-	\begin{split}
-		&i_{1}=\ldots=i_{k_{1}}=1\\
-		&	i_{k_{1}+1}=\ldots=i_{k_{1}+k_{2}}=2\\
-		&\vdots\\
-		&i_{k_{1}+\ldots+k_{N-2}+1}=\ldots=i_{k_{1}+\ldots+k_{N-1}}=N-1
-	\end{split}
-\end{equation}
-We define
-\begin{equation}
-	\begin{split}
-		&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
-		=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}
-	\end{split}
-\end{equation}
-where $Sym$ is the symmetric group among $N-1$ objects. \\
-In this case we do not have a closed formula for all non-equilibrium eigenvectors. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator
-\begin{equation}
-	-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}
-\end{equation}
-This extra creation operator, mixes up the species different from $N$.
-However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do simplify.
-\paragraph{Proof of formula \eqref{W-charges-Bad}}
-Performing a multi-variable power expansion of formula \eqref{WInCharges} using \eqref{veryUsefulSeries} and denoting $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
-\begin{equation}
-	\begin{split}
-		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-	\end{split}
-\end{equation} 
-where we used the fact that 
-\begin{equation}
-	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
-\end{equation}
-This implies \eqref{W-charges-Bad}. 
-%\begin{equation}
-%	\begin{split}
-%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilonQ_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilonQ_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
-%		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
-%	\end{split}
-%\end{equation}
-\begin{flushright}
-	$\square$
-\end{flushright}
-\subsection{Non-equilibrium steady state from the W transformation}\label{subsection-NONSS-W}
-Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state $|\Psi_{m}^{0}\rangle$ of the Hamiltonian $H_{0}$, defined as
-\begin{equation}\label{Vacuum-state}
-	|\Psi_{0}^{0}\rangle:=\underbrace{\begin{pmatrix}
-			0\\
-			\vdots\\
-			0\\
-			1
-		\end{pmatrix}\otimes \cdots \otimes\begin{pmatrix}
-			0\\
-			\vdots\\
-			0\\
-			1
-	\end{pmatrix}}_{L-\text{times}}
-\end{equation} whose eigenvalue is $\Lambda_{0}$. 
-We obtain 
-\begin{equation}\label{SteadyState-W-Good}
-	\begin{split}
-		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
-		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
-	\end{split}
-\end{equation}
-where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. \\
-As a consequence, the steady state of the original process $H$ reads
-\begin{align}
-	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\nonumber\\&
-	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\nonumber\\&
-	\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
-\end{align}
-%\textbf{Remark}: relation \eqref{SteadyState-W-Good} holds only for the action of $W$ on the vacuum state $|\Psi_{0}^{0}\rangle$.
-Acting on different equilibrium eigenstates, exchange relations between $B_{i}^{2L-1}$ and $Q_{0}^{2L}$ are more difficult because of the presence of creation operators that mixes up species and we cannot rewrite \eqref{W-charges-Bad} in such a simple form.
-\subsubsection{Proof of \eqref{SteadyState-W-Good}}
-We prove \eqref{SteadyState-W-Good} in four steps. 
-\paragraph{1. Useful relations} Here we derive some relations that are needed in the following of the proof. 
-We recall the notation, already used in \eqref{Tau-Notation}:
-\begin{equation}
-	|\tau_{1},\ldots,\tau_{L}\rangle\qquad \text{where}\qquad \tau_{x}\in\{1,\ldots,N\}\quad \forall x\in \{1,\ldots,L\}
-\end{equation}
-therefore the vacuum state reads
-\begin{equation}
-	|\Psi_{0}^{0}\rangle=|N,\ldots,N\rangle
-\end{equation}
-We prove that:
-\begin{itemize}
-	\item For all $i\in\{1,\ldots,N-1\}$
-	\begin{equation}\label{BActionVoid}
-		B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
-	\end{equation}
-
-\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
-\begin{align}
-	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
-	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
-\end{align}
-where we used the fact that 
-\begin{equation}\label{eNN-action}
-	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
-\end{equation}
-\begin{flushright}
-	$\square$
-\end{flushright}
-\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
-\begin{equation}\label{Dij-ref}
-	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
-\end{equation}
-The proof is trivial from the definition of \eqref{Dij-Charge}. 
-\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
-\begin{equation}
-	D_{i,j}^{2L}|N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
-\end{equation}
-The proof is trivial from \eqref{Dij-Charge}. 
-\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
-\begin{equation}\label{GoodRelation}
-	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
-\end{equation}
-\textbf{Proof of \eqref{GoodRelation}:}
-\begin{align}
-	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
-	\\&=
-	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
-	\\&=
-	-2\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
-	\\&=
-	-2B_{j}|\Psi_{0}^{0}\rangle
-\end{align}
-\begin{flushright}
-	$\square$
-\end{flushright}
-\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
-\begin{equation}\label{DijBk-different}
-	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
-\end{equation}
-The proof is trivial following the one of \eqref{GoodRelation}. 
-\item For all $ \forall i\in \{1,\ldots,N-1\}$
-\begin{equation}\label{Dii-ref}
-	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}|\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
-\end{equation}
-The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
-\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
-\begin{equation}\label{Diagonal-Q-void}
-	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
-\end{equation}
-\textbf{Proof of \eqref{Diagonal-Q-void}:}
-\begin{align}
-	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber\\&=
-	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber
-	\\&=
-	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
-\end{align}
-where we used the fact that 
-\begin{equation}
-	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
-\end{equation}
-\begin{flushright}
-	$\square$
-\end{flushright}
-\end{itemize}
-
-\paragraph{2. Two indices formula}
-For all $i,j\in\{1,\ldots,N-1\}$
-\begin{equation}\label{Two-Relation}
-	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
-\end{equation}
-\textbf{Proof of \eqref{Two-Relation}:}
-consider \eqref{ExQ0B-charges} then we can write 
-\begin{align}
-	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right\}|\Psi_{0}^{0}\rangle
-\end{align}
-Using \eqref{Dij-ref}, and \eqref{Dii-ref} we obtain 
-\begin{align}
-	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)\right\}|\Psi_{0}^{0}\rangle
-\end{align}
-Now two different cases are possible:
-\begin{itemize}
-	\item \textit{Case 1}: $i=j$ therefore using \eqref{DijBk-different} we obtain 
-	\begin{align}
-		&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-		\\=&
-		B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-	\end{align}
-Using \eqref{ExQ0B-charges}, \eqref{ExDiB-charges} and \eqref{ExDNB-charges} we obtain 
-\begin{align}
-	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)\right.\nonumber\\&\left.-2B_{i}^{2L-1}\sum_{\ell=1\;\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right\}|\Psi_{0}^{0}\rangle
-	\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-\end{align}
-Using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 
-\begin{equation}\label{D2Lp1}
-	D_{i,i}^{2L+1}-D_{N,N}^{2L+1}=-2I
-\end{equation}
-we have 
-\begin{align}
-	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber=\left(B_{i}^{2L-1}\right)^{2}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-\end{align}
-that can be rewritten as \eqref{Two-Relation}.
-\item \textit{Case 2}: $i\neq j$. Using \eqref{GoodRelation} we have
-\begin{align}
-	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,\ell\neq j}^{N-1}B_{\ell}^{2L-1}D_{\ell,j}^{2L}\right\}\\&
-	B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber\\=&\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-\end{align} 
-thus we have 
-\begin{align}
- &Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})+4\right)\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-\end{align}
-Using \eqref{ExQ0B-charges}, \eqref{ExDiB-charges}, \eqref{ExDNB-charges}, \eqref{Commuting-Charges} and \eqref{D2Lp1} we obtain 
-\begin{align}
-	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\=&B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})+4-2D_{j,j}^{2L}-2(D_{N,N}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1})\right)\nonumber\\&\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-\end{align}
-that can be written as \eqref{Two-Relation}. 
-\end{itemize}
-\begin{flushright}
-	$\square$
-\end{flushright}
-Observe that \eqref{Two-Relation} also implies
-\begin{equation}\label{Commutativity-Gained}
-	Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle
-\end{equation}
-i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute when acting on $|\Psi_{0}^{0}\rangle$.\\
-As a further implication of \eqref{Two-Relation} we have
-\begin{align}\label{Two-Points-m1}
-	&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
-\end{align}
-Indeed, as a consequence of \eqref{veryUsefulSeries}, we have 
-\begin{align}
-	&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left\{\left(\Lambda_{0}+\epsilon\right)^{-1}Q_{0}^{2L}\right\}^{n}\left(\Lambda_{0}+\epsilon\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}(Q_{0}^{2L})^{n}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle
-\end{align}
-Moreover, using \eqref{GoodRelation}, \eqref{Dij-ref} and \eqref{Dii-ref},
-\begin{align}
-&(Q_{0}^{2L})^{n}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=(Q_{0}^{2L})^{n-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}^{2L-1}D_{k,i}^{2L}\right\}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-(Q_{0}^{2L})^{n-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{n}|\Psi_{0}^{0}\rangle
-\end{align}
-Therefore
-\begin{align}
-&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}B_{i}^{2L-1}\sum_{n=0}^{\infty}\left(\Lambda_{0}+\epsilon\right)^{-1-n}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{n}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)^{-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle
-\end{align}
-Using again \eqref{veryUsefulSeries} and applying the same argument we have 
-\begin{align}
-&\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{j}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-B_{j}^{2L-1}\sum_{n=0}^{\infty}\left\{\left(\Lambda_{0}+\epsilon\right)^{-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)\right\}^{n}\left(\Lambda_{0}+\epsilon\right)^{-1}B_{i}^{2L-1}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)^{-1}|\Psi_{0}^{0}\rangle\nonumber
-\\=&
-B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
-\end{align}
-\paragraph{3. Generalization for arbitrary number of indices} For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, exploiting \eqref{Two-Relation} and \eqref{Commutativity-Gained} we obtain 
-\begin{equation}\label{k-times-QB}
-	\begin{split}
-		\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle=\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
-	\end{split}
-\end{equation}
-\textbf{Proof of \eqref{k-times-QB}}: we can prove it inductively. For arbitrary $i\in\{1,\ldots,N-1\}$ it is true, since, using \eqref{ExQ0B-charges} and \eqref{Dij-ref} we have that 
-\begin{align}
-	Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&\left(B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)-2\sum_{\ell=1\,:\,\ell\neq i}^{N-1}B_{\ell}^{2L-1}D_{\ell,i}^{2L}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
-\end{align}
-We assume that it is true for all $k_{1},\ldots,k_{N-1}\in\mathbb{N}$ and we aim to show that, for all $i\in\{1,\ldots,N-1\}$,  
-\begin{align}
-&\left(Q_{0}^{2L}B_{i}^{2L-1}\right)\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle=\left(B_{i}^{2L-1}\right)^{k_{i}+1}\prod_{\ell=1\,:\;\ell\neq i}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\nonumber\\&\prod_{j=1}^{k_{1}+\ldots+k_{N-1}+1}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
-\end{align}
-it is also true. This can be shown by aa straight forward computation applying repeatedly \eqref{Two-Relation}.
-\begin{flushright}
-	$\square$
-\end{flushright}
-As a consequence of \eqref{Two-Points-m1} we have that for all  $k_{1},\ldots,k_{N-1}\in\mathbb{N}$
-\begin{equation}\label{k-times-LQB}
-	\begin{split}
-		&\prod_{\ell=1}^{N-1}\left((\Lambda_{0}+\epsilon-Q_{0}^{2L})^{-1}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle\\=&\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
-	\end{split}
-\end{equation}
- %This simplify formula \eqref{W-charges-Bad} as
-%\begin{equation}
-%	\begin{split}
-%	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
-%\end{split}
-%\end{equation}
-%where 
-%\begin{equation}
-	%\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
-%\end{equation}
-\paragraph{4.
-Final formula.} For all $k_{1},\ldots,k_{N-1}\in\mathbb{N}_{0}$, using \eqref{Commutativity-Gained} and \eqref{k-times-LQB} the symmetrization operator introduced in \eqref{W-charges-Bad} acting on the vacuum state $|\Psi_{0}^{0}\rangle$ reads
-\begin{align}
-	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
-	|\Psi_{0}^{0}\rangle\nonumber
-	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}	\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle\nonumber
-	\\=&\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
-\end{align}
-Therefore, the action of the matrix $W$ on $|\Psi_{0}^{0}\rangle$ is given by
-\begin{equation}\label{intermediate-W-ss}
-	\begin{split}
-		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\\&
-		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}
-	\end{split}
-\end{equation}
-Using \eqref{veryUsefulSeries} and observing that  we have that $2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)$ is diagonal we have, for all $j\in\{1,\ldots,k_{1}+\ldots+k_{N-1}\}$ 
-\begin{align}
-&\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\nonumber\\=&
-\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle
-\end{align}
-Therefore, re-summing the series we obtain
-\begin{align}
-	&\lim_{\epsilon\to 0}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle|_{\epsilon=0}\nonumber
-	\\=&
-	\lim_{\epsilon\to 0}\sum_{t=0}^{\infty}\left\{Q_{0}^{2L}-2j(D_{1,1}^{2L}+D_{N,N}^{2L})+4j(j-1)\right\}^{-t}\left(\Lambda_{0}+\epsilon\right)^{-t-1}|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	\lim_{\epsilon\to 0}\left\{\Lambda_{0}+\epsilon-\Lambda_{0}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
-\end{align}
-Using \eqref{Dii-ref} we have 
-\begin{align}
-	&\left\{2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
-	\\=&\left\{2j(2L+2)-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle\nonumber
-	\\=&
-	\frac{1}{4j}\left\{L-j+2\right\}^{-1}|\Psi_{0}^{0}\rangle
-\end{align}
-introducing the Euler $\Gamma$-function we have 
-\begin{align}
-\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\frac{1}{2j}\left\{L-j+2\right\}^{-1}|\Psi_{0}^{0}\rangle=\frac{1}{4^{k_{1}+\ldots+k_{N-1}}}\frac{1}{(k_{1}+\ldots+k_{N-1})!}\frac{\Gamma(L+2-(k_{1}+\ldots+k_{N-1}))}{\Gamma(L+2)}|\Psi_{0}^{0}\rangle
-\end{align}
-Finally, replacing this formula in \eqref{intermediate-W-ss} and using \eqref{eNN-action} we obtain \eqref{SteadyState-W-Good}. 
-\begin{flushright}
-	$\square$
-\end{flushright}
-%\begin{equation}
-%	\begin{split}
-%		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
-%		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
-%	\end{split}
-%\end{equation}
-\begin{comment}
-We do not write the full proof, but only the result for the first non-trivial case, i.e. a chain of length $L=2$ with $N=3$ species. We set $3$ as the empty species.  
-\paragraph{Steady state for a $L=2$ and $N=3$ chain}
-Here we have 
-\begin{equation}
-	|\Psi_{0}^{0}\rangle=\begin{pmatrix}
-		0\\0\\1
-	\end{pmatrix}\otimes \begin{pmatrix}
-	0\\0\\1
-\end{pmatrix}=|\phi_{33}\rangle
-\end{equation}
-where we denoted by $(|\phi_{i}\rangle)_{j}=\delta_{j,i}$ the canonical basis of $\mathbb{C}^{3}$ and $|\phi_{ij}\rangle=|\phi_{i}\rangle\otimes|\phi_{j}\rangle$ the basis of the tensor product space $\mathbb{C}^{3}\otimes\mathbb{C}^{3}$.
-We have
-\begin{equation}
-	\begin{split}
-|\Psi^{''}\rangle=&	W|\Psi_{0}^{0}\rangle =\lim_{\epsilon\to 0}\sum_{k_{1}=0}^{2}\sum_{k_{2}=0}^{2}\Delta_{1}^{k_{1}}\Delta_{2}^{k_{2}}2^{k_{1}+k_{2}}SYM_{k_{1},k_{2}}\left(A_{1},A_{2}\right)|\Psi_{0}^{0}\rangle
-	\\=&\lim_{\epsilon\to 0}\left\{I+2\Delta_{1}A_{1}+2\Delta_{2}A_{2}+4\Delta_{1}^{2}A_{1}^{2}+4\Delta_{2}^{2}A_{2}^{2}+4\Delta_{1}\Delta_{2}\left(A_{1}A_{2}+A_{2}A_{1}\right)\right\}|\Psi_{0}^{0}\rangle
-	\end{split}
-\end{equation}
-where we recall $A_{i}$ defined in \eqref{definitionA}. We need to compute the action of each addend in the last equality on the state $|\Psi_{0}^{0}\rangle$.\\
-Using the charges computed in \eqref{B-charge} and \eqref{Q0Exp} we obtain that 
-\begin{equation}
-	\begin{split}
-A_{i}=	&\left(\Lambda_{0}^{Q}+\epsilon-Q_{0}\right)^{-1}B_{i}^{2L-1}\\=&\left((28+\epsilon)I^{tot}-10e_{33}^{tot}-2(e_{11}^{tot}e_{11}^{tot}+e_{22}^{tot}e_{22}^{tot}+e_{33}e_{33}^{tot})-2(e_{12}^{tot}e_{21}^{tot}+e_{21}^{tot}e_{12}^{tot})\right)^{-1}\\&\left(2e_{i3}^{tot}+2e_{i3}^{tot}e_{33}-2(e_{ii}^{[1]}e_{i3}^{[b]}+e_{i2}^{[2]}e_{23}^{[1]})\right)
-	\end{split}
-\end{equation}
-By the help of an algebraic manipulator we obtain 
-\begin{align}
-	\lim_{\epsilon\to 0}2\Delta_{1}A_{1}|\phi_{33}\rangle&=\frac{2}{3}\Delta_{1}|\phi_{13}\rangle+\frac{1}{3}\Delta_{1}|\phi_{31}\rangle\\
-	\lim_{\epsilon\to 0}2\Delta_{2}A_{2}|\phi_{33}\rangle&=\frac{2}{3}\Delta_{2}|\phi_{23}\rangle+\frac{1}{3}\Delta_{3}|\phi_{32}\rangle\\
-\lim_{\epsilon\to 0}	4\Delta_{1}^{2}A_{1}^{2}|\phi_{33}\rangle&=\frac{1}{6}\Delta_{1}^{2}|\phi_{11}\rangle\\
-\lim_{\epsilon\to 0}	4\Delta_{1}^{2}A_{2}^{2}|\phi_{33}\rangle&=\frac{1}{6}\Delta_{2}^{2}|\phi_{22}\rangle\\
-\lim_{\epsilon\to 0}	4\Delta_{1}\Delta_{2}\left(A_{1}A_{2}+A_{2}A_{1}\right)|\phi_{33}\rangle&=\frac{1}{6}\Delta_{1}\Delta_{2}|\phi_{12}\rangle+\frac{1}{6}\Delta_{21}|\phi_{21}\rangle
-\end{align}
-therefore, we have that
-\begin{equation}
-	\begin{split}
-	W|\Psi_{0}^{0}\rangle=&|\phi_{33}\rangle+\frac{2}{3}\Delta_{1}|\phi_{13}\rangle+\frac{1}{3}\Delta_{1}|\phi_{31}\rangle+\frac{2}{3}\Delta_{2}|\phi_{23}\rangle+\frac{1}{3}\Delta_{3}|\phi_{32}\rangle\\+&\frac{1}{6}\Delta_{1}^{2}|\phi_{11}\rangle+\frac{1}{6}\Delta_{2}^{2}|\phi_{22}\rangle+\frac{1}{6}\Delta_{1}\Delta_{2}|\phi_{12}\rangle+\frac{1}{6}\Delta_{21}|\phi_{21}\rangle
-	\\=& \left(\frac{1}{6}\Delta_{1}^{2},\;\frac{1}{6}\Delta_{1}\Delta_{2},\;\frac{2}{3}\Delta_{1},\;\frac{1}{6}\Delta_{1}\Delta_{2},\;\frac{1}{6}\Delta_{2}^{2},\;\frac{2}{3}\Delta_{2}\;\frac{1}{3}\Delta_{1},\;\frac{1}{3}\Delta_{2},\;1\right)\\=& |\Psi^{''}\rangle
-	\end{split}
-\end{equation}
-that is exactly the steady state $|\Psi^{''}\rangle$ computed in \eqref{ResulsBasis} in the case $L=2$ and $N=3$.
-To obtain the steady state $|\Psi\rangle$ of $H$ we only need to invert the transformations $S_{1}$ and $S_{2}$ defined in \eqref{S1-Whole} and \eqref{S2-Whole}.
-
-%\subsection{Bethe ansatz solution}
-%Describe eigenvalues of $T_0$ following 
-%\cite{belliard2} 
-\subsection{A sequence of similarity transformation}
-In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$
-\begin{equation}
-	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
-\end{equation} 
- Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one $H_{0}$ as 
-\begin{equation}
-	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
-\end{equation}
-As a consequence for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
-\begin{equation}
-	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
-\end{equation}
-Moreover, using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
-\begin{align}
-	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\nonumber\\&
-	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\nonumber\\&
-	\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
-\end{align}
-Observe that, while $S_{1}$ and $S_{2}$ are local, $W$ is not. 
-\end{comment}
+
 \section{Extensions for the non-integrable chain}
-In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
+In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using to integrability.  
 The aim of this section is studying some property of the process when integrability is lost.

### 2023-10-11 main.tex
,

--- 2023-10-10 main.tex
@@
 If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
-\begin{equation}
-\label{rhox}
+ $$
 \rho_{a}^x=\frac{\alpha_{a}}{|\alpha^x|}
-\end{equation}
+$$
 and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}$. 
@@
 \subsection{Definition}
-Consider two Markov processes, $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
+Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
 We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have
@@
 where $\mathbb{E}_{\eta}$ denotes the expectation with respect to the law of the Markov process $(\eta_{t})_{t\geq 0}$ initialized with the particle configuration $\eta$, whereas $\mathbb{E}_{\xi}$ denotes the expectation with respect to the law of the Markov process $(\xi_{t})_{t\geq 0}$ initialized with the particle configuration $\xi$.
-The duality definition can also be formulated as a relation between the generators, provided some minimal technical conditions are satisfied \cite{jansen2014notion}.
+The duality definition can also be formulated as a relation between the generators.
 Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect to the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$
@@
 \textbf{Remark}:
-when the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$.
+when the state spaces of the dual processes is finite, the generators and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$.
 Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as
 \begin{equation}
-    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')
+    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})
 \end{equation}
@@
 where the superscript $T$ denotes the matrix transposition.
-Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}^{\,T}$.
-Working in terms of the Hamiltonian operators the duality relation reads
+Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$.
+Working in terms of the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads
 \begin{equation}\label{DualityRelation}
@@
 \end{equation}
-\subsection{Duality for the open multi-species stirring process}\label{statementDualitySubsection}
-In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ with open boundaries, defined by the generator \eqref{Generator}.
+\subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
+In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}.
 The dual  process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the \textit{enlarged graph} $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E}})$ where 
@@
 \end{equation}
-This means that to each site $x\in V$ we associate an ``extra-site'' via a bijection $u:V\to V$.
-We denote as $u(x)$ the extra-site asspciated to $x\in V$ .
-The configuration space of the dual process is the enlarged state space
+This means that to each site $x\in V$ we associate an ``extra-site'', denoted $u(x)$. The configuration space of the dual process is the enlarged state space
 \begin{equation}\label{dualStateSpace}
-    \widetilde{\Omega}= \bigotimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigotimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
-\end{equation}
-Note that on the extra-site we allow an unbounded number of particles. Thus
-dual particle will accumulate in these extra-sites in the course of time. 
-We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
+    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
+\end{equation}
+Dual particle will accumulate in these extra-sites in the course of time. We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
 \begin{equation}
@@
 
-We define the duality function of the open multi-species stirring process as
+The duality function is given by
 \begin{equation}\label{dualityElements}
@@
 \end{equation}
-where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
-\begin{equation}
-\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
+where we denote the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$  by 
+\begin{equation}
+\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
 \end{equation}
@@
 \textbf{Remark}: in the reversible situation, i.e.
-when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
+when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigtimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
 \begin{equation}
@@
 \subsection{Proof of duality}
-To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.
-To show this, we will use the Hamiltonians and their Lie algebraic description.
-Indeed, in this formalism the proof
-reduces to finding symmetries of the generator (for the bulk duality) and group like transformations (for the ``boundary duality'').
-
+To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{dualityIntertwines} is fulfilled.
+To show this, we will use the Hamiltonians (linked with the Markov generators by \eqref{Hamiltonian-Generator}) and their Lie algebraic description.
+Indeed, in this formalism the proof reduces to finding symmetries and group like transformation of generators of the Lie algebra.\\
 To a configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of a dual process we associate the vector
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
-\end{equation}
-Here we introduced bosonic creation operator $A^{\dagger}$ acting on the left-hand-side as $\langle q|A^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
-We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}.
-From an algebraic point of view, the duality matrix $D$ \eqref{dualityElements} is described as
+    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
+\end{equation}
+Here we introduced bosonic creation operator $a^{\dagger}$ acting on the left-hand-side as $\langle q|a^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
+$(a^{\dagger})_{a}^{u(x)}$ denotes a copy of $a^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
+We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}. The duality matrix $D$ is described as 
 \begin{equation}\label{dualityMatrix}
-    D=\prod_{x\in V}d_{x}\otimes \dd \;.
-\end{equation}
-Here
+    D=\prod_{x\in V}d_{x}\otimes \dd
+\end{equation}
+where
 \begin{equation}\label{bulkElementDualityMatrix}
@@
 with 
+\begin{equation}\label{EquationEx}
+E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}
+\end{equation}
+and
 \begin{equation}\label{Revmatrix}
@@
 \end{equation}
-and
-\begin{equation}\label{EquationEx}
-E^{x}=\sum_{a=1}^{N-1}E_{aN}^{x}\,.
-\end{equation}
-Furthermore
+and where 
 \begin{equation}\label{dualityMatrix2}
@@
 \end{equation}
-We observe that the matrix $R_{x}$ is diagonal.
+The matrix $R_{x}$ is diagonal.
 Its elements are related to the inverse of the weights of the reversible measure \eqref{reversibleMeasure}.
-In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $\rho_{a}=\frac{1}{N}$.
+In particular, to obtain these elements, we have considered the weights of \eqref{reversibleMeasure} when all the parameters $p_{i}=\frac{1}{N}$.
 Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation.
-This $R_{x}$ is called the ``cheap'' duality matrix and is associated to reversibility (see \cite{giardina2009duality}).
+This $R_{x}$ is called the ``cheap'' duality matrix (see \cite{giardina2009duality}).
 \\
-
 Since \eqref{dualityMatrix} is product over sites, proving \eqref{DualityRelation} is equivalent to showing that 
@@
 \end{equation}
-We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove the bulk duality \eqref{edgeDualRealtion}; finally we will show the boundary duality \eqref{siteDualRelation}.
+We perform the proof of duality in three steps: first we will show that matrix \eqref{dualityMatrix} has elements \eqref{dualityElements}; second we will prove \eqref{edgeDualRealtion}; finally we will show \eqref{siteDualRelation}.
 As a preliminary result we note that 
@@
 \end{comment}
-\paragraph{Elements of the duality matrix.}
-Consider the matrix $D$ defined in \eqref{dualityMatrix}.
-We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
+\paragraph{Elements of the duality matrix.}We aim to show that 
 \begin{equation}\label{proofDualityElements}
-\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
-\end{equation}
+\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}
+\end{equation}
+with $D(\bm{n},\bm{\xi})$ defined in \eqref{dualityElements}. 
 Fix an arbitrary site $x\in V$, then we have that 
@@
 \end{align*}
-where {\color{red} we used the orthogonality relation \eqref{ortho}}. 
+where we used the orthogonality relation \eqref{ortho}. 
 On the other hand, on the site $x$, we have 
@@
 As a consequence, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
-Finally, reversing the transformations we retrieve $|\Psi\rangle$.
+Finally, reversing the transformations we can retrieve $|\Psi\rangle$.
 
@@
 \begin{equation}\label{S1-Whole}
-    S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}\dt
+    S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}
 \end{equation}
@@
 \begin{equation}
-S_{1}=\prod_{x=1}^{L}d_{x}^{T}
+S_{1}=\prod_{x=1}^{L}d_{x}^{T}\dt
 \end{equation}
@@
 \begin{equation}\label{hatHamiltonian}
-   H^{'}=H^{'}_{left}+H_{bulk}+H^{'}_{right}
+   H^{'}:=H^{'}_{left}+H_{bulk}+H^{'}_{right}
 \end{equation}
@@
 \end{equation}
-The boundary Hamiltonians of $H^{''}$ reads
+The boundary Hamiltonians of $H^{''}$ read
 \begin{align}\label{tri-diag-boundaryHamiltonians}
@@
 \begin{equation}\label{notation}
-	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
-\end{equation}
-with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\ \\
+	|n^{x}\rangle =\tau_{x}\qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
+\end{equation}
+with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\
 We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
+	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
 	\\&=
@@
 To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle$.
-Calling $\sum_{i=1}^{L}n_{N}^{i}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain
+Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain
 \begin{align*}
@@
 	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\Gamma(2+n_{N})\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
+	|V \rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
 \end{equation}
@@
 \end{equation} 
-We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 
-\begin{equation}
-	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\
-		N\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{i}\}\\
-	\end{cases}\dt
-\end{equation}
-This is a new configuration where the occupations $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ at sites $q_{1},\ldots,q_{i}$ are replaced with $N$'s, while the occupations on the other sites are left untouched.
-The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
-By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain
-\begin{equation}\label{ABS_intermediate}
-	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation}
-For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis},we obtain 
-\begin{equation}
-	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\co
-\end{equation} where we have used the fact that 
-\begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\mu_{x},N})\right)\co
+For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, using equation \eqref{ResulsBasis} and observing that 
+\begin{equation}
+	\left(1+\sum_{j=y}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\mu_{y},N})\right)
+\end{equation}
+we obtain 
+\begin{equation}
+	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\dt
 \end{equation}
@@
 \begin{equation}
-	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}\co
+	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}
 \end{equation}
@@
 \end{equation}
-where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.\\
+where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.
 \begin{comment}
@@
 \end{comment}
+We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ the configuration 
+\begin{equation}
+	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
+		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\
+		N\qquad &\text{otherwise}\\
+	\end{cases}\dt
+\end{equation}
+ This is a new configuration where  $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ with $N$ and leaves the others sites with the same occupation.
+The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
     \begin{comment}
@@
 \end{comment}
-%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
-%Therefore, we have that equation \eqref{ABS_intermediate} becomes
+By considering a fixed $\langle\bm{\tau}|$, by taking \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients \eqref{coefficients-psiSec} and by using \eqref{goodTP-S2} we write
+\begin{equation}\label{ABS_intermediate}
+	\begin{split}
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation}
+
+Therefore, we have that equation \eqref{ABS_intermediate} becomes
+
 %Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
-Therefore, using equation \eqref{ABS_intermediate}, we obtain 
 \begin{equation}\label{elementsABS}

### 2023-10-11 main.tex
Update main.tex

--- 2023-10-11 main.tex
@@
 $(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
+
 We will show below that the Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual in the sense of \eqref{DualityRelation}.
@@
 \hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
-\\&=
-\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
-\\&
-\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+%\\&=
+%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
+%\\&
+%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
 \\&=
@@
 \end{align*}
-where in the last equality we applied the orthogonality relations \eqref{ortho} and the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$.
+where we used the definitions of the action of $E_{ab}$ {\color{red} and the orthogonality relations \eqref{ortho}}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
 Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
@@
 \end{flushright}
-\paragraph{Proof of \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'.
+
+\paragraph{Proof of bulk duality \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'.
 First the existence of a similarity transformation between the Hamiltonian $\mathcal{H}_{x,y}$  and its transposed.
@@
 Second, the possibility of finding a symmetry for the edge Hamiltonian.
-Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$.
-As we will see, this symmetry is $\sum_{a=1}^{N-1}E_{aN}$ \\
+Exploiting \eqref{hamiltonianCasimir}, we can take any symmetry of the Casimir and apply the co-product.
+As we will see, it will be convenient to choose $\sum_{a=1}^{N-1}E_{aN}$.
+
 We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain  
-
 \begin{equation}\label{transpositionPropertyH}
@@
 \begin{equation}
-	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0\dt
+	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}
+	%\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
+	\dt
 \end{equation}
 Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term.
-Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$.
-Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ it holds
-\begin{equation}
-	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0\dt
+Therefore, it is enough to look for a symmetry of $\Delta (C)$.
+Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ the following holds:
+\begin{equation}
+ \text{if } \quad	[C,E]=0\qquad  \text{ then }\qquad \left[\Delta (C),\Delta(E)) \right]=0\dt
 \end{equation}
@@
 \begin{equation}
-	S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
-\end{equation}
-where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. Therefore, this operator $S_{x,y}$ satisfies
+	S_{x,y}=\exp{(\Delta_{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
+\end{equation}
+where $\Delta_{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence, this operator $S_{x,y}$ satisfies
 \begin{equation}\label{symmetryH}
@@
 \end{equation}
-i.e. it is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write
+i.e. it is a symmetry of $\mathcal{H}_{x,y}$. Exploiting these considerations we may write
 

### 2023-10-11 main.tex
Update main.tex

@@
     \begin{split}
-        \mathcal{H}_{x,y}^{T}D&=(R_{x}R_{y})\mathcal{H}_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
-        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)\mathcal{H}_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
+        \mathcal{H}_{x,y}^{T}D&=(R_{x}R_{y})\mathcal{H}_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{u(y)}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{u(z)}\right)
+        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{u(y)}\right)\mathcal{H}_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{u(z)}\right)
         \\&=
@@
  \end{flushright}
- \paragraph{Proof of \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
+ \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
 % that we connect to every site $x\in V$ of the graph $G$.
@@
  \end{equation}
-In the following we need the application of the Hadamard formula with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra with $c,d\in\{1,\ldots,N\}$.
+In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $gl(N)$ with $c,d\in\{1,\ldots,N\}$.
 Therefore we compute
@@
 \end{align}
-From the third commutator on we always obtain zero. All in all we have that 
+From the third commutator on we always obtain zero, i.e. $[B,[B,[B,A]]]=0$. All in all we have that 
  \begin{align}\label{HT-BA}
@@
 %By inserting the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ and 
-By using \eqref{HT-BA} and the fact that the first Casimir operator $C_{1}=\sum_{a,b=1}^{N}E_{ab}$ is central for the algebra we have 
+By using \eqref{HT-BA} and the fact that 
+%the first Casimir operator $C_{1}=
+$\sum_{a,b=1}^{N}E_{ab}$ is central for the algebra we have 
 \begin{comment}
@@
 \end{equation}
-Making the tensor product on both sides of \eqref{siteHadamardI} by 
+Taking the tensor product of both sides of \eqref{siteHadamardI} with 
 \begin{equation}
@@
 \end{equation}
-and we obtain 
+we obtain 
 \begin{equation}\label{siteHadamardII}
@@
 \begin{equation}\label{bosonicKX}
-    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})^{u(x)}_{a}\dt
+    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})^{u(x)}_{a}\dt
 \end{equation}
@@
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{Na}^{x}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}E_{Na}^{x}
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(a^{\dagger})_{a}^{u(x)}E_{Na}^{x}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}E_{Na}^{x}
     \end{split}
@@
 \\&=
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
+d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
 \\&=

### 2023-10-11 main.tex
P assorbimento

@@
 \begin{align}
-	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
+	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\nonumber\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]\nonumber
 	\\&=
@@
 \end{align}
-\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
-
+\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}. \\ \\
+{\color{blue}
+\textbf{How $|\Psi^{'}\rangle$ is related to steady state non-equilibrium correlations and to absorption probabilities?}\\
+We aim to compute correlations between non-empty species in the steady state. We know that for any chain length $L$ we have that the steady state $|\Psi\rangle$ is related to $|\Psi^{'}\rangle$ by
+\begin{equation*}
+	|\Psi\rangle=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle
+\end{equation*}
+We aim to compute the correlations between non-empty particles of an arbitrary configuration $\bm{\tau}$.
+This is equivalent to consider a shorter chain where only non-empty particles are left, while all the sites occupied by the empty $N$ are removed. 
+This chain has length $m=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$, where all these $m$ sites are occupied by particles of species for $1$ to $N-1$.
+To find the desired correlations we compute the steady state of this shorter chain.
+We denote its configuration chain by $\widehat{\bm{\tau}}$.
+This configuration is obtained from $\bm{\tau}$ by re-labelling properly the occupations from $1$ to $m$.
+Then, these $m$ point correlations can be computed by finding $\Psi(\widehat{\bm{\tau}})$.\\ \\ To clarify consider the example $N=3$ and $L=4$ where the empty is the species $3$.
+Take a configuration
+\begin{align*}
+	\bm{\tau}=(\tau_{1}=2,\tau_{2}=3,\tau_{3}=1,\tau_{4}=3)
+\end{align*}
+What is the correlation between the occupied species?
+To compute this we can define the new chain of length $m=2$ with the configuration $\widehat{\bm{\tau}}=(\widehat{\tau}_{1}=2,\widehat{\tau}_{2}=1)$ and find the steady state $|\Psi\rangle$ of this shorter chain.
+\\ \\
+To compute the steady state of the shorter chain we can use the result that we have in the appendix A in equation \eqref{Tensor-S1}:
+\begin{equation*}
+		\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
+\end{equation*}
+Thus, for the shorter chain we have that 
+\begin{equation*}
+	\langle \widehat{\bm{\tau}}|\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{m}\left(\delta_{\mu_{x},\tau_{x}}\right)
+\end{equation*}
+this implies that 
+\begin{equation}
+	\Psi(\widehat{\bm{\tau}})=\Psi^{'}(\widehat{\bm{\tau}})
+\end{equation}
+where here both $|\Psi(\widehat{\bm{\tau}})\rangle$ and $|\Psi^{'}(\widehat{\bm{\tau}})\rangle$ are eigenvector with vanishing eigenvalue of chains of length $m$. 
+We have computed this $\Psi^{'}(\widehat{\bm{\tau}})$ in \eqref{exactCorrelations} as
+\begin{equation*}
+	\Psi^{'}(\widehat{\bm{\tau}})\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
+\end{equation*}
+where 
+\begin{equation*}
+g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
+\end{equation*}
+and 
+\begin{equation*}
+f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
+\end{equation*}
+We also know from \eqref{CorrelationByABS-prob} that 
+\begin{equation*}
+	\Psi(\widehat{\bm{\tau}})= \sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
+\end{equation*}
+therefore, we can read off the absorption probabilities. \\ \\
+This argument can be adapted for any $1\geq m\leq L$ to compute $m$-point correlations between non-empty species.\\ \\ 
+In general $|\Psi^{'}\rangle$ is the eigenvector with vanishing eigenvalue of $H^{'}$, but I believe it cannot be interpreted directly as a steady state, since $H^{'}$ is not a Markov matrix.
+However, it gives by the previous argument the exact correlations and as a consequence the absorption probabilities...
+}
 \section{Extensions for the non-integrable chain}
@@
 therefore, projecting on $\langle \bm{\tau}|$ we have
-\begin{equation}
+\begin{equation}\label{Tensor-S1}
 	\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)

### 2023-10-12 main.tex
notation
'

@@
 %where $\sum_{a=1}^{N}n_{i}=\nu$. 
-{\color{red}
-The basis vectors satisfy the orthogonality relation with respect to the Euclidean scalar product 
+The basis vectors satisfy the orthogonality relation
 \begin{equation}\label{ortho}
-   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}\co
-\end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vectors obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
-}
+   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{m_{a},n_{a}}\co
+\end{equation}
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vectors obtained by transposing $|m\rangle=|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronecker delta.
+
 The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
@@
 \\ \\
-\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
-\begin{equation}
-   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}\dt
-\end{equation}
-{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
+%\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
+%\begin{equation}
+%   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}\dt
+%\end{equation}
+%{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
 The process with generator \eqref{Generator} can be described in terms of $gl(N)$ Lie algebra generators.
@@
 with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
-{\color{red}
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
@@
 \end{equation}
-}
-
 We introduce the Hamiltonian operator
@@
 
-We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the {\color{red} quadratic} Casimir of $gl(N)$
+We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $gl(N)$
 \begin{equation}\label{secondCasimir}
@@
 \Delta:gl(N)&\to gl(N)\otimes gl(N)\\
-E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
+E_{ab}&\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
 \end{split}
@@
 \end{equation}
-We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
+The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section \ref{sectionIntegrabiliy}.
 We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
@@
 \end{equation}
-Here we introduced bosonic creation operator $A^{\dagger}$ acting on the left-hand-side as $\langle q|A^{\dagger}=\langle q+1|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
+Here we introduced the operator $A$ acting on the left-hand-side as $\langle q+1|A^{\dagger}=\langle q|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
 $(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
@@
 \end{align*}
-where {\color{red} we used the orthogonality relation \eqref{ortho}}. 
+where  we used the orthogonality relation \eqref{ortho}. 
 On the other hand, on the site $x$, we have 
@@
 \\&=
-\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\ldots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\ldots(n_{N-1}^{x}-k_{N-1})!}
+\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}
 \\& 
-\hspace{2.cm}\qquad\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
-\\&=
-\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\\&=
+\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
 \end{align*}
-where we used the definitions of the action of $E_{ab}$ {\color{red} and the orthogonality relations \eqref{ortho}}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
+where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
 Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
@@
 \begin{align}
-	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-\delta_{d<N}E_{cN}
+	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-(1-\delta_{dN})E_{cN}
 \end{align}
@@
 \begin{equation}
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \end{equation}
@@
     \begin{split}
-&H_{x}^{T}d_{x}\otimes\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
-\\=&
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}\right)\dt
+&H_{x}^{T}d_{x}\otimes\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\\=& d_{x}\,
+|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
     \end{split}
@@
 \begin{equation}\label{bosonicKX}
-    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})^{u(x)}_{a}\dt
-\end{equation}
-Using \eqref{bosonicKX} by a fixed $a\in \{1,\ldots,N-1\}$ we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
-\begin{equation}
-    \begin{split}
-&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}E_{Na}^{x}
+    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})^{u(x)}_{a}=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
+\end{equation}
+Using \eqref{bosonicKX} we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+\begin{equation}
+    \begin{split}
+&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}E_{Na}^{x}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}E_{Na}^{x}
-    \end{split}
-\end{equation}
-where, in the last equality, we performed a change of summation variable. Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 
-\begin{equation}
-    \begin{split}
-H_{x}^{T}\left(d_{x}\otimes \dd\right)&=
-     H_{x}^{T}d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
-\\&=
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
-\\&=
-d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\widetilde{H}_{x}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
+    \end{split}
+\end{equation}
+where, in the up to last equality, we performed a change of summation variable and where in the last equality we used the fact that  
+\begin{equation}
+	\begin{split}
+&\sum_{\xi_{a}^{u(x)}=0}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
+\end{split}
+\end{equation}
+Indeed, as a consequence of \eqref{bosonicKX} we have 
+\begin{equation}
+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}=0
+\end{equation}
+Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 
+\begin{equation}
+    \begin{split}
+H_{x}^{T}d_{x}\otimes \dd&=
+     H_{x}^{T}d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+\\&=
+\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
+\\&=
+\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\widetilde{H}_{x}
 \\&=
@@
 		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation}
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation}
+{\color{blue}
+	Proposal
+\begin{equation*}
+	\begin{split}
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\tau_{q_{1}}=N,\ldots,\tau_{L})\beta_{q_{1}^{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\tau_{q_{1}}=N,\ldots,\tau_{q_{2}}=N,\ldots,\tau_{L})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation*}
+Other proposal
+\begin{equation*}
+	\begin{split}
+	\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{q_{1}^{1}}\\&+
+	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+\end{split}
+\end{equation*}
+}
 For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis},we obtain 
@@
 therefore, we can read off the absorption probabilities. \\ \\
-This argument can be adapted for any $1\geq m\leq L$ to compute $m$-point correlations between non-empty species.\\ \\ 
+This argument can be adapted for any $1\leq m\leq L$ to compute $m$-point correlations between non-empty species.\\ \\ 
 In general $|\Psi^{'}\rangle$ is the eigenvector with vanishing eigenvalue of $H^{'}$, but I believe it cannot be interpreted directly as a steady state, since $H^{'}$ is not a Markov matrix.

### 2023-10-17 main.tex
Bozza

@@
 \end{flushright}
+
+\subsection{Explicit formula for the steady state $|\Psi\rangle$}
+The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
+\begin{equation}\label{steadyStateH}
+	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
+\end{equation}
+where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
+\begin{equation}\label{SteadyState-coeff-implicit}
+	\begin{split}
+		\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+	\end{split}
+\end{equation}
+To compute correlations it is enough the above expression, however using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, see Appendix \ref{appB}.\\
+The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
+\begin{equation}
+	\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
+\end{equation}
+\textbf{Proof of the normalization}: we aim to show that 
+\begin{align}
+		\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+\end{align}
+We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e.
+$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
+Moreover, we introduce the space
+\begin{equation}
+	\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
+\end{equation}
+Therefore, we can rewrite the normalization condition as 
+\begin{align}
+	&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
+	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+\end{align}
+We first observe that, using \eqref{ABS}, we have that 
+\begin{equation}
+	\Psi^{'}(N,\ldots,N)=1\co
+\end{equation}
+thus we have that it is enough to prove that
+\begin{align}
+	&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
+	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&0
+\end{align}
+We now consider the second term of the above expression.
+For any fixed $\ell$ and for any fixed $\bm{\tau}\in \Omega_{\ell}$, $b$ empty occupations are replaced by all possible non-empty species.
+For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution.
+On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$.
+Each of such a configuration is counted $\binom{L-\ell+b}{b}$.
+By calling $r=\ell-b$ if $b\leq \ell$ we have that
+\begin{align}
+&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
+=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-r\}}\dt
+\end{align} 
+As a consequence, we have that the normalization condition reads
+\begin{align}
+\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt
+\end{align}
+By exchanging the summations we have 
+\begin{equation}
+\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt
+\end{equation}
+It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
+\begin{align}
+	1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
+\end{align}
+This is true because of the Binomial theorem, indeed 
+\begin{equation}
+1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
+\end{equation}
+that implies the normalization of the state $|\Psi\rangle$. 
+\begin{flushright}
+	$\square$
+\end{flushright}
 \begin{comment}
@@
 
-\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$.
+\paragraph{Proof of formula \eqref{exactCorrelations}}
+We aim to compute
+\begin{equation}
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\mathbb{E}_{stat}\left[\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+\end{equation}
+We introduce the space 
+\begin{equation}
+	\widehat{\Omega}^{m}=\left\{\bm{\tau}\in \Omega\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}
+\end{equation}
+where $m$ occupations are fixed and the other $L-m$ can vary in all possible ways. Therefore, we need to compute 
+\begin{equation}
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
+\end{equation}
+Using \eqref{SteadyState-coeff-implicit}, we have that 
+\begin{align}
+&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi^{'}(\tau)\nonumber
+\\+&
+\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+\end{align}
+We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega}^{m}$, i.e.
+$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
+We also introduce the space
+\begin{equation}
+\widehat{\Omega}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
+\end{equation}
+Then we obtain that 
+\begin{align}
+&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber
+\\+&
+\sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+\end{align}
+The second term on the right hand side in the above equation replaces $b$ empty occupations with all possible non-empty species.
+If the configuration $\bm{\tau}\in\widehat{\Omega}_{\ell}^{m}$ has $\ell<b$ no contributions are seen.
+Otherwise, if $\ell\geq b$, $b$ empties are changed, obtaining configuration with $r=\ell-b$ voids occupations, with $r\in \{0,\ldots, L-m-b\}$.
+Each of such a configuration is counted $\binom{L-r-m}{b}$ times.
+Therefore, we obtain
+\begin{align}
+	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+\end{align}
+In the second term we exchange the summations obtaining 
+\begin{equation}
+\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+\end{equation}
+Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-b\}$, we have that
+\begin{equation}
+	1+\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}=0
+\end{equation}
+thus, we obtain 
+\begin{equation}
+\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\end{equation}
+that implies 
+\begin{equation}
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\end{equation}
+% Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$.
 We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$.
 By using duality, we showed in \eqref{CorrelationByABS-prob} that
- \begin{equation}
- 	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
- \end{equation} 
-where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
-Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=s_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 
-\begin{equation}
- \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
+% \begin{equation}
+ %	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
+% \end{equation} 
+%where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
+Using formula \eqref{ABS} we obtain 
+\begin{equation}
+ \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
 \end{equation}
@@
 \end{align}
-\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}. \\ \\
-{\color{blue}
-\textbf{How $|\Psi^{'}\rangle$ is related to steady state non-equilibrium correlations and to absorption probabilities?}\\
-We aim to compute correlations between non-empty species in the steady state. We know that for any chain length $L$ we have that the steady state $|\Psi\rangle$ is related to $|\Psi^{'}\rangle$ by
-\begin{equation*}
-	|\Psi\rangle=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle
-\end{equation*}
-We aim to compute the correlations between non-empty particles of an arbitrary configuration $\bm{\tau}$.
-This is equivalent to consider a shorter chain where only non-empty particles are left, while all the sites occupied by the empty $N$ are removed. 
-This chain has length $m=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$, where all these $m$ sites are occupied by particles of species for $1$ to $N-1$.
-To find the desired correlations we compute the steady state of this shorter chain.
-We denote its configuration chain by $\widehat{\bm{\tau}}$.
-This configuration is obtained from $\bm{\tau}$ by re-labelling properly the occupations from $1$ to $m$.
-Then, these $m$ point correlations can be computed by finding $\Psi(\widehat{\bm{\tau}})$.\\ \\ To clarify consider the example $N=3$ and $L=4$ where the empty is the species $3$.
-Take a configuration
-\begin{align*}
-	\bm{\tau}=(\tau_{1}=2,\tau_{2}=3,\tau_{3}=1,\tau_{4}=3)
-\end{align*}
-What is the correlation between the occupied species?
-To compute this we can define the new chain of length $m=2$ with the configuration $\widehat{\bm{\tau}}=(\widehat{\tau}_{1}=2,\widehat{\tau}_{2}=1)$ and find the steady state $|\Psi\rangle$ of this shorter chain.
-\\ \\
-To compute the steady state of the shorter chain we can use the result that we have in the appendix A in equation \eqref{Tensor-S1}:
-\begin{equation*}
-		\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
-\end{equation*}
-Thus, for the shorter chain we have that 
-\begin{equation*}
-	\langle \widehat{\bm{\tau}}|\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{m}\left(\delta_{\mu_{x},\tau_{x}}\right)
-\end{equation*}
-this implies that 
-\begin{equation}
-	\Psi(\widehat{\bm{\tau}})=\Psi^{'}(\widehat{\bm{\tau}})
-\end{equation}
-where here both $|\Psi(\widehat{\bm{\tau}})\rangle$ and $|\Psi^{'}(\widehat{\bm{\tau}})\rangle$ are eigenvector with vanishing eigenvalue of chains of length $m$. 
-We have computed this $\Psi^{'}(\widehat{\bm{\tau}})$ in \eqref{exactCorrelations} as
-\begin{equation*}
-	\Psi^{'}(\widehat{\bm{\tau}})\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
-\end{equation*}
-where 
-\begin{equation*}
-g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
-\end{equation*}
-and 
-\begin{equation*}
-f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
-\end{equation*}
-We also know from \eqref{CorrelationByABS-prob} that 
-\begin{equation*}
-	\Psi(\widehat{\bm{\tau}})= \sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
-\end{equation*}
-therefore, we can read off the absorption probabilities. \\ \\
-This argument can be adapted for any $1\leq m\leq L$ to compute $m$-point correlations between non-empty species.\\ \\ 
-In general $|\Psi^{'}\rangle$ is the eigenvector with vanishing eigenvalue of $H^{'}$, but I believe it cannot be interpreted directly as a steady state, since $H^{'}$ is not a Markov matrix.
-However, it gives by the previous argument the exact correlations and as a consequence the absorption probabilities...
-}
+\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
 \section{Extensions for the non-integrable chain}
@@
 The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
-\begin{equation}\label{steadyStateH}
+\begin{equation}
 	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle

### 2023-10-17 main.tex
bozza 1

@@
 \end{equation} 
+{\color{blue}
 We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ 
@@
 The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
-By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain
+} \\ By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain
 \begin{equation}\label{ABS_intermediate}
+	\begin{split}
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{q_{1}^{1}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation}
+where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
+\\
+{\color{blue}
+	Old proposal
+\begin{equation*}
 	\begin{split}
@@
 	\end{split}
-\end{equation}
+\end{equation*}}
 {\color{blue}
-	Proposal
+	Other proposal
 \begin{equation*}
@@
 \end{equation*}
-Other proposal
-\begin{equation*}
-	\begin{split}
-	\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{q_{1}^{1}}\\&+
-	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-\end{split}
-\end{equation*}
 }
-For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis},we obtain 
+For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis}, we obtain 
 \begin{equation}
@@
 \begin{equation}\label{coefficients-psiSec}
-	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{y}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
+	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
 \end{equation}
@@
 \end{equation}
-To compute correlations it is enough the above expression, however using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, see Appendix \ref{appB}.\\
+To compute correlations it is enough the above expression.
+Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly.
+We report this explicit formula and the proof in Appendix \ref{appB}.\\
+The expression \eqref{SteadyState-coeff-implicit} has two contribution.
+First a term $\Psi^{'}(\bm{\tau})$ and second a where $b$ of the empty occupations of $\bm{\tau}$ have been replaced by all possible species from $1$ to $N-1$.
+If the configuration $\bm{\tau}$ has no empty species, this second term vanishes.
+The existence of the second term is motivated by the fact that, the empty occupation at each site $x$ depend on the other species via $1=\sum_{a=1}^{N}n_{a}^{x}$.\\
 The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
@@
 	&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
 \end{align}
@@
 \end{equation}
-thus we have that it is enough to prove that
+thus, it is enough to prove that
 \begin{align}
 	&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&0
+	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
 \end{align}
@@
 For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution.
-On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$.
+On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ empties have been replaced by all  species from $1$ to $N-1$.
 Each of such a configuration is counted $\binom{L-\ell+b}{b}$.
@@
 \begin{align}
-	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
+	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
 \end{align}
 In the second term we exchange the summations obtaining 
-\begin{equation}
-\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
-\end{equation}
-Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-b\}$, we have that
+\begin{align}
+\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
+\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+\end{align}
+Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-1\}$, we have that
 \begin{equation}
@@
 \begin{equation}
- \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
+ \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
 \end{equation}
@@
 \end{comment}
-\newline \newline
-	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
-	\begin{equation}\label{LinkABS-corr}
-		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
-	\end{equation}
-	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
+%	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
+%	\begin{equation}\label{LinkABS-corr}
+%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
+%	\end{equation}
+%	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
 

### 2023-10-17 main.tex
Bozza 2

@@
 \begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
 \\&
@@
 \\& 
-\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
 \\&=
@@
 \begin{align}
-	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-\delta_{d<N}E_{cN}\right]\nonumber\\=&
-	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-\delta_{d<N}\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
-	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-\delta_{d<N}\delta_{cN}E_{aN}\right)\nonumber\\=&
-	-\left(\delta_{cN}\delta_{d<N}+\delta_{d<N}\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
+	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-(1-\delta_{dN})E_{cN}\right]\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-(1-\delta_{dN})\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-(1-\delta_{dN})\delta_{cN}E_{aN}\right)\nonumber\\=&
+	-\left(\delta_{cN}(1-\delta_{dN})+(1-\delta_{dN})\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
 	\\=&
-	-2\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
+	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}
 \end{align}
@@
  \begin{align}\label{HT-BA}
- 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+\delta_{d<N}E_{cN}-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}\dt
+ 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+(1-\delta_{dN})E_{cN}-\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
  \end{align}
@@
 Using \eqref{bosonicKX} we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
-\begin{equation}
+\begin{equation}\label{extra-site-trick}
     \begin{split}
@@
 \end{equation}
-where, in the up to last equality, we performed a change of summation variable and where in the last equality we used the fact that  
-\begin{equation}
-	\begin{split}
-&\sum_{\xi_{a}^{u(x)}=0}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
-\end{split}
-\end{equation}
-Indeed, as a consequence of \eqref{bosonicKX} we have 
+where, in the up to last equality, we performed a change of summation variable and we used the fact that  
+\begin{equation}
+	\begin{split}
+&\sum_{\xi_{a}^{u(x)}=0}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\dt
+\end{split}
+\end{equation}
+This is a consequence of 
 \begin{equation}
@@
 \end{equation}
-Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 
+that follows from \eqref{bosonicKX}. Therefore, inserting \eqref{extra-site-trick} in \eqref{siteHadamardII} we obtain 
 \begin{equation}
@@
 \end{flushright}
-\subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
-In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types.
-Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present.
-As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
-This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
-\\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
- \begin{equation}\label{stateSpace-Chain}
- 	\Omega=\bigtimes_{x=1}^{L} \Omega_{x}
- \end{equation} and its generator reads
-\begin{equation}
-	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}\dt
-\end{equation} 
-The bulk is 
-\begin{equation}
-	\mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-while at the boundaries 
-\begin{equation}
-	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\dt
-\end{equation}
- The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
-\begin{equation}\label{stateSpaceDUAL-Chain}	
-	\widetilde{\Omega}=N_{0}^{N}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
-\end{equation}
-whit dual generator
-\begin{equation}
-	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
-\end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundaries are absorbing, i.e. 
-\begin{equation}\label{abs-dual-boundary-chain}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{N}^{1}+\bm{\delta}_{a}^{0})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{N}^{L}+\bm{\delta}_{a}^{L+1})-f(\bm{\xi})\right)
-	\end{split}
-\end{equation}
-where $0$ and $L+1$ are the extra-sites. The duality function reads
-\begin{equation}\label{dualityFunctionChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-The dual process has absorbing boundaries, i.e.
-all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
-This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
-Consider an arbitrary initial configuration of $(\bm{n}(t))_{t\geq 0}$ denoted by $\bm{n}$.
-For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
-The following  equalities holds thanks to the duality relation \eqref{duality-expectation}:
-\begin{equation}\label{ExptationSS}
-	\begin{split}
-		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
-		\\&=
-		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
-	\end{split}
-\end{equation}
-where 
-\begin{equation}\label{Pass}
-	\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
-\end{equation}
-are called the \textit{absorption probabilities}, i.e.
-the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$.
-Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
-The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
-\begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}\dt
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{k}\in\{1,\ldots,N-1\}$ situated at sites $y_{k}\in\{1,\ldots,L\}$ with $k\in \{1,\ldots,m\}$.
-Using \eqref{ExptationSS}, this expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
-However, these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
-\paragraph{One point correlations for the $\nu\geq 1$ case}
-We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt
-\end{equation}
-The average occupation reads
-\begin{equation}\label{OnePtsCORR}
-	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt
-	\end{split}
-\end{equation}
-To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
-This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
-\begin{equation}\label{gamblers-ruin}
-	\begin{cases}
-		\Delta_{y}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
-		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
-		\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
-	\end{cases}
-\end{equation}
-where $\Delta_{y}^{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
-\end{equation}
-\textbf{Remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-\end{equation}
-that is the same result obtained in \cite{vanicat2017exact}. 
-\\
-\\ Already for two-point correlations the computations become more involving and hard to solve.
-In the following we specialize the chain to the integrable case $\nu=1$.
-As it will be shown, in such a situation the non-equilibrium steady state correlations can be computed with different techniques exploiting the integrability of the process (matrix product ansatz and quantum inverse scattering method) combined with duality and, as a by-product, all absorption probabilities can be explicitly found.
+
 \subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
@@
 \begin{equation}\label{boundary-H-dual-chain}
-	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)\dt
+	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
-This simplification will be crucial in Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping}.\\
+This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
 
@@
 \end{equation}
-Repeating the argument of Subsection \ref{Subsection-ss-nonI} and denoting the $m$-point correlations by $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}$ we have 
+Denoting the $m$-point correlations by $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}$ we have 
 %To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
@@
 \begin{enumerate}
-	%\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
 These probability are hard to find in this partial exclusion situation, however correlation can be formally written.
@@
 \end{enumerate}
+\subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
+In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
+Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types.
+Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present.
+As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
+This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
+\\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
+\begin{equation}\label{stateSpace-Chain}
+	\Omega=\bigtimes_{x=1}^{L} \Omega_{x}
+\end{equation} and its generator reads
+\begin{equation}
+	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}\dt
+\end{equation} 
+The bulk is 
+\begin{equation}
+	\mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
+\end{equation}
+while at the boundaries 
+\begin{equation}
+	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\dt
+\end{equation}
+The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
+\begin{equation}\label{stateSpaceDUAL-Chain}	
+	\widetilde{\Omega}=N_{0}^{N}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
+\end{equation}
+whit dual generator
+\begin{equation}
+	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
+\end{equation} 
+where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundaries are absorbing, i.e. 
+\begin{equation}\label{abs-dual-boundary-chain}
+	\begin{split}
+		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{N}^{1}+\bm{\delta}_{a}^{0})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{N}^{L}+\bm{\delta}_{a}^{L+1})-f(\bm{\xi})\right)
+	\end{split}
+\end{equation}
+where $0$ and $L+1$ are the extra-sites. The duality function reads
+\begin{equation}\label{dualityFunctionChain}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
+The dual process has absorbing boundaries, i.e.
+all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
+This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
+We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+Consider an arbitrary initial configuration of $(\bm{n}(t))_{t\geq 0}$ denoted by $\bm{n}$.
+For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
+The following  equalities holds using duality relation \eqref{duality-expectation}:
+\begin{equation}\label{ExptationSS}
+	\begin{split}
+		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\\&=
+		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
+	\end{split}
+\end{equation}
+where 
+\begin{equation}\label{Pass}
+	\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+are called the \textit{absorption probabilities}, i.e.
+the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$.
+Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
+The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
+\begin{equation}
+	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}\dt
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{k}\in\{1,\ldots,N-1\}$ situated at sites $y_{k}\in\{1,\ldots,L\}$ with $k\in \{1,\ldots,m\}$.
+Using \eqref{ExptationSS}, this expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
+However, these absorption probabilities fulfil some difference equations that are not easy to solve.
+For example, we report here the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
+\paragraph{One point correlations for the $\nu\geq 1$ case}
+We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt
+\end{equation}
+The average occupation reads
+\begin{equation}\label{OnePtsCORR}
+	\begin{split}
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt
+	\end{split}
+\end{equation}
+To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
+This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
+\begin{equation}\label{gamblers-ruin}
+	\begin{cases}
+		\Delta_{y}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
+		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
+		\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
+	\end{cases}
+\end{equation}
+where $\Delta_{y}^{L}$ is the discrete Laplace operator on the chain of length $L$.
+The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+\end{equation}
+\textbf{Remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+\end{equation}
+that is the same result obtained in \cite{vanicat2017exact}. 
+\\
+\\ Already for two-point correlations the computations become more involving and hard to solve.
+% In the following we specialize the chain to the integrable case $\nu=1$.
+As it will be shown, in such a situation the non-equilibrium steady state correlations can be computed with different techniques exploiting the integrability of the process (matrix product ansatz and quantum inverse scattering method) combined with duality and, as a by-product, all absorption probabilities can be explicitly found.
 

### 2023-10-18 main.tex
Bozza 3
Argument correlations

@@
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&
 \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
@@
 \left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
-\\&=
-\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\widetilde{H}_{x}
+%\\&=
+%\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\widetilde{H}_{x}
 \\&=
@@
 \end{equation}
-To compute correlations it is enough the above expression.
-Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly.
-We report this explicit formula and the proof in Appendix \ref{appB}.\\
-The expression \eqref{SteadyState-coeff-implicit} has two contribution.
-First a term $\Psi^{'}(\bm{\tau})$ and second a where $b$ of the empty occupations of $\bm{\tau}$ have been replaced by all possible species from $1$ to $N-1$.
-If the configuration $\bm{\tau}$ has no empty species, this second term vanishes.
-The existence of the second term is motivated by the fact that, the empty occupation at each site $x$ depend on the other species via $1=\sum_{a=1}^{N}n_{a}^{x}$.\\
+ Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression.
+We report the explicit formula and the proof in Appendix \ref{appB}.\\
+In \eqref{SteadyState-coeff-implicit} there are two terms.
+For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
+The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$ computed in these new configurations with proper coefficients.
+If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.\\
 The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
@@
 We now consider the second term of the above expression.
-For any fixed $\ell$ and for any fixed $\bm{\tau}\in \Omega_{\ell}$, $b$ empty occupations are replaced by all possible non-empty species.
-For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution.
-On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ empties have been replaced by all  species from $1$ to $N-1$.
-Each of such a configuration is counted $\binom{L-\ell+b}{b}$.
+For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution.
+On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
+Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
 By calling $r=\ell-b$ if $b\leq \ell$ we have that
@@
 &\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
-=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-r\}}\dt
-\end{align} 
-As a consequence, we have that the normalization condition reads
+=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
+\end{align} 
+As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
 \begin{align}
-\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt
+\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
 \end{align}
@@
 \begin{equation}
-\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt
+\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
 \end{equation}
@@
 \end{align}
-The second term on the right hand side in the above equation replaces $b$ empty occupations with all possible non-empty species.
+In the first summation on the right-hand-side, there is only one term that has all sites empty but the one in position $y_{1},\ldots,y_{m}$ that are occupied by $s_{1},\ldots,s_{m}$.
+This is reached when $\ell=L-m$ and we denote it by $\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)$.
+The second term on the right-hand-side in the above equation replaces $b$ empty occupations with all possible non-empty species.
 If the configuration $\bm{\tau}\in\widehat{\Omega}_{\ell}^{m}$ has $\ell<b$ no contributions are seen.
@@
 \end{align}
-In the second term we exchange the summations obtaining 
+In the second term of the above equation we exchange the summations obtaining 
 \begin{align}
@@
 %where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
-Using formula \eqref{ABS} we obtain 
+Using formula \eqref{ABS} we have that 
 \begin{equation}
@@
 \end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we have \eqref{exactCorrelations}.
+Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we prove \eqref{exactCorrelations}.
 \begin{flushright}

### 2023-10-19 main.tex
fix
check
After Meeting October 18

@@
 \end{equation}
+%{\color{blue}
+%	\begin{equation*}
+%		|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)
+%	\end{equation*}}
 %where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
@@
 \begin{equation}\label{siteDualHamiltonian}
-    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
-\end{equation}
-Here we introduced the operator $A$ acting on the left-hand-side as $\langle q+1|A^{\dagger}=\langle q|$ on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian}
-$(A^{\dagger})_{a}^{u(x)}$ denotes a copy of $A^{\dagger}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
+    \widetilde{H}_{x}=|\alpha^{x}|\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{u(x)}\,E_{Na}^{x}-E_{aa}^{x}\right)\dt
+\end{equation}
+Here we introduced the pair of bosonic operators $\mathbf{a},\,\mathbf{a}^{+}$ satisfying $[\mathbf{a},\mathbf{a}^{+}]=1$ and acting as
+\begin{equation}
+	\mathbf{a}^{+}|q\rangle=|q+1\rangle\qquad \mathbf{a}|q\rangle=q|q-1\rangle
+\end{equation}
+\begin{equation}
+	\langle q|\mathbf{a}^{+}=\langle q-1|\qquad \langle q|\mathbf{a}=(q+1) \langle q+1|
+\end{equation}
+on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian} 
+$(\mathbf{a}^{+})_{a}^{u(x)}$ denotes a copy of $\mathbf{a}^{+}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
 
@@
 \begin{equation}
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
-\end{equation}
+\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|_{u(x)}
+\end{equation}
+{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
 we obtain 
@@
     \begin{split}
-&H_{x}^{T}d_{x}\otimes\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
-\\=& d_{x}\,
-|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
+    	H_{x}^{T}d_{x}\otimes\langle\rho|_{u(x)}=
+ d_{x}\,
+|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \langle\rho|_{u(x)}\dt
     \end{split}
@@
 \begin{equation}\label{bosonicKX}
-    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})^{u(x)}_{a}=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
+    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})^{u(x)}_{a}=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
 \end{equation}
@@
     \begin{split}
-&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\rho_{a}^{x}
+&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\rho_{a}^{x}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
     \end{split}
@@
 	\begin{split}
-&\sum_{\xi_{a}^{u(x)}=0}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\dt
-\end{split}
-\end{equation}
-This is a consequence of 
-\begin{equation}
-\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}=0
-\end{equation}
-that follows from \eqref{bosonicKX}. Therefore, inserting \eqref{extra-site-trick} in \eqref{siteHadamardII} we obtain 
+&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
+\end{split}
+\end{equation}
+%This is a consequence of 
+%\begin{equation}
+%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}=0
+%\end{equation}
+%that follows from \eqref{bosonicKX}.
+Therefore, inserting \eqref{extra-site-trick} in \eqref{siteHadamardII} we obtain 
 \begin{equation}
@@
 \end{align}
-This is true because of the Binomial theorem, indeed 
+This is true because of the binomial theorem, indeed 
 \begin{equation}
@@
 	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
-	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\mathbbm{1}_{\{b\leq L-m-r\}}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
 \end{align}
@@
 \sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
-\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
-\end{align}
-Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-1\}$, we have that
+\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}\mathbbm{1}_{\{b\leq L-m-\ell\}}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+\end{align}
+Using the binomial theorem, for every $\ell\in \{0,\ldots, L-m-1\}$, we have that
 \begin{equation}
@@
 \begin{equation}
-\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)\delta_{\mu<N}|N\rangle
+\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
 \end{equation}
@@
 \begin{equation}
-	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)\delta_{\mu_{1}<N}|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)\delta_{\mu_{L}<N}|N\rangle\right)
+	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)(1-\delta_{\mu_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)(1-\delta_{\mu_{L},N})|N\rangle\right)
 \end{equation}

### 2023-10-25 main.tex
^^
ll
l
kk

@@
 \end{equation}
-Using \eqref{bosonicKX} we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ on the right hand side of \eqref{siteHadamardII} as 
+Using the above equation we rewrite the right hand side term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ as 
 \begin{equation}\label{extra-site-trick}
@@
 \end{flushright}
+
+{\color{blue}
+
+\begin{equation}
+\begin{split}
+\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N}\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \left(2+\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)\\
+% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N},-1)\\
+\end{split}
+\end{equation}
+Looks like there is a mistake somewhere...
+}
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}

### 2023-10-26 main.tex
s
ll
Compact formulas
l

--- 2023-10-19 main.tex
@@
 \end{flushright}
+
+{\color{blue}
+
+\begin{equation}
+\begin{split}
+\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
+&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\\
+% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N},-1)\\
+\end{split}
+\end{equation}
+The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
+
+Looks like there is a mistake somewhere...
+}
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}

### 2023-10-29 main.tex
ll
'
c bar

@@
 	\end{equation} 
+{\color{blue}
+	\begin{equation}
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
+	\end{equation}
+\begin{equation}
+	\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+\end{equation}
+	\begin{equation}
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\left(\frac{\lambda_{\tau_{x}}}{\beta_{\tau_x}}\right)^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{1-\delta_{\tau_{x},N} }
+	\end{equation}
+}
 	%\com{Double check this. Sum looks strange}
@@
 	\end{equation}
+{\color{blue}
+\begin{equation}
+	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\frac{1}{(1+L)!}\sum_{c_{1},\ldots,c_{m}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)
+\end{equation}
+\begin{equation}
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\frac{1}{(1+L)!}\sum_{c_{1},\ldots,c_{m}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{k}}\beta_{s_{k}}^{c_{k}}\left(1+\sum_{j=k}^{m}c_{j}\right)
+\end{equation}
+To check!
+}\\
 \textbf{Remark}: using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
@@
 \begin{align}
-	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
+	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
 	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\mathbbm{1}_{\{b\leq L-m-r\}}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
@@
 \begin{align}
-\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
+\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
 \\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}\mathbbm{1}_{\{b\leq L-m-\ell\}}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
@@
 \begin{equation}
-\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
 \end{equation}
@@
 \begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
 \end{equation}
@@
 \begin{equation}
- \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
+ \Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
 \end{equation}

### 2023-10-30 main.tex
intermediate

@@
 This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
-
+\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
+\begin{equation}\label{Tau-Notation}
+	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
+		\tau_{1}\\
+		\vdots\\
+		\tau_{L}
+	\end{pmatrix}
+\end{equation} 
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
+\begin{equation}\label{notation-change-relation}
+	n_{a}^{x}=\delta_{\tau_{x},a}
+\end{equation}
+In this notation, the elements of the duality matrix reads
+\begin{equation}\label{ElementsDualityMatrixChain_1}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
+\end{equation}
+\\
 Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
@@
 \begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{s_{k}}^{s_{k}}=1\}}\dt
-\end{equation}
-Denoting the $m$-point correlations by $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}$ we have 
+	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{y_{k}},s_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\dt
+\end{equation}
+Denoting the $m$-point correlations by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]$ we have 
 %To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
@@
 	\begin{split}
-	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
 	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
@@
 \subsubsection{Explicit formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
+\begin{comment}
 \textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
@@
 \end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-This notation is equivalent to the one introduced in Subsection \ref{subsectionGeneratorStr}.
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
+\begin{equation}
+	n_{a}^{x}=\delta_{\tau_{x},a}
+\end{equation}
+\end{comment}
+\begin{comment}
+
+This notation is equivalent to the one introduced.
 Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$.
@@
 \end{equation}
-with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$. \\ \\
+with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
+\end{comment} 
 We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
-\end{equation}
+	|\Psi^{''} \rangle=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+\end{equation}
+%\begin{equation}\label{ResulsBasis}
+%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
+%\end{equation}
 where 
@@
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
+In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof.
+We recall that these two notations are related by \eqref{notation-change-relation}.
 We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations.
@@
 \end{equation}
-Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ introduced in \eqref{notation} we have 
+Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ with $\bm{\tau}$, related to the one with $\bm{n}$ by \eqref{notation-change-relation}, we have 
 \begin{equation}
@@
 \end{equation}
+
+\begin{equation}
+\begin{split}
+\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
+&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
+&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N}),-1)\\
+\end{split}
+\end{equation}
+The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
 \begin{flushright}
@@
 \end{flushright}
-
-{\color{blue}
-
-\begin{equation}
-\begin{split}
-\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
-&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
-&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
-&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\\
-% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N},-1)\\
-\end{split}
-\end{equation}
-The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
-
-Looks like there is a mistake somewhere...
-}
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
@@
 		\begin{split}
+			\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+		\end{split}
+	\end{equation} 
+%\begin{equation}\label{ABS}
+%	\begin{split}
+%		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
+%	\end{split}
+%\end{equation} 
+\begin{comment}
+{\color{blue}
+	\begin{equation}
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}
+	\end{equation}
+\begin{equation}
 	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
-		\end{split}
-	\end{equation} 
-{\color{blue}
-	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}
-	\end{equation}
-\begin{equation}
-	\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
 \end{equation}
@@
 }
+\end{comment}
 	%\com{Double check this. Sum looks strange}
@@
 %\end{equation}
-\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$.
-Indeed, the empty species does not produce changes in the correlations between the non-empty species.
+\textbf{Remark}: By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{equation}\label{ABS_1}
+	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
+\end{equation}
+ where we used the fact that, for any $\bm{\tau}$ we have 
+\begin{equation}
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N})\right)
+\end{equation}
+This equation for $\Psi^{'}(\bm{\tau})$ will be useful in the computation of non-equilibrium steady state correlations and in the following Remark, where we specialize it to the case $N=2$ of SSEP.
 \\ \\
@@
 We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites.
-We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS} as
+We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS_1} as
 \begin{align}
@@
 
-\paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
+\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
 Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
@@
 \end{equation} 
+\begin{comment}
 {\color{blue}
@@
 The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
-} \\ By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain
+}
+\end{comment}
+ By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 
 \begin{equation}\label{ABS_intermediate}
@@
 \\
+\begin{comment}
 {\color{blue}
@@
 }
-For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis}, we obtain 
+\end{comment}
+For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis} we have
+\begin{equation}
+	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+\end{equation}
+\begin{comment}
 \begin{equation}
 	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\co
-\end{equation} where we have used the fact that 
+\end{equation}
+\end{comment}
+ \begin{comment}
+
+ where we have used the fact that 
 \begin{equation}
@@
 where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.\\
+\end{comment}
 \begin{comment}
@@
 Then, equation  \eqref{ABS_intermediate} reads
-Therefore, using equation \eqref{ABS_intermediate}, we obtain 
+We introduce 
+\begin{equation}
+	c_{x}=\delta_{\mu_{x},N}
+\end{equation}
+Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 
 \begin{equation}\label{elementsABS}
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
 	\end{split}
@@
 \begin{equation}\label{exactCorrelations}
-		\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
 			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
@@
 \begin{equation}
-	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\frac{1}{(1+L)!}\sum_{c_{1},\ldots,c_{m}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)
-\end{equation}
-\begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\frac{1}{(1+L)!}\sum_{c_{1},\ldots,c_{m}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{k}}\beta_{s_{k}}^{c_{k}}\left(1+\sum_{j=k}^{m}c_{j}\right)
-\end{equation}
-To check!
+	\begin{split}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{y_{k}}}\beta_{s_{k}}^{1-c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{y_{j}}\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}c_{y_{k}}\right)
+\end{split}
+\end{equation}
+It seems to me that it is more complicated than \eqref{exactCorrelations}...
 }\\
@@
 \begin{split}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&
 \sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 \begin{split}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
 \sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
@@
 \end{equation}
-Therefore, comparing this formula and \eqref{absProbabilitiesIntegrable}, we can determine the absorption probabilities 
+The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
+\begin{align}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}D(\tau,\hat{\bm{\xi}})\langle\tau|\Psi\rangle
+\end{align}
+where the dual configuration is $\hat{\bm{\xi}}=\sum_{k=1}^{m}\delta^{y_{k}}_{s_{k}}$. 
+Therefore, comparing this formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities 
 \begin{equation}
@@
 \begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
 \end{equation}
@@
 \begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\mathbb{E}_{stat}\left[\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
 \end{equation}
@@
 %where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
-Using formula \eqref{ABS} we have that 
-\begin{equation}
- \Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
+Using formula \eqref{ABS_1} we have that 
+\begin{equation}
+ \Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
 \end{equation}
@@
         \\&+\nonumber
-        \frac{(L-x_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
+        \frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
         \\&+\nonumber
@@
 	\begin{split}
+		\Psi(\bm{\tau})&=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+		\\&+
+		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
+		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
+		\\&
+	\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+	\end{split}
+\end{equation}
+\begin{comment}
+\begin{equation}
+	\begin{split}
 		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
@@
 \end{equation}
+\end{comment}
 where we have introduced, $\forall x\in \{1,\ldots,L\}$
@@
 			\begin{split}
-				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
-				\\&
-				\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
+				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
 			\end{split}

### 2023-10-31 main.tex
^^
Remark...

@@
 	\begin{equation}\label{powerCoeffSpecies}
-		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}
+		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
 	\end{equation}
@@
 	\begin{equation}\label{powerCoeffNOspec}
-		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{i=1}^{m}c_{i})}{\Gamma(L+2)}
+		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
 	\end{equation}
@@
 \begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
 \end{equation}
@@
 that implies 
-\begin{equation}
-\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\begin{equation}\label{shorter-chain}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
 \end{equation}
@@
 \end{flushright}
+{\color{blue}
+\textbf{Remark}: Consider equation \eqref{shorter-chain} and the fact that, from equation \eqref{SteadyState-coeff-implicit} we have  
+\begin{equation}
+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\Psi_{m}^{'}\left(s_{1},\ldots,s_{m}\right)=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
+\end{equation}
+where $|\Psi_{m}^{'}\rangle$ and $|\Psi_{m}\rangle$ are the eigenvector with vanishing eigenvalues of a chain with length $m$. Therefore, we have that 
+\begin{equation}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
+\end{equation}
+i.e., computing the $m$-point correlations is equivalent to computing the steady state of a chain of length $m$ where the occupations are $s_{1},\ldots,s_{m}$ and the coordinates of the sites are $y_{1},\ldots,y_{m}$.
+I still do not have an interpretation to this...
+}
 \begin{comment}

### 2023-11-02 main.tex
to fix

@@
 	\begin{equation}\label{powerCoeffNOspec}
-		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
+		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
 	\end{equation}
@@
 \end{equation}
-It seems to me that it is more complicated than \eqref{exactCorrelations}...
+EQUATION TO CHECK...It seems to me that it is more complicated than \eqref{exactCorrelations}...\\
+\underline{Explanation of the notation issue}:  Assume that we aim to find the 1-point correlation for $s$ at site $y$.
+If we compute it starting from \eqref{ABS_1} we have that all the $c_{x}$ with $x\neq y$ just disappear and we obtain
+\begin{equation}
+	\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{y}=s\}}\right]=\sum_{c_{y}=0}^{1}\frac{\Gamma(2+L-c_{y})}{\Gamma(2+L)}\lambda_{s}^{c_{y}}\beta_{s}^{c_{y}}\left(2+L-y-c_{y}\right)^{c_{y}}
+\end{equation}
+We do not have to keep the product over all $x$ and only the "correlated coordinate" $y$ does appear.
+On the other hand, if we compute 1-point correlation for $s$ at site $y$ using \eqref{ABS} we obtain
+\begin{equation}
+\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{y}=s\}}\right]=\frac{1}{(1+L)!} \sum_{c_{y}=0}^{1}\lambda_{s}^{1-c_{y}}\beta^{c_{y}}
+\end{equation}
+Here we have to keep the product over all $x$ and the "correlated coordinate" hidden in the product $y$.
 }\\

### 2023-11-02 main.tex
fixed

--- 2023-10-31 main.tex
@@
 	\begin{equation}\label{powerCoeffNOspec}
-		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
+		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
 	\end{equation}
 {\color{blue}
-\begin{equation}
-	\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{y_{k}}}\beta_{s_{k}}^{1-c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{y_{j}}\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}c_{y_{k}}\right)
-\end{split}
-\end{equation}
-It seems to me that it is more complicated than \eqref{exactCorrelations}...
+	Equation \eqref{exactCorrelations} is obtained from \eqref{ABS_1}.\\
+	Deriving correlations from \eqref{ABS}
+\begin{equation}\label{exactCorrelation_1}
+	\begin{split}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{y_{k}}}\beta_{s_{k}}^{c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}(1-c_{y_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{y_{k}})\right)
+\end{split}
+\end{equation}
+In \eqref{exactCorrelations} we have the $c_{y_{k}}$ at the exponent but we remove the product over $x$.
+ In \eqref{exactCorrelation_1} we have to keep the product over all $x$ and the "correlated coordinate" but we do not have the $c_{y}$ at the exponent. Which is better?
+\\
 }\\

### 2023-11-04 main.tex
Update main.tex
fixed abs

@@
 \begin{equation}\label{boundary-H-dual-chain}
-	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
+	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((\mathbf{a}{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 \begin{equation}\label{ElementsDualityMatrixChain_1}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
+	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
 \end{equation}
@@
 Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
-Consider a dual configuration $\bm{\hat{\xi}}:=\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}}$ where $s_{k}\in\{1,\ldots,N-1\}$ and $y_{k}\in\{1,\ldots,L\}$ such that $y_{k}<y_{k+1}$ for every $k\in\{1,\ldots,m\}$.
-Fix an arbitrary initial configuration $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\bm{\hat{\xi}}$ read
-\begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{y_{k}},s_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\dt
-\end{equation}
-Denoting the $m$-point correlations by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]$ we have 
+For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
+We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
+\begin{equation}
+	\bm{\xi}=\begin{cases}
+		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
+		\xi_{a}^{x}=0\qquad \text{otherwise}
+	\end{cases}
+\end{equation}
+For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
+\begin{equation}
+	D(\bm{\tau},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{y_{k}},s_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\dt
+\end{equation}
+Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]$ we have 
 %To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
@@
 	\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{\hat{\xi}}(t))\right]
 	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta_{0}+(1-c_{k})\delta_{L+1}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
-\end{equation}
- namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right.
+	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta^{0}_{a_k}+(1-c_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+ namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right.
 Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
@@
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+	|\Psi^{''} \rangle= \sum_{\tau}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\tau\rangle
 \end{equation}

### 2023-11-04 main.tex
ll

@@
 
+{\color{blue}
 \begin{equation}
@@
 \end{equation}
+}
 The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
@@
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
-By knowing the steady state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the steady state of the Hamiltonian $H^{'}$. The result is the following 
+By knowing the ground state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the ground state of the Hamiltonian $H^{'}$. The result is the following 
 \begin{equation}\label{ABS-vect}
@@
 We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS_1} as
+{\color{red}
 \begin{align}
@@
 \end{align}
+}
 For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
@@
 \end{comment}
+
+{\color{blue}$\mu$ or $\tau$ here?}
+
 For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis} we have
@@
 \subsection{Explicit formula for the steady state $|\Psi\rangle$}
+{\color{blue}can we proceed as above? using sth similar to \eqref{goodTP-S2}}
+
 The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 

### 2023-11-06 main.tex
^^

@@
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle= \sum_{\tau}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\tau\rangle
+	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
 \end{equation}
@@
 \end{equation}
-\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
-Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
-Thus, the coefficient of the above formula can be written as
-\begin{align}
-&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
-=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
-\end{align}
-By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore, we write 
-\begin{equation}
-	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
-\end{equation}
+
 %and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
 \paragraph{Proof of formula \eqref{ResulsBasis}} 
-In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof.
+%In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof.
 We recall that these two notations are related by \eqref{notation-change-relation}.
@@
 \end{equation}
-with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{1}$, see \eqref{Xtildes2b}. 
+with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$, see \eqref{Xtildes2b}. 
 Therefore, we obtain the commutation relations for $\Xt_{a}$ 
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle \,|\bm{n}\rangle
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|V \rangle \,|\bm{\tau}\rangle
 \end{equation}
@@
 \end{align}
+\begin{comment}
 The basis is 
@@
 such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. \\
-To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}
+\end{comment}
+To determine the eigenvector \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 |V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
@@
 %	\\&=\ldots\\&=
-	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
-\end{align}
+	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
+\end{align}
+\begin{comment}
 therefore 
@@
 \end{align*}
+\end{comment}
 By taking the product over the sites $x$ from $1$ to $L$ we obtain 
 \begin{equation}
-	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\dt
+	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{n_{a}^{x}}\dt
 \end{equation}
@@
 \begin{align}
-	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
+	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|V \rangle\nonumber&=
+	\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
+\end{align}
+We now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  
+\begin{align*}
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
+	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+\lambda_{a}(n-1)\right)|V\rangle
 	\\&=
-	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle \dt
-\end{align}
-To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle$.
-Calling $\sum_{i=1}^{L}n_{N}^{i}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain
-\begin{align*}
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{N}^{n_{N}-1}|V\rangle
+	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{N}-1)\right)|V\rangle
+	\left(2+n-1\right)\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle+\left(n_{N}+1-1\right)\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
-	\\&=
-	\left(2+n_{N}-1\right)\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
-	\\&=
-	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{1}-1}|V\rangle
+	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
 \end{align*}
@@
 \begin{align}
-		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
+		\langle V^{*}|\widetilde{X}_{N}^{n}|V\rangle=\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
 \end{align}
@@
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
-	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=
-	\Gamma(2+n_{N})
+	\langle V^{*}|\widetilde{X}_{N}^{n}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
+	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\frac{\Gamma(2+n-1)}{\Gamma(2+n-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=
+	\Gamma(2+n)
 \end{align*}
-By using this result we have 
-\begin{equation}
-	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-	|V \rangle=\Gamma(2+n_{N})\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
-\end{equation}
-The normalization constant is computed similarly as 
+By using this result we have that
+\begin{equation}
+	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|V \rangle=\Gamma(2+\sum_{x=1}^{N}\delta_{\tau_{x},N})\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
+\end{equation}
+The normalization constant is then given by
 \begin{align*}
-	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}\widetilde{X}_{N}^{L}|V|\rangle=
+	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle=
 	\Gamma(2+L)\dt
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle\dt
-\end{equation}
+	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
+\end{equation}
+We observe that, for all $x$, we have
+\begin{equation}
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}
+\end{equation}
+\begin{comment}
 Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ with $\bm{\tau}$, related to the one with $\bm{n}$ by \eqref{notation-change-relation}, we have 
@@
 
+\end{comment}
+\begin{comment}
 {\color{blue}
@@
 \end{split}
-\end{equation}
-}
-The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
+\end{equation}}
+\end{comment}
+It follows that 
+\begin{align}\label{remove-exponent}
+&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
+=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\
+=&\frac{\Gamma(2)}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x}^{L}\delta_{\tau_{j},x})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})}\nonumber\\
+=&\frac{1}{(1+L)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+\end{align}
+Therefore, we obtain \eqref{ResulsBasis}.
+%The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
 \begin{flushright}
@@
 \end{flushright}
+\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
+Thus, arguing as in \eqref{remove-exponent}, the coefficient \eqref{ResulsBasis} when $N=2$ are written as
+\begin{align}
+	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+	=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
+\end{align}
+By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore, we write 
+\begin{equation}
+	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
+\end{equation}
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
@@
 \begin{equation}\label{ABS-vect}
-    |\Psi^{'}\rangle =\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
+    |\Psi^{'}\rangle =\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
 \end{equation}

### 2023-11-06 main.tex
''

@@
 \begin{equation}\label{ABS_1}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
+	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
 \end{equation}
@@
 \\ \\
-\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty.
-We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites.
-We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS_1} as
-{\color{red}
-\begin{align}
-	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
-	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
-\end{align}
-}
-For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
+\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we define $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty.
+We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
+We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
+These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
+For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e.
+the coordinate where the particle with label $\ell_{i}$ is placed.
+We this notation we have that
+%and we rewrite \eqref{ABS_1} as
+%{\color{red}
+%\begin{align}
+%	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
+%	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
+%\end{align}
+%}
+%For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,L\}}$ such that its sum is equal to $q$. For any fixed $L$ values of $(c_{i})_{i\in\{1,\ldots,L\}}$ we have   
 \begin{equation}
@@
 \end{equation}
-We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$.
+%We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$.
 Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$.
-It follows that we have
-\begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
+Thus, it follows that
+\begin{equation}
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
 \end{equation} 
@@
 \end{equation}
-
+Therefore, considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP. 
 \paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 \begin{equation}\label{goodTP-S2}
-  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
+  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]
 \end{equation} 
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle=\sum_{\mu\in \Omega}\Psi^{''}(\bm{\mu})\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
+		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
 	\end{split}
@@
 \end{comment}
-
-{\color{blue}$\mu$ or $\tau$ here?}
-
-For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, by using equation \eqref{ResulsBasis} we have
-\begin{equation}
-	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
-\end{equation}
-\begin{comment}
+For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, 
+We introduce 
+\begin{equation}
+	c_{x}=\delta_{\mu_{x},N}
+\end{equation}
+thus, by using equation \eqref{ResulsBasis}, we have
+\begin{equation}
+	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\mu_{x}}^{(1-c_{x})}\left(1+\sum_{j=x}^{L}c_{j}\right)
+\end{equation}
+\begin{comment}
+	\begin{equation}
+		\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\mu_{x}}^{(1-\delta_{\mu_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right)
+	\end{equation}
 \begin{equation}
@@
 Then, equation  \eqref{ABS_intermediate} reads
-We introduce 
-\begin{equation}
-	c_{x}=\delta_{\mu_{x},N}
-\end{equation}
+
 Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 

### 2023-11-06 main.tex
^'^'

@@
 \end{equation} 
+ In this context, it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by
+\begin{equation}\label{Tau-Notation}
+	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
+		\tau_{1}\\
+		\vdots\\
+		\tau_{L}
+	\end{pmatrix}
+\end{equation} 
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The configuration $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by 
+\begin{equation}\label{notation-change-relation}
+	n_{a}^{x}=\delta_{\tau_{x},a}
+\end{equation}
+The state space of the process is now given in terms of $\bm{\tau}$ by
+\begin{equation}
+	\Omega=\bigtimes_{x=1}^{L}\Omega_{x}\qquad \Omega_{x}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
+\end{equation}
+In all situations where we consider the integrable chain, we will use this notation for the configuration variable.\\ 
 The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
@@
 The elements of this duality matrix are given by
-\begin{equation}\label{ElementsDualityMatrixChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
-\end{equation}
+\begin{equation}\label{ElementsDualityMatrixChain_1}
+	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
+\end{equation}
+%\begin{equation}\label{ElementsDualityMatrixChain}
+%	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
+%\end{equation}
 The dual Hamiltonian is
@@
 This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
-\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
-\begin{equation}\label{Tau-Notation}
-	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
-		\tau_{1}\\
-		\vdots\\
-		\tau_{L}
-	\end{pmatrix}
-\end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
-\begin{equation}\label{notation-change-relation}
-	n_{a}^{x}=\delta_{\tau_{x},a}
-\end{equation}
-In this notation, the elements of the duality matrix reads
-\begin{equation}\label{ElementsDualityMatrixChain_1}
-	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
-\end{equation}
-\\
+
+%In this notation, the elements of the duality matrix reads
+%\begin{equation}\label{ElementsDualityMatrixChain_1}
+%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
+%\end{equation}
+%\\
 Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
@@
 \begin{equation}
-	D(\bm{\tau},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{y_{k}},s_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\dt
-\end{equation}
-Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]$ we have 
+	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
+\end{equation}
+Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
 %To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
@@
 	\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{\hat{\xi}}(t))\right]
-	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
+	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
 \end{split}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta^{0}_{a_k}+(1-c_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
-\end{equation}
- namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right.
+	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+\end{equation}
+ namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right.
 Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
@@
  Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations.
-\subsection{The explicit form of the steady state}\label{subsection-exact}
-The MPA gives an abstract form of the steady state in terms of an algebra of operators. This path has been followed in \cite{vanicat2017exact} to find one and two-point correlations. 
-Here we follow the same approach. We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the
+\\ \\The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators.
+However, the computation of exact correlations are in general involving.
+ We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the use of commutators in the
  computation. The idea is summarized as follows. We define a sequence of similarity transformation such that 
@@
 \\
-
-The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
+\subsection{Exact correlations in the non-equilibrium steady state}\label{subsection-exact}
+In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e.
+a species with label from $1$ to $N-1$.
+%This is motivated by the interest of understanding how actual particles of the chain are correlated among each others and also because in the steady state the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=1-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
+ Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$.
+In each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
+Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
+\begin{equation}\label{exactCorrelations}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
+\end{equation}
+where 
+\begin{equation}\label{powerCoeffSpecies}
+	g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+and 
+\begin{equation}\label{powerCoeffNOspec}
+	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
+\end{equation}
+{\color{blue}
+	Equation \eqref{exactCorrelations} is obtained from \eqref{ABS_1}.\\
+	Deriving correlations from \eqref{ABS}
+	\begin{equation}\label{exactCorrelation_1}
+		\begin{split}
+			\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{y_{k}}}\beta_{s_{k}}^{c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}(1-c_{y_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{y_{k}})\right)
+		\end{split}
+	\end{equation}
+	In \eqref{exactCorrelations} we have the $c_{y_{k}}$ at the exponent but we remove the product over $x$.
+	In \eqref{exactCorrelation_1} we have to keep the product over all $x$ and the "correlated coordinate" but we do not have the $c_{y}$ at the exponent. Which is better?
+}
+\paragraph{Absorption probabilities}
+The absorption probabilities are given by  
+\begin{equation}\label{abs-probabilities}
+	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+\end{equation}
+where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. \\ \\
+\textbf{Proof of \eqref{abs-probabilities}}: 
+ using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
+\begin{equation}
+	\begin{split}
+		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&
+		\sum_{c_{1},\ldots,c_{m}=0}^{1}
+		f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\
+		=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
+		f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
+	\end{split}
+\end{equation}
+By exchanging the summations we rewrite as 
+\begin{equation}
+	\begin{split}
+		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+		\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
+		=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
+	\end{split}
+\end{equation}
+%The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
+%\begin{align}
+%	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}D(\tau,\hat{\bm{\xi}})\langle\tau|\Psi\rangle
+%\end{align}
+%where the dual configuration is $\hat{\bm{\xi}}=\sum_{k=1}^{m}\delta^{y_{k}}_{s_{k}}$. 
+Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities. 
+\begin{flushright}
+	$\square$
+\end{flushright}
+\subsubsection{Explicit examples of non-equilibrium steady state correlations}
+We give examples  of correlations for up to three points applying formula \eqref{exactCorrelations}.
+\paragraph{One-point correlations}
+The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
+\begin{equation}
+	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})\dt
+\end{equation}
+Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{equation}\label{one-pts-corr}
+	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}\dt
+\end{equation}
+\paragraph{Two-point correlations}
+The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+\begin{equation}
+	\begin{split}
+		\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})\dt
+	\end{split}
+\end{equation}
+Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{equation}
+	\begin{split}
+		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\dt
+	\end{split}
+\end{equation}
+Therefore, we compute the second cumulant, i.e. the two-point connected correlation
+\begin{equation}\label{two-pts-corr}
+	\begin{split}
+		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)\dt
+	\end{split}
+\end{equation}
+\paragraph{Three-point correlations}
+The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
+\begin{equation}
+	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})\dt
+\end{equation}
+Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+\begin{align}\label{three-pts-corr}
+	\langle n_{a_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
+	\\&+\nonumber
+	\frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
+	\\&+\nonumber
+	\frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
+	\\&+\nonumber
+	\frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
+	\\&+\nonumber
+	\frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
+	\\&+\nonumber
+	\frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
+\end{align}
+Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
+\begin{align}
+	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\nonumber\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]\nonumber
+	\\&=
+	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
+\end{align}
+\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
+%The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
 Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ exploiting the simpler commutators.
@@
 The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix \ref{appB}.
-
 \begin{comment}
@@
 \end{comment}
+\subsection{Proof of th exact correlations in the non-equilibrium steady state}
+[ADD TEXT]
 \subsubsection{The similarity transformations}\label{subsectionSTransf}
@@
 %\end{equation}
-\textbf{Remark}: By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
-\begin{equation}\label{ABS_1}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
-\end{equation}
- where we used the fact that, for any $\bm{\tau}$ we have 
-\begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N})\right)
-\end{equation}
-This equation for $\Psi^{'}(\bm{\tau})$ will be useful in the computation of non-equilibrium steady state correlations and in the following Remark, where we specialize it to the case $N=2$ of SSEP.
-\\ \\
-\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we define $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty.
-We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
-We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
-These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
-For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e.
-the coordinate where the particle with label $\ell_{i}$ is placed.
-We this notation we have that
-%and we rewrite \eqref{ABS_1} as
-%{\color{red}
-%\begin{align}
-%	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
-%	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
-%\end{align}
-%}
-%For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,L\}}$ such that its sum is equal to $q$. For any fixed $L$ values of $(c_{i})_{i\in\{1,\ldots,L\}}$ we have   
-\begin{equation}
-	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)\dt
-\end{equation}
-%We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$.
-Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$.
-Thus, it follows that
-\begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
-\end{equation} 
-Observing that
-\begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
-\end{equation}
-we finally obtain 
-\begin{equation}\label{PsiI-N2}
-	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
-\end{equation}
-Therefore, considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP. 
 \paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 \end{flushright}
-
+\textbf{Remark}: By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{equation}\label{ABS_1}
+	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
+\end{equation}
+where we used the fact that, for any $\bm{\tau}$ we have 
+\begin{equation}
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N})\right)
+\end{equation}
+This equation for $\Psi^{'}(\bm{\tau})$ will be useful in the computation of non-equilibrium steady state correlations and in the following Remark, where we specialize it to the case $N=2$ of SSEP.
+\\ \\
+\textbf{Remark:}  We aim to find equation \eqref{ABS_1} in the case $N=2$.
+For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty.
+We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
+We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
+These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
+For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e.
+the coordinate where the particle with label $\ell_{i}$ is placed.
+We this notation we have that
+%and we rewrite \eqref{ABS_1} as
+%{\color{red}
+	%\begin{align}
+	%	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
+	%	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
+	%\end{align}
+	%}
+%For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,L\}}$ such that its sum is equal to $q$. For any fixed $L$ values of $(c_{i})_{i\in\{1,\ldots,L\}}$ we have   
+\begin{equation}
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)\dt
+\end{equation}
+Thus, it follows that
+\begin{equation}
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
+\end{equation} 
+Observing that
+\begin{equation}
+	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
+\end{equation}
+we finally obtain 
+\begin{equation}\label{PsiI-N2}
+	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation}
+Therefore, considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP. 
+\begin{flushright}
+	$\square$
+\end{flushright}
+\subsubsection{Formula for exact correlations}\label{correlation-section}
+We aim to compute
+\begin{equation}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+\end{equation}
+We observe that 
+\begin{equation}
+	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})
+\end{equation}
+with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. Thus we have
+\begin{align}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+\end{align}
+Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$ and recalling that  
+\begin{equation}
+	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
+\end{equation} 
+we have
+\begin{equation}
+	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
+\end{equation}
+Therefore, we have that 
+\begin{align}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
+	=&\sum_{\bm{\tau}\in \Omega}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
+	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
+	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
+	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\co
+\end{align}
+where in the second line we have used the resolution of the identity and in the last line we have used \eqref{ABS_1}. 
+\begin{flushright}
+	$\square$
+\end{flushright}
+\subsection{The colour-blind case}
+In this subsection we show that, if we stop distinguishing particles, we retrieve the non-equilibrium steady state correlations found in \cite{frassek2020eigenstates}.
+Moreover, for the sake of completeness, we also report the eigenvectors $|\Psi^{''}\rangle$ and $|\Psi^{'}\rangle$ when particles are indistinguishable.
+\paragraph{Correlations of SSEP}
+\paragraph{$|\Psi^{''}\rangle$ for SSEP}
+\paragraph{$|\Psi^{'}\rangle$ for SSEP}
 \subsection{Explicit formula for the steady state $|\Psi\rangle$}
@@
 \end{comment}
-\subsection{Exact steady state correlations}\label{correlation-section}
-In this section we write a formula for the stationary steady state correlations between $m$- points of the chain, each of them occupied by a non empty species, i.e.
-a species with label from $1$ to $N-1$.
-This is motivated by the interest of understanding how actual particles of the chain are correlated among each others and also because in the steady state the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=1-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
-Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $\bm{y}=(y_{1},\ldots,y_{m})$, such that $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$.
-In each of these points there is a particle of species $s_{i}\in \{1,\ldots,N-1\}$.
-Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
-\begin{equation}\label{exactCorrelations}
-		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-			f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
-	\end{equation}
-	where 
-	\begin{equation}\label{powerCoeffSpecies}
-		g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-	\end{equation}
-	and 
-	\begin{equation}\label{powerCoeffNOspec}
-		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
-	\end{equation}
-{\color{blue}
-	Equation \eqref{exactCorrelations} is obtained from \eqref{ABS_1}.\\
-	Deriving correlations from \eqref{ABS}
-\begin{equation}\label{exactCorrelation_1}
-	\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{y_{k}}}\beta_{s_{k}}^{c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}(1-c_{y_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{y_{k}})\right)
-\end{split}
-\end{equation}
-In \eqref{exactCorrelations} we have the $c_{y_{k}}$ at the exponent but we remove the product over $x$.
- In \eqref{exactCorrelation_1} we have to keep the product over all $x$ and the "correlated coordinate" but we do not have the $c_{y}$ at the exponent. Which is better?
-\\
-}\\
-\textbf{Remark}: using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
-\begin{equation}
-\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&
-\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\
-=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
-\end{split}
-\end{equation}
-By exchanging the summations we rewrite as 
-\begin{equation}
-\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
-=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
-\end{split}
-\end{equation}
-The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
-\begin{align}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}D(\tau,\hat{\bm{\xi}})\langle\tau|\Psi\rangle
-\end{align}
-where the dual configuration is $\hat{\bm{\xi}}=\sum_{k=1}^{m}\delta^{y_{k}}_{s_{k}}$. 
-Therefore, comparing this formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities 
-\begin{equation}
-	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
-\end{equation}
-where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{s_{i}}^{y_{i}}$. 
-\\ \\
+\subsubsection{Exact steady state correlations}
 \textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}.
@@
 \paragraph{Proof of formula \eqref{exactCorrelations}}
-We aim to compute
-\begin{equation}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
-\end{equation}
+{\color{blue}
 We introduce the space 
@@
 \end{flushright}
+}
 {\color{blue}
@@
 \end{comment}
-\subsubsection{Explicit examples of steady state correlations}
-We give examples  of correlations for up to three points applying formula \eqref{exactCorrelations}.
-\paragraph{One-point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
-\begin{equation}
-	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})\dt
-\end{equation}
-Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
-\begin{equation}\label{one-pts-corr}
-\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}\dt
-\end{equation}
-\paragraph{Two-point correlations}
-The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
-\begin{equation}
-	\begin{split}
-	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})\dt
-	\end{split}
-\end{equation}
-Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
-\begin{equation}
-	\begin{split}
-	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\dt
-	\end{split}
-\end{equation}
-Therefore, we compute the second cumulant, i.e. the two-point connected correlation
-\begin{equation}\label{two-pts-corr}
-	\begin{split}
-		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)\dt
-	\end{split}
-\end{equation}
-\paragraph{Three-point correlations}
-The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
-\begin{equation}
-    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})\dt
-\end{equation}
-Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
-\begin{align}\label{three-pts-corr}
-        \langle n_{a_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
-        \\&+\nonumber
-        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
-        \\&+\nonumber
-        \frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
-        \\&+\nonumber
-        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
-        \\&+\nonumber
-        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
-        \\&+\nonumber
-        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
-\end{align}
-Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
-\begin{align}
-	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\nonumber\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]\nonumber
-	\\&=
-	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
-\end{align}
-\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
+
 \section{Extensions for the non-integrable chain}

### 2023-11-07 main.tex
^

@@
 \begin{equation}\label{exactCorrelations}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
 \end{equation}
@@
 \begin{equation}\label{powerCoeffSpecies}
-	g_{k}(L,y_{k},c_{k},\ldots,c_{m})=\left(L+2-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
 \end{equation}
@@
 \paragraph{Correlations of SSEP}
+ In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:
+\begin{equation}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation} 
+\textbf{Proof:} Starting from \eqref{exactCorrelations_1} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$, such that $q\in\{0,\ldots,m\}$.
+There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the selected particles $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
+For any $q$, we identify $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ coordinates where the $c_{x_{\ell_{i}}}=1$, then we have that
+	\begin{equation}
+		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
+	\end{equation}
+Moreover, we observe that for fixed $q$ we have
+\begin{equation}
+	\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
+\end{equation}
+Varying all possible $c$'s in \eqref{exactCorrelation_1} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
+\begin{equation}
+	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
+\end{equation}
 \paragraph{$|\Psi^{''}\rangle$ for SSEP}
@@
 \subsubsection{Exact steady state correlations}
-\textbf{Remark}: In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}.
-Indeed, by adapting \eqref{PsiI-N2} we obtain
+
 \begin{comment}
@@
 \end{comment}
-\begin{equation}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
-\end{equation}
 

### 2023-11-07 main.tex
'

@@
 \end{flushright} 
-\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
-Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
-Thus, arguing as in \eqref{remove-exponent}, the coefficient \eqref{ResulsBasis} when $N=2$ are written as
-\begin{align}
-	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
-	=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
-\end{align}
-By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore, we write 
-\begin{equation}
-	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
-\end{equation}
 \subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
@@
 \\ \\
-\textbf{Remark:}  We aim to find equation \eqref{ABS_1} in the case $N=2$.
-For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty.
+\textbf{Remark:}  
+\begin{flushright}
+	$\square$
+\end{flushright}
+\subsubsection{Formula for exact correlations}\label{correlation-section}
+We aim to compute
+\begin{equation}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+\end{equation}
+We observe that 
+\begin{equation}
+	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})
+\end{equation}
+with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. Thus we have
+\begin{align}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+\end{align}
+Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$ and recalling that  
+\begin{equation}
+	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
+\end{equation} 
+we have
+\begin{equation}
+	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
+\end{equation}
+Therefore, we have that 
+\begin{align}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
+	=&\sum_{\bm{\tau}\in \Omega}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
+	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
+	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
+	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\co
+\end{align}
+where in the second line we have used the resolution of the identity and in the last line we have used \eqref{ABS_1}. 
+\begin{flushright}
+	$\square$
+\end{flushright}
+\subsection{The colour-blind case}
+The computations made for the multi-species stirring process can be specialized for the colour-blind case, i.e.
+the situation in which only one type of non-empty particle is considered.
+In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
+We report the Hamiltonians and the similarity transformations.
+\begin{equation}
+	H=H_{left}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{right}
+\end{equation}
+where 
+\begin{equation}
+	H_{x,x+1}=\sum_{a,b=1}^{2}\left(e_{ab}\otimes e_{ba}-e_{bb}\otimes e_{aa}\right)
+\end{equation}
+and 
+\begin{equation}
+	H_{left}=\begin{pmatrix}
+		1-\alpha_{1}&\alpha_{1}\\
+		\alpha_{2}&1-\alpha_{2}
+	\end{pmatrix},\qquad H_{right}=\begin{pmatrix}
+	1-\beta_{1}&\beta_{1}\\
+	\beta_{2}&1-\beta_{2}
+\end{pmatrix}
+\end{equation}
+In this case, the similarity transformations read
+\begin{equation}
+	\mathcal{S}_{1}=\begin{pmatrix}
+		1&0\\
+		1&1
+	\end{pmatrix},\qquad \mathcal{S}_{2}=\begin{pmatrix}
+	1&-\beta_{1}\\
+	0&1
+\end{pmatrix}
+\end{equation}
+Therefore, we have that $H^{'}$ has the following boundaries
+\begin{equation}
+	H^{'}_{left}=\begin{pmatrix}
+		-1&\alpha_{1}\\
+		0&0
+	\end{pmatrix},\qquad H^{'}_{right}=\begin{pmatrix}
+	-1&\beta_{1}\\
+	0&0
+\end{pmatrix}
+\end{equation}
+and $H^{''}$ has the following boundaries 
+\begin{equation}
+	H^{''}_{left}=\begin{pmatrix}
+		-1&(\alpha_{1}-\beta_{1})\\
+		0&0
+	\end{pmatrix},\qquad H^{''}_{right}=\begin{pmatrix}
+	-1&0\\
+	0&0
+\end{pmatrix}
+\end{equation}
+ We only report the main results, since the computations are just a specific case of the ones done in this section for the multi-species stirring process. 
+\paragraph{Correlations of SSEP}
+ In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:
+\begin{equation}\label{correlations-SSEP}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation} 
+\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
+There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the $c$'s equal to $1$ denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ and such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$, i.e.
+$c_{x_{\ell_{i}}}=1$ for $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$.
+Therefore, we have
+	\begin{equation}
+		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
+	\end{equation}
+Moreover, we observe that for fixed $q$ we have
+\begin{equation}\label{Gamma-product}
+	\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
+\end{equation}
+Varying all possible $c$'s in \eqref{exactCorrelations} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
+\begin{equation}
+	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
+\end{equation}
+thus, \eqref{correlations-SSEP} follows. 
+\begin{flushright}
+	$\square$
+\end{flushright}
+\paragraph{$|\Psi^{''}\rangle$ for SSEP} When we stop distinguishing colours we have that 
+\begin{equation}\label{psiII-SSEP}
+	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
+\end{equation}
+\textbf{Proof:} 
+We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
+Thus, arguing as in \eqref{remove-exponent} and using \eqref{Gamma-product} we have that
+\begin{align}
+	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+	=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
+\end{align}
+By varying $q$ and $\ell_{1},\ldots,\ell_{q}$, we have a one-to-one mapping with $\bm{\tau}$, therefore we obtain \eqref{psiII-SSEP}.
+\begin{flushright}
+	$\square$
+\end{flushright}
+\paragraph{$|\Psi^{'}\rangle$ for SSEP} In the colour-blind case, the ground state of $H^{'}$ reads
+\begin{equation}
+	|\Psi^{'}\rangle=\sum_{\bm{\tau}\in\Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle
+\end{equation}
+where 
+\begin{equation}\label{PsiI-N2}
+	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+\end{equation}
+ \textbf{Proof:} For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty.
 We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
@@
 \begin{equation}
-	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)\dt
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt
 \end{equation}
@@
 \end{equation} 
-Observing that
-\begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
-\end{equation}
-we finally obtain 
-\begin{equation}\label{PsiI-N2}
-	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
-\end{equation}
-Therefore, considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP. 
+Therefore, using \eqref{Gamma-product} and by considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP.
 \begin{flushright}
@@
 \end{flushright}
-\subsubsection{Formula for exact correlations}\label{correlation-section}
-We aim to compute
-\begin{equation}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
-\end{equation}
-We observe that 
-\begin{equation}
-	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})
-\end{equation}
-with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. Thus we have
-\begin{align}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
-	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
-\end{align}
-Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$ and recalling that  
-\begin{equation}
-	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
-\end{equation} 
-we have
-\begin{equation}
-	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
-\end{equation}
-Therefore, we have that 
-\begin{align}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
-	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
-	=&\sum_{\bm{\tau}\in \Omega}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
-	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
-	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
-	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\co
-\end{align}
-where in the second line we have used the resolution of the identity and in the last line we have used \eqref{ABS_1}. 
-\begin{flushright}
-	$\square$
-\end{flushright}
-\subsection{The colour-blind case}
-In this subsection we show that, if we stop distinguishing particles, we retrieve the non-equilibrium steady state correlations found in \cite{frassek2020eigenstates}.
-Moreover, for the sake of completeness, we also report the eigenvectors $|\Psi^{''}\rangle$ and $|\Psi^{'}\rangle$ when particles are indistinguishable.
-\paragraph{Correlations of SSEP}
- In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:
-\begin{equation}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
-\end{equation} 
-\textbf{Proof:} Starting from \eqref{exactCorrelations_1} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$, such that $q\in\{0,\ldots,m\}$.
-There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the selected particles $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
-For any $q$, we identify $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ coordinates where the $c_{x_{\ell_{i}}}=1$, then we have that
-	\begin{equation}
-		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
-	\end{equation}
-Moreover, we observe that for fixed $q$ we have
-\begin{equation}
-	\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
-\end{equation}
-Varying all possible $c$'s in \eqref{exactCorrelation_1} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
-\begin{equation}
-	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
-\end{equation}
-\paragraph{$|\Psi^{''}\rangle$ for SSEP}
-\paragraph{$|\Psi^{'}\rangle$ for SSEP}
 \subsection{Explicit formula for the steady state $|\Psi\rangle$}

### 2023-11-07 main.tex
^^

@@
 % \newcommand{\rouven}[1]{{ (* {\color{red}{} \small #1}*)}}
-
+ \newtheorem{remark}{Remark}
 \frenchspacing
@@
 \noindent
-{\bf Remark.} In the following we will often consider type $N$ as a distinguished type
+\begin{remark}
+In the following we will often consider type $N$ as a distinguished type
 (called `holes'), whose number at each site is fixed by the numbers of particles 
@@
 Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.  
+\end{remark}
 
@@
 \end{equation} 
- In this context, it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by
+ In this context it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by
 \begin{equation}\label{Tau-Notation}
@@
 In the specific case where $\mathcal{L}=\widetilde{\mathcal{L}}$ we say that the process is self-dual.
-\newline
-\newline
-\textbf{Remark}:
+\begin{remark}
 when the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$.
@@
 \end{equation}
+\end{remark}
 \subsection{Duality for the open multi-species stirring process}\label{statementDualitySubsection}
@@
 \newline \newline
-\textbf{Remark}: in the reversible situation, i.e.
+\begin{remark} in the reversible situation, i.e.
 when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
@@
 \end{equation}
-
+\end{remark}
 \subsection{Proof of duality}
@@
 Without loss of generality, we further assume that $\langle V^{*}|V\rangle=1$. 
-\newline \newline
-\textbf{Remark}: Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
+\begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
 	\begin{equation}
@@
 	and using  \eqref{ratesConditions} and \eqref{lambdaConditions}.
- Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations.
-\\ \\The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators.
-However, the computation of exact correlations are in general involving.
+ Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
+The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of exact correlations are in general involving. 
  We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the use of commutators in the
@@
 \end{align}
-\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
+\begin{remark} the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
+	\end{remark}
 %The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
@@
 \end{comment}
-\subsection{Proof of th exact correlations in the non-equilibrium steady state}
-[ADD TEXT]
+\subsection{Proof of the exact correlations in the non-equilibrium steady state}
+The proof of formula \eqref{exactCorrelations} is made in some steps:
+\begin{itemize}
+	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular diagonal boundaries respectively.
+Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively.
+	\item In Subsection \ref{subsectionSSHsec} we apply the MPA to $H^{''}$.
+Here the commutation relations defining the matrix algebra are simpler.
+The explicit expression for $|\Psi^{''}\rangle$ is determined (see \eqref{ResulsBasis}).
+	\item In subsection \ref{subsectionSSdual}, we invert one of the similarity transformation recovering the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$ computed in the previous step (see \eqref{ABS}).
+	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step.
+Using duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$.
+However, for the sake of completeness we report it Appendix \ref{appB}.
+\end{itemize}
 \subsubsection{The similarity transformations}\label{subsectionSTransf}
@@
 \end{equation}
-\textbf{Remark:} The boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e.
+\begin{remark}
+	The boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e.
 to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
@@
 $\beta_a$).
-\newline\newline
+\end{remark}
 We have the following correspondence between eigenvectors with zero eigenvalues
@@
 \end{flushright}
-\textbf{Remark}: By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{remark} By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
 \begin{equation}\label{ABS_1}
@@
 \end{equation}
-This equation for $\Psi^{'}(\bm{\tau})$ will be useful in the computation of non-equilibrium steady state correlations and in the following Remark, where we specialize it to the case $N=2$ of SSEP.
-\\ \\
-\textbf{Remark:}  
-\begin{flushright}
-	$\square$
-\end{flushright}
+This formula will be useful in the following. 
+\end{remark}
 \subsubsection{Formula for exact correlations}\label{correlation-section}
@@
 \end{equation}
-with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. Thus we have
+with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$. Thus we have
 \begin{align}
@@
 \subsection{The colour-blind case}
-The computations made for the multi-species stirring process can be specialized for the colour-blind case, i.e.
-the situation in which only one type of non-empty particle is considered.
+The computations made for the multi-species stirring process can be specialized for the colour-blind case $N=2$, i.e.
+when only one type of non-empty particle is considered.
 In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
@@
 \end{flushright}
+\begin{comment}
 \subsection{Explicit formula for the steady state $|\Psi\rangle$}
@@
 where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
-\begin{equation}\label{SteadyState-coeff-implicit}
-	\begin{split}
-		\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-	\end{split}
-\end{equation}
+
  Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression.
 We report the explicit formula and the proof in Appendix \ref{appB}.\\
-In \eqref{SteadyState-coeff-implicit} there are two terms.
-For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
-The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$ computed in these new configurations with proper coefficients.
-If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.\\
+\\
 The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
-\begin{equation}
-	\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
-\end{equation}
-\textbf{Proof of the normalization}: we aim to show that 
-\begin{align}
-		\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
-\end{align}
-We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e.
-$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
-Moreover, we introduce the space
-\begin{equation}
-	\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
-\end{equation}
-Therefore, we can rewrite the normalization condition as 
-\begin{align}
-	&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
-\end{align}
-We first observe that, using \eqref{ABS}, we have that 
-\begin{equation}
-	\Psi^{'}(N,\ldots,N)=1\co
-\end{equation}
-thus, it is enough to prove that
-\begin{align}
-	&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
-\end{align}
-We now consider the second term of the above expression.
-For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution.
-On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
-Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
-By calling $r=\ell-b$ if $b\leq \ell$ we have that
-\begin{align}
-&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
-=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
-\end{align} 
-As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
-\begin{align}
-\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
-\end{align}
-By exchanging the summations we have 
-\begin{equation}
-\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
-\end{equation}
-It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
-\begin{align}
-	1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
-\end{align}
-This is true because of the binomial theorem, indeed 
-\begin{equation}
-1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
-\end{equation}
-that implies the normalization of the state $|\Psi\rangle$. 
-\begin{flushright}
-	$\square$
-\end{flushright}
+\end{comment}
 \begin{comment}
@@
 \end{comment}
+
+\begin{comment}
 	\subsubsection{Exact steady state correlations}
-
-\begin{comment}
  introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
@@
 All in all we have that
-\end{comment}
 
@@
 }
+\end{comment}
 \begin{comment}
@@
 where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
+\begin{equation}\label{SteadyState-coeff-implicit}
+	\begin{split}
+		\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+	\end{split}
+\end{equation}
+In \eqref{SteadyState-coeff-implicit} there are two terms.
+For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
+The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$.
+If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
+\begin{remark}
+	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
+	\begin{equation}
+		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
+	\end{equation}
+As a consequence, one cha interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
+\end{remark}
+\begin{remark}
+The coefficients $\Psi(\bm{\tau})$ can also be written explicitly by replacing $\Psi^{'}(\bm{\tau})$ with formula \eqref{ABS}. They read 
 \begin{equation}
@@
 \end{equation}
-\begin{comment}
-\begin{equation}
-	\begin{split}
-		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-		\\&+
-		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
-		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
-		\\&
-		\sum_{c_{1}=0}^{1-\delta_{\eta_{1}^{b},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L}^{b},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}^{b}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}^{b}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
-	\end{split}
-\end{equation}
-\end{comment}
 where we have introduced, $\forall x\in \{1,\ldots,L\}$
@@
 	The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
+	\end{remark}
 \begin{comment}
@@
 
-	\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
 Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
@@
 		\end{comment}
-	By introducing the notation \eqref{eta-notation} and by considering 
+	Considering 
 	\begin{equation}
@@
 				\\&
-				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})
+				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
 			\end{split}
@@
 		%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-		Using \eqref{elementsABS} we have 
-		\begin{equation}
-			\begin{split}
-				\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
-			\end{split}
-		\end{equation}
+		%Using \eqref{elementsABS} we have 
+	%	\begin{equation}
+		%	\begin{split}
+		%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+	%		\end{split}
+	%	\end{equation}
 	\begin{comment}
@@
 \end{comment}
- Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{steadyStateH}. 
+ Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
+		\begin{flushright}
+			$\square$
+		\end{flushright}
+	The steady state is normalized, i.e.
+	\begin{equation}
+		\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
+	\end{equation}
+	\textbf{Proof of the normalization}: we aim to show that 
+	\begin{align}
+		\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+	\end{align}
+	We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e.
+$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
+Moreover, we introduce the space
+	\begin{equation}
+		\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
+	\end{equation}
+	Therefore, we can rewrite the normalization condition as 
+	\begin{align}
+		&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
+		+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
+	\end{align}
+	We first observe that, using \eqref{ABS}, we have that 
+	\begin{equation}
+		\Psi^{'}(N,\ldots,N)=1\co
+	\end{equation}
+	thus, it is enough to prove that
+	\begin{align}
+		&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
+		+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
+	\end{align}
+	We now consider the second term of the above expression.
+For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution.
+On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
+Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
+By calling $r=\ell-b$ if $b\leq \ell$ we have that
+	\begin{align}
+		&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
+		=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
+	\end{align} 
+	As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
+	\begin{align}
+		\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
+	\end{align}
+	By exchanging the summations we have 
+	\begin{equation}
+		\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
+	\end{equation}
+	It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
+	\begin{align}
+		1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
+	\end{align}
+	This is true because of the binomial theorem, indeed 
+	\begin{equation}
+		1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
+	\end{equation}
+	that implies the normalization of the state $|\Psi\rangle$. 
 	\begin{flushright}

### 2023-11-07 main.tex
''
^^

@@
 \mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
-	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
+	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
 \end{split}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
+	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 \begin{equation}\label{abs-probabilities}
-	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
+	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
 \end{equation}
@@
 \textbf{Proof of \eqref{abs-probabilities}}: 
- using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
-\begin{equation}
-	\begin{split}
-		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&
+From \eqref{exactCorrelations} we have 
+\begin{align}
+		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
 		\sum_{c_{1},\ldots,c_{m}=0}^{1}
-		f(L,c_{1},\ldots,c_{m})\prod_{q=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\right)\\
+		f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
 		=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-		f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
-	\end{split}
-\end{equation}
-By exchanging the summations we rewrite as 
-\begin{equation}
-	\begin{split}
-		\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-		\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\\
-		=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{s_{q}}^{t_{q}}\beta_{s_{q}}^{1-t_{q}}\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,y_{q},c_{q},\ldots,c_{m})\dt
-	\end{split}
-\end{equation}
-%The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
-%\begin{align}
-%	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}D(\tau,\hat{\bm{\xi}})\langle\tau|\Psi\rangle
-%\end{align}
-%where the dual configuration is $\hat{\bm{\xi}}=\sum_{k=1}^{m}\delta^{y_{k}}_{s_{k}}$. 
-Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities. 
+		f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+		\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+		=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\dt
+	\end{align}
+From first to second line we have used the binomial theorem and from third to fourth line we have changed the summation order.
+Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
 \begin{flushright}
@@
 	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step.
-Using duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$.
+Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$.
 However, for the sake of completeness we report it Appendix \ref{appB}.
@@
 	\begin{equation}
-		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
+		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
 	\end{equation}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt
 \end{equation}

### 2023-11-07 main.tex
check

@@
 \end{equation}
-For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
+For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} read
 \begin{equation}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 \paragraph{One-point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
-\begin{equation}
-	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})\dt
+The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
+\begin{equation}
+\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,x_{1},c_{1})\dt
 \end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}\dt
+	\langle \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
 \end{equation}
 \paragraph{Two-point correlations}
-The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
-\begin{equation}
-	\begin{split}
-		\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})\dt
+The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
+\begin{equation}
+	\begin{split}
+		 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})\dt
 	\end{split}
@@
 	\begin{split}
-		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\dt
+	 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
 	\end{split}
@@
 	\begin{split}
-		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)\dt
+		 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 \paragraph{Three-point correlations}
-The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
-\begin{equation}
-	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})\dt
+The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
+\begin{equation}
+ \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{3}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{3})\dt
 \end{equation}
@@
 \begin{align}\label{three-pts-corr}
-	\langle n_{a_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}
+ \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
 	\\&+\nonumber
-	\frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}
+	\frac{(L+1-x_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-x_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}
 	\\&+\nonumber
-	\frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}
+	\frac{(L-x_{2})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}
 	\\&+\nonumber
-	\frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}
+	\frac{(L-x_{1})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}
 	\\&+\nonumber
-	\frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}
+	\frac{(L-x_{1})(L-x_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}
 	\\&+\nonumber
-	\frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
+	\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
 \end{align}
@@
 \begin{align}
-	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\nonumber\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]\nonumber
-	\\&=
-	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt
+	&\mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]-\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
+	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
+	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber
+	\\
+	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
 \end{align}
@@
 \end{equation}
-This formula will be useful in the following. 
+Equation \eqref{ABS_1} will be useful in the following. 
 \end{remark}

### 2023-11-07 main.tex
''

@@
 In this section we aim to use duality and the matrix product ansatz (MPA) to determine the moments and correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
-As it will turn out, the commutation relations of the matrix product ansatz allowing to determine a closed formula for all correlations.
+As it will turn out, the commutation relations of the matrix product ansatz allows to determine a closed formula for all correlations.
 As a by-product, absorption probabilities can be explicitly found.%, giving a further probabilistic interpretation for the non-equilibrium steady state.
 \subsection{Matrix product ansatz for the non-equilibrium steady state}
-The matrix product ansatz has been formulated in \cite{vanicat2017exact}, here we briefly recall it.
+The matrix product ansatz for the multi-species stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.
  Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
@@
 Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler.
-As a consequence, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
+As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
 Finally, reversing the transformations we retrieve $|\Psi\rangle$.
@@
 Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
-\\
 \subsection{Exact correlations in the non-equilibrium steady state}\label{subsection-exact}
@@
  Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$.
-In each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
+In each of these points we assume that there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
 Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
@@
 \paragraph{Absorption probabilities}
-The absorption probabilities are given by  
+Knowing the non-equilibrium steady state correlations, we can read-off the absorption probabilities defined in \eqref{absProbabilitiesIntegrable}. They are given by
 \begin{equation}\label{abs-probabilities}
@@
 \begin{itemize}
-	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular diagonal boundaries respectively.
+	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular-diagonal boundaries respectively.
 Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively.
@@
 	\item In subsection \ref{subsectionSSdual}, we invert one of the similarity transformation recovering the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$ computed in the previous step (see \eqref{ABS}).
-	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step.
+	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state correlations using $|\Psi^{'}\rangle$ of the previous step.
 Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$.
-However, for the sake of completeness we report it Appendix \ref{appB}.
+However, for the sake of completeness we report $|\Psi\rangle$ in Appendix \ref{appB}.
 \end{itemize}
@@
 The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal.
-Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
+Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
 \begin{comment}
@@
 \end{comment} 
-We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
+The ground state of the Hamiltonian $H^{''}$ is given by 
 \begin{equation}\label{ResulsBasis}
@@
 We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations.
-For the sake of notation 
+For the sake of notation we denote by
 \begin{equation}
@@
 \end{equation}
-and, we can also reverse the transformation by $S^{-1}$ and get back: 
+We can also reverse the transformation by $S^{-1}$ and get back: 
 \begin{equation}\label{Xes}
@@
 \end{equation}
-with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$, see \eqref{Xtildes2b}. 
+with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$. 
 Therefore, we obtain the commutation relations for $\Xt_{a}$ 
@@
 \begin{equation}
-	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{n_{a}^{x}}\dt
+	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt
 \end{equation}
@@
 \end{align*}
-Therefore, we write the coefficients of the linear combination \eqref{toDetermineTilde} as 
+Therefore, we write
 \begin{equation}\label{resulEsteady}
@@
 Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
-Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by
+Using the exponential series we have that
 \begin{equation}
@@
 Then, equation  \eqref{ABS_intermediate} reads
-
 Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 
@@
 \subsubsection{Formula for exact correlations}\label{correlation-section}
-We aim to compute
+We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.
+Each of these sites is occupied by $a_{k}\in\{1,\ldots,N-1\}$, we aim to compute
 \begin{equation}
@@
 \end{equation}
-Therefore, we have that 
+Therefore, it follows that 
 \begin{align}
@@
 when only one type of non-empty particle is considered.
-In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
-We report the Hamiltonians and the similarity transformations.
+In this situation we retrieve the SSEP, that was already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
+We report the Hamiltonians and the similarity transformations of SEEP:
 \begin{equation}
@@
 \paragraph{Correlations of SSEP}
- In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:
+We retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:  
 \begin{equation}\label{correlations-SSEP}
@@
 \textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
-There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the $c$'s equal to $1$ denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ and such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$, i.e.
-$c_{x_{\ell_{i}}}=1$ for $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$.
+There are many values of $c$'s that give the same $q$, therefore we define $q$ labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
+These labels are defined in order to $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ are such that $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
 Therefore, we have
@@
 \end{equation}
-Varying all possible $c$'s in \eqref{exactCorrelations} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 
+Varying all possible $c$'s in \eqref{exactCorrelations} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain 
 \begin{equation}
@@
 Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
-Thus, arguing as in \eqref{remove-exponent} and using \eqref{Gamma-product} we have that
+Thus, arguing as before and using \eqref{Gamma-product} we have that
 \begin{align}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt
+	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)\dt
 \end{equation}
@@
 \begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
 \end{equation} 

### 2023-11-07 main.tex
^
^^

@@
 There are many values of $c$'s that give the same $q$, therefore we define $q$ labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
-These labels are defined in order to $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ are such that $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
+To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
 Therefore, we have
@@
 the coordinate where the particle with label $\ell_{i}$ is placed.
-We this notation we have that
+Thus, we have that
 %and we rewrite \eqref{ABS_1} as

### 2023-11-08 main.tex
''
Update main.tex

@@
 \end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The configuration $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by 
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
+Since the maximal occupancy at each site is $\nu=1$,  the configuration $\bm{n}$ introduced in Subsection \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
 \begin{equation}\label{notation-change-relation}
@@
 \end{equation}
-The state space of the process is now given in terms of $\bm{\tau}$ by
-\begin{equation}
-	\Omega=\bigtimes_{x=1}^{L}\Omega_{x}\qquad \Omega_{x}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
-\end{equation}
-In all situations where we consider the integrable chain, we will use this notation for the configuration variable.\\ 
+The state space of the process is now 
+\begin{equation}
+	\Omega=\bigotimes_{x=1}^{L}\Omega_{x}\qquad \Omega_{x}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
+\end{equation}
 The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
@@
 	\begin{split}
-		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle\dt
+		\mathcal{H}| \tau\rangle\otimes   |\tau'\rangle&=|\tau'\rangle \otimes |\tau\rangle-|\tau\rangle \otimes|\tau'\rangle\dt
 	\end{split}
@@
 \begin{equation}
-	H_{left}=\begin{pmatrix}
+	H_{\text{left}}=\begin{pmatrix}
 		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
@@
 \begin{equation}
-	\bm{\xi}=\begin{cases}
+	\begin{cases}
 		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
@@
 \begin{equation}
-	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
-\end{equation}
-Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
+	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
+	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
+\end{equation}
+For the $m$-point correlations in the non-equilibrium steady state (NESS) we have, by duality,
 %To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
@@
 \end{equation}
- namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right.
-Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
+ is the  probability that  $t_{k}$ particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$.
+Therefore, by computing these absorption probabilities we determine the non-equilibrium steady state correlations of the integrable multi-species stirring process.
 
@@
 Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
-\subsection{Exact correlations in the non-equilibrium steady state}\label{subsection-exact}
+\subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
 In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e.
@@
 \begin{equation}\label{one-pts-corr}
-	\langle \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
+	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
 \end{equation}
@@
 	\end{remark}
+[ADD ALSO ABSORPTION PROBABILITIES FOR THE ABOVE CASES???]
 %The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
@@
 	H^{''}_{left}=\begin{pmatrix}
-		-1&(\alpha_{1}-\beta_{1})\\
+		-1&\alpha_{1}-\beta_{1}\\
 		0&0
@@
 \begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
+	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)\dt
 \end{equation} 

### 2023-11-09 main.tex
^^

@@
 % \newcommand{\rouven}[1]{{ (* {\color{red}{} \small #1}*)}}
+\newtheorem{definition}{Definition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
 \newtheorem{remark}{Remark}
@@
 \newcommand{\dd}{\mathcal{D}_{u(x)}}
-\newcommand{\oad}{\mathbf{a}^{\dagger}}
+\newcommand{\oad}{\mathbf{a}^{+}}
 
@@
 \begin{equation}\label{hamiltonian}
-	H=H_{left}+H_{bulk}+H_{right}
+	H=H_{\text{left}}+H_{\text{bulk}}+H_{\text{right}}
 \end{equation}
@@
 \begin{equation}
-	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
+	H_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
 \end{equation}
@@
 \begin{equation}
-	H_{right}=\begin{pmatrix}
+	H_{\text{right}}=\begin{pmatrix}
 		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
@@
 \end{equation} 
-We define also 
-\begin{equation}\label{lambdaConditions}
-	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
-\end{equation}
+%We define also 
+%\begin{equation}\label{lambdaConditions}
+%	(\alpha_{a}-\beta_{a})=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}(\alpha_{a}-\beta_{a})=0\,.
+%\end{equation}
 Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
@@
 and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 
-the extra-site $u(x)$ connected to $x\in V$.
-
-We define the duality function of the open multi-species stirring process as
-\begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
-\end{equation}
-where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
-\begin{equation}
-\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
-\end{equation}
-The dual process is defined by its Markov generator, which reads
+the extra-site $u(x)$ connected to $x\in V$. We state the following duality result.
+\begin{theorem}[Absorbing duality]
+	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to a process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator
 	 \begin{equation}\label{DualGenerator}
@@
 \end{equation}
+The duality function is given by 
+\begin{equation}\label{dualityElements}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
+\end{equation}
+where we have introduced the reservoir densities
+\begin{equation}
+	\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
+\end{equation}
+\end{theorem}
+\begin{comment}
+We define the duality function of the open multi-species stirring process as
+\begin{equation}\label{dualityElements}
+	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
+\end{equation}
+where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
+\begin{equation}
+\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
+\end{equation}
+The dual process is defined by its Markov generator, which reads
+ \begin{equation}\label{DualGenerator}
+    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
+\end{equation}
+where 
+$\mathcal{L}_{x,y}$ is defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+\begin{equation}\label{siteDualGenerator}
+    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)\dt
+\end{equation}
 \newline
-Therefore the dual dynamics is described as follows.
+\end{comment}
+The dual dynamics is described as follows.
 On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual Markov generator gives rise to  the multi-species stirring dynamics on the graph.
@@
 In other words the extra-sites play the role of absorbing boundaries.
-\newline \newline
 \begin{remark} in the reversible situation, i.e.
@@
 reduces to finding symmetries of the generator (for the bulk duality) and group like transformations (for the ``boundary duality'').
-
 To a configuration $\bm{\xi}$ of the configuration space  \eqref{dualStateSpace} of a dual process we associate the vector
@@
 %\begin{equation}
-%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}=0
+%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{+})_{a}^{u(x)}=0
 %\end{equation}
@@
 \\&=
-\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((A^{\dagger})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
+\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
 %\\&=
@@
 \begin{equation}
-	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
+	\widetilde{H}=\widetilde{H}_{\text{left}}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{\text{right}}
 \end{equation}
@@
 \begin{equation}\label{boundary-H-dual-chain}
-	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((\mathbf{a}{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
+	\widetilde{H}_{\text{left}}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{\text{right}}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$.
-We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
+We also notice that, up the the bosonic creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
 This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
@@
 \begin{equation}\label{bulk}
-	\left[X_{a},X_{b}\right]=\lambda_{a}X_{b}-\lambda_{b}X_{a}\qquad\forall a,b=1,\ldots,N
+	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-\lambda_{b}X_{a}\qquad\forall a,b=1,\ldots,N
 \end{equation}
@@
 \begin{equation}\label{leftBoundary}
-	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N\co
+	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a})\langle V^{*}|\qquad\forall a=1,\ldots,N\co
 \end{equation}
 \begin{equation}\label{rightBoundary}
-	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-\lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N\dt
+	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-(\alpha_{a}-\beta_{a})|V\rangle\qquad\forall a=1,\ldots,N\dt
 \end{equation}
@@
 	\begin{equation}
-		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}\lambda_{a}\langle V^{*}|=0
-	\end{equation}
-	and using  \eqref{ratesConditions} and \eqref{lambdaConditions}.
+		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a})\langle V^{*}|=0
+	\end{equation}
+	and using  \eqref{ratesConditions}.
  Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
@@
 a species with label from $1$ to $N-1$.
-%This is motivated by the interest of understanding how actual particles of the chain are correlated among each others and also because in the steady state the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=1-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
+\begin{theorem}\label{thm-correlations}[Explicit non-equilibrium steady state correlations]
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$.
-In each of these points we assume that there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
-Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
+We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
+Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{NESS}$ are given by
+\begin{equation}\label{exactCorrelations}
+	\begin{split}
+		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)
+		\end{split}
+\end{equation}
+where
+\begin{equation}\label{powerCoeffSpecies}
+	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+\end{equation}
+and 
+\begin{equation}\label{powerCoeffNOspec}
+	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
+\end{equation}
+Moreover, the absorption probabilities defined in \eqref{absProbabilitiesIntegrable} are
+\begin{equation}\label{abs-probabilities}
+	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
+\end{equation}
+where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$.
+\end{theorem}
+\begin{comment}
+ Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
 \begin{equation}\label{exactCorrelations}
@@
 \end{equation}
+\end{comment}
+\begin{comment}
 where 
@@
 \end{equation}
-{\color{blue}
-	Equation \eqref{exactCorrelations} is obtained from \eqref{ABS_1}.\\
-	Deriving correlations from \eqref{ABS}
+\end{comment}
+
+	\begin{remark}
+		The non-equilibrium steady state correlations can also be written as 
 			\begin{equation}\label{exactCorrelation_1}
@@
 		\end{equation}
-	In \eqref{exactCorrelations} we have the $c_{y_{k}}$ at the exponent but we remove the product over $x$.
-	In \eqref{exactCorrelation_1} we have to keep the product over all $x$ and the "correlated coordinate" but we do not have the $c_{y}$ at the exponent. Which is better?
-}
+\end{remark}
+\begin{comment}
 \paragraph{Absorption probabilities}
@@
 \end{equation}
-where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. \\ \\
+. \\ \\
 \textbf{Proof of \eqref{abs-probabilities}}: 
 From \eqref{exactCorrelations} we have
-\begin{align}
-		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
-		\sum_{c_{1},\ldots,c_{m}=0}^{1}
-		f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
-		=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-		f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
-	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-		\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
-		=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\dt
-	\end{align}
-From first to second line we have used the binomial theorem and from third to fourth line we have changed the summation order.
-Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
+
 \begin{flushright}
@@
 \end{flushright}
+\end{comment}
 \subsubsection{Explicit examples of non-equilibrium steady state correlations}
@@
 	\begin{split}
-		 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})\dt
+		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})\dt
 	\end{split}
@@
 	\begin{split}
-	 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
+	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
 	\end{split}
@@
 	\begin{split}
-		 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
+		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 \begin{align}
-	&\mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]-\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
+	&\mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
 	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
-	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber
+	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber
 	\\
@@
 	\end{remark}
-[ADD ALSO ABSORPTION PROBABILITIES FOR THE ABOVE CASES???]
 %The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
@@
 \end{comment}
-\subsection{Proof of the exact correlations in the non-equilibrium steady state}
+\subsection{Proof of Theorem \ref{thm-correlations}}
 The proof of formula \eqref{exactCorrelations} is made in some steps:
@@
 \begin{equation}\label{hatHamiltonian}
-   H^{'}=H^{'}_{left}+H_{bulk}+H^{'}_{right}
+   H^{'}=H^{'}_{\text{left}}+H_{\text{bulk}}+H^{'}_{\text{right}}
 \end{equation}
@@
 \begin{equation}
-	H^{'}_{left}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{right}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
+	H^{'}_{\text{left}}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{\text{right}}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 	\begin{split}
-		H_{left}^{'}&=S_{1}H_{left}S_{1}^{-1}=\exp{\left(\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}
+		H_{\text{left}}^{'}&=S_{1}H_{\text{left}}S_{1}^{-1}=\exp{\left(\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}
 		\\&=
@@
 \begin{equation}
-H_{right}^{'}=S_{1}H_{right}S_{1}^{-1}=
+H_{\text{right}}^{'}=S_{1}H_{\text{right}}S_{1}^{-1}=
 % \exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=
@@
 \begin{remark}
-	The boundary Hamiltonians $H_{left}^{'}$ and $H_{right}^{'}$ relates to the transposed of  $\widetilde{H}_{left}$ and $\widetilde{H}_{right}$, i.e.
+	The boundary Hamiltonians $H_{\text{left}}^{'}$ and $H_{\text{right}}^{'}$ relates to the transposed of  $\widetilde{H}_{\text{left}}$ and $\widetilde{H}_{\text{right}}$, i.e.
 to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
-They are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp.
-$(a^{\dagger})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp.
+They are obtained replacing the  extra-site bosonic creation operators $(\mathbf{a}^{+})_{a}^{0}$  (resp.
+$(\mathbf{a}^{+})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp.
 $\beta_a$).
@@
 \begin{equation}\label{HSecond}
-	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}\co
+	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
 \end{equation}
@@
 \begin{align}\label{tri-diag-boundaryHamiltonians}
-	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
+	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
 \end{align}
@@
 	\begin{split}
-		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}
+		H_{\text{left}}^{''}&=S_{2}H_{\text{left}}^{'}S_{2}^{-1}
 % 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
@@
 % <<<<<<< HEAD
-% 			H_{right}^{''}&=S_{2}H_{right}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
+% 			H_{\text{right}}^{''}&=S_{2}H_{\text{right}}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
 % 			\\&=
 % =======
-			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
+			H_{\text{right}}^{''}=S_{2}H_{\text{right}}^{'}S_{2}^{-1}
 % 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
@@
 \begin{equation}\label{bbHamiltonian}
-    \mathbb{H}=\mathbb{B}_{1}+H_{bulk}+\mathbb{B}_{L}
+    \mathbb{H}=\mathbb{B}_{1}+H_{\text{bulk}}+\mathbb{B}_{L}
 \end{equation}
@@
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
+	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
 \end{equation}
 %\begin{equation}\label{ResulsBasis}
-%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
+%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
 %\end{equation}
@@
 \begin{equation} 
-	\left[X_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad\forall a=1,\ldots,N\co
+	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad\forall a=1,\ldots,N\co
 \end{equation}
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{N}\right]=\lambda_{a}\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}\dt
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation}\label{commLEFT}
-	\langle V^{*}|\left(\lambda_{a}\Xt_{N}-\Xt_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N-1
+	\langle V^{*}|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle V^{*}|\qquad\forall a=1,\ldots,N-1
 \end{equation}
 \begin{equation}\label{commRIGHT}
-	\Xt_{a} |V\rangle= \lambda_{a}|V\rangle\qquad\forall a=1,\ldots,N-1
+	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle\qquad\forall a=1,\ldots,N-1
 \end{equation} 
@@
 \begin{equation}\label{UsefulRelation}
-	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left(\lambda_{a}+\widetilde{X}_{a}\right)
+	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)
 \end{equation}
@@
 \begin{align}\label{usefulRelaton-many}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=%\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
-%	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
+	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=%\widetilde{X}_{a}^{n-1}\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
+%	\\&=(\alpha_{a}-\beta_{a})\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
 %	\\&=
-%	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
+%	(\alpha_{a}-\beta_{a})\widetilde{X}_{a}^{n-2}\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
 %	\\&=\ldots\\&=
-	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
+	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}
 \end{align}
@@
 \begin{align*}
-	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}\dt
+	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}(\alpha_{a}-\beta_{a})\right)^{n_{a}}\dt
 \end{align*}
@@
 \begin{equation}
-	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt
+	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt
 \end{equation}
@@
 %	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-%	|V \rangle=\langle %V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
+%	|V \rangle=\langle %V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
 %\end{equation}
@@
 	|V \rangle\nonumber&=
-	\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
+	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
 \end{align}
@@
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
+	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle +\langle V^{*}|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+\lambda_{a}(n-1)\right)|V\rangle
+	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{(\alpha_{a}-\beta_{a})}\langle V^{*}|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right)|V\rangle
 	\\&=
@@
 	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle=\Gamma(2+\sum_{x=1}^{N}\delta_{\tau_{x},N})\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
+	|V \rangle=\Gamma(2+\sum_{x=1}^{N}\delta_{\tau_{x},N})\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
 \end{equation}
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
+	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
 \end{equation}
@@
 \begin{equation}
-	\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}=\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}
+	\prod_{a=1}^{N-1}\left((\alpha_{a}-\beta_{a})\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}=\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}
 \end{equation}
@@
 \begin{equation}
-|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle\dt
+|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle\dt
 \end{equation}
@@
 \begin{split}
-\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
-&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
-&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
-&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
-% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N}),-1)\\
+\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
+&=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
+&=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
+&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+% &=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N}),-1)\\
 \end{split}
@@
 \begin{align}\label{remove-exponent}
-&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
+&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
 =&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\
@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+			\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
 		\end{split}
@@
 %	\begin{split}
-%		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
+%		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
 %	\end{split}
@@
 	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\lambda_{\tau_{x}}^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}
-	\end{equation}
-\begin{equation}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
-\end{equation}
-	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\left(\frac{\lambda_{\tau_{x}}}{\beta_{\tau_x}}\right)^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{1-\delta_{\tau_{x},N} }
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}
+	\end{equation}
+\begin{equation}
+	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
+\end{equation}
+	\begin{equation}
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\left(\frac{(\alpha_{\tau_{x}}-\beta_{\tau_{x}})}{\beta_{\tau_x}}\right)^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{1-\delta_{\tau_{x},N} }
 	\end{equation}
@@
 \end{equation}
-which action on the occupation variable of a site is 
-\begin{equation}
-  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
+which action on the occupation variable $|\sigma\rangle$ of a site is 
+\begin{equation}
+  \mathcal{S}_{2}^{-1} |\sigma\rangle= |\sigma\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
 \end{equation} 
@@
 \begin{equation}
-  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt
+  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\sigma}\rangle=\left( |\sigma_1\rangle+\delta_{N,\sigma_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\sigma_L\rangle+\delta_{N,\sigma_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt
 \end{equation} 
@@
 \begin{equation}\label{goodTP-S2}
-  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]
+  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\sigma}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\sigma_x}+\delta_{N,\sigma_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]
 \end{equation} 
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle=\sum_{\mu\in \Omega}\Psi^{''}(\bm{\mu})\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
+		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle=\sum_{\sigma\in \Omega}\Psi^{''}(\bm{\sigma})\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
 		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
@@
 \end{comment}
-For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, 
+For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, 
 We introduce 
 \begin{equation}
-	c_{x}=\delta_{\mu_{x},N}
+	c_{x}=\delta_{\sigma_{x},N}
 \end{equation}
@@
 %Therefore, we have that equation \eqref{ABS_intermediate} becomes
-%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
+%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
 Then, equation  \eqref{ABS_intermediate} reads
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
+		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
 	\end{split}
@@
 \begin{equation}\label{ABS_1}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
+	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
 \end{equation}
@@
 	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
-	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\co
-\end{align}
-where in the second line we have used the resolution of the identity and in the last line we have used \eqref{ABS_1}. 
+	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
+	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})\co
+\end{align}
+where in the second line we have used the resolution of the identity, in the last line we have used \eqref{ABS_1} and in the last equality we have used the definition of \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec}.
+Using the binomial theorem we have that 
+\begin{align}
+	&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
+	\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
+	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\dt
+\end{align}
+From third to fourth line we have changed the summation order.
+Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
 \begin{flushright}
@@
 \begin{equation}
-	H=H_{left}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{right}
+	H=H_{\text{left}}+\sum_{x=1}^{L-1}H_{x,x+1}+H_{\text{right}}
 \end{equation}
@@
 \begin{equation}
-	H_{left}=\begin{pmatrix}
+	H_{\text{left}}=\begin{pmatrix}
 		1-\alpha_{1}&\alpha_{1}\\
 		\alpha_{2}&1-\alpha_{2}
-	\end{pmatrix},\qquad H_{right}=\begin{pmatrix}
+	\end{pmatrix},\qquad H_{\text{right}}=\begin{pmatrix}
 	1-\beta_{1}&\beta_{1}\\
@@
 \begin{equation}
-	H^{'}_{left}=\begin{pmatrix}
+	H^{'}_{\text{left}}=\begin{pmatrix}
 		-1&\alpha_{1}\\
 		0&0
-	\end{pmatrix},\qquad H^{'}_{right}=\begin{pmatrix}
+	\end{pmatrix},\qquad H^{'}_{\text{right}}=\begin{pmatrix}
 	-1&\beta_{1}\\
@@
 \begin{equation}
-	H^{''}_{left}=\begin{pmatrix}
+	H^{''}_{\text{left}}=\begin{pmatrix}
 		-1&\alpha_{1}-\beta_{1}\\
 		0&0
-	\end{pmatrix},\qquad H^{''}_{right}=\begin{pmatrix}
+	\end{pmatrix},\qquad H^{''}_{\text{right}}=\begin{pmatrix}
 	-1&0\\
@@
 \begin{align}
-	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
 	=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
@@
 \begin{equation}
-	\mathcal{L}=\mathcal{L}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{right}\dt
+	\mathcal{L}=\mathcal{L}_{\text{left}}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\mathcal{L}_{\text{right}}\dt
 \end{equation} 
@@
 \begin{equation}
-	\mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\dt
+	\mathcal{L}_{\text{left}}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{\text{right}}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\dt
 \end{equation}
@@
 \begin{equation}
-	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{left}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{right}
+	\widetilde{\mathcal{L}}=\widetilde{\mathcal{L}}_{\text{left}}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}+\widetilde{\mathcal{L}}_{\text{right}}
 \end{equation} 
@@
 	\begin{split}
-		\widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{N}^{1}+\bm{\delta}_{a}^{0})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{right}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{N}^{L}+\bm{\delta}_{a}^{L+1})-f(\bm{\xi})\right)
+		\widetilde{\mathcal{L}}_{\text{left}}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{N}^{1}+\bm{\delta}_{a}^{0})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{\text{right}}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{N}^{L}+\bm{\delta}_{a}^{L+1})-f(\bm{\xi})\right)
 	\end{split}
@@
 \begin{equation}\label{thermalizedGenerator}
-	\mathcal{L}^{TH}=\mathcal{L}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{right}^{TH}
+	\mathcal{L}^{TH}=\mathcal{L}_{\text{left}}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{\text{right}}^{TH}
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
 		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
@@
 	\begin{split}
-		\mathcal{L}_{right}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},\bm{r})-f(\bm{n})\right\}\\&
+		\mathcal{L}_{\text{right}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},\bm{r})-f(\bm{n})\right\}\\&
 		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
@@
 \begin{equation}
-		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{left}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{right}^{TH}
-\end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{left}^{TH}$ and $\widetilde{\mathcal{L}}_{right}^{TH}$ are absorbing with rate $1$
+		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{\text{left}}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{\text{right}}^{TH}
+\end{equation}
+where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$
 \begin{align}
-		\widetilde{\mathcal{L}}_{left}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{right}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}
+		\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}
 	\end{align}
@@
 \end{equation}
-First, we act with $\mathcal{L}_{left}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
+First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
 \begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
 	\\&\nonumber
@@
 \begin{align}
-	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&=
@@
 \begin{equation}\label{RDGenerator}
-	\mathcal{L}^{rd}=\mathcal{L}_{right}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{right}^{rd}
+	\mathcal{L}^{rd}=\mathcal{L}_{\text{right}}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{\text{right}}^{rd}
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{left}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{\text{left}}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$. \\
-The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$. \\ \\
-\textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$. \\ \\
+\textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
 \paragraph{Action of $\mathcal{L}_{x,+1}^{rd}$ on the occupation variable}
@@
 Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action of $\mathcal{L}_{left}^{rd}$ on the occupation variable}
-Acting on $n_{d}^{1}$  with $\mathcal{L}_{left}^{rd}$ we obtain
+\paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
+Acting on $n_{d}^{1}$  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
 \begin{equation}\label{actionBoudaryRD}
 	\begin{split}
-		\mathcal{L}_{left}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
+		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
 		\\&=
@@
 while $p_{N}=1-\sum_{a=1}^{N-1}p_{a}$\\
-For the boundary generators $\mathcal{L}_{left}^{rd}$ and $\mathcal{L}_{right}^{rd}$ we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
+For the boundary generators $\mathcal{L}_{\text{left}}^{rd}$ and $\mathcal{L}_{\text{right}}^{rd}$ we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
 \subsubsection{Duality for the reaction-diffusion process}
@@
 \begin{equation}\label{DualGeneratorRD}
-	\widetilde{\mathcal{L}}_{left}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{right}^{rd}
+	\widetilde{\mathcal{L}}_{\text{left}}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}
 \end{equation}
 where 
-$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{abs-dual-boundary-chain}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
+$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{abs-dual-boundary-chain}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
 \paragraph{Proof of duality}
@@
 \begin{equation}
-	H^{rd}=H_{left}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{right}
-\end{equation}
-where $\mathcal{H}_{x,x+1}$ and $H_{left},H_{right}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
+	H^{rd}=H_{\text{left}}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{\text{right}}
+\end{equation}
+where $\mathcal{H}_{x,x+1}$ and $H_{\text{left}},H_{\text{right}}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
 \begin{equation}
@@
 \begin{equation}
-    \mathcal{L}_{left}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{right}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
+    \mathcal{L}_{\text{left}}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{\text{right}}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
 \end{equation}
@@
 \begin{split}
-        \widetilde{\mathcal{L}}_{left}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
+        \widetilde{\mathcal{L}}_{\text{left}}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
         \end{split}
@@
 	\begin{split}
-		\Psi(\bm{\tau})&=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+		\Psi(\bm{\tau})&=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
 		\\&+

### 2023-11-09 main.tex
''

@@
 the extra-site $u(x)$ connected to $x\in V$. We state the following duality result.
-\begin{theorem}[Absorbing duality]
+\begin{theorem}[Absorbing duality]\label{thm-duality}
 	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to a process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator
@@
 \end{remark}
-\subsection{Proof of duality}
+\subsection{Proof of Theorem \ref{thm-duality}}
 To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.
@@
 Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
-For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
-We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
+Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.
+%For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
+\begin{proposition}[Correlations via duality]
+Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$.
+Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
+\begin{equation}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
+\end{equation}
+where
+\begin{equation}\label{absProbabilitiesIntegrable}
+	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
+\end{equation}
+is the  probability that  $t_{k}$ particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$.
+The dual configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
 \begin{equation}
@@
 \end{equation}
+\end{proposition}
+\textbf{Proof}:
 For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} read
@@
 \end{equation}
-For the $m$-point correlations in the non-equilibrium steady state (NESS) we have, by duality,
-%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$).
-Therefore, we have the following equalities
+Therefore, by duality we have 
 \begin{equation}\label{CorrelationByABS-prob}
@@
 \end{equation}
-where
-\begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
-\end{equation}
- is the  probability that  $t_{k}$ particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$.
-Therefore, by computing these absorption probabilities we determine the non-equilibrium steady state correlations of the integrable multi-species stirring process.
+\begin{flushright}
+	$\square$
+\end{flushright}
 
@@
 a species with label from $1$ to $N-1$.
-\begin{theorem}\label{thm-correlations}[Explicit non-equilibrium steady state correlations]
+\begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$.
@@
 			\begin{split}
-				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{y_{1}},\ldots,c_{y_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{s_{k}}-\beta_{s_{k}})^{1-c_{y_{k}}}\beta_{s_{k}}^{c_{y_{k}}}\left(2+L-y_{k}-\sum_{j=k}^{m}(1-c_{y_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{y_{1},\ldots,y_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{y_{k}})\right)
+				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
 			\end{split}
@@
 \paragraph{One-point correlations}
-The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
-\begin{equation}
-\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,x_{1},c_{1})\dt
-\end{equation}
-Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
+%\begin{equation}
+%\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
+%\end{equation}
+Using \eqref{abs-probabilities} we obtain the absorption probabilities 
+\begin{equation}
+	\mathcal{P}(0,\bm{\xi})=1-\frac{(L+1-x_{1})}{(1+L)}\qquad \mathcal{P}(1,\bm{\xi})=\frac{(L+1-x_{1})}{(1+L)}
+\end{equation} 
+where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}$. Then, using \eqref{exactCorrelations}, we have
 \begin{equation}\label{one-pts-corr}
-	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
+	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
 \end{equation}
 \paragraph{Two-point correlations}
-The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads
-\begin{equation}
-	\begin{split}
-		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})\dt
-	\end{split}
-\end{equation}
-Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$.
+%\begin{equation}
+%	\begin{split}
+%		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
+%	\end{split}
+%\end{equation}
+Using \eqref{abs-probabilities} we obtain the absorption probabilities
+\begin{equation}
+	\begin{split}
+	&\mathcal{P}(0,0,\bm{\xi})=\frac{x_{1}(x_{2}-1)}{L(L+1)}\\
+	&\mathcal{P}(0,1,\bm{\xi})=\frac{x_{1}(L+1-x_{2})}{L(L+1)}
+\end{split}\quad \begin{split}
+	&\mathcal{P}(1,0,\bm{\xi})=\frac{x_{2}(L+1-x_{1})}{L(L+1)}\\
+	&\mathcal{P}(1,1,\bm{\xi})=\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}
+	\end{split}
+\end{equation}
+where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}$. 
+Then, by using \eqref{exactCorrelations} we have 
 \begin{equation}
@@
 \paragraph{Three-point correlations}
-The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
-\begin{equation}
- \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{3}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{3})\dt
-\end{equation}
-Using \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec} we obtain 
+We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
+Using \eqref{abs-probabilities} we compute the absorption probabilities
+\begin{equation}
+	\begin{split}
+	&\mathcal{P}(0,0,0,\bm{\xi})=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}\\
+	&\mathcal{P}(1,0,0,\bm{\xi})=\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
+		(x_3-2)}{L \left(L^2-1\right)}\\
+	&\mathcal{P}(0,1,0,\bm{\xi})=\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}\\
+	&\mathcal{P}(0,0,1,\bm{\xi})=\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}
+	\end{split}\quad \begin{split}
+	&\mathcal{P}(1,1,0,\bm{\xi})=\frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
+		(x_3-2)}{L \left(L^2-1\right)}\\
+	&\mathcal{P}(1,0,1,\bm{\xi})=\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
+		\left(L^2-1\right)}\\
+	&\mathcal{P}(0,1,1,\bm{\xi})=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
+	&\mathcal{P}(1,1,1,\bm{\xi})=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}
+\end{split}
+\end{equation}
+where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}+\delta_{a_{3}}^{x_{3}}$ Then, by using \eqref{exactCorrelations} we obtain 
 \begin{align}\label{three-pts-corr}

### 2023-11-09 main.tex
^^

@@
 Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present.
-As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
+As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
 This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
@@
 \begin{equation}\label{stateSpace-Chain}
-	\Omega=\bigtimes_{x=1}^{L} \Omega_{x}
+	\Omega=\bigotimes_{x=1}^{L} \Omega_{x}
 \end{equation} and its generator reads
@@
 \end{equation} 
-The bulk is 
+where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the site generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a}^{x})_{a\in \{1,\ldots,N\}}$ respectively.
+\begin{comment}
 \begin{equation}
@@
 \end{equation}
-The process is dual with respect to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space
-\begin{equation}\label{stateSpaceDUAL-Chain}	
-	\widetilde{\Omega}=N_{0}^{N}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
-\end{equation}
-whit dual generator
+\end{comment}
+By Theorem \ref{thm-duality}, the process is dual to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space where two extra-sites with unbounded maximal occupancy $\{0\}$ and $\{L+1\}$ have been added attached to the left of $\{1\}$ and to the right of $\{L+1\}$.
+%\begin{equation}\label{stateSpaceDUAL-Chain}	
+%	\widetilde{\Omega}=N_{0}^{N}\times\bigotimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
+%\end{equation}
+Thus, the dual generator reads
 \begin{equation}
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundaries are absorbing, i.e. 
+where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given from \eqref{siteDualGenerator} absorbing particles from sites $\{1\}$ and $\{L\}$ and putting them at extra-sites $\{0\}$ and $\{L+1\}$ respectively.
+The duality function reads is \eqref{dualityElements} specified on the chain.
+\begin{comment}
 \begin{equation}\label{abs-dual-boundary-chain}
@@
 \end{equation}
-where $0$ and $L+1$ are the extra-sites. The duality function reads
+where $0$ and $L+1$ are the extra-sites.
+\end{comment}
+
+\begin{comment}
+, i.e.
 \begin{equation}\label{dualityFunctionChain}
@@
 where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
+\end{comment}
 The dual process has absorbing boundaries, i.e.
@@
 This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
-Consider an arbitrary initial configuration of $(\bm{n}(t))_{t\geq 0}$ denoted by $\bm{n}$.
-For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
+We call $\mu^{NESS}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\xi}=\sum_{k=1}\delta_{a_{k}}^{x_{k}}$ with $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
 The following  equalities holds using duality relation \eqref{duality-expectation}:
@@
 	\begin{split}
-		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\mathbb{E}_{\mu^{NESS}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\&=
-		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})
-	\end{split}
-\end{equation}
-where 
+		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})
+	\end{split}
+\end{equation}
+where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ and where 
 \begin{equation}\label{Pass} 
-	\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
-\end{equation}
-are called the \textit{absorption probabilities}, i.e.
-the probabilities that $i_{a}$ particles of species $a$ are absorbed at $0$ and $|\xi_{a}|-i_{a}$ are absorbed at $L+1$ when time goes to infinity and starting from a configuration $\hat{\bm{\xi}}$.
-Here we denoted $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$.
-The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
-\begin{equation}
-	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{k=1}^{m}n_{s_{k}}^{y_{k}}}{(\nu-m+1)}\dt
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations among non-empty species of types $s_{k}\in\{1,\ldots,N-1\}$ situated at sites $y_{k}\in\{1,\ldots,L\}$ with $k\in \{1,\ldots,m\}$.
-Using \eqref{ExptationSS}, this expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
+	\mathcal{P}(i_{1},\ldots,i_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{0}+(|\xi_{a}|-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
+\end{equation}
+are the absorption probabilities for the non-integrable chain, i.e.
+the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$.
+Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x_{k}}$.
+The duality function \eqref{dualityElements} computed in the dual configurations $\bm{\xi}$ is given by 
+\begin{equation}
+	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{(\nu-m+1)}\dt
+\end{equation}
+Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
+This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
 However, these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
-\paragraph{One point correlations for the $\nu\geq 1$ case}
-We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt
-\end{equation}
-The average occupation reads
-\begin{equation}\label{OnePtsCORR}
-	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt
-	\end{split}
-\end{equation}
-To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
-This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
-\begin{equation}\label{gamblers-ruin}
-	\begin{cases}
-		\Delta_{y}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
-		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
-		\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
-	\end{cases}
-\end{equation}
-where $\Delta_{y}^{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
-\end{equation}
-\textbf{Remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-\end{equation}
-that is the same result obtained in \cite{vanicat2017exact}. 
-\\
-\\ Already for two-point correlations the computations become more involving and hard to solve.
+For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
+
 % In the following we specialize the chain to the integrable case $\nu=1$.
@@
 \begin{equation}\label{RDGenerator}
-	\mathcal{L}^{rd}=\mathcal{L}_{\text{right}}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{\text{right}}^{rd}
+	\mathcal{L}^{rd}=\mathcal{L}_{\text{right}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{\text{right}}^{rd}
 \end{equation}
@@
 for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$. \\
-The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$. \\ \\
-\textbf{Remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
-\paragraph{Action of $\mathcal{L}_{x,+1}^{rd}$ on the occupation variable}
-For arbitrary site $x\in \{1,\ldots,L\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
-\begin{equation}\label{actionGraphRD}
-	\begin{split}
-		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{q}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
-	\end{split}
-\end{equation}
-Indeed
-\begin{equation}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
-\end{equation}
-while for every $c\in \{1,\ldots,N-2\}$ we have 
-\begin{equation}
-	\begin{split}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
-		\\&=
-		\sum_{a=1}^{N-1}n_{a}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
-		\\&=
-		\nu(n_{q}^{x+1}-n_{d}^{x})
-	\end{split}
-\end{equation}
-where we call $q$ such that $g_{i}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
-Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
-Moreover
-\begin{equation}
-	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
-\end{equation}
-Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-\paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
-Acting on $n_{d}^{1}$  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
-\begin{equation}\label{actionBoudaryRD}
-	\begin{split}
-		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
-		\\&=
-		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
-		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
-		\\&=
-		\nu\sigma_{11}\rho_{d}^{0}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{0}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
-		\\&=
-		\nu \sigma_{11} (\rho_{d}^{0}-n_{d}^{1})+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}(\rho_{b}^{0}-n_{d}^{1})
-	\end{split}
-\end{equation}
-Using equation \eqref{actionGraphRD} we have that $\forall x\in \{2,\ldots,L-1\}$ and $\forall d\in\{1,\ldots,N-1\}$
+The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$.
+\begin{remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+\end{remark}
+\paragraph{Action on the occupation variable}
+We only report the final result.
+The details are written in Appendix \ref{appendix-RD}.
+For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
 \begin{equation}\label{DifferenceEquation}
-	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{c}^{x}-n_{\alpha}^{x})
-\end{equation}
-where with the symbol $\Delta_{L}$ we denote the discrete Laplacian operator on the chain, i.e. $\Delta_{L}n_{a}^{x}=n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$.
-Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have that, $\forall d\in \{1,\ldots,N-1\}$ 
+	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})\co
+\end{equation}
+where $\Delta_{L}n_{x}^{d}= n_{x+1}^{d}+n_{x-1}^{d}-2n_{x}^{d}$. \\For $x=1$ and for all $d\in \{1,\ldots,N-1\}$ we have 
 \begin{equation}\label{actionBDLine}
@@
 where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
-These average occupations evolve according to the Master equation
+These average occupations evolve according to the master equation
 \begin{equation}
@@
 This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries.
-For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
+%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
 Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
@@
 that simplifies to
-\end{comment}
+
 \begin{equation}
@@
 For the boundary generators $\mathcal{L}_{\text{left}}^{rd}$ and $\mathcal{L}_{\text{right}}^{rd}$ we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
+\end{comment}
 \subsubsection{Duality for the reaction-diffusion process}
@@
 where 
-$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{abs-dual-boundary-chain}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
+$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
 \paragraph{Proof of duality}
@@
 \end{equation}
-We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
-\begin{align}
-	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
-\end{align}
-but it is enough of showing 
+We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$,
+%\begin{align}
+%	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
+%\end{align}
+%but it is enough of showing 
 \begin{align}
@@
 %\paragraph{Duality for $H_{x,x+1}^{c}$}
- We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x+1})$.
+ We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\exp{(E^{x})}\exp{(E^{x+1})}$ with $E$ defined in \eqref{EquationEx}.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
 \begin{align*}
-	&\left[\left(\sum_{d=1}^{N-1}E_{dN}^{x}\otimes\sum_{k=1}^{N-1}E_{kN}^{x+1}\right), \sum_{a,b=1}^{N}\left(E_{g_{c}(b)a}^{x}\otimes E_{g_{c}(a)b}^{x+1} -E_{aa}^{x}\otimes E_{bb}^{x+1}\right)\right]
+	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{d,\ell=1}^{N}\left(E_{g_{c}(\ell)d}^{x}\otimes E_{g_{c}(d)\ell}^{x+1} -E_{dd}^{x}\otimes E_{\ell\ell}^{x+1}\right)\right]
 	\\=&
-	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right.
+%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right.
 \\ \otimes&\left.
 \left((E_{kb}^{x+1}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
-	\\=&
-	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
-	\\=&
-	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{aN}^{x}-E_{g_{c}(b)N}^{x}\right)\otimes \left(E_{bN}^{x+1}-E_{g_{c}(a)N}^{x+1}\right)\right\}
+%	\\=&
+%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
+%	\\=&
+	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{g_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{g_{c}(\ell)N}^{x+1}\right)\right\}
 	\\=&0
@@
 %\paragraph{Duality for $H_{x,x+1}^{m}$} 
-Concerning the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x+1})$, the proof is similar and gives
-\begin{equation}
-	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{i=1}^{N}\sum_{a,l=1}^{N}\left(E_{la}^{x}\otimes \mathbbm{1}^{x+1}-E_{aa}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0
+Concerning the commutator between $\mathcal{H}_{x,x+1}^{m}$ the proof is similar and gives
+\begin{equation}
+	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{d,\ell=1}^{N}\left(E_{\ell a}^{x}\otimes \mathbbm{1}^{x+1}-E_{dd}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0
 \end{equation}
@@
 	\end{flushright}
+\section{One point correlations for the $\nu\geq 1$ case}\label{appendix-1pts-general}
+We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt
+\end{equation}
+The average occupation reads
+\begin{equation}\label{OnePtsCORR}
+	\begin{split}
+		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt
+	\end{split}
+\end{equation}
+To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
+This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
+\begin{equation}\label{gamblers-ruin}
+	\begin{cases}
+		\Delta_{y}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
+		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
+		\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
+	\end{cases}
+\end{equation}
+where $\Delta_{y}^{L}$ is the discrete Laplace operator on the chain of length $L$.
+The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+\end{equation}
+\begin{remark}: In case $|\alpha|=|\beta|=\nu=1$ (when the chain is integrable) we have 
+\begin{equation}
+	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
+\end{equation}
+that is the same result obtained in \cite{vanicat2017exact}. 
+\end{remark}
+Already for two-point correlations the computations become more involving and hard to solve.
+\section{Action on the occupation variable of $\mathcal{L}^{rd}$}\label{appendix-RD}
+\paragraph{Action of $\mathcal{L}_{x,+1}^{rd}$ on the occupation variable}
+For all $x\in \{1,\ldots,L-1\}$ and for all $d\in \{1,\ldots,N-1\}$ we have
+\begin{equation}\label{actionGraphRD}
+	\begin{split}
+		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{q}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
+	\end{split}
+\end{equation}
+Indeed
+\begin{equation}
+	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
+\end{equation}
+while for every $c\in \{1,\ldots,N-2\}$ we have 
+\begin{equation}
+	\begin{split}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
+		\\&=
+		\sum_{a=1}^{N-1}n_{a}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
+		\\&=
+		\nu(n_{q}^{x+1}-n_{d}^{x})
+	\end{split}
+\end{equation}
+where we call $q$ such that $g_{i}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
+Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
+Moreover
+\begin{equation}
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
+\end{equation}
+Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
+\paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
+Acting on $n_{d}^{1}$  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
+\begin{equation}\label{actionBoudaryRD}
+	\begin{split}
+		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
+		\\&=
+		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
+		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\\&=
+		\nu\sigma_{11}\rho_{d}^{0}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{0}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\\&=
+		\nu \sigma_{11} (\rho_{d}^{0}-n_{d}^{1})+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}(\rho_{b}^{0}-n_{d}^{1})
+	\end{split}
+\end{equation}
+Using equation \eqref{actionGraphRD} we have \eqref{DifferenceEquation}. Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have \eqref{actionBDLine}.
 \begin{comment}

### 2023-11-09 main.tex
S5-shorter

@@
 \end{equation}
- Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
+ Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is the product over the sites of multinomial distributions we have
 \begin{equation}
@@
 \end{equation}
-Moreover, it holds that 
-\begin{equation}
-\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
-\end{equation}
+%Moreover, it holds that 
+%\begin{equation}
+%\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
+%\end{equation}
 Therefore 
@@
 \end{equation}
-\paragraph{Proof of thermalized duality}
-The proof of the duality consists in showing
-\begin{align}
-	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
-	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
-\end{align}
-Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
-To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function.
-For the sake of notation, we introduce
-\begin{equation}
-	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
-\end{equation}
-First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
-\begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
-	\\&\nonumber
-	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
-	\\&
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
-\end{align}
-We consider the first addend in the curly bracket of the previous equation.
-We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$; we have
-\begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{k}^{1}-\xi_{k}^{1}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\nonumber\\=&
-	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
-	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber
-	\\=&
-	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
-\end{align}
-where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.
-We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ 
-\begin{equation}\label{pezzo2}
-	\begin{split}
-	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
-	\end{split}
-\end{equation}
-where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
-\begin{align}
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
-	\\&=
-	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
-\end{align}
-The proof is similar for $\widetilde{\mathcal{L}}_{y}^{TH}$. 
-\begin{flushright}
-	$\square$
-\end{flushright}
+The proof duality result for the thermalized multi-species stirring process is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.
 \subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
@@
 The details are written in Appendix \ref{appendix-RD}.
-For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads
+For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ reads
 \begin{equation}\label{DifferenceEquation}
-	\mathcal{L}^{rd}n_{d}^{x}=\nu\sigma_{11}\Delta_{L}n_{d}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}\Delta_{L}n_{c}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})\co
-\end{equation}
-where $\Delta_{L}n_{x}^{d}= n_{x+1}^{d}+n_{x-1}^{d}-2n_{x}^{d}$. \\For $x=1$ and for all $d\in \{1,\ldots,N-1\}$ we have 
+	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{a}^{x})\co
+\end{equation}
+where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{x}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 
 \begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{d}^{1}=\sigma_{11}\nu \left(\rho_{d}^{0}-2n_{d}^{1}+n_{d}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq d}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{d}^{1}\right)
-\end{equation}
-On the occupation variable $n_{d}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $d$ at site $x$ as
-\begin{equation}
-	\rho_{d}(x,t)=\mathbb{E}_{\mu}\left[n_{d}^{x}(t)\right]
+	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)
+\end{equation}
+On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $d$ at site $x$ as
+\begin{equation}
+	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
 \end{equation}
@@
 \begin{equation}
-	\frac{d \rho_{d}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{d}^{x}(t)\right]
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
 \end{equation} 
@@
 
-\subsubsection{Reversible measure for the reaction-diffusion process} 
+\subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
 The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
@@
 Already for two-point correlations the computations become more involving and hard to solve.
+\section{Proof of duality of thermalized multi-species stirring}\label{appendix-dualityThermalized}
+The proof of the duality consists in showing
+\begin{align}
+	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
+	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
+\end{align}
+Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
+To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function.
+For the sake of notation, we introduce
+\begin{equation}
+	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+\end{equation}
+First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
+\begin{align}\label{ProvaBordoTH}
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\\&\nonumber
+	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\\&
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+\end{align}
+We consider the first addend in the curly bracket of the previous equation.
+We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$; we have
+\begin{align}\label{pezzo1}
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{k}^{1}-\xi_{k}^{1}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\nonumber\\=&
+	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
+	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber
+	\\=&
+	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
+\end{align}
+where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.
+We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ 
+\begin{equation}\label{pezzo2}
+	\begin{split}
+		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
+	\end{split}
+\end{equation}
+where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
+\begin{align}
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\\&=
+	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+\end{align}
+The proof is similar for $\widetilde{\mathcal{L}}_{y}^{TH}$. 
+\begin{flushright}
+	$\square$
+\end{flushright}
 \section{Action on the occupation variable of $\mathcal{L}^{rd}$}\label{appendix-RD}
-\paragraph{Action of $\mathcal{L}_{x,+1}^{rd}$ on the occupation variable}
+\paragraph{Action of $\mathcal{L}_{x,x+1}^{rd}$ on the occupation variable}
 For all $x\in \{1,\ldots,L-1\}$ and for all $d\in \{1,\ldots,N-1\}$ we have

### 2023-11-10 main.tex
''
nonInt-chain

@@
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&
+%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&
 \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
@@
 	\begin{split}
-&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
-\end{split}
+&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
+%=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\
+=\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
+\end{split}
+\end{equation}
+since
+\begin{equation}
+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt
 \end{equation}
@@
 We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
-Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{NESS}$ are given by
+Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{\text{NESS}}$ are given by
 \begin{equation}\label{exactCorrelations}
@@
 \paragraph{One-point correlations}
-We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
+We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
 %\begin{equation}
-%\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
+%\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
 %\end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
+	 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
 \end{equation}
 \paragraph{Two-point correlations}
-We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$.
+We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$.
 %\begin{equation}
 %	\begin{split}
-%		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
+%		 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
 %	\end{split}
@@
 	\begin{split}
-	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
+	 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
 	\end{split}
@@
 	\begin{split}
-		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
+		 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 \paragraph{Three-point correlations}
-We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
+We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
 Using \eqref{abs-probabilities} we compute the absorption probabilities
@@
 \begin{align}\label{three-pts-corr}
- \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
+ \mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
 	\\&+\nonumber
@@
 \begin{align}
-	&\mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
-	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
-	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber
+	&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
+	-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
+	-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber
 	\\
@@
 In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types.
-Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present.
+Each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
+Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
 As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
-This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}.
-\\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
+This property allows to characterize the steady state non-equilibrium distribution (that it is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
+The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
 \begin{equation}\label{stateSpace-Chain}
@@
 \end{comment} 
-
 \begin{comment}
@@
 This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu^{NESS}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$.
-For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\xi}=\sum_{k=1}\delta_{a_{k}}^{x_{k}}$ with $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$.
-The following  equalities holds using duality relation \eqref{duality-expectation}:
+We call $\mu^{\text{NESS}}$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+For every $m\in\{1,\ldots,L\}$ we consider  $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$ and we introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ meaning that
+\begin{equation}
+	\begin{cases}
+		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=b_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
+		\xi_{a}^{x}=0\qquad &\text{otherwise}
+	\end{cases}\dt
+\end{equation}
+The duality function \eqref{dualityElements} computed in this dual configurations is 
+\begin{equation}
+	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{C(\nu,m)}\dt
+\end{equation}
+where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
+Therefore, up to this constant, $\mathbb{E}_{\mu^{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
+The following equalities hold using duality relation \eqref{duality-expectation}:
 \begin{equation}\label{ExptationSS}
 	\begin{split}
-		\mathbb{E}_{\mu^{NESS}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\frac{\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\&=
@@
 \end{equation}
-where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ and where 
+where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
 \begin{equation}\label{Pass} 
-	\mathcal{P}(i_{1},\ldots,i_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{0}+(|\xi_{a}|-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$.
-Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x_{k}}$.
-The duality function \eqref{dualityElements} computed in the dual configurations $\bm{\xi}$ is given by 
-\begin{equation}
-	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{(\nu-m+1)}\dt
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
+Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
  This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
-However, these absorption probabilities fulfil some difference equations that are not easy to solve.
 For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
+However, these absorption probabilities for higher point correlations fulfil some difference equations that are not easy to solve.
 
@@
 	\end{flushright}
-\section{One point correlations for the $\nu\geq 1$ case}\label{appendix-1pts-general}
-We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt
+\section{One point correlations for $\nu\geq 1$}\label{appendix-1pts-general}
+We take $m=1$ and we fix a site $x\in\{1,\ldots,L\}$ and a species $a\in \{1,\ldots,N-1\}$. We consider the dual configuration $\bm{\xi}=\delta_{a}^{x}$, then 
+\begin{equation}
+	\nu D(\eta,\delta_{a}^{x})=n_{a}^{x}\dt
 \end{equation}
@@
 	\begin{split}
-		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt
-	\end{split}
-\end{equation}
-To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$.
+			\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
+	\end{split}
+\end{equation}
+To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$.
 This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
@@
 	\begin{cases}
-		\Delta_{y}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
-		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
-		\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}
+		\Delta^{L}\mathcal{P}(1,\delta_{a}^{x})=0\\
+		\mathcal{P}(1,\delta_{a}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{a}^{2})\frac{1}{1+|\alpha|}\\
+		\mathcal{P}(1,\delta_{a}^{L})=\mathcal{P}(1,\delta_{a}^{L-1})\frac{1}{1+|\beta|}
 	\end{cases}
 \end{equation}
-where $\Delta_{y}^{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain
-\begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(L|\beta|-|\beta|x+1)+\beta_{s}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+where $\Delta^{L}$ is the discrete Laplace operator on the chain of length $L$.
+The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{a}^{x})=1-\mathcal{P}(0,\delta_{a}^{x})$ we obtain
+\begin{equation}
+	\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
 \end{equation}
@@
 \begin{equation}
-	\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-\end{equation}
-that is the same result obtained in \cite{vanicat2017exact}. 
+		\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
+\end{equation}
+that is the same result obtained in \eqref{one-pts-corr}.  
 \end{remark}

### 2023-11-10 main.tex
^'

@@
 In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using to integrability.  
-The aim of this section is studying some property of the process when integrability is lost.
-We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
-We provide the following extensions:
+The aim is studying some property of the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
 \begin{enumerate}
@@
 As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
-This property allows to characterize the steady state non-equilibrium distribution (that it is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
+This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
 The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
@@
 	\begin{cases}
-		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=b_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
+		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
 		\xi_{a}^{x}=0\qquad &\text{otherwise}
@@
 \subsection{Instantaneous thermalization}\label{Subsection-Thermalized}
-In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}).
+In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality,KMP}).
 The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles.
-The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\bm{\epsilon}=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\bm{\epsilon}$.
+The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\epsilon=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\epsilon$.
 \subsubsection{The thermalization measure}
-We introduce the reversible measure \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond
-\begin{equation}
-	\begin{split}
-	\nu_{TH}(\bm{r}|\bm{\epsilon}):&=\mathbb{P}\left(n^{x}=\bm{r}|\eta^{x}+n^{x+1}=\bm{\epsilon}\right)
+We introduce the reversible measure \eqref{reversibleMeasure} conditioned on the conservation of the particles on that bond
+\begin{equation}
+	\begin{split}
+	\nu_{TH}(r|\epsilon):&=\mathbb{P}\left(n^{x}=r|n^{x}+n^{x+1}=\epsilon\right)
 	\\&
@@
 	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)
-	\end{split}
-\end{equation}
-where
+	\end{split}\dt
+\end{equation}
+Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{1,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
@@
 	\begin{split}
-\nu_{TH}(\bm{r}|\bm{\epsilon})&=\frac{\mathbb{P}\left(\left\{n^{x}=\bm{r}\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\bm{\epsilon}\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}=\frac{\mathbb{P}\left(n^{x}=\bm{r}\right)\,\mathbb{P}\left(n^{x+1}=\bm{\epsilon}-\bm{r}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}
+\nu_{TH}(r|\epsilon)&=\frac{\mathbb{P}\left(\left\{n^{x}=r\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\epsilon\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}=\frac{\mathbb{P}\left(n^{x}=r\right)\,\mathbb{P}\left(n^{x+1}=\epsilon-r\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}
 	\end{split}
@@
 	\begin{split}
-	\nu_{TH}(\bm{r}|\bm{\epsilon})=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
+	\nu_{TH}(r|\epsilon)=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
 	\end{split}
@@
 \begin{equation}
-	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}
-\end{equation}
-provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
+	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}\dt
+\end{equation}
+%provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
 \subsubsection{Thermalized multi-species stirring process}
@@
 	\\&
-	\left\{f(n^{1},\ldots,n^{x-1},\bm{r},n^{x}+n^{x+1}-\bm{r},n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
+	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
 	\end{split}
@@
 	\begin{split}
-		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(r,n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
 		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
@@
 	\end{equation}
-and 
-\begin{equation}
-	\begin{split}
-		\mathcal{L}_{\text{right}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},\bm{r})-f(\bm{n})\right\}\\&
-		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
-	\end{split}
-\end{equation}
-In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n^{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters.
+and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
+%\begin{equation}
+%	\begin{split}
+%		\mathcal{L}_{\text{right}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},r)-f(\bm{n})\right\}\\&
+%		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
+%	\end{split}
+%\end{equation}
+In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters.
 \subsubsection{The dual thermalized process}
-The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{stateSpaceDUAL-Chain}. Its generator reads
+The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$
+where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$:
 \begin{align}
@@
 \end{align}
-i.e. they remove all dual particles at site $1$ (and $L$) and put these particles in the extra-site $0$ (and $L+1$) with rate 1. 
+This means that they remove all dual particles at site $1$ (and $L$) and put these particles in the extra-site $0$ (and $L+1$) with rate 1.
 The duality function is the same as the original process, i.e.
@@
 For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
-In view of what have been proved in the previous section of this work, some questions arise naturally:
+In view of what have been proved in the previous sections of this work, some questions arise naturally:
 \begin{enumerate}
 		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-			\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
-	\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process?
+			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process using the same $gl(N)$ Lie-algebraic structure?
 \end{enumerate}
@@
 \end{equation}
-The left boundary generator reads
-\begin{equation}
-	\mathcal{L}_{\text{left}}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
-\end{equation}
+The left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ is given by \eqref{siteGenerator} at site $1$,
+%reads
+%\begin{equation}
+%	\mathcal{L}_{\text{left}}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
+%\end{equation}
 where the $\alpha$'s parameters are defined in function of the given boundary condition of the difference-differential system:
@@
 \end{equation}
-As a consequence, we can define the boundary values in terms of the reservoir parameters as
+As a consequence, from the above conditions we can define the boundary values in terms of the reservoir parameters as
 \begin{equation}
@@
 The details are written in Appendix \ref{appendix-RD}.
-For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ reads
+For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{a}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ reads
 \begin{equation}\label{DifferenceEquation}
@@
 \end{equation}
-where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{x}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 
+where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 
 \begin{equation}\label{actionBDLine}
@@
 \end{equation}
-On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $d$ at site $x$ as
+On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as
 \begin{equation}
@@
 \end{equation} 
-Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation\eqref{NSpeciesRD} where the discrete Laplacians of all species are coupled and linear reaction terms are present that we aimed for.
+Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}.
 For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question we addressed to in the beginning of this subsection.
-
+This answers the first question we addressed to at the beginning of this subsection.
 \subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
-The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
-	\Lambda_{rev}=\bigtimes_{x=1}^{L}\Lambda_{rev}^{x}
+The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneous product measure \begin{equation}\label{reversibleMeasureRD}
+	\Lambda_{rev}=\bigotimes_{x=1}^{L}\Lambda_{rev}^{x}
 \end{equation}
@@
 \end{equation}
-This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries.
+This can be proved by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries.
 %For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
@@
 In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ still takes values in the enlarged state space $\widetilde{\Omega}$ defined in \eqref{stateSpaceDUAL-Chain}
+The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space $\widetilde{\Omega}$ defined in \eqref{dualStateSpace}
 %\begin{equation}
@@
 %and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
-The duality function is still given by
+The duality function is given by
 \begin{equation}
@@
 where 
-$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.
+$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the specific choice of the reservoirs parameters \eqref{boundaryParamRD}.
+This answer to the second question addressed at the beginning of this Subsection.
 \paragraph{Proof of duality}
@@
 \begin{equation}
-	H^{rd}=H_{\text{left}}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{\text{right}}
-\end{equation}
-where $\mathcal{H}_{x,x+1}$ and $H_{\text{left}},H_{\text{right}}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
+	H^{rd}=H_{\text{left}}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{\text{right}}\dt
+\end{equation}
+Here, $\mathcal{H}_{x,x+1}$ and $H_{\text{left}},H_{\text{right}}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
 \begin{equation}
@@
 \end{align}
-Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x+1})}$ as a symmetry.
-\\
-%\paragraph{Duality for $H_{x,x+1}^{c}$}
- We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\exp{(E^{x})}\exp{(E^{x+1})}$ with $E$ defined in \eqref{EquationEx}.
+Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ commute with $\exp{(E^{x})}\exp{(E^{x+1})}$, where $E$ is defined in \eqref{EquationEx}.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{g_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{g_{c}(\ell)N}^{x+1}\right)\right\}
-	\\=&0
+	\\=&0\dt
 \end{align*}
-where in the last equality we used the fact that map $g_{c}(\cdot)$ is surjective. \\
+In the last equality we used the fact that map $g_{c}(\cdot)$ is surjective. \\
 %\paragraph{Duality for $H_{x,x+1}^{m}$} 
@@
 	\begin{cases}
-		\Delta^{L}\mathcal{P}(1,\delta_{a}^{x})=0\\
+		\Delta_{L}\mathcal{P}(1,\delta_{a}^{x})=0\\
 		\mathcal{P}(1,\delta_{a}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{a}^{2})\frac{1}{1+|\alpha|}\\
@@
 \end{equation}
-where $\Delta^{L}$ is the discrete Laplace operator on the chain of length $L$.
+where $\Delta_{L}$ is the discrete Laplace operator on the chain of length $L$.
 The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{a}^{x})=1-\mathcal{P}(0,\delta_{a}^{x})$ we obtain
@@
 We consider the first addend in the curly bracket of the previous equation.
-We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$; we have
+We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$.
+As a result, we have
 \begin{align}\label{pezzo1}
@@
 where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.
-We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ 
+We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain
 \begin{equation}\label{pezzo2}
@@
 \end{equation}
-where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
+where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that
 \begin{align}
@@
 \end{align}
-The proof is similar for $\widetilde{\mathcal{L}}_{y}^{TH}$. 
+The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 
 \begin{flushright}

### 2023-11-10 main.tex
''

@@
 \end{equation}
-On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as
+On the occupation variable $n_{a}^{L}$ the action is similar. \\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as
 \begin{equation}

### 2023-11-10 main.tex
Update main.tex

@@
 
-\vspace{.5cm}
 \noindent
 \begin{remark}
+\label{hole}
 In the following we will often consider type $N$ as a distinguished type
@@
 %\end{figure}
-\subsection{Reversible measures (equilibrium)}
+\subsection{Reversible measures in the equilibrium set-up}
 For a particular choice of the reservoir parameters one has an $N$-parameter family of reversible measures. More precisely
@@
 \end{equation}
-with marginals $\mu_{rev}^{x}$ given by 
+with marginals $\mu_{\text{rev}}^{x}$ given by 
 \begin{equation}
@@
 
-\subsection{Lie algebraic description}
+\subsection{Lie algebraic description of the process}
 
@@
 \section{Duality}\label{sectionDuality}
+In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
+can be studied by means of a dual process. After recalling the definition of duality between two
+Markov processes in Section \ref{def-duality}, we formulate duality  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
+The duality result is important since it brings in several simplifications, the main one being that the
+dual process has absorbing sites. Therefore, as shown in Proposition \ref{prop-absorbing}, the study of the non-equilibrium steady state for  the multispecies stirring process with open boundary
+is reduced to the study of the absorption probabilities of dual particles.
+
 \subsection{Definition}
+\label{def-duality}
 Consider two Markov processes, $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$.
@@
 \end{remark}
+%
+%
 \subsection{Proof of Theorem \ref{thm-duality}}
+\label{proof-th-duality}
 To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.
@@
 \end{equation}
-{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
+%{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
 we obtain 
@@
 \end{equation}
-since
-\begin{equation}
-\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt
-\end{equation}
+%since
+%\begin{equation}
+%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt
+%\end{equation}
 %This is a consequence of 
@@
 \subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
-Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}.
+Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
 We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
-Now we assume the hard-core exclusion rule, i.e.
-$\nu=1$.
+We also recall the notation for the occupation variable which is called $\bm{\tau}=(\tau_1,\ldots,\tau_L)$ with $\tau_x\in\{1,\ldots,N\}$.
 The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$.
-Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted.
+The duality result stated in Subsection \ref{statementDualitySubsection} can be adapted.
 The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively.
@@
 We also notice that, up the the bosonic creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
-This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
+This simplification will be crucial in Section \ref{sectionIntegrabiliy}.\\
 
@@
 %\\
-Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities.
+Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles.
 Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.
@@
 \begin{proposition}[Correlations via duality]
+\label{prop-absorbing}
 Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$.
@@
 \begin{equation}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
-\end{equation}
-is the  probability that  $t_{k}$ particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$.
-The dual configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
-\begin{equation}
+	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
+\end{equation}
+is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$.
+The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
+\begin{equation}
+\label{xsi-init}
 	\begin{cases}
@@
 \textbf{Proof}:
-For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} read
+For any $\bm{\tau}\in \Omega$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
 \begin{equation}
@@
 \end{equation}
-Therefore, by duality we have 
+Therefore, by duality and ergodicity we have 
 \begin{equation}\label{CorrelationByABS-prob}
@@
 \mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
-	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
+	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})\dt
 \end{split}
@@
 \section{Exact steady state and correlations for the integrable chain}\label{sectionIntegrabiliy}
-In this section we aim to use duality and the matrix product ansatz (MPA) to determine the moments and correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
-As it will turn out, the commutation relations of the matrix product ansatz allows to determine a closed formula for all correlations.
-As a by-product, absorption probabilities can be explicitly found.%, giving a further probabilistic interpretation for the non-equilibrium steady state.
+In this section we combine duality and the matrix product ansatz (MPA) to determine the correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
+As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption correlations and thus (using Proposition \ref{prop-absorbing}) for the correlations.
 \subsection{Matrix product ansatz for the non-equilibrium steady state}
@@
 This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial configuration. 
-We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution. This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
+We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution (non-equilibrium steady state).
+This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e.
+it solves
 \begin{equation}\label{definition-SteadyStateH}
@@
 \begin{equation}\label{bulk}
-	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-\lambda_{b}X_{a}\qquad\forall a,b=1,\ldots,N
+	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}\qquad\forall a,b=1,\ldots,N
 \end{equation}
@@
  Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
-The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of exact correlations are in general involving. 
- We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the use of commutators in the
- computation. The idea is summarized as follows. We define a sequence of similarity transformation such that 
+The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of  correlations are in general involved.
+
+ In the next Section \ref{subsection-exact} we will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the algebra of operators.
+The idea is summarized in the following scheme.
+ We define a sequence of similarity transformation such that 
  \begin{equation}
@@
 Finally, reversing the transformations we retrieve $|\Psi\rangle$.
-
  The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
@@
 \subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
-In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e.
-a species with label from $1$ to $N-1$.
+In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain.
 \begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}
-Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$.
-We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$.
-Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{\text{NESS}}$ are given by
+Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
+and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{\text{NESS}}$ are given by 
 \begin{equation}\label{exactCorrelations}
-	\begin{split}
-		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)
-		\end{split}
+\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
 \end{equation}
 where
+\begin{equation}\label{abs-probabilities}
+	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})
+\end{equation}
+with
+\begin{equation}\label{powerCoeffNOspec}
+	f(c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
+\end{equation}
+and
 \begin{equation}\label{powerCoeffSpecies}
-	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-and 
-\begin{equation}\label{powerCoeffNOspec}
-	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
-\end{equation}
-Moreover, the absorption probabilities defined in \eqref{absProbabilitiesIntegrable} are
-\begin{equation}\label{abs-probabilities}
-	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
-\end{equation}
-where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$.
+	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}
+\end{equation}
 \end{theorem}
@@
 \end{comment}
-
+{\color{blue}
 	\begin{remark}
@@
 \end{remark}
+}
 \begin{comment}
@@
 \end{comment}
-\subsubsection{Explicit examples of non-equilibrium steady state correlations}
-We give examples  of correlations for up to three points applying formula \eqref{exactCorrelations}.
+\subsubsection{Examples of non-equilibrium steady state correlations}
+We give examples  of correlations for $m=1,2,3$ applying formula \eqref{exactCorrelations}.
 \paragraph{One-point correlations}
@@
 \begin{equation}
-	\mathcal{P}(0,\bm{\xi})=1-\frac{(L+1-x_{1})}{(1+L)}\qquad \mathcal{P}(1,\bm{\xi})=\frac{(L+1-x_{1})}{(1+L)}
+	\mathcal{P}(0)=1-\frac{(L+1-x_{1})}{(1+L)}\qquad \mathcal{P}(1)=\frac{(L+1-x_{1})}{(1+L)}
 \end{equation} 

### 2023-11-10 main.tex
Update main.tex

@@
 \end{comment}
-{\color{blue}
-	\begin{remark}
-		The non-equilibrium steady state correlations can also be written as 
-			\begin{equation}\label{exactCorrelation_1}
-			\begin{split}
-				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
-			\end{split}
-		\end{equation}
-\end{remark}
-}
+%{\color{blue}
+%	\begin{remark}
+%		The non-equilibrium steady state correlations can also be written as 
+%			\begin{equation}\label{exactCorrelation_1}
+%			\begin{split}
+%				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
+%			\end{split}
+%		\end{equation}
+%\end{remark}
+%}
 \begin{comment}
@@
 \begin{equation}
-	\mathcal{P}(0)=1-\frac{(L+1-x_{1})}{(1+L)}\qquad \mathcal{P}(1)=\frac{(L+1-x_{1})}{(1+L)}
-\end{equation} 
-where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}$. Then, using \eqref{exactCorrelations}, we have
+	\mathcal{P}_{x_1}(0)=1-\frac{(L+1-x_{1})}{(L+1)}\qquad \mathcal{P}_{x_1}(1)=\frac{(L+1-x_{1})}{(L+1)}
+\end{equation} 
+where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $\{0\}$. Then, using \eqref{exactCorrelations}, we have
 \begin{equation}\label{one-pts-corr}
@@
 \end{align}
-\begin{remark} the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
+\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
 	\end{remark}
@@
 \subsection{Proof of Theorem \ref{thm-correlations}}
-The proof of formula \eqref{exactCorrelations} is made in some steps:
+The proof of formula \eqref{exactCorrelations} is split into the following steps:
 \begin{itemize}
-	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular-diagonal boundaries respectively.
+	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformations $S_1$ and  $S_2$. 
+	 The first turns the Hamiltonian $H$ into $H^{'}= S_{1} H S_{1}^{-1} $ with boundary terms in a triangular form;
+	 the second  turns the Hamiltonian $H'$ into $H^{''} = S_{2}H' S_{2}^{-1}$ having the left boundary in a triangular form and the right boundary is diagonal.
 	Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 
@@
 The explicit expression for $|\Psi^{''}\rangle$ is determined (see \eqref{ResulsBasis}).
-	\item In subsection \ref{subsectionSSdual}, we invert one of the similarity transformation recovering the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$ computed in the previous step (see \eqref{ABS}).
-	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state correlations using $|\Psi^{'}\rangle$ of the previous step.
-Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$.
-However, for the sake of completeness we report $|\Psi\rangle$ in Appendix \ref{appB}.
+	\item In subsection \ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
+	\item In Subsection \ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$.
+By exploiting a binomial formula we rewrite the correlations in terms
+	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities.
+For completeness, we also provide the expression of the steady state $|\Psi\rangle$ in Appendix \ref{appB}.
 \end{itemize}
@@
 \end{equation}
-that is composed by a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
+that is a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$. 
 Observe that $\mathcal{S}_{1}^{x}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
@@
 \end{equation}
-that is related with the duality matrix by 
+that is related with the bulk duality matrix by 
 \begin{equation}
@@
 \end{equation}
- The transformation $S_{1}$ is invertible. We introduce 
+ As the transformation $S_{1}$ is invertible,  we can introduce 
 \begin{equation}\label{hatHamiltonian}
@@
  \end{equation}
-that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
-Therefore, by taking the product over the chain we obtain 
+which is a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
 \begin{equation}\label{S2-Whole}
@@
 where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
-\\
 \begin{comment}
@@
 \end{flushright}
-\begin{remark} By change the summation indices form $c\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by the by the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{remark} By change the summation indices form $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
 \begin{equation}\label{ABS_1}

### 2023-11-11 main.tex
^^
Proof Psi' explicit

@@
 \end{comment}
- By considering a fixed $\langle\bm{\tau}|$, and by using \eqref{goodTP-S2} we obtain 
+ By considering a fixed $\bm{\tau}\in \Omega$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 
 \begin{equation}\label{ABS_intermediate}
 	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle=\sum_{\sigma\in \Omega}\Psi^{''}(\bm{\sigma})\prod_{x=1}^L\left[ \delta_{\tau_x,\mu_x}+\delta_{N,\mu_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation}
-where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega}\frac{1}{(1+L)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
+	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
+	\end{split}
+\end{equation}
+%where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
 \begin{comment}
@@
 \end{comment}
-For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, 
+%For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, \\ \\ 
 We introduce 
 \begin{equation}
-	c_{x}=\delta_{\sigma_{x},N}
-\end{equation}
-thus, by using equation \eqref{ResulsBasis}, we have
-\begin{equation}
-	\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\mu_{x}}^{(1-c_{x})}\left(1+\sum_{j=x}^{L}c_{j}\right)
-\end{equation}
+	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
+\end{equation}
+To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain
+\begin{align}
+	\Psi^{'}(\bm{\tau})%=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
+	=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
+\end{align}
+%Consider the factor $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}$ in the above equation.
+When $\sigma_{x}\neq N$ (then $c_{x}=0$) and $\tau_{x}\neq N$, it becomes $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$.
+On the other hand, when $\sigma_{x}=N$ (then $c_{x}=1$)  and $\tau_{x}\neq N$, then it becomes $1$.
+Finally, if $\sigma_{x}=N$ and $\tau_{x}=N$ it becomes $0$.
+Therefore, we can replace it by $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}$.
+It follows that
+We observe that, for all $x\in \{1,\ldots,L\}$,
+\begin{equation}
+	\begin{split}
+	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\\
+	=&\begin{cases}
+		(\alpha_{\tau_{x}}-\beta_{\tau_{x}})+\beta_{\tau_{x}}\qquad &\text{if}\quad \tau_{x}\neq N\\
+		1\qquad &\text{if}\quad \tau_{x}= N
+	\end{cases}
+\end{split}
+\end{equation}
+Thus, it follows that 
+\begin{equation}
+	\begin{split}
+	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
+	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
+	\end{split}
+\end{equation}
+Therefore we have that
+\begin{align}
+\Psi^{'}(\bm{\tau})%=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+%=&\frac{1}{(1+L)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+\end{align}
+%thus, by using equation \eqref{ResulsBasis}, we have
+%\begin{equation}
+	%\Psi^{''}(\bm{\sigma})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\sigma_{x}}^{(1-c_{x})}\left(1+\sum_{j=x}^{L}c_{j}\right)
+%\end{equation}
 \begin{comment}
@@
 Then, equation  \eqref{ABS_intermediate} reads
-Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 
+Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally obtain
 \begin{equation}\label{elementsABS}
@@
 %Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
-Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
+Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
 \begin{flushright}

### 2023-11-12 main.tex
''
^^

@@
 \label{reversibleMeasure}
-\mu_{rev}=\bigotimes_{x\in V}\mu_{rev}^{x}
+\mu_{\text{rev}}=\bigotimes_{x\in V}\mu_{\text{rev}}^{x}
 \end{equation}
@@
 \begin{equation}
- \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\,.
+ \mu^{x}_{\text{rev}}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\,.
 \end{equation}
@@
 \begin{equation}
-\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}\,.
+\mu_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}\,.
 \end{equation}
@@
 \begin{remark} in the reversible situation, i.e.
-when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{rev} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
+when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{\text{rev}} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
 \begin{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 	\begin{split}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
-	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})\dt
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
+	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
 \end{split}
@@
 \begin{equation}
-	|\Psi\rangle=\frac{1}{Z_{L}}\langle V^{*}|\begin{pmatrix}
+	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}
 		X_{1}\\
@@
 \begin{equation}
-	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle\dt
+	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle\dt
 \end{equation}
@@
 \begin{equation}\label{bulk}
-	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}\qquad\forall a,b=1,\ldots,N
+	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}%\qquad\forall a,b=1,\ldots,N
 \end{equation}
@@
 \begin{equation}\label{leftBoundary}
-	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a})\langle V^{*}|\qquad\forall a=1,\ldots,N\co
+	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N\co
 \end{equation}
 \begin{equation}\label{rightBoundary}
-	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-(\alpha_{a}-\beta_{a})|V\rangle\qquad\forall a=1,\ldots,N\dt
-\end{equation}
-Without loss of generality, we further assume that $\langle V^{*}|V\rangle=1$. 
+	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-(\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N\dt
+\end{equation}
+Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
 \begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
 	\begin{equation}
-		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a})\langle V^{*}|=0
+		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a})\langle W|=0
 	\end{equation}
@@
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
-and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{\text{NESS}}$ are given by 
+and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu_{\text{NESS}}$ are given by 
 \begin{equation}\label{exactCorrelations}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \begin{equation}\label{abs-probabilities}
-	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})
+	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})
 \end{equation}
@@
 \begin{equation}\label{exactCorrelations}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
 	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
@@
 %			\begin{split}
-%				\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
+%				\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
 %			\end{split}
@@
 \paragraph{One-point correlations}
-We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
+We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
 %\begin{equation}
-%\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
+%\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
 %\end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-	 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt
+	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
 \end{equation}
 \paragraph{Two-point correlations}
-We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$.
+We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$.
 %\begin{equation}
 %	\begin{split}
-%		 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
+%		 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
 %	\end{split}
@@
 	\begin{split}
-	&\mathcal{P}(0,0,\bm{\xi})=\frac{x_{1}(x_{2}-1)}{L(L+1)}\\
-	&\mathcal{P}(0,1,\bm{\xi})=\frac{x_{1}(L+1-x_{2})}{L(L+1)}
+	&\mathcal{P}_{x_{1},x_{2}}(0,0)=\frac{x_{1}(x_{2}-1)}{L(L+1)}\\
+	&\mathcal{P}_{x_{1},x_{2}}(0,1)=\frac{x_{1}(L+1-x_{2})}{L(L+1)}
 \end{split}\quad \begin{split}
-	&\mathcal{P}(1,0,\bm{\xi})=\frac{x_{2}(L+1-x_{1})}{L(L+1)}\\
-	&\mathcal{P}(1,1,\bm{\xi})=\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}
-	\end{split}
-\end{equation}
-where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}$. 
+	&\mathcal{P}_{x_{1},x_{2}}(1,0)=\frac{x_{2}(L+1-x_{1})}{L(L+1)}\\
+	&\mathcal{P}_{x_{1},x_{2}}(1,1)=\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}
+	\end{split}
+\end{equation}
+%where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}$. 
 Then, by using \eqref{exactCorrelations} we have 
@@
 \begin{split}
-	 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
-	\end{split}
-\end{equation}
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]=&\frac{x_{1}(x_{2}-1)}{L(L+1)}\beta_{a_{1}}\beta_{a_{2}}+\frac{x_{1}(L+1-x_{2})}{L(L+1)}\beta_{a_{1}}\alpha_{a_{2}}\\
+	+&\frac{x_{2}(L+1-x_{1})}{L(L+1)}\alpha_{a_{1}}\beta_{a_{2}}+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}\alpha_{a_{1}}\alpha_{a_{2}}
+\end{split}
+\end{equation}
+%\begin{equation}
+%	\begin{split}
+%	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
+%	\end{split}
+%\end{equation}
 Therefore, we compute the second cumulant, i.e. the two-point connected correlation
@@
 	\begin{split}
-		 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
+		 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 \paragraph{Three-point correlations}
-We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
+We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
 Using \eqref{abs-probabilities} we compute the absorption probabilities
@@
 	\begin{split}
-	&\mathcal{P}(0,0,0,\bm{\xi})=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}\\
-	&\mathcal{P}(1,0,0,\bm{\xi})=\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,0,0)=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}\\
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,0,0)=\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
 		(x_3-2)}{L \left(L^2-1\right)}\\
-	&\mathcal{P}(0,1,0,\bm{\xi})=\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}\\
-	&\mathcal{P}(0,0,1,\bm{\xi})=\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,0)=\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}\\
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,0,1)=\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}
 	\end{split}\quad \begin{split}
-	&\mathcal{P}(1,1,0,\bm{\xi})=\frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,1,0)=\frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
 		(x_3-2)}{L \left(L^2-1\right)}\\
-	&\mathcal{P}(1,0,1,\bm{\xi})=\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,0,1)=\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
 		\left(L^2-1\right)}\\
-	&\mathcal{P}(0,1,1,\bm{\xi})=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
-	&\mathcal{P}(1,1,1,\bm{\xi})=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,1)=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,1,1)=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}
 \end{split}
@@
 \begin{align}\label{three-pts-corr}
- \mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
+ \mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
 	\\&+\nonumber
@@
 \begin{align}
-	&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
-	-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
-	-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber
+	&\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
+	-&\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
+	-&\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber
 	\\
@@
      X_{N}
-	\end{pmatrix}\quad \forall a\in \{1,\ldots,N-1\}\dt
+	\end{pmatrix}%\quad \forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 	%\end{pmatrix}
-	\qquad \forall a=1,\ldots N-1
+	%\qquad \forall a=1,\ldots N-1
 \end{equation}
@@
 		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
-	\end{pmatrix}\qquad\forall a\in \{1,\ldots,N-1\}\dt
+	\end{pmatrix}%\qquad\forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation} 
-	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad\forall a=1,\ldots,N\co
+	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}%\qquad\forall a=1,\ldots,N\co
 \end{equation}
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad \forall a\in \{1,\ldots,N-1\}\dt
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad %\forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation}\label{commLEFT}
-	\langle V^{*}|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle V^{*}|\qquad\forall a=1,\ldots,N-1
+	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
 \end{equation}
 \begin{equation}\label{commRIGHT}
-	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle\qquad\forall a=1,\ldots,N-1
+	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N-1
 \end{equation} 
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 	|V \rangle \,|\bm{\tau}\rangle
@@
 \begin{align}
-		Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V\rangle\dt
+		Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V\rangle\dt
 \end{align}
@@
 \end{comment}
-To determine the eigenvector \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+To determine the eigenvector \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 |V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
@@
 %\begin{equation}
-%	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
+%	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
 %	|V \rangle=\langle %V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
@@
 \begin{align}
-	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 	|V \rangle\nonumber&=
-	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
-\end{align}
-We now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  
+	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle W|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
+\end{align}
+We now need to compute $\langle W|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle +\langle V^{*}|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
+	\langle W|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{(\alpha_{a}-\beta_{a})}\langle V^{*}|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right)|V\rangle
+	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{(\alpha_{a}-\beta_{a})}\langle W|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right)|V\rangle
 	\\&=
-	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
+	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\left(2+n-1\right)\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
+	\left(2+n-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
-	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
+	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
 \end{align*}
@@
 \begin{align}
-		\langle V^{*}|\widetilde{X}_{N}^{n}|V\rangle=\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
-\end{align}
-with $	\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=1$. 
+		\langle W|\widetilde{X}_{N}^{n}|V\rangle=\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
+\end{align}
+with $	\langle W|\widetilde{X}_{N}^{0}|V\rangle=1$. 
 Therefore, we obtain 
 \begin{align*}
-	\langle V^{*}|\widetilde{X}_{N}^{n}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
-	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\frac{\Gamma(2+n-1)}{\Gamma(2+n-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=
+	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle W|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle W|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
+	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\frac{\Gamma(2+n-1)}{\Gamma(2+n-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle W|\widetilde{X}_{N}^{0}|V\rangle=
 	\Gamma(2+n)
@@
 \begin{equation}
-	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 	|V \rangle=\Gamma(2+\sum_{x=1}^{N}\delta_{\tau_{x},N})\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
@@
 \begin{align*}
-	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle=
+	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V|\rangle=
 	\Gamma(2+L)\dt
@@
 \begin{equation}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
 \end{equation}
@@
 \begin{align}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
 	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
@@
 \begin{align}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
 	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
@@
 	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
-	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
+	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 \begin{align}
-	&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
+	&\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
 	\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 \begin{equation}\label{correlations-SSEP}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
 \end{equation} 
@@
 \begin{equation}\label{psiII-SSEP}
-	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
+	|\Psi^{''}\rangle=\sum_{q=0}^{L}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}(\alpha_{1}-\beta_{1})^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
 \end{equation}
@@
 	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
-	=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
+	=(\alpha_{1}-\beta_{1})_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
 \end{align}
@@
 \begin{equation}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
 \end{equation}
@@
 \begin{equation}\label{shorter-chain}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
 \end{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
 \end{equation}
@@
 This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu^{\text{NESS}}$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+We call $\mu_{\text{NESS}}$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$.
 For every $m\in\{1,\ldots,L\}$ we consider  $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$ and we introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ meaning that
@@
 where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
-Therefore, up to this constant, $\mathbb{E}_{\mu^{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
+Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
 The following equalities hold using duality relation \eqref{duality-expectation}:
@@
 	\begin{split}
-		\frac{\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\&=
@@
 The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneous product measure \begin{equation}\label{reversibleMeasureRD}
-	\Lambda_{rev}=\bigotimes_{x=1}^{L}\Lambda_{rev}^{x}
+	\Lambda_{\text{rev}}=\bigotimes_{x=1}^{L}\Lambda_{\text{rev}}^{x}
 \end{equation}
@@
 \end{equation}
-This measure has marginals $\Lambda_{rev}^{x}$ given by 
-\begin{equation}
-	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
+This measure has marginals $\Lambda_{\text{rev}}^{x}$ given by 
+\begin{equation}
+	\Lambda^{x}_{\text{rev}}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
 \end{equation}
@@
 \begin{equation}
-	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
+	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
 \end{equation}
@@
 		\\&
-	\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+	\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\eta_{x}}-\beta_{\eta_{x}})^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
 	\end{split}
@@
 	\begin{split}
-			\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
 	\end{split}
@@
 \begin{equation}
-	\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
 \end{equation}
@@
 \begin{equation}
-		\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
+		\mathbb{E}_{\mu_{\text{NESS}}}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
 \end{equation}

### 2023-11-13 main.tex
''
fixed

@@
 with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-Since the maximal occupancy at each site is $\nu=1$,  the configuration $\bm{n}$ introduced in Subsection \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
+Since the maximal occupancy at each site is $\nu=1$,  the configuration $\bm{n}$ introduced in Section \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
 \begin{equation}\label{notation-change-relation}
@@
 \subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
-Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
+Here we consider the chain defined in Section \ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
 We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
@@
 The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$.
-The duality result stated in Subsection \ref{statementDualitySubsection} can be adapted.
+The duality result stated in Section \ref{statementDualitySubsection} can be adapted.
 The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively.
@@
 \section{Exact steady state and correlations for the integrable chain}\label{sectionIntegrabiliy}
-In this section we combine duality and the matrix product ansatz (MPA) to determine the correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}.
+In this section we combine duality and the matrix product ansatz (MPA) to determine the correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Section \ref{integrableChain-duality}.
 As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption correlations and thus (using Proposition \ref{prop-absorbing}) for the correlations.
@@
 \begin{equation}\label{powerCoeffNOspec}
-	f(c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
+	f(c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
 \end{equation}
@@
 \begin{equation}\label{powerCoeffNOspec}
-	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
+	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
 \end{equation}
@@
 %			\begin{split}
-%				\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(1+L)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
+%				\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(L+1)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
 %			\end{split}
@@
 \begin{equation}\label{one-pts-corr}
-	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
+	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
 \end{equation}
@@
 	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,1)=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
-	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,1,1)=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}
-\end{split}
-\end{equation}
-where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}+\delta_{a_{3}}^{x_{3}}$ Then, by using \eqref{exactCorrelations} we obtain 
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,1,1)=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}
+\end{split}
+\end{equation}
+%where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}+\delta_{a_{3}}^{x_{3}}$ 
+Then, by using \eqref{exactCorrelations} we obtain 
+\begin{align}
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}&\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
+	(x_3-2)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\
++\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}&\beta_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}&\beta_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
++ \frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
+	(x_3-2)}{L \left(L^2-1\right)}& \alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
+	\left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
++\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}&\alpha_{a_{1}}\alpha_{a_{2}}\alpha_{a_{3}}
+\end{align}
+\begin{comment}
 \begin{align}\label{three-pts-corr}
@@
 \end{align}
+\end{comment}
 Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
@@
 \end{align}
-\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
+\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Section 4.3 of \cite{vanicat2017exact}.
 	\end{remark}
@@
 \begin{itemize}
-	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformations $S_1$ and  $S_2$. 
+	\item In Section \ref{subsectionSTransf}, we introduce two similarity transformations $S_1$ and  $S_2$. 
 	 The first turns the Hamiltonian $H$ into $H^{'}= S_{1} H S_{1}^{-1} $ with boundary terms in a triangular form;
@@
 	Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 
-	\item In Subsection \ref{subsectionSSHsec} we apply the MPA to $H^{''}$.
+	\item In Section \ref{subsectionSSHsec} we apply the MPA to $H^{''}$.
 Here the commutation relations defining the matrix algebra are simpler.
@@
 	\item In subsection \ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
-	\item In Subsection \ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$.
+	\item In Section \ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$.
 By exploiting a binomial formula we rewrite the correlations in terms
@@
 \end{equation}
-The bulk part of the Hamiltonian is left unchanged while the boundaries are given by 
+The bulk part of the Hamiltonian is left unchanged (because it is written using the coproduct of the second Casimir, see equation \eqref{hamiltonianCasimir}) while the boundaries are given by 
 \begin{equation}
@@
 \end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Section \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
 \begin{equation}
@@
 	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V|\rangle=
-	\Gamma(2+L)\dt
+	\Gamma(L+2)\dt
 \end{align*}
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
+	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
 \end{equation}
@@
 \begin{equation}
-	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\dt
+	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(L+2)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\dt
 \end{equation}
@@
 \begin{align}\label{remove-exponent}
-&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
-=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\
-=&\frac{\Gamma(2)}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x}^{L}\delta_{\tau_{j},x})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})}\nonumber\\
-=&\frac{1}{(1+L)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
+=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\
+=&\frac{\Gamma(2)}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x}^{L}\delta_{\tau_{j},x})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
 \end{align}
@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+			\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
 		\end{split}
@@
 	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}
+		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}
 	\end{equation}
@@
 	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\left(\frac{(\alpha_{\tau_{x}}-\beta_{\tau_{x}})}{\beta_{\tau_x}}\right)^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{1-\delta_{\tau_{x},N} }
+		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\left(\frac{(\alpha_{\tau_{x}}-\beta_{\tau_{x}})}{\beta_{\tau_x}}\right)^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{1-\delta_{\tau_{x},N} }
 	\end{equation}
@@
 \begin{equation}
-  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\sigma}\rangle=\left( |\sigma_1\rangle+\delta_{N,\sigma_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\sigma_L\rangle+\delta_{N,\sigma_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt
+ S_{2}^{-1} |\bm{\sigma}\rangle=\left( |\sigma_1\rangle+\delta_{N,\sigma_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\sigma_L\rangle+\delta_{N,\sigma_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt
 \end{equation} 
@@
 \begin{equation}\label{goodTP-S2}
-  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\sigma}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\sigma_x}+\delta_{N,\sigma_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]
+  \langle \bm{\tau}|S_{2}^{-1} |\bm{\sigma}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\sigma_x}+\delta_{N,\sigma_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]
 \end{equation} 
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega}\frac{1}{(1+L)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
 	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
@@
 \begin{align}
-	\Psi^{'}(\bm{\tau})%=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
-	=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
+	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
+	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
 \end{align}
@@
 \begin{align}
-\Psi^{'}(\bm{\tau})%=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(1+L)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-%=&\frac{1}{(1+L)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+%=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
 \end{align}
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
+		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
 	\end{split}
@@
 \begin{equation}\label{ABS_1}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
+	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(L+2-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
 \end{equation}
@@
 	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
-	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
+	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})\co
+	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(y_{k},c_{k},\ldots,c_{m})\co
 \end{align}
@@
 	\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
+	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
 	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
-	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)\dt
+	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt
 \end{align}
@@
 \begin{equation}\label{Gamma-product}
-	\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
+	\frac{\Gamma(L+2-\sum_{k=1}^{m}c_{k})}{\Gamma(L+2)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
 \end{equation}
@@
 \begin{equation}
-	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(2+L-\sum_{k=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
+	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(L+2-\sum_{k=1}^{m}c_{k})}{\Gamma(L+2)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
 \end{equation}
@@
 \begin{comment}
-\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}.
+\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Section \ref{subsectionSSHsec}.
 If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
@@
 \begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
+	\frac{\Gamma(L+2-q)}{\Gamma(L+2)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
 \end{equation}
@@
 \begin{equation}
- \Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
+ \Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
 \end{equation}
@@
 \begin{equation}
-	\Psi(\tau_{1},\ldots,\tau_{m})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
+	\Psi(\tau_{1},\ldots,\tau_{m})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(L+2)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
 \end{equation}
@@
 These probability are hard to find in this partial exclusion situation, however correlation can be formally written.
-Subsection \ref{Subsection-ss-nonI}.
+Section \ref{Subsection-ss-nonI}.
 	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-Subsection \ref{Subsection-Thermalized}.
+Section \ref{Subsection-Thermalized}.
 	\item \textit{Reaction-diffusion process}: a further dynamics is added.
@@
 Duality for the boundary driven process is also proved.
-Subsection \ref{Subsection-RD}
+Section \ref{Subsection-RD}
 \end{enumerate}
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
-In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
+In this subsection we specialize the results of Section \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
 Each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
@@
 		\\&=
-		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})
-	\end{split}
-\end{equation}
-where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
+		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})
+	\end{split}
+\end{equation}
+where we recall that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
 \begin{equation}\label{Pass} 
-	\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
+	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
 \end{equation}
@@
 	\begin{split}
-		g_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
-		k&\to g_{c}(k)
+		h_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
+		k&\to h_{c}(k)
 	\end{split}
@@
 \begin{equation}
-	g_{c}(k)=\begin{cases}
+	h_{c}(k)=\begin{cases}
 		k+c \quad &\text{if}\quad k+c< N \\
@@
 \end{equation}
-Observe that $g_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
+Observe that $h_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
 Moreover,
@@
 %For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
-\begin{comment}
-\begin{equation}
-	\begin{split}
-		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
+Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
+\begin{comment}
+\begin{equation}
+	\begin{split}
+		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{h_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{h_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{h_{c}(b)}^{n_{h_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{h_{c}(a)}^{n_{h_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
 		\\
-		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
+		=&(n_{h_{c}(b)}^{x}+1)(n_{h_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{h_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{h_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
 		\\&
-		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}+1}
+		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{h_{c}(b)}^{n_{h_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{h_{c}(a)}^{n_{h_{c}(a)}^{x+1}+1}
 	\end{split}
@@
 \begin{equation}
-	p_{a}p_{b}=p_{g_{c}(a)}p_{g_{c}(b)}
+	p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
 \end{equation}
@@
 $\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the specific choice of the reservoirs parameters \eqref{boundaryParamRD}.
-This answer to the second question addressed at the beginning of this Subsection.
+This answer to the second question addressed at the beginning of this Section.
 \paragraph{Proof of duality}
-We only need to prove duality for the bulk generator, since the boundary generators are the same as in Subsection \ref{Subsection-ss-nonI}. 
+We only need to prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
 In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
@@
 \begin{equation}
-	\mathcal{H}_{x,x+1}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}\otimes E_{g_{c}(b)a}-E_{aa}\otimes E_{bb}\right)
+	\mathcal{H}_{x,x+1}^{c}=\sum_{a,b=0}^{N}\left(E_{h_{c}(a)b}\otimes E_{h_{c}(b)a}-E_{aa}\otimes E_{bb}\right)
 \end{equation}
@@
 \begin{align*}
-	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{d,\ell=1}^{N}\left(E_{g_{c}(\ell)d}^{x}\otimes E_{g_{c}(d)\ell}^{x+1} -E_{dd}^{x}\otimes E_{\ell\ell}^{x+1}\right)\right]
+	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{d,\ell=1}^{N}\left(E_{h_{c}(\ell)d}^{x}\otimes E_{h_{c}(d)\ell}^{x+1} -E_{dd}^{x}\otimes E_{\ell\ell}^{x+1}\right)\right]
 	\\=&
-%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{g_{c}(b)N}-E_{g_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right.
+%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{h_{c}(b)N}-E_{h_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right.
 \\ \otimes&\left.
-\left((E_{kb}^{x+1}\delta_{g_{c}(a)N}-E_{g_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
+\left((E_{kb}^{x+1}\delta_{h_{c}(a)N}-E_{h_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
 %	\\=&
-%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{g_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{g_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
+%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{h_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{h_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
 %	\\=&
-	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{g_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{g_{c}(\ell)N}^{x+1}\right)\right\}
+	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{h_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{h_{c}(\ell)N}^{x+1}\right)\right\}
 	\\=&0\dt
 \end{align*}
-In the last equality we used the fact that map $g_{c}(\cdot)$ is surjective. \\
+In the last equality we used the fact that map $h_{c}(\cdot)$ is surjective. \\
 %\paragraph{Duality for $H_{x,x+1}^{m}$} 
@@
 	\begin{split}
-		\Psi(\bm{\tau})&=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+		\Psi(\bm{\tau})&=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
 		\\&+
@@
 		\\&
-	\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\eta_{x}}-\beta_{\eta_{x}})^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+	\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\eta_{x}}-\beta_{\eta_{x}})^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
 	\end{split}
@@
 				\\&
-				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
 				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
@@
 \begin{equation}
-	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)(1-\delta_{\mu_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)(1-\delta_{\mu_{L},N})|N\rangle\right)
+S_{1}^{-1}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)(1-\delta_{\mu_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)(1-\delta_{\mu_{L},N})|N\rangle\right)
 \end{equation}
@@
 \begin{equation}\label{Tensor-S1}
-	\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
+	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
 \end{equation}
@@
 			\begin{split}
-				\Psi(\bm{\tau}) &=\langle\bm{\tau}|\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
+				\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
 				\\&
@@
 		%	\begin{split}
-		%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+		%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
 	%		\end{split}
@@
 				\begin{split}
-					&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
+					&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
 					\\&  
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
 		\\&=
@@
 where we call $q$ such that $g_{i}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
-Let us observe that, by the definition of the map $g_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
+Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
 Moreover

### 2023-11-14 main.tex
Steady State
''

@@
 \section{Exact steady state of $H$}\label{appB}
-
-The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
-\begin{equation}
-	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
-\end{equation}
-where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
+\begin{proposition}[Non-equilibrium steady state]
+The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
+\begin{equation}
+	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
+\end{equation}
+where for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$
 \begin{equation}\label{SteadyState-coeff-implicit}
 	\begin{split}
+		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+	\end{split}
+\end{equation}
+where the last expectation is taken with respect to the $\mu^{\text{NESS}}$ of the process $\bm{\sigma}$ and is given in \eqref{exactCorrelations}.
+\end{proposition} %Therefore, 
+%\begin{equation}
+%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+%\end{equation} are computed using \eqref{exactCorrelations}. \\ \\
+\begin{comment}
+\begin{equation}\label{SteadyState-coeff-implicit}
+	\begin{split}
 		\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
@@
 \end{equation}
-In \eqref{SteadyState-coeff-implicit} there are two terms.
+\end{comment}
+%In \eqref{SteadyState-coeff-implicit} there are two terms.
 For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
@@
 \end{remark}
+\begin{comment}
 \begin{remark}
@@
 	\end{remark}
+\end{comment}
 \begin{comment}
@@
 \begin{equation}
-S_{1}^{-1}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)(1-\delta_{\mu_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)(1-\delta_{\mu_{L},N})|N\rangle\right)
+S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
 \end{equation}
@@
 \begin{equation}\label{Tensor-S1}
-	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
+	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
 \end{equation}
@@
 	\begin{equation}
-		|\Psi^{'}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{'}(\bm{\mu})|\bm{\mu}\rangle
+		|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle
 	\end{equation} we obtain  
-		\begin{equation}
-			\begin{split}
-				\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
-				\\&
-				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-			\end{split}
-		\end{equation}
+\begin{align}
+	\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
+	=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
+	=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+\end{align}
+In the last equality we exploited the fact that considering any $\tau_{x}\in \{1,\ldots,N\}$ and $i_{x}\in \{1,\ldots,N-1\}$, and considering a configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$ such that
+\begin{equation}
+	\begin{cases}
+		\sigma_{x}=i_{x}\qquad &\text{if}\quad x\in \{q_{1},\ldots,q_{b}\}\\
+		\sigma_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
+	\end{cases}
+\end{equation}
+we have that 
+\begin{equation}
+	 \Psi^{'}(\bm{\sigma})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+\end{equation}
+as showed in Section \ref{correlation-section}. 
+	%	\begin{equation}
+	%		\begin{split}
+	%			\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
+	%			\\&
+	%			+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+	%		\end{split}
+	%	\end{equation}
 		%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
@@
 		\end{flushright}
+	\begin{remark}[Proof of \eqref{SteadyState-coeff-implicit} using the conservation of probability]
+		Equation \eqref{SteadyState-coeff-implicit} can be proved also using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
+\begin{align}
+			\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
+			=&\sum_{\bm{\sigma}\in \Omega}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\bm{\sigma}|\Psi\rangle\nonumber\\
+			=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
+			%=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
+\end{align}
+Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, one find \eqref{SteadyState-coeff-implicit}.
+\begin{comment}
+where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
+\begin{equation}
+	\begin{cases}
+	\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
+	\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
+	\end{cases}
+\end{equation}
+Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
+\begin{equation}
+\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
+\end{equation}
+Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
+\begin{equation}
+\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+\end{equation}
+\end{comment}
+	\end{remark}
+	\begin{proposition}[Normalization of $|\Psi\rangle$]
 	The steady state is normalized, i.e.
@@
 	\end{equation}
-	\textbf{Proof of the normalization}: we aim to show that 
+\end{proposition}
+	\textbf{Proof}: we aim to show that 
 	\begin{align}

### 2023-11-14 main.tex
^^

@@
 \end{flushright}
+\subsection{Explicit steady state of $H$}\label{appB}
+In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}.
+This formula is follows from the ground state $|\Psi^{'}\rangle$found in \eqref{ABS_1}.
+\begin{proposition}[Non-equilibrium steady state]
+	The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
+	\begin{equation}
+		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
+	\end{equation}
+	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega$,
+	\begin{equation}\label{SteadyState-coeff-implicit}
+		\begin{split}
+			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\dots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+		\end{split}
+	\end{equation}
+	where 
+	\begin{equation}
+		\begin{split}
+			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
+			\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})
+			\end{split}
+		\end{equation}
+	%\begin{equation}
+	%	\begin{split}
+	%	&\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}+Q(1)}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}+Q(L)}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\\
+	%	&\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{1-c_{q_{k}}}\beta_{i_{q_{k}}}^{c_{q_{k}}}\right)\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\right)
+%	\end{split}
+%	\end{equation}
+	with
+	\begin{equation}
+		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
+	\end{equation}
+and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 
+%	\begin{equation}
+%	Q(x)=1-\sum_{k=1}^{b}\delta_{x,q_{k}}
+%\end{equation}
+%	Moreover, $\Psi(\bm{\tau})$ are interpreted as the probabilities in the steady state of having a configuration $\bm{\tau}$, i.e.
+%	\begin{equation}
+%%	\end{equation}
+\end{proposition} %Therefore, 
+%\begin{equation}
+%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+%\end{equation} are computed using \eqref{exactCorrelations}. \\ \\
+\begin{comment}
+	\begin{equation}\label{SteadyState-coeff-implicit}
+		\begin{split}
+			\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+		\end{split}
+	\end{equation}
+\end{comment}
+%In \eqref{SteadyState-coeff-implicit} there are two terms.
+For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
+The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$.
+If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
+\begin{remark}
+	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
+	\begin{equation}
+		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\dt
+	\end{equation}
+%where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
+	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
+\end{remark}
+\begin{comment}
+	\begin{remark}
+		The coefficients $\Psi(\bm{\tau})$ can also be written explicitly by replacing $\Psi^{'}(\bm{\tau})$ with formula \eqref{ABS}. They read 
+		\begin{equation}
+			\begin{split}
+				\Psi(\bm{\tau})&=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+				\\&+
+				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
+				\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
+				\\&
+				\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\eta_{x}}-\beta_{\eta_{x}})^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+			\end{split}
+		\end{equation}
+		where we have introduced, $\forall x\in \{1,\ldots,L\}$
+		\begin{equation}\label{eta-notation}
+			\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
+				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
+				i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
+			\end{cases}%\qquad \theta_{x}=\begin{cases}
+				%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+				%	1 \qquad &\text{otherwise}
+				%\end{cases}
+			\end{equation}
+			The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
+		\end{remark}
+	\end{comment}
+	\begin{comment}
+		{\color{blue}
+			\begin{equation}\label{steadyStateH-coeff}
+				\begin{split}
+					\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+					\\&+
+					\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
+					\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
+					\\&
+					\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
+					\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
+					\\ &
+					\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+					\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+				\end{split}
+			\end{equation}
+		}
+	\end{comment}
+	%	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
+	%	\begin{equation}\label{LinkABS-corr}
+		%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
+		%	\end{equation}
+	%	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
+
+	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
+This matrix $\mathcal{S}_{1}$ is given by
+	\begin{equation}\label{S1-L1}
+		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
+	\end{equation}
+	thus
+	\begin{equation}
+		\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
+	\end{equation}
+	By taking the tensor product over the chain we obtain 
+	\begin{equation}
+		S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
+	\end{equation}
+	therefore, projecting on $\langle \bm{\tau}|$ we have
+	\begin{equation}\label{Tensor-S1}
+		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
+	\end{equation}
+	\begin{comment}
+		Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
+		\begin{equation}
+			\begin{split}
+				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
+				\\&
+				+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
+			\end{split}
+		\end{equation}
+		where we have introduced, $\forall x\in \{1,\ldots,L\}$
+		\begin{equation}
+			%\eta_{x}=\begin{cases}
+				%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+				%	d_{x}\qquad &\text{otherwise}
+				%\end{cases}\qquad
+				\theta_{x}(b)=\begin{cases}
+					\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
+					N \qquad &\text{otherwise}
+				\end{cases}
+			\end{equation}
+			The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
+			This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
+			\begin{align*}
+				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
+				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
+\\&+\left.
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
+				\\&\otimes
+				\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
+				\\&=
+				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
+\\&+\left.
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
+			\end{align*}
+			\begin{comment}
+
+				\begin{equation}
+					F=\left(V^{-1}\right)^{T}
+				\end{equation}
+				and thus 
+				\begin{equation}
+					\mathcal{F}=F^{\otimes L}
+				\end{equation}
+				By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
+				\begin{equation}
+					F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+				\end{equation}
+				Taking the tensor product over two sites we obtain 
+				\begin{equation}
+					\begin{split}
+						F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
+						\right.\\ &+\left. 
+						(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
+					\end{split}
+				\end{equation}
+				therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
+				\begin{equation}
+					\begin{split}
+						\left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
+						\\&+
+						(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
+						\\&=
+						\sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+						+
+						(-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+					\end{split}
+				\end{equation}
+				where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
+\\
+				We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
+We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
+				\begin{equation}
+					\begin{split}
+						\mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
+						\\&
+						+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
+					\end{split}
+				\end{equation}
+				where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+\\
+				The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
+				To find this elements we need to fix the rows correspondent to $\bm{\tau}$.
+Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
+			\end{comment}
+			Considering 
+			\begin{equation}
+				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle
+			\end{equation} we obtain  
+			\begin{align}
+				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})
+			\end{align}
+		In the last equality we have used equation \eqref{ABS_1}. 
+			%	\begin{equation}
+				%		\begin{split}
+					%			\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
+					%			\\&
+					%			+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+					%		\end{split}
+				%	\end{equation}
+			%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+			%Using \eqref{elementsABS} we have 
+			%	\begin{equation}
+				%	\begin{split}
+					%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
+					%		\end{split}
+				%	\end{equation}
+			\begin{comment}
+				{\color{blue}
+					\begin{equation}
+						\begin{split}
+							&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
+							\\&  
+							\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
+							\\&
+							\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
+						\end{split}
+				\end{equation}}
+
+				indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
+			\end{comment}
+			Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
+			\begin{flushright}
+				$\square$
+			\end{flushright}
+			\begin{remark}[Non-equilibrium steady state using exact correlations]
+			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
+				\begin{align}
+					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
+					=&\sum_{\bm{\sigma}\in \Omega}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\bm{\sigma}|\Psi\rangle\nonumber\\
+					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
+					%=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
+				\end{align}
+				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that
+				\begin{equation}
+				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+				\end{equation}
+			where the expectation can be computed using \eqref{exactCorrelations}. 
+				\begin{comment}
+					where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
+					\begin{equation}
+						\begin{cases}
+							\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
+							\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
+						\end{cases}
+					\end{equation}
+					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
+					\begin{equation}
+						\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
+					\end{equation}
+					Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
+					\begin{equation}
+						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+					\end{equation}
+				\end{comment}
+			\end{remark}
+			\begin{proposition}[Normalization of $|\Psi\rangle$]
+				The steady state is normalized, i.e.
+				\begin{equation}
+					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
+				\end{equation}
+			\end{proposition}
+			\textbf{Proof}: here we write  
+			\begin{equation}
+				\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+			\end{equation}
+			meaning that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
+			\begin{equation}
+				\begin{cases}
+					\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,w_{b}\}\\
+					\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
+				\end{cases}
+			\end{equation}
+			We aim to show that 
+			\begin{align}
+				&\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+			\end{align}
+			We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e.
+$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
+Moreover, we introduce the space
+			\begin{equation}
+				\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
+			\end{equation}
+			Therefore, we can rewrite the normalization condition as 
+			\begin{align}
+				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
+				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
+			\end{align}
+			We first observe that, using \eqref{ABS}, we have that 
+			\begin{equation}
+				\Psi^{'}(N,\ldots,N)=1\co
+			\end{equation}
+			thus, it is enough to prove that
+			\begin{align}
+				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
+				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
+			\end{align}
+			We now consider the second term of the above expression.
+For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution.
+On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
+Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
+By calling $r=\ell-b$ if $b\leq \ell$ we have that
+			\begin{align}
+				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
+				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
+			\end{align} 
+			As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
+			\begin{align}
+				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
+			\end{align}
+			By exchanging the summations we have 
+			\begin{equation}
+				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
+			\end{equation}
+			It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
+			\begin{align}
+				1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
+			\end{align}
+			This is true because of the binomial theorem, indeed 
+			\begin{equation}
+				1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
+			\end{equation}
+			that implies the normalization of the state $|\Psi\rangle$. 
+			\begin{flushright}
+				$\square$
+			\end{flushright}
 \subsection{The colour-blind case}
@@
 \end{comment}
-\section{Exact steady state of $H$}\label{appB}
-\begin{proposition}[Non-equilibrium steady state]
-The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
-\begin{equation}
-	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
-\end{equation}
-where for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$
-\begin{equation}\label{SteadyState-coeff-implicit}
-	\begin{split}
-		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-	\end{split}
-\end{equation}
-where the last expectation is taken with respect to the $\mu^{\text{NESS}}$ of the process $\bm{\sigma}$ and is given in \eqref{exactCorrelations}.
-\end{proposition} %Therefore, 
-%\begin{equation}
-%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-%\end{equation} are computed using \eqref{exactCorrelations}. \\ \\
-\begin{comment}
-\begin{equation}\label{SteadyState-coeff-implicit}
-	\begin{split}
-		\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-	\end{split}
-\end{equation}
-\end{comment}
-%In \eqref{SteadyState-coeff-implicit} there are two terms.
-For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
-The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$.
-If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
-\begin{remark}
-	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
-	\begin{equation}
-		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
-	\end{equation}
-As a consequence, one cha interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
-\end{remark}
-\begin{comment}
-\begin{remark}
-The coefficients $\Psi(\bm{\tau})$ can also be written explicitly by replacing $\Psi^{'}(\bm{\tau})$ with formula \eqref{ABS}. They read 
-\begin{equation}
-	\begin{split}
-		\Psi(\bm{\tau})&=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
-		\\&+
-		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
-		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
-		\\&
-	\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\eta_{x}}-\beta_{\eta_{x}})^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
-	\end{split}
-\end{equation}
-where we have introduced, $\forall x\in \{1,\ldots,L\}$
-\begin{equation}\label{eta-notation}
-	\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-		i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
-	\end{cases}%\qquad \theta_{x}=\begin{cases}
-		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-		%	1 \qquad &\text{otherwise}
-		%\end{cases}
-	\end{equation}
-	The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
-	\end{remark}
-\end{comment}
-\begin{comment}
-	{\color{blue}
-		\begin{equation}\label{steadyStateH-coeff}
-			\begin{split}
-				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-				\\&+
-				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
-				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
-				\\&
-				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
-				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
-				\\ &
-				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-			\end{split}
-		\end{equation}
-	}
-\end{comment}
-%	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
-%	\begin{equation}\label{LinkABS-corr}
-%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
-%	\end{equation}
-%	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
-
-	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
-Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
-This matrix $\mathcal{S}_{1}$ is given by
-	\begin{equation}\label{S1-L1}
-		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
-	\end{equation}
-thus
-\begin{equation}
-\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
-\end{equation}
-By taking the tensor product over the chain we obtain 
-\begin{equation}
-S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
-\end{equation}
-therefore, projecting on $\langle \bm{\tau}|$ we have
-\begin{equation}\label{Tensor-S1}
-	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
-\end{equation}
-\begin{comment}
-	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
-	\begin{equation}
-		\begin{split}
-			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-			\\&
-			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
-		\end{split}
-	\end{equation}
-	where we have introduced, $\forall x\in \{1,\ldots,L\}$
-	\begin{equation}
-		%\eta_{x}=\begin{cases}
-			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-			%	d_{x}\qquad &\text{otherwise}
-			%\end{cases}\qquad
-			\theta_{x}(b)=\begin{cases}
-				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-				N \qquad &\text{otherwise}
-			\end{cases}
-		\end{equation}
-		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
-		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
-		\begin{align*}
-			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
-			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-\\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
-			\\&\otimes
-			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
-			\\&=
-			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
-\\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
-		\end{align*}
-		\begin{comment}
-
-			\begin{equation}
-				F=\left(V^{-1}\right)^{T}
-			\end{equation}
-			and thus 
-			\begin{equation}
-				\mathcal{F}=F^{\otimes L}
-			\end{equation}
-			By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
-			\begin{equation}
-				F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
-			\end{equation}
-			Taking the tensor product over two sites we obtain 
-			\begin{equation}
-				\begin{split}
-					F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-					\right.\\ &+\left. 
-					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
-				\end{split}
-			\end{equation}
-			therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
-			\begin{equation}
-				\begin{split}
-					\left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-					\\&+
-					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
-					\\&=
-					\sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-					+
-					(-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-				\end{split}
-			\end{equation}
-			where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
-\\
-			We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
-We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
-			\begin{equation}
-				\begin{split}
-					\mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
-					\\&
-					+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
-				\end{split}
-			\end{equation}
-			where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-\\
-		The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
-		To find this elements we need to fix the rows correspondent to $\bm{\tau}$.
-Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
-		\end{comment}
-	Considering 
-	\begin{equation}
-		|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle
-	\end{equation} we obtain  
-\begin{align}
-	\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
-	=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
-	=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-\end{align}
-In the last equality we exploited the fact that considering any $\tau_{x}\in \{1,\ldots,N\}$ and $i_{x}\in \{1,\ldots,N-1\}$, and considering a configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$ such that
-\begin{equation}
-	\begin{cases}
-		\sigma_{x}=i_{x}\qquad &\text{if}\quad x\in \{q_{1},\ldots,q_{b}\}\\
-		\sigma_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
-	\end{cases}
-\end{equation}
-we have that 
-\begin{equation}
-	 \Psi^{'}(\bm{\sigma})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-\end{equation}
-as showed in Section \ref{correlation-section}. 
-	%	\begin{equation}
-	%		\begin{split}
-	%			\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
-	%			\\&
-	%			+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-	%		\end{split}
-	%	\end{equation}
-		%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-		%Using \eqref{elementsABS} we have 
-	%	\begin{equation}
-		%	\begin{split}
-		%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
-	%		\end{split}
-	%	\end{equation}
-	\begin{comment}
-		{\color{blue}
-			\begin{equation}
-				\begin{split}
-					&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
-					\\&  
-					\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-					\\&
-					\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-				\end{split}
-		\end{equation}}
-
-indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
-\end{comment}
- Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
-		\begin{flushright}
-			$\square$
-		\end{flushright}
-	\begin{remark}[Proof of \eqref{SteadyState-coeff-implicit} using the conservation of probability]
-		Equation \eqref{SteadyState-coeff-implicit} can be proved also using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
-\begin{align}
-			\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-			=&\sum_{\bm{\sigma}\in \Omega}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\bm{\sigma}|\Psi\rangle\nonumber\\
-			=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
-			%=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
-\end{align}
-Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, one find \eqref{SteadyState-coeff-implicit}.
-\begin{comment}
-where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
-\begin{equation}
-	\begin{cases}
-	\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
-	\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
-	\end{cases}
-\end{equation}
-Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
-\begin{equation}
-\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
-\end{equation}
-Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
-\begin{equation}
-\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-\end{equation}
-\end{comment}
-	\end{remark}
-	\begin{proposition}[Normalization of $|\Psi\rangle$]
-	The steady state is normalized, i.e.
-	\begin{equation}
-		\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
-	\end{equation}
-\end{proposition}
-	\textbf{Proof}: we aim to show that 
-	\begin{align}
-		\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
-	\end{align}
-	We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e.
-$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
-Moreover, we introduce the space
-	\begin{equation}
-		\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
-	\end{equation}
-	Therefore, we can rewrite the normalization condition as 
-	\begin{align}
-		&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-		+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
-	\end{align}
-	We first observe that, using \eqref{ABS}, we have that 
-	\begin{equation}
-		\Psi^{'}(N,\ldots,N)=1\co
-	\end{equation}
-	thus, it is enough to prove that
-	\begin{align}
-		&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-		+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
-	\end{align}
-	We now consider the second term of the above expression.
-For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution.
-On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
-Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
-By calling $r=\ell-b$ if $b\leq \ell$ we have that
-	\begin{align}
-		&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
-		=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
-	\end{align} 
-	As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
-	\begin{align}
-		\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
-	\end{align}
-	By exchanging the summations we have 
-	\begin{equation}
-		\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
-	\end{equation}
-	It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
-	\begin{align}
-		1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
-	\end{align}
-	This is true because of the binomial theorem, indeed 
-	\begin{equation}
-		1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
-	\end{equation}
-	that implies the normalization of the state $|\Psi\rangle$. 
-	\begin{flushright}
-		$\square$
-	\end{flushright}
+
 \section{One point correlations for $\nu\geq 1$}\label{appendix-1pts-general}

### 2023-11-14 main.tex
:)

@@
 In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}.
-This formula is follows from the ground state $|\Psi^{'}\rangle$found in \eqref{ABS_1}.
+This formula follows from the ground state $|\Psi^{'}\rangle$ found in \eqref{ABS_1}.
 \begin{proposition}[Non-equilibrium steady state]
@@
 	\end{equation}
-	where 
-	\begin{equation}
-		\begin{split}
-			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
-			\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})
-			\end{split}
-		\end{equation}
+	and where 
+		\begin{equation}
+		\begin{split}
+			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
+			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)
+		\end{split}
+	\end{equation}
+%	\begin{equation}
+	%	\begin{split}
+	%		\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
+	%		\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})
+	%		\end{split}
+	%	\end{equation}
 	%\begin{equation}
@@
 %%	\end{equation}
-\end{proposition} %Therefore, 
+\end{proposition} 
+\begin{remark}[Equilibrium case]
+	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ only the terms with $c_{x}=0$ do survive in \eqref{SteadyState-coeff-implicit}. Therefore we obtain 
+	\begin{equation}
+		\Psi(\bm{\tau})=\prod_{a=1}^{N}\beta_{a}^{\sum_{x=1}^{L}\delta_{\tau_{x},a}}
+	\end{equation}
+i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $p_{a}=\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 
+\end{remark}
+\begin{remark}[Implicit form of $\Psi(\bm{\tau})$]
+	The elements of the the vector $|\Psi\rangle$ can also be written as a linear combination of elements $\Psi^{'}(\bm{\tau})$ as 
+	\begin{equation}\label{implicit-steadyState}
+		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+	\end{equation}
+	where
+	\begin{equation}\label{notation-PSI}
+		\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+	\end{equation}
+	meaning that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
+	\begin{equation}
+		\begin{cases}
+			\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
+			\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
+		\end{cases}
+	\end{equation}	
+\end{remark}
+
+%Therefore, 
 %\begin{equation}
@@
 	\end{equation}
-%where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
+where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
 	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
@@
 				\end{equation}
-			where the expectation can be computed using \eqref{exactCorrelations}. 
+			where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
 				\begin{comment}
@@
 			\end{remark}
-			\begin{proposition}[Normalization of $|\Psi\rangle$]
-				The steady state is normalized, i.e.
-				\begin{equation}
-					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
+			\begin{proposition}[Normalization]
+				The steady state $|\Psi\rangle$ is normalized, i.e.
+				\begin{equation}
+					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=1
 				\end{equation}
 			\end{proposition}
-			\textbf{Proof}: here we write  
-			\begin{equation}
-				\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-			\end{equation}
-			meaning that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
-			\begin{equation}
-				\begin{cases}
-					\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,w_{b}\}\\
-					\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
-				\end{cases}
-			\end{equation}
-			We aim to show that 
+			\textbf{Proof}: Considering \eqref{notation-PSI}, we aim to show that 
 			\begin{align}
-				&\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+				\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
 			\end{align}
@@
 				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
+				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
 			\end{align}
@@
 				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
+				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
 			\end{align}
@@
 			\begin{align}
-				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
+				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
 				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
@@
 Therefore, using \eqref{Gamma-product} and by considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP.
+\begin{flushright}
+	$\square$
+\end{flushright}
+\paragraph{$|\Psi\rangle$ for SSEP}
+In the colour-blind case we have that 
+\begin{equation}
+	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})|\bm{\tau}\rangle
+\end{equation}
+where
+\begin{equation}
+	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},2}\right)\sum_{s=0}^{|\bm{\tau}|+b}(\alpha-\beta)^{s}\beta^{L-s}\sum_{1\leq \ell_{1}<\ldots<\ell_{s}\leq |\bm{\tau}|}\prod_{k=1}^{s}\frac{\left(L+1-x_{\ell_{k}}-s+k\right)}{(2+L-k)}
+\end{equation}
+with
+\begin{equation}
+	|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1} \dt
+\end{equation}
+\textbf{Proof}: the proof follows from \eqref{implicit-steadyState} and \eqref{PsiI-N2}. 
 \begin{flushright}

### 2023-11-14 main.tex
check

@@
 	\end{equation}
-i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $p_{a}=\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 
+i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 
 \end{remark}
@@
 	\end{equation}
-where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
+where the expectation is taken with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
 	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
@@
 	\begin{equation}
-		\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
+		\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
 	\end{equation}
@@
 			\end{align}
+		In the second equality we have rewritten the product by introducing the summation over $b$ and introducing the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$.
 In the last equality we have used equation \eqref{ABS_1}.
@@
 					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-					=&\sum_{\bm{\sigma}\in \Omega}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\bm{\sigma}|\Psi\rangle\nonumber\\
+					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
 					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
@@
 			\end{align} 
-			As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads
+			As a consequence we have that the normalization condition reads
 			\begin{align}
@@
 \end{equation}
+and where $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ . \\ \\
  \textbf{Proof:} For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty.

### 2023-11-17 main.tex
^^

@@
 \begin{equation}
-	\Omega=\bigotimes_{x=1}^{L}\Omega_{x}\qquad \Omega_{x}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
+	\Omega^{'}=\bigotimes_{x=1}^{L}\Omega_{x}^{'}\qquad \Omega_{x}^{'}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
 \end{equation}
@@
 \begin{equation}\label{ResulsBasis}
-	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
+	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
 \end{equation}
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 	|V \rangle \,|\bm{\tau}\rangle
@@
 $$
-such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. \\
+such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}^{'}$. \\
 \end{comment}
@@
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
+	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
 \end{equation}
@@
 \begin{equation}\label{ABS-vect}
-    |\Psi^{'}\rangle =\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
+    |\Psi^{'}\rangle =\sum_{\bm{\tau}\in \Omega^{'}}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
 \end{equation}
@@
 \end{comment}
- By considering a fixed $\bm{\tau}\in \Omega$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 
+ By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 
 \begin{equation}\label{ABS_intermediate}
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
 	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
@@
 \begin{equation}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
 \end{equation}
@@
 \begin{align}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
-	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
 \end{align}
@@
 \begin{align}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
-	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
-	=&\sum_{\bm{\tau}\in \Omega}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
+	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
 	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
@@
 	\begin{equation}
-		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
-	\end{equation}
-	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega$,
+		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
+	\end{equation}
+	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega^{'}$,
 	\begin{equation}\label{SteadyState-coeff-implicit}
@@
 			\begin{equation}
-				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle
+				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle
 			\end{equation} we obtain  
 			\begin{align}
-				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
+				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
 				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})
@@
 			\begin{remark}[Non-equilibrium steady state using exact correlations]
-			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
+			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
 				\begin{align}
-					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
-					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
-					%=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
+					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
+					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
+					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
+					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
 				\end{align}
@@
 				\begin{equation}
-					\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=1
+					\sum_{\bm{\tau}\in\Omega^{'}}\langle \bm{\tau}|\Psi\rangle=1
 				\end{equation}
@@
 			\begin{align}
-				\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
+				\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega^{'}}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
 			\end{align}
@@
 			\begin{equation}
-				\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
+				\Omega_{\ell}^{'}=\left\{\bm{\tau}\in \Omega^{'}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
 			\end{equation}
@@
 			\begin{align}
-				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
+				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
+				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
 			\end{align}
@@
 			\begin{align}
-				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
-				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
+				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
+				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
 			\end{align}
 			We now consider the second term of the above expression.
-For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ has $\ell<b$, then this term do not produce any contribution.
-On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
+For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}^{'}$ has $\ell<b$, then this term do not produce any contribution.
+On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}^{'}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
 Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
@@
 			\begin{align}
-				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
-				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\dt
+				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
+				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}^{'}}\Psi^{'}(\bm{\tau})\dt
 			\end{align} 
@@
 			\begin{align}
-				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
+				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt
 			\end{align}
@@
 			\begin{equation}
-				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})=0\dt
+				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt
 			\end{equation}
@@
 \begin{equation}
-	|\Psi^{'}\rangle=\sum_{\bm{\tau}\in\Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle
+	|\Psi^{'}\rangle=\sum_{\bm{\tau}\in\Omega^{'}}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle
 \end{equation}
@@
 \begin{equation}
-	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})|\bm{\tau}\rangle
+	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})|\bm{\tau}\rangle
 \end{equation}
@@
 \begin{equation}
-	\widehat{\Omega}^{m}=\left\{\bm{\tau}\in \Omega\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}
+	\widehat{\Omega^{'}}^{m}=\left\{\bm{\tau}\in \Omeg^{'}a\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}
 \end{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
+\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)
 \end{equation}
@@
 \begin{align}
-&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi^{'}(\tau)\nonumber
+&\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi^{'}(\tau)\nonumber
 \\+&
-\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-\end{align}
-We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega}^{m}$, i.e.
+\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+\end{align}
+We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega^{'}}^{m}$, i.e.
 $\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
@@
 \begin{equation}
-\widehat{\Omega}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
+\widehat{\Omega^{'}}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega^{'}}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
 \end{equation}
@@
 \begin{align}
-&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber
+&\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber
 \\+&
-\sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+\sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
 \end{align}
@@
 The second term on the right-hand-side in the above equation replaces $b$ empty occupations with all possible non-empty species.
-If the configuration $\bm{\tau}\in\widehat{\Omega}_{\ell}^{m}$ has $\ell<b$ no contributions are seen.
+If the configuration $\bm{\tau}\in\widehat{\Omega^{'}}_{\ell}^{m}$ has $\ell<b$ no contributions are seen.
 Otherwise, if $\ell\geq b$, $b$ empties are changed, obtaining configuration with $r=\ell-b$ voids occupations, with $r\in \{0,\ldots, L-m-b\}$.
@@
 \begin{align}
-	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
-	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\mathbbm{1}_{\{b\leq L-m-r\}}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+	\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
+	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\mathbbm{1}_{\{b\leq L-m-r\}}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
 \end{align}
@@
 \begin{align}
-\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
-\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}\mathbbm{1}_{\{b\leq L-m-\ell\}}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
+\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
+\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}\mathbbm{1}_{\{b\leq L-m-\ell\}}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
 \end{align}
@@
 \begin{equation}
-\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
 \end{equation}

### 2023-11-17 main.tex
Update main.tex

@@
 %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
-\begin{proposition}[Correlations via duality]
+\begin{corollary}[Correlations via duality]
 \label{prop-absorbing}
@@
 \end{equation}
-\end{proposition}
+\end{corollary}
 \textbf{Proof}:
-For any $\bm{\tau}\in \Omega$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
+For any $\bm{\tau}\in \Omega^{'}$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
 \begin{equation}
@@
 \end{flushright} 
+    \begin{corollary}
+ADD
+\end{corollary}
 
@@
 In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain.
-\begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}
+\begin{theorem}[Correlations in the non-equilibrium steady state]\label{thm-correlations}
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
@@
 \begin{align*}
-	\langle W|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
+	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
 	\\&=
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})}
 \end{equation}
@@
 &\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
-=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\
+=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})}\nonumber\\
 =&\frac{\Gamma(2)}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x}^{L}\delta_{\tau_{j},x})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})}\nonumber\\
@@
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
 	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
@@
 \end{flushright}
-\begin{remark} By change the summation indices form $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{remark} By changeing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
 \begin{equation}\label{ABS_1}
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N})\right)
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x_{j}},N})\right)
 \end{equation}
@@
 \end{remark}
-\subsubsection{Formula for exact correlations}\label{correlation-section}
-We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.
-Each of these sites is occupied by $a_{k}\in\{1,\ldots,N-1\}$, we aim to compute
+\subsubsection{Formula for correlations}\label{correlation-section}
+We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
 \begin{equation}

### 2023-11-17 main.tex
^^

@@
 \end{comment}
- By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 
-\begin{equation}\label{ABS_intermediate}
-	\begin{split}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
-	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation}
+ By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} the formula for $|\Psi^{''}\rangle$ we obtain 
+\begin{align}\label{ABS_intermediate}
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]
+	\end{align}
 %where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
@@
 %For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, \\ \\ 
-We introduce 
-\begin{equation}
-	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
-\end{equation}
-To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain
+We rewrite the above equation as
+%\begin{equation}
+%	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
+%\end{equation}
+%To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain
 \begin{align}
 	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
-	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
+	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
+	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
+	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
 \end{align}
@@
 	\begin{split}
-	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\\
+	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\
 	=&\begin{cases}
@@
 	\begin{split}
-	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
-	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
+	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
+	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
 	\end{split}
@@
 \Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
 %=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
-\end{align}
+%=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+\end{align}
+We introduce the summation indices $c_{x}\in \{\delta_{\tau_{x},N},1\}$ for all $x\in \{1,\ldots,L\}$.
+and we observe that 
+\begin{align}
+	&\sum_{\sigma_{x}=1}^{N}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
+	=
+	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+\end{align} Then, we replace the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$ as 
+\begin{equation}
+	\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+\end{equation}
 %thus, by using equation \eqref{ResulsBasis}, we have

### 2023-11-20 main.tex
''

@@
 \begin{equation}
-	\Omega^{'}=\bigotimes_{x=1}^{L}\Omega_{x}^{'}\qquad \Omega_{x}^{'}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
+	\Omega^{'}=\left\{(\tau_{1},\ldots,\tau_{L})\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
 \end{equation}
@@
  \end{flushright}
- \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
+ \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
 % that we connect to every site $x\in V$ of the graph $G$.
@@
 Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.
+In the following we denote by $\mu$ the non-equilibrium steady state distribution.
 %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
@@
 \begin{equation}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
+\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 	\begin{split}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
+\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
 	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
@@
 \end{flushright} 
+\begin{remark}
+	The result written in the previous Corollary \ref{prop-absorbing} holds also for chains with higher maximal occupancy ($\nu>1)$, as specified in Section \ref{Subsection-ss-nonI}. 
+\end{remark}
     \begin{corollary}
@@
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
-and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu_{\text{NESS}}$ are given by 
+and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu$ are given by 
 \begin{equation}\label{exactCorrelations}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
+\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \begin{equation}\label{exactCorrelations}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
 	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
@@
 %			\begin{split}
-%				\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(L+1)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
+%				\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(L+1)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
 %			\end{split}
@@
 \paragraph{One-point correlations}
-We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
+We consider the average with respect to $\mu$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
 %\begin{equation}
-%\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
+%\mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
 %\end{equation}
@@
 \begin{equation}\label{one-pts-corr}
-	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
+		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
 \end{equation}
 \paragraph{Two-point correlations}
-We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$.
+We consider the average with respect to $\mu$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 
 %\begin{equation}
 %	\begin{split}
-%		 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
+%		 \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
 %	\end{split}
@@
 %where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}$. 
-Then, by using \eqref{exactCorrelations} we have 
-\begin{equation}
-\begin{split}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]=&\frac{x_{1}(x_{2}-1)}{L(L+1)}\beta_{a_{1}}\beta_{a_{2}}+\frac{x_{1}(L+1-x_{2})}{L(L+1)}\beta_{a_{1}}\alpha_{a_{2}}\\
-	+&\frac{x_{2}(L+1-x_{1})}{L(L+1)}\alpha_{a_{1}}\beta_{a_{2}}+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}\alpha_{a_{1}}\alpha_{a_{2}}
-\end{split}
-\end{equation}
+%Then, by using \eqref{exactCorrelations} we have 
+%\begin{equation}
+%\begin{split}
+%	\mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]=&\frac{x_{1}(x_{2}-1)}{L(L+1)}\beta_{a_{1}}\beta_{a_{2}}+\frac{x_{1}(L+1-x_{2})}{L(L+1)}\beta_{a_{1}}\alpha_{a_{2}}\\
+%	+&\frac{x_{2}(L+1-x_{1})}{L(L+1)}\alpha_{a_{1}}\beta_{a_{2}}+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}\alpha_{a_{1}}\alpha_{a_{2}}
+%\end{split}
+%\end{equation}
 %\begin{equation}
 %	\begin{split}
-%	 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
+%	 \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
 %	\end{split}
@@
 	\begin{split}
-		 \mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
+		 \mathbb{E}_{\mu}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 \paragraph{Three-point correlations}
-We consider the average with respect to $\mu_{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
+We consider the average with respect to $\mu$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$.
 Using \eqref{abs-probabilities} we compute the absorption probabilities
@@
 %where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}+\delta_{a_{3}}^{x_{3}}$ 
-Then, by using \eqref{exactCorrelations} we obtain 
-\begin{align}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}&\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
-	(x_3-2)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\
-+\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}&\beta_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}&\beta_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
-+ \frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
-	(x_3-2)}{L \left(L^2-1\right)}& \alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
-	\left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
-+\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}&\alpha_{a_{1}}\alpha_{a_{2}}\alpha_{a_{3}}
-\end{align}
+%Then, by using \eqref{exactCorrelations} we obtain 
+%\begin{align}
+%\mathbb{E}_{\mu}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}&\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
+%	(x_3-2)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\
+%+\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}&\beta_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}&\beta_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
+%+ \frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
+%	(x_3-2)}{L \left(L^2-1\right)}& \alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
+%	\left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
+%+\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}&\alpha_{a_{1}}\alpha_{a_{2}}\alpha_{a_{3}}
+%\end{align}
 \begin{comment}
 \begin{align}\label{three-pts-corr}
- \mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
+ \mathbb{E}_{\mu}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
 	\\&+\nonumber
@@
 \begin{align}
-	&\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
-	-&\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
-	 -&\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber
-	\\
+	&\mathbb{E}_{\mu}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
 	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
 \end{align}
-\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Section 4.3 of \cite{vanicat2017exact}.
+\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.
 	\end{remark}
@@
 \end{comment}
-To determine the eigenvector \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 |V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
@@
 	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle\nonumber&=
+	|V \rangle=
 	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle W|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
 \end{align}
-We now need to compute $\langle W|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  
-\begin{align*}
-	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
+We now compute $\langle W|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  
+\begin{align}
+	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle\nonumber
 	\\&=
-	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{(\alpha_{a}-\beta_{a})}\langle W|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right)|V\rangle
+	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{(\alpha_{a}-\beta_{a})}\langle W|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right)|V\rangle\nonumber
 	\\&=
-	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
+	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle\nonumber
 	\\&=
-	\left(2+n-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
+	\left(2+n-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle\nonumber
 	\\&=
-	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
-\end{align*}
+	\frac{(1+n)!}{n!}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
+\end{align}
 where in the second equality we used \eqref{usefulRelaton-many}. 
@@
 \begin{align}
-		\langle W|\widetilde{X}_{N}^{n}|V\rangle=\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
+		\langle W|\widetilde{X}_{N}^{n}|V\rangle=\frac{(1+n)!}{n!}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
 \end{align}
@@
 Therefore, we obtain 
-\begin{align*}
+\begin{align}
 	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle W|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle W|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
-	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\frac{\Gamma(2+n-1)}{\Gamma(2+n-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle W|\widetilde{X}_{N}^{0}|V\rangle=
-	\Gamma(2+n)
-\end{align*}
+	\frac{(1+n)!}{n!}\frac{n!}{(n-1)!}\ldots \frac{3!}{2!}\frac{2!}{1!}\langle W|\widetilde{X}_{N}^{0}|V\rangle=
+	(1+n)!
+\end{align}
 By using this result we have that
@@
 	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle=\Gamma(2+\sum_{x=1}^{N}\delta_{\tau_{x},N})\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
+	|V \rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
 \end{equation}
 The normalization constant is then given by
-\begin{align*}
+\begin{align}
 	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V|\rangle=
-	\Gamma(L+2)\dt
-\end{align*}
+	(L+1)!\dt
+\end{align}
 Therefore, we write
 \begin{equation}\label{resulEsteady}
-	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
+	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega^{'}}\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
 \end{equation}
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})}
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}
 \end{equation}
@@
 \begin{align}\label{remove-exponent}
-&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
-=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})}\nonumber\\
-=&\frac{\Gamma(2)}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x}^{L}\delta_{\tau_{j},x})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})}\nonumber\\
+&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
+=&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},x})!}\nonumber\\
 =&\frac{1}{(L+1)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
@@
 %\end{equation}
-\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
+\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
 Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
@@
 \Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
 %=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
@@
 \begin{equation}
-	\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+	\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
 \end{equation}
@@
 The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
-To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
+To find these quantities we fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
 Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
@@
 \end{equation}
-where we used the fact that, for any $\bm{\tau}$ we have 
-\begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x_{j}},N})\right)
+where we used the fact that 
+\begin{equation}
+	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-c_{j})\right)
 \end{equation}
@@
 \begin{equation}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
 \end{equation}
@@
 \begin{align}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
 	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
 \end{align}
-Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$ and recalling that  
+Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $\{0\}$ and $\{L+1\}$ and recalling that  
 \begin{equation}
@@
 \begin{align}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
 	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
@@
 \begin{align}
-	&\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
+	&\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
 	\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 		\begin{split}
-			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\dots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\dots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})%\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
 		\end{split}
@@
 %\begin{equation}
-%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+%\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
 %\end{equation} are computed using \eqref{exactCorrelations}. \\ \\
@@
 	\begin{equation}
-		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\dt
-	\end{equation}
-where the expectation is taken with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
+		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\dt
+	\end{equation}
+where the expectation is taken with respect to the $\mu$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
 	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
@@
 
-	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
+	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
 Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
@@
 				The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
-				To find this elements we need to fix the rows correspondent to $\bm{\tau}$.
+				To find this elements we fix the rows correspondent to $\bm{\tau}$.
 Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
@@
 				\begin{equation}
-				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
 				\end{equation}
@@
 					\begin{equation}
-						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
 					\end{equation}
@@
 \begin{equation}\label{correlations-SSEP}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
 \end{equation} 
@@
 \end{equation}
-where $m$ occupations are fixed and the other $L-m$ can vary in all possible ways. Therefore, we need to compute 
-\begin{equation}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)
+where $m$ occupations are fixed and the other $L-m$ can vary in all possible ways. Therefore, we compute 
+\begin{equation}
+\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)
 \end{equation}
@@
 \begin{equation}\label{shorter-chain}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
+\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
 \end{equation}
@@
 \begin{equation}
-\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
+\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
 \end{equation}
@@
 This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu_{\text{NESS}}$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$.
+We call $\mu$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$.
 For every $m\in\{1,\ldots,L\}$ we consider  $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$ and we introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ meaning that
@@
 where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
-Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
+Therefore, up to this constant, $\mathbb{E}_{\mu}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
 The following equalities hold using duality relation \eqref{duality-expectation}:
@@
 	\begin{split}
-		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\frac{\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\&=
@@
 \paragraph{Proof of duality}
-We only need to prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
+We only prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
 In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 
@@
 \end{equation}
-We need to prove that, for arbitrary $x\in\{1,\ldots,L\}$,
+We prove that, for arbitrary $x\in\{1,\ldots,L\}$,
 %\begin{align}
@@
 	\begin{split}
-			\mathbb{E}_{\mu_{\text{NESS}}}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
+			\mathbb{E}_{\mu}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
 	\end{split}
@@
 \begin{equation}
-	\mathbb{E}_{\mu_{\text{NESS}}}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+	\mathbb{E}_{\mu}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
 \end{equation}
@@
 \begin{equation}
-		\mathbb{E}_{\mu_{\text{NESS}}}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
+		\mathbb{E}_{\mu}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
 \end{equation}

### 2023-11-20 main.tex
^'^'

@@
 As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
-Finally, reversing the transformations we retrieve $|\Psi\rangle$.
+Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e.
+the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.
  The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
-Therefore, $H^{'}$ is not stochastic.
+Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state.
 The second transformation $S_{2}$ diagonalizes the right boundary.
@@
 \end{equation}
-We observe that 
+We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$ and we have 
 \begin{equation}
@@
 \end{equation}
-with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$. Thus we have
+Thus it follows that 
 \begin{align}
@@
 \end{equation}
-Therefore, it follows that 
+Therefore, it follows that, using the resolution of the identity
 \begin{align}
@@
 	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
-	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
-	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
+	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle
+\end{align}
+Using $\Psi^{'}(\bm{\tau})$ in \eqref{ABS_1} we have 
+\begin{align}
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(y_{k},c_{k},\ldots,c_{m})\co
-\end{align}
-where in the second line we have used the resolution of the identity, in the last line we have used \eqref{ABS_1} and in the last equality we have used the definition of \eqref{powerCoeffSpecies} and \eqref{powerCoeffNOspec}.
-Using the binomial theorem we have that 
+	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\co
+\end{align}
+where in the last equality we have used the definition of \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies}.
+As a last step, using the binomial theorem, we rewrite the previous expression as a polynomial in the boundary densities: 
 \begin{align}
@@
 \end{flushright}
-\subsection{Explicit steady state of $H$}\label{appB}
+\subsection{Steady state}\label{appB}
 In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}.
 This formula follows from the ground state $|\Psi^{'}\rangle$ found in \eqref{ABS_1}.
-\begin{proposition}[Non-equilibrium steady state]
+\begin{corollary}[Non-equilibrium steady state]
 	The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
@@
 \begin{equation}\label{SteadyState-coeff-implicit}
-		\begin{split}
-			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\dots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})%\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-		\end{split}
-	\end{equation}
-	and where 
-		\begin{equation}
-		\begin{split}
-			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
-			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)
-		\end{split}
-	\end{equation}
+	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+\end{equation}
+where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
+%	and where 
+%		\begin{equation}
+%		\begin{split}
+	%		\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
+%			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)
+%		\end{split}
+%	\end{equation}
 %	\begin{equation}
@@
 %	\end{equation}
-	with
-	\begin{equation}
-		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
-	\end{equation}
-and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 
+%	with
+%	\begin{equation}
+%		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
+%	\end{equation}
+%and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 
 %	\begin{equation}
@@
 %%	\end{equation}
-\end{proposition} 
+\end{corollary} 
 \begin{remark}[Equilibrium case]
-	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ only the terms with $c_{x}=0$ do survive in \eqref{SteadyState-coeff-implicit}. Therefore we obtain 
+	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ we obtain 
 	\begin{equation}
@@
 \end{remark}
+\begin{comment}
 \begin{remark}[Implicit form of $\Psi(\bm{\tau})$]
@@
 	\end{equation}
-	where
-	\begin{equation}\label{notation-PSI}
+	where the notation
+	\begin{equation}%\label{notation-PSI}
 		\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
 	\end{equation}
-	meaning that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
+	means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
 	\begin{equation}
@@
 \end{remark}
-
+\end{comment}
 %Therefore, 
@@
 				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})
-			\end{align}
-		In the second equality we have rewritten the product by introducing the summation over $b$ and introducing the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$.
-In the last equality we have used equation \eqref{ABS_1}.
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+			\end{align}
+where the notation
+		\begin{equation}\label{notation-PSI}
+			\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+		\end{equation}
+		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
+		\begin{equation}
+			\begin{cases}
+				\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
+				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
+			\end{cases}
+		\end{equation}
+		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$.
+In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
+From Section \ref{correlation-section} we recall that the components of $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state.
+Thus, we have that
+			\begin{equation}
+			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+		\end{equation}
 			%	\begin{equation}
@@
 			\end{flushright}
+		\begin{comment}
 			\begin{remark}[Non-equilibrium steady state using exact correlations]
@@
 			where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
+				\end{remark}
+		\end{comment}
 				\begin{comment}
@@
 				\end{comment}
-			\end{remark}
-			\begin{proposition}[Normalization]
-				The steady state $|\Psi\rangle$ is normalized, i.e.
-				\begin{equation}
-					\sum_{\bm{\tau}\in\Omega^{'}}\langle \bm{\tau}|\Psi\rangle=1
-				\end{equation}
-			\end{proposition}
-			\textbf{Proof}: Considering \eqref{notation-PSI}, we aim to show that 
-			\begin{align}
-				\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega^{'}}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
-			\end{align}
-			We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e.
-$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
-Moreover, we introduce the space
-			\begin{equation}
-				\Omega_{\ell}^{'}=\left\{\bm{\tau}\in \Omega^{'}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
-			\end{equation}
-			Therefore, we can rewrite the normalization condition as 
-			\begin{align}
-				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
-				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=1
-			\end{align}
-			We first observe that, using \eqref{ABS}, we have that 
-			\begin{equation}
-				\Psi^{'}(N,\ldots,N)=1\co
-			\end{equation}
-			thus, it is enough to prove that
-			\begin{align}
-				&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})\nonumber
-				+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\&=0
-			\end{align}
-			We now consider the second term of the above expression.
-For a fixed $b$, $\ell$ and $\bm{\tau}$, if the configuration $\bm{\tau}\in \Omega_{\ell}^{'}$ has $\ell<b$, then this term do not produce any contribution.
-On the other hand, if $b\geq \ell$ we obtain all possible configuration in the space $ \Omega_{\ell-b}^{'}$, where $b$ of the $\ell$ empties have been replaced by all  species from $1$ to $N-1$.
-Each of such a configuration is counted $\binom{L-\ell+b}{b}$, since we have added,  in all possible ways, $b$ non-empty occupations to the configuration $\bm{\tau}$ that had originally $L-\ell$ sites occupied with non-empty species.
-By calling $r=\ell-b$ if $b\leq \ell$ we have that
-			\begin{align}
-				&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\sum_{b=1}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<i_{q_{b}\leq L}=1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
-				=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\mathbbm{1}_{\{b\leq L-r\}}\sum_{\bm{\tau}\in \Omega_{r}^{'}}\Psi^{'}(\bm{\tau})\dt
-			\end{align} 
-			As a consequence we have that the normalization condition reads
-			\begin{align}
-				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt
-			\end{align}
-			By exchanging the summations we have 
-			\begin{equation}
-				\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\mathbbm{1}_{\{b\leq L-\ell\}}\sum_{\bm{\tau}\in \Omega_{\ell}^{'}}\Psi^{'}(\bm{\tau})=0\dt
-			\end{equation}
-			It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
-			\begin{align}
-				1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
-			\end{align}
-			This is true because of the binomial theorem, indeed 
-			\begin{equation}
-				1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
-			\end{equation}
-			that implies the normalization of the state $|\Psi\rangle$. 
-			\begin{flushright}
-				$\square$
-			\end{flushright}
+
 \subsection{The colour-blind case}

### 2023-11-20 main.tex
partial

@@
 \end{flushright}
+\begin{remark}[Interpretation the elements $\Psi^{'}(\bm{\tau})$]
+	For any given $\bm{\tau}\in \Omega^{'}$ we have that 
+	\begin{equation}\label{interpretation-PsiP}
+		\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]
+	\end{equation} 
+Indeed, arguing as in the previous proof, we have that
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\sigma\in \Omega}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle
+\end{align}
+We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it in a vector of dimension $L$ to one of dimension $L+2$.
+More explicitly, this dual configuration is given by
+\begin{equation}
+	\begin{cases}
+	\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
+	\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
+\end{cases}
+\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$. Therefore, we have
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\sum_{\sigma\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle
+\end{align}
+We observe that for any $x\in \{1,\ldots,L\}$ the duality function \eqref{ElementsDualityMatrixChain_1} is
+\begin{equation}
+	d_{x}(\sigma_{x},\xi^{x}(\bm{\tau}))=\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
+		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
+		1\qquad  &\text{if}\quad \tau_{x}= N
+	\end{cases}
+\end{equation}
+ Therefore, equation \eqref{interpretation-PsiP} follows. 
+\end{remark}
 \subsection{Steady state}\label{appB}
@@
 \begin{equation}\label{SteadyState-coeff-implicit}
-	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{1-\delta_{\tau_{x},N}}\right]
 \end{equation}
@@
 In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
-From Section \ref{correlation-section} we recall that the components of $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state.
+From Section \ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}.
 Thus, we have that
 			\begin{equation}
-			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{b}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{1-\delta_{\tau_{x},N}}\right]
 		\end{equation}
@@
 			\end{flushright}
+		\begin{remark}
+Formula \eqref{SteadyState-coeff-implicit} can be also obtained without inverting the matrix $S_{1}$, but just using the conservation of probability in the non-equilibrium steady state.
+Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have
+			\begin{align}
+				\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\mu\left(\sigma_{1}=\tau_{1},\ldots,\sigma_{L}=\tau_{L}\right)=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\nonumber\\
+				=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\right]\nonumber\\
+				=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}\right)\right)\right]
+				%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
+			%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
+			%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
+				%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
+			\end{align}
+		where in the up to last line we exploited the fact that 
+		\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}
+		\end{equation}
+		Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$	we retrieve \eqref{SteadyState-coeff-implicit}.
+			\end{remark}
 		\begin{comment}

### 2023-11-20 main.tex
''

@@
 \end{flushright}
-\begin{remark}[Interpretation the elements $\Psi^{'}(\bm{\tau})$]
-	For any given $\bm{\tau}\in \Omega^{'}$ we have that 
-	\begin{equation}\label{interpretation-PsiP}
-		\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]
-	\end{equation} 
-Indeed, arguing as in the previous proof, we have that
+\begin{remark}[Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution]
+We argue as in the previous proof. For any given $\bm{\tau}\in \Omega^{'}$ we have that 
 \begin{align}
@@
 \end{cases}
-\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$. Therefore, we have
+\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
 \begin{align}
@@
 \end{equation}
- Therefore, equation \eqref{interpretation-PsiP} follows. 
+ Therefore, we obtain 
+ 	\begin{equation}\label{interpretation-PsiP}
+ 	\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]
+ \end{equation} 
+ where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$.
+Equation \eqref{interpretation-PsiP} will be useful in the exact formula for the steady state.
+Given $\bm{\tau}$ as before, we can introduce $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ the number of occupied sites.
+Then we denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle is present.
+Finally, we call
+ \begin{equation}
+ 	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}
+ \end{equation} 
+Then, we have that
+\begin{equation}
+	\Psi(\bm{\tau})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})
+\end{equation}
+where 
+\begin{equation}
+	\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})
+\end{equation}
+is marginal on $m$ sites of the steady state distribution.  
 \end{remark}
@@
 If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
-\begin{remark}
+\begin{remark}%[Correlation as the steady state of a $m$-chain ]
 	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
@@
 where the expectation is taken with respect to the $\mu$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$.
+\begin{comment}
+ As a consequence, we can give a different interpretation to correlation computed in \eqref{exactCorrelations}.
+Consider the sites $(x_{k})_{k\in \{1,\ldots,m\}}$ and fix $(a_{k})_{k\in \{1,\ldots,m\}}$ introduced in Theorem \ref{thm-correlations}.
+We define a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$.
+We denote by $|\Psi_{m}\rangle$ the non-equilibrium steady state of this $m$-chain.
+Then, we have that the correlations computed in \eqref{exactCorrelations} can be written as
+\begin{equation}
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\Psi_{m}(a_{1},\ldots,a_{m})
+\end{equation}
+This means that we can define a mapping between the $m$-point correlation of chain of length $L$ and the non-equilibrium steady state of a chain of length $m$. This mapping, 
+\end{comment}
 	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.

### 2023-11-21 main.tex
''

@@
 Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
-\begin{equation}
+\begin{equation}\label{NESS-expectation-ABS}
 \mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
@@
 \end{remark}
-    \begin{corollary}
-ADD
+    \begin{corollary}[Non-equilibrium steady state measure]\label{Corollary-NESS-ABS}
+For any configuration $\bm{\tau}\in \Omega^{'}$ the non-equilibrium steady state probability mass function is given by 
+\begin{equation}\label{implicit-mass-function}
+	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\right]
+\end{equation}
+where the expectation, computed with respect to the process $\bm{\sigma}$, is given in \eqref{NESS-expectation-ABS} in terms of absorption probabilities. 
 \end{corollary}
+\textbf{Proof:}
+Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
+\begin{align}
+	\mu\left(\bm{\tau}\right)=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
+	=\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\right]\nonumber\\
+	=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\right)\right)\right]
+	%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
+	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
+	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
+	%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
+\end{align}
+where in the last equality we exploited the fact that 
+\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}
+\end{equation}
+The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
+Then, we rewrite the argument of the expectation above as
+\begin{align}
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\right)\right)\nonumber\\
+=&
+\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{\sigma_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}
+\end{align} 
+Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 
+\begin{flushright}
+	$\square$
+\end{flushright}
 
@@
 \begin{remark}[Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution]
-We argue as in the previous proof. For any given $\bm{\tau}\in \Omega^{'}$ we have that 
+We argue as in the previous proof. For any $\bm{\tau}\in \Omega^{'}$ we have that 
 \begin{align}
@@
  \end{equation} 
-Then, we have that
-\begin{equation}
-	\Psi(\bm{\tau})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})
-\end{equation}
-where 
+Observe that, if $\ell=0$ then $\Omega_{\ell}^{'}(\bm{\tau})$ does coincide with the whole state space $\Omega^{'}$, while, if $\ell=L$ then $\Omega_{\ell}^{'}(\bm{\tau})$ reduces to the configuration $\bm{\tau}$.
+Denoting the marginal on $\ell$ sites of the steady state distribution by
 \begin{equation}
@@
 \end{equation}
-is marginal on $m$ sites of the steady state distribution.  
+we have that 
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}_{\mu}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{\sigma_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})
+\end{align} 
+It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution, in the sense described above.
+In particular, when the configuration $\bm{\tau}$ has at $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function.
+As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
 \end{remark}
@@
 \begin{equation}\label{SteadyState-coeff-implicit}
-	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{1-\delta_{\tau_{x},N}}\right]
-\end{equation}
-where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
+	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\right]
+\end{equation}
+where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and are computed using \eqref{exactCorrelations}. 
 %	and where 
@@
 
-	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$.
-Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain.
-This matrix $\mathcal{S}_{1}$ is given by
+	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}}
+	The elements $\Psi(\bm{\tau})$ of the vector $|\Psi\rangle$ are the probabilities of having a certain configuration $\bm{\tau}\in \Omega^{'}$ in the non-equilibrium steady state, i.e.
+	\begin{equation}
+		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle= \mu(\bm{\tau})
+	\end{equation}
+ Therefore, they are given by the probability mass function of equation \eqref{implicit-mass-function} in Corollary \ref{Corollary-NESS-ABS}. 
+	\begin{flushright}
+		$\square$
+	\end{flushright}
+\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]
+	 As a consequence of \eqref{S1-Inverse}, the non-equilibrium steady state $|\Psi\rangle$ can also be obtained by inverting the similarity transformation $S_{1}$. On a single site we have that 
 	\begin{equation}\label{S1-L1}
@@
 	\begin{equation}\label{Tensor-S1}
-		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
+		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)
 	\end{equation}
@@
 			\begin{align}
-				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
 			\end{align}
@@
 		\begin{equation}\label{notation-PSI}
-			\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
 		\end{equation}
@@
 In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
-From Section \ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}.
-Thus, we have that
+Finally, using equation \eqref{interpretation-PsiP}, the result follows.
+	\end{remark}
+		\begin{comment}
+
+		From Section \ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}. Thus, we have that  
 			\begin{equation}
@@
 		\end{equation}
+	\end{comment}
 			%	\begin{equation}
@@
 			\end{comment}
-			Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
-			\begin{flushright}
-				$\square$
-			\end{flushright}
+		%	Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
+		%	\begin{flushright}
+		%		$\square$
+		%	\end{flushright}
+		\begin{comment}
 		\begin{remark}
@@
 			\end{align}
-		where in the up to last line we exploited the fact that 
+		where in the last equality we exploited the fact that 
 		\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}
@@
 			\end{remark}
+		\end{comment}
 		\begin{comment}

### 2023-11-21 main.tex
^^

@@
 \paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
-Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain.
 Using the exponential series we have that
@@
 \begin{align}\label{ABS_intermediate}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]
 	\end{align}
@@
 %For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, \\ \\ 
-We rewrite the above equation as
+We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\tau_{x},\sigma_{x}\in \{1,\ldots,N\}$, we have 
+\begin{align}
+	\delta_{\tau_{x},\sigma_{x}}+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})=&\delta_{\tau_{x},\sigma_{x}}(\delta_{\sigma_{x},N}+1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
+	=&\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
+	=&\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})
+\end{align}
 %\begin{equation}
@@
 %To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain
-\begin{align}
-	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
-	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
-	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
-	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-\end{align}
+%\begin{align}
+%	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
+%	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
+%	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+%	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
+%	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
+%\end{align}
 %Consider the factor $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}$ in the above equation.
@@
 It follows that
-We observe that, for all $x\in \{1,\ldots,L\}$,
-\begin{equation}
-	\begin{split}
-	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\
+It follows that 
+\begin{equation}
+	\begin{split}
+	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\
 	=&\begin{cases}
@@
 \end{equation}
-Thus, it follows that 
-\begin{equation}
-	\begin{split}
-	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-	\end{split}
-\end{equation}
-Therefore we have that
+Therefore we can replace $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$ with $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ in \eqref{ABS_intermediate}. 
+%\begin{equation}
+%	\begin{split}
+%	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
+%	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
+%	\end{split}
+%\end{equation}
+As a consequence we rewrite \eqref{ABS_intermediate} as 
 \begin{align}
@@
 \end{align}
-We introduce the summation indices $c_{x}\in \{\delta_{\tau_{x},N},1\}$ for all $x\in \{1,\ldots,L\}$.
-and we observe that 
+For all $x\in \{1,\ldots,L\}$ we introduce the summation index $c_{x}\in \{\delta_{\tau_{x},N},1\}$ and we have that 
 \begin{align}
-	&\sum_{\sigma_{x}=1}^{N}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-	=
-	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
-\end{align} Then, we replace the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$ as 
+	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+	=&
+	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+\end{align} 
+and
+\begin{align}
+	\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)=\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)
+\end{align}
+Then, by replacing the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$, we obtain  
 \begin{equation}
@@
 %Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
-Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
+Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, \eqref{ABS-vect} follows.
 \begin{flushright}
@@
 \end{flushright}
-\begin{remark} By changeing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
 \begin{equation}\label{ABS_1}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(L+2-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt
+	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(L+2-\sum_{x=1}^{L}c^{'}_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}\dt
 \end{equation}
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-c_{j})\right)
+	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)
 \end{equation}
@@
 \end{align}
-We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it in a vector of dimension $L$ to one of dimension $L+2$.
+We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.
 More explicitly, this dual configuration is given by
@@
  where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$.
-Equation \eqref{interpretation-PsiP} will be useful in the exact formula for the steady state.
-Given $\bm{\tau}$ as before, we can introduce $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ the number of occupied sites.
-Then we denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle is present.
+Equation \eqref{interpretation-PsiP} will be useful in Remark \ref{remark-NESS-invertingS1}.
+Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
+We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present.
 Finally, we call
@@
 \subsection{Steady state}\label{appB}
-In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}.
-This formula follows from the ground state $|\Psi^{'}\rangle$ found in \eqref{ABS_1}.
+In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula follows from Corollary \ref{Corollary-NESS-ABS}.
 \begin{corollary}[Non-equilibrium steady state]
@@
 	\end{flushright}
-\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]
+\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]\label{remark-NESS-invertingS1}
 	 As a consequence of \eqref{S1-Inverse}, the non-equilibrium steady state $|\Psi\rangle$ can also be obtained by inverting the similarity transformation $S_{1}$. On a single site we have that 
@@
 			\end{equation} we obtain  
-			\begin{align}
+			\begin{align}\label{implicit-PSI-PSIp}
 				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
@@
 			\begin{cases}
-				\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
+				\tau_{x}=a_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
 				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
@@
 		\end{equation}
-		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$.
+		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$.
 In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
@@
 \end{flushright}
-\paragraph{$|\Psi^{''}\rangle$ for SSEP} When we stop distinguishing colours we have that 
+\paragraph{$|\Psi^{''}\rangle$ for SSEP} The ground state of $H^{''}$ is 
 \begin{equation}\label{psiII-SSEP}
@@
 \end{flushright}
-\paragraph{$|\Psi^{'}\rangle$ for SSEP} In the colour-blind case, the ground state of $H^{'}$ reads
+\paragraph{$|\Psi^{'}\rangle$ for SSEP} The ground state of $H^{'}$ reads
 \begin{equation}
@@
 \end{equation}
-\textbf{Proof}: the proof follows from \eqref{implicit-steadyState} and \eqref{PsiI-N2}. 
+\textbf{Proof}: the proof follows from \eqref{implicit-PSI-PSIp} and \eqref{PsiI-N2}. 
 \begin{flushright}

### 2023-11-21 main.tex
Update

@@
  A new technique to compute absorption probabilities has been proposed in \cite{floreani2023non}.
+ \\
+ \\
+ \textbf{Some interesting references and extensions?}:
+ Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
+ Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
+ Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
+ Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
+Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.
+
 \paragraph{Organization of the paper}
@@
 \begin{equation}
-    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|
-\end{equation}
-
+    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|\dt
+\end{equation}
 We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $gl(N)$
 \begin{equation}\label{secondCasimir}
-    C=\sum_{a,b=1}^{N}E_{ab}E_{ba}
+    C=\sum_{a,b=1}^{N}E_{ab}E_{ba}\co
 \end{equation}
@@
 		0\quad \text{otherwise}
-	\end{cases}
+	\end{cases}\dt
 \end{equation}
@@
 \begin{equation}
-	H_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
+	H_{\text{bulk}}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}\dt
 \end{equation}
@@
 \begin{equation}\label{notation-change-relation}
-	n_{a}^{x}=\delta_{\tau_{x},a}
+	n_{a}^{x}=\delta_{\tau_{x},a}\dt
 \end{equation}
@@
 \begin{equation}
-	\Omega^{'}=\left\{(\tau_{1},\ldots,\tau_{L})\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
+	\Omega^{'}=\left\{(\tau_{1},\ldots,\tau_{L})\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}\dt
 \end{equation}
@@
 \end{equation}
+and 
 \begin{equation}
@@
 \begin{equation}\label{dualityRelationGenerator}
-    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)
+    \left(\mathcal{L}D(\cdot,\xi)\right)(\eta)=\left(\widetilde{\mathcal{L}}D(\eta,\cdot)\right)(\xi)\dt
 \end{equation}
@@
 \begin{equation}
-    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')
+    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')\co
 \end{equation}
@@
 \begin{equation}\label{transpositionPropertyR}
-(E_{ba}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V
+(E_{ba}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V\co
 \end{equation}
@@
 Fix an arbitrary site $x\in V$, then we have that 
-\begin{align*}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
+\begin{align}
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
 	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
-\end{align*}
+\end{align}
 where we used \eqref{transpositionPropertyR}. \\
 On one hand, on the extra-site $u(x)$ we have 
-\begin{align*}
+\begin{align}
 \sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
-\end{align*}
+\end{align}
 where  we used the orthogonality relation \eqref{ortho}. 
 On the other hand, on the site $x$, we have 
-\begin{align*}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
+\begin{align}
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)\nonumber
 \\&
-\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
 %\\&=
@@
 \\&=
-\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}
+\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}\nonumber
 \\& 
-\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
+\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
 \\&=
 \frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
-\end{align*}
+\end{align}
 where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
@@
 	\\=&
-	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}
+	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
 \end{align}
@@
 %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
-\begin{corollary}[Correlations via duality]
+\begin{corollary}[Correlations via duality]\label{Corolollary-ABS_Corr-abstract}
 \label{prop-absorbing}
@@
 		\xi_{a}^{x}=0\qquad \text{otherwise}
-	\end{cases}
+	\end{cases}\dt
 \end{equation}
 \end{corollary}
-\textbf{Proof}:
+\textbf{Proof of Corollary \ref{Corolollary-ABS_Corr-abstract}}:
 For any $\bm{\tau}\in \Omega^{'}$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
@@
 \end{corollary}
-\textbf{Proof:}
+\textbf{Proof of \ref{Corollary-NESS-ABS}:}
 Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
@@
 where in the last equality we exploited the fact that 
-\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}
+\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\dt
 \end{equation}
@@
 +&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{\sigma_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\dt
 \end{align} 
@@
 \begin{equation}\label{powerCoeffNOspec}
-	f(c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
+	f(c_{1},\ldots,c_{m})=\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}
 \end{equation}
@@
 \begin{equation}\label{powerCoeffSpecies}
-	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}
+	g_{j}(x_{j},c_{j},\ldots,c_{m})=\left(L+2-x_{j}-\sum_{k=j}^{m}c_{k}\right)^{c_{j}}\dt
 \end{equation}
@@
 	&\mathcal{P}_{x_{1},x_{2}}(1,1)=\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}
-	\end{split}
+	\end{split}\dt
 \end{equation}
@@
 	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,1,1)=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}
-\end{split}
+\end{split}\dt
 \end{equation}
@@
         0\quad \text{otherwise}
-    \end{cases}
+    \end{cases}\dt
 \end{equation}
@@
 %and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
-\paragraph{Proof of formula \eqref{ResulsBasis}} 
+\paragraph{Proof of \eqref{ResulsBasis}} 
 %In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof.
@@
      X_{N}
-	\end{pmatrix}%\quad \forall a\in \{1,\ldots,N-1\}\dt
+	\end{pmatrix}\dt%\quad \forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 				X_{1}+\ldots +X_{N}\\
-	\end{pmatrix}%=\begin{pmatrix} 
+	\end{pmatrix}\dt%=\begin{pmatrix} 
 	%	X_{a}-\beta_{a}\Xt_{N}\\ 
@@
 		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
-	\end{pmatrix}%\qquad\forall a\in \{1,\ldots,N-1\}\dt
+	\end{pmatrix}\dt%\qquad\forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\qquad %\forall a\in \{1,\ldots,N-1\}\dt
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation}\label{commLEFT}
-	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
+	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle\co W|%\qquad\forall a=1,\ldots,N-1
 \end{equation}
@@
 \begin{equation}\label{UsefulRelation}
-	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)
+	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left((\alpha_{a}-\beta_{a})+\widetilde{X}_{a}\right)\dt
 \end{equation}
@@
 %	\\&=\ldots\\&=
-	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}
+	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}\dt
 \end{align}
@@
 	\frac{(1+n)!}{n!}\frac{n!}{(n-1)!}\ldots \frac{3!}{2!}\frac{2!}{1!}\langle W|\widetilde{X}_{N}^{0}|V\rangle=
-	(1+n)!
+	(1+n)!\dt
 \end{align}
@@
 	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
+	|V \rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
 \end{equation}
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}
+	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\dt
 \end{equation}
@@
 =&\frac{1}{(L+1)!}\prod_{x=1}^{L}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},x})!}\nonumber\\
-=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\dt
 \end{align}
@@
 		\begin{split}
-			\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
+			\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
 		\end{split}
@@
 \begin{equation}\label{goodTP-S2}
-  \langle \bm{\tau}|S_{2}^{-1} |\bm{\sigma}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\sigma_x}+\delta_{N,\sigma_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]
+  \langle \bm{\tau}|S_{2}^{-1} |\bm{\sigma}\rangle=\prod_{x=1}^L\left[ \delta_{\tau_x,\sigma_x}+\delta_{N,\sigma_x}\beta_{\tau_x} (1-\delta_{\tau_x,N})\right]\dt
 \end{equation} 
@@
 \begin{align}\label{ABS_intermediate}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]\dt
 	\end{align}
@@
 	=&\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
-	=&\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})
+	=&\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\dt
 \end{align}
@@
 		(\alpha_{\tau_{x}}-\beta_{\tau_{x}})+\beta_{\tau_{x}}\qquad &\text{if}\quad \tau_{x}\neq N\\
-		1\qquad &\text{if}\quad \tau_{x}= N
+		1\qquad &\text{if}\quad \tau_{x}= N\dt
 	\end{cases}
@@
 \Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\dt
 %=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
@@
 \begin{align}
-	\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)=\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)
+	\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)=\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\dt
 \end{align}
@@
 \begin{equation}
-	\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
+	\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}\dt
 \end{equation}
@@
 \begin{equation}\label{ABS_1}
-	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(L+2-\sum_{x=1}^{L}c^{'}_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}\dt
+	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
 \end{equation}
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)
+	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
 \end{equation}
@@
 \begin{equation}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
 \end{equation}
@@
 \begin{equation}
-	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})
+	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
 \end{equation}
@@
 	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
-	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
 \end{align}
@@
 	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
-	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle
+	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
 \end{align}
@@
 \begin{align}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
+	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 \begin{align}
-	&\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&
+	&\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
 	\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 \begin{align}
-	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\sigma\in \Omega}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle
+	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\sigma\in \Omega}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
 \end{align}
@@
 	\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
-\end{cases}
+\end{cases}\dt
 \end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
 \begin{align}
-	\Psi^{'}(\bm{\tau})=&\sum_{\sigma\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle
+	\Psi^{'}(\bm{\tau})=&\sum_{\sigma\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
 \end{align}
@@
 		1\qquad  &\text{if}\quad \tau_{x}= N
-	\end{cases}
+	\end{cases}\dt
 \end{equation}
@@
  	\begin{equation}\label{interpretation-PsiP}
- 	\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]
+ 	\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
  \end{equation} 
@@
  \begin{equation}
- 	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}
+ 	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}\dt
  \end{equation} 
@@
 \begin{align}
-	\Psi^{'}(\bm{\tau})=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}_{\mu}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{\sigma_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})
+	\Psi^{'}(\bm{\tau})=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}_{\mu}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{\sigma_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
 \end{align} 
@@
 	\begin{equation}
-		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\dt
+		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
 	\end{equation}
@@
 	\begin{equation}
-		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle= \mu(\bm{\tau})
+		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle= \mu(\bm{\tau})\dt
 	\end{equation}
@@
 	\end{equation}
-	thus
+	thus,
 	\begin{equation}
@@
 	\begin{equation}\label{Tensor-S1}
-		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)
+		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\dt
 	\end{equation}
@@
 			\begin{equation}
-				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle
+				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
 			\end{equation} we obtain  
@@
 				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
-			\end{cases}
+			\end{cases}\dt
 		\end{equation}
@@
 \end{equation}
-where 
-\begin{equation}
-	H_{x,x+1}=\sum_{a,b=1}^{2}\left(e_{ab}\otimes e_{ba}-e_{bb}\otimes e_{aa}\right)
-\end{equation}
-and 
+where the bulk Hamiltonian densities are 
+\begin{equation}
+	H_{x,x+1}=\sum_{a,b=1}^{2}\left(e_{ab}\otimes e_{ba}-e_{bb}\otimes e_{aa}\right)\dt
+\end{equation}
+Here $e_{ab}$ are the basis elements of the fundamental representation of $gl(2)$. The boundary Hamiltonians are
 \begin{equation}
@@
 	\beta_{2}&1-\beta_{2}
-\end{pmatrix}
+\end{pmatrix}\dt
 \end{equation}
@@
 	0&1
-\end{pmatrix}
+\end{pmatrix}\dt
 \end{equation}
@@
 	0&0
-\end{pmatrix}
-\end{equation}
-and $H^{''}$ has the following boundaries 
+\end{pmatrix}\co
+\end{equation}
+while the boundary Hamiltonians of $H^{''}$ are
 \begin{equation}
@@
 	0&0
-\end{pmatrix}
-\end{equation}
- We only report the main results, since the computations are just a specific case of the ones done in this section for the multi-species stirring process. 
+\end{pmatrix}\dt
+\end{equation}
+ We only report the main results, since the computations are just a specific case of the ones done for the multi-species stirring process. 
 \paragraph{Correlations of SSEP}
@@
 \end{equation} 
-\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
-There are many values of $c$'s that give the same $q$, therefore we define $q$ labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
-To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
-Therefore, we have
-	\begin{equation}
-		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)
-	\end{equation}
-Moreover, we observe that for fixed $q$ we have
+\textbf{Proof of \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
+There are many values of $c$'s that give the same $q$, therefore we define $q$ %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
+$1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$.
+To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
+Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$.
+Then, we obtain
+	\begin{equation}
+		\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)\dt
+	\end{equation}
+Indeed, in the product on the left hand side only $q$ terms at coordinates $x_{\ell_{1}},\ldots x_{\ell_{q}}$ do survive. Moreover, any fixed $x_{\ell_{k}}$ has $q-k$ occupied sites at its right.
+Furthermore, sing the properties of the factorials, we have that 
 \begin{equation}\label{Gamma-product}
-	\frac{\Gamma(L+2-\sum_{k=1}^{m}c_{k})}{\Gamma(L+2)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
+	\frac{(L+1-\sum_{k=1}^{m}c_{k})!}{(L+2)!}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
 \end{equation}
@@
 \begin{equation}
-	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{\Gamma(L+2-\sum_{k=1}^{m}c_{k})}{\Gamma(L+2)}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
-\end{equation}
-thus, \eqref{correlations-SSEP} follows. 
+	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{(L+1-\sum_{k=1}^{m}c_{k})!}{(L+1)!}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
+\end{equation}
+and \eqref{correlations-SSEP} follows. 
 \begin{flushright}
@@
 \end{equation}
-\textbf{Proof:} 
+where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. \\ \\
+\textbf{Proof of \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the colour-blind case.
 We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
-Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
-Thus, arguing as before and using \eqref{Gamma-product} we have that
-\begin{align}
-	&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
-	=(\alpha_{1}-\beta_{1})_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
+For each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
+Thus, arguing as in the proof of \eqref{correlations-SSEP} and using \eqref{Gamma-product} we have that
+\begin{align}
+	&\frac{\left(1+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)!}{\left(1+L\right)!}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\nonumber\\%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+	=&\frac{\left(1+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},2})\right)!}{\left(1+L\right)!}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},2})\right)\right]^{1-\delta_{\tau_{x},2}}\nonumber\\
+	=&(\alpha_{1}-\beta_{1})^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}\dt
 \end{align}
@@
 and where $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ . \\ \\
- \textbf{Proof:} For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty.
+ \textbf{Proof of \eqref{PsiI-N2}:}  For any configuration $\bm{\tau}\in \Omega$ we denote by  $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},2}$ the number of occupied sites.
+Then, considering equation \eqref{ABS_1} we have the result by adapting the proof of \eqref{correlations-SSEP} in the following way.
 We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
 We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
-These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
-For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e.
-the coordinate where the particle with label $\ell_{i}$ is placed.
+These $(\ell_{k})_{k\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
+For each $\ell_{k}$ we introduce $x_{\ell_{k}}$, i.e.
+the coordinate where the particle with label $\ell_{k}$ is placed.
 Thus, we have that
-%and we rewrite \eqref{ABS_1} as
-%{\color{red}
-	%\begin{align}
-	%	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
-	%	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
-	%\end{align}
-	%}
-%For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,L\}}$ such that its sum is equal to $q$. For any fixed $L$ values of $(c_{i})_{i\in\{1,\ldots,L\}}$ we have   
 \begin{equation}
@@
 \end{equation}
-Thus, it follows that
+It follows that
 \begin{equation}
@@
 In the colour-blind case we have that 
-\begin{equation}
+\begin{equation}\label{NESS-SSEP}
 	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}\Psi(\bm{\tau})|\bm{\tau}\rangle
@@
 \begin{equation}
-	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},2}\right)\sum_{s=0}^{|\bm{\tau}|+b}(\alpha-\beta)^{s}\beta^{L-s}\sum_{1\leq \ell_{1}<\ldots<\ell_{s}\leq |\bm{\tau}|}\prod_{k=1}^{s}\frac{\left(L+1-x_{\ell_{k}}-s+k\right)}{(2+L-k)}
-\end{equation}
-with
-\begin{equation}
-	|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1} \dt
-\end{equation}
-\textbf{Proof}: the proof follows from \eqref{implicit-PSI-PSIp} and \eqref{PsiI-N2}. 
+	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},2}\right)\sum_{s=0}^{|\bm{\tau}|+b}(\alpha-\beta)^{s}\beta^{L-s}\sum_{1\leq \ell_{1}<\ldots<\ell_{s}\leq |\bm{\tau}|}\prod_{k=1}^{s}\frac{\left(L+1-x_{\ell_{k}}-s+k\right)}{(2+L-k)}\dt
+\end{equation}
+%with
+%\begin{equation}
+%	|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1} \dt
+%\end{equation}
+\textbf{Proof of \eqref{NESS-SSEP}:} the proof follows from \eqref{implicit-PSI-PSIp} and \eqref{PsiI-N2}. 
 \begin{flushright}
@@
 \subsection{Explicit formula for the steady state $|\Psi\rangle$}
-{\color{blue}can we proceed as above? using sth similar to \eqref{goodTP-S2}}
+{\color{blue}can we proceed as above? uing sth similar to \eqref{goodTP-S2}}
 
@@
 We introduce the reversible measure \eqref{reversibleMeasure} conditioned on the conservation of the particles on that bond
-\begin{equation}
-	\begin{split}
-	\nu_{TH}(r|\epsilon):&=\mathbb{P}\left(n^{x}=r|n^{x}+n^{x+1}=\epsilon\right)
+\begin{align}
+	\nu_{TH}(r|\epsilon):&=\mathbb{P}\left(n^{x}=r|n^{x}+n^{x+1}=\epsilon\right)\nonumber
 	\\&
 	=\mathbb{P}\left((n_{1}^{x},\ldots,n_{N}^{x})=
-	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)
-	\end{split}\dt
-\end{equation}
+	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)\dt
+\end{align}
 Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{1,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
-	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{N}=\nu-\sum_{a=1}^{N-1}r_{a}
+	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a},\qquad r_{N}=\nu-\sum_{a=1}^{N-1}r_{a}\dt
 \end{equation}
@@
 	\begin{split}
-\nu_{TH}(r|\epsilon)&=\frac{\mathbb{P}\left(\left\{n^{x}=r\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\epsilon\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}=\frac{\mathbb{P}\left(n^{x}=r\right)\,\mathbb{P}\left(n^{x+1}=\epsilon-r\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}
+\nu_{TH}(r|\epsilon)&=\frac{\mathbb{P}\left(\left\{n^{x}=r\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\epsilon\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}=\frac{\mathbb{P}\left(n^{x}=r\right)\,\mathbb{P}\left(n^{x+1}=\epsilon-r\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}\dt
 	\end{split}
@@
 \begin{align}
-	\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}
+	\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}\dt
 \end{align}
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}\dt
 \end{equation}
@@
 \begin{equation}\label{NSpeciesRD}
-	\frac{d}{dt} \rho_{a}(x,t)=\nu\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\nu\sigma_{12}\sum_{b=1,b\neq a}^{N-1}\Delta_{L}\rho_{b}(x,t)+\Upsilon\sum_{b=1,b\neq a}^{N-1}\left(\rho_{b}(x,t)-\rho_{a}(x,t)\right)
+	\frac{d}{dt} \rho_{a}(x,t)=\nu\sigma_{11}\Delta_{L}\rho_{a}(x,t)+\nu\sigma_{12}\sum_{b=1,b\neq a}^{N-1}\Delta_{L}\rho_{b}(x,t)+\Upsilon\sum_{b=1,b\neq a}^{N-1}\left(\rho_{b}(x,t)-\rho_{a}(x,t)\right)\dt
 \end{equation} 
@@
 		N\quad &\text{if}\quad k=N
-	\end{cases}
+	\end{cases}\dt
 \end{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N-1}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)
+	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N-1}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)\dt
 \end{equation}
@@
 where the $\alpha$'s parameters are defined in function of the given boundary condition of the difference-differential system:
-\begin{equation}\label{boundaryParamRD}
-	\begin{split}
-		\alpha_{a}&=\sigma_{11}\rho_{a}^{0}+\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\rho_{b}^{0}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\\
-		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}
-	\end{split}
-\end{equation}
+\begin{align}\label{boundaryParamRD}
+		\alpha_{a}&=\sigma_{11}\rho_{a}^{0}+\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\rho_{b}^{0}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\nonumber\\
+		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}\dt
+\end{align}
 As a consequence, from the above conditions we can define the boundary values in terms of the reservoir parameters as
@@
 \begin{equation}\label{DifferenceEquation}
-	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{a}^{x})\co
+	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{a}^{x})
 \end{equation}
@@
 \begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)
+	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt
 \end{equation}
@@
 \begin{equation}
-	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt
 \end{equation} 
@@
 \begin{equation}\label{reversibilityConditionRD}
-	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}
+	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}\dt
 \end{equation}
@@
 \begin{equation}
-	\mathcal{H}_{x,x+1}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}\otimes \mathbbm{1}-E_{aa}\otimes \mathbbm{1}\right)
+	\mathcal{H}_{x,x+1}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}\otimes \mathbbm{1}-E_{aa}\otimes \mathbbm{1}\right)\dt
 \end{equation}
@@
 	&(\mathcal{H}_{x,x+1}^{c})^{T}D=D\mathcal{H}_{x,x+1}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
-	&(\mathcal{H}_{x,x+1}^{m})^{T}D=D\mathcal{H}_{x,x+1}^{m}\label{mDualityRelation}
+	&(\mathcal{H}_{x,x+1}^{m})^{T}D=D\mathcal{H}_{x,x+1}^{m}\label{mDualityRelation}\dt
 \end{align}
@@
 \begin{equation}
-	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{d,\ell=1}^{N}\left(E_{\ell a}^{x}\otimes \mathbbm{1}^{x+1}-E_{dd}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0
+	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{d,\ell=1}^{N}\left(E_{\ell a}^{x}\otimes \mathbbm{1}^{x+1}-E_{dd}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0\dt
 \end{equation}
@@
 
-\section{Conclusion and outlook}
-Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
-Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
-Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
-Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
+%\section{Conclusion and outlook}
+%Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
+%Use exact solution to compute large deviation rate function extending to the multi-species case results %proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
+%Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
+%Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
 Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.

### 2023-11-21 main.tex
'
Reversibility correct

@@
 \end{equation}
+{\color{blue}
+In the most general case we have reversibility if 
+\begin{equation*}
+	\alpha_{k}^{x}\left(|\alpha^{y}|-\alpha_{k}^{y}\right)=\alpha_{k}^{y}\left(|\alpha^{x}|-\alpha_{k}^{x}\right)\qquad \forall x,y\in V,\quad \forall k\in \{1,\ldots,N\}
+\end{equation*}
+where
+\begin{equation*}
+	|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}
+\end{equation*}
+this is the multi-species counterpart of $\alpha\delta=\beta\gamma$ of the SEP case (see Section 3.2 of \cite{carinci2013duality}) \\
+Should we say that or can we restrict to the case where $\alpha_{a}^{x}=\alpha_{a}$... Maybe we put a remark.\\
+}
 then the process described by the generator \eqref{Generator} is reversible with respect to the 
@@
 \subsubsection{Formula for correlations}\label{correlation-section}
-We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
+We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.
+We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
 \begin{equation}
@@
 \end{equation}
-We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$ and we have 
+We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
 \begin{equation}

### 2023-11-21 main.tex
''

@@
 \end{equation}
+then the process described by the generator \eqref{Generator} is reversible with respect to the 
+homogeneous product measure 
+\begin{equation}
+\label{reversibleMeasure}
+\mu_{\text{rev}}=\bigotimes_{x\in V}\mu_{\text{rev}}^{x}
+\end{equation}
+with marginals $\mu_{\text{rev}}^{x}$ given by 
+\begin{equation}
+ \mu^{x}_{\text{rev}}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\,.
+\end{equation}
+Here
+ $$
+\rho_{a}=\frac{\alpha_{a}}{|\alpha|}\co
+$$
+is the density of specie $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 
+\begin{equation}
+\mu_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}\,.
+\end{equation}
+This can be proved  by checking that detailed balance is satisfied. 
+If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
+\begin{equation}
+\label{rhox}
+\rho_{a}^x=\frac{\alpha_{a}}{|\alpha^x|}
+\end{equation}
+and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}$. 
+Currents will arise when at least two reservoirs have different densities. 
 	{\color{blue}
+\begin{remark}[Should we add this?]
 		In the most general case we have reversibility if 
@@
 		this is the multi-species counterpart of $\alpha\delta=\beta\gamma$ of the SEP case (see Section 3.2 of \cite{carinci2013duality}) \\
-Should we say that or can we restrict to the case where $\alpha_{a}^{x}=\alpha_{a}$... Maybe we put a remark.\\
+		Should we say that or can we restrict to the case where $\alpha_{a}^{x}=\alpha_{a}$?
+		 Maybe we put a remark. It does not affect duality, since the matrix $R$ that we define in Section \ref{sectionDuality} does not depend on the density of the multinomials.
+		\end{remark}
 	}
-then the process described by the generator \eqref{Generator} is reversible with respect to the 
-homogeneous product measure 
-\begin{equation}
-\label{reversibleMeasure}
-\mu_{\text{rev}}=\bigotimes_{x\in V}\mu_{\text{rev}}^{x}
-\end{equation}
-with marginals $\mu_{\text{rev}}^{x}$ given by 
-\begin{equation}
- \mu^{x}_{\text{rev}}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\,.
-\end{equation}
-Here
- $$
-\rho_{a}=\frac{\alpha_{a}}{|\alpha|}\co
-$$
-is the density of specie $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 
-\begin{equation}
-\mu_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}\,.
-\end{equation}
-This can be proved  by checking that detailed balance is satisfied. 
-If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
-\begin{equation}
-\label{rhox}
-\rho_{a}^x=\frac{\alpha_{a}}{|\alpha^x|}
-\end{equation}
-and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}$. 
-Currents will arise when at least two reservoirs have different densities.
-
 \subsection{Lie algebraic description of the process}

### 2023-11-22 main.tex
Update main.tex

--- 2023-11-21 main.tex
@@
 $$
-is the density of specie $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 
+is the density of species $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 
 \begin{equation}
@@
 This can be proved  by checking that detailed balance is satisfied. 
-If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
+If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost (but see remark \ref{rem-rev} below): 
+each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
 \begin{equation}
@@
 Currents will arise when at least two reservoirs have different densities. 
-
+\begin{remark}
+\label{rem-rev}
+		One can check that the following condition on the reservoir parameters implies reversibility:
+		\begin{equation}
+		\label{cond-gen}
+			\alpha_{k}^{x}\left(|\alpha^{y}|-\alpha_{k}^{y}\right)=\alpha_{k}^{y}\left(|\alpha^{x}|-\alpha_{k}^{x}\right)\qquad\qquad \forall x,y\in V,\quad \forall k\in \{1,\ldots,N\}
+		\end{equation}
+		where
+		\begin{equation}
+			|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}\dt
+		\end{equation}
+		This is slightly more general than \eqref{reversibilityCondition}.
+In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites
+		then condition \eqref{cond-gen} is the multi-species counterpart of $\alpha\delta=\beta\gamma$ of the boundary driven partially excluded process introduced in \cite{schutzSandow} (see Section 3.2 of \cite{carinci2013duality}).
+		\end{remark}
 \subsection{Lie algebraic description of the process}
@@
 can be studied by means of a dual process. After recalling the definition of duality between two
-Markov processes in Section \ref{def-duality}, we formulate duality  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
-The duality result is important since it brings in several simplifications, the main one being that the
-dual process has absorbing sites. Therefore, as shown in Proposition \ref{prop-absorbing}, the study of the non-equilibrium steady state for  the multispecies stirring process with open boundary
+Markov processes in Section \ref{def-duality}, we formulate our duality result  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
+The duality result is important since it yields several simplifications, the main one being that the
+dual process has absorbing sites.
+Therefore, as shown in Corollary \ref{prop-absorbing}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
 is reduced to the study of the absorption probabilities of dual particles.
@@
 \begin{remark}
-when the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$.
+When the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$.
 Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as
@@
 \begin{theorem}[Absorbing duality]\label{thm-duality}
-	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to a process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator
+	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator
 	 \begin{equation}\label{DualGenerator}
@@
 \end{equation}
-where we have introduced the reservoir densities
+where we recall the definition of the reservoir densities (cf. \eqref{rhox})
 \begin{equation}
@@
 In other words the extra-sites play the role of absorbing boundaries.
-\begin{remark} in the reversible situation, i.e.
+\begin{remark} In the reversible situation, i.e.
 when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{\text{rev}} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is
@@
 The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$.
-The duality result stated in Section \ref{statementDualitySubsection} can be adapted.
-The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively.
-The matrix $R_{x}$ defined in \eqref{Revmatrix}
+The duality result stated in Section \ref{statementDualitySubsection} is adapted to the present situation as follows.
+The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
 reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
@@
 Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.
-In the following we denote by $\mu$ the non-equilibrium steady state distribution.
-%For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
+In the following we denote by $\mu$ the non-equilibrium steady state distribution and we call $\bm{Y} = (Y_1,\ldots,Y_L)$ the random vector with law $\mu$.
+Furthermore we write $\mathbb{E}[\cdot]$ for the expectation with respect to $\mu$.%For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
 \begin{corollary}[Correlations via duality]\label{Corolollary-ABS_Corr-abstract}
 \label{prop-absorbing}
-Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$.
-Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
+Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
+$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then, the $m$-point correlations in the non-equilibrium steady state read
 \begin{equation}\label{NESS-expectation-ABS}
-\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \end{equation}
-is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$.
-The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
+where the initial dual configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
 \begin{equation}
@@
 \end{equation}
+In \eqref{absProbabilitiesIntegrable} the variable $t_k$ is $1$ (resp.
+$0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $\{0\}$ (resp.
+$\{L+1\}$).
 \end{corollary}
@@
 \end{equation}
-Therefore, by duality and ergodicity we have 
+Therefore, by ergodicity and duality  we have 
 \begin{equation}\label{CorrelationByABS-prob}
 	\begin{split}
-\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
 	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
@@
 \end{equation}
+\begin{flushright}
+	$\square$
+\end{flushright} 
+    \begin{corollary}[Non-equilibrium steady state]\label{Corollary-NESS-ABS}
+For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is given by 
+\begin{equation}\label{implicit-mass-function}
+	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}
+	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\right)\right]\,.
+\end{equation}
+\end{corollary}
+\textbf{Proof of Corollary \ref{Corollary-NESS-ABS}:}
+Given $\bm{\tau}\in \Omega^{'}$,  we have 
+\begin{align}
+	\mu\left(\bm{\tau}\right)=&\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]
+	=\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_x\}}\right)\right]\nonumber\\
+	=&\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}\right)\right)\right]
+	%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
+	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{Y_x=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
+	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
+	%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
+\end{align}
+where in the last equality we exploited the fact that 
+\begin{equation}			\mathbbm{1}_{\{Y_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}\dt
+\end{equation}
+The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ sites are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
+Therefore, we may write
+\begin{align}
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=a_{x}\}}\right)\right)\nonumber\\
+=&
+\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\dt
+\end{align} 
+Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 
 \begin{flushright}
@@
 \begin{remark}
-	The result written in the previous Corollary \ref{prop-absorbing} holds also for chains with higher maximal occupancy ($\nu>1)$, as specified in Section \ref{Subsection-ss-nonI}. 
+	The results in Corollary \ref{Corolollary-ABS_Corr-abstract} and in Corollary \ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for higher maximal occupancies $\nu >1$.
+	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
+	Thus we chose to present them in such a context.
 \end{remark}
-    \begin{corollary}[Non-equilibrium steady state measure]\label{Corollary-NESS-ABS}
-For any configuration $\bm{\tau}\in \Omega^{'}$ the non-equilibrium steady state probability mass function is given by 
-\begin{equation}\label{implicit-mass-function}
-	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\right]
-\end{equation}
-where the expectation, computed with respect to the process $\bm{\sigma}$, is given in \eqref{NESS-expectation-ABS} in terms of absorption probabilities. 
-\end{corollary}
-\textbf{Proof of \ref{Corollary-NESS-ABS}:}
-Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
-\begin{align}
-	\mu\left(\bm{\tau}\right)=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-	=\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\right]\nonumber\\
-	=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\right)\right)\right]
-	%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
-	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
-	%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
-\end{align}
-where in the last equality we exploited the fact that 
-\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\dt
-\end{equation}
-The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
-Then, we rewrite the argument of the expectation above as
-\begin{align}
-&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\right)\right)\nonumber\\
-=&
-\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{\sigma_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\dt
-\end{align} 
-Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 
-\begin{flushright}
-	$\square$
-\end{flushright}
-
-\section{Exact steady state and correlations for the integrable chain}\label{sectionIntegrabiliy}
-In this section we combine duality and the matrix product ansatz (MPA) to determine the correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Section \ref{integrableChain-duality}.
-As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption correlations and thus (using Proposition \ref{prop-absorbing}) for the correlations.
+
+\section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
+In this section we combine duality and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Section \ref{integrableChain-duality}.
+As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary \ref{Corolollary-ABS_Corr-abstract}) for the correlations
+and (using Corollary \ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
+We start by recalling the formulation of the MPA  and then we explain our strategy.
+
 \subsection{Matrix product ansatz for the non-equilibrium steady state}
@@
 
- In the next Section \ref{subsection-exact} we will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the algebra of operators.
-The idea is summarized in the following scheme.
+\subsection{Strategy}
+ In the next Section \ref{subsection-exact} we will show that the existence of the absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the algebra of operators $X_a$ defined in previous
+ section.  The idea is summarized in the following scheme. 
  We define a sequence of similarity transformation such that 
@@
  The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
-Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlation in the non-equilibrium steady state.
-The second transformation $S_{2}$ diagonalizes the right boundary.
-Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra.
-\subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
+Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlations in the non-equilibrium steady state.
+ %The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
+\subsection{Correlations in the non-equilibrium steady state}\label{subsection-exact}
 In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain.
 \begin{theorem}[Correlations in the non-equilibrium steady state]\label{thm-correlations}
-Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
-and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu$ are given by 
+%Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
+%and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. 
+Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
+$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure are given by 
 \begin{equation}\label{exactCorrelations}
-\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \end{comment}
-\subsubsection{Examples of non-equilibrium steady state correlations}
+\subsubsection{Examples}
 We give examples  of correlations for $m=1,2,3$ applying formula \eqref{exactCorrelations}.
@@
 \begin{equation}\label{one-pts-corr}
-		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
+		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
 \end{equation}
@@
 	\begin{split}
-		 \mathbb{E}_{\mu}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
+		 \mathbb{E}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 By exploiting a binomial formula we rewrite the correlations in terms
-	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities.
-For completeness, we also provide the expression of the steady state $|\Psi\rangle$ in Appendix \ref{appB}.
+	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary \ref{Corolollary-ABS_Corr-abstract}.
+	For completeness, we also show that Corollary \ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$.
 	\end{itemize}
@@
 \end{comment}
-\subsubsection{Explicit formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
+\subsubsection{Closed formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
 \begin{comment}
@@
 %and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
-\paragraph{Proof of \eqref{ResulsBasis}} 
+\paragraph{Proof of formula \eqref{ResulsBasis}} 
 %In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof.
@@
 \end{flushright} 
-\subsubsection{Explicit formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
+\subsubsection{Closed formula for $|\Psi^{'}\rangle$}\label{subsectionSSdual}
 By knowing the ground state  of the Hamiltonian $H^{''}$ we use \eqref{S2-Inverse} to retrieve the ground state of the Hamiltonian $H^{'}$. The result is the following 
@@
 \begin{equation}
-  \mathcal{S}_{2}^{-1} |\sigma\rangle= |\sigma\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
+  \mathcal{S}_{2}^{-1} |\sigma\rangle= |\sigma\rangle+\delta_{N,\sigma}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
 \end{equation} 
@@
 \begin{equation}
- S_{2}^{-1} |\bm{\sigma}\rangle=\left( |\sigma_1\rangle+\delta_{N,\sigma_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\sigma_L\rangle+\delta_{N,\sigma_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\dt
+ S_{2}^{-1} |\bm{\sigma}\rangle=\left( |\sigma_1\rangle+\delta_{N,\sigma_1}\sum_{a_1=1}^{N-1}\beta_{a_1}|a_1\rangle\right)\otimes\ldots\otimes \left( |\sigma_L\rangle+\delta_{N,\sigma_L}\sum_{a_L=1}^{N-1}\beta_{a_L}|a_L\rangle\right)\dt
 \end{equation} 
@@
 %\begin{align}
-%	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
+%	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,Y_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,Y_x}\right]\nonumber\\
 %	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
@@
 \end{remark}
-\subsubsection{Formula for correlations}\label{correlation-section}
-We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
-\begin{equation}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
-\end{equation}
-We fix $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$ and we have 
+\subsubsection{Closed formula for correlations}\label{correlation-section}
+We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.
+We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
+\begin{equation}
+	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+\end{equation}
+We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
 \begin{equation}
@@
 \begin{align}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
 	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
@@
 \begin{align}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
+	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
 	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
@@
 \begin{align}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
+	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{(L+1-\sum_{a=1}^{m}c_{a})!}{(L+1)!}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\nonumber\\
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 \begin{align}
-	&\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
+	&\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
 	\sum_{c_{1},\ldots,c_{m}=0}^{1}
@@
 				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
+				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},Y_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
 				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})

### 2023-11-23 main.tex
''

@@
 %For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, \\ \\ 
-We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\tau_{x},\sigma_{x}\in \{1,\ldots,N\}$, we have 
-\begin{align}
-	\delta_{\tau_{x},\sigma_{x}}+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})=&\delta_{\tau_{x},\sigma_{x}}(\delta_{\sigma_{x},N}+1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
-	=&\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
-	=&\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\dt
-\end{align}
+We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\bm{\tau},\bm{\sigma}\in\Omega^{'}$, we have 
+\begin{align}
+	\left[\delta_{\tau_{x},\sigma_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\beta_{\tau_{x}}\right]\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}=	\left[\delta_{\tau_{x},\sigma_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\beta_{\tau_{x}}\right]\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\dt
+\end{align}
+Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$.
+On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=1=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}$.
+\\
+Moreover, we have that 
+\begin{align}
+	\delta_{\sigma_{x},\tau_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\beta_{\tau_{x}}=&\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\tau_{x},\sigma_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right)\nonumber\\
+	=&\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+(1-\delta_{\tau_{x},N})\delta_{\sigma_{x},N}\right)\nonumber\\
+	=&\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)
+\end{align}
+Indeed: if $\tau_{x}=\sigma_{x}N$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$. 
 %\begin{equation}
@@
 It follows that
-It follows that 
-\begin{equation}
-	\begin{split}
-	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\
-	=&\begin{cases}
-		(\alpha_{\tau_{x}}-\beta_{\tau_{x}})+\beta_{\tau_{x}}\qquad &\text{if}\quad \tau_{x}\neq N\\
-		1\qquad &\text{if}\quad \tau_{x}= N\dt
-	\end{cases}
-\end{split}
-\end{equation}
-Therefore we can replace $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$ with $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ in \eqref{ABS_intermediate}. 
 %\begin{equation}
@@
 %\end{equation}
-As a consequence we rewrite \eqref{ABS_intermediate} as 
+As a consequence we can write \eqref{ABS_intermediate} as 
 \begin{align}
 \Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\dt
+=&\frac{1}{(L+1)!}\sum_{\bm{\sigma}\in \Omega^{'}}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\&\left[\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)\right]\dt
 %=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
@@
 \end{align}
-For all $x\in \{1,\ldots,L\}$ we introduce the summation index $c_{x}\in \{\delta_{\tau_{x},N},1\}$ and we have that 
-\begin{align}
-	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-	=&
-	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
-\end{align} 
-and
-\begin{align}
-	\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)=\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\dt
-\end{align}
-Then, by replacing the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$, we obtain  
+We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether $\sigma_{x}$ is occupied or empty.
+Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$.
+Thus, we obtain
+\begin{align}
+\Psi^{'}(\bm{\tau})	=&\frac{1}{(L+1)!}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\left[\beta_{\tau_{x}}^{c_{x}}\left(c_{x}+(1-c_{x})(1-\delta_{\tau_{x},N})\right)\right]\dt
+\end{align}
+Moreover, because of the term $\delta_{\tau_{x},N}(1-c_{x})$, we can make vary the indices $c_{x}$ in the set $\{\delta_{\tau_{x},N},1\}$.
+Indeed, when $c_{x}=0$, the addend of the summation is non-vanishing only if $\tau_{x}=N$.
+Therefore, we obtain
 \begin{equation}
@@
 Then, equation  \eqref{ABS_intermediate} reads
-Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally obtain
+Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally have
 \begin{equation}\label{elementsABS}
 	\begin{split}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
+		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
 	\end{split}

### 2023-11-23 main.tex
^'^

@@
 Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$.
-On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=1=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}$.
+On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$.
 \\
@@
 \end{align}
-Indeed: if $\tau_{x}=\sigma_{x}N$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$. 
+Indeed, considering the first and last equalities we have that: if $\tau_{x}=\sigma_{x}$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$.
 %\begin{equation}
@@
 \end{align}
-We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether $\sigma_{x}$ is occupied or empty.
+We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether, at each site $x$, $\sigma_{x}$ is occupied or empty.
 Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$.
@@
 \end{align}
-Moreover, because of the term $\delta_{\tau_{x},N}(1-c_{x})$, we can make vary the indices $c_{x}$ in the set $\{\delta_{\tau_{x},N},1\}$.
-Indeed, when $c_{x}=0$, the addend of the summation is non-vanishing only if $\tau_{x}=N$.
+Moreover, because of the term $(1-\delta_{\tau_{x},N})(1-c_{x})$ we can make the indices $c_{x}$ vary in the set $\{\delta_{\tau_{x},N},1\}$.
+Indeed, when $c_{x}=0$, this term is non-vanishing only if $\tau_{x}\neq N$.
 Therefore, we obtain
@@
 \end{flushright}
-\begin{remark}[Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution]
-We argue as in the previous proof. For any $\bm{\tau}\in \Omega^{'}$ we have that 
+\subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
+We argue similarly as in the Section \ref{correlation-section}. For any $\bm{\tau}\in \Omega^{'}$ we have that 
 \begin{align}
@@
 \end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
-\begin{align}
+\begin{align}\label{useful-InInterpretation}
 	\Psi^{'}(\bm{\tau})=&\sum_{\sigma\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
 \end{align}
-We observe that for any $x\in \{1,\ldots,L\}$ the duality function \eqref{ElementsDualityMatrixChain_1} is
-\begin{equation}
-	d_{x}(\sigma_{x},\xi^{x}(\bm{\tau}))=\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
+We observe that for any $x\in \{1,\ldots,L\}$
+\begin{equation}
+	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
+	%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
+	%	1\qquad  &\text{if}\quad \tau_{x}= N
+%	\end{cases}\dt
+\end{equation}
+Indeed, we have that 
+\begin{equation}
+	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
 			\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
@@
 \end{equation}
- Therefore, we obtain 
+ Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation \ref{useful-InInterpretation}, we obtain 
  	\begin{equation}\label{interpretation-PsiP}
- 	\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
- \end{equation} 
- where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$.
-Equation \eqref{interpretation-PsiP} will be useful in Remark \ref{remark-NESS-invertingS1}.
-Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
+ 	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
+ \end{equation} 
+ This last equation will be used in Section \ref{appB}.
+{\color{blue}Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
 We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present.
@@
 \begin{align}
-	\Psi^{'}(\bm{\tau})=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}_{\mu}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{\sigma_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
+	\Psi^{'}(\bm{\tau})=&\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
 \end{align} 
@@
 As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
-\end{remark}
-\subsection{Steady state}\label{appB}
-In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula follows from Corollary \ref{Corollary-NESS-ABS}.
-\begin{corollary}[Non-equilibrium steady state]
-	The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
-	\begin{equation}
-		|\Psi\rangle=\sum_{\bm{\tau}\in \Omega^{'}}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
-	\end{equation}
-	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega^{'}$,
-\begin{equation}\label{SteadyState-coeff-implicit}
-	\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\right]
-\end{equation}
-where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and are computed using \eqref{exactCorrelations}. 
+}
+\subsubsection{Steady state}\label{appB}
+By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary \ref{Corollary-NESS-ABS}.
+Therefore, the vector $|\Psi\rangle$ is also determined.
+For the sake of completeness we show here that $|\Psi\rangle$ can be equivalently determined by inverting the similarity transformation $S_{1}$, using $|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ (cf.
+\eqref{S1-Inverse}).
+On a single site we have that 
+\begin{equation}\label{S1-L1}
+	\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
+\end{equation}
+thus,
+\begin{equation}
+	\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
+\end{equation}
+By taking the tensor product over the chain we obtain 
+\begin{equation}
+	S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
+\end{equation}
+therefore, projecting on $\langle \bm{\tau}|$ we have
+\begin{equation}\label{Tensor-S1}
+	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\dt
+\end{equation}
+\begin{comment}
+	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
+	\begin{equation}
+		\begin{split}
+			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
+			\\&
+			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
+		\end{split}
+	\end{equation}
+	where we have introduced, $\forall x\in \{1,\ldots,L\}$
+	\begin{equation}
+		%\eta_{x}=\begin{cases}
+			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
+			%	d_{x}\qquad &\text{otherwise}
+			%\end{cases}\qquad
+			\theta_{x}(b)=\begin{cases}
+				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
+				N \qquad &\text{otherwise}
+			\end{cases}
+		\end{equation}
+		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
+		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
+		\begin{align*}
+			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
+			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
+\\&+\left.
+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
+			\\&\otimes
+			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
+			\\&=
+			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
+\\&+\left.
+\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
+		\end{align*}
+		\begin{comment}
+
+			\begin{equation}
+				F=\left(V^{-1}\right)^{T}
+			\end{equation}
+			and thus 
+			\begin{equation}
+				\mathcal{F}=F^{\otimes L}
+			\end{equation}
+			By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
+			\begin{equation}
+				F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
+			\end{equation}
+			Taking the tensor product over two sites we obtain 
+			\begin{equation}
+				\begin{split}
+					F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
+					\right.\\ &+\left. 
+					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
+				\end{split}
+			\end{equation}
+			therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
+			\begin{equation}
+				\begin{split}
+					\left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
+					\\&+
+					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
+					\\&=
+					\sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+					+
+					(-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
+				\end{split}
+			\end{equation}
+			where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
+\\
+			We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
+We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
+			\begin{equation}
+				\begin{split}
+					\mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
+					\\&
+					+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
+				\end{split}
+			\end{equation}
+			where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
+\\
+			The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
+			To find this elements we fix the rows correspondent to $\bm{\tau}$.
+Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
+		\end{comment}
+		Considering 
+		\begin{equation}
+			|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
+		\end{equation} we obtain  
+		\begin{align}\label{implicit-PSI-PSIp}
+			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
+			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},Y_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
+			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+		\end{align}
+		where the notation
+		\begin{equation}\label{notation-PSI}
+			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+		\end{equation}
+		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
+		\begin{equation}
+			\begin{cases}
+				\tau_{x}=a_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
+				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
+			\end{cases}\dt
+		\end{equation}
+		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$.
+In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
+Finally, using equation \eqref{interpretation-PsiP}, the result follows.
+
 %	and where 
@@
 %	\begin{equation}
-%%	\end{equation}
-\end{corollary} 
+%%	\end{equation\end{corollary} 
 \begin{remark}[Equilibrium case]
-	In the equilibrium case, when  $\alpha_{a}=\beta_{a}$ for all $a\in\{1,\ldots,N\}$ we obtain 
-	\begin{equation}
-		\Psi(\bm{\tau})=\prod_{a=1}^{N}\beta_{a}^{\sum_{x=1}^{L}\delta_{\tau_{x},a}}
-	\end{equation}
-i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 
+	Using equation \eqref{implicit-mass-function} with correlation computed in \eqref{exactCorrelations} in the equilibrium case ($\beta_{a}=\alpha_{a}$), we obtain 
+	\begin{equation}
+		\Psi(\bm{\tau})=\prod_{a=1}^{N}\alpha_{a}^{\sum_{x=1}^{L}\delta_{\tau_{x},a}}
+	\end{equation}
+As it has to, this is the probability of the configuration $\bm{\tau}$ under the reversible measure \eqref{reversibleMeasure}, with site marginals distributed as $\text{Multinomial}(1,\alpha_{1},\ldots,\alpha_{N})$.
 \end{remark}
@@
 \begin{remark}%[Correlation as the steady state of a $m$-chain ]
-	We observe that if $\bm{\tau}$ has only non-empty occupations, i.e. $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then 
-	\begin{equation}
-		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-	\end{equation}
-where the expectation is taken with respect to the $\mu$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$.
+	We observe that, as a consequence of Section \ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e.
+$\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then
+	\begin{equation}
+		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]
+	\end{equation}
 \begin{comment}
@@
 	%	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
-
-	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}}
-	The elements $\Psi(\bm{\tau})$ of the vector $|\Psi\rangle$ are the probabilities of having a certain configuration $\bm{\tau}\in \Omega^{'}$ in the non-equilibrium steady state, i.e.
-	\begin{equation}
-		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle= \mu(\bm{\tau})\dt
-	\end{equation}
- Therefore, they are given by the probability mass function of equation \eqref{implicit-mass-function} in Corollary \ref{Corollary-NESS-ABS}. 
-	\begin{flushright}
-		$\square$
-	\end{flushright}
-\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]\label{remark-NESS-invertingS1}
-	 As a consequence of \eqref{S1-Inverse}, the non-equilibrium steady state $|\Psi\rangle$ can also be obtained by inverting the similarity transformation $S_{1}$. On a single site we have that 
-	\begin{equation}\label{S1-L1}
-		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
-	\end{equation}
-	thus,
-	\begin{equation}
-		\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
-	\end{equation}
-	By taking the tensor product over the chain we obtain 
-	\begin{equation}
-		S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
-	\end{equation}
-	therefore, projecting on $\langle \bm{\tau}|$ we have
-	\begin{equation}\label{Tensor-S1}
-		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\dt
-	\end{equation}
-	\begin{comment}
-		Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
-		\begin{equation}
-			\begin{split}
-				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-				\\&
-				+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
-			\end{split}
-		\end{equation}
-		where we have introduced, $\forall x\in \{1,\ldots,L\}$
-		\begin{equation}
-			%\eta_{x}=\begin{cases}
-				%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-				%	d_{x}\qquad &\text{otherwise}
-				%\end{cases}\qquad
-				\theta_{x}(b)=\begin{cases}
-					\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-					N \qquad &\text{otherwise}
-				\end{cases}
-			\end{equation}
-			The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
-			This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
-			\begin{align*}
-				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
-				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-\\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
-				\\&\otimes
-				\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
-				\\&=
-				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
-\\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
-			\end{align*}
-			\begin{comment}
-
-				\begin{equation}
-					F=\left(V^{-1}\right)^{T}
-				\end{equation}
-				and thus 
-				\begin{equation}
-					\mathcal{F}=F^{\otimes L}
-				\end{equation}
-				By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
-				\begin{equation}
-					F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
-				\end{equation}
-				Taking the tensor product over two sites we obtain 
-				\begin{equation}
-					\begin{split}
-						F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-						\right.\\ &+\left. 
-						(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
-					\end{split}
-				\end{equation}
-				therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
-				\begin{equation}
-					\begin{split}
-						\left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-						\\&+
-						(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
-						\\&=
-						\sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-						+
-						(-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-					\end{split}
-				\end{equation}
-				where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
-\\
-				We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
-We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
-				\begin{equation}
-					\begin{split}
-						\mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
-						\\&
-						+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
-					\end{split}
-				\end{equation}
-				where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-\\
-				The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
-				To find this elements we fix the rows correspondent to $\bm{\tau}$.
-Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
-			\end{comment}
-			Considering 
-			\begin{equation}
-				|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
-			\end{equation} we obtain  
-			\begin{align}\label{implicit-PSI-PSIp}
-				\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},Y_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
-				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-			\end{align}
-where the notation
-		\begin{equation}\label{notation-PSI}
-			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-		\end{equation}
-		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
-		\begin{equation}
-			\begin{cases}
-				\tau_{x}=a_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
-				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
-			\end{cases}\dt
-		\end{equation}
-		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$.
-In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
-Finally, using equation \eqref{interpretation-PsiP}, the result follows.
-	\end{remark}
 		\begin{comment}
@@
 %\end{equation}
-\textbf{Proof of \eqref{NESS-SSEP}:} the proof follows from \eqref{implicit-PSI-PSIp} and \eqref{PsiI-N2}. 
+\textbf{Proof of \eqref{NESS-SSEP}:} the proof follows from \eqref{implicit-PSI-PSIp} and from the coefficients $\Psi^{'}(\bm{\tau})$ computed in \eqref{PsiI-N2}. 
 \begin{flushright}
@@
 \begin{equation}
-	\rho_{a}(x,t)=\mathbb{E}_{\mu}\left[n_{a}^{x}(t)\right]
-\end{equation}
-where $\mathbb{E}_{\mu}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu$.
+	\rho_{a}(x,t)=\mathbb{E}_{\mu_{0}}\left[n_{a}^{x}(t)\right]
+\end{equation}
+where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$.
 These average occupations evolve according to the master equation
 \begin{equation}
-	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu_{0}}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt
 \end{equation} 
@@
 \begin{equation}
-	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
+	p_{a}=p=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
 \end{equation}
@@
 \end{equation}
-This can be proved by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries.
-%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
+This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.% Arguing as in Remark \ref{rem-rev}, conditions \eqref{cond-gen} become here
+%\begin{equation}
+%	\alpha((N-2)\beta+\beta_{N})=\beta((N-2)\alpha+\alpha_{N})
+%\end{equation} 
+%where $\alpha_{a}=\alpha_{b}=\alpha$ and $\beta_{a}=\beta_{b}=\beta$ for all $a,b\in \{1,\ldots,N-1\}$.%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
 Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
@@
 This answer to the second question addressed at the beginning of this Section.
-\paragraph{Proof of duality}
-We only prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
+\paragraph{Proof of duality:}
+we only prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
 In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as 

### 2023-11-23 main.tex
^-^
^_^

@@
 dual process has absorbing sites.
-Therefore, as shown in Corollary \ref{prop-absorbing}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
+Therefore, as shown in Corollary \ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
 is reduced to the study of the absorption probabilities of dual particles.
@@
 %\begin{equation}
-%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{+})_{a}^{u(x)}=0
+%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|($\mathbf{a}$^{+})_{a}^{u(x)}=0
 %\end{equation}
@@
 \begin{corollary}[Correlations via duality]\label{Corolollary-ABS_Corr-abstract}
-\label{prop-absorbing}
 Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
@@
 =&
-\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
+\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
 +&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
@@
 \end{flushright}
-\begin{remark}
+\begin{remark}\label{Remark-extension-graph-nu}
 	The results in Corollary \ref{Corolollary-ABS_Corr-abstract} and in Corollary \ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for higher maximal occupancies $\nu >1$.
@@
 \begin{align}
-	&\mathbb{E}_{\mu}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
+	&\mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
 	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
@@
 \begin{equation}\label{correlations-SSEP}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
+	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=1\}}\right]=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
 \end{equation} 
@@
 Section \ref{Subsection-ss-nonI}.
+\textbf{[Do we need this or it is enough Remark \ref{Remark-extension-graph-nu}?]}
 	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
@@
 where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
-Therefore, up to this constant, $\mathbb{E}_{\mu}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
+Therefore, up to this constant, $\mathbb{E}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
 The following equalities hold using duality relation \eqref{duality-expectation}:
@@
 	\begin{split}
-		\frac{\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\frac{\mathbb{E}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\&=
@@
 	\begin{split}
-			\mathbb{E}_{\mu}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
+			\mathbb{E}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
 	\end{split}
@@
 \begin{equation}
-	\mathbb{E}_{\mu}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+	\mathbb{E}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
 \end{equation}
@@
 \begin{equation}
-		\mathbb{E}_{\mu}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
+		\mathbb{E}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
 \end{equation}

### 2023-11-23 main.tex
'

@@
 Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$.
-On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$.
+On the other hand, if $\sigma_{x}=N$ we have $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$.
 \\

### 2023-11-23 main.tex
^-^

@@
 \begin{equation}\label{stateSpace-Chain}
-	\Omega=\bigotimes_{x=1}^{L} \Omega_{x}
+	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega_{x}
 \end{equation} and its generator reads
@@
 \end{align}
-Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{1,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
+Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{0,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
@@
 %\end{equation}
-Therefore 
+Therefore the thermalization measure reads
 \begin{equation}
@@
 %\end{equation}
-In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters.
-\subsubsection{The dual thermalized process}
-The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
+In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ ($L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters.
+\subsubsection{The dual thermalized process}\label{subsection-dualTHM}
+Here we state the duality result for the thermalized multi-species stirring process with boundary driving.
+In the following, the dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively.
+To recall it we denote this dual space by $\widetilde{\Omega}_{L}$.
+\begin{proposition}[Duality for the thermalized multi-species stirring process]\label{proposition-dualityTHM}
+The thermalized multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ on the state space $\Omega_{L}$, with generator $\mathcal{L}^{TH}$ defined in \eqref{thermalizedGenerator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ on the enlarged configuration space $\widetilde{\Omega}_{L}$, with dual generator
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$:
+where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$:
 \begin{align}
@@
 \end{align}
-This means that they remove all dual particles at site $1$ (and $L$) and put these particles in the extra-site $0$ (and $L+1$) with rate 1.
-The duality function is the same as the original process, i.e.
+The duality function is the same of the multi-species stirring process, i.e. 
 \begin{equation}
@@
 \end{equation}
-The proof duality result for the thermalized multi-species stirring process is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.
+(cf. \eqref{dualityElements}).
+\end{proposition}
+This dual process is absorbing since the dual boundary generator $\mathcal{L}_{\text{left}}^{TH}$ ($\mathcal{L}_{\text{left}}^{TH}$) remove all dual particles at site $1$ ($L$) and put these particles in the extra-site $0$ ($L+1$) with rate 1.
+The proof of proposition \ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.
 \subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
+We define the average density occupation of species $a$ at site $x$ as
+\begin{equation}
+	\rho_{a}(x,t)=\mathbb{E}_{\mu_{0}}\left[n_{a}^{x}(t)\right]
+\end{equation}
+where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$.
+These average occupations evolve according to the evolution equation
+\begin{equation}\label{EE-density}
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu_{0}}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt
+\end{equation} 
 In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
@@
 The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$.
-\begin{remark}: observe that, up to a specific choice of the $\alpha$'s, the left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+\begin{remark}: observe that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
 \end{remark}
@@
 \end{equation}
-On the occupation variable $n_{a}^{L}$ the action is similar. \\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as
-\begin{equation}
-	\rho_{a}(x,t)=\mathbb{E}_{\mu_{0}}\left[n_{a}^{x}(t)\right]
-\end{equation}
-where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$.
-These average occupations evolve according to the master equation
-\begin{equation}
-	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu_{0}}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt
-\end{equation} 
-Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}.
+On the occupation variable $n_{a}^{L}$ the action is similar.
+Therefore, using the evolution equation \eqref{EE-density} for the average densities and  the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}.
 For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question we addressed to at the beginning of this subsection.
+This answers the first question we addressed to at the beginning of this section.
 \subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
@@
 \subsubsection{Duality for the reaction-diffusion process}
-In this subsection we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{RDGenerator}.
-The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space $\widetilde{\Omega}$ defined in \eqref{dualStateSpace}
+In this subsection we formulate duality for the multi-species reaction diffusion stirring process.
+This answer to the second question addressed at the beginning of this Section.
+The dual process is defined on the enlarged state space $\widetilde{\Omega}_{L}$, introduced in Section \ref{subsection-dualTHM}.
+\begin{proposition}[Duality for the reaction-diffusion process]\label{propositin-duality-RD}
+The reaction-diffusion multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, on the state space $\Omega_{L}$, with generator $\mathcal{L}^{rd}$ defined in \eqref{RDGenerator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ on the state space $\widetilde{\Omega}_{L}$ with dual generator
+\begin{equation}\label{DualGeneratorRD}
+	\widetilde{\mathcal{L}}_{\text{left}}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}
+\end{equation}
+where 
+$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator} and acting at sites $1$ and $L$, with the specific choice of the reservoirs parameters \eqref{boundaryParamRD}.
+The duality function
+is the same of the stirring process, i.e.
+\begin{equation}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
+\end{equation}
+(cf. \eqref{dualityElements}).
+\end{proposition} 
 %\begin{equation}
@@
 %and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
-The duality function is given by
-\begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}\dt
-\end{equation}
 %where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
@@
 %\end{equation}
-The dual generator now reads
-\begin{equation}\label{DualGeneratorRD}
-	\widetilde{\mathcal{L}}_{\text{left}}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}
-\end{equation}
-where 
-$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the specific choice of the reservoirs parameters \eqref{boundaryParamRD}.
-This answer to the second question addressed at the beginning of this Section.
-\paragraph{Proof of duality:}
-we only prove duality for the bulk generator, since the boundary generators are the same as in Section \ref{Subsection-ss-nonI}. 
+
+\paragraph{Proof of Proposition \ref{propositin-duality-RD}:}
+we only prove duality for the bulk generator, since the boundary generators are the same of the multi-species stirring process.
 In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
@@
 \end{equation}
-Here, $\mathcal{H}_{x,x+1}$ and $H_{\text{left}},H_{\text{right}}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
+Here, $\mathcal{H}_{x,x+1}$ is  \eqref{edgeHamiltonian}  and $H_{\text{left}},H_{\text{right}}$ is \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}).
+We, then have that
 \begin{equation}
@@
 We prove that, for arbitrary $x\in\{1,\ldots,L\}$,
-%\begin{align}
-%	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}
-%\end{align}
-%but it is enough of showing 
 \begin{align}

### 2023-11-24 main.tex
^^

@@
 \section{Introduction} 
+Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics.
+In a boundary-driven system, the model is put in contact with reservoirs at its "boundaries" imposing different particle densities, and a current is generated through the system.
+In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
+The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite[....].
+
+For the single species case, the exclusion process with open boundaries has been of crucial importance in our understanding of the structural properties of non-equilibrium state states, such as long-range correlations and non-local density large deviation functions.
+The results available for the exclusion process are rooted in the algebraic properties of the corresponding integrable quantum spin chain, i.e.
+the XXX Heisenberg Hamiltonian with $\mathfrak{su}(2)$ spins of value 1/2.
+In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context, i.e.
+the stirring process with open boundaries.
+The bulk part of the model with $N$ species is associated with the integrable Hamiltonian having  $\mathfrak{gl}(N)$ symmetry.
+
+Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of duality.
+This approach, starting from the pioneering approach of [Presutti] and [Spohn] has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up.
+The boundary-driven process is mapped to
+a dual process with absorbing extra sites and the problem of describing the stationary state
+is reduced to the problem of computing the absorption probabilities of the dual particles. 
+In general, this is a difficult task. However, there are cases in which these absorption
+probabilities can be computed thanks to the integrability property of the system.
+For a recent example see [Frassek,Giardinà].
+
+The remainder of this paper is organized as follows. In Section \ref{} we define the open multispecies stirring
+process and provide its Lie algebraic description. In Section \ref{} we prove duality (Theorem \ref{}) 
+and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
+steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
+system has a general spatial structure described by a graph. In Section \ref{} we obtain a closed formula 
+for the stationary correlations (Theorem \ref{}) for the case of a one-dimensional chain with at most one 
+particle per site, which is driven to steady-state by two reservoirs acting at the left and right boundaries. 
+Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz,
+which is in fact also simplified by the use of duality. Finally in Section \ref{} we discuss a few extensions 
+and generalizations of the model, including instantaneous thermalization limits, ......
+In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
+model with non-compact Lie-algebras, both integrable and non-integrable, which will be presented in a 
+future paper.
+
+Acknowledgments: GNFM, PRIN, FAR UNIMORE,...
+
+{\color{blue}
 In the past years duality has been developed to study stochastic processes, especially in the boundary driven case, i.e.
@@
 Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.
+}
 
@@
 \begin{equation}
-\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt
+\mathbb{E}_{\mu_{\text{rev}}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt
 \end{equation}
@@
 \end{enumerate}
-\subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
-In this subsection we specialize the results of Section \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
+In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
 Each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
 Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
-As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$.
-This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
-The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
+All the processes considered, denoted by $\left(\bm{n}(t)\right)_{t\geq0}$ with the generator specified in each subsection, will be defined on the space
 \begin{equation}\label{stateSpace-Chain}
 	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega_{x}
-\end{equation} and its generator reads
+\end{equation}
+ The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case.
+The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively.
+To recall it we denote this dual space by $\widetilde{\Omega}_{L}$, i.e.
+\begin{equation}\label{dualSpace-chain}
+	\widetilde{\Omega_{L}}=\mathbb{N}_{0}^{N}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N}\dt
+\end{equation}
+\subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
+ As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by types $N$ (the empty).
+This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
+This is a generalization for the non-integrable chain of the Corollary \ref{Corolollary-ABS_Corr-abstract}.
+The process $\left(\bm{n}(t)\right)_{t\geq0}$ has generator
 \begin{equation}
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the site generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a}^{x})_{a\in \{1,\ldots,N\}}$ respectively.
+where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a})_{a\in \{1,\ldots,N\}}$ respectively.
 \begin{comment}
@@
 \end{comment}
-By Theorem \ref{thm-duality}, the process is dual to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space where two extra-sites with unbounded maximal occupancy $\{0\}$ and $\{L+1\}$ have been added attached to the left of $\{1\}$ and to the right of $\{L+1\}$.
-%\begin{equation}\label{stateSpaceDUAL-Chain}	
-%	\widetilde{\Omega}=N_{0}^{N}\times\bigotimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
-%\end{equation}
-Thus, the dual generator reads
+The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, has generator
 \begin{equation}
@@
 \end{comment}
-The dual process has absorbing boundaries, i.e.
-all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability.
-This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following.
-We call $\mu$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$.
-For every $m\in\{1,\ldots,L\}$ we consider  $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$ and we introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ meaning that
+The dual process has absorbing boundaries.
+This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process.\\
+We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
+For every $m\in\{1,\ldots,L\}$ we consider  $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$.
+We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
 \begin{equation}
@@
 \end{equation}
-The duality function \eqref{dualityElements} computed in this dual configurations is 
+The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
 \begin{equation}
@@
 \end{equation}
-where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
-Therefore, up to this constant, $\mathbb{E}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations.
-The following equalities hold using duality relation \eqref{duality-expectation}:
+where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal occupancy $\nu$. 
+Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state.
+The following equalities hold using ergodicity and duality:
 \begin{equation}\label{ExptationSS}
 	\begin{split}
-		\frac{\mathbb{E}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
+		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\mathcal{Y}_{a_{k}}^{x_{k}}=n_{a_{k}}^{x_{k}}\}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
 		\\&=
@@
 the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$.
-Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
- This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.
+Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
+ These correlations can be computed once the absorption probabilities are known.
 For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
@@
 Here we state the duality result for the thermalized multi-species stirring process with boundary driving.
-In the following, the dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively.
-To recall it we denote this dual space by $\widetilde{\Omega}_{L}$.
 \begin{proposition}[Duality for the thermalized multi-species stirring process]\label{proposition-dualityTHM}
@@
 	\begin{split}
-			\mathbb{E}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
 	\end{split}
@@
 \begin{equation}
-	\mathbb{E}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
+	\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt
 \end{equation}
@@
 \begin{equation}
-		\mathbb{E}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
+		\mathbb{E}\left[\mathbbm{1}_{\{Y_{x}=a\}}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}
 \end{equation}
@@
 \end{equation}
-First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
+First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. By writing explicitly $\rho_{a}^{L}=\frac{\alpha_{a}}{|\alpha|}$, this action gives
 \begin{align}\label{ProvaBordoTH}
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
 	\\&\nonumber
-	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left.\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)-D(\bm{n},\bm{\xi})\right\}
 	\\&
@@
 We consider the first addend in the curly bracket of the previous equation.
-We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$.
-As a result, we have
+We add and remove $|\xi^{1}|-\xi_{N}^{1}=\xi_{1}^{1}+\ldots+\xi_{N-1}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$.
+Thus, we have
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{k}^{1}-\xi_{k}^{1}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\nonumber\\=&
-	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
-	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\nonumber\\
+	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+|\xi^{1}|-\xi_{N}^{1}-|\xi^{1}|+\xi_{N}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
+	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\right)\nonumber\\=&
+	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
+	\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\left(\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\nonumber
 	\\=&
-	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
-\end{align}
-where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.
+	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)
+\end{align}
+where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets\textbf{FINISH TO CHECK}.
 We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain
@@
 	\begin{split}
-		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
+		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\right)\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
 	\end{split}

### 2023-11-24 main.tex
iyguy

@@
 %\bf Multispecies stirring process: duality and exact solution
-\bf Multispecies stirring process \\
+\bf Exact solution of the multispecies stirring process \\
  with open boundaries
@@
 
-% \newpage
+ \newpage
 
@@
 Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics.
-In a boundary-driven system, the model is put in contact with reservoirs at its "boundaries" imposing different particle densities, and a current is generated through the system.
+In a boundary-driven system, the model is put in contact with reservoirs at its ``boundaries'' imposing different particle densities, and a current is generated through the system.
 In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
-The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite[....].
-
-For the single species case, the exclusion process with open boundaries has been of crucial importance in our understanding of the structural properties of non-equilibrium state states, such as long-range correlations and non-local density large deviation functions.
+The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal}.
+
+For the single species case, the exclusion process with open boundaries \cite{derrida1993exact} has been of crucial importance in our understanding of the structural properties of non-equilibrium state states, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviation \cite{mallick2022exact,bodineau2005current}.
 The results available for the exclusion process are rooted in the algebraic properties of the corresponding integrable quantum spin chain, i.e.
 the XXX Heisenberg Hamiltonian with $\mathfrak{su}(2)$ spins of value 1/2.
-In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context, i.e.
-the stirring process with open boundaries.
-The bulk part of the model with $N$ species is associated with the integrable Hamiltonian having  $\mathfrak{gl}(N)$ symmetry.
-
-Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of duality.
-This approach, starting from the pioneering approach of [Presutti] and [Spohn] has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up.
-The boundary-driven process is mapped to
-a dual process with absorbing extra sites and the problem of describing the stationary state
+In this paper, we investigate the multi-species analog of the exclusion process in the boundary-driven context, i.e.
+the {\em  multi-species stirring process with open boundaries}.
+The bulk part of the model with $N$ species is associated with the integrable higher-rank
+Heisenberg XXX Hamiltonian having  $\mathfrak{gl}(N)$ symmetry.
+
+Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of {\em duality} \cite{schutzSandow}.
+This approach, starting from the pioneering work of Kipnis, Marchiorio and Presutti \cite{KMP},
+has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up \cite{giardina2009duality,carinci2013duality,frassek2020duality,carinci2023open}. 
+The boundary-driven process is mapped to a dual process with absorbing extra sites and the problem of describing the stationary state of the original system
 is reduced to the problem of computing the absorption probabilities of the dual particles. 
@@
 probabilities can be computed thanks to the integrability property of the system.
-For a recent example see [Frassek,Giardinà].
-
-The remainder of this paper is organized as follows. In Section \ref{} we define the open multispecies stirring
-process and provide its Lie algebraic description. In Section \ref{} we prove duality (Theorem \ref{}) 
+For recent examples in the framework of single-species systems, see \cite{frassek2020eigenstates, frassek2022exact, frassek2020non, floreani2023non}.
+Here we generalize the duality approach to the set-up of multi-species particle systems.
+
+The remainder of this paper is organized as follows. In Section \ref{sec1} we define the open multispecies stirring
+process and provide its Lie algebraic description. In Section \ref{sectionDuality} we prove duality (Theorem \ref{thm-duality}) 
 and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
 steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
-system has a general spatial structure described by a graph. In Section \ref{} we obtain a closed formula 
-for the stationary correlations (Theorem \ref{}) for the case of a one-dimensional chain with at most one 
-particle per site, which is driven to steady-state by two reservoirs acting at the left and right boundaries. 
-Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz,
-which is in fact also simplified by the use of duality. Finally in Section \ref{} we discuss a few extensions 
-and generalizations of the model, including instantaneous thermalization limits, ......
+system has a general spatial structure described by a general graph. In Section \ref{sectionIntegrabiliy} we then obtain a closed formula 
+for the stationary correlations (Theorem \ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
+particle per site, which is driven out-of-equilbrium by two reservoirs acting at the left and right boundaries. 
+Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz \cite{vanicat2017exact},
+which is in fact also simplified by the use of duality. Finally in Section \ref{sec5} we discuss a few extensions 
+and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
+
 In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
@@
 
-Acknowledgments: GNFM, PRIN, FAR UNIMORE,...
-
-{\color{blue}
-In the past years duality has been developed to study stochastic processes, especially in the boundary driven case, i.e.
+{\bf Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM), Prin-project {\color{blue} xxxx}, FAR-project {\color{blue} xxxx} UniMoRe.
+
+%
+%{\color{blue}
+%In the past years duality has been developed to study stochastic processes, especially in the boundary driven case, i.e.
 when the system is put in contact with boundaries that generate a non-equilibrium current.
@@
 How far can we push our analysis for the characterization of the non equilibrium steady state?\\
-The way one can define a multi-type (or multi-species) interacting particle system is not unique.
+%The way one can define a multi-type (or multi-species) interacting particle system is not unique.
 In the literature there are many.
@@
 \\
-In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e.
+%In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e.
 a dynamic in which a maximum amount of particles can be present in each site at each time.
@@
 In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}.
-{\color{red}
-The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
+%{\color{red}
+%The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
 Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
-}
-We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
+%}
+%We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
 The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator.
 \\
- For a complete review of the quantum inverse scattering method see \cite{Sklyanin:1988yz} and \cite{faddeev1996algebraic}.
+% For a complete review of the quantum inverse scattering method see \cite{Sklyanin:1988yz} and \cite{faddeev1996algebraic}.
 For application of the QISM to interacting particle systems we refer to \cite{frassek2020eigenstates,frassek2019non,frassek2022exact,vanicat2017exact}.
 \\
- A new technique to compute absorption probabilities has been proposed in \cite{floreani2023non}.
- \\
- \\
- \textbf{Some interesting references and extensions?}:
- Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
- Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
- Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
- Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
+% A new technique to compute absorption probabilities has been proposed in \cite{floreani2023non}.
+% \\
+% \\
+% \textbf{Some interesting references and extensions?}:
+% Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
+% Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
+% Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
+% Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
 Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.
-}
-
-\paragraph{Organization of the paper}
+%}
 %
@@
 \section{The stirring process with open boundaries}
+\label{sec1}
 \subsection{Informal description of the process}
@@
 %\end{equation}
-\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
+\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we  show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
 Using the exponential series we have that
@@
 \end{comment}
- By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} the formula for $|\Psi^{''}\rangle$ we obtain 
+% By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} the formula for $|\Psi^{''}\rangle$ we obtain 
+From this it follows that
 \begin{align}\label{ABS_intermediate}
-		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]\dt
-	\end{align}
+		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle = \sum_{\bm{\sigma}\in \Omega'}  \langle \bm{\tau}|S_{2}^{-1} |\bm{\sigma}\rangle\langle\bm{\sigma}|\Psi^{''}\rangle \nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]\dt
+	\end{align}
+	where we used the expression \eqref{ResulsBasis} for $\Psi^{''}(\bm{\sigma})$.
 %where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
@@
 \section{Extensions for the non-integrable chain}
+\label{sec5}
 In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using to integrability.  

### 2023-11-24 main.tex
^-^

@@
 \end{align}
-Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$.
-On the other hand, if $\sigma_{x}=N$ we have $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$.
+Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square brackets of the above equation, that is non-vanishing only if $\sigma_{x}=\tau_{x}$.
+This implies that both the left-hand-side and the right-hand-side are either $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ ro $0$.
+On the other hand, if $\sigma_{x}=N$ we have $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$, thus both sides of the equality are either $\beta_{\tau_{x}}$ or $0$.
 \\
@@
 \end{align}
-We consider the first addend in the curly bracket of the previous equation.
-We add and remove $|\xi^{1}|-\xi_{N}^{1}=\xi_{1}^{1}+\ldots+\xi_{N-1}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$.
+We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$.
 Thus, we have
@@
 	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\nonumber\\
-	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+|\xi^{1}|-\xi_{N}^{1}-|\xi^{1}|+\xi_{N}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
+	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
 	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\right)\nonumber\\=&
@@
 \end{align}
-where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets\textbf{FINISH TO CHECK}.
+where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
 We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain

### 2023-11-24 main.tex
''
^_^
ewffdw

--- 2023-11-24 main.tex
@@
 	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
-	Thus we chose to present them in such a context.
+	Thus we chose to present them in such a context. For the chain with higher maximal occupancies $\nu >1$ see Section \ref{Subsection-ss-nonI}.
 \end{remark}
@@
 Then, equation  \eqref{ABS_intermediate} reads
-Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally have
+Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
 \begin{equation}\label{elementsABS}
@@
 %Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
-Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, \eqref{ABS-vect} follows.
+%Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, \eqref{ABS-vect} follows.
 \begin{flushright}
@@
 \begin{align}
+\label{corr-psi1}
 	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
@@
 	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
-	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+%	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
+%	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
 	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt
@@
 \subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
-We argue similarly as in the Section \ref{correlation-section}. For any $\bm{\tau}\in \Omega^{'}$ we have that 
+%We argue similarly as in the Section \ref{correlation-section}. 
+We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau})= (N,\ldots,N)$. We show here that for this particular configuration
+$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
 \begin{align}
@@
  \end{equation} 
- This last equation will be used in Section \ref{appB}.
-{\color{blue}Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
+ This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.
+
+ Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
+ Let $\ell$ be the number of occupied sites in the configuration $\bm{\tau}$, i.e.
+$\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
 We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present.
@@
 \end{align} 
-It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution, in the sense described above.
-In particular, when the configuration $\bm{\tau}$ has at $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function.
-As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
-}
+It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution.
+In particular, when the configuration $\bm{\tau}$ has $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function.
+%As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
+
 \subsubsection{Steady state}\label{appB}
 By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary \ref{Corollary-NESS-ABS}.
-Therefore, the vector $|\Psi\rangle$ is also determined.
-For the sake of completeness we show here that $|\Psi\rangle$ can be equivalently determined by inverting the similarity transformation $S_{1}$, using $|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ (cf.
-\eqref{S1-Inverse}).
+Indeed we show here that
+$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary \ref{Corollary-NESS-ABS}.
 On a single site we have that 
@@
 			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
-			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},Y_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
+			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
 			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
@@
 %	\begin{equation}
-%	Q(x)=1-\sum_{k=1}^{b}\delta_{x,q_{k}}
  %\end{equation}
@@
 	\end{equation}
-As it has to, this is the probability of the configuration $\bm{\tau}$ under the reversible measure \eqref{reversibleMeasure}, with site marginals distributed as $\text{Multinomial}(1,\alpha_{1},\ldots,\alpha_{N})$.
+As it has to be, this is the probability of the configuration $\bm{\tau}$ under the reversible measure \eqref{reversibleMeasure}, with site marginals distributed as $\text{Multinomial }(1,\alpha_{1},\ldots,\alpha_{N})$.
 \end{remark}
@@
 If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
-\begin{remark}%[Correlation as the steady state of a $m$-chain ]
-	We observe that, as a consequence of Section \ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e.
+%\begin{remark}%[Correlation as the steady state of a $m$-chain ]
+%	We observe that, as a consequence of Section \ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e.
 $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then
-	\begin{equation}
-		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]
-	\end{equation}
-\begin{comment}
- As a consequence, we can give a different interpretation to correlation computed in \eqref{exactCorrelations}.
+%	\begin{equation}
+%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]
+%	\end{equation}
+%\begin{comment}
+% As a consequence, we can give a different interpretation to correlation computed in \eqref{exactCorrelations}.
 Consider the sites $(x_{k})_{k\in \{1,\ldots,m\}}$ and fix $(a_{k})_{k\in \{1,\ldots,m\}}$ introduced in Theorem \ref{thm-correlations}.
@@
 Then, we have that the correlations computed in \eqref{exactCorrelations} can be written as
-\begin{equation}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\Psi_{m}(a_{1},\ldots,a_{m})
-\end{equation}
-This means that we can define a mapping between the $m$-point correlation of chain of length $L$ and the non-equilibrium steady state of a chain of length $m$. This mapping, 
-\end{comment}
-	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
-\end{remark}
+%\begin{equation}
+%	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\Psi_{m}(a_{1},\ldots,a_{m})
+%\end{equation}
+%This means that we can define a mapping between the $m$-point correlation of chain of length $L$ and the non-equilibrium steady state of a chain of length $m$. This mapping, 
+%\end{comment}
+%	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
+%\end{remark}
 \begin{comment}
@@
 
-\subsection{The colour-blind case}
-The computations made for the multi-species stirring process can be specialized for the colour-blind case $N=2$, i.e.
-when only one type of non-empty particle is considered.
+\subsection{The single-species case (SSEP)}
+The computations made for the multi-species stirring process can be specialized to the single-species case $N=2$.
 In this situation we retrieve the SSEP, that was already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
@@
  We only report the main results, since the computations are just a specific case of the ones done for the multi-species stirring process. 
-\paragraph{Correlations of SSEP}
+\paragraph{Correlations of SSEP.}
 We retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:  
@@
 \end{equation} 
-\textbf{Proof of \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
+\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
 There are many values of $c$'s that give the same $q$, therefore we define $q$ %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
@@
 Indeed, in the product on the left hand side only $q$ terms at coordinates $x_{\ell_{1}},\ldots x_{\ell_{q}}$ do survive. Moreover, any fixed $x_{\ell_{k}}$ has $q-k$ occupied sites at its right.
-Furthermore, sing the properties of the factorials, we have that 
+Furthermore, using the properties of the factorials, we have that 
 \begin{equation}\label{Gamma-product}
@@
 \end{flushright}
-\paragraph{$|\Psi^{''}\rangle$ for SSEP} The ground state of $H^{''}$ is 
+\paragraph{The vector $|\Psi^{''}\rangle$ for SSEP.} The ground state of $H^{''}$ is 
 \begin{equation}\label{psiII-SSEP}
@@
 where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. \\ \\
-\textbf{Proof of \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the colour-blind case.
+\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the colour-blind case.
 We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
@@
 \end{flushright}
-\paragraph{$|\Psi^{'}\rangle$ for SSEP} The ground state of $H^{'}$ reads
+\paragraph{The vector $|\Psi^{'}\rangle$ for SSEP.} The ground state of $H^{'}$ reads
 \begin{equation}
@@
 and where $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ . \\ \\
- \textbf{Proof of \eqref{PsiI-N2}:}  For any configuration $\bm{\tau}\in \Omega$ we denote by  $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},2}$ the number of occupied sites.
+ \textbf{Proof of formula \eqref{PsiI-N2}:}  For any configuration $\bm{\tau}\in \Omega$ we denote by  $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},2}$ the number of occupied sites.
 Then, considering equation \eqref{ABS_1} we have the result by adapting the proof of \eqref{correlations-SSEP} in the following way.
@@
 \end{equation} 
-Therefore, using \eqref{Gamma-product} and by considering all possible $\bm{\tau}$ one finds $|\Psi^{'}\rangle$ for the SSEP.
+Therefore, using \eqref{Gamma-product}  one finds $|\Psi^{'}\rangle$ for the SSEP.
 \begin{flushright}
@@
 \end{flushright}
-\paragraph{$|\Psi\rangle$ for SSEP}
+\paragraph{The vector $|\Psi\rangle$ for SSEP.}
 In the colour-blind case we have that 
@@
 
-\section{Extensions for the non-integrable chain}
+\section{Extensions beyond the integrable chain}
 \label{sec5}
-In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using to integrability.  
-The aim is studying some property of the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
+In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using integrability.  
+The aim of this section is to study the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
 \begin{enumerate}
-	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
-These probability are hard to find in this partial exclusion situation, however correlation can be formally written.
-Section \ref{Subsection-ss-nonI}.
-\textbf{[Do we need this or it is enough Remark \ref{Remark-extension-graph-nu}?]}
-	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+	\item \textit{Correlations} (Section \ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+These probability are hard to find when $\nu>1$, however correlation can be formally written.
+	\item \textit{Instantaneous thermalization} (Section \ref{Subsection-Thermalized}): starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-Section \ref{Subsection-Thermalized}.
-	\item \textit{Reaction-diffusion process}: a further dynamics is added.
+	\item \textit{Reaction-diffusion process}(Section \ref{Subsection-RD}): a further dynamics is added.
 Particle can now change type.
@@
 Duality for the boundary driven process is also proved.
-Section \ref{Subsection-RD}
 \end{enumerate}

### 2023-11-24 main.tex

@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
 		\\&=
-		\sum_{a=1}^{N-1}n_{a}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
+		\sum_{k=1}^{N-1}n_{k}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
 		\\&=
@@
 \end{equation}
-where we call $q$ such that $g_{i}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
+where we call $q$ such that $h_{c}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
 Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .

### 2023-11-25 main.tex
''
partial

@@
 		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(r,n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
-		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
+		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
 		\end{split}
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}\dt
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}\dt
 \end{equation}
@@
 \begin{equation}\label{DifferenceEquation}
-	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{a}^{x})
+	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1\,:\,b\neq a}^{N-1}(n_{b}^{x}-n_{a}^{x})
 \end{equation}
@@
 \begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt
+	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq a}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt
 \end{equation}
@@
 \begin{align}
-	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
-	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
-\end{align}
+	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+\end{align}
+Duality for the right boundary is similar. \\
 Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
@@
 	\\&
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
 \end{align}
 We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
-We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$.
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}^{1}+r_{\ell}^{1}}$.
 Thus, we have
@@
 	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
-	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\right)\nonumber\\=&
+	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{\ell}+r_{\ell}}\right)\nonumber\\=&
 	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
@@
 \end{align}
-where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain
+Where we used {\color{blue}
+\begin{equation*}
+\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\frac{\nu!}{r_{1}!\cdots r_{N}!}=\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}
+\end{equation*}
+and 
+\begin{align*}
+&\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{\ell}+r_{\ell}}\right)\\=&	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}
+\end{align*}
+and }the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
+We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain
 \begin{equation}\label{pezzo2}
 	\begin{split}
-		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\right)\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
-	\end{split}
-\end{equation}
-where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that
+		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
+	\end{split}
+\end{equation}
+where we used the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that
 \begin{align}
@@
 	\\&=
-	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
-\end{align}
-The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 
+	\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+\end{align}
+%The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 
 \begin{flushright}
@@
 \end{equation}
-Indeed
-\begin{equation}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
-\end{equation}
-while for every $c\in \{1,\ldots,N-2\}$ we have 
+Indeed we have that 
+\begin{enumerate}
+	\item \textit{Stirring generator}:
+
+\begin{equation}
+	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)
+\end{equation}
+The only terms that survive are: in one case the ones with $a=d$ and $b\neq d$, giving a contribution $-n_{d}^{x}n_{b}^{x+1}$; in the other case the ones with $a\neq d$ and $b=d$, giving a contribution $n_{a}^{x}n_{d}^{x+1}$.
+Thus we obtain
+\begin{align*}
+	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1\,:\,a\neq d}^{N}n_{a}^{x}n_{d}^{x+1}-\sum_{b=1\,:\,b\neq d}^{N}n_{d}^{x}n_{b}^{x+1}\\
+	=&\sum_{a=1\,:\,a\neq d}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1\,:\,b\neq d}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
+	=&\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
+\end{align*} 
+where we have used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
+\item \textit{Stirring-mutation generator}: for every $c\in \{1,\ldots,N-2\}$ we have 
 \begin{equation}
@@
 \end{equation}
+\end{enumerate}
 Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
+
 \paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
@@
 	\begin{split}
-		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
+		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{1}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
 		\\&=

### 2023-11-25 main.tex
^-^

@@
 \end{equation}
+In the following of this section we will denote by 
+\begin{equation}
+	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\alpha_{a}}{|\alpha|}
+\end{equation}
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
@@
 		\\&=
-		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})
-	\end{split}
-\end{equation}
-where we recall that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
+		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{t_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})
+	\end{split}
+\end{equation}
+here we recall that, generalizing Corollary \ref{Corolollary-ABS_Corr-abstract}, %that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and
 \begin{equation}\label{Pass} 
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}\dt
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\dt
 \end{equation}
@@
 where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$.
-These average occupations evolve according to the evolution equation
+These average occupations evolves according to the evolution equation
 \begin{equation}\label{EE-density}
@@
 \end{equation} 
-In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied for a proper diffusivity constant) and a linear reaction term (mutation), i.e.
+In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied by a proper diffusivity constant) and a linear reaction term (mutation), i.e.
 \begin{equation}\label{2SpeciesRD}
@@
 for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$. Here $\Delta_{L}\rho(x,t)=\rho_{a}(x+1,t)+\rho_{a}(x-1,t)-2\rho_{a}(x,t)$.
-This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
+This equation is endowed with boundary conditions $\rho_{a}^{\text{left}},\rho_{\overline{a}}^{\text{left}}$ on the left and $\rho_{a}^{\text{right}},\rho_{\overline{a}}^{\text{right}}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
 For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
@@
 		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process using the same $gl(N)$ Lie-algebraic structure?
+			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same $gl(N)$ Lie-algebraic structure?
 \end{enumerate}
-Therefore, we aim to find a process whose average occupations $\rho_{a}(x,t)$ for any species $a\in\{1,\ldots,N-1\}$ evolve as a system of difference differential equation given by 
+Therefore, we aim to find a process whose average occupations $\rho_{a}(x,t)$ for any species $a\in\{1,\ldots,N-1\}$ evolve as a system of difference-differential equation given by 
 \begin{equation}\label{NSpeciesRD}
@@
 \end{equation}
-with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce
+with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator
 \begin{equation}
@@
 		k+c \quad &\text{if}\quad k+c< N \\
-		k+c-N+1\quad &\text{if}\quad k+c\geq N,\quad k\neq N\\
+		k+c-N+1\quad &\text{if}\quad k+c\geq N\quad \text{and}\quad k\neq N\\
 		N\quad &\text{if}\quad k=N
@@
 Observe that $h_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
-Moreover,
+Moreover, we define the \textit{pure-mutation} generator
 \begin{equation}
@@
 \begin{align}\label{boundaryParamRD}
-		\alpha_{a}&=\sigma_{11}\rho_{a}^{0}+\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\rho_{b}^{0}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\nonumber\\
+		\alpha_{a}&=\sigma_{11}\rho_{a}^{\text{left}}+\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\rho_{b}^{\text{left}}\qquad \text{if} \quad a\in \{1,\ldots,N-1\}\nonumber\\
 		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}\dt
@@
 \begin{equation}
-	\rho_{a}^{0}=\frac{\alpha_{a}\sigma_{11}-\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\alpha_{b}}{(\sigma_{11}-(N-2)\sigma_{12})(\sigma_{11}+(N-2)\sigma_{12})}\qquad \rho_{N}^{0}=\frac{\alpha_{N}}{(\sigma_{11}+(N-2)\sigma_{12})}
-\end{equation}
-for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$. \\
-The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values are considered at site $L+1$.
-\begin{remark}: observe that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+	\rho_{a}^{\text{left}}=\frac{\alpha_{a}\sigma_{11}-\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\alpha_{b}}{(\sigma_{11}-(N-2)\sigma_{12})(\sigma_{11}+(N-2)\sigma_{12})}\qquad \rho_{N}^{\text{left}}=\frac{\alpha_{N}}{(\sigma_{11}+(N-2)\sigma_{12})}
+\end{equation}
+for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\nu$. \\
+The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values $\rho_{a}^{\text{right}}$.
+\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
 \end{remark}
@@
 The details are written in Appendix \ref{appendix-RD}.
-For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{a}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ reads
+For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{a}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ at site $x$ reads
 \begin{equation}\label{DifferenceEquation}
@@
 \begin{equation}\label{actionBDLine}
-	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq a}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt
+	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{\text{left}}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{\text{left}}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq a}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt
 \end{equation}
@@
 \begin{equation}
-	\Lambda^{x}_{\text{rev}}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
+	\Lambda^{x}_{\text{rev}}\sim \text{Multinomial}\left(\twoj,p,\ldots,p,p_{N}\right)
 \end{equation}
@@
 \begin{equation}
-	p_{a}=p=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
+	p=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
 \end{equation}
@@
 \end{equation}
-This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.% Arguing as in Remark \ref{rem-rev}, conditions \eqref{cond-gen} become here
+This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
+{\color{blue} 
+	Indeed, we impose the detailed balance for the stirring-mutation generator $\mathcal{L}_{x,x+1}^{c}$, for arbitrary $c\in \{1,\ldots,N-2\}$. Consider the transition 
+				\begin{equation*}
+			\bm{n} \to\bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c(a)}}^{x+1}-\delta_{b}^{x+1}
+			\end{equation*} 
+		we obtain that 
+		\begin{equation*}
+			p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
+		\end{equation*}
+		that is verified if $p_{a}=p_{b}$ for all $a,b\in \{1,\ldots,N-1\}$.
+A similar argument for the generator $\mathcal{L}^{m}$ gives the same conditions for the $p$'s.
+Considering the boundary generators, one obtain the result.}
+% Arguing as in Remark \ref{rem-rev}, conditions \eqref{cond-gen} become here
 %\begin{equation}
@@
 \subsubsection{Duality for the reaction-diffusion process}
-In this subsection we formulate duality for the multi-species reaction diffusion stirring process.
-This answer to the second question addressed at the beginning of this Section.
-The dual process is defined on the enlarged state space $\widetilde{\Omega}_{L}$, introduced in Section \ref{subsection-dualTHM}.
+In this section we formulate duality for the multi-species reaction diffusion process.
+This answer to the second question addressed at the beginning of Section \ref{Subsection-RD}.
+The dual process is defined on the enlarged state space $\widetilde{\Omega}_{L}$.
 \begin{proposition}[Duality for the reaction-diffusion process]\label{propositin-duality-RD}
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}
 \end{equation}
@@
 \begin{equation}
-	\nu D(\eta,\delta_{a}^{x})=n_{a}^{x}\dt
+	\nu D(\bm{n},\delta_{a}^{x})=n_{a}^{x}\dt
 \end{equation}
@@
 	\begin{split}
-			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{t_{s}}\left(\rho_{s}^{\text{right}}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
 	\end{split}
@@
 	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\label{boundaryDualityTH}
 \end{align}
@@
 We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
-We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}^{1}+r_{\ell}^{1}}$.
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$.
 Thus, we have
@@
 	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
-	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{\ell}+r_{\ell}}\right)\nonumber\\=&
+	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}\nonumber\\=&
 	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
@@
 	\\=&
-	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)
+	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
 \end{align}
@@
 and }the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain
+We multiplying it by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}+\ldots+r_{N-1})+(r_{1}+\ldots+r_{N-1})}$ and we obtain
 \begin{equation}\label{pezzo2}
 	\begin{split}
-		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
+		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}+\ldots+r_{N-1})+(r_{1}+\ldots+r_{N-1})}\\=&D(\bm{n},\bm{\xi})
 	\end{split}
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{q}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})
-	\end{split}
-\end{equation}
-Indeed we have that 
+		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})
+	\end{split}
+\end{equation}
+Indeed, 
 \begin{enumerate}
@@
 \end{equation}
-The only terms that survive are: in one case the ones with $a=d$ and $b\neq d$, giving a contribution $-n_{d}^{x}n_{b}^{x+1}$; in the other case the ones with $a\neq d$ and $b=d$, giving a contribution $n_{a}^{x}n_{d}^{x+1}$.
-Thus we obtain
+In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{b}^{x+1}$, when $a=d$; a contribution $n_{a}^{x}n_{d}^{x+1}$, when $b=d$. Thus we obtain 
 \begin{align*}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1\,:\,a\neq d}^{N}n_{a}^{x}n_{d}^{x+1}-\sum_{b=1\,:\,b\neq d}^{N}n_{d}^{x}n_{b}^{x+1}\\
-	=&\sum_{a=1\,:\,a\neq d}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1\,:\,b\neq d}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
+	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{a}^{x}n_{d}^{x+1}-\sum_{b=1}^{N}n_{d}^{x}n_{b}^{x+1}\\
+	=&\sum_{a=1}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
 	=&\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)
+	\end{split}
+\end{equation}
+In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{\ell}^{x+1}$, when $a=d$ (here we call $\ell=h_{c}(b)$); a contribution $n_{a}^{x}n_{q}^{x+1}$, when $h_{c}(b)=d$.
+Thus we obtain
+\begin{align}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a=1}^{N}n_{a}^{x}n_{b}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
 		\\&=
-		\sum_{k=1}^{N-1}n_{k}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
+		\sum_{k=1}^{N-1}n_{k}^{x}n_{b}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{b}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
 		\\&=
-		\nu(n_{q}^{x+1}-n_{d}^{x})
-	\end{split}
-\end{equation}
-where we call $q$ such that $h_{c}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
-Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
-Moreover
+		\nu(n_{b}^{x+1}-n_{d}^{x})
+\end{align}
+where  we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
+Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $b\neq d$ and $b\neq N$.
+\item \textit{Pure-mutation generator}: here we have that 
 \begin{equation}
@@
 \end{enumerate}
-Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.
-
+Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD} and \eqref{DifferenceEquation} follows.
 \paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
@@
 		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{1}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
-		\\&=
+	\end{split}
+\end{equation}
+Using equation \eqref{boundaryParamRD}, we obtain 
+\begin{align}
+			\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=
 		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
@@
 		\\&=
-		\nu\sigma_{11}\rho_{d}^{0}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{0}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\nu\sigma_{11}\rho_{d}^{\text{left}}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{\text{left}}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
 		\\&=
-		\nu \sigma_{11} (\rho_{d}^{0}-n_{d}^{1})+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}(\rho_{b}^{0}-n_{d}^{1})
-	\end{split}
-\end{equation}
-Using equation \eqref{actionGraphRD} we have \eqref{DifferenceEquation}. Similarly, using \eqref{actionGraphRD}  and \eqref{actionBoudaryRD} we have \eqref{actionBDLine}.
+		\nu \sigma_{11} (\rho_{d}^{\text{left}}-n_{d}^{1})+\nu\sigma_{12}\sum_{b=1\,:\,b\neq d}^{N-1}(\rho_{b}^{\text{left}}-n_{d}^{1})
+	\end{align}
+Therefore, \eqref{actionBDLine} follows.
 \begin{comment}

### 2023-11-27 main.tex
''
iuyfg

@@
  \begingroup\LARGE
-%\bf Multispecies stirring process: duality and exact solution
-\bf Exact solution of the multispecies stirring process \\
+\bf Exact solution of the multi-species stirring process \\
  with open boundaries
@@
  \begingroup\large \bf
-% {Rouven Frassek}
+ {Francesco Casini$^{(a,b)}$, Rouven Frassek$^{(b)}$, Cristian Giardin\`a$^{(b)}$}
  \par\endgroup
@@
 \begingroup\sffamily
-%  
-% Università degli Studi di Modena e Reggio Emilia
-%University of Modena and Reggio Emilia, 
-%\\Department of Physics, Informatics and Mathematics,\\
-%Via G. Campi 213/b, 41125 Modena, Italy\\ 
+
+ %Università degli Studi di Modena e Reggio Emilia
+(a) University of Parma, \\
+Department of ....,\\
+Via ...., .... Parma, Italy\\
+
+ \vspace{.5cm}
+
+(b) University of Modena and Reggio Emilia, \\
+Department of Physics, Informatics and Mathematics,\\
+Via G. Campi 213/b, 41125 Modena, Italy\\ 
 \par\endgroup
@@
 
+\newpage
 \tableofcontents
@@
 	\item \textit{Correlations} (Section \ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
-These probability are hard to find when $\nu>1$, however correlation can be formally written.
-	\item \textit{Instantaneous thermalization} (Section \ref{Subsection-Thermalized}): starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+These probability are hard to find when $\nu>1$.
+We give
+	in Appendix \ref{appendix-1pts-general} the expression for the one-point correlation.
+	\item \textit{Instantaneous thermalization} (Section \ref{Subsection-Thermalized}): starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process}(Section \ref{Subsection-RD}): a further dynamics is added.
+	\item \textit{Reaction-diffusion process} (Section \ref{Subsection-RD}): a further dynamics is added.
 Particle can now change type.
-The model is carefully constructed with the goal of having the average densities evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+The model is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
 Duality for the boundary driven process is also proved.
@@
 In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can host $\nu\geq 1$ particles, chosen among the $N$ types.
-Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
-All the processes considered, denoted by $\left(\bm{n}(t)\right)_{t\geq0}$ with the generator specified in each subsection, will be defined on the space
+Each site can host $\nu\geq 1$ particles, whose type is chosen among the $N$ available ones.
+The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
+The processes considered in this section will be denoted with same name $\left(\bm{n}(t)\right)_{t\geq0}$, their generator will be specified in each subsection.
+We use the notation of Section \ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
+E.g. the state space is denoted by 
 \begin{equation}\label{stateSpace-Chain}
-	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega_{x}
+	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega_{x}\,.
 \end{equation}
@@
 The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively.
-To recall it we denote this dual space by $\widetilde{\Omega}_{L}$, i.e.
+ We denote the space of the dual process by $\widetilde{\Omega}_{L}$, i.e.
 \begin{equation}\label{dualSpace-chain}
@@
 \begin{equation}
-	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\alpha_{a}}{|\alpha|}
+	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\beta_{a}}{|\beta|}\,.
 \end{equation}
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given from \eqref{siteDualGenerator} absorbing particles from sites $\{1\}$ and $\{L\}$ and putting them at extra-sites $\{0\}$ and $\{L+1\}$ respectively.
+where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $\{0\}$ and $\{L+1\}$ respectively.
 The duality function reads is \eqref{dualityElements} specified on the chain.
@@
 \end{comment}
-The dual process has absorbing boundaries.
+
+%The dual process has absorbing boundaries.
 This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process.\\
@@
 For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
-However, these absorption probabilities for higher point correlations fulfil some difference equations that are not easy to solve.
+The absorption probabilities for higher point correlations fulfill  difference equations.
 
@@
 \subsection{Instantaneous thermalization}\label{Subsection-Thermalized}
-In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality,KMP}).
+In this subsection we aim to extend to the multi-species stirring process the concept of \textit{instantaneous thermalization limit} (see \cite{carinci2013duality,KMP}).
 The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles.
-The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\epsilon=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\epsilon$.
+The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} as follows: for each bond $(x,x+1)$ the total number of particles $\epsilon=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\epsilon$.
 \subsubsection{The thermalization measure}
@@
 \end{align}
-Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{0,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
+Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall a\in\{1,\ldots,N\}$ we have $r_{a}\in \{0,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
@@
 This dual process is absorbing since the dual boundary generator $\mathcal{L}_{\text{left}}^{TH}$ ($\mathcal{L}_{\text{left}}^{TH}$) remove all dual particles at site $1$ ($L$) and put these particles in the extra-site $0$ ($L+1$) with rate 1.
-The proof of proposition \ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.
+The proof of Proposition \ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.
 \subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
@@
 \end{equation}
-where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$.
-These average occupations evolves according to the evolution equation
+where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$. Calling
+$\mathcal{L}^{rd}$ the generator of the process, these average occupations evolves according to the evolution equation
 \begin{equation}\label{EE-density}
@@
 for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$. Here $\Delta_{L}\rho(x,t)=\rho_{a}(x+1,t)+\rho_{a}(x-1,t)-2\rho_{a}(x,t)$.
-This equation is endowed with boundary conditions $\rho_{a}^{\text{left}},\rho_{\overline{a}}^{\text{left}}$ on the left and $\rho_{a}^{\text{right}},\rho_{\overline{a}}^{\text{right}}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
+This equation is endowed with boundary conditions $\rho_{a}^{\text{left}},\rho_{\overline{a}}^{\text{left}}$ on the left and $\rho_{a}^{\text{right}},\rho_{\overline{a}}^{\text{right}}$ on the right. 
+The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}).
 For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}).
@@
 \end{equation} 
- We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{0}$ and $\rho_{a}^{L+1}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$.
+ We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{\text{left}}$ and $\rho_{a}^{\text{right}}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\sum_{a=1}^{N}\rho_{a}^{\text{right}}=\nu$.
  We construct the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$.
 Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality.
-\subsubsection{The process on a chain}
+\subsubsection{The reaction-diffusion process on a chain}
 We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $L$.
@@
 \end{equation}
-with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator
+where $\mathcal{L}_{x,x+1}$ is the edge-generator \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator
 \begin{equation}
@@
 \end{equation}
-Observe that $h_{c}(\cdot)$ is surjective and injective, and thus invertible. \\
+Observe that $h_{c}(\cdot)$ is surjective and injective, and thus invertible.
+
 Moreover, we define the \textit{pure-mutation} generator
@@
 \end{equation}
-for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\nu$. \\
+for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\nu$. 
 The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values $\rho_{a}^{\text{right}}$.
-\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
-\end{remark}
+%\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+%\end{remark}
 \paragraph{Action on the occupation variable}
@@
 \end{equation}
-where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 
+where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$. For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 
 \begin{equation}\label{actionBDLine}
@@
 For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-This answers the first question we addressed to at the beginning of this section.
+%This answers the first question we addressed to at the beginning of this section. 
 \subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
@@
 This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
-{\color{blue} 
-	Indeed, we impose the detailed balance for the stirring-mutation generator $\mathcal{L}_{x,x+1}^{c}$, for arbitrary $c\in \{1,\ldots,N-2\}$. Consider the transition 
-				\begin{equation*}
-			\bm{n} \to\bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c(a)}}^{x+1}-\delta_{b}^{x+1}
-			\end{equation*} 
-		we obtain that 
-		\begin{equation*}
-			p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
-		\end{equation*}
-		that is verified if $p_{a}=p_{b}$ for all $a,b\in \{1,\ldots,N-1\}$.
+%{\color{blue} 
+%	Indeed, we impose the detailed balance for the stirring-mutation generator $\mathcal{L}_{x,x+1}^{c}$, for arbitrary $c\in \{1,\ldots,N-2\}$. Consider the transition 
+%				\begin{equation*}
+%			\bm{n} \to\bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c(a)}}^{x+1}-\delta_{b}^{x+1}
+%			\end{equation*} 
+%		we obtain that 
+%		\begin{equation*}
+%			p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
+%		\end{equation*}
+%		that is verified if $p_{a}=p_{b}$ for all $a,b\in \{1,\ldots,N-1\}$.
 A similar argument for the generator $\mathcal{L}^{m}$ gives the same conditions for the $p$'s.
@@
 %	\\=&
-	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{h_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{h_{c}(\ell)N}^{x+1}\right)\right\}
-	\\=&0\dt
+	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{h_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{h_{c}(\ell)N}^{x+1}\right)\right\}=0\dt
 \end{align*}
-In the last equality we used the fact that map $h_{c}(\cdot)$ is surjective. \\
+In the last equality we used the fact that map $h_{c}(\cdot)$ is surjective. 
 %\paragraph{Duality for $H_{x,x+1}^{m}$} 
@@
 \end{remark}
-Already for two-point correlations the computations become more involving and hard to solve.
+%Already for two-point correlations the computations become more involving and hard to solve.
 \section{Proof of duality of thermalized multi-species stirring}\label{appendix-dualityThermalized}
@@
 	\\=&
-	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
-\end{align}
-Where we used {\color{blue}
+	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{\text{left}}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
+\end{align}
+Where we used 
 \begin{equation*}
@@
 \end{align*}
-and }the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
+and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
 We multiplying it by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}+\ldots+r_{N-1})+(r_{1}+\ldots+r_{N-1})}$ and we obtain

### 2023-11-27 main.tex
giuygiuy

@@
 (a) University of Parma, \\
-Department of ....,\\
-Via ...., .... Parma, Italy\\
+Department of Mathematica, Physics, Computer Science,\\
+Parco Area delle Scienze, 7/A, 43124 Parma, Italy\\
 
@@
 (b) University of Modena and Reggio Emilia, \\
-Department of Physics, Informatics and Mathematics,\\
+Department of Physics, Computer Science and Mathematics,\\
 Via G. Campi 213/b, 41125 Modena, Italy\\ 
@@
 
- Version: \today
+% Version: \today
 \end{center}
@@
 \noindent
-...
+We study the boundary-driven version of the stirring process with $N-1$ species
+on a generic graph $G=(V,\mathcal{E})$ with reservoirs. 
+The multi-species stirring process generalizes the symmetric exclusion process, 
+which is recovered in the case $N=2$.
+We prove the existence of a dual process defined on
+an extended graph $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E})}$ which 
+includes additional extra-sites $\widetilde{V}\setminus V$ where
+dual particles gets absorbed in the long-time limit.  
+We thus obtain a characterization of the non-equilibrium
+steady state of the bounbdary-driven system in terms of the absorption
+probabilities of dual particles.
+For the case of one-dimensional chains with two reservoirs
+at the boundaries and with maximum one particle per site,
+we compute these absorption probabilities by relying
+on the underlying $\mathfrak{gl}(N)$ symmetry and the
+matrix product ansatz. Thus one gets a closed-formula
+for (long-ranged) correlations and for the 
+non-equilibrium stationary measure.
+Extensions beyond this integrable set-up
+are also discussed.
 \end{abstract}
@@
 %{\color{red}
-%The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $gl(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
+%The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $\mathfrak{gl}(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
 Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
@@
 
-Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
+Consider the Lie algebra $\mathfrak{gl}(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
 \begin{equation}\label{eq:comgl}
@@
 %{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-The process with generator \eqref{Generator} can be described in terms of $gl(N)$ Lie algebra generators.
+The process with generator \eqref{Generator} can be described in terms of $\mathfrak{gl}(N)$ Lie algebra generators.
 The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site.
@@
 \end{equation}
-We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $gl(N)$
+We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $\mathfrak{gl}(N)$
 \begin{equation}\label{secondCasimir}
@@
 \end{equation}
-that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
+that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $\mathfrak{gl}(N)$ (i.e. it commutes with all the algebra elements).  
 More precisely,  considering the standard coproduct 
@@
 \begin{split}
-\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
+\Delta:\mathfrak{gl}(N)&\to \mathfrak{gl}(N)\otimes \mathfrak{gl}(N)\\
 E_{ab}&\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
@@
 \begin{split}
-\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
+\Delta:\mathfrak{gl}(N)&\to \mathfrak{gl}(N)\otimes \mathfrak{gl}(N)\\
 E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
@@
 The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section \ref{sectionIntegrabiliy}.
-We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
+We will denote the element of the representation of the $\mathfrak{gl}(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
 $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
@@
 Therefore, it is enough to look for a symmetry of $\Delta (C)$.
-Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ the following holds:
+Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in \mathfrak{gl}(N)$ the following holds:
 \begin{equation}
@@
 Moreover, the coproduct is a Lie algebra homomorphism, i.e.
-$\forall A,B\in gl(N)$
+$\forall A,B\in \mathfrak{gl}(N)$
 \begin{equation}\label{symmetryCoproduct}
@@
 \end{equation}
-This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of $gl(N)$, and therefore it commutes with all the element of this algebra. Consider
+This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of $\mathfrak{gl}(N)$, and therefore it commutes with all the element of this algebra. Consider
 \begin{equation}\label{equationE}
@@
 \\
- Considering $A,B\in gl(N)$, the Hadamard formula reads 
+ Considering $A,B\in \mathfrak{gl}(N)$, the Hadamard formula reads 
  \begin{equation}\label{HadamardFormula}
@@
  \end{equation}
-In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $gl(N)$ with $c,d\in\{1,\ldots,N\}$.
+In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $\mathfrak{gl}(N)$ with $c,d\in\{1,\ldots,N\}$.
 Therefore we compute
@@
 We also recall the notation for the occupation variable which is called $\bm{\tau}=(\tau_1,\ldots,\tau_L)$ with $\tau_x\in\{1,\ldots,N\}$.
-The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$.
+The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $\mathfrak{gl}(N)$.
 The duality result stated in Section \ref{statementDualitySubsection} is adapted to the present situation as follows.
@@
 		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same $gl(N)$ Lie-algebraic structure?
+			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same $\mathfrak{gl}(N)$ Lie-algebraic structure?
 \end{enumerate}
@@
 we only prove duality for the bulk generator, since the boundary generators are the same of the multi-species stirring process.
-In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $gl(N)$ Lie algebra as
+In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $\mathfrak{gl}(N)$ Lie algebra as
 \begin{equation}
@@
 
- The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
+ The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $\mathfrak{gl}(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
   \begin{equation}\label{creationOperators}
@@
 Then, duality will be found by symmetry argument.\\
-We chose the $gl(N)$ Lie algebra. This is compact. The abstract basis elements are denoted by $E_{a,b}$ with $a,b\in \{1,\ldots,N\}$ that obeys to the Lie bracket relations given by
+We chose the $\mathfrak{gl}(N)$ Lie algebra. This is compact. The abstract basis elements are denoted by $E_{a,b}$ with $a,b\in \{1,\ldots,N\}$ that obeys to the Lie bracket relations given by
 \begin{equation}
@@
 \end{equation}
-We define the the following representation $(\mathcal{C}^{D},\Pi)$, where $D$ is the dimension of the representation and $\Pi:gl(N):\to \mathcal{M}_{D\times D}$ is an homeomorfism between the Lie algebra and the space $\mathcal{M}_{D\times D}$ of $D\times D$ matrices with complex coefficients.
+We define the the following representation $(\mathcal{C}^{D},\Pi)$, where $D$ is the dimension of the representation and $\Pi:\mathfrak{gl}(N):\to \mathcal{M}_{D\times D}$ is an homeomorfism between the Lie algebra and the space $\mathcal{M}_{D\times D}$ of $D\times D$ matrices with complex coefficients.
 For every elements $E_{ab}$ of the abstract Lie algebra, it associates $\Pi(E_{ab})=e_{ab}$ Since this Lie algebra is compact and semi-simple, we can characterize every irreducible representation by defining its own \textit{highest weight state}.
@@
 Thus, we can define the "highest weight" of a representation the $\mu_{0}$ that is bigger then all the other weights.
-As already pointed out, every irreducible representation of $gl(N)$ is in a one to one correspondence with its heights weight.
+As already pointed out, every irreducible representation of $\mathfrak{gl}(N)$ is in a one to one correspondence with its heights weight.
 That means that we can characterize the representations via the highest weight.
@@
 
-The algebra $gl(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it.
+The algebra $\mathfrak{gl}(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it.
 It is also possible to see that this representation can be written as a direct sum of representation of $su(2)$, each with representation $2j$ and each associated with a positive root.

### 2023-11-27 main.tex
''
^-^

@@
 In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
-The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal}.
+The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multi-species} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal}.
 
@@
 
-The remainder of this paper is organized as follows. In Section \ref{sec1} we define the open multispecies stirring
+The remainder of this paper is organized as follows. In Section \ref{sec1} we define the open multi-species stirring
 process and provide its Lie algebraic description. In Section \ref{sectionDuality} we prove duality (Theorem \ref{thm-duality}) 
-and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
+and we show that, even in the presence of multi-species, the problem of characterizing the non-equilibrium 
 steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
@@
 
-In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
+In closing this introduction we mention that we are currently working on the boundary-driven multi-species 
 model with non-compact Lie-algebras, both integrable and non-integrable, which will be presented in a 
@@
 
-In this paper we will often use the fact that the Markov generator of the multispecies stirring process can be described in terms a Lie algebra of rank $N$.
+In this paper we will often use the fact that the Markov generator of the multi-species stirring process can be described in terms a Lie algebra of rank $N$.
 In this section we provide details about this.
@@
 \section{Duality}\label{sectionDuality}
-In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
+In this section we prove the first main result of this paper. We show that the multi-species stirring process with open boundary
 can be studied by means of a dual process. After recalling the definition of duality between two
@@
 dual process has absorbing sites.
-Therefore, as shown in Corollary \ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
+Therefore, as shown in Corollary \ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multi-species stirring process with open boundary
 is reduced to the study of the absorption probabilities of dual particles.
@@
 	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,0,0)=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}\\
-	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,0,0)=\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
-		(x_3-2)}{L \left(L^2-1\right)}\\
-	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,0)=\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}\\
+ &\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,1)=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,0)=\frac{x_1 (L(1-x_3)+x_2 (x_3-2)+1)}{L(L^2-1)}\\
 	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,0,1)=\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}
@@
 		\left(L^2-1\right)}\\
-	&\mathcal{P}_{x_{1},x_{2},x_{3}}(0,1,1)=\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}\\
+	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,0,0)=\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
+	(x_3-2)}{L \left(L^2-1\right)}\\
 	&\mathcal{P}_{x_{1},x_{2},x_{3}}(1,1,1)=\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}
-\end{split}\dt
+\end{split}
 \end{equation}
@@
 while $p_{N}=1-\sum_{a=1}^{N-1}p_{a}$\\
-For the boundary generators $\mathcal{L}_{\text{left}}^{rd}$ and $\mathcal{L}_{\text{right}}^{rd}$ we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
+For the boundary generators $\mathcal{L}_{\text{left}}^{rd}$ and $\mathcal{L}_{\text{right}}^{rd}$ we have that, analogously to what happens for the multi-species stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
 \end{comment}
@@
 and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We multiplying it by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}+\ldots+r_{N-1})+(r_{1}+\ldots+r_{N-1})}$ and we obtain
+We multiplying it by $\prod_{k=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{k}+r_{k}}$ and we obtain
 \begin{equation}\label{pezzo2}

### 2023-11-27 main.tex
ack
bf
some changes: title and minor things

--- 2023-11-27 main.tex
@@
  \begingroup\LARGE
-\bf Exact solution of the multi-species stirring process \\
+% \bf Exact solution of the multispecies stirring process \\
+%  with open boundaries
+
+\bf Duality for the multispecies stirring process 
  with open boundaries
@@
  \begingroup\large \bf
- {Francesco Casini$^{(a,b)}$, Rouven Frassek$^{(b)}$, Cristian Giardin\`a$^{(b)}$}
+ {Francesco Casini$^{(a,b)}$, Rouven Frassek$^{(a)}$, Cristian Giardin\`a$^{(a)}$}
  \par\endgroup
@@
  %Università degli Studi di Modena e Reggio Emilia
-(a) University of Parma, \\
-Department of Mathematica, Physics, Computer Science,\\
-Parco Area delle Scienze, 7/A, 43124 Parma, Italy\\
-
- \vspace{.5cm}
-
-(b) University of Modena and Reggio Emilia, \\
+$(a)$ University of Modena and Reggio Emilia, \\
 Department of Physics, Computer Science and Mathematics,\\
 Via G. Campi 213/b, 41125 Modena, Italy\\ 
+ \vspace{.5cm}
+$(b)$ University of Parma, \\
+Department of Mathematical, Physical and and Computer Sciences\\
+Parco Area delle Scienze, 7/A, 43124 Parma, Italy\\
+ %
 \par\endgroup
@@
 on a generic graph $G=(V,\mathcal{E})$ with reservoirs. 
-The multi-species stirring process generalizes the symmetric exclusion process, 
+The multispecies stirring process generalizes the symmetric exclusion process, 
 which is recovered in the case $N=2$.
@@
 the XXX Heisenberg Hamiltonian with $\mathfrak{su}(2)$ spins of value 1/2.
-In this paper, we investigate the multi-species analog of the exclusion process in the boundary-driven context, i.e.
-the {\em  multi-species stirring process with open boundaries}.
+In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context, i.e.
+the {\em  multispecies stirring process with open boundaries}.
 The bulk part of the model with $N$ species is associated with the integrable higher-rank
@@
 For recent examples in the framework of single-species systems, see \cite{frassek2020eigenstates, frassek2022exact, frassek2020non, floreani2023non}.
-Here we generalize the duality approach to the set-up of multi-species particle systems.
-
-The remainder of this paper is organized as follows. In Section \ref{sec1} we define the open multispecies stirring
-process and provide its Lie algebraic description. In Section \ref{sectionDuality} we prove duality (Theorem \ref{thm-duality}) 
+Here we generalize the duality approach to the set-up of multispecies particle systems.
+
+The remainder of this paper is organized as follows. In Section~\ref{sec1} we define the open multispecies stirring
+process and provide its Lie algebraic description. In Section~\ref{sectionDuality} we prove duality (Theorem~\ref{thm-duality}) 
 and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
 steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
-system has a general spatial structure described by a general graph. In Section \ref{sectionIntegrabiliy} we then obtain a closed formula 
-for the stationary correlations (Theorem \ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
+system has a general spatial structure described by a general graph. In Section~\ref{sectionIntegrabiliy} we then obtain a closed formula 
+for the stationary correlations (Theorem~\ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
 particle per site, which is driven out-of-equilbrium by two reservoirs acting at the left and right boundaries. 
 Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz \cite{vanicat2017exact},
-which is in fact also simplified by the use of duality. Finally in Section \ref{sec5} we discuss a few extensions 
+which is in fact also simplified by the use of duality. Finally in Section~\ref{sec5} we discuss a few extensions 
 and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
@@
 In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
-model with non-compact Lie-algebras, both integrable and non-integrable, which will be presented in a 
+model with non-compact Lie algebras, both integrable and non-integrable, which will be presented in a 
 future paper.
@@
 {\bf Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM), Prin-project {\color{blue} xxxx}, FAR-project {\color{blue} xxxx} UniMoRe.
+
+INFN Progetto Giovani
 
@@
 How far can we push our analysis for the characterization of the non equilibrium steady state?\\
-%The way one can define a multi-type (or multi-species) interacting particle system is not unique.
+%The way one can define a multi-type (or multispecies) interacting particle system is not unique.
 In the literature there are many.
@@
 % \textbf{Some interesting references and extensions?}:
-% Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
-% Use exact solution to compute large deviation rate function extending to the multi-species case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
+% Multispecies version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
+% Use exact solution to compute large deviation rate function extending to the multispecies case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
 % Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
@@
 \subsection{Informal description of the process}
-The process studied in this paper is the {\em multi-species stirring process}
+The process studied in this paper is the {\em multispecies stirring process}
 with open boundaries. 
@@
 The choice of type $N$ for the distinguished type is arbitrary and does not affect
-the results. In particular, we shall see in Section \ref{sectionDuality} about duality, that
+the results. In particular, we shall see in Section~\ref{sectionDuality} about duality, that
 the dual process eventually has only particles of type $N$ on the graph.
@@
 \subsection{The process generator}\label{subsectionGeneratorStr}
-We now give the mathematical description of the multi-species stirring process.
+We now give the mathematical description of the multispecies stirring process.
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
@@
 %For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$. 
-%See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dynamics. 
+%See Figure~\ref{fig:1} and  Figure~\ref{fig:2} for a visualisation of the dynamics. 
 %\begin{figure}[h]
@@
 This can be proved  by checking that detailed balance is satisfied. 
-If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost (but see remark \ref{rem-rev} below): 
+If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost (but see Remark~\ref{rem-rev} below): 
 each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
@@
 In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites
-		then condition \eqref{cond-gen} is the multi-species counterpart of $\alpha\delta=\beta\gamma$ of the boundary driven partially excluded process introduced in \cite{schutzSandow} (see Section 3.2 of \cite{carinci2013duality}).
+		then condition \eqref{cond-gen} is the multispecies counterpart of $\alpha\delta=\beta\gamma$ of the boundary driven partially excluded process introduced in \cite{schutzSandow} (see Section 3.2 of \cite{carinci2013duality}).
 		\end{remark}
@@
 %\newline 
-%\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
+%\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix~\ref{appA}.
 \\ \\
@@
 Namely,
-a vector $|{\bf n}\rangle \in \Omega$ can be written as
+a vector $|{\bm{n}}\rangle \in \Omega$ can be written as
 %We now define the equivalent of \eqref{stateSpace} in the vector notation
@@
 \begin{equation}
-|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
+|{\bm{n}}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1}^{x},\ldots,n_{N}^{x}\rangle\right)
 \end{equation}
@@
 %	\begin{equation*}
-%		|{\bf n}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)
+%		|{\bm{n}}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)
 %	\end{equation*}}
@@
 \begin{equation}
-    \langle {\bf n}|{\bf m}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
+    \langle {\bm{n}}|{\bm{m}}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
 \end{equation}
@@
 \begin{equation}
-    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
+    \mathcal{L}f( {\bm{n}})=\langle f|H| {\bm{n}}\rangle
 \end{equation}
@@
 \begin{equation}
-    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|\dt
+    \langle f|=\sum_{ {{\bm{m}}\in \Omega}}f( {\bm{m}})\langle  {\bm{m}}|\dt
 \end{equation}
@@
 \subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
-In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
+In this section we specialize the multispecies stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
 These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium.
@@
 \end{equation}
-The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section \ref{sectionIntegrabiliy}.
+The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section~\ref{sectionIntegrabiliy}.
 We will denote the element of the representation of the $\mathfrak{gl}(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
@@
 with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-Since the maximal occupancy at each site is $\nu=1$,  the configuration $\bm{n}$ introduced in Section \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
+Since the maximal occupancy at each site is $\nu=1$,  the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
 \begin{equation}\label{notation-change-relation}
@@
 %\end{equation}
-Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
+Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
 
@@
 can be studied by means of a dual process. After recalling the definition of duality between two
-Markov processes in Section \ref{def-duality}, we formulate our duality result  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
+Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
 The duality result is important since it yields several simplifications, the main one being that the
 dual process has absorbing sites.
-Therefore, as shown in Corollary \ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
+Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
 is reduced to the study of the absorption probabilities of dual particles.
@@
 \end{remark}
-\subsection{Duality for the open multi-species stirring process}\label{statementDualitySubsection}
-In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ with open boundaries, defined by the generator \eqref{Generator}.
+\subsection{Duality for the open multispecies stirring process}\label{statementDualitySubsection}
+In this section we formulate duality for the multispecies stirring process $(\bm{n}(t))_{t\geq 0}$ with open boundaries, defined by the generator \eqref{Generator}.
 The dual  process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the \textit{enlarged graph} $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E}})$ where 
@@
 \begin{theorem}[Absorbing duality]\label{thm-duality}
-	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator
+	The multispecies stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator
 	 \begin{equation}\label{DualGenerator}
@@
 \begin{comment}
-We define the duality function of the open multi-species stirring process as
+We define the duality function of the open multispecies stirring process as
 \begin{equation}\label{dualityElements}
@@
 The dual dynamics is described as follows.
-On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual Markov generator gives rise to  the multi-species stirring dynamics on the graph.
+On one hand, the edge part $\mathcal{L}_{x,y}$ of the dual Markov generator gives rise to  the multispecies stirring dynamics on the graph.
 On the other hand, the site
@@
 %
-\subsection{Proof of Theorem \ref{thm-duality}}
+\subsection{Proof of Theorem~\ref{thm-duality}}
 \label{proof-th-duality}
@@
 \subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
-Here we consider the chain defined in Section \ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
+Here we consider the chain defined in Section~\ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
 We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
@@
 The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $\mathfrak{gl}(N)$.
-The duality result stated in Section \ref{statementDualitySubsection} is adapted to the present situation as follows.
+The duality result stated in Section~\ref{statementDualitySubsection} is adapted to the present situation as follows.
 The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
@@
 We also notice that, up the the bosonic creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
-This simplification will be crucial in Section \ref{sectionIntegrabiliy}.\\
+This simplification will be crucial in Section~\ref{sectionIntegrabiliy}.\\
 
@@
 Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles.
-Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.
+Therefore, to determine the non-equilibrium steady state correlations of the integrable multispecies stirring process, it is enough to compute these absorption probabilities.
 In the following we denote by $\mu$ the non-equilibrium steady state distribution and we call $\bm{Y} = (Y_1,\ldots,Y_L)$ the random vector with law $\mu$.
@@
 \end{corollary}
-\textbf{Proof of Corollary \ref{Corolollary-ABS_Corr-abstract}}:
+\textbf{Proof of Corollary~\ref{Corolollary-ABS_Corr-abstract}}:
 For any $\bm{\tau}\in \Omega^{'}$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
@@
 \end{corollary}
-\textbf{Proof of Corollary \ref{Corollary-NESS-ABS}:}
+\textbf{Proof of Corollary~\ref{Corollary-NESS-ABS}:}
 Given $\bm{\tau}\in \Omega^{'}$,  we have 
@@
 \begin{remark}\label{Remark-extension-graph-nu}
-	The results in Corollary \ref{Corolollary-ABS_Corr-abstract} and in Corollary \ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for higher maximal occupancies $\nu >1$.
+	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for higher maximal occupancies $\nu >1$.
 	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
-	Thus we chose to present them in such a context. For the chain with higher maximal occupancies $\nu >1$ see Section \ref{Subsection-ss-nonI}.
+	Thus we chose to present them in such a context. For the chain with higher maximal occupancies $\nu >1$ see Section~\ref{Subsection-ss-nonI}.
 \end{remark}
@@
 \section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
-In this section we combine duality and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Section \ref{integrableChain-duality}.
-As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary \ref{Corolollary-ABS_Corr-abstract}) for the correlations
-and (using Corollary \ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
+In this section we combine duality and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}.
+As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
+and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
 We start by recalling the formulation of the MPA  and then we explain our strategy.
@@
 \subsection{Matrix product ansatz for the non-equilibrium steady state}
-The matrix product ansatz for the multi-species stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.
+The matrix product ansatz for the multispecies stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.
  Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
@@
 \subsection{Strategy}
- In the next Section \ref{subsection-exact} we will show that the existence of the absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the algebra of operators $X_a$ defined in previous
+ In the next Section~\ref{subsection-exact} we will show that the existence of the absorbing dual process established in Section~\ref{sectionDuality} simplifies substantially the algebra of operators $X_a$ defined in previous
  section.  The idea is summarized in the following scheme. 
@@
 Finally, we invert the similarities and retrieve the right eigenvector of $H^{'}$ with vanishing eigenvalue and  the arbitrary correlations in the non-equilibrium steady state.
-The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix \ref{appB}.
+The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix~\ref{appB}.
 \begin{comment}
@@
 Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}.
-In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
+In subsection~\ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
 This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary.
@@
 \end{comment}
-\subsection{Proof of Theorem \ref{thm-correlations}}
+\subsection{Proof of Theorem~\ref{thm-correlations}}
 The proof of formula \eqref{exactCorrelations} is split into the following steps:
 \begin{itemize}
-	\item In Section \ref{subsectionSTransf}, we introduce two similarity transformations $S_1$ and  $S_2$. 
+	\item In Section~\ref{subsectionSTransf}, we introduce two similarity transformations $S_1$ and  $S_2$. 
 	 The first turns the Hamiltonian $H$ into $H^{'}= S_{1} H S_{1}^{-1} $ with boundary terms in a triangular form;
@@
 	Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 
-	\item In Section \ref{subsectionSSHsec} we apply the MPA to $H^{''}$.
+	\item In Section~\ref{subsectionSSHsec} we apply the MPA to $H^{''}$.
 Here the commutation relations defining the matrix algebra are simpler.
 The explicit expression for $|\Psi^{''}\rangle$ is determined (see \eqref{ResulsBasis}).
-	\item In subsection \ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
-	\item In Section \ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$.
+	\item In subsection~\ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
+	\item In Section~\ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$.
 By exploiting a binomial formula we rewrite the correlations in terms
-	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary \ref{Corolollary-ABS_Corr-abstract}.
-	For completeness, we also show that Corollary \ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$.
+	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary~\ref{Corolollary-ABS_Corr-abstract}.
+	For completeness, we also show that Corollary~\ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$.
 	\end{itemize}
@@
 \end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Section \ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Section~\ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
 \begin{equation}
@@
 \subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
-%We argue similarly as in the Section \ref{correlation-section}. 
+%We argue similarly as in the Section~\ref{correlation-section}. 
 We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau})= (N,\ldots,N)$. We show here that for this particular configuration
@@
 \end{equation}
- Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation \ref{useful-InInterpretation}, we obtain 
+ Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
  	\begin{equation}\label{interpretation-PsiP}
@@
 \subsubsection{Steady state}\label{appB}
-By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary \ref{Corollary-NESS-ABS}.
+By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary~\ref{Corollary-NESS-ABS}.
 Indeed we show here that
-$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary \ref{Corollary-NESS-ABS}.
+$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary~\ref{Corollary-NESS-ABS}.
 On a single site we have that 
@@
 %\begin{remark}%[Correlation as the steady state of a $m$-chain ]
-%	We observe that, as a consequence of Section \ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e.
+%	We observe that, as a consequence of Section~\ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e.
 $\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then
@@
 % As a consequence, we can give a different interpretation to correlation computed in \eqref{exactCorrelations}.
-Consider the sites $(x_{k})_{k\in \{1,\ldots,m\}}$ and fix $(a_{k})_{k\in \{1,\ldots,m\}}$ introduced in Theorem \ref{thm-correlations}.
+Consider the sites $(x_{k})_{k\in \{1,\ldots,m\}}$ and fix $(a_{k})_{k\in \{1,\ldots,m\}}$ introduced in Theorem~\ref{thm-correlations}.
 We define a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$.
@@
 
-		From Section \ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}. Thus, we have that  
+		From Section~\ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}. Thus, we have that  
 			\begin{equation}
@@
 				\end{align}
-				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that
+				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section~\ref{correlation-section}, we have that
 				\begin{equation}
@@
 					\end{equation}
-					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
+					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section~\ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
 					\begin{equation}
@@
 \subsection{The single-species case (SSEP)}
-The computations made for the multi-species stirring process can be specialized to the single-species case $N=2$.
+The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$.
 In this situation we retrieve the SSEP, that was already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
@@
 \end{equation}
- We only report the main results, since the computations are just a specific case of the ones done for the multi-species stirring process. 
+ We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process. 
 \paragraph{Correlations of SSEP.}
@@
  Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression.
-We report the explicit formula and the proof in Appendix \ref{appB}.\\
+We report the explicit formula and the proof in Appendix~\ref{appB}.\\
 \\
@@
 \begin{comment}
-\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Section \ref{subsectionSSHsec}.
+\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Section~\ref{subsectionSSHsec}.
 If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
@@
 \label{sec5}
-In Sections \ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using integrability.  
+In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using integrability.  
 The aim of this section is to study the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
 \begin{enumerate}
-	\item \textit{Correlations} (Section \ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
 These probability are hard to find when $\nu>1$.
 We give
-	in Appendix \ref{appendix-1pts-general} the expression for the one-point correlation.
-	\item \textit{Instantaneous thermalization} (Section \ref{Subsection-Thermalized}): starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+	in Appendix~\ref{appendix-1pts-general} the expression for the one-point correlation.
+	\item \textit{Instantaneous thermalization} (Section~\ref{Subsection-Thermalized}): starting from the multispecies stirring dynamics, we define the thermalized process, where particle are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section \ref{Subsection-RD}): a further dynamics is added.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): a further dynamics is added.
 Particle can now change type.
@@
 The processes considered in this section will be denoted with same name $\left(\bm{n}(t)\right)_{t\geq0}$, their generator will be specified in each subsection.
-We use the notation of Section \ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
+We use the notation of Section~\ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
 E.g. the state space is denoted by 
@@
 This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
-This is a generalization for the non-integrable chain of the Corollary \ref{Corolollary-ABS_Corr-abstract}.
+This is a generalization for the non-integrable chain of the Corollary~\ref{Corolollary-ABS_Corr-abstract}.
 The process $\left(\bm{n}(t)\right)_{t\geq0}$ has generator
@@
 \end{equation}
-here we recall that, generalizing Corollary \ref{Corolollary-ABS_Corr-abstract}, %that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and
+here we recall that, generalizing Corollary~\ref{Corolollary-ABS_Corr-abstract}, %that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and
 \begin{equation}\label{Pass} 
@@
  These correlations can be computed once the absorption probabilities are known.
-For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
+For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
 The absorption probabilities for higher point correlations fulfill  difference equations.
@@
 \subsection{Instantaneous thermalization}\label{Subsection-Thermalized}
-In this subsection we aim to extend to the multi-species stirring process the concept of \textit{instantaneous thermalization limit} (see \cite{carinci2013duality,KMP}).
+In this subsection we aim to extend to the multispecies stirring process the concept of \textit{instantaneous thermalization limit} (see \cite{carinci2013duality,KMP}).
 The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles.
@@
 %provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
-\subsubsection{Thermalized multi-species stirring process}
-The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace-Chain} and its generator reads
+\subsubsection{Thermalized multispecies stirring process}
+The thermalized multispecies stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace-Chain} and its generator reads
 \begin{equation}\label{thermalizedGenerator}
@@
 \subsubsection{The dual thermalized process}\label{subsection-dualTHM}
-Here we state the duality result for the thermalized multi-species stirring process with boundary driving.
-\begin{proposition}[Duality for the thermalized multi-species stirring process]\label{proposition-dualityTHM}
-The thermalized multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ on the state space $\Omega_{L}$, with generator $\mathcal{L}^{TH}$ defined in \eqref{thermalizedGenerator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ on the enlarged configuration space $\widetilde{\Omega}_{L}$, with dual generator
+Here we state the duality result for the thermalized multispecies stirring process with boundary driving.
+\begin{proposition}[Duality for the thermalized multispecies stirring process]\label{proposition-dualityTHM}
+The thermalized multispecies stirring process $(\bm{n}(t))_{t\geq 0}$ on the state space $\Omega_{L}$, with generator $\mathcal{L}^{TH}$ defined in \eqref{thermalizedGenerator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ on the enlarged configuration space $\widetilde{\Omega}_{L}$, with dual generator
 \begin{equation}
@@
 \end{align}
-The duality function is the same of the multi-species stirring process, i.e. 
+The duality function is the same of the multispecies stirring process, i.e. 
 \begin{equation}
@@
 This dual process is absorbing since the dual boundary generator $\mathcal{L}_{\text{left}}^{TH}$ ($\mathcal{L}_{\text{left}}^{TH}$) remove all dual particles at site $1$ ($L$) and put these particles in the extra-site $0$ ($L+1$) with rate 1.
-The proof of Proposition \ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.
-\subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
+The proof of Proposition~\ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix~\ref{appendix-dualityThermalized}.
+\subsection{Multispecies stirring process with reaction} \label{Subsection-RD}
 We define the average density occupation of species $a$ at site $x$ as
@@
 		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same $\mathfrak{gl}(N)$ Lie-algebraic structure?
+			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same $\mathfrak{gl}(N)$ Lie algebraic structure?
 \end{enumerate}
@@
 \end{equation}
-where $\mathcal{L}_{x,x+1}$ is the edge-generator \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator
+where $\mathcal{L}_{x,x+1}$ is the edge-generator \eqref{edgeGenerator} of the multispecies stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator
 \begin{equation}
@@
 The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values $\rho_{a}^{\text{right}}$.
-%\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}.
+%\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multispecies stirring process \eqref{siteGenerator}.
 %\end{remark}
@@
 We only report the final result.
-The details are written in Appendix \ref{appendix-RD}.
+The details are written in Appendix~\ref{appendix-RD}.
 For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{a}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ at site $x$ reads
@@
 Considering the boundary generators, one obtain the result.}
-% Arguing as in Remark \ref{rem-rev}, conditions \eqref{cond-gen} become here
+% Arguing as in Remark~\ref{rem-rev}, conditions \eqref{cond-gen} become here
 %\begin{equation}
@@
 %\end{equation} 
-%where $\alpha_{a}=\alpha_{b}=\alpha$ and $\beta_{a}=\beta_{b}=\beta$ for all $a,b\in \{1,\ldots,N-1\}$.%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring.
+%where $\alpha_{a}=\alpha_{b}=\alpha$ and $\beta_{a}=\beta_{b}=\beta$ for all $a,b\in \{1,\ldots,N-1\}$.%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multispecies stirring.
 Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
@@
 \subsubsection{Duality for the reaction-diffusion process}
-In this section we formulate duality for the multi-species reaction diffusion process.
-This answer to the second question addressed at the beginning of Section \ref{Subsection-RD}.
+In this section we formulate duality for the multispecies reaction diffusion process.
+This answer to the second question addressed at the beginning of Section~\ref{Subsection-RD}.
 The dual process is defined on the enlarged state space $\widetilde{\Omega}_{L}$.
 \begin{proposition}[Duality for the reaction-diffusion process]\label{propositin-duality-RD}
-The reaction-diffusion multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, on the state space $\Omega_{L}$, with generator $\mathcal{L}^{rd}$ defined in \eqref{RDGenerator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ on the state space $\widetilde{\Omega}_{L}$ with dual generator
+The reaction-diffusion multispecies stirring process $(\bm{n}(t))_{t\geq 0}$, on the state space $\Omega_{L}$, with generator $\mathcal{L}^{rd}$ defined in \eqref{RDGenerator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ on the state space $\widetilde{\Omega}_{L}$ with dual generator
 \begin{equation}\label{DualGeneratorRD}
@@
 
-\paragraph{Proof of Proposition \ref{propositin-duality-RD}:}
-we only prove duality for the bulk generator, since the boundary generators are the same of the multi-species stirring process.
-In the spirit of Section \ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $\mathfrak{gl}(N)$ Lie algebra as
+\paragraph{Proof of Proposition~\ref{propositin-duality-RD}:}
+we only prove duality for the bulk generator, since the boundary generators are the same of the multispecies stirring process.
+In the spirit of Section~\ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $\mathfrak{gl}(N)$ Lie algebra as
 \begin{equation}
@@
 \end{align}
-Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ commute with $\exp{(E^{x})}\exp{(E^{x+1})}$, where $E$ is defined in \eqref{EquationEx}.
+Since the matrix $R_{x}$ is the same as in Section~\ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ commute with $\exp{(E^{x})}\exp{(E^{x+1})}$, where $E$ is defined in \eqref{EquationEx}.
 Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain
@@
 However, something about correlations can be said using duality.
-In this subsection we still consider the same geometry of \ref{subsection-exact}.
+In this subsection we still consider the same geometry of~\ref{subsection-exact}.
 As pointed out in section~\ref{sectionDuality}, the dual process voids the chain.
@@
 %\section{Conclusion and outlook}
-%Multi-species version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
-%Use exact solution to compute large deviation rate function extending to the multi-species case results %proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
+%Multispecies version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
+%Use exact solution to compute large deviation rate function extending to the multispecies case results %proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
 %Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
@@
 %Already for two-point correlations the computations become more involving and hard to solve.
-\section{Proof of duality of thermalized multi-species stirring}\label{appendix-dualityThermalized}
+\section{Proof of duality of thermalized multispecies stirring}\label{appendix-dualityThermalized}
 The proof of the duality consists in showing
@@
 Duality for the right boundary is similar. \\
-Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process.
+Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multispecies stirring process.
 To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function.

### 2023-11-28 main.tex
Section 4.2

@@
 \section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
-In this section we combine duality and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}.
-As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
+In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}.
+As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
 and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
@@
 \subsection{Strategy}
- In the next Section~\ref{subsection-exact} we will show that the existence of the absorbing dual process established in Section~\ref{sectionDuality} simplifies substantially the algebra of operators $X_a$ defined in previous
- section.  The idea is summarized in the following scheme. 
+ In the next Section~\ref{subsection-exact} we will show that the DEHP albegra in \eqref{bulk}-\eqref{rightBoundary} can be simplified substantially using the ${gl}(N)$ invariance of the bulk.
+In fact, such simplification can always be achieved if
+  there exists an absorbing dual process as established in Section~\ref{sectionDuality}
+
+ The idea is summarized in the following scheme. 
  We define a sequence of similarity transformation such that 
@@
  where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal.
-Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler.
-As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly.
+Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} simplify significantly.
+More precisely for the components of $\tilde X=S_2S_1 X$ we obtain the bulk relations
+\begin{equation}\label{commutationsBula2}
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt
+\end{equation}
+for $a=1,\ldots,N-1$. 
+At the boundaries 
+\begin{equation}\label{commLEFT2}
+	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
+	\co \qquad 
+	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N-1
+	\,.
+\end{equation} 
+where again we have  $a=1,\ldots,N-1$.
+As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written exactly in closed-form.
 Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e.
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt
-\end{equation}
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co %\forall a\in \{1,\ldots,N-1\}\dt
+\end{equation}
+cf.~\eqref{commutationsBula2}.
 Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ on the boundary vectors are given by 
 \begin{equation}\label{commLEFT}
-	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle\co W|%\qquad\forall a=1,\ldots,N-1
+	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
+	\co
 \end{equation}
@@
 	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N-1
-\end{equation} 
+	\co
+\end{equation} 
+cf.~\eqref{commLEFT2}.
 Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as

### 2023-11-28 main.tex
ll

@@
 We thus obtain a characterization of the non-equilibrium
-steady state of the bounbdary-driven system in terms of the absorption
+steady state of the boundary-driven system in terms of the absorption
 probabilities of dual particles.
@@
 we compute these absorption probabilities by relying
-on the underlying $\mathfrak{gl}(N)$ symmetry and the
+on the underlying ${gl}(N)$ symmetry and the
 matrix product ansatz. Thus one gets a closed-formula
@@
 In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
-The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal}.
-
-For the single species case, the exclusion process with open boundaries \cite{derrida1993exact} has been of crucial importance in our understanding of the structural properties of non-equilibrium state states, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviation \cite{mallick2022exact,bodineau2005current}.
+{\color{red} The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal}.}
+{\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
+
+For the single species case, {\color{blue} the solution of } the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviation \cite{mallick2022exact,bodineau2005current}.
 The results available for the exclusion process are rooted in the algebraic properties of the corresponding integrable quantum spin chain, i.e.
-the XXX Heisenberg Hamiltonian with $\mathfrak{su}(2)$ spins of value 1/2.
+the XXX Heisenberg Hamiltonian with ${su}(2)$ spins of value 1/2.
 In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context, i.e.
@@
 The bulk part of the model with $N$ species is associated with the integrable higher-rank
-Heisenberg XXX Hamiltonian having  $\mathfrak{gl}(N)$ symmetry.
+Heisenberg XXX Hamiltonian having  ${gl}(N)$ symmetry.
 
@@
 %{\color{red}
-%The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank $\mathfrak{gl}(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
+%The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank ${gl}(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
 Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
@@
 
-Consider the Lie algebra $\mathfrak{gl}(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
+Consider the Lie algebra ${gl}(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
 \begin{equation}\label{eq:comgl}
@@
 %{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-The process with generator \eqref{Generator} can be described in terms of $\mathfrak{gl}(N)$ Lie algebra generators.
+The process with generator \eqref{Generator} can be described in terms of ${gl}(N)$ Lie algebra generators.
 The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site.
@@
 \end{equation}
-We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of $\mathfrak{gl}(N)$
+We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the quadratic Casimir of ${gl}(N)$
 \begin{equation}\label{secondCasimir}
@@
 \end{equation}
-that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of $\mathfrak{gl}(N)$ (i.e. it commutes with all the algebra elements).  
+that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  
 More precisely,  considering the standard coproduct 
@@
 \begin{split}
-\Delta:\mathfrak{gl}(N)&\to \mathfrak{gl}(N)\otimes \mathfrak{gl}(N)\\
+\Delta:{gl}(N)&\to {gl}(N)\otimes {gl}(N)\\
 E_{ab}&\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
@@
 \begin{split}
-\Delta:\mathfrak{gl}(N)&\to \mathfrak{gl}(N)\otimes \mathfrak{gl}(N)\\
+\Delta:{gl}(N)&\to {gl}(N)\otimes {gl}(N)\\
 E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
@@
 The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section~\ref{sectionIntegrabiliy}.
-We will denote the element of the representation of the $\mathfrak{gl}(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
+We will denote the element of the representation of the ${gl}(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
 $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
@@
 Therefore, it is enough to look for a symmetry of $\Delta (C)$.
-Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in \mathfrak{gl}(N)$ the following holds:
+Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in {gl}(N)$ the following holds:
 \begin{equation}
@@
 Moreover, the coproduct is a Lie algebra homomorphism, i.e.
-$\forall A,B\in \mathfrak{gl}(N)$
+$\forall A,B\in {gl}(N)$
 \begin{equation}\label{symmetryCoproduct}
@@
 \end{equation}
-This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of $\mathfrak{gl}(N)$, and therefore it commutes with all the element of this algebra. Consider
+This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of ${gl}(N)$, and therefore it commutes with all the element of this algebra. Consider
 \begin{equation}\label{equationE}
@@
 \\
- Considering $A,B\in \mathfrak{gl}(N)$, the Hadamard formula reads 
+ Considering $A,B\in {gl}(N)$, the Hadamard formula reads 
  \begin{equation}\label{HadamardFormula}
@@
  \end{equation}
-In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $\mathfrak{gl}(N)$ with $c,d\in\{1,\ldots,N\}$.
+In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra ${gl}(N)$ with $c,d\in\{1,\ldots,N\}$.
 Therefore we compute
@@
 We also recall the notation for the occupation variable which is called $\bm{\tau}=(\tau_1,\ldots,\tau_L)$ with $\tau_x\in\{1,\ldots,N\}$.
-The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $\mathfrak{gl}(N)$.
+The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of ${gl}(N)$.
 The duality result stated in Section~\ref{statementDualitySubsection} is adapted to the present situation as follows.
@@
 		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
-			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same $\mathfrak{gl}(N)$ Lie algebraic structure?
+			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same ${gl}(N)$ Lie algebraic structure?
 \end{enumerate}
@@
 we only prove duality for the bulk generator, since the boundary generators are the same of the multispecies stirring process.
-In the spirit of Section~\ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the $\mathfrak{gl}(N)$ Lie algebra as
+In the spirit of Section~\ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the ${gl}(N)$ Lie algebra as
 \begin{equation}
@@
 
- The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $\mathfrak{gl}(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
+ The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of ${gl}(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
   \begin{equation}\label{creationOperators}
@@
 Then, duality will be found by symmetry argument.\\
-We chose the $\mathfrak{gl}(N)$ Lie algebra. This is compact. The abstract basis elements are denoted by $E_{a,b}$ with $a,b\in \{1,\ldots,N\}$ that obeys to the Lie bracket relations given by
+We chose the ${gl}(N)$ Lie algebra. This is compact. The abstract basis elements are denoted by $E_{a,b}$ with $a,b\in \{1,\ldots,N\}$ that obeys to the Lie bracket relations given by
 \begin{equation}
@@
 \end{equation}
-We define the the following representation $(\mathcal{C}^{D},\Pi)$, where $D$ is the dimension of the representation and $\Pi:\mathfrak{gl}(N):\to \mathcal{M}_{D\times D}$ is an homeomorfism between the Lie algebra and the space $\mathcal{M}_{D\times D}$ of $D\times D$ matrices with complex coefficients.
+We define the the following representation $(\mathcal{C}^{D},\Pi)$, where $D$ is the dimension of the representation and $\Pi:{gl}(N):\to \mathcal{M}_{D\times D}$ is an homeomorfism between the Lie algebra and the space $\mathcal{M}_{D\times D}$ of $D\times D$ matrices with complex coefficients.
 For every elements $E_{ab}$ of the abstract Lie algebra, it associates $\Pi(E_{ab})=e_{ab}$ Since this Lie algebra is compact and semi-simple, we can characterize every irreducible representation by defining its own \textit{highest weight state}.
@@
 Thus, we can define the "highest weight" of a representation the $\mu_{0}$ that is bigger then all the other weights.
-As already pointed out, every irreducible representation of $\mathfrak{gl}(N)$ is in a one to one correspondence with its heights weight.
+As already pointed out, every irreducible representation of ${gl}(N)$ is in a one to one correspondence with its heights weight.
 That means that we can characterize the representations via the highest weight.
@@
 
-The algebra $\mathfrak{gl}(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it.
+The algebra ${gl}(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it.
 It is also possible to see that this representation can be written as a direct sum of representation of $su(2)$, each with representation $2j$ and each associated with a positive root.

### 2023-11-28 main.tex
lll

@@
 In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
-{\color{red} The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal}.}
+{\color{red} The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal,floreani2023non}.}
 {\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
 
-For the single species case, {\color{blue} the solution of } the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviation \cite{mallick2022exact,bodineau2005current}.
-The results available for the exclusion process are rooted in the algebraic properties of the corresponding integrable quantum spin chain, i.e.
-the XXX Heisenberg Hamiltonian with ${su}(2)$ spins of value 1/2.
-In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context, i.e.
+{\color{red} I do not understand why we immediately start with XXX although the duality approach is much more general.}
+For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
+The results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable quantum spin chain, i.e.
+the XXX Heisenberg Hamiltonian with ${su}(2)$ spins of value $s=1/2$.
+In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context \cite{vanicat2017exact}, i.e.
 the {\em  multispecies stirring process with open boundaries}.
-The bulk part of the model with $N$ species is associated with the integrable higher-rank
-Heisenberg XXX Hamiltonian having  ${gl}(N)$ symmetry.
+See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.
+The bulk part of the model with $N$ species is associated with the integrable ${gl}(N)$
+Heisenberg XXX Hamiltonian with integrable non-diagonal open boundaries.
 
@@
 is reduced to the problem of computing the absorption probabilities of the dual particles. 
-In general, this is a difficult task. However, there are cases in which these absorption
-probabilities can be computed thanks to the integrability property of the system.
-For recent examples in the framework of single-species systems, see \cite{frassek2020eigenstates, frassek2022exact, frassek2020non, floreani2023non}.
+In general, this is a difficult task. However,  for the case of integrable systems they can be computed exactly in closed-form. 
+For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2022exact}.  
 Here we generalize the duality approach to the set-up of multispecies particle systems.

### 2023-11-28 main.tex
kk

@@
 
-{\color{red} I do not understand why we immediately start with XXX although the duality approach is much more general.}
+{\color{red} Missing the part about non integrable model and duality.}
+
 For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
@@
 particle per site, which is driven out-of-equilbrium by two reservoirs acting at the left and right boundaries. 
-Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz \cite{vanicat2017exact},
-which is in fact also simplified by the use of duality. Finally in Section~\ref{sec5} we discuss a few extensions 
+Here the computation of the absorption probabilities relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact},{\color{red}
+which is in fact also simplified by the use of duality. }Finally in Section~\ref{sec5} we discuss a few extensions 
 and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.

### 2023-11-29 main.tex
abstract and cup

@@
 For the case of one-dimensional chains with two reservoirs
-at the boundaries and with maximum one particle per site,
-we compute these absorption probabilities by relying
+at the boundaries and with maximum one particle per site the process is integrable. Based on the results of \cite{vanicat2017exact},
+we compute the absorption probabilities by relying
 on the underlying ${gl}(N)$ symmetry and the
@@
 For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2022exact}.  
-Here we generalize the duality approach to the set-up of multispecies particle systems.
+{\color{red}
+Here we generalize the duality approach to the set-up of multispecies particle systems.}
 
@@
 
-{\bf Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM), Prin-project {\color{blue} xxxx}, FAR-project {\color{blue} xxxx} UniMoRe.
-
-INFN Progetto Giovani
+{\bf Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM),  the INFN grant Gauge and String Theory (GAST),  the PRIN project CUP-E53D23002220006,  the FAR UNIMORE project CUP-E93C23002040005 and  the INdAM–GNFM project CUP-E53C22001930001.
+
+% Prin-project {\color{blue} xxxx}, FAR-project {\color{blue} xxxx} UniMoRe.
+% 
+% INFN Progetto Giovani
 

### 2023-11-30 main.tex
S2

@@
 
+% \usepackage[margin=2.5cm]{geometry}
+
+%%%%%  TODO NOTES ETC  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\usepackage[left=1.7cm,right=4.3cm,bottom=4cm]{geometry}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+\definecolor{todocolor}{HTML}{D7E1E5}
+\usepackage[textsize=tiny, 
+            backgroundcolor=todocolor, 
+            bordercolor=todocolor, 
+            linecolor=todocolor, 
+            textwidth=3.9cm]{todonotes}
+\newcommand{\todoWARN}[1]{\todo{\colorbox{yellow}{\parbox{3.4cm}{#1}}}}
+\newcommand{\todoERR}[1]{\todo{\colorbox{red}{\parbox{3.4cm}{#1}}}}
+\usepackage{comment}
+\usepackage{rotating}
+\usepackage[left]{showlabels}
+\renewcommand{\showlabelfont}{\tiny}
+\renewcommand{\showlabelsetlabel}[1]
+{\begin{turn}{65}\showlabelfont \llap{#1}\end{turn}}
+\newcommand{\wiptitle}[1]{
+    \par\noindent\hspace*{-0.5cm}\texttt{\scriptsize\color{gray} \lbrack #1\rbrack} \par\noindent\ignorespaces}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\usepackage[textsize=tiny]{todonotes}
@@
 \setcounter{tocdepth}{2}
-
-\usepackage[margin=2.5cm]{geometry}
 
@@
 future paper. 
+\todo{I prefer to remove this sentence}
 
@@
 (called `holes'), whose number at each site is fixed by the numbers of particles 
-of the remaining $N-1$ types. It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
-(those of types $\{1,\ldots,N-1\}$), we retrieve the 
-boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
+of the remaining $N-1$ types. 
+% It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
+% (those of types $\{1,\ldots,N-1\}$), we retrieve the 
+% boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
+In the case $N=2$, we retrieve the  boundary-driven version of the symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
+% \todo{I would prefer to say this is for N=2}
 The choice of type $N$ for the distinguished type is arbitrary and does not affect
-the results. In particular, we shall see in Section~\ref{sectionDuality} about duality, that
-the dual process eventually has only particles of type $N$ on the graph.
+the results. However, we shall see in Section~\ref{sectionDuality}, that
+the dual process breaks the symmetry.
+In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
 Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.  
+\todo{Exchange hole with void? Also can the remark be just text?}
 \end{remark}
@@
 \end{equation}
-with marginals $\mu_{\text{rev}}^{x}$ given by 
+with marginals $\mu_{\text{rev}}^{x}$ given by  the multinomial distribution
 \begin{equation}
@@
 If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost (but see Remark~\ref{rem-rev} below): 
-each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
+each reservoir at site $x$ {\color{red}wants to fix}\todo{?} its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
 \begin{equation}
@@
 		\end{remark}
+		\todo{?}
 \subsection{Lie algebraic description of the process}
 
-In this paper we will often use the fact that the Markov generator of the multispecies stirring process can be described in terms a Lie algebra of rank $N$.
+In this paper we will often use the fact that the Markov generator of the multispecies stirring process can be described in terms a Lie algebra ${gl}(N)$.
 In this section we provide details about this.
@@
 \begin{equation}
-  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
+  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{such that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
 \end{equation}
@@
 \end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vectors obtained by transposing $|m\rangle=|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronecker delta.
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle=|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronecker delta.
 
@@
 \end{equation}  
-The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
+The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield highest Dynkin weight \eqref{eq:dynkin}. \\
 %{\color{red} Is this remark relevant for us?}
@@
 %{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
-The process with generator \eqref{Generator} can be described in terms of ${gl}(N)$ Lie algebra generators.
+As mentioned above, the process with generator \eqref{Generator} can be described in terms of ${gl}(N)$ Lie algebra generators.
 The state space \eqref{stateSpace} is given by the $|V|$-fold tensor product of the vector space with basis elements $|n^x\rangle$ at a given site.
@@
 %where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
-with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$. Sometimes it will bw convenient to write $|n^{x}\rangle$ to denote, for a fixed $x\in V$, the vector $|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
+with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$.
+For a fixed $x\in V$ we write $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
 The following orthogonality relation is a consequence of the single site relation \eqref{ortho}
@@
 \end{equation}
-where the edge Hamiltonian that describes the interaction between two connected sites is
+where the edge Hamiltonian $\mathcal{H}_{x,y}$ that describes the interaction between two connected sites is
 \begin{equation}\label{edgeHamiltonian}
@@
  \end{equation}
-  and where the site Hamiltonian is
+  and where the site Hamiltonian $H_{x}$  is
  \begin{equation}\label{siteHamiltonian}
@@
 \end{equation}
-Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
-acting trivially as the identity on the other sites). 
-Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
+Here $E_{ab}^{x}$ denotes the generator $E_{ab}$ in \eqref{actionE} acting non-trivially on site $x$ (and as the identity on the other sites). 
+The Hamiltonian in \eqref{OriginalHamiltonian} is stochastic and is linked to the Markov generator  by
 \begin{equation}\label{Hamiltonian-Generator}
-H=\mathcal{L}^{T}\dt
-\end{equation}
-The action of the generator can also be expressed as 
+H=\mathcal{L}^{T} 
+\end{equation}
+where $T$ denotes transposition, see e.g.  \cite{belitsky2015self}.
+The action of the generator on functions $f$ can then  be expressed as 
 \begin{equation}
@@
 \end{equation}
-that acts diagonally as $C|\bm{n}\rangle=\twoj(\twoj+N)|\bm{n}\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  
+that acts diagonally as $C|{n}\rangle=\twoj(\twoj+N)|{n}\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  
 More precisely,  considering the standard coproduct 
@@
 \begin{split}
-\Delta:{gl}(N)&\to {gl}(N)\otimes {gl}(N)\\
-E_{ab}&\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
-\end{split}
+\Delta:{gl}(N)\to {gl}(N)\otimes {gl}(N)
+\end{split}
+\end{equation}
+with
+\begin{equation}
+E_{ab}\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}\co
 \end{equation} 

### 2023-11-30 main.tex
kk

@@
 \subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
-In this section we specialize the multispecies stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
-These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium.
+In this section we specialize the multispecies stirring process to the geometry of the one-dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
+The reservoirs, exchanging particle with the external environment, put the chain out of equilibrium.
+This process was studied previously in \cite{vanicat2017exact}.
+
 The Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are

### 2023-12-01 main.tex
kk

@@
 \noindent
-We study the boundary-driven version of the stirring process with $N-1$ species
-on a generic graph $G=(V,\mathcal{E})$ with reservoirs. 
+We study the stirring process with $N-1$ species
+on a generic graph $G=(V,\mathcal{E})$ introduced with reservoirs.
 The multispecies stirring process generalizes the symmetric exclusion process, 
@@
 includes additional extra-sites $\widetilde{V}\setminus V$ where
-dual particles gets absorbed in the long-time limit.  
+dual particles get absorbed in the long-time limit.
 We thus obtain a characterization of the non-equilibrium
 steady state of the boundary-driven system in terms of the absorption
-probabilities of dual particles.
-For the case of one-dimensional chains with two reservoirs
-at the boundaries and with maximum one particle per site the process is integrable. Based on the results of \cite{vanicat2017exact},
+probabilities of dual particles.  The process is integrable
+for the case of the one-dimensional chain with two reservoirs
+at the boundaries and with maximally one particle per site. Based on the results of \cite{vanicat2017exact},
 we compute the absorption probabilities by relying
@@
 In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
-{\color{red} The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi, zhou2021orthogonal, franceschini2022orthogonal,floreani2023non}.}
-{\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
-
-{\color{red} Missing the part about non integrable model and duality.}
-
-For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
-The results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable quantum spin chain, i.e.
-the XXX Heisenberg Hamiltonian with ${su}(2)$ spins of value $s=1/2$.
-In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context \cite{vanicat2017exact}, i.e.
-the {\em  multispecies stirring process with open boundaries}.
-See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.
-The bulk part of the model with $N$ species is associated with the integrable ${gl}(N)$
-Heisenberg XXX Hamiltonian with integrable non-diagonal open boundaries.
+The aim of this paper is to develop the theory of stochastic duality and  study the stationary measure of certain symmetric boundary-driven {\em multispecies} particle systems with exclusion.
 
 Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of {\em duality} \cite{schutzSandow}.
-This approach, starting from the pioneering work of Kipnis, Marchiorio and Presutti \cite{KMP},
-has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up \cite{giardina2009duality,carinci2013duality,frassek2020duality,carinci2023open}. 
+Starting from the pioneering work of Kipnis, Marchiorio and Presutti \cite{KMP}, this approach
+has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up \cite{giardina2009duality,carinci2013duality}.
 The boundary-driven process is mapped to a dual process with absorbing extra sites and the problem of describing the stationary state of the original system
@@
 In general, this is a difficult task. However,  for the case of integrable systems they can be computed exactly in closed-form.
-For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2022exact}.  
-{\color{red}
-Here we generalize the duality approach to the set-up of multispecies particle systems.}
-
-The remainder of this paper is organized as follows. In Section~\ref{sec1} we define the open multispecies stirring
-process and provide its Lie algebraic description. In Section~\ref{sectionDuality} we prove duality (Theorem~\ref{thm-duality}) 
-and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
-steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
-system has a general spatial structure described by a general graph. In Section~\ref{sectionIntegrabiliy} we then obtain a closed formula 
+
+For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
+One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain [SCHUTZ,RAGOUCY].
+
+The model studied in this paper is the multispecies analog of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
+{\color{red}Explain the model here.... $N$-species }
+
+We refer to the model as the {\em  multispecies stirring process with open boundaries}.
+%
+
+The  paper is organized as follows.
+In Section~\ref{sec1} we define the open multispecies stirring
+process and provide its Lie algebraic description in terms of $gl(N)$ generators. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
+and show that the problem of characterizing the non-equilibrium
+steady state can be reduced to the computation of the absorption probabilities similar to the single species case [SPOHN?]. The duality is proved for a
+system whose spatial structure is described by a general graph. In Section~\ref{sectionIntegrabiliy} we then obtain a closed formula
 for the stationary correlations (Theorem~\ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
@@
 \todo{I prefer to remove this sentence}
+
+\cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
+
+ See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.
+
+For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
+{\color{red}
+Here we generalize the duality approach to the set-up of multispecies particle systems.}
+
+{\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
+
+{\color{red} Missing the part about non integrable model and duality.}
 
@@
 \label{rhox}
-\rho_{a}^x=\frac{\alpha_{a}}{|\alpha^x|}
-\end{equation}
-and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}$. 
+\rho_{a}^x=\frac{\alpha_{a}^x}{|\alpha^x|}
+\end{equation}
+and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$.
 Currents will arise when at least two reservoirs have different densities. 
@@
 \begin{equation}\label{Tau-Notation}
-	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
-		\tau_{1}\\
-		\vdots\\
-		\tau_{L}
-	\end{pmatrix}
+	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle
 \end{equation} 
@@
 \label{proof-th-duality}
-To prove duality between $(\bm{n}(t))_{t\geq 0}$ and $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.
+To prove duality between the process $(\bm{n}(t))_{t\geq 0}$ and the process  $(\bm{\xi}(t))_{t\geq 0}$ we  show that \eqref{DualityRelation} is fulfilled.
 To show this, we will use the Hamiltonians and their Lie algebraic description.
@@
 \end{align}
+\todo{something wrong...}
 where we used \eqref{transpositionPropertyR}. \\

### 2023-12-01 main.tex
kk

@@
 is reduced to the problem of computing the absorption probabilities of the dual particles.
-In general, this is a difficult task. However,  for the case of integrable systems they can be computed exactly in closed-form.
+{\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
+% However,  for the case of integrable systems they can be computed exactly in closed-form.
+
+{\color{red} Explain here that we consider the chain with only two reservoirs at the end of the chain}
 
@@
 The model studied in this paper is the multispecies analog of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
-{\color{red}Explain the model here.... $N$-species }
+{\color{red}Explain the model here.... $N$-species, say that it becomes integrable for the line }
 
@@
 In Section~\ref{sec1} we define the open multispecies stirring
-process and provide its Lie algebraic description in terms of $gl(N)$ generators. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
+process on a general graph and provide its Lie algebraic description in terms of $gl(N)$ generators. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
 and show that the problem of characterizing the non-equilibrium
-steady state can be reduced to the computation of the absorption probabilities similar to the single species case [SPOHN?]. The duality is proved for a
-system whose spatial structure is described by a general graph. In Section~\ref{sectionIntegrabiliy} we then obtain a closed formula
-for the stationary correlations (Theorem~\ref{thm-correlations}) for the case of a one-dimensional chain with at most one 
-particle per site, which is driven out-of-equilbrium by two reservoirs acting at the left and right boundaries. 
-Here the computation of the absorption probabilities relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact},{\color{red}
-which is in fact also simplified by the use of duality. }Finally in Section~\ref{sec5} we discuss a few extensions 
-and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
-
-In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
-model with non-compact Lie algebras, both integrable and non-integrable, which will be presented in a 
-future paper. 
-\todo{I prefer to remove this sentence}
-
-\cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
-
- See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.
-
-For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
-{\color{red}
-Here we generalize the duality approach to the set-up of multispecies particle systems.}
-
-{\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
-
-{\color{red} Missing the part about non integrable model and duality.}
+steady state can be reduced to the computation of the absorption probabilities similar to the singlespecies case on the line [SPOHN?] and for a general graph \cite{ frassek2020duality}. 
+% The duality is proved for a system whose spatial structure is described by a general graph.
+In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
+particle per site, which is driven out-of-equilbrium by two reservoirs on the left and right boundaries.
+In this case we obtain a closed-form expression for the stationary correlations (Theorem~\ref{thm-correlations}).
+Here the computation
+% of the absorption probabilities 
+relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(n)$ invariance of the process in the bulk.
+Finally in Section~\ref{sec5} we discuss a few extensions
+and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions. {\color{red} mention the results you have in appendix}.
+
+% In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
+% model with non-compact Lie algebras, both integrable and non-integrable, which will be presented in a 
+% future paper. 
+% \todo{I prefer to remove this sentence}
+
+% \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
+
+%  See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.
+
+% For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
+% {\color{red}
+% Here we generalize the duality approach to the set-up of multispecies particle systems.}
+
+% {\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
+
+% {\color{red} Missing the part about non integrable model and duality.}
 

### 2023-12-02 main.tex
lk

@@
 Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
-\todo{Exchange hole with void? Also can the remark be just text?}
 \end{remark}
@@
 This can be proved  by checking that detailed balance is satisfied. 
-If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost (but see Remark~\ref{rem-rev} below): 
+If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost: 
 each reservoir at site $x$ {\color{red}wants to fix}\todo{?} its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
@@
 		\end{remark}
-		\todo{?}
+% 		\todo{?}
 \subsection{Lie algebraic description of the process}
@@
 \subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
-In this section we specialize the multispecies stirring process to the geometry of the one-dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$.
-The reservoirs, exchanging particle with the external environment, put the chain out of equilibrium.
-This process was studied previously in \cite{vanicat2017exact}.
-
+In this section we specialize the multispecies stirring process to the geometry of the one-dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs are attached to the boundary sites $1$ and $L$.
+The reservoirs, exchanging particles with the external environment, put the chain out of equilibrium.
 The  Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are
@@
 \end{equation}
-The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section~\ref{sectionIntegrabiliy}.
-We will denote the element of the representation of the ${gl}(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e.
-$(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
-The Hamiltonian now reads
+The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{ab})_{a,b\in\{1,\ldots,N\}}$.
+The Hamiltonian can then be written as
 \begin{equation}\label{hamiltonian}
@@
 \end{equation}
-with 
+with the permutation matrix
 \begin{equation}
@@
 \end{equation} 
- In this context it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by
+ In this context it will be useful to introduce the following notation for the occupation variables of the process. Each configuration is denoted by
 \begin{equation}\label{Tau-Notation}
@@
 Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
+
+We will consider it extensively in Section~\ref{sectionIntegrabiliy}.
 

### 2023-12-02 main.tex
l

@@
 The model studied in this paper is the multispecies analog of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
-{\color{red}Explain the model here.... $N$-species, say that it becomes integrable for the line }
+{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty. What is the graph? say that it becomes integrable for the line }
 
@@
 with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-Since the maximal occupancy at each site is $\nu=1$,  the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
+Since the maximal occupancy at each site is $\nu=1$,\todo{but is it at max 1?
+I do not understand what we call the stirring process....}  the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
 \begin{equation}\label{notation-change-relation}

### 2023-12-02 main.tex
ss
ll

@@
 The model studied in this paper is the multispecies analog of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
-{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty. What is the graph? say that it becomes integrable for the line }
+{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
 
@@
 \end{remark}
+\todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}
 
@@
 The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
-For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{ab})_{a,b\in\{1,\ldots,N\}}$.
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{ab})_{a,b\in\{1,\ldots,N\}}$ obeying $(e_{ab})_{cd}=\delta_{ac}\delta_{bd}$.
 The Hamiltonian can then be written as
@@
 \end{equation}
-Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the vertices of the edge $x,x+1$) of the two-site Hamiltonian
+Here $\mathcal{H}_{x,x+1}$  denotes  the two-site Hamiltonian 
 \begin{equation}\label{H-corsivo}
@@
 \begin{equation}
-	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
-\end{equation} 
+	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}\,,
+\end{equation} 
+acting non-trivially on the vertices of the edge $x,x+1$.
  In this context it will be useful to introduce the following notation for the occupation variables of the process. Each configuration is denoted by
@@
 \end{equation}
-The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
+The action of the Hamiltonian density $\mathcal{H}$ on the tensor product of the configuration of two sites follows immediately from \eqref{H-corsivo} and reads
 \begin{equation}
@@
 \end{equation}
-The boundary terms are given by 
+The boundary terms of the Hamiltonian \eqref{hamiltonian}  are given by 
 \begin{equation}
@@
 %\end{equation}
-Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).
-
-We will consider it extensively in Section~\ref{sectionIntegrabiliy}.
+Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable.
+This has been schown in \cite{vanicat2017exact} within  the Quantum Inverse Scattering Method.
+We will consider this process more extensively in Section~\ref{sectionIntegrabiliy}.
 
 \section{Duality}\label{sectionDuality}
-In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
+In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundaries
 can be studied by means of a dual process. After recalling the definition of duality between two
 Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
-The duality result is important since it yields several simplifications, the main one being that the
+The duality result yields several simplifications, \todo{which else?} the main one being that the
 dual process has absorbing sites.
-Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
+Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundaries
 is reduced to the study of the absorption probabilities of dual particles.
@@
 where the superscript $T$ denotes the matrix transposition.
-Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}^{\,T}$.
+Therefore, the duality relation \eqref{dualityIntertwines}  intertwines between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}^{\,T}$.
 Working in terms of the Hamiltonian operators the duality relation reads
@@
 This means that to each site $x\in V$ we associate an ``extra-site'' via a bijection $u:V\to V$.
-We denote as $u(x)$ the extra-site asspciated to $x\in V$ .
+We denote as $u(x)$ the extra-site associated to $x\in V$ .
 The configuration space of the dual process is the enlarged state space
@@
 Note that on the extra-site we allow an unbounded number of particles. Thus
-dual particle will accumulate in these extra-sites in the course of time. 
+dual particles will accumulate in these extra-sites in the course of time. 
 We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
@@
 Then, the constant $\left(\frac{1}{N}\right)^{\nu}$ has been neglected, since it does not change the duality relation.
-This $R_{x}$ is called the ``cheap'' duality matrix and is associated to reversibility (see \cite{giardina2009duality}).
+This $R_{x}$   is associated to reversibility, see \cite{giardina2009duality}.
 \\
@@
 \\&
-\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
+\hspace{2.cm}\qquad\times |\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
 %\\&=
@@
 \\& 
-\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
+\hspace{2.cm}\qquad\times \frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
 \\&=
@@
 \end{equation}
+\todo{somehow this now has extra index for the space and everywhere else not.... please fix}
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
@@
 \begin{equation}\label{NESS-expectation-ABS}
-\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\left[\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right]\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\Big| \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 \begin{equation}\label{implicit-mass-function}
-	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}
-	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\right)\right]\,.
-\end{equation}
+	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}{\color{red}
+	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\right)\right]}\,.
+\end{equation}
+\todo{Explain this expectation...}
 \end{corollary}
@@
 \end{align}
+	\todo{To me this looks like it is zero. Can you explain the notation?}
 where in the last equality we exploited the fact that 
@@
 \end{align} 
+\todo{indices are strange. What happens here?}
 Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 

### 2023-12-02 main.tex
ll
kk

@@
 \end{equation}
-that acts diagonally as $C|{n}\rangle=\twoj(\twoj+N)|{n}\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  
+that acts diagonally as $C|{n}\rangle=\twoj(\twoj+N)|{n}\rangle$ on any state $|n\rangle$ and belogs to the center of ${gl}(N)$ (i.e. it commutes with all the algebra elements).  
 More precisely,  considering the standard coproduct 
@@
 \begin{equation}
-    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
-\end{equation}
+    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )_{x\in V}
+\end{equation}
+\todo{OK? but this has no index $x$?}
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
@@
 \begin{align}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
+	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
 	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
@@
 \begin{align}
-\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
-\end{align}
+\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
+\end{align}
+\todo{what happens to $q_N$?}
 where  we used the orthogonality relation \eqref{ortho}. 

### 2023-12-02 main.tex
''

@@
 is reduced to the problem of computing the absorption probabilities of the dual particles.
+{\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form.
+On the other hand, absorption probabilities are hard to to find since they fulfil multilinear algebraic equation with proper boundary conditions.
+The situation simplifies when the graph reduces to a chain with two reservoirs on the boundary sites.
+In this context, the integrable structure of the process can be combined with duality to compute non-equilibrium steady state.
+Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.}
 {\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
@@
 \begin{equation}
-    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )_{x\in V}
-\end{equation}
-\todo{OK? but this has no index $x$?}
+    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}
+\end{equation}
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
@@
 \begin{align}
-	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
+	 &\langle n^{x}_{1},\ldots,n_{N}^{x}|\left(d_{x}\otimes \dd\right)\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
 	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
@@
 \begin{align}
-\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
-\end{align}
-\todo{what happens to $q_N$?}
+\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
+\end{align}
 where  we used the orthogonality relation \eqref{ortho}. 
@@
 \end{equation}
-Taking the tensor product of both sides of \eqref{siteHadamardI} with 
-\begin{equation}
-\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|_{u(x)}
-\end{equation}
+Taking the tensor product of both sides of \eqref{siteHadamardI}% with 
+%\begin{equation}
+%\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}%\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|_{u(x)}
+%\end{equation}
 %{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
@@
     \begin{split}
-    	H_{x}^{T}d_{x}\otimes\langle\rho|_{u(x)}=
+    	&H_{x}^{T}d_{x}\otimes\left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right)\\=&
  d_{x}\,
-|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \langle\rho|_{u(x)}\dt
+|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right)
     \end{split}

### 2023-12-02 main.tex
''
kk
3.4.12
s
ll

@@
 Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics.
-In a boundary-driven system, the model is put in contact with reservoirs at its ``boundaries'' imposing different particle densities, and a current is generated through the system.
+In a boundary-driven system, the model is put in contact with reservoirs at its {\color{red}``boundaries'' } imposing different particle densities, and a current is generated through the system.
 In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
@@
 The boundary-driven process is mapped to a dual process with absorbing extra sites and the problem of describing the stationary state of the original system
-is reduced to the problem of computing the absorption probabilities of the dual particles.
+is simplified to the problem of computing the absorption probabilities of the dual particles. In general, however,  there is little hope to compute the absorption probabilities exactly.
+
 {\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form.
@@
 	=\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_x\}}\right)\right]\nonumber\\
-	=&\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}\right)\right)\right]
+	=&\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a\}}\right)\right)\right]
 	%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
@@
 \end{align}
-	\todo{To me this looks like it is zero. Can you explain the notation?}
+% {\color{blue}Is it not an identity? Take for example 3 sites: $\tau_{1}=\tau_{2}=1$ and $\tau_{3}=N$. Then we have that 
+% $$
+% \prod_{x=1}^{3}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=\mathbbm{1}_{\{Y_{1}=\tau_{1}\}}\mathbbm{1}_{\{Y_{2}=\tau_{2}\}}\mathbbm{1}_{\{Y_{3}=\tau_{3}\}}=\left(\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right)\left(\mathbbm{1}_{\{Y_{3}=N\}}\right)=\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{3}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}= N}^{3}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)
+% $$} 
+\todo{removed subindex $a_x$ here}
 where in the last equality we exploited the fact that 
-\begin{equation}			\mathbbm{1}_{\{Y_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}\dt
-\end{equation}
+\begin{equation}\label{prova}			\mathbbm{1}_{\{Y_{x}=N\}}=1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a\}}\dt
+\end{equation}
+% {\color{blue}
+% Here I mean 
+% \begin{equation}
+% 	\mathbbm{1}_{\{Y_{x}=a\}}=\begin{cases}
+% 		1\qquad \text{if}\qquad  Y_{x}=a\\
+% 		0\qquad \text{if}\qquad Y_{x}\neq a
+% 	\end{cases}
+% \end{equation}
+% Therefore, \begin{equation}
+% 	\mathbbm{1}_{\{Y_{x}=N\}}=\begin{cases}
+% 		1\qquad \text{if}\qquad  Y_{x}=N\\
+% 		0\qquad \text{if}\qquad Y_{x}\neq N
+% 	\end{cases}
+% \end{equation}
+% and 
+% \begin{equation}
+% 1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}=\begin{cases}
+% 	1\qquad \text{if}\qquad  Y_{x}=N\\
+% 	0\qquad \text{if}\qquad Y_{x}\neq N
+% \end{cases}
+% \end{equation}
+% therefore \eqref{prova} follows.
+% }
 The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ sites are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
@@
 \end{align} 
-\todo{indices are strange. What happens here?}
+\todo{indices are strange. Say what happens here}
 Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 

### 2023-12-03 main.tex
densities

@@
 {\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form.
-On the other hand, absorption probabilities are hard to to find since they fulfil multilinear algebraic equation with proper boundary conditions.
+On the other hand, absorption probabilities are hard to find since they fulfil multilinear algebraic equation with proper boundary conditions.
 The situation simplifies when the graph reduces to a chain with two reservoirs on the boundary sites.
@@
 
-\noindent
-\begin{remark}
-\label{hole}
+%\noindent
+%\begin{remark}
+%\label{hole}
 In the following we will often consider type $N$ as a distinguished type
@@
 Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
-\end{remark}
+%\end{remark}
 \todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}
+{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
+Second question: I think yes. The concept of boundary is general, not only for the chain}
 
@@
 This can be proved  by checking that detailed balance is satisfied. 
-If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost: 
-each reservoir at site $x$ {\color{red}wants to fix}\todo{?} its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with
+If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost: indeed, in this situation, each reservoir at site $x$ has  its own set of densities vector $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with components
 \begin{equation}
@@
 and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$.
-Currents will arise when at least two reservoirs have different densities. 
+{\color{blue} As a consequence, particles are injected and removed in the graph with different rates.
+When, for any $a\in \{1,\ldots,N\}$ there are at least two reservoirs at sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility.
+Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}
+\todo{?}
+%Currents will arise when at least two reservoirs have different densities. 
 \begin{remark}
 \label{rem-rev}
-		One can check that the following condition on the reservoir parameters implies reversibility:
+		{\color{blue}One can check that conditions \eqref{reversibilityCondition} are not the most general that implies reversibility. Indeed, by choosing the reservoir parameters as }
 		\begin{equation}
@@
 		\end{equation}
-		This is slightly more general than \eqref{reversibilityCondition}.
+		reversibility holds. 
+		%This is slightly more general than \eqref{reversibilityCondition}.
 		 In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites
@@
 \end{equation}
+{\color{blue}where the expectation is take with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}
 \todo{Explain this expectation...}
@@
  Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
-\begin{equation}\label{exactCorrelations}
+\begin{equation}%\label{exactCorrelations}
 	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}

### 2023-12-03 main.tex
l

--- 2023-12-02 main.tex
@@
 \end{equation}
-where $\Delta_{x,y}(C)$ denotes a copy of $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.
+where $\Delta_{x,y}(C)$ denotes  $\Delta(C)$ acting on  the sites of edge $(x,y)\in \mathcal{E}$ and acting trivially on the other sites of the graph.
 
@@
 on a generic vector $\langle q|$ with $q\in \mathbb{N}_{0}$, so that in \eqref{siteDualHamiltonian} 
-$(\mathbf{a}^{+})_{a}^{u(x)}$ denotes a copy of $\mathbf{a}^{+}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
+$(\mathbf{a}^{+})_{a}^{u(x)}$ denotes  $\mathbf{a}^{+}$ acting on the extra-site $u(x)$ and on the species $a\in\{1,\ldots,N-1\}$. \\
 
@@
 \end{equation}
-where $\Delta_{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. As a consequence, this operator $S_{x,y}$ satisfies
+where $\Delta_{x,y}(E)$ denotes the coproduct acting on sites $x$ and $y$. As a consequence, this operator $S_{x,y}$ satisfies
 \begin{equation}\label{symmetryH}
@@
 \end{equation}
-that is a copy of $\mathcal{S}_{1}$ (see \eqref{S1Gen}) acting at site $x$. 
+to denote $\mathcal{S}_{1}$ (see \eqref{S1Gen}) when acting at site $x$. 
 Observe that $\mathcal{S}_{1}^{x}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}).
@@
  \end{equation}
-which is a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
+whichdenotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
 \begin{equation}\label{S2-Whole}
@@
 	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
-These probability are hard to find when $\nu>1$.
+These probabilities are hard to find when $\nu>1$.
 We give

### 2023-12-03 main.tex
''

--- 2023-12-03 main.tex
@@
 For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
-One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain [SCHUTZ,RAGOUCY].
+One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain \cite{schutzManyBody,SSEPReviewRagoucy}.
 
@@
 Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
-The duality result yields several simplifications, \todo{which else?} the main one being that the
-dual process has absorbing sites.
+The duality result yields {\color{blue} to a dual process that} %several simplifications,  the main one being that the
+%dual process
+ has absorbing sites\todo{which else?}.
 Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundaries
@@
 and 
-\begin{equation}
+\begin{equation}\label{bosonic_2}
 	\langle q|\mathbf{a}^{+}=\langle q-1|\qquad \langle q|\mathbf{a}=(q+1) \langle q+1|
@@
 \end{align}
-\todo{something wrong...}
+\todo{something wrong...} {\color{blue} [I have added the vector at site $u(x)$]}
 where we used \eqref{transpositionPropertyR}. \\
@@
 \end{align}
-\todo{what happens to $q_N$?}
+\todo{what happens to $q_N$?} {\color{blue} we used the orthogonality between $\langle q_{1}^{u(x)} ,\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,q_{N}^{u(x)}\rangle=1$ on the extra-site $u(x)$}
 where  we used the orthogonality relation \eqref{ortho}. 
@@
 \end{equation}
-\todo{somehow this now has extra index for the space and everywhere else not.... please fix}
+\todo{somehow this now has extra index for the space and everywhere else not....
+please fix} {\color{blue} We have defined the bosonic operator with the extra-site, see under equation \eqref{bosonic_2}}
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
@@
 \end{equation}
-{\color{blue}where the expectation is take with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}
+{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}
 \todo{Explain this expectation...}
@@
 Therefore, we may write
-\begin{align}
+\begin{align}\label{sum}
 &\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=a_{x}\}}\right)\right)\nonumber\\
@@
 \todo{indices are strange. Say what happens here}
-Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 
+Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.{\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
 \begin{flushright}

### 2023-12-04 main.tex
^-^

@@
 {\color{blue} As a consequence, particles are injected and removed in the graph with different rates.
-When, for any $a\in \{1,\ldots,N\}$ there are at least two reservoirs at sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility.
+When, for any $a\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility.
 Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}
@@
 \begin{equation}
-    \bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )_{x\in V}
+    \bm{\xi}=\left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )\right)_{x\in V}
 \end{equation}
@@
 and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 
-the extra-site $u(x)$ connected to $x\in V$. We state the following duality result.
+the extra-site $u(x)$ connected to $x\in V$.
+{\color{blue} We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, since it is defined on $\mathbb{N}_{0}^{N}$}.
+We state the following duality result.
 \begin{theorem}[Absorbing duality]\label{thm-duality}
@@
 \end{equation}
+{\color{blue} Here $|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle$ is the vector associated to the configuration of in the extra site $u(x)$.
+For all $q_{1},\ldots,q_{N}\in \mathbb{N}_{0}$, we assume that it satisfy an orthogonality relation
+\begin{equation}\label{ortho-extraSite}
+	\langle q_{1},\ldots,q_{N}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a}^{u(x)},q_{a}}
+\end{equation} }
 The Hamiltonian of the dual process reads
@@
 \end{align}
-\todo{what happens to $q_N$?} {\color{blue} we used the orthogonality between $\langle q_{1}^{u(x)} ,\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,q_{N}^{u(x)}\rangle=1$ on the extra-site $u(x)$}
-where  we used the orthogonality relation \eqref{ortho}. 
+\todo{what happens to $q_N$?} {\color{blue} 
+where we used the orthogonality relation \eqref{ortho-extraSite}}. 
 On the other hand, on the site $x$, we have 
@@
 \end{equation}
-{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}
+{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, then it is given in \eqref{exactCorrelations}.}
 \todo{Explain this expectation...}
@@
  \paragraph{Proof of formula \eqref{exactCorrelations}}
- We aim to compute the correlations between the sites $\mathbf{x}=\left(x_{1},\ldots,x_{m}\right)$ occupied by the species $\mathbf{a}=\left(a_{1},\ldots,a_{m}\right)$, such that $a_{1},\ldots,a_{m}\in \{2,\ldots,N\}$ i.e.
-\begin{equation}\label{Prob-m}
-	\begin{split}
-		\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{\text{stat}}&
-		=\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)
-	\end{split}
-\end{equation}
-where we denote $\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This corresponds to the steady state probability of a chain of length $m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$.Therefore, using again the notation \eqref{notation} and calling $\tau_{i}=a_{i}$, we have
+ We aim to compute the correlations between the sites% $\mathbf{x}=\left(x_{1},\ldots,x_{m}\right)$ occupied by the species $\mathbf{a}=\left(a_{1},\ldots,a_{m}\right)$, such that $a_{1},\ldots,a_{m}\in \{2,\ldots,N\}$ i.e.
+\begin{equation}%\label{Prob-m}
+	%\begin{split}
+	%	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{\text{stat}}&
+	%	=\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)
+%	\end{split}
+\end{equation}
+where we denote %$\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
+This corresponds to the steady state probability of a chain of length %$m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$.Therefore, using again the notation \eqref{notation} and calling %$\tau_{i}=a_{i}$, we have
 \begin{equation}

### 2023-12-04 main.tex
''

@@
  \newpage
-
 \section{Introduction} 
@@
 
-The model studied in this paper is the multispecies analog of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
+The model studied in this paper is the multispecies analogue of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
+{\color{blue}This particle system is defined on a generic connected and undirected graph.
+At each site $\nu\in \mathbb{N}$ particles of $N$ types (species) are hosted.
+There is an exclusion constraint that makes the occupancy of each site dependent on $N-1$ species only.
+Two sites do interact when there is an edge between them and this interaction consists in an swap of two different types of particles between these sites.
+Furthermore, reservoirs are attached at each site of the graph, making the system interact with external environments with fixed average particle densities.
+When the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and when $\nu=1$, the process becomes integrable (see \cite{vanicat2017exact}).}
 {\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
@@
 
-The  paper is organized as follows.
+%The  paper is organized as follows.
+\subsection*{Organization of the paper}
 In Section~\ref{sec1} we define the open multispecies stirring
@@
 Finally in Section~\ref{sec5} we discuss a few extensions
-and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions. {\color{red} mention the results you have in appendix}.
+and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
+{\color{blue} In particular, a thermalized boundary-driven version of the multispecies stirring process is introduced, showing that it has an absorbing duality.
+Moreover, a further interaction mechanism of reaction type is added in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction}).
+Absorbing duality is proved.
+The duality function for the termalized and the reaction diffusion process turns out to be the same of the multispecies stirring process.} {\color{red} mention the results you have in appendix}.
 

### 2023-12-04 main.tex
Comments Removed

@@
 
-\begin{comment}
-We introduce the Hamiltonian operator
-
-\begin{equation}\label{OriginalHamiltonian}
-	\begin{split}
-		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
-	\end{split}
-\end{equation}
-where the edge Hamiltonian is
-\begin{equation}\label{edgeHamiltonian}
-\mathcal{H}_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
- \end{equation}
- and where the site Hamiltonian is
- \begin{equation}\label{siteHamiltonian}
-H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(E_{al}^{x}-E_{ll}^{x}\right)
-\end{equation}
-Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$.
-
-We can write this Hamiltonian in function of the coproduct of the second Casimir
-\begin{equation}
-    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
-\end{equation}
-It reads
-\begin{equation}
-	\mathcal{H}_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
-\end{equation}
-Here we introduced the standard coproduct
-\begin{equation}
-\begin{split}
-\Delta:{gl}(N)&\to {gl}(N)\otimes {gl}(N)\\
-E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
-\end{split}
-\end{equation} acting on sites $x,y$ and used that $C_{2}|n\rangle=\twoj(\twoj+N)|n\rangle$. 
-\end{comment}
-
 \subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
@@
 \begin{equation}\label{dualStateSpace}
-    \widetilde{\Omega}= \bigotimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigotimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
+    \widetilde{\Omega}= \bigotimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigotimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})\dt
 \end{equation}
@@
 \begin{equation}
-    \bm{\xi}=\left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)} )\right)_{x\in V}
+    \bm{\xi}=\left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)} )\right)_{x\in V}
 \end{equation}
@@
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N\}$ at 
+and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
 the extra-site $u(x)$ connected to $x\in V$.
-{\color{blue} We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, since it is defined on $\mathbb{N}_{0}^{N}$}.
+{\color{blue} We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, i.e.
+an unbounded number of particles can be hosted at extra-site $u(x)$.
+Therefore, the occupation variable of species $N$ (the one dependent on the species $1,\ldots,N-1$) is not present}.
 We state the following duality result.
@@
 \end{theorem}
-\begin{comment}
-We define the duality function of the open multispecies stirring process as
-\begin{equation}\label{dualityElements}
-	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)
-\end{equation}
-where we recall the notation (see \eqref{rhox}) for the \textit{density} of the species $a\in \{1,\ldots,N-1\}$ imposed by the reservoir at site $x\in V$:
-\begin{equation}
-\rho_{a}^{x}=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}\dt
-\end{equation}
-The dual process is defined by its Markov generator, which reads
- \begin{equation}\label{DualGenerator}
-    \widetilde{\mathcal{L}}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}
-\end{equation}
-where 
-$\mathcal{L}_{x,y}$ is defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
-\begin{equation}\label{siteDualGenerator}
-    \widetilde{\mathcal{L}}_{x}f(\bm{\xi})=|\alpha^{x}|\sum_{a=1}^{N-1}\xi_{a}^{x}\left(f(\bm{\xi}-\bm{\delta}_{a}^{x}+\bm{\delta}_{N}^{x}+\bm{\delta}_{a}^{u(x)})-f(\bm{\xi})\right)\dt
-\end{equation}
-\newline
-\end{comment}
 The dual dynamics is described as follows.
@@
 \begin{equation}
-    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\dt
-\end{equation}
-{\color{blue} Here $|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle$ is the vector associated to the configuration of in the extra site $u(x)$.
-For all $q_{1},\ldots,q_{N}\in \mathbb{N}_{0}$, we assume that it satisfy an orthogonality relation
+    |\bm{\xi}\rangle=\bigotimes_{x\in V}\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes |\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle\right)\dt
+\end{equation}
+{\color{blue} Here $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ is the vector associated to the configuration of in the extra site $u(x)$.
+For all $q_{1},\ldots,q_{N-1}\in \mathbb{N}_{0}$, we assume that it satisfy an orthogonality relation
 \begin{equation}\label{ortho-extraSite}
-	\langle q_{1},\ldots,q_{N}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a}^{u(x)},q_{a}}
+	\langle q_{1},\ldots,q_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}
 \end{equation} }
@@
 \begin{equation}\label{dualityMatrix2}
-\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
+\dd=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\dt
 \end{equation}
@@
 that follows immediately from the definition of $E_{ab}$. 
-\begin{comment}
-
-\begin{align*}
-R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
-	\\&
-	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
-	\\&
-	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
- \\=&\sum_{r^{x}\in \Omega_{x}}
-	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
-	\\=&
-	\left(E_{ba}^{x}\right)^{T}
-\end{align*}
-where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
-\end{comment}
 \paragraph{Elements of the duality matrix.}
@@
 \begin{align}
-	 &\langle n^{x}_{1},\ldots,n_{N}^{x}|\left(d_{x}\otimes \dd\right)\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle\right)\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
-	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
+	 &\langle n^{x}_{1},\ldots,n_{N}^{x}|\left(d_{x}\otimes \dd\right)\left(|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\otimes|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle\right)\nonumber\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\nonumber
+	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle
 \end{align}
@@
 \begin{align}
-\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
+\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\right)\langle q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
 \end{align}
@@
 
-\begin{comment}
-As already pointed out, $\mathcal{H}_{x,y}$ is a linear function of $\Delta(C_{2})$.
-This implies that symmetries of  $\Delta(C_{2})$ are also symmetries of  $\mathcal{H}_{x,y}$.
-Moreover, the coproduct is a Lie algebra homomorphism, i.e.
-$\forall A,B\in {gl}(N)$
-\begin{equation}\label{symmetryCoproduct}
-    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
-\end{equation}
-This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of ${gl}(N)$, and therefore it commutes with all the element of this algebra. Consider
-\begin{equation}\label{equationE}
-    E=\sum_{a=2}^{N}E_{a1}
-\end{equation}
-To obtain a product structure of the elements of the duality matrix, we introduce
-\begin{equation}
-    S=\exp{(\Delta(E))}
-\end{equation}
-Finally, for fixed $(x,y)\in \mathcal{E}$, we define
-\begin{equation}
-    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
-\end{equation}
-where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. This operator $S^{x,y}$ satisfies
-\begin{equation}\label{symmetryH}
-    \left[S_{x,y},\mathcal{H}_{x,y}\right]=0
-\end{equation}
-i.e. $S_{x,y}$ is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write
-\end{comment}
 \begin{equation}
@@
  \end{align}
-\begin{comment}
-\begin{enumerate}
-    \item for $A=E_{b N}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
-    \begin{equation}\label{HT_El1}
-        \exp{(-E)}E_{b N}\exp{(E)}=E_{b N}
-    \end{equation}
-    because $E_{b N}$ commutes with $E$
-    \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
-    \begin{equation}\label{HT_Ell}
-        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b N}
-    \end{equation}
-Indeed, using \eqref{eq:comgl} we have 
-    \begin{equation}
-       \left[E, E_{bb}\right]=\sum_{a=1}^{N-1}\left(E_{ab}\delta_{b N}-E_{b N}\delta_{ab}\right)=-E_{bN}
-    \end{equation}
-    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
-    \item for $A=E_{Nb}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
-    \begin{equation}\label{HT-E1l}
-        \exp{(-E)}E_{N a}\exp{(E)}=E_{Na}+E_{NN}-\sum_{c=1}^{N-1}\left(E_{cN}+E_{ca}\right)
-    \end{equation}
-  %\com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}
-
-    Indeed, using \eqref{eq:comgl} we have 
-    \begin{equation}
-[E,E_{Na}]=\sum_{c=1}^{N-1}\left(E_{ca}\delta_{NN}-E_{NN}\delta_{ca}\right)= (\sum_{c=1}^{N-1}E_{ca} ) -E_{NN};
-\end{equation}
-and 
-\begin{equation}
-\begin{split}
-\left[E,[E,E_{Na}]\right]&=\sum_{d=1}^{N-1}\sum_{c=1}^{N-1}\left[E_{dN},E_{ca}\right]-\sum_{d=1}^{N-1}\left[E_{dN},E_{NN}\right]
-\\&=
-\sum_{d,c=1}^{N-1}\left(E_{da}\delta_{cN}-E_{cN}\delta_{da}\right)-\sum_{d=1}^{N-1}\left(E_{dN}\delta_{NN}-E_{NN}\delta_{dN}\right)
-\\=&
--2\sum_{c=1}^{N-1}E_{cN};
-\end{split}
-\end{equation}
-therefore we have that 
-\begin{equation}
-	content...
-\end{equation}
-Inserting the above commutators in \eqref{HadamardFormula}, we obtain \eqref{HT-E1l}.
-\item for $A=E_{ba}$ with $a,b \in \{1,\ldots,N-1\}$ we obtain 
-\begin{equation}\label{HT-Ekl}
-    \exp{(-E)}E_{a b}\exp{(E)}=E_{ba}+E_{bN}
-\end{equation}
-   Indeed, using \eqref{eq:comgl} we have 
-\begin{equation}
-[E,E_{ba}]=\sum_{c=1}^{N-1}\left(E_{ca}\delta_{b1}-E_{bN}\delta_{c a}\right)=-E_{bN};
-\end{equation}
-Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-Ekl}.
-\item for $A=E_{NN}$ we obtain 
-\begin{equation}\label{HT-E11}
-    \exp{(-E)}E_{NN}\exp{(E)}=E_{NN}-\sum_{a=1}^{N-1}E_{aN}
-\end{equation}
-  Indeed, using \eqref{eq:comgl} we have
-
-\begin{align*}
-[E,E_{NN}]=\sum_{c=1}^{N-1}\left(E_{cN}\delta_{NN}-E_{NN}\delta_{cN}\right)=\sum_{c=1}^{N-1}E_{cN};
-\end{align*}
-  Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT-E11}.
-\end{enumerate}
-\end{comment}
+
 Using \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
@@
 $\sum_{a,b=1}^{N}E_{ab}$ is central for the algebra we have
-\begin{comment}
-then, in the right hand side
-\begin{equation}\label{intermediateTransposeSite}
-H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\exp{(-E^{x})}\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}
-\end{equation}
-\end{comment}
-%where $E^{x}$ is a copy of $E$ acting on site $x\in V$ and $E_{ab}^{x}$ with $a,b\in \{1,\ldots,N\}$ are copies of $E_{ab}$ acting at site $x\in V$.
-% Using 
- \begin{comment}
- \eqref{HT_El1}, \eqref{HT_Ell},\eqref{HT-E1l}, \eqref{HT-Ekl}, \eqref{HT-E11} we have that 
-\begin{align}
-    &\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}\nonumber
-    \\&=\nonumber
-    \sum_{a=2}^{N}\alpha_{a}^{x}\left(E_{Na}^{x}+E_{NN}^{x}-\sum_{c=1}^{N-1}(E_{cN}^{x})-\sum_{c=1}^{N-1}(E_{ca}^{x})-E_{NN}^{x}+
-    \sum_{c=2}^{N}(E_{cN}^{x})\right)
-    \\&+\nonumber
-    \alpha_{N}^{x}\sum_{b=1}^{N-1}\left(E_{bN}^{x}-E_{bb}^{x}-E_{bN}^{x}\right)+\sum_{a=1}^{N-1}\sum_{b=1}^{N-1}\alpha_{a}^{x}\left(E_{ba}^{x}+E_{bN}^{x}-E_{bb}^{x}-E_{bN}^{x}\right)
-    \\&=\nonumber
-    \sum_{a=1}^{N-1}\alpha_{a}^{x}E_{Na}^{x}-|\alpha^{x}|\sum_{b=1}^{N-1}E_{bb}^{x}=
-    \sum_{a=1}^{N-1}\left(\alpha_{a}^{x}E_{Na}^{x}-|\alpha^{x}|E_{aa}^{x}\right)
-    \\&=\nonumber
-    |\alpha^{x}|\sum_{a=1}^{N-1}\left(\frac{\alpha_{a}^{x}}{|\alpha^{x}|}E_{Na}^{x}-E_{aa}^{x}\right)
-    \\&=
-    |\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)
- \end{align}
-in short
-\end{comment}
+
 \begin{equation}\label{HadTransfBoundary}
@@
 %\begin{equation}
-%\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}%\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|_{u(x)}
+%\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}%\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|_{u(x)}
 %\end{equation}
-%{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
+%{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
 we obtain 
@@
     \begin{split}
-    	&H_{x}^{T}d_{x}\otimes\left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right)\\=&
+    	&H_{x}^{T}d_{x}\otimes\left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right)\\=&
  d_{x}\,
-|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right)
+|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right)
     \end{split}
@@
 \begin{equation}\label{bosonicKX}
-    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})^{u(x)}_{a}=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|\dt
+    \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})^{u(x)}_{a}=  \langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\dt
 \end{equation}
@@
     \begin{split}
-&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\rho_{a}^{x}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+&\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\rho_{a}^{x}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|
 \\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}+1}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)}+1,\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
 \\=&
-%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&
-\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
+%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&
+\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
     \end{split}
@@
 	\begin{split}
-&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
-%=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\
-=\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
+&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
+%=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^-1{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\
+=\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
 \end{split}
@@
 %\begin{equation}
-%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt
+%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt
 %\end{equation}
@@
 %\begin{equation}
-%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|($\mathbf{a}$^{+})_{a}^{u(x)}=0
+%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N-1}^{u(x)}|($\mathbf{a}$^{+})_{a}^{u(x)}=0
 %\end{equation}
@@
 H_{x}^{T}d_{x}\otimes \dd&=
-     H_{x}^{T}d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|
+     H_{x}^{T}d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|
 \\&=
-\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
+\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
 %\\&=
-%\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}|\right\}\widetilde{H}_{x}
+%\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right\}\widetilde{H}_{x}
 \\&=
@@
 \end{theorem}
-\begin{comment}
- Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
-\begin{equation}%\label{exactCorrelations}
-	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
-\end{equation}
-\end{comment}
-\begin{comment}
-where 
-\begin{equation}\label{powerCoeffSpecies}
-	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-and 
-\begin{equation}\label{powerCoeffNOspec}
-	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}
-\end{equation}
-\end{comment}
-%{\color{blue}
-%	\begin{remark}
-%		The non-equilibrium steady state correlations can also be written as 
-%			\begin{equation}\label{exactCorrelation_1}
-%			\begin{split}
-%				\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\frac{1}{(L+1)!}\sum_{c_{x_{1}},\ldots,c_{x_{m}}=0}^{1}\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{1-c_{x_{k}}}\beta_{a_{k}}^{c_{x_{k}}}\left(2+L-x_{k}-\sum_{j=k}^{m}(1-c_{x_{j}})\right)\\&\prod_{x=1\,:\,x\notin \{x_{1},\ldots,x_{m}\}}^{L}\left(2+L-x-\sum_{k=1}^{m}\mathbbm{1}_{\{x<y_{k}\}}(1-c_{x_{k}})\right)
-%			\end{split}
-%		\end{equation}
-%\end{remark}
-%}
-\begin{comment}
-\paragraph{Absorption probabilities}
-Knowing the non-equilibrium steady state correlations, we can read-off the absorption probabilities defined in \eqref{absProbabilitiesIntegrable}. They are given by
-\begin{equation}\label{abs-probabilities}
-	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
-\end{equation}
-. \\ \\
-\textbf{Proof of \eqref{abs-probabilities}}: 
-From \eqref{exactCorrelations} we have
-
-\begin{flushright}
-	$\square$
-\end{flushright}
-\end{comment}
+
 \subsubsection{Examples}
@@
 \end{equation}
-%where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}+\delta_{a_{3}}^{x_{3}}$ 
-%Then, by using \eqref{exactCorrelations} we obtain 
-%\begin{align}
-%\mathbb{E}_{\mu}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\frac{x_{1}(x_{2}-1)(x_{3}-2)}{L(L^{2}-1)}&\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{ x_{2} (x_3-1)(L-1)-x_1 (x_2-1)
-%	(x_3-2)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}\nonumber\\
-%+\frac{x_1 (L (-x_3)+L+x_2 (x_3-2)+1)}{L(L^2-1)}&\beta_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{x_1 (x_2-1) (L-x_3+1)}{L \left(L^2-1\right)}&\beta_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
-%+ \frac{(L-1) x_2 (x_3-1)-x_1 (x_2-1)
-%	(x_3-2)}{L \left(L^2-1\right)}& \alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_3+1) (x_2 (L-x_1-1)+x_1)}{L
-%	\left(L^2-1\right)}&\alpha_{a_{1}}\beta_{a_{2}}\alpha_{a_{3}}\nonumber\\
-%+\frac{x_1 (L-x_2) (L-x_3+1)}{L \left(L^2-1\right)}&\alpha_{a_{1}}\alpha_{a_{2}}\beta_{a_{3}}\nonumber\\+\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L^{2}-1)}&\alpha_{a_{1}}\alpha_{a_{2}}\alpha_{a_{3}}
-%\end{align}
-\begin{comment}
-\begin{align}\label{three-pts-corr}
- \mathbb{E}_{\mu}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}
-	\\&+\nonumber
-	\frac{(L+1-x_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-x_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}
-	\\&+\nonumber
-	\frac{(L-x_{2})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}
-	\\&+\nonumber
-	\frac{(L-x_{1})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}
-	\\&+\nonumber
-	\frac{(L-x_{1})(L-x_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}
-	\\&+\nonumber
-	\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
-\end{align}
-\end{comment}
+
 Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
@@
 	\end{remark}
-%The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$.
-Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ exploiting the simpler commutators.
-Finally, we invert the similarities and retrieve the right eigenvector of $H^{'}$ with vanishing eigenvalue and  the arbitrary correlations in the non-equilibrium steady state.
-The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix~\ref{appB}.
-\begin{comment}
-{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$.
-The MPA gives the steady state in terms of an abstract algebra of operators.
-If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}.
-Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}.
-For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}.
-Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}.
-In subsection~\ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$.
-This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary.
-Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}.
-A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}.
-Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
-\end{comment}
+
 \subsection{Proof of Theorem~\ref{thm-correlations}}
@@
 Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
-\begin{comment}
- We compute
-\begin{enumerate}
-	\item $A_{N}=e_{aN}$ with $a\neq 1$
-	\begin{equation}
-		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
-	\end{equation}
-\item $A_{a}=e_{aa}$ with $a\neq 1$
-\begin{equation}
-		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
-	\end{equation}
-Indeed 
-\begin{equation}
-	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
-\end{equation}
-\end{enumerate}
-\end{comment}
+
 Therefore, using \eqref{HT-BA} we obtain for the left boundary 
@@
 	\begin{split}
-% <<<<<<< HEAD
-% 			H_{\text{right}}^{''}&=S_{2}H_{\text{right}}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
-% 			\\&=
-% =======
 			H_{\text{right}}^{''}=S_{2}H_{\text{right}}^{'}S_{2}^{-1}
-% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
 			=
-% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
 			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
@@
 
-\begin{comment}
-Using \eqref{transformationV} we introduce the \textit{similarity transformation} 
-\begin{equation}\label{similarity}
-    S:=\sum_{a=2}^{N}\beta_{a}\sum_{b=1}^{N}e_{ab}+V=-\sum_{a=2}^{N}\beta_{a}\sum_{b=1}^{N}e_{ab}+\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}
-\end{equation}
-Taking the tensor product over the sites of the chain we further define
-\begin{equation}
-    \mathcal{S}:=S^{\otimes L}
-\end{equation}
-Therefore, we call
-\begin{equation}\label{bbHamiltonian}
-    \mathbb{H}=\mathbb{B}_{1}+H_{\text{bulk}}+\mathbb{B}_{L}
-\end{equation}
-such that 
-\begin{equation}\label{similarS}
-    H=\mathcal{S}^{-1} \mathbb{H}\mathcal{S}
-\end{equation}
-The Hamiltonian $\mathbb{H}$ has lower-triangular left boundary and diagonal right boundary, i.e.
-\begin{equation}
-    \mathbb{B}_{1}=SB_{1}S^{-1}=e_{11}-\mathbbm{1}+\sum_{a=2}^{N}\left(\alpha_{a}-\beta_{a}\right)e_{a1}=\begin{pmatrix}
-		0&0&\ldots&0&0\\
-		\alpha_{2}-\beta_{2}&-1&\ldots&0&0\\
-		\vdots&\vdots&\ddots&\vdots&\vdots\\
-		\alpha_{N-1}-\beta_{N-1}&0&\ldots&-1&0\\
-		\alpha_{N}-\beta_{N}&0&\ldots&0&-1
-	\end{pmatrix}
-\end{equation}
-and 
-\begin{equation}
-    \mathbb{B}_{L}=SB_{L}S^{-1}=e_{11}-\mathbbm{1}=\begin{pmatrix}
-		0&0&\ldots&0&0\\
-		0&-1&\ldots&0&0\\
-		\vdots&\vdots&\ddots&\vdots&\vdots\\
-		0&0&\ldots&-1&0\\
-		0&0&\ldots&0&-1
-  \end{pmatrix}
-\end{equation}
-The bulk part of $\mathbb{H}$ is left unchanged by this transformation, i.e.
-\begin{equation}
-    \mathcal{H}_{x,x+1}=\left(S\otimes S\right)\mathcal{H}_{x,x+1}\left(S\otimes S\right)^{-1}
-\end{equation}
-In the following of our analysis it will be useful to have a relation between \eqref{hatHamiltonian} and \eqref{bbHamiltonian}. This relation reads as
-\begin{equation}
-    \widehat{H}=\mathcal{T}^{-1}\mathbb{H}\;\mathcal{T}
-\end{equation}
-where
-\begin{equation}
-    T=\left(S^{-1}\right)^{T}V=\exp{\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)}
-\end{equation}
-and 
-\begin{equation}
-    \mathcal{T}:=T^{\otimes L}
-\end{equation}
-Indeed, by imposing equal \eqref{similarV} and \eqref{similarS} we obtain 
-\begin{align*}
-    		\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}\mathcal{V}^{T}&=\mathcal{S}\mathbb{H}\mathcal{S}^{-1}\\
-		\mathcal{V}\widehat{H}\mathcal{V}^{-1}&=\mathcal{S}^{T}\mathbb{H}^{T}\left(\mathcal{S}^{-1}\right)^{T}\\
-		\widehat{H}&=\mathcal{V}^{-1}\mathcal{S}^{T}\mathbb{H}^{T}\left(\mathcal{S}^{-1}\right)^{T}\mathcal{V}\\
-		\widehat{H}&=\mathcal{T}^{-1}\mathbb{H}^{T}\mathcal{T}
-\end{align*}
-Associated with these new Hamiltonians $\widehat{H}$ and $\mathbb{H}$ we define the following steady states
-\begin{equation}
-	\mathbb{H}|\widetilde{\Psi}\rangle=0\qquad \widehat{H}^{T}|\widehat{\Psi}\rangle=0
-\end{equation}
-The steady states $|\Psi\rangle$, $|\widehat{\Psi}\rangle$ and $|\widetilde{\Psi}\rangle$ are linked by 
-\begin{align}
-	|\Psi\rangle=&\left(\mathcal{S}^{-1}\right)|\widetilde{\Psi}\rangle\label{SteadystateTilde}
- \\|\Psi\rangle =&\left((\mathcal{{V}}^{T})^{-1}\right)|\widehat{\Psi}\rangle \label{SteadystateHat}
- \\|\widehat{\Psi}\rangle=&\left(\mathcal{T}^{T}\right)|\widetilde{\Psi}\rangle\label{SteadyStateHatTilde}
-\end{align}
-In the following subsections we will first compute the steady state $|\widetilde{\Psi}\rangle$.
-Then, using the transformation $\mathcal{T}$ we will retrieve $|\widehat{\Psi}\rangle$.
-Finally, using the transformation $\mathcal{V}$ we will find $|\Psi\rangle$.
-\end{comment}
 \subsubsection{Closed formula for $|\Psi^{''}\rangle$}\label{subsectionSSHsec}
-\begin{comment}
-\textbf{Notation}: sometimes, in the following, we will denote differently the configuration of this hard-core chain. Each configuration can be written as
-\begin{equation}\label{Tau-Notation}
-	|\bm{\tau}\rangle=|\tau_{1},\ldots,\tau_{L}\rangle =\begin{pmatrix}
-		\tau_{1}\\
-		\vdots\\
-		\tau_{L}
-	\end{pmatrix}
-\end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The notation with $\bm{n}$, introduced in Section~\ref{subsectionGeneratorStr} and the one with $\bm{\tau}$ are related by 
-\begin{equation}
-	n_{a}^{x}=\delta_{\tau_{x},a}
-\end{equation}
-\end{comment}
-\begin{comment}
-
-This notation is equivalent to the one introduced.
-Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$.
-Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$.
-With this notation, we have that
-\begin{equation}\label{notation}
-	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
-\end{equation}
-with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
-\end{comment} 
+
 The ground state of the Hamiltonian $H^{''}$ is given by 
@@
 \end{equation}
-%\begin{equation}\label{ResulsBasis}
-%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
-%\end{equation}
+
 where 
@@
 
-%and the basis vector $|\bm{\tau}\rangle =\bigotimes_{x=1}^{L}|\tau_{x}\rangle$ with $\tau_{x}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
 \paragraph{Proof of formula \eqref{ResulsBasis}}  
-%In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof.
-We recall that these two notations are related by \eqref{notation-change-relation}.
 We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations.
@@
      X_{N}
-	\end{pmatrix}\dt%\quad \forall a\in \{1,\ldots,N-1\}\dt
+	\end{pmatrix}\dt
 \end{equation}
@@
 				X_{1}+\ldots +X_{N}\\
-	\end{pmatrix}\dt%=\begin{pmatrix} 
-	%	X_{a}-\beta_{a}\Xt_{N}\\ 
-		%	X_{1}+\ldots +X_{N}\\
-	%\end{pmatrix}
-	%\qquad \forall a=1,\ldots N-1
+	\end{pmatrix}\dt
 \end{equation}
@@
 		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
-	\end{pmatrix}\dt%\qquad\forall a\in \{1,\ldots,N-1\}\dt
+	\end{pmatrix}\dt
 \end{equation}
@@
 \begin{equation} 
-	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}%\qquad\forall a=1,\ldots,N\co
+	\left[X_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}
 \end{equation}
@@
 \begin{equation}\label{commutationsBula}
-	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co %\forall a\in \{1,\ldots,N-1\}\dt
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co
 \end{equation}
@@
 \begin{equation}\label{commLEFT}
-	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
+	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|
 	\co
@@
 \begin{equation}\label{commRIGHT}
-	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N-1
+	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle
 	\co
@@
 \end{align}
-\begin{comment}
-The basis is 
-$$
-|\bm{n}\rangle =|n_{1}^{1},\ldots,n_{N}^{1}\rangle \otimes \ldots\otimes |n_{1}^{L},\ldots,n_{N}^{L}\rangle
-$$
-such that, for each site $x\in \{1,\ldots,L\}$, $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}^{'}$. \\
-\end{comment}
+
 To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
@@
 \begin{align}\label{usefulRelaton-many}
-	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=%\widetilde{X}_{a}^{n-1}\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
-%	\\&=(\alpha_{a}-\beta_{a})\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
-%	\\&=
-%	(\alpha_{a}-\beta_{a})\widetilde{X}_{a}^{n-2}\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left((\alpha_{a}-\beta_{a})\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
-%	\\&=\ldots\\&=
+	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=
 	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell(\alpha_{a}-\beta_{a})\right)^{n}\dt
 \end{align}
-\begin{comment}
-therefore 
-\begin{align*}
-	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}(\alpha_{a}-\beta_{a})\right)^{n_{a}}\dt
-\end{align*}
-\end{comment}
+
 By taking the product over the sites $x$ from $1$ to $L$ we obtain 
@@
 Multiplying by the boundary vectors and by using \eqref{commRIGHT} we have 
-%\begin{equation}
-%	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
-%	|V \rangle=\langle %V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
-%\end{equation}
-%Using 
 \begin{align}
@@
 \end{equation}
-\begin{comment}
-Using the notation $\tau_{x}$, $|\bm{\tau}\rangle $ with $\bm{\tau}$, related to the one with $\bm{n}$ by \eqref{notation-change-relation}, we have 
-\begin{equation}
-	\prod_{a=1}^{N-1}\left((\alpha_{a}-\beta_{a})\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}=\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}
-\end{equation}
-and 
-\begin{equation}
-	\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(L+2)}=\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\dt
-\end{equation}
-Therefore we obtain
-\begin{equation}
-|\Psi^{''}\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle\dt
-\end{equation}
-
-\end{comment}
-\begin{comment}
-{\color{blue}
-\begin{equation}
-\begin{split}
-\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
-&=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},N})\right)}\\
-&=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}{\Gamma\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)}\\
-&=  \frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} (\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
-% &=\left[\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{(1-\delta_{\tau_{x},N})}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N}),-1)\\
-\end{split}
-\end{equation}}
-\end{comment}
+
 It follows that 
@@
 Therefore, we obtain \eqref{ResulsBasis}.
-%The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.
 \begin{flushright}
@@
 	\end{equation} 
-%\begin{equation}\label{ABS}
-%	\begin{split}
-%		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
-%	\end{split}
-%\end{equation} 
-\begin{comment}
-{\color{blue}
-	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}
-	\end{equation}
-\begin{equation}
-	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
-\end{equation}
-	\begin{equation}
-		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\prod_{x=1}^{L}\left(\frac{(\alpha_{\tau_{x}}-\beta_{\tau_{x}})}{\beta_{\tau_x}}\right)^{c_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{1-\delta_{\tau_{x},N} }
-	\end{equation}
-}
-\end{comment}
-	%\com{Double check this. Sum looks strange}
-%and where
-% \begin{equation}\label{CiEquation}
-%	c_{y}=\begin{cases}
-%		1\quad \text{if}\quad \tau_{y}\neq 1\\
-%		0\quad \text{if}\quad \tau_{y}=1
-%	\end{cases}\qquad \forall y\in \{1,\ldots,L\}
-%\end{equation}
 \paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we  show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$.
@@
 \end{equation} 
-\begin{comment}
-{\color{blue}
-We introduce $\forall x\in\{1,\ldots,L\}$, for $i\in \{1,\ldots,L\}$ and $q_{1},\ldots,q_{i}\in\{1,\ldots,L\}$ 
-\begin{equation}
-	\varphi_{x}^{i}(q_{1},\ldots,q_{i})=\begin{cases}
-		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{i}\}\\
-		N\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{i}\}\\
-	\end{cases}\dt
-\end{equation}
-This is a new configuration at site $x$ where, if $x\in\{q_{1},\ldots,q_{i}\}$, the occupation $\tau_{x}$ is replaced by $N$, while it is left uncaged if $x\notin \{q_{1},\ldots,q_{i}\}$.
-The dependence of $\varphi_{x}^{i}(q_{1},\ldots,q_{i})$ with respect to $q_{1},\ldots,q_{i}$ is usually understood for the sake of notation.
-}
-\end{comment}
-% By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} the formula for $|\Psi^{''}\rangle$ we obtain 
 From this it follows that
@@
 	where we used the expression \eqref{ResulsBasis} for $\Psi^{''}(\bm{\sigma})$.
-%where, for arbitrary $i\in\{1,\ldots,L\}$,  $\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{i}}\ldots,\tau_{L})$ means that the $\tau_{q_{1}},\ldots,\tau_{q_{i}}$ have been replaced by $N$.
-\begin{comment}
-{\color{blue}
-	Old proposal
-\begin{equation*}
-	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\varphi_{1}^{1},\ldots,\varphi_{L}^{1})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\varphi_{1}^{2},\ldots,\varphi_{L}^{2})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation*}}
-{\color{blue}
-	Other proposal
-\begin{equation*}
-	\begin{split}
-		\Psi^{'}(\bm{\tau})&=\langle \bm{\tau}|(\mathcal{S}_{2}^{-1})^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\tau_{q_{1}}=N,\ldots,\tau_{L})\beta_{q_{1}^{1}}\\&+
-		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\tau_{q_{1}}=N,\ldots,\tau_{q_{2}}=N,\ldots,\tau_{L})\beta_{q_{1}}\beta_{q_{2}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}
-	\end{split}
-\end{equation*}
-}
-\end{comment}
-%For a fixed configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$, \\ \\ 
 We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\bm{\tau},\bm{\sigma}\in\Omega^{'}$, we have 
@@
 Indeed, considering the first and last equalities we have that: if $\tau_{x}=\sigma_{x}$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$.
-%\begin{equation}
-%	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
-%\end{equation}
-%To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain
-%\begin{align}
-%	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,Y_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,Y_x}\right]\nonumber\\
-%	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
-%	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-%	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
-%	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-%\end{align}
-%Consider the factor $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}$ in the above equation.
-When $\sigma_{x}\neq N$ (then $c_{x}=0$) and $\tau_{x}\neq N$, it becomes $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$.
-On the other hand, when $\sigma_{x}=N$ (then $c_{x}=1$)  and $\tau_{x}\neq N$, then it becomes $1$.
-Finally, if $\sigma_{x}=N$ and $\tau_{x}=N$ it becomes $0$.
-Therefore, we can replace it by $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}$.
-It follows that
-%\begin{equation}
-%	\begin{split}
-%	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-%	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
-%	\end{split}
-%\end{equation}
+
 As a consequence we can write \eqref{ABS_intermediate} as 
@@
 \end{equation}
-%thus, by using equation \eqref{ResulsBasis}, we have
-%\begin{equation}
-	%\Psi^{''}(\bm{\sigma})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\sigma_{x}}^{(1-c_{x})}\left(1+\sum_{j=x}^{L}c_{j}\right)
-%\end{equation}
-\begin{comment}
-	\begin{equation}
-		\Psi^{''}(\bm{\mu})=\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\mu_{x}}^{(1-\delta_{\mu_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right)
-	\end{equation}
-\begin{equation}
-	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\co
-\end{equation}
-\end{comment}
- \begin{comment}
-
- where we have used the fact that 
-\begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\mu_{x},N})\right)\co
-\end{equation}
-Introducing $c_{x}$ defined as 
-\begin{equation}
-	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}\co
-\end{equation}
-we obtain 
-\begin{equation}\label{coefficients-psiSec}
-	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
-\end{equation}
-where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.\\
-\end{comment}
-\begin{comment}
-We introduce the following notation
-\begin{equation}\label{notation1}
-    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
-\end{equation}
-and 
-\begin{equation}\label{notation2}
-    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
-    \end{equation}
-    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that
-
-    \begin{equation}\label{InverseS2}
-    	\begin{split}
-    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\right.
-    		\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
-    		\\&+\left.
-    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L-1},\ldots,\varphi_{L}^{L-1}}
-    		\right. \\&+ \left. 
-    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}} \right\}
-    	\end{split}
-    \end{equation}
-\end{comment}
-    \begin{comment}
-    We prove it by induction. When $L=1$ it is true, indeed
-    \begin{equation}
-    	\mathcal{S}_{2}^{-1}=\sum_{\tau_{1}=1}^{N}\left\{e_{\tau_{1}}^{\tau_{1}}+(1-\delta_{\tau_{1},N})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
-    \end{equation}
-    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
-\begin{align*}
-    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=%\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right.
-    	%\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
-    	%\\&+\left.
-    	%\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
-    	%\right. \\&+ \left. 
-    	%\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\right.
-    	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
-    	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L-1},\ldots,\varphi_{L}^{L-1}}
-    	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}} \right\}
-    	\\&
-    	\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},N})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
-    	\\&=
-    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{1},\ldots,\varphi_{L+1}^{1}}\beta_{\tau_{q_{1}}}\right.
-    	\\&+\left.
-\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{2},\ldots,\varphi_{L+1}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
-    	\\&+\left.
-    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L+1}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},N})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L},\ldots,\varphi_{L+1}^{L}}
-    	\right. \\&+ \left. 
-    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L+1}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},N})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1}^{L+1},\ldots,\varphi_{L+1}^{L+1}} \right\}
-    	\\&=
-    	\left(\mathcal{S}_{2}^{\otimes L+1}\right)^{-1}
-\end{align*}
-\end{comment}
-    \begin{comment}
-    \begin{equation}
-        S_{2}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+Q
-    \end{equation}
-    where
-    \begin{equation}
-	Q:=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}
-\end{equation}
-We compute
-\begin{equation}
-    \begin{split}
-        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
-         \\&=
-         I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
-    \end{split}
-\end{equation}
-where the addends are 
-\begin{equation}
-\begin{split}
-	&I_{N\times N}\otimes I_{N\times N}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{\tau_{1},s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}\\
-	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1,s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},1}\beta_{s_{2}}\\
-	&Q\otimes I_{N\times N}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2,s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{1,s_{2}}\beta_{\tau_{1}}\\
-	&Q\otimes Q=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1},s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{1,1}\beta_{\tau_{1}}\beta_{s_{2}}
- \end{split}
-\end{equation}
-The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
-\begin{equation}
-	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}^{q_{1},q_{2}}\right\}_{\tau_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
-\end{equation}
-where the subscripts $\tau_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $\tau_{1},s_{2}$ reads
-\begin{equation}
-	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{\tau_{1},s_{2}}^{\tau_{1},1}+(1-\delta_{\tau_{1},1})\beta_{\tau_{1}}e_{\tau_{1},s_{2}}^{1,s_{2}}+(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\beta_{\tau_{1}}\beta_{s_{2}}e_{\tau_{1},s_{2}}^{1,1}
-\end{equation}
-
-The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
-To find these quantities we fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$.
-Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
-\begin{equation}
-	\begin{split}
-\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
-  \\&+
-  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
-	\end{split}
-\end{equation}
-\end{comment}
-%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
-%Therefore, we have that equation \eqref{ABS_intermediate} becomes
-%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}.
-Then, equation  \eqref{ABS_intermediate} reads
+
 Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
@@
 \end{equation} 
-%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
-%Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, \eqref{ABS-vect} follows.
 \begin{flushright}
@@
 \end{equation}
-\begin{comment}
-	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
-	\begin{equation}
-		\begin{split}
-			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-			\\&
-			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\}
-		\end{split}
-	\end{equation}
-	where we have introduced, $\forall x\in \{1,\ldots,L\}$
-	\begin{equation}
-		%\eta_{x}=\begin{cases}
-			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-			%	d_{x}\qquad &\text{otherwise}
-			%\end{cases}\qquad
-			\theta_{x}(b)=\begin{cases}
-				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-				N \qquad &\text{otherwise}
-			\end{cases}
-		\end{equation}
-		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
-		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
-		\begin{align*}
-			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
-			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
-\\&+\left.
-\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
-			\\&\otimes
-			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
-			\\&=
-			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right.
-\\&+\left.
-\sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
-		\end{align*}
-		\begin{comment}
-
-			\begin{equation}
-				F=\left(V^{-1}\right)^{T}
-			\end{equation}
-			and thus 
-			\begin{equation}
-				\mathcal{F}=F^{\otimes L}
-			\end{equation}
-			By direct computations and using the notation introduced in \eqref{notation1} and \eqref{notation2} we have 
-			\begin{equation}
-				F=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+\delta_{\tau_{1},1}(-1)\sum_{d_{1}=2}^{N}e_{1}^{d_{1}}
-			\end{equation}
-			Taking the tensor product over two sites we obtain 
-			\begin{equation}
-				\begin{split}
-					F\otimes F&=\sum_{\tau_{1},s_{2}=1}^{N}\left(e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-					\right.\\ &+\left. 
-					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}\right)
-				\end{split}
-			\end{equation}
-			therefore, fixing a raw with indices $\tau_{1},s_{2}\in \{1,\ldots,N\}$ of the matrix $F\otimes F$ we obtain 
-			\begin{equation}
-				\begin{split}
-					\left(F\otimes F\right)_{\tau_{1},s_{2}}&=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(-1)\delta_{s_{2},1}\sum_{d_{2}=2}^{N}e_{\tau_{1},1}^{\tau_{1},d_{2}}
-					\\&+
-					(-1)\delta_{\tau_{1},1}\sum_{d_{1}=2}^{N}e_{1,s_{2}}^{d_{1},s_{2}}+(-1)^{2}\delta_{\tau_{1},1}\delta_{s_{2},1}\sum_{d_{1},d_{2}=2}^{N}e_{1,1}^{d_{1},d_{2}}
-					\\&=
-					\sum_{q_{1}=1}^{2}\prod_{r=1}^{1}\delta_{s_{q_{r}},1}\sum_{r=1}^{1}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-					+
-					(-1)\sum_{q_{1}=1}^{2}\sum_{q_{2}=q_{1}+1}^{2}\prod_{r=1}^{2}\delta_{s_{q_{r}},1}\sum_{r=1}^{2}\sum_{d_{q_{r}}=2}^{N}e_{\tau_{x},1}^{\tau_{x}d_{q_{r}}}
-				\end{split}
-			\end{equation}
-			where $e_{\tau_{x},d_{q_{r}}}$ denotes the matrix $e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}$ where the subscripts $s_{q_{r}}$ have been replaced by "1" and the superscript $s_{q_{r}}$ have been replaced by $d_{q_{r}}$, with $r=1,2$.
-\\
-			We generalize this tensor product to an arbitrary number of sites $L$ obtaining the matrix $\mathcal{F}$.
-We write the expression of a fixed raw with indices $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$ as
-			\begin{equation}
-				\begin{split}
-					\mathcal{F}_{\tau_{1},\ldots,\tau_{L}}&=e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}
-					\\&
-					+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right)\sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}
-				\end{split}
-			\end{equation}
-			where $e_{\ldots,\tau_{x},\ldots,\underbrace{1}_{q_{r}},\ldots}^{\ldots,\tau_{x},\ldots,\,d_{q_{r}}\,,\ldots}$ denotes the matrix $e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}$ where the subscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by "1" and the superscripts $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-\\
-			The product $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ gives a vector whose component are denoted by $\Psi(\bm{\tau})$. 
-			To find this elements we fix the rows correspondent to $\bm{\tau}$.
-Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row of the vector $\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle$ reads
-		\end{comment}
+
 		Considering 
@@
 Finally, using equation \eqref{interpretation-PsiP}, the result follows.
-
-%	and where 
-%		\begin{equation}
-%		\begin{split}
-	%		\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}g_{x}(x,c_{x},\ldots,c_{L})\\&
-%			\;\;\;\;\;\;\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{c_{q_{k}}}\beta_{i_{q_{k}}}^{1-c_{q_{k}}}\right)\left(\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\right)
-%		\end{split}
-%	\end{equation}
-%	\begin{equation}
-	%	\begin{split}
-	%		\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
-	%		\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})
-	%		\end{split}
-	%	\end{equation}
-	%\begin{equation}
-	%	\begin{split}
-	%	&\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}+Q(1)}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}+Q(L)}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\\
-	%	&\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{1-c_{q_{k}}}\beta_{i_{q_{k}}}^{c_{q_{k}}}\right)\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\right)
-%	\end{split}
-%	\end{equation}
-%	with
-%	\begin{equation}
-%		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
-%	\end{equation}
-%and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 
-%	\begin{equation}
- %\end{equation}
-%	Moreover, $\Psi(\bm{\tau})$ are interpreted as the probabilities in the steady state of having a configuration $\bm{\tau}$, i.e.
-%	\begin{equation}
-%%	\end{equation\end{corollary} 
 \begin{remark}[Equilibrium case]
@@
 \end{remark}
-\begin{comment}
-\begin{remark}[Implicit form of $\Psi(\bm{\tau})$]
-	The elements of the the vector $|\Psi\rangle$ can also be written as a linear combination of elements $\Psi^{'}(\bm{\tau})$ as 
-	\begin{equation}\label{implicit-steadyState}
-		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-	\end{equation}
-	where the notation
-	\begin{equation}%\label{notation-PSI}
-		\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-	\end{equation}
-	means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
-	\begin{equation}
-		\begin{cases}
-			\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
-			\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
-		\end{cases}
-	\end{equation}	
-\end{remark}
-\end{comment}
-%Therefore, 
-%\begin{equation}
-%\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-%\end{equation} are computed using \eqref{exactCorrelations}. \\ \\
-\begin{comment}
-	\begin{equation}\label{SteadyState-coeff-implicit}
-		\begin{split}
-			\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-		\end{split}
-	\end{equation}
-\end{comment}
-%In \eqref{SteadyState-coeff-implicit} there are two terms.
-For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}.
-The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$.
-If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.
-%\begin{remark}%[Correlation as the steady state of a $m$-chain ]
-%	We observe that, as a consequence of Section~\ref{subsection-interpretationPSIp}, if $\bm{\tau}$ has only non-empty occupations, i.e.
-$\tau_{x}\in \{1,\ldots,N-1\}$ for all $x\in \{1,\ldots,L\}$, then
-%	\begin{equation}
-%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]
-%	\end{equation}
-%\begin{comment}
-% As a consequence, we can give a different interpretation to correlation computed in \eqref{exactCorrelations}.
-Consider the sites $(x_{k})_{k\in \{1,\ldots,m\}}$ and fix $(a_{k})_{k\in \{1,\ldots,m\}}$ introduced in Theorem~\ref{thm-correlations}.
-We define a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$.
-We denote by $|\Psi_{m}\rangle$ the non-equilibrium steady state of this $m$-chain.
-Then, we have that the correlations computed in \eqref{exactCorrelations} can be written as
-%\begin{equation}
-%	\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\Psi_{m}(a_{1},\ldots,a_{m})
-%\end{equation}
-%This means that we can define a mapping between the $m$-point correlation of chain of length $L$ and the non-equilibrium steady state of a chain of length $m$. This mapping, 
-%\end{comment}
-%	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$.
-%\end{remark}
-\begin{comment}
-	\begin{remark}
-		The coefficients $\Psi(\bm{\tau})$ can also be written explicitly by replacing $\Psi^{'}(\bm{\tau})$ with formula \eqref{ABS}. They read 
-		\begin{equation}
-			\begin{split}
-				\Psi(\bm{\tau})&=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}
-				\\&+
-				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
-				\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
-				\\&
-				\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)(\alpha_{\eta_{x}}-\beta_{\eta_{x}})^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
-			\end{split}
-		\end{equation}
-		where we have introduced, $\forall x\in \{1,\ldots,L\}$
-		\begin{equation}\label{eta-notation}
-			\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
-				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
-				i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
-			\end{cases}%\qquad \theta_{x}=\begin{cases}
-				%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
-				%	1 \qquad &\text{otherwise}
-				%\end{cases}
-			\end{equation}
-			The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
-		\end{remark}
-	\end{comment}
-	\begin{comment}
-		{\color{blue}
-			\begin{equation}\label{steadyStateH-coeff}
-				\begin{split}
-					\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-					\\&+
-					\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
-					\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
-					\\&
-					\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
-					\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
-					\\ &
-					\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-					\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-				\end{split}
-			\end{equation}
-		}
-	\end{comment}
-	%	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
-	%	\begin{equation}\label{LinkABS-corr}
-		%		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
-		%	\end{equation}
-	%	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.
-		\begin{comment}
-
-		From Section~\ref{correlation-section} we recall that the components $\Psi^{'}(\bm{\tau})$ of $|\Psi^{'}\rangle$ can be written as in equation \eqref{interpretation-PsiP}. Thus, we have that  
-			\begin{equation}
-			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1}^{L}\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{1-\delta_{\tau_{x},N}}\right]
-		\end{equation}
-	\end{comment}
-			%	\begin{equation}
-				%		\begin{split}
-					%			\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
-					%			\\&
-					%			+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-					%		\end{split}
-				%	\end{equation}
-			%where $\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)$ denotes the component $\Psi{'}(\tau_{1},\ldots,\tau_{L})$ where the occupations  $\tau_{q_{1}},\ldots,\tau_{q_{b}}$ have been replaced by $d_{q_{1}},\ldots,d_{q_{b}}$.
-			%Using \eqref{elementsABS} we have 
-			%	\begin{equation}
-				%	\begin{split}
-					%		\Psi{'}(\eta_{1},\ldots,\eta_{L})=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\eta_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\eta_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\eta_{x}}^{1-c_{x}}\beta_{\eta_{x}}^{c_{x}-\delta_{\eta_{x},N}}
-					%		\end{split}
-				%	\end{equation}
-			\begin{comment}
-				{\color{blue}
-					\begin{equation}
-						\begin{split}
-							&\Psi{'}(\ldots,\tau_{x},\ldots,d_{q_{r}},\ldots)=\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{l}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}
-							\\&  
-							\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
-							\\&
-							\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
-						\end{split}
-				\end{equation}}
-
-				indeed, in each coordinate $q_{r}$ with $r=1,\ldots b$ the species $N$ is replaced by all other possible species from $1$ to $N-1$.
-			\end{comment}
-		%	Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{SteadyState-coeff-implicit}. 
-		%	\begin{flushright}
-		%		$\square$
-		%	\end{flushright}
-		\begin{comment}
-		\begin{remark}
-Formula \eqref{SteadyState-coeff-implicit} can be also obtained without inverting the matrix $S_{1}$, but just using the conservation of probability in the non-equilibrium steady state.
-Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have
-			\begin{align}
-				\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\mu\left(\sigma_{1}=\tau_{1},\ldots,\sigma_{L}=\tau_{L}\right)=\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\nonumber\\
-				=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\right]\nonumber\\
-				=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}\right)\right)\right]
-				%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-			%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
-			%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
-				%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
-			\end{align}
-		where in the last equality we exploited the fact that 
-		\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a\}}
-		\end{equation}
-		Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$	we retrieve \eqref{SteadyState-coeff-implicit}.
-			\end{remark}
-		\end{comment}
-		\begin{comment}
-			\begin{remark}[Non-equilibrium steady state using exact correlations]
-			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
-				\begin{align}
-					\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
-					=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
-					%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
-				\end{align}
-				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section~\ref{correlation-section}, we have that
-				\begin{equation}
-				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-				\end{equation}
-			where the expectation is taken with respect to the non-equilibrium steady state distribution of the variables $\bm{\sigma}$ and can be computed using \eqref{exactCorrelations}. 
-				\end{remark}
-		\end{comment}
-				\begin{comment}
-					where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
-					\begin{equation}
-						\begin{cases}
-							\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
-							\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
-						\end{cases}
-					\end{equation}
-					Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section~\ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
-					\begin{equation}
-						\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
-					\end{equation}
-					Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
-					\begin{equation}
-						\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
-					\end{equation}
-				\end{comment}
-
 \subsection{The single-species case (SSEP)}
@@
 \end{equation}
-%with
-%\begin{equation}
-%	|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1} \dt
-%\end{equation}
+
 \textbf{Proof of \eqref{NESS-SSEP}:} the proof follows from \eqref{implicit-PSI-PSIp} and from the coefficients $\Psi^{'}(\bm{\tau})$ computed in \eqref{PsiI-N2}. 
@@
 \end{flushright}
-\begin{comment}
-\subsection{Explicit formula for the steady state $|\Psi\rangle$}
-{\color{blue}can we proceed as above? uing sth similar to \eqref{goodTP-S2}}
-
-The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
-\begin{equation}\label{steadyStateH}
-	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
-\end{equation}
-where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
-
- Using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, however to compute correlations it is enough the above expression.
-We report the explicit formula and the proof in Appendix~\ref{appB}.\\
-\\
-The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
-\end{comment}
-\begin{comment}
-\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Section~\ref{subsectionSSHsec}.
-If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
-\begin{align}
-	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
-	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
-\end{align}
- For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
-\begin{equation}
-	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
-\end{equation}
-where $x_{k}$ is the position of the $k$-th particle among $q$. 
-We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, thus we have that 
-\begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
-\end{equation}
-Moreover, we observe that 
-\begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(L+2)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
-\end{equation}
-All in all we obtain 
-\begin{equation}\label{PsiI-N2}
-\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
-\end{equation}
-\end{comment}
-
-\begin{comment}
-	\subsubsection{Exact steady state correlations}
- introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
-\begin{align}
-	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
-	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
-\end{align}
-We observe that, at most $q$ factors do survive in the product over $k$.
-For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$.
-For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by
-\begin{equation}
-	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
-\end{equation}
-We can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
-\begin{equation}
-	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
-\end{equation}
-Moreover, we observe that 
-\begin{equation}
-	\frac{\Gamma(L+2-q)}{\Gamma(L+2)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\dt
-\end{equation}
-All in all we have that
-
-\paragraph{Proof of formula \eqref{exactCorrelations}}
-{\color{blue}
-We introduce the space 
-\begin{equation}
-	\widehat{\Omega^{'}}^{m}=\left\{\bm{\tau}\in \Omeg^{'}a\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}
-\end{equation}
-where $m$ occupations are fixed and the other $L-m$ can vary in all possible ways. Therefore, we compute 
-\begin{equation}
-\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)
-\end{equation}
-Using \eqref{SteadyState-coeff-implicit}, we have that 
-\begin{align}
-&\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi^{'}(\tau)\nonumber
-\\+&
-\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-\end{align}
-We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega^{'}}^{m}$, i.e.
-$\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$.
-We also introduce the space
-\begin{equation}
-\widehat{\Omega^{'}}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega^{'}}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
-\end{equation}
-Then we obtain that 
-\begin{align}
-&\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber
-\\+&
-\sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-\end{align}
-In the first summation on the right-hand-side, there is only one term that has all sites empty but the one in position $y_{1},\ldots,y_{m}$ that are occupied by $s_{1},\ldots,s_{m}$.
-This is reached when $\ell=L-m$ and we denote it by $\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)$.
-The second term on the right-hand-side in the above equation replaces $b$ empty occupations with all possible non-empty species.
-If the configuration $\bm{\tau}\in\widehat{\Omega^{'}}_{\ell}^{m}$ has $\ell<b$ no contributions are seen.
-Otherwise, if $\ell\geq b$, $b$ empties are changed, obtaining configuration with $r=\ell-b$ voids occupations, with $r\in \{0,\ldots, L-m-b\}$.
-Each of such a configuration is counted $\binom{L-r-m}{b}$ times.
-Therefore, we obtain
-\begin{align}
-	\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
-	\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\mathbbm{1}_{\{b\leq L-m-r\}}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
-\end{align}
-In the second term of the above equation we exchange the summations obtaining 
-\begin{align}
-\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=&\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\nonumber
-\\+&\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}\mathbbm{1}_{\{b\leq L-m-\ell\}}\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
-\end{align}
-Using the binomial theorem, for every $\ell\in \{0,\ldots, L-m-1\}$, we have that
-\begin{equation}
-	1+\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}=0
-\end{equation}
-thus, we obtain 
-\begin{equation}
-\sum_{\bm{\tau}\in \widehat{\Omega^{'}}^{m}}\Psi(\tau)=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
-\end{equation}
-that implies 
-\begin{equation}\label{shorter-chain}
-\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
-\end{equation}
-% Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$.
-We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$.
-By using duality, we showed in \eqref{CorrelationByABS-prob} that
-% \begin{equation}
- %	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
-% \end{equation} 
-%where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
-Using formula \eqref{ABS_1} we have that 
-\begin{equation}
- \Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt
-\end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,y_{k},c_{k},\ldots,c_{m})$ we prove \eqref{exactCorrelations}.
-\begin{flushright}
-	$\square$
-\end{flushright}
-}
-{\color{blue}
-\textbf{Remark}: Consider equation \eqref{shorter-chain} and the fact that, from equation \eqref{SteadyState-coeff-implicit} we have  
-\begin{equation}
-\Psi^{'}(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\Psi_{m}^{'}\left(s_{1},\ldots,s_{m}\right)=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
-\end{equation}
-where $|\Psi_{m}^{'}\rangle$ and $|\Psi_{m}\rangle$ are the eigenvector with vanishing eigenvalues of a chain with length $m$. Therefore, we have that 
-\begin{equation}
-\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\Psi_{m}\left(s_{1},\ldots,s_{m}\right)
-\end{equation}
-i.e., computing the $m$-point correlations is equivalent to computing the steady state of a chain of length $m$ where the occupations are $s_{1},\ldots,s_{m}$ and the coordinates of the sites are $y_{1},\ldots,y_{m}$.
-I still do not have an interpretation to this...
-}
-\end{comment}
-\begin{comment}
-{\color{blue}
- \paragraph{Proof of formula \eqref{exactCorrelations}}
- We aim to compute the correlations between the sites% $\mathbf{x}=\left(x_{1},\ldots,x_{m}\right)$ occupied by the species $\mathbf{a}=\left(a_{1},\ldots,a_{m}\right)$, such that $a_{1},\ldots,a_{m}\in \{2,\ldots,N\}$ i.e.
-\begin{equation}%\label{Prob-m}
-	%\begin{split}
-	%	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{\text{stat}}&
-	%	=\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)
-%	\end{split}
-\end{equation}
-where we denote %$\mathbb{P}_{stat}$ the non-equilibrium steady state distribution. 
-This corresponds to the steady state probability of a chain of length %$m$ with each coordinates $x_{i}$ occupied by $a_{i}\neq 1$.Therefore, using again the notation \eqref{notation} and calling %$\tau_{i}=a_{i}$, we have
-\begin{equation}
-	\mathbb{P}_{stat}\left(n_{a_{1}}^{x_{1}}=1,\ldots,n_{a_{m}}^{x_{m}}=1\right)=\Psi\left(\tau_{1},\ldots,\tau_{m}\right)
-\end{equation}
-where $\Psi(\bm{\tau})$ is the element of the vector \eqref{steadyStateH} computed for this chain $m$.
-As already remarked in \eqref{LinkABS-corr}, for non-empty configurations we have:
-\begin{equation}\label{Corr-mABS}
-	\Psi(\tau_{1},\ldots,\tau_{m})=\Psi^{'}(\tau_{1},\ldots,\tau_{m})
-\end{equation}
-Thus, by applying \eqref{ABS_intermediate} we have 
-\begin{equation}
-	\Psi(\tau_{1},\ldots,\tau_{m})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(L+2)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
-\end{equation}
-Introducing $f(L,c_{1},\ldots,c_{m})$ and $g_{k}(L,x_{k},c_{k},\ldots,c_{m})$ and using $\tau_{i}=a_{i}$ $\forall i=1,\ldots,m$, we have the formulas for arbitrary correlations.
-\begin{flushright}
-    $\square$
-\end{flushright}}
-\end{comment}
 
@@
 where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a})_{a\in \{1,\ldots,N\}}$ respectively.
-\begin{comment}
-\begin{equation}
-	\mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-while at the boundaries 
-\begin{equation}
-	\mathcal{L}_{\text{left}}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{\text{right}}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)\dt
-\end{equation}
-\end{comment}
 The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, has generator
@@
 The duality function reads is \eqref{dualityElements} specified on the chain.
-\begin{comment}
-\begin{equation}\label{abs-dual-boundary-chain}
-	\begin{split}
-		\widetilde{\mathcal{L}}_{\text{left}}f(\bm{\xi})&=|\alpha|\sum_{a=1}^{N-1}\xi_{a}^{1}\left(f(\bm{\xi}-\bm{\delta}_{a}^{1}+\bm{\delta}_{N}^{1}+\bm{\delta}_{a}^{0})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{\text{right}}f(\bm{\xi})&=|\beta|\sum_{a=1}^{N-1}\xi_{a}^{L}\left(f(\bm{\xi}-\bm{\delta}_{a}^{L}+\bm{\delta}_{N}^{L}+\bm{\delta}_{a}^{L+1})-f(\bm{\xi})\right)
-	\end{split}
-\end{equation}
-where $0$ and $L+1$ are the extra-sites.
-\end{comment} 
-\begin{comment}
-, i.e.
-\begin{equation}\label{dualityFunctionChain}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-\end{comment}
-
-%The dual process has absorbing boundaries.
-This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process.\\
 We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
@@
 The absorption probabilities for higher point correlations fulfill  difference equations.
-
-% In the following we specialize the chain to the integrable case $\nu=1$.
-As it will be shown, in such a situation the non-equilibrium steady state correlations can be computed with different techniques exploiting the integrability of the process (matrix product ansatz and quantum inverse scattering method) combined with duality and, as a by-product, all absorption probabilities can be explicitly found.
 
@@
 This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
-%{\color{blue} 
-%	Indeed, we impose the detailed balance for the stirring-mutation generator $\mathcal{L}_{x,x+1}^{c}$, for arbitrary $c\in \{1,\ldots,N-2\}$. Consider the transition 
-%				\begin{equation*}
-%			\bm{n} \to\bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c(a)}}^{x+1}-\delta_{b}^{x+1}
-%			\end{equation*} 
-%		we obtain that 
-%		\begin{equation*}
-%			p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
-%		\end{equation*}
-%		that is verified if $p_{a}=p_{b}$ for all $a,b\in \{1,\ldots,N-1\}$.
-A similar argument for the generator $\mathcal{L}^{m}$ gives the same conditions for the $p$'s.
-Considering the boundary generators, one obtain the result.}
-% Arguing as in Remark~\ref{rem-rev}, conditions \eqref{cond-gen} become here
-%\begin{equation}
-%	\alpha((N-2)\beta+\beta_{N})=\beta((N-2)\alpha+\alpha_{N})
-%\end{equation} 
-%where $\alpha_{a}=\alpha_{b}=\alpha$ and $\beta_{a}=\beta_{b}=\beta$ for all $a,b\in \{1,\ldots,N-1\}$.%For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multispecies stirring.
-Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
-\begin{comment}
-\begin{equation}
-	\begin{split}
-		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{h_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{h_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{h_{c}(b)}^{n_{h_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{h_{c}(a)}^{n_{h_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
-		\\
-		=&(n_{h_{c}(b)}^{x}+1)(n_{h_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{h_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{h_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
-		\\&
-		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{h_{c}(b)}^{n_{h_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{h_{c}(a)}^{n_{h_{c}(a)}^{x+1}+1}
-	\end{split}
-\end{equation}
-that simplifies to
-
-\begin{equation}
-	p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
-\end{equation}
-By the arbitrariness of $a,b,$ it is true if and only if
-\begin{equation}\label{p-equal}
-	p_{a}=p\qquad \forall a\in \{1,\ldots,N-1\}
-\end{equation}
-while $p_{N}=1-\sum_{a=1}^{N-1}p_{a}$\\
-For the boundary generators $\mathcal{L}_{\text{left}}^{rd}$ and $\mathcal{L}_{\text{right}}^{rd}$ we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and, due to \eqref{p-equal}, we also need $\alpha_{a}=\alpha$ for all $a\in\{1,\ldots,N-1\}$.
-\end{comment}
+
 \subsubsection{Duality for the reaction-diffusion process}
@@
 \end{flushright}
-\begin{comment}
-\subsection{One points correlations of the non-integrable multi-speceis stirring process on a chain[To check, something could be wrong]}
-In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{a})_{a=1,\ldots,N}$ and $(\beta_{a})_{a=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability.
-When the maximal occupation of each site $\nu>1$, this nice property is lost.
-However, something about correlations can be said using duality.
-In this subsection we still consider the same geometry of~\ref{subsection-exact}.
-As pointed out in section~\ref{sectionDuality}, the dual process voids the chain.
-Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.
-In this context it is better to work agin with generators.
-We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry.
-\\
-We consider the process $(\bm{n}(t))_{t\geq 0}$ on a chain of length $L$ with the end sites connected with two reservoirs.
-This interaction with the external environment is described by the generators
-\begin{equation}
-    \mathcal{L}_{\text{left}}f(\bm{n})=\sum_{a,b=0}^{N}\alpha_{a}n_{b}^{1}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)\qquad \mathcal{L}_{\text{right}}f(\bm{n})=\sum_{a,b=0}^{N}\beta_{a}n_{b}^{L}\left(f(\bm{n}-\delta_{b}^{x}+\delta_{a}^{x})-f(\bm{n})\right)
-\end{equation}
-The bulk generator is 
-\begin{equation}
-    \mathcal{L}_{\text{bula}}=\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}\quad \text{where}\quad \mathcal{L}_{x,x+1}f(\bm{n})=\sum_{a,b=0}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\delta_{a}^{x}+\delta_{b}^{x}+\delta_{a}^{x+1}-\delta_{b}^{x+1})-f(\bm{n})\right)
-\end{equation}
-This process is dual to $(\bm{\xi}(t))_{t\geq0} $ on the enlarged configuration space $\widetilde{\Omega}=N_{0}^{N-1}\times\bigtimes_{x=1}^{L} \Omega_{x}\times N_{0}^{L-1}$ with the same $\mathcal{L}_{\text{bula}}$ and with absorbing boundaries, i.e.
-\begin{equation}
-\begin{split}
-        \widetilde{\mathcal{L}}_{\text{left}}f(\bm{\xi})&=|\alpha|\sum_{a=2}^{N}\xi_{a}^{1}\left(f(\bm{\xi}-\delta_{a}^{1}+\delta_{a}^{0}+\delta_{a}^{1})f(\bm{\xi})\right)\\\widetilde{\mathcal{L}}_{L}f(\bm{\xi})&=\sum_{i=1}^{L}\beta_{i}\sum_{a=2}^{N}\xi_{a}^{L}\left(f(\bm{\xi}-\delta_{a}^{L}+\delta_{a}^{L+1}+\delta_{a}^{L})-f(\bm{\xi})\right)
-        \end{split}
-\end{equation}
-where $0$ and $L+1$ are the extra-sites. The duality function on the chain is
-\begin{equation}\label{dualityFunctionChain}
-    D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(ò\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
-Calling $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$ starting from a configuration $\bm{n}$, and considering a generic configuration $\bm{\xi}$ of the dual process, we write the following equalities using \eqref{DualityRelation}
-\begin{equation}\label{ExptationSS}
-\begin{split}
-\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
-\\=&
-\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})
-\end{split}
-\end{equation}
-where 
-\begin{equation}\label{Pass}
-    a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=2}^{N}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
-\end{equation}
-where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}.
-Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{2,\ldots,N\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
-We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{i}<y_{i+1}$ $\forall i\in \{1,\ldots,m-1\}$ and $s_{x}\in \{2,\ldots,N\}$ $\forall i=\{2,\ldots,m\}$ is given by
-\begin{equation}
-    D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{a=1}^{m}n_{s_{a}}^{x_{a}}}{(\nu-m+1)}
-\end{equation}
-Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species.
-This expectation is computed by \eqref{ExptationSS} once the absorption probabilities $a_{i_{s_{a}}}(\widehat{\bm{\xi}})$.
-The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve.
-For example, we report here the solution for the one points correlations.
-\paragraph{One point correlations for the non-integrable case}
-We have that $\widehat{\bm{\xi}}=\delta_{s}^{x}$, then 
-\begin{equation}
-	\nu D(\eta,\delta_{s}^{x})=n_{s}^{x}
-\end{equation}
-Thus
-\begin{equation}\label{OnePtsCORR}
-\begin{split}
-	\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\frac{\alpha_{s}}{\alpha_{1}+\ldots+\alpha_{N}}\right)^{i_{s}}\left(\frac{\beta_{s}}{\beta_{1}+\ldots+\beta_{N}}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
- \end{split}
-\end{equation}
-we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries.
-This $a_{s}^{x}(1)$ fulfils the following equations
-\begin{equation}\label{gamblers-ruin}
-	\begin{cases}
-		\Delta_{x}^{L}a^{x}_{s}(1)=0\\
-		a^{1}_{s}(1)=\frac{A}{1+A}+a^{2}_{s}(1)\frac{1}{1+A}\\
-		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+B}
-		\end{cases}
-\end{equation}
-where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where, for the sake of notation, we call $\alpha_{1}+\ldots+\alpha_{N}=A$ and $\beta_{1}+\ldots+\beta_{N}=B$.
-The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain
-\begin{equation}
-\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{1}{\nu}\frac{\alpha_{s}(LB-Bx+1)+\beta_{s}(Ax+1-A)}{ABL-AB+A+B}
-\end{equation}
-\textbf{Remark}: In case $A=B=1$ we have 
-	\begin{equation}
-\langle n_{s}^{x}\rangle_{\text{stat}}=\frac{\alpha_{s}(L-x+1)+\beta_{s}x}{L+1}
-	\end{equation}
-that gives back \eqref{one-pts-corr}.  
-\end{comment}
-
-%\section{Conclusion and outlook}
-%Multispecies version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
-%Use exact solution to compute large deviation rate function extending to the multispecies case results %proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
-%Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
-%Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
-Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.
 
@@
 \section*{Appendix}
-\begin{comment}
-{\color{blue}
-\section{Oscillator realization}\label{appA}
-
- The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of ${gl}(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
-  \begin{equation}\label{creationOperators}
-	\begin{cases}
-	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
-	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
-	\end{cases}
-\end{equation}
-with commutaion relations
-\begin{equation}
-	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
-\end{equation}
-Therefore, we have that 
-\begin{equation}
-		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
-\end{equation} 
-fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
-\end{comment}
 
@@
 Therefore, \eqref{actionBDLine} follows.
-\begin{comment}
-\section{Representation}
-The approach we use to find duality relations is the Lie algebraic one.
-The main idea is to describe the infinitesimal generator (or better, its transposed, i.e.
-the Hamiltonian operator) via a proper combination of the basis of a certain Lie algebra.
-Then, duality will be found by symmetry argument.\\
-We chose the ${gl}(N)$ Lie algebra. This is compact. The abstract basis elements are denoted by $E_{a,b}$ with $a,b\in \{1,\ldots,N\}$ that obeys to the Lie bracket relations given by
-\begin{equation}
-\left[E_{ab},E_{cd}\right]=E_{ab}E_{cd}-E_{cd}E_{ab}=E_{ad}\delta_{bc}-E_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
-\end{equation}
-We define the the following representation $(\mathcal{C}^{D},\Pi)$, where $D$ is the dimension of the representation and $\Pi:{gl}(N):\to \mathcal{M}_{D\times D}$ is an homeomorfism between the Lie algebra and the space $\mathcal{M}_{D\times D}$ of $D\times D$ matrices with complex coefficients.
-For every elements $E_{ab}$ of the abstract Lie algebra, it associates $\Pi(E_{ab})=e_{ab}$ Since this Lie algebra is compact and semi-simple, we can characterize every irreducible representation by defining its own \textit{highest weight state}.
-We recall that a weight is a vector $\mu=(\mu_{0},\ldots,\mu_{N})$ with $\mu_{i}\in\mathbb{N}_{0}$ such that there exist a state $|\mu\rangle$ with the property $e_{ii}|\mu\rangle=\mu_{i}|\mu\rangle$ $\forall i=0,\ldots,N$ (where $e_{ii}$ is the Cartan element).
-Let's consider two weights $\mu$,$\nu$, then we say that $\mu$ is positive if the first non zero component is positive.
-Then, we say that $\mu>\nu$ if $\mu-\nu>0$.
-Thus, we can define the "highest weight" of a representation the $\mu_{0}$ that is bigger then all the other weights.
-As already pointed out, every irreducible representation of ${gl}(N)$ is in a one to one correspondence with its heights weight.
-That means that we can characterize the representations via the highest weight.
-A more formal definitions: $\mu^{hws}=(\mu_{1},\ldots,\mu_{N})$ with $\mu_{i}\geq \mu_{i+1}$ is the heights weight of the representation if
-\begin{equation}
-	e_{ii}|\mu^{hws}\rangle=\mu_{i}^{hws}|\mu^{hws}\rangle\qquad \text{and}\qquad e_{ij}|\mu^{hws}\rangle=0\quad \forall i<j
-\end{equation}
-The representation that we choose is characterized by the heighest weight state $|\mu^{hws}\rangle$ such that 
-\begin{equation}
-	e_{11}|\mu^{hws}\rangle=2j|\mu^{hws}\rangle\qquad \mu^{hws}=(2j,0,\ldots,0)
-\end{equation}
-The dimension of this representation is given by the combination of $N$ objects in $2j$ positions with repetition:
-\begin{equation}
-	D= \frac{(N+2j-1)!}{(2j)!(N-1)!}
-\end{equation}
-For example, in the case of spin $1/2$ (hard-core exclusion) with $N=2$ species we have dim$=\frac{(2+1-1)!}{1!(2-1)!}=2$ and in case of spin $1$, dim$=\frac{(3+2-1)!}{(2)!(2)!}=6$.\\
-The basis element of the vector space of the representation $\mathbb{C}^{D}$ are given by 
-\begin{equation}
-    |n_{1},\ldots,n_{N}\rangle\qquad \forall
-    n=(n_{1},\ldots,n_{N})
-\end{equation}
-$\forall n=(n_{1},\ldots,n_{N})\in \chi$ where $\chi:=\left\{n\;:\;\sum_{a=1}^{N}n_{a}=2j\right\}$ (let us notice that $\Omega=\xi^{|V|}$.
-This vector can be mapped in a one-to-one correspondence with the canonical basis of $\mathbb{C}^{D}$.
-By consequence, this basis vector are orthonormal, i.e.
-\begin{equation}
-    \langle q_{1},\ldots,q_{N}|_{x}|t_{1},\ldots,t_{N}\rangle_{x}=\prod_{a=1}^{N}\delta_{q_{a},t_{a}}
-\end{equation}
-
-The algebra ${gl}(N)$ is isomorphic to $su(N)$ and we have chosen a $2j$ spin representation of it.
-It is also possible to see that this representation can be written as a direct sum of representation of $su(2)$, each with representation $2j$ and each associated with a positive root.
-The generator of this $su(2)$ sub-algebras can be written by:  $J^{+}=e_{ab}$, $J^{-}=e_{ba}$, $J^{0}=1/2(e_{bb}-e_{aa})$ $\forall a,b=1,\ldots,N$.
-\\
-The explicit actions of the basis element of the algebra on the vectors of the space $\mathcal{C}^{D}$ are the following, for non Cartan and Cartan elements respectively: 
-\begin{equation}
-	\begin{cases}
-		e_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\\
-		e_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle
-	\end{cases}\qquad \forall a,b\in\{1,\ldots,N\}
-\end{equation}
-In matrix form $\forall a,b\in \{1,\ldots,N\}$
-\begin{equation}\label{matrixFormulaE}
-	\begin{split}
-	&e_{ab}=\sum_{n\in\chi}n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots n_{N}\rangle \langle n_{1},\ldots,n_{N}|
-	\end{split}
-\end{equation}
-\textbf{Reamrk}: in this algebraic setting it is more convenient to use the \textit{Bra-Ket} notation for the states of the process.
-The mapping with the vectors written in \eqref{stateSpace} is the following
-\begin{equation}
-(n_{1}^{x},\ldots,n_{N}^{x})^{T}=|n_{1},\ldots,n_{N}\rangle_{x}\qquad(n_{1}^{x},\ldots,n_{N}^{x})=\langle n_{1},\ldots,n_{N}|_{x}
-\end{equation}
-\begin{flushright}
-    $\square$
-\end{flushright}
-This Lie algebra has second Casimir element given by 
-\begin{equation}
-    C_{2}=\sum_{a,b=1}^{N}e_{ab}e_{ba}
-\end{equation}
-This element is diagonal, and its action on a generic state is the following:
-\begin{equation}
-	C_{2}=2j(2j+N)\mathbbm{1}
-\end{equation}
-where $\mathbbm{1}$ is the $D\times D$ dimensional identity matrix. \\
-By introducing the \textit{coproduct} operator \begin{equation}\begin{split}\Delta:(\mathbb{C}^{D},\Pi)&\to(\mathbb{C}^{D}\otimes \mathbb{C}^{D},\Pi\otimes \Pi) \\
- e_{ab}&\to e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}
-\end{split}
-\end{equation}
-then we can compute 
-\begin{equation}\label{coproductC2}
-	\begin{split}
-	\Delta(C_{2}&)=\sum_{a,b=0}^{N}\Delta(e_{ab})\Delta(e_{ba})
-	=
-	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}+e_{ab}\otimes \mathbbm{1}\right)\left(\mathbbm{1}\otimes e_{ba}+e_{ba}\otimes \mathbbm{1}\right)
-	\\&=
-	\sum_{a,b=0}^{N}\left(\mathbbm{1}\otimes e_{ab}e_{ba}+e_{ba}\otimes e_{ab}+e_{ab}\otimes e_{ba}+e_{ab}e_{ba}\otimes \mathbbm{1}\right)
-	\\&=
-	2\left(\sum_{a,b=0}^{N}e_{ab}\otimes e_{ba}\right)+\mathbbm{1}\otimes C_{2}+C_{2}\otimes\mathbbm{1}
-	\end{split}
-\end{equation}
-We now define the equivalent of \eqref{stateSpace} in the vector notation
- \begin{equation}
-	\Omega:=\left\{|n_{1},\ldots,n_{N}\rangle \;:\;\sum_{a=1}^{N}n_{a}=2j\right\}^{\otimes|V|}
-	\end{equation}
-where we denote 
-\begin{equation}
-|n\rangle=\bigotimes_{x\in V}	\left(|n_{1},\ldots,n_{N}\rangle_{x}\right)\in \Omega
-\end{equation}
-The Hamiltonian operator can be written in term of the basis element of the Lie algebra as
-
-\begin{equation}
-	\begin{split}
-		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
-	\end{split}
-\end{equation}
-where the edge Hamiltonian is
-\begin{equation}
-\mathcal{H}_{x,y}=\sum_{a,l=1}^{N}\left(e_{al}\otimes e_{la}-e_{ll}\otimes e_{aa}\right)
- \end{equation}
- and where the site Hamiltonian is
- \begin{equation}
-H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(e_{a,l}-e_{ll}\right)
-\end{equation}
-Moreover, by the \eqref{coproductC2} and by computing the explicit action of the diagonal part, we can write this Hamiltonian in function of the coproduct of the second Casimir
-\begin{equation}
-	H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left\{\frac{1}{2}\Delta(C_{2})-2j(4j+N)\frac{1}{2}\mathbbm{1}\otimes\mathbbm{1}\right\}+\sum_{x\in V}\Gamma_{x}\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(e_{a,l}-2j\mathbbm{1}\right)
-\end{equation}
-\end{comment}
 \bibliography{ref}

### 2023-12-05 main.tex
ll

@@
 \end{equation}
+\todo{but these are the correlations, no?}
 \begin{flushright}
@@
 \section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
-In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}.
-As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
-and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
+In this section we combine the matrix product ansatz (MPA) \cite{vanicat2017exact} and  the $gl(N)$ invariance of the process in the bulk, cf.~\eqref{symmetryH}, to exactly compute the correlations in the non-equilibrium steady state
+ for the integrable version of the multispecies stirring process on a defined on a line segment, see Section~\ref{integrableChain-duality}. 
+This allows further to determine the absorption probabilities and the probability mass-function of the non-equilibrium steady state in closed form.
 We start by recalling the formulation of the MPA  and then we explain our strategy.
+
+% In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}.
+% As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
+% and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
+% We start by recalling the formulation of the MPA  and then we explain our strategy.
 
@@
 \begin{equation}
-	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}
+	|\Psi\rangle=\frac{1}{Z_{L}} \langle \langle W|  \begin{pmatrix}
 		X_{1}\\
@@
 		X_{N}
-	\end{pmatrix}|V\rangle
+	\end{pmatrix} |V\rangle\rangle 
 \end{equation}
@@
 \begin{equation}
-	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle\dt
+	Z_{L}= \langle \langle W|  (X_{1}+\ldots +X_{N})^{L} |V\rangle\rangle \dt
 \end{equation}
@@
 \begin{equation}\label{leftBoundary}
-	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N\co
+	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  %\qquad\forall a=1,\ldots,N\co
 \end{equation}
 \begin{equation}\label{rightBoundary}
-	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-(\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N\dt
-\end{equation}
-Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
+	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right) |V\rangle\rangle =-(\alpha_{a}-\beta_{a}) |V\rangle\rangle %\qquad\forall a=1,\ldots,N\dt
+\end{equation}
+Without loss of generality, we further assume that $ \langle \langle W|  V\rangle=1$. 
 \begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
 	\begin{equation}
-		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a})\langle W|=0
+		\sum_{a=1}^{N}	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a}) \langle \langle W|  =0
 	\end{equation}
@@
 \begin{equation}\label{commLEFT2}
-	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
+	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  %\qquad\forall a=1,\ldots,N-1
 	\co \qquad 
-	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N-1
+	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle %\qquad\forall a=1,\ldots,N-1
 	\,.
@@
 \begin{equation}\label{commLEFT}
-	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|
+	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  
 	\co
@@
 \begin{equation}\label{commRIGHT}
-	\Xt_{a} |V\rangle= (\alpha_{a}-\beta_{a})|V\rangle
+	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle 
 	\co
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}}\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle \,|\bm{\tau}\rangle
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}} \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|V\rangle\rangle \,|\bm{\tau}\rangle
 \end{equation}
@@
 \begin{align}
-		Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V\rangle\dt
-\end{align}
-
-To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+		Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L} |V\rangle\rangle \dt
+\end{align}
+
+To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $ \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 |V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
@@
 \begin{align}
-	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
 	|V \rangle=
-	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle W|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
-\end{align}
-We now compute $\langle W|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  
-\begin{align}
-	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle\nonumber
+	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}} \langle \langle W|  \widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle  \dt
+\end{align}
+We now compute $ \langle \langle W|  \widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle $. For all $n\in \mathbb{N}$ we have that  
+\begin{align}
+	 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle &= \langle \langle W|  \widetilde{X}_{N}\widetilde{X}_{N}^{n-1} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle  + \langle \langle W|  \frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1} |V\rangle\rangle \nonumber
 	\\&=
-	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{(\alpha_{a}-\beta_{a})}\langle W|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right)|V\rangle\nonumber
+	 \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle +\frac{1}{(\alpha_{a}-\beta_{a})} \langle \langle W|  \widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+(\alpha_{a}-\beta_{a})(n-1)\right) |V\rangle\rangle \nonumber
 	\\&=
-	\langle W|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle\nonumber
+	 \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle +\left(n+1-1\right) \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle \nonumber
 	\\&=
-	\left(2+n-1\right)\langle W|\widetilde{X}_{N}^{n-1}|V\rangle\nonumber
+	\left(2+n-1\right) \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle \nonumber
 	\\&=
-	\frac{(1+n)!}{n!}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
+	\frac{(1+n)!}{n!} \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle 
 \end{align}
@@
 \begin{align}
-		\langle W|\widetilde{X}_{N}^{n}|V\rangle=\frac{(1+n)!}{n!}\langle W|\widetilde{X}_{N}^{n-1}|V\rangle
-\end{align}
-with $	\langle W|\widetilde{X}_{N}^{0}|V\rangle=1$. 
+		 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle =\frac{(1+n)!}{n!} \langle \langle W|  \widetilde{X}_{N}^{n-1} |V\rangle\rangle 
+\end{align}
+with $	 \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle =1$. 
 Therefore, we obtain 
 \begin{align}
-	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle W|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle W|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
-	\frac{(1+n)!}{n!}\frac{n!}{(n-1)!}\ldots \frac{3!}{2!}\frac{2!}{1!}\langle W|\widetilde{X}_{N}^{0}|V\rangle=
+	 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle &=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)} \langle \langle W|  \widetilde{X}_{N}^{n_{N}-1} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{n_{N}} |V\rangle\rangle =\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)} \langle \langle W|  \widetilde{X}_{N}^{n_{N}-2} |V\rangle\rangle \\&=
+	\frac{(1+n)!}{n!}\frac{n!}{(n-1)!}\ldots \frac{3!}{2!}\frac{2!}{1!} \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle =
 	(1+n)!\dt
@@
 \begin{equation}
-	\langle W|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
+	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|V\rangle\rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
 \end{equation}
@@
 \begin{align}
-	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{N}^{L}|V|\rangle=
+	Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L}|V|\rangle=
 	(L+1)!\dt

### 2023-12-05 main.tex
l
ll

@@
 \end{equation} 
-\todo{but these are the correlations, no?}
 \begin{flushright}
@@
 	\item In subsection~\ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
-	\item In Section~\ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$.
+	\item In Section~\ref{correlation-section} we show that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$. 
 	By exploiting a binomial formula we rewrite the correlations in terms
-	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary~\ref{Corolollary-ABS_Corr-abstract}.
+of polynomials in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary~\ref{Corolollary-ABS_Corr-abstract}.
 	For completeness, we also show that Corollary~\ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$.
+	\todo{to discuss}
 	\end{itemize}
 \subsubsection{The similarity transformations}\label{subsectionSTransf}
-Consider the matrices
-\begin{align}
-	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\co\\
-	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
-\end{align}
-We introduce
+Consider the matrix
+\begin{align}
+	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\co
+\end{align}
+and
 \begin{equation}\label{transformationV}
@@
 We introduce
+\begin{align} 
+	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
+\end{align}
+and
  \begin{equation}
@@
  \end{equation}
-whichdenotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
+which denotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
 \begin{equation}\label{S2-Whole}

### 2023-12-05 main.tex
ll

@@
 \end{align}
+
 Using $\Psi^{'}(\bm{\tau})$ in \eqref{ABS_1} we have 
@@
 \end{flushright}
+
+{\color{blue}
+\begin{remark}
+Alternatively by a direct computation we immediately find 
+\begin{equation}
+\begin{split}
+ \mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]&=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle
+ \end{split}
+\end{equation} 
+where the entries $a_i\neq N$ are at position $x_i$. Here we only  used that  we used that $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and
+\begin{equation}
+ \langle \tau |S_1=\begin{cases}
+                    \sum_{\sigma=1}^N\langle \sigma|  \quad\text{if}\quad \tau=N\\
+                    \langle \tau| \quad\text{else} 
+                   \end{cases}\,.
+\end{equation} 
+\end{remark}
+
+}
+
 \subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
 %We argue similarly as in the Section~\ref{correlation-section}. 
-We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau})= (N,\ldots,N)$. We show here that for this particular configuration
+We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
 $\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
@@
 \end{align}
+\todo{what was Omega again?}
 We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.

### 2023-12-05 main.tex
ll

@@
 \end{equation}
-Without loss of generality, we further assume that $ \langle \langle W|  V\rangle=1$. 
+Without loss of generality, we further assume that $ \langle \langle W|  V\rangle\rangle =1$. 
 \begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
@@
  The idea is summarized in the following scheme. 
- We define a sequence of similarity transformation such that 
- \begin{equation}
+ We define a sequence of local similarity transformations such that 
+ \begin{equation}\label{eq:scheme}
  	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}
@@
 As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written exactly in closed-form.
-Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e.
+Finally, reversing the transformations in \eqref{eq:scheme} we retrieve $|\Psi\rangle$, i.e.
 the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.
- The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
-Therefore, $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlations in the non-equilibrium steady state.
+ The first transformation $S_{1}$ is closely related to the duality matrix \eqref{dualityMatrix} and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}.
+The Hamiltonian $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlations in the non-equilibrium steady state.
  %The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
@@
 Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
-$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure are given by 
+$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$.
+\todo{should this not be particles or so ? Maybe we can call particles 1 to N-1 excitations....}
+Then the $m$-point correlations with respect to the non-equilibrium steady state measure are given by 
 \begin{equation}\label{exactCorrelations}
@@
 \end{equation} 
-where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $\{0\}$. Then, using \eqref{exactCorrelations}, we have
+where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $\{0\}$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have
 \begin{equation}\label{one-pts-corr}
-		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\dt
-\end{equation}
+		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\co
+\end{equation}
+\todo{here Y instead of $\tau$?}
+{\color{blue}where we defined $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
 \paragraph{Two-point correlations}
@@
 \end{equation}
+\todo{here Y instead of $\tau$?}
 \paragraph{Three-point correlations}
@@
 \end{align}
+\todo{should this all be $Y$ in the identities?}
 \begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.
@@
 The explicit expression for $|\Psi^{''}\rangle$ is determined (see \eqref{ResulsBasis}).
-	\item In subsection~\ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
+	\item In Section~\ref{subsectionSSdual}, we invert the similarity transformation $S_2$ to recover  the ground state $|\Psi^{'}\rangle$ from the explicit expression of $|\Psi^{''}\rangle$  (see \eqref{ABS}).
 	\item In Section~\ref{correlation-section} we show that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$. 
@@
 of polynomials in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary~\ref{Corolollary-ABS_Corr-abstract}.
-	For completeness, we also show that Corollary~\ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$.
-	\todo{to discuss}
+	For completeness, we also show that Corollary~\ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$ in Section~\ref{appB}.
+	\todo{added ref... What about Section 4.4.5?}
 	\end{itemize}
@@
 \end{align}
-with $	 \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle =1$. 
+with $	 \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle=	 \langle \langle W |V\rangle\rangle  =1$. 
 Therefore, we obtain 
@@
 \begin{align}
-	Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L}|V|\rangle=
+	Z_{L}&= \langle \langle W|  (X_{1}+\ldots+X_{N})^{L} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{L}|V\rangle \rangle=
 	(L+1)!\dt
@@
 Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square brackets of the above equation, that is non-vanishing only if $\sigma_{x}=\tau_{x}$.
-This implies that both the left-hand-side and the right-hand-side are either $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ ro $0$.
+This implies that both the left-hand-side and the right-hand-side are either $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ or $0$.
 On the other hand, if $\sigma_{x}=N$ we have $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}=1$, thus both sides of the equality are either $\beta_{\tau_{x}}$ or $0$.
@@
 \begin{remark}
-Alternatively by a direct computation we immediately find 
-\begin{equation}
-\begin{split}
- \mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]&=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle
- \end{split}
-\end{equation} 
-where the entries $a_i\neq N$ are at position $x_i$. Here we only  used that  we used that $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and
+Alternatively, by a direct computation we immediately verify 
+\begin{equation}
+\begin{split}
+\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle
+ =\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]
+ \end{split}
+\end{equation} 
+where the entries $a_i\neq N$ are at position $x_i$. Here we only  used  that $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and
 \begin{equation}
@@
 }
+\todo{ok?}
 

### 2023-12-05 main.tex
ll

@@
 \end{equation} 
+\todo{double check and ref to $d_x$}
 we have
@@
 \begin{remark} 
-Alternatively, by a direct computation we immediately verify 
-\begin{equation}
-\begin{split}
-\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle
- =\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]
- \end{split}
-\end{equation} 
-where the entries $a_i\neq N$ are at position $x_i$. Here we only  used  that $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and
+Without using duality but only  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
 \begin{equation}
@@
                     \langle \tau| \quad\text{else} 
-                   \end{cases}\,.
-\end{equation} 
+                   \end{cases}\,,
+\end{equation} 
+  we immediately verify 
+\begin{equation}\label{eq:EE}
+\begin{split}
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
+\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle\dt
+ \end{split}
+\end{equation} 
+Here the entries $a_i\neq N$ in \eqref{eq:EE} are at position $x_i$. 
 \end{remark}
@@
 }
-\todo{ok?}
+\todo{ok? adopt notation?}
 
 \subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
+\todo{discuss section}
 %We argue similarly as in the Section~\ref{correlation-section}. 
@@
 		\end{align}
+		\todo{can we remove q index in sum?}
 		where the notation
@@
 		\end{equation}
+		\todo{?}
 		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$.
@@
 The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$.
-In this situation we retrieve the SSEP, that was already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}.
+In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.
 We report the Hamiltonians and the similarity transformations of SEEP:
@@
 \end{equation}
+\todo{double check}
 In this case, the similarity transformations read
@@
  We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process. 
+ \todo{?}
 \paragraph{Correlations of SSEP.}
@@
 $1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$. 
+\todo{?}
 To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.

### 2023-12-05 main.tex
ll

@@
 To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $ \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-|V \rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
+|V \rangle\rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
 \begin{equation}\label{UsefulRelation}
@@
 	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V \rangle=
+	|V \rangle\rangle=
 	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}} \langle \langle W|  \widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle  \dt

### 2023-12-05 main.tex
ll

@@
 \end{equation}
-
 It follows that 

### 2023-12-05 main.tex
ll

@@
 The bulk part of the Hamiltonian is left unchanged (because it is written using the coproduct of the second Casimir, see equation \eqref{hamiltonianCasimir}) while the boundaries are given by 
-\begin{equation}
+\begin{equation}\label{eq:Hprimes}
 	H^{'}_{\text{left}}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{\text{right}}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
@@
 \begin{remark}
-	The boundary Hamiltonians $H_{\text{left}}^{'}$ and $H_{\text{right}}^{'}$ relates to the transposed of  $\widetilde{H}_{\text{left}}$ and $\widetilde{H}_{\text{right}}$, i.e.
+	The boundary Hamiltonians $H_{\text{left}}^{'}$ and $H_{\text{right}}^{'}$ in \eqref{eq:Hprimes} resemble the transposed of  $\widetilde{H}_{\text{left}}$ and $\widetilde{H}_{\text{right}}$, i.e.
 to the transposed of the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian}.
-They are obtained replacing the  extra-site bosonic creation operators $(\mathbf{a}^{+})_{a}^{0}$  (resp.
+They can be identified  when replacing the  extra-site bosonic creation operators $(\mathbf{a}^{+})_{a}^{0}$  (resp.
 $(\mathbf{a}^{+})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp.
@@
 \end{equation}
+\todo{that's a 1 right?}
 
@@
 We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations.
-For the sake of notation we denote by
-\begin{equation}
-    \begin{pmatrix}
-		X_{a}\\ 
-		X_{N}
-	\end{pmatrix}=\begin{pmatrix}
-	    X_{1}\\
-     \vdots\\
-     X_{N}
-	\end{pmatrix}\dt
-\end{equation}
+% For the sake of notation we denote by
+% \begin{equation}
+%     \begin{pmatrix}
+% 		X_{a}\\ 
+% 		X_{N}
+% 	\end{pmatrix}=\begin{pmatrix}
+% 	    X_{1}\\
+%      \vdots\\
+%      X_{N}
+% 	\end{pmatrix}\co
+% \end{equation}
 We define the transformed matrix product operators
@@
 	\begin{pmatrix}
-		\Xt_{a}\\ 
+		\Xt_{1}\\ 
+		\vdots\\
+		\Xt_{N-1}\\
 		\Xt_{N}
 	\end{pmatrix} =S\begin{pmatrix}
-		X_{a}\\X_{N}
+		X_{1}\\
+		\vdots 
+		\\
+		X_{N-1}
+		\\X_{N}
 	\end{pmatrix}=\begin{pmatrix} 
-		X_{a}-\beta_{a}(X_{1}+\ldots+X_{N})\\
+		X_{1}-\beta_{1}(X_{1}+\ldots+X_{N})\\
+		\vdots \\
+		X_{N-1}-\beta_{N-1}(X_{1}+\ldots+X_{N})\\
 				X_{1}+\ldots +X_{N}\\
@@
 \end{equation}
-We can also reverse the transformation by $S^{-1}$ and get back: 
+We can also reverse the transformation by $S^{-1}$ and get: 
 \begin{equation}\label{Xes}
-	\begin{pmatrix}
-		X_{a}\\
-		X_{N} 
-	\end{pmatrix} =S^{-1}\begin{pmatrix}
-		\widetilde{X}_{a}\\
-		\widetilde{X}_{N}
-	\end{pmatrix}=\begin{pmatrix}
-		\Xt_{a}+\beta_{a}\Xt_{N}\\ 
-		\beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
-	\end{pmatrix}\dt
-\end{equation}
+ X_{a}=	\Xt_{a}+\beta_{a}\Xt_{N}\,,\qquad
+	X_{N} = \beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
+\end{equation}
+where  $ a\in \{1,\ldots,N-1\}$.
+
 Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have
@@
 \end{equation}
-with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$. 
-Therefore, we obtain the commutation relations for $\Xt_{a}$ 
+with $\widetilde{X}_{N}= {X}_{1}+\ldots+ {X}_{N}$. 
+Therefore, using \eqref{Xes}
+we obtain the commutation relations for $\Xt_{a}$ 
 \begin{equation}\label{commutationsBula}
@@
 \end{equation}
+for $a=1,\ldots,N-1$,
 cf.~\eqref{commutationsBula2}.
@@
 \end{equation} 
+for $a=1,\ldots,N-1$,
 cf.~\eqref{commLEFT2}.
@@
 \begin{equation}\label{toDetermineTilde}
-	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}} \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega^{'}} \langle \langle W| \widetilde{X}_{\tau_{1}}\cdots \widetilde{X}_{\tau_{L}}
 	|V\rangle\rangle \,|\bm{\tau}\rangle
 \end{equation}
-where the normalization is given by 
+\todo{these do not commute. Introduced ordered product. Please check if ok}
+where
+the normalization is given by 
 \begin{align}
@@
 
-To determine the eigenvector \eqref{toDetermineTilde}, we compute the coefficient $ \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-|V \rangle\rangle$ and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
+To determine the eigenvector \eqref{toDetermineTilde} in closed form, we compute the coefficients and the normalization $Z_{L}$. Using \eqref{commutationsBula} we have
 \begin{equation}\label{UsefulRelation}
@@
 \end{equation}
-Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
+Fix  $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
 \begin{align}\label{usefulRelaton-many}
@@
 
-By taking the product over the sites $x$ from $1$ to $L$ we obtain 
-\begin{equation}
-	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt
+Using \eqref{usefulRelaton-many} we obtain
+\begin{equation}
+	\sideset{}{'}\prod_{x=1}^L\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\sideset{}{'}\prod_{x=1}^L\left(\widetilde{X}_{\tau_{x}}+(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\co
+\end{equation}
+where for convenience we introduce the ordered product
+\begin{equation}
+ \sideset{}{'}\prod_{x=1}^L \widetilde{X}_{\tau_{x}}= \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}\,.
 \end{equation} 
@@
 \begin{align}
-	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
+	 \langle \langle W| \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}
 	|V \rangle\rangle=
@@
 \begin{equation}
-	 \langle \langle W|  \prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
-	|V\rangle\rangle=(1+\sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
+	 \langle \langle W|  \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}
+	|V\rangle\rangle=(1+\textstyle \sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
 \end{equation}
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\dt
+	\left(1+\textstyle\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\dt
 \end{equation}

### 2023-12-06 main.tex
l
''
fuef2

@@
 \section{Introduction} 
-Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics.
-In a boundary-driven system, the model is put in contact with reservoirs at its {\color{red}``boundaries'' } imposing different particle densities, and a current is generated through the system.
-In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
+Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics. In a boundary-driven system, the model is put in contact with reservoirs, 
+%at its {\color{red}``boundaries'' } imposing different particle densities, 
+and a current is generated through the system. In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
  The aim of this paper is to develop the theory of stochastic duality and  study the stationary measure of certain symmetric boundary-driven {\em multispecies} particle systems with exclusion.
@@
 The boundary-driven process is mapped to a dual process with absorbing extra sites and the problem of describing the stationary state of the original system
-is simplified to the problem of computing the absorption probabilities of the dual particles. In general, however,  there is little hope to compute the absorption probabilities exactly.
-
-{\color{blue}On one hand, this absorbing duality allows to formally write the non-equilibrium steady state in a different (simpler) form.
-On the other hand, absorption probabilities are hard to find since they fulfil multilinear algebraic equation with proper boundary conditions.
-The situation simplifies when the graph reduces to a chain with two reservoirs on the boundary sites.
+is simplified to the problem of computing the absorption probabilities of the dual particles.
+
+%In general, however,  there is little hope to compute the absorption probabilities exactly.
+
+On one hand, this absorbing duality allows to write the non-equilibrium steady state in terms of these absorption probabilities and then
+one can deduce macroscopic properties. For instance this sufficed in  \cite{KMP} to prove local equilibrium for the KMP model.
+On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
+The situation simplifies for a chain with two reservoirs on the boundary sites. 
 In this context, the integrable structure of the process can be combined with duality to compute non-equilibrium steady state. 
-Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.}
-{\color{red} Say that for a  general graph with boundaries attached to any site, this is a difficult task. }
+%Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.
+%Say that for a  general graph with boundaries attached to any site, this is a difficult task. 
 % However,  for the case of integrable systems they can be computed exactly in closed-form.
-
-{\color{red} Explain here that we consider the chain with only two reservoirs at the end of the chain}
+%{\color{red} Explain here that we consider the chain with only two reservoirs at the end of the chain}
 
@@
 
-The model studied in this paper is the multispecies analogue of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
-{\color{blue}This particle system is defined on a generic connected and undirected graph.
-At each site $\nu\in \mathbb{N}$ particles of $N$ types (species) are hosted.
-There is an exclusion constraint that makes the occupancy of each site dependent on $N-1$ species only.
-Two sites do interact when there is an edge between them and this interaction consists in an swap of two different types of particles between these sites.
-Furthermore, reservoirs are attached at each site of the graph, making the system interact with external environments with fixed average particle densities.
-When the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and when $\nu=1$, the process becomes integrable (see \cite{vanicat2017exact}).}
-{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
-
-We refer to the model as the {\em  multispecies stirring process with open boundaries}.
+The model studied in this paper is the {\em  multispecies stirring process with open boundaries}, i.e.
+the multispecies analogue of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
+This particle system is defined on a generic connected and undirected graph. At each site 
+the maximal number of allowed particles is $\nu\in \mathbb{N}$.
+These particles can be of $N-1$ types (or species).
+Two sites do interact when there is an edge between them and this interaction consists in swapping the occupations of these two sites (for a precise definition of the process see Section \ref{sec1}).
+Furthermore, reservoirs are attached at each site of the graph, creating and removing particle.
+When the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and when $\nu=1$, the process becomes integrable (see \cite{vanicat2017exact}).
+%{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
+%We refer to the model as the {\em  multispecies stirring process with open boundaries}.
 %
@@
 and show that the problem of characterizing the non-equilibrium
-steady state can be reduced to the computation of the absorption probabilities similar to the singlespecies case on the line [SPOHN?] and for a general graph \cite{ frassek2020duality}. 
+steady state can be reduced to the computation of the absorption probabilities similar to the single-species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}. 
 % The duality is proved for a system whose spatial structure is described by a general graph.
@@
 % of the absorption probabilities 
-relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(n)$ invariance of the process in the bulk.
+relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(N)$ invariance of the process in the bulk.
 Finally in Section~\ref{sec5} we discuss a few extensions
 and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
-{\color{blue} In particular, a thermalized boundary-driven version of the multispecies stirring process is introduced, showing that it has an absorbing duality.
+In particular, a thermalized boundary-driven version of the multispecies stirring process is introduced, showing that it has an absorbing duality.
 Moreover, a further interaction mechanism of reaction type is added in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction}).
-Absorbing duality is proved.
-The duality function for the termalized and the reaction diffusion process turns out to be the same of the multispecies stirring process.} {\color{red} mention the results you have in appendix}.
-
+Again, an absorbing duality is proved and the duality function for the thermalized and the reaction diffusion process turns out to be the same of the multispecies stirring process.
 % In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
@@
 
-% \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
-
-%  See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.
+\bigskip
+
+{\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
+ \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
+See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
 
@@
 % {\color{red} Missing the part about non integrable model and duality.}
+
+\bigskip
 
@@
 In words, the dynamics is described as follows. Each site
-of a connected graph can host up to $\nu\in \mathbb{N}$ particles.
+of a connected graph can host a maximal number of particles called $\nu\in \mathbb{N}$ .
 The particles have a {\em type} (sometimes called {\em species} or {\em color})
-which can take $N$ values.
-Then, the dynamics has two parts: on each edge of the graph, 
-any two types are swapped at rate $1$; additionally, on each site $x$, 
-a particles of a given type (if present) is replaced with a
-particle of type $a$ at rate $\alpha_a^x >0$.
+which can take $N-1$ values.
+Then, the dynamics has two parts: 
+\begin{itemize}
+\item
+on each edge of the graph, any two types of particles are swapped at rate $1$;
+moreover a particle of any type and a hole are also swapped at rate $1$;
+\item
+on each vertex $x$ of the graph, a particle of type $a \in \{1,\ldots,N-1\}$ is created  at rate $\alpha_a^x >0$;
+additionally a particles of any type is replaced with a
+particle of type $a$ at rate $\alpha_a^x >0$ and it is removed at rate $\alpha_N^x >0$.
+\end{itemize}
 The swap dynamics taking place on the edges is of Kawasaki-type 
@@
 steady state sets in.
-
 %\noindent
@@
 %\label{hole}
-In the following we will often consider type $N$ as a distinguished type
-(called `holes'), whose number at each site is fixed by the numbers of particles 
-of the remaining $N-1$ types. 
+%In the following we will often consider type $N$ as a distinguished type
+%(called `holes'), whose number at each site is fixed by the numbers of particles 
+%of the remaining $N-1$ types. 
 % It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
@@
 % \todo{I would prefer to say this is for N=2}
-The choice of type $N$ for the distinguished type is arbitrary and does not affect
-the results. However, we shall see in Section~\ref{sectionDuality}, that
-the dual process breaks the symmetry.
-In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
-Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
+%
+%The choice of type $N$ for the distinguished type is arbitrary and does not affect
+%the results. However, we shall see in Section~\ref{sectionDuality}, that
+%the dual process breaks the symmetry.
+%In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
+%Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
+%
 %\end{remark}
-\todo{It is misleading to have to different interpretations. Like what is the number of particles per site? Another confusion is for the reservoirs/open boundaries... Is it the same on general graph?}
-{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
-Second question: I think yes. The concept of boundary is general, not only for the chain}
+%\todo{It is misleading to have to different interpretations.
+Like what is the number of particles per site?
+Another confusion is for the reservoirs/open boundaries...
+Is it the same on general graph?}
+%{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
+%Second question: I think yes. The concept of boundary is general, not only for the chain}
 
@@
 \begin{equation}\label{implicit-mass-function}
-	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}{\color{red}
-	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\right)\right]}\,.
+	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{red}
+	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\right)\right]}\,.
 \end{equation}
@@
 =&
-\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\dt
+\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}
+=
+a_{1}\}}\right\}+\nonumber\\
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{1},a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{1}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{2}\}}\right\}+\ldots+
+\nonumber\\
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots,a_{L-\ell}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{q_{k}}=a_{k}\}}\dt
 \end{align} 
@@
 \begin{equation}\label{one-pts-corr}
-		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\co
+		\langle\rho_{a_{1}}^{x_{1}}\rangle= \mathbb{E}\left[\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{(L+1)}\alpha_{a_{1}}+\frac{x_{1}}{(L+1)}\beta_{a_{1}}\co
 \end{equation}
@@
 \begin{align}
-	&\mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
+	&\mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
 	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
@@
 	 \langle \langle W|  \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}
-	|V\rangle\rangle=(1+\textstyle \sum_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
+	|V\rangle\rangle=(1+{\textstyle \sum}_{x=1}^{N}\delta_{\tau_{x},N})!\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\dt
 \end{equation}
@@
 \begin{align}
-	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\sigma\in \Omega}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
+	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
 \end{align}
@@
 \begin{align}\label{useful-InInterpretation}
-	\Psi^{'}(\bm{\tau})=&\sum_{\sigma\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
+	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
 \end{align}
@@
 		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$.
-In the last equality we have summed over all possible $\sigma\in \Omega^{'}$.
+In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$.
 Finally, using equation \eqref{interpretation-PsiP}, the result follows.

### 2023-12-06 main.tex
Boundary duality motivation
lll

@@
 When the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and when $\nu=1$, the process becomes integrable (see \cite{vanicat2017exact}).
+{\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is motivated from the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and on the maximal number of particle hosted at each site}.
 %{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
@@
 Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}
-\todo{?}
+% \todo{?}
 %Currents will arise when at least two reservoirs have different densities. 
@@
 %dual process
- has absorbing sites\todo{which else?}.
+ has absorbing sites.
 Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundaries
@@
 \begin{equation}
-    \bm{\xi}=\left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)} )\right)_{x\in V}
-\end{equation}
-\todo{OK? but this has no index $x$?}
+    \bm{\xi}=\bigotimes_{x\in V} \left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)} )\right) 
+\end{equation} 
 where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
@@
 \end{equation}
-with 
+with  the diagonal part
 \begin{equation}\label{Revmatrix}
-    R_{x}=\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+    R_{x} =\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
 \end{equation}
@@
 \end{align} 
-\todo{something wrong...} {\color{blue} [I have added the vector at site $u(x)$]}
 where we used \eqref{transpositionPropertyR}. \\
@@
 \end{align}
-\todo{what happens to $q_N$?} {\color{blue} 
+{ 
 where we used the orthogonality relation \eqref{ortho-extraSite}}. 
@@
 \end{equation}
-\todo{somehow this now has extra index for the space and everywhere else not....
-please fix} {\color{blue} We have defined the bosonic operator with the extra-site, see under equation \eqref{bosonic_2}}
+\todo{explain extra index }  
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
@@
     \delta_{\tau_{x},N}:=\begin{cases}
-        N\quad \text{if}\quad \tau_{x}=N\\
+        1\quad \text{if}\quad \tau_{x}=N\\
         0\quad \text{otherwise}
@@
 \end{equation}
-\todo{that's a 1 right?}
 
@@
 \end{equation} 
-\todo{these do not commute. Introduced ordered product. Please check if ok}
 where
@@
 	 \langle \langle W| \widetilde{X}_{\tau_{1}}\cdots  \widetilde{X}_{\tau_{L}}
-	|V \rangle\rangle=
-	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}} \langle \langle W|  \widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle  \dt
+	|V \rangle\rangle=\langle \langle W|  \widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}} |V\rangle\rangle
+	\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}   \dt
 \end{align}
@@
 \Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-=&\frac{1}{(L+1)!}\sum_{\bm{\sigma}\in \Omega^{'}}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\&\left[\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)\right]\dt
+=&\frac{1}{(L+1)!}\sum_{\bm{\sigma}\in \Omega^{'}}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\&\times\left[\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)\right]\dt
 %=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
@@
 \end{equation} 
-\todo{double check and ref to $d_x$}
+\todo{double check and ref to $d_x$ and say that R is id}
 we have

### 2023-12-07 main.tex
''

@@
 \todo{here Y instead of $\tau$?}
-{\color{blue}where we defined $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
+{\color{blue}where, for the sake of notation, we have introduced $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
 \paragraph{Two-point correlations}
@@
 	\begin{split}
-		 \mathbb{E}\left[\left(\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
+		 \mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt
 	\end{split}
@@
 \end{align}
-Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $\{0\}$ and $\{L+1\}$ and recalling that  
+We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e.
+the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $\{0\}$ and $\{L+1\}$.
+Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
+\begin{equation}
+	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
+	\end{equation} then the following holds}
 \begin{equation}
@@
 \todo{double check and ref to $d_x$ and say that R is id}
-we have
+{\color{blue}As a consequence we have that }
 \begin{equation}
@@
 
-{\color{blue}
 \begin{remark} 
@@
 
-}
 \todo{ok? adopt notation?}
-
-\subsubsection{Interpretation of $\Psi^{'}(\bm{\tau})$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
-\todo{discuss section}
-%We argue similarly as in the Section~\ref{correlation-section}. 
-We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
-$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
-\begin{align}
-	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
-\end{align}
-\todo{what was Omega again?}
-We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.
-More explicitly, this dual configuration is given by
-\begin{equation}
-	\begin{cases}
-	\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
-	\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
-\end{cases}\dt
-\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
-\begin{align}\label{useful-InInterpretation}
-	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
-\end{align}
-We observe that for any $x\in \{1,\ldots,L\}$
-\begin{equation}
-	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
-	%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
-	%	1\qquad  &\text{if}\quad \tau_{x}= N
-%	\end{cases}\dt
-\end{equation}
-Indeed, we have that 
-\begin{equation}
-	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
-			\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
-			1\qquad  &\text{if}\quad \tau_{x}= N
-			\end{cases}\dt
-\end{equation}
- Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
- 	\begin{equation}\label{interpretation-PsiP}
- 	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
- \end{equation} 
- This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.
-
- Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
- Let $\ell$ be the number of occupied sites in the configuration $\bm{\tau}$, i.e.
-$\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
-We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present.
-Finally, we call
- \begin{equation}
- 	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}\dt
- \end{equation} 
-Observe that, if $\ell=0$ then $\Omega_{\ell}^{'}(\bm{\tau})$ does coincide with the whole state space $\Omega^{'}$, while, if $\ell=L$ then $\Omega_{\ell}^{'}(\bm{\tau})$ reduces to the configuration $\bm{\tau}$.
-Denoting the marginal on $\ell$ sites of the steady state distribution by
-\begin{equation}
-	\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})
-\end{equation}
-we have that 
-\begin{align}
-	\Psi^{'}(\bm{\tau})=&\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
-\end{align} 
-It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution.
-In particular, when the configuration $\bm{\tau}$ has $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function.
-%As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
 
@@
 	H_{\text{left}}=\begin{pmatrix}
-		1-\alpha_{1}&\alpha_{1}\\
-		\alpha_{2}&1-\alpha_{2}
+		\alpha_{1}-1&\alpha_{1}\\
+		\alpha_{2}&\alpha_{2}-1
 	\end{pmatrix},\qquad H_{\text{right}}=\begin{pmatrix}
-	1-\beta_{1}&\beta_{1}\\
-	\beta_{2}&1-\beta_{2}
+	\beta_{1}-1&\beta_{1}\\
+	\beta_{2}&\beta_{2}-1
 \end{pmatrix}\dt
@@
 \end{equation}
- We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process. 
+{\color{blue}As a further check we report here the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
+the situation where the process has only one species of particles and holes.
+}
+ %We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process. 
  \todo{?}
@@
 \textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
-There are many values of $c$'s that give the same $q$, therefore we define $q$ %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
+There are many values of $c$'s that give the same $q$, therefore we define {\color{blue} $q$ labels denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
 $1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$. 
@@
 \section*{Appendix}
+\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
+We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
+$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
+\end{align}
+\todo{what was Omega again?}
+We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.
+More explicitly, this dual configuration is given by
+\begin{equation}
+	\begin{cases}
+		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
+		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
+	\end{cases}\dt
+\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
+\begin{align}\label{useful-InInterpretation}
+	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
+\end{align}
+We observe that for any $x\in \{1,\ldots,L\}$
+\begin{equation}
+	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
+		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
+		%	1\qquad  &\text{if}\quad \tau_{x}= N
+		%	\end{cases}\dt
+\end{equation}
+Indeed, we have that 
+\begin{equation}
+	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
+		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
+		1\qquad  &\text{if}\quad \tau_{x}= N
+	\end{cases}\dt
+\end{equation}
+Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
+\begin{equation}\label{interpretation-PsiP}
+	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
+\end{equation} 
+This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.
+
+Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
+Let $\ell$ be the number of occupied sites in the configuration $\bm{\tau}$, i.e.
+$\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
+We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present.
+Finally, we call
+\begin{equation}
+	\Omega_{\ell}^{'}(\bm{\tau}):=\left\{\bm{\sigma}\in \Omega^{'}\;:\; \sigma_{x_{1}}=\tau_{x_{1}},\ldots,\sigma_{x_{\ell}}=\tau_{x_{\ell}}\right\}\dt
+\end{equation} 
+Observe that, if $\ell=0$ then $\Omega_{\ell}^{'}(\bm{\tau})$ does coincide with the whole state space $\Omega^{'}$, while, if $\ell=L$ then $\Omega_{\ell}^{'}(\bm{\tau})$ reduces to the configuration $\bm{\tau}$.
+Denoting the marginal on $\ell$ sites of the steady state distribution by
+\begin{equation}
+	\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})
+\end{equation}
+we have that 
+\begin{align}
+	\Psi^{'}(\bm{\tau})=&\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]=\mathbb{E}\left[\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=\tau_{x_{k}}\}}\right]=\sum_{\bm{\sigma}\in \Omega_{\ell}^{'}(\bm{\tau})}\mu(\bm{\sigma})=\mu_{x_{1},\ldots,x_{\ell}}(\bm{\tau})\dt
+\end{align} 
+It follows that $\Psi^{'}(\bm{\tau})$ is the marginal on $\ell$ sites $x_{1},\ldots,x_{\ell}$ of the non-equilibrium steady state distribution.
+In particular, when the configuration $\bm{\tau}$ has $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function.
+%As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
 

### 2023-12-07 main.tex
ll

--- 2023-12-06 main.tex
@@
 The situation simplifies for a chain with two reservoirs on the boundary sites. 
-In this context, the integrable structure of the process can be combined with duality to compute non-equilibrium steady state. 
+In this context, the integrable structure of the process can be combined with duality.
+As shown in \cite{frassek2020eigenstates,frassek2020duality}, this approach leads to closed-form expressions for the correlations and the non-equilibrium steady state.
+
+\todo{which process do we mean here? SEP?}
 %Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.
@@
 Furthermore, reservoirs are attached at each site of the graph, creating and removing particle.
-When the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and when $\nu=1$, the process becomes integrable (see \cite{vanicat2017exact}).
+The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal  number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}.
 {\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is motivated from the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and on the maximal number of particle hosted at each site}.
@@
 \end{equation}
+\todo{is there $c_j$ and $c_k$ missing?}
 and \eqref{correlations-SSEP} follows. 

### 2023-12-08 main.tex
expectation

@@
 On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
-The situation simplifies for a chain with two reservoirs on the boundary sites. 
-In this context, the integrable structure of the process can be combined with duality.
+The situation simplifies {\color{blue} for the simple symmetric exclusion process \cite{schutzSandow} on the geometry of } a chain with two reservoirs on the boundary sites. 
+{\color{blue}In this context, the process posses an integrable structure \cite{schutzManyBody,SSEPReviewRagoucy}.
+This integrability property can be combined with duality to compute absorption probabilities}.
 As shown in \cite{frassek2020eigenstates,frassek2020duality}, this approach leads to closed-form expressions for the correlations and the non-equilibrium steady state.
@@
 We write the configurations $\bm{\xi} \in \widetilde\Omega$  as
-\begin{equation}
+\begin{equation}\label{row-dual-vectors}
     \bm{\xi}=\bigotimes_{x\in V} \left(\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)\otimes (\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)} )\right) 
@@
 \begin{equation}\label{ortho-extraSite}
-	\langle q_{1},\ldots,q_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}
+	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}
 \end{equation} }
+{\color{blue} \begin{remark}
+	In the following, with a slightly abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$.
+This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$.
+Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}.
+\end{remark}}
 The Hamiltonian of the dual process reads
@@
 In \eqref{absProbabilitiesIntegrable} the variable $t_k$ is $1$ (resp.
-$0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $\{0\}$ (resp.
-$\{L+1\}$).
+$0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $0$ (resp.
+$L+1$).
 \end{corollary}
@@
 \end{flushright} 
+{\color{blue}By using the correlations in the non-equilibrium steady state \eqref{exactCorrelations}, it is possible to determine the non-equilibrium steady probability distribution. }
     \begin{corollary}[Non-equilibrium steady state]\label{Corollary-NESS-ABS}
@@
 \end{equation}
-{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, then it is given in \eqref{exactCorrelations}.}
+{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation \eqref{exactCorrelations}.}
 \todo{Explain this expectation...}
 \end{corollary}
+{\color{blue} The quantity $\mu(\bm{\tau})$ gives the probability, under the non-equilibrium steady distribution, of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
+However, from Corollary \ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
+Therefore, to write the probability mass function $\mu$ for occupations containing holes we have to use the conservation of probability to get rid of the indicators of these holes.
+Then, equation \eqref{implicit-mass-function} is derived (for details see below the proof of Corollary \ref{Corollary-NESS-ABS}).\\
+ The expectation on the right-hand-side of \eqref{implicit-mass-function} contains only indicators of particles configurations: indeed in the first product  $\tau_{x}\neq N$ are considered, while in the second product we have $a_{k}\neq N$ for all $k\in\{1,\ldots,N\}$.
+As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary \ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
+For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\
 \textbf{Proof of Corollary~\ref{Corollary-NESS-ABS}:}
@@
 \begin{align}\label{sum}
-&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=a_{x}\}}\right)\right)\nonumber\\
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_x=a\}}\right)\right)\nonumber\\
 =&
@@
 \todo{indices are strange. Say what happens here}
-Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.{\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
+Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.
+{\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
 \begin{flushright}
@@
 \end{equation} 
-where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $\{0\}$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have
+where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $0$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have
 \begin{equation}\label{one-pts-corr}
@@
 We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e.
-the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $\{0\}$ and $\{L+1\}$.
+the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$.
 Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
@@
 \mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
-\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle\dt
- \end{split}
-\end{equation} 
-Here the entries $a_i\neq N$ in \eqref{eq:EE} are at position $x_i$. 
+\langle N,\ldots,N,\underbrace{a_1}_{x_{1}},N,\ldots,N,\underbrace{a_m}_{x_{m}},N,\ldots,N|\Psi^{'}\rangle\dt
+ \end{split}
+\end{equation} 
+{\color{blue}Here the notation means that the entries $a_k\neq N$ in \eqref{eq:EE} are at position $x_k$ for $k\in\{1,\ldots,m\}$.} 
 \end{remark}
@@
 \begin{equation}\label{Tensor-S1}
-	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\dt
+	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\dt
 \end{equation}
@@
 		\begin{align}\label{implicit-PSI-PSIp}
-			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
-			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
-			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
+			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
+			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
+			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})
 		\end{align}
 		\todo{can we remove q index in sum?}
-		where the notation
+			{\color{blue}In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{1},\ldots,a_{b}$.
+In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$, taking into account the Kronecker deltas.} Here, the notation
 		\begin{equation}\label{notation-PSI}
-			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
-		\end{equation}
-		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
-		\begin{equation}
-			\begin{cases}
-				\tau_{x}=a_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
-				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
-			\end{cases}\dt
-		\end{equation}
+			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})
+		\end{equation}
+		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites ($x\notin\{q_{1},\ldots,q_{b}\}$) the occupation $\tau_{x}$ is left unchanged.
+}
 		\todo{?}
-		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$.
-In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$.
-Finally, using equation \eqref{interpretation-PsiP}, the result follows.
+	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 
 \begin{remark}[Equilibrium case]
@@
 \subsection{The single-species case (SSEP)}
-The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$.
-In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.
+The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {\color{blue}i.e.
+when only a type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.
 We report the Hamiltonians and the similarity transformations of SEEP:
@@
 \begin{equation}
-	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{(L+1-\sum_{k=1}^{m}c_{k})!}{(L+1)!}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
+	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{(L+1-\sum_{k=1}^{m}c_{k})!}{(L+1)!}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}
 \end{equation}
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $\{0\}$ and $\{L+1\}$ respectively.
+where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $0$ and $L+1$ respectively.
 The duality function reads is \eqref{dualityElements} specified on the chain.
@@
 are the absorption probabilities for the non-integrable chain, i.e.
-the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$.
+the probabilities that $t_{a}$ particles of species $a$ are absorbed at $0$.
 Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.

### 2023-12-08 main.tex
refs

--- 2023-12-07 main.tex
@@
  \end{equation} 
- where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal.
+ where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal, we further refer the reader to \cite{Alcaraz:1992zc,2005NuPhB.711..565M,SSEPReviewRagoucy,frassek2020eigenstates} where this idea was explored for the monospecies case.
 Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} simplify significantly.

### 2023-12-08 main.tex
ll

@@
 \usepackage{subcaption} 
+\usepackage[numbers,sort]{natbib}
 
@@
 The situation simplifies {\color{blue} for the simple symmetric exclusion process \cite{schutzSandow} on the geometry of } a chain with two reservoirs on the boundary sites. 
-{\color{blue}In this context, the process posses an integrable structure \cite{schutzManyBody,SSEPReviewRagoucy}.
-This integrability property can be combined with duality to compute absorption probabilities}.
-As shown in \cite{frassek2020eigenstates,frassek2020duality}, this approach leads to closed-form expressions for the correlations and the non-equilibrium steady state.
-
-\todo{which process do we mean here? SEP?}
+% {\color{blue}In this context, the process possesses an integrable structure, see e.g. \cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews. 
+% 
+% }
+
 %Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.
@@
 For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
-One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain \cite{schutzManyBody,SSEPReviewRagoucy}.
+One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain, see e.g.
+\cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews.
+.
+%
+This integrability property can be combined with duality and leads to closed-form expressions for the correlations and the non-equilibrium steady state, as shown in \cite{frassek2020eigenstates,frassek2020duality}.
+
+\todo{moved down this last paragraph. all good?}
 

### 2023-12-08 main.tex
aa

@@
 This integrability property can be combined with duality and leads to closed-form expressions for the correlations and the non-equilibrium steady state, as shown in \cite{frassek2020eigenstates,frassek2020duality}.
+% by extending the previous results of \cite{frassek2020eigenstates}.
 
@@
 The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal  number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}.
-{\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is motivated from the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and on the maximal number of particle hosted at each site}.
+{\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and on the maximal number of particle hosted at each site}.
 %{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }

### 2023-12-08 main.tex
in progress

@@
 \cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews.
-.
 %
@@
 This particle system is defined on a generic connected and undirected graph. At each site 
-the maximal number of allowed particles is $\nu\in \mathbb{N}$.
+the maximal number of allowed particles {\color{blue}(also called \textit{maximal occupancy})} is $\nu\in \mathbb{N}$.
 These particles can be of $N-1$ types (or species).
@@
 {\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
- \cite{schutz2017kardar, vanicat2017exact, crampe2016integrable, finn2018matrix, floreani2022switching, casini2022uphill, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
+ \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, floreani2022switching, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
 See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$.
-On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$.
+At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}.
 Then, the configuration space of the process on the graph $G$ is
@@
 with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-Since the maximal occupancy at each site is $\nu=1$,\todo{but is it at max 1?
+Since the {\color{blue} maximal occupancy at each site is $\nu=1$},\todo{but is it at max 1?
 I do not understand what we call the stirring process....}  the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
@@
 \subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
-Here we consider the chain defined in Section~\ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
+Here we consider the chain defined in Section~\ref{subsection-description-process-LINE} with the hard-core constrain {\color{blue} (at most one particle per site)}, i.e. $\nu=1$. 
 We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
@@
 \end{corollary}
-{\color{blue} The quantity $\mu(\bm{\tau})$ gives the probability, under the non-equilibrium steady distribution, of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
+{\color{blue} The quantity $\mu(\bm{\tau})$ is the probability, under the non-equilibrium steady distribution, of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
 However, from Corollary \ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
@@
 \begin{remark}\label{Remark-extension-graph-nu}
-	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for higher maximal occupancies $\nu >1$.
+	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for {\color{blue} higher maximal number of particles allowed at each site}, that is for $\nu >1$.
 	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
-	Thus we chose to present them in such a context. For the chain with higher maximal occupancies $\nu >1$ see Section~\ref{Subsection-ss-nonI}.
+	Thus we chose to present them in such a context. For the chain with {\color{blue} more than one particle allowed at each site} $\nu >1$ see Section~\ref{Subsection-ss-nonI}.
 \end{remark}
@@
 \todo{double check}
-In this case, the similarity transformations read
+where we assume that $(\alpha_{1}+\alpha_{2})=(\beta_{1}+\beta_{2})=1$. In this case, the similarity transformations read
 \begin{equation}
@@
 	0&1
+\end{pmatrix},\qquad \mathcal{S}=\mathcal{S}_{2}\mathcal{S}_{1}=\begin{pmatrix}
+1-\beta_{1}&-\beta_{1}\\
+1&1
 \end{pmatrix}\dt
@@
 \end{equation}
-{\color{blue}As a further check we report here the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
-the situation where the process has only one species of particles and holes.
+{\color{blue}As a further check we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
+the situation where the process has only one species of particles and holes, with maximal occupancy $\nu=1$.
 }
@@
 In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can host $\nu\geq 1$ particles, whose type is chosen among the $N$ available ones.
+Each site can {\color{blue} host at most $\nu\geq 1$ particles per site}, whose type is chosen among the $N$ available ones.
 The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
@@
 \end{equation}
-where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal occupancy $\nu$. 
+where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal number of particle per site $\nu$. 
 Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state.
@@
 \begin{align}
-	\nu_{TH}(r|\epsilon):&=\mathbb{P}\left(n^{x}=r|n^{x}+n^{x+1}=\epsilon\right)\nonumber
+	\mu_{TH}(r|\epsilon):&=\mathbb{P}\left(n^{x}=r|n^{x}+n^{x+1}=\epsilon\right)\nonumber
 	\\&
@@
 	\begin{split}
-\nu_{TH}(r|\epsilon)&=\frac{\mathbb{P}\left(\left\{n^{x}=r\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\epsilon\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}=\frac{\mathbb{P}\left(n^{x}=r\right)\,\mathbb{P}\left(n^{x+1}=\epsilon-r\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}\dt
+\mu_{TH}(r|\epsilon)&=\frac{\mathbb{P}\left(\left\{n^{x}=r\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\epsilon\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}=\frac{\mathbb{P}\left(n^{x}=r\right)\,\mathbb{P}\left(n^{x+1}=\epsilon-r\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}\dt
 	\end{split}
@@
 	\begin{split}
-	\nu_{TH}(r|\epsilon)=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
+	\mu_{TH}(r|\epsilon)=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
 	\end{split}
@@
 	\\&
-	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
+	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\mu_{TH}(\bm{r}|\bm{\epsilon})
 	\end{split}
@@
 %\end{equation}
-In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ ($L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters.
+In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\mu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ ($L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters.
 \subsubsection{The dual thermalized process}\label{subsection-dualTHM}

### 2023-12-11 main.tex
ll

@@
 
-\todo{moved down this last paragraph. all good?}
+% \todo{moved down this last paragraph. all good?}
 
@@
 %The  paper is organized as follows.
-\subsection*{Organization of the paper}
+% \subsubsection*{Organization of the paper}
+\paragraph{Organization of the paper}
 In Section~\ref{sec1} we define the open multispecies stirring
@@
 \end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$.
-Since the {\color{blue} maximal occupancy at each site is $\nu=1$},\todo{but is it at max 1?
-I do not understand what we call the stirring process....}  the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. Since the {\color{blue} maximal occupancy at each site is $\nu=1$},
+% \todo{but is it at max 1? I do not understand what we call the stirring process....}  
+the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by 
 \begin{equation}\label{notation-change-relation}
@@
 % $$} 
-\todo{removed subindex $a_x$ here}
+% \todo{removed subindex $a_x$ here}
 where in the last equality we exploited the fact that 
@@
 \end{align} 
-\todo{indices are strange. Say what happens here}
+% \todo{indices are strange. Say what happens here}
 Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.

### 2023-12-11 main.tex
''

@@
 		reversibility holds. 
-		%This is slightly more general than \eqref{reversibilityCondition}.
 		 In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites
@@
 \end{equation} }
-{\color{blue} \begin{remark}
-	In the following, with a slightly abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$.
+{\color{blue} \begin{remark}\label{reamrk-extraSite}
+	In the following, with a slight abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$.
 This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$.
-Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}.
+Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which the components $\xi_{a}^{u(x)}$ denotes the number of dual particles of type $a$ at site $u(x)$.
 \end{remark}}
@@
 \end{equation}
+{\color{blue}With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, in equation \eqref{siteHadamardII}, we still denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$.}
 \todo{explain extra index }  
@@
 \end{equation} 
-where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $0$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have
+where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed {\color{blue}at site $0$}.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have
 \begin{equation}\label{one-pts-corr}
@@
 \end{equation}
-\todo{here Y instead of $\tau$?}
+\todo{here Y instead of $\tau$? [DONE]}
 {\color{blue}where, for the sake of notation, we have introduced $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
@@
 \end{equation}
-\todo{here Y instead of $\tau$?}
+\todo{here Y instead of $\tau$? [DONE]}
 \paragraph{Three-point correlations}
@@
 \end{align}
-\todo{should this all be $Y$ in the identities?}
+\todo{should this all be $Y$ in the identities?[DONE]}
 \begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.
@@
 	For completeness, we also show that Corollary~\ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$ in Section~\ref{appB}.
-	\todo{added ref... What about Section 4.4.5?}
+	\todo{added ref... What about Section 4.4.5?[PREVIOUS SECTION 4.4.5 NOW MOVED IN THE APPENDIX A]}
 	\end{itemize}
@@
 	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
-	\end{equation} then the following holds}
+	\end{equation} then, considering equation \eqref{transformationV}, the following holds}
 \begin{equation}
@@
 \end{equation} 
-\todo{double check and ref to $d_x$ and say that R is id}
+\todo{double check and ref to $d_x$ and say that R is id [DONE]}
 {\color{blue}As a consequence we have that }
@@
 		\end{align}
-		\todo{can we remove q index in sum?}
+		\todo{can we remove q index in sum?[SUB-INDICES q REMOVED]}
 			{\color{blue}In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{1},\ldots,a_{b}$.
@@
 }
-		\todo{?}
+		\todo{?[EXPLAINED]}
 	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 
@@
 The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {\color{blue}i.e.
-when only a type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.
+when only one type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.
 We report the Hamiltonians and the similarity transformations of SEEP:
@@
 \end{equation}
-\todo{double check}
+\todo{double check [DONE]}
 where we assume that $(\alpha_{1}+\alpha_{2})=(\beta_{1}+\beta_{2})=1$. In this case, the similarity transformations read
@@
  %We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process. 
- \todo{?}
+ \todo{? [SENTENCE REWRITTEN]}
 \paragraph{Correlations of SSEP.}
@@
 $1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$. 
-\todo{?}
+\todo{?[BLUE SENTENCE REWRITTEN]}
 To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
@@
 \end{equation}
-\todo{is there $c_j$ and $c_k$ missing?}
+\todo{is there $c_j$ and $c_k$ missing?[DONE]}
 and \eqref{correlations-SSEP} follows. 
@@
 \end{align}
-\todo{what was Omega again?}
+\todo{what was Omega again?[DONE]}
 We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.

### 2023-12-11 main.tex
Upper-Lower case indices

@@
 At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}.
-Then, the configuration space of the process on the graph $G$ is
+{\color{blue} In the following we introduce the indices denoted by lowercase letters $a,b,c,d,k\in \{1,\ldots,N-1\}$ when only particles are taken into account.
+Moreover, we introduce the indices denoted by uppercase letters $A,B,C,D,K\in\{1,\ldots,N\}$ when we also consider the hole, that we recall is denoted by $N$.
+The link between the two indices is given by
+\begin{equation}
+	a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad A=(a,N)
+	\end{equation} 
+and the same for the other letters.} Then, the configuration space of the process on the graph $G$ is 
 \begin{equation}\label{stateSpace}
@@
 \begin{equation}
-\Omega_{x}:=\left\{n^x=(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}\,.
-\end{equation}
-We denote a particle configuration on the graph as $\bm{n}\in \Omega$, where $\bm{n}=(n_{a}^{x})_{x\in V,\,a\in\{1,\ldots,N\}}$.
+\Omega_{x}:=\left\{n^x=(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{A=1}^{N}n_{A}^{x}=\twoj\right\}\,.
+\end{equation}
+We denote a particle configuration on the graph as $\bm{n}\in \Omega$, where $\bm{n}=(n_{A}^{x})_{x\in V,\,A\in\{1,\ldots,N\}}$.
 The infinitesimal generator of the process reads
@@
 \begin{equation}\label{edgeGenerator}
-\mathcal{L}_{x,y}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left[f(\bm{n}-\bm{\delta}^{x}_{a}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right]\co
+\mathcal{L}_{x,y}f(\bm{n})=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{y}\left[f(\bm{n}-\bm{\delta}^{x}_{A}+\bm{\delta}_{B}^{x}+\bm{\delta}_{A}^{y}-\bm{\delta}_{B}^{y})-f(\bm{n})\right]\co
 \end{equation}
 \begin{equation}\label{siteGenerator}
-    \mathcal{L}_{x}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left[f(\bm{n}+\bm{\delta}_{a}^{x}-\bm{\delta}_{b}^{x})-f(\bm{n})\right]\co
+    \mathcal{L}_{x}f(\bm{n})=\sum_{A,B=1}^{N}\alpha_{A}^{x}n_{B}^{x}\left[f(\bm{n}+\bm{\delta}_{A}^{x}-\bm{\delta}_{B}^{x})-f(\bm{n})\right]\co
 \end{equation}
@@
 \begin{equation}
-(\bm{\delta}_{a}^{x})^{y}_{b}=\begin{cases}
-1\qquad &\text{if}\quad y=x,\;b=a\;,\\
+(\bm{\delta}_{A}^{x})^{y}_{B}=\begin{cases}
+1\qquad &\text{if}\quad y=x,\;B=A\;,\\
 0\qquad &\text{otherwise}\dt
@@
 Thus the dynamics consists in an exchange of particles between connected vertices at Poissonian times. 
-This means that on the edge $(x,y)\in \mathcal{E}$  a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$. 
-Moreover, each vertex  exchanges particles with the external environment (reservoirs). 
-Namely, on each site $x\in V$  a particle of type $b$ is replaced with a particle of type $a$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$. 
+This means that on the edge $(x,y)\in \mathcal{E}$  a particle {\color{blue}or a hole} of type $A$ at site $x$ is exchanged with a particle {\color{blue}or a hole} of type $B$ at site $y$ at rate $\omega_{x,y}n_{A}^{x}n_{B}^{y}$.
+{\color{blue} The transitions where an hole is exchanged by a particle, can be interpreted as \textit{purely diffusive}.}
+Moreover, each vertex  exchanges particles {\color{blue} or holes} with the external environment (reservoirs). 
+Namely, on each site $x\in V$  a particle {\color{blue} or a hole} of type $B$ is replaced with a particle {\color{blue} or a hole} of type $A$ at rate $\Gamma_{x}\alpha_{A}^{x}n_{B}^{x}$.
+{\color{blue}The transitions where the a particle is replaced by a hole can be interpreted as a removal/injection of particles.}
 %
@@
 $$
-is the density of species $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 
-\begin{equation}
-\mu_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\prod_{a=1}^{N}\rho_{a}^{n_{a}^{x}}\,.
+is the density of species $a$ and we used the notation $|\alpha|=\sum_{A=1}^{N}\alpha_{A}$. Explicitly, 
+\begin{equation}
+\mu_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{A=1}^{N}n_{A}^{x}!}\prod_{A=1}^{N}\rho_{A}^{n_{A}^{x}}\,.
 \end{equation}
@@
 \end{equation}
-and  $|\alpha^x|=\sum_{a=1}^{N}\alpha_{a}^x$.
+and  $|\alpha^x|=\sum_{A=1}^{N}\alpha_{A}^x$.
 {\color{blue} As a consequence, particles are injected and removed in the graph with different rates.
-When, for any $a\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{a}^{x}\neq  \rho_{a}^{y}$, a  non-zero current sets in, breaking the reversibility.
+When, for any $A\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{A}^{x}\neq  \rho_{A}^{y}$, a  non-zero current sets in, breaking the reversibility.
 Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}
@@
 
-Consider the Lie algebra ${gl}(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
+Consider the Lie algebra ${gl}(N)$ with generators denoted by $\EE_{AB}$ with $A,B\in \{1,\ldots,N\}$ and commutation relations
 \begin{equation}\label{eq:comgl}
-\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}\,.
+\left[\EE_{AB},\EE_{CD}\right]=\EE_{AD}\delta_{CB}-\EE_{CB}\delta_{AD}\qquad \forall A,B\in \{1,\ldots,N\}\,.
 \end{equation}
@@
 \end{equation} 
-The generators of the symmetric representations will be denoted by $E_{ab}$.
+The generators of the symmetric representations will be denoted by $E_{AB}$.
 A basis of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
 \begin{equation}
-  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{such that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
+  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{A}\in\mathbb{N}_{0}\quad \text{such that}\quad \sum_{A=1}^{N}n_{A}=\nu\,.
 \end{equation}
@@
 \begin{equation}\label{ortho}
-   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{m_{a},n_{a}}\co
-\end{equation}
-where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle=|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{a},n_{a}}$ is the Kronecker delta.
+   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{A=1}^{N}\delta_{m_{A},n_{A}}\co
+\end{equation}
+where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m\rangle=|m_{1},\ldots,m_{N}\rangle$ and $\delta_{m_{A},n_{A}}$ is the Kronecker delta.
 
@@
 	\begin{cases}
-		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\qquad\qquad a\neq b\\[0.1cm]
-		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle\dt
+		E_{AB}|n_{1},\ldots,n_{A},\ldots,n_{B},\ldots,n_{N}\rangle =n_{B}|n_{1},\ldots,n_{A}+1,\ldots,n_{B}-1,\ldots,n_{N}\rangle\qquad\qquad A\neq B\\[0.1cm]
+		E_{AA}|n_{1},\ldots,n_{A},\ldots,n_{N}\rangle = n_{A} |n_{1},\ldots,n_{A},\ldots,n_{N}\rangle\dt
 	\end{cases}
@@
 \begin{equation}
-    \langle {\bm{n}}|{\bm{m}}\rangle =\prod_{x\in V}\prod_{a=1}^N\delta_{n^x_a,m^{x}_a}\,.
+    \langle {\bm{n}}|{\bm{m}}\rangle =\prod_{x\in V}\prod_{A=1}^N\delta_{n^x_{A},m^{x}_{A}}\,.
 \end{equation}
@@
 \begin{equation}\label{edgeHamiltonian}
-\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
+\mathcal{H}_{x,y}=\sum_{A,B=1}^{N}\Big(E_{AB}^{x} E_{BA}^{y}-E_{BB}^{x} E_{AA}^{y}\Big)
  \end{equation}
@@
  \begin{equation}\label{siteHamiltonian}
-H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
+H_{x}=\sum_{A,B=1}^{N}\alpha_{A}^{x}\left(E_{AB}^{x}-E_{BB}^{x}\right)
 \end{equation}
@@
 \begin{equation}\label{secondCasimir}
-    C=\sum_{a,b=1}^{N}E_{ab}E_{ba}\co
+    C=\sum_{a,b=1}^{N}E_{AB}E_{BA}\co
 \end{equation}
@@
 \begin{equation}
-E_{ab}\mapsto E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}\co
+E_{AB}\mapsto E_{AB}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{AB}\co
 \end{equation} 
@@
 \begin{equation}
-\Delta(C)=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C\otimes \mathbbm{1}+\mathbbm{1}\otimes C\,.
+\Delta(C)=\sum_{A,B=1}^{N}\Delta(E_{AB})\Delta(E_{BA})=2\sum_{A,B=1}^{N}E_{AB}\otimes E_{BA}+C\otimes \mathbbm{1}+\mathbbm{1}\otimes C\,.
 \end{equation}
@@
 The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
-For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{ab})_{a,b\in\{1,\ldots,N\}}$ obeying $(e_{ab})_{cd}=\delta_{ac}\delta_{bd}$.
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CS}=\delta_{AC}\delta_{BD}$.
 The Hamiltonian can then be written as
@@
 \begin{equation}
-	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}\,,
+	P=\sum_{A,B=1}^Ne_{AB}\otimes e_{BA}\,,
 \end{equation} 
@@
 \begin{equation}\label{notation-change-relation}
-	n_{a}^{x}=\delta_{\tau_{x},a}\dt
+	n_{A}^{x}=\delta_{\tau_{x},A}\dt
 \end{equation}
@@
 \begin{equation}\label{ratesConditions}
-	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1\;.
+	\sum_{A=1}^{N}\alpha_{A}=1,\qquad\sum_{A=1}^{N}\beta_{A}=1\;.
 \end{equation} 
@@
 \end{equation} 
-where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
+where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at site $x$, {\color{blue} while $\xi_{N}^{x}$ is interpreted as the number of holes at site $x$ of the dual process.}
+The component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
 the extra-site $u(x)$ connected to $x\in V$.
 {\color{blue} We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, i.e.
-an unbounded number of particles can be hosted at extra-site $u(x)$.
-Therefore, the occupation variable of species $N$ (the one dependent on the species $1,\ldots,N-1$) is not present}.
+an unbounded number of particles can be hosted.
+Therefore, an infinite number of holes is available at each extra-site $u(x)$.
+As a consequence, the hole occupation variable $\xi_{N}^{u(x)}$ is not considered}.
 We state the following duality result.
@@
 This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$.
-Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which the components $\xi_{a}^{u(x)}$ denotes the number of dual particles of type $a$ at site $u(x)$.
+Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which we recall that the components $\xi_{a}^{u(x)}$ denotes the number of dual particles of type $a$ at site $u(x)$.
 \end{remark}}
@@
 \begin{equation}\label{Revmatrix}
-    R_{x} =\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{a=1}^{N}n_{a}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
+    R_{x} =\sum_{n^{x}\in\Omega_{x}}\frac{\prod_{A=1}^{N}n_{A}^{x}!}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
 \end{equation}
@@
 \\
- Considering $A,B\in {gl}(N)$, the Hadamard formula reads 
+ Considering {\color{blue}$\mathcal{A},\mathcal{B}\in {gl}(N)$}, the Hadamard formula reads 
  \begin{equation}\label{HadamardFormula}
-     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
- \end{equation}
-In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra ${gl}(N)$ with $c,d\in\{1,\ldots,N\}$.
+     \exp{(-\mathcal{B})}A\exp{(\mathcal{B})}=\mathcal{A}-\left[\mathcal{B},\mathcal{A}\right]+\frac{1}{2!}\left[B\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]-\frac{1}{3!}\left[\mathcal{B},\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]\right]+\ldots
+ \end{equation}
+In the following we need the application of this with $\mathcal{B}=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $\mathcal{A}$ equal to some of the generator $E_{CD}$ of the Lie algebra ${gl}(N)$ with $C,D\in\{1,\ldots,N\}$.
 Therefore we compute
 \begin{align}
-	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-(1-\delta_{dN})E_{cN}
+	\left[\mathcal{B},\mathcal{A}\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{CD}\right]=\delta_{CN}\sum_{a=1}^{N-1}E_{aD}-(1-\delta_{DN})E_{CN}
 \end{align}
@@
 \begin{align}
-	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-(1-\delta_{dN})E_{cN}\right]\nonumber\\=&
-	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-(1-\delta_{dN})\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
-	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-(1-\delta_{dN})\delta_{cN}E_{aN}\right)\nonumber\\=&
-	-\left(\delta_{cN}(1-\delta_{dN})+(1-\delta_{dN})\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
+	\left[\mathcal{B}\left[\mathcal{B},\mathcal{A}\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{CN}\sum_{b=1}^{N-1}E_{bD}-(1-\delta_{DN})E_{CN}\right]\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(\delta_{CN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bD}\right]-(1-\delta_{DN})\left[E_{aN},E_{CN}\right]\right)\nonumber\\=&
+	\sum_{a=1}^{N-1}\left(-\delta_{CN}\delta_{aD}\sum_{b=1}^{N-1}E_{bN}-(1-\delta_{DN})\delta_{CN}E_{aN}\right)\nonumber\\=&
+	-\left(\delta_{CN}(1-\delta_{DN})+(1-\delta_{DN})\delta_{CN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
 	\\=&
-	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
-\end{align}
-From the third commutator on we always obtain zero, i.e. $[B,[B,[B,A]]]=0$. All in all we have that 
+	-2\delta_{CN}(1-\delta_{DN})\sum_{b=1}^{N-1}E_{bN}\dt
+\end{align}
+From the third commutator on we always obtain zero, i.e. $[\mathcal{B},[\mathcal{B},[\mathcal{B},\mathcal{A}]]]=0$. All in all we have that 
  \begin{align}\label{HT-BA}
- 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+(1-\delta_{dN})E_{cN}-\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
+ 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{CD}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{CD}-\delta_{CN}\sum_{a=1}^{N-1}E_{aD}+(1-\delta_{DN})E_{CN}-\delta_{CN}(1-\delta_{DN})\sum_{b=1}^{N-1}E_{bN}\dt
  \end{align}
@@
     \begin{split}
-H_{x}^{T}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)^{T}=R_{x}\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)R_{x}^{-1}\dt
+H_{x}^{T}=\sum_{A,B=1}^{N}\alpha_{A}^{x}\left(E_{AB}^{x}-E_{BB}^{x}\right)^{T}=R_{x}\sum_{A,B=1}^{N}\alpha_{A}^{x}\left(E_{BA}^{x}-E_{BB}^{x}\right)R_{x}^{-1}\dt
     \end{split}
@@
 \begin{equation}\label{intermediateTransposeSite}
-    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{a,b =1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}\dt
+    H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\sum_{A,B =1}^{N}\alpha_{A}^{x}\left(E_{B A}^{x}-E_{BB}^{x}\right)\exp{(E^{x})}\dt
 \end{equation}
@@
 %the first Casimir operator $C_{1}=
-$\sum_{a,b=1}^{N}E_{ab}$ is central for the algebra we have
+$\sum_{a,b=1}^{N}E_{AB}$ is central for the algebra we have
 
 \begin{equation}\label{HadTransfBoundary}
-\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\dt
+\exp{(-E^{x})}\sum_{A=1}^{N}\sum_{B=1}^{N}\alpha_{A}^{x}\left(E_{B A}^{x}-E_{BB}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\dt
 \end{equation}
@@
 	\begin{cases}
-		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
-		\xi_{a}^{x}=0\qquad \text{otherwise}
+		\xi_{A}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; A=a_{k}\\
+		\xi_{A}^{x}=0\qquad \text{otherwise}
 	\end{cases}\dt
@@
 As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary \ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
-For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\
+For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\ \\
 \textbf{Proof of Corollary~\ref{Corollary-NESS-ABS}:}
@@
 \begin{remark}\label{Remark-extension-graph-nu}
-	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for {\color{blue} higher maximal number of particles allowed at each site}, that is for $\nu >1$.
+	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for {\color{blue} higher maximal maximal occupancy}, that is for $\nu >1$.
 	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
@@
 	\begin{split}
-		H_{\text{left}}^{'}&=S_{1}H_{\text{left}}S_{1}^{-1}=\exp{\left(\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}
+		H_{\text{left}}^{'}&=S_{1}H_{\text{left}}S_{1}^{-1}=\exp{\left(\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}\sum_{A,B=1}^{N}\alpha_{a}\left(e_{AB}^{1}-e_{BB}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{1}\right)}
 		\\&=
-		\left\{\exp{\left(-\sum_{c=1}^{N-1}e_{cN}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ba}^{1}-e_{bb}^{1}\right)\exp{\left(\sum_{c=1}^{N-1}e_{cN}^{1}\right)}\right\}^{T}
+		\left\{\exp{\left(-\sum_{c=1}^{N-1}e_{cN}^{1}\right)}\sum_{A,B=1}^{N}\alpha_{A}\left(e_{BA}^{1}-e_{BB}^{1}\right)\exp{\left(\sum_{c=1}^{N-1}e_{cN}^{1}\right)}\right\}^{T}
 		\\&=
@@
 The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal.
-Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
+Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $\mathcal{B}=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $\mathcal{A}_{N}=e_{aN},$ and $\mathcal{A}_{a}=e_{aa}$.
 
@@
 In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can {\color{blue} host at most $\nu\geq 1$ particles per site}, whose type is chosen among the $N$ available ones.
+Each site can {\color{blue} host at most $\nu\geq 1$ particles per site, whose type is chosen among the $N-1$ available ones}.
 The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
@@
  The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case.
-The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively.
+The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.
  We denote the space of the dual process by $\widetilde{\Omega}_{L}$, i.e.
 \begin{equation}\label{dualSpace-chain}
-	\widetilde{\Omega_{L}}=\mathbb{N}_{0}^{N}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N}\dt
-\end{equation}
-In the following of this section we will denote by 
+	\widetilde{\Omega_{L}}=\mathbb{N}_{0}^{N-1}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N-1}\dt
+\end{equation}
+In the following, for $a\in \{1,\ldots,N-1\}$ of this section we will denote by 
 \begin{equation}
@@
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
- As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by types $N$ (the empty).
+ As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by the holes $N$.
 This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a})_{a\in \{1,\ldots,N\}}$ respectively.
+where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the generators \eqref{siteGenerator} acting on sites $1$ and $L$ with parameters $(\alpha_{A})_{A\in \{1,\ldots,N\}}$ and $(\beta_{A})_{A\in \{1,\ldots,N\}}$ respectively.
 The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, has generator
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $0$ and $L+1$ respectively.
+where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively.
 The duality function reads is \eqref{dualityElements} specified on the chain.
@@
 	\begin{cases}
-		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
-		\xi_{a}^{x}=0\qquad &\text{otherwise}
+		\xi_{A}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}\\
+		\xi_{A}^{x}=0\qquad &\text{otherwise}
 	\end{cases}\dt
@@
 \end{align}
-Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall a\in\{1,\ldots,N\}$ we have $r_{a}\in \{0,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints
+Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall A\in\{1,\ldots,N\}$ we have $r_{A}\in \{0,\ldots,\nu\}$ and $\epsilon_{A}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
@@
 \end{equation}
-where we denote the multinomial coefficient
+where we recall that the multinomial coefficient reads
 \begin{equation}
@@
 \subsection{Multispecies stirring process with reaction} \label{Subsection-RD}
-We define the average density occupation of species $a$ at site $x$ as
+We define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ as
 \begin{equation}
@@
 \begin{equation}
-	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)
+	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left(f(\bm{n}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-f(\bm{n})\right)
 \end{equation}
@@
 		h_{c}(\cdot):\{1,\ldots,N\}&\to\{1,\ldots,N\}\\
-		k&\to h_{c}(k)
+		A&\to h_{c}(A)
 	\end{split}
@@
 \begin{equation}
-	h_{c}(k)=\begin{cases}
-		k+c \quad &\text{if}\quad k+c< N \\
-		k+c-N+1\quad &\text{if}\quad k+c\geq N\quad \text{and}\quad k\neq N\\
-		N\quad &\text{if}\quad k=N
+	h_{c}(A)=\begin{cases}
+		A+c \quad &\text{if}\quad A+c< N \\
+		A+c-N+1\quad &\text{if}\quad A+c\geq N\quad \text{and}\quad A\neq N\\
+		N\quad &\text{if}\quad A=N
 	\end{cases}\dt
@@
 \end{equation}
-for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\nu$. 
-The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values $\rho_{a}^{\text{right}}$.
+for every $a\in\{1,\ldots,N-1\}$. Moreover, with this choice we have that $\sum_{A=1}^{N}\alpha_{A}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{A=1}^{N}\rho_{A}^{\text{left}}=\nu$. 
+The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values $\rho_{A}^{\text{right}}$.
 %\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multispecies stirring process \eqref{siteGenerator}.
@@
 \begin{equation}
-	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
+	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{A=1}^{N}n_{A}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
 \end{equation}
@@
 \begin{equation}
-	\mathcal{H}_{x,x+1}^{c}=\sum_{a,b=0}^{N}\left(E_{h_{c}(a)b}\otimes E_{h_{c}(b)a}-E_{aa}\otimes E_{bb}\right)
+	\mathcal{H}_{x,x+1}^{c}=\sum_{A,B=1}^{N}\left(E_{h_{c}(A)B}\otimes E_{h_{c}(B)A}-E_{AA}\otimes E_{BB}\right)
 \end{equation}
@@
 \begin{equation}
-	\mathcal{H}_{x,x+1}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}\otimes \mathbbm{1}-E_{aa}\otimes \mathbbm{1}\right)\dt
+	\mathcal{H}_{x,x+1}^{m}=\sum_{A,B=1}^{N}\left(E_{BA}\otimes \mathbbm{1}-E_{AA}\otimes \mathbbm{1}\right)\dt
 \end{equation}
@@
 \begin{align*}
-	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{d,\ell=1}^{N}\left(E_{h_{c}(\ell)d}^{x}\otimes E_{h_{c}(d)\ell}^{x+1} -E_{dd}^{x}\otimes E_{\ell\ell}^{x+1}\right)\right]
+	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{D,K=1}^{N}\left(E_{h_{c}(K)D}^{x}\otimes E_{h_{c}(D)K}^{x+1} -E_{DD}^{x}\otimes E_{KK}^{x+1}\right)\right]
 	\\=&
@@
 %	\\=&
-	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{h_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{h_{c}(\ell)N}^{x+1}\right)\right\}=0\dt
+	\sum_{a,b=1}^{N-1}\sum_{D,k=1}^{N}\left\{\left(E_{DN}^{x}-E_{h_{c}(k)N}^{x}\right)\otimes \left(E_{DN}^{x+1}-E_{h_{c}(K)N}^{x+1}\right)\right\}=0\dt
 \end{align*}
@@
 \begin{equation}
-	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{d,\ell=1}^{N}\left(E_{\ell a}^{x}\otimes \mathbbm{1}^{x+1}-E_{dd}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0\dt
+	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{D,K=1}^{N}\left(E_{K a}^{x}\otimes \mathbbm{1}^{x+1}-E_{DD}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0\dt
 \end{equation}

### 2023-12-11 main.tex
bib

@@
 The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}.
-{\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and on the maximal number of particle hosted at each site}.
+{\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and regardless of the maximal number of particle hosted at each site ($\nu$ can any natural number)}.\\
+{\color{blue}In this paper we concentrate our effort in studying the symmetric multispecies model.
+In literature, also multispecies asymmetric models have been introduced \cite{schutz2017kardar,crampe2016integrable, finn2018matrix} and integrability results have been proved.
+Moreover, different transition mechanism (beyond the diffusive one) have been recently studied \cite{chatterjee2023multi}.
+Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}).
+As far as we know, in these contexts integrability does not hold.}
 %{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
@@
 \mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
-\langle N,\ldots,N,\underbrace{a_1}_{x_{1}},N,\ldots,N,\underbrace{a_m}_{x_{m}},N,\ldots,N|\Psi^{'}\rangle\dt
+\langle N,\ldots,N,\underset{\uparrow}{a_1}_{x_{1}},N,\ldots,N,\underset{\uparrow}{a_m}_{x_{m}},N,\ldots,N|\Psi^{'}\rangle\dt
  \end{split}
@@
 
-\todo{ok? adopt notation?}
+\todo{ok? adopt notation?[DONE]}
 
@@
 			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
-			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})
+			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
 		\end{align}

### 2023-12-11 main.tex
''

@@
 At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}.
-{\color{blue} In the following we introduce the indices denoted by lowercase letters $a,b,c,d,k\in \{1,\ldots,N-1\}$ when only particles are taken into account.
-Moreover, we introduce the indices denoted by uppercase letters $A,B,C,D,K\in\{1,\ldots,N\}$ when we also consider the hole, that we recall is denoted by $N$.
+{\color{blue} In the following we introduce the indices denoted by lowercase letters (for instance $a,b,c,d,k\in \{1,\ldots,N-1\}$) when only particles are taken into account.
+Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D,K\in\{1,\ldots,N\}$) when we also consider the hole, that we recall is denoted by $N$.
 The link between the two indices is given by

### 2023-12-11 main.tex
^^^

@@
 {\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and regardless of the maximal number of particle hosted at each site ($\nu$ can any natural number)}.\\
-{\color{blue}In this paper we concentrate our effort in studying the symmetric multispecies model.
-In literature, also multispecies asymmetric models have been introduced \cite{schutz2017kardar,crampe2016integrable, finn2018matrix} and integrability results have been proved.
-Moreover, different transition mechanism (beyond the diffusive one) have been recently studied \cite{chatterjee2023multi}.
+{\color{blue}In this paper we concentrate our effort in studying the boundary driven symmetric multispecies model.
+In literature, also multispecies asymmetric models have been introduced \cite{schutz2017kardar} and integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}.
+Moreover, different transition mechanisms (beyond the diffusive one) have been recently studied \cite{chatterjee2023multi}.
 Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}).
-As far as we know, in these contexts integrability does not hold.}
+As far as we know, in this last context integrability does not hold.}
 %{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
@@
 \begin{equation}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)
-\end{equation}
-In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{b}^{x+1}$, when $a=d$; a contribution $n_{a}^{x}n_{d}^{x+1}$, when $b=d$. Thus we obtain 
+	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{B}^{x}+\bm{\delta}_{A}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)
+\end{equation}
+In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{B}^{x+1}$, when $A=d$; a contribution $n_{A}^{x}n_{d}^{x+1}$, when $B=d$. Thus we obtain 
 \begin{align*}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{a}^{x}n_{d}^{x+1}-\sum_{b=1}^{N}n_{d}^{x}n_{b}^{x+1}\\
+	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{bB=1}^{N}n_{d}^{x}n_{B}^{x+1}\\
 	=&\sum_{a=1}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)
-	\end{split}
-\end{equation}
-In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{\ell}^{x+1}$, when $a=d$ (here we call $\ell=h_{c}(b)$); a contribution $n_{a}^{x}n_{q}^{x+1}$, when $h_{c}(b)=d$.
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)
+	\end{split}
+\end{equation}
+In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{K}^{x+1}$, when $A=d$ (here we call $K=h_{c}(B)$); a contribution $n_{A}^{x}n_{q}^{x+1}$, when $h_{c}(B)=d$.
 Thus we obtain
 \begin{align}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a=1}^{N}n_{a}^{x}n_{b}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A=1}^{N}n_{A}^{x}n_{b}^{x+1}-\sum_{K=1}^{N}n_{d}^{x}n_{K}^{x+1}
 		\\&=
-		\sum_{k=1}^{N-1}n_{k}^{x}n_{b}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{b}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
+		\sum_{k=1}^{N-1}n_{k}^{x}n_{b}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{b}^{x+1}-\sum_{K=1}^{N-1}n_{d}^{x}n_{K}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
 		\\&=
@@
 where  we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
-Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $b\neq d$ and $b\neq N$.
+Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $B\neq d$ and $B\neq N$.
 \item \textit{Pure-mutation generator}: here we have that 
 \begin{equation}
-	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
+	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{A,B=1}^{N-1}n_{A}^{x}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{B}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{1}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
+		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{B}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,b\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{B=1\,:B\neq d}^{N}\alpha_{B}
 	\end{split}

### 2023-12-11 main.tex
''
l

@@
 {\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
- \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, floreani2022switching, casini2023density, redig2022ergodic, redig2023equilibrium, chatterjee2023multi,  franceschini2022orthogonal,floreani2023non,carinci2023open}
+ \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, chatterjee2023multi,redig2022ergodic, floreani2022switching} and \cite{casini2023density,  franceschini2022orthogonal,redig2023equilibrium,floreani2023non,carinci2023open}
 See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
@@
 %	\\=&
-	\sum_{a,b=1}^{N-1}\sum_{D,k=1}^{N}\left\{\left(E_{DN}^{x}-E_{h_{c}(k)N}^{x}\right)\otimes \left(E_{DN}^{x+1}-E_{h_{c}(K)N}^{x+1}\right)\right\}=0\dt
+	\sum_{a,b=1}^{N-1}\sum_{D,K=1}^{N}\left\{\left(E_{DN}^{x}-E_{h_{c}(K)N}^{x}\right)\otimes \left(E_{DN}^{x+1}-E_{h_{c}(K)N}^{x+1}\right)\right\}=0\dt
 \end{align*}
@@
 \begin{align*}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{bB=1}^{N}n_{d}^{x}n_{B}^{x+1}\\
+	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{B=1}^{N}n_{d}^{x}n_{B}^{x+1}\\
 	=&\sum_{a=1}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
@@
 	\begin{split}
-		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{B}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,b\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{B=1\,:B\neq d}^{N}\alpha_{B}
+		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{B}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,B\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{B=1\,:B\neq d}^{N}\alpha_{B}
 	\end{split}

### 2023-12-12 main.tex
ll

@@
 The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}.
-{\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and regardless of the maximal number of particle hosted at each site ($\nu$ can any natural number)}.\\
+{\color{blue}As we will see, this choice of the boundary reservoirs is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and  the maximal number of particle hosted at each site ($\nu$ can any natural number)}.\\
 {\color{blue}In this paper we concentrate our effort in studying the boundary driven symmetric multispecies model.
-In literature, also multispecies asymmetric models have been introduced \cite{schutz2017kardar} and integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}.
+In literature, also asymmetric multispecies  models have been introduced \cite{schutz2017kardar} and integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}.
 Moreover, different transition mechanisms (beyond the diffusive one) have been recently studied \cite{chatterjee2023multi}.
@@
 Again, an absorbing duality is proved and the duality function for the thermalized and the reaction diffusion process turns out to be the same of the multispecies stirring process.
+\todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.}
 % In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
@@
 
-{\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
- \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, chatterjee2023multi,redig2022ergodic, floreani2022switching} and \cite{casini2023density,  franceschini2022orthogonal,redig2023equilibrium,floreani2023non,carinci2023open}
-See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
+% {\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
+%  \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, chatterjee2023multi,redig2022ergodic, floreani2022switching} and \cite{casini2023density,  franceschini2022orthogonal,redig2023equilibrium,floreani2023non,carinci2023open}
+% See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
 
@@
 on each edge of the graph, any two types of particles are swapped at rate $1$;
-moreover a particle of any type and a hole are also swapped at rate $1$;
+moreover a particle of any type and a hole are also swapped at rate $1$;\todo{explain what is a hole... Maybe stress that there can be at max $\nu$ holes per site?}
 \item
@@
 {\color{blue} In the following we introduce the indices denoted by lowercase letters (for instance $a,b,c,d,k\in \{1,\ldots,N-1\}$) when only particles are taken into account.
-Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D,K\in\{1,\ldots,N\}$) when we also consider the hole, that we recall is denoted by $N$.
+Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D,K\in\{1,\ldots,N\}$) \todo{any chance we can remove index K and k?} when we also consider the hole, that we recall is denoted by $N$.
 The link between the two indices is given by

### 2023-12-12 main.tex
ss

@@
 \end{equation}
-The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with  $\lambda_i\geq \lambda_{i+1}$,  $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu\in\mathbb{N}$.
+The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with  $\lambda_A\geq \lambda_{A+1}$,  $\lambda_A\in \mathbb{N}$ and $\sum_{A=1}^N \lambda_A = \nu\in\mathbb{N}$.
 We are interested in the {\em symmetric} finite-dimensional representations with 
@@
 %where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
-with $\sum_{a=1}^{N}n_{a}^{x}=\nu$ for any $x\in V$.
+with $\sum_{A=1}^{N}n_{A}^{x}=\nu$ for any $x\in V$.
 For a fixed $x\in V$ we write $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle$.
@@
 \end{equation}
-Here $E_{ab}^{x}$ denotes the generator $E_{ab}$ in \eqref{actionE} acting non-trivially on site $x$ (and as the identity on the other sites). 
+Here $E_{AB}^{x}$ denotes the generator $E_{AB}$ in \eqref{actionE} acting non-trivially on site $x$ (and as the identity on the other sites). 
 The Hamiltonian in \eqref{OriginalHamiltonian} is stochastic and is linked to the Markov generator  by
@@
 The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
-For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CS}=\delta_{AC}\delta_{BD}$.
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$.
 The Hamiltonian can then be written as
@@
 \begin{equation}\label{transpositionPropertyR}
-(E_{ba}^{x})^{T}=R_{x}E_{ab}^{x}R_{x}^{-1}\qquad \forall x\in V\co
-\end{equation}
-that follows immediately from the definition of $E_{ab}$. 
+(E_{BA}^{x})^{T}=R_{x}E_{AB}^{x}R_{x}^{-1}\qquad \forall x\in V\co
+\end{equation}
+\todo{changed to big indices. OK?}
+that follows immediately from the definition of $E_{AB}$. 
 \paragraph{Elements of the duality matrix.}
@@
 \end{align}
-where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
+where we used the definitions of the action of $E_{AB}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
 Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.

### 2023-12-12 main.tex
ss

@@
 Therefore, it is enough to look for a symmetry of $\Delta (C)$.
-Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in {gl}(N)$ the following holds:
+Using the bilinearity of the coproduct operator and the fact that $C$ belongs to the centre of the Lie algebra, it is easy to show that for any linear combination of generators $E\in {gl}(N)$ the following holds:
 \begin{equation}
@@
 \end{equation}
-We chose 
+Let
 \begin{equation}
@@
  \begin{equation}\label{HadamardFormula}
-     \exp{(-\mathcal{B})}A\exp{(\mathcal{B})}=\mathcal{A}-\left[\mathcal{B},\mathcal{A}\right]+\frac{1}{2!}\left[B\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]-\frac{1}{3!}\left[\mathcal{B},\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]\right]+\ldots
+     \exp{(-\mathcal{B})}A\exp{(\mathcal{B})}=\mathcal{A}-\left[\mathcal{B},\mathcal{A}\right]+\frac{1}{2!}\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]-\frac{1}{3!}\left[\mathcal{B},\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]\right]+\ldots
  \end{equation}
@@
 \begin{equation}\label{transpostionPropertyFund}
-	e_{ab}^T= e_{ba}\dt
+	e_{AB}^T= e_{BA}\dt
 \end{equation}
@@
 Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
-$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then, the $m$-point correlations in the non-equilibrium steady state read
+$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then, the $m$-point correlations in the non-equilibrium steady state read\todo{this I find still confusing}
 \begin{equation}\label{NESS-expectation-ABS}

### 2023-12-12 main.tex
ss

@@
     \begin{corollary}[Non-equilibrium steady state]\label{Corollary-NESS-ABS}
-For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is given by 
+For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is fully determined by the correlations of equation \eqref{exactCorrelations} through the relation
 \begin{equation}\label{implicit-mass-function}
@@
 \end{equation}
-{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation \eqref{exactCorrelations}.}
-\todo{Explain this expectation...}
+% {\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation
+% \eqref{exactCorrelations}.}
+\todo{Are you ok with that? It is still not super clear....}
 \end{corollary}

### 2023-12-12 main.tex
ss
ll

@@
 \end{equation} 
-where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed {\color{blue}at site $0$}.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have
+where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed. Then, using \eqref{exactCorrelations}, we have
 \begin{equation}\label{one-pts-corr}
@@
 \end{equation} 
-\todo{here Y instead of $\tau$? [DONE]}
 {\color{blue}where, for the sake of notation, we have introduced $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
@@
 \end{equation} 
-\todo{here Y instead of $\tau$? [DONE]}
 \paragraph{Three-point correlations}
@@
 \end{align} 
-\todo{should this all be $Y$ in the identities?[DONE]}
 \begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.
@@
 	For completeness, we also show that Corollary~\ref{Corollary-NESS-ABS} is in turn corresponding to the transformation $|\Psi\rangle = S_{1}^{-1} |\Psi'\rangle$ in Section~\ref{appB}. 
-	\todo{added ref... What about Section 4.4.5?[PREVIOUS SECTION 4.4.5 NOW MOVED IN THE APPENDIX A]}
 	\end{itemize}
@@
 We define the transformed matrix product operators
+via $\tilde X=S X$ such that
 \begin{equation}\label{Xtildes2b}
-	\begin{pmatrix}
-		\Xt_{1}\\ 
-		\vdots\\
-		\Xt_{N-1}\\
-		\Xt_{N}
-	\end{pmatrix} =S\begin{pmatrix}
-		X_{1}\\
-		\vdots 
-		\\
-		X_{N-1}
-		\\X_{N}
-	\end{pmatrix}=\begin{pmatrix} 
-		X_{1}-\beta_{1}(X_{1}+\ldots+X_{N})\\
-		\vdots \\
-		X_{N-1}-\beta_{N-1}(X_{1}+\ldots+X_{N})\\
-				X_{1}+\ldots +X_{N}\\
-	\end{pmatrix}\dt
-\end{equation}
+ \tilde X_a=X_{a}-\beta_{a}(X_{a}+\ldots+X_{N})\,,\qquad \tilde X_N= 
+				X_{1}+\ldots +X_{N}
+\end{equation} 
+where  $ a\in \{1,\ldots,N-1\}$.
+% 
+% \begin{equation}
+% 	\begin{pmatrix}
+% 		\Xt_{1}\\ 
+% 		\vdots\\
+% 		\Xt_{N-1}\\
+% 		\Xt_{N}
+% 	\end{pmatrix} =S\begin{pmatrix}
+% 		X_{1}\\
+% 		\vdots 
+% 		\\
+% 		X_{N-1}
+% 		\\X_{N}
+% 	\end{pmatrix}=\begin{pmatrix} 
+% 		X_{1}-\beta_{1}(X_{1}+\ldots+X_{N})\\
+% 		\vdots \\
+% 		X_{N-1}-\beta_{N-1}(X_{1}+\ldots+X_{N})\\
+% 				X_{1}+\ldots +X_{N}\\
+% 	\end{pmatrix}\dt
+% \end{equation}
 We can also reverse the transformation by $S^{-1}$ and get: 
@@
  X_{a}=	\Xt_{a}+\beta_{a}\Xt_{N}\,,\qquad
-	X_{N} = \beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})
-\end{equation}
-where  $ a\in \{1,\ldots,N-1\}$.
+	X_{N} = \beta_N\Xt_{N}-(\Xt_{1}+\ldots+\Xt_{N-1})\,.
+\end{equation}
 
@@
 \end{equation} 
-for $a=1,\ldots,N-1$,
 cf.~\eqref{commutationsBula2}.
@@
 \end{equation}  
-for $a=1,\ldots,N-1$,
 cf.~\eqref{commLEFT2}.
@@
 
-\todo{ok? adopt notation?[DONE]}
-
 \subsubsection{Steady state}\label{appB}
@@
 \end{equation} 
-\todo{double check [DONE]}
 where we assume that $(\alpha_{1}+\alpha_{2})=(\beta_{1}+\beta_{2})=1$. In this case, the similarity transformations read
@@
 \end{equation} 
-\todo{is there $c_j$ and $c_k$ missing?[DONE]}
 and \eqref{correlations-SSEP} follows. 
@@
 \begin{equation}
-	\begin{cases}
-		\xi_{A}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}\\
-		\xi_{A}^{x}=0\qquad &\text{otherwise}
+	\xi_{A}^{x}=	\begin{cases}
+	\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}\\
+		 0\qquad &\text{otherwise}
 	\end{cases}\dt
@@
 	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
-	\\&
+	\\&\times
 	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\mu_{TH}(\bm{r}|\bm{\epsilon})
@@
 	\begin{split}
-		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(r,n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
+		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(r,n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&\times
 		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
@@
 	\end{equation}
+	\todo{is the last term in the product?}
 and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
@@
 \end{equation}
+\todo{Why not merge sum or is there a typo?}
 This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}
-\end{equation}
-(cf. \eqref{dualityElements}).
+	D(\bm{n},\bm{\xi})=\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\right)\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\right)\co
+\end{equation}
+cf. \eqref{dualityElements}.
 \end{proposition} 
@@
 \end{equation}
+\todo{shall we remove all site indices given that there is the tensor product?}
 \begin{flushright}
@@
 \section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
+\todo{Why do we never refer to this appendix?}
 We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
@@
 \end{align} 
-\todo{what was Omega again?[DONE]}
 We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.

### 2023-12-12 main.tex
ll

@@
 \end{equation}
-{\color{blue}As a further check we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
-the situation where the process has only one species of particles and holes, with maximal occupancy $\nu=1$.
+{\color{blue}As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
+the situation where the process has only one species of particles and holes, with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}.
 }
  %We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process.  
- \todo{? [SENTENCE REWRITTEN]}
 \paragraph{Correlations of SSEP.}

### 2023-12-12 main.tex
ll

@@
 \end{equation} 
-\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
+\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability\todo{can we just say $N=2$ as we discussed several times now} of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
 There are many values of $c$'s that give the same $q$, therefore we define {\color{blue} $q$ labels denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
@@
 \textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the colour-blind case.
-We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+\todo{can we just say $N=2$ as we discussed several times now}We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
 For each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
@@
 \paragraph{The vector $|\Psi\rangle$ for SSEP.}
-In the colour-blind case we have that 
+In the colour-blind case we have that \todo{can we just say $N=2$ as we discussed several times now}
 \begin{equation}\label{NESS-SSEP}

### 2023-12-12 main.tex
ll

@@
 \end{equation}  
-\todo{double check and ref to $d_x$ and say that R is id [DONE]}
 {\color{blue}As a consequence we have that }
@@
 		\begin{equation}\label{notation-PSI}
-			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})
-		\end{equation}
-		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites ($x\notin\{q_{1},\ldots,q_{b}\}$) the occupation $\tau_{x}$ is left unchanged.
+			\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
+		\end{equation}
+		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
 }
-		\todo{?[EXPLAINED]}
+		\todo{mention also fat $\bm{\tau}$ in this sentence somehow.}
 	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 
@@
 \label{sec5}
-In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable using integrability.  
-The aim of this section is to study the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
+In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model \todo{which model?} is exactly solvable using integrability.  
+The aim of this section is to study the process when integrability is lost.\todo{but we got duality on any graph} We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
+We provide the following extensions:
 \begin{enumerate}
@@
 We give
-	in Appendix~\ref{appendix-1pts-general} the expression for the one-point correlation.
-	\item \textit{Instantaneous thermalization} (Section~\ref{Subsection-Thermalized}): starting from the multispecies stirring dynamics, we define the thermalized process, where particle are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
+	in Appendix~\ref{appendix-1pts-general} the expression for the one-point correlation. \todo{is this on a chain?}
+	\item \textit{Instantaneous thermalization} (Section~\ref{Subsection-Thermalized}): starting from the multispecies stirring dynamics, we define the thermalized process, where particles are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): a further dynamics is added.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): a further dynamics is added\todo{a further dynamic or further dynemics are?
+Maybe explain better}.
 Particle can now change type.
-The model is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+The model \todo{which model?} is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
 Duality for the boundary driven process is also proved.
@@
 The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
-The processes considered in this section will be denoted with same name $\left(\bm{n}(t)\right)_{t\geq0}$, their generator will be specified in each subsection.
+\todo{this is said before} The processes considered in this section will be denoted with same name \todo{variables?} $\left(\bm{n}(t)\right)_{t\geq0}$, their corresponding generator  will be specified in each subsection.
 We use the notation of Section~\ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
-E.g. the state space is denoted by 
+For example, the state space is denoted by 
 \begin{equation}\label{stateSpace-Chain}
@@
 \end{equation}
- The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case.
+ The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case \todo{?}.
 The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.
@@
 \begin{equation}\label{dualSpace-chain}
-	\widetilde{\Omega_{L}}=\mathbb{N}_{0}^{N-1}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N-1}\dt
-\end{equation}
-In the following, for $a\in \{1,\ldots,N-1\}$ of this section we will denote by 
+	\widetilde{\Omega}_{L}=\mathbb{N}_{0}^{N-1}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N-1}\dt
+\end{equation}
+In the following, for $a\in \{1,\ldots,N-1\}$ of this section we will denote by \todo{?}
 \begin{equation}

### 2023-12-12 main.tex
''

@@
 and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
-In particular, a thermalized boundary-driven version of the multispecies stirring process is introduced, showing that it has an absorbing duality.
-Moreover, a further interaction mechanism of reaction type is added in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction}).
-Again, an absorbing duality is proved and the duality function for the thermalized and the reaction diffusion process turns out to be the same of the multispecies stirring process.
+{\color{blue} The first generalization, is to derive a formula, in terms of the absorption probabilities of the dual process, for the non-equilibrium steady state correlation $\nu\geq 1$, i.e.
+when more than one particle is allowed at each site.
+In this situation, integrability is lost and we cannot derive explicit formulas for these absorption probabilities.
+However, in Appendix \ref{appendix-1pts-general}, we show how to compute the one-point correlation by using the properties of a random walk.} The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process.
+Moreover, we show that it has an absorbing duality  {\color{blue}with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}).
+Finally, the third generalization is the introduction of an "ad-hoc" interaction mechanism of reaction type, in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction})}.
+{\color{blue}We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}}.
+Again, an absorbing duality is proved and the duality function turns out to be the same of the multispecies stirring process.
 \todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.}
@@
 of a connected graph can host a maximal number of particles called $\nu\in \mathbb{N}$ .
-The particles have a {\em type} (sometimes called {\em species} or {\em color})
+The particles have a {\em type} (sometimes called {\em species} or {\em colour})
 which can take $N-1$ values.
+{\color{blue}This means that at each site there are $\nu$ available places (called \textit{holes}) that can be either occupied by particles or not.
+As a consequence, each site can be totally empty (when no particles are present and thus $\nu$ holes are available), totally occupied (when $\nu$ particles, of any type, are present and thus no holes are there) or partially occupied (when some of the holes are occupied and some are available).
+These situations can be described by introducing the \textit{exclusion constraint} that tells that, at each site and at any time, the sum of the number of particles of any type and of the number of holes is $\nu$.}
+
 Then, the dynamics has two parts: 
@@
 \end{equation}
-\todo{changed to big indices. OK?}
+\todo{changed to big indices. OK?[YES]}
 that follows immediately from the definition of $E_{AB}$. 
@@
 {\color{blue}With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, in equation \eqref{siteHadamardII}, we still denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$.}
-\todo{explain extra index }  
+\todo{explain extra index [Is the explanation of the remark 4 enough?]}  
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
@@
 the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$.
-Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
-\begin{equation}
-	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
-	\end{equation} then, considering equation \eqref{transformationV}, the following holds}
+Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$, defined in \eqref{bulkElementDualityMatrix}, becomes
+\begin{equation}
+	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}\dt
+	\end{equation} Then, considering equation \eqref{transformationV}, the following holds}
 \begin{equation}
@@
 \end{equation}
+
+\todo{double check and ref to $d_x$ and say that R is id [DONE]}
 {\color{blue}As a consequence we have that }
@@
 Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
+{\color{blue}\begin{remark}
+From equation \eqref{corr-psi1}, we observe that, for any configuration $\bm{\tau}$ that has at least a particle, we interpret the coefficient $\Psi^{'}(\tau)$ of the vector $|\Psi^{'}\rangle$ as a correlation.
+However, this interpretation does not cover the case when $\bm{\tau}=(N,\ldots,N)$, i.e.
+when no particles are present in the configuration.
+In Appendix \ref{subsection-interpretationPSIp} we show that, for any configuration $\bm{\tau}\in \Omega^{'}$ we have
+\begin{equation}\label{interpretation-PsiP}
+	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
+\end{equation} 
+The above formula \eqref{interpretation-PsiP} allows to interpret these coefficients as marginals of the non-equilibrium steady distribution $\mu$.
+As a by-product, we obtain that $\Psi^{'}(N,\ldots,N)=1$, i.e.
+it is the normalization of the measure $\mu$.
+In particular, these marginal are the non-equilibrium steady state correlations as soon as the configuration $\bm{\tau}$ does contain at least a particle.
+\end{remark} }
 \begin{flushright}
@@
 \end{equation} 
-\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit indistinguishability\todo{can we just say $N=2$ as we discussed several times now} of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
+\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit {\color{blue} the fact that $N=2$, i.e.
+that each site can be either occupied by a particle or empty.}\todo{can we just say $N=2$ as we discussed several times now [DONE]} We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
 There are many values of $c$'s that give the same $q$, therefore we define {\color{blue} $q$ labels denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
@@
 \todo{?[BLUE SENTENCE REWRITTEN]}
-To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
+To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
 Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$.
@@
 where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. \\ \\
-\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the colour-blind case.
-\todo{can we just say $N=2$ as we discussed several times now}We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the {\color{blue} $N=2$ case}.
+\todo{can we just say $N=2$ as we discussed several times now [DONE]}We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
 For each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
@@
 \paragraph{The vector $|\Psi\rangle$ for SSEP.}
-In the colour-blind case we have that \todo{can we just say $N=2$ as we discussed several times now}
+In the {\color{blue} $N=2$} case we have that \todo{can we just say $N=2$ as we discussed several times now[DONE]}
 \begin{equation}\label{NESS-SSEP}
@@
 	\end{equation}
-	\todo{is the last term in the product?}
+	\todo{is the last term in the product?[Correct, I have done it also in appendix C]}
 and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
@@
 \begin{equation}
-	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{A=1}^{N}n_{A}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
-\end{equation}
-\todo{Why not merge sum or is there a typo?}
+	\Lambda_{\text{rev}}^{x}(n^{x})=\frac{\nu!}{\prod_{A=1}^{N}n_{A}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p_{N}^{n_{N}^{x}}
+\end{equation}
+\todo{Why not merge sum or is there a typo? [There was a typo]}
 This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
@@
 \begin{align*}
-	&\left[\left(\sum_{a=1}^{N-1}E_{aN}^{x}\otimes\sum_{a=1}^{N-1}E_{aN}^{x+1}\right), \sum_{D,K=1}^{N}\left(E_{h_{c}(K)D}^{x}\otimes E_{h_{c}(D)K}^{x+1} -E_{DD}^{x}\otimes E_{KK}^{x+1}\right)\right]
+	&\left[\left(\sum_{a=1}^{N-1}E_{aN}\otimes\sum_{a=1}^{N-1}E_{aN}\right), \sum_{A,B=1}^{N}\left(E_{h_{c}(B)A}\otimes E_{h_{c}(A)B} -E_{AA}\otimes E_{BB}\right)\right]
 	\\=&
@@
 %	\\=&
-	\sum_{a,b=1}^{N-1}\sum_{D,K=1}^{N}\left\{\left(E_{DN}^{x}-E_{h_{c}(K)N}^{x}\right)\otimes \left(E_{DN}^{x+1}-E_{h_{c}(K)N}^{x+1}\right)\right\}=0\dt
+	\sum_{a,b=1}^{N-1}\sum_{A,B=1}^{N}\left\{\left(E_{AN}-E_{h_{c}(B)N}\right)\otimes \left(E_{AN}-E_{h_{c}(B)N}\right)\right\}=0\dt
 \end{align*}
@@
 \begin{equation}
-	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN}^{x},\;\sum_{D,K=1}^{N}\left(E_{K a}^{x}\otimes \mathbbm{1}^{x+1}-E_{DD}^{x}\otimes \mathbbm{1}^{x+1}\right)\right]=0\dt
-\end{equation}
-\todo{shall we remove all site indices given that there is the tensor product?}
+	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN},\;\sum_{A,B=1}^{N}\left(E_{B a}\otimes \mathbbm{1}-E_{AA}\otimes \mathbbm{1}\right)\right]=0\dt
+\end{equation}
+\todo{shall we remove all site indices given that there is the tensor product?[Correct, DONE]}
 \begin{flushright}
@@
 \section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
-\todo{Why do we never refer to this appendix?}
+\todo{Why do we never refer to this appendix?[DONE, REMARK 10]}
 We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
@@
 Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
-\begin{equation}\label{interpretation-PsiP}
+\begin{equation}%\label{interpretation-PsiP}
 	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
@@
 	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.
-	\\&\nonumber
+	\\
+	\times &\nonumber
 	\left.\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)-D(\bm{n},\bm{\xi})\right\}
-	\\&
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
+	\\\times &
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\right)
 \end{align}
@@
 \begin{align}\label{pezzo1}
-	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\nonumber\\
-	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
-	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}\nonumber\\=&
-	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
-	\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\left(\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\nonumber
+	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\nonumber
+	\\
+	\times&
+	\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
+	\times	&\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}\nonumber
 	\\=&
-	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{\text{left}}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
+	\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\
+	\times& \left(\prod_{b=1}^{N-1}\left(\frac{\alpha_{b}}{|\alpha|}\right)^{r_{b}-\xi_{b}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\left(\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\nonumber
+	\\=&
+	\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
 \end{align}
@@
 \begin{align*}
-&\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{\ell}+r_{\ell}}\right)\\=&	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}
+&\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\left(\prod_{b=1}^{N-1}\left(\frac{\alpha_{b}}{\alpha_{N}}\right)^{r_{b}}\right)\left(\prod_{c=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{c}+r_{c}}\right)\\=&	\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\left(\prod_{b=1}^{N-1}\left(\frac{\alpha_{b}}{|\alpha|}\right)^{r_{b}-\xi_{b}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}
 \end{align*}
 and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We multiplying it by $\prod_{k=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{k}+r_{k}}$ and we obtain
+We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ and we obtain
 \begin{equation}\label{pezzo2}
 	\begin{split}
-		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}+\ldots+r_{N-1})+(r_{1}+\ldots+r_{N-1})}\\=&D(\bm{n},\bm{\xi})
+		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}+\ldots+r_{N-1})+(r_{1}+\ldots+r_{N-1})}\\=&D(\bm{n},\bm{\xi})
 	\end{split}
@@
 	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{B=1}^{N}n_{d}^{x}n_{B}^{x+1}\\
-	=&\sum_{a=1}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
+	=&\sum_{a=1}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{c=1}^{N-1}n_{c}^{x})n_{d}^{x+1}-\sum_{b=1}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{c=1}^{N-1}n_{c}^{x+1})\\
 	=&\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
 \end{align*} 
-where we have used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
+where we have used the fact that $n_{N}^{x}=\nu-\sum_{c=1}^{N-1}n_{c}^{x}$.
 \item \textit{Stirring-mutation generator}: for every $c\in \{1,\ldots,N-2\}$ we have 
@@
 \end{equation}
-In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{K}^{x+1}$, when $A=d$ (here we call $K=h_{c}(B)$); a contribution $n_{A}^{x}n_{q}^{x+1}$, when $h_{c}(B)=d$.
+In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{D}^{x+1}$, when $A=d$ (here we call $D=h_{c}(B)$); a contribution $n_{A}^{x}n_{h_{c}(B^{'})}^{x+1}$, where we denoted by $B^{'}\in \{1,\ldots,N\}$ the type of particle such that $h_{c}(B^{'})=d$.
+Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $h_{c}(B^{'})\neq d$ and $h_{c}(B^{'})\neq N$.
 Thus we obtain
 \begin{align}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A=1}^{N}n_{A}^{x}n_{b}^{x+1}-\sum_{K=1}^{N}n_{d}^{x}n_{K}^{x+1}
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A=1}^{N}n_{A}^{x}n_{h_{c}(B^{'})}^{x+1}-\sum_{D=1}^{N}n_{d}^{x}n_{D}^{x+1}
 		\\&=
-		\sum_{k=1}^{N-1}n_{k}^{x}n_{b}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{b}^{x+1}-\sum_{K=1}^{N-1}n_{d}^{x}n_{K}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
+		\sum_{a=1}^{N-1}n_{a}^{x}n_{h_{c}(B^{'})}^{x+1}+\left(\nu-\sum_{b=1}^{N-1}n_{h_{c}(B^{'})b}^{x}\right)n_{b}^{x+1}-\sum_{a=1}^{N-1}n_{d}^{x}n_{a}^{x+1}-n_{d}^{x}\left(\nu-\sum_{b=1}^{N-1}n_{b}^{x+1}\right)
 		\\&=
-		\nu(n_{b}^{x+1}-n_{d}^{x})
-\end{align}
-where  we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
-Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $B\neq d$ and $B\neq N$.
+		\nu(n_{h_{c}(B^{'})}^{x+1}-n_{d}^{x})
+\end{align}
+where  we used the fact that $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$. 
 \item \textit{Pure-mutation generator}: here we have that 
@@
 \end{equation}
-Using equation \eqref{boundaryParamRD}, we obtain 
+Indeed, by using equation \eqref{boundaryParamRD}, we obtain 
 \begin{align}

### 2023-12-12 main.tex
ll

@@
 	In the following, with a slight abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$.
-This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$.
-Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which we recall that the components $\xi_{a}^{u(x)}$ denotes the number of dual particles of type $a$ at site $u(x)$.
+This allows to stress that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$.
+Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which we recall that the components $\xi_{a}^{u(x)}$ denote the number of dual particles of type $a$ at site $u(x)$.
 \end{remark}}
+\todo{good, discuss}
 The Hamiltonian of the dual process reads

### 2023-12-12 main.tex
ll

@@
 \end{equation} 
-\todo{changed to big indices. OK?[YES]}
 that follows immediately from the definition of $E_{AB}$. 
@@
  \begin{equation}\label{HadamardFormula}
-     \exp{(-\mathcal{B})}A\exp{(\mathcal{B})}=\mathcal{A}-\left[\mathcal{B},\mathcal{A}\right]+\frac{1}{2!}\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]-\frac{1}{3!}\left[\mathcal{B},\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]\right]+\ldots
+     \exp{(-\mathcal{B})}\mathcal{A}\exp{(\mathcal{B})}=\mathcal{A}-\left[\mathcal{B},\mathcal{A}\right]+\frac{1}{2!}\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]-\frac{1}{3!}\left[\mathcal{B},\left[\mathcal{B},\left[\mathcal{B},\mathcal{A}\right]\right]\right]+\ldots
  \end{equation}
@@
 Therefore we compute
+\todo{discuss}
 \begin{align}
@@
 \end{equation}
-{\color{blue}With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, in equation \eqref{siteHadamardII}, we still denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$.}
+{\color{blue}With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, in equation \eqref{siteHadamardII}, we denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$
+% although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$
+.
+}
 \todo{explain extra index [Is the explanation of the remark 4 enough?]}  

### 2023-12-12 main.tex
''

@@
 		\end{equation}
-		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
+		means that, {\color{blue} given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
 }
-		\todo{mention also fat $\bm{\tau}$ in this sentence somehow.}
+		\todo{mention also fat $\bm{\tau}$ in this sentence somehow.[DONE]}
 	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 

### 2023-12-12 main.tex
ll

--- 2023-12-12 main.tex
@@
 the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$.
-Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$, defined in \eqref{bulkElementDualityMatrix}, becomes
+Recalling that {in the case $\nu=1$ the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$, defined in \eqref{bulkElementDualityMatrix}, becomes
 \begin{equation}
@@
 \begin{equation}
-	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
-\end{equation}
-
-\todo{double check and ref to $d_x$ and say that R is id [DONE]}
-{\color{blue}As a consequence we have that }
+	S_{1}^{T}=\prod_{x=1}^{L}d_{x}\dt
+\end{equation}  
+{As a consequence we have that }
 \begin{equation}
@@
 \begin{remark} 
-Without using duality but only  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
+Using  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
 \begin{equation}
@@
 \end{equation} 
-{\color{blue}Here the notation means that the entries $a_k\neq N$ in \eqref{eq:EE} are at position $x_k$ for $k\in\{1,\ldots,m\}$.} 
+{Here the notation means that the entries $a_k\neq N$ in \eqref{eq:EE} are at position $x_k$ for $k\in\{1,\ldots,m\}$.} 
 \end{remark}
@@
 		\end{align} 
-		\todo{can we remove q index in sum?[SUB-INDICES q REMOVED]}
-			{\color{blue}In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{1},\ldots,a_{b}$.
+			{In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupation variables $a_{1},\ldots,a_{b}$.
 In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$, taking into account the Kronecker deltas.} Here, the notation
@@
 		\end{equation}
-		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
+		means that, {given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
 }
-		\todo{mention also fat $\bm{\tau}$ in this sentence somehow.}
 	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 
@@
 \subsection{The single-species case (SSEP)}
-The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {\color{blue}i.e.
+The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {i.e.
 when only one type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.
@@
 \end{equation} 
-\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit {\color{blue} the fact that $N=2$, i.e.
-that each site can be either occupied by a particle or empty.}\todo{can we just say $N=2$ as we discussed several times now [DONE]} We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
-There are many values of $c$'s that give the same $q$, therefore we define {\color{blue} $q$ labels denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
+\textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit {the fact that for $N=2$  each site can be either occupied by a particle or empty.} 
+We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
+There are many values of $c$'s that give the same $q$, therefore we define {$q$ variables denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
 $1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$.  
-\todo{?[BLUE SENTENCE REWRITTEN]}
-To each of these label we associate the coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
-Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$.
+To each of these variables we associate coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
+Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$\todo{you mean the sum is q?} and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$.
 Then, we obtain
@@
 where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. \\ \\
-\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the {\color{blue} $N=2$ case}.
-\todo{can we just say $N=2$ as we discussed several times now [DONE]}We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
+\textbf{Proof of formula \eqref{psiII-SSEP}:} We specialize equation \eqref{resulEsteady} to the {$N=2$ case} and introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$.
 For each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present.
@@
 \paragraph{The vector $|\Psi\rangle$ for SSEP.}
-In the {\color{blue} $N=2$} case we have that \todo{can we just say $N=2$ as we discussed several times now[DONE]}
+In the single species case {$N=2$} we have that  
 \begin{equation}\label{NESS-SSEP}

### 2023-12-12 main.tex
ll

@@
 \subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
-Here we consider the chain defined in Section~\ref{subsection-description-process-LINE} with the hard-core constrain {\color{blue} (at most one particle per site)}, i.e. $\nu=1$. 
+Here we consider the chain defined in Section~\ref{subsection-description-process-LINE} with the hard-core constrain {(at most one particle per site)}, i.e. $\nu=1$. 
 We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
@@
 \end{flushright} 
-{\color{blue}By using the correlations in the non-equilibrium steady state \eqref{exactCorrelations}, it is possible to determine the non-equilibrium steady probability distribution. }
+{By using the correlations in the non-equilibrium steady state \eqref{exactCorrelations}, it is possible to determine the non-equilibrium steady probability distribution. }
     \begin{corollary}[Non-equilibrium steady state]\label{Corollary-NESS-ABS}
@@
 \begin{remark}\label{Remark-extension-graph-nu}
-	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for {\color{blue} higher maximal maximal occupancy}, that is for $\nu >1$.
+	The results in Corollary~\ref{Corolollary-ABS_Corr-abstract} and in Corollary~\ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and to {higher maximal occupancy}, i.e.
+$\nu >1$.
 	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
-	Thus we chose to present them in such a context. For the chain with {\color{blue} more than one particle allowed at each site} $\nu >1$ see Section~\ref{Subsection-ss-nonI}.
+	Thus we chose to present them in such a context. For the chain with {more than one particle allowed at each site} $\nu >1$ see Section~\ref{Subsection-ss-nonI}.
 \end{remark}

### 2023-12-13 main.tex
;;

@@
 \begin{equation}
-	\left[\sum_{a=1}^{N-1}E_{aN}^{x}\otimes \sum_{b=1}^{N-1}E_{bN},\;\sum_{A,B=1}^{N}\left(E_{B a}\otimes \mathbbm{1}-E_{AA}\otimes \mathbbm{1}\right)\right]=0\dt
-\end{equation}
-\todo{shall we remove all site indices given that there is the tensor product?[Correct, DONE]}
+	\left[\sum_{a=1}^{N-1}E_{aN}\otimes \sum_{b=1}^{N-1}E_{bN},\;\sum_{A,B=1}^{N}\left(E_{B a}\otimes \mathbbm{1}-E_{AA}\otimes \mathbbm{1}\right)\right]=0\dt
+\end{equation} 
 \begin{flushright}
@@
 \section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp} 
-\todo{Why do we never refer to this appendix?[DONE, REMARK 10]}
 We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
@@
 \begin{enumerate}
-	\item \textit{Stirring generator}:
-
+	\item \textit{\underline{Stirring generator}}:
+\todo{add text here}
 \begin{equation}
@@
 where we have used the fact that $n_{N}^{x}=\nu-\sum_{c=1}^{N-1}n_{c}^{x}$.
-\item \textit{Stirring-mutation generator}: for every $c\in \{1,\ldots,N-2\}$ we have 
+\item \textit{\underline{Stirring-mutation generator}}: for every $c\in \{1,\ldots,N-2\}$ we have 
 \begin{equation}
@@
 where  we used the fact that $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$. 
-\item \textit{Pure-mutation generator}: here we have that 
+\item \textit{\underline{Pure-mutation generator}}: here we have that 
 \begin{equation}

### 2023-12-13 main.tex
Some comments fixed

@@
 Again, an absorbing duality is proved and the duality function turns out to be the same of the multispecies stirring process.
-\todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.}
+\todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.[DONE, SEE BLUE TEXT]}
 % In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
@@
 on each edge of the graph, any two types of particles are swapped at rate $1$;
-moreover a particle of any type and a hole are also swapped at rate $1$;\todo{explain what is a hole... Maybe stress that there can be at max $\nu$ holes per site?}
+moreover a particle of any type and a hole are also swapped at rate $1$;\todo{explain what is a hole... Maybe stress that there can be at max $\nu$ holes per site? [DONE, SEE BLUE TEXT JUST ABOVE]}
 \item
@@
 At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}.
-{\color{blue} In the following we introduce the indices denoted by lowercase letters (for instance $a,b,c,d,k\in \{1,\ldots,N-1\}$) when only particles are taken into account.
-Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D,K\in\{1,\ldots,N\}$) \todo{any chance we can remove index K and k?} when we also consider the hole, that we recall is denoted by $N$.
+{\color{blue} In the following we introduce the indices denoted by lowercase letters (for instance $a,b,c,d\in \{1,\ldots,N-1\}$) when only particles are taken into account.
+Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D\in\{1,\ldots,N\}$) \todo{any chance we can remove index K and k?[DONE, I REMOVED THESE INDICES IN THE APPENDICES]} when we also consider the hole, that we recall is denoted by $N$.
 The link between the two indices is given by
@@
 }
-\todo{explain extra index [Is the explanation of the remark 4 enough?]}  
+\todo{explain extra index [IS THE EXPLANATION OF REMARK 4 ENOUGH?]}  
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
@@
 Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
-$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then, the $m$-point correlations in the non-equilibrium steady state read\todo{this I find still confusing}
+{\color{blue}$m$ colours denoted by $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$, chosen among the $N-1$ available species.} Then, the $m$-point correlations in the non-equilibrium steady state read\todo{this I find still confusing [WHAT ABOUT THE BLUE SENTENCE?]}
 \begin{equation}\label{NESS-expectation-ABS}
@@
 We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
-There are many values of $c$'s that give the same $q$, therefore we define {$q$ variables denoted by } %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
+There are many values of $c$'s that give the same $q$, therefore we define $q$ variables denoted by  %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
 $1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$.  
 To each of these variables we associate coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
-Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$\todo{you mean the sum is q?} and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$.
-Then, we obtain
+Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ {\color{blue} (by the summation $\textstyle{\sum_{k=1}^{m}}c_{x_{k}}=q$)} \todo{you mean the sum is q?[FIXED]} and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$ {\color{blue} as explained.} Then, we obtain
 	\begin{equation}
@@
 	\end{equation}
-	\todo{is the last term in the product?[Correct, I have done it also in appendix C]}
+	\todo{is the last term in the product?[CORRECT, I HAVE DONE IT ALSO IN APPENDIX C]}
 and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
@@
 \end{equation}
-\todo{Why not merge sum or is there a typo? [There was a typo]}
+\todo{Why not merge sum or is there a typo? [FIXED,THERE WAS A TYPO]}
 This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
@@
 \begin{enumerate}
-	\item \textit{\underline{Stirring generator}}:
+	\item \textit{\underline{Stirring generator}}: {\color{blue}this is the edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$).
+As already pointed out, in this nearest neighbour chain, its action consists in exchanging the particles or the holes and the particles of two adjacent sites.
+Here we show that its action on the occupation variable of any species gives the discrete gradient of the occupation variable itself.
+Indeed, we have that }
 \todo{add text here}

### 2023-12-13 main.tex
''
Intro 5

@@
 \label{sec5}
-In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model \todo{which model?} is exactly solvable using integrability.  
-The aim of this section is to study the process when integrability is lost.\todo{but we got duality on any graph} We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
+{\color{blue}In Section \ref{sectionIntegrabiliy} we have shown that, combining duality and integrability of the multispcies stirring process with $\nu=1$ and on the geometry of chain with two boundaries, the non-equilibrium steady state can be found in an explicit form.
+As soon as $\nu>1$ the integrability property is lost, but duality still hold.
+Therefore, in this section we first address the following question: \textit{can we use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities}?
+This question can be extend to the geometry of the graph $G$ introduced in Section \ref{sec1}, however, for the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
+\\
+Inspired by the results for the thermalized version of the symmetric exclusion process reported in \cite{carinci2013duality}, in this section we also investigate its multispecies counterpart.
+More precisely, we try to answer these questions: \textit{can we define a thermalized version of the boundary driven multispecies stirring process?
+Does this thermalized process keep the absorbing duality properties as in the single species case?} Again, we restrict our analysis on the chain with two reservoirs at the end sites.
+\\ Finally we add a reaction mechanism of transition to the boundary driven multispeices stirring process.
+The aim is to answer the following question: \textit{Can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?} Moreover, in \cite{casini2022uphill} the duality for this reaction-diffusion process was proved only for the equilibrium case and the result was achieved by direct computation (without using a $gl(3)$ symmetry).
+Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section \ref{sectionDuality}.\\ The section is organized as follows: }
+
+%In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model \todo{which model?} is exactly solvable using integrability.  
+%The aim of this section is to study the process when integrability is lost.\todo{but we got duality on any graph} We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
 We provide the following extensions:
 \begin{enumerate}
-	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles.
+	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations {\color{blue} of the boundary driven multispecies stirring process on a chain with two reservoirs} is expressed in terms of absorption probabilities of the dual particles.
 These probabilities are hard to find when $\nu>1$.
-We give
-	in Appendix~\ref{appendix-1pts-general} the expression for the one-point correlation. \todo{is this on a chain?}
+As an example we give,
+	in Appendix~\ref{appendix-1pts-general}, the expression for the one-point correlation. \todo{is this on a chain?[ DONE]}
 	\item \textit{Instantaneous thermalization} (Section~\ref{Subsection-Thermalized}): starting from the multispecies stirring dynamics, we define the thermalized process, where particles are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): a further dynamics is added\todo{a further dynamic or further dynemics are?
-Maybe explain better}.
-Particle can now change type.
-The model \todo{which model?} is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
-Duality for the boundary driven process is also proved.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section \ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction-type} dynamics are added\todo{a further dynamic or further dynemics are?
+Maybe explain better[DONE]}.
+Particle can now change type {\color{blue} with two different mechanism: a \textit{pure mutation} (with rate $\Upsilon$) and a \textit{stirring-mutation} (at rate $\sigma_{12}$), i.e.
+a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own types.} {\color{blue} This reaction-diffusion} model \todo{which model?[DONE]} is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+{\color{blue} Exploiting the $gl(N)$ symmetry of this reaction-diffusion process, absorbing duality} for the boundary driven process is also proved.
 \end{enumerate}
-In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can {\color{blue} host at most $\nu\geq 1$ particles per site, whose type is chosen among the $N-1$ available ones}.
-The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$).
-\todo{this is said before} The processes considered in this section will be denoted with same name \todo{variables?} $\left(\bm{n}(t)\right)_{t\geq0}$, their corresponding generator  will be specified in each subsection.
-We use the notation of Section~\ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
-For example, the state space is denoted by 
+{\color{blue}As already pointed out at the beginning, in this section we always assume that the geometry is a chain of length $L$ where two reservoirs are connected to the end sites $1$ and $L$.
+In all the three investigated situations, we will denote the original processes by the variables $\left(\bm{n}(t)\right)_{t\geq0}$, while their dual processes will be denoted by the variables  $(\bm{\xi}(t))_{t\geq 0}$.
+Moreover, we will always denote the configuration spaces of the original processes by
 \begin{equation}\label{stateSpace-Chain}
@@
 \end{equation}
- The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case \todo{?}.
-The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.
- We denote the space of the dual process by $\widetilde{\Omega}_{L}$, i.e.
+and their dual configuration spaces 
 \begin{equation}\label{dualSpace-chain}
@@
 \end{equation}
-In the following, for $a\in \{1,\ldots,N-1\}$ of this section we will denote by \todo{?}
-\begin{equation}
-	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\beta_{a}}{|\beta|}\,.
-\end{equation}
+We recall that the dual processes are defined on an enlarged chin with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.}
+%In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
+Each site can {\color{blue} host at most $\nu\geq 1$ particles per site, whose type is chosen among the $N-1$ available ones}.
+%The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). \todo{this is said before} 
+%The processes considered in this section will be denoted with same {\color{blue} random variable} \todo{variables?[DONE]} $\left(\bm{n}(t)\right)_{t\geq0}$.
+{\color{blue} We will specify the generators case by case}.
+%their corresponding generator will be specified in each subsection.
+%We use the notation of Section~\ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
+%{\color{blue}The state space of the original process} is denoted by 
+%\begin{equation}%\label{stateSpace-Chain}
+%	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega%_{x}\,.
+%\end{equation}
+% The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the dual generator specified case by case \todo{?}.
+The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.
+% We denote the space of the dual process by $\widetilde{\Omega}_{L}$, i.e.%
+%\begin{equation}%\label{dualSpace-chain}
+%	\widetilde{\Omega}_{L}=\mathbb{N}_{0}^{N-1}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N-1}\dt
+%\end{equation}
+%In the following, for $a\in \{1,\ldots,N-1\}$ of this section we will denote by \todo{?}
+%\begin{equation}
+%	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\beta_{a}}{|\beta|}\,.
+%\end{equation}
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
@@
 As already pointed out, in this nearest neighbour chain, its action consists in exchanging the particles or the holes and the particles of two adjacent sites.
-Here we show that its action on the occupation variable of any species gives the discrete gradient of the occupation variable itself.
+Here we show that its action on the occupation variable of any species gives a discrete gradient in the occupation variable itself.
 Indeed, we have that }
-\todo{add text here}
+\todo{add text here [DONE]}
 \begin{equation}

### 2023-12-13 main.tex
''

@@
 	\item \textit{\underline{Stirring generator}}: {\color{blue}this is the edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$).
-As already pointed out, in this nearest neighbour chain, its action consists in exchanging the particles or the holes and the particles of two adjacent sites.
+As already pointed out, in this nearest neighbour chain, its action consists in exchanging two particles or an hole and a particle on two adjacent sites.
 Here we show that its action on the occupation variable of any species gives a discrete gradient in the occupation variable itself.

### 2023-12-13 main.tex
ll

@@
 Again, an absorbing duality is proved and the duality function turns out to be the same of the multispecies stirring process.
-\todo{mention that there is an appendix. In particular Appendix B could be interesting to stress.[DONE, SEE BLUE TEXT]}
 % In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
@@
 % {\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
-%  \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, chatterjee2023multi,redig2022ergodic, floreani2022switching} and \cite{casini2023density,  franceschini2022orthogonal,redig2023equilibrium,floreani2023non,carinci2023open}
+%  \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, chatterjee2023multi,redig2022ergodic, floreani2022switching} and
+
+% \cite{casini2023density,  franceschini2022orthogonal,redig2023equilibrium,floreani2023non,carinci2023open}
 % See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
@@
 with open boundaries. 
-In words, the dynamics is described as follows. Each site
+In words, the process is described as follows. Each site
 of a connected graph can host a maximal number of particles called $\nu\in \mathbb{N}$ .
 The particles have a {\em type} (sometimes called {\em species} or {\em colour})
-which can take $N-1$ values.
-{\color{blue}This means that at each site there are $\nu$ available places (called \textit{holes}) that can be either occupied by particles or not.
-As a consequence, each site can be totally empty (when no particles are present and thus $\nu$ holes are available), totally occupied (when $\nu$ particles, of any type, are present and thus no holes are there) or partially occupied (when some of the holes are occupied and some are available).
-These situations can be described by introducing the \textit{exclusion constraint} that tells that, at each site and at any time, the sum of the number of particles of any type and of the number of holes is $\nu$.}
+which can takes  values $\{1,2,\ldots,N-1\}$.
+{More precisely, at each site there are $\nu$ available places (called \textit{holes} or \textit{vacancies}) that can be either occupied by particles or not.
+As a consequence, each site can be totally empty (when no particles are present and thus $\nu$ holes are available), totally occupied (when $\nu$ particles, of any type, are present and thus no holes are available) or partially occupied (when some of the holes are occupied and some are available).
+All these configurations obey the \textit{exclusion constraint} that tells that, at each site and at any time, the sum of the number of particles of any type plus the number of holes is $\nu$.}
 
@@
 on each edge of the graph, any two types of particles are swapped at rate $1$;
-moreover a particle of any type and a hole are also swapped at rate $1$;\todo{explain what is a hole... Maybe stress that there can be at max $\nu$ holes per site? [DONE, SEE BLUE TEXT JUST ABOVE]}
+moreover a particle of any type and a hole are also swapped at rate $1$; 
 \item
@@
 We consider a connected graph $G=(V,\mathcal{E})$ with vertex set $V$ and edge set $\mathcal{E}$.
-At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {\color{blue} denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ denotes the number of holes at site $x$.} On each vertex we {\color{blue} allow a total maximal number of particles $\nu\in \mathbb{N}$}.
-{\color{blue} In the following we introduce the indices denoted by lowercase letters (for instance $a,b,c,d\in \{1,\ldots,N-1\}$) when only particles are taken into account.
-Moreover, we introduce the indices denoted by uppercase letters (for instance $A,B,C,D\in\{1,\ldots,N\}$) \todo{any chance we can remove index K and k?[DONE, I REMOVED THESE INDICES IN THE APPENDICES]} when we also consider the hole, that we recall is denoted by $N$.
+At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ {denotes the number of particles of species $a\in \{1,\ldots,N-1\}$, while the component $n_{N}^{x}$ counts the number of holes at site $x$.} On each vertex we {allow a total maximal number of particles $\nu\in \mathbb{N}$}.
+{In the following we use indices denoted by lowercase letters (for instance $a,b,c,d\in \{1,\ldots,N-1\}$) when only particles are taken into account.
+Moreover, we introduce indices denoted by uppercase letters (for instance $A,B,C,D\in\{1,\ldots,N\}$)  to also incorporate the holes, that correspond to the index $N$.
 The link between the two indices is given by
 \begin{equation}
-	a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad A=(a,N)
-	\end{equation} 
-and the same for the other letters.} Then, the configuration space of the process on the graph $G$ is 
+	a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad A=(a,N)\,.
+	\end{equation} 
+} 
+The configuration space of the process on the graph $G$ is 
 \begin{equation}\label{stateSpace}
@@
 Thus the dynamics consists in an exchange of particles between connected vertices at Poissonian times. 
-This means that on the edge $(x,y)\in \mathcal{E}$  a particle {\color{blue}or a hole} of type $A$ at site $x$ is exchanged with a particle {\color{blue}or a hole} of type $B$ at site $y$ at rate $\omega_{x,y}n_{A}^{x}n_{B}^{y}$.
-{\color{blue} The transitions where an hole is exchanged by a particle, can be interpreted as \textit{purely diffusive}.}
-Moreover, each vertex  exchanges particles {\color{blue} or holes} with the external environment (reservoirs). 
-Namely, on each site $x\in V$  a particle {\color{blue} or a hole} of type $B$ is replaced with a particle {\color{blue} or a hole} of type $A$ at rate $\Gamma_{x}\alpha_{A}^{x}n_{B}^{x}$.
-{\color{blue}The transitions where the a particle is replaced by a hole can be interpreted as a removal/injection of particles.}
+This means that on the edge $(x,y)\in \mathcal{E}$  a particle {or a hole} indicated by $A$ at site $x$ is exchanged with a particle {or a hole} indicated by $B$ at site $y$ at rate $\omega_{x,y}n_{A}^{x}n_{B}^{y}$.
+% {\color{blue} The transitions where a hole is exchanged with a particle, can be interpreted as \textit{purely diffusive}.}
+Moreover, each vertex  exchanges particles {or holes} with the external environment (reservoirs). 
+Namely, on each site $x\in V$  a particle {or a hole} indicated by $B$ is replaced with a particle {or a hole} indicated $A$ at rate $\Gamma_{x}\alpha_{A}^{x}n_{B}^{x}$.
+{The transitions where the a particle is replaced by a hole/a hole is replaced by a particle is interpreted as a removal/injection of particles.}
 %
@@
 and  $|\alpha^x|=\sum_{A=1}^{N}\alpha_{A}^x$.
-{\color{blue} As a consequence, particles are injected and removed in the graph with different rates.
+{As a consequence, particles are injected and removed in the graph with different rates.
 When, for any $A\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{A}^{x}\neq  \rho_{A}^{y}$, a  non-zero current sets in, breaking the reversibility.
-Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.} %{\color{red}wants to fix}
-% \todo{?}
-%Currents will arise when at least two reservoirs have different densities. 
+Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.}
 \begin{remark}
 \label{rem-rev}
-		{\color{blue}One can check that conditions \eqref{reversibilityCondition} are not the most general that implies reversibility. Indeed, by choosing the reservoir parameters as }
+		{One can check that conditions \eqref{reversibilityCondition} are not the most general that implies reversibility. Indeed, by choosing the reservoir parameters as }
 		\begin{equation}
@@
 \end{equation} 
-with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. Since the {\color{blue} maximal occupancy at each site is $\nu=1$},
+with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. Since the {maximal occupancy at each site is $\nu=1$},
 % \todo{but is it at max 1? I do not understand what we call the stirring process....}  
@@
 Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
-The duality result yields {\color{blue} to a dual process that} %several simplifications,  the main one being that the
+The duality result yields {to a dual process that} %several simplifications,  the main one being that the
 %dual process
@@
 \end{equation} 
-where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at site $x$, {\color{blue} while $\xi_{N}^{x}$ is interpreted as the number of holes at site $x$ of the dual process.}
+where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at site $x$, {while $\xi_{N}^{x}$ is interpreted as the number of holes at site $x$ of the dual process.}
 The component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
 the extra-site $u(x)$ connected to $x\in V$.
-{\color{blue} We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, i.e.
+{We observe that the configuration variable at the extra site $u(x)$ does not have to satisfy any exclusion constraint, i.e.
 an unbounded number of particles can be hosted.
@@
 \end{equation}
-{\color{blue} Here $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ is the vector associated to the configuration of in the extra site $u(x)$.
-For all $q_{1},\ldots,q_{N-1}\in \mathbb{N}_{0}$, we assume that it satisfy an orthogonality relation
+{Here $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ is the vector associated to the configuration at the extra site $u(x)$.
+For $q_{1},\ldots,q_{N-1}\in \mathbb{N}_{0}$, we assume that it satisfies an orthogonality relation
 \begin{equation}\label{ortho-extraSite}
-	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}
+	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}\,.
 \end{equation} }
-{\color{blue} \begin{remark}\label{reamrk-extraSite}
-	In the following, with a slight abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$.
-This allows to stress that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$.
-Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which we recall that the components $\xi_{a}^{u(x)}$ denote the number of dual particles of type $a$ at site $u(x)$.
+{\begin{remark}\label{reamrk-extraSite}
+	In the following, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$.
+This allows to stress that these vectors belong to the extra-space $N_{0}^{N-1}$ "attached" to site $x$.
+Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which we recall that the components $\xi_{a}^{u(x)}$ denote the number of dual particles of type $a$ at site $u(x)$.
 \end{remark}} 
-\todo{good, discuss}
 The Hamiltonian of the dual process reads
@@
  \end{equation}
-In the following we need the application of this with $\mathcal{B}=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $\mathcal{A}$ equal to some of the generator $E_{CD}$ of the Lie algebra ${gl}(N)$ with $C,D\in\{1,\ldots,N\}$.
-Therefore we compute
-\todo{discuss}
+In the following we evaluate this formula for $\mathcal{B}=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and $\mathcal{A}=E_{CD}$  with $C,D\in\{1,\ldots,N\}$. We find  
 \begin{align}
@@
 \end{equation}
-Taking the tensor product of both sides of \eqref{siteHadamardI}% with 
-%\begin{equation}
-%\langle \rho|_{u(x)}=\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}%\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|_{u(x)}
-%\end{equation}
-%{\color{blue}Think about replacing $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ with $\langle \xi_{1},\ldots,\xi_{N}|_{u(x)}$}\\
+Taking the tensor product of both sides of  \eqref{siteHadamardI} 
 we obtain 
@@
 \end{equation}
-{\color{blue}With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, in equation \eqref{siteHadamardII}, we denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$
+{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ 
 % although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$
@@
 } 
-\todo{explain extra index [IS THE EXPLANATION OF REMARK 4 ENOUGH?]}  
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
@@
 % \eqref{exactCorrelations}.} 
-\todo{Are you ok with that? It is still not super clear....}
 \end{corollary}
-{\color{blue} The quantity $\mu(\bm{\tau})$ is the probability, under the non-equilibrium steady distribution, of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
+{\color{blue} Here $\mu(\bm{\tau})$ is the  non-equilibrium steady probability of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
 However, from Corollary \ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
@@
 % \todo{indices are strange. Say what happens here}
-Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.
-{\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
+Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.
+{Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
 \begin{flushright}
@@
 \end{equation} 
-{\color{blue}where, for the sake of notation, we have introduced $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
+{where, for the sake of notation, we have introduced $\langle\rho_{a_{1}}^{x_{1}}\rangle$.}
 \paragraph{Two-point correlations}
@@
 \end{equation}
-{\color{blue}As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
+{As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
 the situation where the process has only one species of particles and holes, with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}.
@@
 \begin{equation}\label{Pass} 
-	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 	\end{equation} 
-	\todo{is the last term in the product?[CORRECT, I HAVE DONE IT ALSO IN APPENDIX C]}
 and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
@@
 \end{equation} 
-\todo{Why not merge sum or is there a typo? [FIXED,THERE WAS A TYPO]}
 This can be proved by imposing the detailed balance conditions for the bond $(x,x+1)$ and for the boundaries $\{1,L\}$.\\
@@
 Indeed, we have that }
-\todo{add text here [DONE]}
+\todo{shorter? }
 \begin{equation}

### 2023-12-13 main.tex
ll

@@
 As an example we give,
-	in Appendix~\ref{appendix-1pts-general}, the expression for the one-point correlation. \todo{is this on a chain?[ DONE]}
+	in Appendix~\ref{appendix-1pts-general}, the expression for the one-point correlation.  
 	\item \textit{Instantaneous thermalization} (Section~\ref{Subsection-Thermalized}): starting from the multispecies stirring dynamics, we define the thermalized process, where particles are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond.
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section \ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction-type} dynamics are added\todo{a further dynamic or further dynemics are?
-Maybe explain better[DONE]}.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section \ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction-type} dynamics are added.
 Particle can now change type {\color{blue} with two different mechanism: a \textit{pure mutation} (with rate $\Upsilon$) and a \textit{stirring-mutation} (at rate $\sigma_{12}$), i.e.
-a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own types.} {\color{blue} This reaction-diffusion} model \todo{which model?[DONE]} is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own types.} {\color{blue} This reaction-diffusion} model   is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
 {\color{blue} Exploiting the $gl(N)$ symmetry of this reaction-diffusion process, absorbing duality} for the boundary driven process is also proved.

### 2023-12-14 main.tex
d

@@
  \newpage
+ {\color{blue}
+ To do
+ \begin{itemize}
+  \item Read introduction
+  \item Try to clarify text in Corollary 1 and Theorem 2
+  \item Read Section 5
+  \item Clarify Corollary 2
+  \item double check Remark 10
+  \item Read appendix
+ \end{itemize}
+}
 \section{Introduction} 
@@
 \\
- Considering {\color{blue}$\mathcal{A},\mathcal{B}\in {gl}(N)$}, the Hadamard formula reads 
+ Considering {$\mathcal{A},\mathcal{B}\in {gl}(N)$}, the Hadamard formula reads 
  \begin{equation}\label{HadamardFormula}
@@
 {\color{blue}In Section \ref{sectionIntegrabiliy} we have shown that, combining duality and integrability of the multispcies stirring process with $\nu=1$ and on the geometry of chain with two boundaries, the non-equilibrium steady state can be found in an explicit form.
-As soon as $\nu>1$ the integrability property is lost, but duality still hold.
-Therefore, in this section we first address the following question: \textit{can we use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities}?
-This question can be extend to the geometry of the graph $G$ introduced in Section \ref{sec1}, however, for the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
+As soon as $\nu>1$ the integrability property is lost, but duality still holds.
+Therefore, in this section we first address the  question whether we can use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities.
+This question can be extended to the geometry of the graph $G$ introduced in Section \ref{sec1}, however, for the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
 \\

### 2023-12-14 main.tex
ee
ll
ss
''

@@
  \begin{itemize}
-  \item Read introduction
+  \item Clean introduction
   \item Try to clarify text in Corollary 1 and Theorem 2
-  \item Read Section 5
+  \item Clean Section 5
   \item Clarify Corollary 2
   \item double check Remark 10
-  \item Read appendix
+  \item Clean appendix
  \end{itemize}
@@
 \begin{equation}\label{reversibilityCondition}
-\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V\,,
+\alpha_{A}^{x}=\alpha_{A}\qquad \forall x\in V\,,
 \end{equation}
@@
  $$
-\rho_{a}=\frac{\alpha_{a}}{|\alpha|}\co
+\rho_{A}=\frac{\alpha_{A}}{|\alpha|}\co
 $$
@@
 	\label{rhox}
-	\rho_{a}^x=\frac{\alpha_{a}^x}{|\alpha^x|}
+	\rho_{A}^x=\frac{\alpha_{A}^x}{|\alpha^x|}
 \end{equation}
@@
 		\label{cond-gen}
-			\alpha_{k}^{x}\left(|\alpha^{y}|-\alpha_{k}^{y}\right)=\alpha_{k}^{y}\left(|\alpha^{x}|-\alpha_{k}^{x}\right)\qquad\qquad \forall x,y\in V,\quad \forall k\in \{1,\ldots,N\}
+			\alpha_{A}^{x}\left(|\alpha^{y}|-\alpha_{A}^{y}\right)=\alpha_{A}^{y}\left(|\alpha^{x}|-\alpha_{A}^{x}\right)\qquad\qquad \forall x,y\in V,\quad \forall A\in \{1,\ldots,N\}
 		\end{equation}
@@
 		\begin{equation}
-			|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}\dt
+			|\alpha^{x}|=\sum_{A=1}^{N}\alpha_{A}^{x}\dt
 		\end{equation}
@@
 \begin{equation}\label{secondCasimir}
-    C=\sum_{a,b=1}^{N}E_{AB}E_{BA}\co
+    C=\sum_{A,B=1}^{N}E_{AB}E_{BA}\co
 \end{equation}
@@
 \begin{equation}\label{ElementsDualityMatrixChain_1}
-	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
+	D(\bm{\tau},\bm{\xi})=\left(\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\right)\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\left(\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\right)\dt
 \end{equation}
@@
 \begin{equation}\label{NESS-expectation-ABS}
-\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\left[\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right]\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
 \end{equation}
@@
 \mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
-	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
+	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
 \end{split}
@@
 	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
+	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
 %	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
@@
 To each of these variables we associate coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
-Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ {\color{blue} (by the summation $\textstyle{\sum_{k=1}^{m}}c_{x_{k}}=q$)} \todo{you mean the sum is q?[FIXED]} and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$ {\color{blue} as explained.} Then, we obtain
+Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ { (by the summation $\textstyle{\sum_{k=1}^{m}}c_{x_{k}}=q$)} %\todo{you mean the sum is q?[FIXED]}
+ and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$ { as explained.} Then, we obtain  
 	\begin{equation}
@@
 \begin{enumerate}
-	\item \textit{\underline{Stirring generator}}: {\color{blue}this is the edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$).
-As already pointed out, in this nearest neighbour chain, its action consists in exchanging two particles or an hole and a particle on two adjacent sites.
-Here we show that its action on the occupation variable of any species gives a discrete gradient in the occupation variable itself.
-Indeed, we have that }
+	\item \textit{\underline{Stirring generator}}: {\color{blue}using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$) we have that}
 \todo{shorter? }

### 2023-12-15 main.tex
ll

@@
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
- As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by the holes $N$.
+ As already pointed out, the dual process voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by the holes $N$.
 This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}.
@@
 where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the generators \eqref{siteGenerator} acting on sites $1$ and $L$ with parameters $(\alpha_{A})_{A\in \{1,\ldots,N\}}$ and $(\beta_{A})_{A\in \{1,\ldots,N\}}$ respectively.
-The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, has generator
+The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, and has generator
 \begin{equation}
@@
 where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively.
-The duality function reads is \eqref{dualityElements} specified on the chain.
+The duality function is \eqref{dualityElements} specified on the chain.
 We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
@@
 where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal number of particle per site $\nu$. 
-Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state.
+Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$point correlations in the non-equilibrium steady state.
 The following equalities hold using ergodicity and duality:
@@
  These correlations can be computed once the absorption probabilities are known.
-For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
+For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one-point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
 The absorption probabilities for higher point correlations fulfill  difference equations.
@@
 		%	1\qquad  &\text{if}\quad \tau_{x}= N
-		%	\end{cases}\dt
+		%	\end{cases}
+		\dt
 \end{equation}
@@
 	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\label{boundaryDualityTH}
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\dt\label{boundaryDualityTH}
 \end{align}
@@
 For the sake of notation, we introduce
-\begin{equation}
-	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
+%
+\begin{equation}
+	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\dt
 \end{equation}
@@
 	\\\times &
-	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\right)
+	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\right)\dt
 \end{align}
 We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
-We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$.
-Thus, we have
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$.\todo{fix text?} Thus, we have
 \begin{align}\label{pezzo1}
@@
 	\\=&
-	\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
+	\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)\dt
 \end{align}
@@
 \end{equation}
+\todo{doublecheck}
 where we used the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that
@@
 	\\&=
-	\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
+	\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\dt
 \end{align}
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})
+		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})\dt
 	\end{split}
@@
 \begin{equation}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{B}^{x}+\bm{\delta}_{A}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)
+	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{B}^{x}+\bm{\delta}_{A}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)\dt
 \end{equation}
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)
+		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)\dt
 	\end{split}

### 2023-12-15 main.tex
ll

@@
 
-% \usepackage[margin=2.5cm]{geometry}
-
-%%%%%  TODO NOTES ETC  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\usepackage[left=1.7cm,right=4.3cm,bottom=4cm]{geometry}
-\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\definecolor{todocolor}{HTML}{D7E1E5}
-\usepackage[textsize=tiny, 
-            backgroundcolor=todocolor, 
-            bordercolor=todocolor, 
-            linecolor=todocolor, 
-            textwidth=3.9cm]{todonotes}
-\newcommand{\todoWARN}[1]{\todo{\colorbox{yellow}{\parbox{3.4cm}{#1}}}}
-\newcommand{\todoERR}[1]{\todo{\colorbox{red}{\parbox{3.4cm}{#1}}}}
-\usepackage{comment}
-\usepackage{rotating}
-\usepackage[left]{showlabels}
-\renewcommand{\showlabelfont}{\tiny}
-\renewcommand{\showlabelsetlabel}[1]
-{\begin{turn}{65}\showlabelfont \llap{#1}\end{turn}}
-\newcommand{\wiptitle}[1]{
-    \par\noindent\hspace*{-0.5cm}\texttt{\scriptsize\color{gray} \lbrack #1\rbrack} \par\noindent\ignorespaces}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[margin=2.5cm]{geometry}
+
+% %%%%%  TODO NOTES ETC  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+% \usepackage[left=1.7cm,right=4.3cm,bottom=4cm]{geometry}
+% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+% \definecolor{todocolor}{HTML}{D7E1E5}
+% \usepackage[textsize=tiny, 
+%             backgroundcolor=todocolor, 
+%             bordercolor=todocolor, 
+%             linecolor=todocolor, 
+%             textwidth=3.9cm]{todonotes}
+% \newcommand{\todoWARN}[1]{\todo{\colorbox{yellow}{\parbox{3.4cm}{#1}}}}
+% \newcommand{\todoERR}[1]{\todo{\colorbox{red}{\parbox{3.4cm}{#1}}}}
+% \usepackage{comment}
+% \usepackage{rotating}
+% \usepackage[left]{showlabels}
+% \renewcommand{\showlabelfont}{\tiny}
+% \renewcommand{\showlabelsetlabel}[1]
+% {\begin{turn}{65}\showlabelfont \llap{#1}\end{turn}}
+% \newcommand{\wiptitle}[1]{
+%     \par\noindent\hspace*{-0.5cm}\texttt{\scriptsize\color{gray} \lbrack #1\rbrack} \par\noindent\ignorespaces}
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
  \newpage 
- {\color{blue}
- To do
- \begin{itemize}
-  \item Clean introduction
-  \item Try to clarify text in Corollary 1 and Theorem 2
-  \item Clean Section 5
-  \item Clarify Corollary 2
-  \item double check Remark 10
-  \item Clean appendix
- \end{itemize}
-}
 \section{Introduction} 
@@
 Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
-{\color{blue}$m$ colours denoted by $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$, chosen among the $N-1$ available species.} Then, the $m$-point correlations in the non-equilibrium steady state read\todo{this I find still confusing [WHAT ABOUT THE BLUE SENTENCE?]}
+{$m$ colours denoted by $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$, chosen among the $N-1$ available species.} Then, the $m$-point correlations in the non-equilibrium steady state read 
 \begin{equation}\label{NESS-expectation-ABS}
@@
 %and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. 
-Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
-$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$.
-\todo{should this not be particles or so ? Maybe we can call particles 1 to N-1 excitations....}
+Let $m\in \{1,\ldots,L\}$. Consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
+{$m$ colours denoted by $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$, chosen among the $N-1$ available species.}  
 Then the $m$-point correlations with respect to the non-equilibrium steady state measure are given by 
@@
 We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
-We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$.\todo{fix text?} Thus, we have
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$ to get
 \begin{align}\label{pezzo1}
@@
 \end{equation} 
-\todo{doublecheck}
 where we used the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that
@@
 \begin{enumerate}
-	\item \textit{\underline{Stirring generator}}: {\color{blue}using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section \ref{sec1} (with $y=x+1$) we have that}
-\todo{shorter? }
+	\item \textit{\underline{Stirring generator}}: {using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section~\ref{sec1} (with $y=x+1$) we have that} 
 \begin{equation}

### 2023-12-15 main.tex
examples-corllary2

@@
 As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary \ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
-For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\ \\
+For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\
+{\color{blue} \paragraph{Example for an $L=2$ chain.} To clarify equation \eqref{implicit-mass-function} we report the example of a chain with $L=2$, where we compute the probability mass functions of three configurations.
+Without loss of generality we assume that the particles are always of species $1$.
+We have that
+ \begin{itemize}
+ 	\item probability of two occupied site:
+ 	\begin{equation}
+ 		\mu(1,1)=\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right]\dt
+ 	\end{equation}
+ 	Here the right-hand-side corresponds to $b=0$ and average can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
+ 	\item probability of the first site occupied and the second empty:
+ 	\begin{align}
+ 		\mu(1,N)=&\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right]=\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_{2}=a\}}\right)\right]\nonumber
+ 		\\=&
+ 		\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\right]-\sum_{a=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=a\}}\right]\dt
+ 	\end{align}
+ 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
+The second term on the right-hand-side corresponds to $b=1$ in \eqref{implicit-mass-function} and can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=1,\;a_{2}=a$ for all $a=1,\ldots N-1$.
+ 	\item probability of both sites empty:
+ 	\begin{align}
+ 		\mu(N,N)=&\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right]=\mathbb{E}\left[\left(1-\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{1}=_{1}a\}}\right)\left(1-\sum_{a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right)\right]\nonumber
+ 		\\=&
+ 		1-\sum_{a_{1}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=a_{1}\}}\right]-\sum_{a_{2}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{Y_{2}=a_{2}}\right]+\sum_{a_{1},a_{2}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=a_{1}\}}\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right]\dt
+ 	\end{align}
+ 	Here the first term on the right-hand-side corresponds to $b=0$ and since $\bm{\tau}=(N,N)$ we obtain $1$.
+The second and the third term on the right-hand-side correspond to $b=1$.
+They can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively.
+The fourth term on the right-hand-side corresponds to $b=2$ and it can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$.
+ \end{itemize}}
 \textbf{Proof of Corollary~\ref{Corollary-NESS-ABS}:}

### 2023-12-15 main.tex
sec 5 double-checked

@@
 Therefore, in this section we first address the  question whether we can use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities.
-This question can be extended to the geometry of the graph $G$ introduced in Section \ref{sec1}, however, for the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
+For the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
+However, this question can be extended to the geometry of the graph $G$ introduced in Section \ref{sec1}.
 \\
@@
 The aim is to answer the following question: \textit{Can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?} Moreover, in \cite{casini2022uphill} the duality for this reaction-diffusion process was proved only for the equilibrium case and the result was achieved by direct computation (without using a $gl(3)$ symmetry).
-Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section \ref{sectionDuality}.\\ The section is organized as follows: }
+Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section \ref{sectionDuality} and based on Lie algebras.\\ The section is organized as follows: }
 
@@
 \begin{enumerate}
-	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations {\color{blue} of the boundary driven multispecies stirring process on a chain with two reservoirs} is expressed in terms of absorption probabilities of the dual particles.
+	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting the duality, the steady state correlations {\color{blue} of the boundary driven multispecies stirring process on a chain with two reservoirs} is expressed in terms of absorption probabilities of the dual particles.
 These probabilities are hard to find when $\nu>1$.
@@
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section \ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction-type} dynamics are added.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section \ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction} dynamics are added.
 Particle can now change type {\color{blue} with two different mechanism: a \textit{pure mutation} (with rate $\Upsilon$) and a \textit{stirring-mutation} (at rate $\sigma_{12}$), i.e.
-a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own types.} {\color{blue} This reaction-diffusion} model   is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own species.} {\color{blue} This reaction-diffusion} model   is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
 {\color{blue} Exploiting the $gl(N)$ symmetry of this reaction-diffusion process, absorbing duality} for the boundary driven process is also proved.
@@
 {\color{blue}As already pointed out at the beginning, in this section we always assume that the geometry is a chain of length $L$ where two reservoirs are connected to the end sites $1$ and $L$.
-In all the three investigated situations, we will denote the original processes by the variables $\left(\bm{n}(t)\right)_{t\geq0}$, while their dual processes will be denoted by the variables  $(\bm{\xi}(t))_{t\geq 0}$.
-Moreover, we will always denote the configuration spaces of the original processes by
+In all the three investigated situations, we denote the original processes by the variables $\left(\bm{n}(t)\right)_{t\geq0}$, while their dual processes is denoted by the variables  $(\bm{\xi}(t))_{t\geq 0}$.
+Moreover, we always denote the configuration spaces of the original processes by
 \begin{equation}\label{stateSpace-Chain}
@@
 We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
-For every $m\in\{1,\ldots,L\}$ we consider  $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$.
+For every $m\in\{1,\ldots,L\}$ we consider {\color{blue}the coordinates $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
 We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
@@
 \end{equation}
-The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
+{\color{blue}As already pointed out,} the duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
 \begin{equation}
@@
 \end{equation}
-where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal number of particle per site $\nu$. 
+where $C(\nu,m)$ is a constant that depends on $m$ and {\color{blue}on the maximal occupancy} per site $\nu$. 
 Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$point correlations in the non-equilibrium steady state.
@@
 \subsubsection{The thermalization measure}
-We introduce the reversible measure \eqref{reversibleMeasure} conditioned on the conservation of the particles on that bond
+We introduce the reversible measure \eqref{reversibleMeasure} conditioned on the conservation of the particles on the bond $(x,x+1)$
 \begin{align}
@@
 \subsubsection{Thermalized multispecies stirring process}
-The thermalized multispecies stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace-Chain} and its generator reads
+The thermalized multispecies stirring process is defined on the configuration space $\Omega_{L}$ introduced in \eqref{stateSpace-Chain} and its generator reads
 \begin{equation}\label{thermalizedGenerator}
@@
 \subsection{Multispecies stirring process with reaction} \label{Subsection-RD}
-We define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ as
+{\color{blue} We recall a general fact.
+Considering a generic $N-1$ species Markov process $(\bm{n}(t))_{t\geq 0}$ (where in the spirit of Section \ref{sec1}, $n_{A}^{x}$ denotes the number of particles or the number of holes at site $x$), we define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ and at time $t$ as
 \begin{equation}
@@
 where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$. Calling
-$\mathcal{L}^{rd}$ the generator of the process, these average occupations evolves according to the evolution equation
+$\mathcal{L}$ the generator of this process, these average occupations evolves according to the evolution equation
 \begin{equation}\label{EE-density}
-	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu_{0}}\left[\mathcal{L}^{rd}n_{a}^{x}(t)\right]\dt
-\end{equation} 
-In \cite{casini2022uphill} it has been defined a process whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied by a proper diffusivity constant) and a linear reaction term (mutation), i.e.
+	\frac{d \rho_{a}(x,t)}{dt}=\mathbb{E}_{\mu_{0}}\left[\mathcal{L}n_{a}^{x}(t)\right]\dt
+\end{equation} }
+In \cite{casini2022uphill} {\color{blue}it has been defined a process with two species $a=1,2$ and the holes (denoted by $0$ in that context)} whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied by a proper diffusivity constant) and a linear reaction term (mutation), i.e.
 \begin{equation}\label{2SpeciesRD}
@@
 \begin{enumerate}
-		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $N\in \mathbb{N}$ and arbitrary maximal site occupation $\nu\in \mathbb{N}$?
+		\item Is it possible to extend the results of \cite{casini2022uphill} to a case with arbitrary number of species $(N-1)\in \mathbb{N}$ and arbitrary maximal occupation $\nu\in \mathbb{N}$?
 			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process, using the same ${gl}(N)$ Lie algebraic structure?
 \end{enumerate}
-Therefore, we aim to find a process whose average occupations $\rho_{a}(x,t)$ for any species $a\in\{1,\ldots,N-1\}$ evolve as a system of difference-differential equation given by 
+Therefore, we aim to find a process whose average occupations $\rho_{a}(x,t)$ for any species $a\in\{1,\ldots,N-1\}$ evolves as a system of difference-differential equation given by 
 \begin{equation}\label{NSpeciesRD}
@@
 \end{equation} 
- We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{\text{left}}$ and $\rho_{a}^{\text{right}}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\sum_{a=1}^{N}\rho_{a}^{\text{right}}=\nu$.
- We construct the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$.
+ We assume that the boundary condition are given and denoted by $\rho_{a}^{\text{left}}$ and $\rho_{a}^{\text{right}}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{A=1}^{N}\rho_{A}^{\text{left}}=\sum_{A=1}^{N}\rho_{A}^{\text{right}}=\nu$.
+In the following of this section, we first construct the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of species $a$.
 Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality.
 \subsubsection{The reaction-diffusion process on a chain}
-We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $L$.
-The state space is $\Omega$ given in \eqref{stateSpace-Chain} and the generator reads
+We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{A})_{A\in\{1,\ldots,N\}}$ is attached at site $1$ and a reservoir with parameters $(\beta_{A})_{A\in\{1,\ldots,N\}}$ is attached at site $L$.
+The state space is $\Omega_{L}$ given in \eqref{stateSpace-Chain} and the generator reads
 \begin{equation}\label{RDGenerator}
@@
 \end{equation}
-The left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ is given by \eqref{siteGenerator} at site $1$,
-%reads
-%\begin{equation}
-%	\mathcal{L}_{\text{left}}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)
-%\end{equation}
-where the $\alpha$'s parameters are defined in function of the given boundary condition of the difference-differential system:
+The left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ is given by \eqref{siteGenerator} at site $1$,where the $\alpha$'s parameters are defined in function of the given boundary condition of the difference-differential system as
 \begin{align}\label{boundaryParamRD}
@@
 \end{align}
-As a consequence, from the above conditions we can define the boundary values in terms of the reservoir parameters as
+As a consequence, from the above conditions we write the boundary values in terms of the reservoir parameters as
 \begin{equation}
@@
 Therefore, using the evolution equation \eqref{EE-density} for the average densities and  the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}.
-For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
+For these reasons, this model is a generalization to $N-1$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
 %This answers the first question we addressed to at the beginning of this section. 
 \subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
-The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneous product measure \begin{equation}\label{reversibleMeasureRD}
+The process described by the generator $\mathcal{L}^{rd}$ introduced in \eqref{RDGenerator} is reversible with respect to the homogeneous product measure \begin{equation}\label{reversibleMeasureRD}
 	\Lambda_{\text{rev}}=\bigotimes_{x=1}^{L}\Lambda_{\text{rev}}^{x}
 \end{equation}
-when for any $a\in\{1,\ldots,N\}$
+when
 \begin{equation}\label{reversibilityConditionRD}
-	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}\dt
+	\alpha_{A}=\beta_{A}\quad\forall A\in\{1,\ldots,N\}\qquad \text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}\dt
 \end{equation}
@@
 \subsubsection{Duality for the reaction-diffusion process}
-In this section we formulate duality for the multispecies reaction diffusion process.
-This answer to the second question addressed at the beginning of Section~\ref{Subsection-RD}.
-The dual process is defined on the enlarged state space $\widetilde{\Omega}_{L}$.
+In this section we formulate duality for the multispecies reaction diffusion process. This answer to the second question addressed at the beginning of Section~\ref{Subsection-RD}.
 \begin{proposition}[Duality for the reaction-diffusion process]\label{propositin-duality-RD}
@@
 \paragraph{Proof of Proposition~\ref{propositin-duality-RD}:}
-we only prove duality for the bulk generator, since the boundary generators are the same of the multispecies stirring process.
-In the spirit of Section~\ref{sectionDuality}, it is convenient to write the Hamiltonian of the process, that is defined through the basis elements \eqref{actionE} of the ${gl}(N)$ Lie algebra as
+it is enough to prove duality for the bulk generator, since the boundary generators are the same of the multispecies stirring process.
+In the spirit of Section~\ref{sectionDuality}, it is convenient to write the Hamiltonian of the process through the basis elements \eqref{actionE} of the ${gl}(N)$ Lie algebra.
+We have that
 \begin{equation}
@@
 \begin{equation}
-	\mathcal{H}_{x,x+1}^{c}=\sum_{A,B=1}^{N}\left(E_{h_{c}(A)B}\otimes E_{h_{c}(B)A}-E_{AA}\otimes E_{BB}\right)
+	\mathcal{H}_{x,x+1}^{c}=\sum_{A,B=1}^{N}\left(E_{h_{c}(A)B}\otimes E_{h_{c}(B)A}-E_{BB}\otimes E_{AA}\right)
 \end{equation}
@@
 \begin{align*}
-	&\left[\left(\sum_{a=1}^{N-1}E_{aN}\otimes\sum_{a=1}^{N-1}E_{aN}\right), \sum_{A,B=1}^{N}\left(E_{h_{c}(B)A}\otimes E_{h_{c}(A)B} -E_{AA}\otimes E_{BB}\right)\right]
+	&\left[\left(\sum_{a=1}^{N-1}E_{aN}\otimes\sum_{a=1}^{N-1}E_{aN}\right), \sum_{A,B=1}^{N}\left(E_{h_{c}(A)B}\otimes E_{h_{c}(B)A} -E_{BB}\otimes E_{AA}\right)\right]
 	\\=&
@@
 %\paragraph{Duality for $H_{x,x+1}^{m}$} 
-Concerning the commutator between $\mathcal{H}_{x,x+1}^{m}$ the proof is similar and gives
+Concerning the commutator of $\mathcal{H}_{x,x+1}^{m}$ the proof is similar and gives
 \begin{equation}

### 2023-12-15 main.tex
Appendix A fixed

@@
 \end{align} 
-We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$.
-More explicitly, this dual configuration is given by
+{\color{blue}We introduce the dual configuration constructed by attaching two extra-sites (without any particle) to the vector $\bm{\tau}$, transforming its dimension from $L$ to $L+2$.
+We denote it by $\bm{\xi}(\bm{\tau})=(0,\tau_{1},\ldots,\tau_{L},0)$, where we wrote $0$ in the two extra-sites to indicate that no dual particles are present there.}  More explicitly, this dual configuration is given by
 \begin{equation}
 	\begin{cases}
-		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
-		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
+		\xi_{A}^{x}(\bm{\tau})= \delta_{\tau_{x},A}\qquad \forall A\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
+		\xi_{1}^{0}(\bm{\tau})=\ldots=\xi_{N-1}^{0}(\bm{\tau})=0\\
+		\xi_{1}^{L+1}(\bm{\tau})=\ldots=\xi_{N-1}^{L+1}(\bm{\tau})=0
 	\end{cases}\dt
-\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
+\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and, {\color{blue} since no dual particles are present in the extra-sites $0$ and $L+1$}, we have
 \begin{align}\label{useful-InInterpretation}
@@
 Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
-Let $\ell$ be the number of occupied sites in the configuration $\bm{\tau}$, i.e.
+Let $\ell$ be the number of sites {\color{blue}occupied by a particle} in the configuration $\bm{\tau}$, i.e.
 $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
-We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present.
+We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any species is present.
 Finally, we call

### 2023-12-15 main.tex
Appendices B,C,D

@@
 To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$.
-This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
+This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries {\color{blue}is absorbed at extra-site $0$.
+It fulfils the following equations discrete Laplace equation}
 \begin{equation}\label{gamblers-ruin}
@@
 and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ and we obtain
+We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ to get
 \begin{equation}\label{pezzo2}
@@
 	\begin{split}
-		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})\dt
+		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})\dt
 	\end{split}
@@
 \begin{align*}
-	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{B=1}^{N}n_{d}^{x}n_{B}^{x+1}\\
+	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{A=1}^{N}n_{A}^{x}n_{d}^{x+1}-\sum_{B=1}^{N}n_{d}^{x}n_{B}^{x+1}\\
 	=&\sum_{a=1}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{c=1}^{N-1}n_{c}^{x})n_{d}^{x+1}-\sum_{b=1}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{c=1}^{N-1}n_{c}^{x+1})\\
@@
 \end{equation}
-In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{D}^{x+1}$, when $A=d$ (here we call $D=h_{c}(B)$); a contribution $n_{A}^{x}n_{h_{c}(B^{'})}^{x+1}$, where we denoted by $B^{'}\in \{1,\ldots,N\}$ the type of particle such that $h_{c}(B^{'})=d$.
-Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that in the above equation $h_{c}(B^{'})\neq d$ and $h_{c}(B^{'})\neq N$.
+In the brackets of the right-hand-side of the above equation we have: a contribution $-n_{d}^{x}n_{D}^{x+1}$, when $A=d$ (here we call $D=h_{c}(B)$); a contribution $n_{A}^{x}n_{h_{c}(B^{'})}^{x+1}$, where we denoted by $B^{'}\in \{1,\ldots,N\}$ the species of particle such that $h_{c}(B^{'})=d$.
+Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $h_{c}(B^{'})\neq d$ and $h_{c}(B^{'})\neq N$.
 Thus we obtain
@@
 	\begin{split}
-		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{B}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,B\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{B=1\,:B\neq d}^{N}\alpha_{B}
-	\end{split}
-\end{equation}
-Indeed, by using equation \eqref{boundaryParamRD}, we obtain 
+		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{A,B=1}^{N}\alpha_{A}n_{B}^{1}\left((n_{d}^{1}-\bm{\delta}_{B}^{1}+\bm{\delta}_{A}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{B=1\,:\,B\neq d}^{N}n_{B}^{1}-n_{d}^{1}\sum_{A=1\,:A\neq d}^{N}\alpha_{A}
+	\end{split}
+\end{equation}
+Using equation \eqref{boundaryParamRD}, we obtain 
 \begin{align}
 			\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=
-		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
-		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)\nonumber
+		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})\nonumber
 		\\&=
-		\nu\sigma_{11}\rho_{d}^{\text{left}}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{\text{left}}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
+		\nu\sigma_{11}\rho_{d}^{\text{left}}+\nu\sigma_{12}\left(\sum_{b=1\,:\,b\neq d}^{N-1}\rho_{b}^{\text{left}}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})\nonumber
 		\\&=

### 2023-12-15 main.tex
''

@@
 These particles can be of $N-1$ types (or species).
-Two sites do interact when there is an edge between them and this interaction consists in swapping the occupations of these two sites (for a precise definition of the process see Section \ref{sec1}).
+Two sites do interact when there is an edge between them and this interaction consists in swapping the occupations of these two sites (for a precise definition of the process see Section~\ref{sec1}).
 Furthermore, reservoirs are attached at each site of the graph, creating and removing particle.
@@
 {\color{blue} Here $\mu(\bm{\tau})$ is the  non-equilibrium steady probability of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
-However, from Corollary \ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
+However, from Corollary~\ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
 Therefore, to write the probability mass function $\mu$ for occupations containing holes we have to use the conservation of probability to get rid of the indicators of these holes.
-Then, equation \eqref{implicit-mass-function} is derived (for details see below the proof of Corollary \ref{Corollary-NESS-ABS}).\\
+Then, equation \eqref{implicit-mass-function} is derived (for details see below the proof of Corollary~\ref{Corollary-NESS-ABS}).\\
  The expectation on the right-hand-side of \eqref{implicit-mass-function} contains only indicators of particles configurations: indeed in the first product  $\tau_{x}\neq N$ are considered, while in the second product we have $a_{k}\neq N$ for all $k\in\{1,\ldots,N\}$.
-As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary \ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
+As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary~\ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
 For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\
@@
  	\end{equation}
- 	Here the right-hand-side corresponds to $b=0$ and average can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
+ 	Here the right-hand-side corresponds to $b=0$ and average can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
  	\item probability of the first site occupied and the second empty:
  	\begin{align}
- 		\mu(1,N)=&\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right]=\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_{2}=a\}}\right)\right]\nonumber
+ 		\mu(1,N)=&\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=N\}}\right]=\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_{2}=a\}}\right)\right]\nonumber
  		\\=&
@@
  	\end{align}
- 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
-The second term on the right-hand-side corresponds to $b=1$ in \eqref{implicit-mass-function} and can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=1,\;a_{2}=a$ for all $a=1,\ldots N-1$.
+ 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
+The second term on the right-hand-side corresponds to $b=1$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=1,\;a_{2}=a$ for all $a=1,\ldots N-1$.
  	\item probability of both sites empty:
  	\begin{align}
- 		\mu(N,N)=&\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right]=\mathbb{E}\left[\left(1-\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{1}=_{1}a\}}\right)\left(1-\sum_{a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right)\right]\nonumber
+ 		\mu(N,N)=&\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=N\}}\mathbbm{1}_{\{Y_{2}=N\}}\right]=\mathbb{E}\left[\left(1-\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{1}=a_{1}\}}\right)\left(1-\sum_{a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right)\right]\nonumber
  		\\=&
- 		1-\sum_{a_{1}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=a_{1}\}}\right]-\sum_{a_{2}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{Y_{2}=a_{2}}\right]+\sum_{a_{1},a_{2}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=a_{1}\}}\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right]\dt
+ 		1-\sum_{a_{1}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=a_{1}\}}\right]-\sum_{a_{2}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right]+\sum_{a_{1},a_{2}=1}^{N-1}\mathbb{E}\left[\mathbbm{1}_{\{Y_{1}=a_{1}\}}\mathbbm{1}_{\{Y_{2}=a_{2}\}}\right]\dt
  	\end{align}
@@
 The second and the third term on the right-hand-side correspond to $b=1$.
-They can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively.
-The fourth term on the right-hand-side corresponds to $b=2$ and it can be computed by Corollary \ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$.
+They can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively.
+The fourth term on the right-hand-side corresponds to $b=2$ and it can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$.
  \end{itemize}}
@@
 		\begin{align}\label{implicit-PSI-PSIp}
-			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
+			\Psi(\bm{\tau})=&\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
 			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
@@
 		means that, {given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
-}
+}  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}.
 	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 
@@
 \label{sec5}
-{\color{blue}In Section \ref{sectionIntegrabiliy} we have shown that, combining duality and integrability of the multispcies stirring process with $\nu=1$ and on the geometry of chain with two boundaries, the non-equilibrium steady state can be found in an explicit form.
+{\color{blue}In Section~\ref{sectionIntegrabiliy} we have shown that, combining duality and integrability of the multispcies stirring process with $\nu=1$ and on the geometry of chain with two boundaries, the non-equilibrium steady state can be found in an explicit form.
 As soon as $\nu>1$ the integrability property is lost, but duality still holds.
@@
 For the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
-However, this question can be extended to the geometry of the graph $G$ introduced in Section \ref{sec1}.
+However, this question can be extended to the geometry of the graph $G$ introduced in Section~\ref{sec1}.
 \\
@@
 The aim is to answer the following question: \textit{Can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?} Moreover, in \cite{casini2022uphill} the duality for this reaction-diffusion process was proved only for the equilibrium case and the result was achieved by direct computation (without using a $gl(3)$ symmetry).
-Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section \ref{sectionDuality} and based on Lie algebras.\\ The section is organized as follows: }
+Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section~\ref{sectionDuality} and based on Lie algebras.\\ The section is organized as follows: }
 
@@
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section \ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction} dynamics are added.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section~\ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction} dynamics are added.
 Particle can now change type {\color{blue} with two different mechanism: a \textit{pure mutation} (with rate $\Upsilon$) and a \textit{stirring-mutation} (at rate $\sigma_{12}$), i.e.
@@
 {\color{blue} We recall a general fact.
-Considering a generic $N-1$ species Markov process $(\bm{n}(t))_{t\geq 0}$ (where in the spirit of Section \ref{sec1}, $n_{A}^{x}$ denotes the number of particles or the number of holes at site $x$), we define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ and at time $t$ as
+Considering a generic $N-1$ species Markov process $(\bm{n}(t))_{t\geq 0}$ (where in the spirit of Section~\ref{sec1}, $n_{A}^{x}$ denotes the number of particles or the number of holes at site $x$), we define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ and at time $t$ as
 \begin{equation}

### 2023-12-17 main.tex
;

@@
 $(b)$ University of Parma, \\
-Department of Mathematical, Physical and and Computer Sciences\\
+Department of Mathematical, Physical and and Computer Sciences,\\
 Parco Area delle Scienze, 7/A, 43124 Parma, Italy\\

### 2023-12-19 main.tex
''

--- 2023-12-15 main.tex
@@
 $(b)$ University of Parma, \\
-Department of Mathematical, Physical and and Computer Sciences\\
+Department of Mathematical, Physical and Computer Sciences,\\
 Parco Area delle Scienze, 7/A, 43124 Parma, Italy\\

### 2023-12-20 main.tex
l
ll
''

@@
 Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities given in \eqref{abs-probabilities}.
+\begin{flushright}
+	$\square$
+\end{flushright}
 {\color{blue}\begin{remark}
@@
 \end{remark} }
-\begin{flushright}
-	$\square$
-\end{flushright}
 
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\dt
-\end{equation}
-(cf. \eqref{dualityElements}).
+	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\co
+\end{equation}
+cf.~\eqref{dualityElements}.
 \end{proposition}

### 2023-12-21 main.tex
try
revision-cristian-21Dec

@@
 We study the stirring process with $N-1$ species
-on a generic graph $G=(V,\mathcal{E})$ introduced with reservoirs.
+on a generic graph $G=(V,\mathcal{E})$  with reservoirs.
 The multispecies stirring process generalizes the symmetric exclusion process, 
@@
 \section{Introduction}
+
+\paragraph{Motivations.}
 Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics. In a boundary-driven system, the model is put in contact with reservoirs, 
-%at its {\color{red}``boundaries'' } imposing different particle densities, 
 and a current is generated through the system. In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current.
- The aim of this paper is to develop the theory of stochastic duality and  study the stationary measure of certain symmetric boundary-driven {\em multispecies} particle systems with exclusion.
-
 Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of {\em duality} \cite{schutzSandow}.
@@
 is simplified to the problem of computing the absorption probabilities of the dual particles.  
-
+ The aim of this paper is to develop the theory of stochastic duality and  study the stationary measure of certain symmetric boundary-driven {\em multispecies} particle systems with exclusion.
+
+\paragraph{The model.}
+The model we consider is the {\em  multispecies stirring process with open boundaries}, 
+i.e. the multispecies analogue of the exclusion process as introduced in \cite{zhou2021orthogonal}, 
+with additional boundary reservoirs as proposed in \cite{vanicat2017exact}. 
+In our set-up, particles can be of $N-1$ types (or species) and they can move
+on a generic connected and undirected graph $G=(V,\mathcal{E})$ with vertex set $V$ and
+edge set $\mathcal{E}$. The maximal number of particles allowed at each vertex (also called \textit{maximal occupancy}) is denoted by $\nu\in \mathbb{N}$. 
+Two particles do interact when they sit on two sites connected by a graph edge and this interaction consists in swapping them. 
+Furthermore, reservoirs are attached at each site of the graph, creating and removing particles. For a precise definition of the rates of the process 
+we refer to Section~\ref{sec1}. As we will see, the choice of the boundary reservoirs is motivated by the fact that they allow to determine an absorbing dual process, 
+regardless of the graph $G$ on which the process is defined and of the maximal occupancy $\nu$ at each site.
+
+A special case is obtained when the graph $G$ is a finite chain, 
+with two reservoirs attached to the first and the last sites respectively, 
+and the maximal number of particles allowed at each site is fixed to be $\nu=1$.
+In this case the multispecies stirring process with open boundaries 
+becomes integrable (see \cite{vanicat2017exact}). 
+%As a consequence,
+%we will show that in this case it is possible to compute correlation functions 
+%and the stationary state in a closed-form. 
 %In general, however,  there is little hope to compute the absorption probabilities exactly. 
-
-On one hand, this absorbing duality allows to write the non-equilibrium steady state in terms of these absorption probabilities and then
-one can deduce macroscopic properties. For instance this sufficed in  \cite{KMP} to prove local equilibrium for the KMP model.
-On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
-The situation simplifies {\color{blue} for the simple symmetric exclusion process \cite{schutzSandow} on the geometry of } a chain with two reservoirs on the boundary sites. 
-% {\color{blue}In this context, the process possesses an integrable structure, see e.g. \cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews. 
+%
+%On one hand, this absorbing duality allows to write the non-equilibrium steady state in terms of these absorption probabilities and then
+%one can deduce macroscopic properties. For instance this sufficed in  \cite{KMP} to prove local equilibrium for the KMP model.
+%On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
+%The situation simplifies {\color{blue} for the simple symmetric exclusion process \cite{schutzSandow} on the geometry of } a chain with two reservoirs on the boundary sites. 
+%% {\color{blue}In this context, the process possesses an integrable structure, see e.g. \cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews. 
 % 
 % }
-
 %Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.
@@
 %{\color{red} Explain here that we consider the chain with only two reservoirs at the end of the chain}
-
-For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
+We recall that for the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
 One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain, see e.g.
@@
 This integrability property can be combined with duality and leads to closed-form expressions for the correlations and the non-equilibrium steady state, as shown in \cite{frassek2020eigenstates,frassek2020duality}.
-% by extending the previous results of \cite{frassek2020eigenstates}.
-
-% \todo{moved down this last paragraph. all good?}
-
-The model studied in this paper is the {\em  multispecies stirring process with open boundaries}, i.e.
-the multispecies analogue of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}.
-This particle system is defined on a generic connected and undirected graph. At each site 
-the maximal number of allowed particles {\color{blue}(also called \textit{maximal occupancy})} is $\nu\in \mathbb{N}$.
-These particles can be of $N-1$ types (or species).
-Two sites do interact when there is an edge between them and this interaction consists in swapping the occupations of these two sites (for a precise definition of the process see Section~\ref{sec1}).
-Furthermore, reservoirs are attached at each site of the graph, creating and removing particle.
-The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}.
-{\color{blue}As we will see, this choice of the boundary reservoirs is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and  the maximal number of particle hosted at each site ($\nu$ can any natural number)}.\\
-{\color{blue}In this paper we concentrate our effort in studying the boundary driven symmetric multispecies model.
-In literature, also asymmetric multispecies  models have been introduced \cite{schutz2017kardar} and integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}.
-Moreover, different transition mechanisms (beyond the diffusive one) have been recently studied \cite{chatterjee2023multi}.
-Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}).
-As far as we know, in this last context integrability does not hold.}
+
+In this paper we focus on the multispecies stirring process with open bundaries.
+In particular we consider the symmetric multispecies models, see also  \cite{redig2022ergodic,floreani2022switching}.
+Asymmetric multispecies  models have been considered in \cite{schutz2017kardar, chatterjee2023multi, franceschini2022orthogonal}. 
+Integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}. 
+%Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}).
+As far as we know, in this last context integrability does not hold.
 %{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
@@
 
+% by extending the previous results of \cite{frassek2020eigenstates}.
+
+% \todo{moved down this last paragraph. all good?}
+
 %The  paper is organized as follows.
 % \subsubsection*{Organization of the paper}
-\paragraph{Organization of the paper}
-In Section~\ref{sec1} we define the open multispecies stirring
-process on a general graph and provide its Lie algebraic description in terms of $gl(N)$ generators. In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
+\paragraph{Organization of the paper and main results.}
+We start in Section~\ref{sec1} by defineing the open multispecies stirring
+process on a general graph and providing its Lie algebraic description in terms of the generators of the $gl(N)$ Lie algebra.
+In Section~\ref{sectionDuality} we prove an absorption duality (Theorem~\ref{thm-duality})
 and show that the problem of characterizing the non-equilibrium
@@
 In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
-particle per site, which is driven out-of-equilbrium by two reservoirs on the left and right boundaries.
+particle per site ($\nu=1$), which is driven out-of-equilbrium by two reservoirs on the left and right boundaries.
 In this case we obtain a closed-form expression for the stationary correlations (Theorem~\ref{thm-correlations}).
@@
 Finally in Section~\ref{sec5} we discuss a few extensions
-and generalizations of the model, including instantaneous thermalization limits and reaction-diffusions.
-{\color{blue} The first generalization, is to derive a formula, in terms of the absorption probabilities of the dual process, for the non-equilibrium steady state correlation $\nu\geq 1$, i.e.
-when more than one particle is allowed at each site.
-In this situation, integrability is lost and we cannot derive explicit formulas for these absorption probabilities.
-However, in Appendix \ref{appendix-1pts-general}, we show how to compute the one-point correlation by using the properties of a random walk.} The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process.
-Moreover, we show that it has an absorbing duality  {\color{blue}with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}).
-Finally, the third generalization is the introduction of an "ad-hoc" interaction mechanism of reaction type, in order to have closed evolution equation for average particle density (inspired by \cite{casini2022uphill,schutzReaction})}.
-{\color{blue}We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}}.
-Again, an absorbing duality is proved and the duality function turns out to be the same of the multispecies stirring process.
+and generalizations of the model.
+%, including instantaneous thermalization limits and reaction-diffusions. 
+The first generalization is the formula for the correlations for the boundary driven chain in the case when more than one particle is allowed at each site ($\nu > 1$). 
+In this situation integrability is lost and we cannot derive explicit formulas for the absorption probabilities.
+However, in Appendix \ref{appendix-1pts-general}, we show how to compute the one-point correlation by using the properties of a random walk.
+The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process and the formulation of the the absorbing duality with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}).
+Finally, the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities (inspired by \cite{casini2022uphill,schutzReaction}).
+We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}. 
+Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.  
 % In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
@@
 
-\bigskip
-
-{\bf Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM),  the INFN grant Gauge and String Theory (GAST),  the PRIN project CUP-E53D23002220006,  the FAR UNIMORE project CUP-E93C23002040005 and  the INdAM–GNFM project CUP-E53C22001930001.
+\paragraph{Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM),  the INFN grant Gauge and String Theory (GAST),  the PRIN project CUP-E53D23002220006,  the FAR UNIMORE project CUP-E93C23002040005 and  the INdAM–GNFM project CUP-E53C22001930001.
 
@@
 with open boundaries. 
-In words, the process is described as follows. Each site
+%In words, the process is described as follows. 
+Each site
 of a connected graph can host a maximal number of particles called $\nu\in \mathbb{N}$ .
@@
 \begin{equation}\label{implicit-mass-function}
-	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{red}
-	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\right)\right]}\,.
-\end{equation}
-% {\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation
-% \eqref{exactCorrelations}.} 
+	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{black}
+	\mathbb{E}\left[\Bigg( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\Bigg) \Bigg(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\Bigg)\right]}\,.
+\end{equation} 
 \end{corollary}
-{\color{blue} Here $\mu(\bm{\tau})$ is the  non-equilibrium steady probability of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
+%{\color{blue} Here $\mu(\bm{\tau})$ is the  non-equilibrium steady probability of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
 However, from Corollary~\ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
@@
 Then, equation \eqref{implicit-mass-function} is derived (for details see below the proof of Corollary~\ref{Corollary-NESS-ABS}).\\
- The expectation on the right-hand-side of \eqref{implicit-mass-function} contains only indicators of particles configurations: indeed in the first product  $\tau_{x}\neq N$ are considered, while in the second product we have $a_{k}\neq N$ for all $k\in\{1,\ldots,N\}$.
+% The expectation on the right-hand-side of \eqref{implicit-mass-function} contains only indicators of particles configurations: indeed in the first product  $\tau_{x}\neq N$ are considered, while in the second product we have $a_{k}\neq N$ for all $k\in\{1,\ldots,N\}$.
 As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary~\ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
 For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\
-{\color{blue} \paragraph{Example for an $L=2$ chain.} To clarify equation \eqref{implicit-mass-function} we report the example of a chain with $L=2$, where we compute the probability mass functions of three configurations.
-Without loss of generality we assume that the particles are always of species $1$.
-We have that
+\paragraph{Example for an $L=2$ chain.} To clarify equation \eqref{implicit-mass-function} we report the example of a chain with $L=2$, where we compute the probability mass functions of three configurations.
+Without loss of generality we write only the formulae involving particles of species $1$.
+We have:
  \begin{itemize}
@@
  	\end{equation}
- 	Here the right-hand-side corresponds to $b=0$ and average can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
+ 	Here we have only one term corresponding to $b=0$ in formula  \eqref{implicit-mass-function}.
+	%and average can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
  	\item probability of the first site occupied and the second empty:
@@
  	\end{align}
- 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
+	Here we have two terms, the first corresponding to $b=0$  and the second corresponding to $b=1$ in formula  \eqref{implicit-mass-function}.
+% 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
 The second term on the right-hand-side corresponds to $b=1$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=1,\;a_{2}=a$ for all $a=1,\ldots N-1$.
@@
  	\end{align}
- 	Here the first term on the right-hand-side corresponds to $b=0$ and since $\bm{\tau}=(N,N)$ we obtain $1$.
-The second and the third term on the right-hand-side correspond to $b=1$.
-They can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively.
-The fourth term on the right-hand-side corresponds to $b=2$ and it can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$.
- \end{itemize}}
+ 	Here the first term on the right-hand-side corresponds to $b=0$ and since $\bm{\tau}=(N,N)$ we obtain $1$. The second and the third term correspond to $b=1$. 
+	%They can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively. 
+	The fourth term corresponds to $b=2$.
+	%and it can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$. 
+ \end{itemize}
 \textbf{Proof of Corollary~\ref{Corollary-NESS-ABS}:}
@@
 \end{flushright}
-{\color{blue}\begin{remark}
+\begin{remark}
 From equation \eqref{corr-psi1}, we observe that, for any configuration $\bm{\tau}$ that has at least a particle, we interpret the coefficient $\Psi^{'}(\tau)$ of the vector $|\Psi^{'}\rangle$ as a correlation.
@@
 In particular, these marginal are the non-equilibrium steady state correlations as soon as the configuration $\bm{\tau}$ does contain at least a particle.
-\end{remark} }
+\end{remark}
 
@@
                     \sum_{\sigma=1}^N\langle \sigma|  \quad\text{if}\quad \tau=N\\
-                    \langle \tau| \quad\text{else} 
+                    \langle \tau| \qquad\qquad\text{else} 
                    \end{cases}\,,
@@
 \label{sec5}
-{\color{blue}In Section~\ref{sectionIntegrabiliy} we have shown that, combining duality and integrability of the multispcies stirring process with $\nu=1$ and on the geometry of chain with two boundaries, the non-equilibrium steady state can be found in an explicit form.
+In Section~\ref{sectionIntegrabiliy} we have shown that, combining duality and integrability of the multispcies stirring process with $\nu=1$ and on the geometry of chain with two boundaries, the non-equilibrium steady state can be found in an explicit form.
 As soon as $\nu>1$ the integrability property is lost, but duality still holds.
@@
 Inspired by the results for the thermalized version of the symmetric exclusion process reported in \cite{carinci2013duality}, in this section we also investigate its multispecies counterpart.
-More precisely, we try to answer these questions: \textit{can we define a thermalized version of the boundary driven multispecies stirring process?
-Does this thermalized process keep the absorbing duality properties as in the single species case?} Again, we restrict our analysis on the chain with two reservoirs at the end sites.
-\\ Finally we add a reaction mechanism of transition to the boundary driven multispeices stirring process.
-The aim is to answer the following question: \textit{Can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?} Moreover, in \cite{casini2022uphill} the duality for this reaction-diffusion process was proved only for the equilibrium case and the result was achieved by direct computation (without using a $gl(3)$ symmetry).
-Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section~\ref{sectionDuality} and based on Lie algebras.\\ The section is organized as follows: }
-
+More precisely, we ask whether a thermalized version of the boundary driven multispecies stirring process can be defined and if it keeps the absorbing duality properties as in the single species case.
+Again, we restrict our analysis on the chain with two reservoirs at the end sites.
+Finally we add a reaction mechanism of transition to the boundary driven multispecies stirring process.
+The aim is to answer the following question: Can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?
+Moreover, in \cite{casini2022uphill} the duality for this reaction-diffusion process was proved only for the equilibrium case and the result was achieved by direct computation (without using a $gl(3)$ symmetry).
+Thus, we also investigate if this last duality result can be extended to a boundary driven process by using an approach similar to the one of Section~\ref{sectionDuality} and based on Lie algebras.
+The section is organized as follows:
 %In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model \todo{which model?} is exactly solvable using integrability.  
@@
 \begin{enumerate}
-	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting the duality, the steady state correlations {\color{blue} of the boundary driven multispecies stirring process on a chain with two reservoirs} is expressed in terms of absorption probabilities of the dual particles.
+	\item \textit{Correlations} (Section~\ref{Subsection-ss-nonI}): exploiting the duality, the steady state correlations {\color{black} of the boundary driven multispecies stirring process on a chain with two reservoirs} is expressed in terms of absorption probabilities of the dual particles.
 These probabilities are hard to find when $\nu>1$.
@@
 Also for this thermalized process we prove duality.
-	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{blue} starting from the usual stirring dynamics (see Section~\ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{blue}two further reaction} dynamics are added.
-Particle can now change type {\color{blue} with two different mechanism: a \textit{pure mutation} (with rate $\Upsilon$) and a \textit{stirring-mutation} (at rate $\sigma_{12}$), i.e.
-a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own species.} {\color{blue} This reaction-diffusion} model   is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
-{\color{blue} Exploiting the $gl(N)$ symmetry of this reaction-diffusion process, absorbing duality} for the boundary driven process is also proved.
+	\item \textit{Reaction-diffusion process} (Section~\ref{Subsection-RD}): {\color{black} starting from the usual stirring dynamics (see Section~\ref{sec1}) where particles and holes are exchanged in two nearest neighbour sites (now at a constant rate $\sigma_{11}$),} {\color{black}two additional reaction} dynamics are added.
+Particle can now change type {\color{black} with two different mechanism: a \textit{pure mutation} (with rate $\Upsilon$) and a \textit{stirring-mutation} (at rate $\sigma_{12}$), i.e.
+a transition where particles perform an exchange of their occupancies at nearest neighbour sites but, at the same time, they also mutate their own species.} {\color{black} This reaction-diffusion} model   is  constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}.
+{\color{black} Exploiting the $gl(N)$ symmetry of this reaction-diffusion process, absorbing duality} for the boundary driven process is also proved.
 \end{enumerate}
-{\color{blue}As already pointed out at the beginning, in this section we always assume that the geometry is a chain of length $L$ where two reservoirs are connected to the end sites $1$ and $L$.
+{\color{black}In this section we always assume that the geometry is a chain of length $L$ where two reservoirs are connected to the end sites $1$ and $L$.
 In all the three investigated situations, we denote the original processes by the variables $\left(\bm{n}(t)\right)_{t\geq0}$, while their dual processes is denoted by the variables  $(\bm{\xi}(t))_{t\geq 0}$.
@@
 We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
-For every $m\in\{1,\ldots,L\}$ we consider {\color{blue}the coordinates $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
+For every $m\in\{1,\ldots,L\}$ we consider {\color{black}the coordinates $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
 We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
@@
 \end{equation}
-{\color{blue}As already pointed out,} the duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
+The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
 \begin{equation}
@@
 \end{equation}
-where $C(\nu,m)$ is a constant that depends on $m$ and {\color{blue}on the maximal occupancy} per site $\nu$. 
+where $C(\nu,m)$ is a constant that depends on $m$ and {\color{black} on the maximal occupancy} per site $\nu$. 
 Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$point correlations in the non-equilibrium steady state.
@@
 \subsection{Multispecies stirring process with reaction} \label{Subsection-RD}
-{\color{blue} We recall a general fact.
-Considering a generic $N-1$ species Markov process $(\bm{n}(t))_{t\geq 0}$ (where in the spirit of Section~\ref{sec1}, $n_{A}^{x}$ denotes the number of particles or the number of holes at site $x$), we define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ and at time $t$ as
+{\color{black}  Considering a generic $N-1$ species Markov process $(\bm{n}(t))_{t\geq 0}$ (where in the spirit of Section~\ref{sec1}, $n_{A}^{x}$ denotes the number of particles or the number of holes at site $x$), we define the average density occupation of species $a\in\{1,\ldots,N-1\}$ at site $x$ and at time $t$ as
 \begin{equation}
@@
 \end{equation} }
-In \cite{casini2022uphill} {\color{blue}it has been defined a process with two species $a=1,2$ and the holes (denoted by $0$ in that context)} whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied by a proper diffusivity constant) and a linear reaction term (mutation), i.e.
+In \cite{casini2022uphill} {\color{black}it has been defined a process with two species $a=1,2$ and the holes (denoted by $0$ in that context)} whose evolution equation for the average occupation $\rho_{a}(x,t)$ of species $a\in \{1,2\}$ is given by a difference-differential equation with two discrete Laplacians (one for each species, multiplied by a proper diffusivity constant) and a linear reaction term (mutation), i.e.
 \begin{equation}\label{2SpeciesRD}
@@
 \end{align} 
-{\color{blue}We introduce the dual configuration constructed by attaching two extra-sites (without any particle) to the vector $\bm{\tau}$, transforming its dimension from $L$ to $L+2$.
+{\color{black}We introduce the dual configuration constructed by attaching two extra-sites (without any particle) to the vector $\bm{\tau}$, transforming its dimension from $L$ to $L+2$.
 We denote it by $\bm{\xi}(\bm{\tau})=(0,\tau_{1},\ldots,\tau_{L},0)$, where we wrote $0$ in the two extra-sites to indicate that no dual particles are present there.}  More explicitly, this dual configuration is given by
@@
 	\end{cases}\dt
-\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and, {\color{blue} since no dual particles are present in the extra-sites $0$ and $L+1$}, we have
+\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and, {\color{black} since no dual particles are present in the extra-sites $0$ and $L+1$}, we have
 \begin{align}\label{useful-InInterpretation}
@@
 Equivalently, we can interpret the components of $\Psi'(\bm{\tau})$ as follows.
-Let $\ell$ be the number of sites {\color{blue}occupied by a particle} in the configuration $\bm{\tau}$, i.e.
+Let $\ell$ be the number of sites {\color{black}occupied by a particle} in the configuration $\bm{\tau}$, i.e.
 $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$.
@@
 To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$.
-This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries {\color{blue}is absorbed at extra-site $0$.
-It fulfils the following equations discrete Laplace equation}
+This is the probability that a random walker
+(started at $x$) on the chain $\{1,\ldots,L\}$ with absorbing boundaries {\color{black}is absorbed at extra-site $0$. It fulfils the following equations discrete Laplace equation}
 \begin{equation}\label{gamblers-ruin}

### 2023-12-22 main.tex
citations updated

@@
 with additional boundary reservoirs as proposed in \cite{vanicat2017exact}. 
+The hydrodynamic limit and fluctuations of the multispecies stirring process on $\mathbb{Z}^d$
+has been recently studied in \cite{casini2023density}.
 In our set-up, particles can be of $N-1$ types (or species) and they can move
@@
 This integrability property can be combined with duality and leads to closed-form expressions for the correlations and the non-equilibrium steady state, as shown in \cite{frassek2020eigenstates,frassek2020duality}.
-
-In this paper we focus on the multispecies stirring process with open bundaries.
-In particular we consider the symmetric multispecies models, see also  \cite{redig2022ergodic,floreani2022switching}.
-Asymmetric multispecies  models have been considered in \cite{schutz2017kardar, chatterjee2023multi, franceschini2022orthogonal}. 
-Integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}. 
+In this paper we focus on the multispecies stirring process with open boundaries.
+We choose to restrict to the symmetric version of the model, as the formulation
+of duality in the presence of both asymmetry and boundary driving is substantially
+more involved (for recent results on the single species case see \cite{schuetz2022reverse}).
+%, see also  \cite{redig2022ergodic,floreani2022switching}.
+%Asymmetric multispecies  models have been considered in \cite{schutz2017kardar, chatterjee2023multi, franceschini2022orthogonal}. 
+%Integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}.
+
 %Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}).

### 2023-12-22 main.tex
''

@@
  \end{equation} 
- where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal, we further refer the reader to \cite{Alcaraz:1992zc,2005NuPhB.711..565M,SSEPReviewRagoucy,frassek2020eigenstates} where this idea was explored for the monospecies case.
+ where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal, we further refer the reader to \cite{alcaraz,melo2005bethe,SSEPReviewRagoucy,frassek2020eigenstates} where this idea was explored for the monospecies case.
 Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} simplify significantly.

### 2023-12-22 main.tex
''

@@
 For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is fully determined by the correlations of equation \eqref{exactCorrelations} through the relation
+{\color{blue}
 \begin{equation}\label{implicit-mass-function}
-	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{black}
-	\mathbb{E}\left[\Bigg( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\Bigg) \Bigg(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\Bigg)\right]}\,.
-\end{equation} 
+	\mu(\bm{\tau})=
+	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]
+\end{equation}}
+%\begin{equation}\label{implicit-mass-function}
+%	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{black}
+%	\mathbb{E}\left[\Bigg( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\Bigg) \Bigg(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\Bigg)\right]}\,.
+%\end{equation} 
 \end{corollary}
@@
  	\end{equation}
- 	Here we have only one term corresponding to $b=0$ in formula  \eqref{implicit-mass-function}.
+ 	Here we have only one term corresponding to $m=2$ in formula  \eqref{implicit-mass-function}.
 	%and average can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
@@
  	\end{align}
-	Here we have two terms, the first corresponding to $b=0$  and the second corresponding to $b=1$ in formula  \eqref{implicit-mass-function}.
+	{\color{blue}Here in the last equality we have two terms: the first corresponding to $m=1$ (with $x_{1}=1$) and the second corresponding to $m=2$ in formula \eqref{implicit-mass-function}.}
 % 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
@@
  	\end{align}
- 	Here the first term on the right-hand-side corresponds to $b=0$ and since $\bm{\tau}=(N,N)$ we obtain $1$. The second and the third term correspond to $b=1$. 
+ 	{\color{blue}Here in the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}.
+}
 	%They can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively.
-	The fourth term corresponds to $b=2$.
+
 	%and it can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$. 
@@
 =&
-\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}
+\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{x_{1}=1}^{L}\delta_{\tau_{x_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{x_{1}}
 =
 a_{1}\}}\right\}+\nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{1},a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{1}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{2}\}}\right\}+\ldots+
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq x_{1}<x_{2}\leq L}\delta_{\tau_{x_{1}},N}\delta_{\tau_{x_{2}},N}\sum_{a_{1},a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{Y_{x_{2}}=a_{2}\}}\right\}+\ldots+
 \nonumber\\
-+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots,a_{L-\ell}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{q_{k}}=a_{k}\}}\dt
++&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq x_{1}<\ldots<x_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{x_{k}},N}\right)\sum_{a_{1},\ldots,a_{L-\ell}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\dt
 \end{align} 
 % \todo{indices are strange. Say what happens here}
-Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.
-{Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
+{\color{blue}In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered.
+Similarly, the second addend is the product of the indicator of $\ell+1$ sites.
+Indeed, in addition to the $\ell$ occupied sites of $\bm{\tau}$ one empty site is in turn chosen and its hole is filled with all possible particles.
+In the next addends the idea is repeated with $2,3,...L-\ell$ empty sites in turn filled with all possible particles.
+We notice that the exponent of the factors (-1) is given by the number of holes that have been turned into particles.
+Then, we introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated sites.
+For each $m$ we introduce the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$.
+Then, we associate to to each of these $m$ one of the addend in \eqref{sum}.
+In particular, for $m=\ell$ we associate the first addend and we rewrite it as
+	\begin{align}
+		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
+	\\	=&
+		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
+	\end{align}
+	Similarly, the second addend in \eqref{sum} is associate to $m=\ell +1$ and it is rewritten as 
+	\begin{align}
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{x_{1}=1}^{L}\delta_{\tau_{x_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{x_{1}}
+	=
+	a_{1}\}}\right\}
+			\\=&
+		\sum_{1\leq x_{1}<\ldots<x_{\ell+1}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell+1}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell+1}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell+1}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
+	\end{align}
+	The idea goes on for $m=\ell+2,\ldots L$ and we obtain that 
+\begin{align}
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_x=a\}}\right)\right)\nonumber\\
+=&
+\sum_{m=\ell}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}
+\end{align}
+The above sum can be extended from $m=0$ since all the terms before $m=0,\ldots,\ell-1$ are vanishing. 
+Finally, by taking the expectation with respect to the steady state distribution we obtain \eqref{implicit-mass-function}.}  %{Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.} }
 \begin{flushright}
@@
 \end{equation}
-
-		Considering 
-		\begin{equation}
-			|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
-		\end{equation} we obtain  
+	By inserting the resolution of identity $\sum_{\bm{\sigma}\in \Omega^{'}} |\bm{\sigma}\rangle\langle\bm{\sigma}|$ we have that 
+{\color{blue}
+	\begin{align}
+		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle=\langle \bm{\tau}|S^{-1}_{1}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{-1}|\bm{\sigma}\rangle \langle \bm{\sigma}|\Psi^{'}\rangle\dt
+		%=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
+	\end{align}
+	%Considering 
+	%\begin{equation}
+	%|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
+	%\end{equation} and 
+	Using \eqref{Tensor-S1} we obtain 
 			 \begin{align}\label{implicit-PSI-PSIp}
-			\Psi(\bm{\tau})=&\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
-			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
-			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
-		\end{align} 
-			{In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupation variables $a_{1},\ldots,a_{b}$.
-In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$, taking into account the Kronecker deltas.} Here, the notation
+			\Psi(\bm{\tau})=&\sum_{m=0}^{L}\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x_{k}},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\nonumber\\
+			\times &			
+			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
+			%=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
+			%=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
+		\end{align} 
+			In the second equality we have rewritten the product by introducing the summation over $m$, the coordinates $x_{1},\ldots,x_{m}$ and the occupation variables $b_{1},\ldots,b_{m}$.
+Here, the notation
 		\begin{equation}\label{notation-PSI}
-			\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
-		\end{equation}
-		means that, {given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
+		%	\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
+			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
+		\end{equation}
+		indicates that in positions $x_{1},\ldots,x_{m}$ we have particles of species $b_{1},\ldots,b_{m}$ and we have holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
 }  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}.

### 2023-12-22 main.tex
New Formula Corollary 2

@@
 	\mu(\bm{\tau})=
-	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]
+	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]
 \end{equation}}
@@
  	\end{equation}
- 	Here we have only one term corresponding to $m=2$ in formula  \eqref{implicit-mass-function}.
+ 	Here we have only one term corresponds to $m=2$ in formula  \eqref{implicit-mass-function}.
 	%and average can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
@@
  	\end{align}
-	{\color{blue}Here in the last equality we have two terms: the first corresponding to $m=1$ (with $x_{1}=1$) and the second corresponding to $m=2$ in formula \eqref{implicit-mass-function}.}
+	{\color{blue}In the last equality we have two terms: the first corresponds to $m=1$ (with $x_{1}=1$) and the second corresponds to $m=2$ in formula \eqref{implicit-mass-function}.}
 % 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
@@
  	\end{align}
- 	{\color{blue}Here in the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}.
+ 	{\color{blue}In the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}.
 }
@@
 {\color{blue}In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered.
-Similarly, the second addend is the product of the indicator of $\ell+1$ sites.
-Indeed, in addition to the $\ell$ occupied sites of $\bm{\tau}$ one empty site is in turn chosen and its hole is filled with all possible particles.
-In the next addends the idea is repeated with $2,3,...L-\ell$ empty sites in turn filled with all possible particles.
-We notice that the exponent of the factors (-1) is given by the number of holes that have been turned into particles.
-Then, we introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated sites.
-For each $m$ we introduce the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$.
+Similarly, the second addend is the product of the indicator of $\ell+1$ occupied sites.
+Indeed, in addition to the $\ell$ occupied sites of the configuration $\bm{\tau}$, one empty site is in turn chosen and its hole is filled with all possible species particles.
+The idea is repeated in the next addends with $2,3,...L-\ell$ empty sites that are, in turn, filled with all possible species of particles.
+We notice that the exponent of the factors (-1) is given by the number of holes that have been filled with all possible species of particles.
+We introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated site and we define the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$.
 Then, we associate to to each of these $m$ one of the addend in \eqref{sum}.
@@
 	\begin{align}
-		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
-	\\	=&
-		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
-	\end{align}
-	Similarly, the second addend in \eqref{sum} is associate to $m=\ell +1$ and it is rewritten as 
+		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&%\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
+	%\\	=&
+		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}})\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
+	\end{align}
+	Similarly, the second addend in \eqref{sum} is associated to $m=\ell +1$ and it is rewritten as 
 	\begin{align}
@@
 			\\=&
-		\sum_{1\leq x_{1}<\ldots<x_{\ell+1}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell+1}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell+1}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell+1}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
+		\sum_{1\leq x_{1}<\ldots<x_{\ell+1}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell+1}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell+1}=1}^{N-1}\left(\prod_{k=1}^{\ell+1}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}})\right)\left(\prod_{k=1}^{\ell+1}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
 	\end{align}
@@
 =&
-\sum_{m=\ell}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}
-\end{align}
-The above sum can be extended from $m=0$ since all the terms before $m=0,\ldots,\ell-1$ are vanishing. 
+\sum_{m=\ell}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\left(\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
+\end{align}
+The above sum can be extended until $m=0$ since all the terms $m=0,\ldots,\ell-1$ are vanishing. 
 Finally, by taking the expectation with respect to the steady state distribution we obtain \eqref{implicit-mass-function}.}  %{Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.} }
@@
 			 \begin{align}\label{implicit-PSI-PSIp}
-			\Psi(\bm{\tau})=&\sum_{m=0}^{L}\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x_{k}},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\nonumber\\
+			\Psi(\bm{\tau})=&\sum_{m=0}^{L}\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\nonumber\\
 			\times &			
@@
 		\end{equation}
-		indicates that in positions $x_{1},\ldots,x_{m}$ we have particles of species $b_{1},\ldots,b_{m}$ and we have holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
+		indicates that in positions $x_{1},\ldots,x_{m}$ there are particles of species $b_{1},\ldots,b_{m}$, while there are holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
 }  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}.

### 2023-12-22 main.tex
fix bib

@@
 of duality in the presence of both asymmetry and boundary driving is substantially
-more involved (for recent results on the single species case see \cite{schuetz2022reverse}).
+more involved (for recent results on the single species case see
+\cite{schuetz2022reverse}).
 %, see also  \cite{redig2022ergodic,floreani2022switching}.

### 2023-12-24 main.tex
added barrauqand corwin duality paper
ok
kk

@@
 for the case of the one-dimensional chain with two reservoirs
-at the boundaries and with maximally one particle per site. Based on the results of \cite{vanicat2017exact},
-we compute the absorption probabilities by relying
+at the boundaries and with maximally one particle per site.
+% Based on the results of \cite{vanicat2017exact},
+We compute the absorption probabilities by relying
 on the underlying ${gl}(N)$ symmetry and the
@@
 more involved (for recent results on the single species case see
-\cite{schuetz2022reverse}).
+\cite{schuetz2022reverse,barraquand2022markov}).
 %, see also  \cite{redig2022ergodic,floreani2022switching}.
@@
 
-%Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}).
-As far as we know, in this last context integrability does not hold.
-%{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
-%We refer to the model as the {\em  multispecies stirring process with open boundaries}.
-%
-
-% by extending the previous results of \cite{frassek2020eigenstates}.
-
-% \todo{moved down this last paragraph. all good?}
-
-%The  paper is organized as follows.
-% \subsubsection*{Organization of the paper}
 \paragraph{Organization of the paper and main results.}
@@
 steady state can be reduced to the computation of the absorption probabilities similar to the single-species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}.  
-% The duality is proved for a system whose spatial structure is described by a general graph.
 In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
@@
 and generalizations of the model. 
-%, including instantaneous thermalization limits and reaction-diffusions. 
 The first generalization is the formula for the correlations for the boundary driven chain in the case when more than one particle is allowed at each site ($\nu > 1$). 
@@
 Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.
-% In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
-% model with non-compact Lie algebras, both integrable and non-integrable, which will be presented in a 
-% future paper. 
-% \todo{I prefer to remove this sentence}
 
@@
 \paragraph{Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM),  the INFN grant Gauge and String Theory (GAST),  the PRIN project CUP-E53D23002220006,  the FAR UNIMORE project CUP-E93C23002040005 and  the INdAM–GNFM project CUP-E53C22001930001.
+RF thanks  Rodrigo A.
+Pimenta for related discussions.
 
@@
 	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N})\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]
-\end{equation}}
+\end{equation}
+where $\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}=(-1)^{\delta_{\tau_{x_{k}},N}}$.
+}
 %\begin{equation}\label{implicit-mass-function}
@@
 We introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated site and we define the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$.
-Then, we associate to to each of these $m$ one of the addend in \eqref{sum}.
+Then, we associate to each of these $m$ one of the addend in \eqref{sum}.
 In particular, for $m=\ell$ we associate the first addend and we rewrite it as

### 2023-12-24 main.tex
''

@@
 and show that the problem of characterizing the non-equilibrium
-steady state can be reduced to the computation of the absorption probabilities similar to the single-species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}.  
+steady state can be reduced to the computation of the absorption probabilities similar to the single species case on the line  \cite{KMP} and for a general graph \cite{ frassek2020duality}.  
 In Section~\ref{sectionIntegrabiliy}  we consider  the case of the one-dimensional chain with at most one 
@@
 
-% For recent examples in the framework of singlespecies systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
+% For recent examples in the framework of single species systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
 % {\color{red}
@@
 \subsection{Strategy}
- In the next Section~\ref{subsection-exact} we will show that the DEHP albegra in \eqref{bulk}-\eqref{rightBoundary} can be simplified substantially using the ${gl}(N)$ invariance of the bulk.
+ In the next Section~\ref{subsection-exact} we will show that the DEHP algebra in \eqref{bulk}-\eqref{rightBoundary} can be simplified substantially using the ${gl}(N)$ invariance of the bulk.
 In fact, such simplification can always be achieved if
@@
 \end{remark}
-\subsection{The single-species case (SSEP)}
-The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {i.e.
+\subsection{The single species case (SSEP)}
+The computations made for the multispecies stirring process can be specialized to the single species case $N=2$, {i.e.
 when only one type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}.

### 2023-12-24 main.tex
^^

@@
 \usepackage[T1]{fontenc}
-%\usepackage{microtype}
 \usepackage[pagebackref=false]{hyperref}
@@
 
-% %%%%%  TODO NOTES ETC  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-% \usepackage[left=1.7cm,right=4.3cm,bottom=4cm]{geometry}
-% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-% \definecolor{todocolor}{HTML}{D7E1E5}
-% \usepackage[textsize=tiny, 
-%             backgroundcolor=todocolor, 
-%             bordercolor=todocolor, 
-%             linecolor=todocolor, 
-%             textwidth=3.9cm]{todonotes}
-% \newcommand{\todoWARN}[1]{\todo{\colorbox{yellow}{\parbox{3.4cm}{#1}}}}
-% \newcommand{\todoERR}[1]{\todo{\colorbox{red}{\parbox{3.4cm}{#1}}}}
-% \usepackage{comment}
-% \usepackage{rotating}
-% \usepackage[left]{showlabels}
-% \renewcommand{\showlabelfont}{\tiny}
-% \renewcommand{\showlabelsetlabel}[1]
-% {\begin{turn}{65}\showlabelfont \llap{#1}\end{turn}}
-% \newcommand{\wiptitle}[1]{
-%     \par\noindent\hspace*{-0.5cm}\texttt{\scriptsize\color{gray} \lbrack #1\rbrack} \par\noindent\ignorespaces}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\usepackage[textsize=tiny]{todonotes}
-
-% \usepackage[notref,notcite]{showkeys}
 \usepackage{xspace}
-%\usepackage{bibentry}
-%\usepackage{easybmat}
 
@@
 
-%\usepackage[numbers,sort&compress]{natbib}
-%\usepackage{hypernat}
-
 \usepackage{tikz}
 \usetikzlibrary{decorations.pathreplacing}
-% MACROS
-% % 
-% \newcommand{\cristian}[1]{{\bf (* {\color{ForestGreen}V:{} \small #1}*)}}
-% \newcommand{\jorge}[1]{{\bf (* {\color{BlueViolet}G:{} \small #1}*)}}
-% \newcommand{\rouven}[1]{{ (* {\color{red}{} \small #1}*)}}
+
 \newtheorem{definition}{Definition}
@@
 
-%%%%%  oscillators
 \newcommand{\osc}[1]{\mathbf{#1}}
@@
 
-\newcommand*\pFq[6][8]{%
-  \begingroup % only local assignments
+\newcommand*\pFq[6][8]{
+  \begingroup s
   \pFqmuskip=#1mu\relax
   \mathchardef\normalcomma=\mathcode`,
-  % make the comma math active
+
   \mathcode`\,=\string"8000
-  % and define it to be \pFqcomma
+
   \begingroup\lccode`\~=`\,
   \lowercase{\endgroup\let~}\pFqcomma
-  % typeset the formula
+
   {}_{#2}\phi_{#3}{\left[\genfrac..{0pt}{}{#4}{#5};#6\right]}%
@@
 \begingroup
-% \centering
+
 \begin{center}
  \begingroup\LARGE
-% \bf Exact solution of the multispecies stirring process \\
-%  with open boundaries
 
@@
 
- %Università degli Studi di Modena e Reggio Emilia
 $(a)$ University of Modena and Reggio Emilia, \\
@@
 Parco Area delle Scienze, 7/A, 43124 Parma, Italy\\
- %
 \par\endgroup
@@
 
-% Version: \today
 \end{center}
-%
 
@@
 at the boundaries and with maximally one particle per site.
-% Based on the results of \cite{vanicat2017exact},
 We compute the absorption probabilities by relying
@@
 \end{abstract}
-
-%\vfill
 
@@
 becomes integrable (see \cite{vanicat2017exact}). 
-%As a consequence,
-%we will show that in this case it is possible to compute correlation functions 
-%and the stationary state in a closed-form. 
-%In general, however,  there is little hope to compute the absorption probabilities exactly. 
-%
-%On one hand, this absorbing duality allows to write the non-equilibrium steady state in terms of these absorption probabilities and then
-%one can deduce macroscopic properties. For instance this sufficed in  \cite{KMP} to prove local equilibrium for the KMP model.
-%On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
-%The situation simplifies {\color{blue} for the simple symmetric exclusion process \cite{schutzSandow} on the geometry of } a chain with two reservoirs on the boundary sites. 
-%% {\color{blue}In this context, the process possesses an integrable structure, see e.g. \cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews. 
-% 
-% }
-%Recently, probabilistic techniques have been developped to compute absorption probabilities for the simple symmetric exclusion process \cite{floreani2023non}.
-%Say that for a  general graph with boundaries attached to any site, this is a difficult task. 
-% However,  for the case of integrable systems they can be computed exactly in closed-form.
-%{\color{red} Explain here that we consider the chain with only two reservoirs at the end of the chain}
 We recall that for the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}.
@@
 \cite{schutzManyBody,SSEPReviewRagoucy} for two excellent reviews.
-%
 This integrability property can be combined with duality and leads to closed-form expressions for the correlations and the non-equilibrium steady state, as shown in \cite{frassek2020eigenstates,frassek2020duality}.
@@
 \cite{schuetz2022reverse,barraquand2022markov}).
-%, see also  \cite{redig2022ergodic,floreani2022switching}.
-%Asymmetric multispecies  models have been considered in \cite{schutz2017kardar, chatterjee2023multi, franceschini2022orthogonal}. 
-%Integrability results have been proved both with \cite{crampe2016integrable, finn2018matrix} and without boundary driving \cite{mallick1,mallick2}.
 
@@
 Here the computation
-% of the absorption probabilities 
 relies on the extension of the  Matrix Product Ansatz \cite{derrida1993exact} to multiple species \cite{vanicat2017exact} and the $gl(N)$ invariance of the process in the bulk.
@@
 
-% {\color{magenta} Cristian I think it is good to keep some of the following citations, especailly the one to Schutz...
-%  \cite{schutz2017kardar, crampe2016integrable, finn2018matrix, chatterjee2023multi,redig2022ergodic, floreani2022switching} and
-
-% \cite{casini2023density,  franceschini2022orthogonal,redig2023equilibrium,floreani2023non,carinci2023open}
-% See also \cite{crampe2016integrable, finn2018matrix} for the asymmetric setup.}
-
-% For recent examples in the framework of single species systems, see \cite{frassek2020eigenstates, frassek2020duality,frassek2022exact}.
-% {\color{red}
-% Here we generalize the duality approach to the set-up of multispecies particle systems.}
-
-% {\color{blue} I think this is to general...  Do all the references study the steady state? Also the main point is about duality no?}
-
-% {\color{red} Missing the part about non integrable model and duality.}
-
 \paragraph{Acknowledgments.} We acknowledge support from Istituto Nazionale di Alta Matematica (GNFM),  the INFN grant Gauge and String Theory (GAST),  the PRIN project CUP-E53D23002220006,  the FAR UNIMORE project CUP-E93C23002040005 and  the INdAM–GNFM project CUP-E53C22001930001.
@@
 
-% Prin-project {\color{blue} xxxx}, FAR-project {\color{blue} xxxx} UniMoRe.
-% 
-% INFN Progetto Giovani
-
-%
-%{\color{blue}
-%In the past years duality has been developed to study stochastic processes, especially in the boundary driven case, i.e.
-when the system is put in contact with boundaries that generate a non-equilibrium current.
-The literature is huge.
-We can address , for instance, to \cite{giardina2009duality,carinci2013duality,frassek2020duality}.
-One application of duality is the attempt to characterize the non equilibrium steady state of boundary driven process via the so called absorption probabilities.
-Indeed, there are many cases where the dual process has absorbing boundaries.
-This means that the the chain is eventually empty in the long time scale.
-Moreover, there are cases in which the steady state of a stochastic process can be computed explicitly, thanks to the integrability property of the system (quantum inverse scattering method, matrix product ansatz).
-In this direction, some examples can be found in \cite{derrida1993exact,frassek2019non,frassek2020eigenstates}.
-In the past, the focus has been on processes where one can distinguish, in each site of a certain graph, a (or many) particles or an empty state.
-However, this particles are indistinguishable, in the sense that you can pile up in a site just one type of particles.
-Some natural questions arise: what happens if we imagine to assign different colours to the particles?
-Is the duality property still holding?
-How far can we push our analysis for the characterization of the non equilibrium steady state?\\
-%The way one can define a multi-type (or multispecies) interacting particle system is not unique.
-In the literature there are many.
-Two of them are the following.
-On one hand, the \textit{multi-layer models}, in which the process is constructed on a many layer graph where each graph correspond to a type and perform a kind of dynamic (independent jump, exclusion/inclusion walkers) and the layers communicate each other with some "switching probabilities".
-The state space of the Markov process is the Cartesian product of the state spaces of each layer, i.e.
-of the two species.
-For example see \cite{floreani2022switching,redig2022ergodic,redig2023equilibrium}.
-On the other hand, the \textit{single layer models}.
-Here, there is just one layer, where particles of each type can pile up, in a way that the exclusion dynamic concerns many species together.
-In other words, now the species can interact "directly", not just by switching layer.
-Here the state space contains all the species and it is not product anymore.
-Some examples of such a dynamic can be found in \cite{casini2022uphill,vanicat2017exact,zhou2021orthogonal,casini2023density}.
-\\
-%In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e.
-a dynamic in which a maximum amount of particles can be present in each site at each time.
-We will call this amount, the "maximal occupancy" and it will indicated with $\twoj$ where $\twoj\in\mathbb{N}$.
-Particle of any species can exchange their position in the graph, under this exclusion constraint.
-The system will be put out of equilibrium and some absorbing duality result are investigated.
-Moreover, we will use this duality, to study the out of equilibrium steady state.
-In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}.
-%{\color{red}
-%The case of $\twoj=1$ distinguishes itself from other values of $\twoj$ as in this case the model can be mapped to an integrable higher rank ${gl}(N)$ Heisenberg XXX spin chain with open (non-diagonal) boundaries.
-Furthermore the matrix product ansatz \cite{derrida1993exact}  is applicable, see \cite{Crampe:2014aoa,vanicat2017exact}.
-%}
-%We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case.
-The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator.
-\\
-% For a complete review of the quantum inverse scattering method see \cite{Sklyanin:1988yz} and \cite{faddeev1996algebraic}.
-For application of the QISM to interacting particle systems we refer to \cite{frassek2020eigenstates,frassek2019non,frassek2022exact,vanicat2017exact}.
-\\
-% A new technique to compute absorption probabilities has been proposed in \cite{floreani2023non}.
-% \\
-% \\
-% \textbf{Some interesting references and extensions?}:
-% Multispecies version of non-compact chains. Extension of \cite{frassek2022exact},\cite{frassek2022integrable},\cite{frassek2020non},\cite{frassek2021duality}. \\
-% Use exact solution to compute large deviation rate function extending to the multispecies case results proved in \cite{derrida1998exact}, \cite{mallick2022exact}. \\
-% Extend the result to a-symmetric situation. See \cite{belitsky2018self}, \cite{belitsky2015quantum}, \cite{crampe2016integrable}, \cite{finn2018matrix}. \\
-% Extend the QISM technique to models which include reaction trying to apply the method exposed in \cite{de2021yang} for stirring process with a proper reaction term.
-Extend the duality to stirring models with different mechanism of transition \cite{chatterjee2023multi}.
-%}
-%
-%
-%
-%
 \section{The stirring process with open boundaries}
@@
 with open boundaries. 
-%In words, the process is described as follows. 
 Each site
@@
 steady state sets in.
-%\noindent
-%\begin{remark}
-%\label{hole}
-%In the following we will often consider type $N$ as a distinguished type
-%(called `holes'), whose number at each site is fixed by the numbers of particles 
-%of the remaining $N-1$ types. 
-% It is interesting to observe that, in case we stop distinguishing the types of the ``true'' particles of types 
-% (those of types $\{1,\ldots,N-1\}$), we retrieve the 
-% boundary-driven version of the partial symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
 In the case $N=2$, we retrieve the  boundary-driven version of the symmetric exclusion process \cite{schutzSandow,carinci2013duality}.
-% \todo{I would prefer to say this is for N=2}
-%
-%The choice of type $N$ for the distinguished type is arbitrary and does not affect
-%the results. However, we shall see in Section~\ref{sectionDuality}, that
-%the dual process breaks the symmetry.
-%In particular, in the  long-time limit the dual process has only particles of type $N$ on the graph.
-%Interpreting type $N$ as an hole, one can then say that the dual process voids the graph.   
-%
-%\end{remark}
-%\todo{It is misleading to have to different interpretations.
-Like what is the number of particles per site?
-Another confusion is for the reservoirs/open boundaries...
-Is it the same on general graph?}
-%{\color{blue} First question: Do you mean that we should specify it like "the maximal occupancy at each site is..."?\\
-%Second question: I think yes. The concept of boundary is general, not only for the chain}
 
@@
 This means that on the edge $(x,y)\in \mathcal{E}$  a particle {or a hole} indicated by $A$ at site $x$ is exchanged with a particle {or a hole} indicated by $B$ at site $y$ at rate $\omega_{x,y}n_{A}^{x}n_{B}^{y}$.
-% {\color{blue} The transitions where a hole is exchanged with a particle, can be interpreted as \textit{purely diffusive}.}
 Moreover, each vertex  exchanges particles {or holes} with the external environment (reservoirs). 
@@
 {The transitions where the a particle is replaced by a hole/a hole is replaced by a particle is interpreted as a removal/injection of particles.}
-%
-%For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$. 
-%See Figure~\ref{fig:1} and  Figure~\ref{fig:2} for a visualisation of the dynamics. 
-%\begin{figure}[h]
-%    \centering
-%    \includegraphics[scale=0.45]{BulkStirring.eps}
-%    \caption{The edge dynamics.
-Maximal occupation is $\nu=6$.
-A particle of type $2$ is removed in $x$ and placed in $y$.
-A particle of type $3$ is removed in $y$ and placed in $x$.
-This transition occurs at rate $n_{2}^{x}n_{3}^{y}=2\cdot 3$.}
-%    \label{fig:1}
-%\end{figure}
-%\begin{figure}[h]
-%    \centering
-%    \includegraphics[scale=0.4]{BoundaryStirring.eps}
-%    \caption{The site dynamics.
-Here the maxiaml occupation is $\nu=6$.
-The reservoir, represented by a square "box" containing all types of particles, remove a type $2$ from site $x$ and replace it with a type $3$.
-This transition occurs at rate $\alpha_{3}^{x}n_{2}^{x}$.}
-%    \label{fig:2}
-%\end{figure}
 \subsection{Reversible measures in the equilibrium set-up}
@@
 		\end{remark}
-% 		\todo{?}
 \subsection{Lie algebraic description of the process}
@@
     \lambda=(\twoj,0,\ldots,0) \;.
-    %\qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
 \end{equation} 
@@
 \end{equation}
-%where $\sum_{a=1}^{N}n_{i}=\nu$. 
 The basis vectors satisfy the orthogonality relation
@@
 The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield highest Dynkin weight \eqref{eq:dynkin}. \\
-%{\color{red} Is this remark relevant for us?}
-%\newline 
-%\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix~\ref{appA}.
 \\ \\
-%\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
-%\begin{equation}
-%   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}\dt
-%\end{equation}
-%{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
 As mentioned above, the process with generator \eqref{Generator} can be described in terms of ${gl}(N)$ Lie algebra generators.
@@
 a vector $|{\bm{n}}\rangle \in \Omega$ can be written as
-%We now define the equivalent of \eqref{stateSpace} in the vector notation
-% \begin{equation}
-%	\Omega':=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle \;:\;n\in\mathbb{N}_0^N,\;\;|n|=\twoj\right\}^{\otimes|V|}
-%	\end{equation}
-%where we denote 
+
 \begin{equation}
@@
 \end{equation}
-%{\color{blue}
-%	\begin{equation*}
-%		|{\bm{n}}\rangle=\left(\,\bigotimes_{x\in V}	|n_{1},\ldots,n_{N}\rangle_{x}\right)
-%	\end{equation*}}
-%where we require that $n_{a}^{x}\in \mathbb{N}_{0}$ and $\forall x\in V$ we have 
 with $\sum_{A=1}^{N}n_{A}^{x}=\nu$ for any $x\in V$.
@@
 with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. Since the {maximal occupancy at each site is $\nu=1$},
-% \todo{but is it at max 1? I do not understand what we call the stirring process....}  
 the configuration $\bm{n}$ introduced in Section~\ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by 
@@
 \end{equation} 
-%We define also 
-%\begin{equation}\label{lambdaConditions}
-%	(\alpha_{a}-\beta_{a})=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}(\alpha_{a}-\beta_{a})=0\,.
-%\end{equation}
 Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable.
@@
 Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
-The duality result yields {to a dual process that} %several simplifications,  the main one being that the
-%dual process
+The duality result yields {to a dual process that} 
  has absorbing sites.
@@
 \end{remark}
-%
-%
 \subsection{Proof of Theorem~\ref{thm-duality}}
@@
 \hspace{2.cm}\qquad\times |\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber
-%\\&=
-%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
-%\\&
-%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
 \\&=
@@
 	\mathcal{H}_{x,y}S_{x,y}=S_{x,y}\mathcal{H}_{x,y}
-	%\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
 	\dt
@@
  where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
- %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $a\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$.
-This implies that the dynamics of the dual process is simpler, because described by a lower number of particles.
-By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
- %{\color{blue} That's confusing. What is E?}
-
-% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
  \begin{flushright}
@@
  \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
-% that we connect to every site $x\in V$ of the graph $G$.
-\\
  Considering {$\mathcal{A},\mathcal{B}\in {gl}(N)$}, the Hadamard formula reads 
@@
 \end{equation}
-%By inserting the identity $I=\exp{(E^{x})}\exp{(-E^{x})}$ and 
 By using \eqref{HT-BA} and the fact that 
-%the first Casimir operator $C_{1}=
 $\sum_{a,b=1}^{N}E_{AB}$ is central for the algebra we have
@@
 {With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$
-% although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$
+
 .
@@
 \\=&
-%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&
 \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
@@
 &\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
-%=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^-1{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\
 =\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
@@
 \end{equation}
-%since
-%\begin{equation}
-%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N-1}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt
-%\end{equation}
-%This is a consequence of 
-%\begin{equation}
-%\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N-1}^{u(x)}|($\mathbf{a}$^{+})_{a}^{u(x)}=0
-%\end{equation}
-%that follows from \eqref{bosonicKX}.
 Therefore, inserting \eqref{extra-site-trick} in \eqref{siteHadamardII} we obtain 
@@
 \left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right\}\,|\alpha^{x}|\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{u(x)}E_{Na}^{x}-E_{aa}^{x}\right)
-%\\&=
-%\left\{d_{x}\otimes \sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right\}\widetilde{H}_{x}
 \\&=
@@
 \end{equation}
-%\begin{equation}\label{ElementsDualityMatrixChain}
-%	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
-%\end{equation}
 The dual Hamiltonian is
@@
 This simplification will be crucial in Section~\ref{sectionIntegrabiliy}.\\
-
-%In this notation, the elements of the duality matrix reads
-%\begin{equation}\label{ElementsDualityMatrixChain_1}
-%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
-%\end{equation}
-%\\
 Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles.
@@
 In the following we denote by $\mu$ the non-equilibrium steady state distribution and we call $\bm{Y} = (Y_1,\ldots,Y_L)$ the random vector with law $\mu$.
-Furthermore we write $\mathbb{E}[\cdot]$ for the expectation with respect to $\mu$.%For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$.
+Furthermore we write $\mathbb{E}[\cdot]$ for the expectation with respect to $\mu$.
 \begin{corollary}[Correlations via duality]\label{Corolollary-ABS_Corr-abstract}
@@
 \begin{equation}
-	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
+	D(\bm{\tau},\bm{\xi})
 	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
@@
 For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is fully determined by the correlations of equation \eqref{exactCorrelations} through the relation
-{\color{blue}
+{
 \begin{equation}\label{implicit-mass-function}
@@
 }
-%\begin{equation}\label{implicit-mass-function}
-%	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{black}
-%	\mathbb{E}\left[\Bigg( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\Bigg) \Bigg(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\Bigg)\right]}\,.
-%\end{equation} 
 \end{corollary}
-%{\color{blue} Here $\mu(\bm{\tau})$ is the  non-equilibrium steady probability of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well.
-However, from Corollary~\ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$).
-Therefore, to write the probability mass function $\mu$ for occupations containing holes we have to use the conservation of probability to get rid of the indicators of these holes.
-Then, equation \eqref{implicit-mass-function} is derived (for details see below the proof of Corollary~\ref{Corollary-NESS-ABS}).\\
-% The expectation on the right-hand-side of \eqref{implicit-mass-function} contains only indicators of particles configurations: indeed in the first product  $\tau_{x}\neq N$ are considered, while in the second product we have $a_{k}\neq N$ for all $k\in\{1,\ldots,N\}$.
-As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary~\ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$.
-For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\
 \paragraph{Example for an $L=2$ chain.} To clarify equation \eqref{implicit-mass-function} we report the example of a chain with $L=2$, where we compute the probability mass functions of three configurations.
@@
  	Here we have only one term corresponds to $m=2$ in formula  \eqref{implicit-mass-function}.
-	%and average can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=a_{2}=1$.
+
  	\item probability of the first site occupied and the second empty:
@@
  	\end{align}
-	{\color{blue}In the last equality we have two terms: the first corresponds to $m=1$ (with $x_{1}=1$) and the second corresponds to $m=2$ in formula \eqref{implicit-mass-function}.}
-% 	Here the first term on the right-hand-side corresponds to $b=0$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$, $x_{1}=1$ and $a_{1}=1$.
-The second term on the right-hand-side corresponds to $b=1$ in \eqref{implicit-mass-function} and can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\;x_{2}=2$ and $a_{1}=1,\;a_{2}=a$ for all $a=1,\ldots N-1$.
+	{In the last equality we have two terms: the first corresponds to $m=1$ (with $x_{1}=1$) and the second corresponds to $m=2$ in formula \eqref{implicit-mass-function}.}
  	\item probability of both sites empty:
@@
  	\end{align}
- 	{\color{blue}In the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}.
+ 	{In the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}.
 }
-	%They can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=1$ and by fixing $x_{1}=1$, $a_{1}=1,\ldots,N-1$ and $x_{2}=2$, $a_{2}=1,\ldots,N-1$ respectively.
-
-	%and it can be computed by Corollary~\ref{Corolollary-ABS_Corr-abstract} with $m=2$, $x_{1}=1,\,x_{2}=2$ and $a_{1},a_{2}=1,\ldots,N-1$. 
  \end{itemize}
@@
 	=&\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a\}}\right)\right)\right]
-	%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
-	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{Y_x=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
-	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
-	%=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
-\end{align}
-% {\color{blue}Is it not an identity? Take for example 3 sites: $\tau_{1}=\tau_{2}=1$ and $\tau_{3}=N$. Then we have that 
-% $$
-% \prod_{x=1}^{3}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=\mathbbm{1}_{\{Y_{1}=\tau_{1}\}}\mathbbm{1}_{\{Y_{2}=\tau_{2}\}}\mathbbm{1}_{\{Y_{3}=\tau_{3}\}}=\left(\mathbbm{1}_{\{Y_{1}=1\}}\mathbbm{1}_{\{Y_{2}=1\}}\right)\left(\mathbbm{1}_{\{Y_{3}=N\}}\right)=\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{3}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}= N}^{3}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)
-% $$} 
-% \todo{removed subindex $a_x$ here}
+\end{align}
 where in the last equality we exploited the fact that 
@@
 \end{equation}
-% {\color{blue}
-% Here I mean 
-% \begin{equation}
-% 	\mathbbm{1}_{\{Y_{x}=a\}}=\begin{cases}
-% 		1\qquad \text{if}\qquad  Y_{x}=a\\
-% 		0\qquad \text{if}\qquad Y_{x}\neq a
-% 	\end{cases}
-% \end{equation}
-% Therefore, \begin{equation}
-% 	\mathbbm{1}_{\{Y_{x}=N\}}=\begin{cases}
-% 		1\qquad \text{if}\qquad  Y_{x}=N\\
-% 		0\qquad \text{if}\qquad Y_{x}\neq N
-% 	\end{cases}
-% \end{equation}
-% and 
-% \begin{equation}
-% 1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}=\begin{cases}
-% 	1\qquad \text{if}\qquad  Y_{x}=N\\
-% 	0\qquad \text{if}\qquad Y_{x}\neq N
-% \end{cases}
-% \end{equation}
-% therefore \eqref{prova} follows.
-% }
-The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ sites are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
+The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ sites are empty. 
 Therefore, we may write
@@
 \end{align} 
-% \todo{indices are strange. Say what happens here}
-{\color{blue}In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered.
+{In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered.
 Similarly, the second addend is the product of the indicator of $\ell+1$ occupied sites.
@@
 	\begin{align}
-		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&%\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
-	%\\	=&
+		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&
 		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}(\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}})\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
@@
 The above sum can be extended until $m=0$ since all the terms $m=0,\ldots,\ell-1$ are vanishing. 
-Finally, by taking the expectation with respect to the steady state distribution we obtain \eqref{implicit-mass-function}.}  %{Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.} }
+Finally, by taking the expectation with respect to the steady state distribution we obtain \eqref{implicit-mass-function}.} 
 \begin{flushright}
@@
 
-% In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}.
-% As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
-% and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
-% We start by recalling the formulation of the MPA  and then we explain our strategy.
-
 \subsection{Matrix product ansatz for the non-equilibrium steady state}
@@
 \begin{equation}\label{bulk}
-	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}%\qquad\forall a,b=1,\ldots,N
+	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}
 \end{equation}
@@
 \begin{equation}\label{leftBoundary}
-	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  %\qquad\forall a=1,\ldots,N\co
+	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  
 \end{equation}
 \begin{equation}\label{rightBoundary}
-	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right) |V\rangle\rangle =-(\alpha_{a}-\beta_{a}) |V\rangle\rangle %\qquad\forall a=1,\ldots,N\dt
+	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right) |V\rangle\rangle =-(\alpha_{a}-\beta_{a}) |V\rangle\rangle 
 \end{equation}
@@
 	\begin{equation}
-		\sum_{a=1}^{N}	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a}) \langle \langle W|  =0
+		\sum_{a=1}^{N}	 \langle \langle W|  \left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,
 	\end{equation}
@@
 \begin{equation}\label{commutationsBula2}
-	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt %\forall a\in \{1,\ldots,N-1\}\dt
+	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\dt 
 \end{equation}
@@
 \begin{equation}\label{commLEFT2}
-	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  %\qquad\forall a=1,\ldots,N-1
+	 \langle \langle W|  \left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a}) \langle \langle W|  
 	\co \qquad 
-	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle %\qquad\forall a=1,\ldots,N-1
+	\Xt_{a}  |V\rangle\rangle = (\alpha_{a}-\beta_{a}) |V\rangle\rangle
 	\,.
@@
 The Hamiltonian $H^{'}$ is not stochastic, however it turns out that the components of its eigenvector with zero eigenvalue $|\Psi^{'}\rangle$ are the correlations in the non-equilibrium steady state.
- %The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
 \subsection{Correlations in the non-equilibrium steady state}\label{subsection-exact}
@@
 \begin{theorem}[Correlations in the non-equilibrium steady state]\label{thm-correlations}
-%Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$
-%and consider $m$ species $a_{k}\in \{1,\ldots,N-1\}$. 
 Let $m\in \{1,\ldots,L\}$. Consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
@@
 \paragraph{One-point correlations}
-We consider the average with respect to $\mu$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads
-%\begin{equation}
-%\mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt
-%\end{equation}
+We consider the average with respect to $\mu$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. 
 Using \eqref{abs-probabilities} we obtain the absorption probabilities 
@@
 We consider the average with respect to $\mu$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 
-%\begin{equation}
-%	\begin{split}
-%		 \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt
-%	\end{split}
-%\end{equation}
 Using \eqref{abs-probabilities} we obtain the absorption probabilities
@@
 \end{equation}
-%where $\bm{\xi}=\delta_{a_{1}}^{x_{1}}+\delta_{a_{2}}^{x_{2}}$. 
-%Then, by using \eqref{exactCorrelations} we have 
-%\begin{equation}
-%\begin{split}
-%	\mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]=&\frac{x_{1}(x_{2}-1)}{L(L+1)}\beta_{a_{1}}\beta_{a_{2}}+\frac{x_{1}(L+1-x_{2})}{L(L+1)}\beta_{a_{1}}\alpha_{a_{2}}\\
-%	+&\frac{x_{2}(L+1-x_{1})}{L(L+1)}\alpha_{a_{1}}\beta_{a_{2}}+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}\alpha_{a_{1}}\alpha_{a_{2}}
-%\end{split}
-%\end{equation}
-%\begin{equation}
-%	\begin{split}
-%	 \mathbb{E}_{\mu}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt
-%	\end{split}
-%\end{equation}
 Therefore, we compute the second cumulant, i.e. the two-point connected correlation
@@
 \begin{equation}\label{transformationV}
- \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}\co %=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
+ \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}\co 
 \end{equation}
@@
 H_{\text{right}}^{'}=S_{1}H_{\text{right}}S_{1}^{-1}=
-% \exp{\left(\sum_{c=1}^{N-1}e_{1N}^{L}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{L}-e_{bb}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}e_{Nc}^{L}\right)}=
 \sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
@@
  \begin{equation}
- 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
+ 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co
  \end{equation}
@@
 		H_{\text{left}}^{''}&=S_{2}H_{\text{left}}^{'}S_{2}^{-1}
-% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
 		=
@@
 We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations.
-% For the sake of notation we denote by
-% \begin{equation}
-%     \begin{pmatrix}
-% 		X_{a}\\ 
-% 		X_{N}
-% 	\end{pmatrix}=\begin{pmatrix}
-% 	    X_{1}\\
-%      \vdots\\
-%      X_{N}
-% 	\end{pmatrix}\co
-% \end{equation}
 We define the transformed matrix product operators
@@
 where  $ a\in \{1,\ldots,N-1\}$.
-% 
-% \begin{equation}
-% 	\begin{pmatrix}
-% 		\Xt_{1}\\ 
-% 		\vdots\\
-% 		\Xt_{N-1}\\
-% 		\Xt_{N}
-% 	\end{pmatrix} =S\begin{pmatrix}
-% 		X_{1}\\
-% 		\vdots 
-% 		\\
-% 		X_{N-1}
-% 		\\X_{N}
-% 	\end{pmatrix}=\begin{pmatrix} 
-% 		X_{1}-\beta_{1}(X_{1}+\ldots+X_{N})\\
-% 		\vdots \\
-% 		X_{N-1}-\beta_{N-1}(X_{1}+\ldots+X_{N})\\
-% 				X_{1}+\ldots +X_{N}\\
-% 	\end{pmatrix}\dt
-% \end{equation}
 We can also reverse the transformation by $S^{-1}$ and get: 
@@
 \begin{align}
-	 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle &=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)} \langle \langle W|  \widetilde{X}_{N}^{n_{N}-1} |V\rangle\rangle = \langle \langle W|  \widetilde{X}_{N}^{n_{N}} |V\rangle\rangle =\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)} \langle \langle W|  \widetilde{X}_{N}^{n_{N}-2} |V\rangle\rangle \\&=
+	 \langle \langle W|  \widetilde{X}_{N}^{n} |V\rangle\rangle &=
 	\frac{(1+n)!}{n!}\frac{n!}{(n-1)!}\ldots \frac{3!}{2!}\frac{2!}{1!} \langle \langle W|  \widetilde{X}_{N}^{0} |V\rangle\rangle =
@@
 \begin{align}
-\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
+\Psi^{'}(\bm{\tau})
 =&\frac{1}{(L+1)!}\sum_{\bm{\sigma}\in \Omega^{'}}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\&\times\left[\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)\right]\dt
-%=&\frac{1}{(L+1)!} \sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\
-%=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
 \end{align}
@@
 \begin{equation}
-	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
+	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt
 \end{equation}
@@
 	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
-%	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
-%	\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}\alpha_{s_{k}}^{t_{k}}\beta_{s_{k}}^{1-t_{k}}\right)\left(\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})\right)\nonumber\\
 	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt
@@
 	By inserting the resolution of identity $\sum_{\bm{\sigma}\in \Omega^{'}} |\bm{\sigma}\rangle\langle\bm{\sigma}|$ we have that 
-{\color{blue}
+{
 	\begin{align}
 		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle=\langle \bm{\tau}|S^{-1}_{1}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{-1}|\bm{\sigma}\rangle \langle \bm{\sigma}|\Psi^{'}\rangle\dt
-		%=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
-	\end{align}
-	%Considering 
-	%\begin{equation}
-	%|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
-	%\end{equation} and 
+	\end{align} 
 	Using \eqref{Tensor-S1} we obtain 
@@
 			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
-			%=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
-			%=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
 		\end{align} 
@@
 		\begin{equation}\label{notation-PSI}
-		%	\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
 			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
 		\end{equation}
-		indicates that in positions $x_{1},\ldots,x_{m}$ there are particles of species $b_{1},\ldots,b_{m}$, while there are holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$).
-}  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}.
-	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 
+		indicates that in positions $x_{1},\ldots,x_{m}$ there are particles of species $b_{1},\ldots,b_{m}$, while there are holes $N$ in all other positions.} 
 \begin{remark}[Equilibrium case]
@@
 }
- %We only report the main results, since the computations are just a specific case of the ones done for the multispecies stirring process.  
 \paragraph{Correlations of SSEP.}
@@
 \textbf{Proof of formula \eqref{correlations-SSEP}:} Starting from \eqref{exactCorrelations} we exploit {the fact that for $N=2$  each site can be either occupied by a particle or empty.} 
-We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$.
-There are many values of $c$'s that give the same $q$, therefore we define $q$ variables denoted by  %labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that
+We introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ variables denoted by  
 $1\leq \ell_{1}<\ell_{2}<\ldots<\ell_{q}\leq m$.  
 To each of these variables we associate coordinates $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ that are such that $c_{x_{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$.
-Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ { (by the summation $\textstyle{\sum_{k=1}^{m}}c_{x_{k}}=q$)} %\todo{you mean the sum is q?[FIXED]}
+Therefore, for any fixed $c_{x_{1}},\ldots,c_{x_{m}}$, we find $q$ { (by the summation $\textstyle{\sum_{k=1}^{m}}c_{x_{k}}=q$)}
  and $\ell_{1},\ldots,\ell_{q}$ from which we fix $x_{\ell_{1}},\ldots,x_{\ell_{q}}$ { as explained.} Then, we obtain  
@@
 \begin{align}
-	&\frac{\left(1+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)!}{\left(1+L\right)!}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\nonumber\\%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
+	&\frac{\left(1+\sum_{x=1}^{L}\delta_{\tau_{x},2}\right)!}{\left(1+L\right)!}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},2}\right)\right]^{1-\delta_{\tau_{x},2}}\nonumber\\
 	=&\frac{\left(1+L-\sum_{x=1}^{L}(1-\delta_{\tau_{x},2})\right)!}{\left(1+L\right)!}\prod_{x=1}^{L}\left[(\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{j},2})\right)\right]^{1-\delta_{\tau_{x},2}}\nonumber\\
@@
 The section is organized as follows:
-%In Sections~\ref{sectionIntegrabiliy} we have shown that, on the geometry of a chain and with hard-core interaction the model \todo{which model?} is exactly solvable using integrability.  
-%The aim of this section is to study the process when integrability is lost.\todo{but we got duality on any graph} We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain.
-We provide the following extensions:
 \begin{enumerate}
@@
 We recall that the dual processes are defined on an enlarged chin with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.}
-%In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$.
-Each site can {\color{blue} host at most $\nu\geq 1$ particles per site, whose type is chosen among the $N-1$ available ones}.
-%The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). \todo{this is said before} 
-%The processes considered in this section will be denoted with same {\color{blue} random variable} \todo{variables?[DONE]} $\left(\bm{n}(t)\right)_{t\geq0}$.
-{\color{blue} We will specify the generators case by case}.
-%their corresponding generator will be specified in each subsection.
-%We use the notation of Section~\ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
-%{\color{blue}The state space of the original process} is denoted by 
-%\begin{equation}%\label{stateSpace-Chain}
-%	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega%_{x}\,.
-%\end{equation}
-% The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the dual generator specified case by case \todo{?}.
-The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.
-% We denote the space of the dual process by $\widetilde{\Omega}_{L}$, i.e.%
-%\begin{equation}%\label{dualSpace-chain}
-%	\widetilde{\Omega}_{L}=\mathbb{N}_{0}^{N-1}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N-1}\dt
-%\end{equation}
-%In the following, for $a\in \{1,\ldots,N-1\}$ of this section we will denote by \todo{?}
-%\begin{equation}
-%	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\beta_{a}}{|\beta|}\,.
-%\end{equation}
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
@@
 \end{equation}
-here we recall that, generalizing Corollary~\ref{Corolollary-ABS_Corr-abstract}, %that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and
+here we recall that, generalizing Corollary~\ref{Corolollary-ABS_Corr-abstract},
 \begin{equation}\label{Pass} 
@@
 For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one-point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.
- The absorption probabilities for higher point correlations fulfill  difference equations.
+ The absorption probabilities for higher point correlations fulfil  difference equations.
 
@@
 \end{equation}
-%Moreover, it holds that 
-%\begin{equation}
-%\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
-%\end{equation}
 Therefore the thermalization measure reads
@@
 \end{equation}
-%provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
+
 \subsubsection{Thermalized multispecies stirring process}
@@
 and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
-%\begin{equation}
-%	\begin{split}
-%		\mathcal{L}_{\text{right}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},r)-f(\bm{n})\right\}\\&
-%		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
-%	\end{split}
-%\end{equation}
 In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\mu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ ($L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters.
@@
 The boundary generator $\mathcal{L}_{\text{right}}^{rd}$ is defined analogously, but the $\alpha$'s are replaced by $\beta$'s and the boundary values $\rho_{A}^{\text{right}}$.
-%\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multispecies stirring process \eqref{siteGenerator}.
-%\end{remark}
 \paragraph{Action on the occupation variable}
@@
 For these reasons, this model is a generalization to $N-1$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}.
-%This answers the first question we addressed to at the beginning of this section. 
 \subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
@@
 \end{proposition}
-%\begin{equation}
-%	\widetilde{\Omega}=\mathbb{N}_{0}^{N}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N}
-%\end{equation}
-%We associate an ``extra site'', denoted by $0$ and $L+1$ attached to $1$ and $L$ respectively,
-%where dual particles will accumulate in the course of time. 
-%and we denote its configurations by $\bm{\xi} \in \widetilde\Omega$.
-%\begin{equation}
-%	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
-%\end{equation}
-%where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
-%and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
-%where we denote the \textit{density} of the species $a\in \{2,\ldots,N\}$ imposed by the reservoir at site $x\in V$  by 
-%\begin{equation}
-%	\rho_{a}^{x}:=\frac{\alpha_{a}^{x}}{|\alpha^{x}|}
-%\end{equation}
 
@@
 	\\=&
-%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left((E_{da}^{x}\delta_{h_{c}(b)N}-E_{h_{c}(b)N}^{x}\delta_{ad})-(E_{da}^{x}\delta_{aN}-E_{aN}^{x}\delta_{da})\right)\right.
-\\ \otimes&\left.
-\left((E_{kb}^{x+1}\delta_{h_{c}(a)N}-E_{h_{c}N}^{x+1}\delta_{kb})-(E_{kb}^{x+1}\delta_{bN}-E_{bN}^{x+1}\delta_{kb})\right)\right\}
-%	\\=&
-%	\sum_{d,k=1}^{N-1}\sum_{a,b=1}^{N}\left\{\left(E_{da}^{x}-E_{h_{c}(b)N}^{x}-E_{da}^{x}+E_{aN}^{x}\right)\otimes\left(E_{kb}^{x+1}-E_{h_{c}(a)N}^{x+1}-E_{kb}^{x+1}+E_{bN}^{x+1}\right)\right\}
-%	\\=&
 	\sum_{a,b=1}^{N-1}\sum_{A,B=1}^{N}\left\{\left(E_{AN}-E_{h_{c}(B)N}\right)\otimes \left(E_{AN}-E_{h_{c}(B)N}\right)\right\}=0\dt
@@
 In the last equality we used the fact that map $h_{c}(\cdot)$ is surjective. 
-%\paragraph{Duality for $H_{x,x+1}^{m}$} 
 Concerning the commutator of $\mathcal{H}_{x,x+1}^{m}$ the proof is similar and gives
@@
 \begin{equation}
-	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
-		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
-		%	1\qquad  &\text{if}\quad \tau_{x}= N
-		%	\end{cases}
-		\dt
+	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}\dt
 \end{equation}
@@
 Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
-\begin{equation}%\label{interpretation-PsiP}
+\begin{equation}
 	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
@@
 In particular, when the configuration $\bm{\tau}$ has $\ell$ particles, $\Psi^{'}(\bm{\tau})$ does coincide with the $\ell$-point correlation function.
-%As a consequence, all the marginals of $\mu$ can be found using the absorption probabilities by equation \eqref{exactCorrelations}.
 
@@
 \end{remark}
-%Already for two-point correlations the computations become more involving and hard to solve.
+
 \section{Proof of duality of thermalized multispecies stirring}\label{appendix-dualityThermalized}
@@
 For the sake of notation, we introduce
-%
 \begin{equation}
@@
 \end{align}
-%The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 
+
 \begin{flushright}

### 2024-05-07 main.tex
'''
jh

@@
 \usepackage{array}
+\usepackage{hyperref}
 \numberwithin{equation}{section}
@@
 \end{equation}
-{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$
-
-.
-} 
+{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$.
+} \\
 Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 

### 2024-05-14 main.tex
update

@@
 \newcommand{\twoj}{\nu}
+\newcommand{\fra}[1]{\textcolor[rgb]{0,0,1}{#1}}
 \allowdisplaybreaks
@@
 an extended graph $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E})}$ which 
-includes additional extra-sites $\widetilde{V}\setminus V$ where
+includes additional \fra{sites (sometimes called "extra-sites")} $\widetilde{V}\setminus V$ where
 dual particles get absorbed in the long-time limit.
@@
 \paragraph{Organization of the paper and main results.}
-We start in Section~\ref{sec1} by defineing the open multispecies stirring
+We start in Section~\ref{sec1} by \fra{defining} the open multispecies stirring
 process on a general graph and providing its Lie algebraic description in terms of the generators of the $gl(N)$ Lie algebra.
@@
 The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process and the formulation of the the absorbing duality with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}).
-Finally, the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities (inspired by \cite{casini2022uphill,schutzReaction}).
-We report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD}. 
+Finally, the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities, \fra{inspired by \cite{casini2022uphill,schutzReaction}
+(we report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD})}. 
 Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.
@@
 The particles have a {\em type} (sometimes called {\em species} or {\em colour})
-which can takes  values $\{1,2,\ldots,N-1\}$.
+which can \fra{take}  values $\{1,2,\ldots,N-1\}$.
 {More precisely, at each site there are $\nu$ available places (called \textit{holes} or \textit{vacancies}) that can be either occupied by particles or not.
@@
 on each vertex $x$ of the graph, a particle of type $a \in \{1,\ldots,N-1\}$ is created  at rate $\alpha_a^x >0$;
-additionally a particles of any type is replaced with a
+additionally a \fra{particle} of any type is replaced with a
 particle of type $a$ at rate $\alpha_a^x >0$ and it is removed at rate $\alpha_N^x >0$.
@@
 The swap dynamics taking place on the edges is of Kawasaki-type 
-with $N$ conservation laws
-(the total number of particles of each type). 
+with $N$ conservation laws, \fra{where $N$ is the number of species plus the holes. This means that the total number of particle of each species and the number of holes is conserved by the dynamics.}
+%(the total number of particles of each type). 
 The site-dynamics is instead of Glauber-type. 
@@
 Namely, on each site $x\in V$  a particle {or a hole} indicated by $B$ is replaced with a particle {or a hole} indicated $A$ at rate $\Gamma_{x}\alpha_{A}^{x}n_{B}^{x}$.
-{The transitions where the a particle is replaced by a hole/a hole is replaced by a particle is interpreted as a removal/injection of particles.}
+{The transitions where \fra{a} particle is replaced by a hole/a hole is replaced by a particle is interpreted as a removal/injection of particles.}
 \subsection{Reversible measures in the equilibrium set-up}
@@
 When, for any $A\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{A}^{x}\neq  \rho_{A}^{y}$, a  non-zero current sets in, breaking the reversibility.
-Informally, one can say that the reservoirs try to impose their different densities at the boundaries of the the graph, putting the system out-of-equilibrium.}
+Informally, one can say that the reservoirs try to impose their different densities at the boundaries of \fra{the} graph, putting the system out-of-equilibrium.}
 \begin{remark}
@@
 The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
-For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$.
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ \footnote{\fra{In this set-up we have chosen the fundamental (defining) representation of the Lie algebra, therefore the generators $(E_{AB})_{A,B\in\{1,\ldots,N\}}$ do coincide with the elementary matrices $(e_{AB})_{A,B\in\{1,\ldots,N\}}$.
+Therefore, we denote them by lowercase letters}}.
 The Hamiltonian can then be written as
@@
 Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable.
-This has been schown in \cite{vanicat2017exact} within  the Quantum Inverse Scattering Method.
+This has been \fra{shown} in \cite{vanicat2017exact} within  the Quantum Inverse Scattering Method.
 We will consider this process more extensively in Section~\ref{sectionIntegrabiliy}.
@@
  \begin{align}\label{HT-BA}
- 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{CD}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{CD}-\delta_{CN}\sum_{a=1}^{N-1}E_{aD}+(1-\delta_{DN})E_{CN}-\delta_{CN}(1-\delta_{DN})\sum_{b=1}^{N-1}E_{bN}\dt
+ 	\fra{\exp{\left(%-\sum_{a=1}^{N-1}E_{aN}
+ 			-E\right)}E_{CD}\exp{\left(
+ 		E%\sum_{a=1}^{N-1}E_{aN}
+ 		\right)}}=E_{CD}-\delta_{CN}\sum_{a=1}^{N-1}E_{aD}+(1-\delta_{DN})E_{CN}-\delta_{CN}(1-\delta_{DN})\sum_{b=1}^{N-1}E_{bN}\dt
  \end{align}
@@
 By using \eqref{HT-BA} and the fact that 
-$\sum_{a,b=1}^{N}E_{AB}$ is central for the algebra we have
+\fra{$\sum_{A,B=1}^{N}E_{AB}$} is central for the algebra we have
 
@@
 Taking the tensor product of both sides of  \eqref{siteHadamardI} 
-we obtain 
+we obtain \fra{
 \begin{equation}\label{siteHadamardII}
     \begin{split}
-    	&H_{x}^{T}d_{x}\otimes\left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right)\\=&
+    	H_{x}^{T}d_{x}\otimes\left(\mathcal{D}_{u(x)}%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|
+    	\right)=
  d_{x}\,
-|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \left(\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|\right)
-    \end{split}
-\end{equation}
+|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\otimes \left(\mathcal{D}_{u(x)}
+%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|
+\right)
+    \end{split}
+\end{equation}}
 {With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$.
@@
 \end{equation}
-Using the above equation we rewrite the right hand side term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ as 
+Using the above equation \fra{and considering the addends multiplied by the Lie generator $E_{Na}^{x}$ (for all $a\in \{1,\ldots,N-1\}$) on the right hand side term of \eqref{siteHadamardII}} we have that
 \begin{equation}\label{extra-site-trick}
@@
 all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$.
-We also notice that, up the the bosonic creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
+We also notice that, \fra{up to the the bosonic} creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
 This simplification will be crucial in Section~\ref{sectionIntegrabiliy}.\\
@@
 In this section we combine the matrix product ansatz (MPA) \cite{vanicat2017exact} and  the $gl(N)$ invariance of the process in the bulk, cf.~\eqref{symmetryH}, to exactly compute the correlations in the non-equilibrium steady state
- for the integrable version of the multispecies stirring process on a defined on a line segment, see Section~\ref{integrableChain-duality}. 
+ for the integrable version of the multispecies stirring process \fra{defined on a line segment}, see Section~\ref{integrableChain-duality}. 
 This allows further to determine the absorption probabilities and the probability mass-function of the non-equilibrium steady state in closed form.
@@
 The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal.
-Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $\mathcal{B}=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $\mathcal{A}_{N}=e_{aN},$ and $\mathcal{A}_{a}=e_{aa}$.
+Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $\mathcal{B}=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$\fra{, and either $\mathcal{A}=e_{aN},$ or $\mathcal{A}=e_{aa}$}.
 
@@
 \begin{equation}\label{similarity}
-	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
+	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\fra{\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}}\dt
 \end{equation}
@@
 \begin{equation}\label{Xtildes2b}
- \tilde X_a=X_{a}-\beta_{a}(X_{a}+\ldots+X_{N})\,,\qquad \tilde X_N= 
+ \tilde X_a=X_{a}-\beta_{a}(\fra{X_{1}}+\ldots+X_{N})\,,\qquad \tilde X_N= 
 				X_{1}+\ldots +X_{N}
@@
 cf.~\eqref{commLEFT2}.
-Using the transformed operators $(\widetilde{X}_{a})_{a\in\{1,\ldots,N\}}$, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
+Using the transformed operators \fra{$(\widetilde{X}_{A})_{A\in\{1,\ldots,N\}}$}, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
 \begin{equation}\label{toDetermineTilde}
@@
 \end{equation}
-which action on the occupation variable $|\sigma\rangle$ of a site is 
+\fra{whose action} on the occupation variable $|\sigma\rangle$ of a site is 
 \begin{equation}
@@
 \end{equation}
-We recall that the dual processes are defined on an enlarged chin with two extra-site $0$ and $L+1$ attached to $1$ and $L$ respectively.}
+We recall that the dual processes are defined on an enlarged \fra{chain} with \fra{two extra-sites} $0$ and $L+1$ attached to $1$ and $L$ respectively.}
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively.
+where $\mathcal{L}_{x,x+1}$ is given by \fra{\eqref{edgeGenerator}} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively.
 The duality function is \eqref{dualityElements} specified on the chain.
@@
 \end{align}
-Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall A\in\{1,\ldots,N\}$ we have $r_{A}\in \{0,\ldots,\nu\}$ and $\epsilon_{A}\in \{0,\ldots,2\nu\}$, under the constraints
+\fra{Here we introduce the vectors $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall A\in\{1,\ldots,N\}$, for each of their components $(r_{A})_{A\in\{1,\ldots,N\}},(\epsilon_{A})_{A\in\{1,\ldots,N\}}$ we have $r_{A}\in \{0,\ldots,\nu\}$ and $\epsilon_{A}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
 	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a},\qquad r_{N}=\nu-\sum_{a=1}^{N-1}r_{a}\dt
-\end{equation}
+\end{equation}}
  Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is the product over the sites of multinomial distributions we have
@@
 	\\&\times
-	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\mu_{TH}(\bm{r}|\bm{\epsilon})
+	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\fra{\mu_{TH}({r}|{\epsilon})}
 	\end{split}
@@
 \end{proposition}
-This dual process is absorbing since the dual boundary generator $\mathcal{L}_{\text{left}}^{TH}$ ($\mathcal{L}_{\text{left}}^{TH}$) remove all dual particles at site $1$ ($L$) and put these particles in the extra-site $0$ ($L+1$) with rate 1.
+This dual process is absorbing since the dual boundary generator $\mathcal{L}_{\text{left}}^{TH}$ ($\mathcal{L}_{\text{left}}^{TH}$) remove all dual particles at site $1$ ($L$) and put these particles in the extra-sites $0$ ($L+1$) with rate 1.
 The proof of Proposition~\ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix~\ref{appendix-dualityThermalized}.
@@
 	\begin{split}
-			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{t_{s}}\left(\rho_{s}^{\text{right}}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
-	\end{split}
-\end{equation}
-To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$.
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{t_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-t_{a}}\fra{\mathcal{P}(t_{a})}\dt
+	\end{split}
+\end{equation}
+\fra{where 
+\begin{equation*}
+	\mathcal{P}(t_{a})=\mathbb{P}\left(\bm{\xi}(\infty)=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}|\bm{\xi}(0)=\delta_{a}^{x}\right)
+\end{equation*} are the absorption probabilities.}
+\fra{To explicitly find the result, we aim to determine $\mathcal{P}(t_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$.
 This is the probability that a random walker 
@@
 \end{equation}
-First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. By writing explicitly $\rho_{a}^{L}=\frac{\alpha_{a}}{|\alpha|}$, this action gives
+First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. By writing explicitly $\fra{\rho_{a}^{\text{left}}}=\frac{\alpha_{a}}{|\alpha|}$, this action gives
 \begin{align}\label{ProvaBordoTH}
@@
 We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
-We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$ to get
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ \fra{and then we multiply} this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$ to get
 \begin{align}\label{pezzo1}
@@
 and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ to get
+We \fra{multiply} it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ to get
 \begin{equation}\label{pezzo2}
@@
 \begin{align}
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}\fra{(\rho_{a}^{\text{right}})}^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&=

### 2024-05-14 main.tex
vwr

@@
 Furthermore, reservoirs are attached at each site of the graph, creating and removing particles. For a precise definition of the rates of the process 
-we refer to Section~\ref{sec1}. As we will see, the choice of the boundary reservoirs is motivated by the fact that they allow to determine an absorbing dual process, 
+we refer to Section~\ref{sec1}. As we will see, the choice of the boundary reservoirs is motivated by the fact that they allow to determine an absorbing dual process
+\fra{that does not permit  color-changing until absorption at the boundary}, 
 regardless of the graph $G$ on which the process is defined and of the maximal occupancy $\nu$ at each site.
@@
 We choose to restrict to the symmetric version of the model, as the formulation
-of duality in the presence of both asymmetry and boundary driving is substantially
+of duality in the presence of bvmmetry and boundary driving is substantially
 more involved (for recent results on the single species case see
@@
 Moreover, we introduce indices denoted by uppercase letters (for instance $A,B,C,D\in\{1,\ldots,N\}$)  to also incorporate the holes, that correspond to the index $N$.
-The link between the two indices is given by
-\begin{equation}
-	a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad A=(a,N)\,.
-	\end{equation} 
+%The link between the two indices is given by 
+%\begin{equation}
+%	a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad A=(a,N)\,.
+%	\end{equation} 
 } 
@@
  \end{flushright}
- \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$.
+ \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula \footnote{\fra{See \cite{khuan} for an application of the Hadamard formula in the multispecies asymmetric context.}} the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then we  introduce a creation operator acting on an extra-site $u(x)$.
  Considering {$\mathcal{A},\mathcal{B}\in {gl}(N)$}, the Hadamard formula reads 

### 2024-05-15 main.tex
ll

@@
 \numberwithin{equation}{subsection}
+\usepackage[pagewise]{lineno}
 
@@
 \begin{document} 
-
+ \linenumbers
 \begingroup
@@
 \begin{equation}\label{ortho-extraSite}
-	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}\,.
+	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},\fra{q_{a}^{u(x)}}}\,.
 \end{equation} }
@@
 \begin{equation}\label{NESS-expectation-ABS}
-\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{s_{1}=0}^{1}\ldots \sum_{s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\mathcal{P}_{x_1,\ldots,x_m}(s_{1},\ldots,s_{m})
 \end{equation}
@@
 \begin{equation}\label{absProbabilitiesIntegrable}
-	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\Big| \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}_{x_1,\ldots,x_m}(s_{1},\ldots,s_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(s_{k}\delta^{0}_{a_k}+(1-s_{k})\delta^{L+1}_{a_k}\right)\Big| \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
 \end{equation}
-In \eqref{absProbabilitiesIntegrable} the variable $t_k$ is $1$ (resp.
+In \eqref{absProbabilitiesIntegrable} the variable $s_k$ is $1$ (resp.
 $0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $0$ (resp.
@@
 \mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
-	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
+	\\&=\sum_{s_{1}=0}^{1}\ldots \sum_{s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{m})\dt
 \end{split}
@@
 \end{equation}
-Here the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
+Here the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfill the commutators
 \begin{equation}\label{bulk}
@@
 \end{equation}
-and their action on the boundary vectors are
+and their action on the boundary vectors  \fra{$\langle \langle W|$ and $|V\rangle \rangle$} are
 \begin{equation}\label{leftBoundary}
@@
 \begin{equation}\label{exactCorrelations}
-\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\fra{\sum_{s_{1},\ldots,s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{m})}
 \end{equation}
@@
 \begin{equation}\label{abs-probabilities}
-	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})
+	\mathcal{P}_{x_{1},\ldots,x_{m}}\fra{(s_{1},\ldots,s_{m})=\sum_{c_{1}=s_{1}}^{1}\ldots\sum_{c_{m}=s_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-s_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})}
 \end{equation}
@@
 &\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
-=&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
-=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},x})!}\nonumber\\
-=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\dt
+=&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},x})!}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\dt
 \end{align}
@@
 We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether, at each site $x$, $\sigma_{x}$ is occupied or empty.
-Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$.
+Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$\fra{, where $c_{x}=\delta_{\sigma_{x},N}$}.
 Thus, we obtain
@@
 \begin{equation}
-	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
-\end{equation}
-Equation \eqref{ABS_1} will be useful in the following. 
+	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)
+\end{equation}
+\fra{and where we used equations \eqref{remove-exponent}.}
+Formula \eqref{ABS_1} will be useful in the following. 
 \end{remark}
@@
 	&\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
-	\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{t_{k}=0}^{c_{k}}(-1)^{c_{k}-t_{k}}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
-	=&\sum_{c_{1},\ldots,c_{m}=0}^{1}
-	f(c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\nonumber\\
-	=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt
+	\fra{\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{s_{k}=0}^{c_{k}}(-1)^{c_{k}-s_{k}}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)}\nonumber\\
+	=&\fra{\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	f(c_{1},\ldots,c_{m})\sum_{s_{1}=0}^{c_{1}}\ldots\sum_{s_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\left(\prod_{k=1}^{m}(-1)^{c_{k}-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)}\nonumber\\
+	=&\fra{\sum_{s_{1},\ldots,s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\sum_{c_{1}=s_{1}}^{1}\ldots\sum_{c_{m}=s_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt}
 \end{align}
@@
 		\\&=
-		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{t_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})
+		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\sum_{s_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N})
 	\end{split}
@@
 \begin{equation}\label{Pass} 
-	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
+	\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
 are the absorption probabilities for the non-integrable chain, i.e.
-the probabilities that $t_{a}$ particles of species $a$ are absorbed at $0$.
+the probabilities that $s_{a}$ particles of species $a$ are absorbed at $0$.
 Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
@@
 	\begin{split}
-			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{t_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-t_{a}}\fra{\mathcal{P}(t_{a})}\dt
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{s_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-s_{a}}\fra{\mathcal{P}(s_{a})}\dt
 	\end{split}
@@
 \begin{equation*}
-	\mathcal{P}(t_{a})=\mathbb{P}\left(\bm{\xi}(\infty)=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}|\bm{\xi}(0)=\delta_{a}^{x}\right)
+	\mathcal{P}(s_{a})=\mathbb{P}\left(\bm{\xi}(\infty)=s_{a}\delta_{0}+(1-s_{a})\delta_{L+1}|\bm{\xi}(0)=\delta_{a}^{x}\right)
 \end{equation*} are the absorption probabilities.}
-\fra{To explicitly find the result, we aim to determine $\mathcal{P}(t_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$.
+\fra{To explicitly find the result, we aim to determine $\mathcal{P}(s_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=s_{a}\delta_{a}^{0}+(1-s_{a})\delta_{a}^{L+1}\right)$.
 This is the probability that a random walker 

### 2024-05-15 Answer to referee/answer-to-referee.tex
ii

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[pagebackref=false]{hyperref}
\usepackage{bbm}
\usepackage{bm}
\usepackage{appendix}
\usepackage{comment}
\usepackage{mathtools}
\usepackage{array}
\usepackage{hyperref}
\usepackage{xcolor}
\numberwithin{equation}{section}
\numberwithin{equation}{subsection}
\usepackage[pagewise]{lineno}
\usepackage{xspace}

\newcommand{\fra}[1]{\textcolor[rgb]{0,0,1}{#1}}

\usepackage[margin=2.5cm]{geometry} 
\title{Answer to the referee for: \textit{Duality for the multispecies stirring process with open boundaries}}
	\begin{document}
		\maketitle
		\section*{Answer to general comments}
		\begin{enumerate}
			\item% \fra{P3, line 25: Could you provide more detail on the ”choice of the boundary reservoirs”? Is this selection the most general case that allows for the determination of an absorbing dual process?}\\ \\
				We expanded the sentence in the introduction to explain our choice of the boundary generators. One could in principle consider other choices of boundaries but then this would imply that dual particles could possibly change their color before getting absorbed at the boundaries. In view of the application of duality to the computation of the non-equilibrium steady state we are interested in we limit ourselves to the choice that avoid this color-changing.
				\item% \fra{P4, line 33: The rates αa are strictly positive, what happens when they are zero? Does the corresponding
				%	duality degenerates to nontrivial duality for closed system?} \\ \\
					When the rates are zero, then the generator of the process in (2.2.6) [DOUBLE CHECK] is zero and therefore we get indeed for the closed system the expected duality in product form.
					\item %\fra{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
						%formula, which was first utilized for duality in the paper arXiv:2209.03531. The authors should consider
						%citing that paper as well.}\\ \\
						A citation has been added on page [ADD PAGE NUMBER]
						%\item \fra{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
						%	process as established in Section 3”: It looks like this method is general, could you be more precise
						%	about the conditions for simplification and maybe analogues for (4.2.1)? Additionally, I find equations
						%	(4.2.2) to (4.2.3) distracting in this context. It’s better to keep the introduction as simple as possible.
						%	In fact, I find this section redundant with the steps outlined on page 22. Please consider rewriting
						%	these two parts together.}\\ \\
						\item 	As the computations in section 4 are rather lengthy and technical, we believe it is useful to keep a small introductory subsection where we explain the main ideas and show that the matrix product ansatz simplies after the similarity transformations.
							We considered the option of moving section 4.2 at the end of 4.1, but we believe it is useful to explain the strategy of proof right at the beginning.							
		\end{enumerate}
		\section*{Minor issues}
		\begin{enumerate}
			\item Done.
			\item Done.
			\item Done.
			\item Done.
			\item Done.
			\item Yes, $N$ is the number of species. 
			\item We deleted line 52.
			\item Done.
			\item Done.
			\item The reason is that when $\nu=1$ the we have the fundamental (defining) representation of the $gl(N)$ Lie algebra. Therefore, the matrices $E_{AB}$ coincide with the elementary matrices $e_{AB}$ such that $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ for all $A,B,C,D\in\{1,\ldots,N\}$. A footnote has been added.
			\item Done.
			\item Done.
			\item Done.
			\item We agree with this suggestion. $E$ and $\mathcal{D}_{u(x)}$ have been added in the suggested equations.
			\item Done.
			\item Equations (3.3.30), (3.3.31) and (3.3.32) have been added at page 15. Moreover, they have been used to add an intermediate step in equation (3.3.35) at page 15.
			\item Done.
			\item We made a more precise statement. 
			\item Done.
			\item We replaced everywhere the symbol $t_{i}$ with $s_{i}$.
			\item Done. 
			\item NOT CLEAR
			\item GOOD NOW
			\item Done.
			\item Done.
			\item Fixed, the index is now $A$.
			\item NOT CLEAR
			\item Done.
			\item Done.
		\end{enumerate}
	\end{document}

### 2024-05-15 main.tex
ii

@@
 where 
-$\mathcal{L}_{x,y}$ is defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+$\mathcal{L}_{x,y}$ \fra{are} defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
 \begin{equation}\label{siteDualGenerator}
@@
  \end{align}
-
-Using \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} 
+\fra{It follows that}
+\begin{align}\label{uno}
+	\fra{\exp{(-E)}\left(\sum_{a,b=1\,b\neq a}^{N-1}\alpha_{a}\left(E_{ba}-E_{bb}\right)\right)\exp{(E)}=\sum_{a,b=1\,b\neq a}^{N-1}\alpha_{a}\left(E_{ba}-E_{bb}\right)}\co
+\end{align}
+\begin{align}\label{due}
+	\fra{\exp{(-E)}\left(\sum_{a=1}^{N-1}\alpha_{a}\left(E_{Na}-E_{NN}\right)\right)\exp{(E)}=\sum_{a=1}^{N-1}\left(E_{Na}-E_{aa}-\sum_{b=1\,b\neq a}^{N-1}E_{ba}\right)}
+\end{align}
+\fra{and}
+\begin{align}\label{tre}
+	\fra{\exp{(-E)}\left(\alpha_{N}\sum_{b=1}^{N-1}\alpha_{a}\left(E_{bN}-E_{bb}\right)\right)\exp{(E)}=-\alpha_{N}\sum_{b=1}^{N-1}E_{bb}}
+\end{align}
+Using \eqref{transpositionPropertyR} we write the transpose of site Hamiltonian \eqref{siteHamiltonian} as
 \begin{equation}
@@
 \end{equation}
-By using \eqref{HT-BA} and the fact that 
+By using \fra{\eqref{uno},\eqref{due} and \eqref{tre})} and the fact that 
 \fra{$\sum_{A,B=1}^{N}E_{AB}$} is central for the algebra we have
 
-\begin{equation}\label{HadTransfBoundary}
-\exp{(-E^{x})}\sum_{A=1}^{N}\sum_{B=1}^{N}\alpha_{A}^{x}\left(E_{B A}^{x}-E_{BB}^{x}\right)\exp{(E^{x})}=	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)\dt
-\end{equation}
+\begin{align}\label{HadTransfBoundary}
+&\exp{(-E^{x})}\sum_{A=1}^{N}\sum_{B=1}^{N}\alpha_{A}^{x}\left(E_{B A}^{x}-E_{BB}^{x}\right)\exp{(E^{x})}\nonumber
+\\=&
+\fra{\sum_{a=1}^{N-1}\alpha_{a}\left(E_{Na}^{x}-E_{aa}^{x}\right)-\sum_{a,b=1\, a\neq b}^{N-1}\alpha_{a}^{x}E_{bb}^{x}-\alpha_{N}\sum_{a=1}^{N-1}E_{aa}^{x}\nonumber}
+\\=&
+\fra{	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)}\dt
+\end{align}
 Thus, we rewrite \eqref{intermediateTransposeSite} as
@@
 =&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
-=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},x})!}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
 =&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\dt
@@
 \end{flushright}
-\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ \fra{(implying that $c_{x}=1-c_{x}^{'}$)} and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
 \begin{equation}\label{ABS_1}
@@
 			In the second equality we have rewritten the product by introducing the summation over $m$, the coordinates $x_{1},\ldots,x_{m}$ and the occupation variables $b_{1},\ldots,b_{m}$.
-Here, the notation
-		\begin{equation}\label{notation-PSI}
-			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
-		\end{equation}
-		indicates that in positions $x_{1},\ldots,x_{m}$ there are particles of species $b_{1},\ldots,b_{m}$, while there are holes $N$ in all other positions.} 
+\fra{[Lines commented, referring to point 32]}.
+			%Here, the notation
+		%\begin{equation}\label{notation-PSI}
+		%	\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
+		%\end{equation}
+		%indicates that in positions $x_{1},\ldots,x_{m}$ there are particles of species $b_{1},\ldots,b_{m}$, while there are holes $N$ in all other positions.} 
 \begin{remark}[Equilibrium case]
@@
 We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
-We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
+We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,\fra{|\bm{\tau}|}\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
 These $(\ell_{k})_{k\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
@@
 \begin{equation}
-	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\co
+	\fra{D(\bm{n},\bm{\xi})=\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\right)\left(\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\right)}\co
 \end{equation}
@@
 \begin{equation}\label{DualGeneratorRD}
-	\widetilde{\mathcal{L}}_{\text{left}}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}
+	\fra{\widetilde{\mathcal{L}}^{rd}=\widetilde{\mathcal{L}}_{\text{left}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}}
 \end{equation}

### 2024-05-15 Answer to referee/answer-to-referee.tex
iii

@@
 			\item Done.
+			\item Done.
+			\item Some details have been added in the remark.
+			\item Done.
+			\item NOT CLEAR
+			\item Done.
+			\item NOT CLEAR
+			\item Done.
+			\item Done.
+			\item Done, all without bold.
+			\item Done.
+			\item Done. DID HE MEAN EXCHANGED?
+			\item Done, now we put a consistent notation.
+			\item Done, now we put consistent notation.
+			\item Done.
+			\item NOT CLEAR.
 		\end{enumerate}

### 2024-05-16 Answer to referee/answer-to-referee.tex
dd

@@
 				%	duality degenerates to nontrivial duality for closed system?} \\ \\
-					When the rates are zero, then the generator of the process in (2.2.6) [DOUBLE CHECK] is zero and therefore we get indeed for the closed system the expected duality in product form.
+					When the rates are zero, then the generator of the process in (2.2.5) is zero and therefore we get indeed for the closed system the expected duality in product form.
 					\item %\fra{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
@@
 						%citing that paper as well.}\\ \\
-						A citation has been added on page [ADD PAGE NUMBER]
+						A citation has been added on page 14
 						%\item \fra{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
@@
 			\item Done. 
-			\item NOT CLEAR
-			\item GOOD NOW
+			\item Done, more details added at page 21. 
+			\item Done, details added (4.4.17), (4.4.18)
 			\item Done.
@@
 			\item Done.
-			\item Done. DID HE MEAN EXCHANGED?
+			\item Done, compare new and old equation (5.3.20). Is it what he meant?
 			\item Done, now we put a consistent notation.

### 2024-05-16 main.tex
dd

@@
 \end{equation}
+\fra{From \cite{vanicat2017exact} we recall that the matrices $X_{A}$ act on a \textit{supplementary space} and that the boundary vectors are bra-ket vectors living in this space.}
 Without loss of generality, we further assume that $ \langle \langle W|  V\rangle\rangle =1$. 
@@
 
-Therefore, using \eqref{HT-BA} we obtain for the left boundary 
+\fra{Using \eqref{HT-BA} we obtain}
+\begin{align}
+	\fra{S_{2}\left(\sum_{a=1}^{N-1}\alpha_{a}e_{aN}^{1}\right)S_{2}^{-1}=\sum_{a=1}^{N-1}\alpha_{a}e_{aN}^{1}}
+\end{align}
+\fra{and}
+\begin{align}
+\fra{-S_{2}\sum_{a=1}^{N-1}e_{aa}^{1}S_{2}^{-1}=-\sum_{a=1}^{N-1}\left(e_{aa}^{1}+\beta_{a}e_{aN}^{1}\right)}
+\end{align}
+\fra{Therefore,  for the left boundary} 
 \begin{equation}

### 2024-05-16 main.tex
ii

@@
 The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process and the formulation of the the absorbing duality with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}).
-Finally, the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities, \fra{inspired by \cite{casini2022uphill,schutzReaction}
-(we report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD})}. 
+\fra{Finally, inspired by \cite{casini2022uphill,schutzReaction},} the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities, \fra{(we report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD})}.
 Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.
@@
 The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
-For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ \footnote{\fra{In this set-up we have chosen the fundamental (defining) representation of the Lie algebra, therefore the generators $(E_{AB})_{A,B\in\{1,\ldots,N\}}$ do coincide with the elementary matrices $(e_{AB})_{A,B\in\{1,\ldots,N\}}$.
-Therefore, we denote them by lowercase letters}}.
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ \footnote{\fra{In this set-up we have chosen the fundamental (defining) representation of the $gl(N)$ Lie algebra, therefore the generators $(E_{AB})_{A,B\in\{1,\ldots,N\}}$ do coincide with the elementary matrices $(e_{AB})_{A,B\in\{1,\ldots,N\}}$.
+As a consequence, we denote these generators by lowercase letters}}.
 The Hamiltonian can then be written as
@@
 \begin{align}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)\nonumber
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\fra{\sum_{r\in\Omega_{x}}\frac{r_{1}^{x}!\cdots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\langle r_{1}^{x},\ldots,r_{N}^{x}|}\right)\nonumber
 \\&
@@
 \end{equation}}
-{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$.
+{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$\fra{.}
 } \\
-Recalling the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
+\fra{Recalling} the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
 \begin{equation}\label{bosonicKX}
@@
 	\begin{split}
-			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{s_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-s_{a}}\fra{\mathcal{P}(s_{a})}\dt
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{s_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-s_{a}}\fra{\mathcal{P}_{x_{a}}(s_{a})}\dt
 	\end{split}
@@
 \begin{equation*}
-	\mathcal{P}(s_{a})=\mathbb{P}\left(\bm{\xi}(\infty)=s_{a}\delta_{0}+(1-s_{a})\delta_{L+1}|\bm{\xi}(0)=\delta_{a}^{x}\right)
+	\mathcal{P}_{x_{a}}(s_{a})=\mathbb{P}\left(\bm{\xi}(\infty)=s_{a}\delta_{0}+(1-s_{a})\delta_{L+1}|\bm{\xi}(0)=\delta_{a}^{x}\right)
 \end{equation*} are the absorption probabilities.}
-\fra{To explicitly find the result, we aim to determine $\mathcal{P}(s_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=s_{a}\delta_{a}^{0}+(1-s_{a})\delta_{a}^{L+1}\right)$.
+\fra{To explicitly find the result, we aim to determine $\mathcal{P}_{x_{a}}(s_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=s_{a}\delta_{a}^{0}+(1-s_{a})\delta_{a}^{L+1}\right)$.
 This is the probability that a random walker 
@@
 	\begin{cases}
-		\Delta_{L}\mathcal{P}(1,\delta_{a}^{x})=0\\
-		\mathcal{P}(1,\delta_{a}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{a}^{2})\frac{1}{1+|\alpha|}\\
-		\mathcal{P}(1,\delta_{a}^{L})=\mathcal{P}(1,\delta_{a}^{L-1})\frac{1}{1+|\beta|}
+		\fra{\Delta_{L}\mathcal{P}_{x_{a}}(1)=0}\\
+		\fra{\mathcal{P}_{1}(1)=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}_{2}(1)\frac{1}{1+|\alpha|}}\\
+		\fra{\mathcal{P}_{L}(1)=\mathcal{P}_{L-1}(1)\frac{1}{1+|\beta|}}
 	\end{cases}
@@
 where $\Delta_{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{a}^{x})=1-\mathcal{P}(0,\delta_{a}^{x})$ we obtain
+The equations \eqref{gamblers-ruin} can be solved and using \fra{$\mathcal{P}_{x_{a}}(1)=1-\mathcal{P}_{x_{a}}(0)$} we obtain
 \begin{equation}

### 2024-05-16 Answer to referee/answer-to-referee.tex
ii
jijij

@@
 			\item Done.
-			\item We replaced everywhere the symbol $t_{i}$ with $s_{i}$.
+			\item We replaced everywhere the symbol $t_{i}$ with $s_{i}$. Notice also that, to avoid confusion, the $s_{a}^{x}$ in equation (3.3.18) have been replaced by $r_{a}^{x}$.
 			\item Done. 
@@
 		\end{enumerate}
+\section*{Further corrections}
+\begin{enumerate}
+\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (5.2.10). 
+\item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they where before.
+Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorbe particles, not holes.
+\item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the $m-$mixed moments in the non-equilibrium steady state.
+I have fixed equation (5.1.3) and above and I have added Remark 13 to clarify.
+\end{enumerate}
 	\end{document}

### 2024-05-16 main.tex
jijij

@@
 \end{equation}
-\fra{From \cite{vanicat2017exact} we recall that the matrices $X_{A}$ act on a \textit{supplementary space} and that the boundary vectors are bra-ket vectors living in this space.}
+\fra{From \cite{vanicat2017exact} we recall that the matrices $(X_{A})_{A\in \{1,\ldots,N\}}$ act on a \textit{supplementary space} and that the boundary vectors are bra-ket vectors living in this space.}
 Without loss of generality, we further assume that $ \langle \langle W|  V\rangle\rangle =1$. 
@@
 Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $\mathcal{B}=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$\fra{, and either $\mathcal{A}=e_{aN},$ or $\mathcal{A}=e_{aa}$}.
-
-\fra{Using \eqref{HT-BA} we obtain}
+\fra{Namely, by using \eqref{HT-BA} we obtain}
 \begin{align}
@@
 \end{equation}
-\fra{and where we used equations \eqref{remove-exponent}.}
+\fra{and where we exploited equation \eqref{remove-exponent}.}
 Formula \eqref{ABS_1} will be useful in the following. 
@@
 We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
-For every $m\in\{1,\ldots,L\}$ we consider {\color{black}the coordinates $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
+For every $m\in\{1,\ldots,L\}$ we consider {\color{black}the coordinates \fra{$1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$} and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
 We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
-\begin{equation}
-	\xi_{A}^{x}=	\begin{cases}
-	\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}\\
-		 0\qquad &\text{otherwise}
-	\end{cases}\dt
-\end{equation}
+%\begin{equation}
+%	\xi_{A}^{x}=	\begin{cases}
+%	\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}\\
+%		 0\qquad &\text{otherwise}
+%	\end{cases}\dt
+%\end{equation}
+\begin{equation}\label{dual-config}
+\fra{	\hat{\xi}_{A}^{x}=}	\begin{cases}
+		\fra{1\qquad} &\fra{\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}}\\
+		\fra{0\qquad} &\fra{\text{otherwise}}
+	\end{cases}
+\end{equation}
+
 The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
@@
 		\\&=
-		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\sum_{s_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N})
+		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\fra{\sum_{s_{N-1}=0}^{|\xi_{N-1}|}}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}
 	\end{split}
@@
 \begin{equation}\label{Pass} 
-	\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
+\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
  The absorption probabilities for higher point correlations fulfil  difference equations.
+  \begin{remark}
+	\fra{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the $m$-mixed factorial moments under the non-equilibrium stationary distribution.}
+\end{remark}
 
@@
 	\begin{align}
-	\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}\dt
-\end{align}
+	\fra{\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})}&\fra{=\left\{f\left(\xi^{0}+\sum_{a=1}^{N-1}\bm{\delta}_{a}^{0}\xi_{a}^{1},\;\xi^{1}-\sum_{a=1}^{N-1}\bm{\delta}_{a}^{1}\xi_{a}^{1}+\bm{\delta}_{N}^{1}\sum_{a=1}^{N-1}\xi_{a}^{1},\;\xi^{2},\ldots,\xi^{L}\right)-f\left(\bm{\xi}\right)\right\}}\nonumber\\ \fra{\widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})}&\fra{=\left\{f\left(\xi^{0},\ldots,\xi^{L-1},\;\xi^{L}-\sum_{a=1}^{N-1}\bm{\delta}_{a}^{L}\xi_{a}^{L}+\bm{\delta}_{N}^{L}\sum_{a=1}^{N-1}\xi_{a}^{L},\;\xi^{L+1}+\sum_{a=1}^{N-1}\bm{\delta}_{a}^{L+1}\xi_{a}^{L}\right)-f\left(\bm{\xi}\right)\right\}}\dt
+\end{align}
+%\begin{align}
+%	\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{L})-f(\bm{\xi})\right\}\nonumber\\ \widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})&=\left\{f(\xi^{0},\ldots,\xi^{L-1},0,\xi^{L}+\xi^{L+1})-f(\bm{\xi})\right\}\dt
+%\end{align}
 The duality function is the same of the multispecies stirring process, i.e. 

### 2024-05-16 Answer to referee/answer-to-referee.tex
jkl

@@
 			\item Fixed, the index is now $A$.
-			\item NOT CLEAR
+			\item Done, probably the referee was confused by the fact that we use (4.4.37) in the third and not in the second equality. We clarified which equations are used. 
 			\item Done.
@@
 			\item Done.
-			\item NOT CLEAR
+			\item Done, but double check need.
 			\item Done.
-			\item NOT CLEAR
+			\item NOT CLEAR what is redundant.
 			\item Done.
@@
 			\item Done.
-			\item NOT CLEAR.
+			\item NOT CLEAR what is redundant.
 		\end{enumerate}
@@
 \begin{enumerate}
-\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (5.2.10). 
+\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (5.2.10) in the arxiv version of the paper. 
 \item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they where before.
-Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorbe particles, not holes.
-\item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the $m-$mixed moments in the non-equilibrium steady state.
+Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorbe particles, not the holes.
+\item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the mixed moments in the non-equilibrium steady state.
 I have fixed equation (5.1.3) and above and I have added Remark 13 to clarify.

### 2024-05-16 main.tex
jkl

@@
 \end{align}
-where in the second equality we used \eqref{usefulRelaton-many}. 
+where in the second equality \fra{we used \eqref{commLEFT} and in the third equality we used  \eqref{usefulRelaton-many}}. 
 This leads to the recursion relation
@@
 \end{equation}
-{As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, i.e.
-the situation where the process has only one species of particles and holes, with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}.
-}
+{As a check of our results we report the steady state correlations and the vectors $|\Psi^{''}\rangle$, $|\Psi^{'}\rangle$ and $|\Psi\rangle$ for the SSEP, %i.e.
+the situation where the process has only one species of particles and holes,
+with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}. \fra{[Words removed for point 33]}}
 \paragraph{Correlations of SSEP.}
@@
   \begin{remark}
-	\fra{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the $m$-mixed factorial moments under the non-equilibrium stationary distribution.}
+	\fra{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the mixed factorial moments under the non-equilibrium stationary distribution.}
 \end{remark}

### 2024-05-21 Answer to referee/answer-to-referee.tex
fixed

@@
 		\section*{Answer to general comments}
+		All the page and equation cited in the answers do refer to the new file. 
 		\begin{enumerate}
-			\item% \fra{P3, line 25: Could you provide more detail on the ”choice of the boundary reservoirs”?
-Is this selection the most general case that allows for the determination of an absorbing dual process?}\\ \\
+			\item \textbf{P3, line 25: Could you provide more detail on the ”choice of the boundary reservoirs”? Is this selection
+				the most general case that allows for the determination of an absorbing dual process?}\\ \\
 				We expanded the sentence in the introduction to explain our choice of the boundary generators.
@@
 In view of the application of duality to the computation of the non-equilibrium steady state we are interested in we limit ourselves to the choice that avoid this color-changing.
-				\item% \fra{P4, line 33: The rates αa are strictly positive, what happens when they are zero? Does the corresponding
-				%	duality degenerates to nontrivial duality for closed system?} \\ \\
+				\item \textbf{P4, line 33: The rates $\alpha_{A}$ are strictly positive, what happens when they are zero? Does the corresponding duality degenerates to nontrivial duality for closed system?} \\ \\
 					When the rates are zero, then the generator of the process in (2.2.5) is zero and therefore we get indeed for the closed system the expected duality in product form.
-					\item %\fra{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
-						%formula, which was first utilized for duality in the paper arXiv:2209.03531. The authors should consider
-						%citing that paper as well.}\\ \\
+					\item \textbf{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
+						formula, which was first utilized for duality in the paper arXiv:2209.03531. The authors should consider
+						citing that paper as well.}\\ \\
 						A citation has been added on page 14
-						%\item \fra{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
-						%	process as established in Section 3”: It looks like this method is general, could you be more precise
-						%	about the conditions for simplification and maybe analogues for (4.2.1)? Additionally, I find equations
-						%	(4.2.2) to (4.2.3) distracting in this context. It’s better to keep the introduction as simple as possible.
-						%	In fact, I find this section redundant with the steps outlined on page 22. Please consider rewriting
-						%	these two parts together.}\\ \\
-						\item 	As the computations in section 4 are rather lengthy and technical, we believe it is useful to keep a small introductory subsection where we explain the main ideas and show that the matrix product ansatz simplies after the similarity transformations.
+						\item \textbf{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
+							process as established in Section 3”: It looks like this method is general, could you be more precise
+							about the conditions for simplification and maybe analogues for (4.2.1)? Additionally, I find equations
+							(4.2.2) to (4.2.3) distracting in this context. It’s better to keep the introduction as simple as possible.
+							In fact, I find this section redundant with the steps outlined on page 22. Please consider rewriting
+							these two parts together.}\\ \\ 	As the computations in section 4 are rather lengthy and technical, we believe it is useful to keep a small introductory subsection where we explain the main ideas and show that the matrix product ansatz simplies after the similarity transformations.
 							We considered the option of moving section 4.2 at the end of 4.1, but we believe it is useful to explain the strategy of proof right at the beginning.							
@@
 			\item Done.
-			\item Yes, $N$ is the number of species. 
+			\item We fixed it. $N$ is the number of species. 
 			\item We deleted line 52.
@@
 			\item The reason is that when $\nu=1$ the we have the fundamental (defining) representation of the $gl(N)$ Lie algebra.
-Therefore, the matrices $E_{AB}$ coincide with the elementary matrices $e_{AB}$ such that $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ for all $A,B,C,D\in\{1,\ldots,N\}$.
+We added a footnote at page 8.
+%Therefore, the matrices $E_{AB}$ coincide with the elementary matrices $e_{AB}$ such that $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ for all $A,B,C,D\in\{1,\ldots,N\}$.
 A footnote has been added.
@@
 			\item Done.
-			\item We agree with this suggestion. $E$ and $\mathcal{D}_{u(x)}$ have been added in the suggested equations.
+			\item  $E$ and $\mathcal{D}_{u(x)}$ have been added in the suggested equations.
 			\item Done.
@@
 			\item Done.
-			\item We made a more precise statement. 
+			\item We made a more precise statement at page 16. 
 			\item Done.
@@
 			\item Done. 
-			\item Done, more details added at page 21. 
-			\item Done, details added (4.4.17), (4.4.18)
+			\item Details about $\langle \langle W|$ have been added at page 21. 
+			\item Details and equations (4.4.17), (4.4.18) have been added at page 25. 
 			\item Done.
@@
 			\item Fixed, the index is now $A$.
-			\item Done, probably the referee was confused by the fact that we use (4.4.37) in the third and not in the second equality. We clarified which equations are used. 
+			\item Done, probably the sentence was confusing by the fact that we used (4.4.32) in the second equality and (4.4.37) in the third and not just (4.4.37) in the second equality (as it was mistakenly written).
+We clarified which equations are used.
 			\item Done.
 			\item Done.
-			\item Done.
-			\item Some details have been added in the remark.
-			\item Done.
-			\item Done, but double check need.
-			\item Done.
-			\item NOT CLEAR what is redundant.
+			\item $c_{j}=\delta_{\sigma_{j},N}$ has been added at page 29.
+			\item Details have been added in Remark 9 at page 30. See the bracket in the first sentence and the reference to equation (4.4.48) just below equation (4.4.63).
+			\item Words removed in the sentence just above Remark 12 at page 32. 
+			\item Words removed in the sentence just above the paragraph with title "Correlations of SSEP" at page 33.
+			\item In the third line of the paragraph with title "Proof of formula (4.5.14)" at page 34, in the second curly bracket there was $|\tau|$ instead of $|\bm{\tau}|$. We fixed it.
+			\item Words removed in the sixth line after the title of Section 5 at page 35. 
 			\item Done.
 			\item Done.
-			\item Done, all without bold.
+			\item More details added in the paragraph just above equation (5.2.2) at page 37. Bold removed in equation (5.2.7) at page 38.
+			\item Brackets added in equation (5.2.11), page 38.
+			\item Subscripts fixed in equation (5.3.20) page 41.
+			\item We put a consistent notation for the absorption probabilities in Appendix C, pages 44-45. 
+			\item We put a consistent notation for the boundary densities in Appendix B, pages 43-44.
 			\item Done.
-			\item Done, compare new and old equation (5.3.20). Is it what he meant?
-			\item Done, now we put a consistent notation.
-			\item Done, now we put consistent notation.
-			\item Done.
-			\item NOT CLEAR what is redundant.
+			\item For the sake of clarity we prefer to keep this part like it was.
 		\end{enumerate}
@@
 \begin{enumerate}
-\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (5.2.10) in the arxiv version of the paper. 
+\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (ArXiv) equation (5.2.10) with the new equation (5.2.10).
 \item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they where before.
-Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorbe particles, not the holes.
+Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorb particles, not the holes.
 \item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the mixed moments in the non-equilibrium steady state.

### 2024-05-23 main.tex
add

@@
 \begin{equation}\label{eq:Hprimes}
-	H^{'}_{\text{left}}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{\text{right}}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
+	H^{'}_{\text{left}}=\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right),\qquad\qquad H^{'}_{\text{right}}=\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\dt
 \end{equation}
@@
 \begin{align}\label{tri-diag-boundaryHamiltonians}
-	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
+	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1},\qquad\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
 \end{align}
@@
 As soon as $\nu>1$ the integrability property is lost, but duality still holds.
-Therefore, in this section we first address the  question whether we can use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities.
-For the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
+Therefore, in this section we first address the  question whether we can use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities.\fra{[Lines removed referring to point 35 report.]}\\ %For the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
 However, this question can be extended to the geometry of the graph $G$ introduced in Section~\ref{sec1}.
@@
 where $\mathcal{L}_{x,x+1}$ is the edge-generator \eqref{edgeGenerator} of the multispecies stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator
-\begin{equation}
+\begin{equation}\label{stirring-mutation-generatorDensity}
 	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left(f(\bm{n}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-f(\bm{n})\right)
@@
 Moreover, we define the \textit{pure-mutation} generator
-\begin{equation}
+\begin{equation}\label{pure-mutation-gneratorDensity}
 	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N-1}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)\dt
@@
 \begin{enumerate}
-	\item \textit{\underline{Stirring generator}}: {using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section~\ref{sec1} (with $y=x+1$) we have that} 
+	\item \textit{\underline{Stirring generator}} : {using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section~\ref{sec1} (with $y=x+1$) \fra{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have that}
 \begin{equation}
@@
 where we have used the fact that $n_{N}^{x}=\nu-\sum_{c=1}^{N-1}n_{c}^{x}$.
-\item \textit{\underline{Stirring-mutation generator}}: for every $c\in \{1,\ldots,N-2\}$ we have 
+\item \textit{\underline{Stirring-mutation generator}} : \fra{considering the generator $\mathcal{L}_{x,x+1}^{c}$, defined in \eqref{stirring-mutation-generatorDensity} for every $c\in \{1,\ldots,N-2\}$} \fra{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have
 \begin{equation}
@@
 where  we used the fact that $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$. 
-\item \textit{\underline{Pure-mutation generator}}: here we have that 
+\item \textit{\underline{Pure-mutation generator}} : \fra{considering the generator $\mathcal{L}_{x,x+1}^{m}$, defined in equation \eqref{pure-mutation-gneratorDensity}} \fra{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have that
 \begin{equation}
@@
 \paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
-Acting on $n_{d}^{1}$  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
+\fra{Acting on the function $f(\bm{n})=n_{d}^{1}$}  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
 \begin{equation}\label{actionBoudaryRD}

### 2024-05-23 Answer to referee/answer-to-referee.tex
ewfe

@@
 \usepackage[margin=2.5cm]{geometry} 
-\title{Answer to the referee for: \textit{Duality for the multispecies stirring process with open boundaries}}
+\title{Answer to the referee
+%: \textit{Duality for the multispecies stirring process with open boundaries}
+}
 	\begin{document}
-		\maketitle
+	%	\maketitle
+
 		\section*{Answer to general comments}
@@
 		\begin{enumerate}
-			\item \textbf{P3, line 25: Could you provide more detail on the ”choice of the boundary reservoirs”? Is this selection
+			\item \textit{P3, line 25: Could you provide more detail on the ”choice of the boundary reservoirs”? Is this selection
 				the most general case that allows for the determination of an absorbing dual process?}\\ \\
 				We expanded the sentence in the introduction to explain our choice of the boundary generators.
-One could in principle consider other choices of boundaries but then this would imply that dual particles could possibly change their color before getting absorbed at the boundaries.
-In view of the application of duality to the computation of the non-equilibrium steady state we are interested in we limit ourselves to the choice that avoid this color-changing.
+One could in principle consider other choices but then this would imply that dual particles could possibly change their color before getting absorbed at the boundaries.
+In view of the application of duality to the computation of the non-equilibrium steady state we are interested in, we limit ourselves to the choice that avoids this color-changing.
 				\item \textbf{P4, line 33: The rates $\alpha_{A}$ are strictly positive, what happens when they are zero? Does the corresponding duality degenerates to nontrivial duality for closed system?} \\ \\
-					When the rates are zero, then the generator of the process in (2.2.5) is zero and therefore we get indeed for the closed system the expected duality in product form.
+					When the rates $\alpha_{A}$ are zero, then the generator of the process in (2.2.5) is zero and therefore we get indeed for the closed system the expected duality in product form.
 					\item \textbf{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
@@
 						citing that paper as well.}\\ \\
-						A citation has been added on page 14
+						A citation has been added on page 14.
 						\item \textbf{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
@@
 							these two parts together.}\\ \\ 	As the computations in section 4 are rather lengthy and technical, we believe it is useful to keep a small introductory subsection where we explain the main ideas and show that the matrix product ansatz simplies after the similarity transformations.
-							We considered the option of moving section 4.2 at the end of 4.1, but we believe it is useful to explain the strategy of proof right at the beginning.							
+							We considered the option of moving section 4.2 at the end of 4.1, but we believe it is useful to explain the strategy of the proof right at the beginning of the section.							
 		\end{enumerate}
@@
 \item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (ArXiv) equation (5.2.10) with the new equation (5.2.10).
-\item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they where before.
+\item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they were before.
 Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorb particles, not the holes.

### 2024-05-24 Answer to referee/answer-to-referee.tex
dd

@@
 In view of the application of duality to the computation of the non-equilibrium steady state we are interested in, we limit ourselves to the choice that avoids this color-changing.
-				\item \textbf{P4, line 33: The rates $\alpha_{A}$ are strictly positive, what happens when they are zero? Does the corresponding duality degenerates to nontrivial duality for closed system?} \\ \\
+				\item \textit{P4, line 33: The rates $\alpha_{A}$ are strictly positive, what happens when they are zero? Does the corresponding duality degenerates to nontrivial duality for closed system?} \\ \\
 					When the rates $\alpha_{A}$ are zero, then the generator of the process in (2.2.5) is zero and therefore we get indeed for the closed system the expected duality in product form.
-					\item \textbf{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
+					\item \textit{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
 						formula, which was first utilized for duality in the paper arXiv:2209.03531. The authors should consider
@@
 						A citation has been added on page 14.
-						\item \textbf{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
+						\item \textit{P20, Section 4.2: “In fact, such simplification can always be achieved if there exists an absorbing dual
 							process as established in Section 3”: It looks like this method is general, could you be more precise

### 2024-06-03 main.tex
giufe3

@@
 an extended graph $\widetilde{G}=(\widetilde{V},\widetilde{\mathcal{E})}$ which 
-includes additional \fra{sites (sometimes called "extra-sites")} $\widetilde{V}\setminus V$ where
+includes additional sites in $\widetilde{V}\setminus V$ where
 dual particles get absorbed in the long-time limit.
@@
 The swap dynamics taking place on the edges is of Kawasaki-type 
-with $N$ conservation laws, \fra{where $N$ is the number of species plus the holes. This means that the total number of particle of each species and the number of holes is conserved by the dynamics.}
+with $N$ conservation laws, \fra{where $N$ is the number of species plus the holes.
+This means that the sum of the particle number of each species and the number of holes is conserved by the dynamics.}
 %(the total number of particles of each type). 
@@
 As soon as $\nu>1$ the integrability property is lost, but duality still holds.
-Therefore, in this section we first address the  question whether we can use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities.\fra{[Lines removed referring to point 35 report.]}\\ %For the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
+Therefore, in this section we first address the  question whether we can use duality to characterize the non-equilibrium steady state of the boundary driven multispecies stirring process on a chain with $\nu>1$ via absorption probabilities.
+%\fra{[Lines removed referring to point 35 report.]}\\ %For the sake of simplicity and  for the sake of clarity, we keep the geometry of a chain with two reservoirs attached to the end sites $1$ and $L$ of the chain.
 However, this question can be extended to the geometry of the graph $G$ introduced in Section~\ref{sec1}.
 \\
+
 Inspired by the results for the thermalized version of the symmetric exclusion process reported in \cite{carinci2013duality}, in this section we also investigate its multispecies counterpart.

### 2024-06-03 main.tex
final

@@
 \newcommand{\twoj}{\nu}
-\newcommand{\fra}[1]{\textcolor[rgb]{0,0,1}{#1}}
+\newcommand{\fra}[1]{\textcolor[rgb]{1,0,0}{#1}}
+\newcommand{\fraT}[1]{\textcolor[rgb]{0,0,0}{#1}}
 \allowdisplaybreaks
@@
 \begin{document} 
- \linenumbers
+ %\linenumbers
 \begingroup
@@
 we refer to Section~\ref{sec1}. As we will see, the choice of the boundary reservoirs is motivated by the fact that they allow to determine an absorbing dual process
-\fra{that does not permit  color-changing until absorption at the boundary}, 
+\fraT{that does not permit  color-changing until absorption at the boundary}, 
 regardless of the graph $G$ on which the process is defined and of the maximal occupancy $\nu$ at each site.
@@
 \paragraph{Organization of the paper and main results.}
-We start in Section~\ref{sec1} by \fra{defining} the open multispecies stirring
+We start in Section~\ref{sec1} by \fraT{defining} the open multispecies stirring
 process on a general graph and providing its Lie algebraic description in terms of the generators of the $gl(N)$ Lie algebra.
@@
 The second generalization is the definition of a thermalized version of the boundary-driven multispecies stirring process and the formulation of the the absorbing duality with the same duality function of the multispecies stirring process (the details of the proof are reported in Appendix \ref{appendix-dualityThermalized}).
-\fra{Finally, inspired by \cite{casini2022uphill,schutzReaction},} the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities, \fra{(we report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD})}.
+\fraT{Finally, inspired by \cite{casini2022uphill,schutzReaction},} the third generalization is the introduction of an ``ad-hoc'' interaction mechanism of reaction type, in order to have closed evolution equation for average particle densities, \fraT{(we report the details of the computations for the closure of the average density evolution equation in Appendix \ref{appendix-RD})}.
 Again, an absorbing duality is proved with the same duality function of the multispecies stirring process.
@@
 The particles have a {\em type} (sometimes called {\em species} or {\em colour})
-which can \fra{take}  values $\{1,2,\ldots,N-1\}$.
+which can \fraT{take}  values $\{1,2,\ldots,N-1\}$.
 {More precisely, at each site there are $\nu$ available places (called \textit{holes} or \textit{vacancies}) that can be either occupied by particles or not.
@@
 on each vertex $x$ of the graph, a particle of type $a \in \{1,\ldots,N-1\}$ is created  at rate $\alpha_a^x >0$;
-additionally a \fra{particle} of any type is replaced with a
+additionally a \fraT{particle} of any type is replaced with a
 particle of type $a$ at rate $\alpha_a^x >0$ and it is removed at rate $\alpha_N^x >0$.
@@
 The swap dynamics taking place on the edges is of Kawasaki-type 
-with $N$ conservation laws, \fra{where $N$ is the number of species plus the holes.
+with $N$ conservation laws, \fraT{where $N$ is the number of species plus the holes.
 This means that the sum of the particle number of each species and the number of holes is conserved by the dynamics.}
@@
 Namely, on each site $x\in V$  a particle {or a hole} indicated by $B$ is replaced with a particle {or a hole} indicated $A$ at rate $\Gamma_{x}\alpha_{A}^{x}n_{B}^{x}$.
-{The transitions where \fra{a} particle is replaced by a hole/a hole is replaced by a particle is interpreted as a removal/injection of particles.}
+{The transitions where \fraT{a} particle is replaced by a hole/a hole is replaced by a particle is interpreted as a removal/injection of particles.}
 \subsection{Reversible measures in the equilibrium set-up}
@@
 When, for any $A\in \{1,\ldots,N\}$, there are at least two reservoirs at two different sites $x,y$ such that $\rho_{A}^{x}\neq  \rho_{A}^{y}$, a  non-zero current sets in, breaking the reversibility.
-Informally, one can say that the reservoirs try to impose their different densities at the boundaries of \fra{the} graph, putting the system out-of-equilibrium.}
+Informally, one can say that the reservoirs try to impose their different densities at the boundaries of \fraT{the} graph, putting the system out-of-equilibrium.}
 \begin{remark}
@@
 The case $\nu=1$, i.e. one particle at most for each site, is integrable and has been considered previously in \cite{vanicat2017exact}. 
-For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ \footnote{\fra{In this set-up we have chosen the fundamental (defining) representation of the $gl(N)$ Lie algebra, therefore the generators $(E_{AB})_{A,B\in\{1,\ldots,N\}}$ do coincide with the elementary matrices $(e_{AB})_{A,B\in\{1,\ldots,N\}}$.
+For  $\nu=1$ we denote the ${gl}(N)$  generators   as  $(e_{AB})_{A,B\in\{1,\ldots,N\}}$ obeying $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ \footnote{\fraT{In this set-up we have chosen the fundamental (defining) representation of the $gl(N)$ Lie algebra, therefore the generators $(E_{AB})_{A,B\in\{1,\ldots,N\}}$ do coincide with the elementary matrices $(e_{AB})_{A,B\in\{1,\ldots,N\}}$.
 As a consequence, we denote these generators by lowercase letters}}.
@@
 Under these assumption the Hamiltonian~\ref{hamiltonian} is integrable.
-This has been \fra{shown} in \cite{vanicat2017exact} within  the Quantum Inverse Scattering Method.
+This has been \fraT{shown} in \cite{vanicat2017exact} within  the Quantum Inverse Scattering Method.
 We will consider this process more extensively in Section~\ref{sectionIntegrabiliy}.
@@
 where 
-$\mathcal{L}_{x,y}$ \fra{are} defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
+$\mathcal{L}_{x,y}$ \fraT{are} defined in \eqref{edgeGenerator} and, for any function $f:\widetilde{\Omega}\to \mathbb{R}$ 
 \begin{equation}\label{siteDualGenerator}
@@
 \begin{equation}\label{ortho-extraSite}
-	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},\fra{q_{a}^{u(x)}}}\,.
+	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},\fraT{q_{a}^{u(x)}}}\,.
 \end{equation} }
@@
 \begin{align}
-&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\fra{\sum_{r\in\Omega_{x}}\frac{r_{1}^{x}!\cdots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\langle r_{1}^{x},\ldots,r_{N}^{x}|}\right)\nonumber
+&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\nonumber\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\fraT{\sum_{r\in\Omega_{x}}\frac{r_{1}^{x}!\cdots r_{N}^{x}!}{\nu!}|r_{1}^{x},\ldots,r_{N}^{x}\rangle\langle r_{1}^{x},\ldots,r_{N}^{x}|}\right)\nonumber
 \\&
@@
  \end{flushright}
- \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula \footnote{\fra{See \cite{khuan} for an application of the Hadamard formula in the multispecies asymmetric context.}} the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then we  introduce a creation operator acting on an extra-site $u(x)$.
+ \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we transform via the Hadamard formula \footnote{\fraT{See \cite{khuan} for an application of the Hadamard formula in the multispecies asymmetric context.}} the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then we  introduce a creation operator acting on an extra-site $u(x)$.
  Considering {$\mathcal{A},\mathcal{B}\in {gl}(N)$}, the Hadamard formula reads 
@@
  \begin{align}\label{HT-BA}
- 	\fra{\exp{\left(%-\sum_{a=1}^{N-1}E_{aN}
+ 	\fraT{\exp{\left(%-\sum_{a=1}^{N-1}E_{aN}
  			-E\right)}E_{CD}\exp{\left(
@@
  \end{align}
-\fra{It follows that}
+\fraT{It follows that}
 \begin{align}\label{uno}
-	\fra{\exp{(-E)}\left(\sum_{a,b=1\,b\neq a}^{N-1}\alpha_{a}\left(E_{ba}-E_{bb}\right)\right)\exp{(E)}=\sum_{a,b=1\,b\neq a}^{N-1}\alpha_{a}\left(E_{ba}-E_{bb}\right)}\co
+	\fraT{\exp{(-E)}\left(\sum_{a,b=1\,b\neq a}^{N-1}\alpha_{a}\left(E_{ba}-E_{bb}\right)\right)\exp{(E)}=\sum_{a,b=1\,b\neq a}^{N-1}\alpha_{a}\left(E_{ba}-E_{bb}\right)}\co
 \end{align}
 \begin{align}\label{due}
-	\fra{\exp{(-E)}\left(\sum_{a=1}^{N-1}\alpha_{a}\left(E_{Na}-E_{NN}\right)\right)\exp{(E)}=\sum_{a=1}^{N-1}\left(E_{Na}-E_{aa}-\sum_{b=1\,b\neq a}^{N-1}E_{ba}\right)}
-\end{align}
-\fra{and}
+	\fraT{\exp{(-E)}\left(\sum_{a=1}^{N-1}\alpha_{a}\left(E_{Na}-E_{NN}\right)\right)\exp{(E)}=\sum_{a=1}^{N-1}\left(E_{Na}-E_{aa}-\sum_{b=1\,b\neq a}^{N-1}E_{ba}\right)}
+\end{align}
+\fraT{and}
 \begin{align}\label{tre}
-	\fra{\exp{(-E)}\left(\alpha_{N}\sum_{b=1}^{N-1}\alpha_{a}\left(E_{bN}-E_{bb}\right)\right)\exp{(E)}=-\alpha_{N}\sum_{b=1}^{N-1}E_{bb}}
+	\fraT{\exp{(-E)}\left(\alpha_{N}\sum_{b=1}^{N-1}\alpha_{a}\left(E_{bN}-E_{bb}\right)\right)\exp{(E)}=-\alpha_{N}\sum_{b=1}^{N-1}E_{bb}}
 \end{align}
@@
 \end{equation}
-By using \fra{\eqref{uno},\eqref{due} and \eqref{tre})} and the fact that 
-\fra{$\sum_{A,B=1}^{N}E_{AB}$} is central for the algebra we have
+By using \fraT{\eqref{uno},\eqref{due} and \eqref{tre})} and the fact that 
+\fraT{$\sum_{A,B=1}^{N}E_{AB}$} is central for the algebra we have
 
@@
 \\=&
-\fra{\sum_{a=1}^{N-1}\alpha_{a}\left(E_{Na}^{x}-E_{aa}^{x}\right)-\sum_{a,b=1\, a\neq b}^{N-1}\alpha_{a}^{x}E_{bb}^{x}-\alpha_{N}\sum_{a=1}^{N-1}E_{aa}^{x}\nonumber}
+\fraT{\sum_{a=1}^{N-1}\alpha_{a}\left(E_{Na}^{x}-E_{aa}^{x}\right)-\sum_{a,b=1\, a\neq b}^{N-1}\alpha_{a}^{x}E_{bb}^{x}-\alpha_{N}\sum_{a=1}^{N-1}E_{aa}^{x}\nonumber}
 \\=&
-\fra{	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)}\dt
+\fraT{	|\alpha^{x}|\sum_{a=1}^{N-1}\left(\rho_{a}^{x}E_{Na}^{x}-E_{aa}^{x}\right)}\dt
 \end{align}
@@
 Taking the tensor product of both sides of  \eqref{siteHadamardI} 
-we obtain \fra{
+we obtain \fraT{
 \begin{equation}\label{siteHadamardII}
@@
 \end{equation}}
-{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$\fra{.}
+{With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, we here denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$\fraT{.}
 } \\
-\fra{Recalling} the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
+\fraT{Recalling} the action of the bosonic creation operator acting at site $u(x)$ and on the species $a\in \{1,\ldots,N-1\}$ we have that 
 \begin{equation}\label{bosonicKX}
@@
 \end{equation}
-Using the above equation \fra{and considering the addends multiplied by the Lie generator $E_{Na}^{x}$ (for all $a\in \{1,\ldots,N-1\}$) on the right hand side term of \eqref{siteHadamardII}} we have that
+Using the above equation \fraT{and considering the addends multiplied by the Lie generator $E_{Na}^{x}$ (for all $a\in \{1,\ldots,N-1\}$) on the right hand side term of \eqref{siteHadamardII}} we have that
 \begin{equation}\label{extra-site-trick}
@@
 all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$.
-We also notice that, \fra{up to the the bosonic} creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
+We also notice that, \fraT{up to the the bosonic} creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular.
 This simplification will be crucial in Section~\ref{sectionIntegrabiliy}.\\
@@
 In this section we combine the matrix product ansatz (MPA) \cite{vanicat2017exact} and  the $gl(N)$ invariance of the process in the bulk, cf.~\eqref{symmetryH}, to exactly compute the correlations in the non-equilibrium steady state
- for the integrable version of the multispecies stirring process \fra{defined on a line segment}, see Section~\ref{integrableChain-duality}. 
+ for the integrable version of the multispecies stirring process \fraT{defined on a line segment}, see Section~\ref{integrableChain-duality}. 
 This allows further to determine the absorption probabilities and the probability mass-function of the non-equilibrium steady state in closed form.
@@
 \end{equation}
-and their action on the boundary vectors  \fra{$\langle \langle W|$ and $|V\rangle \rangle$} are
+and their action on the boundary vectors  \fraT{$\langle \langle W|$ and $|V\rangle \rangle$} are
 \begin{equation}\label{leftBoundary}
@@
 \end{equation}
-\fra{From \cite{vanicat2017exact} we recall that the matrices $(X_{A})_{A\in \{1,\ldots,N\}}$ act on a \textit{supplementary space} and that the boundary vectors are bra-ket vectors living in this space.}
+\fraT{From \cite{vanicat2017exact} we recall that the matrices $(X_{A})_{A\in \{1,\ldots,N\}}$ act on a \textit{supplementary space} and that the boundary vectors are bra-ket vectors living in this space.}
 Without loss of generality, we further assume that $ \langle \langle W|  V\rangle\rangle =1$. 
@@
 \begin{equation}\label{exactCorrelations}
-\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\fra{\sum_{s_{1},\ldots,s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{m})}
+\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\\=\fraT{\sum_{s_{1},\ldots,s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{m})}
 \end{equation}
@@
 \begin{equation}\label{abs-probabilities}
-	\mathcal{P}_{x_{1},\ldots,x_{m}}\fra{(s_{1},\ldots,s_{m})=\sum_{c_{1}=s_{1}}^{1}\ldots\sum_{c_{m}=s_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-s_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})}
+	\mathcal{P}_{x_{1},\ldots,x_{m}}\fraT{(s_{1},\ldots,s_{m})=\sum_{c_{1}=s_{1}}^{1}\ldots\sum_{c_{m}=s_{m}}^{1}f(c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-s_{j}}g_{j}(x_{j},c_{j},\ldots,c_{m})}
 \end{equation}
@@
 The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal.
-Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $\mathcal{B}=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$\fra{, and either $\mathcal{A}=e_{aN},$ or $\mathcal{A}=e_{aa}$}.
-\fra{Namely, by using \eqref{HT-BA} we obtain}
-\begin{align}
-	\fra{S_{2}\left(\sum_{a=1}^{N-1}\alpha_{a}e_{aN}^{1}\right)S_{2}^{-1}=\sum_{a=1}^{N-1}\alpha_{a}e_{aN}^{1}}
-\end{align}
-\fra{and}
-\begin{align}
-\fra{-S_{2}\sum_{a=1}^{N-1}e_{aa}^{1}S_{2}^{-1}=-\sum_{a=1}^{N-1}\left(e_{aa}^{1}+\beta_{a}e_{aN}^{1}\right)}
-\end{align}
-\fra{Therefore,  for the left boundary} 
+Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $\mathcal{B}=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$\fraT{, and either $\mathcal{A}=e_{aN},$ or $\mathcal{A}=e_{aa}$}.
+\fraT{Namely, by using \eqref{HT-BA} we obtain}
+\begin{align}
+	\fraT{S_{2}\left(\sum_{a=1}^{N-1}\alpha_{a}e_{aN}^{1}\right)S_{2}^{-1}=\sum_{a=1}^{N-1}\alpha_{a}e_{aN}^{1}}
+\end{align}
+\fraT{and}
+\begin{align}
+\fraT{-S_{2}\sum_{a=1}^{N-1}e_{aa}^{1}S_{2}^{-1}=-\sum_{a=1}^{N-1}\left(e_{aa}^{1}+\beta_{a}e_{aN}^{1}\right)}
+\end{align}
+\fraT{Therefore,  for the left boundary} 
 \begin{equation}
@@
 \begin{equation}\label{similarity}
-	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\fra{\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}}\dt
+	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\fraT{\exp{\left(\sum_{a=1}^{N-1}e_{Na}^{x}\right)}}\dt
 \end{equation}
@@
 \begin{equation}\label{Xtildes2b}
- \tilde X_a=X_{a}-\beta_{a}(\fra{X_{1}}+\ldots+X_{N})\,,\qquad \tilde X_N= 
+ \tilde X_a=X_{a}-\beta_{a}(\fraT{X_{1}}+\ldots+X_{N})\,,\qquad \tilde X_N= 
 				X_{1}+\ldots +X_{N}
@@
 cf.~\eqref{commLEFT2}.
-Using the transformed operators \fra{$(\widetilde{X}_{A})_{A\in\{1,\ldots,N\}}$}, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
+Using the transformed operators \fraT{$(\widetilde{X}_{A})_{A\in\{1,\ldots,N\}}$}, the vector $|\Psi^{''}\rangle$ of the matrix product ansatz is written as
 \begin{equation}\label{toDetermineTilde}
@@
 \end{align}
-where in the second equality \fra{we used \eqref{commLEFT} and in the third equality we used  \eqref{usefulRelaton-many}}. 
+where in the second equality \fraT{we used \eqref{commLEFT} and in the third equality we used  \eqref{usefulRelaton-many}}. 
 This leads to the recursion relation
@@
 &\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
-=&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
-=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
-=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fra{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\dt
+=&\frac{(1+\sum_{x=1}^{L}\delta_{\tau_{x},N})!}{(L+1)!}\prod_{x=1}^{L}\fraT{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fraT{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\frac{(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})!}{(\sum_{j=x}^{L}\delta_{\tau_{j},N})!}\nonumber\\
+=&\frac{1}{(L+1)!}\prod_{x=1}^{L}\fraT{\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\dt
 \end{align}
@@
 \end{equation}
-\fra{whose action} on the occupation variable $|\sigma\rangle$ of a site is 
+\fraT{whose action} on the occupation variable $|\sigma\rangle$ of a site is 
 \begin{equation}
@@
 We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether, at each site $x$, $\sigma_{x}$ is occupied or empty.
-Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$\fra{, where $c_{x}=\delta_{\sigma_{x},N}$}.
+Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$\fraT{, where $c_{x}=\delta_{\sigma_{x},N}$}.
 Thus, we obtain
@@
 \end{flushright}
-\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ \fra{(implying that $c_{x}=1-c_{x}^{'}$)} and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
+\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ \fraT{(implying that $c_{x}=1-c_{x}^{'}$)} and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as
 \begin{equation}\label{ABS_1}
@@
 \end{equation}
-\fra{and where we exploited equation \eqref{remove-exponent}.}
+\fraT{and where we exploited equation \eqref{remove-exponent}.}
 Formula \eqref{ABS_1} will be useful in the following. 
@@
 	&\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]\nonumber\\=&
-	\fra{\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	\fraT{\sum_{c_{1},\ldots,c_{m}=0}^{1}
 	f(c_{1},\ldots,c_{m})\prod_{k=1}^{m}\left(\sum_{s_{k}=0}^{c_{k}}(-1)^{c_{k}-s_{k}}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)}\nonumber\\
-	=&\fra{\sum_{c_{1},\ldots,c_{m}=0}^{1}
+	=&\fraT{\sum_{c_{1},\ldots,c_{m}=0}^{1}
 	f(c_{1},\ldots,c_{m})\sum_{s_{1}=0}^{c_{1}}\ldots\sum_{s_{m}=0}^{c_{m}}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\left(\prod_{k=1}^{m}(-1)^{c_{k}-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)}\nonumber\\
-	=&\fra{\sum_{s_{1},\ldots,s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\sum_{c_{1}=s_{1}}^{1}\ldots\sum_{c_{m}=s_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt}
+	=&\fraT{\sum_{s_{1},\ldots,s_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{s_{k}}\beta_{a_{k}}^{1-s_{k}}\right)\sum_{c_{1}=s_{1}}^{1}\ldots\sum_{c_{m}=s_{m}}^{1}f(c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-s_{k}}g_{k}(x_{k},c_{k},\ldots,c_{m})\right)\dt}
 \end{align}
@@
 			In the second equality we have rewritten the product by introducing the summation over $m$, the coordinates $x_{1},\ldots,x_{m}$ and the occupation variables $b_{1},\ldots,b_{m}$.
-\fra{[Lines commented, referring to point 32]}.
+%\fra{[Lines commented, referring to point 32]}.
 			%Here, the notation
@@
 the situation where the process has only one species of particles and holes,
-with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}. \fra{[Words removed for point 33]}}
+with maximal occupancy $\nu=1$ and compare the results to \cite{frassek2020eigenstates}. %\fra{[Words removed for point 33]}}
 \paragraph{Correlations of SSEP.}
@@
 We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones.
-We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,\fra{|\bm{\tau}|}\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
+We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,\fraT{|\bm{\tau}|}\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$.
 These $(\ell_{k})_{k\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected.
@@
 Finally we add a reaction mechanism of transition to the boundary driven multispecies stirring process.
-The aim is to answer the following question: Can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?
+The aim is to answer the following question: can we generalize to the case with $\nu>1$ with arbitrary number of species the boundary driven model introduced in \cite{casini2022uphill}?
 Moreover, in \cite{casini2022uphill} the duality for this reaction-diffusion process was proved only for the equilibrium case and the result was achieved by direct computation (without using a $gl(3)$ symmetry).
@@
 \end{equation}
-We recall that the dual processes are defined on an enlarged \fra{chain} with \fra{two extra-sites} $0$ and $L+1$ attached to $1$ and $L$ respectively.}
+We recall that the dual processes are defined on an enlarged \fraT{chain} with \fraT{two extra-sites} $0$ and $L+1$ attached to $1$ and $L$ respectively.}
 \subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}
@@
 \end{equation} 
-where $\mathcal{L}_{x,x+1}$ is given by \fra{\eqref{edgeGenerator}} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively.
+where $\mathcal{L}_{x,x+1}$ is given by \fraT{\eqref{edgeGenerator}} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively.
 The duality function is \eqref{dualityElements} specified on the chain.
 We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$.
-For every $m\in\{1,\ldots,L\}$ we consider {\color{black}the coordinates \fra{$1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$} and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
+For every $m\in\{1,\ldots,L\}$ we consider {\color{black}the coordinates \fraT{$1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$} and we select $m$ colours $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$ among the $N-1$ available ones}.
 We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that
@@
 \begin{equation}\label{dual-config}
-\fra{	\hat{\xi}_{A}^{x}=}	\begin{cases}
-		\fra{1\qquad} &\fra{\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}}\\
-		\fra{0\qquad} &\fra{\text{otherwise}}
+\fraT{	\hat{\xi}_{A}^{x}=}	\begin{cases}
+		\fraT{1\qquad} &\fraT{\text{if}\quad x=x_{k}\;\text{and} \; A=a_{k}}\\
+		\fraT{0\qquad} &\fraT{\text{otherwise}}
 	\end{cases}
@@
 		\\&=
-		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\fra{\sum_{s_{N-1}=0}^{|\xi_{N-1}|}}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}
+		\sum_{s_{1}=0}^{|\xi_{1}|}\ldots\fraT{\sum_{s_{N-1}=0}^{|\xi_{N-1}|}}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-s_{a}}\fraT{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}
 	\end{split}
@@
 \begin{equation}\label{Pass} 
-\fra{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
+\fraT{\mathcal{P}_{x_{1},\ldots,x_{m}}(s_{1},\ldots,s_{N-1})}	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(s_{a}\delta_{a}^{0}+(|\xi_{a}|-s_{a})\delta_{a}^{L+1}\right)\Big|  \bm{\xi}(0)=\bm{\xi}\right)
 \end{equation}
@@
   \begin{remark}
-	\fra{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the mixed factorial moments under the non-equilibrium stationary distribution.}
+	\fraT{Considering arbitrary coordinates $(x_{k})_{k\in\{1,\ldots,m\}}$ (not necessary different) and considering proper dual configurations, the technique explained above can be used to compute, in function of the absorption probabilities, the mixed factorial moments under the non-equilibrium stationary distribution.}
 \end{remark}
@@
 \end{align}
-\fra{Here we introduce the vectors $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall A\in\{1,\ldots,N\}$, for each of their components $(r_{A})_{A\in\{1,\ldots,N\}},(\epsilon_{A})_{A\in\{1,\ldots,N\}}$ we have $r_{A}\in \{0,\ldots,\nu\}$ and $\epsilon_{A}\in \{0,\ldots,2\nu\}$, under the constraints
+\fraT{Here we introduce the vectors $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall A\in\{1,\ldots,N\}$, for each of their components $(r_{A})_{A\in\{1,\ldots,N\}},(\epsilon_{A})_{A\in\{1,\ldots,N\}}$ we have $r_{A}\in \{0,\ldots,\nu\}$ and $\epsilon_{A}\in \{0,\ldots,2\nu\}$, under the constraints
 \begin{equation}
@@
 	\\&\times
-	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\fra{\mu_{TH}({r}|{\epsilon})}
+	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\fraT{\mu_{TH}({r}|{\epsilon})}
 	\end{split}
@@
 	\begin{align}
-	\fra{\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})}&\fra{=\left\{f\left(\xi^{0}+\sum_{a=1}^{N-1}\bm{\delta}_{a}^{0}\xi_{a}^{1},\;\xi^{1}-\sum_{a=1}^{N-1}\bm{\delta}_{a}^{1}\xi_{a}^{1}+\bm{\delta}_{N}^{1}\sum_{a=1}^{N-1}\xi_{a}^{1},\;\xi^{2},\ldots,\xi^{L}\right)-f\left(\bm{\xi}\right)\right\}}\nonumber\\ \fra{\widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})}&\fra{=\left\{f\left(\xi^{0},\ldots,\xi^{L-1},\;\xi^{L}-\sum_{a=1}^{N-1}\bm{\delta}_{a}^{L}\xi_{a}^{L}+\bm{\delta}_{N}^{L}\sum_{a=1}^{N-1}\xi_{a}^{L},\;\xi^{L+1}+\sum_{a=1}^{N-1}\bm{\delta}_{a}^{L+1}\xi_{a}^{L}\right)-f\left(\bm{\xi}\right)\right\}}\dt
+	\fraT{\widetilde{\mathcal{L}}_{\text{left}}^{TH}f(\bm{\xi})}&\fraT{=\left\{f\left(\xi^{0}+\sum_{a=1}^{N-1}\bm{\delta}_{a}^{0}\xi_{a}^{1},\;\xi^{1}-\sum_{a=1}^{N-1}\bm{\delta}_{a}^{1}\xi_{a}^{1}+\bm{\delta}_{N}^{1}\sum_{a=1}^{N-1}\xi_{a}^{1},\;\xi^{2},\ldots,\xi^{L}\right)-f\left(\bm{\xi}\right)\right\}}\nonumber\\ \fraT{\widetilde{\mathcal{L}}_{\text{right}}^{TH}f(\bm{\xi})}&\fraT{=\left\{f\left(\xi^{0},\ldots,\xi^{L-1},\;\xi^{L}-\sum_{a=1}^{N-1}\bm{\delta}_{a}^{L}\xi_{a}^{L}+\bm{\delta}_{N}^{L}\sum_{a=1}^{N-1}\xi_{a}^{L},\;\xi^{L+1}+\sum_{a=1}^{N-1}\bm{\delta}_{a}^{L+1}\xi_{a}^{L}\right)-f\left(\bm{\xi}\right)\right\}}\dt
 \end{align}
@@
 \begin{equation}
-	\fra{D(\bm{n},\bm{\xi})=\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\right)\left(\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\right)}\co
+	\fraT{D(\bm{n},\bm{\xi})=\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}}\right)\left(\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{right}}\right)^{\xi_{a}^{L+1}}\right)}\co
 \end{equation}
@@
 \begin{equation}\label{DualGeneratorRD}
-	\fra{\widetilde{\mathcal{L}}^{rd}=\widetilde{\mathcal{L}}_{\text{left}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}}
+	\fraT{\widetilde{\mathcal{L}}^{rd}=\widetilde{\mathcal{L}}_{\text{left}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{\text{right}}^{rd}}
 \end{equation}
@@
 	\begin{split}
-			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{s_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-s_{a}}\fra{\mathcal{P}_{x_{a}}(s_{a})}\dt
-	\end{split}
-\end{equation}
-\fra{where 
+			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{s_{a}=0}^{1}\left(\rho_{a}^{\text{left}}\right)^{s_{a}}\left(\rho_{a}^{\text{right}}\right)^{1-s_{a}}\fraT{\mathcal{P}_{x_{a}}(s_{a})}\dt
+	\end{split}
+\end{equation}
+\fraT{where 
 \begin{equation*}
@@
 \end{equation*} are the absorption probabilities.}
-\fra{To explicitly find the result, we aim to determine $\mathcal{P}_{x_{a}}(s_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=s_{a}\delta_{a}^{0}+(1-s_{a})\delta_{a}^{L+1}\right)$.
+\fraT{To explicitly find the result, we aim to determine $\mathcal{P}_{x_{a}}(s_{a})$.}%=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=s_{a}\delta_{a}^{0}+(1-s_{a})\delta_{a}^{L+1}\right)$.
 This is the probability that a random walker 
@@
 	\begin{cases}
-		\fra{\Delta_{L}\mathcal{P}_{x_{a}}(1)=0}\\
-		\fra{\mathcal{P}_{1}(1)=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}_{2}(1)\frac{1}{1+|\alpha|}}\\
-		\fra{\mathcal{P}_{L}(1)=\mathcal{P}_{L-1}(1)\frac{1}{1+|\beta|}}
+		\fraT{\Delta_{L}\mathcal{P}_{x_{a}}(1)=0}\\
+		\fraT{\mathcal{P}_{1}(1)=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}_{2}(1)\frac{1}{1+|\alpha|}}\\
+		\fraT{\mathcal{P}_{L}(1)=\mathcal{P}_{L-1}(1)\frac{1}{1+|\beta|}}
 	\end{cases}
@@
 where $\Delta_{L}$ is the discrete Laplace operator on the chain of length $L$.
-The equations \eqref{gamblers-ruin} can be solved and using \fra{$\mathcal{P}_{x_{a}}(1)=1-\mathcal{P}_{x_{a}}(0)$} we obtain
+The equations \eqref{gamblers-ruin} can be solved and using \fraT{$\mathcal{P}_{x_{a}}(1)=1-\mathcal{P}_{x_{a}}(0)$} we obtain
 \begin{equation}
@@
 \end{equation}
-First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. By writing explicitly $\fra{\rho_{a}^{\text{left}}}=\frac{\alpha_{a}}{|\alpha|}$, this action gives
+First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. By writing explicitly $\fraT{\rho_{a}^{\text{left}}}=\frac{\alpha_{a}}{|\alpha|}$, this action gives
 \begin{align}\label{ProvaBordoTH}
@@
 We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}.
-We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ \fra{and then we multiply} this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$ to get
+We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ \fraT{and then we multiply} this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$ to get
 \begin{align}\label{pezzo1}
@@
 and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
-We \fra{multiply} it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ to get
+We \fraT{multiply} it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{a}+r_{a}}$ to get
 \begin{equation}\label{pezzo2}
@@
 \begin{align}
-	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}\fra{(\rho_{a}^{\text{right}})}^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
+	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}\fraT{(\rho_{a}^{\text{right}})}^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
 	\\&=
@@
 \begin{enumerate}
-	\item \textit{\underline{Stirring generator}} : {using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section~\ref{sec1} (with $y=x+1$) \fra{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have that}
+	\item \textit{\underline{Stirring generator}} : {using edge generator $\mathcal{L}_{x,x+1}$ of the multispecies stirring process introduced in Section~\ref{sec1} (with $y=x+1$) \fraT{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have that}
 \begin{equation}
@@
 where we have used the fact that $n_{N}^{x}=\nu-\sum_{c=1}^{N-1}n_{c}^{x}$.
-\item \textit{\underline{Stirring-mutation generator}} : \fra{considering the generator $\mathcal{L}_{x,x+1}^{c}$, defined in \eqref{stirring-mutation-generatorDensity} for every $c\in \{1,\ldots,N-2\}$} \fra{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have
+\item \textit{\underline{Stirring-mutation generator}} : \fraT{considering the generator $\mathcal{L}_{x,x+1}^{c}$, defined in \eqref{stirring-mutation-generatorDensity} for every $c\in \{1,\ldots,N-2\}$} \fraT{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have
 \begin{equation}
@@
 where  we used the fact that $n_{N}^{x}=\nu-\sum_{b=1}^{N-1}n_{b}^{x}$. 
-\item \textit{\underline{Pure-mutation generator}} : \fra{considering the generator $\mathcal{L}_{x,x+1}^{m}$, defined in equation \eqref{pure-mutation-gneratorDensity}} \fra{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have that
+\item \textit{\underline{Pure-mutation generator}} : \fraT{considering the generator $\mathcal{L}_{x,x+1}^{m}$, defined in equation \eqref{pure-mutation-gneratorDensity}} \fraT{and acting on the function $f(\bm{n})=n_{d}^{x}$} we have that
 \begin{equation}
@@
 \paragraph{Action of $\mathcal{L}_{\text{left}}^{rd}$ on the occupation variable}
-\fra{Acting on the function $f(\bm{n})=n_{d}^{1}$}  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
+\fraT{Acting on the function $f(\bm{n})=n_{d}^{1}$}  with $\mathcal{L}_{\text{left}}^{rd}$ we obtain
 \begin{equation}\label{actionBoudaryRD}

### 2024-06-04 Answer to referee/answer-to-referee.tex
fix

@@
 
+		We thank the referees for their comments and suggestions. We amended the paper by taking into account the suggested changes.
+		Page and equation numbering used in the answers below refers to the resubmitted version of the paper.
+
 		\section*{Answer to general comments}
-		All the page and equation cited in the answers do refer to the new file. 
 		\begin{enumerate}
@@
 					When the rates $\alpha_{A}$ are zero, then the generator of the process in (2.2.5) is zero and therefore we get indeed for the closed system the expected duality in product form.
-					\item \textit{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker–Campbell–Hausdorff
+					\item \textit{P14, line 20: In my understanding, the Hadamard formula is a special case of the Baker-Campbell-Hausdorff
 						formula, which was first utilized for duality in the paper arXiv:2209.03531. The authors should consider
@@
 			\item Done.
-			\item The reason is that when $\nu=1$ the we have the fundamental (defining) representation of the $gl(N)$ Lie algebra.
-We added a footnote at page 8.
+			\item The reason is that when $\nu=1$ then we have the fundamental (defining) representation of the $gl(N)$ Lie algebra.
+We added a footnote on page 8.
 %Therefore, the matrices $E_{AB}$ coincide with the elementary matrices $e_{AB}$ such that $(e_{AB})_{CD}=\delta_{AC}\delta_{BD}$ for all $A,B,C,D\in\{1,\ldots,N\}$.
@@
 			\item Done.
-			\item Equations (3.3.30), (3.3.31) and (3.3.32) have been added at page 15. Moreover, they have been used to add an intermediate step in equation (3.3.35) at page 15.
+			\item Equations (3.3.30), (3.3.31) and (3.3.32) have been added on page 15. Moreover, they have been used to add an intermediate step in equation (3.3.35) on page 15.
 			\item Done.
@@
 		\end{enumerate}
-\section*{Further corrections}
-\begin{enumerate}
-\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (ArXiv) equation (5.2.10) with the new equation (5.2.10).
-\item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they were before.
+%\section*{Further corrections}
+%\begin{enumerate}
+%\item \textbf{Equation (5.2.10)}: the boundary dual generator of the thermalized process was wrong. Compare with the old (ArXiv) equation (5.2.10) with the new equation (5.2.10).
+%\item \textbf{Equations (5.1.5), (5.1.6)}: the absorption probabilities of the dual particles should be written for $s_{1},\ldots,s_{N-1}$ and not until $s_{N}$ as they were before.
 Indeed, $s_{a}$ denotes the number of particles of species $a$ that we absorbed at $0$ and we can only absorb particles, not the holes.
-\item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the mixed moments in the non-equilibrium steady state.
-I have fixed equation (5.1.3) and above and I have added Remark 13 to clarify.
-\end{enumerate}
+%\item \textbf{Section 5.1}: we can talk about $m$-point correlations only if we choose $1\leq x_{1}<\ldots<x_{m}\leq L$ otherwise  we obtain the mixed moments in the non-equilibrium steady state.
+We have fixed equation (5.1.3) and above and we have added Remark 13 for  clarification.
+%\end{enumerate}
 	\end{document}

### 2024-06-06 main.tex
iytdf

@@
  \begingroup\large \bf
- {Francesco Casini$^{(a,b)}$, Rouven Frassek$^{(a)}$, Cristian Giardin\`a$^{(a)}$}
+ {Francesco Casini$^{(a,b)}$, Rouven Frassek$^{(a)}$, Cristian Giardin\`a$^{(a)}${\footnote{Author to whom any correspondence should be addressed: cristian.giardina@unimore.it }}}
  \par\endgroup
